### 2024-10-16 index.qmd
Set up of manuscript quarto project.

---
title: title
authors:
  - name: Norah Jones
    affiliation: The University
    roles: writing
    corresponding: true
bibliography: references.bib
---

## Section
This is a simple placeholder for the manuscript's main document [@knuth84].

### 2024-10-16 index.qmd
modified .gitignore and index.qmd

@@
 title: title
+shorttitle: A Short title # aog-article-pdf
+shortauthors: Isaiah      # aog-article-pdf
 authors:
-  - name: Norah Jones
-    affiliation: The University
-    roles: writing
+  - name: Isaiah Espinoza
+    email: gespinoz@umd.edu
+    roles: author
     corresponding: true
-bibliography: references.bib
+affiliations:
+  - id: uni
+    name: University of Maryland
+    department: Department of Government and Politics
+reference-section-title: Bibliography
+date: "2024-10-16"
 ---

### 2024-10-16 docs/_tex/index.tex
push to docs/ and add notebooks

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
  letterpaper,
]{article}

\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
    \setmainfont[]{Palatino Linotype}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

% -----------------------
% CUSTOM PREAMBLE STUFF
% -----------------------

\usepackage{orcidlink}
\definecolor{mypink}{RGB}{219, 48, 122}
\usepackage{endnotes}
\usepackage[nolists]{endfloat}

% ---------------------------
% END CUSTOM PREAMBLE STUFF
% ---------------------------
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={title},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={red},
  pdfcreator={LaTeX via pandoc}}

\title{title}
\author{
Isaiah Espinoza\\University of Maryland, Department of Government and
Politics\\\href{mailto:gespinoz@umd.edu}{gespinoz@umd.edu}}
\date{2024-10-16}
\begin{document}

\maketitle

\setstretch{2}
\subsection{Section}\label{section}

This is a simple placeholder for the manuscript's main document (Knuth
1984).

\section*{References}\label{bibliography}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{1}
\bibitem[\citeproctext]{ref-knuth84}
Knuth, Donald E. 1984. {``Literate Programming.''} \emph{Comput. J.}
27(2): 97--111.
doi:\href{https://doi.org/10.1093/comjnl/27.2.97}{10.1093/comjnl/27.2.97}.

\end{CSLReferences}

\processdelayedfloats
\end{document}

### 2024-10-16 index.qmd
push to docs/ and add notebooks

--- 2024-10-16 index.qmd
@@
 title: title
+shorttitle: A Short title # aog-article-pdf
+shortauthors: Isaiah      # aog-article-pdf
 authors:
-  - name: Norah Jones
-    affiliation: The University
-    roles: writing
-    corresponding: true
-bibliography: references.bib
+  - name: Isaiah Espinoza
+    email: gespinoz@umd.edu
+    roles: author
+    affiliation:
+      - name: University of Maryland
+        department: Department of Government and Politics
+        city: College Park
+        state: MD
+        country: US
+reference-section-title: References
+date: "2024-10-16"
 ---

### 2024-10-16 notebooks/01-data-import-clean-process.qmd
push to docs/ and add notebooks

---
title: Data Import, Clean, and Process
author: Isaiah
format: 
  html: 
    code-fold: false
    code-tools: true
    code-overflow: wrap
    code-copy: true
    code-annotations: true
---

This document describes and executes the cleaning and processing of the survey data set downloaded from Qualtrics on 2024-09-11 at 11:39AM. Currently, this notebook is mainly to describe and explain the process undertaken in R to import, clean, wrangle, and transform the data set for later analysis. To see the process without all my explanatory text, see the relevant R script viewed [here](https://github.com/isaiahespi/cdce_vets/blob/80e843e8a9fa24d1d7524c76631b709f9f675876/scripts/01-data.R).

## Load data

```{r}
#| label: load-data

# load raw SPSS export that includes display order vars
# downloaded 2024-09-11 at 11:38 AM
raw_spss <- haven::read_sav(file = "data-raw/vets_spss_do_2024-09-11_11.38.sav")

```

## Create data dictionary/codebook

A data dictionary contains metadata about the data. The `labelled::generate_dictionary` function is used to create a data dictionary. A dataframe is loaded into the R environment with the number of observations equal to number of variables in the original data set. One problem that I encountered was that I was unable to quickly save the data dictionary generated using the `labelled` R package. As an alternative, I utilized the `data_dict()` function from the R package `surveytoolbox` in order to save the dictionary as a `.csv` file.

```{r}
#| label: raw-data-dict

# data dictionary from labelled package. Won't save as .csv file
raw_spss_dict <- raw_spss |> labelled::generate_dictionary()

# data dictionary from labelled package. Will save as .csv file
raw_spss_dict <- raw_spss |> surveytoolbox::data_dict()

# uncomment to save the data dictionary as a .csv file
# write.csv(raw_spss_dict, file = "codebooks/raw_spss_dict.csv")

```

## create dataframe from raw data

The following code is lengthy, but creates a dataframe (object class `tbl_df` `tbl` `data.frame`) assigned as `data_spss`.

```{r}
#| label: create-dataframe

# create dataframe
data_spss <- raw_spss |>
  janitor::clean_names() |>

  # decision was made to include only those who fully completed the survey
  filter(finished==1) |>

  # get rid of superfluous Qualtrics columns
  # Keep Qualtrics `response_id`
  dplyr::select(!1:8 & !10:17 & !265) |>

  # put demographic data up front
  dplyr::relocate(q59:q74, .before = q1) |>

  # rename demographic vars and timing vars and identify lucid vars
  dplyr::rename(
    q13_treat_time = q13_page_submit,
    q16_control_time = q16_page_submit,
    lucid_gender = gender,
    lucid_age = age,
    lucid_hhi = hhi,
    lucid_ethnicity = ethnicity,
    lucid_hispanic = hispanic,
    lucid_education = education,
    lucid_political_party = political_party,
    lucid_region = region,
    lucid_zip = zip,
    lucid_rid = rid,
    gender = q59,
    hisp = q60,
    race = q61,
    educ = q62,
    milserv1 = q63,
    milserv2 = q64,
    milservfam = q65,
    voted2020 = q66,
    choice2020 = q67,
    voteintent = q68,
    partyid = q69,
    partystr_rep = q70,
    partystr_dem = q71,
    partylean = q72,
    ideo = q73,
    ideolean = q74
  ) |>

  # put both response ID variables next to each other
  dplyr::relocate(lucid_rid, .after = response_id) |>

  # set variable labels for embedded lucid vars
  # set variable labels for select questions
  labelled::set_variable_labels(
    lucid_age = "Lucid: age",
    lucid_gender = "Lucid: What is your gender?",
    lucid_hhi = "Lucid: What is your current Annual household income before taxes?",
    lucid_ethnicity = "Lucid: What is your race?",
    lucid_hispanic = "Lucid: Are you Hispanic, Latino, or Spanish Origin?",
    lucid_education = "Lucid: What is the highest level of education you have completed?",
    lucid_political_party = "Lucid: Generally Speaking, do you usually think yourself as a Republican, a Democrat, an Independent, or what?",
    lucid_region = "Lucid: For Region, ZIP is asked which is automatically mapped to the Region",
    lucid_zip = "Lucid: What is your ZIP code?",
    lucid_rid = "Lucid respondent ID",
    q1 = "Consent to Participate...",
    q28_1 = "There will be voter fraud...",
    q28_2 = "Many votes will not actually be counted",
    q28_3 = "Many people will show up to vote and be told they are not eligible",
    q28_4 = "A foreign country will tamper with the votes cast in Maricopa County, Arizona...",
    q28_5 = "Election officials in Maricopa County, Arizoa will try to discourage some people from voting",
    q40_1 = "There will be voter fraud...",
    q40_2 = "Many votes will not actually be counted",
    q40_3 = "Many people will show up to vote and be told they are not eligible",
    q40_4 = "A foreign country will tamper with the votes cast in your local area...",
    q40_5 = "Election officials in your community will try to discourage some people from voting",
    q41_1 = "Election officials test every machine used in the election to ensure they are secure.",
    q41_2 = "Election officials conduct audits of ballots after every election...",
    q41_3 = "Poll watchers affiliated with the political parties or candidates observe the election.",
    q41_4 = "Election staff and volunteers include military veterans and their family members from the community.",
    q41_5 = "Election staff and volunteers include lawyers from the community.",
    q41_6 = "Election staff and volunteers include college students from the community.",
    q43_1 = "Election officials ensure that law enforcement officers are present at polling sites.",
    q43_2 = "Poll watchers affiliated with the political parties or candidates observe the election.",
    q43_3 = "People holding signs or giving out literature in support of a candidate or ballot question.",
    q43_4 = "Election staff and volunteers include military veterans and their family members from the community.",
    q43_5 = "Election staff and volunteers include lawyers from the community.",
    q43_6 = "Election staff and volunteers include college students from the community.",
    q44_1 = "Election officials test every machine used in the election to ensure they are secure.",
    q44_2 = "Election officials conduct audits of ballots after every election to confirm the results were accurate.",
    q44_3 = "Poll watchers affiliated with the political parties or candidates observe the election.",
    q44_4 = "The majority of election staff and volunteers consist of military veterans and their family members from the community.",
    q44_5 = "The majority of election staff and volunteers consist of lawyers from the community.",
    q44_6 = "The majority of election staff and volunteers consist of college students from the community.",
    q46_1 = "Election officials ensure that law enforcement officers are present at polling sites.",
    q46_2 = "People holding signs or giving out literature in support of a candidate or ballot question.",
    q46_3 = "Poll watchers affiliated with the political parties or candidates observe the election.",
    q46_4 = "The majority of election staff and volunteers consist of military veterans and their family members from the community.",
    q46_5 = "The majority of election staff and volunteers consist of lawyers from the community.",
    q46_6 = "The majority of election staff and volunteers consist of college students from the community.",
    group = "Experimental condition",
    qset = "Condition A = question set [q41, q43] ; Condition B = question set [q44, q46]"
  ) |>

  # filter the data to only include those who consented, U.S. citizens, 
  # and those who didn't fail the attention check
  dplyr::filter(q1 == 1, # include only those who consented
         q3 != 3,        # exclude non-U.S. citizens
         q9 == 1 | q9 == 0 & q10 == 1 #exclude attn check failures
         ) |>

  # add a column of ascending sequential row ids starting at 1
  tibble::rowid_to_column("rowID")

```

The `janitor` R package is used to `clean_names()` which ensures the column names of the dataframe are unique, consist only of the '_' character, numbers, and letters. All uppercase column names will be converted to lowercase (e.g., Q1 to q1). The `dplyr::select()`, `dplyr::relocate()`, and `dplyr::rename()` functions utilize the dplyr R package to...

-   selectively remove superfluous columns that come standard when survey data is downloaded from Qualtrics; 
-   relocate demographic variables (e.g., Q59 to Q74) to a position just before the Q1 column and the Lucid rid ('lucid_rid') to a position just after the Qualtrics Response ID ('response_id');
-   rename specific columns/variables.

In addition, the function `set_variable_labels()` from the `labelled` R package sets the *variable labels* attached to each respective variable[^1]. Crucially, the raw data is filtered using `dplyr::filter()` so the resulting dataframe only includes survey respondents who...

-   Consented to take the survey
-   Is a U.S. citizen
-   Passed either attention check embedded within the survey.

Finally, a column is added at the front of the dataframe ('rowID') which simply adds a column at the start of the dataframe of ascending sequential row ids starting at 1. The resulting dataframe (`tbl_df`) consists of 1,388 rows, where each row consists of a valid survey response, and 254 columns/variables.

[^1]: *Variable* labels differ from *value* labels. The variable labels of this data set contain the question text of the particular survey question, truncated for some. For more detailed explanation and guidance on working with labelled data, usually imported from an SPSS .sav file, see the following resources: Shannon Pileggi's [Leveraging labelled data in R](https://www.pipinghotdata.com/posts/2020-12-23-leveraging-labelled-data-in-r/) and [The case for variable labels in R](https://www.pipinghotdata.com/posts/2022-09-13-the-case-for-variable-labels-in-r/); Joseph Larmarange's R package [labelled](https://larmarange.github.io/labelled/); and Daniel Lüdecke's [Labelled Data and the sjlabelled-Package](https://strengejacke.github.io/sjlabelled/articles/intro_sjlabelled.html) and the [sjlabelled package](https://strengejacke.github.io/sjlabelled/index.html). Also see Martin Chan's R package [surveytoolbox](https://martinctc.github.io/surveytoolbox/) which is also very helpful for [Working with SPSS labels in R](https://martinctc.github.io/blog/working-with-spss-labels-in-r/).

## Resolving errors in data

The responses to the age survey question (`Q2`) in the dataframe (`data_spss`) reflect the response code rather than the respondent's actual reported age as selected from the drop-down list of ages ranging from '18' to '90 or
older'. Since age was indicated using a drop down list, the first response is coded as `1` which corresponds to age 18 in years. In addition, embedded data from Lucid also reflects the respondent's age, which has been renamed to `lucid_age`. The following code is used to illustrate this discrepancy.

```{r}
#| label: age-discrepancies
#| echo: true
#| output: true

# verify that `age` and `q2` do not match at all in the numeric data frame
# due to `q2` reflecting codes, not ages
# note `lucid_age` is a character class object which is temporarily treated 
# as numeric
data_spss |> 
  dplyr::select(lucid_age, q2) |> 
  dplyr::mutate("match" = 
                  ifelse(as.numeric(lucid_age) == q2, "match", "no match")) |> 
  head(10)

```

The output displays the first 10 observations and no match is found comparing the numeric values of the two variable columns. Note, however, that the `lbl` of `q2` do, in fact, match the `lucid_age` values[^2].

[^2]: At this point, most of the variable objects of the dataframe are class `"haven_labelled"` `"vctrs_vctr"` `"double"`, which means that the variable object in R has numeric values with *value labels* attached, hence `<dbl+lbl>`. According to description of the `labelled()` function in the `haven` R package, "A labelled vector is a common data structure in other statistical environments, allowing you to assign text labels to specific values. This class makes it possible to import such labelled vectors in to R without loss of fidelity."

As such, the variable `q2` cannot simply be converted to numeric (class) using the `as.numeric()` function because value label (i.e., the `'lbl'` in `<dbl+lbl>`) would be dropped, leaving the age values to incorrectly reflect the response codes rather than the actual age of the respondent. To resolve this problem, I use `dplyr::mutate()` and `dplyr::case_match()` to re-name the variable column and re-code the values to reflect the correct age and convert the object to a numeric class.

```{r}
#| label: numeric-age-fix

data_spss <- data_spss |>
  # rename `q2` to 'age' and recode values
  dplyr::mutate(age = dplyr::case_match(
      q2,
      1 ~ 18,
      2 ~ 19,
      3 ~ 20,
      4 ~ 21,
      5 ~ 22,
      6 ~ 23,
      7 ~ 24,
      8 ~ 25,
      9 ~ 26,
      10 ~ 27,
      11 ~ 28,
      12 ~ 29,
      13 ~ 30,
      14 ~ 31,
      15 ~ 32,
      16 ~ 33,
      17 ~ 34,
      18 ~ 35,
      19 ~ 36,
      20 ~ 37,
      21 ~ 38,
      22 ~ 39,
      23 ~ 40,
      24 ~ 41,
      25 ~ 42,
      26 ~ 43,
      27 ~ 44,
      28 ~ 45,
      29 ~ 46,
      30 ~ 47,
      31 ~ 48,
      32 ~ 49,
      33 ~ 50,
      34 ~ 51,
      35 ~ 52,
      36 ~ 53,
      37 ~ 54,
      38 ~ 55,
      39 ~ 56,
      40 ~ 57,
      41 ~ 58,
      42 ~ 59,
      43 ~ 60,
      44 ~ 61,
      45 ~ 62,
      46 ~ 63,
      47 ~ 64,
      48 ~ 65,
      49 ~ 66,
      50 ~ 67,
      51 ~ 68,
      52 ~ 69,
      53 ~ 70,
      54 ~ 71,
      55 ~ 72,
      56 ~ 73,
      57 ~ 74,
      58 ~ 75,
      59 ~ 76,
      60 ~ 77,
      61 ~ 78,
      62 ~ 79,
      63 ~ 80,
      64 ~ 81,
      65 ~ 82,
      66 ~ 83,
      67 ~ 84,
      68 ~ 85,
      69 ~ 86,
      70 ~ 87,
      71 ~ 88,
      72 ~ 89,
      73 ~ 92 # one person reported '90 or older'. R's age in Lucid data is 92
    ),
    .after = q2, # place 'age' after `q2`
    .keep = "unused" # drop `q2` from dataframe
  ) |> 
  # set variable label consisting of question text
  labelled::set_variable_labels(age = "What is your age?")

```

It is still possible that the `lucid_age` variable doesn't match the re-coded `age` (formally `q2`) values. In fact, this is the case, as demonstrated by running the code below.

```{r}
#| label: lucid-age-discrepancies
#| echo: true
#| output: true

# Identify counts of discrepancies between `lucid_age` and 'age'
data_spss |> 
  dplyr::select(rowID, lucid_age, age) |> 
  dplyr::mutate(match = ifelse(age == lucid_age, TRUE, FALSE)) |>
  dplyr::summarise(
    "Matches" = sum(match == TRUE, na.rm = T),
    "Non-match" = sum(match == FALSE, na.rm = T)
  )

```

What results is confirmation that there are a total of 170 discrepancies between the respondent's age as indicated by the embedded Lucid data and the age reported by the respondent in the survey. Thus, the age reported by the respondent in the survey will take precedence over the embedded data provided by Lucid[^3].

[^3]: Note, however, that one of the response options for the question "What is your age?" (Q2) was "90 or older", and one respondent's age reported by Lucid was 92 years old. Since there was no response code associated with being 92 years of age, the response code `73` was recoded to represent 92. In this one case, it was a stroke of luck that no more than one of the survey respondents happened to be 90 years of age or older. If there was, however, then there would have been no way to recode the `age` variable to reflect those respondent's actual age *and* convert the variable object to a numeric class. This issue isn't insurmountable, of course, but the lesson here is that it seems like best practice is to ensure respondents have to manually enter their age or birth year in the survey rather than choose from a list of options.

## Recode variables to identify question display order

Survey question items `Q51` to `Q58` were split up into two question sets: `Q51` to `Q54` and `Q55` to `Q58`. The order of these question sets were randomly reversed. For order 1, questions `Q51` to `Q54` ('agent-aim') were presented first, followed by the next set, `Q55` to `Q58` ('agent-action-aim'). For order 2, the presentation was reversed. Two variable columns in the data set identify the question display order. Here I use those two variables to construct a single dummy variable where order 1 = 1, and order 2 = 0.

```{r}
#| label: popeff-qdo

# create var to identify display order of popular efficacy questions
data_spss <- data_spss |>
  dplyr::mutate(
    popeff_qdo = dplyr::case_when(
      fl_22_do_popular_efficacy_agent_aim == 1 &
        fl_22_do_popularefficacy_agent_action_aim == 2 ~ 1,
      fl_22_do_popular_efficacy_agent_aim == 2 &
        fl_22_do_popularefficacy_agent_action_aim == 1 ~ 0
    ),
    .after = qset,
    .keep = "unused"
  )
```

## Create dataframe with factors

As mentioned previously, labelled (SPSS) data is, well, labelled; the labelled variables are `<dbl+lbl>` which differs from factors `<fct>`[^4]. The following creates a new dataframe where the all the labelled variables `<dbl+lbl>` are converted to factors using `haven::as_factor()`.

```{r}
#| label: data-clean

# covert all <dbl+lbl> vars to factor <fct> vars
# remove all display order variables, as well as click counts
# specifically convert `group` and `qset` to factor vars and set value labels
# with associated values, i.e, levels with labels
# re-code all blank levels "" to NA

data <- data_spss |>
  # subset spss data set to omit the display order variables
  dplyr::select(!contains("_do_")
         & !contains("_ado_")
         & !contains("_click")
         & !contains("_count")) |>

  # make `group` and `qset` factors
  dplyr::mutate(
    group = forcats::fct(group, levels = c("Treatment", "Control")),
    qset = forcats::fct(qset, levels = c("A", "B"), na = "")
  ) |>

  # adds labels as attribute (named "labels") to group and qset, assign values
  sjlabelled::set_labels(group, labels = c("Treatment" = 1, "Control" = 0)) |>
  sjlabelled::set_labels(qset, labels = c("A" = 1, "B" = 0)) |>

  # convert all labelled variables in dataframe to factors
  haven::as_factor(only_labelled = T) |>

  # re-code any empty/blank levels to NA
  dplyr::mutate(dplyr::across(where(is.factor), 
                              ~ forcats::fct_recode(., NULL = ""))) |>

  # reverse order of identified factor levels for consist direction
  dplyr::mutate(dplyr::across(c(q8, q20, q23, q24, q31, q34, q35, q49, q50), 
                .fns = ~ forcats::fct_rev(.))) |>

  # reverse order of group levels so control comes first. Better table display
  mutate(group = forcats::fct_rev(group))

```

In addition, the following unnecessary variables are removed...

-   variable columns that indicate the display order of survey questions and the response option display order (e.g., `q5_do`, `q28_ado`)
-   variable columns related to timing spent on a particular page: the first click, number, or count of clicks (e.g., `q13_first_click`, `q13_last_click`, `q13_click_count`)

The `group` variable identifies whether a survey respondent was in the "Treatment" or "Control" condition. The `qset` variable identifies which question set a respondent answered; set "A" indicates the respondent was presented `Q41` and `Q43`, whereas set "B" indicates the respondent was presented `Q44` and `Q46` instead. Each of these variables were converted to factors using `forcats::fct()` prior to running `haven::as_factor()` because each is an object of class `character`. By default, `haven::as_factor()` applies `forcats::as_factor()` only to labelled variables in the dataframe. Since `group` and `qset` do no contain an associated *value* nor a *value label*, they would not be converted to class `factor`[^5]. The default argument of the function could be set to FALSE (i.e., `haven::as_factor(only_labelled = FALSE)`), but this would then convert **all** variables in the dataframe to factors, which is problematic considering the numeric variables that need to be preserved as such.

[^4]: Factors (variable objects of class `factor`) are used for categorical variables in R. Mostly. To learn more, see the chapter on Factors in [R for Data Science](https://r4ds.hadley.nz/factors) by Hadley Wickham, Mine
      Çetinkaya-Rundel, and Garrett Grolemund.

[^5]: Of course, I could have simply used `dplyr::mutate(x = haven::as_factor(x))` again after running `as_factor()` for the whole dataframe, but this resulted in weirdness with the two variables that I didn't want to investigate and resolve.

Moreover, any blank levels are recoded to `NA`. Finally, an identified set of factor variables in the dataframe needed to have the orders of their levels reversed to remain consistent. Later, a similar, but different, operation is executed for the purely numeric dataframe.

## Putting variable labels back into factor dataframe

It's easier to analyze variables in data as factors, but losing the variable labels (i.e., question text) is kind of a bummer. Variable labels are nice to have for plenty of reasons. The following puts the variable labels from the labelled (SPSS) data set back into the 'factor-ized' dataset.

```{r}
#| label: put-var-labels-back

# To quickly assign the variable labels, first create a named vector via
# deframe() with values as the variable labels and names as the variable names.
data_labels <- data_spss_dict |>
  dplyr::select(variable, label) |> 
  tibble::deframe()

# Now assign the labels using the splice operator. Using the splice operator,
# labels are assigned via matching against the variable name, which means that
# variable order does not matter.
data <- data |> 
  labelled::set_variable_labels(!!!data_labels)

```

## Add Variables to the dataframe

Here I construct the `partyid_3cat` variable from partisanship-related variables in the dataframe. Simply, this variable simplifies a respondent's self-reported party identification into either Democrat, Republican, or Independent by re-coding and combining responses to survey questions Q69, Q70, Q71, and Q72. I combined everyone who indicates some attachment to either the Democrat or Republican party (e.g., "Strong" and "Not very strong") to include self-described Independents who reportedly 'lean' more towards one party over the other. So, strong and weak Democrats as well as those who lean Democratic are all lumped into the Democrat group, and likewise for Republicans. Independents in this case only consist of true or 'pure' independents who don't think of themselves as Democrat or Republican and don't think of themselves as closer to either political party.

```{r}
#| label: add-partyid_3cat

# construct the partyid var with 3 categories, true independents
data <- data |>
  dplyr::mutate(
    partyid_3cat = pewmethods::fct_case_when(
      partyid == "Republican" ~ "Republican",
      partystr_rep == "Strong" ~ "Republican",
      partystr_rep == "Not very strong" ~ "Republican",
      partylean == "Republican" ~ "Republican",
      partyid == "Democrat" ~ "Democrat",
      partystr_dem == "Strong" ~ "Democrat",
      partystr_dem == "Not very strong" ~ "Democrat",
      partylean == "Democratic" ~ "Democrat",
      partyid == "Independent" ~ "Independent",
      partyid == "Other" ~ "Independent",
      partylean == "Neither" ~ "Independent"
    ),
    .before = partyid) |> 
  labelled::set_variable_labels(
    partyid_3cat = "Party ID 3 categories, with true Independents")

```

Next I construct a variable consisting of eight age groups: 18-24, 25-34, 35-44, 45-54, 55-64, 65-74, 75-84, and 85-92 years of age.

```{r}

# create an age group variable
data <- data |>    
  dplyr::mutate(age_cat = 
           forcats::fct_collapse(
             forcats::as_factor(age),
             "18-24" = c(18:24),
             "25-34" = c(25:34),
             "35-44" = c(35:44),
             "45-54" = c(45:54),
             "55-64" = c(55:64),
             "65-74" = c(65:74),
             "75-84" = c(75:82, 84),
             "85-92" = c(85:88, 92)
             ),
         .after = age) |> 
  labelled::set_variable_labels(
    age_cat = "Age categorized into eight groups"
  )

```

Here I collapse the gender variable into gender_3cat, and voted2020 into voted2020.clps.

```{r}

df <- df |> 
  dplyr::mutate(gender_3cat = forcats::fct_collapse(
    gender,
    "Male" = "Male",
    "Female" = "Female",
    "Other/Refused" = c("Non-binary / third gender", "Prefer not to say")),
    voted2020.clps = forcats::fct_collapse(
      voted2020,
      "Voted" = "Yes, I'm sure I voted",
      "Didn't vote" = c("I'm sure I didn't vote", "I don't think I voted"),
      "Unsure/Ineligible" = c("I think I voted","I was not eligible to vote")
      )) |>
  labelled::set_variable_labels(
    voted2020.clps = "Turnout 2020"
  )

```

## Dummify and Collapse Factors

Most survey items consisted of Likert-type items with four or five response options to choose from. Many response items were ordinal in nature, with four options ranging from "Not at all___", "Not too \___", to "Somewhat \___",  "Very ___" or "Always". Collapsing such response options into two levels is done to illustrate comparison and highlight treatment effects should any be present between treatment and control groups. For instance, to illustrate distinction between expressing concern and expressing little to no concern about potential violence at polling sites, the four levels of the `q25` factor variable were collapsed into two levels, "not_concerned" and "concerned". The modified variable name was affixed with `.clps` to distinguish it in the dataframe. For survey items `Q41` through `Q46` where there were five response options, factor levels were collapsed into three levels where a neutral middle option was maintained: "Increase confidence", "No impact", and "Decrease confidence".

```{r}
#| label: add-dummy

# collapse categorical variables with 4-point response items into factors with
# two levels. Those with 5-point response options are converted into factors
# with 3 levels. Affix ".clps" to colname to identify collapsed factor vars,
# e.g., q19.clps

df <- df |>
  dplyr::mutate(across(
    c(q19, q20, q22, q23, q24, q26, q30, q31, q33, q34, q35, q37),
    ~ forcats::fct_collapse(
      .,
      Not_confident = c("Not at all confident", "Not too confident"),
      Confident = c("Somewhat confident", "Very confident")
    ),
    .names = "{.col}.clps"
  )) |>
  dplyr::mutate(across(
    c(q21, q32),
    ~ forcats::fct_collapse(
      .,
      not_committed = c("Not at all committed", "Not too committed"),
      committed = c("Somewhat committed", "Very committed")
    ),
    .names = "{.col}.clps"
  )) |>
  # whoops. Need to change "somewhat unconcerned" to "Not too concerned"
  # recall: fct_recode(x, old_level = new_level)
  dplyr::mutate(
    q36 = forcats::fct_recode(
      q36,
      "Not at all concerned" = "Not at all concerned",
      "Not too concerned" = "Somewhat unconcerned",
      "Somewhat concerned" = "Somewhat concerned",
      "Very concerned" = "Very concerned"
    )
  ) |>
  dplyr::mutate(across(
    c(q25, q36),
    ~ forcats::fct_collapse(
      .,
      not_concerned = c("Not at all concerned", "Not too concerned"),
      concerned = c("Somewhat concerned", "Very concerned")
    ),
    .names = "{.col}.clps"
  )) |>
  dplyr::mutate(q38.clps =
           forcats::fct_collapse(
             q38,
             unsafe = c("Not safe at all", "Not too safe"),
             safe = c("Somewhat safe", "Very safe")
           )) |>
  dplyr::mutate(across(
    c(q27, q39),
    ~ forcats::fct_collapse(
      .,
      disapprove = c("Strongly disapprove", "Somewhat disapprove"),
      approve = c("Somewhat approve", "Strongly approve")
    ),
    .names = "{.col}.clps"
  )) |>
  dplyr::mutate(q29.clps = forcats::fct_collapse(
    q29,
    oppose = c("Definitely should not adopt", "Probably should not adopt"),
    support = c("Probably should adopt", "Definitely should adopt")
  )) |> 
  dplyr::mutate(across(q28_1:q28_5 | q40_1:q40_5,~forcats::fct_collapse(
    .,
    Not_likely = c("Not likely at all", "Not too likely"),
    Likely = c("Somewhat likely", "Very likely")),
    .names = "{.col}.clps"
    )) |>
  dplyr::mutate(
    across(
      q41_1:q41_6 |
        q43_1:q43_6 | q44_1:q44_6 | q46_1:q46_6,
      ~ forcats::fct_collapse(
        .,
        decrease = c("Decrease confidence a lot", "Decrease confidence somewhat"),
        no_impact = "No impact on confidence",
        increase = c("Increase confidence somewhat", "Increase confidence a lot")
      ),
    .names = "{.col}.clps"
    )
  )

```

Variable labels are important for presentation purposes but the length of the survey question text is too long to fit neatly into a table or figure. Here I add labels to the modified and collapsed factor variables. I also reorder the variable columns in the data frame using `dplyr::relocate()`.

```{r}

# set shorter levels for some demographic vars
df <- df |> labelled::set_variable_labels(
  gender_3cat = "What is your current gender?",
  race = "Primary race reported by respondent",
  educ = "Highest level of education completed",
  milserv1 = "Have you ever served in the Armed Forces?",
  milserv2 = "Are you now serving in the Armed Forces?",
  milservfam = "Member of immediate family served or is currently serving",
  choice2020 = "Who did you vote for?",
  voteintent = "Do you plan to vote?"
)

df <- df |>
  labelled::set_variable_labels(
    q5         = "Attention to Political Affairs",
    q6         = "EO Favorability",
    q7         = "Legitimacy of 2020 election",
    q8         = "General Trust in others",
    q19.clps   = "Confidence vote counts will be accurate, AZ",
    q20.clps   = "Competence of Election Staff, AZ",
    q21.clps   = "Commitment of Election Staff, AZ",
    q22.clps   = "Fair Process, AZ",
    q23.clps   = "Fair Outcomes, AZ",
    q24.clps   = "Security of Voting Tech, AZ",
    q25.clps   = "Voters Will Be Free From Intimidation/Violence, AZ",
    q26.clps   = "Safe In-person Voting, AZ",
    q27.clps   = "Election Official Approval, AZ",
    q28_1.clps = "Voter fraud, AZ",
    q28_2.clps = "Votes won't be counted, AZ",
    q28_3.clps = "People will turned away, AZ",
    q28_4.clps = "Foreign interference with votes, AZ",
    q28_5.clps = "EOs discourage people from voting, AZ",
    q29.clps   = "Adopt AZ Program",
    q30.clps   = "Accurate counts, Local",
    q31.clps   = "Competence of Election Staff, Local" ,
    q32.clps   = "Commitment of Election Staff, Local",
    q33.clps   = "Fair Process, Local",
    q34.clps   = "Fair Outcomes, Local",
    q35.clps   = "Secure Voting Tech, Local",
    q36.clps   = "Voter Intimidation/Violence, Local",
    q37.clps   = "Safe in-person voting, Local",
    q38.clps   = "Safe to vote in-person, Local",
    q39.clps   = "EO Approval, Local",
    q40_1.clps = "Voter fraud, Local",
    q40_2.clps = "Votes won't be counted, Local",
    q40_3.clps = "People will be turned away, Local",
    q40_4.clps = "Foreign interference with votes, Local",
    q40_5.clps = "EO discourage people from voting, Local",

    q41_1.clps = "Election officials test machines",
    q41_2.clps = "Election officials conduct audits",
    q41_3.clps = "Partisan Poll watchers observe the election.",
    q41_4.clps = "Election staff include veterans and family",
    q41_5.clps = "Election staff include lawyers",
    q41_6.clps = "Election staff include college students",

    q43_1.clps = "Law enforcement presence.",
    q43_2.clps = "Partisan Poll watchers observe the election",
    q43_3.clps = "People holding signs or giving out literature",
    q43_4.clps = "Election staff includes veterans",
    q43_5.clps = "Election staff includes lawyers",
    q43_6.clps = "Election staff includes students",

    q44_1.clps = "Election officials test machines",
    q44_2.clps = "Majority of Election staff are veterans",
    q44_3.clps = "Majority of Election staff are lawyers",
    q44_4.clps = "Election officials conduct audits",
    q44_5.clps = "Partisan Poll watchers observe the election",
    q44_6.clps = "Majority of Election staff are students",

    q46_1.clps = "Law enforcement presence.",
    q46_2.clps = "Majority of Election staff are veterans",
    q46_3.clps = "Majority of Election staff are lawyers",
    q46_4.clps = "Partisan Poll watchers observe the election",
    q46_5.clps = "Majority of Election staff are students",
    q46_6.clps = "People holding signs or giving out literature",
  )

# Now do some heavy duty relocating of columns in the dataframe
df <- df |>  
  dplyr::relocate(
    gender_3cat, .after = gender
  ) |> 
  dplyr::relocate(
    voted2020.clps, .after = voted2020
  ) |>
  dplyr::relocate(
  c(
    q20.clps,
    q21.clps,
    q22.clps,
    q23.clps,
    q24.clps,
    q25.clps,
    q26.clps,
    q27.clps,
    q28_1.clps,
    q28_2.clps,
    q28_3.clps,
    q28_4.clps,
    q28_5.clps,
    q29.clps,
    q30.clps,
    q31.clps,
    q32.clps,
    q33.clps,
    q34.clps,
    q35.clps,
    q36.clps,
    q37.clps,
    q38.clps,
    q39.clps,
    q40_1.clps,
    q40_2.clps,
    q40_3.clps,
    q40_4.clps,
    q40_5.clps,
    q41_1.clps,
    q41_2.clps,
    q41_3.clps,
    q41_4.clps,
    q41_5.clps,
    q41_6.clps,
    q43_1.clps,
    q43_2.clps,
    q43_3.clps,
    q43_4.clps,
    q43_5.clps,
    q43_6.clps,
    q44_1.clps,
    q44_2.clps,
    q44_3.clps,
    q44_4.clps,
    q44_5.clps,
    q44_6.clps,
    q46_1.clps,
    q46_2.clps,
    q46_3.clps,
    q46_4.clps,
    q46_5.clps,
    q46_6.clps
  ),
  .after = q19.clps)

```

# Merge question sets that have no significant differences between them

The `Qset` variable (which stands for 'Question set') identified respondents who responded to question set 'A' and those who responded to question set 'B'. The two question sets contained a pair of matrix-style (i.e., grid) questions where survey participants responded to a series of six statements per question. To be clear, each question set contained two questions and each question contained a series of six statements. The question sets differed only in the wording that was used in some, but not all, of the question item statements. Those in `Qset A` responded to `Q41` and `Q43`, whereas those assigned to `Qset B` responded to `Q44` and `Q46`. After some preliminary analysis was conducted, no significant differences in proportion of responses were found between `Qset A` and `Qset B`, which allowed the question sets to be combined, or coalesced. The code below does just that, as well as assigns variable labels.

```{r}

# merge (or coalesce) the qset vars that can be merged this merges some vars
# from the q44 and q46 set into q41 and q43 there was no sig diff found for all
# but the qset B questions regarding lawyers and students. However these are
# being coalesced into single question vars anyway since I am able to to still
# distinguish responses by the grouping var `qset`
df <- df |> 
  group_by(rowID) |> 
  mutate(q41.1 = dplyr::coalesce(q41_1, q44_1),
         q41.2 = dplyr::coalesce(q41_2, q44_4),
         q41.3 = dplyr::coalesce(q41_3, q44_5),
         q41.4 = dplyr::coalesce(q41_4, q44_2),
         q41.5 = dplyr::coalesce(q41_5, q44_3),
         q41.6 = dplyr::coalesce(q41_6, q44_6),

         q43.1 = dplyr::coalesce(q43_1, q46_1),
         q43.2 = dplyr::coalesce(q43_2, q46_4),
         q43.3 = dplyr::coalesce(q43_3, q46_6),
         q43.4 = dplyr::coalesce(q43_4, q46_2),
         q43.5 = dplyr::coalesce(q43_5, q46_3),
         q43.6 = dplyr::coalesce(q43_6, q46_5),

         q41.1.clps = dplyr::coalesce(q41_1.clps, q44_1.clps),
         q41.2.clps = dplyr::coalesce(q41_2.clps, q44_4.clps),
         q41.3.clps = dplyr::coalesce(q41_3.clps, q44_5.clps),
         q41.4.clps = dplyr::coalesce(q41_4.clps, q44_2.clps),
         q41.5.clps = dplyr::coalesce(q41_5.clps, q44_3.clps),
         q41.6.clps = dplyr::coalesce(q41_6.clps, q44_6.clps),

         q43.1.clps = dplyr::coalesce(q43_1.clps, q46_1.clps),
         q43.2.clps = dplyr::coalesce(q43_2.clps, q46_4.clps),
         q43.3.clps = dplyr::coalesce(q43_3.clps, q46_6.clps),
         q43.4.clps = dplyr::coalesce(q43_4.clps, q46_2.clps),
         q43.5.clps = dplyr::coalesce(q43_5.clps, q46_3.clps),
         q43.6.clps = dplyr::coalesce(q43_6.clps, q46_5.clps)
         ) |>
  ungroup() |>

  # assign variable labels to these coalesced variables
  sjlabelled::var_labels(
    q41.1 = "Election officials test machines",
    q41.2 = "Election officials conduct audits",
    q41.3 = "Partisan Poll watchers observe the election.",
    q41.4 = "Election staff includes veterans and family",
    q41.5 = "Election staff includes lawyers",
    q41.6 = "Election staff includes college students",

    q43.1 = "Election officials test machines",
    q43.2 = "Election officials conduct audits",
    q43.3 = "Partisan Poll watchers observe the election.",
    q43.4 = "Election staff includes veterans and family",
    q43.5 = "Election staff includes lawyers",
    q43.6 = "Election staff includes college students",

    q41.1.clps = "Election officials test machines",
    q41.2.clps = "Election officials conduct audits",
    q41.3.clps = "Partisan Poll watchers observe the election.",
    q41.4.clps = "Election staff includes veterans and family",
    q41.5.clps = "Election staff includes lawyers",
    q41.6.clps = "Election staff includes college students",

    q43.1.clps = "Election officials test machines",
    q43.2.clps = "Election officials conduct audits",
    q43.3.clps = "Partisan Poll watchers observe the election.",
    q43.4.clps = "Election staff includes veterans and family",
    q43.5.clps = "Election staff includes lawyers",
    q43.6.clps = "Election staff includes college students"
  )

```

Finally, dummy variables were created from the newly coalesced variables where 1 = "Increase in confidence" and 0 = "No impact" or "Decrease in confidence". This was done for the sake of conducting comparisons between treatment and control groups.

```{r}

# create dummy variables where 1 = 'Increase in confidence' and 0 = "No increase
# in confidence".
# add dummy variables to dataframe
df <- df |> 
  mutate(across(c(q41.1.clps:q43.6.clps), 
                ~ dplyr::case_when(
                . == "increase" ~ 1, 
                . == "no_impact" ~ 0,
                . == 'decrease' ~ 0
                ), .names = "{.col}.dum"))

```

## Creating a purely numeric dataframe

For whatever reasons, it is sometimes preferred to use a purely numeric dataframe. The following code creates a dataframe from the earlier `data_spss` dataframe that removes all value labels from the numeric values of the variables, i.e., drops all the `lbl` from `<dbl+lbl>`.

The following code merely duplicates the source code from an R script located in the project directory, which can be found and viewed [here](https://github.com/isaiahespi/cdce_vets/blob/80e843e8a9fa24d1d7524c76631b709f9f675876/scripts/02-data-numeric.R).

```{r}
#| label: numeric-data-clean

data2 <- data_spss |>
  # subset spss data set to omit the display order variables
  select(!contains("_do_")
         & !contains("_ado_")
         & !contains("_click")
         & !contains("_count")) |>
  mutate(
    group = case_when(
      group == "Treatment" ~ 1,
      group == "Control" ~ 0),
    qset = case_when(
      qset == "A" ~ 1,
      qset == "B" ~ 0)) |>

  # remove all 'lbl' from all <dbl+lbl> variables, making them all numeric
  haven::zap_labels() |> 
  # re-code values for consistent direction with like variables
  mutate(
    q8  = case_match(q8, 1 ~ 5, 2 ~ 4, 3 ~3, 4~2, 5 ~ 1),
    q20 = case_match(q20, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
    q23 = case_match(q23, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
    q24 = case_match(q24, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
    q31 = case_match(q31, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
    q34 = case_match(q34, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
    q35 = case_match(q35, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
    q49 = case_match(q49, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
    q50 = case_match(q50, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1))

```

## Save the dataframe

All that is left to do is to save the dataframe that is now ready for further analysis. Remove the unnecessary data frames that may be clogging up the working environment.

```{r}

# save df processed data set.
save(df, file = "data/df-2024-09-11.Rdata")
write.csv(df, file = "data/df-2024-09-11.csv")

# save the numeric only processed data set.
save(data2, file = "data/data_numeric_vets_survey-exp-2024-09-11.Rdata")
write.csv(data2, file = "data/data_numeric_vets_survey-exp-2024-09-11.csv")

# save a data dict that can be saved as .csv
# generate data dictionary
df_dict <- surveytoolbox::data_dict(df) # I prefer this to the labelled dict
write.csv(df_dict, file = "codebooks/df_dict.csv")

# remove uneeded dataframes and leave df and df_dict
rm(data, data_dict_spss, data_spss, data_spss_dict, data2_dict_num, raw_spss, raw_spss_dict)

```

### 2024-10-16 notebooks/02-crosstables.qmd
push to docs/ and add notebooks

---
title: Crosstabulations
author: Isaiah
format: 
  html: 
    code-fold: false
    code-tools: true
    code-overflow: wrap
    code-copy: true
    code-annotations: true
---

## Crosstables

```{r}
#| label: tbl-q19
#| tbl-cap: "Confidence vote counts will be accurate in Maricopa County, AZ by Experiment Condition"

# Crosstab of Q19 by treatment group
df |> 
  janitor::tabyl(group, q19, show_na = F) |>
  janitor::adorn_percentages(denominator = 'row') |>
  janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Group",
    col_name = 'Q19') |>
  gt::gt(
    rowname_col = 'Q19',
    groupname_col = 'Group' 
  ) |>  
  gt::cols_label(
    c('Group/Q19') ~ "Group") |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Q19. Vote Count Confidence for Maricopa County, AZ"
  ) |>  
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q19. How confident are you that votes in Maricopa County, AZ will be counted as voters intend in the elections this November?",
    locations = gt::cells_column_spanners()) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

# df |> 
#   janitor::tabyl(group, q19, show_na = F) |>  
#   janitor::adorn_totals('both', na.rm = T) |> 
#   janitor::adorn_percentages(denominator = 'row') |>
#   janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
#   janitor::adorn_ns() |> 
#   janitor::adorn_title(
#     'combined',
#     row_name = "Group",
#     col_name = 'Q19') |> 
#   kableExtra::kbl() |> 
#   kableExtra::kable_styling(
#     bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
#     latex_options = "basic",
#     font_size = 13
#   )

```

```{r}
#| label: tbl-q21
#| tbl-cap: "Election Staff Commitment to Fairness and Accuracy by Experiment Condition"
#| tbl-cap-location: top

df |> 
  janitor::tabyl(group, q21, show_na = F) |> 
  # janitor::adorn_totals("both") |> 
  janitor::adorn_percentages("row") |> 
  janitor::adorn_pct_formatting(digits = 2, affix_sign = F) |>
  janitor::adorn_ns("rear") |> 
  janitor::adorn_title("combined", 
                       row_name = "Group",
                       col_name = "Q21") |>
  # bind_rows(.id = "group_var") |>   
  gt::gt(
    rowname_col = "row_var",
    groupname_col = "group_var") |>   
  gt::cols_label(
    c('Group/Q21') ~ "Group") |>
  # gt::cols_label_with(columns = '...1', fn = ~sjlabelled::get_label(df$q5.clps)) |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Q21. Election staff commitment to fairness and accuracy"
  ) |>
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q21. Think about the election staff and volunteers who handle the administration and conduct of elections in Maricopa County, AZ. How committed do you think they will be to making sure the elections held this November are fair and accurate?",
    locations = gt::cells_column_spanners()) |>
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

# df |> 
#   janitor::tabyl(group, q21, show_na = F) |> 
#   janitor::adorn_totals("both") |> 
#   janitor::adorn_percentages("row") |> 
#   janitor::adorn_pct_formatting(digits = 2, affix_sign = F) |>
#   janitor::adorn_ns("rear") |> 
#   janitor::adorn_title("combined", 
#                        row_name = "Group",
#                        col_name = "Q21")

```

```{r}
#| label: tbl-q22
#| tbl-cap: "Q22. Confidence in Fair Voting Process by Experiment Condition in Maricopa County, AZ by Experiment Condition"
#| tbl-cap-location: top

# Crosstab of Q22 by treatment group
df |> 
  janitor::tabyl(group, q22, show_na = F) |>
  janitor::adorn_percentages(denominator = 'row') |>
  janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Group",
    col_name = 'Q22') |>
  gt::gt(
    rowname_col = 'Q22',
    groupname_col = 'Group' 
  ) |>  
  gt::cols_label(
    c('Group/Q22') ~ "Group") |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Q22. Confidence in Fair Voting Process for Maricopa County, AZ"
  ) |>  
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q22.How confident are you that the voting process will be fair in Maricopa County, AZ?",
    locations = gt::cells_column_spanners()) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

# df |> 
#   janitor::tabyl(group, q22, show_na = F) |>  
#   janitor::adorn_totals('both', na.rm = T) |> 
#   janitor::adorn_percentages(denominator = 'row') |>
#   janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
#   janitor::adorn_ns() |> 
#   janitor::adorn_title(
#     'combined',
#     row_name = "Group",
#     col_name = 'Q22') |> 
#   kableExtra::kbl() |> 
#   kableExtra::kable_styling(
#     bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
#     latex_options = "basic",
#     font_size = 13
#   )

```

```{r}

df |> 
  janitor::tabyl(q7, q22, group, show_na = F) |> 
  # janitor::adorn_totals("both") |>
  janitor::adorn_percentages("row") |> 
  janitor::adorn_pct_formatting(digits = 2, affix_sign = F) |>
  janitor::adorn_ns("rear") |> 
  janitor::adorn_title("combined", 
                       row_name = "Q7. Legitimacy of 2020 Election",
                       col_name = "Q22") |>
  bind_rows(.id = "group_var") |>   
  gt::gt(
    rowname_col = "row_var",
    groupname_col = "group_var") |>  
  gt::row_group_order(groups = c("Control", "Treatment")) |> 
  gt::cols_label(
    c('Q7. Legitimacy of 2020 Election/Q22') ~ "Q7. Legitimacy of 2020 Election") |>
  # gt::cols_label_with(columns = '...1', fn = ~sjlabelled::get_label(df$q5.clps)) |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 3:6,
    label = "Q22. Confidence in Fair Voting process for Maricopa County, AZ"
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q22.How confident are you that the voting process will be fair in Maricopa County, AZ?",
    locations = gt::cells_column_spanners()) |> 
  gt::tab_footnote(
    footnote = "Q7.Regardless of whom you supported in the 2020 election, \ndo you think Joe Biden's election as president was legitimate, or was he not legitimately elected?",
    locations = gt::cells_column_labels('Q7. Legitimacy of 2020 Election/Q22')
    ) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )
```

```{r}
#| label: tbl-q23
#| tbl-cap: "q23. Confidence in Fair Voting Process by Experiment Condition in Maricopa County, AZ by Experiment Condition"
#| tbl-cap-location: top

# Crosstab of q23 by treatment group
df |> 
  janitor::tabyl(group, q23, show_na = F) |>
  janitor::adorn_percentages(denominator = 'row') |>
  janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Group",
    col_name = 'Q23') |>
  gt::gt(
    rowname_col = 'Q23',
    groupname_col = 'Group' 
  ) |>  
  gt::cols_label(
    c('Group/Q23') ~ "Group") |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Q23. Confidence in Fair Voting Outcomesfor Maricopa County, AZ"
  ) |>  
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q23.How confident are you that the voting outcomes will be fair in Maricopa County, AZ?",
    locations = gt::cells_column_spanners()) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

# df |> 
#   janitor::tabyl(group, q23, show_na = F) |>  
#   janitor::adorn_totals('both', na.rm = T) |> 
#   janitor::adorn_percentages(denominator = 'row') |>
#   janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
#   janitor::adorn_ns() |> 
#   janitor::adorn_title(
#     'combined',
#     row_name = "Group",
#     col_name = 'q23') |> 
#   kableExtra::kbl() |> 
#   kableExtra::kable_styling(
#     bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
#     latex_options = "basic",
#     font_size = 13
#   )

```

```{r}

df |> 
  janitor::tabyl(q7, q23, group, show_na = F) |> 
  # janitor::adorn_totals("both") |> 
  janitor::adorn_percentages("row") |> 
  janitor::adorn_pct_formatting(digits = 2, affix_sign = F) |>
  janitor::adorn_ns("rear") |> 
  janitor::adorn_title("combined", 
                       row_name = "Q7. Legitimacy of 2020 Election",
                       col_name = "Q23") |>
  bind_rows(.id = "group_var") |>   
  gt::gt(
    rowname_col = "row_var",
    groupname_col = "group_var") |>  
  gt::row_group_order(groups = c("Control", "Treatment")) |> 
  gt::cols_label(
    c('Q7. Legitimacy of 2020 Election/Q23') ~ "Q7. Legitimacy of 2020 Election") |>
  # gt::cols_label_with(columns = '...1', fn = ~sjlabelled::get_label(df$q5.clps)) |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 3:6,
    label = "Q23. Confidence in Fair Voting Outcomesfor Maricopa County, AZ"
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q23.How confident are you that the voting outcomes will be fair in Maricopa County, AZ?",
    locations = gt::cells_column_spanners()) |> 
  gt::tab_footnote(
    footnote = "Q7.Regardless of whom you supported in the 2020 election, \ndo you think Joe Biden's election as president was legitimate, or was he not legitimately elected?",
    locations = gt::cells_column_labels('Q7. Legitimacy of 2020 Election/Q23')
    ) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )
```

```{r}
#| label: tbl-q24-crab
#| tbl-cap: "q24. Confidence in Fair Voting Process by Experiment Condition in Maricopa County, AZ by Experiment Condition"
#| tbl-cap-location: top

# Crosstab of q24 by treatment group
df |> 
  janitor::tabyl(group, q24, show_na = F) |>
  janitor::adorn_percentages(denominator = 'row') |>
  janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Group",
    col_name = 'Q24') |>
  gt::gt(
    rowname_col = 'Q24',
    groupname_col = 'Group' 
  ) |>  
  gt::cols_label(
    c('Group/Q24') ~ "Group") |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Q24. Confidence in Fair Voting Outcomesfor Maricopa County, AZ"
  ) |>  
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q24.How confident are you that the voting outcomes will be fair in Maricopa County, AZ?",
    locations = gt::cells_column_spanners()) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

# df |>
#   janitor::tabyl(group, q24, show_na = F) |>
#   janitor::adorn_totals('both', na.rm = T) |>
#   janitor::adorn_percentages(denominator = 'row') |>
#   janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
#   janitor::adorn_ns() |>
#   janitor::adorn_title(
#     'combined',
#     row_name = "Group",
#     col_name = 'q24') |>
#   kableExtra::kbl() |>
#   kableExtra::kable_styling(
#     bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
#     latex_options = "basic",
#     font_size = 13
#   )

```

```{r}
#| label: tbl-q25-crab
#| tbl-cap: "Concern for violence, threats, or voter intimidation in Maricopa County, AZ by Experiment Condition"
#| tbl-cap-location: top

# Crosstab of Q25 by treatment group
df |> 
  janitor::tabyl(group, q25, show_na = F) |>
  janitor::adorn_percentages(denominator = 'row') |>
  janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Group",
    col_name = 'Q25') |>
  gt::gt(
    rowname_col = 'Q25',
    groupname_col = 'Group' 
  ) |>  
  gt::cols_label(
    c('Group/Q25') ~ "Group") |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Concern for violence, threats, or voter intimidation in Maricopa County, AZ"
  ) |>  
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q25. Thinking about Maricopa County, AZ, how concerned should voters feel \nabout potential violence, \nthreats of violence, or intimidation while voting in person at their local polling place?",
    locations = gt::cells_column_spanners()) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

# alternative crosstab
# df |> 
#   janitor::tabyl(group, q25, show_na = F) |>  
#   janitor::adorn_totals('both', na.rm = T) |> 
#   janitor::adorn_percentages(denominator = 'row') |>
#   janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
#   janitor::adorn_ns() |> 
#   janitor::adorn_title(
#     'combined',
#     row_name = "Group",
#     col_name = 'Q25') |> 
#   kableExtra::kbl() |> 
#   kableExtra::kable_styling(
#     bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
#     latex_options = "basic",
#     font_size = 13
#   )

```

```{r}
#| label: tbl-q26-crab
#| tbl-cap: "Q26. In-person voter safety in Maricopa County, AZ by Experiment Condition"
#| tbl-cap-location: top

# Crosstab of Q26 by treatment group
df |> 
  janitor::tabyl(group, q26, show_na = F) |>
  janitor::adorn_percentages(denominator = 'row') |>
  janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Group",
    col_name = 'Q26') |>
  gt::gt(
    rowname_col = 'Q26',
    groupname_col = 'Group' 
  ) |>  
  gt::cols_label(
    c('Group/Q26') ~ "Group") |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Confidence for In-person voter safety in Maricopa County, AZ"
  ) |>  
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q26. How confident, if at all, are you that in person polling places in Maricopa County, AZ \nwill be safe places for voters to cast their ballots during the upcoming elections in November?",
    locations = gt::cells_column_spanners()) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

# df |> 
#   janitor::tabyl(group, q26, show_na = F) |>  
#   janitor::adorn_totals('both', na.rm = T) |> 
#   janitor::adorn_percentages(denominator = 'row') |>
#   janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
#   janitor::adorn_ns() |> 
#   janitor::adorn_title(
#     'combined',
#     row_name = "Group",
#     col_name = 'Q26') |> 
#   kableExtra::kbl() |> 
#   kableExtra::kable_styling(
#     bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
#     latex_options = "basic",
#     font_size = 13
#   )

```

```{r}
#| label: tbl-q27-crab
#| tbl-cap: "Q27. Approval for Election official in Maricopa County, AZ"
#| tbl-cap-location: top

df |> 
  janitor::tabyl(group, q27, show_na = F) |>
  janitor::adorn_percentages(denominator = 'row') |>
  janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Group",
    col_name = 'Q27') |>
  gt::gt(
    rowname_col = 'Q27',
    groupname_col = 'Group' 
  ) |>  
  gt::cols_label(
    c('Group/Q27') ~ "Group") |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Approval for Election official in Maricopa County, AZ"
  ) |>  
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q27. Do you approve or disapprove of the way election officials in Maricopa County, AZ are handling their jobs?",
    locations = gt::cells_column_spanners()) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

# df |> 
#   janitor::tabyl(group, q27, show_na = F) |>  
#   janitor::adorn_totals('both', na.rm = T) |> 
#   janitor::adorn_percentages(denominator = 'row') |>
#   janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
#   janitor::adorn_ns() |> 
#   janitor::adorn_title(
#     'combined',
#     row_name = "Group",
#     col_name = 'Q27') |> 
#   kableExtra::kbl() |> 
#   kableExtra::kable_styling(
#     bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
#     latex_options = "basic",
#     font_size = 13
#   )

```

```{r}
#| label: tbl-q29-crab
#| tbl-cap: "Q29. Should Local Area Adopt Recruitment Program of Maricopa County, AZ"
#| tbl-cap-location: top

df |> 
  janitor::tabyl(group, q29, show_na = F) |>
  janitor::adorn_percentages(denominator = 'row') |>
  janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Group",
    col_name = 'Q29') |>
  gt::gt(
    rowname_col = 'Q29',
    groupname_col = 'Group' 
  ) |>  
  gt::cols_label(
    c('Group/Q29') ~ "Group") |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Should Local Community Adopt Maricopa County, AZ Recruitment Program"
  ) |>  
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q29. How much would you like to see your local community adopt a program for recruiting elections staff like the one you read about in Maricopa County, AZ?",
    locations = gt::cells_column_spanners()) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

# df |> 
#   janitor::tabyl(group, q29, show_na = F) |>  
#   janitor::adorn_totals('both', na.rm = T) |> 
#   janitor::adorn_percentages(denominator = 'row') |>
#   janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
#   janitor::adorn_ns() |> 
#   janitor::adorn_title(
#     'combined',
#     row_name = "Group",
#     col_name = 'Q29') |> 
#   kableExtra::kbl() |> 
#   kableExtra::kable_styling(
#     bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
#     latex_options = "basic",
#     font_size = 13
#   )

```

```{r}

df |> 
  janitor::tabyl(group, q41.4, show_na = F) |>
  janitor::adorn_percentages(denominator = 'row') |>
  janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Group",
    col_name = 'Q41.4') |>
  gt::gt(
    rowname_col = 'Q41.4',
    groupname_col = 'Group' 
  ) |>  
  gt::cols_label(
    c('Group/Q41.4') ~ "Group") |> 
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_row_groups()
  ) |> 
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_labels()
  ) |> 
  gt::tab_spanner(
    columns = 2:5,
    label = "Election staff and volunteers include military veterans and their family members"
  ) |>  
  gt::tab_style(
    style = gt::cell_text(weight = 'bold'),
    locations = gt::cells_column_spanners()
    ) |> 
  gt::tab_footnote(
    footnote = "Table reflects row percentages. NAs omitted") |> 
  gt::tab_footnote(
    footnote = "Q41.4. How would the following impact your confidence in the fairness and accuracy of elections conducted this November? Election staff and volunteers include military veterans and their family members from the community",
    locations = gt::cells_column_spanners()) |> 
  gt::cols_align(align = 'left', columns = everything()) |> 
  gt::tab_options(
    table.font.size = "small",
    data_row.padding = gt::px(1)
  )

# "Regardless of whether any of these are actually the case, how would the following impact your confidence in the fairness and accuracy of elections conducted this November?"
# Election staff and volunteers include military veterans and their family members from the community.

# df |> 
#   janitor::tabyl(group, q29, show_na = F) |>  
#   janitor::adorn_totals('both', na.rm = T) |> 
#   janitor::adorn_percentages(denominator = 'row') |>
#   janitor::adorn_pct_formatting(digits = 1, affix_sign = F) |>
#   janitor::adorn_ns() |> 
#   janitor::adorn_title(
#     'combined',
#     row_name = "Group",
#     col_name = 'Q29') |> 
#   kableExtra::kbl() |> 
#   kableExtra::kable_styling(
#     bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
#     latex_options = "basic",
#     font_size = 13
#   )

```

```{r}
#| label: tbl-7
#| tbl-cap: "Confidence Impact on In-person Voter Safety"
#| results: asis

# Simple Crosstab to show response breakdown by experiment condition
# NAs omitted. 
df |>
  mutate(
    confimpct_vets = dplyr::case_when(
      q43.4.clps == "increase" ~ 'Increase Confidence',
      q43.4.clps == "no_impact" ~ 'No Impact',
      q43.4.clps == 'decrease' ~ 'Decrease Confidence'
      )) |> 
  janitor::tabyl(group, confimpct_vets,  show_na = F) |> 
  janitor::adorn_totals('both') |> 
  janitor::adorn_percentages('row') |> 
  janitor::adorn_pct_formatting(digits = 2, affix_sign = T) |> 
  janitor::adorn_ns("rear") |> 
  janitor::adorn_title(
    'combined',
    row_name = 'Condition',
    col_name = 'Election staff include veterans and family') |>
  dplyr::relocate(
    "No Impact", .before = "Increase Confidence"
  ) |> 
  kableExtra::kbl() |> 
  kableExtra::footnote(
    general = "NA omitted. % (n)"
    ) |> 
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
    latex_options = "basic",
    font_size = 13,
    full_width = T,
    fixed_thead = T
  )

```

### 2024-10-16 notebooks/03-plots.qmd
push to docs/ and add notebooks

---
title: Figures, Plots, Graphs
author: Isaiah
format: 
  html: 
    code-fold: false
    code-tools: true
    code-overflow: wrap
    code-copy: true
    code-annotations: true
---

```{r}
#| label: setup
#| output: false

# load packages
library(tidyverse)
library(janitor)

# load data
load("data/df-2024-09-11.Rdata") # df set as factor with dummy vars

# To avoid excessive copy/paste, I made a function to create Likert plots
# it is mostly a wrapper around `ggstats::gglikert`, but with a specific set up
# particular colors, theme, etc. 
likert_plot <- function(data, x, y){
  ggstats::gglikert(data = data, include = {{ x }}, y = {{ y }}, 
                    facet_rows = vars(.question))+
    # customize color
    scale_fill_manual(values = c("black", "grey35", "firebrick1", "firebrick3"))+
    theme_bw()+
    theme(
      legend.position = 'bottom',    # place legend on bottom
      axis.text.x = element_blank(), # remove percentage text along x-axis
      strip.text = element_blank() # remove label of facet
        )
}

```

## Figures

```{r}
#| label: fig-q19-likert
#| fig-cap: "Confidence in Accurate Vote Count by Experiment Condition"
#| fig-cap-location: top

# Q19 by experiment condition, Likert style plot
likert_plot(df, q19, group)+
  labs(
    title = "Confidence in Vote Count by Recruitment Program",
    caption = "VMF Recruitment = 639, Standard Recruitment = 624",
    x = str_wrap(attr(df$q19, "label"), width = 95))

# same plot, without the function
df |>
  ggstats::gglikert(include = c(q19), y = 'group')+
  ggplot2::facet_grid(cols = vars(.question))+
  labs(
    title = "Confidence in Vote Count by Experiment Condition",
    caption = "VMF Recruitment = 639, Standard Recruitment = 624",
    x = "How confident are you that votes in Maricopa County, AZ will be counted as voters intend in the elections this November?"
  )+
  # customize color
  scale_fill_manual(
    values = c("black", "grey35", "firebrick1", "firebrick3")
  )+
  theme_bw()+
  theme(legend.position = 'bottom',    # place legend on bottom
        axis.text.x = element_blank(), # remove percentage text along x-axis
        strip.text.x = element_blank()) # remove label of facet

```

```{r}
#| label: fig-q19-barplot
#| fig-cap: "Confidence in Accurate Vote Count by Experiment Condition"
#| fig-cap-location: top

# Q19 by experiment condition, barplot
# black and white. Includes number of obs
df |> 
  # compute frequency within each combination
  group_by(group, q19) |> 
  count() |>  
  # compute proportion within group
  # n is the default variable created by count()
  group_by(group) |> 
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'% (', n, ')', sep = "")) |> 
  ggplot(aes(x = q19, y = pct, fill = group))+
  geom_bar(position = 'dodge', stat = 'identity')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5, vjust = -0.5)+
  scale_fill_grey(start = 0.5, end = 0.1)+
  # \n in a string tells R to break the line there
  labs(y = "Percentage",
       x = "Q19. How confident are you that votes in Maricopa County, AZ \nwill be counted as voters intend in the elections this November?",
       fill = "Group\nExperiment\nCondition",
       caption = 'Treatment n = 639, Control n = 624')+
  theme_bw()
```

```{r}
#| label: fig-q19-barplot2
#| fig-cap: "Confidence in Accurate Vote Count by Experiment Condition"
#| fig-cap-location: top

# alternate
# Q19 by experiment condition, barplot
# different colors. Removes number of obs
df |> 
  # compute frequency within each combination
  group_by(group, q19) |> 
  count() |>  
  # compute proportion within group
  # n is the default variable created by count()
  group_by(group) |> 
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'%')) |> 
  ggplot(aes(x = q19, y = pct, fill = group))+
  geom_bar(position = 'dodge', stat = 'identity')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5, vjust = -0.5)+
  # set fill colors manually
  scale_fill_manual(
    values = c("grey28", 'firebrick3'))+
  # scale_fill_grey(start = 0.5, end = 0.1)+
  # \n in a string tells R to break the line there
  labs(y = "Percentage",
       x = "How confident are you that votes in Maricopa County, AZ \nwill be counted as voters intend in the elections this November?",
       fill = "Group\nExperiment\nCondition",
       caption = 'Treatment n = 639, Control n = 624')+
  theme_bw()+
  theme(legend.position = "bottom")
```

```{r}
#| label: fig-q19-legit
#| fig-cap: "Confidence in Accuracy of Vote counts in Maricopa County, AZ among those who believe Biden's 2020 election was or was not legitimate"
#| fig-subcap: "Proportion of confidence in vote count by 2020 election legitimacy and group condition "
#| fig-cap-location: top

df |> 
  select(group, q7, q19, q19.clps) |>
  drop_na() |> 
  ggstats::gglikert(include = c(q19), y = 'group')+
  ggplot2::facet_grid(rows = vars(q7))+
  # customize color
  scale_fill_manual(values = c("black", "grey35", "firebrick1", "firebrick3"))+
  labs(
    title = "Confidence in Vote Count by Beliefs of 2020 Election Legitimacy and Election Staff Recruitment",
    subtitle = "Do you think Joe Biden's election as president was legitimate, or was he not legitimately elected?",
    caption = "VMF Recruitment = 639, Standard Recruitment = 624",
    x = "How confident are you that votes in Maricopa County, AZ will be counted as voters intend in the elections this November?"
  )+
  theme_bw()+
  theme(legend.position = 'bottom', axis.text.x = element_blank())

```

```{r}
#| label: fig-q19-legit-coef-plot
#| fig-cap: "Confidence in Accuracy of Vote counts in Maricopa County, AZ among those who believe Biden's 2020 election was not legitimate"
#| fig-subcap: "Means comparison with 95% confidence intervals 'Very confident' and 'Somewhat confident' = 1, 'Not too confident' and 'Not confident at all' = 0'"

# model difference 
modq19_q7 <- df |> 
  # mutate q19 into a dummy numeric var 
  # where 'Somewhat' and 'Very' confident = 1
  mutate(q19.dum = dplyr::case_when(
    q19.clps == "Confident" ~ 1,
    q19.clps == "Not_confident" ~ 0,
    TRUE ~ NA
  ),
  # mutate q7 into a numeric dummy var where legitimate = 1, not legit = 0
  q7.dum = dplyr::case_when(
    q7 == "Legitimate" ~ 1,
    q7 == "Not legitimate" ~ 0,
    TRUE ~ NA
  )) |>
  # select only those vars that will be in the model
  select(group, q7.dum, q19.dum) |>
  # drop any NA values from data
  drop_na() %>%
  # filter by those who believe that Biden's 2020 election was not legitimate
  filter(q7.dum == 0) %>% # idk why the magitr pipe works but not the native pipe
  # run a linear model
  lm(q19.dum ~ group, data = .)

# create a coef plot of the linear model with confidence interval error bars 
ggstats::ggcoef_model(model = modq19_q7, conf.int = T)+
  labs(
    caption = "estimate = 0.145, SE = 0.0460, t-statistic = 3.16, CI [0.0548, 0.236]"
  )+
  theme_bw()+
  theme(legend.position = 'bottom')

```

```{r}
#| label: fig-q20-barplot
#| fig-cap: "Confidence Election Officials in Maricopa County, AZ will do a good job by Experiment Condition"
#| fig-cap-location: top

# Q20 by experiment condition, barplot
df |> 
  # compute frequency within each combination
  group_by(group, q20) |> 
  count() |>  
  # compute proportion within group
  # n is the default variable created by count()
  group_by(group) |> 
  drop_na() |> 
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'% (', n, ')', sep = "")) |> 
  ggplot(aes(x = q20, y = pct, fill = group))+
  geom_bar(position = 'dodge', stat = 'identity')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5, vjust = -0.5)+
  scale_fill_grey(start = 0.5, end = 0.1)+
  # \n in a string tells R to break the line there
  labs(y = "Percentage",
       x = "Q20. How confident are you that election officials, their staff, and volunteers in Maricopa County, AZ \nwill do a good job conducting the elections this November?",
       fill = "Group\nExperiment\nCondition",
       caption = 'Treatment n = 638, Control n = 624')+
  theme_bw()

```

```{r}
#| label: fig-q20-likert
#| fig-cap: "Election staff in Maricopa County, AZ will do a good job by Experiment Condition"
#| fig-cap-location: top

df |>
  labelled::set_variable_labels(
    q19 = "Votes will be counted as voters intend",
    q20 = "Election staff in Maricopa County, AZ will do a good job",
    q22 = "Voting process will be fair in Maricopa County, AZ",
    q23 = "Voting outcomes will be fair in Maricopa county, AZ",
    q24 = "Election systems will be secure from technological threats",
    q26 = "Voting sites will be safe places for in-person voting"
  ) |> 
  ggstats::gglikert(include = c(q20), y = 'group', facet_rows = vars(.question))+ 
  theme_bw()+
  theme(legend.position = 'bottom')

```

```{r}
#| label: fig-q20-coefplot

modq20 <- df |> 
  select(group, q20, q20.clps) |> 
  drop_na() |> 
  mutate(q20.dum = dplyr::case_when(
    q20.clps == "Confident" ~ 1,
    q20.clps == "Not_confident" ~ 0,
    TRUE ~ NA
  )) %>%
  lm(q20.dum ~ group, data = .)

# modq20 |> summary() |> broom::tidy(conf.int = T)

# create a coef plot of the linear model with confidence interval error bars 
ggstats::ggcoef_model(model = modq20, conf.int = T)+
  theme_bw()+
  theme(legend.position = 'bottom')

```

```{r}
#| label: fig-q21-barplot
#| fig-cap: "Confidence in Commitment of Election Staff and Volunteers by Experiment Condition"
#| fig-cap-location: top

df |> 
  # compute frequency within each combination
  group_by(group, q21) |> 
  count() |>  
  # compute proportion within group
  # n is the default variable created by count()
  group_by(group) |> 
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'% (', n, ')', sep = "")) |> 
  ggplot(aes(x = q21, y = pct, fill = group))+
  geom_bar(position = 'dodge', stat = 'identity')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5 , vjust = -0.5)+
  scale_fill_grey(start = 0.5, end = 0.1)+
  # \n in a string tells R to break the line there
  labs(y = "Percentage",
       x = "How committed do you think Election Staff will be \nto making sure the elections held this November are fair and accurate?",
       fill = "Group\nExperiment\nCondition",
       caption = 'Treatment n = 639, Control n = 624')+
  theme_bw()

```

```{r}
#| label: fig-q21-likert
#| fig-cap: "Confidence in Commitment of Election Staff and Volunteers by Experiment Condition"
#| fig-cap-location: top

df |>
  ggstats::gglikert(include = c(q21), y = 'group')+
  ggplot2::facet_grid(cols = vars(.question))+
  labs(
    title = "Confidence in Commitment of Election Staff and Volunteers by Experiment Condition",
    caption = "VMF Recruitment = 639, Standard Recruitment = 624",
    x = "How committed do you think Election Staff will be \nto making sure the elections held this November are fair and accurate?"
  )+
  # customize color
  scale_fill_manual(
    values = c("black", "grey35", "firebrick1", "firebrick3")
  )+
  theme_bw()+
  theme(legend.position = 'bottom',    # place legend on bottom
        axis.text.x = element_blank(), # remove percentage text along x-axis
        strip.text.x = element_blank()) # remove label of facet

```

```{r}
#| label: fig-q22-likert
#| fig-cap: "Confidence in Fair Voting Process by Experiment Condition"
#| fig-cap-location: top

df |>
  ggstats::gglikert(include = c(q22), y = 'group')+
  ggplot2::facet_grid(cols = vars(.question))+
  labs(
    title = "Confidence in Fair Voting Process by Experiment Condition",
    caption = "VMF Recruitment = 639, Standard Recruitment = 624",
    x = "How confident are you that the voting process will be fair in Maricopa County, AZ?"
  )+
  # customize color
  scale_fill_manual(
    values = c("black", "grey35", "firebrick1", "firebrick3")
  )+
  theme_bw()+
  theme(legend.position = 'bottom',    # place legend on bottom
        axis.text.x = element_blank(), # remove percentage text along x-axis
        strip.text.x = element_blank()) # remove label of facet

```

```{r}
#| label: fig-q22-barplot
#| fig-cap: "Confidence in Fair Voting Process by Experiment Condition"
#| fig-cap-location: top

df |> 
  # compute frequency within each combination
  group_by(group, q22) |> 
  count() |>  
  # compute proportion within group
  # n is the default variable created by count()
  group_by(group) |> 
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'% (', n, ')', sep = "")) |> 
  ggplot(aes(x = q22, y = pct, fill = group))+
  geom_bar(position = 'dodge', stat = 'identity')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5 , vjust = -0.5)+
  scale_fill_grey(start = 0.5, end = 0.1)+
  # \n in a string tells R to break the line there
  labs(y = "Percentage",
       x = "How confident are you that the voting process will be fair in Maricopa County, AZ?",
       fill = "Group\nExperiment\nCondition",
       caption = 'Treatment n = 639, Control n = 624')+
  theme_bw()

```

```{r}
#| label: fig-q22-legit-coef-plot
#| fig-cap: "Confidence in Electoral Process in Maricopa County, AZ among those who believe Biden's 2020 election was not legitimate"
#| fig-subcap: "Means comparison with 95% confidence intervals 'Very confident' and 'Somewhat confident' = 1, 'Not too confident' and 'Not confident at all' = 0'"

# model difference 
modq22_q7 <- df |> 
  # mutate q19 into a dummy numeric var 
  # where 'Somewhat' and 'Very' confident = 1
  mutate(q22.dum = dplyr::case_when(
    q22.clps == "Confident" ~ 1,
    q22.clps == "Not_confident" ~ 0,
    TRUE ~ NA
  ),
  # mutate q7 into a numeric dummy var where legitimate = 1, not legit = 0
  q7.dum = dplyr::case_when(
    q7 == "Legitimate" ~ 1,
    q7 == "Not legitimate" ~ 0,
    TRUE ~ NA
  )) |>
  # select only those vars that will be in the model
  select(group, q7.dum, q22.dum) |>
  # drop any NA values from data
  drop_na() %>%
  # filter by those who believe that Biden's 2020 election was not legitimate
  filter(q7.dum == 0) %>% # idk why the magitr pipe works but not native pipe
  # run a linear model
  lm(q22.dum ~ group, data = .)

# show the (tidy) results of the model
# the (Intercept) estimate reflects the mean "confident" in the control group among those
# who believe the 2020 election was not legitimate
# the 'groupTreatment' estimate is the mean of "confident" in the treatment
# group among those who believe the 2020 election was not legitimate
# 'statistic' reflects the t-value, and p-value = 0.001706 
summary(modq22_q7) |> broom::tidy(conf.int = T)

# create a coef plot of the linear model with confidence interval error bars 
ggstats::ggcoef_model(model = modq19_q7, conf.int = T)+
  labs(
    caption = "estimate = 0.145, SE = 0.0460, t-statistic = 3.16, CI [0.0548, 0.236]"
  )+
  theme_bw()+
  theme(legend.position = 'bottom')

```

```{r}
#| label: fig-q23-likert
#| fig-cap: "Confidence in Fair Voting Outcomes by Recruitment Program"
#| fig-cap-location: top

df |>
  ggstats::gglikert(include = c(q23), y = 'group')+
  ggplot2::facet_grid(cols = vars(.question))+
  labs(
    title = "Confidence in Fair Voting Outcomes by Recruitment Program",
    caption = "VMF Recruitment = 639, Standard Recruitment = 624",
    x = "How confident are you that the voting outcomes will be fair in Maricopa County, AZ?"
  )+
  # customize color
  scale_fill_manual(
    values = c("black", "grey35", "firebrick1", "firebrick3")
  )+
  theme_bw()+
  theme(legend.position = 'bottom',    # place legend on bottom
        axis.text.x = element_blank(), # remove percentage text along x-axis
        strip.text.x = element_blank()) # remove label of facet

```

```{r}
#| label: fig-q23-barplot

df |> 
  # compute frequency within each combination
  group_by(group, q23) |>
  count() |>  
  # compute proportion within group
  # n is the default variable created by count()
  group_by(group) |>  
  drop_na() |> 
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'% (', n, ')', sep = "")) |> 
  ggplot(aes(x = q23, y = pct, fill = group))+
  geom_bar(position = 'dodge', stat = 'identity')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5 , vjust = -0.5)+
  scale_fill_grey(start = 0.5, end = 0.1)+
  # \n in a string tells R to break the line there
  labs(y = "Percentage",
       x = "Q23. How confident are you that the voting outcomes will be fair in Maricopa County, AZ?",
       fill = "Group\nExperiment\nCondition",
       caption = 'Treatment n = 639, Control n = 624')+
  theme_bw()

```

```{r}
#| label: fig-q22-q23-legit
#| fig-cap: "Confidence in Electoral Process and Outcome in Maricopa County, AZ among those who believe Biden's 2020 election was or was not legitimate"
#| fig-cap-location: top
#| column: body-outset

df |> 
  select(group, q7, q22, q23, q22.clps) |>
  drop_na() |> 
  filter(q7 == "Not legitimate") |> 
  ggstats::gglikert(
    include = c(q22, q23),
    y = 'group',
    facet_rows = vars(q7),
    facet_cols = vars(.question))+
  theme_bw()+
  theme(legend.position = 'bottom')

```

```{r}
#| label: fig-q24-likert
#| fig-cap: "Trust in Election Systems Tech by Recruitment Program"
#| fig-cap-location: top

df |>
  select(q24, group) |> 
  drop_na() |> 
  ggstats::gglikert(include = c(q24), y = 'group')+
  ggplot2::facet_grid(cols = vars(.question))+
  labs(
    title = "Trust in Election Systems Tech by Recruitment Program",
    caption = "VMF Recruitment = 639, Standard Recruitment = 623",
    x = "How confident are you that election systems in Maricopa County, AZ will be secure from hacking and other technological threats?"
  )+
  # customize color
  scale_fill_manual(
    values = c("black", "grey35", "firebrick1", "firebrick3")
  )+
  theme_bw()+
  theme(legend.position = 'bottom',    # place legend on bottom
        axis.text.x = element_blank(), # remove percentage text along x-axis
        strip.text.x = element_blank()) # remove label of facet

```

```{r}
#| label: fig-q24-barplot
#| fig-cap: "Confidence in Election Systems Tech by Experiment Condition"
#| fig-cap-location: top

df |> 
  # compute frequency within each combination
  group_by(group, q24) |>
  count() |>  
  # compute proportion within group
  # n is the default variable created by count()
  group_by(group) |>  
  drop_na() |> 
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'% (', n, ')', sep = "")) |> 
  ggplot(aes(x = q24, y = pct, fill = group))+
  geom_bar(position = 'dodge', stat = 'identity')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5 , vjust = -0.5)+
  scale_fill_grey(start = 0.5, end = 0.1)+
  # \n in a string tells R to break the line there
  labs(y = "Percentage",
       x = "Q24.How confident are you that election systems in Maricopa County, AZ will be secure from hacking and other technological threats?",
       fill = "Group\nExperiment\nCondition",
       caption = 'Treatment n = 639, Control n = 624')+
  theme_bw()

```

```{r}
#| label: fig-q25-likert
#| fig-cap: "Concern for violence, threats, or voter intimidation in Maricopa County, AZ by Recruitment Program"
#| fig-cap-location: top

df |>
  select(q25, group) |> 
  drop_na() |> 
  # dplyr::mutate(q25 = forcats::fct_rev(q25)) |> 
  ggstats::gglikert(include = c(q25), y = 'group', reverse_likert = F)+
  ggplot2::facet_grid(cols = vars(.question))+
  labs(
    title ="Concern for violence, threats, or voter intimidation in Maricopa County, AZ by Recruitment Program",
    caption = "VMF Recruitment = 639, Standard Recruitment = 623",
    x = "Thinking about Maricopa County, AZ, how concerned should voters feel about \npotential violence, threats of violence, or intimidation while voting in person at their local polling place?"
  )+
  # customize color
  scale_fill_manual(
    values = c("black", "grey35", "firebrick1", "firebrick3")
  )+
  theme_bw()+
  theme(legend.position = 'bottom',    # place legend on bottom
        axis.text.x = element_blank(), # remove percentage text along x-axis
        strip.text.x = element_blank()) # remove label of facet

```

```{r}
#| label: fig-q25-barplot
#| fig-cap: "Concern for violence, threats, or voter intimidation in Maricopa County, AZ by Experiment Condition"
#| fig-cap-location: top

df |>
  # compute frequency within each combination
  group_by(group, q25) |>
  count() |>
  # compute proportion within group
  # n is the default variable created by count()
  group_by(group) |>
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'% (', n, ')', sep = "")) |>
  ggplot(aes(x = q25, y = pct, fill = group))+
  geom_col(position = 'dodge')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5 , vjust = -0.5)+
  scale_fill_grey(start = 0.5, end = 0.1)+
  # \n in a string tells R to break the line there
  labs(y = "Percentage",
       x = "Q25. Thinking about Maricopa County, AZ, how concerned should voters feel about \npotential violence, threats of violence, or intimidation while voting in person at their local polling place?",
       fill = "Group\nExperiment\nCondition",
       caption = 'Treatment n = 639, Control n = 624')+
  theme_bw()

```

```{r}
#| label: fig-q26-barplot
#| fig-cap: "In-person voter safety in Maricopa County, AZ by Experiment Condition"
#| fig-cap-location: top

df |>
  drop_na(q26) |>
  # compute frequency within each combination
  group_by(group, q26) |>
  count() |>
  # compute proportion within group
  # n is the default variable created by count()
  group_by(group) |>
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'% (', n, ')', sep = "")) |>
  ggplot(aes(x = q26, y = pct, fill = group))+
  geom_col(position = 'dodge')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5 , vjust = -0.5)+
  scale_fill_grey(start = 0.5, end = 0.1)+
  # \n in a string tells R to break the line there
  labs(y = "Percentage",
       x = "Q26. How confident, if at all, are you that in person polling places in Maricopa County, AZ \nwill be safe places for voters to cast their ballots during the upcoming elections in November?",
       fill = "Group\nExperiment\nCondition",
       caption = 'Treatment n = 638, Control n = 624')+
  theme_bw()

```

```{r}
#| label: fig-q26-likert
#| fig-cap: "In-person voter safety in Maricopa County, AZ by Experiment Condition"
#| fig-cap-location: top

# q26
df |> 
  ggstats::gglikert(include = q26, 
                    variable_labels = c(q26 ="Confidence in Voter Safety"),
                    y = 'group',
                    facet_rows = vars(.question))+
  labs(
    title = "Confidence for In-person voter safety in Maricopa County, AZ by Experiment Condition",
    subtitle = "Q26. How confident, if at all, are you that in person polling places in Maricopa County, AZ \nwill be safe places for voters to cast their ballots during the upcoming elections in November?",
       caption = 'Treatment n = 638, Control n = 624')+
  theme_bw()+
  theme(legend.position = 'bottom')

```

```{r}
#| label: fig-safe
#| fig-cap: "Concern for violence and Confidence in Voter Safety in Maricopa County, AZ by Experiment Condition"
#| fig-cap-location: top
#| fig-subcap: 
#|   - "Concern for voter intimidation, threats, or violence"
#|   - "In-person voter safety at polling sites"
#| layout-ncol: 2
#| column: body-outset

# q25 concern for violence, threats, intimidation
df |> 
  mutate(q25 = forcats::fct_rev(q25)) |> 
  labelled::set_variable_labels(
    q25 = 'Concern for voter intimidation, threats, or violence'
  ) |> 
  ggstats::gglikert(include = q25,
                    y = 'group',
                    facet_rows = vars(.question))+
  labs(
    title = "Concern for voter intimidation, threats, or violence")+
  theme_bw()+
  theme(legend.position = 'bottom')

# q26 In-person voter safety at polling sites
df |> 
  ggstats::gglikert(include = q26, 
                    variable_labels = c(q26 ="Confidence in Voter Safety"),
                    y = 'group',
                    facet_rows = vars(.question))+
  labs(
    title = "Confidence for In-person voter safety in Maricopa County, AZ by Experiment Condition")+
  theme_bw()+
  theme(legend.position = 'bottom')

```

```{r}
#| label: fig-q27-barplot
#| fig-cap: "Approval of Election Officials in Maricopa County, AZ by Experiment Condition"
#| fig-cap-location: top

df |>
  # compute frequency within each combination
  group_by(group, q27) |>
  count() |>
  # compute proportion within group
  # n is the default variable created by count()
  group_by(group) |>
  drop_na() |> 
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'% (', n, ')', sep = "")) |>
  ggplot(aes(x = q27, y = pct, fill = group))+
  geom_col(position = 'dodge')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5 , vjust = -0.5)+
  scale_fill_grey(start = 0.5, end = 0.1)+
  # \n in a string tells R to break the line there
  labs(y = "Percentage",
       x = "Q27. Do you approve or disapprove of the way election officials in Maricopa County, AZ are handling their jobs?",
       fill = "Group\nExperiment\nCondition",
       caption = 'Treatment n = 636, Control n = 623')+
  theme_bw()

```

```{r}
#| label: fig-q27-likert
#| fig-cap: "Approval of Election Officials in Maricopa County, AZ by Experiment Condition"
#| fig-cap-location: top

# Q27
likert_plot(df, q27, group)+
  labs(
    title = "Approval of Election Officials in Maricopa County, AZ by Recruitment Program",
    caption = 'VMF Recruitment =  636, Standard Recruitment = 623',
    x = str_wrap(attr(df$q27, "label"), width = 95)
    )

# same thing, but not wrapped within the function
# df |> 
#   ggstats::gglikert(
#     include = q27, 
#     variable_labels = c(q27 ="Election Official Approval"),
#     y = 'group',
#     facet_rows = vars(.question))+
#   labs(
#     title = "Approval of Election Officials in Maricopa County, AZ by Recruitment Program",
#     subtitle = "Do you approve or disapprove of the way \nelection officials in Maricopa County, AZ are handling their jobs?",
#     caption = 'Treatment n = 636, Control n = 623')+
#   # customize color
#   scale_fill_manual(
#     values = c("black", "grey35", "firebrick1", "firebrick3")
#   )+
#   theme_bw()+
#   theme(legend.position = 'bottom',    # place legend on bottom
#         axis.text.x = element_blank(), # remove percentage text along x-axis
#         strip.text.x = element_blank()) # remove label of facet

```

```{r}
#| label: fig-q28-likert
#| fig-cap: "Expectation of Electoral Fraud in Maricopa County, AZ by Recruitment Program"
#| fig-cap-location: top

df |>
  mutate(across(c(q28_1:q28_5), ~ forcats::fct_rev(.))) |>
  labelled::set_variable_labels(
    q28_1 = "Voter fraud",
    q28_2 = "Vote Miscount",
    q28_3 = "Rejected",
    q28_4 = "Interference",
    q28_5 = "Discouraged"
  ) |>
  ggstats::gglikert(
    include = q28_1:q28_5,
    y = 'group',
    facet_rows = vars(.question)
  ) +
  # customize color
  scale_fill_manual(values = c("black", "grey35", "firebrick1", "firebrick3")) +
  labs(
    title = "Expectation of Electoral Fraud in Maricopa County, AZ by Recruitment Program",
    caption = 'VMF Recruitment = 639, Standard Recruitment = 624', 
    x = "How likely do you think any or all of the following will \nhappen during this year´s elections in Maricopa County, AZ?") +
  theme_bw() +
  theme(
    legend.position = 'bottom',     # place legend on bottom
    axis.text.x = element_blank(),  # remove percentage text along x-axis
    strip.text.x = element_blank()) # remove label of facet

```

```{r}
#| label: fig-q29-barplot
#| fig-cap: "Adopt by Experiment Condition"
#| fig-cap-location: top

df |>
  # compute frequency within each combination
  group_by(group, q29) |>
  count() |>
  # compute proportion within group
  # n is the default variable created by count()
  group_by(group) |>
  drop_na() |> 
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'% (', n, ')', sep = "")) |>
  ggplot(aes(x = q29, y = pct, fill = group))+
  geom_col(position = 'dodge')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5 , vjust = -0.5)+
  scale_fill_grey(start = 0.5, end = 0.1)+
  # \n in a string tells R to break the line there
  labs(y = "Percentage",
       x = "Q29. How much would you like to see your local community adopt a program for recruiting elections staff like the one you read about in Maricopa County, AZ?",
       fill = "Group\nExperiment\nCondition",
       caption = 'Treatment n = 638, Control n = 622')+
  theme_bw()

```

```{r}
#| label: fig-q29-likert
#| fig-cap: "Approval of Election Officials in Maricopa County, AZ by Recruitment Program"
#| fig-cap-location: top

# Q29
likert_plot(df, q29, group)+
  labs(
    title = "Approval of Election Officials in Maricopa County, AZ by Recruitment Program",
    x = str_wrap(attr(df$q29, "label"), width = 95),
    caption = 'VMF Recruitment = 638, Standard Recruitment = 622')

# df |> 
#   ggstats::gglikert(
#     include = q29, 
#     variable_labels = c(q29 ="Adopt Maricopa County Program"),
#     y = 'group',
#     facet_rows = vars(.question))+
#   labs(
#     subtitle = "How much would you like to see your local community adopt a program for recruiting elections staff like the one you read about in Maricopa County, AZ?",
#        caption = 'Treatment n = 638, Control n = 622')+
#   theme_bw()+
#   theme(legend.position = 'bottom')

```

```{r}
#| label: fig-q29-coefplot

modq29 <- df |> 
  select(group, q29, q29.clps) |> 
  drop_na() |> 
  mutate(q29.dum = dplyr::case_when(
    q29.clps == "support" ~ 1,
    q29.clps == "oppose" ~ 0,
    TRUE ~ NA
  )) %>%
  lm(q29.dum ~ group, data = .)

modq29 |> summary() |> broom::tidy(conf.int = T)
# this one is right on the line of statistical significance. t-statistic = 1.955, p-value = 0.0508
# so technically it is not statistically significant, which means we can't reject null that mean support (i.e., should adopt) is different from mean support for those in the control group with a one-tailed test.

# create a coef plot of the linear model with confidence interval error bars 
ggstats::ggcoef_model(model = modq29, conf.int = T)+
  theme_bw()+
  theme(legend.position = 'bottom')

# I ran a t-test and a prop.test to confirm the results that were reported in the draft
# df |> 
#   select(group, q29, q29.clps) |> 
#   drop_na() |> 
#   mutate(q29.dum = dplyr::case_when(
#     q29.clps == "support" ~ 1,
#     q29.clps == "oppose" ~ 0,
#     TRUE ~ NA
#   ),
#   group = dplyr::case_when(
#     group == "VMF Recruitment" ~ 1,
#     group == "Standard Recruitment" ~ 0,
#     TRUE ~ NA
#   )) %>%
#   t.test(q29.dum ~ group, data = ., alternative = 'l') |> broom::tidy()
# 
# df |> 
#   select(group, q29, q29.clps) |> 
#   drop_na() |>
#   mutate(q29.clps = fct_rev(q29.clps)) |> 
#   mutate(q29.dum = dplyr::case_when(
#     q29.clps == "support" ~ 1,
#     q29.clps == "oppose" ~ 0,
#     TRUE ~ NA
#   ),
#   group = dplyr::case_when(
#     group == "VMF Recruitment" ~ 1,
#     group == "Standard Recruitment" ~ 0,
#     TRUE ~ NA
#   )) %>%
#   janitor::tabyl(group, q29.dum, show_na = F) |> 
#   dplyr::relocate("1", .before = "0") |> 
#   select(-1) %>% 
#   rstatix::prop_test(alternative = "l", detailed = T)

```

```{r}
#| label: fig-elec-conf
#| fig-cap-location: top
#| fig-cap: "Confidence in Election Administration by Experiment Condition"

df |>
  labelled::set_variable_labels(
    q19 = "Accurate Vote counts",
    q22 = "Fair Voting Process",
    q23 = "Fair Voting Outcomes",
    q24 = "Secure Election Tech",
    q26 = "Safe In-person Voting"
  ) |> 
  ggstats::gglikert(include = c(q19, q22,q23,q24,q26), y = 'group')+
  ggplot2::facet_grid(rows = vars(.question), labeller = label_wrap_gen(15))+
  labs(
    title = "Confidence in Election Administration by Experiment Condition"
  )+
  theme_bw()+
  theme(legend.position = 'bottom')

# df |>
#   labelled::set_variable_labels(
#     q19 = "Votes will be counted as voters intend",
#     q20 = "Election staff in Maricopa County, AZ will do a good job",
#     q22 = "Voting process will be fair in Maricopa County, AZ",
#     q23 = "Voting outcomes will be fair in Maricopa county, AZ",
#     q24 = "Election systems will be secure from technological threats",
#     q26 = "Voting sites will be safe places for in-person voting"
#   ) |> 
#   ggstats::gglikert(include = c(q19,q20,q22,q23,q24,q26),
#                     facet_cols = vars(group))+ 
#   labs(
#     title = "Trust and Confidence Electoral Process by Experiment Condition"
#   )+
#   theme_bw()+
#   theme(legend.position = 'bottom')

```

```{r}
#| label: fig-q41-vets-barplot
#| fig-cap: "Confidence in Election Fairness when Election Staff includes Veterans by Experiment Condition"
#| column: body-outset

# barplot of q41.4 by group
df |> 
  select(group, q41.4, q41.5, q41.6) |> 
  drop_na() |> 
  # compute frequency within each combination
  group_by(group, q41.4) |> 
  count() |> 
  # compute proportion within group
  # n is the default variable created by count()
  group_by(group) |> 
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'% (', n, ')', sep = "")) |> 
  # add y to inform geom_bar what to put in y-axis
  ggplot(aes(x = q41.4, y = prop, fill = group))+
  geom_col(position = 'dodge')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5 , vjust = -0.5)+
  scale_fill_grey(start = 0.5, end = 0.1)+
  # coord_flip()+
  labs(y = "Prop",
       x = "Q41.4",
       fill = "Group\nExperiment\nCondition")

```

```{r}
#| label: fig-q41-lawyers-barplot
#| fig-cap: "Confidence in Election Fairness when Election Staff includes Lawyers by Experiment Condition"
#| column: body-outset

df |> 
  select(group, q41.5.clps) |> 
  drop_na() |> 
  mutate(q41.5.clps = dplyr::case_when(
    q41.5.clps == "decrease" ~ "Decrease Confidence",
    q41.5.clps == "no_impact" ~ "No Impact",
    q41.5.clps == "increase" ~ "Increase Confidence",
    TRUE ~ NA
  )) |> 
  ggstats::gglikert(include = c(group), y = 'q41.5.clps', facet_row = vars(.question),  symmetric = T, add_totals = T)+
  # change color to black and grey
  scale_fill_grey(start = 0.7, end = 0.1)+
  labs(
    title = "How would the following impact your confidence in the fairness and accuracy of elections conducted this November?",
    subtitle = "Election staff and volunteers include lawyers from the community.",
    caption = "Treatment = 638, Control = 623"
  )+
  theme_bw()+
  theme(legend.position = 'bottom', strip.text = element_blank())

```

```{r}
#| label: fig-q41-students-barplot
#| fig-cap: "Confidence in Election Fairness when Election Staff includes College Students by Experiment Condition"
#| column: body-outset

df |> 
  select(group, q41.6.clps) |> 
  drop_na() |> 
  mutate(q41.6.clps = dplyr::case_when(
    q41.6.clps == "decrease" ~ "Decrease Confidence",
    q41.6.clps == "no_impact" ~ "No Impact",
    q41.6.clps == "increase" ~ "Increase Confidence",
    TRUE ~ NA
  )) |> 
  ggstats::gglikert(include = c(group), y = 'q41.6.clps', facet_row = vars(.question),  symmetric = T, add_totals = T)+
  # change color to black and grey
  scale_fill_grey(start = 0.7, end = 0.1)+
  labs(
    title = "How would the following impact your confidence in the fairness and accuracy of elections conducted this November?",
    subtitle = "Election staff and volunteers include college students from the community.",
    caption = "Treatment = 638, Control = 623"
  )+
  theme_bw()+
  theme(legend.position = 'bottom', strip.text = element_blank())

```

```{r}
#| label: fig-q41-likert
#| fig-cap: "Impact on Confidence in Election Fairness and Accuracy by Experiment Condition"
#| column: body-outset

# Q41.4 (vets), Q41.5 (lawyers), Q41.6 (students), by treatment
df |> 
  ggstats::gglikert(include = c(q41.4:q41.6), y = 'group',  symmetric = T, add_totals = F)+ 
  facet_grid(rows = vars(.question), labeller = label_wrap_gen(15))+
  labs(
    subtitle = "Q41. How would the following impact your confidence in the fairness and accuracy of elections conducted this November?"
  )+
  theme_bw()+
  theme(legend.position = 'bottom')

```

```{r}
#| label: fig-q41-coef-plot
#| fig-column: page-inset-right
#| warning: false
#| message: false

mod.q41.1 <- lm(formula = q41.1.clps.dum ~ group, data = df)
mod.q41.2 <- lm(formula = q41.2.clps.dum ~ group, data = df)
mod.q41.3 <- lm(formula = q41.3.clps.dum ~ group, data = df)
mod.q41.4 <- lm(formula = q41.4.clps.dum ~ group, data = df)
mod.q41.5 <- lm(formula = q41.5.clps.dum ~ group, data = df)
mod.q41.6 <- lm(formula = q41.6.clps.dum ~ group, data = df)

# place all the models in a list assigned as 'models' and include them in the
# ggstats::ggcoef_compare() function
models.q41 <- list(
  "Test Every Machine" = mod.q41.1,
  "Audit Ballots" = mod.q41.2,
  "Partisan Poll Watchers" = mod.q41.3,
  "Election Staff Includes Veterans" = mod.q41.4,
  "Election Staff Includes Lawyers" = mod.q41.5,
  "Election Staff Includes Students" = mod.q41.6
)

# print the coef plot and selectively color coefficients
ggstats::ggcoef_compare(
  models.q41, 
  conf.int = T, 
  add_reference_rows = F,
  categorical_terms_pattern = "{level} (ref: {reference_level})")+
  ggplot2::scale_color_manual(
    values = c("black", "black", "black", "red", "black", "black"))+
  labs(
    title = "Impact on Confidence in Election Fairness when Election Staff \nIncludes Veterans and Family by Experiment Condition",
    subtitle = "Means comparison with 95% confidence intervals\n'Increase in confidence' = 1, 'No increase in confidence = 0'",
    caption = "estimate = 0.11635, SE = 0.02799, t-statistic = 4.157, CI [-0.171, -0.0614]"
  )+
  theme_bw()+
  theme(legend.position = 'bottom')

```

```{r}
#| include: false

mod.q43.1 <- lm(formula = q43.1.clps.dum ~ group, data = df)
mod.q43.2 <- lm(formula = q43.2.clps.dum ~ group, data = df)
mod.q43.3 <- lm(formula = q43.3.clps.dum ~ group, data = df)
mod.q43.4 <- lm(formula = q43.4.clps.dum ~ group, data = df)
mod.q43.5 <- lm(formula = q43.5.clps.dum ~ group, data = df)
mod.q43.6 <- lm(formula = q43.6.clps.dum ~ group, data = df)

# place all the models in a list assigned as 'models' and include them in the
# ggstats::ggcoef_compare() function
models.q43 <- list(
  "Test Every Machine" = mod.q43.1,
  "Audit Ballots" = mod.q43.2,
  "Partisan Poll Watchers" = mod.q43.3,
  "Election Staff Includes Veterans" = mod.q43.4,
  "Election Staff Includes Lawyers" = mod.q43.5,
  "Election Staff Includes Students" = mod.q43.6
)
```

```{r}
#| label: fig-q43-coefplot
#| fig-column: page-inset-right
#| warning: false
#| message: false

# print the coef plot and selectively color coefficients
ggstats::ggcoef_compare(
  models.q43, 
  conf.int = T, 
  add_reference_rows = F, 
  categorical_terms_pattern = "{level} (ref: {reference_level})")+
  ggplot2::scale_color_manual(
    values = c("black", "black", "black", "red", "black", "black"))+
  labs(
    title = "Impact on Confidence in Voter Safety when Election Staff \nIncludes Veterans and Family by Experiment Condition",
    subtitle = "Means comparison with 95% confidence intervals\n'Increase in confidence' = 1, 'No increase in confidence = 0'",
    caption = "estimate = 0.0841, SE = 0.0280, t-statistic = 3.00, CI [0.0291, 0.139]"
  )+
  theme_bw()+
  theme(legend.position = 'bottom')

```

### 2024-10-16 notebooks/question-set-differences.qmd
push to docs/ and add notebooks

---
title: Analysis of Question Wording Differences
author: Isaiah
---

## Differences from Question Wording

::: {.callout-note}
This supplement is under construction. Resolution of various formatting issues are in progress.
:::

The following is an analysis of results from a question wording experiment embedded within a survey of public opinion on election administration and election staff. Certain questions were included in the survey to assess whether certain actions taken by election officials or circumstances at polling sites would;

  1) impact one's confidence in the fairness and accuracy of upcoming elections, or 
  2) impact confidence in voter safety while voting in-person.

It was hypothesized that different statement wording would have some effect on response choice to certain item statements. In order to test this hypothesis, another set of the same questions were constructed and half of the sample was presented with one version of item statements, while the other half was presented with a different version in which a few statements were slightly modified. Specifically, three of the six statements in question set 'B' [`Q44`, `Q46`] differed from three statements in question set 'A' [`Q41`, `Q43`]. See the table below for the full breakdown.

```{r}
#| label: qset-setup
#| include: false

# create a table containing the differing statements for question sets A and B

qsetA <- df |> 
  select(q41_1:q46_6) |> 
  labelled::set_variable_labels(
    q41_1 = "Election officials test every machine used in the election to ensure they are secure.",
    q41_2 = "Election officials conduct audits of ballots after every election to confirm the results were accurate.",
    q41_3 = "Poll watchers affiliated with the political parties or candidates observe the election.",
    q41_4 = "Election staff and volunteers include military veterans and their family members from the community.",
    q41_5 = "Election staff and volunteers include lawyers from the community.",
    q41_6 = "Election staff and volunteers include college students from the community.",
    q43_1 = "Election officials ensure that law enforcement officers are present at polling sites.",
    q43_2 = "Poll watchers affiliated with the political parties or candidates observe the election.",
    q43_3 = "People holding signs or giving out literature in support of a candidate or ballot question.",
    q43_4 = "Election staff and volunteers include military veterans and their family members from the community.",
    q43_5 = "Election staff and volunteers include lawyers from the community.",
    q43_6 = "Election staff and volunteers include college students from the community."
    ) |> 
  surveytoolbox::varl_tb() |> 
  select(var, var_label) |> 
  dplyr::slice(1:12) |> 
  dplyr::rename('Qset A' = var,
                'A statements' = var_label)

qsetB <- df |> 
  select(q41_1:q46_6) |> 
  labelled::set_variable_labels(
    q44_1 = "Election officials test every machine used in the election to ensure they are secure.",
    q44_2 = "The majority of election staff and volunteers consist of military veterans and their family members from the community.",
    q44_3 = "The majority of election staff and volunteers consist of lawyers from the community.",
    q44_4 = "Election officials conduct audits of ballots after every election to confirm the results were accurate.",
    q44_5 = "Poll watchers affiliated with the political parties or candidates observe the election.",
    q44_6 = "The majority of election staff and volunteers consist of college students from the community.",
    q46_1 = "Election officials ensure that law enforcement officers are present at polling sites.",
    q46_2 = "The majority of election staff and volunteers consist of military veterans and their family members from the community.",
    q46_3 = "The majority of election staff and volunteers consist of lawyers from the community.",
    q46_4 = "Poll watchers affiliated with the political parties or candidates observe the election.",
    q46_5 = "The majority of election staff and volunteers consist of college students from the community.",
    q46_6 = "People holding signs or giving out literature in support of a candidate or ballot question."
    ) |> 
  surveytoolbox::varl_tb() |> 
  select(var, var_label) |> 
  dplyr::slice(13:24) |> 
  dplyr::rename('Qset B' = var,
                'B statements' = var_label)

# bind the dataframes together as one with two columns
qsetAB <- dplyr::bind_cols(qsetA, qsetB)
rm(qsetA, qsetB)
```

```{r}
#| label: tbl-qset
#| tbl-cap: "Question Numbers and Statements"
#| fig-cap: "Question Numbers and Statements"
#| column: page-inset-right

# create a table containing the differing statements for question sets A and B
kableExtra::kbl(qsetAB, format = 'html', align = 'l') |> 
  kableExtra::pack_rows("Regardless of whether any of these are actually the case, how would the following impact your confidence in the fairness and accuracy of elections conducted this November?", 1, 6) |>
  kableExtra::pack_rows("How would the following impact your confidence that voters are safe from violence, threats of violence, or intimidation while voting in-person during elections this November?", 7, 12) |>
  kableExtra::row_spec(c(2,9), align = 'l') |> 
  kableExtra::footnote(
    general ="Response options ranged from 'Decrease confidence a lot', 'Decrease confidence somewhat', 'No impact on confidence', 'Increase confidence somewhat', and 'Increase confidence a lot'.",
    footnote_as_chunk = T
  ) |> 
  kableExtra::kable_styling(
    font_size = 13,
    row_label_position = 'l',
    bootstrap_options = c('striped',
                          'bordered',
                          'hover',
                          'condensed',
                          'responsive'))

```

Survey participants were randomly grouped according to the set of questions presented to them, `Qset A` or `Qset B` respectively, and responses were analyzed to test for significant differences between the different item statements. If significant differences were observed for each modified item statement in comparison to the unmodified versions, then response effects could be attributed to the change in statement wording. However, if differences were significant for one or two of the statements but not all three, then response effects could not be attributed to statement wording alone. If no differences were found, then the responses from the two question sets would be considered equivalent and coalesced into one variable per question for subsequent analysis.

To put it simply, significant differences in proportion needed to be observed for all three statements that differed between `Qset A` and `Qset B` in order to reject the null hypothesis that the two question sets were equivalent, and support the theory that response effects were due to the difference in question wording.

In order to test the statement-wording hypothesis, the five-point Likert item response options were re-coded as dichotomous 'dummy' variables. For instance, "Increase confidence a lot" and "Increase confidence somewhat" were collapsed and recoded such that "Increase" = 1, whereas all other responses were collapsed and re-coded such that "No increase" = 0. The same process was done for any "Decrease" responses. Proportions of responses were compared for both the 'Increase' and 'Decrease' dummy categories.

```{r}
#| label: law-school-setup1
#| include: false

# I coalesce these vars so I can put them in a cross tab by qset
law_skool <- df |> 
  group_by(rowID) |> 
  mutate(
    q41.5.clps = dplyr::coalesce(q41_5.clps, q44_3.clps),
    q41.6.clps = dplyr::coalesce(q41_6.clps, q44_6.clps),
    q43.5.clps = dplyr::coalesce(q43_5.clps, q46_3.clps),
    q43.6.clps = dplyr::coalesce(q43_6.clps, q46_5.clps),) |>
  ungroup() |>
  filter(!is.na(qset))

law_skool <- law_skool |> 
  select(qset, q41.5.clps, q41.6.clps, q43.5.clps, q43.6.clps) |> 
  mutate(
    fair_lawyers = dplyr::case_when(
      q41.5.clps == 'increase'  ~ 'Increase',
      q41.5.clps == 'no_impact'  ~ 'No increase',
      q41.5.clps == 'decrease'  ~ 'No increase',
      TRUE ~ NA
    )) |> 
  mutate(
    fair_students = dplyr::case_when(
      q41.6.clps == 'increase'  ~ 'Increase',
      q41.6.clps == 'no_impact'  ~ 'No increase',
      q41.6.clps == 'decrease'  ~ 'No increase',
      TRUE ~ NA
    )) |> 
  mutate(
    safe_lawyers = dplyr::case_when(
      q43.5.clps == 'increase'  ~ 'Increase',
      q43.5.clps == 'no_impact'  ~ 'No increase',
      q43.5.clps == 'decrease'  ~ 'No increase',
      TRUE ~ NA
    )) |> 
  mutate(
    safe_students = dplyr::case_when(
      q43.6.clps == 'increase'  ~ 'Increase',
      q43.6.clps == 'no_impact'  ~ 'No increase',
      q43.6.clps == 'decrease'  ~ 'No increase',
      TRUE ~ NA
    )) |> 
  select(qset, fair_lawyers, fair_students, safe_lawyers, safe_students)

law_skool <- law_skool |> 
  mutate(qset = forcats::fct_recode(qset, Includes = "A", Majority = "B"))
```

```{r}
#| label: law-school-setup2
#| include: false

var_names <- law_skool[,2:5] |> colnames()

# function to run prop_tests over a list of crosstabs 
tabyl.fun <- function(x){
  crab_df <- law_skool |> select(qset, all_of(x)) |> 
    janitor::tabyl(qset, !!sym(x), show_na = F) |> 
    select(-1) |> 
    rstatix::prop_test(detailed = T)
}

# this maps the function tabyl.fun to each character string in 'var_names'
# the results are put into a list of tibbles, in this case, a list of 4 tibbles
law_skool_prop_tests <- map(var_names, tabyl.fun)

# I combine the 4 tibbles within the list into a single tibble
pt_lawyers_students <- purrr::reduce(law_skool_prop_tests, dplyr::full_join)

# add column that identifies rows of different prop_tests
pt_lawyers_students$items <- var_names

# add column that identifies response compared
response <- c("Increase", "Increase", "Increase", "Increase")
pt_lawyers_students$response <- response

# relocate columns to better positions, rename columns, remove df column
pt_lawyers_students <- pt_lawyers_students |>
  dplyr::relocate(c(items, response), .before = n) |>
  dplyr::relocate(p.signif, .after = p) |>
  dplyr::rename(valid_n = n,
                Qset_A_n = n1,
                Qset_B_n = n2) |>
  dplyr::mutate(prop.diff = estimate1 - estimate2,
                .before = statistic) |> 
  select(-df)
```

::: {.panel-tabset}

## Fairness-Lawyers

```{r}
#| label: tbl-fair-lawyers
#| tbl-cap: "'Increase' confidence in election fairness by question wording: Lawyers"
#| fig-cap: "Proportion of those who report an 'Increase' in confidence in fairness of elections when election staff either 'Includes' or is a 'majority' of lawyers"

# crabs
law_skool |> 
  janitor::tabyl(qset, fair_lawyers, show_na = F) |> 
  janitor::adorn_totals('both') |> 
  janitor::adorn_percentages(denominator = 'row') |> 
  janitor::adorn_pct_formatting(digits = 2, affix_sign = F) |> 
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Wording") |> 
  kableExtra::kbl() |> 
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
    latex_options = "basic",
    font_size = 13
  )
```

## Fairness-Students

```{r}
#| label: tbl-fair-students
#| tbl-cap: "'Increase' confidence in election fairness by question wording: College Students"
#| fig-cap: "Proportion of those who report an 'Increase' in confidence in fairness of elections when election staff either 'Includes' or is a 'majority' of college students"

# crabs
law_skool |> 
  janitor::tabyl(qset, fair_students, show_na = F) |> 
  janitor::adorn_totals('both') |> 
  janitor::adorn_percentages(denominator = 'row') |> 
  janitor::adorn_pct_formatting(digits = 2, affix_sign = F) |> 
  janitor::adorn_ns() |> 
  janitor::adorn_title(
    'combined',
    row_name = "Wording") |>  
  kableExtra::kbl() |> 
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
    latex_options = "basic",
    font_size = 13
  )
```

## Safety-Lawyers

```{r}
#| label: tbl-safe-lawyers
#| tbl-cap: "'Increase' confidence in voter safety by question wording: Lawyers"
#| fig-cap: "Proportion of those who report an 'Increase' in confidence in voter safety when election staff either 'Includes' or is a 'majority' of college students"

# crabs
law_skool |> 
  janitor::tabyl(qset, safe_lawyers, show_na = F) |> 
  janitor::adorn_totals('both') |> 
  janitor::adorn_percentages(denominator = 'row') |> 
  janitor::adorn_pct_formatting(digits = 2, affix_sign = F) |> 
  janitor::adorn_ns() |>  
  janitor::adorn_title(
    'combined',
    row_name = "Wording") |> 
  kableExtra::kbl() |> 
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
    latex_options = "basic",
    font_size = 13
  )
```

## Safety-Students

```{r}
#| label: tbl-safe-students
#| tbl-cap: "'Increase' confidence in voter safety by question wording: College Students"
#| fig-cap: "'Increase' confidence in voter safety by question wording: College Students"

# crabs
law_skool |> 
  janitor::tabyl(qset, safe_students, show_na = F) |> 
  janitor::adorn_totals('both') |> 
  janitor::adorn_percentages(denominator = 'row') |> 
  janitor::adorn_pct_formatting(digits = 2, affix_sign = F) |> 
  janitor::adorn_ns() |>  
  janitor::adorn_title(
    'combined',
    row_name = "Wording") |> 
  kableExtra::kbl() |> 
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
    latex_options = "basic",
    font_size = 13
  )

```

:::

Results of testing revealed no statistically significant differences *attributable to differences in question wording*. However, there were significant differences observed between the fifth and sixth statements pertaining to lawyers and college students. Significant differences were found between the following items;

```{r}
#| label: tbl-qset2
#| tbl-cap: "Statements with significant differences between Question Set"
#| column: page-inset-right

# create a table containing the differing statements for question sets A and B
A <- qsetAB |> 
  filter(row_number() == 5:6 | row_number() == 11:12) |> 
  select(1:2)

B <- qsetAB |> 
  filter(row_number() == 3 | row_number() == 6 | row_number() == 9 | row_number() == 11) |> 
  select(3:4)

AB <- dplyr::bind_cols(A, B)
rm(A, B)

kableExtra::kbl(AB, format = 'html', align = 'l') |>
  kableExtra::pack_rows(
    "...how would the following impact your confidence in the fairness and accuracy of elections conducted this November?",
    1,
    2
  ) |>
  kableExtra::pack_rows(
    "How would the following impact your confidence that voters are safe from violence, threats of violence, or intimidation while voting in-person during elections this November?",
    3,
    4
  ) |>
  kableExtra::row_spec(c(2, 5), align = 'l') |>
  kableExtra::kable_styling(
    font_size = 13,
    row_label_position = 'l',
    bootstrap_options = c('striped', 'bordered', 'hover', 'condensed', 'responsive')
  )

```

```{r}

df |> 
  mutate(qset = forcats::fct_recode(
    qset,
    "Election staff 'includes'..." = 'A',
    "Election staff is 'Majority' of... " = 'B'
  )) |> 
  sjlabelled::var_labels(
    q41.4 = "Veterans",
    q41.5 = "Lawyers",
    q41.6 = "College Students",
    q43.4 = "Veterans",
    q43.5 = "Lawyers",
    q43.6 = "College Students"
  ) |> 
  ggstats::gglikert(include = c(q41.4, q41.5, q41.6, q43.4, q43.5, q43.6),
                    y = 'qset', facet_rows = vars(.question))+
  labs(
    title = "Differences in Proportion Between Question Wording")+
  theme_bw()+
  theme(legend.position = 'bottom')

```

```{r}
#| label: pt-law-school
#| tbl-cap: "Prop. Test Results Comparing Qset A to Qset B"
#| fig-cap: "Prop. Test Results Comparing Qset A to Qset B"
#| column: page-inset-right
#| echo: false

# print prop_tests as table 
kableExtra::kbl(
  pt_lawyers_students,
  format = 'html',
  format.args = list(scientific = F),
  digits = 5
  ) |> 
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "bordered", "condensed", "responsive"),
    latex_options = "basic",
    font_size = 13,
    fixed_thead = T
  )

```

Comparison of responses between `Qset A` and `Qset B` revealed differences in response to item statements concerning lawyers and students. The difference in proportions were initially attributed to the different statement wording between question sets A and B. However, the effect appears to be conditional on the group identified in the statement. Since differences are only present when the statement concerns either lawyers or students . That is, significant differences were observed when a statement read, "The majority of election staff and volunteers consist of lawyers/college students in the community" (qset B) compared to when a statement read, "Election staff and volunteers includes lawyers/college students in the community" (qset A).

Moreover, the direction of the difference remained consistent. Confidence in fairness and accuracy of elections, as well as confidence in voter safety at the polls, was reported to increase less and decrease more under the prospect of having the majority of election staff consist of lawyers/college students compared to when election staff is said to merely *include* lawyers/college students.

To put in other words, there was a higher proportion of those who reported that their confidence in fairness and voter safety would decrease among those who read that the majority of election staff consists of either lawyers or college students compared to those who read that election staff merely included lawyers or college students. Conversely, no significant differences were observed between question/statement wording when the group was identified as military veterans and their family members in the community.

These results suggest that the differences in proportion initially attributed to question/statement wording are likely an artifact of a rival cause, potentially related to general impressions of the groups involved.

Where proportions between the two independent samples were equivalent (i.e., no significant differences in proportion were found), responses were coalesced (i.e., merged) into one variable.

-   Q44_1 coalesced into Q41_1
-   Q44_4 coalesced into Q41_2
-   Q44_5 coalesced into Q41_3
-   Q44_2 coalesced into Q41_4
-   Q46_1 coalesced into Q43_1
-   Q46_4 coalesced into Q43_2
-   Q46_6 coalesced into Q43_3
-   Q46_2 coalesced into Q43_4

### 2024-10-22 notebooks/01-data-import-clean-process.qmd
added data import and process notebook document, codebook, and more

@@
 
-# uncomment to save the data dictionary as a .csv file
-# write.csv(raw_spss_dict, file = "codebooks/raw_spss_dict.csv")
+# save data dictionary of raw_spss dataset download
+write.csv(raw_spss_dict, file = "data/raw_spss_dict.csv")
 
 ```
+
+## Filter Raw data
+
+From the raw data set, there are `r dim(raw_spss)[1]` observations in the data set (each observation is a row). The survey was programmed in such a way to automatically drop participants who,
+
+1.    Didn't consent to take part in the survey. 
+2.    Were under 18 years of age[^1]
+3.    Self-identified as not being a U.S. citizen
+4.    Failed two attention checks embedded within the survey
+
+Although the survey was programmed in this way, however, any responses of these participants were still recorded and included in the data.
+Survey participants may not have been dropped from participating in the survey until after they had already entered in a few responses.
+For instance, a respondent failing both attention checks would not have been dropped from the survey until the tenth question (Q10) within the survey, but their responses prior to being dropped would still be included in a row within the data set.
+This results in a lot of missing data (i.e., NA values) filling up observations (rows) in the data.
+The following code filters the data set to exclude any respondent who met the aforementioned exclusion criteria.
+
+[^1]: The panel of participants gathered by Lucid already excluded anyone under 18 years of age, however a number of discrepancies were found between the age of respondents included in the Lucid embedded data and the age reported by the respondents themselves.
+However, the survey question asking the respondent's age was programmed so that respondents selected their age from a drop down menu.
+Since the lowest available option in the drop down list of ages was 18, there was no way for respondents who may have been under 18 to report their actual age from the drop down menu.
+Of course, it is always possible for any respondent to simply lie about their age, but this footnote is added for posterity.
+
+```{r}
+#| label: subset-data
+
+data_spss <- raw_spss |> 
+  tibble::rowid_to_column("rowID") |>   # <1>
+  filter(Q1 == 1, # consent = 1         # <2>
+         Q3 != 3,                       # <3>
+         Q9 == 1 | Q9 == 0 & Q10 == 1   # <4>
+         )
+
+```
+
+1.    Adds a column at the start of the dataframe (`rowID`) of sequential row ids starting at 1.
+2.    Exclude anyone who didn't consent to partake in the survey
+3.    Exclude non-U.S. citizens
+4.    Exclude anyone who failed the two attention checks
+
+This results in `r dim(data_spss)[1]` number of observations in the data set after excluding those who met the exclusion criteria.
+There are still a number of respondents who failed to fully complete the survey.
+These respondents either closed the survey prior to completion or failed to click the submit button at the end of the survey.
+They can be identified in the data set by the `Finished` variable in the data set where `Finished = 1`.
+
+```{r}
+#| label: finished-count
+
+# identify and count the number of partial responses in the data
+data_spss |> 
+  group_by(finished) |> 
+  count()
+
+```
+
+From the code above, I found that there were `125` participants who didn't complete the survey.
+It seemed important to identify the number of incomplete or partial responses in the data set considering subsequent analysis will have to take missing values into consideration.
+I decided to keep partial responses instead of dropping any respondent who didn't fully complete the survey.
+I reasoned that the responses were still validly recorded and because I could only speculate the reasons why so many respondents failed to complete the survey.
 
@@
 data_spss <- raw_spss |>
-  janitor::clean_names() |>
-
-  # decision was made to include only those who fully completed the survey
-  filter(finished==1) |>
-
-  # get rid of superfluous Qualtrics columns
-  # Keep Qualtrics `response_id`
-  dplyr::select(!1:8 & !10:17 & !265) |>
-
-  # put demographic data up front
-  dplyr::relocate(q59:q74, .before = q1) |>
-
-  # rename demographic vars and timing vars and identify lucid vars
+  janitor::clean_names() |>                                       # <1>
+  select(!1:8 & !10:17 & !265) |>                                 # <2>
+  relocate(q59:q74, .before = q1) |>                              # <3>
   dplyr::rename(
@@
     ideolean = q74
-  ) |>
-
-  # put both response ID variables next to each other
-  dplyr::relocate(lucid_rid, .after = response_id) |>
-
-  # set variable labels for embedded lucid vars
-  # set variable labels for select questions
-  labelled::set_variable_labels(
+  ) |>                                                           # <4>
+  relocate(lucid_rid, .after = response_id) |>                   # <5>
+  labelled::set_variable_labels(                                 # <6>
     lucid_age = "Lucid: age",
@@
     q28_4 = "A foreign country will tamper with the votes cast in Maricopa County, Arizona...",
-    q28_5 = "Election officials in Maricopa County, Arizoa will try to discourage some people from voting",
+    q28_5 = "Election officials in Maricopa County, Arizona will try to discourage some people from voting",
     q40_1 = "There will be voter fraud...",
@@
     q40_5 = "Election officials in your community will try to discourage some people from voting",
+
     q41_1 = "Election officials test every machine used in the election to ensure they are secure.",
@@
     q41_6 = "Election staff and volunteers include college students from the community.",
+
     q43_1 = "Election officials ensure that law enforcement officers are present at polling sites.",
@@
     q43_6 = "Election staff and volunteers include college students from the community.",
+
     q44_1 = "Election officials test every machine used in the election to ensure they are secure.",
-    q44_2 = "Election officials conduct audits of ballots after every election to confirm the results were accurate.",
-    q44_3 = "Poll watchers affiliated with the political parties or candidates observe the election.",
-    q44_4 = "The majority of election staff and volunteers consist of military veterans and their family members from the community.",
-    q44_5 = "The majority of election staff and volunteers consist of lawyers from the community.",
+    q44_2 = "The majority of election staff and volunteers consist of military veterans and their family members from the community.",
+    q44_3 = "The majority of election staff and volunteers consist of lawyers from the community.",
+    q44_4 = "Election officials conduct audits of ballots after every election to confirm the results were accurate.",
+    q44_5 = "Poll watchers affiliated with the political parties or candidates observe the election.",
     q44_6 = "The majority of election staff and volunteers consist of college students from the community.",
+
     q46_1 = "Election officials ensure that law enforcement officers are present at polling sites.",
-    q46_2 = "People holding signs or giving out literature in support of a candidate or ballot question.",
-    q46_3 = "Poll watchers affiliated with the political parties or candidates observe the election.",
-    q46_4 = "The majority of election staff and volunteers consist of military veterans and their family members from the community.",
-    q46_5 = "The majority of election staff and volunteers consist of lawyers from the community.",
-    q46_6 = "The majority of election staff and volunteers consist of college students from the community.",
+    q46_2 = "The majority of election staff and volunteers consist of military veterans and their family members from the community.",
+    q46_3 = "The majority of election staff and volunteers consist of lawyers from the community.",
+    q46_4 = "Poll watchers affiliated with the political parties or candidates observe the election.",
+    q46_5 = "The majority of election staff and volunteers consist of college students from the community.",
+    q46_6 = "People holding signs or giving out literature in support of a candidate or ballot question.",
     group = "Experimental condition",
-    qset = "Condition A = question set [q41, q43] ; Condition B = question set [q44, q46]"
-  ) |>
-
-  # filter the data to only include those who consented, U.S. citizens, 
-  # and those who didn't fail the attention check
-  dplyr::filter(q1 == 1, # include only those who consented
-         q3 != 3,        # exclude non-U.S. citizens
-         q9 == 1 | q9 == 0 & q10 == 1 #exclude attn check failures
-         ) |>
-
-  # add a column of ascending sequential row ids starting at 1
-  tibble::rowid_to_column("rowID")
+    qset = "A = question set [q41, q43]; B = question set [q44, q46]"
+  )
 
@@
 
+1.
 The `janitor` R package is used to `clean_names()` which ensures the column names of the dataframe are unique, consist only of the '_' character, numbers, and letters.
 All uppercase column names will be converted to lowercase (e.g., Q1 to q1).
-The `dplyr::select()`, `dplyr::relocate()`, and `dplyr::rename()` functions utilize the dplyr R package to...
-
--   selectively remove superfluous columns that come standard when survey data is downloaded from Qualtrics; 
--   relocate demographic variables (e.g., Q59 to Q74) to a position just before the Q1 column and the Lucid rid ('lucid_rid') to a position just after the Qualtrics Response ID ('response_id');
--   rename specific columns/variables.
-
-In addition, the function `set_variable_labels()` from the `labelled` R package sets the *variable labels* attached to each respective variable[^1].
-Crucially, the raw data is filtered using `dplyr::filter()` so the resulting dataframe only includes survey respondents who...
-
--   Consented to take the survey
--   Is a U.S. citizen
--   Passed either attention check embedded within the survey.
-
-Finally, a column is added at the front of the dataframe ('rowID') which simply adds a column at the start of the dataframe of ascending sequential row ids starting at 1.
-The resulting dataframe (`tbl_df`) consists of 1,388 rows, where each row consists of a valid survey response, and 254 columns/variables.
+2.    The `dplyr::select()` selectively removes superfluous columns that come standard when survey data is downloaded from Qualtrics. 
+2.    Keep Qualtrics `response_id`
+3.    Use `dplyr::relocate()` to relocate demographic variables (e.g., Q59 to Q74) to a position just before the Q1 column
+4.    Use `dplyr::rename()` functions to rename demographic vars and timing vars and identify Lucid variables
+5.    Use `dplyr::relocate()` to put the Lucid rid ('lucid_rid') to a position just after the Qualtrics Response ID ('response_id')
+6.    Use `labelled::set_variable_labels()` to set the *variable labels* attached to each respective variable[^1].
 
@@
   dplyr::select(lucid_age, q2) |> 
-  dplyr::mutate("match" = 
-                  ifelse(as.numeric(lucid_age) == q2, "match", "no match")) |> 
+  dplyr::mutate(
+    "match" = ifelse(as.numeric(lucid_age) == q2, "match", "no match")) |> 
   head(10)
@@
 To resolve this problem, I use `dplyr::mutate()` and `dplyr::case_match()` to re-name the variable column and re-code the values to reflect the correct age and convert the object to a numeric class.
+Admittedly, this was quite tedious.
 
@@
   # rename `q2` to 'age' and recode values
-  dplyr::mutate(age = dplyr::case_match(
+  dplyr::mutate(
+    q2 = dplyr::case_match(
       q2,
@@
     ),
-    .after = q2, # place 'age' after `q2`
     .keep = "unused" # drop `q2` from dataframe
@@
   # set variable label consisting of question text
-  labelled::set_variable_labels(age = "What is your age?")
+  labelled::set_variable_labels(q2 = "What is your age?")
 
@@
 
-It is still possible that the `lucid_age` variable doesn't match the re-coded `age` (formally `q2`) values. In fact, this is the case, as demonstrated by running the code below.
+It is still possible that the `lucid_age` variable doesn't match the re-coded `q2` values. In fact, this is the case, as demonstrated by running the code below.
 
@@
 What results is confirmation that there are a total of 170 discrepancies between the respondent's age as indicated by the embedded Lucid data and the age reported by the respondent in the survey.
-Thus, the age reported by the respondent in the survey will take precedence over the embedded data provided by Lucid[^3].
+The age reported by the respondent in the survey will take precedence over the embedded data provided by Lucid[^3].
 
-[^3]: Note, however, that one of the response options for the question "What is your age?" (Q2) was "90 or older", and one respondent's age reported by Lucid was 92 years old.
+[^3]: Note, however, that one of the response options for the question "What is your age?" (`q2`) was "90 or older", and one respondent's age reported by Lucid was 92 years old.
 Since there was no response code associated with being 92 years of age, the response code `73` was recoded to represent 92.
 In this one case, it was a stroke of luck that no more than one of the survey respondents happened to be 90 years of age or older.
-If there was, however, then there would have been no way to recode the `age` variable to reflect those respondent's actual age *and* convert the variable object to a numeric class.
-This issue isn't insurmountable, of course, but the lesson here is that it seems like best practice is to ensure respondents have to manually enter their age or birth year in the survey rather than choose from a list of options.
+If there was, however, then there would have been no way to recode the `q2` variable to reflect those respondent's actual age *and* convert the variable object to a numeric class.
+This issue isn't insurmountable, of course, but the lesson here is to ensure respondents manually enter their age or birth year in the survey rather than choose from a drop down list of options.
 
@@
 
-# merge (or coalesce) the qset vars that can be merged this merges some vars
-# from the q44 and q46 set into q41 and q43 there was no sig diff found for all
-# but the qset B questions regarding lawyers and students. However these are
-# being coalesced into single question vars anyway since I am able to to still
-# distinguish responses by the grouping var `qset`
+# merge (or coalesce) the qset vars that can be merged. 
+# The following merges vars from the q44 and q46 set into q41 and q43. `qset` A
+# was presented to one half of the respondents, whereas `qset` B was presented
+# to the other half. Because of this, the variable columns in the dataframe for
+# each question in the series contains missing values representing this fact.
+# Below I coalesce the `qset` B question items with `qset` A. The function finds
+# the first non-missing value at each position, allowing me to generate a
+# complete vector that contains the responses to the series of questions from
+# either set. I am able to distinguish between the different question sets since
+# they are still grouped by the `qset` variable.
+
 df <- df |> 
@@
 
-  # assign variable labels to these coalesced variables
+  # add variable labels to coalesced variables
   sjlabelled::var_labels(
@@
     q41.3 = "Partisan Poll watchers observe the election.",
-    q41.4 = "Election staff includes veterans and family",
-    q41.5 = "Election staff includes lawyers",
-    q41.6 = "Election staff includes college students",
+    q41.4 = "Election staff includes/is majority of veterans and family",
+    q41.5 = "Election staff includes/is majority of lawyers",
+    q41.6 = "Election staff includes/is majority of college students",
 
@@
     q43.3 = "Partisan Poll watchers observe the election.",
-    q43.4 = "Election staff includes veterans and family",
-    q43.5 = "Election staff includes lawyers",
-    q43.6 = "Election staff includes college students",
+    q43.4 = "Election staff includes/is majority of veterans and family",
+    q43.5 = "Election staff includes/is majority of lawyers",
+    q43.6 = "Election staff includes/is majority of college students",
 
@@
     q41.3.clps = "Partisan Poll watchers observe the election.",
-    q41.4.clps = "Election staff includes veterans and family",
-    q41.5.clps = "Election staff includes lawyers",
-    q41.6.clps = "Election staff includes college students",
+    q41.4.clps = "Election staff includes/is majority of veterans and family",
+    q41.5.clps = "Election staff includes/is majority of lawyers",
+    q41.6.clps = "Election staff includes/is majority of college students",
 
@@
     q43.3.clps = "Partisan Poll watchers observe the election.",
-    q43.4.clps = "Election staff includes veterans and family",
-    q43.5.clps = "Election staff includes lawyers",
-    q43.6.clps = "Election staff includes college students"
+    q43.4.clps = "Election staff includes/is majority of veterans and family",
+    q43.5.clps = "Election staff includes/is majority of lawyers",
+    q43.6.clps = "Election staff includes/is majority of college students"
   )
@@
 # add dummy variables to dataframe
+# this is to test treatment effects
 df <- df |> 
@@
                 . == 'decrease' ~ 0
-                ), .names = "{.col}.dum"))
-
-```
-
-## Creating a purely numeric dataframe
-
-For whatever reasons, it is sometimes preferred to use a purely numeric dataframe.
-The following code creates a dataframe from the earlier `data_spss` dataframe that removes all value labels from the numeric values of the variables, i.e., drops all the `lbl` from `<dbl+lbl>`.
-
-The following code merely duplicates the source code from an R script located in the project directory, which can be found and viewed [here](https://github.com/isaiahespi/cdce_vets/blob/80e843e8a9fa24d1d7524c76631b709f9f675876/scripts/02-data-numeric.R).
-
-```{r}
-#| label: numeric-data-clean
-
-data2 <- data_spss |>
-  # subset spss data set to omit the display order variables
-  select(!contains("_do_")
-         & !contains("_ado_")
-         & !contains("_click")
-         & !contains("_count")) |>
-  mutate(
-    group = case_when(
-      group == "Treatment" ~ 1,
-      group == "Control" ~ 0),
-    qset = case_when(
-      qset == "A" ~ 1,
-      qset == "B" ~ 0)) |>
-
-  # remove all 'lbl' from all <dbl+lbl> variables, making them all numeric
-  haven::zap_labels() |> 
-  # re-code values for consistent direction with like variables
-  mutate(
-    q8  = case_match(q8, 1 ~ 5, 2 ~ 4, 3 ~3, 4~2, 5 ~ 1),
-    q20 = case_match(q20, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
-    q23 = case_match(q23, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
-    q24 = case_match(q24, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
-    q31 = case_match(q31, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
-    q34 = case_match(q34, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
-    q35 = case_match(q35, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
-    q49 = case_match(q49, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1),
-    q50 = case_match(q50, 1 ~ 4, 2 ~ 3, 3 ~ 2, 4 ~ 1))
+                ), .names = "{.col}.dum")) |> 
+  # add variable labels
+  sjlabelled::var_labels(
+    q41.1.clps.dum = "Election officials test machines",
+    q41.2.clps.dum = "Election officials conduct audits",
+    q41.3.clps.dum = "Partisan Poll watchers observe the election.",
+    q41.4.clps.dum = "Election staff includes/is majority of veterans and family",
+    q41.5.clps.dum = "Election staff includes/is majority of lawyers",
+    q41.6.clps.dum = "Election staff includes/is majority of college students",
+    q43.1.clps.dum = "Election officials test machines",
+    q43.2.clps.dum = "Election officials conduct audits",
+    q43.3.clps.dum = "Partisan Poll watchers observe the election.",
+    q43.4.clps.dum = "Election staff includes/is majority of veterans and family",
+    q43.5.clps.dum = "Election staff includes/is majority of lawyers",
+    q43.6.clps.dum = "Election staff includes/is majority of college students"
+  )
 
@@
 # save df processed data set.
-save(df, file = "data/df-2024-09-11.Rdata")
-write.csv(df, file = "data/df-2024-09-11.csv")
-
-# save the numeric only processed data set.
-save(data2, file = "data/data_numeric_vets_survey-exp-2024-09-11.Rdata")
-write.csv(data2, file = "data/data_numeric_vets_survey-exp-2024-09-11.csv")
+save(df, file = "data/research-paper-df-2024-09-11.Rdata")
+write.csv(df, file = "data/research-paper-df-2024-09-11.csv")
 
@@
 # generate data dictionary
-df_dict <- surveytoolbox::data_dict(df) # I prefer this to the labelled dict
-write.csv(df_dict, file = "codebooks/df_dict.csv")
+df_dictionary <- surveytoolbox::data_dict(df)
+write.csv(df_dictionary, file = "data/df_dictionary.csv")
 
-# remove uneeded dataframes and leave df and df_dict
-rm(data, data_dict_spss, data_spss, data_spss_dict, data2_dict_num, raw_spss, raw_spss_dict)
+# remove uneeded dataframes from global environment ::::::::::::::::::::::::####
+rm(data, data_dict_spss, data_spss, raw_spss, raw_spss_dict, data_labels)
 

### 2024-10-30 src/01-data.R
updated src script

@@ -1,0 +1,536 @@
+# using data exported from Qualtrics on 2024-10-23
+# The most recent (i.e., last) response was recorded 2024-09-18 at 6:40pm (1840)
+# When exporting the data, Qualtrics allows me to recode 'seen but unanswered'
+# questions with code 99. I downloaded the data again just for that because I
+# want to see how many of the missing values in my 2024-09-11 dataset are
+# attributed to people who skipped survey questions.
+
+# load packages ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
+library(tidyverse)
+library(haven)
+library(surveytoolbox)
+library(labelled)
+library(sjlabelled)
+
+# load data ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
+
+# load raw SPSS export (includes display order vars)
+# downloaded on 2024-10-29 at 12:02 PM
+raw_spss <- haven::read_sav("data-raw/VMF_Election_Worker_Recruitment_Survey_with_display_order_20241029_T12.02.sav")
+
+# load raw SPSS export (doesn't include display order vars)
+# downloaded 2024-10-23 at 1:54 PM
+# raw_spss3 <- haven::read_sav(file = "data-raw/VMF_Election_Worker_Recruitment_Survey_2024-10-23_13.54.sav")
+
+# despite being a .sav file imported using `haven::read_sav()`, 
+# the data set is not "haven_labelled"
+# haven::is.labelled(raw_spss)
+
+# create data dictionary of raw SPSS data set ::::::::::::::::::::::::::::::####
+
+# A data dictionary contains metadata about the data. The
+# `labelled::generate_dictionary` function is used to create a data
+# dictionary. (alt. `surveytoolbox::data_dict`)
+# a data frame is loaded into the R environment with the number of
+# observations equal to number of variables in the original data set.
+# NOTE: surveytoolbox::data_dict function is used here because the resulting
+# dataframe can be saved as a .csv
+raw_spss_dict <- raw_spss |> surveytoolbox::data_dict()
+
+# save data dictionary of raw_spss dataset download
+write.csv(raw_spss_dict, file = "data/raw_spss_dict.csv")
+
+# create and save survey codebook ::::::::::::::::::::::::::::::::::::::::::####
+
+# this includes only the survey questions: question number (var), the question
[…]

### 2024-11-02 docs/_tex/index.tex
added files

@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
 \makeatother
-% definitions for citeproc citations
-\NewDocumentCommand\citeproctext{}{}
-\NewDocumentCommand\citeproc{mm}{%
-  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
-\makeatletter
- % allow citations to break across lines
- \let\@cite@ofmt\@firstofone
- % avoid brackets around text for \cite:
- \def\@biblabel#1{}
- \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
-\makeatother
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
- {\begin{list}{}{%
-  \setlength{\itemindent}{0pt}
-  \setlength{\leftmargin}{0pt}
-  \setlength{\parsep}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-   \setlength{\leftmargin}{\cslhangindent}
-   \setlength{\itemindent}{-1\cslhangindent}
-  \fi
-  % set entry spacing
-  \setlength{\itemsep}{#2\baselineskip}}}
- {\end{list}}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 % ---------------------------
+\usepackage{booktabs}
+\usepackage{caption}
+\usepackage{longtable}
+\usepackage{colortbl}
+\usepackage{array}
+\usepackage{anyfontsize}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \makeatletter
@@
 
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
 \usepackage{bookmark}
@@
 \setstretch{2}
-\subsection{Section}\label{section}
+\pagebreak
 
-This is a simple placeholder for the manuscript's main document (Knuth
-1984).
+\subsection{Intro}\label{intro}
 
-\section*{References}\label{bibliography}
-\addcontentsline{toc}{section}{References}
+Here are intro words
 
-\phantomsection\label{refs}
-\begin{CSLReferences}{1}{1}
-\bibitem[\citeproctext]{ref-knuth84}
-Knuth, Donald E. 1984. {``Literate Programming.''} \emph{Comput. J.}
-27(2): 97--111.
-doi:\href{https://doi.org/10.1093/comjnl/27.2.97}{10.1093/comjnl/27.2.97}.
+\pagebreak
 
-\end{CSLReferences}
+\section{Appendix}\label{appendix}
+
+There should be nothing below here
+
+\begin{table}
+
+\caption{\label{tbl-desc-pdf}Description of Sample Demographics}
+
+\centering{
+
+\centering\begingroup\fontsize{8}{10}\selectfont
+
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{20em}rr}
+\toprule
+Name & n & Pct\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Qset}}\\
+\cellcolor{gray!10}{\hspace{1em}A} & \cellcolor{gray!10}{644} & \cellcolor{gray!10}{50.04}\\
+\hspace{1em}B & 643 & 49.96\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Age}}\\
+\cellcolor{gray!10}{\hspace{1em}18-24} & \cellcolor{gray!10}{108} & \cellcolor{gray!10}{8.39}\\
+\hspace{1em}25-34 & 242 & 18.80\\
+\cellcolor{gray!10}{\hspace{1em}35-44} & \cellcolor{gray!10}{254} & \cellcolor{gray!10}{19.74}\\
+\hspace{1em}45-54 & 226 & 17.56\\
+\cellcolor{gray!10}{\hspace{1em}55-64} & \cellcolor{gray!10}{242} & \cellcolor{gray!10}{18.80}\\
+\hspace{1em}65-74 & 148 & 11.50\\
+\cellcolor{gray!10}{\hspace{1em}75-84} & \cellcolor{gray!10}{57} & \cellcolor{gray!10}{4.43}\\
+\hspace{1em}85-92 & 10 & 0.78\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Gender}}\\
+\cellcolor{gray!10}{\hspace{1em}Male} & \cellcolor{gray!10}{598} & \cellcolor{gray!10}{47.01}\\
+\hspace{1em}Female & 658 & 51.73\\
+\cellcolor{gray!10}{\hspace{1em}Other/Refused} & \cellcolor{gray!10}{16} & \cellcolor{gray!10}{1.26}\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Education}}\\
+\hspace{1em}H.S. or less & 362 & 28.46\\
+\cellcolor{gray!10}{\hspace{1em}Some college no degree} & \cellcolor{gray!10}{283} & \cellcolor{gray!10}{22.25}\\
+\hspace{1em}Undergraduate level degree & 461 & 36.24\\
+\cellcolor{gray!10}{\hspace{1em}Graduate level degree} & \cellcolor{gray!10}{166} & \cellcolor{gray!10}{13.05}\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Race}}\\
+\hspace{1em}White or Caucasian & 975 & 76.65\\
+\cellcolor{gray!10}{\hspace{1em}Black or African American} & \cellcolor{gray!10}{164} & \cellcolor{gray!10}{12.89}\\
+\hspace{1em}American Indian & 22 & 1.73\\
+\cellcolor{gray!10}{\hspace{1em}Asian} & \cellcolor{gray!10}{56} & \cellcolor{gray!10}{4.40}\\
+\hspace{1em}Other & 55 & 4.32\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Party ID}}\\
+\cellcolor{gray!10}{\hspace{1em}Republican} & \cellcolor{gray!10}{540} & \cellcolor{gray!10}{42.59}\\
+\hspace{1em}Democrat & 566 & 44.64\\
+\cellcolor{gray!10}{\hspace{1em}Independent} & \cellcolor{gray!10}{162} & \cellcolor{gray!10}{12.78}\\
+\bottomrule
+\end{tabular}}
+\endgroup{}
+
+}
+
+\end{table}%
+
+\textsubscript{Source:
+\href{https://isaiahespi.github.io/rea-paper/index.qmd.html}{Article
+Notebook}}
+
+\begin{table}
+
+\caption{\label{tbl-desc-pdf-2}}
+
+\centering{
+
+\centering\begingroup\fontsize{9}{11}\selectfont
+
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
+\begin{tabular}{lcccc}
+\toprule
+\textbf{Variable} & \textbf{N} & \makecell[c]{\textbf{Overall}\ \ \\N = 1,287} & \makecell[c]{\textbf{A}\ \ \\N = 644} & \makecell[c]{\textbf{B}\ \ \\N = 643}\\
+\midrule
+\cellcolor{gray!10}{\textbf{Age group, in years}} & \cellcolor{gray!10}{1,287} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{}\\
+\hspace{1em}18-24 &  & 108 (8.4\%) & 47 (7.3\%) & 61 (9.5\%)\\
+\cellcolor{gray!10}{\hspace{1em}25-34} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{242 (19\%)} & \cellcolor{gray!10}{117 (18\%)} & \cellcolor{gray!10}{125 (19\%)}\\
+\hspace{1em}35-44 &  & 254 (20\%) & 127 (20\%) & 127 (20\%)\\
+\cellcolor{gray!10}{\hspace{1em}45-54} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{226 (18\%)} & \cellcolor{gray!10}{109 (17\%)} & \cellcolor{gray!10}{117 (18\%)}\\
+\hspace{1em}55-64 &  & 242 (19\%) & 127 (20\%) & 115 (18\%)\\
+\cellcolor{gray!10}{\hspace{1em}65-74} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{148 (11\%)} & \cellcolor{gray!10}{83 (13\%)} & \cellcolor{gray!10}{65 (10\%)}\\
+\hspace{1em}75-84 &  & 57 (4.4\%) & 27 (4.2\%) & 30 (4.7\%)\\
+\cellcolor{gray!10}{\hspace{1em}85-92} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{10 (0.8\%)} & \cellcolor{gray!10}{7 (1.1\%)} & \cellcolor{gray!10}{3 (0.5\%)}\\
+\textbf{Gender reported by respondent} & 1,272 &  &  & \\
+\cellcolor{gray!10}{\hspace{1em}Male} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{598 (47\%)} & \cellcolor{gray!10}{300 (47\%)} & \cellcolor{gray!10}{298 (47\%)}\\
+\hspace{1em}Female &  & 658 (52\%) & 333 (52\%) & 325 (51\%)\\
+\cellcolor{gray!10}{\hspace{1em}Other/Refused} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{16 (1.3\%)} & \cellcolor{gray!10}{4 (0.6\%)} & \cellcolor{gray!10}{12 (1.9\%)}\\
+\textbf{Primary race reported by respondent} & 1,272 &  &  & \\
+\cellcolor{gray!10}{\hspace{1em}White or Caucasian} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{975 (77\%)} & \cellcolor{gray!10}{501 (79\%)} & \cellcolor{gray!10}{474 (75\%)}\\
+\hspace{1em}Black or African American &  & 164 (13\%) & 76 (12\%) & 88 (14\%)\\
+\cellcolor{gray!10}{\hspace{1em}American Indian} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{22 (1.7\%)} & \cellcolor{gray!10}{8 (1.3\%)} & \cellcolor{gray!10}{14 (2.2\%)}\\
+\hspace{1em}Asian &  & 56 (4.4\%) & 24 (3.8\%) & 32 (5.0\%)\\
+\cellcolor{gray!10}{\hspace{1em}Other} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{55 (4.3\%)} & \cellcolor{gray!10}{28 (4.4\%)} & \cellcolor{gray!10}{27 (4.3\%)}\\
+\textbf{Highest level of education completed} & 1,272 &  &  & \\
+\cellcolor{gray!10}{\hspace{1em}H.S. or less} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{362 (28\%)} & \cellcolor{gray!10}{183 (29\%)} & \cellcolor{gray!10}{179 (28\%)}\\
+\hspace{1em}Some college no degree &  & 283 (22\%) & 145 (23\%) & 138 (22\%)\\
+\cellcolor{gray!10}{\hspace{1em}Undergraduate level degree} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{461 (36\%)} & \cellcolor{gray!10}{229 (36\%)} & \cellcolor{gray!10}{232 (37\%)}\\
+\hspace{1em}Graduate level degree &  & 166 (13\%) & 80 (13\%) & 86 (14\%)\\
+\cellcolor{gray!10}{\textbf{partyid\_3cat}} & \cellcolor{gray!10}{1,268} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{}\\
+\hspace{1em}Republican &  & 540 (43\%) & 278 (44\%) & 262 (41\%)\\
+\cellcolor{gray!10}{\hspace{1em}Democrat} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{566 (45\%)} & \cellcolor{gray!10}{277 (44\%)} & \cellcolor{gray!10}{289 (46\%)}\\
+\hspace{1em}Independent &  & 162 (13\%) & 78 (12\%) & 84 (13\%)\\
+\cellcolor{gray!10}{\textbf{Political Ideology}} & \cellcolor{gray!10}{1,267} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{}\\
+\hspace{1em}Extremely Liberal &  & 118 (9.3\%) & 67 (11\%) & 51 (8.0\%)\\
+\cellcolor{gray!10}{\hspace{1em}Liberal} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{177 (14\%)} & \cellcolor{gray!10}{85 (13\%)} & \cellcolor{gray!10}{92 (15\%)}\\
+\hspace{1em}Slightly liberal &  & 97 (7.7\%) & 48 (7.6\%) & 49 (7.7\%)\\
+\cellcolor{gray!10}{\hspace{1em}Moderate: middle of the road} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{365 (29\%)} & \cellcolor{gray!10}{182 (29\%)} & \cellcolor{gray!10}{183 (29\%)}\\
+\hspace{1em}Slightly conservative &  & 107 (8.4\%) & 45 (7.1\%) & 62 (9.8\%)\\
+\cellcolor{gray!10}{\hspace{1em}Conservative} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{189 (15\%)} & \cellcolor{gray!10}{98 (15\%)} & \cellcolor{gray!10}{91 (14\%)}\\
+\hspace{1em}Extremely conservative &  & 116 (9.2\%) & 62 (9.8\%) & 54 (8.5\%)\\
+\cellcolor{gray!10}{\hspace{1em}Haven't thought much about this} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{98 (7.7\%)} & \cellcolor{gray!10}{46 (7.3\%)} & \cellcolor{gray!10}{52 (8.2\%)}\\
+\textbf{Political Ideology, lean} & 98 &  &  & \\
+\cellcolor{gray!10}{\hspace{1em}Liberal} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{11 (11\%)} & \cellcolor{gray!10}{6 (13\%)} & \cellcolor{gray!10}{5 (9.6\%)}\\
+\hspace{1em}Conservative &  & 19 (19\%) & 8 (17\%) & 11 (21\%)\\
+\cellcolor{gray!10}{\hspace{1em}None of these} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{68 (69\%)} & \cellcolor{gray!10}{32 (70\%)} & \cellcolor{gray!10}{36 (69\%)}\\
+\textbf{Turnout in 2020} & 1,272 &  &  & \\
+\cellcolor{gray!10}{\hspace{1em}I'm sure I didn't vote} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{185 (15\%)} & \cellcolor{gray!10}{93 (15\%)} & \cellcolor{gray!10}{92 (14\%)}\\
+\hspace{1em}I don't think I voted &  & 64 (5.0\%) & 35 (5.5\%) & 29 (4.6\%)\\
+\cellcolor{gray!10}{\hspace{1em}I think I voted} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{43 (3.4\%)} & \cellcolor{gray!10}{19 (3.0\%)} & \cellcolor{gray!10}{24 (3.8\%)}\\
+\hspace{1em}Yes, I'm sure I voted &  & 920 (72\%) & 463 (73\%) & 457 (72\%)\\
+\cellcolor{gray!10}{\hspace{1em}I was not eligible to vote} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{60 (4.7\%)} & \cellcolor{gray!10}{27 (4.2\%)} & \cellcolor{gray!10}{33 (5.2\%)}\\
+\textbf{Vote Choice 2020} & 1,025 &  &  & \\
+\cellcolor{gray!10}{\hspace{1em}Donald Trump} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{439 (43\%)} & \cellcolor{gray!10}{230 (45\%)} & \cellcolor{gray!10}{209 (41\%)}\\
+\hspace{1em}Joe Biden &  & 527 (51\%) & 257 (50\%) & 270 (53\%)\\
+\cellcolor{gray!10}{\hspace{1em}Other} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{59 (5.8\%)} & \cellcolor{gray!10}{28 (5.4\%)} & \cellcolor{gray!10}{31 (6.1\%)}\\
+\textbf{Vote Intent 2024} & 1,270 &  &  & \\
+\cellcolor{gray!10}{\hspace{1em}Yes} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{1,036 (82\%)} & \cellcolor{gray!10}{518 (82\%)} & \cellcolor{gray!10}{518 (82\%)}\\
+\hspace{1em}No &  & 111 (8.7\%) & 49 (7.7\%) & 62 (9.8\%)\\
+\cellcolor{gray!10}{\hspace{1em}Undecided} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{123 (9.7\%)} & \cellcolor{gray!10}{68 (11\%)} & \cellcolor{gray!10}{55 (8.7\%)}\\
+\textbf{Prior service in the Armed Forces} & 1,272 &  &  & \\
+\cellcolor{gray!10}{\hspace{1em}Yes} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{121 (9.5\%)} & \cellcolor{gray!10}{61 (9.6\%)} & \cellcolor{gray!10}{60 (9.4\%)}\\
+\hspace{1em}No &  & 1,151 (90\%) & 576 (90\%) & 575 (91\%)\\
+\cellcolor{gray!10}{\textbf{Currently serving in the Armed Forces}} & \cellcolor{gray!10}{121} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{}\\
+\hspace{1em}Yes &  & 15 (12\%) & 5 (8.2\%) & 10 (17\%)\\
+\cellcolor{gray!10}{\hspace{1em}No} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{106 (88\%)} & \cellcolor{gray!10}{56 (92\%)} & \cellcolor{gray!10}{50 (83\%)}\\
+\textbf{Member of immediate family served or is currently serving} & 1,272 &  &  & \\
+\cellcolor{gray!10}{\hspace{1em}Yes} & \cellcolor{gray!10}{} & \cellcolor{gray!10}{439 (35\%)} & \cellcolor{gray!10}{212 (33\%)} & \cellcolor{gray!10}{227 (36\%)}\\
+\hspace{1em}No &  & 833 (65\%) & 425 (67\%) & 408 (64\%)\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
+\end{tabular}}
+\endgroup{}
+
+}
+
+\end{table}%
+
+\textsubscript{Source:
+\href{https://isaiahespi.github.io/rea-paper/index.qmd.html}{Article
+Notebook}}
 

### 2024-11-02 index.qmd
updated src script
added files

@@
 
-## Section
-This is a simple placeholder for the manuscript's main document [@knuth84].
+```{r}
+#| label: setup
+#| include: false
+
+# load packages
+library(tidyverse)
+
+# load data
+load("data/research-paper-data-20241029.Rdata")
+
+# load data dictionary/codebook
+codebook <- read.csv("data/survey_codebook.csv")
+data_dict <- read.csv("data/data_dictionary.csv")
+
+# also load the raw data dict for comparison
+raw_spss_dict <- read.csv("data/raw_spss_dict.csv")
+
+```
+
+```{r}
+#| label: fns
+#| include: false
+
+source(here::here('src', 'funs.R'))
+
+```
+
+\pagebreak
+
+## Intro
+
+Here are intro words
+
+\pagebreak
+
+# Appendix {.appendix}
+
+::: {.content-visible when-format="html" unless-format="pdf"}
+
+```{r}
+#| label: tbl-desc
+#| tbl-cap: "Description of Sample Demographics"
+#| tbl-cap-location: top
+
+# quick, informative, easy table of sample demographics w/ some other questions.
+tbl.desc <- data |>  
+  labelled::set_variable_labels(
+    age_cat = "Age group, in years"
+  ) |> 
+  gtsummary::tbl_summary(
+    by = qset,
+    include = c(
+    qset,
+    age_cat, 
+    gender_3cat, 
+    race, 
+    educ_4cat, 
+    partyid_3cat,
+    ideo,
+    ideolean,
+    voted2020,
+    choice2020, 
+    voteintent,
+    milserv1,
+    milserv2,
+    milservfam),
+    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"),
+    type = list(milserv1 ~ "categorical",
+
+                milserv2 ~ "categorical",
+                milservfam ~"categorical"), 
+    missing = "no") |> 
+  gtsummary::add_n() |> 
+  gtsummary::add_overall() |> 
+  gtsummary::modify_header(label = "**Variable**") |> 
+  gtsummary::bold_labels()
+
+gtsummary::as_gt(tbl.desc) |>  
+  gt::tab_footnote(
+    footnote = "'true' Independents do not identify nor 'lean' toward either political party",
+    placement = "left"
+    ) |>  
+  gt::cols_align(align = 'left', columns = everything()) |> 
+  gt::tab_options(
+    table.font.size = "small",
+    data_row.padding = gt::px(1)
+  )
+
+```
+
+:::
+
+There should be nothing below here
+
+::: {.content-hidden unless-format="pdf"}
+
+```{r}
+#| label: tbl-desc-pdf
+#| tbl-cap: "Description of Sample Demographics"
+#| tbl-cap-location: top
+
+frqs <- data |> 
+  select(qset, age_cat, gender_3cat, educ_4cat, race, partyid_3cat) |>
+  map(count_prop)
+
+demog_df <- purrr::reduce(frqs, dplyr::full_join)
+
+kableExtra::kbl(demog_df,
+                booktabs = T, 
+                digits = 2,
+                col.names = c("Name", "n", "Pct")) |> 
+  kableExtra::pack_rows("Qset", 1, 2) |> 
+  kableExtra::pack_rows("Age", 3, 10) |> 
+  kableExtra::pack_rows("Gender", 11, 13) |> 
+  kableExtra::pack_rows("Education", 14, 17) |> 
+  kableExtra::pack_rows("Race", 18, 22) |> 
+  kableExtra::pack_rows("Party ID", 23, 25) |> 
+  kableExtra::kable_styling(
+    latex_options = c("striped", "scale_down"),
+    full_width = F,
+    font_size = 8) |> 
+  kableExtra::column_spec(1, width = "20em")
+
+```
+
+```{r}
+#| label: tbl-desc-pdf-2
+
+tbl.desc <- data |> 
+  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99"))) |> 
+  labelled::set_variable_labels(
+    age_cat = "Age group, in years",
+    gender_3cat = "Gender",
+    race = "Race",
+    educ_4cat = "Highest level of education completed",
+    milserv1 = "Prior service in the Armed Forces",
+    milserv2 = "Currently serving in the Armed Forces",
+    milservfam = "Member of immediate family served or is currently serving",
+    voted2020 = "Turnout in 2020",
+    choice2020 = "Vote Choice 2020",
+    voteintent = "Vote Intent 2024",
+    ideo = "Political Ideology",
+    ideolean = "Political Ideology, lean",
+    partyid_3cat = "Party ID"
+  ) |>
+  gtsummary::tbl_summary(
+    by = qset,
+    include = c(
+      age_cat,
+      gender_3cat,
+      race,
+      educ_4cat,
+      partyid_3cat,
+      ideo,
+      ideolean,
+      voted2020,
+      choice2020,
+      voteintent,
+      milserv1,
+      milserv2,
+      milservfam
+    ),
+    statistic = list(gtsummary::all_categorical() ~ "{n} ({p}%)"),
+    type = list(
+      milserv1 ~ "categorical",
+
+      milserv2 ~ "categorical",
+      milservfam ~ "categorical"
+    ),
+    missing = "no"
+  ) |>
+  gtsummary::add_n() |>
+  gtsummary::add_overall() |>
+  gtsummary::modify_header(label = "**Variable**") |>
+  gtsummary::bold_labels()
+
+gtsummary::as_kable_extra(
+  tbl.desc, 
+  booktabs = T,
+  digits = 2,
+  addtl_fmt = T,
+  linesep = ""
+) |> 
+  kableExtra::kable_styling(
+    latex_options = c("striped", "scale_down"),
+    font_size = 9)
+
+```
+
+:::

### 2024-11-02 notebooks/01-data-import-clean-process.qmd
added files

@@
 
-This document describes and executes the cleaning and processing of the survey data set downloaded from Qualtrics on 2024-09-11 at 11:39AM.
-Currently, this notebook is mainly to describe and explain the process undertaken in R to import, clean, wrangle, and transform the data set for later analysis.
-To see the process without all my explanatory text, see the relevant R script viewed [here](https://github.com/isaiahespi/cdce_vets/blob/80e843e8a9fa24d1d7524c76631b709f9f675876/scripts/01-data.R).
+This document describes and executes the cleaning and processing of the survey data set downloaded from Qualtrics on 2024-10-23.
+Currently, this notebook is mainly to describe and explain the process undertaken in R to import, clean, wrangle, transform, and process the data set for later analysis.
+To see the process without all my explanatory text, see the relevant R script viewed [here](https://github.com/isaiahespi/rea-paper/blob/0bd7138259d244e9a046828fdcf09f2a33837b95/src/01-data.R).
 
@@
 
-# load raw SPSS export that includes display order vars
-# downloaded 2024-09-11 at 11:38 AM
-raw_spss <- haven::read_sav(file = "data-raw/vets_spss_do_2024-09-11_11.38.sav")
+# load raw SPSS export (includes display order vars)
+# downloaded on 2024-10-29 at 12:02 PM
+raw_spss <- haven::read_sav("data-raw/VMF_Election_Worker_Recruitment_Survey_with_display_order_20241029_T12.02.sav")
 
@@
 
-## Create data dictionary/codebook
+## Create data dictionary and Survey Codebook
 
@@
 write.csv(raw_spss_dict, file = "data/raw_spss_dict.csv")
+
+```
+
+The data dictionary is the same as a codebook, but I also wanted to have a codebook that contained only the survey questions, variable labels (i.e., question text), responses (value labels), and associated values.
+So the saved `codebook` contains only the survey questions and the two grouping variables (`qset` and `group`).
+
+```{r}
+#| label: survey_codebook
+
+# create and save survey codebook
+
+# this includes only the survey questions: question number (var), the question
+# text (label_var), the value labels (label_val), and the numeric codes (value)
+codebook <- raw_spss |> 
+  janitor::clean_names() |> 
+  # get rid of superfluous Qualtrics columns
+  # Keep Qualtrics `response_id`
+  select(!1:8 & !10:17 & !265) |>
+  # subset spss data set to omit the display order variables
+  select(!contains("_do_")
+         & !contains("_ado_")
+         & !contains("_click")
+         & !contains("_count")) |>
+  select(contains("q"), group) |>
+  surveytoolbox::data_dict()
+
+# save codebook as .csv file in data/ directory
+write.csv(codebook, file = "data/survey_codebook.csv")
 

### 2024-11-02 notebooks/02-tables.qmd
added files

--- 2024-10-16 notebooks/02-crosstables.qmd
@@
 ---
-title: Crosstabulations
+title: Tables
 author: Isaiah
@@
 
+```{r}
+#| label: setup
+#| include: false
+
+# load packages
+library(tidyverse)
+library(datawizard)
+
+# load data
+load("data/research-paper-data-20241029.Rdata")
+
+# load data dictionary/codebook
+codebook <- read.csv("data/survey_codebook.csv")
+data_dict <- read.csv("data/data_dictionary.csv")
+
+# also load the raw data dict for comparison
+raw_spss_dict <- read.csv("data/raw_spss_dict.csv")
+
+```
+
+## Descriptive table
+```{r}
+#| label: tbl-1
+#| tbl-cap: "Description of Sample Demographics"
+#| tbl-cap-location: top
+
+# quick, informative, easy table of sample demographics w/ some other questions.
+tbl1 <- data |>  
+  labelled::set_variable_labels(
+    age_cat = "Age group, in years"
+  ) |> 
+  gtsummary::tbl_summary(
+    by = qset,
+    include = c(
+    qset,
+    age_cat, 
+    gender_3cat, 
+    race, 
+    educ_4cat, 
+    partyid_3cat,
+    ideo,
+    ideolean,
+    voted2020,
+    choice2020, 
+    voteintent,
+    milserv1,
+    milserv2,
+    milservfam),
+    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"),
+    type = list(milserv1 ~ "categorical",
+
+                milserv2 ~ "categorical",
+                milservfam ~"categorical"), 
+    missing = "no") |> 
+  gtsummary::add_n() |> 
+  gtsummary::add_overall() |> 
+  gtsummary::modify_header(label = "**Variable**") |> 
+  gtsummary::bold_labels()
+
+gtsummary::as_gt(tbl1) |>  
+  gt::tab_footnote(
+    footnote = "'true' Independents do not identify nor 'lean' toward either political party",
+    placement = "left"
+    ) |>  
+  gt::cols_align(align = 'left', columns = everything()) |> 
+  gt::tab_options(
+    table.font.size = "small",
+    data_row.padding = gt::px(1)
+  )
+
+```
+
+```{r}
+#| label: tbl-1-pdf
+#| tbl-cap: "Description of Sample Demographics"
+#| tbl-cap-location: top
+
+# compute counts and proportions
+count_prop <- function(x, drop_na = TRUE, sort = FALSE){
+  p <- data |>  
+    count({{ x }})
+  if (drop_na == FALSE){
+    p |> 
+      mutate(prop = n/sum(n))
+  } else {
+    p |> drop_na() |> 
+      mutate(prop = n/sum(n)*100)
+  }
+}
+
+frqs <- data |> 
+  select(qset, age_cat, gender_3cat, educ_4cat, race, partyid_3cat) |>
+  map(count_prop)
+
+demog_df <- purrr::reduce(frqs, dplyr::full_join)
+
+kableExtra::kbl(demog_df,
+                booktabs = T, 
+                digits = 2,
+                col.names = c("Name", "n", "Pct")) |> 
+  kableExtra::pack_rows("Qset", 1, 2) |> 
+  kableExtra::pack_rows("Age", 3, 10) |> 
+  kableExtra::pack_rows("Gender", 11, 13) |> 
+  kableExtra::pack_rows("Education", 14, 17) |> 
+  kableExtra::pack_rows("Race", 18, 22) |> 
+  kableExtra::pack_rows("Party ID", 23, 25) |> 
+  kableExtra::kable_styling(
+    latex_options = c("striped", "scale_down"),
+    full_width = F,
+    font_size = 8) |> 
+  kableExtra::column_spec(1, width = "20em")
+
+```
 ## Crosstables

### 2024-11-02 src/01-data.R

@@ -408,9 +408,15 @@ data <- data |>
       "Voted" = "Yes, I'm sure I voted",
       "Didn't vote" = c("I'm sure I didn't vote", "I don't think I voted"),
       "Unsure/Ineligible" = c("I think I voted","I was not eligible to vote")
-      )) |>
+      )) |> 
+  mutate(ideo_3cat = pewmethods::fct_case_when(
+    ideo == "Extremely Liberal" | ideo == "Liberal" | ideo == "Slightly liberal" ~ "Liberal",
+    ideo == "Extremely conservative" | ideo == "Conservative" | ideo == "Slightly conservative" ~ "Conservative",
+    TRUE ~ ideo
+  )) |> 
   labelled::set_variable_labels(
-    voted2020.clps = "Turnout 2020"
+    voted2020.clps = "Turnout 2020",
+    ideo_3cat = "Ideology, 4 categories"
   )
 
 
@@ -433,7 +439,35 @@ data <- data |>
   ) |> 
   dplyr::relocate(
     voted2020.clps, .after = voted2020
+  ) |> 
+  dplyr::relocate(
+    ideo_3cat, .before = ideo
   )
+
+# create dummy variables where 1 = 'Increase in confidence' and 0 = "No increase
+# in confidence".
+# add dummy variables to dataframe
+data <- data |>
+  mutate(across(
+    c(q41.1:q43.6),
+    ~ dplyr::case_when(
+      . == "Decrease confidence a lot" ~ "Decrease",
+      . == "Decrease confidence somewhat" ~ "Decrease",
+      . == "No impact on confidence" ~ "No impact",
+      . == "Increase confidence somewhat" ~ "Increase",
+      . == "Increase confidence a lot" ~ "Increase",
+      .default = as.character(.)), .names = "{.col}.clps")) |> 
+  mutate(across(c(q41.1.clps:q43.6.clps), 
+                ~ dplyr::case_when(
+                . == "Increase" ~ 1, 
+                . == "No impact" ~ 0,
+                . == 'Decrease' ~ 0),
+                .names = "{.col}.dum")) |> 
+  mutate(across(c(q41.1.clps, q41.2.clps, q41.3.clps, q41.4.clps,
+                  q41.5.clps, q41.6.clps, q43.1.clps, q43.2.clps,
+                  q43.3.clps, q43.4.clps, q43.5.clps, q43.6.clps),
+                ~ haven::as_factor(.)))
+
 
[…]

### 2024-11-19 index.qmd
commit of index with includes much of the initial draft of the research paper

@@
 date: "2024-10-16"
+crossref:
+  custom: 
+    - key: hyp
+      kind: float
+      reference-prefix: H
+      latex-env: hypothesis # required for PDF format
+
 ---
@@
 
-Here are intro words
+Election administration officials make efforts to sustain public trust and confidence in the fairness and accuracy of elections, and attempt to boost such confidence where ever it may be deprived.
+Concerns for safety have developed among election staff and voters in more recent elections.
+Regular measures are taken to enhance the *trustworthiness*[^1] of the electoral process through practices meant to improve the conduct, transparency, or overall administration of elections in the United States.
+
+Although election officials undertake great efforts to enhance the trustworthiness of election administration, public *trust* in elections is a psychological construct influenced by many things outside of election official control such as partisanship or elite rhetoric [@hooghe2018; @sances2015].
+Moreover, a person's evaluation of the election in hindsight is often influenced by the election outcome itself [@daniller2019 ;@stewart2022].
+Thus, measures taken by election officials can be undermined, trivialized, or made irrelevant depending on how one feels after the election results have come out.
+
+Such volatile attitudes and evaluations post-election can leave a lasting impression that election officials must contend with upon the next election cycle [@levendusky2024; @bowler2024].
+For instance, we have witnessed many people's outright refusal to accept the 2020 U.S.
+election results as legitimate despite consistent review of the evidence confirming the results as fair and accurate.
+Such a case demonstrates that public trust in elections is, at best, only partial to trustworthiness of election administration in the United States[^2].
+Or in other words, there is only so much that election officials can do to sustain or improve public trust in election administration.
+
+Even though election officials can do a lot to secure election integrity, especially under intense scrutiny, there's not much they can do to cement public confidence after election night passes.
+At best, election officials can ease public anxieties prior to election night.
+As mentioned, this usually consists of enhancing procedures and practices and adapting to advancing election technology.
+
+One point of contention that election officials have faced in the past regard evaluation of election workers.
+Previous literature has focused on how voter interaction with election workers [@claassen2008], or the voter experience generally [@atkeson2007], influences evaluations of election administration.
+As such, election worker competency has been examined as a factor significant to evaluations of performance of elections [@hall2007; @hall2009].
+However, considering that individual perceptions and preconceived notions play a huge role in cognition [@cikara2014; @vanbavel2021], it is reasonable to expect that the group an election worker hails from would be an important influence upon the voter's perception or evaluation of their own experience as well as subsequent evaluations of the electoral process.
+Supposing such is the case, we can expect that information about *who* (i.e., which groups) election officials are targeting in publicized recruitment efforts would lessen particular election anxieties.
+That is to say, it is reasonable to expect that telling people *who* will be working as election staff and volunteers would ease election anxieties, therefore improve confidence that the election will be conducted fairly, accurately, and safe for all involved.
+
+In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would ease election anxieties (e.g., concern for electoral fairness and accuracy, as well as concerns for voter safety).
+Results of the survey experiment support the hypothesis that emphasizing veterans as the target of election worker recruitment efforts eases pre-elections anxieties to an extent.
+In particular, among those who read the treatment vignette, confidence that the elections would be fair and accurate was higher in comparison.
+In addition, expectations of electoral fraud were lower, as were concerns for voter safety compared to those who read a control vignette.
+Notable is that there was a significant increase in confidence, and lower expectations of fraud, among those who believe that the 2020 election was illegitimate.
+
+-   when distinguished by partisanship...
+-   moreover, broken down by other demographic variables such as race, gender, education, etc.
+-   holding these factors constant demonstrates a [increased/decreased] likelihood that a respondent's confidence would likely [increase/decrease], expectations of fraud would likely [increase/decrease], and concerns for safety would lessen among those in the treatment group compared to those in the control.
+These results allow us to attribute the differences to the treatment stimulus, namely, the prospect of having veterans serve as election staff or volunteers.
+
+[^1]: I adopt a distinction made between *trustworthiness* and *trust* in elections [@stewart2022].
+The "*worthiness*" of one's trust in the conduct and administration of elections is based on the extent that outcomes of an election reasonably follow the rules prescribed and can be adjudicated as such.
+"If the process is conducted fairly and competently, and the results are determined by the actions of voters...we can call this a trustworthy election" [@stewart2022, 237].
+*Trustworthiness* is distinguished from *trust* as a psychological construct, "...the conclusion reached by the public about the functioning of the process" [@stewart2022, 237].
+To put in other terms, trustworthiness is built by the structure, procedures, and practices of the institution, in this case election administration.
+The public's trust in elections, however, is amendable to an indefinite number of factors that may be seemingly unrelated to the formal procedures of election administration.
+To illustrate, my car is trustworthy because I've known it to function quite well as a car should; it passes whatever criteria upon inspection, its sufficiently fueled, and is in generally good working order.
+I have every reason to deem it worthy of my trust.
+However, I don't trust my car because I am sure it is haunted.
+
+[^2]: It is important to point out here that election administration is just one institution that interacts with many other institutions and processes which form the electoral system *writ large* [@stewart2022].
+The way in which I discuss the institution of election administration, as well as the way in which I discuss and distinguish public trust in elections from broader conceptions of public trust, is borrowed substantively from @stewart2022's conceptual framework of the same.
+Distinctions between *trust* and *trustworthiness* and the notion of election administration as an institution are already apparent inspirations convenient for situating the theory of this research inquiry.
+
+## Background: Election Administration and Public Confidence
+
+Election officials have tried hard to inspire confidence in the administration and conduct of elections by improving the degree to which elections are trustworthy.
+Development and implementation of procedures such as post-election auditing of ballots and logic-and-accuracy testing of ballot tabulation equipment are prominent examples adding to the long history of efforts to enhance the trustworthiness of election administration in the United States.
+
+Prior to the year 2000, one of the main issues facing election administration was recruiting enough election workers to volunteer at the polls (i.e., poll workers) [@maidenberg1996].
+Election worker recruitment is still much of an issue in the current era as it was then, perhaps worse [@ferrer2024].
+In addition to ensuring election admin offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections.
+In particular, voting technology [@herrnson2009] and election worker competence was a of interest in election studies [@classen2008; @hall2009; @hall2007].
+Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007].
+These somewhat generic issues of election worker staffing, competence, and voting technology were likely mere stepping stones leading to more intense election administration issues.
+
+In 2024, election officials made valiant efforts to boost public confidence in the fairness and accuracy of elections within an intensified political climate that appeared quite hostile to election officials [@edlin2024; @brennancenterforjustice2024].
+Although polling around the time indicated that most people thought that U.S.
+elections would be run at least somewhat well [@nadeem2024], many election officials nationwide took efforts to assuage the worry of those most skeptical.
+Enhancing trustworthiness in election administration is a regular duty for election officials, but baseless allegations regarding the fairness and accuracy of the 2020 election loomed ever larger, and the fear of political violence became prominent for both election officials and the public.
+Safety concerns for election staff, volunteers, and voters alike only added to, and perhaps exacerbated, public concern for the integrity of election administration in the United States.
+Especially as the steady increase in election official turnover seems to be increasing even more [@ferrer2024].
+
+Election anxiety was high in the lead up to the 2024 elections in the United States.
+Concerns for voter safety and the prospect of political violence remained prescient and compelled many local officials to prepare for the worst [@edlin2024; @doubek2024].
+Election officials in Washoe County, Nevada, installed panic buttons for election staff that would alert a monitoring center to summon law enforcement [@lincoln2024].
+Nevada also passed a law making it a felony to harass, threaten, or intimidate election workers [@nevadasecretaryofstate2023].
+Leading up to election day, news outlets reported that election work had become a seemingly dangerous job [@wire2024].
+A Brennan Center survey report stated that, "...large numbers of election officials report having experienced threats, abuse, or harassment for doing their jobs" [@edlin2024].
+Concerns over the fairness of elections and accuracy of vote counts intensified, heightening concerns over the prospect of political violence and, in turn, engendered increased worry for the safety of voters and election workers alike.
+
+Suffice to say, pre-election anxiety consists of more than concerns over fairness and accuracy of vote counts in light of added safety concerns.
+It is not hard to recognize that increased tension in the pre-election period makes for a volatile political environment.
+
+## Literature Reivew
+
+Assessing the public's *trust* in elections has not been straightforward.
+Inquiry into public trust in elections has been approached by scholars of political science in many different ways [@cook2005], often distinguishable by the scope of the research question and more or less constrained by the particular conception of public trust.
+Quite often, trust in election administration is conflated with trust in government writ large, government legitimacy, government or system responsiveness, or even satisfaction with democracy [@daniller2019].
+At this level, not only is the level of public trust in elections sometimes vague, but there's little consideration over the difference between such attitudes pre-election and post-election.
+In contrast, a considerable amount of research tends to conceive of public trust in accordance with the institution in question [@atkeson2007; @hooghe2018].
+
+Election administration is just one part of the larger set of institutions which form the electoral system.
+As such, the performance of the institution along with the rest "...lends credibility to the outcome of an election: whether it is considered by citizens and the international community to be fair and legitimate." [@stewart2022, 236].
+
+Trust and confidence in the conduct of elections concerns aspects of elections that fall squarely within the institution of election administration.
+At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended).
+Or in other words, public trust is ascertained by the extent the public perceives the institution of election administration as trustworthy.
+
+Intuitively, enhancing public trust in elections would best be accomplished by enhancing the *trustworthiness* of the institution, i.e., consistently doing the things that election officials already regularly do come election time.
+However, trust and confidence in elections has become ever more precarious over the last few election cycles.
+Especially considering public polling data since 2000 shows that confidence that votes were, or would be, counted as intended was in a consistent decline despite efforts towards bolstering election integrity and trustworthiness [@sances2015].
+This is even more pronounced considering the role that partisanship has had on such confidence over accuracy of vote count [@sances2015; @stewart2022].
+
+There's also stark difference in public trust before the election has occurred compared to after, a phenomenon referred to as the "winner-loser gap"; the "winners" are those who supported the winning candidate and the "losers" are those who supported the losing candidate.
+Much research has been dedicated to analyzing the sentiment of electoral winners vs losers, and vice versa [@nadeau1993; @daniller2019].
+Opinions of electoral trust gathered after the election has occurred are limited considering the well-recognized impact that the electoral outcome itself has on feelings of public trust in elections [@daniller2019].
+
+As such, it is questionable whether we can characterize public trust in the pre-election period as the same trust after the election results have come out[^3].
+The former is *anticipatory*---i.e., the kind that is more or less anxious given the uncertainties surrounding the election.
+The latter is *evaluative*---a judgement discerned empirically in hindsight after the election event has occurred.
+The evaluative form of trust lends to inquiries interested in public opinion on regime legitimacy, satisfaction with democracy, and perceived responsiveness [@daniller2019].
+This study focuses primarily on that *anticipatory* kind of trust and confidence, which speaks more to electoral anxieties over the institution of election administration.
+Not to mention that by definition, one feels anxiety over impending uncertainties located in the future[^4].
+
+[^3]: There's little that could justify a conceptual distinction between public trust pre-election and public trust post-election.
+The temporal element renders the difference between pre- and post-election operative rather than conceptual.
+
+[^4]: Note that *anxiety* is taken to be the inverse of *trust and confidence*, as in, one who is less confident in this or that is thereby more anxious over the matter in question.
+As such, anxiety may equivalently be discussed as trust/confidence without issue except for framing of said discussion.
+Electoral anxiety is used in place of electoral trust/confidence simply to emphasize the anticipatory nature of the attitudes in question.
+
+The primary interest of this study concerns *election anxieties*, which is distinguished into two categories: fairness and accuracy, and voter safety.
+Of course, the direction of electoral outcomes are a particular source of electoral anxiety, but only the election outcome itself can resolve any nail-biting stress over its anticipated direction.
+In contrast, the anxieties of interest here are able to be relaxed to some extent prior to the election given some intervention.
+
+Interventions aimed at improving public trust, or rather, aimed at easing election anxieties may not be within the usual repertoire election officials draw upon.
+Regardless of the measures taken by election officials to boost public confidence in the *trustworthiness* of election administration (e.g., conducting audits, testing election machines), public *trust* and confidence in elections more generally is apt to shift dramatically post-election based on factors such as partisanship, elite rhetoric, particular state policies, and more [@nadeau1993; @carter2024; @coll2024a].
+Moreover, prior research has found that evaluation of election workers themselves are an important factor when it comes to levels of public confidence in the electoral process [@hall2007; @hall2009; @classen2008].
+Such studies focused on the quality of the voter experience with reference to the interaction between voter and election worker.
+
+Beyond the general competence of election workers, however, the quality of the voter experience may be influenced merely by impressions about *who* comprises election staff and volunteers.
+Political and other social science researchers have recognized for some time the power that group identity can have over attitudes and perception [@xiao2016; @xiao2012; @vanbavel2021].
+As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve trust and confidence in election administration, i.e., ease election anxieties.
+It was hypothesized that information on recruitment efforts targeting military veterans to work as election staff would ease election anxieties.
+The next section elaborates further on why military veterans are of particular interest.
+
+## Why Veterans
+
+Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work.
+Staffing issues have been an issue since at least the 1990s [@maidenberg1996; @ferrer2024].
+In 2020, such efforts were made far more difficult by the COVID-19 pandemic [@mena2020; @abbate2020a].
+Sure, it makes sense to recruit veterans, but no more than any other group.
+After all, ensuring election offices are adequately staffed is everyone's problem.
+So there's no special reason to target veterans for recruitment above other groups.
+Indeed, there's no reason to discriminate recruitment efforts at all if the point is purely to fill staffing vacancies.
+However the interest in veterans as a special group to consider arose in light of increased and sudden efforts to recruit veterans into election work.
+
+The reason why veterans arose as a special subset of the population to consider for this inquiry is because there was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021.
+After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterants2022; @nflfootballoperations2022].
+Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts[^4] [@powerthepolls2020; @herndon2020].
+Generally, however, recruitment efforts cast a wide net, indiscriminate of who applies [@ross2020; @conde2020].
+Recruitment efforts in 2022 targeted young students, lawyers, and military veterans [@wang2022].
+
+One can speculate that the motivation to associate military veterans with civic engagement and democracy may be intended to counter negative perceptions and impressions given by the proportion of veteran service members arrested for taking part in the events on January 6th [@milton2021; @loewenson2023; @jensen2022a].
+Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results[^5] (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024].
+This is in addition to a strengthened association portrayed in media outlets between military veterans and militias [@steinhauer2020].
+Although such media output reeks of the contemporary political context, prior research has substantiated such a connection between veterans and militia groups.
+@cooter2024 notes from her 3-year ethnographic fieldwork among Michigan militia members that, "...approximately 40% of militia leaders and 30% of members had previous military experience.
+Most of these veterans actively sought out such groups, as opposed to being recruited by them" [-@cooter2024; see also @cooter2013].
+Thus, countering such associations by promoting a different image of veterans to the mass public and veterans alike seems like a reasonable motivation.
+Yet such speculation is just that.
+
+That being said, the general public perception, attitudes, or even stereotypes about military veterans are significant to consider.
+Although military recruitment shows a downward trend as of late, public perception of veterans are overwhelmingly positive [@kleykamp2023].
+Veterans are a particularly potent group where mention of veteran status seems to have a positive, calming, or nullifying effect on attitudes.
+For instance, recent research shows that, during his campaign in the 2020 Democratic Primaries, Pete Buttigieg's military background mitigated discrimination against him when he was presented as a veteran married to man [@magni2024].
+Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@hardy2019].
+Moreover, veteran status seems to mitigate or nullify usual stigmas associated with mental illness.
+That is to say, there is negative stigma associated with mental illness [@corrigan2002] and such stigma incurs labor market discrimination [@hipes2016], but evidence suggests that veteran status overrides such stigma and discrimination [@maclean2014].
+Or, in another light, mental illness is seemingly more *understandable* (i.e., permissible) for veterans given the presumptive reasons for their mental strife.
+And media framing as such plays an important role on public perception [@kleykamp2015].
+
+[^4]: Prior to 2021, I found one online recruitment brochure intent on recruiting veterans to serve as election workers [@studentveteransofamerica2020].
+
+[^5]: The cited study defined "insurrectionist sentiments" as, "...willingness to support violent efforts to overturn the results of an election in favor of another, unelected political leader." [@pape2024, 7].
+It should be noted, however, that despite the general definition, the operative items used to measure such sentiments ask about Donald Trump specifically, not an "unelected political leader".
+
+## Research Design and Method
+
+To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would ease election anxieties, a recent survey experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland (UMD).
+The survey was fielded from August 29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287 U.S.
+citizens 18 years of age or older.
+Survey participants were randomly assigned to read one of two fabricated news articles (i.e., vignettes) about recruitment efforts for election jobs.
+
+Participants read either a treatment or control vignette, which was a fabricated news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election.
+The vignettes were identical save for mention of the group targeted for election work recruitment efforts.
+The treatment vignette focused on the announcement of a program by county election officials designed to recruit military veterans and their family members from the community, whereas the control vignette omitted mention of "military veterans and their family members", leaving in place "members of the community"[^6].
+It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignettes due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
+In addition, the survey includes a series of items which ask specifically about Maricopa County, AZ and a comparable series of questions about one's local area[^7].
+
+[^6]: Complete text of treatment and control vignettes are included in the Appendix
+
+[^7]: The setting of the vignettes and inclusion of duplicate questions in the survey are highlighted and discussed later as a potential limitation.
+
+Over the past two decades it became commonplace for national polls to gauge public confidence in election administration by asking some variety of the question, "How confident are you that your vote [will be/was] counted as you intended in the most recent election?" [@hall2009; @sances2015; @stewart2022].
+In addition, since 2008, the Survey of the Performance of American Elections (SPAE) has included a good number of relevant questions to more thoroughly assess trust and confidence in election administration.
+Such questions inquire into the voter experience with the institution more directly.
+This study borrows, modifies, or takes inspiration from certain questions found within the 2022 SPAE and other survey items used by the Pew Research Center [@dunn2018].
+These survey items comprise the dependent variables[^8].
+
+[^8]: All survey items are included in the Appendix.
+
+The outcomes of interest (i.e., dependent variables) are broadly referred to as *election anxieties*, but more specifically refer to concern over fairness and accuracy of the election administration; expectations of fraudulent activity intent on manipulating the electoral outcomes; and concern for voter safety, i.e., comfort voting in-person as it relates to expectations of violence, threats, or intimidation.
+
+The first outcome of interest regards trust and confidence in the electoral process, which refers to trust and confidence in the integrity and security of the electoral systems, administration, technology, and people or organizations to fairly and accurately conduct elections.
+Survey items  measured the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats.
+The first hypothesis is as follows:
+
+::: {#hyp-1}
+
+### Hypothesis 1
+
+Trust and confidence in election administration will be higher among those who were presented information about efforts to recruit veterans as election workers compared to those who were not
+
+:::
+
+Survey participants also responded to questions asking about expectations of fraudulent activity intent on manipulating the electoral outcome.
+
+The second outcome of interest regards an individual's personal safety concerns about the prospect of voting in-person at a polling site.
+That is, the extent people feel safe enough to cast a vote at polling sites free from violence, threats of violence, or intimidation.
+
+The primary independent variable is the prospect of military veterans as poll workers.
+It was considered that veterans would elicit high degrees of approval and support for whatever cause or issue presented.
+For example, I'd expect high approval and support for recruiting veterans to baseball teams just as much as for recruiting them to work as election staff.
+Asking participants whether they supported programs intent on recruiting veterans to work as election staff would garner support regardless of the target group.
+Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require survey questions designed to determine whether veterans have any special effect on electoral confidence and voter safety distinct from the generally high admiration observed most often.
+
+The literature concerning public regard for veterans gives substantial reason to expect that publicized efforts to recruit veterans to work as election staff and volunteers would have the effect of easing election anxieties.
+
+This is a one-sided directional hypothesis. Previous research on public perception and regard for U.S. military veterans gives credence to the directional hypothesis [@kleykamp2018; @kleykamp2023].
+
+Simply put, anything special about veterans that influences people's trust and confidence in election administration is expected to be observable in participants' survey responses.
+However, exactly what makes veterans special in this regard will not; this study did not inquire into details of public perception about veterans specifically (e.g., positive stereotypes, typical characteristics).
+
+The goal was to determine whether there is anything special in having veterans volunteer as election staff (i.e., poll workers).
+That is, does it make any difference in terms of concerns over election security, fairness, and voter safety to include veterans as election staff and volunteers compared to other groups?
+The extent people believe veterans are more trustworthy as election workers than non-veterans in general is difficult without comparable groups to consider.
+
+A series of survey questions sought to determine whether support for veterans as election staff would be notably higher when compared to other relatively neutral groups.
+
+It was hypothesized that different versions of statements in a series of survey questions would result in consistent response effects.
 
@@
 :::
+
+## Conclusion
+
+### Limitations
+
+-   limitations: interpretations of the treatment effect are limited.
+  -   The sample may not be generalizable to the population.
+  -   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts. 
+  -   Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
+  -   Moreover, results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons. 
+    -   First, the vignettes and many survey questions ask about Maricopa County, AZ specifically.
+Adding a specific county in the vignette adds in a factor that cannot be accounted for without additional treatments that eliminate the setting as a potential influence.
+Moreover, the specificity of the setting adds in even more unexplained error---some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S.
+they've know nothing about.
+Adding the county undermines the confidence that treatment effects are solely attributable to veterans to an unknown degree.
+    -   Second, questions ask about one's own local community in addition to identical questions which asked about Maricopa County, AZ.
+Consequently, many questions within the questionnaire were duplicates with that one differences.
+This isn't uncommon in surveys, however in this case, it lengthened the survey to a degree that likely resulted in a higher drop off rate.
+More importantly, the quality of responses were likely diminished to some unknown extent.
+Although it is possible to compare questions asked about Maricopa County, AZ to questions about one's local area, the quality of that comparison is limited by the unknown extent of fatigue induced by answering the same questions twice.
+It wasn't just that some questions were asked multiple times, almost all of the questions were duplicated; after completing a long series on Maricopa County, participants then answered the same questions about the local community.
+The rate to which participants dropped from the survey is ___, which suggests fatigue as an important factor.
+Survey fatigue is a known issue that should be taken into consideration.
+Comparison of treatment effects between the MC series and the local area series is undermined by the unknown influence that fatigue would have on response choices.
+Any differences couldn't confidently be attributed to "my area" vs Maricopa county.
+We also can't determine whether treatment effects are sustained when comparing the Maricopa County series to the local area series asked subsequently.
+We would have to assume the setting as irrelevant, which we can't reasonably do.
+
+\pagebreak
+
+# Appendix A: Survey Experiment Vignettes {#sec-appendix-a}
+
+::::: {#fig-vignettes layout-ncol=2 .content-visible when-format="html" unless-format="pdf"}
+::: {#fig-treatment}
+### Treatment Vignette
+
+| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
+| 
+|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
+As the U.S.
+general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
+| 
+|   Army veteran Jordan Braxton just joined the elections workforce.
+Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
+I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
+
+Text of the Treatment Condition: Recruitment of Veterans and Military Family Members
+:::
+
+::: {#fig-control}
+### Control Vignette
+
+| **Local Residents Recruited for Election Jobs in Maricopa County**
+| 
+|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
+As the U.S.
+general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
+| 
+|   Jordan Braxton just joined the elections workforce.
+Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
+I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
+
+Text of the Control Condition: Recruitment of Community Members
+:::
+
+Fabricated Article Vignettes utilized as Experimental Stimulus
+:::::
+
+::::: {#fig-vignettes layout-ncol=2 .content-hidden unless-format="pdf"}
+::: {#fig-treatment}
+### Treatment Vignette
+
+| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
+| 
+|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
+As the U.S.
+general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
+| 
+|   Army veteran Jordan Braxton just joined the elections workforce.
+Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
+I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
+
+Text of the Treatment Condition: Recruitment of Veterans and Military Family Members
+:::
+
+::: {#fig-control}
+### Control Vignette
+
+| **Local Residents Recruited for Election Jobs in Maricopa County**
+| 
+|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
+As the U.S.
+general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
+| 
+|   Jordan Braxton just joined the elections workforce.
+Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
+I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
+
+Text of the Control Condition: Recruitment of Community Members
+:::
+
+Fabricated Article Vignettes utilized as Experimental Stimulus
+:::::

### 2024-11-21 docs/_tex/index.tex
working on analysis. rough draft needs trim

--- 2024-10-16 docs/_tex/index.tex
@@
 \documentclass[
-  12pt,
-  letterpaper,
-]{article}
+  11pt,
+  a4paper,
+]{scrartcl}
 
@@
     % xetex/luatex font selection
-    \setmainfont[]{Palatino Linotype}
+    \setmainfont[]{TeX Gyre Termes}
+  \setmathfont[]{TeX Gyre Termes Math}
 \fi
@@
 }{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
 \usepackage{xcolor}
-\usepackage[margin=1in]{geometry}
+\usepackage[inner=3cm,outer=4cm,top=3cm,bottom=4cm,headsep=22pt,headheight=11pt,footskip=33pt,ignorehead,ignorefoot,heightrounded]{geometry}
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\newsavebox\pandoc@box
+\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
+  \sbox\pandoc@box{#1}%
+  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
+  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
+  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
+  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
+  \else\usebox{\pandoc@box}%
+  \fi%
+}
 % Set default figure placement to htbp
-\makeatletter
 \def\fps@figure{htbp}
@@
 
-% -----------------------
-% CUSTOM PREAMBLE STUFF
-% -----------------------
+\addtokomafont{disposition}{\rmfamily}
+\setkomafont{pageheadfoot}{\normalfont\normalcolor\footnotesize}
+\setkomafont{pagenumber}{\normalfont\normalcolor\footnotesize}
 
-\usepackage{orcidlink}
-\definecolor{mypink}{RGB}{219, 48, 122}
-\usepackage{endnotes}
-\usepackage[nolists]{endfloat}
-
-% ---------------------------
-% END CUSTOM PREAMBLE STUFF
-% ---------------------------
+% ------------------
+% Headers/Footers
+% ------------------
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\fancyhf{}
+\fancyhead[L,C,R]{}
+\fancyfoot[L,C]{}
+\fancyfoot[R]{\thepage}
+\renewcommand{\headrulewidth}{1pt}
+\fancypagestyle{plain}{%
+    \renewcommand{\headrulewidth}{0pt}%
+    \fancyhf{}%
+    \fancyfoot[R]{\thepage}%
+}
+\renewcommand\footnoterule{\rule{\linewidth}{0.1pt}\vspace{5pt}}
+\usepackage{booktabs}
+\usepackage{caption}
+\usepackage{longtable}
+\usepackage{colortbl}
+\usepackage{array}
+\usepackage{anyfontsize}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\makeatletter
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{plain}
+\@ifundefined{c@chapter}{\newfloat{hypothesis}{h}{lohyp}}{\newfloat{hypothesis}{h}{lohyp}[chapter]}
+\floatname{hypothesis}{H}
+\newcommand*\listofhypothesiss{\listof{hypothesis}{List of Hs}}
+\makeatother
 \makeatletter
@@
   filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={red},
+  citecolor={RoyalBlue},
+  urlcolor={Blue},
   pdfcreator={LaTeX via pandoc}}
@@
 \title{title}
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
+\subtitle{subtitle}
+
 \author{
-Isaiah Espinoza\\University of Maryland, Department of Government and
-Politics\\\href{mailto:gespinoz@umd.edu}{gespinoz@umd.edu}}
+{\bfseries \normalsize Isaiah Espinoza}%
+ \\%
+ \small University of Maryland, Department of Government and
+Politics \\%
+{\footnotesize \url{gespinoz@umd.edu}} \\\vspace{10pt}
+}
+
 \date{2024-10-16}
+
 \begin{document}
 
+% for some reason this does not work in header
+\renewcommand{\abstractname}{Abstract.}
+
+% add the short title to the fancy header
+\fancyhead[R]{A Short title}
+\fancyhead[L]{Isaiah}
+
 \maketitle
+%\noindent \rule{\linewidth}{.5pt}
+\newcommand{\datemodified}[1]{Last modified: #1}
+{\centering
+\hbox{}
+{\datemodified{2024-11-20} \par}}
+%\noindent \rule{\linewidth}{.5pt}
 
 \setstretch{2}
-\subsection{Section}\label{section}
+\pagebreak
 
-This is a simple placeholder for the manuscript's main document (Knuth
-1984).
+\subsection{Introduction}\label{introduction}
+
+Election administration officials make efforts to sustain public trust
+and confidence in the fairness and accuracy of elections, and attempt to
+boost such confidence where ever it may be deprived. Concerns for safety
+have developed among election staff and voters in more recent elections.
+Regular measures are taken to enhance the
+\emph{trustworthiness}\footnote{I adopt a distinction made between
+  \emph{trustworthiness} and \emph{trust} in elections
+  (\citeproc{ref-stewart2022}{Stewart 2022}). The ``\emph{worthiness}''
+  of one's trust in the conduct and administration of elections is based
+  on the extent that outcomes of an election reasonably follow the rules
+  prescribed and can be adjudicated as such. ``If the process is
+  conducted fairly and competently, and the results are determined by
+  the actions of voters\ldots we can call this a trustworthy election''
+  (\citeproc{ref-stewart2022}{Stewart 2022, 237}).
+  \emph{Trustworthiness} is distinguished from \emph{trust} as a
+  psychological construct, ``\ldots the conclusion reached by the public
+  about the functioning of the process''
+  (\citeproc{ref-stewart2022}{Stewart 2022, 237}). To put in other
+  terms, trustworthiness is built by the structure, procedures, and
+  practices of the institution, in this case election administration.
+  The public's trust in elections, however, is amendable to an
+  indefinite number of factors that may be seemingly unrelated to the
+  formal procedures of election administration. To illustrate, my car is
+  trustworthy because I've known it to function quite well as a car
+  should; it passes whatever criteria upon inspection, its sufficiently
+  fueled, and is in generally good working order. I have every reason to
+  deem it worthy of my trust. However, I don't trust my car because I am
+  sure it is haunted.} of the electoral process through practices meant
+to improve the conduct, transparency, or overall administration of
+elections in the United States.
+
+Although election officials undertake great efforts to enhance the
+trustworthiness of election administration, public \emph{trust} in
+elections is a psychological construct influenced by many things outside
+of election official control such as partisanship or elite rhetoric
+(\citeproc{ref-hooghe2018}{Hooghe 2018};
+\citeproc{ref-sances2015}{Sances and Stewart 2015}). Moreover, a
+person's evaluation of the election in hindsight is often influenced by
+the election outcome itself (\citeproc{ref-daniller2019}{Daniller and
+Mutz 2019}; \citeproc{ref-stewart2022}{Stewart 2022}). Thus, measures
+taken by election officials can be undermined, trivialized, or made
+irrelevant depending on how one feels after the election results have
+come out.
+
+Such volatile attitudes and evaluations post-election can leave a
+lasting impression that election officials must contend with upon the
+next election cycle (\citeproc{ref-bowler2024}{Bowler and Donovan 2024};
+\citeproc{ref-levendusky2024}{Levendusky et al. 2024}). For instance, we
+have witnessed many people's outright refusal to accept the 2020 U.S.
+election results as legitimate despite consistent review of the evidence
+confirming the results as fair and accurate. Such a case demonstrates
+that public trust in elections is, at best, only partial to
+trustworthiness of election administration in the United
+States\footnote{It is important to point out here that election
+  administration is just one institution that interacts with many other
+  institutions and processes which form the electoral system \emph{writ
+  large} (\citeproc{ref-stewart2022}{Stewart 2022}). The way in which I
+  discuss the institution of election administration, as well as the way
+  in which I discuss and distinguish public trust in elections from
+  broader conceptions of public trust, is borrowed substantively from
+  Stewart (\citeproc{ref-stewart2022}{2022})'s conceptual framework of
+  the same. Distinctions between \emph{trust} and \emph{trustworthiness}
+  and the notion of election administration as an institution are
+  already apparent inspirations convenient for situating the theory of
+  this research inquiry.}. Or in other words, there is only so much that
+election officials can do to sustain or improve public trust in election
+administration.
+
+Even though election officials can do a lot to secure election
+integrity, especially under intense scrutiny, there's not much they can
+do to cement public confidence after election night passes. At best,
+election officials can ease public anxieties prior to election night. As
+mentioned, this usually consists of enhancing procedures and practices
+and adapting to advancing election technology.
+
+One point of contention that election officials have faced in the past
+regard evaluation of election workers. Previous literature has focused
+on how voter interaction with election workers
+(\citeproc{ref-claassen2008}{Claassen et al. 2008}), or the voter
+experience generally (\citeproc{ref-atkeson2007}{Atkeson and Saunders
+2007}), influences evaluations of election administration. As such,
+election worker competency has been examined as a factor significant to
+evaluations of performance of elections (\citeproc{ref-hall2007}{T.
+Hall, Monson, and Patterson 2007}; \citeproc{ref-hall2009}{T. E. Hall,
+Quin Monson, and Patterson 2009}). However, considering that individual
+perceptions and preconceived notions play a huge role in cognition
+(\citeproc{ref-cikara2014}{Cikara and Bavel 2014};
+\citeproc{ref-vanbavel2021}{Van Bavel and Packer 2021}), it is
+reasonable to expect that the group an election worker hails from would
+be an important influence upon the voter's perception or evaluation of
+their own experience as well as subsequent evaluations of the electoral
+process. Supposing such is the case, we can expect that information
+about \emph{who} (i.e., which groups) election officials are targeting
+in publicized recruitment efforts would lessen particular election
+anxieties. That is to say, it is reasonable to expect that telling
+people \emph{who} will be working as election staff and volunteers would
+ease election anxieties, therefore improve confidence that the election
+will be conducted fairly, accurately, and safe for all involved.
+
+In this paper, I report results from a recent survey experiment
+administered to test whether publicized efforts to recruit veterans to
+work as election staff and volunteers would ease election anxieties
+(e.g., concern for electoral fairness and accuracy, as well as concerns
+for voter safety). Results of the survey experiment support the
+hypothesis that emphasizing veterans as the target of election worker
+recruitment efforts eases pre-elections anxieties to an extent. In
+particular, among those who read the treatment vignette, confidence that
+the elections would be fair and accurate was higher in comparison. In
+addition, expectations of electoral fraud were lower, as were concerns
+for voter safety compared to those who read a control vignette. Notable
+is that there was a significant increase in confidence, and lower
+expectations of fraud, among those who believe that the 2020 election
+was illegitimate.
+
+\begin{itemize}
+\tightlist
+\item
+  when distinguished by partisanship\ldots{}
+\item
+  moreover, broken down by other demographic variables such as race,
+  gender, education, etc.
+\item
+  holding these factors constant demonstrates a
+  {[}increased/decreased{]} likelihood that a respondent's confidence
+  would likely {[}increase/decrease{]}, expectations of fraud would
+  likely {[}increase/decrease{]}, and concerns for safety would lessen
+  among those in the treatment group compared to those in the control.
+  These results allow us to attribute the differences to the treatment
+  stimulus, namely, the prospect of having veterans serve as election
+  staff or volunteers.
+\end{itemize}
+
+\subsection{Background: Election Administration and Public
+Confidence}\label{background-election-administration-and-public-confidence}
+
+Election officials have tried hard to inspire confidence in the
+administration and conduct of elections by improving the degree to which
+elections are trustworthy. Development and implementation of procedures
+such as post-election auditing of ballots and logic-and-accuracy testing
+of ballot tabulation equipment are prominent examples adding to the long
+history of efforts to enhance the trustworthiness of election
+administration in the United States.
+
+Prior to the year 2000, one of the main issues facing election
+administration was recruiting enough election workers to volunteer at
+the polls (i.e., poll workers) (\citeproc{ref-maidenberg1996}{Maidenberg
+1996}). Election worker recruitment is still much of an issue in the
+current era as it was then, perhaps worse
+(\citeproc{ref-ferrer2024}{Ferrer, Thompson, and Orey 2024}). In
+addition to ensuring election admin offices were adequately staffed, the
+controversy of the 2000 general election made the public more attentive
+to issues concerning the conduct and administration of elections. In
+particular, voting technology (\citeproc{ref-herrnson2009}{Herrnson,
+Niemi, and Hanmer 2009}) and election worker competence was a of
+interest in election studies (\citeproc{ref-claassen2008}{Claassen et
+al. 2008}; \citeproc{ref-hall2007}{T. Hall, Monson, and Patterson 2007};
+\citeproc{ref-hall2009}{T. E. Hall, Quin Monson, and Patterson 2009}).
+Following the passage of the Help America Vote Act in 2002, election
+officials efforts to boost public confidence in the conduct and
+administration of elections revolved primarily around the accuracy of
+vote counts, ballot tabulation equipment or voting machines, the
+commitment of election staff, and more
+(\citeproc{ref-atkeson2007}{Atkeson and Saunders 2007}). These somewhat
+generic issues of election worker staffing, competence, and voting
+technology were likely mere stepping stones leading to more intense
+election administration issues.
+
+In 2024, election officials made valiant efforts to boost public
+confidence in the fairness and accuracy of elections within an
+intensified political climate that appeared quite hostile to election
+officials (\citeproc{ref-brennancenterforjustice2024}{Brennan Center for
+Justice 2024}; \citeproc{ref-edlin2024}{Edlin and Norden 2024}).
+Although polling around the time indicated that most people thought that
+U.S. elections would be run at least somewhat well
+(\citeproc{ref-nadeem2024}{Nadeem 2024}), many election officials
+nationwide took efforts to assuage the worry of those most skeptical.
+Enhancing trustworthiness in election administration is a regular duty
+for election officials, but baseless allegations regarding the fairness
+and accuracy of the 2020 election loomed ever larger, and the fear of
+political violence became prominent for both election officials and the
+public. Safety concerns for election staff, volunteers, and voters alike
+only added to, and perhaps exacerbated, public concern for the integrity
+of election administration in the United States. Especially as the
+steady increase in election official turnover seems to be increasing
+even more (\citeproc{ref-ferrer2024}{Ferrer, Thompson, and Orey 2024}).
+
+Election anxiety was high in the lead up to the 2024 elections in the
+United States. Concerns for voter safety and the prospect of political
+violence remained prescient and compelled many local officials to
+prepare for the worst (\citeproc{ref-doubek2024}{Doubek 2024};
+\citeproc{ref-edlin2024}{Edlin and Norden 2024}). Election officials in
+Washoe County, Nevada, installed panic buttons for election staff that
+would alert a monitoring center to summon law enforcement
+(\citeproc{ref-lincoln2024}{Lincoln 2024}). Nevada also passed a law
+making it a felony to harass, threaten, or intimidate election workers
+(\citeproc{ref-nevadasecretaryofstate2023}{Nevada Secretary of State
+2023}). Leading up to election day, news outlets reported that election
+work had become a seemingly dangerous job (\citeproc{ref-wire2024}{Wire
+et al. 2024}). A Brennan Center survey report stated that,
+``\ldots large numbers of election officials report having experienced
+threats, abuse, or harassment for doing their jobs''
+(\citeproc{ref-edlin2024}{Edlin and Norden 2024}). Concerns over the
+fairness of elections and accuracy of vote counts intensified,
+heightening concerns over the prospect of political violence and, in
+turn, engendered increased worry for the safety of voters and election
+workers alike.
+
+Suffice to say, pre-election anxiety consists of more than concerns over
+fairness and accuracy of vote counts in light of added safety concerns.
+It is not hard to recognize that increased tension in the pre-election
+period makes for a volatile political environment.
+
+\subsection{Literature Reivew}\label{literature-reivew}
+
+Assessing the public's \emph{trust} in elections has not been
+straightforward. Inquiry into public trust in elections has been
+approached by scholars of political science in many different ways
+(\citeproc{ref-cook2005}{Cook and Gronke 2005}), often distinguishable
+by the scope of the research question and more or less constrained by
+the particular conception of public trust. Quite often, trust in
+election administration is conflated with trust in government writ
+large, government legitimacy, government or system responsiveness, or
+even satisfaction with democracy (\citeproc{ref-daniller2019}{Daniller
+and Mutz 2019}). At this level, not only is the level of public trust in
+elections sometimes vague, but there's little consideration over the
+difference between such attitudes pre-election and post-election. In
+contrast, a considerable amount of research tends to conceive of public
+trust in accordance with the institution in question
+(\citeproc{ref-atkeson2007}{Atkeson and Saunders 2007};
+\citeproc{ref-hooghe2018}{Hooghe 2018}).
+
+Election administration is just one part of the larger set of
+institutions which form the electoral system. As such, the performance
+of the institution along with the rest ``\ldots lends credibility to the
+outcome of an election: whether it is considered by citizens and the
+international community to be fair and legitimate.''
+(\citeproc{ref-stewart2022}{Stewart 2022, 236}).
+
+Trust and confidence in the conduct of elections concerns aspects of
+elections that fall squarely within the institution of election
+administration. At this level, for instance, public trust is ascertained
+by capturing assessments about the perceived accuracy of vote counts
+(e.g., whether votes are/were counted as intended). Or in other words,
+public trust is ascertained by the extent the public perceives the
+institution of election administration as trustworthy.
+
+Intuitively, enhancing public trust in elections would best be
+accomplished by enhancing the \emph{trustworthiness} of the institution,
+i.e., consistently doing the things that election officials already
+regularly do come election time. However, trust and confidence in
+elections has become ever more precarious over the last few election
+cycles. Especially considering public polling data since 2000 shows that
+confidence that votes were, or would be, counted as intended was in a
+consistent decline despite efforts towards bolstering election integrity
+and trustworthiness (\citeproc{ref-sances2015}{Sances and Stewart
+2015}). This is even more pronounced considering the role that
+partisanship has had on such confidence over accuracy of vote count
+(\citeproc{ref-sances2015}{Sances and Stewart 2015};
+\citeproc{ref-stewart2022}{Stewart 2022}).
+
+There's also stark difference in public trust before the election has
+occurred compared to after, a phenomenon referred to as the
+``winner-loser gap''; the ``winners'' are those who supported the
+winning candidate and the ``losers'' are those who supported the losing
+candidate. Much research has been dedicated to analyzing the sentiment
+of electoral winners vs losers, and vice versa
+(\citeproc{ref-daniller2019}{Daniller and Mutz 2019};
+\citeproc{ref-nadeau1993}{Nadeau and Blais 1993}). Opinions of electoral
+trust gathered after the election has occurred are limited considering
+the well-recognized impact that the electoral outcome itself has on
+feelings of public trust in elections
+(\citeproc{ref-daniller2019}{Daniller and Mutz 2019}).
+
+As such, it is questionable whether we can characterize public trust in
+the pre-election period as the same trust after the election results
+have come out\footnote{There's little that could justify a conceptual
+  distinction between public trust pre-election and public trust
+  post-election. The temporal element renders the difference between
+  pre- and post-election operative rather than conceptual.}. The former
+is \emph{anticipatory}---i.e., the kind that is more or less anxious
+given the uncertainties surrounding the election. The latter is
+\emph{evaluative}---a judgement discerned empirically in hindsight after
+the election event has occurred. The evaluative form of trust lends to
+inquiries interested in public opinion on regime legitimacy,
+satisfaction with democracy, and perceived responsiveness
+(\citeproc{ref-daniller2019}{Daniller and Mutz 2019}). This study
+focuses primarily on that \emph{anticipatory} kind of trust and
+confidence, which speaks more to electoral anxieties over the
+institution of election administration. Not to mention that by
+definition, one feels anxiety over impending uncertainties located in
+the future\footnote{Note that \emph{anxiety} is taken to be the inverse
+  of \emph{trust and confidence}, as in, one who is less confident in
+  this or that is thereby more anxious over the matter in question. As
+  such, anxiety may equivalently be discussed as trust/confidence
+  without issue except for framing of said discussion. Electoral anxiety
+  is used in place of electoral trust/confidence simply to emphasize the
+  anticipatory nature of the attitudes in question.}.
+
+The primary interest of this study concerns \emph{election anxieties},
+which is distinguished into two categories: fairness and accuracy, and
+voter safety. Of course, the direction of electoral outcomes are a
+particular source of electoral anxiety, but only the election outcome
+itself can resolve any nail-biting stress over its anticipated
+direction. In contrast, the anxieties of interest here are able to be
+relaxed to some extent prior to the election given some intervention.
+
+Interventions aimed at improving public trust, or rather, aimed at
+easing election anxieties may not be within the usual repertoire
+election officials draw upon. Regardless of the measures taken by
+election officials to boost public confidence in the
+\emph{trustworthiness} of election administration (e.g., conducting
+audits, testing election machines), public \emph{trust} and confidence
+in elections more generally is apt to shift dramatically post-election
+based on factors such as partisanship, elite rhetoric, particular state
+policies, and more (\citeproc{ref-carter2024}{Carter et al. 2024};
+\citeproc{ref-coll2024a}{Coll and Clark 2024};
+\citeproc{ref-nadeau1993}{Nadeau and Blais 1993}). Moreover, prior
+research has found that evaluation of election workers themselves are an
+important factor when it comes to levels of public confidence in the
+electoral process (\citeproc{ref-claassen2008}{Claassen et al. 2008};
+\citeproc{ref-hall2007}{T. Hall, Monson, and Patterson 2007};
+\citeproc{ref-hall2009}{T. E. Hall, Quin Monson, and Patterson 2009}).
+Such studies focused on the quality of the voter experience with
+reference to the interaction between voter and election worker.
+
+Beyond the general competence of election workers, however, the quality
+of the voter experience may be influenced merely by impressions about
+\emph{who} comprises election staff and volunteers. Political and other
+social science researchers have recognized for some time the power that
+group identity can have over attitudes and perception
+(\citeproc{ref-vanbavel2021}{Van Bavel and Packer 2021};
+\citeproc{ref-xiao2016}{Xiao, Coppin, and Van Bavel 2016};
+\citeproc{ref-xiao2012}{Xiao and Van Bavel 2012}). As such, we can
+expect that information identifying the particular groups being
+recruited to serve as election staff will be enough to improve trust and
+confidence in election administration, i.e., ease election anxieties. It
+was hypothesized that information on recruitment efforts targeting
+military veterans to work as election staff would ease election
+anxieties. The next section elaborates further on why military veterans
+are of particular interest.
+
+\subsection{Why Veterans}\label{why-veterans}
+
+Election officials are likely to be agnostic as to who dedicates their
+time to civil service such as election work. Staffing issues have been
+an issue since at least the 1990s (\citeproc{ref-ferrer2024}{Ferrer,
+Thompson, and Orey 2024}; \citeproc{ref-maidenberg1996}{Maidenberg
+1996}). In 2020, such efforts were made far more difficult by the
+COVID-19 pandemic (\citeproc{ref-abbate2020a}{Abbate 2020};
+\citeproc{ref-mena2020}{Mena 2020}). Sure, it makes sense to recruit
+veterans, but no more than any other group. After all, ensuring election
+offices are adequately staffed is everyone's problem. So there's no
+special reason to target veterans for recruitment above other groups.
+Indeed, there's no reason to discriminate recruitment efforts at all if
+the point is purely to fill staffing vacancies. However the interest in
+veterans as a special group to consider arose in light of increased and
+sudden efforts to recruit veterans into election work.
+
+The reason why veterans arose as a special subset of the population to
+consider for this inquiry is because there was a sudden push to target
+veterans for recruitment efforts that arose shortly after the events on
+Capitol Hill on January 6th, 2021. After the 2020 election, large
+efforts were made to recruit military veterans and their families to
+work or volunteer as election staff
+(\citeproc{ref-nflfootballoperations2022}{NFL Football Operations 2022};
+\citeproc{ref-wetheveterans2022}{We The Veterans 2022}). Prior to that
+point, young people were sometimes given special mention as targets of
+election worker recruitment efforts\footnote{The cited study defined
+  ``insurrectionist sentiments'' as, ``\ldots willingness to support
+  violent efforts to overturn the results of an election in favor of
+  another, unelected political leader.'' (\citeproc{ref-pape2024}{Pape
+  et al. 2024, 7}). It should be noted, however, that despite the
+  general definition, the operative items used to measure such
+  sentiments ask about Donald Trump specifically, not an ``unelected
+  political leader''.} (\citeproc{ref-herndon2020}{Herndon 2020};
+\citeproc{ref-powerthepolls2020}{Power the Polls 2020}). Generally,
+however, recruitment efforts cast a wide net, indiscriminate of who
+applies (\citeproc{ref-conde2020}{Conde 2020};
+\citeproc{ref-ross2020}{Ross 2020}).
+
+One can speculate that the motivation to associate military veterans
+with civic engagement and democracy may be intended to counter negative
+perceptions and impressions given by the proportion of veteran service
+members arrested for taking part in the events on January 6th
+(\citeproc{ref-jensen2022a}{Jensen, Yates, and Kane 2022};
+\citeproc{ref-loewenson2023}{Loewenson 2023};
+\citeproc{ref-milton2021}{Milton and Mines 2021}). Especially with
+regard to research demonstrating that willingness to support violent
+efforts to overturn election results\footnote{Prior to 2021, I found one
+  online recruitment brochure intent on recruiting veterans to serve as
+  election workers (\citeproc{ref-studentveteransofamerica2020}{Student
+  Veterans of America 2020}).} (in support of Trump) is, on average,
+more common among veterans than among matched samples of non-veterans
+(\citeproc{ref-pape2024}{Pape et al. 2024}). This is in addition to a
+strengthened association portrayed in media outlets between military
+veterans and militias (\citeproc{ref-steinhauer2020}{Steinhauer 2020}).
+Although such media output reeks of the contemporary political context,
+prior research has substantiated such a connection between veterans and
+militia groups. A. Cooter (\citeproc{ref-cooter2024}{2024}) notes from
+her 3-year ethnographic fieldwork among Michigan militia members that,
+``\ldots approximately 40\% of militia leaders and 30\% of members had
+previous military experience. Most of these veterans actively sought out
+such groups, as opposed to being recruited by them''
+(\citeproc{ref-cooter2024}{2024}; see also \citeproc{ref-cooter2013}{A.
+B. Cooter 2013}). Thus, countering such associations by promoting a
+different image of veterans to the mass public and veterans alike seems
+like a reasonable motivation. Yet such speculation is just that.
+
+That being said, the general public perception, attitudes, or even
+stereotypes about military veterans are significant to consider.
+Although military recruitment shows a downward trend as of late, public
+perception of veterans are overwhelmingly positive
+(\citeproc{ref-kleykamp2023}{Kleykamp, Schwam, and Wenig 2023}).
+Veterans are a particularly potent group where mention of veteran status
+seems to have a positive, calming, or nullifying effect on attitudes.
+For instance, recent research shows that, during his campaign in the
+2020 Democratic Primaries, Pete Buttigieg's military background
+mitigated discrimination against him when he was presented as a veteran
+married to man (\citeproc{ref-magni2024}{Magni and Reynolds 2024}).
+Similar research has also found that a candidate's veteran status
+affords them better evaluations regarding competency in particular issue
+areas (e.g., war competence) (\citeproc{ref-hardy2019}{Hardy et al.
+2019}). Moreover, veteran status seems to mitigate or nullify usual
+stigmas associated with mental illness. That is to say, there is
+negative stigma associated with mental illness
+(\citeproc{ref-corrigan2002}{Corrigan et al. 2002}) and such stigma
+incurs labor market discrimination (\citeproc{ref-hipes2016}{Hipes et
+al. 2016}), but evidence suggests that veteran status overrides such
+stigma and discrimination (\citeproc{ref-maclean2014}{MacLean and
+Kleykamp 2014}). Or, in another light, mental illness is seemingly more
+\emph{understandable} (i.e., permissible) for veterans given the
+presumptive reasons for their mental strife. And media framing as such
+plays an important role on public perception
+(\citeproc{ref-kleykamp2015}{Kleykamp and Hipes 2015}).
+
+\subsection{Research Design and
+Method}\label{research-design-and-method}
+
+To test the theory that publicized efforts to recruit veterans to work
+as election staff and volunteers would ease election anxieties, a recent
+survey experiment was embedded in a survey developed and conducted by
+the Center for Democracy and Civic Engagement (CDCE) at the University
+of Maryland (UMD). The survey was fielded from August 29th, 2024 to
+September 18th, 2024 on a non-probability sample of 1,287 U.S. citizens
+18 years of age or older.
+
+The primary independent variable is the prospect of military veterans as
+poll workers. It was considered that veterans would elicit high degrees
+of approval and support for whatever cause or issue presented. For
+example, I'd expect high approval and support for recruiting veterans to
+baseball teams just as much as for recruiting them to work as election
+staff. Asking participants whether they supported programs intent on
+recruiting veterans to work as election staff would garner support
+regardless of the target group. Considering that support and admiration
+for veterans is generally high among the population
+(\citeproc{ref-kleykamp2023}{Kleykamp, Schwam, and Wenig 2023}), then
+discerning the impact on one's confidence would require a survey
+experiment and questions designed to determine whether veterans have any
+special effect on electoral confidence and voter safety distinct from
+the generally high admiration observed most often.
+
+Survey participants were randomly assigned to read one of two fabricated
+news articles (i.e., vignettes) about recruitment efforts for election
+jobs. Participants read either a treatment or control vignette, which
+was a fabricated news article about efforts in Maricopa County, AZ to
+recruit election staff and volunteers for the 2024 general election. The
+treatment vignette referred to a program designed to recruit veterans
+and their family members and describes an interviewee ``Jordan Braxton''
+as an Army veteran; whereas the control vignette simply omitted any
+mention of veterans and their family members, and didn't describe
+``Jordan Braxton'' as an Army veteran. Beyond those small differences
+and the headlines, the article vignettes are identical. Any effects can
+be attributed to the information about veterans in the treatment
+vignette\footnote{Complete text of treatment and control vignettes are
+  included in the Appendix}.
+
+It should be noted that Maricopa County, AZ was chosen as the setting of
+the story in the vignettes due to the increased scrutiny levied toward
+election administration there after the 2020 election
+(\citeproc{ref-giles2021}{Giles 2021};
+\citeproc{ref-maricopacountyelectionsdepartment2022}{Maricopa County
+Elections Department 2022}). In addition, the survey includes a series
+of items which ask specifically about Maricopa County, AZ and a
+comparable series of questions about one's local area\footnote{The
+  setting of the vignettes and inclusion of duplicate questions in the
+  survey are highlighted and discussed later.}.
+
+Over the past two decades it became commonplace for national polls to
+gauge public confidence in election administration by asking some
+variety of the question, ``How confident are you that your vote {[}will
+be/was{]} counted as you intended in the most recent election?''
+(\citeproc{ref-hall2009}{T. E. Hall, Quin Monson, and Patterson 2009};
+\citeproc{ref-sances2015}{Sances and Stewart 2015};
+\citeproc{ref-stewart2022}{Stewart 2022}). In addition, since 2008, the
+Survey of the Performance of American Elections (SPAE) has included a
+good number of relevant questions to more thoroughly assess trust and
+confidence in election administration. Such questions inquire into the
+voter experience with the institution more directly. This study borrows,
+modifies, or takes inspiration from certain questions found within the
+2022 SPAE and other survey items used by the Pew Research Center
+(\citeproc{ref-dunn2018}{Dunn 2018}). These survey items comprise the
+dependent variables\footnote{All survey items are included in the
+  Appendix.}.
+
+The outcomes of interest (i.e., dependent variables) are broadly
+referred to as \emph{election anxieties}, but more specifically refer to
+confidence over fairness and accuracy of the election administration;
+expectations of fraudulent activity intent on manipulating the electoral
+outcomes; and concern for voter safety, i.e., comfort voting in-person
+as it relates to expectations of violence, threats, or intimidation. The
+following presents multiple one-sided directional hypotheses. Previous
+research on public perception and regard for U.S. military veterans
+gives credence to the directional hypotheses
+(\citeproc{ref-kleykamp2018}{Kleykamp, Hipes, and MacLean 2018};
+\citeproc{ref-kleykamp2023}{Kleykamp, Schwam, and Wenig 2023}).
+
+The first outcome of interest regards \emph{trust and confidence} in
+election administration, which includes the integrity and security of
+the electoral process, administration, technology, and people or
+organizations to fairly and accurately conduct elections. Survey items
+measured the degree of confidence that votes will be counted as voters
+intend, confidence that electoral systems are secure from technological
+threats, perceived commitment of election staff, confidence that
+outcomes will be fair, as well as confidence that the voting process
+will be fair.
+
+The first hypothesis is as follows:
+
+\(H_{1}:\) Trust and confidence in election administration will be
+higher among those who were presented information about efforts to
+recruit veterans as election workers compared to those who were not
+
+In total, six survey items measure different aspects of trust and
+confidence in election administration. These items were analyzed
+individually but were also transformed into a composite scale of trust
+and confidence.
+
+The literature concerning public regard for veterans gives substantial
+reason to expect that publicized efforts to recruit veterans to work as
+election staff and volunteers would have the effect of easing election
+anxieties. As such, survey participants also responded to a series of
+questions that inquired into expectations of electoral fraud---i.e.,
+fraudulent activity intent on manipulating the electoral outcome.
+
+Note, however, that an \emph{expectation} of electoral fraud implies a
+degree of distrust more so than an agitated state of anxiety over the
+\emph{potential} for electoral fraud. Conceptually, this may be
+considered a particular kind of `anxiety' given that is it pre-election
+(hence, an expectation), however, not necessarily. A person may be
+rather confident with regard to how much they distrust the integrity of
+electoral administration, resulting in such expectations.
+
+For instance, the first item of the 5-item series asks participants to
+report their expectation that ``There will be voter fraud, that is,
+people who are not eligible to vote will vote or vote more than once''
+on a 4-option response scale ranging from ``Not likely at all'' to
+``very likely''. This statement, as well as the rest in the series,
+asserts an expected compromise of election integrity, which speaks to
+the trustworthiness of the institution. What the individual expects,
+more or less, is that electoral fraud will occur, implying that
+fraudulent attempts will be successful.
+
+It was expected that the experimental stimulus would result in lower
+expectation for electoral fraud among those who read the treatment
+vignette compared to those who read the control vignette. The second
+hypothesis is,
+
+\(H_{2}:\) Expectations of electoral fraud will be lower among those who
+were presented information about efforts to recruit veterans as election
+workers compared to those who were not
+
+Another outcome of interest regards concerns about voting in-person at a
+polling site, i.e., voter safety. That is, the extent people feel that
+voters are safe enough to cast a vote at polling sites free from
+violence, threats of violence, or intimidation. Two survey items use
+slightly different questions to inquire about the same essential
+issue---i.e., perceptions of physical safety at the polls. The third
+hypothesis follows,
+
+\(H_{3}:\) Concerns for voter safety be lower among those who are
+presented information about efforts to recruit veterans as election
+workers compared to those who are not
+
+Another outcome of interest concerned how particular actions of election
+officials, or circumstances at polling sites, would impact the
+confidence of election integrity as well as voter safety \emph{from the
+perspective of survey respondents}. Survey participants responded to a
+series of six statements, all prefaced with the same question,
+``Regardless of whether any of these are actually the case, how would
+the following impact your confidence in the fairness and accuracy of
+elections conducted this November?'' The six statements were,
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Election officials test every machine used in the election to ensure
+  they are secure.
+\item
+  Election officials conduct audits of ballots after every election to
+  confirm the results were accurate.
+\item
+  Poll watchers affiliated with the political parties or candidates
+  observe the election.
+\item
+  Election staff and volunteers include military veterans and their
+  family members from the community.
+\item
+  Election staff and volunteers include lawyers from the community.
+\item
+  Election staff and volunteers include college students from the
+  community.
+\end{enumerate}
+
+For each statement, survey participants responded by selecting one of
+five response options:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Decrease confidence a lot
+\item
+  Decrease confidence somewhat
+\item
+  No impact on confidence
+\item
+  Increase confidence somewhat
+\item
+  Increase confidence a lot
+\end{enumerate}
+
+It was expected that respondents would estimate stronger impact on their
+confidence given they were assigned to read the treatment vignette
+compared to those who were not. Thus, the hypothesis is,
+
+\(H_{4}:\) Respondents who read the treatment vignette will report
+stronger impact on their personal confidence in fairness and accuracy of
+election administration when veterans are stated to be included among
+election staff and volunteers compared to those who read the control
+vignette.
+
+The extent people believe veterans are more trustworthy as election
+workers than non-veterans in general is difficult without comparable
+groups to consider. Recruitment efforts in 2022 targeted young students,
+lawyers, and military veterans (\citeproc{ref-wang2022}{Wang 2022}).
+Thus, lawyers and college students were selected as two groups for which
+responses could be compared between different statement versions.
+
+The goal was to determine whether there is anything special in having
+veterans volunteer as election staff (i.e., poll workers) compared to
+other groups. That is, does it make any difference in terms of concerns
+over election security, fairness, and voter safety to include veterans
+as election staff and volunteers compared to other groups? The fourth
+hypothesis, irrespective of the experimental stimulus, reads,
+
+\(H_{5}:\) Respondents who read the treatment vignette will report
+stronger impact on their personal confidence in fairness and accuracy of
+election administration when veterans are stated to be included among
+election staff and volunteers compared to identical statements about
+lawyers or college students.
+
+\subsection{Results}\label{results}
+
+\pagebreak
+
+\subsection{Conclusion}\label{conclusion}
+
+\subsubsection{Limitations}\label{limitations}
+
+\begin{itemize}
+\tightlist
+\item
+  limitations: interpretations of the treatment effect are limited.
+\item
+  The sample may not be generalizable to the population.
+\item
+  It's hard to say whether merely mentioning veterans is enough, as
+  compared to explicitly naming veterans as the target of particular
+  recruitment efforts.
+\item
+  Interpretation is also limited considering that no other particular
+  group, or groups are compared directly against the veteran treatment
+  vignette, i.e., additional vignettes for other comparable groups.
+\item
+  Moreover, results are limited by the survey questions, questionnaire
+  design, and experimental stimulus (i.e., vignette) for two reasons. -
+  First, the vignettes and many survey questions ask about Maricopa
+  County, AZ specifically. Adding a specific county in the vignette adds
+  in a factor that cannot be accounted for without additional treatments
+  that eliminate the setting as a potential influence. Moreover, the
+  specificity of the setting adds in even more unexplained error---some
+  people may have attitudes about the county in question, others won't,
+  while others may be muffed to consider a random county in the U.S.
+  they've know nothing about. Adding the county undermines the
+  confidence that treatment effects are solely attributable to veterans
+  to an unknown degree. - Second, questions ask about one's own local
+  community in addition to identical questions which asked about
+  Maricopa County, AZ. Consequently, many questions within the
+  questionnaire were duplicates with that one differences. This isn't
+  uncommon in surveys, however in this case, it lengthened the survey to
+  a degree that likely resulted in a higher drop off rate. More
+  importantly, the quality of responses were likely diminished to some
+  unknown extent. Although it is possible to compare questions asked
+  about Maricopa County, AZ to questions about one's local area, the
+  quality of that comparison is limited by the unknown extent of fatigue
+  induced by answering the same questions twice. It wasn't just that
+  some questions were asked multiple times, almost all of the questions
+  were duplicated; after completing a long series on Maricopa County,
+  participants then answered the same questions about the local
+  community. The rate to which participants dropped from the survey is
+  \_\_\_, which suggests fatigue as an important factor. Survey fatigue
+  is a known issue that should be taken into consideration. Comparison
+  of treatment effects between the MC series and the local area series
+  is undermined by the unknown influence that fatigue would have on
+  response choices. Any differences couldn't confidently be attributed
+  to ``my area'' vs Maricopa county. We also can't determine whether
+  treatment effects are sustained when comparing the Maricopa County
+  series to the local area series asked subsequently. We would have to
+  assume the setting as irrelevant, which we can't reasonably do.
+\end{itemize}
+
+\pagebreak
+
+\subsection{Appendix A: Survey Experiment
+Vignettes}\label{sec-appendix-a}
+
+\begin{figure}
+
+\begin{minipage}{0.50\linewidth}
+
+\subsubsection{Treatment Vignette}\label{treatment-vignette-1}
+
+\textbf{Local Military Veterans Recruited for Election Jobs in Maricopa
+County}\\
+\strut \\
+\strut ~~PHOENIX (AP) --- Election officials in Maricopa County,
+Arizona, announced a program designed to recruit military veterans and
+their family members from the community to serve as election
+administrators, including election polling place workers, temporary
+workers, and full-time staff. As the U.S. general elections in November
+near, election officials must fill several thousand temporary positions
+and hundreds of other open positions to ensure sufficient staffing for
+the 2024 elections and beyond.\\
+\strut \\
+\strut ~~Army veteran Jordan Braxton just joined the elections
+workforce. Jordan believes their role is important to ensuring a secure,
+accurate, and transparent election, ``Many places are short on staff
+this election cycle. I served my country in the Army, and I want to do
+my part as a veteran and a citizen to ensure that everyone trusts the
+process and the outcome of the election.''
+
+\end{minipage}%
+%
+\begin{minipage}{0.50\linewidth}
+
+\subsubsection{Control Vignette}\label{control-vignette-1}
+
+\textbf{Local Residents Recruited for Election Jobs in Maricopa
+County}\\
+\strut \\
+\strut ~~PHOENIX (AP) ---Election officials in Maricopa County, Arizona,
+announced a program to recruit members of the community to serve as
+election administrators, including election polling place workers,
+temporary workers, and full-time staff. As the U.S. general elections in
+November near, election officials must fill several thousand temporary
+positions and hundreds of other open positions to ensure sufficient
+staffing for the 2024 elections and beyond.\\
+\strut \\
+\strut ~~Jordan Braxton just joined the elections workforce. Jordan
+believes their role is important to ensuring a secure, accurate, and
+transparent election, ``Many places are short on staff this election
+cycle. I want to do my part as a citizen to ensure that everyone trusts
+the process and the outcome of the election.''
+
+Text of the Control Condition: Recruitment of Community
+Members\end{minipage}%
+
+\end{figure}%
+
+\subsection{Appendix B: Sample Demographics}\label{sec-appendix-b}
+
+There should be nothing below here
+
+\begin{table}
+
+\caption{\label{tbl-desc-pdf}Description of Sample Demographics}
+
+\centering{
+
+\centering\begingroup\fontsize{8}{10}\selectfont
+
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{20em}rr}
+\toprule
+Name & n & Pct\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Experiment Condition}}\\
+\cellcolor{gray!10}{\hspace{1em}Control} & \cellcolor{gray!10}{637} & \cellcolor{gray!10}{49.49}\\
+\hspace{1em}Treatment & 650 & 50.51\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Question Set}}\\
+\cellcolor{gray!10}{\hspace{1em}A} & \cellcolor{gray!10}{644} & \cellcolor{gray!10}{50.04}\\
+\hspace{1em}B & 643 & 49.96\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Age}}\\
+\cellcolor{gray!10}{\hspace{1em}18-24} & \cellcolor{gray!10}{108} & \cellcolor{gray!10}{8.39}\\
+\hspace{1em}25-34 & 242 & 18.80\\
+\cellcolor{gray!10}{\hspace{1em}35-44} & \cellcolor{gray!10}{254} & \cellcolor{gray!10}{19.74}\\
+\hspace{1em}45-54 & 226 & 17.56\\
+\cellcolor{gray!10}{\hspace{1em}55-64} & \cellcolor{gray!10}{242} & \cellcolor{gray!10}{18.80}\\
+\hspace{1em}65-74 & 148 & 11.50\\
+\cellcolor{gray!10}{\hspace{1em}75-84} & \cellcolor{gray!10}{57} & \cellcolor{gray!10}{4.43}\\
+\hspace{1em}85-92 & 10 & 0.78\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Gender}}\\
+\cellcolor{gray!10}{\hspace{1em}Male} & \cellcolor{gray!10}{598} & \cellcolor{gray!10}{47.01}\\
+\hspace{1em}Female & 658 & 51.73\\
+\cellcolor{gray!10}{\hspace{1em}Other/Refused} & \cellcolor{gray!10}{16} & \cellcolor{gray!10}{1.26}\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Education}}\\
+\hspace{1em}H.S. or less & 362 & 28.46\\
+\cellcolor{gray!10}{\hspace{1em}Some college no degree} & \cellcolor{gray!10}{283} & \cellcolor{gray!10}{22.25}\\
+\hspace{1em}Undergraduate level degree & 461 & 36.24\\
+\cellcolor{gray!10}{\hspace{1em}Graduate level degree} & \cellcolor{gray!10}{166} & \cellcolor{gray!10}{13.05}\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Race}}\\
+\hspace{1em}White or Caucasian & 975 & 76.65\\
+\cellcolor{gray!10}{\hspace{1em}Black or African American} & \cellcolor{gray!10}{164} & \cellcolor{gray!10}{12.89}\\
+\hspace{1em}American Indian & 22 & 1.73\\
+\cellcolor{gray!10}{\hspace{1em}Asian} & \cellcolor{gray!10}{56} & \cellcolor{gray!10}{4.40}\\
+\hspace{1em}Other & 55 & 4.32\\
+\addlinespace[0.3em]
+\multicolumn{3}{l}{\textbf{Party ID}}\\
+\cellcolor{gray!10}{\hspace{1em}Republican} & \cellcolor{gray!10}{540} & \cellcolor{gray!10}{42.59}\\
+\hspace{1em}Democrat & 566 & 44.64\\
+\cellcolor{gray!10}{\hspace{1em}Independent} & \cellcolor{gray!10}{162} & \cellcolor{gray!10}{12.78}\\
+\bottomrule
+\end{tabular}}
+\endgroup{}
+
+}
+
+\end{table}%
+
+\textsubscript{Source:
+\href{https://isaiahespi.github.io/rea-paper/index.qmd.html}{Article
+Notebook}}
+
+\pagebreak
 
@@
 \begin{CSLReferences}{1}{1}
-\bibitem[\citeproctext]{ref-knuth84}
-Knuth, Donald E. 1984. {``Literate Programming.''} \emph{Comput. J.}
-27(2): 97--111.
-doi:\href{https://doi.org/10.1093/comjnl/27.2.97}{10.1093/comjnl/27.2.97}.
+\bibitem[\citeproctext]{ref-abbate2020a}
+Abbate, Andrea. 2020. {``39 {Ways Election Offices} Are {Responding} to
+{COVID-19}.''}
+\url{https://www.techandciviclife.org/covid-19-responses/}.
+
+\bibitem[\citeproctext]{ref-atkeson2007}
+Atkeson, Lonna Rae, and Kyle L. Saunders. 2007. {``The {Effect} of
+{Election Administration} on {Voter Confidence}: {A Local Matter}?''}
+\emph{PS: Political Science \& Politics} 40(4): 655--60.
+doi:\href{https://doi.org/10.1017/S1049096507071041}{10.1017/S1049096507071041}.
+
+\bibitem[\citeproctext]{ref-bowler2024}
+Bowler, Shaun, and Todd Donovan. 2024. {``Confidence in {US Elections
+After} the {Big Lie}.''} \emph{Political Research Quarterly} 77(1):
+283--96.
+doi:\href{https://doi.org/10.1177/10659129231206179}{10.1177/10659129231206179}.
+
+\bibitem[\citeproctext]{ref-brennancenterforjustice2024}
+Brennan Center for Justice. 2024. \emph{Local {Election Officials
+Survey} --- {May} 2024 \textbar{} {Brennan Center} for {Justice}}.
+Brennan Center Research Department.
+\url{https://www.brennancenter.org/our-work/research-reports/local-election-officials-survey-may-2024}
+(November 5, 2024).
+
+\bibitem[\citeproctext]{ref-carter2024}
+Carter, Luke, Ashlan Gruwell, J Quin Monson, and Kelly D Patterson.
+2024. {``From {Confidence} to {Convenience}: {Changes} in {Voting
+Systems}, {Donald Trump}, and {Voter Confidence}.''} \emph{Public
+Opinion Quarterly} 88: 516--35.
+doi:\href{https://doi.org/10.1093/poq/nfae034}{10.1093/poq/nfae034}.
+
+\bibitem[\citeproctext]{ref-cikara2014}
+Cikara, Mina, and Jay J Van Bavel. 2014. {``The {Neuroscience} of
+{Intergroup Relations}.''} \emph{Perspectives on Psychological Science}
+9(3): 245--74.
+
+\bibitem[\citeproctext]{ref-claassen2008}
+Claassen, Ryan L., David B. Magleby, J. Quin Monson, and Kelly D.
+Patterson. 2008. {``{`{At Your Service}'}: {Voter Evaluations} of {Poll
+Worker Performance}.''} \emph{American Politics Research} 36(4):
+612--34.
+doi:\href{https://doi.org/10.1177/1532673X08319006}{10.1177/1532673X08319006}.
+
+\bibitem[\citeproctext]{ref-coll2024a}
+Coll, Joseph A, and Christopher J Clark. 2024. {``A {Racial Model} of
+{Electoral Reform}: {The Relationship} Between {Restrictive Voting
+Policies} and {Voter Confidence} for {Black} and {White Voters}.''}
+\emph{Public Opinion Quarterly} 88: 561--84.
+doi:\href{https://doi.org/10.1093/poq/nfae032}{10.1093/poq/nfae032}.
+
+\bibitem[\citeproctext]{ref-conde2020}
+Conde, Ximena. 2020. {``Philly Area Counties Say Efforts to Recruit Poll
+Workers for {Election Day} Are Paying Off.''} \emph{WHYY NPR}.
+\url{https://whyy.org/articles/philly-area-counties-say-efforts-to-recruit-poll-workers-for-election-day-are-paying-off/}.
+
+\bibitem[\citeproctext]{ref-cook2005}
+Cook, Timothy E., and Paul Gronke. 2005. {``The {Skeptical American}:
+{Revisiting} the {Meanings} of {Trust} in {Government} and {Confidence}
+in {Institutions}.''} \emph{The Journal of Politics} 67(3): 784--803.
+doi:\href{https://doi.org/10.1111/j.1468-2508.2005.00339.x}{10.1111/j.1468-2508.2005.00339.x}.
+
+\bibitem[\citeproctext]{ref-cooter2024}
+Cooter, Amy. 2024. {``Veterans and {Extremism}: {From Militias} to
+{January} 6th and {Real Patriots} \textbar{} {Middlebury Institute} of
+{International Studies} at {Monterey}.''}
+\url{https://www.middlebury.edu/institute/academics/centers-initiatives/ctec/ctec-publications/veterans-and-extremism-militias-january-6th}.
+
+\bibitem[\citeproctext]{ref-cooter2013}
+Cooter, Amy B. 2013. {``Americanness, {Masculinity}, and {Whiteness}:
+{How Michigan Militia Men Navigate Evolving Social Norms}.''} Thesis.
+\url{http://deepblue.lib.umich.edu/handle/2027.42/98077}.
+
+\bibitem[\citeproctext]{ref-corrigan2002}
+Corrigan, Patrick W., David Rowan, Amy Green, Robert Lundin, Philip
+River, Kyle Uphoff-Wasowski, Kurt White, and Mary Anne Kubiak. 2002.
+{``Challenging {Two Mental Illness Stigmas}: {Personal Responsibility}
+and {Dangerousness}.''} \emph{Schizophrenia Bulletin} 28(2): 293--309.
+doi:\href{https://doi.org/10.1093/oxfordjournals.schbul.a006939}{10.1093/oxfordjournals.schbul.a006939}.
+
+\bibitem[\citeproctext]{ref-daniller2019}
+Daniller, Andrew M, and Diana C Mutz. 2019. {``The {Dynamics} of
+{Electoral Integrity}: {A Three-Election Panel Study}.''} \emph{Public
+Opinion Quarterly} 83(1): 46--67.
+doi:\href{https://doi.org/10.1093/poq/nfz002}{10.1093/poq/nfz002}.
+
+\bibitem[\citeproctext]{ref-doubek2024}
+Doubek, James. 2024. {``States and Cities Beef up Security to Prepare
+for Potential Election-Related Violence.''} \emph{NPR: 2024 Election}.
+\url{https://www.npr.org/2024/11/04/nx-s1-5178083/national-guard-police-election-security}
+(November 5, 2024).
+
+\bibitem[\citeproctext]{ref-dunn2018}
+Dunn, Amina. 2018. {``Elections in {America}: {Concerns Over Security},
+{Divisions Over Expanding Access} to {Voting}.''}
+\url{https://www.pewresearch.org/politics/2018/10/29/elections-in-america-concerns-over-security-divisions-over-expanding-access-to-voting/}.
+
+\bibitem[\citeproctext]{ref-edlin2024}
+Edlin, Ruby, and Lawrence Norden. 2024. {``Poll of {Election Officials
+Finds Concerns About Safety}, {Political Interference} \textbar{}
+{Brennan Center} for {Justice}.''}
+\url{https://www.brennancenter.org/our-work/analysis-opinion/poll-election-officials-finds-concerns-about-safety-political}.
+
+\bibitem[\citeproctext]{ref-ferrer2024}
+Ferrer, Joshua, Daniel M Thompson, and Rachel Orey. 2024. \emph{Election
+{Official Turnover Rates} from 2000--2024}. Bipartisan Policy Center.
+\url{https://bipartisanpolicy.org/download/?file=/wp-content/uploads/2024/04/WEB_BPC_Elections_Admin_Turnover_R01.pdf}.
+
+\bibitem[\citeproctext]{ref-giles2021}
+Giles, Ben. 2021. {``Arizona {Recount Of} 2020 {Election Ballots Found
+No Proof Of Corruption}.''} \emph{NPR: 2024 Election}.
+\url{https://www.npr.org/2021/09/25/1040672550/az-audit}.
+
+\bibitem[\citeproctext]{ref-hall2009}
+Hall, Thad E., J. Quin Monson, and Kelly D. Patterson. 2009. {``The
+{Human Dimension} of {Elections}: {How Poll Workers Shape Public
+Confidence} in {Elections}.''} \emph{Political Research Quarterly}
+62(3): 507--22.
+doi:\href{https://doi.org/10.1177/1065912908324870}{10.1177/1065912908324870}.
+
+\bibitem[\citeproctext]{ref-hall2007}
+Hall, Thad, J. Quin Monson, and Kelly D. Patterson. 2007. {``Poll
+{Workers} and the {Vitality} of {Democracy}: {An Early Assessment}.''}
+\emph{PS: Political Science \& Politics} 40(4): 647--54.
+doi:\href{https://doi.org/10.1017/S104909650707103X}{10.1017/S104909650707103X}.
+
+\bibitem[\citeproctext]{ref-hardy2019}
+Hardy, Molly M., Calvin R. Coker, Michelle E. Funk, and Benjamin R.
+Warner. 2019. {``Which Ingroup, When? {Effects} of Gender, Partisanship,
+Veteran Status, and Evaluator Identities on Candidate Evaluations.''}
+\emph{Communication Quarterly} 67(2): 199--220.
+doi:\href{https://doi.org/10.1080/01463373.2019.1573201}{10.1080/01463373.2019.1573201}.
+
+\bibitem[\citeproctext]{ref-herndon2020}
+Herndon, Astead W. 2020. {``{LeBron James} and a {Multimillion-Dollar
+Push} for {More Poll Workers}.''} \emph{The New York Times: U.S.}
+\url{https://www.nytimes.com/2020/08/24/us/politics/lebron-james-poll-workers.html}
+(November 13, 2024).
+
+\bibitem[\citeproctext]{ref-herrnson2009}
+Herrnson, Paul S., Richard G. Niemi, and Michael J. Hanmer. 2009.
+\emph{Voting Technology : The Not-so-Simple Act of Casting a Ballot}.
+Washington, D.C: Brookings Institution Press.
+
+\bibitem[\citeproctext]{ref-hipes2016}
+Hipes, Crosby, Jeffrey Lucas, Jo C. Phelan, and Richard C. White. 2016.
+{``The Stigma of Mental Illness in the Labor Market.''} \emph{Social
+Science Research} 56: 16--25.
+doi:\href{https://doi.org/10.1016/j.ssresearch.2015.12.001}{10.1016/j.ssresearch.2015.12.001}.
+
+\bibitem[\citeproctext]{ref-hooghe2018}
+Hooghe, Marc. 2018. {``Trust and {Elections}.''} In \emph{The {Oxford
+Handbook} of {Social} and {Political Trust}}, ed. Eric M. Uslaner.
+Oxford University Press, 0.
+doi:\href{https://doi.org/10.1093/oxfordhb/9780190274801.013.17}{10.1093/oxfordhb/9780190274801.013.17}.
+
+\bibitem[\citeproctext]{ref-jensen2022a}
+Jensen, Michael, Elizabeth Yates, and Sheehan Kane. 2022.
+\emph{Radicalization in the {Ranks}: {An Assessment} of the {Scope} and
+{Nature} of {Criminal Extremism} in the {United States Military}}.
+{National Consortium for the Study of Terrorism and Responses to
+Terrorism (START): College Park}.
+\url{https://www.start.umd.edu/pubs/Radicalization\%20in\%20the\%20Ranks_April\%202022.pdf}.
+
+\bibitem[\citeproctext]{ref-kleykamp2015}
+Kleykamp, Meredith, and Crosby Hipes. 2015. {``Coverage of {Veterans} of
+the {Wars} in {Iraq} and {Afghanistan} in the {U}.{S}. {Media}.''}
+\emph{Sociological Forum} 30(2): 348--68.
+doi:\href{https://doi.org/10.1111/socf.12166}{10.1111/socf.12166}.
+
+\bibitem[\citeproctext]{ref-kleykamp2018}
+Kleykamp, Meredith, Crosby Hipes, and Alair MacLean. 2018. {``Who
+{Supports U}.{S}. {Veterans} and {Who Exaggerates Their Support}?''}
+\emph{Armed Forces \& Society} 44(1): 92--115.
+doi:\href{https://doi.org/10.1177/0095327X16682786}{10.1177/0095327X16682786}.
+
+\bibitem[\citeproctext]{ref-kleykamp2023}
+Kleykamp, Meredith, Daniel Schwam, and Gilad Wenig. 2023. \emph{What
+{Americans Think About Veterans} and {Military Service}: {Findings} from
+a {Nationally Representative Survey}}. RAND Corporation.
+\url{https://www.rand.org/pubs/research_reports/RRA1363-7.html}.
+
+\bibitem[\citeproctext]{ref-levendusky2024}
+Levendusky, Matthew, Shawn Patterson Jr., Michele Margolis, Yotam Ophir,
+Dror Walter, and Kathleen Hall Jamieson. 2024. {``The {Long Shadow} of
+the {Big Lie}: {How Beliefs} about the {Legitimacy} of the 2020
+{Election Spill Over} onto {Future Elections}.''} \emph{Public Opinion
+Quarterly}: nfae047.
+doi:\href{https://doi.org/10.1093/poq/nfae047}{10.1093/poq/nfae047}.
+
+\bibitem[\citeproctext]{ref-lincoln2024}
+Lincoln, Sophie. 2024. {``Washoe {County} Staff Prepare for {Election
+Day}, Announce New Safety Feature at Polls.''}
+\url{https://mynews4.com/news/local/washoe-county-staff-prepare-for-election-day-announce-new-safety-feature-at-polls}
+(November 5, 2024).
+
+\bibitem[\citeproctext]{ref-loewenson2023}
+Loewenson, Irene. 2023. {``Mattis Says Vets at {Jan}. 6 {Capitol} Riot
+{`Don't Define the Military'}.''} \emph{Marine Corps Times: name}.
+\url{https://www.marinecorpstimes.com/news/your-marine-corps/2023/11/06/mattis-says-vets-at-jan-6-capitol-riot-dont-define-the-military/}.
+
+\bibitem[\citeproctext]{ref-maclean2014}
+MacLean, Alair, and Meredith Kleykamp. 2014. {``Coming {Home}:
+{Attitudes} Toward {U}.{S}. {Veterans Returning} from {Iraq}.''}
+\emph{Social Problems} 61(1): 131--54.
+doi:\href{https://doi.org/10.1525/sp.2013.12074}{10.1525/sp.2013.12074}.
+
+\bibitem[\citeproctext]{ref-magni2024}
+Magni, Gabriele, and Andrew Reynolds. 2024. {``Candidate {Identity} and
+{Campaign Priming}: {Analyzing Voter Support} for {Pete Buttigieg}'s
+{Presidential Run} as an {Openly Gay Man}.''} \emph{Political Research
+Quarterly} 77(1): 184--98.
+doi:\href{https://doi.org/10.1177/10659129231194325}{10.1177/10659129231194325}.
+
+\bibitem[\citeproctext]{ref-maidenberg1996}
+Maidenberg, David H. 1996. \emph{Recruiting {Poll Workers}}. Office of
+Election Administration, Federal Election Commission.
+\url{https://purl.fdlp.gov/GPO/gpo18585}.
+
+\bibitem[\citeproctext]{ref-maricopacountyelectionsdepartment2022}
+Maricopa County Elections Department. 2022. \emph{Correcting the
+{Record}: {Maricopa County}'s {In-Depth Analysis} of the {Senate
+Inquiry}}. Maricopa County, Arizona: {Maricopa County Elections
+Department and Office of the Recorder}.
+\url{https://elections.maricopa.gov/asset/jcr:a9e03750-0a8f-4162-859f-1d46ac54b485/Correcting\%20The\%20Record\%20-\%20January\%202022\%20Report.pdf}.
+
+\bibitem[\citeproctext]{ref-mena2020}
+Mena, Kelly. 2020. {``States Scramble to Recruit Thousands of Poll
+Workers Amid Pandemic Shortage \textbar{} {CNN Politics}.''}
+\url{https://www.cnn.com/2020/08/13/politics/poll-worker-shortage-2020-election/index.html}.
+
+\bibitem[\citeproctext]{ref-milton2021}
+Milton, Daniel, and Andrew Mines. 2021. \emph{{``{This} Is {War}:''}
+{Examining Military Experience Among} the {Capitol Hill Siege
+Participants}}. George Washington University.
+doi:\href{https://doi.org/10.4079/poe.04.2021.00}{10.4079/poe.04.2021.00}.
+
+\bibitem[\citeproctext]{ref-nadeau1993}
+Nadeau, Richard, and André Blais. 1993. {``Accepting the {Election
+Outcome}: {The Effect} of {Participation} on {Losers}' {Consent}.''}
+\emph{British Journal of Political Science} 23(4): 553--63.
+doi:\href{https://doi.org/10.1017/S0007123400006736}{10.1017/S0007123400006736}.
+
+\bibitem[\citeproctext]{ref-nadeem2024}
+Nadeem, Reem. 2024. {``Harris, {Trump Voters Differ Over Election
+Security}, {Vote Counts} and {Hacking Concerns}.''}
+\url{https://www.pewresearch.org/politics/2024/10/24/harris-trump-voters-differ-over-election-security-vote-counts-and-hacking-concerns/}
+(November 5, 2024).
+
+\bibitem[\citeproctext]{ref-nevadasecretaryofstate2023}
+Nevada Secretary of State. 2023. {``Governor {Joe Lombardo}, {Secretary}
+of {State Francisco V}. {Aguilar} Sign {Election Worker Protection Bill}
+into Law.''}
+\url{https://www.nvsos.gov/sos/Home/Components/News/News/3368/309?backlist=\%2Fsos}
+(November 5, 2024).
+
+\bibitem[\citeproctext]{ref-nflfootballoperations2022}
+NFL Football Operations. 2022. {``Vet the {Vote}.''}
+\url{https://operations.nfl.com/inside-football-ops/social-justice/vet-the-vote/}.
+
+\bibitem[\citeproctext]{ref-pape2024}
+Pape, Robert A., Keven G. Ruby, Kyle D. Larson, and Kentaro Nakamura.
+2024. {``Understanding the {Impact} of {Military Service} on {Support}
+for {Insurrection} in the {United States}.''} \emph{Journal of Conflict
+Resolution}: 00220027241267216.
+doi:\href{https://doi.org/10.1177/00220027241267216}{10.1177/00220027241267216}.
+
+\bibitem[\citeproctext]{ref-powerthepolls2020}
+Power the Polls. 2020. {``Power {The Polls Launches First-of-its-Kind
+Effort} to {Recruit New Wave} of {Poll Workers} for {Election Day}.''}
+\url{https://www.powerthepolls.org/press-release-2020-06-30}.
+
+\bibitem[\citeproctext]{ref-ross2020}
+Ross, Doug. 2020. {``Porter {County} Election Officials Recruit Students
+to Work Polls.''} \emph{nwitimes.com}.
+\url{https://www.nwitimes.com/news/local/porter/porter-newsletter/porter-county-election-officials-recruit-students-to-work-polls/article_b2f1aaf8-1e5f-550e-bbbe-113dcb679f7e.html}.
+
+\bibitem[\citeproctext]{ref-sances2015}
+Sances, Michael W., and Charles Stewart. 2015. {``Partisanship and
+Confidence in the Vote Count: {Evidence} from {U}.{S}. National
+Elections Since 2000.''} \emph{Electoral Studies} 40: 176--88.
+doi:\href{https://doi.org/10.1016/j.electstud.2015.08.004}{10.1016/j.electstud.2015.08.004}.
+
+\bibitem[\citeproctext]{ref-steinhauer2020}
+Steinhauer, Jennifer. 2020. {``Veterans {Fortify} the {Ranks} of
+{Militias Aligned With Trump}'s {Views}.''} \emph{The New York Times:
+U.S.}
+\url{https://www.nytimes.com/2020/09/11/us/politics/veterans-trump-protests-militias.html}.
+
+\bibitem[\citeproctext]{ref-stewart2022}
+Stewart, Charles, III. 2022. {``Trust in {Elections}.''} \emph{Daedalus}
+151(4): 234--53.
+doi:\href{https://doi.org/10.1162/daed_a_01953}{10.1162/daed\_a\_01953}.
+
+\bibitem[\citeproctext]{ref-studentveteransofamerica2020}
+Student Veterans of America. 2020. {``Volunteer to {Power The Polls}.''}
+\url{https://studentveterans.org/news/power-the-polls/}.
+
+\bibitem[\citeproctext]{ref-vanbavel2021}
+Van Bavel, Jay J., and Dominic J. Packer. 2021. \emph{The Power of Us :
+Harnessing Our Shared Identities to Improve Performance, Increase
+Cooperation, and Promote Social Harmony}. First edition. New York:
+Little, Brown Spark.
+
+\bibitem[\citeproctext]{ref-wang2022}
+Wang, Hansi Lo. 2022. {``The Midterm Elections Need Workers. {Teens},
+Veterans and Lawyers Are Stepping Up.''} \emph{NPR: 2024 Election}.
+\url{https://www.npr.org/2022/09/07/1120065844/midterms-elections-poll-worker-shortage-recruitment}.
+
+\bibitem[\citeproctext]{ref-wetheveterans2022}
+We The Veterans. 2022. {``Launch of {Vet} the {Vote}.''}
+\url{https://vetthe.vote/blogs/news/launch-of-vet-the-vote}.
+
+\bibitem[\citeproctext]{ref-wire2024}
+Wire, Sarah D., Phillip M. Bailey, Mary Jo Pitzl, Trevor Hughes, Erik
+Pfantz, John Wisely, and Deborah Barfield Berry. 2024. {``Counting Votes
+Is Now a Dangerous Job: How It Feels for Frontline, Swing-State
+Workers.''}
+\url{https://www.usatoday.com/story/news/politics/elections/2024/10/28/election-workers-2024-hostility/75586254007/}
+(November 5, 2024).
+
+\bibitem[\citeproctext]{ref-xiao2016}
+Xiao, Y. Jenny, Géraldine Coppin, and Jay J. Van Bavel. 2016.
+{``Perceiving the {World Through Group-Colored Glasses}: {A Perceptual
+Model} of {Intergroup Relations}.''} \emph{Psychological Inquiry} 27(4):
+255--74. \url{https://www.jstor.org/stable/26159704} (October 26, 2024).
+
+\bibitem[\citeproctext]{ref-xiao2012}
+Xiao, Y. Jenny, and Jay J. Van Bavel. 2012. {``See {Your Friends Close}
+and {Your Enemies Closer}: {Social Identity} and {Identity Threat Shape}
+the {Representation} of {Physical Distance}.''} \emph{Personality and
+Social Psychology Bulletin} 38(7): 959--72.
+doi:\href{https://doi.org/10.1177/0146167212442228}{10.1177/0146167212442228}.
 
@@
 
-\processdelayedfloats
 \end{document}

### 2024-11-21 index.qmd
working on analysis. rough draft needs trim

@@
 title: title
+subtitle: subtitle
 shorttitle: A Short title # aog-article-pdf
@@
 date: "2024-10-16"
+date-modified: today
 crossref:
@@
       latex-env: hypothesis # required for PDF format
-
 ---
@@
 
-## Intro
+## Introduction
 
@@
 Although election officials undertake great efforts to enhance the trustworthiness of election administration, public *trust* in elections is a psychological construct influenced by many things outside of election official control such as partisanship or elite rhetoric [@hooghe2018; @sances2015].
-Moreover, a person's evaluation of the election in hindsight is often influenced by the election outcome itself [@daniller2019 ;@stewart2022].
+Moreover, a person's evaluation of the election in hindsight is often influenced by the election outcome itself [@daniller2019; @stewart2022].
 Thus, measures taken by election officials can be undermined, trivialized, or made irrelevant depending on how one feels after the election results have come out.
@@
 -   moreover, broken down by other demographic variables such as race, gender, education, etc.
--   holding these factors constant demonstrates a [increased/decreased] likelihood that a respondent's confidence would likely [increase/decrease], expectations of fraud would likely [increase/decrease], and concerns for safety would lessen among those in the treatment group compared to those in the control.
+-   holding these factors constant demonstrates a \[increased/decreased\] likelihood that a respondent's confidence would likely \[increase/decrease\], expectations of fraud would likely \[increase/decrease\], and concerns for safety would lessen among those in the treatment group compared to those in the control.
 These results allow us to attribute the differences to the treatment stimulus, namely, the prospect of having veterans serve as election staff or volunteers.
-
-[^1]: I adopt a distinction made between *trustworthiness* and *trust* in elections [@stewart2022].
-The "*worthiness*" of one's trust in the conduct and administration of elections is based on the extent that outcomes of an election reasonably follow the rules prescribed and can be adjudicated as such.
-"If the process is conducted fairly and competently, and the results are determined by the actions of voters...we can call this a trustworthy election" [@stewart2022, 237].
-*Trustworthiness* is distinguished from *trust* as a psychological construct, "...the conclusion reached by the public about the functioning of the process" [@stewart2022, 237].
-To put in other terms, trustworthiness is built by the structure, procedures, and practices of the institution, in this case election administration.
-The public's trust in elections, however, is amendable to an indefinite number of factors that may be seemingly unrelated to the formal procedures of election administration.
-To illustrate, my car is trustworthy because I've known it to function quite well as a car should; it passes whatever criteria upon inspection, its sufficiently fueled, and is in generally good working order.
-I have every reason to deem it worthy of my trust.
-However, I don't trust my car because I am sure it is haunted.
-
-[^2]: It is important to point out here that election administration is just one institution that interacts with many other institutions and processes which form the electoral system *writ large* [@stewart2022].
-The way in which I discuss the institution of election administration, as well as the way in which I discuss and distinguish public trust in elections from broader conceptions of public trust, is borrowed substantively from @stewart2022's conceptual framework of the same.
-Distinctions between *trust* and *trustworthiness* and the notion of election administration as an institution are already apparent inspirations convenient for situating the theory of this research inquiry.
 
@@
 In addition to ensuring election admin offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections.
-In particular, voting technology [@herrnson2009] and election worker competence was a of interest in election studies [@classen2008; @hall2009; @hall2007].
+In particular, voting technology [@herrnson2009] and election worker competence was a of interest in election studies [@claassen2008; @hall2009; @hall2007].
 Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007].
@@
 
-[^3]: There's little that could justify a conceptual distinction between public trust pre-election and public trust post-election.
-The temporal element renders the difference between pre- and post-election operative rather than conceptual.
-
-[^4]: Note that *anxiety* is taken to be the inverse of *trust and confidence*, as in, one who is less confident in this or that is thereby more anxious over the matter in question.
-As such, anxiety may equivalently be discussed as trust/confidence without issue except for framing of said discussion.
-Electoral anxiety is used in place of electoral trust/confidence simply to emphasize the anticipatory nature of the attitudes in question.
-
 The primary interest of this study concerns *election anxieties*, which is distinguished into two categories: fairness and accuracy, and voter safety.
@@
 Regardless of the measures taken by election officials to boost public confidence in the *trustworthiness* of election administration (e.g., conducting audits, testing election machines), public *trust* and confidence in elections more generally is apt to shift dramatically post-election based on factors such as partisanship, elite rhetoric, particular state policies, and more [@nadeau1993; @carter2024; @coll2024a].
-Moreover, prior research has found that evaluation of election workers themselves are an important factor when it comes to levels of public confidence in the electoral process [@hall2007; @hall2009; @classen2008].
+Moreover, prior research has found that evaluation of election workers themselves are an important factor when it comes to levels of public confidence in the electoral process [@hall2007; @hall2009; @claassen2008].
 Such studies focused on the quality of the voter experience with reference to the interaction between voter and election worker.
@@
 The reason why veterans arose as a special subset of the population to consider for this inquiry is because there was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021.
-After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterants2022; @nflfootballoperations2022].
-Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts[^4] [@powerthepolls2020; @herndon2020].
+After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterans2022; @nflfootballoperations2022].
+Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts[^5] [@powerthepolls2020; @herndon2020].
 Generally, however, recruitment efforts cast a wide net, indiscriminate of who applies [@ross2020; @conde2020].
-Recruitment efforts in 2022 targeted young students, lawyers, and military veterans [@wang2022].
 
 One can speculate that the motivation to associate military veterans with civic engagement and democracy may be intended to counter negative perceptions and impressions given by the proportion of veteran service members arrested for taking part in the events on January 6th [@milton2021; @loewenson2023; @jensen2022a].
-Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results[^5] (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024].
+Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results[^6] (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024].
 This is in addition to a strengthened association portrayed in media outlets between military veterans and militias [@steinhauer2020].
@@
 
-[^4]: Prior to 2021, I found one online recruitment brochure intent on recruiting veterans to serve as election workers [@studentveteransofamerica2020].
-
-[^5]: The cited study defined "insurrectionist sentiments" as, "...willingness to support violent efforts to overturn the results of an election in favor of another, unelected political leader." [@pape2024, 7].
-It should be noted, however, that despite the general definition, the operative items used to measure such sentiments ask about Donald Trump specifically, not an "unelected political leader".
-
 ## Research Design and Method
@@
 citizens 18 years of age or older.
-Survey participants were randomly assigned to read one of two fabricated news articles (i.e., vignettes) about recruitment efforts for election jobs.
-
-Participants read either a treatment or control vignette, which was a fabricated news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election.
-The vignettes were identical save for mention of the group targeted for election work recruitment efforts.
-The treatment vignette focused on the announcement of a program by county election officials designed to recruit military veterans and their family members from the community, whereas the control vignette omitted mention of "military veterans and their family members", leaving in place "members of the community"[^6].
-It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignettes due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
-In addition, the survey includes a series of items which ask specifically about Maricopa County, AZ and a comparable series of questions about one's local area[^7].
-
-[^6]: Complete text of treatment and control vignettes are included in the Appendix
-
-[^7]: The setting of the vignettes and inclusion of duplicate questions in the survey are highlighted and discussed later as a potential limitation.
-
-Over the past two decades it became commonplace for national polls to gauge public confidence in election administration by asking some variety of the question, "How confident are you that your vote [will be/was] counted as you intended in the most recent election?" [@hall2009; @sances2015; @stewart2022].
-In addition, since 2008, the Survey of the Performance of American Elections (SPAE) has included a good number of relevant questions to more thoroughly assess trust and confidence in election administration.
-Such questions inquire into the voter experience with the institution more directly.
-This study borrows, modifies, or takes inspiration from certain questions found within the 2022 SPAE and other survey items used by the Pew Research Center [@dunn2018].
-These survey items comprise the dependent variables[^8].
-
-[^8]: All survey items are included in the Appendix.
-
-The outcomes of interest (i.e., dependent variables) are broadly referred to as *election anxieties*, but more specifically refer to concern over fairness and accuracy of the election administration; expectations of fraudulent activity intent on manipulating the electoral outcomes; and concern for voter safety, i.e., comfort voting in-person as it relates to expectations of violence, threats, or intimidation.
-
-The first outcome of interest regards trust and confidence in the electoral process, which refers to trust and confidence in the integrity and security of the electoral systems, administration, technology, and people or organizations to fairly and accurately conduct elections.
-Survey items  measured the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats.
-The first hypothesis is as follows:
-
-::: {#hyp-1}
-
-### Hypothesis 1
-
-Trust and confidence in election administration will be higher among those who were presented information about efforts to recruit veterans as election workers compared to those who were not
-
-:::
-
-Survey participants also responded to questions asking about expectations of fraudulent activity intent on manipulating the electoral outcome.
-
-The second outcome of interest regards an individual's personal safety concerns about the prospect of voting in-person at a polling site.
-That is, the extent people feel safe enough to cast a vote at polling sites free from violence, threats of violence, or intimidation.
 
@@
 Asking participants whether they supported programs intent on recruiting veterans to work as election staff would garner support regardless of the target group.
-Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require survey questions designed to determine whether veterans have any special effect on electoral confidence and voter safety distinct from the generally high admiration observed most often.
+Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require a survey experiment and questions designed to determine whether veterans have any special effect on electoral confidence and voter safety distinct from the generally high admiration observed most often.
+
+Survey participants were randomly assigned to read one of two fabricated news articles (i.e., vignettes) about recruitment efforts for election jobs.
+Participants read either a treatment or control vignette, which was a fabricated news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election.
+The treatment vignette referred to a program designed to recruit veterans and their family members and describes an interviewee "Jordan Braxton" as an Army veteran; whereas the control vignette simply omitted any mention of veterans and their family members, and didn't describe "Jordan Braxton" as an Army veteran.
+Beyond those small differences and the headlines, the article vignettes are identical.
+Any effects can be attributed to the information about veterans in the treatment vignette[^7].
+
+It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignettes due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
+In addition, the survey includes a series of items which ask specifically about Maricopa County, AZ and a comparable series of questions about one's local area[^8].
+
+Over the past two decades it became commonplace for national polls to gauge public confidence in election administration by asking some variety of the question, "How confident are you that your vote \[will be/was\] counted as you intended in the most recent election?" [@hall2009; @sances2015; @stewart2022].
+In addition, since 2008, the Survey of the Performance of American Elections (SPAE) has included a good number of relevant questions to more thoroughly assess trust and confidence in election administration.
+Such questions inquire into the voter experience with the institution more directly.
+This study borrows, modifies, or takes inspiration from certain questions found within the 2022 SPAE and other survey items used by the Pew Research Center [@dunn2018].
+These survey items comprise the dependent variables[^9].
+
+The outcomes of interest (i.e., dependent variables) are broadly referred to as *election anxieties*, but more specifically refer to confidence over fairness and accuracy of the election administration; expectations of fraudulent activity intent on manipulating the electoral outcomes; and concern for voter safety, i.e., comfort voting in-person as it relates to expectations of violence, threats, or intimidation.
+The following presents multiple one-sided directional hypotheses.
+Previous research on public perception and regard for U.S.
+military veterans gives credence to the directional hypotheses [@kleykamp2018; @kleykamp2023].
+
+The first outcome of interest regards *trust and confidence* in election administration, which includes the integrity and security of the electoral process, administration, technology, and people or organizations to fairly and accurately conduct elections.
+Survey items measured the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, as well as confidence that the voting process will be fair.
+
+The first hypothesis is as follows:
+
+$H_{1}:$ Trust and confidence in election administration will be higher among those who were presented information about efforts to recruit veterans as election workers compared to those who were not
+
+In total, six survey items measure different aspects of trust and confidence in election administration.
+These items were analyzed individually but were also transformed into a composite scale of trust and confidence.
 
 The literature concerning public regard for veterans gives substantial reason to expect that publicized efforts to recruit veterans to work as election staff and volunteers would have the effect of easing election anxieties.
+As such, survey participants also responded to a series of questions that inquired into expectations of electoral fraud---i.e., fraudulent activity intent on manipulating the electoral outcome.
 
-This is a one-sided directional hypothesis. Previous research on public perception and regard for U.S. military veterans gives credence to the directional hypothesis [@kleykamp2018; @kleykamp2023].
+Note, however, that an *expectation* of electoral fraud implies a degree of distrust more so than an agitated state of anxiety over the *potential* for electoral fraud.
+Conceptually, this may be considered a particular kind of 'anxiety' given that is it pre-election (hence, an expectation), however, not necessarily.
+A person may be rather confident with regard to how much they distrust the integrity of electoral administration, resulting in such expectations.
 
-Simply put, anything special about veterans that influences people's trust and confidence in election administration is expected to be observable in participants' survey responses.
-However, exactly what makes veterans special in this regard will not; this study did not inquire into details of public perception about veterans specifically (e.g., positive stereotypes, typical characteristics).
+For instance, the first item of the 5-item series asks participants to report their expectation that "There will be voter fraud, that is, people who are not eligible to vote will vote or vote more than once" on a 4-option response scale ranging from "Not likely at all" to "very likely".
+This statement, as well as the rest in the series, asserts an expected compromise of election integrity, which speaks to the trustworthiness of the institution.
+What the individual expects, more or less, is that electoral fraud will occur, implying that fraudulent attempts will be successful.
 
-The goal was to determine whether there is anything special in having veterans volunteer as election staff (i.e., poll workers).
+It was expected that the experimental stimulus would result in lower expectation for electoral fraud among those who read the treatment vignette compared to those who read the control vignette.
+The second hypothesis is,
+
+$H_{2}:$ Expectations of electoral fraud will be lower among those who were presented information about efforts to recruit veterans as election workers compared to those who were not
+
+Another outcome of interest regards concerns about voting in-person at a polling site, i.e., voter safety.
+That is, the extent people feel that voters are safe enough to cast a vote at polling sites free from violence, threats of violence, or intimidation.
+Two survey items use slightly different questions to inquire about the same essential issue—i.e., perceptions of physical safety at the polls.
+The third hypothesis follows,
+
+$H_{3}:$ Concerns for voter safety be lower among those who are presented information about efforts to recruit veterans as election workers compared to those who are not
+
+Another outcome of interest concerned how particular actions of election officials, or circumstances at polling sites, would impact the confidence of election integrity as well as voter safety *from the perspective of survey respondents*.
+Survey participants responded to a series of six statements, all prefaced with the same question, "Regardless of whether any of these are actually the case, how would the following impact your confidence in the fairness and accuracy of elections conducted this November?" The six statements were,
+
+1.  Election officials test every machine used in the election to ensure they are secure.
+2.  Election officials conduct audits of ballots after every election to confirm the results were accurate.
+3.  Poll watchers affiliated with the political parties or candidates observe the election.
+4.  Election staff and volunteers include military veterans and their family members from the community.
+5.  Election staff and volunteers include lawyers from the community.
+6.  Election staff and volunteers include college students from the community.
+
+For each statement, survey participants responded by selecting one of five response options:
+
+1.  Decrease confidence a lot
+2.  Decrease confidence somewhat
+3.  No impact on confidence
+4.  Increase confidence somewhat
+5.  Increase confidence a lot
+
+It was expected that respondents would estimate stronger impact on their confidence given they were assigned to read the treatment vignette compared to those who were not. Thus, the hypothesis is,
+
+$H_{4}:$ Respondents who read the treatment vignette will report stronger impact on their personal confidence in fairness and accuracy of election administration when veterans are stated to be included among election staff and volunteers compared to those who read the control vignette.
+
+The extent people believe veterans are more trustworthy as election workers than non-veterans in general is difficult without comparable groups to consider.
+Recruitment efforts in 2022 targeted young students, lawyers, and military veterans [@wang2022].
+Thus, lawyers and college students were selected as two groups for which responses could be compared between different statement versions.
+
+The goal was to determine whether there is anything special in having veterans volunteer as election staff (i.e., poll workers) compared to other groups.
 That is, does it make any difference in terms of concerns over election security, fairness, and voter safety to include veterans as election staff and volunteers compared to other groups?
-The extent people believe veterans are more trustworthy as election workers than non-veterans in general is difficult without comparable groups to consider.
+The fourth hypothesis, irrespective of the experimental stimulus, reads,
 
-A series of survey questions sought to determine whether support for veterans as election staff would be notably higher when compared to other relatively neutral groups.
+$H_{5}:$ Respondents who read the treatment vignette will report stronger impact on their personal confidence in fairness and accuracy of election administration when veterans are stated to be included among election staff and volunteers compared to identical statements about lawyers or college students.
 
-It was hypothesized that different versions of statements in a series of survey questions would result in consistent response effects.
+## Results
 
@@
 
-# Appendix {.appendix}
+## Conclusion
+
+### Limitations
+
+-   limitations: interpretations of the treatment effect are limited.
+-   The sample may not be generalizable to the population.
+-   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts.
+-   Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
+-   Moreover, results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons.
+- First, the vignettes and many survey questions ask about Maricopa County, AZ specifically.
+Adding a specific county in the vignette adds in a factor that cannot be accounted for without additional treatments that eliminate the setting as a potential influence.
+Moreover, the specificity of the setting adds in even more unexplained error---some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S.
+they've know nothing about.
+Adding the county undermines the confidence that treatment effects are solely attributable to veterans to an unknown degree.
+- Second, questions ask about one's own local community in addition to identical questions which asked about Maricopa County, AZ.
+Consequently, many questions within the questionnaire were duplicates with that one differences.
+This isn't uncommon in surveys, however in this case, it lengthened the survey to a degree that likely resulted in a higher drop off rate.
+More importantly, the quality of responses were likely diminished to some unknown extent.
+Although it is possible to compare questions asked about Maricopa County, AZ to questions about one's local area, the quality of that comparison is limited by the unknown extent of fatigue induced by answering the same questions twice.
+It wasn't just that some questions were asked multiple times, almost all of the questions were duplicated; after completing a long series on Maricopa County, participants then answered the same questions about the local community.
+The rate to which participants dropped from the survey is \_\_\_, which suggests fatigue as an important factor.
+Survey fatigue is a known issue that should be taken into consideration.
+Comparison of treatment effects between the MC series and the local area series is undermined by the unknown influence that fatigue would have on response choices.
+Any differences couldn't confidently be attributed to "my area" vs Maricopa county.
+We also can't determine whether treatment effects are sustained when comparing the Maricopa County series to the local area series asked subsequently.
+We would have to assume the setting as irrelevant, which we can't reasonably do.
+
+\pagebreak
+
+## Appendix A: Survey Experiment Vignettes {#sec-appendix-a}
+
+::::: {#fig-vignettes .content-visible layout-ncol="2" when-format="html" unless-format="pdf"}
+::: {#fig-treatment}
+### Treatment Vignette
+
+| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
+| 
+|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
+As the U.S.
+general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
+| 
+|   Army veteran Jordan Braxton just joined the elections workforce.
+Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
+I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
+:::
+
+::: {#fig-control}
+### Control Vignette
+
+| **Local Residents Recruited for Election Jobs in Maricopa County**
+| 
+|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
+As the U.S.
+general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
+| 
+|   Jordan Braxton just joined the elections workforce.
+Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
+I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
+:::
+
+Fabricated Article Vignettes utilized as Experimental Stimulus
+:::::
+
+::::: {.content-hidden layout-ncol="2" unless-format="pdf"}
+<div>
+
+### Treatment Vignette
+
+| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
+| 
+|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
+As the U.S.
+general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
+| 
+|   Army veteran Jordan Braxton just joined the elections workforce.
+Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
+I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
+
+</div>
+
+<div>
+
+### Control Vignette
+
+| **Local Residents Recruited for Election Jobs in Maricopa County**
+| 
+|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
+As the U.S.
+general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
+| 
+|   Jordan Braxton just joined the elections workforce.
+Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
+I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
+
+Text of the Control Condition: Recruitment of Community Members
+
+</div>
+:::::
+
+## Appendix B: Sample Demographics {#sec-appendix-b}
 
 ::: {.content-visible when-format="html" unless-format="pdf"}
-
 ```{r}
@@
 ```
-
 :::
@@
 ::: {.content-hidden unless-format="pdf"}
-
 ```{r}
@@
 frqs <- data |> 
-  select(qset, age_cat, gender_3cat, educ_4cat, race, partyid_3cat) |>
+  select(group, qset, age_cat, gender_3cat, educ_4cat, race, partyid_3cat) |> 
   map(count_prop)
@@
                 col.names = c("Name", "n", "Pct")) |> 
-  kableExtra::pack_rows("Qset", 1, 2) |> 
-  kableExtra::pack_rows("Age", 3, 10) |> 
-  kableExtra::pack_rows("Gender", 11, 13) |> 
-  kableExtra::pack_rows("Education", 14, 17) |> 
-  kableExtra::pack_rows("Race", 18, 22) |> 
-  kableExtra::pack_rows("Party ID", 23, 25) |> 
+  kableExtra::pack_rows("Experiment Condition", 1, 2) |>
+  kableExtra::pack_rows("Question Set", 3, 4) |>
+  kableExtra::pack_rows("Age", 5, 12) |> 
+  kableExtra::pack_rows("Gender", 13, 15) |> 
+  kableExtra::pack_rows("Education", 16, 19) |> 
+  kableExtra::pack_rows("Race", 20, 24) |> 
+  kableExtra::pack_rows("Party ID", 25, 27) |> 
   kableExtra::kable_styling(
@@
 
-```{r}
-#| label: tbl-desc-pdf-2
-
-tbl.desc <- data |> 
-  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99"))) |> 
-  labelled::set_variable_labels(
-    age_cat = "Age group, in years",
-    gender_3cat = "Gender",
-    race = "Race",
-    educ_4cat = "Highest level of education completed",
-    milserv1 = "Prior service in the Armed Forces",
-    milserv2 = "Currently serving in the Armed Forces",
-    milservfam = "Member of immediate family served or is currently serving",
-    voted2020 = "Turnout in 2020",
-    choice2020 = "Vote Choice 2020",
-    voteintent = "Vote Intent 2024",
-    ideo = "Political Ideology",
-    ideolean = "Political Ideology, lean",
-    partyid_3cat = "Party ID"
-  ) |>
-  gtsummary::tbl_summary(
-    by = qset,
-    include = c(
-      age_cat,
-      gender_3cat,
-      race,
-      educ_4cat,
-      partyid_3cat,
-      ideo,
-      ideolean,
-      voted2020,
-      choice2020,
-      voteintent,
-      milserv1,
-      milserv2,
-      milservfam
-    ),
-    statistic = list(gtsummary::all_categorical() ~ "{n} ({p}%)"),
-    type = list(
-      milserv1 ~ "categorical",
-
-      milserv2 ~ "categorical",
-      milservfam ~ "categorical"
-    ),
-    missing = "no"
-  ) |>
-  gtsummary::add_n() |>
-  gtsummary::add_overall() |>
-  gtsummary::modify_header(label = "**Variable**") |>
-  gtsummary::bold_labels()
-
-gtsummary::as_kable_extra(
-  tbl.desc, 
-  booktabs = T,
-  digits = 2,
-  addtl_fmt = T,
-  linesep = ""
-) |> 
-  kableExtra::kable_styling(
-    latex_options = c("striped", "scale_down"),
-    font_size = 9)
-
-```
-
 :::
-
-## Conclusion
-
-### Limitations
-
--   limitations: interpretations of the treatment effect are limited.
-  -   The sample may not be generalizable to the population.
-  -   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts. 
-  -   Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
-  -   Moreover, results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons. 
-    -   First, the vignettes and many survey questions ask about Maricopa County, AZ specifically.
-Adding a specific county in the vignette adds in a factor that cannot be accounted for without additional treatments that eliminate the setting as a potential influence.
-Moreover, the specificity of the setting adds in even more unexplained error---some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S.
-they've know nothing about.
-Adding the county undermines the confidence that treatment effects are solely attributable to veterans to an unknown degree.
-    -   Second, questions ask about one's own local community in addition to identical questions which asked about Maricopa County, AZ.
-Consequently, many questions within the questionnaire were duplicates with that one differences.
-This isn't uncommon in surveys, however in this case, it lengthened the survey to a degree that likely resulted in a higher drop off rate.
-More importantly, the quality of responses were likely diminished to some unknown extent.
-Although it is possible to compare questions asked about Maricopa County, AZ to questions about one's local area, the quality of that comparison is limited by the unknown extent of fatigue induced by answering the same questions twice.
-It wasn't just that some questions were asked multiple times, almost all of the questions were duplicated; after completing a long series on Maricopa County, participants then answered the same questions about the local community.
-The rate to which participants dropped from the survey is ___, which suggests fatigue as an important factor.
-Survey fatigue is a known issue that should be taken into consideration.
-Comparison of treatment effects between the MC series and the local area series is undermined by the unknown influence that fatigue would have on response choices.
-Any differences couldn't confidently be attributed to "my area" vs Maricopa county.
-We also can't determine whether treatment effects are sustained when comparing the Maricopa County series to the local area series asked subsequently.
-We would have to assume the setting as irrelevant, which we can't reasonably do.
 
@@
 
-# Appendix A: Survey Experiment Vignettes {#sec-appendix-a}
+[^1]: I adopt a distinction made between *trustworthiness* and *trust* in elections [@stewart2022].
+The "*worthiness*" of one's trust in the conduct and administration of elections is based on the extent that outcomes of an election reasonably follow the rules prescribed and can be adjudicated as such.
+"If the process is conducted fairly and competently, and the results are determined by the actions of voters...we can call this a trustworthy election" [@stewart2022, 237].
+*Trustworthiness* is distinguished from *trust* as a psychological construct, "...the conclusion reached by the public about the functioning of the process" [@stewart2022, 237].
+To put in other terms, trustworthiness is built by the structure, procedures, and practices of the institution, in this case election administration.
+The public's trust in elections, however, is amendable to an indefinite number of factors that may be seemingly unrelated to the formal procedures of election administration.
+To illustrate, my car is trustworthy because I've known it to function quite well as a car should; it passes whatever criteria upon inspection, its sufficiently fueled, and is in generally good working order.
+I have every reason to deem it worthy of my trust.
+However, I don't trust my car because I am sure it is haunted.
 
-::::: {#fig-vignettes layout-ncol=2 .content-visible when-format="html" unless-format="pdf"}
-::: {#fig-treatment}
-### Treatment Vignette
+[^2]: It is important to point out here that election administration is just one institution that interacts with many other institutions and processes which form the electoral system *writ large* [@stewart2022].
+The way in which I discuss the institution of election administration, as well as the way in which I discuss and distinguish public trust in elections from broader conceptions of public trust, is borrowed substantively from @stewart2022's conceptual framework of the same.
+Distinctions between *trust* and *trustworthiness* and the notion of election administration as an institution are already apparent inspirations convenient for situating the theory of this research inquiry.
 
-| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Army veteran Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
+[^3]: There's little that could justify a conceptual distinction between public trust pre-election and public trust post-election.
+The temporal element renders the difference between pre- and post-election operative rather than conceptual.
 
-Text of the Treatment Condition: Recruitment of Veterans and Military Family Members
-:::
+[^4]: Note that *anxiety* is taken to be the inverse of *trust and confidence*, as in, one who is less confident in this or that is thereby more anxious over the matter in question.
+As such, anxiety may equivalently be discussed as trust/confidence without issue except for framing of said discussion.
+Electoral anxiety is used in place of electoral trust/confidence simply to emphasize the anticipatory nature of the attitudes in question.
 
-::: {#fig-control}
-### Control Vignette
+[^5]: The cited study defined "insurrectionist sentiments" as, "...willingness to support violent efforts to overturn the results of an election in favor of another, unelected political leader." [@pape2024, 7].
+It should be noted, however, that despite the general definition, the operative items used to measure such sentiments ask about Donald Trump specifically, not an "unelected political leader".
 
-| **Local Residents Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
+[^6]: Prior to 2021, I found one online recruitment brochure intent on recruiting veterans to serve as election workers [@studentveteransofamerica2020].
 
-Text of the Control Condition: Recruitment of Community Members
-:::
+[^7]: Complete text of treatment and control vignettes are included in the Appendix
 
-Fabricated Article Vignettes utilized as Experimental Stimulus
-:::::
+[^8]: The setting of the vignettes and inclusion of duplicate questions in the survey are highlighted and discussed later.
 
-::::: {#fig-vignettes layout-ncol=2 .content-hidden unless-format="pdf"}
-::: {#fig-treatment}
-### Treatment Vignette
-
-| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Army veteran Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
-
-Text of the Treatment Condition: Recruitment of Veterans and Military Family Members
-:::
-
-::: {#fig-control}
-### Control Vignette
-
-| **Local Residents Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
-
-Text of the Control Condition: Recruitment of Community Members
-:::
-
-Fabricated Article Vignettes utilized as Experimental Stimulus
-:::::
+[^9]: All survey items are included in the Appendix.

### 2024-11-21 index.qmd
revising and editing draft. make likert tables and plots

@@
 raw_spss_dict <- read.csv("data/raw_spss_dict.csv")
+```
+
+```{r}
+#| label: post_processing
+#| include: false
+
+# Some post-processing of the dataframe :::::::::::::::::::::::::::::::::::::###
+
+# code to recode levels "-99" in factor vars
+data <- data |> 
+  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99")))
+
+# recode factor levels 
+data <- data |> 
+  # use `pewmethods` to preserve order of factor levels
+  mutate(across(c(q19, q20, q21, q22, q23,q24, q25, q26,
+                  q30, q31, q32, q33, q34, q35, q36, q37), 
+                ~pewmethods::fct_case_when(
+    .x == "Not at all confident" |
+      .x == "Not at all committed" ~ "Not at all",
+    .x == "Not too confident" |
+      .x == "Not too committed"|
+      .x == "Not too concerned"|
+      .x == "Somewhat unconcerned" ~ "Not that much",
+    .x == "Somewhat confident" |
+      .x == "Somewhat committed" ~ "Somewhat",
+    .x == "Very confident" |
+      .x == "Very committed" ~ "Very",
+    TRUE ~ NA
+  )))
 
@@
 Such a case demonstrates that public trust in elections is, at best, only partial to trustworthiness of election administration in the United States[^2].
-Or in other words, there is only so much that election officials can do to sustain or improve public trust in election administration.
 
-Even though election officials can do a lot to secure election integrity, especially under intense scrutiny, there's not much they can do to cement public confidence after election night passes.
+Even though election officials can do a lot to secure election integrity, there's not much they can do to cement public confidence after election night passes.
 At best, election officials can ease public anxieties prior to election night.
-As mentioned, this usually consists of enhancing procedures and practices and adapting to advancing election technology.
 
@@
 As such, election worker competency has been examined as a factor significant to evaluations of performance of elections [@hall2007; @hall2009].
-However, considering that individual perceptions and preconceived notions play a huge role in cognition [@cikara2014; @vanbavel2021], it is reasonable to expect that the group an election worker hails from would be an important influence upon the voter's perception or evaluation of their own experience as well as subsequent evaluations of the electoral process.
+However, considering that individual perceptions and preconceived notions play a huge role in cognition [@cikara2014; @vanbavel2021], it is reasonable to expect that the group an election worker hails from would be an important influence upon the voter's evaluation of the electoral process.
+
 Supposing such is the case, we can expect that information about *who* (i.e., which groups) election officials are targeting in publicized recruitment efforts would lessen particular election anxieties.
@@
 
-In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would ease election anxieties (e.g., concern for electoral fairness and accuracy, as well as concerns for voter safety).
+In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would ease election anxieties.
 Results of the survey experiment support the hypothesis that emphasizing veterans as the target of election worker recruitment efforts eases pre-elections anxieties to an extent.
-In particular, among those who read the treatment vignette, confidence that the elections would be fair and accurate was higher in comparison.
+In particular, among those in the treatment condition, confidence that the elections would be fair and accurate was higher in comparison to those in the control.
 In addition, expectations of electoral fraud were lower, as were concerns for voter safety compared to those who read a control vignette.
-Notable is that there was a significant increase in confidence, and lower expectations of fraud, among those who believe that the 2020 election was illegitimate.
+Notable is that there was a significant difference in confidence, and lower expectations of fraud, among those in the treatment condition who believe that the 2020 election was illegitimate.
 
@@
 Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007].
-These somewhat generic issues of election worker staffing, competence, and voting technology were likely mere stepping stones leading to more intense election administration issues.
 
-In 2024, election officials made valiant efforts to boost public confidence in the fairness and accuracy of elections within an intensified political climate that appeared quite hostile to election officials [@edlin2024; @brennancenterforjustice2024].
+In 2024, election officials made valiant efforts to boost public confidence elections within an intensified political climate that appeared quite hostile to election officials [@edlin2024; @brennancenterforjustice2024].
 Although polling around the time indicated that most people thought that U.S.
 elections would be run at least somewhat well [@nadeem2024], many election officials nationwide took efforts to assuage the worry of those most skeptical.
-Enhancing trustworthiness in election administration is a regular duty for election officials, but baseless allegations regarding the fairness and accuracy of the 2020 election loomed ever larger, and the fear of political violence became prominent for both election officials and the public.
-Safety concerns for election staff, volunteers, and voters alike only added to, and perhaps exacerbated, public concern for the integrity of election administration in the United States.
-Especially as the steady increase in election official turnover seems to be increasing even more [@ferrer2024].
 
@@
 A Brennan Center survey report stated that, "...large numbers of election officials report having experienced threats, abuse, or harassment for doing their jobs" [@edlin2024].
-Concerns over the fairness of elections and accuracy of vote counts intensified, heightening concerns over the prospect of political violence and, in turn, engendered increased worry for the safety of voters and election workers alike.
+Concerns over the fairness of elections and accuracy of vote counts intensified, heightening concerns over the prospect of political violence and, in turn, increased worry for the safety of voters and election workers alike.
 
-Suffice to say, pre-election anxiety consists of more than concerns over fairness and accuracy of vote counts in light of added safety concerns.
+Suffice to say, pre-election anxiety consists of more than confidence in fairness and accuracy of vote counts in light of added safety concerns.
 It is not hard to recognize that increased tension in the pre-election period makes for a volatile political environment.
@@
 At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended).
-Or in other words, public trust is ascertained by the extent the public perceives the institution of election administration as trustworthy.
+Or in other words, public trust is ascertained by the extent the public is confident in the administration of elections.
 
@@
 This study focuses primarily on that *anticipatory* kind of trust and confidence, which speaks more to electoral anxieties over the institution of election administration.
-Not to mention that by definition, one feels anxiety over impending uncertainties located in the future[^4].
+Not to mention that by definition, one feels anxiety over impending uncertainties located in the future.
 
-The primary interest of this study concerns *election anxieties*, which is distinguished into two categories: fairness and accuracy, and voter safety.
+The primary interest of this study is public trust in election administration prior to the election, but differentiates between confidence and concern, or otherwise trust v.
+anxiety.
+The two are inversely related, at least conceptually.
+As such, we might also expect an inverse relationship between reported confidence and reported concern over the different aspects of electoral administration and process.
+Though that leads to the conceptual wrinkle that distinguishes between trust, distrust, and anxiety, which is addressed later.
+
+*election anxieties*[^4], which is distinguished into 
+two categories: fairness and accuracy, and voter safety.
 Of course, the direction of electoral outcomes are a particular source of electoral anxiety, but only the election outcome itself can resolve any nail-biting stress over its anticipated direction.
@@
 And media framing as such plays an important role on public perception [@kleykamp2015].
+
+## Theory
 

### 2024-11-21 notebooks/02-tables.qmd
revising and editing draft. make likert tables and plots

@@
 
-## Descriptive table
+```{r}
+#| label: post_processing
+#| include: false
+
+# Some post-processing of the dataframe :::::::::::::::::::::::::::::::::::::###
+
+# code to recode levels "-99" in factor vars
+data <- data |> 
+  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99")))
+
+# recode factor levels 
+data <- data |> 
+  # use `pewmethods` to preserve order of factor levels
+  mutate(across(c(q19, q20, q21, q22, q23,q24, q25, q26,
+                  q30, q31, q32, q33, q34, q35, q36, q37), 
+                ~pewmethods::fct_case_when(
+    .x == "Not at all confident" |
+      .x == "Not at all committed" ~ "Not at all",
+    .x == "Not too confident" |
+      .x == "Not too committed"|
+      .x == "Not too concerned"|
+      .x == "Somewhat unconcerned" ~ "Not that much",
+    .x == "Somewhat confident" |
+      .x == "Somewhat committed" ~ "Somewhat",
+    .x == "Very confident" |
+      .x == "Very committed" ~ "Very",
+    TRUE ~ NA
+  )))
+
+```
+
+```{r}
+#| label: fns
+#| include: false
+
+source(here::here('src', 'funs.R'))
+
+```
+
+## Demographics
+
 ```{r}
@@
 ```
+
+## Summary Tables
+
+```{r}
+#| label: tbl-tc
+#| tbl-cap: "Trust and Confidence in Election Administration"
+
+# Likert table summary of Trust and confidence variables
+tbl_tc <- data |> 
+  select(q19:q24) |>
+  gtsummary::tbl_likert(
+    statistic = ~"{n} ({p}%)", 
+    label = list(q19 = "Votes will be counted as intended",
+                 q20 = "Election officials will do good job",
+                 q21 = "Election workers will be committed",
+                 q22 = "Voting process will be fair",
+                 q23 = "Voting outcome will be fair",
+                 q24 = "Election technology will be secure"))
+
+# add continuous summary of Likert scores. Merge tables into one
+tbl_tc_summary <- list(
+  tbl_tc,
+  gtsummary::tbl_wide_summary(
+    data |>
+      select(q19:q24) |> mutate(across(where(is.factor), as.numeric)),
+    statistic = c("{mean}", "{sd}"),
+    label = list(
+      q19 = "Votes will be counted as intended",
+      q20 = "Election officials will do good job",
+      q21 = "Election workers will be committed",
+      q22 = "Voting process will be fair",
+      q23 = "Voting outcome will be fair",
+      q24 = "Election technology will be secure"
+    ),
+    type = ~ "continuous"
+  )
+) |>
+  gtsummary::tbl_merge(tab_spanner = F) |> 
+  gtsummary::modify_header(label="")
+
+# print as huxtable and modify using `huxtable` R package
+gtsummary::as_hux_table(tbl_tc_summary) |>
+  huxtable::set_width(0.6) |> 
+  huxtable::set_col_width(rep(c(0.4))) |> 
+  huxtable::theme_article() |> 
+  huxtable::set_position("center")
+
+```
+
+```{r}
+#| label: tbl-eef
+#| tbl-cap: "Expectation of Electoral Fraud"
+
+# Likert table summary of Expectation of electoral fraud :::::::::::::::::::####
+tbl_eef <- data |> 
+  select(contains("q28_")) |>
+  gtsummary::tbl_likert(
+    statistic = ~"{n} ({p}%)", 
+    label = list(q28_1 = "There will be voter fraud",
+                 q28_2 = "Many votes will not be counted",
+                 q28_3 = "Voters will be turned away",
+                 q28_4 = "Foreign Interference",
+                 q28_5 = "Election officials will discourage some voters"))
+
+# add continuous summary of Likert scores
+tbl_eef_summary <- list(
+  tbl_eef,
+  gtsummary::tbl_wide_summary(
+    data |>
+      select(contains("q28_")) |> mutate(across(where(is.factor), as.numeric)),
+    statistic = c("{mean}", "{sd}"), 
+    label = list(q28_1 = "There will be voter fraud",
+                 q28_2 = "Many votes will not be counted",
+                 q28_3 = "Voters will be turned away",
+                 q28_4 = "Foreign Interference",
+                 q28_5 = "Election officials will discourage some voters"),
+    type = ~ "continuous"
+  )
+) |>
+  gtsummary::tbl_merge(tab_spanner = F) |> 
+  gtsummary::modify_header(label="")
+
+# print as huxtable and modify using `huxtable` R package
+gtsummary::as_hux_table(tbl_eef_summary) |>
+  huxtable::set_width(0.6) |> 
+  huxtable::set_col_width(rep(c(0.4))) |> 
+  huxtable::theme_article() |> 
+  huxtable::add_footnote(border = 0.8,
+    "Note: Full survey question and statement wording can be found in the appendix") |> 
+  huxtable::set_position("center")
+
+```
+
+```{r}
+#| label: tbl-safe
+#| tbl-cap: "Concern for voter safety"
+
+# Likert table summary of Concerns for Voter Safety ::::::::::::::::::::::::####
+tbl_safe <- data |> 
+  select(q25, q26) |>
+  gtsummary::tbl_likert(
+    statistic = ~"{n} ({p}%)", 
+    label = list(q25 = "Potential for violence, threats, or intimidation",
+                 q26 = "Polling sites will be safe for voters"))
+
+# add continuous summary of Likert scores
+tbl_safe_summary <- list(
+  tbl_safe,
+  gtsummary::tbl_wide_summary(
+    data |>
+      select(q25, q26) |> mutate(across(where(is.factor), as.numeric)),
+    statistic = c("{mean}", "{sd}"),  
+    label = list(q25 = "Potential for violence, threats, or intimidation",
+                 q26 = "Polling sites will be safe for voters"),
+    type = ~ "continuous"
+  )
+) |>
+  gtsummary::tbl_merge(tab_spanner = F) |> 
+  gtsummary::modify_header(label="**Concern**")
+
+# print as huxtable and modify using `huxtable` R package
+gtsummary::as_hux_table(tbl_safe_summary) |>
+  huxtable::set_width(0.6) |> 
+  huxtable::set_col_width(rep(c(0.4))) |> 
+  huxtable::theme_article() |> 
+  huxtable::add_footnote(border = 0.8,
+    "Note: Full survey question and statement wording can be found in the appendix") |> 
+  huxtable::set_position("center")
+
+```
+
 ## Crosstables
@@
 # Crosstab of Q19 by treatment group
-df |> 
+data |> 
   janitor::tabyl(group, q19, show_na = F) |>
@@
 
-df |> 
+data |> 
   janitor::tabyl(group, q21, show_na = F) |> 

### 2024-12-18 index.qmd
long time no commit

@@
 data <- data |> 
-  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99")))
+  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99"))) |> 
+  # Reverse response options to show increase in *less concern*
+  mutate(q25 = forcats::fct_rev(q25))
 
@@
 
+# re-assign var labels to variables
+# To quickly assign the variable labels, first create a named vector via
+# deframe() with values as the variable labels and names as the variable names.
+data_labels <- data_dict |>
+  select(var, label_var) |> 
+  deframe()
+
+# Now assign the labels using the splice operator. Using the splice operator,
+# labels are assigned via matching against the variable name, which means that
+# variable order does not matter.
+data <- data |> 
+  labelled::set_variable_labels(!!!data_labels)
+
 ```
@@
 
-Election administration officials make efforts to sustain public trust and confidence in the fairness and accuracy of elections, and attempt to boost such confidence where ever it may be deprived.
+Election administration officials make efforts to sustain public trust and confidence in the fairness and accuracy of elections, and attempt to boost such confidence where it may be deprived.
 Concerns for safety have developed among election staff and voters in more recent elections.
@@
 
-In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would ease election anxieties.
+In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election anxieties.
 Results of the survey experiment support the hypothesis that emphasizing veterans as the target of election worker recruitment efforts eases pre-elections anxieties to an extent.
@@
 Notable is that there was a significant difference in confidence, and lower expectations of fraud, among those in the treatment condition who believe that the 2020 election was illegitimate.
+
+[Insert why this is an important contribution]
+
+This paper is structured as follows.
+First, I provide a brief background on public trust in election administration.
+Second, I synthesize a review of relevant literature with a focus on how political and social science has conceptualized and ascertained public trust in elections.
+Next, I supply reasoning for why military veterans are singled out as the relevant subset of the population in this study.
 
@@
 It is not hard to recognize that increased tension in the pre-election period makes for a volatile political environment.
+Sustaining trustworthiness in election administration is only more difficult in an environment where turnover of election workers increases and the struggle to recruit volunteers worsens in light of safety concerns.
+Since election worker performance is significant to public evaluation of elections, added safety concerns that drive out election staff and repel volunteers can only detract from trustworthiness of the institution.
 
@@
 
-Assessing the public's *trust* in elections has not been straightforward.
-Inquiry into public trust in elections has been approached by scholars of political science in many different ways [@cook2005], often distinguishable by the scope of the research question and more or less constrained by the particular conception of public trust.
-Quite often, trust in election administration is conflated with trust in government writ large, government legitimacy, government or system responsiveness, or even satisfaction with democracy [@daniller2019].
+Trust and confidence in the conduct of elections concerns aspects of elections that fall squarely within the institution of election administration.
+At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended).
+Or in other words, by the extent the public is confident in the accurate administration of elections.
+
+Assessing the public's *trust* in elections has not been straightforward, however.
+Inquiry into public trust in elections has been approached by scholars of political science in many different ways [@cook2005; @hardin2004], often distinguishable by the scope of the research question and more or less constrained by the particular conception of public trust.
+Quite often, trust in election administration is conflated with trust in government *writ* large, government legitimacy, government or system responsiveness, or even satisfaction with democracy [@daniller2019].
 At this level, not only is the level of public trust in elections sometimes vague, but there's little consideration over the difference between such attitudes pre-election and post-election.
@@
 
-Election administration is just one part of the larger set of institutions which form the electoral system.
+Election administration is just one institution a part of the larger set of institutions which form the electoral system.
 As such, the performance of the institution along with the rest "...lends credibility to the outcome of an election: whether it is considered by citizens and the international community to be fair and legitimate." [@stewart2022, 236].
-
-Trust and confidence in the conduct of elections concerns aspects of elections that fall squarely within the institution of election administration.
-At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended).
-Or in other words, public trust is ascertained by the extent the public is confident in the administration of elections.
-
 Intuitively, enhancing public trust in elections would best be accomplished by enhancing the *trustworthiness* of the institution, i.e., consistently doing the things that election officials already regularly do come election time.
@@
 
-As such, it is questionable whether we can characterize public trust in the pre-election period as the same trust after the election results have come out[^3].
+As such, it is questionable whether we can characterize public trust in the pre-election period as the same trust after the election results have come out.
 The former is *anticipatory*---i.e., the kind that is more or less anxious given the uncertainties surrounding the election.
-The latter is *evaluative*---a judgement discerned empirically in hindsight after the election event has occurred.
-The evaluative form of trust lends to inquiries interested in public opinion on regime legitimacy, satisfaction with democracy, and perceived responsiveness [@daniller2019].
-This study focuses primarily on that *anticipatory* kind of trust and confidence, which speaks more to electoral anxieties over the institution of election administration.
-Not to mention that by definition, one feels anxiety over impending uncertainties located in the future.
+The latter is *empirical*---a judgement discerned in hindsight after the experience of the election event has occurred.
+Evaluations of one's own trust and confidence in election administration based on the experience of voting is influenced by that very experience.
+As discussed by @stewart2022, not only was confidence in vote count accuracy influenced by the voter experience, but so too were evaluations of election officials [-@stewart2022, 242-243].
+Not to mention the influence that the election results would also have on such evaluations.
+In other words, evaluations of trust and confidence post-election are influenced by one's interpretation of their experience.
+The subtle difference is simply the degree of uncertainty one feels in anticipation of the next election event.
+This study focuses primarily on that *anticipatory* kind of trust and confidence, which speaks more to those anxieties[^3] based on perceptions of the institution's trustworthiness than upon the particular voter experience.
 
-The primary interest of this study is public trust in election administration prior to the election, but differentiates between confidence and concern, or otherwise trust v.
-anxiety.
-The two are inversely related, at least conceptually.
-As such, we might also expect an inverse relationship between reported confidence and reported concern over the different aspects of electoral administration and process.
-Though that leads to the conceptual wrinkle that distinguishes between trust, distrust, and anxiety, which is addressed later.
-
-*election anxieties*[^4], which is distinguished into 
-two categories: fairness and accuracy, and voter safety.
-Of course, the direction of electoral outcomes are a particular source of electoral anxiety, but only the election outcome itself can resolve any nail-biting stress over its anticipated direction.
-In contrast, the anxieties of interest here are able to be relaxed to some extent prior to the election given some intervention.
-
-Interventions aimed at improving public trust, or rather, aimed at easing election anxieties may not be within the usual repertoire election officials draw upon.
 Regardless of the measures taken by election officials to boost public confidence in the *trustworthiness* of election administration (e.g., conducting audits, testing election machines), public *trust* and confidence in elections more generally is apt to shift dramatically post-election based on factors such as partisanship, elite rhetoric, particular state policies, and more [@nadeau1993; @carter2024; @coll2024a].
@@
 
-Beyond the general competence of election workers, however, the quality of the voter experience may be influenced merely by impressions about *who* comprises election staff and volunteers.
+Beyond the general competence of election workers, however, the quality of the voter experience may be influenced merely by *a priori* impressions about *who* comprises election staff and volunteers.
 Political and other social science researchers have recognized for some time the power that group identity can have over attitudes and perception [@xiao2016; @xiao2012; @vanbavel2021].
-As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve trust and confidence in election administration, i.e., ease election anxieties.
-It was hypothesized that information on recruitment efforts targeting military veterans to work as election staff would ease election anxieties.
-The next section elaborates further on why military veterans are of particular interest.
+As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve trust and confidence in election administration, and lessen expectations of electoral fraud.
+The next section elaborates on why military veterans are of particular interest in this regard.
 
@@
 After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterans2022; @nflfootballoperations2022].
-Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts[^5] [@powerthepolls2020; @herndon2020].
+Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts [@powerthepolls2020; @herndon2020].
 Generally, however, recruitment efforts cast a wide net, indiscriminate of who applies [@ross2020; @conde2020].
@@
 One can speculate that the motivation to associate military veterans with civic engagement and democracy may be intended to counter negative perceptions and impressions given by the proportion of veteran service members arrested for taking part in the events on January 6th [@milton2021; @loewenson2023; @jensen2022a].
-Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results[^6] (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024].
+Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024].
 This is in addition to a strengthened association portrayed in media outlets between military veterans and militias [@steinhauer2020].
-Although such media output reeks of the contemporary political context, prior research has substantiated such a connection between veterans and militia groups.
+Prior research has substantiated such a connection between veterans and militia groups.
 @cooter2024 notes from her 3-year ethnographic fieldwork among Michigan militia members that, "...approximately 40% of militia leaders and 30% of members had previous military experience.
@@
 
-## Theory
+## Design and Measures
 
-## Research Design and Method
-
-To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would ease election anxieties, a recent survey experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland (UMD).
+To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would improve trust in elections and ease election anxieties, a recent survey experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland.
 The survey was fielded from August 29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287 U.S.
 citizens 18 years of age or older.
+Respondents were randomly split into either the treatment (n = 650, 50.51%) control (n = 637, 49.49%) conditions[^Demographic breakdown of the sample are included in Appendix B.].
 
-The primary independent variable is the prospect of military veterans as poll workers.
-It was considered that veterans would elicit high degrees of approval and support for whatever cause or issue presented.
-For example, I'd expect high approval and support for recruiting veterans to baseball teams just as much as for recruiting them to work as election staff.
-Asking participants whether they supported programs intent on recruiting veterans to work as election staff would garner support regardless of the target group.
-Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require a survey experiment and questions designed to determine whether veterans have any special effect on electoral confidence and voter safety distinct from the generally high admiration observed most often.
-
-Survey participants were randomly assigned to read one of two fabricated news articles (i.e., vignettes) about recruitment efforts for election jobs.
-Participants read either a treatment or control vignette, which was a fabricated news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election.
-The treatment vignette referred to a program designed to recruit veterans and their family members and describes an interviewee "Jordan Braxton" as an Army veteran; whereas the control vignette simply omitted any mention of veterans and their family members, and didn't describe "Jordan Braxton" as an Army veteran.
+Survey participants read either a treatment or control vignette, which was a fabricated news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election.
+The treatment vignette referred to a program designed to recruit veterans and their family members and describes an interviewee "Jordan Braxton" as an Army veteran.
+The control vignette simply omitted any mention of veterans and their family members, and didn't describe "Jordan Braxton" as an Army veteran.
 Beyond those small differences and the headlines, the article vignettes are identical.
-Any effects can be attributed to the information about veterans in the treatment vignette[^7].
+Any effects can be attributed to the information about veterans in the treatment vignette[^5].
 
 It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignettes due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
-In addition, the survey includes a series of items which ask specifically about Maricopa County, AZ and a comparable series of questions about one's local area[^8].
+A block of survey items asked specifically about Maricopa County, AZ, followed by an identical block of items that asked the same questions about one's local area.
+Results between the items where the setting differs are compared and discussed.
 
-Over the past two decades it became commonplace for national polls to gauge public confidence in election administration by asking some variety of the question, "How confident are you that your vote \[will be/was\] counted as you intended in the most recent election?" [@hall2009; @sances2015; @stewart2022].
+### Trust in Elections Admin
+
+Over the past two decades it became commonplace for national polls to gauge public confidence in election administration (i.e., voter confidence) by asking some variety of the question, "How confident are you that your vote \[will be/was\] counted as you intended in the most recent election?" [@hall2009; @sances2015; @stewart2022].
 In addition, since 2008, the Survey of the Performance of American Elections (SPAE) has included a good number of relevant questions to more thoroughly assess trust and confidence in election administration.
 Such questions inquire into the voter experience with the institution more directly.
-This study borrows, modifies, or takes inspiration from certain questions found within the 2022 SPAE and other survey items used by the Pew Research Center [@dunn2018].
-These survey items comprise the dependent variables[^9].
+This study borrows, modifies, or takes inspiration from certain question items found within the 2022 SPAE and other survey items from the Pew Research Center's 2018 American Trends Panel wave 38 [@dunn2018].
 
-The outcomes of interest (i.e., dependent variables) are broadly referred to as *election anxieties*, but more specifically refer to confidence over fairness and accuracy of the election administration; expectations of fraudulent activity intent on manipulating the electoral outcomes; and concern for voter safety, i.e., comfort voting in-person as it relates to expectations of violence, threats, or intimidation.
-The following presents multiple one-sided directional hypotheses.
-Previous research on public perception and regard for U.S.
-military veterans gives credence to the directional hypotheses [@kleykamp2018; @kleykamp2023].
+Note that, except for the item assessing voter confidence (i.e., votes counted as voters intend), most other question items from the 2022 SPAE inquire into the voter experience after the election has occurred.
+The items in this study, however, all inquire into confidence over one's expectations in anticipation of upcoming elections.
+In addition, other survey questionnaires ask similar questions that specifically contrast between a respondent's own local community, their state, and nationwide.
+This is in addition, or complementary to, items that distinguish between local area officials, state election officials, state government, and the U.S.
+federal government.
+The survey of this study, instead, focused on attitudes regarding election workers such as election officials, staff, and volunteers.
+As such, the items are utilized to comprise a component[^7] I broadly refer to as *trust in elections*.
 
-The first outcome of interest regards *trust and confidence* in election administration, which includes the integrity and security of the electoral process, administration, technology, and people or organizations to fairly and accurately conduct elections.
-Survey items measured the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, as well as confidence that the voting process will be fair.
+[^7]: The methodological concerns between the use of (unit weighted) sum scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
+The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024].
+The use of either appears to largely depend on the researcher's particular research objective, theoretical suppositions, and necessity.
+Another common concern is the inappropriate treatment of ordinal variables as interval which levy strong assumptions, e.g., each item contributes equally to the variable being measured and that ordinal response categories are equidistant as though on an interval scale [@wang2013; for contrast, see @robitzsch2020].
 
-The first hypothesis is as follows:
+A set of five survey items measured public trust in elections by inquiring into the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, as well as confidence that the voting process will be fair.
+The items measuring trust and confidence in elections include:
 
-$H_{1}:$ Trust and confidence in election administration will be higher among those who were presented information about efforts to recruit veterans as election workers compared to those who were not
+-   How confident are you that votes in Maricopa County, AZ will be counted as voters intend in the elections this November?[^8]
+-   How confident are you that election officials, their staff, and volunteers in Maricopa County, AZ will do a good job conducting the elections this November?
+-   Think about the election staff and volunteers who handle the administration and conduct of elections in Maricopa County, AZ.
+How committed do you think they will be to making sure the elections held this November are fair and accurate?
+-   How confident are you that the voting process will be fair in Maricopa County, AZ?
+-   How confident are you that election systems in Maricopa County, AZ will be secure from hacking and other technological threats?
 
+[^8]: Note that confidence, or lack thereof, that votes will be counted as voters intend could easily be construed as an expectation of electoral fraud.
+It is a given that the votes will be counted, but the question is whether they will be counted *as intended*.
+Although fraud isn't provided as the reason for why votes wouldn't be counted as intended, it also isn't implied that miscounts would be due to some negligent mistake.
+A nefarious insinuation might be somewhat implicit, but perhaps only to those who are inclined to suspect as such.
+A lack of confidence here doesn't necessarily impart the reason for that lack of confidence, which makes it suitable as a survey item to measure the presence of trust in election administration rather than an expectation of fraud.
+
+Each item in this series presented four response options from "Not at all [confident/committed]", "Not too [confident/committed]", "Somewhat [confident/committed]", and "Very [confident/committed]".
 In total, six survey items measure different aspects of trust and confidence in election administration.
-These items were analyzed individually but were also transformed into a composite scale of trust and confidence.
+From these items, I generated a composite score for each respondent that represents their variable level of trust in elections.
 
-The literature concerning public regard for veterans gives substantial reason to expect that publicized efforts to recruit veterans to work as election staff and volunteers would have the effect of easing election anxieties.
-As such, survey participants also responded to a series of questions that inquired into expectations of electoral fraud---i.e., fraudulent activity intent on manipulating the electoral outcome.
+### Expecatation of Electoral Fraud
 
-Note, however, that an *expectation* of electoral fraud implies a degree of distrust more so than an agitated state of anxiety over the *potential* for electoral fraud.
-Conceptually, this may be considered a particular kind of 'anxiety' given that is it pre-election (hence, an expectation), however, not necessarily.
-A person may be rather confident with regard to how much they distrust the integrity of electoral administration, resulting in such expectations.
+A series of five survey items captured *expectation of electoral fraud*.
+These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in Maricopa County, AZ?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
 
-For instance, the first item of the 5-item series asks participants to report their expectation that "There will be voter fraud, that is, people who are not eligible to vote will vote or vote more than once" on a 4-option response scale ranging from "Not likely at all" to "very likely".
-This statement, as well as the rest in the series, asserts an expected compromise of election integrity, which speaks to the trustworthiness of the institution.
-What the individual expects, more or less, is that electoral fraud will occur, implying that fraudulent attempts will be successful.
+-   There will be voter fraud, that is, people who are not eligible to vote will vote, or vote more than once
+-   Many votes will not actually be counted
+-   Many people will show up to vote and be told they are not eligible
+-   A foreign country will tamper with the votes cast in this area to change the results
+-   Election officials in Maricopa County, Arizona will try to discourage some people from voting
 
-It was expected that the experimental stimulus would result in lower expectation for electoral fraud among those who read the treatment vignette compared to those who read the control vignette.
-The second hypothesis is,
+Similar to the items capturing trust in elections, I computed a composite score for each respondent reflecting their expectations of electoral fraud.
 
-$H_{2}:$ Expectations of electoral fraud will be lower among those who were presented information about efforts to recruit veterans as election workers compared to those who were not
+## Model and Data Specification
 
-Another outcome of interest regards concerns about voting in-person at a polling site, i.e., voter safety.
-That is, the extent people feel that voters are safe enough to cast a vote at polling sites free from violence, threats of violence, or intimidation.
-Two survey items use slightly different questions to inquire about the same essential issue—i.e., perceptions of physical safety at the polls.
-The third hypothesis follows,
+The outcome of interest concerns both public trust in election administration and the expectation of electoral fraud.
+Because these variables are assessed by multiple Likert items, conventional methods call for combining the items of each set into separate Likert scales, also known as a summated rating scales.
+However, many of the items comprising the trust scale directly oppose items capturing expectations of electoral fraud.
+For instance, one item has the respondent report their confidence that votes will be counted as voter's intend; whereas a contrasting item has the the respondent report their expectation that many votes will not be counted.
+These two items directly oppose each other, but there's no guarantee that individual's responded as such.
 
-$H_{3}:$ Concerns for voter safety be lower among those who are presented information about efforts to recruit veterans as election workers compared to those who are not
+Since many of the items are not symmetric---i.e., response options are not bipolar with contrasting positive and negative response options---then a "trust in elections" scale could only be understood as a measure of trust in the positive use of the term (i.e., unipolar).
+Likewise, the expectation of fraud items fit to a scale that corresponds to a unipolar measure of *confident distrust* so to speak.
 
-Another outcome of interest concerned how particular actions of election officials, or circumstances at polling sites, would impact the confidence of election integrity as well as voter safety *from the perspective of survey respondents*.
-Survey participants responded to a series of six statements, all prefaced with the same question, "Regardless of whether any of these are actually the case, how would the following impact your confidence in the fairness and accuracy of elections conducted this November?" The six statements were,
+I would expect composite sum or mean scores, and item responses, on these two measures to be inversely correlated among the sample, but not mutually exclusive. Indeed, this is what I find.
 
-1.  Election officials test every machine used in the election to ensure they are secure.
-2.  Election officials conduct audits of ballots after every election to confirm the results were accurate.
-3.  Poll watchers affiliated with the political parties or candidates observe the election.
-4.  Election staff and volunteers include military veterans and their family members from the community.
-5.  Election staff and volunteers include lawyers from the community.
-6.  Election staff and volunteers include college students from the community.
+I first constructed two multi-item composite scales of both *trust in elections* and *expectation of fraud*.
+Cronbach's internal consistency reliability coefficient \alpha were estimated for both scales and were adequate (\alpha > 0.8); the trust in elections scale \alpha = 0.93 and the expectation of electoral fraud scale \alpha = 0.86.
+In other words, the items in each of the scales were intercorrelated well enough to compose a single scale of a (presumed) unidimensional construct.
+I then plotted separate histograms of scores across the sample to visualize the distribution for each seen in @fig-dist.
+Note that for both scales, higher values indicate less expectation of electoral fraud and greater trust in elections, respectively.
 
-For each statement, survey participants responded by selecting one of five response options:
+```{r}
+#| label: fig-dist
+#| fig-cap: "Histograms of Composite (mean) Scores for Trust in Elections And Expectation of Electoral Fraud"
 
-1.  Decrease confidence a lot
-2.  Decrease confidence somewhat
-3.  No impact on confidence
-4.  Increase confidence somewhat
-5.  Increase confidence a lot
+# trust scores are not normally distributed, bi-modal, neg skew
+trst.scores.hist <- ggplot(data, aes(trst.mean.scores))+
+  geom_histogram(aes(y = after_stat(density)), bins = 15,
+                 color = 1, fill = "grey")+
+  geom_density(lwd = 1.5, color = 1, fill = 1, alpha = 0.35)+
+  geom_segment(x = round(mean(data$trst.mean.scores), 2), y = 0, yend = 0.80, color = "red")+
+  labs(
+    x = "Trust in Elections Mean Scores",
+    y = "Density",
+    caption = "mean = 3.09, sd = 0.69, median = 3.0, skew = -0.67, kurtosis = 0.25"
+  )+
+  annotate("text", x = round(mean(data$trst.mean.scores), 2), y = 0.85,
+           label = paste("mean =", round(mean(data$trst.mean.scores), 2)), color = "red")
 
-It was expected that respondents would estimate stronger impact on their confidence given they were assigned to read the treatment vignette compared to those who were not. Thus, the hypothesis is,
+# eef scores are not normally distributed, also bi-modal pos skew
+eef.scores.hist <- ggplot(data, aes(eef.mean.scores))+
+  geom_histogram(aes(y = after_stat(density)), bins = 15,
+                 color = 1, fill = "grey")+
+  geom_density(lwd = 1.5, color = 1, fill = 1, alpha = 0.35)+
+  geom_segment(x = round(mean(data$eef.mean.scores), 2), y = 0, yend = 0.80, color = "red")+
+  labs(
+    x = "Exp. of Electoral Fraud Mean Scores",
+    y = "Density",
+    caption = "mean = 2.27, sd = 0.75, median = 2.2, skew = 0.19, kurtosis = -0.55"
+  )+
+  annotate("text", x = round(mean(data$eef.mean.scores), 2), y = 0.85,
+           label = paste("mean =", round(mean(data$eef.mean.scores), 2)), color = "red")
 
-$H_{4}:$ Respondents who read the treatment vignette will report stronger impact on their personal confidence in fairness and accuracy of election administration when veterans are stated to be included among election staff and volunteers compared to those who read the control vignette.
+# place plots side by side
+gridExtra::grid.arrange(eef.scores.hist, trst.scores.hist, ncol = 2)
+```
 
-The extent people believe veterans are more trustworthy as election workers than non-veterans in general is difficult without comparable groups to consider.
-Recruitment efforts in 2022 targeted young students, lawyers, and military veterans [@wang2022].
-Thus, lawyers and college students were selected as two groups for which responses could be compared between different statement versions.
+Given the non-normal (or at least un-equal skew of the) distribution of the two scale scores and ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho$ -0.49 (Kendall's \tau = -0.39) between summated scores on the two scales.
 
-The goal was to determine whether there is anything special in having veterans volunteer as election staff (i.e., poll workers) compared to other groups.
-That is, does it make any difference in terms of concerns over election security, fairness, and voter safety to include veterans as election staff and volunteers compared to other groups?
-The fourth hypothesis, irrespective of the experimental stimulus, reads,
+The negative correlation between the items and the composite scores makes sense.
+Theoretically speaking, a person who is certain that electoral fraud will occur clearly lacks trust in the election.
+That is, expectation of electoral fraud does imply lack of trust in elections.
+However, the reverse isn't also necessarily true; it is reasonable to hold a degree of trust in elections alongside expectations that electoral fraud will occur.
+Holding both considerations isn't necessarily an example of cognitive dissonance, as a lack of confidence in elections doesn't necessarily imply an expectation of electoral fraud.
+A lack of trust in elections might render one open to potentialities, but expectation of fraud is in no way necessitated by lacking trust in elections.
+When considered along a spectrum, both can be considered as degrees of *confidence*; and in the absence of confidence, insecure.
 
-$H_{5}:$ Respondents who read the treatment vignette will report stronger impact on their personal confidence in fairness and accuracy of election administration when veterans are stated to be included among election staff and volunteers compared to identical statements about lawyers or college students.
+Accordingly, those whose responses to the "trust in elections" items would be cancelled out by their responses to the "expectation of fraud" items.
+Those who are, or are close to being, equally confident in both directions would be the most *insecure* about their expectations[^Insecure in terms of their confidence.
+Not insecure as to imply some anxious or concerned affect.].
+Having no trust in elections and no expectation that electoral fraud will occur is functionally equivalent to having equal degree of both.
+Quite literally, an uncertain feeling of "it could go one way or the other".
+Operationally, this would reflect a middling 0 on a scale of *confidence*.
+Seeing as how expectation of electoral fraud is also a level of confidence, then it is reasonable to place all items onto a symmetric scale where positive values represent trust in elections and negative values represent expectation of electoral fraud.
+
+The primary dependent variable is *confidence in elections*, which reflects one's trust in election administration minus their expectations of electoral fraud.
+Operationally, the dependent variable is a linear composite scale of item responses across items measuring trust in elections and expectations of electoral fraud re-scaled to range from -3 to 3.
+Items comprising trust in elections were positively coded to range from 0 "Not at all confident/committed" to 3 "Very confident/committed".
+Likewise, items capturing expectation of electoral fraud were coded negatively to range from 0 "Not likely at all" to -3 "Very likely".
+
+Computed mean or sum scores for multiple Likert items are commonly acceptable, as they are relatively robust in spite of violating assumptions of a normal distribution of data (or residuals).
+due to the somewhat non-normal distribution of the sum or mean scores and the ordinal nature of the variable items, an ordered regression analysis is preferred.
+
+The primary independent variable is the prospect of military veterans as election workers (i.e., staff or volunteers).
 
 ## Results
+
+The key question is whether trust in elections (or voter confidence) is response to the treatment vignette.
+
+Note that the question wording for the survey items derived from the 2022 SPAE are modified slightly but substantially.
+The question wording in this study is most similar to those in 2022 SPAE that assess confidence that votes will be counted as voters intend without specific reference to their own vote (e.g., in their county, state, or nationwide).
+In this study, two survey items ask about confidence in vote counts in one specific county in Arizona and another referencing their local community.
+Moreover, the 2022 SPAE includes "I don't know" as a response option, whereas the comparable item in this study did not include a "don't know" response option.
+Comparison between responses to the two similar items was conducted....
 
@@
 
+The median age was 46 (mean age was 47).
+There was 51.7% (n = 658) women, 47% (n = 598) men, and approximately 1.3% who identified as either Non-binary/third gender (n = 7) or preferred not to say (n = 9).
+A large proportion of the sample identified as White or Caucasian (n = 975, 76.65%), while all other non-White respondents comprised 27.83% of the sample.
+Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised 13% of the sample; those with either degree at the Associate or Bachelor's level comprised 36.24%, while 22.25% had some college but no degree; and 28.46% had either a high school level or equivalent education or less than high school.
+The largest proportion of the sample identified as Democrat at 44.64%, followed by Republicans at 42.59%.
+The proportion of true Independents was 12.78%.
+
 ::: {.content-visible when-format="html" unless-format="pdf"}
@@
 
+\pagebreak
+
 [^1]: I adopt a distinction made between *trustworthiness* and *trust* in elections [@stewart2022].
@@
 
-[^2]: It is important to point out here that election administration is just one institution that interacts with many other institutions and processes which form the electoral system *writ large* [@stewart2022].
-The way in which I discuss the institution of election administration, as well as the way in which I discuss and distinguish public trust in elections from broader conceptions of public trust, is borrowed substantively from @stewart2022's conceptual framework of the same.
-Distinctions between *trust* and *trustworthiness* and the notion of election administration as an institution are already apparent inspirations convenient for situating the theory of this research inquiry.
+[^2]: There's little that could justify a conceptual distinction between public trust pre-election and public trust post-election.
+The temporal element renders the difference between pre- and post-election more operative than conceptual at a foundational level.
 
-[^3]: There's little that could justify a conceptual distinction between public trust pre-election and public trust post-election.
-The temporal element renders the difference between pre- and post-election operative rather than conceptual.
+[^3]: Note that *electoral anxiety* is used in place of electoral trust/confidence simply to emphasize the anticipatory nature of the attitudes in question.
+Election anxiety is not taken to be the inverse of trust and confidence.
+A lack of trust does not necessarily imply (a state of) anxiety.
 
-[^4]: Note that *anxiety* is taken to be the inverse of *trust and confidence*, as in, one who is less confident in this or that is thereby more anxious over the matter in question.
-As such, anxiety may equivalently be discussed as trust/confidence without issue except for framing of said discussion.
-Electoral anxiety is used in place of electoral trust/confidence simply to emphasize the anticipatory nature of the attitudes in question.
-
-[^5]: The cited study defined "insurrectionist sentiments" as, "...willingness to support violent efforts to overturn the results of an election in favor of another, unelected political leader." [@pape2024, 7].
+[^4]: The cited study defined "insurrectionist sentiments" as, "...willingness to support violent efforts to overturn the results of an election in favor of another, unelected political leader." [@pape2024, 7].
 It should be noted, however, that despite the general definition, the operative items used to measure such sentiments ask about Donald Trump specifically, not an "unelected political leader".
 
-[^6]: Prior to 2021, I found one online recruitment brochure intent on recruiting veterans to serve as election workers [@studentveteransofamerica2020].
-
-[^7]: Complete text of treatment and control vignettes are included in the Appendix
-
-[^8]: The setting of the vignettes and inclusion of duplicate questions in the survey are highlighted and discussed later.
-
-[^9]: All survey items are included in the Appendix.
+[^5]: Complete text of treatment and control vignettes are included in the Appendix

### 2024-12-18 src/01-data.R

@@ -59,6 +59,7 @@ codebook <- raw_spss |>
 
 # save codebook as .csv file in data/ directory
 write.csv(codebook, file = "data/survey_codebook.csv")
+
 # clean up data set ::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
 data <- raw_spss |> 
   janitor::clean_names() |> 
@@ -313,7 +314,7 @@ data_dict <- data |>
   labelled::generate_dictionary()
 
 #####
-# convert all labelled variables to factor
+# convert all labelled variables to factor :::::::::::::::::::::::::::::::::####
 
 data <- data |> 
   # make `group` and `qset` factors (because they are character class)
@@ -322,35 +323,17 @@ data <- data |>
   sjlabelled::set_labels(group, labels = c("Control" = 0, "Treatment" = 1)) |>
   sjlabelled::set_labels(qset, labels = c("A" = 0, "B" = 1)) |> 
   # convert all labelled variables to factors
-  haven::as_factor(only_labelled = T) |>
+  haven::as_factor(only_labelled = T, ordered = TRUE) |>
   # re-code any empty/blank levels to NA
   mutate(across(where(is.factor), ~ fct_recode(., NULL = ""))) |> 
+  
+  # code to recode levels "-99" in factor vars to NA
+  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99"))) |>
+  
   # reverse order of identified factor levels for consist direction
-  mutate(across(c(q8, q20, q23, q24, q31, q34, q35, q49, q50), .fns = ~fct_rev(.))) |> 
+  mutate(across(c(q8, q20, q23, q24, q25, q31, q34, q35, q49, q50), .fns = ~fct_rev(.))) |> 
   # reverse order of group levels so control comes first. Better table display
   mutate(group = forcats::fct_rev(group))
-
-
-# add variable labels back into factorized data set ::::::::::::::::::::::::####
-
-# variable labels are nice to have for plenty of reasons
-# since SPSS data is labelled, usually, the variables are <dbl+lbl> instead of
-# factors <fct>. It's easier to analyze vars in data as factors, but losing the
-# variable labels (i.e., question text) is kind of a bummer. The following puts
-# the variable labels form the SPSS data set back into the 'factor-ized' dataset
-
-# To quickly assign the variable labels, first create a named vector via
-# deframe() with values as the variable labels and names as the variable names.
[…]

### 2024-12-20 docs/index.qmd
checkpoint Dec 20th

--- 2024-12-18 index.qmd
@@
 # Some post-processing of the dataframe :::::::::::::::::::::::::::::::::::::###
-
-# code to recode levels "-99" in factor vars
-data <- data |> 
-  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99"))) |> 
-  # Reverse response options to show increase in *less concern*
-  mutate(q25 = forcats::fct_rev(q25))
 
@@
 
-## Design and Measures
+## Design and Survey Measures
 
@@
 citizens 18 years of age or older.
-Respondents were randomly split into either the treatment (n = 650, 50.51%) control (n = 637, 49.49%) conditions[^Demographic breakdown of the sample are included in Appendix B.].
+Respondents were randomly split into either the treatment (n = 650) control (n = 637) conditions[^4].
 
@@
 
-### Trust in Elections Admin
+### Trust in Elections
 
@@
 The survey of this study, instead, focused on attitudes regarding election workers such as election officials, staff, and volunteers.
-As such, the items are utilized to comprise a component[^7] I broadly refer to as *trust in elections*.
-
-[^7]: The methodological concerns between the use of (unit weighted) sum scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
-The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024].
-The use of either appears to largely depend on the researcher's particular research objective, theoretical suppositions, and necessity.
-Another common concern is the inappropriate treatment of ordinal variables as interval which levy strong assumptions, e.g., each item contributes equally to the variable being measured and that ordinal response categories are equidistant as though on an interval scale [@wang2013; for contrast, see @robitzsch2020].
+As such, the items are utilized to comprise a component[^6] I broadly refer to as *trust in elections*.
 
@@
 
--   How confident are you that votes in Maricopa County, AZ will be counted as voters intend in the elections this November?[^8]
--   How confident are you that election officials, their staff, and volunteers in Maricopa County, AZ will do a good job conducting the elections this November?
--   Think about the election staff and volunteers who handle the administration and conduct of elections in Maricopa County, AZ.
+::: {#tbl-1}
+| **Trust in Elections** |
+|---|
+| How confident are you that votes in Maricopa County, AZ will be counted as voters intend in the elections this November?[^7] |
+| How confident are you that election officials, their staff, and volunteers in Maricopa County, AZ will do a good job conducting the elections this November? |
+| Think about the election staff and volunteers who handle the administration and conduct of elections in Maricopa County, AZ.
 How committed do you think they will be to making sure the elections held this November are fair and accurate?
--   How confident are you that the voting process will be fair in Maricopa County, AZ?
--   How confident are you that election systems in Maricopa County, AZ will be secure from hacking and other technological threats?
-
-[^8]: Note that confidence, or lack thereof, that votes will be counted as voters intend could easily be construed as an expectation of electoral fraud.
-It is a given that the votes will be counted, but the question is whether they will be counted *as intended*.
-Although fraud isn't provided as the reason for why votes wouldn't be counted as intended, it also isn't implied that miscounts would be due to some negligent mistake.
-A nefarious insinuation might be somewhat implicit, but perhaps only to those who are inclined to suspect as such.
-A lack of confidence here doesn't necessarily impart the reason for that lack of confidence, which makes it suitable as a survey item to measure the presence of trust in election administration rather than an expectation of fraud.
+|
+| How confident are you that the voting process will be fair in Maricopa County, AZ? |
+| How confident are you that election systems in Maricopa County, AZ will be secure from hacking and other technological threats? |
+:::
 
@@
 
--   There will be voter fraud, that is, people who are not eligible to vote will vote, or vote more than once
--   Many votes will not actually be counted
--   Many people will show up to vote and be told they are not eligible
--   A foreign country will tamper with the votes cast in this area to change the results
--   Election officials in Maricopa County, Arizona will try to discourage some people from voting
+::: {#tbl-2}
+| **Expectation of Electoral Fraud** |
+|---|
+| There will be voter fraud, that is, people who are not eligible to vote will vote, or vote more than once |
+| Many votes will not actually be counted |
+| Many people will show up to vote and be told they are not eligible |
+| A foreign country will tamper with the votes cast in this area to change the results |
+| Election officials in Maricopa County, Arizona will try to discourage some people from voting |
+:::
 
-Similar to the items capturing trust in elections, I computed a composite score for each respondent reflecting their expectations of electoral fraud.
+Similar to the items capturing trust in elections (@tbl-1), I computed a composite score for each respondent reflecting their expectations of electoral fraud.
 
-## Model and Data Specification
+## Data Specification
 
@@
 For instance, one item has the respondent report their confidence that votes will be counted as voter's intend; whereas a contrasting item has the the respondent report their expectation that many votes will not be counted.
-These two items directly oppose each other, but there's no guarantee that individual's responded as such.
+These two items directly oppose each other, but there's no guarantee that individual responded as such.
 
@@
 
-I would expect composite sum or mean scores, and item responses, on these two measures to be inversely correlated among the sample, but not mutually exclusive. Indeed, this is what I find.
-
-I first constructed two multi-item composite scales of both *trust in elections* and *expectation of fraud*.
-Cronbach's internal consistency reliability coefficient \alpha were estimated for both scales and were adequate (\alpha > 0.8); the trust in elections scale \alpha = 0.93 and the expectation of electoral fraud scale \alpha = 0.86.
+I would expect composite sum or mean scores, and item responses, on these two measures to be inversely correlated among the sample, but not mutually exclusive.
+Indeed, this is what I find.
+Upon construction of the two multi-item composite scales of *trust in elections* and *expectation of fraud*, internal consistency reliability coefficient $\alpha$ were estimated for both and found to be adequate ($\alpha$ > 0.8); the trust in elections scale $\alpha$ = 0.93 and the expectation of electoral fraud scale $\alpha$ = 0.86.
 In other words, the items in each of the scales were intercorrelated well enough to compose a single scale of a (presumed) unidimensional construct.
@@
 
--   limitations: interpretations of the treatment effect are limited.
--   The sample may not be generalizable to the population.
--   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts.
--   Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
--   Moreover, results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons.
+* limitations: interpretations of the treatment effect are limited.
+  + The sample may not be generalizable to the population.
+  + It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts.
+* Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
+* Moreover, results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons.
 - First, the vignettes and many survey questions ask about Maricopa County, AZ specifically.
@@
 #| label: tbl-desc
-#| tbl-cap: "Description of Sample Demographics"
+#| tbl-cap: "Demographics and Balance"
 #| tbl-cap-location: top
@@
 # quick, informative, easy table of sample demographics w/ some other questions.
+# best method for html document
 tbl.desc <- data |>  
   labelled::set_variable_labels(
-    age_cat = "Age group, in years"
+    age_4cat = "Age group, in years",
+    gender_3cat = "Gender",
+    race2 = "Race/Ethnicity",
+    educ_4cat = "Education",
+    partyid_3cat = "Party ID"
   ) |> 
   gtsummary::tbl_summary(
-    by = qset,
+    by = group,
     include = c(
-    qset,
-    age_cat, 
+    age_4cat, 
     gender_3cat, 
-    race, 
+    race2, 
     educ_4cat, 
-    partyid_3cat,
-    ideo,
-    ideolean,
-    voted2020,
-    choice2020, 
-    voteintent,
-    milserv1,
-    milserv2,
-    milservfam),
+    partyid_3cat),
     statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
-    type = list(milserv1 ~ "categorical",
-
-                milserv2 ~ "categorical",
-                milservfam ~"categorical"), 
-    missing = "no") |> 
+    missing = "ifany",
+    missing_text = "NA") |> 
   gtsummary::add_n() |> 
@@
   gt::tab_footnote(
-    footnote = "'true' Independents do not identify nor 'lean' toward either political party",
+    footnote = "Independents do not identify nor 'lean' toward either political party",
     placement = "left"
@@
 #| label: tbl-desc-pdf
-#| tbl-cap: "Description of Sample Demographics"
+#| tbl-cap: "Demographics and Balance"
 #| tbl-cap-location: top
 
-frqs <- data |> 
-  select(group, qset, age_cat, gender_3cat, educ_4cat, race, partyid_3cat) |> 
-  map(count_prop)
-
-demog_df <- purrr::reduce(frqs, dplyr::full_join)
-
-kableExtra::kbl(demog_df,
-                booktabs = T, 
-                digits = 2,
-                col.names = c("Name", "n", "Pct")) |> 
-  kableExtra::pack_rows("Experiment Condition", 1, 2) |>
-  kableExtra::pack_rows("Question Set", 3, 4) |>
-  kableExtra::pack_rows("Age", 5, 12) |> 
-  kableExtra::pack_rows("Gender", 13, 15) |> 
-  kableExtra::pack_rows("Education", 16, 19) |> 
-  kableExtra::pack_rows("Race", 20, 24) |> 
-  kableExtra::pack_rows("Party ID", 25, 27) |> 
-  kableExtra::kable_styling(
-    latex_options = c("striped", "scale_down"),
-    full_width = F,
-    font_size = 8) |> 
-  kableExtra::column_spec(1, width = "20em")
+gtsummary::as_gt(tbl.desc) |>  
+  gt::tab_footnote(
+    footnote = "Independents do not identify nor 'lean' toward either political party",
+    placement = "left"
+    ) |>  
+  gt::cols_align(align = 'left', columns = everything()) |> 
+  gt::tab_options(
+    table.font.size = "small",
+    data_row.padding = gt::px(1)
+  )
 
@@
 The "*worthiness*" of one's trust in the conduct and administration of elections is based on the extent that outcomes of an election reasonably follow the rules prescribed and can be adjudicated as such.
-"If the process is conducted fairly and competently, and the results are determined by the actions of voters...we can call this a trustworthy election" [@stewart2022, 237].
-*Trustworthiness* is distinguished from *trust* as a psychological construct, "...the conclusion reached by the public about the functioning of the process" [@stewart2022, 237].
-To put in other terms, trustworthiness is built by the structure, procedures, and practices of the institution, in this case election administration.
-The public's trust in elections, however, is amendable to an indefinite number of factors that may be seemingly unrelated to the formal procedures of election administration.
-To illustrate, my car is trustworthy because I've known it to function quite well as a car should; it passes whatever criteria upon inspection, its sufficiently fueled, and is in generally good working order.
-I have every reason to deem it worthy of my trust.
+To put it briefly, trustworthiness is built by the structure, procedures, and practices of the institution, in this case election administration.
+The public's trust in elections, however, is amendable to an indefinite number of factors that may be unrelated to the formal structure or procedures of election administration.
+To illustrate, I can recognize that my car is trustworthy prior to ever driving it because it is structurally sound; it passes whatever criteria upon inspection, it is sufficiently fueled, and appears to be in generally good working order.
+I have every reason to deem it *worthy of my trust*.
 However, I don't trust my car because I am sure it is haunted.
@@
 
-[^4]: The cited study defined "insurrectionist sentiments" as, "...willingness to support violent efforts to overturn the results of an election in favor of another, unelected political leader." [@pape2024, 7].
-It should be noted, however, that despite the general definition, the operative items used to measure such sentiments ask about Donald Trump specifically, not an "unelected political leader".
+[^4]: Demographic breakdown of the sample are included in Appendix B.
 
 [^5]: Complete text of treatment and control vignettes are included in the Appendix
+
+[^6]: The methodological concerns between the use of (unit weighted) sum scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
+The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024].
+The use of either appears to largely depend on the researcher's particular research objective, theoretical suppositions, and necessity.
+Another common concern is the inappropriate treatment of ordinal variables as interval which levy strong assumptions, e.g., each item contributes equally to the variable being measured and that ordinal response categories are equidistant as though on an interval scale [@wang2013; for contrast, see @robitzsch2020].
+
+[^7]: Note a lack of confidence that votes will be counted as voters intend does not imply an expectation of electoral fraud.
+The reason for one's lack of confidence is uncertain, which makes it suitable as a survey item to measure the presence of trust in election administration rather than an expectation of fraud.

### 2024-12-20 docs/src/01-data.R

@@ -1,0 +1,930 @@
+# using data exported from Qualtrics on 2024-10-23
+# The most recent (i.e., last) response was recorded 2024-09-18 at 6:40pm (1840)
+# When exporting the data, Qualtrics allows me to recode 'seen but unanswered'
+# questions with code 99. I downloaded the data again just for that because I
+# want to see how many of the missing values in my 2024-09-11 dataset are
+# attributed to people who skipped survey questions.
+
+# load packages ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
+library(tidyverse)
+library(haven)
+library(surveytoolbox)
+library(labelled)
+library(sjlabelled)
+
+# load data ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
+
+# load raw SPSS export (includes display order vars)
+# downloaded on 2024-10-29 at 12:02 PM
+raw_spss <- haven::read_sav("data-raw/VMF_Election_Worker_Recruitment_Survey_with_display_order_20241029_T12.02.sav")
+
+# load raw SPSS export (doesn't include display order vars)
+# downloaded 2024-10-23 at 1:54 PM
+# raw_spss3 <- haven::read_sav(file = "data-raw/VMF_Election_Worker_Recruitment_Survey_2024-10-23_13.54.sav")
+
+# despite being a .sav file imported using `haven::read_sav()`, 
+# the data set is not "haven_labelled"
+# haven::is.labelled(raw_spss)
+
+# create data dictionary of raw SPSS data set ::::::::::::::::::::::::::::::####
+
+# A data dictionary contains metadata about the data. The
+# `labelled::generate_dictionary` function is used to create a data
+# dictionary. (alt. `surveytoolbox::data_dict`)
+# a data frame is loaded into the R environment with the number of
+# observations equal to number of variables in the original data set.
+# NOTE: surveytoolbox::data_dict function is used here because the resulting
+# dataframe can be saved as a .csv
+raw_spss_dict <- raw_spss |> surveytoolbox::data_dict()
+
+# save data dictionary of raw_spss dataset download
+write.csv(raw_spss_dict, file = "data/raw_spss_dict.csv")
+
+# create and save survey codebook ::::::::::::::::::::::::::::::::::::::::::####
+
+# this includes only the survey questions: question number (var), the question
[…]

### 2025-02-26 docs/_tex/index.tex
long overdue commit.

@@
 % Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{unicode,pdfwindowui,pdfpagemode=FullScreen}{hyperref}
 \PassOptionsToPackage{hyphens}{url}
@@
 \documentclass[
-  11pt,
-  a4paper,
-]{scrartcl}
+  12pt,
+  letterpaper,
+]{article}
 
 \usepackage{amsmath,amssymb}
-\usepackage{setspace}
 \usepackage{iftex}
@@
 }{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
 \usepackage{xcolor}
-\usepackage[inner=3cm,outer=4cm,top=3cm,bottom=4cm,headsep=22pt,headheight=11pt,footskip=33pt,ignorehead,ignorefoot,heightrounded]{geometry}
+\usepackage[margin=1in]{geometry}
 \setlength{\emergencystretch}{3em} % prevent overfull lines
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\makeatletter
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}{
-    \@ifstar
-      \xxxParagraphStar
-      \xxxParagraphNoStar
-  }
-  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
-  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}{
-    \@ifstar
-      \xxxSubParagraphStar
-      \xxxSubParagraphNoStar
-  }
-  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
-  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-\makeatother
 
@@
 
-\addtokomafont{disposition}{\rmfamily}
-\setkomafont{pageheadfoot}{\normalfont\normalcolor\footnotesize}
-\setkomafont{pagenumber}{\normalfont\normalcolor\footnotesize}
+% -----------------------
+% CUSTOM PREAMBLE STUFF
+% -----------------------
+
+% -----------------
+% Title block stuff
+% -----------------
+
+% Abstract
+\usepackage[runin]{abstract}
+\renewcommand{\abstractnamefont}{\sffamily\small\bfseries}
+\renewcommand{\abstracttextfont}{\sffamily\small}
+\setlength{\absleftindent}{5pt}
+\setlength{\absrightindent}{\absleftindent}
+
+% Title
+\usepackage{titling}
+\pretitle{\par\begin{flushleft}\LARGE\sffamily\bfseries}
+\posttitle{\par\end{flushleft}\vskip 10pt}
+
+% Keywords
+\newenvironment{keywords}
+{\small\sffamily{\sffamily\small\bfseries{Keywords.}}}
+
+% Authors
+\usepackage{orcidlink}  % Create automatic ORCID icons/links
+%\renewcommand{\and}{\end{tabular} \hskip 3em \begin{tabular}[t]{@{\hspace{0em}}l@{}}}
+\preauthor{\begin{flushleft}
+           \lineskip 1.5em}
+\postauthor{\end{flushleft}}
+
+% ------------------
+% Section headings
+% ------------------
+\usepackage{titlesec}
+\titleformat*{\section}{\Large\sffamily\bfseries\raggedright}
+\titleformat*{\subsection}{\large\sffamily\bfseries\raggedright}
+\titleformat*{\subsubsection}{\normalsize\sffamily\bfseries\raggedright}
+\titleformat*{\paragraph}{\small\sffamily\bfseries\raggedright}
+
+%\titlespacing{<command>}{<left>}{<before-sep>}{<after-sep>}
+% Starred version removes indentation in following paragraph
+\titlespacing*{\section}{0em}{2em}{0.1em}
+\titlespacing*{\subsection}{0em}{1.25em}{0.1em}
+\titlespacing*{\subsubsection}{0em}{0.75em}{0em}
 
@@
 \renewcommand\footnoterule{\rule{\linewidth}{0.1pt}\vspace{5pt}}
+
+% ------------------
+% Captions
+% ------------------
+\usepackage[labelfont=bf,labelsep=period]{caption}
+\captionsetup[figure]{font=footnotesize,justification=raggedright,singlelinecheck=false,format=hang}
+
+% ---------------------------
+% END CUSTOM PREAMBLE STUFF
+% ---------------------------
 \usepackage{booktabs}
-\usepackage{caption}
 \usepackage{longtable}
-\usepackage{colortbl}
 \usepackage{array}
-\usepackage{anyfontsize}
 \usepackage{multirow}
@@
 \usepackage{float}
+\usepackage{colortbl}
 \usepackage{pdflscape}
@@
 \usepackage{xcolor}
-\makeatletter
-\@ifpackageloaded{float}{}{\usepackage{float}}
-\floatstyle{plain}
-\@ifundefined{c@chapter}{\newfloat{hypothesis}{h}{lohyp}}{\newfloat{hypothesis}{h}{lohyp}[chapter]}
-\floatname{hypothesis}{H}
-\newcommand*\listofhypothesiss{\listof{hypothesis}{List of Hs}}
-\makeatother
 \makeatletter
@@
   filecolor={Maroon},
-  citecolor={RoyalBlue},
-  urlcolor={Blue},
+  citecolor={Blue},
+  urlcolor={RoyalBlue},
   pdfcreator={LaTeX via pandoc}}
@@
 \title{title}
-\usepackage{etoolbox}
-\makeatletter
-\providecommand{\subtitle}[1]{% add subtitle to \maketitle
-  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
-}
-\makeatother
-\subtitle{subtitle}
+% subtitles do not seem to work with article class?
+%%\usepackage{etoolbox}
+%\makeatletter
+%\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+%  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+%}
+%\makeatother
+%%\subtitle{subtitle}
 
@@
 
-\date{2024-10-16}
-
+\predate{}
+\postdate{}
+\date{}
 \begin{document}
@@
 %\noindent \rule{\linewidth}{.5pt}
-\newcommand{\datemodified}[1]{Last modified: #1}
-{\centering
-\hbox{}
-{\datemodified{2024-11-20} \par}}
 %\noindent \rule{\linewidth}{.5pt}
 
-\setstretch{2}
 \pagebreak
@@
 and confidence in the fairness and accuracy of elections, and attempt to
-boost such confidence where ever it may be deprived. Concerns for safety
-have developed among election staff and voters in more recent elections.
+boost such confidence where it may be deprived. Concerns for safety have
+developed among election staff and voters in more recent elections.
 Regular measures are taken to enhance the
@@
   on the extent that outcomes of an election reasonably follow the rules
-  prescribed and can be adjudicated as such. ``If the process is
-  conducted fairly and competently, and the results are determined by
-  the actions of voters\ldots we can call this a trustworthy election''
-  (\citeproc{ref-stewart2022}{Stewart 2022, 237}).
-  \emph{Trustworthiness} is distinguished from \emph{trust} as a
-  psychological construct, ``\ldots the conclusion reached by the public
-  about the functioning of the process''
-  (\citeproc{ref-stewart2022}{Stewart 2022, 237}). To put in other
-  terms, trustworthiness is built by the structure, procedures, and
-  practices of the institution, in this case election administration.
-  The public's trust in elections, however, is amendable to an
-  indefinite number of factors that may be seemingly unrelated to the
-  formal procedures of election administration. To illustrate, my car is
-  trustworthy because I've known it to function quite well as a car
-  should; it passes whatever criteria upon inspection, its sufficiently
-  fueled, and is in generally good working order. I have every reason to
-  deem it worthy of my trust. However, I don't trust my car because I am
-  sure it is haunted.} of the electoral process through practices meant
-to improve the conduct, transparency, or overall administration of
-elections in the United States.
+  prescribed and can be adjudicated as such. To put it briefly,
+  trustworthiness is built by the structure, procedures, and practices
+  of the institution, in this case election administration. The public's
+  trust in elections, however, is amendable to an indefinite number of
+  factors that may be unrelated to the formal structure or procedures of
+  election administration. To illustrate, I can recognize that my car is
+  trustworthy prior to ever driving it because it is structurally sound;
+  it passes whatever criteria upon inspection, it is sufficiently
+  fueled, and appears to be in generally good working order. I have
+  every reason to deem it \emph{worthy of my trust}. However, I don't
+  trust my car because I am sure it is haunted.} of the electoral
+process through practices meant to improve the conduct, transparency, or
+overall administration of elections in the United States.
 
@@
 trustworthiness of election administration in the United
-States\footnote{It is important to point out here that election
-  administration is just one institution that interacts with many other
-  institutions and processes which form the electoral system \emph{writ
-  large} (\citeproc{ref-stewart2022}{Stewart 2022}). The way in which I
-  discuss the institution of election administration, as well as the way
-  in which I discuss and distinguish public trust in elections from
-  broader conceptions of public trust, is borrowed substantively from
-  Stewart (\citeproc{ref-stewart2022}{2022})'s conceptual framework of
-  the same. Distinctions between \emph{trust} and \emph{trustworthiness}
-  and the notion of election administration as an institution are
-  already apparent inspirations convenient for situating the theory of
-  this research inquiry.}. Or in other words, there is only so much that
-election officials can do to sustain or improve public trust in election
-administration.
+States\footnote{There's little that could justify a conceptual
+  distinction between public trust pre-election and public trust
+  post-election. The temporal element renders the difference between
+  pre- and post-election more operative than conceptual at a
+  foundational level.}.
 
 Even though election officials can do a lot to secure election
-integrity, especially under intense scrutiny, there's not much they can
-do to cement public confidence after election night passes. At best,
-election officials can ease public anxieties prior to election night. As
-mentioned, this usually consists of enhancing procedures and practices
-and adapting to advancing election technology.
+integrity, there's not much they can do to cement public confidence
+after election night passes. At best, election officials can ease public
+insecurities prior to election night.
 
@@
 reasonable to expect that the group an election worker hails from would
-be an important influence upon the voter's perception or evaluation of
-their own experience as well as subsequent evaluations of the electoral
-process. Supposing such is the case, we can expect that information
-about \emph{who} (i.e., which groups) election officials are targeting
-in publicized recruitment efforts would lessen particular election
-anxieties. That is to say, it is reasonable to expect that telling
-people \emph{who} will be working as election staff and volunteers would
-ease election anxieties, therefore improve confidence that the election
-will be conducted fairly, accurately, and safe for all involved.
+be an important influence upon the voter's evaluation of the electoral
+process.
+
+Supposing such is the case, we can expect that information about
+\emph{who} (i.e., which groups) election officials are targeting in
+publicized recruitment efforts would lessen particular election
+insecurity, and concurrently, boost confidence. That is to say, it is
+reasonable to expect that telling people \emph{who} will be working and
+volunteering as election staff would ease election insecurity, and
+therefore improve confidence that the election will be conducted fairly,
+accurately, and safe for all involved.
 
@@
 administered to test whether publicized efforts to recruit veterans to
-work as election staff and volunteers would ease election anxieties
-(e.g., concern for electoral fairness and accuracy, as well as concerns
-for voter safety). Results of the survey experiment support the
-hypothesis that emphasizing veterans as the target of election worker
-recruitment efforts eases pre-elections anxieties to an extent. In
-particular, among those who read the treatment vignette, confidence that
-the elections would be fair and accurate was higher in comparison. In
-addition, expectations of electoral fraud were lower, as were concerns
-for voter safety compared to those who read a control vignette. Notable
-is that there was a significant increase in confidence, and lower
-expectations of fraud, among those who believe that the 2020 election
-was illegitimate.
-
-\begin{itemize}
-\tightlist
-\item
-  when distinguished by partisanship\ldots{}
-\item
-  moreover, broken down by other demographic variables such as race,
-  gender, education, etc.
-\item
-  holding these factors constant demonstrates a
-  {[}increased/decreased{]} likelihood that a respondent's confidence
-  would likely {[}increase/decrease{]}, expectations of fraud would
-  likely {[}increase/decrease{]}, and concerns for safety would lessen
-  among those in the treatment group compared to those in the control.
-  These results allow us to attribute the differences to the treatment
-  stimulus, namely, the prospect of having veterans serve as election
-  staff or volunteers.
-\end{itemize}
+work as election staff and volunteers would improve public trust in
+elections and ease election insecurity. Results of the survey experiment
+support the notion that emphasizing veterans as the target of election
+worker recruitment efforts eases pre-election insecurity to a limited
+extent. Expectations of electoral fraud and concerns for voter safety
+were lower among those who read a fabricated announcement that veterans
+are being recruited to work as election staff and volunteers compared to
+those who read a control vignette where veterans were not mentioned.
+Notable is that there was a significant difference in confidence among
+those in the treatment condition who believe that results of the 2020
+election were illegitimate.
+
+This paper is structured as follows. First, I provide a brief background
+on public trust in election administration. I synthesize a review of
+relevant literature with a focus on how political and social science has
+conceptualized and ascertained public trust in elections. Next, I supply
+reasoning for why military veterans are singled out as the relevant
+subset of the population in this study. I then explicitly provide the
+simple theory and testable hypotheses of the study before moving on to
+describe the design of the survey, the measurement instruments therein,
+and the conceptual and operational definitions of the variables of
+interest. I explain my reasoning and method for constructing the primary
+dependent variable, which I broadly refer to as \emph{confidence in
+elections}. I preview the different methods of analysis alongside
+presentation of the results. Before concluding, I dedicate time to
+discuss the limitations of the study and lessons learned. I close by
+offering my interpretation of the results and suggest potential avenues
+for future inquiry.
 
@@
 commitment of election staff, and more
-(\citeproc{ref-atkeson2007}{Atkeson and Saunders 2007}). These somewhat
-generic issues of election worker staffing, competence, and voting
-technology were likely mere stepping stones leading to more intense
-election administration issues.
+(\citeproc{ref-atkeson2007}{Atkeson and Saunders 2007}).
 
 In 2024, election officials made valiant efforts to boost public
-confidence in the fairness and accuracy of elections within an
-intensified political climate that appeared quite hostile to election
-officials (\citeproc{ref-brennancenterforjustice2024}{Brennan Center for
-Justice 2024}; \citeproc{ref-edlin2024}{Edlin and Norden 2024}).
-Although polling around the time indicated that most people thought that
-U.S. elections would be run at least somewhat well
+confidence elections within an intensified political climate that
+appeared quite hostile to election officials
+(\citeproc{ref-brennancenterforjustice2024}{Brennan Center for Justice
+2024}; \citeproc{ref-edlin2024}{Edlin and Norden 2024}). Although
+polling around the time indicated that most people thought that U.S.
+elections would be run at least somewhat well
 (\citeproc{ref-nadeem2024}{Nadeem 2024}), many election officials
 nationwide took efforts to assuage the worry of those most skeptical.
-Enhancing trustworthiness in election administration is a regular duty
-for election officials, but baseless allegations regarding the fairness
-and accuracy of the 2020 election loomed ever larger, and the fear of
-political violence became prominent for both election officials and the
-public. Safety concerns for election staff, volunteers, and voters alike
-only added to, and perhaps exacerbated, public concern for the integrity
-of election administration in the United States. Especially as the
-steady increase in election official turnover seems to be increasing
-even more (\citeproc{ref-ferrer2024}{Ferrer, Thompson, and Orey 2024}).
 
@@
 heightening concerns over the prospect of political violence and, in
-turn, engendered increased worry for the safety of voters and election
-workers alike.
-
-Suffice to say, pre-election anxiety consists of more than concerns over
+turn, increased worry for the safety of voters and election workers
+alike.
+
+Suffice to say, pre-election anxiety consists of more than confidence in
 fairness and accuracy of vote counts in light of added safety concerns.
 It is not hard to recognize that increased tension in the pre-election
-period makes for a volatile political environment.
+period makes for a volatile political environment. Sustaining
+trustworthiness in election administration is only more difficult in an
+environment where turnover of election workers increases and the
+struggle to recruit volunteers worsens in light of safety concerns.
+Since election worker performance is significant to public evaluation of
+elections, added safety concerns that drive out election staff and repel
+volunteers can only detract from trustworthiness of the institution.
 
@@
 
+Trust and confidence in the conduct of elections concerns aspects of
+elections that fall squarely within the institution of election
+administration. At this level, for instance, public trust is ascertained
+by capturing assessments about the perceived accuracy of vote counts
+(e.g., whether votes are/were counted as intended). Or in other words,
+by the extent the public is confident in the accurate administration of
+elections.
+
 Assessing the public's \emph{trust} in elections has not been
-straightforward. Inquiry into public trust in elections has been
-approached by scholars of political science in many different ways
-(\citeproc{ref-cook2005}{Cook and Gronke 2005}), often distinguishable
-by the scope of the research question and more or less constrained by
-the particular conception of public trust. Quite often, trust in
-election administration is conflated with trust in government writ
-large, government legitimacy, government or system responsiveness, or
-even satisfaction with democracy (\citeproc{ref-daniller2019}{Daniller
-and Mutz 2019}). At this level, not only is the level of public trust in
+straightforward, however. Inquiry into public trust in elections has
+been approached by scholars of political science in many different ways
+(\citeproc{ref-cook2005}{Cook and Gronke 2005};
+\citeproc{ref-hardin2004}{Hardin 2004}), often distinguishable by the
+scope of the research question and more or less constrained by the
+particular conception of public trust. Quite often, trust in election
+administration is conflated with trust in government \emph{writ} large,
+government legitimacy, government or system responsiveness, or even
+satisfaction with democracy (\citeproc{ref-daniller2019}{Daniller and
+Mutz 2019}). At this level, not only is the level of public trust in
 elections sometimes vague, but there's little consideration over the
@@
 
-Election administration is just one part of the larger set of
-institutions which form the electoral system. As such, the performance
-of the institution along with the rest ``\ldots lends credibility to the
-outcome of an election: whether it is considered by citizens and the
-international community to be fair and legitimate.''
-(\citeproc{ref-stewart2022}{Stewart 2022, 236}).
-
-Trust and confidence in the conduct of elections concerns aspects of
-elections that fall squarely within the institution of election
-administration. At this level, for instance, public trust is ascertained
-by capturing assessments about the perceived accuracy of vote counts
-(e.g., whether votes are/were counted as intended). Or in other words,
-public trust is ascertained by the extent the public perceives the
-institution of election administration as trustworthy.
-
-Intuitively, enhancing public trust in elections would best be
-accomplished by enhancing the \emph{trustworthiness} of the institution,
-i.e., consistently doing the things that election officials already
-regularly do come election time. However, trust and confidence in
-elections has become ever more precarious over the last few election
-cycles. Especially considering public polling data since 2000 shows that
-confidence that votes were, or would be, counted as intended was in a
-consistent decline despite efforts towards bolstering election integrity
-and trustworthiness (\citeproc{ref-sances2015}{Sances and Stewart
-2015}). This is even more pronounced considering the role that
-partisanship has had on such confidence over accuracy of vote count
-(\citeproc{ref-sances2015}{Sances and Stewart 2015};
-\citeproc{ref-stewart2022}{Stewart 2022}).
+Elections administration is just one institution a part of the larger
+set of institutions which form the electoral system. As such, the
+performance of the institution along with the rest ``\ldots lends
+credibility to the outcome of an election: whether it is considered by
+citizens and the international community to be fair and legitimate.''
+(\citeproc{ref-stewart2022}{Stewart 2022, 236}). Intuitively, enhancing
+public trust in elections would best be accomplished by enhancing the
+\emph{trustworthiness} of the institution, i.e., consistently doing the
+things that election officials already regularly do come election time.
+However, trust and confidence in elections has become ever more
+precarious over the last few election cycles. Especially considering
+public polling data since 2000 shows that confidence that votes were, or
+would be, counted as intended was in a consistent decline despite
+efforts towards bolstering election integrity and trustworthiness
+(\citeproc{ref-sances2015}{Sances and Stewart 2015}). This is even more
+pronounced considering the role that partisanship has had on such
+confidence over accuracy of vote count (\citeproc{ref-sances2015}{Sances
+and Stewart 2015}; \citeproc{ref-stewart2022}{Stewart 2022}).
 
@@
 the pre-election period as the same trust after the election results
-have come out\footnote{There's little that could justify a conceptual
-  distinction between public trust pre-election and public trust
-  post-election. The temporal element renders the difference between
-  pre- and post-election operative rather than conceptual.}. The former
-is \emph{anticipatory}---i.e., the kind that is more or less anxious
-given the uncertainties surrounding the election. The latter is
-\emph{evaluative}---a judgement discerned empirically in hindsight after
-the election event has occurred. The evaluative form of trust lends to
-inquiries interested in public opinion on regime legitimacy,
-satisfaction with democracy, and perceived responsiveness
-(\citeproc{ref-daniller2019}{Daniller and Mutz 2019}). This study
-focuses primarily on that \emph{anticipatory} kind of trust and
-confidence, which speaks more to electoral anxieties over the
-institution of election administration. Not to mention that by
-definition, one feels anxiety over impending uncertainties located in
-the future\footnote{Note that \emph{anxiety} is taken to be the inverse
-  of \emph{trust and confidence}, as in, one who is less confident in
-  this or that is thereby more anxious over the matter in question. As
-  such, anxiety may equivalently be discussed as trust/confidence
-  without issue except for framing of said discussion. Electoral anxiety
-  is used in place of electoral trust/confidence simply to emphasize the
-  anticipatory nature of the attitudes in question.}.
-
-The primary interest of this study concerns \emph{election anxieties},
-which is distinguished into two categories: fairness and accuracy, and
-voter safety. Of course, the direction of electoral outcomes are a
-particular source of electoral anxiety, but only the election outcome
-itself can resolve any nail-biting stress over its anticipated
-direction. In contrast, the anxieties of interest here are able to be
-relaxed to some extent prior to the election given some intervention.
-
-Interventions aimed at improving public trust, or rather, aimed at
-easing election anxieties may not be within the usual repertoire
-election officials draw upon. Regardless of the measures taken by
-election officials to boost public confidence in the
-\emph{trustworthiness} of election administration (e.g., conducting
-audits, testing election machines), public \emph{trust} and confidence
-in elections more generally is apt to shift dramatically post-election
-based on factors such as partisanship, elite rhetoric, particular state
-policies, and more (\citeproc{ref-carter2024}{Carter et al. 2024};
+have come out. The former is \emph{anticipatory}---i.e., the kind that
+is more or less anxious given the uncertainties surrounding the
+election. The latter is \emph{empirical}---a judgement discerned in
+hindsight after the experience of the election event has occurred.
+Evaluations of one's own trust and confidence in election administration
+based on the experience of voting is influenced by that very experience.
+As discussed by Stewart (\citeproc{ref-stewart2022}{2022}), not only was
+confidence in vote count accuracy influenced by the voter experience,
+but so too were evaluations of election officials
+(\citeproc{ref-stewart2022}{2022, 242--43}). Not to mention the
+influence that the election results would also have on such evaluations.
+In other words, evaluations of trust and confidence post-election are
+influenced by one's interpretation of their experience. The subtle
+difference is simply the degree of uncertainty one feels in anticipation
+of the next election event. This study focuses primarily on that
+\emph{anticipatory} kind of confidence, which speaks more to those
+insecurities\footnote{Note that election insecurity is used in place of
+  electoral confidence simply to emphasize the anticipatory nature of
+  the attitudes in question. Election insecurity is taken to denote a
+  lack of confidence.} based on perceptions of the institution's
+trustworthiness than upon the particular voter experience.
+
+Regardless of the measures taken by election officials to boost public
+confidence in the \emph{trustworthiness} of election administration
+(e.g., conducting audits, testing election machines), public
+\emph{trust} and confidence in elections more generally is apt to shift
+dramatically post-election based on factors such as partisanship, elite
+rhetoric, particular state policies, and more
+(\citeproc{ref-carter2024}{Carter et al. 2024};
 \citeproc{ref-coll2024a}{Coll and Clark 2024};
@@
 Beyond the general competence of election workers, however, the quality
-of the voter experience may be influenced merely by impressions about
-\emph{who} comprises election staff and volunteers. Political and other
-social science researchers have recognized for some time the power that
-group identity can have over attitudes and perception
-(\citeproc{ref-vanbavel2021}{Van Bavel and Packer 2021};
+of the voter experience may be influenced merely by \emph{a priori}
+impressions about \emph{who} comprises election staff and volunteers.
+Political and other social science researchers have recognized for some
+time the power that group identity can have over attitudes and
+perception (\citeproc{ref-vanbavel2021}{Van Bavel and Packer 2021};
 \citeproc{ref-xiao2016}{Xiao, Coppin, and Van Bavel 2016};
@@
 recruited to serve as election staff will be enough to improve trust and
-confidence in election administration, i.e., ease election anxieties. It
-was hypothesized that information on recruitment efforts targeting
-military veterans to work as election staff would ease election
-anxieties. The next section elaborates further on why military veterans
-are of particular interest.
+confidence in election administration, and lessen expectations of
+electoral fraud. The next section elaborates on why military veterans
+are of particular interest in this regard.
 
@@
 point, young people were sometimes given special mention as targets of
-election worker recruitment efforts\footnote{The cited study defined
-  ``insurrectionist sentiments'' as, ``\ldots willingness to support
-  violent efforts to overturn the results of an election in favor of
-  another, unelected political leader.'' (\citeproc{ref-pape2024}{Pape
-  et al. 2024, 7}). It should be noted, however, that despite the
-  general definition, the operative items used to measure such
-  sentiments ask about Donald Trump specifically, not an ``unelected
-  political leader''.} (\citeproc{ref-herndon2020}{Herndon 2020};
-\citeproc{ref-powerthepolls2020}{Power the Polls 2020}). Generally,
-however, recruitment efforts cast a wide net, indiscriminate of who
-applies (\citeproc{ref-conde2020}{Conde 2020};
+election worker recruitment efforts (\citeproc{ref-herndon2020}{Herndon
+2020}; \citeproc{ref-powerthepolls2020}{Power the Polls 2020}).
+Generally, however, recruitment efforts cast a wide net, indiscriminate
+of who applies (\citeproc{ref-conde2020}{Conde 2020};
 \citeproc{ref-ross2020}{Ross 2020}).
@@
 regard to research demonstrating that willingness to support violent
-efforts to overturn election results\footnote{Prior to 2021, I found one
-  online recruitment brochure intent on recruiting veterans to serve as
-  election workers (\citeproc{ref-studentveteransofamerica2020}{Student
-  Veterans of America 2020}).} (in support of Trump) is, on average,
-more common among veterans than among matched samples of non-veterans
-(\citeproc{ref-pape2024}{Pape et al. 2024}). This is in addition to a
-strengthened association portrayed in media outlets between military
-veterans and militias (\citeproc{ref-steinhauer2020}{Steinhauer 2020}).
-Although such media output reeks of the contemporary political context,
-prior research has substantiated such a connection between veterans and
-militia groups. A. Cooter (\citeproc{ref-cooter2024}{2024}) notes from
-her 3-year ethnographic fieldwork among Michigan militia members that,
+efforts to overturn election results (in support of Trump) is, on
+average, more common among veterans than among matched samples of
+non-veterans (\citeproc{ref-pape2024}{Pape et al. 2024}). This is in
+addition to a strengthened association portrayed in media outlets
+between military veterans and militias
+(\citeproc{ref-steinhauer2020}{Steinhauer 2020}). Prior research has
+substantiated such a connection between veterans and militia groups. A.
+Cooter (\citeproc{ref-cooter2024}{2024}) notes from her 3-year
+ethnographic fieldwork among Michigan militia members that,
 ``\ldots approximately 40\% of militia leaders and 30\% of members had
@@
 
-\subsection{Research Design and
-Method}\label{research-design-and-method}
-
-To test the theory that publicized efforts to recruit veterans to work
-as election staff and volunteers would ease election anxieties, a recent
-survey experiment was embedded in a survey developed and conducted by
-the Center for Democracy and Civic Engagement (CDCE) at the University
-of Maryland (UMD). The survey was fielded from August 29th, 2024 to
-September 18th, 2024 on a non-probability sample of 1,287 U.S. citizens
-18 years of age or older.
-
-The primary independent variable is the prospect of military veterans as
-poll workers. It was considered that veterans would elicit high degrees
-of approval and support for whatever cause or issue presented. For
-example, I'd expect high approval and support for recruiting veterans to
-baseball teams just as much as for recruiting them to work as election
-staff. Asking participants whether they supported programs intent on
-recruiting veterans to work as election staff would garner support
-regardless of the target group. Considering that support and admiration
-for veterans is generally high among the population
+\subsection{Theory and Hypotheses}\label{theory-and-hypotheses}
+
+Considering the generally positive perception afforded to veterans by
+the public, it is reasonable to suspect that efforts that promote
+recruitment of veterans and their family members to work as election
+staff and volunteers would boost public confidence in election
+administration. Indeed, that is the primary hypothesis of this study.
+Although citizens may vote in various ways across the country (e.g., by
+mail, ballot drop box, in-person), the simple announcement that election
+officials are engaging in efforts to recruit veterans to work as
+election staff may boost confidence in elections administration
+regardless of how, or whether, an individual plans to vote. Formally,
+
+\begin{quote}
+H\textsubscript{1}: Announcements that election officials are recruiting
+miilitary service veterans to work as election staff and volunteers will
+be associated with greater confidence in elections administration
+compared to announcements that do not mention military veterans.
+\end{quote}
+
+I considered that veterans would elicit high degrees of approval and
+support for whatever cause or issue presented. For example, I'd expect
+high approval and support for recruiting veterans to baseball teams just
+as much as for recruiting them to work as election staff. Likewise,
+asking participants whether they supported programs intent on recruiting
+anyone to work as election staff would garner support regardless of the
+target group. Considering that support and admiration for veterans is
+generally high among the population
 (\citeproc{ref-kleykamp2023}{Kleykamp, Schwam, and Wenig 2023}), then
 discerning the impact on one's confidence would require a survey
-experiment and questions designed to determine whether veterans have any
-special effect on electoral confidence and voter safety distinct from
-the generally high admiration observed most often.
-
-Survey participants were randomly assigned to read one of two fabricated
-news articles (i.e., vignettes) about recruitment efforts for election
-jobs. Participants read either a treatment or control vignette, which
+experiment designed to determine whether publicized recruitment efforts
+targeting veterans as a group would have any special effect on
+confidence in elections administration.
+
+Since the results and events following the 2020 election loomed large in
+anticipation of the U.S. 2024 general elections, it is reasonable to
+take into account beliefs about legitimacy of the 2020 election. This
+group who denies the legitimacy of the 2020 election results were
+possibly the most distrusting of the 2024 election. However, given that
+veteran service members are held in high regard, generally speaking,
+announcing that veterans are being actively recruited to work as
+election staff and volunteers is expected to positively influence
+confidence in elections among those who remained firm in the belief that
+the 2020 election results were illegitimate. I take into account that
+legitimacy beliefs about the 2020 election and expectations of electoral
+fraud are related to partisanship and include partisanship as a control
+in the analysis.
+
+In addition, I expect that both expectations of electoral fraud and
+concerns for voter safety would lessen (shrink) when presented with
+information that veterans are being actively recruited to work and
+volunteer in election offices.
+
+Finally, prior research has shown that confidence that one's own vote
+would be counted as intended has been much stronger than confidence that
+votes nationwide would be treated likewise
+(\citeproc{ref-sances2015}{Sances and Stewart 2015};
+\citeproc{ref-stewart2022}{Stewart 2022}). In other words, the public is
+more trusting of elections closer to home. Taking into account that
+confidence is lower for elections conducted outside of one's local area,
+then information that veterans are being recruited to help conduct
+elections in locations beyond one's locale may close this gap between
+confidence in elections within one's local area and confidence in
+elections elsewhere. Although it may be difficult to discern whether
+recruiting veteran service members would improve confidence in elections
+near one's local area in light of such hometown favoritism, a positive
+effect on confidence in elections held beyond one's local area---where
+confidence is already expectedly lower---can help discern the impact of
+the group alone. Therefore, any observed disparity of confidence in
+elections (i.e., the ``confidence gap'') between elections within one's
+local area and elections beyond will be smaller when people are
+presented with information about election official recruitment efforts
+of veteran service members.
+
+\subsection{Experiment Design and Survey
+Measures}\label{experiment-design-and-survey-measures}
+
+To test the theory that publicized efforts to recruit veterans to work
+as election staff and volunteers would improve confidence in elections
+and ease insecurity, a recent experiment was embedded in a survey
+developed and conducted by the Center for Democracy and Civic Engagement
+(CDCE) at the University of Maryland. The survey was fielded from August
+29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287
+U.S. citizens 18 years of age or older. Respondents were randomly split
+into either the treatment (\(n =\) 650) control (\(n =\) 637)
+conditions\footnote{Demographic breakdown of the sample are included in
+  Appendix B.}.
+
+Survey participants read either a treatment or control vignette, which
 was a fabricated news article about efforts in Maricopa County, AZ to
@@
 and their family members and describes an interviewee ``Jordan Braxton''
-as an Army veteran; whereas the control vignette simply omitted any
-mention of veterans and their family members, and didn't describe
-``Jordan Braxton'' as an Army veteran. Beyond those small differences
-and the headlines, the article vignettes are identical. Any effects can
+as an Army veteran. The control vignette simply omitted any mention of
+veterans and their family members, and didn't describe ``Jordan
+Braxton'' as an Army veteran. Beyond those small differences and the
+headlines, the article vignettes are identical. Therefore, effects can
 be attributed to the information about veterans in the treatment
@@
 It should be noted that Maricopa County, AZ was chosen as the setting of
-the story in the vignettes due to the increased scrutiny levied toward
+the story in the vignette due to the increased scrutiny levied toward
 election administration there after the 2020 election
@@
 \citeproc{ref-maricopacountyelectionsdepartment2022}{Maricopa County
-Elections Department 2022}). In addition, the survey includes a series
-of items which ask specifically about Maricopa County, AZ and a
-comparable series of questions about one's local area\footnote{The
-  setting of the vignettes and inclusion of duplicate questions in the
-  survey are highlighted and discussed later.}.
+Elections Department 2022}). Because of this, treatment effects are
+potentially limited or constrained to attitudes concerning the location
+specified in the vignette. A block of survey items asked specifically
+about Maricopa County, AZ, followed by an identical block of items that
+asked the same questions about one's local area. Later, I compare and
+discuss results between the items pertaining to different settings.
 
 Over the past two decades it became commonplace for national polls to
-gauge public confidence in election administration by asking some
-variety of the question, ``How confident are you that your vote {[}will
-be/was{]} counted as you intended in the most recent election?''
-(\citeproc{ref-hall2009}{T. E. Hall, Quin Monson, and Patterson 2009};
-\citeproc{ref-sances2015}{Sances and Stewart 2015};
+gauge public confidence in election administration (i.e., voter
+confidence) by asking some variety of the question, ``How confident are
+you that your vote {[}will be/was{]} counted as you intended in the most
+recent election?'' (\citeproc{ref-hall2009}{T. E. Hall, Quin Monson, and
+Patterson 2009}; \citeproc{ref-sances2015}{Sances and Stewart 2015};
 \citeproc{ref-stewart2022}{Stewart 2022}). In addition, since 2008, the
@@
 voter experience with the institution more directly. This study borrows,
-modifies, or takes inspiration from certain questions found within the
-2022 SPAE and other survey items used by the Pew Research Center
-(\citeproc{ref-dunn2018}{Dunn 2018}). These survey items comprise the
-dependent variables\footnote{All survey items are included in the
-  Appendix.}.
-
-The outcomes of interest (i.e., dependent variables) are broadly
-referred to as \emph{election anxieties}, but more specifically refer to
-confidence over fairness and accuracy of the election administration;
-expectations of fraudulent activity intent on manipulating the electoral
-outcomes; and concern for voter safety, i.e., comfort voting in-person
-as it relates to expectations of violence, threats, or intimidation. The
-following presents multiple one-sided directional hypotheses. Previous
-research on public perception and regard for U.S. military veterans
-gives credence to the directional hypotheses
-(\citeproc{ref-kleykamp2018}{Kleykamp, Hipes, and MacLean 2018};
-\citeproc{ref-kleykamp2023}{Kleykamp, Schwam, and Wenig 2023}).
-
-The first outcome of interest regards \emph{trust and confidence} in
-election administration, which includes the integrity and security of
-the electoral process, administration, technology, and people or
-organizations to fairly and accurately conduct elections. Survey items
-measured the degree of confidence that votes will be counted as voters
-intend, confidence that electoral systems are secure from technological
-threats, perceived commitment of election staff, confidence that
-outcomes will be fair, as well as confidence that the voting process
-will be fair.
-
-The first hypothesis is as follows:
-
-\(H_{1}:\) Trust and confidence in election administration will be
-higher among those who were presented information about efforts to
-recruit veterans as election workers compared to those who were not
-
-In total, six survey items measure different aspects of trust and
-confidence in election administration. These items were analyzed
-individually but were also transformed into a composite scale of trust
-and confidence.
-
-The literature concerning public regard for veterans gives substantial
-reason to expect that publicized efforts to recruit veterans to work as
-election staff and volunteers would have the effect of easing election
-anxieties. As such, survey participants also responded to a series of
-questions that inquired into expectations of electoral fraud---i.e.,
-fraudulent activity intent on manipulating the electoral outcome.
-
-Note, however, that an \emph{expectation} of electoral fraud implies a
-degree of distrust more so than an agitated state of anxiety over the
-\emph{potential} for electoral fraud. Conceptually, this may be
-considered a particular kind of `anxiety' given that is it pre-election
-(hence, an expectation), however, not necessarily. A person may be
-rather confident with regard to how much they distrust the integrity of
-electoral administration, resulting in such expectations.
-
-For instance, the first item of the 5-item series asks participants to
-report their expectation that ``There will be voter fraud, that is,
-people who are not eligible to vote will vote or vote more than once''
-on a 4-option response scale ranging from ``Not likely at all'' to
-``very likely''. This statement, as well as the rest in the series,
-asserts an expected compromise of election integrity, which speaks to
-the trustworthiness of the institution. What the individual expects,
-more or less, is that electoral fraud will occur, implying that
-fraudulent attempts will be successful.
-
-It was expected that the experimental stimulus would result in lower
-expectation for electoral fraud among those who read the treatment
-vignette compared to those who read the control vignette. The second
-hypothesis is,
-
-\(H_{2}:\) Expectations of electoral fraud will be lower among those who
-were presented information about efforts to recruit veterans as election
-workers compared to those who were not
-
-Another outcome of interest regards concerns about voting in-person at a
-polling site, i.e., voter safety. That is, the extent people feel that
-voters are safe enough to cast a vote at polling sites free from
-violence, threats of violence, or intimidation. Two survey items use
-slightly different questions to inquire about the same essential
-issue---i.e., perceptions of physical safety at the polls. The third
-hypothesis follows,
-
-\(H_{3}:\) Concerns for voter safety be lower among those who are
-presented information about efforts to recruit veterans as election
-workers compared to those who are not
-
-Another outcome of interest concerned how particular actions of election
-officials, or circumstances at polling sites, would impact the
-confidence of election integrity as well as voter safety \emph{from the
-perspective of survey respondents}. Survey participants responded to a
-series of six statements, all prefaced with the same question,
-``Regardless of whether any of these are actually the case, how would
-the following impact your confidence in the fairness and accuracy of
-elections conducted this November?'' The six statements were,
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Election officials test every machine used in the election to ensure
-  they are secure.
-\item
-  Election officials conduct audits of ballots after every election to
-  confirm the results were accurate.
-\item
-  Poll watchers affiliated with the political parties or candidates
-  observe the election.
-\item
-  Election staff and volunteers include military veterans and their
-  family members from the community.
-\item
-  Election staff and volunteers include lawyers from the community.
-\item
-  Election staff and volunteers include college students from the
-  community.
-\end{enumerate}
-
-For each statement, survey participants responded by selecting one of
-five response options:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Decrease confidence a lot
-\item
-  Decrease confidence somewhat
-\item
-  No impact on confidence
-\item
-  Increase confidence somewhat
-\item
-  Increase confidence a lot
-\end{enumerate}
-
-It was expected that respondents would estimate stronger impact on their
-confidence given they were assigned to read the treatment vignette
-compared to those who were not. Thus, the hypothesis is,
-
-\(H_{4}:\) Respondents who read the treatment vignette will report
-stronger impact on their personal confidence in fairness and accuracy of
-election administration when veterans are stated to be included among
-election staff and volunteers compared to those who read the control
-vignette.
-
-The extent people believe veterans are more trustworthy as election
-workers than non-veterans in general is difficult without comparable
-groups to consider. Recruitment efforts in 2022 targeted young students,
-lawyers, and military veterans (\citeproc{ref-wang2022}{Wang 2022}).
-Thus, lawyers and college students were selected as two groups for which
-responses could be compared between different statement versions.
-
-The goal was to determine whether there is anything special in having
-veterans volunteer as election staff (i.e., poll workers) compared to
-other groups. That is, does it make any difference in terms of concerns
-over election security, fairness, and voter safety to include veterans
-as election staff and volunteers compared to other groups? The fourth
-hypothesis, irrespective of the experimental stimulus, reads,
-
-\(H_{5}:\) Respondents who read the treatment vignette will report
-stronger impact on their personal confidence in fairness and accuracy of
-election administration when veterans are stated to be included among
-election staff and volunteers compared to identical statements about
-lawyers or college students.
+modifies, or takes inspiration from certain question items found within
+the 2022 SPAE and other survey items from the Pew Research Center's 2018
+American Trends Panel wave 38 (\citeproc{ref-dunn2018}{Dunn 2018}).
+
+Note that, except for the item assessing voter confidence (i.e., votes
+counted as voters intend), most other question items from the 2022 SPAE
+inquire into the voter experience after the election has occurred. The
+items in this study, however, all inquire into confidence over one's
+expectations in anticipation of upcoming elections. In addition, other
+survey questionnaires ask similar questions that specifically contrast
+between a respondent's own local community, their state, and nationwide;
+this is in addition, or complementary to, items that distinguish between
+local area officials, state election officials, state government, and
+the U.S. federal government. The survey of this study, instead, focused
+on attitudes regarding election workers such as election officials,
+staff, and volunteers specific to the location mentioned in the
+vignette---Maricopa County, AZ---as well as specific to one's local
+area\footnote{Note that I refer to the items as either `AZ items' or
+  `local items' in order to distinguish the location in which they
+  pertain.}.
+
+The survey included items that assessed both trust in elections
+administration and expectations of electoral fraud, referred to simply
+as \emph{trust} and \emph{distrust}, respectively. Responses from these
+two sets of items were utilized to construct the primary dependent
+variable, \emph{confidence in elections}.
+
+Prior to the reading the treatment or control vignette, participants
+responded to distinct survey items assessing one's favorability to local
+election officials (``In general, how favorable or unfavorable is your
+impression of local election officials?'') and legitimacy of the 2020
+election results (``Regardless of whom you supported in the 2020
+election, do you think Joe Biden's election as president was legitimate,
+or was he not legitimately elected?''). The former presented five
+response options from ``Strongly favorable'' to ``Strongly
+unfavorable''; the latter item presented a binary of either
+``Legitimate'' or ``Not Legitimate''.
+
+The conventional multiple item assessment of partisanship was included
+and used to construct a variable of partisanship consisting of three
+categories: Democrat, Republican, and Independent. In this case,
+Independents are ``true'' Independents in that they do not identify with
+either political party and do not ``lean'' toward either Republican or
+Democratic parties. Self-described ``Independent leaners'' are re-coded
+as falling into the partisan category in which they lean e.g.,
+Independents who expressly report that they lean Republican are denoted
+as Republican.
+
+Finally, a pair of survey items assessed concerns for potential violence
+and confidence in voter safety. The pair was asked once in regard to
+Maricopa County, AZ and again with respect to one's local
+area\footnote{Survey item wording and responses are included in Appendix
+  A.}.
+
+\subsubsection{Trust and Distrust in
+Elections}\label{trust-and-distrust-in-elections}
+
+A set of five survey items measured public trust in elections by
+inquiring into the degree of confidence that votes will be counted as
+voters intend, confidence that electoral systems are secure from
+technological threats, perceived commitment of election staff,
+confidence that outcomes will be fair, and confidence that the voting
+process will be fair. Each item in this series presented four response
+options from ``Not at all {[}confident/committed{]}'', ``Not too
+{[}confident/committed{]}'', ``Somewhat {[}confident/committed{]}'', and
+``Very {[}confident/committed{]}''. In total, five survey items measure
+different aspects of trust in elections administration. The items
+measuring confidence in elections include:
+
+Another series of five survey items captured an individual's level of
+\emph{distrust} in elections administration based on the extent to which
+they \emph{expect electoral fraud} to occur. These items were prefaced
+with the question, ``How likely do you think any or all of the following
+will happen during this year´s elections in {[}Maricopa County, AZ/ your
+local area{]}?'' Each item presented four response options: ``Not likely
+at all'', ``Not too likely'', ``Somewhat likely'', and ``Very likely''.
+
+\begin{table}
+
+\caption{\label{tbl-items}Survey Items for Trust and Distrust in
+Elections}
+
+\centering{
+
+\begingroup\fontsize{8}{10}\selectfont
+
+\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{8cm}>{\raggedright\arraybackslash}p{8cm}}
+\toprule
+Trust & Distrust\\
+\midrule
+How confident are you that votes in Maricopa County, AZ will be counted as voters intend in the elections this November?
+& There will be voter fraud, that is, people who are not eligible to vote will vote, or vote more than once\\
+\addlinespace
+How confident are you that election officials, their staff, and volunteers in Maricopa County, AZ will do a good job conducting the elections this November? & Many votes will not actually be counted\\
+\addlinespace
+How commited do you think election staff and volunteers in Maricopa County, AZ will be to making sure the elections are fair and accurate?
+& Many people will show up to vote and be told they are not eligible\\
+\addlinespace
+How confident are you that the voting process will be fair in Maricopa County, AZ? & A foreign country will tamper with the votes cast in this area to change the results\\
+\addlinespace
+How confident are you that election systems in Maricopa County, AZ will be secure from hacking and other technological threats?
+& Election officials in Maricopa County, Arizona will try to discourage some people from voting\\
+\bottomrule
+\end{tabu}
+\endgroup{}
+
+}
+
+\end{table}%
+
+Similar to the items capturing trust in elections
+(Table~\ref{tbl-items}), I computed a summated score for each respondent
+reflecting the extent of their distrust in elections.
+
+Upon construction of the two summated scales of \emph{trust} and
+\emph{distrust}, internal consistency reliability coefficient \(\alpha\)
+were estimated for both and found to be adequate (\(\alpha\)
+\textgreater{} 0.8); the trust in elections scale \(\alpha\) = 0.93 and
+the distrust scale \(\alpha\) = 0.86. In other words, the items in each
+of the scales were intercorrelated well enough for each to compose a
+single scale presuming a unidimensional construct for each.
+
+I expected item responses from these two scales to be inversely
+correlated among the sample, but not mutually exclusive. Indeed, this is
+what I find. Polychoric correlations between the trust and distrust
+items negatively correlate as expected{[}\^{}See Appendix C{]}, as does
+the correlation between the two sum score scales. Given the ordinal
+nature of the variable items, I conducted a Spearman's rank correlation
+test (\citeproc{ref-spearman1907}{Spearman 1907}) and found a negative
+correlation of \(\rho = -0.49\) (\(95\%\) CI {[}-0.53, -0.44{]};
+Kendall's \(\tau = -0.39\)) between scores on the two scales for the AZ
+items (For the local item scale score correlation: \(\rho = -0.52\),
+\(95\%\) CI {[}-0.56, -0.48{]}; Kendall's \(\tau = -0.39\)). The
+negative correlation between the trust and distrust items and scores
+makes intuitive sense.
+
+\subsection{Data Specification}\label{data-specification}
+
+The primary outcome of interest concerns public confidence in elections
+administration compensated by one's distrust in elections, i.e., their
+expectations of electoral fraud. Because trust and distrust are assessed
+by multiple Likert items, conventional methods call for combining the
+items of each set into separate Likert scales (also known as summated
+rating scales). Since the item response options are not
+symmetric---i.e., not bipolar with contrasting positive and negative
+response options to include a neutral middle option---then the
+\emph{trust in elections} scale could only be understood as a measure of
+trust in the positive use of the term (i.e., unipolar). Likewise, the
+expectation of fraud items fit to a scale that corresponds to a unipolar
+measure of confident \emph{distrust}, so to speak. However, many of the
+items comprising the trust scale directly oppose items capturing
+distrust. For instance, one item from the trust scale has the respondent
+report their confidence that votes will be counted as voter's intend,
+whereas a separate item from the distrust scale has the the respondent
+report their expectation that many votes will not be counted. Positive
+responses to these two items directly contradict each other, and would
+thus cancel out.
+
+The relationship is that trust and distrust represent opposing degrees
+of confidence along the same spectrum. However, despite the inherent
+contrast, one can hold both positive degrees of trust and distrust,
+feeling similarly confident in both respects. Accordingly, equivalent
+degrees of trust and distrust cancel out, rendering one relatively more
+\emph{insecure} about their expectations of the future despite the fact
+that they may feel confident in either direction. When trust and
+distrust are considered as reflective of one's confidence about future
+expectations, then both can be placed along the same spectrum.
+Therefore, a lack of confidence denotes insecurity.
+
+Something may cause a person to have greater expectations that election
+fraud will occur, which in turn will always lower their trust in
+elections administration. In contrast, a person may feel a bit more
+confident in the integrity of elections, but this confidence is
+constrained by the extent to which they expect election fraud to occur.
+This means that a person's baseline level of confidence in elections
+admin must take into account their present degree of distrust---i.e.,
+their expectations of electoral fraud.
+
+Those who are, or are close to being, equally confident in both
+directions would be the most \emph{insecure} about their expectations.
+Having no trust in elections and no expectation that electoral fraud
+will occur is functionally equivalent to having equal degree of both.
+Quite literally, this reflects an uncertain feeling of ``it could go one
+way or the other'' with respect to the integrity of elections
+administration. Operationally, this would reflect a middling point on a
+scale of \emph{confidence}.
+
+In light of this, I reverse coded positive expectations of electoral
+fraud and added responses from the distrust scale to the trust in
+elections scale. That is, item responses on the trust scale ranged from
+0 (``Not confident at all'') to 3 (``Very confident), whereas responses
+on the distrust scale ranged from 0 (''Not likely at all'') to -3
+(``Very likely''). Combining responses in this way resulted in an
+overall measure of \emph{confidence in elections} to serve as the
+dependent variable\footnote{The methodological concerns between the use
+  of (unit weighted) sum or mean scores compared to the use of estimated
+  factor scores for Likert scales composed of multiple Likert items are
+  legion. The use of either computed sum scores or estimated factor
+  scores as a general practice is continuously debated
+  (\citeproc{ref-mcneish2023}{McNeish 2023};
+  \citeproc{ref-mcneish2020}{McNeish and Wolf 2020};
+  \citeproc{ref-widaman2022}{Widaman and Revelle 2022},
+  \citeproc{ref-widaman2024}{2024}), yet there is no general consensus
+  on the most appropriate method generally. The use of either appears to
+  largely depend on the researcher's particular research objective,
+  theoretical suppositions, and necessity. Another common concern is the
+  inappropriate treatment of ordinal variables as interval which levy
+  strong assumptions, e.g., each item contributes equally to the
+  variable being measured and that ordinal response categories are
+  equidistant as though on an interval scale
+  (\citeproc{ref-wang2013}{Wang et al. 2013}; for contrast, see
+  \citeproc{ref-robitzsch2020}{Robitzsch 2020}).}. On this scale,
+positive values reflect higher confidence in elections, negative values
+reflect greater distrust, and values closer to zero correspond to an
+individual's degree of insecurity.
+
+The advantage is that this permits a better test of the treatment effect
+as theorized. Of course, it is easy enough to examine the effect of the
+treatment on both trust and distrust separately. However, the theory
+presents a hypothesis that the treatment will impose influence upon both
+variables \emph{concurrently and in a positive direction} with respect
+to the relationship between trust and distrust. That is to say,
+confidence increases insofar as trust in elections increases and
+distrust decreases; since distrust detracts from trust, then an accurate
+measure of confidence must take that constraint into account.
 
@@
 
+I first review responses to the survey items capturing trust and
+distrust separately by treatment condition. When distinguished by
+experiment condition, trust in elections admin is noticeably higher for
+those who read the treatment vignette. The difference is more pronounced
+for some items over others. That being said, there is a definite
+distinction between items pertaining to Maricopa County, AZ compared to
+items that pertain to a respondent's local area. In fact, the treatment
+appears to have hardly made a difference when the items concerned one's
+local area.
+
+\phantomsection\label{cell-fig-trustlikert}
+\begin{figure}[h]
+
+\caption{\label{fig-trustlikert}Trust in Election Administration by
+Experiment Condition}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-trustlikert-1.png}}
+
+}
+
+\end{figure}%
+
+Reviewing item responses distinguished by treatment condition reveals
+particulars of the treatment effect (Figure~\ref{fig-trustlikert}).
+Among the items that asked about Maricopa County, AZ, it is a bit easier
+to see upon which items the treatment vignette had the greatest effect.
+It appears that the main effect of the treatment is upon responses to
+the item that measures confidence in the security of election
+technology.
+
+Regarding confidence in the commitment of election staff and volunteers,
+a higher proportion of respondents in the treatment group selected
+``Very confident'' over ``Somewhat confident'' compared to the control
+group, but only for items concerning Maricopa County, AZ. Although
+confidence in election workers was generally high across the board, the
+shift from ``Somewhat'' to ``Very'' confident for items pertaining to
+election worker \emph{commitment} to fairness and accuracy seems to
+clearly speak to the group being recruited, i.e., veterans and family
+members. However, the same visible shift in proportion from ``Somewhat''
+to ``Very'' confident isn't observed when items asked about one's local
+area, which undermines the suggestion that the treatment effect can be
+cleanly attributed to respondent's feelings about veteran service
+members and their families. It may be the case that respondents harbor
+particular attitudes or sentiment about Maricopa County, AZ itself, or
+there may be nothing uniquely special about Maricopa County, AZ
+supposing that elections anywhere beyond one's local area generally
+garner slightly less confidence.
+
+What this does suggest, however, is that trust in the fairness and
+accuracy of the electoral process is notably higher upon the notion that
+military veterans will be directly engaged as election staff and
+volunteers in places where such trust falters. The question turns to
+whether this also lowers distrust, or the extent to which one expects
+electoral fraud to occur.
+
+\phantomsection\label{cell-fig-distrustlikert}
+\begin{figure}[h]
+
+\caption{\label{fig-distrustlikert}Disrust in Election Administration by
+Experiment Condition}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-distrustlikert-1.png}}
+
+}
+
+\end{figure}%
+
+Similar to the trust scale items, the items on the distrust scale were
+associated with lower distrust in the treatment condition compared to
+the control. A quick glance at Figure~\ref{fig-distrustlikert} shows
+what appears to be a significant reduction in distrust, especially
+regarding the expectations that many votes wouldn't be counted, many
+voters would be turned away, and that election officials would
+discourage voters from casting a ballot. Interestingly, the expectation
+that there would be foreign interference in elections in Maricopa
+County, AZ were pretty resilient against the treatment. And again,
+responses for items pertaining to elections in one's local area are
+practically indistinguishable between treatment and control.
+
+\subsubsection{Confidence in elections}\label{confidence-in-elections}
+
+Once trust and distrust were composed into unified variable of
+confidence in elections, I then examined distribution of the dependent
+variable followed by analysis of the effect of the treatment by
+comparison of mean differences between experiment conditions. Recall
+that on this scale, zero reflects insecurity (e.g., similar or equal
+values of trust and distrust), whereas values diverging from zero
+reflect confidence in either direction, trust or distrust respectively.
+Positive values reflect trust in elections administration (e.g.,
+elections will be fair and accurate), whereas negative values reflect
+distrust in elections (i.e., expectation that election fraud will
+occur). To retain a meaningful zero, I rescaled the sum scores to range
+from -3 to 3\footnote{This range is mostly arbitrary, as a range from -1
+  to 1 works much the same. When relying on simple sum total score, the
+  scale ranges from -15 to 15. So a single point increase from 0 to 1
+  may reflect a combination of a single ``Very confident'' response on a
+  trust item compensated by a single ``Somewhat likely'' response on a
+  distrust item (i.e., 3-2 = 1), or some other equivalent combination.
+  Although the use of mean scores would place scores back onto the
+  response scale metric (e.g., from 0 to 3, reflective of ``not at all''
+  to ``very''), this results in a unipolar scale (from 0 to 3). The
+  bipolar scale resulting from the composition of positive trust and
+  negative distrust engenders meaning to zero and negative values. As
+  such, composite mean scores become inappropriate and interpretation of
+  scores would no longer be feasible. In other words, negative values on
+  the scale for confidence in elections hold substantive meaning (e.g.,
+  distrust, absent trust), which makes transforming scores to fit a
+  unipolar scale inappropriate.} and then superimposed two histograms of
+confidence scores: one derived from AZ items and another for scores
+derived from local area items. Doing this is illustrative of the
+relative distribution of confidence that differed depending on the
+location of elections referred to in the survey items (e.g., Maricopa
+County, AZ).
+
+As revealed by review of the item responses, the distribution of
+confidence differed depending on whether survey items pertained to
+elections in Maricopa County, AZ, or elections within one's local area.
+
+\phantomsection\label{cell-fig-dist}
+\begin{figure}[H]
+
+\caption{\label{fig-dist}Overlapping Distribution of Confidence in
+Elections for AZ and Local Area}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-dist-1.png}}
+
+}
+
+\end{figure}%
+
+Overall, the sample expressed more trust in elections relative to
+distrust seeing as how the distribution of confidence is largely
+positive (Figure~\ref{fig-dist}). However, there's a clear difference
+between confidence in Maricopa county, AZ elections and elections within
+one's local area. A paired t-test confirms that this difference was
+statistically significant, though somewhat small (mean difference
+\(= 0.325\), \(95\%\) CI \([0.27, 0.38]\), \(t(1286) = 11.61\),
+\(p < .001\)). Nonetheless, respondents appeared less confident
+regarding elections in Maricopa County, AZ, but held more confidence in
+elections administration in their local area. This complements previous
+research that demonstrates a similar bias favorable to one's local area
+(\citeproc{ref-stewart2022}{Stewart 2022}).
+
+Accordingly, when confidence levels are distinguished by experiment
+condition, the treatment vignette only had an effect upon survey items
+pertaining to elections in Maricopa County, AZ. Conducting an
+independent samples t-test (i.e., Welch Two Sample t-test) suggests that
+the effect of the treatment compared to the control condition is
+positive, statistically significant, yet substantially pretty small.
+
+\begin{table}[H]
+
+\caption{\label{tbl-ttest}Mean Difference Effect of Treatment Compared
+to Control Condition}
+
+\centering{
+
+\centering\begingroup\fontsize{9}{11}\selectfont
+
+\begin{tabular}[t]{llllllllll}
+\toprule
+Place & $\bar{x}_{diff}$ & $\bar{x}_{treat}$ & $\bar{x}_{control}$ & $treat_{n}$ & $control_{n}$ & t & p & df & CI\\
+\midrule
+Maricopa County, AZ & 0.20 & 0.93 & 0.72 & 650.00 & 637.00 & 2.96 & 0.003** & 1283.73 & {}[ 0.07, 0.33]\\
+Local Area & 0.06 & 1.18 & 1.12 & 650.00 & 637.00 & 0.87 & 0.383 & 1282.95 & {}[-0.08, 0.20]\\
+\bottomrule
+\multicolumn{10}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{10}{l}{\rule{0pt}{1em}Welch Two Sample t-tests of difference between Confidence in Elections by Treatment Condition.}\\
+\end{tabular}
+\endgroup{}
+
+}
+
+\end{table}%
+
+The results of Table~\ref{tbl-ttest} show that, on a scale ranging from
+-3 to 3, the effect of the treatment is associated with a \(0.20\)
+average difference in confidence in elections in Maricopa County, AZ,
+compared to the control group. When the dependent variable is centered
+to have a mean of \(0\) and standard deviation of \(1\), standardized
+parameters permit interpretation of the treatment effect in terms of
+standard deviations; the standardized difference in confidence between
+treatment and control is \(0.16\) (CI \([0.06, 0.27]\)). Nothing is more
+illustrative than graphs and lines, however.
+
+\begin{figure}[!t]
+
+\caption{\label{fig-coef1}Confidence in Elections by Experiment
+Condition}
+
+\begin{minipage}{\linewidth}
+
+\subcaption{\label{fig-coef1-1}Confidence by Treatment Condition}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-coef1-1.png}}
+
+}
+
+\end{minipage}%
+\newline
+\begin{minipage}{\linewidth}
+
+\subcaption{\label{fig-coef1-2}Trust and Distrust by Treatment
+Condition}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-coef1-2.png}}
+
+}
+
+\end{minipage}%
+
+\end{figure}%
+
+Figure~\ref{fig-coef1} displays standard difference estimates of
+confidence in elections by treatment condition (control condition as
+reference). Figure~\ref{fig-coef1-1} displays two models for confidence
+in elections in Maricopa County, AZ, and one's local area by treatment
+condition; Figure~\ref{fig-coef1-2} displays four models for trust and
+distrust in elections in AZ or one's local area by treatment condition
+
+the treatment effect on both trust and distrust is clear. Although the
+effect is only there when questions pertained to Maricopa County, AZ.
+The treatment effect on trust and distrust is conditional on whether the
+survey questions inquired about elections in Maricopa County, AZ.
+Announcing efforts to recruit veterans and their families to work as
+election staff and volunteers increases confidence in elections
+administration in places outside of one's local area, but doesn't boost
+confidence in elections within one's local area. However, bear in mind
+that confidence in elections for one's local area is already higher than
+for those outside. Thus, there's already less insecurity concerning
+elections in one's local area, but publicized efforts to recruit
+veterans to work as election staff and volunteers is a small but
+positive step towards closing that gap in confidence for elections that
+occur elsewhere.
+
+I now turn to results examining those who held onto the belief that the
+2020 election results were illegitimate. I think check to see if
+recruiting veterans simply makes people feel safer at the polls.
+
 \pagebreak
@@
 \subsubsection{Limitations}\label{limitations}
+
+As far as I'm aware, both the items, their wording, and their
+composition into measurement scales are unique to this study. This
+renders the composite scores for trust in elections sample dependent and
+limits comparability with other cross-sectional survey data.
 
@@
   limitations: interpretations of the treatment effect are limited.
+
+  \begin{itemize}
+  \tightlist
   \item
@@
     recruitment efforts.
+  \end{itemize}
 \item
@@
 
-\subsection{Appendix A: Survey Experiment
-Vignettes}\label{sec-appendix-a}
+\subsection{Appendix A: Survey Experiment Vignettes and Survey
+Items}\label{sec-appendix-a}
 
@@
 
-\begin{minipage}{0.50\linewidth}
+\begin{minipage}{0.45\linewidth}
 
@@
 %
-\begin{minipage}{0.50\linewidth}
+\begin{minipage}{0.10\linewidth}
+~\end{minipage}%
+%
+\begin{minipage}{0.45\linewidth}
 
@@
 
-Text of the Control Condition: Recruitment of Community
-Members\end{minipage}%
+\end{minipage}%
 
@@
 
+\pagebreak
+
 \subsection{Appendix B: Sample Demographics}\label{sec-appendix-b}
 
-There should be nothing below here
-
-\begin{table}
-
-\caption{\label{tbl-desc-pdf}Description of Sample Demographics}
-
-\centering{
-
-\centering\begingroup\fontsize{8}{10}\selectfont
-
-\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{20em}rr}
-\toprule
-Name & n & Pct\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Experiment Condition}}\\
-\cellcolor{gray!10}{\hspace{1em}Control} & \cellcolor{gray!10}{637} & \cellcolor{gray!10}{49.49}\\
-\hspace{1em}Treatment & 650 & 50.51\\
-\addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Question Set}}\\
-\cellcolor{gray!10}{\hspace{1em}A} & \cellcolor{gray!10}{644} & \cellcolor{gray!10}{50.04}\\
-\hspace{1em}B & 643 & 49.96\\
-\addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Age}}\\
-\cellcolor{gray!10}{\hspace{1em}18-24} & \cellcolor{gray!10}{108} & \cellcolor{gray!10}{8.39}\\
-\hspace{1em}25-34 & 242 & 18.80\\
-\cellcolor{gray!10}{\hspace{1em}35-44} & \cellcolor{gray!10}{254} & \cellcolor{gray!10}{19.74}\\
-\hspace{1em}45-54 & 226 & 17.56\\
-\cellcolor{gray!10}{\hspace{1em}55-64} & \cellcolor{gray!10}{242} & \cellcolor{gray!10}{18.80}\\
-\hspace{1em}65-74 & 148 & 11.50\\
-\cellcolor{gray!10}{\hspace{1em}75-84} & \cellcolor{gray!10}{57} & \cellcolor{gray!10}{4.43}\\
-\hspace{1em}85-92 & 10 & 0.78\\
-\addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Gender}}\\
-\cellcolor{gray!10}{\hspace{1em}Male} & \cellcolor{gray!10}{598} & \cellcolor{gray!10}{47.01}\\
-\hspace{1em}Female & 658 & 51.73\\
-\cellcolor{gray!10}{\hspace{1em}Other/Refused} & \cellcolor{gray!10}{16} & \cellcolor{gray!10}{1.26}\\
-\addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Education}}\\
-\hspace{1em}H.S. or less & 362 & 28.46\\
-\cellcolor{gray!10}{\hspace{1em}Some college no degree} & \cellcolor{gray!10}{283} & \cellcolor{gray!10}{22.25}\\
-\hspace{1em}Undergraduate level degree & 461 & 36.24\\
-\cellcolor{gray!10}{\hspace{1em}Graduate level degree} & \cellcolor{gray!10}{166} & \cellcolor{gray!10}{13.05}\\
-\addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Race}}\\
-\hspace{1em}White or Caucasian & 975 & 76.65\\
-\cellcolor{gray!10}{\hspace{1em}Black or African American} & \cellcolor{gray!10}{164} & \cellcolor{gray!10}{12.89}\\
-\hspace{1em}American Indian & 22 & 1.73\\
-\cellcolor{gray!10}{\hspace{1em}Asian} & \cellcolor{gray!10}{56} & \cellcolor{gray!10}{4.40}\\
-\hspace{1em}Other & 55 & 4.32\\
-\addlinespace[0.3em]
-\multicolumn{3}{l}{\textbf{Party ID}}\\
-\cellcolor{gray!10}{\hspace{1em}Republican} & \cellcolor{gray!10}{540} & \cellcolor{gray!10}{42.59}\\
-\hspace{1em}Democrat & 566 & 44.64\\
-\cellcolor{gray!10}{\hspace{1em}Independent} & \cellcolor{gray!10}{162} & \cellcolor{gray!10}{12.78}\\
-\bottomrule
-\end{tabular}}
-\endgroup{}
-
-}
-
-\end{table}%
-
-\textsubscript{Source:
-\href{https://isaiahespi.github.io/rea-paper/index.qmd.html}{Article
-Notebook}}
+The median age was 46 (mean age was 47). There was 51.7\% (n = 658)
+women, 47\% (n = 598) men, and approximately 1.3\% who identified as
+either Non-binary/third gender (n = 7) or preferred not to say (n = 9).
+A large proportion of the sample identified as White or Caucasian (n =
+975, 76.65\%), while all other non-White respondents comprised 27.83\%
+of the sample. Those who held a graduate level degree (e.g., Master's,
+Doctorate, or Professional level) comprised 13\% of the sample; those
+with either degree at the Associate or Bachelor's level comprised
+36.24\%, while 22.25\% had some college but no degree; and 28.46\% had
+either a high school level or equivalent education or less than high
+school. The largest proportion of the sample identified as Democrat at
+44.64\%, followed by Republicans at 42.59\%. The proportion of true
+Independents was 12.78\%.
+
+\pagebreak
 
@@
 doi:\href{https://doi.org/10.1017/S104909650707103X}{10.1017/S104909650707103X}.
+
+\bibitem[\citeproctext]{ref-hardin2004}
+Hardin, Russell. 2004. \emph{Distrust}. New York: Russell Sage
+Foundation.
 
@@
 
-\bibitem[\citeproctext]{ref-kleykamp2018}
-Kleykamp, Meredith, Crosby Hipes, and Alair MacLean. 2018. {``Who
-{Supports U}.{S}. {Veterans} and {Who Exaggerates Their Support}?''}
-\emph{Armed Forces \& Society} 44(1): 92--115.
-doi:\href{https://doi.org/10.1177/0095327X16682786}{10.1177/0095327X16682786}.
-
 \bibitem[\citeproctext]{ref-kleykamp2023}
@@
 
+\bibitem[\citeproctext]{ref-mcneish2023}
+McNeish, Daniel. 2023. {``Psychometric Properties of Sum Scores and
+Factor Scores Differ Even When Their Correlation Is 0.98: {A} Response
+to {Widaman} and {Revelle}.''} \emph{Behavior Research Methods} 55(8):
+4269--90.
+doi:\href{https://doi.org/10.3758/s13428-022-02016-x}{10.3758/s13428-022-02016-x}.
+
+\bibitem[\citeproctext]{ref-mcneish2020}
+McNeish, Daniel, and Melissa Gordon Wolf. 2020. {``Thinking Twice about
+Sum Scores.''} \emph{Behavior Research Methods} 52(6): 2287--2305.
+doi:\href{https://doi.org/10.3758/s13428-020-01398-0}{10.3758/s13428-020-01398-0}.
+
 \bibitem[\citeproctext]{ref-mena2020}
@@
 
+\bibitem[\citeproctext]{ref-robitzsch2020}
+Robitzsch, Alexander. 2020. {``Why {Ordinal Variables Can} ({Almost})
+{Always Be Treated} as {Continuous Variables}: {Clarifying Assumptions}
+of {Robust Continuous} and {Ordinal Factor Analysis Estimation
+Methods}.''} \emph{Frontiers in Education} 5.
+doi:\href{https://doi.org/10.3389/feduc.2020.589965}{10.3389/feduc.2020.589965}.
+
 \bibitem[\citeproctext]{ref-ross2020}
@@
 
+\bibitem[\citeproctext]{ref-spearman1907}
+Spearman, Charles. 1907. {``Demonstration of {Formulæ} for {True
+Measurement} of {Correlation}.''} \emph{The American Journal of
+Psychology} 18(2): 161--69.
+doi:\href{https://doi.org/10.2307/1412408}{10.2307/1412408}.
+
 \bibitem[\citeproctext]{ref-steinhauer2020}
@@
 
-\bibitem[\citeproctext]{ref-studentveteransofamerica2020}
-Student Veterans of America. 2020. {``Volunteer to {Power The Polls}.''}
-\url{https://studentveterans.org/news/power-the-polls/}.
-
 \bibitem[\citeproctext]{ref-vanbavel2021}
@@
 
-\bibitem[\citeproctext]{ref-wang2022}
-Wang, Hansi Lo. 2022. {``The Midterm Elections Need Workers. {Teens},
-Veterans and Lawyers Are Stepping Up.''} \emph{NPR: 2024 Election}.
-\url{https://www.npr.org/2022/09/07/1120065844/midterms-elections-poll-worker-shortage-recruitment}.
+\bibitem[\citeproctext]{ref-wang2013}
+Wang, Lihshing Leigh, Amber S. Watts, Rawni A. Anderson, and Todd D.
+Little. 2013. {``Common {Fallacies} in {Quantitative Research
+Methodology}.''} In \emph{The {Oxford Handbook} of {Quantitative
+Methods} in {Psychology}: {Vol}. 2: {Statistical Analysis}}, ed. Todd D.
+Little. Oxford University Press, 0.
+doi:\href{https://doi.org/10.1093/oxfordhb/9780199934898.013.0031}{10.1093/oxfordhb/9780199934898.013.0031}.
 
@@
 \url{https://vetthe.vote/blogs/news/launch-of-vet-the-vote}.
+
+\bibitem[\citeproctext]{ref-widaman2022}
+Widaman, Keith F., and William Revelle. 2022. {``Thinking Thrice about
+Sum Scores, and Then Some More about Measurement and Analysis.''}
+\emph{Behavior Research Methods} 55(2): 788--806.
+doi:\href{https://doi.org/10.3758/s13428-022-01849-w}{10.3758/s13428-022-01849-w}.
+
+\bibitem[\citeproctext]{ref-widaman2024}
+Widaman, Keith F., and William Revelle. 2024. {``Thinking {About Sum
+Scores Yet Again}, {Maybe} the {Last Time}, {We Don}'t {Know}, {Oh No} .
+. .: {A Comment} On.''} \emph{Educational and Psychological Measurement}
+84(4): 637--59.
+doi:\href{https://doi.org/10.1177/00131644231205310}{10.1177/00131644231205310}.
 

### 2025-02-26 index.qmd
long overdue commit.

@@
 date-modified: today
-crossref:
-  custom: 
-    - key: hyp
-      kind: float
-      reference-prefix: H
-      latex-env: hypothesis # required for PDF format
+knitr: 
+  opts_chunk: 
+    dev: "ragg_png" # same as knitr::opts_chunk$set(dev = "ragg_png")
 ---
@@
 
+set.seed(1234)
+
 # load packages
 library(tidyverse)
+library(easystats)
+
+options("huxtable.latex_use_fontspec" = TRUE) # if TRUE, uses the LaTeX “fontspec” package which lets you use the same fonts in TeX and HTML.
+You will need to use the xetex or xelatex engine for output.
 
 # load data
-load("data/research-paper-data-20241029.Rdata")
+load("data/research-paper-df-20250203.Rdata") #df
 
@@
 codebook <- read.csv("data/survey_codebook.csv")
-data_dict <- read.csv("data/data_dictionary.csv")
-
-# also load the raw data dict for comparison
-raw_spss_dict <- read.csv("data/raw_spss_dict.csv")
-```
-
-```{r}
-#| label: post_processing
-#| include: false
-
-# Some post-processing of the dataframe :::::::::::::::::::::::::::::::::::::###
-
-# code to recode levels "-99" in factor vars
-data <- data |> 
-  mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99"))) |> 
-  # Reverse response options to show increase in *less concern*
-  mutate(q25 = forcats::fct_rev(q25))
-
-# recode factor levels 
-data <- data |> 
-  # use `pewmethods` to preserve order of factor levels
-  mutate(across(c(q19, q20, q21, q22, q23,q24, q25, q26,
-                  q30, q31, q32, q33, q34, q35, q36, q37), 
-                ~pewmethods::fct_case_when(
-    .x == "Not at all confident" |
-      .x == "Not at all committed" ~ "Not at all",
-    .x == "Not too confident" |
-      .x == "Not too committed"|
-      .x == "Not too concerned"|
-      .x == "Somewhat unconcerned" ~ "Not that much",
-    .x == "Somewhat confident" |
-      .x == "Somewhat committed" ~ "Somewhat",
-    .x == "Very confident" |
-      .x == "Very committed" ~ "Very",
-    TRUE ~ NA
-  )))
-
-# re-assign var labels to variables
-# To quickly assign the variable labels, first create a named vector via
-# deframe() with values as the variable labels and names as the variable names.
-data_labels <- data_dict |>
-  select(var, label_var) |> 
-  deframe()
-
-# Now assign the labels using the splice operator. Using the splice operator,
-# labels are assigned via matching against the variable name, which means that
-# variable order does not matter.
-data <- data |> 
-  labelled::set_variable_labels(!!!data_labels)
-
-```
-
-```{r}
-#| label: fns
-#| include: false
-
-source(here::here('src', 'funs.R'))
+df_dict <- read.csv("data/df_dictionary.csv")
 
@@
 Even though election officials can do a lot to secure election integrity, there's not much they can do to cement public confidence after election night passes.
-At best, election officials can ease public anxieties prior to election night.
+At best, election officials can ease public insecurities prior to election night.
 
@@
 
-Supposing such is the case, we can expect that information about *who* (i.e., which groups) election officials are targeting in publicized recruitment efforts would lessen particular election anxieties.
-That is to say, it is reasonable to expect that telling people *who* will be working as election staff and volunteers would ease election anxieties, therefore improve confidence that the election will be conducted fairly, accurately, and safe for all involved.
+Supposing such is the case, we can expect that information about *who* (i.e., which groups) election officials are targeting in publicized recruitment efforts would lessen particular election insecurity, and concurrently, boost confidence.
+That is to say, it is reasonable to expect that telling people *who* will be working and volunteering as election staff would ease election insecurity, and therefore improve confidence that the election will be conducted fairly, accurately, and safe for all involved.
 
-In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election anxieties.
-Results of the survey experiment support the hypothesis that emphasizing veterans as the target of election worker recruitment efforts eases pre-elections anxieties to an extent.
-In particular, among those in the treatment condition, confidence that the elections would be fair and accurate was higher in comparison to those in the control.
-In addition, expectations of electoral fraud were lower, as were concerns for voter safety compared to those who read a control vignette.
-Notable is that there was a significant difference in confidence, and lower expectations of fraud, among those in the treatment condition who believe that the 2020 election was illegitimate.
-
-[Insert why this is an important contribution]
+In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
+Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity to a limited extent.
+Expectations of electoral fraud and concerns for voter safety were lower among those who read a fabricated announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned.
+Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
 
@@
 First, I provide a brief background on public trust in election administration.
-Second, I synthesize a review of relevant literature with a focus on how political and social science has conceptualized and ascertained public trust in elections.
+I synthesize a review of relevant literature with a focus on how political and social science has conceptualized and ascertained public trust in elections.
 Next, I supply reasoning for why military veterans are singled out as the relevant subset of the population in this study.
-
--   when distinguished by partisanship...
--   moreover, broken down by other demographic variables such as race, gender, education, etc.
--   holding these factors constant demonstrates a \[increased/decreased\] likelihood that a respondent's confidence would likely \[increase/decrease\], expectations of fraud would likely \[increase/decrease\], and concerns for safety would lessen among those in the treatment group compared to those in the control.
-These results allow us to attribute the differences to the treatment stimulus, namely, the prospect of having veterans serve as election staff or volunteers.
+I then explicitly provide the simple theory and testable hypotheses of the study before moving on to describe the design of the survey, the measurement instruments therein, and the conceptual and operational definitions of the variables of interest.
+I explain my reasoning and method for constructing the primary dependent variable, which I broadly refer to as *confidence in elections*.
+I preview the different methods of analysis alongside presentation of the results.
+Before concluding, I dedicate time to discuss the limitations of the study and lessons learned.
+I close by offering my interpretation of the results and suggest potential avenues for future inquiry.
 
@@
 
-Election administration is just one institution a part of the larger set of institutions which form the electoral system.
+Elections administration is just one institution a part of the larger set of institutions which form the electoral system.
 As such, the performance of the institution along with the rest "...lends credibility to the outcome of an election: whether it is considered by citizens and the international community to be fair and legitimate." [@stewart2022, 236].
@@
 The subtle difference is simply the degree of uncertainty one feels in anticipation of the next election event.
-This study focuses primarily on that *anticipatory* kind of trust and confidence, which speaks more to those anxieties[^3] based on perceptions of the institution's trustworthiness than upon the particular voter experience.
+This study focuses primarily on that *anticipatory* kind of confidence, which speaks more to those insecurities[^3] based on perceptions of the institution's trustworthiness than upon the particular voter experience.
 
@@
 
-## Design and Measures
+## Theory and Hypotheses
 
-To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would improve trust in elections and ease election anxieties, a recent survey experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland.
+Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veterans and their family members to work as election staff and volunteers would boost public confidence in election administration.
+Indeed, that is the primary hypothesis of this study.
+Although citizens may vote in various ways across the country (e.g., by mail, ballot drop box, in-person), the simple announcement that election officials are engaging in efforts to recruit veterans to work as election staff may boost confidence in elections administration regardless of how, or whether, an individual plans to vote.
+Formally,
+
+> H~1~: Announcements that election officials are recruiting miilitary service veterans to work as election staff and volunteers will be associated with greater confidence in elections administration compared to announcements that do not mention military veterans.
+
+I considered that veterans would elicit high degrees of approval and support for whatever cause or issue presented.
+For example, I'd expect high approval and support for recruiting veterans to baseball teams just as much as for recruiting them to work as election staff.
+Likewise, asking participants whether they supported programs intent on recruiting anyone to work as election staff would garner support regardless of the target group.
+Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require a survey experiment designed to determine whether publicized recruitment efforts targeting veterans as a group would have any special effect on confidence in elections administration.
+
+Since the results and events following the 2020 election loomed large in anticipation of the U.S.
+2024 general elections, it is reasonable to take into account beliefs about legitimacy of the 2020 election.
+This group who denies the legitimacy of the 2020 election results were possibly the most distrusting of the 2024 election.
+However, given that veteran service members are held in high regard, generally speaking, announcing that veterans are being actively recruited to work as election staff and volunteers is expected to positively influence confidence in elections among those who remained firm in the belief that the 2020 election results were illegitimate.
+I take into account that legitimacy beliefs about the 2020 election and expectations of electoral fraud are related to partisanship and include partisanship as a control in the analysis.
+
+In addition, I expect that both expectations of electoral fraud and concerns for voter safety would lessen (shrink) when presented with information that veterans are being actively recruited to work and volunteer in election offices.
+
+Finally, prior research has shown that confidence that one's own vote would be counted as intended has been much stronger than confidence that votes nationwide would be treated likewise [@sances2015; @stewart2022].
+In other words, the public is more trusting of elections closer to home.
+Taking into account that confidence is lower for elections conducted outside of one's local area, then information that veterans are being recruited to help conduct elections in locations beyond one's locale may close this gap between confidence in elections within one's local area and confidence in elections elsewhere.
+Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone.
+Therefore, any observed disparity of confidence in elections (i.e., the "confidence gap") between elections within one's local area and elections beyond will be smaller when people are presented with information about election official recruitment efforts of veteran service members.
+
+## Experiment Design and Survey Measures
+
+To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would improve confidence in elections and ease insecurity, a recent experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland.
 The survey was fielded from August 29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287 U.S.
 citizens 18 years of age or older.
-Respondents were randomly split into either the treatment (n = 650, 50.51%) control (n = 637, 49.49%) conditions[^Demographic breakdown of the sample are included in Appendix B.].
+Respondents were randomly split into either the treatment ($n =$ 650) control ($n =$ 637) conditions[^4].
 
@@
 Beyond those small differences and the headlines, the article vignettes are identical.
-Any effects can be attributed to the information about veterans in the treatment vignette[^5].
+Therefore, effects can be attributed to the information about veterans in the treatment vignette[^5].
 
-It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignettes due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
+It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignette due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
+Because of this, treatment effects are potentially limited or constrained to attitudes concerning the location specified in the vignette.
 A block of survey items asked specifically about Maricopa County, AZ, followed by an identical block of items that asked the same questions about one's local area.
-Results between the items where the setting differs are compared and discussed.
-
-### Trust in Elections Admin
+Later, I compare and discuss results between the items pertaining to different settings.
 
@@
 The items in this study, however, all inquire into confidence over one's expectations in anticipation of upcoming elections.
-In addition, other survey questionnaires ask similar questions that specifically contrast between a respondent's own local community, their state, and nationwide.
-This is in addition, or complementary to, items that distinguish between local area officials, state election officials, state government, and the U.S.
+In addition, other survey questionnaires ask similar questions that specifically contrast between a respondent's own local community, their state, and nationwide; this is in addition, or complementary to, items that distinguish between local area officials, state election officials, state government, and the U.S.
 federal government.
-The survey of this study, instead, focused on attitudes regarding election workers such as election officials, staff, and volunteers.
-As such, the items are utilized to comprise a component[^7] I broadly refer to as *trust in elections*.
+The survey of this study, instead, focused on attitudes regarding election workers such as election officials, staff, and volunteers specific to the location mentioned in the vignette---Maricopa County, AZ---as well as specific to one's local area[^6].
 
-[^7]: The methodological concerns between the use of (unit weighted) sum scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
-The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024].
-The use of either appears to largely depend on the researcher's particular research objective, theoretical suppositions, and necessity.
-Another common concern is the inappropriate treatment of ordinal variables as interval which levy strong assumptions, e.g., each item contributes equally to the variable being measured and that ordinal response categories are equidistant as though on an interval scale [@wang2013; for contrast, see @robitzsch2020].
+The survey included items that assessed both trust in elections administration and expectations of electoral fraud, referred to simply as *trust* and *distrust*, respectively.
+Responses from these two sets of items were utilized to construct the primary dependent variable, *confidence in elections*.
 
-A set of five survey items measured public trust in elections by inquiring into the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, as well as confidence that the voting process will be fair.
-The items measuring trust and confidence in elections include:
+Prior to the reading the treatment or control vignette, participants responded to distinct survey items assessing one's favorability to local election officials ("In general, how favorable or unfavorable is your impression of local election officials?") and legitimacy of the 2020 election results ("Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected?").
+The former presented five response options from "Strongly favorable" to "Strongly unfavorable"; the latter item presented a binary of either "Legitimate" or "Not Legitimate".
 
--   How confident are you that votes in Maricopa County, AZ will be counted as voters intend in the elections this November?[^8]
--   How confident are you that election officials, their staff, and volunteers in Maricopa County, AZ will do a good job conducting the elections this November?
--   Think about the election staff and volunteers who handle the administration and conduct of elections in Maricopa County, AZ.
-How committed do you think they will be to making sure the elections held this November are fair and accurate?
--   How confident are you that the voting process will be fair in Maricopa County, AZ?
--   How confident are you that election systems in Maricopa County, AZ will be secure from hacking and other technological threats?
+The conventional multiple item assessment of partisanship was included and used to construct a variable of partisanship consisting of three categories: Democrat, Republican, and Independent.
+In this case, Independents are "true" Independents in that they do not identify with either political party and do not "lean" toward either Republican or Democratic parties.
+Self-described "Independent leaners" are re-coded as falling into the partisan category in which they lean e.g., Independents who expressly report that they lean Republican are denoted as Republican.
 
-[^8]: Note that confidence, or lack thereof, that votes will be counted as voters intend could easily be construed as an expectation of electoral fraud.
-It is a given that the votes will be counted, but the question is whether they will be counted *as intended*.
-Although fraud isn't provided as the reason for why votes wouldn't be counted as intended, it also isn't implied that miscounts would be due to some negligent mistake.
-A nefarious insinuation might be somewhat implicit, but perhaps only to those who are inclined to suspect as such.
-A lack of confidence here doesn't necessarily impart the reason for that lack of confidence, which makes it suitable as a survey item to measure the presence of trust in election administration rather than an expectation of fraud.
+Finally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
+The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^7].
 
-Each item in this series presented four response options from "Not at all [confident/committed]", "Not too [confident/committed]", "Somewhat [confident/committed]", and "Very [confident/committed]".
-In total, six survey items measure different aspects of trust and confidence in election administration.
-From these items, I generated a composite score for each respondent that represents their variable level of trust in elections.
+### Trust and Distrust in Elections
 
-### Expecatation of Electoral Fraud
+A set of five survey items measured public trust in elections by inquiring into the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, and confidence that the voting process will be fair.
+Each item in this series presented four response options from "Not at all \[confident/committed\]", "Not too \[confident/committed\]", "Somewhat \[confident/committed\]", and "Very \[confident/committed\]".
+In total, five survey items measure different aspects of trust in elections administration.
+The items measuring confidence in elections include:
 
-A series of five survey items captured *expectation of electoral fraud*.
-These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in Maricopa County, AZ?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
+Another series of five survey items captured an individual's level of *distrust* in elections administration based on the extent to which they *expect electoral fraud* to occur.
+These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in \[Maricopa County, AZ/ your local area\]?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
 
--   There will be voter fraud, that is, people who are not eligible to vote will vote, or vote more than once
--   Many votes will not actually be counted
--   Many people will show up to vote and be told they are not eligible
--   A foreign country will tamper with the votes cast in this area to change the results
--   Election officials in Maricopa County, Arizona will try to discourage some people from voting
+```{r}
+#| label: tbl-items
+#| tbl-cap: "Survey Items for Trust and Distrust in Elections"
 
-Similar to the items capturing trust in elections, I computed a composite score for each respondent reflecting their expectations of electoral fraud.
+trust_txt <- df |> select(q19, q20, q21, q22, q24) |>
+  labelled::set_variable_labels(
+    q21 = "How commited do you think election staff and volunteers in Maricopa County, AZ will be to making sure the elections are fair and accurate?"
+  ) |> 
+  labelled::generate_dictionary() |> 
+  dplyr::as_tibble() |> 
+  select(Trust=label)
 
-## Model and Data Specification
+distrust_txt <- df |> select(q28_1:q28_5) |>
+  labelled::generate_dictionary() |> 
+  dplyr::as_tibble() |> 
+  select(Distrust=label)
 
-The outcome of interest concerns both public trust in election administration and the expectation of electoral fraud.
-Because these variables are assessed by multiple Likert items, conventional methods call for combining the items of each set into separate Likert scales, also known as a summated rating scales.
-However, many of the items comprising the trust scale directly oppose items capturing expectations of electoral fraud.
-For instance, one item has the respondent report their confidence that votes will be counted as voter's intend; whereas a contrasting item has the the respondent report their expectation that many votes will not be counted.
-These two items directly oppose each other, but there's no guarantee that individual's responded as such.
+conf_items_text <- trust_txt |> 
+  mutate(Distrust = pull(distrust_txt))
 
-Since many of the items are not symmetric---i.e., response options are not bipolar with contrasting positive and negative response options---then a "trust in elections" scale could only be understood as a measure of trust in the positive use of the term (i.e., unipolar).
-Likewise, the expectation of fraud items fit to a scale that corresponds to a unipolar measure of *confident distrust* so to speak.
+kableExtra::kbl(conf_items_text, booktabs = T,
+                col.names = c("Trust", "Distrust"),
+                linesep = "\\addlinespace") |> 
+  kableExtra::kable_styling(full_width = T,
+                            font_size = 8,
+                            latex_options = c("HOLD_position")) |> 
+  kableExtra::column_spec(column = 1:2, width = "8cm")
 
-I would expect composite sum or mean scores, and item responses, on these two measures to be inversely correlated among the sample, but not mutually exclusive. Indeed, this is what I find.
+```
 
-I first constructed two multi-item composite scales of both *trust in elections* and *expectation of fraud*.
-Cronbach's internal consistency reliability coefficient \alpha were estimated for both scales and were adequate (\alpha > 0.8); the trust in elections scale \alpha = 0.93 and the expectation of electoral fraud scale \alpha = 0.86.
-In other words, the items in each of the scales were intercorrelated well enough to compose a single scale of a (presumed) unidimensional construct.
-I then plotted separate histograms of scores across the sample to visualize the distribution for each seen in @fig-dist.
-Note that for both scales, higher values indicate less expectation of electoral fraud and greater trust in elections, respectively.
+Similar to the items capturing trust in elections (@tbl-items), I computed a summated score for each respondent reflecting the extent of their distrust in elections.
+
+Upon construction of the two summated scales of *trust* and *distrust*, internal consistency reliability coefficient $\alpha$ were estimated for both and found to be adequate ($\alpha$ \> 0.8); the trust in elections scale $\alpha$ = 0.93 and the distrust scale $\alpha$ = 0.86.
+In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each.
+
+I expected item responses from these two scales to be inversely correlated among the sample, but not mutually exclusive.
+Indeed, this is what I find.
+Polychoric correlations between the trust and distrust items negatively correlate as expected\[\^See Appendix C\], as does the correlation between the two sum score scales.
+Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
+The negative correlation between the trust and distrust items and scores makes intuitive sense.
+
+## Data Specification
+
+The primary outcome of interest concerns public confidence in elections administration compensated by one's distrust in elections, i.e., their expectations of electoral fraud.
+Because trust and distrust are assessed by multiple Likert items, conventional methods call for combining the items of each set into separate Likert scales (also known as summated rating scales).
+Since the item response options are not symmetric---i.e., not bipolar with contrasting positive and negative response options to include a neutral middle option---then the *trust in elections* scale could only be understood as a measure of trust in the positive use of the term (i.e., unipolar).
+Likewise, the expectation of fraud items fit to a scale that corresponds to a unipolar measure of confident *distrust*, so to speak.
+However, many of the items comprising the trust scale directly oppose items capturing distrust.
+For instance, one item from the trust scale has the respondent report their confidence that votes will be counted as voter's intend, whereas a separate item from the distrust scale has the the respondent report their expectation that many votes will not be counted.
+Positive responses to these two items directly contradict each other, and would thus cancel out.
+
+The relationship is that trust and distrust represent opposing degrees of confidence along the same spectrum.
+However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling similarly confident in both respects.
+Accordingly, equivalent degrees of trust and distrust cancel out, rendering one relatively more *insecure* about their expectations of the future despite the fact that they may feel confident in either direction.
+When trust and distrust are considered as reflective of one's confidence about future expectations, then both can be placed along the same spectrum.
+Therefore, a lack of confidence denotes insecurity.
+
+Something may cause a person to have greater expectations that election fraud will occur, which in turn will always lower their trust in elections administration.
+In contrast, a person may feel a bit more confident in the integrity of elections, but this confidence is constrained by the extent to which they expect election fraud to occur.
+This means that a person's baseline level of confidence in elections admin must take into account their present degree of distrust---i.e., their expectations of electoral fraud.
+
+Those who are, or are close to being, equally confident in both directions would be the most *insecure* about their expectations.
+Having no trust in elections and no expectation that electoral fraud will occur is functionally equivalent to having equal degree of both.
+Quite literally, this reflects an uncertain feeling of "it could go one way or the other" with respect to the integrity of elections administration.
+Operationally, this would reflect a middling point on a scale of *confidence*.
+
+In light of this, I reverse coded positive expectations of electoral fraud and added responses from the distrust scale to the trust in elections scale.
+That is, item responses on the trust scale ranged from 0 ("Not confident at all") to 3 ("Very confident), whereas responses on the distrust scale ranged from 0 ("Not likely at all") to -3 ("Very likely").
+Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable.
+On this scale, positive values reflect higher confidence in elections, negative values reflect greater distrust, and values closer to zero correspond to an individual's degree of insecurity[^8].
+
+The advantage is that this permits a better test of the treatment effect as theorized.
+Of course, it is easy enough to examine the effect of the treatment on both trust and distrust separately.
+However, the theory presents a hypothesis that the treatment will impose influence upon both variables *concurrently and in a positive direction* in light of the relationship between trust and distrust.
+Confidence increases insofar as trust in elections increases and distrust decreases; since distrust detracts from trust, then an accurate measure of confidence must take that constraint into account.
+
+## Results
+
+I first review responses to the survey items capturing trust and distrust, respectively.
+When distinguished by experiment condition, trust in elections admin is noticeably higher for those who read the treatment vignette.
+The difference is more pronounced for some items over others.
+That being said, there is a definite distinction between items pertaining to Maricopa County, AZ compared to items that pertain to a respondent's local area.
+In fact, the treatment appears to have hardly made a difference when the items concerned one's local area.
+
+```{r}
+#| label: fig-trustlikert
+#| fig-cap: "Trust in Election Administration by Experiment Condition"
+
+# Likert plot of trust and confidence in election admin comparing treatment and
+# control groups
+trust.likert.treat.az <- df |>
+  # relabel factor labels for plotting
+  mutate(across(
+    c(q19, q20, q21, q22, q23, q24, q30, q31, q32, q33, q34, q35),
+    ~ pewmethods::fct_case_when(
+      .x %in% c("Not at all confident", "Not at all committed") ~ "Not at all confident",
+      .x %in% c("Not too confident", "Not too committed") ~ "Not too confident",
+      .x %in% c("Somewhat confident", "Somewhat committed") ~ "Somewhat confident",
+      .x %in% c("Very confident", "Very committed") ~ "Very confident",
+      TRUE ~ NA
+    )
+  )) |>
+  ggstats::gglikert(
+    include = c(q19, q20, q21, q22, q24),
+    y = 'group',
+    facet_rows = vars(.question),
+    symmetric = F,
+    labels_size = 2.5,
+    add_totals = T
+  ) +
+  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+  # ggplot2::scale_fill_brewer(palette = "Greys")+
+  labs(subtitle = str_wrap("Maricopa County, Arizona", width = 95)) +
+  theme_bw() +
+  theme(
+    text = element_text(family = "Palatino Linotype"),
+    legend.position = 'bottom',
+    axis.text.x = element_blank(), # remove percentage text along x-axis
+    strip.text.y.right = element_blank()
+  )
+
+# confidence in elections between experiment conditions for items concerning local area
+trust.likert.treat.lcl <- df |>
+  # relabel factor labels for plotting
+  mutate(across(
+    c(q19, q20, q21, q22, q23, q24, q30, q31, q32, q33, q34, q35),
+    ~ pewmethods::fct_case_when(
+      .x %in% c("Not at all confident", "Not at all committed") ~ "Not at all confident",
+      .x %in% c("Not too confident", "Not too committed") ~ "Not too confident",
+      .x %in% c("Somewhat confident", "Somewhat committed") ~ "Somewhat confident",
+      .x %in% c("Very confident", "Very committed") ~ "Very confident",
+      TRUE ~ NA
+    )
+  )) |>
+  ggstats::gglikert(
+    include = c(q30, q31, q32, q33, q35),
+    y = 'group',
+    facet_rows = vars(.question),
+    variable_labels = c(
+      q30 = "Votes counted as intended",
+      q31 = "Election officials will do good job",
+      q32 = "Election workers will be committed",
+      q33 = "Voting process will be fair",
+      q35 = "Election technology will be secure"
+    ),
+    facet_label_wrap = 10,
+    labels_size = 2.5,
+    symmetric = F,
+    add_totals = T
+  ) +
+  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+  # ggplot2::scale_fill_brewer(palette = "Greys")+
+  labs(subtitle = str_wrap("Local Area", width = 95)) +
+  theme_bw() +
+  theme(
+    text = element_text(family = "Palatino Linotype"),
+    legend.position = 'bottom',
+    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
+    axis.text.x = element_blank(), # remove percentage text along x-axis
+    strip.text.y.right = element_text(angle = 0, size = 8)
+  )
+
+# trust.likert.treat.az
+# trust.likert.treat.lcl
+
+# Instead of two separate plots, arrange into one plot while remaining separated
+# use `ggpubr` package to print multiple plots side-by-side (or alt. row-by-row)
+ggpubr::ggarrange(
+  trust.likert.treat.az,
+  trust.likert.treat.lcl,
+  ncol = 2,
+  common.legend = T,
+  legend = "bottom", 
+  font.label = list(family = "Palatino Linotype")
+)
+```
+
+Reviewing item responses distinguished by treatment condition reveals particulars of the treatment effect (@fig-trustlikert).
+Among the items that asked about Maricopa County, AZ, it is a bit easier to see upon which items the treatment vignette had the greatest effect.
+It appears that the main effect of the treatment is upon responses to the item that measures confidence in the security of election technology.
+
+Regarding confidence in the commitment of election staff and volunteers, a higher proportion of respondents in the treatment group selected "Very confident" over "Somewhat confident" compared to the control group, but only for items concerning Maricopa County, AZ.
+Although confidence in election workers was generally high across the board, the shift from "Somewhat" to "Very" confident for items pertaining to election worker *commitment* to fairness and accuracy seems to clearly speak to the group being recruited, i.e., veterans and family members.
+However, the same visible shift in proportion from "Somewhat" to "Very" confident isn't observed when items asked about one's local area, which undermines the suggestion that the treatment effect can be cleanly attributed to respondent's feelings about veteran service members and their families.
+It may be the case that respondents harbor particular attitudes or sentiment about Maricopa County, AZ itself, or there may be nothing uniquely special about Maricopa County, AZ supposing that elections anywhere beyond one's local area generally garner slightly less confidence.
+
+What this does suggest, however, is that trust in the fairness and accuracy of the electoral process is notably higher upon the notion that military veterans will be directly engaged as election staff and volunteers in places where such trust falters.
+The question turns to whether this also lowers distrust, or the extent to which one expects electoral fraud to occur.
+
+```{r}
+#| label: fig-distrustlikert
+#| fig-cap: "Disrust in Election Administration by Experiment Condition"
+
+# distrust in elections in AZ by experimental condition
+distrust.likert.az <- df |>
+  # reverse levels of factor vars to show positive difference in "not likely"
+  mutate(across(c(q28_1:q28_5), ~forcats::fct_rev(.))) |> 
+  ggstats::gglikert(
+    include = c(q28_1:q28_5),
+    y = 'group',
+    facet_rows = vars(.question),
+    variable_labels = c(
+      q28_1 = "Voter fraud will occur",
+      q28_2 = "Many votes won't be counted",
+      q28_3 = "Many voters will be turned away",
+      q28_4 = "Foreign Interference",
+      q28_5 = "Election officials will discourage voting"),
+    facet_label_wrap = 10,
+    labels_size = 2.5,
+    symmetric = F,
+    add_totals = T
+  ) +
+  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+  # ggplot2::scale_fill_brewer(palette = "Greys")+
+  labs(subtitle = str_wrap("Maricopa County, Arizona", width = 95)) +
+  theme_bw() +
+  theme(
+    text = element_text(family = "Palatino Linotype"),
+    legend.position = 'bottom',
+    axis.text.x = element_blank(), # remove percentage text along x-axis
+    strip.text.y.right = element_blank()
+  )
+
+# distrust in elections in Local area by experimental condition
+distrust.likert.lcl <- df |>
+  # reverse levels of factor vars to show positive difference in "not likely"
+  mutate(across(c(q40_1:q40_5), ~forcats::fct_rev(.))) |> 
+  ggstats::gglikert(
+    include = c(q40_1:q40_5),
+    y = 'group',
+    facet_rows = vars(.question),
+    variable_labels = c(
+      q40_1 = "Voter Fraud will occur",
+      q40_2 = "Many Votes won't be counted",
+      q40_3 = "Many voters will be turned away",
+      q40_4 = "Foreign Interference",
+      q40_5 = "Election officials will discourage voting"),
+    facet_label_wrap = 10,
+    labels_size = 2.5,
+    symmetric = F,
+    add_totals = T
+  )+
+  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+  # ggplot2::scale_fill_brewer(palette = "Greys")+
+  labs(subtitle = str_wrap("Local Area", width = 95)) +
+  theme_bw() +
+  theme(
+    text = element_text(family = "Palatino Linotype"),
+    legend.position = 'bottom',
+    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
+    axis.text.x = element_blank(), # remove percentage text along x-axis
+    strip.text.y.right = element_text(angle = 0, size = 8)
+  )
+
+# Instead of two separate plots, arrange into one plot while remaining separated
+# use `ggpubr` package to print multiple plots side-by-side (or alt. row-by-row)
+ggpubr::ggarrange(
+  distrust.likert.az,
+  distrust.likert.lcl,
+  ncol = 2,
+  common.legend = T,
+  legend = "bottom", 
+  font.label = list(family = "Palatino Linotype")
+)
+
+```
+
+Similar to the trust scale items, the items on the distrust scale were associated with lower distrust in the treatment condition compared to the control.
+A quick glance at @fig-distrustlikert shows what appears to be a significant reduction in distrust, especially regarding the expectations that many votes wouldn't be counted, many voters would be turned away, and that election officials would discourage voters from casting a ballot.
+Interestingly, the expectation that there would be foreign interference in elections in Maricopa County, AZ were pretty resilient against the treatment.
+And again, responses for items pertaining to elections in one's local area are practically indistinguishable between treatment and control.
+
+### Confidence in elections
+
+Once trust and distrust were composed into unified variable of confidence in elections, I then examined distribution of the dependent variable followed by analysis of the effect of the treatment by comparison of mean differences for confidence in elections by experiment condition.
+Recall that on this scale, zero reflects insecurity (e.g., similar or equal values of trust and distrust), whereas values diverging from zero reflect confidence in either direction, trust or distrust respectively.
+Positive values reflect confidence as trust in elections administration (e.g., elections will be fair and accurate), whereas negative values reflect confidence as distrust in elections (i.e., expectation that election fraud will occur).
+To retain a meaningful zero, I rescaled the sum scores to range from -3 to 3[^9] and then superimposed two histograms of confidence scores: one derived from AZ items and another for scores derived from local area items.
+Doing this is illustrative of the relative distribution of confidence that differed depending on the location of elections referred to in the survey items (e.g., Maricopa County, AZ).
+
+As revealed by review of the item responses, the distribution of confidence differed depending on whether survey items pertained to elections in Maricopa County, AZ, or elections within one's local area.
 
@@
 #| label: fig-dist
-#| fig-cap: "Histograms of Composite (mean) Scores for Trust in Elections And Expectation of Electoral Fraud"
+#| fig-cap: "Overlapping histograms of Confidence in Elections for AZ and Local Area"
+#| fig-pos: "H"
 
-# trust scores are not normally distributed, bi-modal, neg skew
-trst.scores.hist <- ggplot(data, aes(trst.mean.scores))+
-  geom_histogram(aes(y = after_stat(density)), bins = 15,
-                 color = 1, fill = "grey")+
-  geom_density(lwd = 1.5, color = 1, fill = 1, alpha = 0.35)+
-  geom_segment(x = round(mean(data$trst.mean.scores), 2), y = 0, yend = 0.80, color = "red")+
+ggplot(df) +
+  geom_histogram(
+    aes(x = conf.az.rescaled , y = after_stat(density)),
+    bins = 15,
+    alpha = 0.2,
+    color = 1,
+    fill = "red"
+  ) +
+  geom_histogram(
+    aes(x = conf.lcl.rescaled , y = after_stat(density)),
+    bins = 15,
+    alpha = 0.2,
+    color = 1,
+    fill = "blue"
+  ) +
+  geom_segment(
+    x = round(mean(df$conf.az.rescaled), 2),
+    y = 0,
+    yend = 0.35,
+    color = "firebrick",
+    lwd = 1.4,
+    linetype = 2
+  ) +
+  geom_segment(
+    x = round(mean(df$conf.lcl.rescaled), 2),
+    y = 0,
+    yend = 0.35,
+    color = "darkblue",
+    lwd = 1.4,
+    linetype = 2
+  ) +
+  annotate(
+    "text",
+    x = round(mean(df$conf.az.rescaled), 2),
+    y = 0.40,
+    label = paste("AZ =", round(mean(
+      df$conf.az.rescaled
+    ), 2), "(", round(sd(
+      df$conf.az.rescaled
+    ), 2), ")"),
+    color = "firebrick"
+  ) +
+  annotate(
+    "text",
+    x = round(mean(df$conf.lcl.rescaled), 2),
+    y = 0.43,
+    label = paste("Local area =", round(mean(
+      df$conf.lcl.rescaled
+    ), 2), "(", round(sd(
+      df$conf.lcl.rescaled
+    ), 2), ")"),
+    color = "darkblue"
+  ) +
   labs(
-    x = "Trust in Elections Mean Scores",
+    x = str_wrap("Confidence", width = 85),
     y = "Density",
-    caption = "mean = 3.09, sd = 0.69, median = 3.0, skew = -0.67, kurtosis = 0.25"
-  )+
-  annotate("text", x = round(mean(data$trst.mean.scores), 2), y = 0.85,
-           label = paste("mean =", round(mean(data$trst.mean.scores), 2)), color = "red")
+    caption = str_wrap(
+     "Mean (std.deviation). Difference = 0.20, CI [0.068, 0.33], t = 2.959, df=1283.733, p = 0.003",width = 95)) +
+  theme_bw()
 
-# eef scores are not normally distributed, also bi-modal pos skew
-eef.scores.hist <- ggplot(data, aes(eef.mean.scores))+
-  geom_histogram(aes(y = after_stat(density)), bins = 15,
-                 color = 1, fill = "grey")+
-  geom_density(lwd = 1.5, color = 1, fill = 1, alpha = 0.35)+
-  geom_segment(x = round(mean(data$eef.mean.scores), 2), y = 0, yend = 0.80, color = "red")+
-  labs(
-    x = "Exp. of Electoral Fraud Mean Scores",
-    y = "Density",
-    caption = "mean = 2.27, sd = 0.75, median = 2.2, skew = 0.19, kurtosis = -0.55"
-  )+
-  annotate("text", x = round(mean(data$eef.mean.scores), 2), y = 0.85,
-           label = paste("mean =", round(mean(data$eef.mean.scores), 2)), color = "red")
-
-# place plots side by side
-gridExtra::grid.arrange(eef.scores.hist, trst.scores.hist, ncol = 2)
 ```
 
-Given the non-normal (or at least un-equal skew of the) distribution of the two scale scores and ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho$ -0.49 (Kendall's \tau = -0.39) between summated scores on the two scales.
+Overall, the sample expressed more trust in elections relative to distrust seeing as how the distribution of confidence is largely positive (@fig-dist).
+However, there's a clear difference between items that asked about elections in Maricopa county, AZ and those that asked about one's local area.
+Confidence in elections within one's local area positively differed from confidence in elections held in Maricopa County, AZ.
+A paired t-test suggests that this difference was statistically significant, though somewhat small (mean difference $= -0.33$, $95\%$ CI $[-0.38, -0.27]$, $t(1286) = -11.61$, $p < .001$; Cohen's $d = -0.32$, $95\%$ CI $[-0.38, -0.27]$).
+Nonetheless, respondents appeared less confident regarding elections in Maricopa County, AZ, but held more confidence in elections administration in their local area.
+This complements previous research that demonstrates a similar bias favorable to one's local area [@stewart2022].
 
-The negative correlation between the items and the composite scores makes sense.
-Theoretically speaking, a person who is certain that electoral fraud will occur clearly lacks trust in the election.
-That is, expectation of electoral fraud does imply lack of trust in elections.
-However, the reverse isn't also necessarily true; it is reasonable to hold a degree of trust in elections alongside expectations that electoral fraud will occur.
-Holding both considerations isn't necessarily an example of cognitive dissonance, as a lack of confidence in elections doesn't necessarily imply an expectation of electoral fraud.
-A lack of trust in elections might render one open to potentialities, but expectation of fraud is in no way necessitated by lacking trust in elections.
-When considered along a spectrum, both can be considered as degrees of *confidence*; and in the absence of confidence, insecure.
+Accordingly, when confidence levels are distinguished by experiment condition, the treatment vignette only had an effect upon survey items pertaining to elections in Maricopa County, AZ.
+Conducting an independent samples t-test (i.e., Welch Two Sample t-test) suggests that the effect of the treatment compared to the control condition is positive, statistically significant, yet substantially pretty small.
 
-Accordingly, those whose responses to the "trust in elections" items would be cancelled out by their responses to the "expectation of fraud" items.
-Those who are, or are close to being, equally confident in both directions would be the most *insecure* about their expectations[^Insecure in terms of their confidence.
-Not insecure as to imply some anxious or concerned affect.].
-Having no trust in elections and no expectation that electoral fraud will occur is functionally equivalent to having equal degree of both.
-Quite literally, an uncertain feeling of "it could go one way or the other".
-Operationally, this would reflect a middling 0 on a scale of *confidence*.
-Seeing as how expectation of electoral fraud is also a level of confidence, then it is reasonable to place all items onto a symmetric scale where positive values represent trust in elections and negative values represent expectation of electoral fraud.
+```{r}
+#| label: tbl-ttest
+#| tbl-cap: "Mean Difference Effect of Treatment Compared to Control Condition"
+#| fig-pos: "h"
+#| include: false
 
-The primary dependent variable is *confidence in elections*, which reflects one's trust in election administration minus their expectations of electoral fraud.
-Operationally, the dependent variable is a linear composite scale of item responses across items measuring trust in elections and expectations of electoral fraud re-scaled to range from -3 to 3.
-Items comprising trust in elections were positively coded to range from 0 "Not at all confident/committed" to 3 "Very confident/committed".
-Likewise, items capturing expectation of electoral fraud were coded negatively to range from 0 "Not likely at all" to -3 "Very likely".
+df |> 
+  mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |> 
+  rstatix::t_test(formula = conf.az.rescaled ~ group, var.equal = F, detailed = T) |>
+  select(Difference = estimate, 
+         conf.low, conf.high, 
+         t = statistic, df, p, 
+         -alternative, -method, -.y., -estimate1, -estimate2, -group1, -group2,
+         -n1, -n2) |> 
+  # insight::format_table(stars = T) |> 
+  kableExtra::kbl(booktabs = T, digits = 4) |> 
+  kableExtra::kable_styling(
+    full_width = T,
+    latex_options = c("hold_position"))
 
-Computed mean or sum scores for multiple Likert items are commonly acceptable, as they are relatively robust in spite of violating assumptions of a normal distribution of data (or residuals).
-due to the somewhat non-normal distribution of the sum or mean scores and the ordinal nature of the variable items, an ordered regression analysis is preferred.
+```
 
-The primary independent variable is the prospect of military veterans as election workers (i.e., staff or volunteers).
+The results of @tbl-ttest show that, on a scale ranging from -3 to 3, the effect of the treatment is associated with a $0.20$ average difference in confidence in elections in Maricopa County, AZ, compared to average confidence among those in the control group.
+A simple difference of means test on this scale, however, does not lend itself well to interpretation; its hard to really grasp what a $0.20$ positive difference, on average, really amounts to.
+When the dependent variable is centered and scaled to have a mean = 0 and standard deviation = 1, standardized parameters permit interpretation of the treatment effect in terms of standard deviations.
 
-## Results
+> "tbl-mod1" here
 
-The key question is whether trust in elections (or voter confidence) is response to the treatment vignette.
+The table above shows that effect of the treatment on confidence in elections is associated with a 0.16 standard deviation positive difference on average compared to confidence of those in the control group.
+I also include models where trust and distrust are regressed on the treatment condition separately in order to illustrate the divergent effect of the treatment.
+Nothing is more illustrative than graphs and lines, however.
 
-Note that the question wording for the survey items derived from the 2022 SPAE are modified slightly but substantially.
-The question wording in this study is most similar to those in 2022 SPAE that assess confidence that votes will be counted as voters intend without specific reference to their own vote (e.g., in their county, state, or nationwide).
-In this study, two survey items ask about confidence in vote counts in one specific county in Arizona and another referencing their local community.
-Moreover, the 2022 SPAE includes "I don't know" as a response option, whereas the comparable item in this study did not include a "don't know" response option.
-Comparison between responses to the two similar items was conducted....
+> "fig-coef1" and "fig-coef2" here
+
+Visualized in @fig-coef2, the treatment effect on both trust and distrust is clear.
+Although the effect is only there when questions pertained to Maricopa County, AZ.
+The treatment effect on trust and distrust is conditional on whether the survey questions inquired about elections in Maricopa County, AZ.
+Announcing efforts to recruit veterans and their families to work as election staff and volunteers increases confidence in elections administration in places outside of one's local area, but doesn't boost confidence in elections within one's local area.
+However, bear in mind that confidence in elections for one's local area is already higher than for those outside.
+Thus, there's already less insecurity concerning elections in one's local area, but publicized efforts to recruit veterans to work as election staff and volunteers is a small but positive step towards closing that gap in confidence for elections that occur elsewhere.
+
+I now turn to results examining those who held onto the belief that the 2020 election results were illegitimate.
+I think check to see if recruiting veterans simply makes people feel safer at the polls.
 
@@
 ### Limitations
+
+As far as I'm aware, both the items, their wording, and their composition into measurement scales are unique to this study.
+This renders the composite scores for trust in elections sample dependent and limits comparability with other cross-sectional survey data.
 
@@
 
-## Appendix A: Survey Experiment Vignettes {#sec-appendix-a}
+## Appendix A: Survey Experiment Vignettes and Survey Items {#sec-appendix-a}
 
@@
 
-::::: {.content-hidden layout-ncol="2" unless-format="pdf"}
-<div>
-
+::::: {.content-hidden unless-format="pdf" layout="[0.45, -0.1, 0.45]"}
+::: {#first-column}
 ### Treatment Vignette
@@
 I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
+:::
 
-</div>
-
-<div>
-
+::: {#second-column}
 ### Control Vignette
@@
 I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
+:::
+:::::
 
-Text of the Control Condition: Recruitment of Community Members
-
-</div>
-:::::
+\pagebreak
 
@@
 
-::: {.content-visible when-format="html" unless-format="pdf"}
-```{r}
-#| label: tbl-desc
-#| tbl-cap: "Description of Sample Demographics"
-#| tbl-cap-location: top
-
-# quick, informative, easy table of sample demographics w/ some other questions.
-tbl.desc <- data |>  
-  labelled::set_variable_labels(
-    age_cat = "Age group, in years"
-  ) |> 
-  gtsummary::tbl_summary(
-    by = qset,
-    include = c(
-    qset,
-    age_cat, 
-    gender_3cat, 
-    race, 
-    educ_4cat, 
-    partyid_3cat,
-    ideo,
-    ideolean,
-    voted2020,
-    choice2020, 
-    voteintent,
-    milserv1,
-    milserv2,
-    milservfam),
-    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"),
-    type = list(milserv1 ~ "categorical",
-
-                milserv2 ~ "categorical",
-                milservfam ~"categorical"), 
-    missing = "no") |> 
-  gtsummary::add_n() |> 
-  gtsummary::add_overall() |> 
-  gtsummary::modify_header(label = "**Variable**") |> 
-  gtsummary::bold_labels()
-
-gtsummary::as_gt(tbl.desc) |>  
-  gt::tab_footnote(
-    footnote = "'true' Independents do not identify nor 'lean' toward either political party",
-    placement = "left"
-    ) |>  
-  gt::cols_align(align = 'left', columns = everything()) |> 
-  gt::tab_options(
-    table.font.size = "small",
-    data_row.padding = gt::px(1)
-  )
-
-```
-:::
-
-There should be nothing below here
-
-::: {.content-hidden unless-format="pdf"}
-```{r}
-#| label: tbl-desc-pdf
-#| tbl-cap: "Description of Sample Demographics"
-#| tbl-cap-location: top
-
-frqs <- data |> 
-  select(group, qset, age_cat, gender_3cat, educ_4cat, race, partyid_3cat) |> 
-  map(count_prop)
-
-demog_df <- purrr::reduce(frqs, dplyr::full_join)
-
-kableExtra::kbl(demog_df,
-                booktabs = T, 
-                digits = 2,
-                col.names = c("Name", "n", "Pct")) |> 
-  kableExtra::pack_rows("Experiment Condition", 1, 2) |>
-  kableExtra::pack_rows("Question Set", 3, 4) |>
-  kableExtra::pack_rows("Age", 5, 12) |> 
-  kableExtra::pack_rows("Gender", 13, 15) |> 
-  kableExtra::pack_rows("Education", 16, 19) |> 
-  kableExtra::pack_rows("Race", 20, 24) |> 
-  kableExtra::pack_rows("Party ID", 25, 27) |> 
-  kableExtra::kable_styling(
-    latex_options = c("striped", "scale_down"),
-    full_width = F,
-    font_size = 8) |> 
-  kableExtra::column_spec(1, width = "20em")
-
-```
-
-:::
-
 \pagebreak
@@
 
-[^3]: Note that *electoral anxiety* is used in place of electoral trust/confidence simply to emphasize the anticipatory nature of the attitudes in question.
-Election anxiety is not taken to be the inverse of trust and confidence.
-A lack of trust does not necessarily imply (a state of) anxiety.
+[^3]: Note that election insecurity is used in place of electoral confidence simply to emphasize the anticipatory nature of the attitudes in question.
+Election insecurity is taken to denote a lack of confidence.
 
-[^4]: The cited study defined "insurrectionist sentiments" as, "...willingness to support violent efforts to overturn the results of an election in favor of another, unelected political leader." [@pape2024, 7].
-It should be noted, however, that despite the general definition, the operative items used to measure such sentiments ask about Donald Trump specifically, not an "unelected political leader".
+[^4]: Demographic breakdown of the sample are included in Appendix B.
 
 [^5]: Complete text of treatment and control vignettes are included in the Appendix
+
+[^6]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
+
+[^7]: Survey item wording and responses are included in Appendix A.
+
+[^8]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
+The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024], yet there is no general consensus on the most appropriate method generally.
+The use of either appears to largely depend on the researcher's particular research objective, theoretical suppositions, and necessity.
+Another common concern is the inappropriate treatment of ordinal variables as interval which levy strong assumptions, e.g., each item contributes equally to the variable being measured and that ordinal response categories are equidistant as though on an interval scale [@wang2013; for contrast, see @robitzsch2020].
+
+[^9]: This range is mostly arbitrary, as a range from -1 to 1 works much the same.
+When relying on simple sum total score, the scale ranges from -15 to 15.
+So a single point increase from 0 to 1 may reflect a combination of a single "Very confident" response on a trust item compensated by a single "Somewhat likely" response on a distrust item (i.e., 3-2 = 1), or some other equivalent combination.
+Although the use of mean scores would place scores back onto the response scale metric (e.g., from 0 to 3, reflective of "not at all" to "very"), this results in a unipolar scale (from 0 to 3).
+The bipolar scale resulting from the composition of positive trust and negative distrust engenders meaning to zero and negative values.
+As such, composite mean scores become inappropriate and interpretation of scores would no longer be feasible.
+In other words, negative values on the scale for confidence in elections hold substantive meaning (e.g., distrust, absent trust), which makes transforming scores to fit a unipolar scale inappropriate.

### 2025-02-26 docs/src/01-data.R

@@ -1,930 +1,0 @@
-# using data exported from Qualtrics on 2024-10-23
-# The most recent (i.e., last) response was recorded 2024-09-18 at 6:40pm (1840)
-# When exporting the data, Qualtrics allows me to recode 'seen but unanswered'
-# questions with code 99. I downloaded the data again just for that because I
-# want to see how many of the missing values in my 2024-09-11 dataset are
-# attributed to people who skipped survey questions.
-
-# load packages ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
-library(tidyverse)
-library(haven)
-library(surveytoolbox)
-library(labelled)
-library(sjlabelled)
-
-# load data ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
-
-# load raw SPSS export (includes display order vars)
-# downloaded on 2024-10-29 at 12:02 PM
-raw_spss <- haven::read_sav("data-raw/VMF_Election_Worker_Recruitment_Survey_with_display_order_20241029_T12.02.sav")
-
-# load raw SPSS export (doesn't include display order vars)
-# downloaded 2024-10-23 at 1:54 PM
-# raw_spss3 <- haven::read_sav(file = "data-raw/VMF_Election_Worker_Recruitment_Survey_2024-10-23_13.54.sav")
-
-# despite being a .sav file imported using `haven::read_sav()`, 
-# the data set is not "haven_labelled"
-# haven::is.labelled(raw_spss)
-
-# create data dictionary of raw SPSS data set ::::::::::::::::::::::::::::::####
-
-# A data dictionary contains metadata about the data. The
-# `labelled::generate_dictionary` function is used to create a data
-# dictionary. (alt. `surveytoolbox::data_dict`)
-# a data frame is loaded into the R environment with the number of
-# observations equal to number of variables in the original data set.
-# NOTE: surveytoolbox::data_dict function is used here because the resulting
-# dataframe can be saved as a .csv
-raw_spss_dict <- raw_spss |> surveytoolbox::data_dict()
-
-# save data dictionary of raw_spss dataset download
-write.csv(raw_spss_dict, file = "data/raw_spss_dict.csv")
-
-# create and save survey codebook ::::::::::::::::::::::::::::::::::::::::::####
-
-# this includes only the survey questions: question number (var), the question
[…]

### 2025-02-26 src/01-data.R

@@ -331,7 +331,7 @@ data <- data |>
   mutate(across(where(is.factor), ~forcats::fct_recode(., NULL = "-99"))) |>
   
   # reverse order of identified factor levels for consist direction
-  mutate(across(c(q8, q20, q23, q24, q25, q31, q34, q35, q49, q50), .fns = ~fct_rev(.))) |> 
+  mutate(across(c(q8, q20, q23, q24, q25, q31, q34, q35, q36, q49, q50), .fns = ~fct_rev(.))) |> 
   # reverse order of group levels so control comes first. Better table display
   mutate(group = forcats::fct_rev(group))
 
@@ -378,6 +378,22 @@ data <- data |>
   labelled::set_variable_labels(
     age_cat = "Age categorized into eight groups"
   )
+
+# create another age group variable with fewer age categories
+data <- data |>    
+  mutate(age_4cat = 
+           forcats::fct_collapse(
+             as_factor(q2),
+             "18-34" = c(18:34),
+             "35-54" = c(35:54),
+             "55-74" = c(55:74),
+             "75-85+" = c(75:82, 84, 85:86, 88, 92)
+             ),
+         .after = age_cat) |> 
+  labelled::set_variable_labels(
+    age_cat = "Age categorized into three groups"
+  )
+
 # create gender_3cat, collapsed version of voted2020, and set var label
 data <- data |> 
   dplyr::mutate(gender_3cat = forcats::fct_collapse(
@@ -696,8 +712,47 @@ data_dict <- data |>
 # get a glimpse of the data
 # glimpse(data)
 
-# adding some more things:::::::::::::::::::::::::::::::::::::::::::::::::::####
+# Re-code select variables :::::::::::::::::::::::::::::::::::::::::::::::::####
 
+# recode select factor variables as numeric
+data <- data |> 
+  mutate(across(c(q19, q20, q22, q23, q24, q30, q31, q33, q34, q35),
+                ~ dplyr::case_when(
+  .x == "Not at all confident" ~ 0,
+  .x == "Not too confident" ~ 1,
+  .x == "Somewhat confident" ~ 2,
+  .x == "Very confident" ~ 3,
+  TRUE ~ NA), 
+  .names = "{col}.r")) |>
+  mutate(across(c(q21, q32), ~ dplyr::case_when(
+    .x == "Very committed" ~ 3,
+    .x == "Somewhat committed" ~ 2,
+    .x == "Not too committed"  ~ 1,
[…]

### 2025-02-26 src/02-data-postprocessing.R

@@ -1,0 +1,254 @@
+set.seed(1234)
+
+# load packages
+library(tidyverse)
+
+# load data
+load("data/research-paper-data-20241029.Rdata")
+
+# subset data and do some other stuff ::::::::::::::::::::::::::::::::::::::####
+
+df <- data |> 
+  select(
+    rowID,
+    response_id,
+    group,          # Experimental condition: treatment or control
+    partyid_3cat,   # partyID in 3 categories, true independents (not leaners)
+    dem.dum,        # dummy variable of democrats
+    rep.dum,        # dummy variable of republican
+    ind.dum,        # dummy variable of independents
+    race2,          # race including Hispanic/Latino/Spanish origin
+    race_wnw,       # race dichotomous between White and Non-White
+    educ_4cat,      # educational attainment in four categories
+    educ_4cat.num,  # educational attainment in four categories, numeric
+    age_4cat,       # age in years in 4 groups
+    mil_anyrelation,# relation or no relationship with military service
+    milrelation,    # particular relationship with military service
+    gender_3cat,    # gender: male, female, other or preferred not to say
+    q5:q8,          # pre-treatment survey items
+    q19:q24,        # trust in elections in Maricopa County, AZ
+    q25:q26,        # concern for voter safety in Maricopa County, AZ
+    q28_1:q28_5,    # eef in Maricopa County, AZ
+    q30:q35,        # trust in elections in local area
+    q36:q38,        # concern for voter safety in local area
+    q40_1:q40_5,    # eef in Maricopa County, AZ
+    contains(".r"), # recoded numeric versions of the variables above
+    contains(".n")  # recoded numeric versions of the variables above
+)
+
+df <- df |> labelled::set_variable_labels(
+  q28_1 ="There will be voter fraud, that is, people who are not eligible to vote will vote, or vote more than once",
+  q28_2 ="Many votes will not actually be counted",
+  q28_3 ="Many people will show up to vote and be told they are not eligible",
+  q28_4 ="A foreign country will tamper with the votes cast in this area to change the results",
+  q28_5 ="Election officials in Maricopa County, Arizona will try to discourage some people from voting",
[…]

### 2025-02-26 src/scores.R

@@ -1,0 +1,123 @@
+set.seed(1234)
+
+
+# Construct composite score variables using `psych::scoreItems` ::::::::::::####
+
+# create a list of scoring keys for scales for AZ and Local area
+conf.keys <- list(
+  conf.az = c("q19.r","q20.r","q21.r","q22.r","q24.r",
+              "q28_1.r","q28_2.r","q28_3.r","q28_4.r","q28_5.r"),
+  conf.local = c("q30.r","q31.r","q32.r","q33.r","q35.r",
+                 "q40_1.r","q40_2.r","q40_3.r","q40_4.r","q40_5.r"),
+  trust.az = c("q19.r","q20.r","q21.r","q22.r","q24.r"),
+  trust.local = c("q30.r","q31.r","q32.r","q33.r","q35.r"),
+  distrust.az = c("q28_1.n","q28_2.n","q28_3.n","q28_4.n","q28_5.n"),
+  distrust.local = c("q40_1.n","q40_2.n","q40_3.n","q40_4.n","q40_5.n")
+)
+
+
+conf.sum.scores <- psych::scoreItems(
+  keys = conf.keys,
+  items = df,
+  totals = T,
+  missing = T,
+  impute = "median"
+)
+
+# The item by scale correlations for each item, corrected for item overlap by
+# replacing the item variance with the smc for that item.
+# Note that, when SMC < 0, SMC were set to .0
+item.cor.corrected <- conf.sum.scores$item.corrected
+
+conf.mean.scores <- psych::scoreItems(
+  keys = conf.keys,
+  items = df,
+  totals = F,
+  missing = T,
+  impute = "mean"
+)
+
+
+
+# head(conf.sum.scores$scores)
+# conf.sum.scores$scores[,1] # conf.sum.az
+# conf.sum.scores$scores[,2] # conf.sum.lcl
+# conf.sum.scores$scores[,3] # trust.az
+# conf.sum.scores$scores[,4] # trust.lcl
+# conf.sum.scores$scores[,5] # distrust.az
+# conf.sum.scores$scores[,6] # distrust.lcl
+# 
+# head(conf.mean.scores$scores)
+# conf.mean.scores$scores[,1] # conf.sum.az
+# conf.mean.scores$scores[,2] # conf.sum.lcl
+# conf.mean.scores$scores[,3] # trust.az
+# conf.mean.scores$scores[,4] # trust.lcl
+# conf.mean.scores$scores[,5] # distrust.az
[…]

### 2025-02-26 index.qmd
modifications to index and 01-data.R script

@@
     dev: "ragg_png" # same as knitr::opts_chunk$set(dev = "ragg_png")
+editor_options: 
+  chunk_output_type: console
 ---
@@
 library(easystats)
-
-options("huxtable.latex_use_fontspec" = TRUE) # if TRUE, uses the LaTeX “fontspec” package which lets you use the same fonts in TeX and HTML.
-You will need to use the xetex or xelatex engine for output.
+library(patchwork)
 
@@
 That is, item responses on the trust scale ranged from 0 ("Not confident at all") to 3 ("Very confident), whereas responses on the distrust scale ranged from 0 ("Not likely at all") to -3 ("Very likely").
-Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable.
-On this scale, positive values reflect higher confidence in elections, negative values reflect greater distrust, and values closer to zero correspond to an individual's degree of insecurity[^8].
+Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^8].
+On this scale, positive values reflect higher confidence in elections, negative values reflect greater distrust, and values closer to zero correspond to an individual's degree of insecurity.
 
@@
 Of course, it is easy enough to examine the effect of the treatment on both trust and distrust separately.
-However, the theory presents a hypothesis that the treatment will impose influence upon both variables *concurrently and in a positive direction* in light of the relationship between trust and distrust.
-Confidence increases insofar as trust in elections increases and distrust decreases; since distrust detracts from trust, then an accurate measure of confidence must take that constraint into account.
+However, the theory presents a hypothesis that the treatment will impose influence upon both variables *concurrently and in a positive direction* with respect to the relationship between trust and distrust.
+That is to say, confidence increases insofar as trust in elections increases and distrust decreases; since distrust detracts from trust, then an accurate measure of confidence must take that constraint into account.
 
@@
 
-I first review responses to the survey items capturing trust and distrust, respectively.
+I first review responses to the survey items capturing trust and distrust separately by treatment condition.
 When distinguished by experiment condition, trust in elections admin is noticeably higher for those who read the treatment vignette.
@@
 #| fig-cap: "Trust in Election Administration by Experiment Condition"
+#| fig-height: 4.5
+#| fig-pos: "h"
 
@@
   font.label = list(family = "Palatino Linotype")
-)
+) +
+  # add figure footnote annotation
+  patchwork::plot_annotation(
+    caption = str_wrap("Missing values removed. Displays percent proportions of responses by experiment condition and combined percentage proportions for two categories.",
+               width = 85), theme = theme(text = element_text(family = "Palatino Linotype")))
+
 ```
@@
 #| fig-cap: "Disrust in Election Administration by Experiment Condition"
+#| fig-height: 4.5
+#| fig-pos: "h"
 
@@
   font.label = list(family = "Palatino Linotype")
-)
+) +
+  # add figure footnote annotation
+  patchwork::plot_annotation(
+    caption = str_wrap("Missing values removed. Displays percent proportions of responses by experiment condition and combined percentage proportions for two categories.",
+               width = 85), theme = theme(text = element_text(family = "Palatino Linotype")))
 
@@
 
-Once trust and distrust were composed into unified variable of confidence in elections, I then examined distribution of the dependent variable followed by analysis of the effect of the treatment by comparison of mean differences for confidence in elections by experiment condition.
+Once trust and distrust were composed into unified variable of confidence in elections, I then examined distribution of the dependent variable followed by analysis of the effect of the treatment by comparison of mean differences between experiment conditions.
 Recall that on this scale, zero reflects insecurity (e.g., similar or equal values of trust and distrust), whereas values diverging from zero reflect confidence in either direction, trust or distrust respectively.
-Positive values reflect confidence as trust in elections administration (e.g., elections will be fair and accurate), whereas negative values reflect confidence as distrust in elections (i.e., expectation that election fraud will occur).
+Positive values reflect trust in elections administration (e.g., elections will be fair and accurate), whereas negative values reflect distrust in elections (i.e., expectation that election fraud will occur).
 To retain a meaningful zero, I rescaled the sum scores to range from -3 to 3[^9] and then superimposed two histograms of confidence scores: one derived from AZ items and another for scores derived from local area items.
@@
 #| label: fig-dist
-#| fig-cap: "Overlapping histograms of Confidence in Elections for AZ and Local Area"
+#| fig-cap: "Overlapping Distribution of Confidence in Elections for AZ and Local Area"
 #| fig-pos: "H"
@@
     caption = str_wrap(
-     "Mean (std.deviation). Difference = 0.20, CI [0.068, 0.33], t = 2.959, df=1283.733, p = 0.003",width = 95)) +
-  theme_bw()
+     "Mean (std.deviation). Mean difference = 0.33, CI [0.27, 0.38], t = 11.613, df = 1286, p < 0.01",
+     width = 95)) +
+  theme_bw(base_family = "Palatino Linotype")
 
@@
 Overall, the sample expressed more trust in elections relative to distrust seeing as how the distribution of confidence is largely positive (@fig-dist).
-However, there's a clear difference between items that asked about elections in Maricopa county, AZ and those that asked about one's local area.
-Confidence in elections within one's local area positively differed from confidence in elections held in Maricopa County, AZ.
-A paired t-test suggests that this difference was statistically significant, though somewhat small (mean difference $= -0.33$, $95\%$ CI $[-0.38, -0.27]$, $t(1286) = -11.61$, $p < .001$; Cohen's $d = -0.32$, $95\%$ CI $[-0.38, -0.27]$).
+However, there's a clear difference between confidence in Maricopa county, AZ elections and elections within one's local area.
+A paired t-test confirms that this difference was statistically significant, though somewhat small (mean difference $= 0.325$, $95\%$ CI $[0.27, 0.38]$, $t(1286) = 11.61$, $p < .001$).
 Nonetheless, respondents appeared less confident regarding elections in Maricopa County, AZ, but held more confidence in elections administration in their local area.
@@
 #| tbl-cap: "Mean Difference Effect of Treatment Compared to Control Condition"
-#| fig-pos: "h"
-#| include: false
+#| tbl-pos: H
 
-df |> 
-  mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |> 
-  rstatix::t_test(formula = conf.az.rescaled ~ group, var.equal = F, detailed = T) |>
-  select(Difference = estimate, 
-         conf.low, conf.high, 
-         t = statistic, df, p, 
-         -alternative, -method, -.y., -estimate1, -estimate2, -group1, -group2,
-         -n1, -n2) |> 
-  # insight::format_table(stars = T) |> 
-  kableExtra::kbl(booktabs = T, digits = 4) |> 
+# conduct two t-tests using `rstatix::t_test`, bind results by row, and pipe
+# into table
+dplyr::bind_rows(
+  df |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
+  rstatix::t_test(formula = conf.az.rescaled ~ group,var.equal = F,detailed = T),
+  df |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
+  rstatix::t_test(formula = conf.lcl.rescaled ~ group,var.equal = F, detailed = T)
+  ) |> 
+  # specify columns and column names
+  select(
+    Diff = estimate,
+    treat_mean = estimate1,
+    control_mean = estimate2,
+    treat_n = n1,
+    control_n = n2,
+    t = statistic,
+    p, df, conf.low, conf.high) |> 
+  mutate(
+    Place = dplyr::case_when(
+      p <= 0.05 ~ "Maricopa County, AZ", 
+      p > 0.05 ~ "Local Area"), 
+    .before = Diff) |> 
+  insight::format_table(stars = T) |> 
+  # insight::export_table(format = "md") # alternate
+  # output table as `kable` for LaTeX pdf
+  kableExtra::kbl(
+    format = "latex", 
+    booktabs = T,
+    col.names = c("Place", "$\\bar{x}_{diff}$", "$\\bar{x}_{treat}$", "$\\bar{x}_{control}$",
+                  "$treat_{n}$", "$control_{n}$", "t", "p", "df", "CI"), 
+    escape = F) |> 
+  kableExtra::footnote(general = "Welch Two Sample t-tests of difference between Confidence in Elections by Treatment Condition.") |> 
   kableExtra::kable_styling(
-    full_width = T,
-    latex_options = c("hold_position"))
+    font_size = 9, 
+    protect_latex = T)
 
@@
 
-The results of @tbl-ttest show that, on a scale ranging from -3 to 3, the effect of the treatment is associated with a $0.20$ average difference in confidence in elections in Maricopa County, AZ, compared to average confidence among those in the control group.
-A simple difference of means test on this scale, however, does not lend itself well to interpretation; its hard to really grasp what a $0.20$ positive difference, on average, really amounts to.
-When the dependent variable is centered and scaled to have a mean = 0 and standard deviation = 1, standardized parameters permit interpretation of the treatment effect in terms of standard deviations.
-
-> "tbl-mod1" here
-
-The table above shows that effect of the treatment on confidence in elections is associated with a 0.16 standard deviation positive difference on average compared to confidence of those in the control group.
-I also include models where trust and distrust are regressed on the treatment condition separately in order to illustrate the divergent effect of the treatment.
+The results of @tbl-ttest show that, on a scale ranging from -3 to 3, the effect of the treatment is associated with a $0.20$ average difference in confidence in elections in Maricopa County, AZ, compared to the control group.
+When the dependent variable is centered to have a mean of $0$ and standard deviation of $1$, standardized parameters permit interpretation of the treatment effect in terms of standard deviations; the standardized difference in confidence between treatment and control is $0.16$ (CI $[0.06, 0.27]$).
 Nothing is more illustrative than graphs and lines, however.
 
-> "fig-coef1" and "fig-coef2" here
+```{r}
+#| label: fig-coef1
+#| layout-nrow: 2
+#| fig-height: 3.5
+#| fig-cap: "Confidence in Elections by Experiment Condition"
+#| fig-subcap: 
+#|   - "Confidence by Treatment Condition"
+#|   - "Trust and Distrust by Treatment Condition"
 
-Visualized in @fig-coef2, the treatment effect on both trust and distrust is clear.
-Although the effect is only there when questions pertained to Maricopa County, AZ.
-The treatment effect on trust and distrust is conditional on whether the survey questions inquired about elections in Maricopa County, AZ.
-Announcing efforts to recruit veterans and their families to work as election staff and volunteers increases confidence in elections administration in places outside of one's local area, but doesn't boost confidence in elections within one's local area.
-However, bear in mind that confidence in elections for one's local area is already higher than for those outside.
-Thus, there's already less insecurity concerning elections in one's local area, but publicized efforts to recruit veterans to work as election staff and volunteers is a small but positive step towards closing that gap in confidence for elections that occur elsewhere.
+# coef plot of treatment effect on confidence distinguished by location
+conf.coef1 <- jtools::plot_summs(
+  lm(conf.az.rescaled ~ group, data = df), 
+  lm(conf.lcl.rescaled ~ group, data = df), 
+  center = T, scale = T, transform.response = T,
+  model.names = c("Conf.AZ", "Conf.Local"),
+  coefs = c("Treatment" = "groupTreatment"), 
+  colors = c("red", "black"),
+  point.shape = c(8, 1))+
+  ggplot2::expand_limits(x = c(-0.25, 0.25))+
+  labs(y = "")+
+  theme_bw(base_family = "Palatino Linotype")
+
+# Coef plots of trust and distrust models for AZ and Local items
+conf.coef2 <- jtools::plot_summs(
+  lm(trust.scores.az ~ group, data = df),
+  lm(distrust.scores.az ~ group, data = df),
+  lm(trust.scores.lcl ~ group, data = df),
+  lm(distrust.scores.lcl ~ group, data = df),
+  center = T, scale = T, transform.response = T,
+  model.names = c("Trust.AZ", "Distrust.AZ", "Trust.Local", "Distrust.Local"),
+  coefs = c("Treatment" = "groupTreatment"),
+  colors = c("red", "red", "black", "black"),
+  point.shape = c(8, 8, 1, 1)
+)+
+  ggplot2::expand_limits(x = c(-0.25, 0.25))+
+  labs(y = "")+
+  theme_bw(base_family = "Palatino Linotype")
+
+conf.coef1
+conf.coef2
+
+```
+
+@fig-coef1 displays standard difference estimates of confidence in elections by treatment condition (control condition as reference).
+@fig-coef1-1 displays two models for confidence in elections in Maricopa County, AZ, and one's local area by treatment condition; @fig-coef1-2 displays four models for trust and distrust in elections in AZ or one's local area by treatment condition.
+These figures merely illustrate the effect of the treatment with respect to the relationship between trust and distrust; ultimately confidence improves.
+
+Confidence in elections was higher among those who read the treatment vignette but remained conditional on whether the survey questions inquired about elections in Maricopa County, AZ.
+This evidence suggests that announcing efforts to recruit veterans and their families to work as election staff and volunteers may increase confidence in elections administration in places outside of one's local area, but may not boost confidence in elections within one's local area.
 
@@
 ## Conclusion
+
+Bear in mind that confidence in elections for one's local area is already higher than for those beyond.
+Thus, there's already more insecurity concerning elections elsewhere for whatever reason.
+In the anticipatory period prior to national elections, publicized efforts to recruit veterans to work as election staff and volunteers may be a small, but positive, step towards reducing insecurity in elections that occur elsewhere.
+Especially among those who maintained a steadfast degree of distrust in elections.
+Despite a lack of evidence that systematic electoral fraud had occurred in the 2020 election, a substantial proportion of the population were unwilling to affirm the legitimacy of the results.
+However, despite such legitimacy beliefs, most were not consistent as they expressed varying levels of trust in different aspects of elections administration.
 

### 2025-02-26 src/01-data.R

@@ -752,196 +752,90 @@ data <- data |>
     .x == "Somewhat confident" | .x == "Somewhat safe" ~ 2,
     .x == "Very confident" | .x == "Very safe" ~ 3,
     TRUE ~ NA), 
-    .names = "{col}.r"))
-
-# using psych package to construct composite scores for each respondent ::: ####
-# psych::scoreItems()
-# These are just sum scores
-
-# get the question text (variable label) for each question
-# uncomment following line to get variable labels
-# data |> select(q19, q20, q21, q22, q23, q24) |> sjlabelled::get_label()
-
-# Q19: How confident are you that votes in Maricopa County, AZ will be counted
-# as voters intend in the elections this November ?
-
-# Q20: How confident are you that election officials, their staff, and
-# volunteers in Maricopa County, AZ will do a good job conducting the elections
-# this November?
-
-# Q21: Think about the election staff and volunteers who handle the
-# administration and conduct of elections in Maricopa County, AZ. How committed
-# do you think they will be to making sure the elections held this November are
-# fair and accurate?
-
-# Q22: How confident are you that the voting process will be fair in Maricopa
-# County, AZ?
-
-# Q23: How confident are you that the voting outcomes will be fair in Maricopa
-# County, AZ?
-
-# Q24: How confident are you that election systems in Maricopa County, AZ will
-# be secure from hacking and other technological threats?
-
-
-# make dataframe containing only items of interest
-trust <- data |> 
-  select(q19.r, q20.r, q21.r, q22.r, q23.r, q24.r) |> 
-  # shorten variable labels
-  sjlabelled::var_labels(
-    q19 ="accurate",
-    q20 = "goodjob",
-    q21 = "committed",
-    q22 = "fairprocess",
-    q23 = "fairoutcome",
-    q24 = "securetech")
-
-
-# create a list of scoring keys
-trust.keys <- list(trust = c("q19.r", "q20.r", "q21.r", "q22.r", "q23.r", "q24.r"))
-
-# compute average composite scores on trust from multi-item Likert scale
-data$trst.mean.scores <- psych::scoreItems(
-  keys = trust.keys, 
-  items = trust,
-  digits = 2,
-  missing = T, 
-  impute = "mean")$scores |> as.numeric()
-
-
-
[…]

### 2025-02-27 index.qmd
late

@@
 That being said, the general public perception, attitudes, or even stereotypes about military veterans are significant to consider.
-Although military recruitment shows a downward trend as of late, public perception of veterans are overwhelmingly positive [@kleykamp2023].
+Although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023].
 Veterans are a particularly potent group where mention of veteran status seems to have a positive, calming, or nullifying effect on attitudes.
@@
   kableExtra::kbl( 
-    format = "latex", 
     booktabs = T,
@@
 
+Publicized announcements that election officials are actively recruiting former military service members to work as election staff and volunteers is associated with slightly greater confidence in elections compared to election worker recruitment announcements that do not explicitly mention targeted recruitment of former military service members.
+Moreover, increased levels of confidence is limited to elections beyond one's local area and, of course, in anticipation of election night.
+Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
+
+Additionally, these results cannot give any indication whether confidence in the electoral process or its administration writ large is higher among those who, while voting in person, interacted with military veterans who were working as election staff or volunteers.
+In other words, this research can provide no indication that having veterans on staff at election sites or individual interaction with veterans while voting has any influence on voter confidence in the post-election period.
+
+All that can be said from the results presented is that public announcement of efforts to recruit veterans to work as election workers results in a small boost in confidence in elections held in places where confidence in elections administration is lower relative to the confidence in elections within one's local area.
+
 Bear in mind that confidence in elections for one's local area is already higher than for those beyond.
@@
 However, despite such legitimacy beliefs, most were not consistent as they expressed varying levels of trust in different aspects of elections administration.
+
+These results speaks more to the influence that military veterans have among those who distrust the electoral process and refute the legitimacy of prior outcomes than it does to the public more generally.
+In general, public confidence appears strongest when the elections under consideration regard those within one's local community.
+Yet, such strong confidence is not generalized outward to the institution of elections administration as a whole.
+Insecurity in the integrity of the electoral process and its administration may be naturally higher for elections that occur further from home.
+Whether that is due to some local favorability bias or some outward negativity bias is hard to say.
+And seeing as how insecurity presents vulnerability, it is perhaps far easier to inspire a general sense of distrust in the process and its administration in places not near and around one's local area.
 

### 2025-02-28 docs/index.qmd
scripts

@@
 date-modified: today
-crossref:
-  custom: 
-    - key: hyp
-      kind: float
-      reference-prefix: H
-      latex-env: hypothesis # required for PDF format
+knitr: 
+  opts_chunk: 
+    dev: "ragg_png" # same as knitr::opts_chunk$set(dev = "ragg_png")
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
+set.seed(1234)
+
 # load packages
 library(tidyverse)
+library(easystats)
+library(patchwork)
 
 # load data
-load("data/research-paper-data-20241029.Rdata")
+load("data/research-paper-df-20250203.Rdata") #df
 
@@
 codebook <- read.csv("data/survey_codebook.csv")
-data_dict <- read.csv("data/data_dictionary.csv")
-
-# also load the raw data dict for comparison
-raw_spss_dict <- read.csv("data/raw_spss_dict.csv")
-```
-
-```{r}
-#| label: post_processing
-#| include: false
-
-# Some post-processing of the dataframe :::::::::::::::::::::::::::::::::::::###
-
-# recode factor levels 
-data <- data |> 
-  # use `pewmethods` to preserve order of factor levels
-  mutate(across(c(q19, q20, q21, q22, q23,q24, q25, q26,
-                  q30, q31, q32, q33, q34, q35, q36, q37), 
-                ~pewmethods::fct_case_when(
-    .x == "Not at all confident" |
-      .x == "Not at all committed" ~ "Not at all",
-    .x == "Not too confident" |
-      .x == "Not too committed"|
-      .x == "Not too concerned"|
-      .x == "Somewhat unconcerned" ~ "Not that much",
-    .x == "Somewhat confident" |
-      .x == "Somewhat committed" ~ "Somewhat",
-    .x == "Very confident" |
-      .x == "Very committed" ~ "Very",
-    TRUE ~ NA
-  )))
-
-# re-assign var labels to variables
-# To quickly assign the variable labels, first create a named vector via
-# deframe() with values as the variable labels and names as the variable names.
-data_labels <- data_dict |>
-  select(var, label_var) |> 
-  deframe()
-
-# Now assign the labels using the splice operator. Using the splice operator,
-# labels are assigned via matching against the variable name, which means that
-# variable order does not matter.
-data <- data |> 
-  labelled::set_variable_labels(!!!data_labels)
-
-```
-
-```{r}
-#| label: fns
-#| include: false
-
-source(here::here('src', 'funs.R'))
+df_dict <- read.csv("data/df_dictionary.csv")
 
@@
 
-## Design and Survey Measures
+## Theory and Hypotheses
 
-To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would improve trust in elections and ease election anxieties, a recent survey experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland.
+Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veterans and their family members to work as election staff and volunteers would boost public confidence in election administration.
+Indeed, that is the primary hypothesis of this study.
+Although citizens may vote in various ways across the country (e.g., by mail, ballot drop box, in-person), the simple announcement that election officials are engaging in efforts to recruit veterans to work as election staff may boost confidence in elections administration regardless of how, or whether, an individual plans to vote.
+Formally,
+
+> H~1~: Announcements that election officials are recruiting miilitary service veterans to work as election staff and volunteers will be associated with greater confidence in elections administration compared to announcements that do not mention military veterans.
+
+I considered that veterans would elicit high degrees of approval and support for whatever cause or issue presented.
+For example, I'd expect high approval and support for recruiting veterans to baseball teams just as much as for recruiting them to work as election staff.
+Likewise, asking participants whether they supported programs intent on recruiting anyone to work as election staff would garner support regardless of the target group.
+Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require a survey experiment designed to determine whether publicized recruitment efforts targeting veterans as a group would have any special effect on confidence in elections administration.
+
+Since the results and events following the 2020 election loomed large in anticipation of the U.S.
+2024 general elections, it is reasonable to take into account beliefs about legitimacy of the 2020 election.
+This group who denies the legitimacy of the 2020 election results were possibly the most distrusting of the 2024 election.
+However, given that veteran service members are held in high regard, generally speaking, announcing that veterans are being actively recruited to work as election staff and volunteers is expected to positively influence confidence in elections among those who remained firm in the belief that the 2020 election results were illegitimate.
+I take into account that legitimacy beliefs about the 2020 election and expectations of electoral fraud are related to partisanship and include partisanship as a control in the analysis.
+
+In addition, I expect that both expectations of electoral fraud and concerns for voter safety would lessen (shrink) when presented with information that veterans are being actively recruited to work and volunteer in election offices.
+
+Finally, prior research has shown that confidence that one's own vote would be counted as intended has been much stronger than confidence that votes nationwide would be treated likewise [@sances2015; @stewart2022].
+In other words, the public is more trusting of elections closer to home.
+Taking into account that confidence is lower for elections conducted outside of one's local area, then information that veterans are being recruited to help conduct elections in locations beyond one's locale may close this gap between confidence in elections within one's local area and confidence in elections elsewhere.
+Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone.
+Therefore, any observed disparity of confidence in elections (i.e., the "confidence gap") between elections within one's local area and elections beyond will be smaller when people are presented with information about election official recruitment efforts of veteran service members.
+
+## Experiment Design and Survey Measures
+
+To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would improve confidence in elections and ease insecurity, a recent experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland.
 The survey was fielded from August 29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287 U.S.
 citizens 18 years of age or older.
-Respondents were randomly split into either the treatment (n = 650) control (n = 637) conditions[^4].
+Respondents were randomly split into either the treatment ($n =$ 650) control ($n =$ 637) conditions[^4].
 
@@
 Beyond those small differences and the headlines, the article vignettes are identical.
-Any effects can be attributed to the information about veterans in the treatment vignette[^5].
+Therefore, effects can be attributed to the information about veterans in the treatment vignette[^5].
 
-It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignettes due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
+It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignette due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
+Because of this, treatment effects are potentially limited or constrained to attitudes concerning the location specified in the vignette.
 A block of survey items asked specifically about Maricopa County, AZ, followed by an identical block of items that asked the same questions about one's local area.
-Results between the items where the setting differs are compared and discussed.
-
-### Trust in Elections
+Later, I compare and discuss results between the items pertaining to different settings.
 
@@
 The items in this study, however, all inquire into confidence over one's expectations in anticipation of upcoming elections.
-In addition, other survey questionnaires ask similar questions that specifically contrast between a respondent's own local community, their state, and nationwide.
-This is in addition, or complementary to, items that distinguish between local area officials, state election officials, state government, and the U.S.
+In addition, other survey questionnaires ask similar questions that specifically contrast between a respondent's own local community, their state, and nationwide; this is in addition, or complementary to, items that distinguish between local area officials, state election officials, state government, and the U.S.
 federal government.
-The survey of this study, instead, focused on attitudes regarding election workers such as election officials, staff, and volunteers.
-As such, the items are utilized to comprise a component[^6] I broadly refer to as *trust in elections*.
+The survey of this study, instead, focused on attitudes regarding election workers such as election officials, staff, and volunteers specific to the location mentioned in the vignette---Maricopa County, AZ---as well as specific to one's local area[^6].
 
-A set of five survey items measured public trust in elections by inquiring into the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, as well as confidence that the voting process will be fair.
-The items measuring trust and confidence in elections include:
+The survey included items that assessed both trust in elections administration and expectations of electoral fraud, referred to simply as *trust* and *distrust*, respectively.
+Responses from these two sets of items were utilized to construct the primary dependent variable, *confidence in elections*.
 
-::: {#tbl-1}
-| **Trust in Elections** |
-|---|
-| How confident are you that votes in Maricopa County, AZ will be counted as voters intend in the elections this November?[^7] |
-| How confident are you that election officials, their staff, and volunteers in Maricopa County, AZ will do a good job conducting the elections this November? |
-| Think about the election staff and volunteers who handle the administration and conduct of elections in Maricopa County, AZ.
-How committed do you think they will be to making sure the elections held this November are fair and accurate?
-|
-| How confident are you that the voting process will be fair in Maricopa County, AZ? |
-| How confident are you that election systems in Maricopa County, AZ will be secure from hacking and other technological threats? |
-:::
+Prior to the reading the treatment or control vignette, participants responded to distinct survey items assessing one's favorability to local election officials ("In general, how favorable or unfavorable is your impression of local election officials?") and legitimacy of the 2020 election results ("Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected?").
+The former presented five response options from "Strongly favorable" to "Strongly unfavorable"; the latter item presented a binary of either "Legitimate" or "Not Legitimate".
 
-Each item in this series presented four response options from "Not at all [confident/committed]", "Not too [confident/committed]", "Somewhat [confident/committed]", and "Very [confident/committed]".
-In total, six survey items measure different aspects of trust and confidence in election administration.
-From these items, I generated a composite score for each respondent that represents their variable level of trust in elections.
+The conventional multiple item assessment of partisanship was included and used to construct a variable of partisanship consisting of three categories: Democrat, Republican, and Independent.
+In this case, Independents are "true" Independents in that they do not identify with either political party and do not "lean" toward either Republican or Democratic parties.
+Self-described "Independent leaners" are re-coded as falling into the partisan category in which they lean e.g., Independents who expressly report that they lean Republican are denoted as Republican.
 
-### Expecatation of Electoral Fraud
+Finally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
+The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^7].
 
-A series of five survey items captured *expectation of electoral fraud*.
-These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in Maricopa County, AZ?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
+### Trust and Distrust in Elections
 
-::: {#tbl-2}
-| **Expectation of Electoral Fraud** |
-|---|
-| There will be voter fraud, that is, people who are not eligible to vote will vote, or vote more than once |
-| Many votes will not actually be counted |
-| Many people will show up to vote and be told they are not eligible |
-| A foreign country will tamper with the votes cast in this area to change the results |
-| Election officials in Maricopa County, Arizona will try to discourage some people from voting |
-:::
+A set of five survey items measured public trust in elections by inquiring into the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, and confidence that the voting process will be fair.
+Each item in this series presented four response options from "Not at all \[confident/committed\]", "Not too \[confident/committed\]", "Somewhat \[confident/committed\]", and "Very \[confident/committed\]".
+In total, five survey items measure different aspects of trust in elections administration.
+The items measuring confidence in elections include:
 
-Similar to the items capturing trust in elections (@tbl-1), I computed a composite score for each respondent reflecting their expectations of electoral fraud.
+Another series of five survey items captured an individual's level of *distrust* in elections administration based on the extent to which they *expect electoral fraud* to occur.
+These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in \[Maricopa County, AZ/ your local area\]?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
+
+```{r}
+#| label: tbl-items
+#| tbl-cap: "Survey Items for Trust and Distrust in Elections"
+
+trust_txt <- df |> select(q19, q20, q21, q22, q24) |>
+  labelled::set_variable_labels(
+    q21 = "How commited do you think election staff and volunteers in Maricopa County, AZ will be to making sure the elections are fair and accurate?"
+  ) |> 
+  labelled::generate_dictionary() |> 
+  dplyr::as_tibble() |> 
+  select(Trust=label)
+
+distrust_txt <- df |> select(q28_1:q28_5) |>
+  labelled::generate_dictionary() |> 
+  dplyr::as_tibble() |> 
+  select(Distrust=label)
+
+conf_items_text <- trust_txt |> 
+  mutate(Distrust = pull(distrust_txt))
+
+kableExtra::kbl(conf_items_text, booktabs = T,
+                col.names = c("Trust", "Distrust"),
+                linesep = "\\addlinespace") |> 
+  kableExtra::kable_styling(full_width = T,
+                            font_size = 8,
+                            latex_options = c("HOLD_position")) |> 
+  kableExtra::column_spec(column = 1:2, width = "8cm")
+
+```
+
+Similar to the items capturing trust in elections (@tbl-items), I computed a summated score for each respondent reflecting the extent of their distrust in elections.
+
+Upon construction of the two summated scales of *trust* and *distrust*, internal consistency reliability coefficient $\alpha$ were estimated for both and found to be adequate ($\alpha$ \> 0.8); the trust in elections scale $\alpha$ = 0.93 and the distrust scale $\alpha$ = 0.86.
+In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each.
+
+I expected item responses from these two scales to be inversely correlated among the sample, but not mutually exclusive.
+Indeed, this is what I find.
+Polychoric correlations between the trust and distrust items negatively correlate as expected\[\^See Appendix C\], as does the correlation between the two sum score scales.
+Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
+The negative correlation between the trust and distrust items and scores makes intuitive sense.
 
@@
 
-The outcome of interest concerns both public trust in election administration and the expectation of electoral fraud.
-Because these variables are assessed by multiple Likert items, conventional methods call for combining the items of each set into separate Likert scales, also known as a summated rating scales.
-However, many of the items comprising the trust scale directly oppose items capturing expectations of electoral fraud.
-For instance, one item has the respondent report their confidence that votes will be counted as voter's intend; whereas a contrasting item has the the respondent report their expectation that many votes will not be counted.
-These two items directly oppose each other, but there's no guarantee that individual responded as such.
+The primary outcome of interest concerns public confidence in elections administration compensated by one's distrust in elections, i.e., their expectations of electoral fraud.
+Because trust and distrust are assessed by multiple Likert items, conventional methods call for combining the items of each set into separate Likert scales (also known as summated rating scales).
+Since the item response options are not symmetric---i.e., not bipolar with contrasting positive and negative response options to include a neutral middle option---then the *trust in elections* scale could only be understood as a measure of trust in the positive use of the term (i.e., unipolar).
+Likewise, the expectation of fraud items fit to a scale that corresponds to a unipolar measure of confident *distrust*, so to speak.
+However, many of the items comprising the trust scale directly oppose items capturing distrust.
+For instance, one item from the trust scale has the respondent report their confidence that votes will be counted as voter's intend, whereas a separate item from the distrust scale has the the respondent report their expectation that many votes will not be counted.
+Positive responses to these two items directly contradict each other, and would thus cancel out.
 
-Since many of the items are not symmetric---i.e., response options are not bipolar with contrasting positive and negative response options---then a "trust in elections" scale could only be understood as a measure of trust in the positive use of the term (i.e., unipolar).
-Likewise, the expectation of fraud items fit to a scale that corresponds to a unipolar measure of *confident distrust* so to speak.
+The relationship is that trust and distrust represent opposing degrees of confidence along the same spectrum.
+However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling similarly confident in both respects.
+Accordingly, equivalent degrees of trust and distrust cancel out, rendering one relatively more *insecure* about their expectations of the future despite the fact that they may feel confident in either direction.
+When trust and distrust are considered as reflective of one's confidence about future expectations, then both can be placed along the same spectrum.
+Therefore, a lack of confidence denotes insecurity.
 
-I would expect composite sum or mean scores, and item responses, on these two measures to be inversely correlated among the sample, but not mutually exclusive.
-Indeed, this is what I find.
-Upon construction of the two multi-item composite scales of *trust in elections* and *expectation of fraud*, internal consistency reliability coefficient $\alpha$ were estimated for both and found to be adequate ($\alpha$ > 0.8); the trust in elections scale $\alpha$ = 0.93 and the expectation of electoral fraud scale $\alpha$ = 0.86.
-In other words, the items in each of the scales were intercorrelated well enough to compose a single scale of a (presumed) unidimensional construct.
-I then plotted separate histograms of scores across the sample to visualize the distribution for each seen in @fig-dist.
-Note that for both scales, higher values indicate less expectation of electoral fraud and greater trust in elections, respectively.
+Something may cause a person to have greater expectations that election fraud will occur, which in turn will always lower their trust in elections administration.
+In contrast, a person may feel a bit more confident in the integrity of elections, but this confidence is constrained by the extent to which they expect election fraud to occur.
+This means that a person's baseline level of confidence in elections admin must take into account their present degree of distrust---i.e., their expectations of electoral fraud.
+
+Those who are, or are close to being, equally confident in both directions would be the most *insecure* about their expectations.
+Having no trust in elections and no expectation that electoral fraud will occur is functionally equivalent to having equal degree of both.
+Quite literally, this reflects an uncertain feeling of "it could go one way or the other" with respect to the integrity of elections administration.
+Operationally, this would reflect a middling point on a scale of *confidence*.
+
+In light of this, I reverse coded positive expectations of electoral fraud and added responses from the distrust scale to the trust in elections scale.
+That is, item responses on the trust scale ranged from 0 ("Not confident at all") to 3 ("Very confident), whereas responses on the distrust scale ranged from 0 ("Not likely at all") to -3 ("Very likely").
+Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^8].
+On this scale, positive values reflect higher confidence in elections, negative values reflect greater distrust, and values closer to zero correspond to an individual's degree of insecurity.
+
+The advantage is that this permits a better test of the treatment effect as theorized.
+Of course, it is easy enough to examine the effect of the treatment on both trust and distrust separately.
+However, the theory presents a hypothesis that the treatment will impose influence upon both variables *concurrently and in a positive direction* with respect to the relationship between trust and distrust.
+That is to say, confidence increases insofar as trust in elections increases and distrust decreases; since distrust detracts from trust, then an accurate measure of confidence must take that constraint into account.
+
+## Results
+
+I first review responses to the survey items capturing trust and distrust separately by treatment condition.
+When distinguished by experiment condition, trust in elections admin is noticeably higher for those who read the treatment vignette.
+The difference is more pronounced for some items over others.
+That being said, there is a definite distinction between items pertaining to Maricopa County, AZ compared to items that pertain to a respondent's local area.
+In fact, the treatment appears to have hardly made a difference when the items concerned one's local area.
+
+```{r}
+#| label: fig-trustlikert
+#| fig-cap: "Trust in Election Administration by Experiment Condition"
+#| fig-height: 4.5
+#| fig-pos: "h"
+
+# Likert plot of trust and confidence in election admin comparing treatment and
+# control groups
+trust.likert.treat.az <- df |>
+  # relabel factor labels for plotting
+  mutate(across(
+    c(q19, q20, q21, q22, q23, q24, q30, q31, q32, q33, q34, q35),
+    ~ pewmethods::fct_case_when(
+      .x %in% c("Not at all confident", "Not at all committed") ~ "Not at all confident",
+      .x %in% c("Not too confident", "Not too committed") ~ "Not too confident",
+      .x %in% c("Somewhat confident", "Somewhat committed") ~ "Somewhat confident",
+      .x %in% c("Very confident", "Very committed") ~ "Very confident",
+      TRUE ~ NA
+    )
+  )) |>
+  ggstats::gglikert(
+    include = c(q19, q20, q21, q22, q24),
+    y = 'group',
+    facet_rows = vars(.question),
+    symmetric = F,
+    labels_size = 2.5,
+    add_totals = T
+  ) +
+  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+  # ggplot2::scale_fill_brewer(palette = "Greys")+
+  labs(subtitle = str_wrap("Maricopa County, Arizona", width = 95)) +
+  theme_bw() +
+  theme(
+    text = element_text(family = "Palatino Linotype"),
+    legend.position = 'bottom',
+    axis.text.x = element_blank(), # remove percentage text along x-axis
+    strip.text.y.right = element_blank()
+  )
+
+# confidence in elections between experiment conditions for items concerning local area
+trust.likert.treat.lcl <- df |>
+  # relabel factor labels for plotting
+  mutate(across(
+    c(q19, q20, q21, q22, q23, q24, q30, q31, q32, q33, q34, q35),
+    ~ pewmethods::fct_case_when(
+      .x %in% c("Not at all confident", "Not at all committed") ~ "Not at all confident",
+      .x %in% c("Not too confident", "Not too committed") ~ "Not too confident",
+      .x %in% c("Somewhat confident", "Somewhat committed") ~ "Somewhat confident",
+      .x %in% c("Very confident", "Very committed") ~ "Very confident",
+      TRUE ~ NA
+    )
+  )) |>
+  ggstats::gglikert(
+    include = c(q30, q31, q32, q33, q35),
+    y = 'group',
+    facet_rows = vars(.question),
+    variable_labels = c(
+      q30 = "Votes counted as intended",
+      q31 = "Election officials will do good job",
+      q32 = "Election workers will be committed",
+      q33 = "Voting process will be fair",
+      q35 = "Election technology will be secure"
+    ),
+    facet_label_wrap = 10,
+    labels_size = 2.5,
+    symmetric = F,
+    add_totals = T
+  ) +
+  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+  # ggplot2::scale_fill_brewer(palette = "Greys")+
+  labs(subtitle = str_wrap("Local Area", width = 95)) +
+  theme_bw() +
+  theme(
+    text = element_text(family = "Palatino Linotype"),
+    legend.position = 'bottom',
+    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
+    axis.text.x = element_blank(), # remove percentage text along x-axis
+    strip.text.y.right = element_text(angle = 0, size = 8)
+  )
+
+# trust.likert.treat.az
+# trust.likert.treat.lcl
+
+# Instead of two separate plots, arrange into one plot while remaining separated
+# use `ggpubr` package to print multiple plots side-by-side (or alt. row-by-row)
+ggpubr::ggarrange(
+  trust.likert.treat.az,
+  trust.likert.treat.lcl,
+  ncol = 2,
+  common.legend = T,
+  legend = "bottom", 
+  font.label = list(family = "Palatino Linotype")
+) +
+  # add figure footnote annotation
+  patchwork::plot_annotation(
+    caption = str_wrap("Missing values removed. Displays percent proportions of responses by experiment condition and combined percentage proportions for two categories.",
+               width = 85), theme = theme(text = element_text(family = "Palatino Linotype")))
+
+```
+
+Reviewing item responses distinguished by treatment condition reveals particulars of the treatment effect (@fig-trustlikert).
+Among the items that asked about Maricopa County, AZ, it is a bit easier to see upon which items the treatment vignette had the greatest effect.
+It appears that the main effect of the treatment is upon responses to the item that measures confidence in the security of election technology.
+
+Regarding confidence in the commitment of election staff and volunteers, a higher proportion of respondents in the treatment group selected "Very confident" over "Somewhat confident" compared to the control group, but only for items concerning Maricopa County, AZ.
+Although confidence in election workers was generally high across the board, the shift from "Somewhat" to "Very" confident for items pertaining to election worker *commitment* to fairness and accuracy seems to clearly speak to the group being recruited, i.e., veterans and family members.
+However, the same visible shift in proportion from "Somewhat" to "Very" confident isn't observed when items asked about one's local area, which undermines the suggestion that the treatment effect can be cleanly attributed to respondent's feelings about veteran service members and their families.
+It may be the case that respondents harbor particular attitudes or sentiment about Maricopa County, AZ itself, or there may be nothing uniquely special about Maricopa County, AZ supposing that elections anywhere beyond one's local area generally garner slightly less confidence.
+
+What this does suggest, however, is that trust in the fairness and accuracy of the electoral process is notably higher upon the notion that military veterans will be directly engaged as election staff and volunteers in places where such trust falters.
+The question turns to whether this also lowers distrust, or the extent to which one expects electoral fraud to occur.
+
+```{r}
+#| label: fig-distrustlikert
+#| fig-cap: "Disrust in Election Administration by Experiment Condition"
+#| fig-height: 4.5
+#| fig-pos: "h"
+
+# distrust in elections in AZ by experimental condition
+distrust.likert.az <- df |>
+  # reverse levels of factor vars to show positive difference in "not likely"
+  mutate(across(c(q28_1:q28_5), ~forcats::fct_rev(.))) |> 
+  ggstats::gglikert(
+    include = c(q28_1:q28_5),
+    y = 'group',
+    facet_rows = vars(.question),
+    variable_labels = c(
+      q28_1 = "Voter fraud will occur",
+      q28_2 = "Many votes won't be counted",
+      q28_3 = "Many voters will be turned away",
+      q28_4 = "Foreign Interference",
+      q28_5 = "Election officials will discourage voting"),
+    facet_label_wrap = 10,
+    labels_size = 2.5,
+    symmetric = F,
+    add_totals = T
+  ) +
+  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+  # ggplot2::scale_fill_brewer(palette = "Greys")+
+  labs(subtitle = str_wrap("Maricopa County, Arizona", width = 95)) +
+  theme_bw() +
+  theme(
+    text = element_text(family = "Palatino Linotype"),
+    legend.position = 'bottom',
+    axis.text.x = element_blank(), # remove percentage text along x-axis
+    strip.text.y.right = element_blank()
+  )
+
+# distrust in elections in Local area by experimental condition
+distrust.likert.lcl <- df |>
+  # reverse levels of factor vars to show positive difference in "not likely"
+  mutate(across(c(q40_1:q40_5), ~forcats::fct_rev(.))) |> 
+  ggstats::gglikert(
+    include = c(q40_1:q40_5),
+    y = 'group',
+    facet_rows = vars(.question),
+    variable_labels = c(
+      q40_1 = "Voter Fraud will occur",
+      q40_2 = "Many Votes won't be counted",
+      q40_3 = "Many voters will be turned away",
+      q40_4 = "Foreign Interference",
+      q40_5 = "Election officials will discourage voting"),
+    facet_label_wrap = 10,
+    labels_size = 2.5,
+    symmetric = F,
+    add_totals = T
+  )+
+  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+  # ggplot2::scale_fill_brewer(palette = "Greys")+
+  labs(subtitle = str_wrap("Local Area", width = 95)) +
+  theme_bw() +
+  theme(
+    text = element_text(family = "Palatino Linotype"),
+    legend.position = 'bottom',
+    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
+    axis.text.x = element_blank(), # remove percentage text along x-axis
+    strip.text.y.right = element_text(angle = 0, size = 8)
+  )
+
+# Instead of two separate plots, arrange into one plot while remaining separated
+# use `ggpubr` package to print multiple plots side-by-side (or alt. row-by-row)
+ggpubr::ggarrange(
+  distrust.likert.az,
+  distrust.likert.lcl,
+  ncol = 2,
+  common.legend = T,
+  legend = "bottom", 
+  font.label = list(family = "Palatino Linotype")
+) +
+  # add figure footnote annotation
+  patchwork::plot_annotation(
+    caption = str_wrap("Missing values removed. Displays percent proportions of responses by experiment condition and combined percentage proportions for two categories.",
+               width = 85), theme = theme(text = element_text(family = "Palatino Linotype")))
+
+```
+
+Similar to the trust scale items, the items on the distrust scale were associated with lower distrust in the treatment condition compared to the control.
+A quick glance at @fig-distrustlikert shows what appears to be a significant reduction in distrust, especially regarding the expectations that many votes wouldn't be counted, many voters would be turned away, and that election officials would discourage voters from casting a ballot.
+Interestingly, the expectation that there would be foreign interference in elections in Maricopa County, AZ were pretty resilient against the treatment.
+And again, responses for items pertaining to elections in one's local area are practically indistinguishable between treatment and control.
+
+### Confidence in elections
+
+Once trust and distrust were composed into unified variable of confidence in elections, I then examined distribution of the dependent variable followed by analysis of the effect of the treatment by comparison of mean differences between experiment conditions.
+Recall that on this scale, zero reflects insecurity (e.g., similar or equal values of trust and distrust), whereas values diverging from zero reflect confidence in either direction, trust or distrust respectively.
+Positive values reflect trust in elections administration (e.g., elections will be fair and accurate), whereas negative values reflect distrust in elections (i.e., expectation that election fraud will occur).
+To retain a meaningful zero, I rescaled the sum scores to range from -3 to 3[^9] and then superimposed two histograms of confidence scores: one derived from AZ items and another for scores derived from local area items.
+Doing this is illustrative of the relative distribution of confidence that differed depending on the location of elections referred to in the survey items (e.g., Maricopa County, AZ).
+
+As revealed by review of the item responses, the distribution of confidence differed depending on whether survey items pertained to elections in Maricopa County, AZ, or elections within one's local area.
 
@@
 #| label: fig-dist
-#| fig-cap: "Histograms of Composite (mean) Scores for Trust in Elections And Expectation of Electoral Fraud"
+#| fig-cap: "Overlapping Distribution of Confidence in Elections for AZ and Local Area"
+#| fig-pos: "H"
 
-# trust scores are not normally distributed, bi-modal, neg skew
-trst.scores.hist <- ggplot(data, aes(trst.mean.scores))+
-  geom_histogram(aes(y = after_stat(density)), bins = 15,
-                 color = 1, fill = "grey")+
-  geom_density(lwd = 1.5, color = 1, fill = 1, alpha = 0.35)+
-  geom_segment(x = round(mean(data$trst.mean.scores), 2), y = 0, yend = 0.80, color = "red")+
+ggplot(df) +
+  geom_histogram(
+    aes(x = conf.az.rescaled , y = after_stat(density)),
+    bins = 15,
+    alpha = 0.2,
+    color = 1,
+    fill = "red"
+  ) +
+  geom_histogram(
+    aes(x = conf.lcl.rescaled , y = after_stat(density)),
+    bins = 15,
+    alpha = 0.2,
+    color = 1,
+    fill = "blue"
+  ) +
+  geom_segment(
+    x = round(mean(df$conf.az.rescaled), 2),
+    y = 0,
+    yend = 0.35,
+    color = "firebrick",
+    lwd = 1.4,
+    linetype = 2
+  ) +
+  geom_segment(
+    x = round(mean(df$conf.lcl.rescaled), 2),
+    y = 0,
+    yend = 0.35,
+    color = "darkblue",
+    lwd = 1.4,
+    linetype = 2
+  ) +
+  annotate(
+    "text",
+    x = round(mean(df$conf.az.rescaled), 2),
+    y = 0.40,
+    label = paste("AZ =", round(mean(
+      df$conf.az.rescaled
+    ), 2), "(", round(sd(
+      df$conf.az.rescaled
+    ), 2), ")"),
+    color = "firebrick"
+  ) +
+  annotate(
+    "text",
+    x = round(mean(df$conf.lcl.rescaled), 2),
+    y = 0.43,
+    label = paste("Local area =", round(mean(
+      df$conf.lcl.rescaled
+    ), 2), "(", round(sd(
+      df$conf.lcl.rescaled
+    ), 2), ")"),
+    color = "darkblue"
+  ) +
   labs(
-    x = "Trust in Elections Mean Scores",
+    x = str_wrap("Confidence", width = 85),
     y = "Density",
-    caption = "mean = 3.09, sd = 0.69, median = 3.0, skew = -0.67, kurtosis = 0.25"
-  )+
-  annotate("text", x = round(mean(data$trst.mean.scores), 2), y = 0.85,
-           label = paste("mean =", round(mean(data$trst.mean.scores), 2)), color = "red")
+    caption = str_wrap(
+     "Mean (std.deviation). Mean difference = 0.33, CI [0.27, 0.38], t = 11.613, df = 1286, p < 0.01",
+     width = 95)) +
+  theme_bw(base_family = "Palatino Linotype")
 
-# eef scores are not normally distributed, also bi-modal pos skew
-eef.scores.hist <- ggplot(data, aes(eef.mean.scores))+
-  geom_histogram(aes(y = after_stat(density)), bins = 15,
-                 color = 1, fill = "grey")+
-  geom_density(lwd = 1.5, color = 1, fill = 1, alpha = 0.35)+
-  geom_segment(x = round(mean(data$eef.mean.scores), 2), y = 0, yend = 0.80, color = "red")+
-  labs(
-    x = "Exp. of Electoral Fraud Mean Scores",
-    y = "Density",
-    caption = "mean = 2.27, sd = 0.75, median = 2.2, skew = 0.19, kurtosis = -0.55"
-  )+
-  annotate("text", x = round(mean(data$eef.mean.scores), 2), y = 0.85,
-           label = paste("mean =", round(mean(data$eef.mean.scores), 2)), color = "red")
-
-# place plots side by side
-gridExtra::grid.arrange(eef.scores.hist, trst.scores.hist, ncol = 2)
 ```
 
-Given the non-normal (or at least un-equal skew of the) distribution of the two scale scores and ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho$ -0.49 (Kendall's \tau = -0.39) between summated scores on the two scales.
+Overall, the sample expressed more trust in elections relative to distrust seeing as how the distribution of confidence is largely positive (@fig-dist).
+However, there's a clear difference between confidence in Maricopa county, AZ elections and elections within one's local area.
+A paired t-test confirms that this difference was statistically significant, though somewhat small (mean difference $= 0.325$, $95\%$ CI $[0.27, 0.38]$, $t(1286) = 11.61$, $p < .001$).
+Nonetheless, respondents appeared less confident regarding elections in Maricopa County, AZ, but held more confidence in elections administration in their local area.
+This complements previous research that demonstrates a similar bias favorable to one's local area [@stewart2022].
 
-The negative correlation between the items and the composite scores makes sense.
-Theoretically speaking, a person who is certain that electoral fraud will occur clearly lacks trust in the election.
-That is, expectation of electoral fraud does imply lack of trust in elections.
-However, the reverse isn't also necessarily true; it is reasonable to hold a degree of trust in elections alongside expectations that electoral fraud will occur.
-Holding both considerations isn't necessarily an example of cognitive dissonance, as a lack of confidence in elections doesn't necessarily imply an expectation of electoral fraud.
-A lack of trust in elections might render one open to potentialities, but expectation of fraud is in no way necessitated by lacking trust in elections.
-When considered along a spectrum, both can be considered as degrees of *confidence*; and in the absence of confidence, insecure.
+Accordingly, when confidence levels are distinguished by experiment condition, the treatment vignette only had an effect upon survey items pertaining to elections in Maricopa County, AZ.
+Conducting an independent samples t-test (i.e., Welch Two Sample t-test) suggests that the effect of the treatment compared to the control condition is positive, statistically significant, yet substantially pretty small.
 
-Accordingly, those whose responses to the "trust in elections" items would be cancelled out by their responses to the "expectation of fraud" items.
-Those who are, or are close to being, equally confident in both directions would be the most *insecure* about their expectations[^Insecure in terms of their confidence.
-Not insecure as to imply some anxious or concerned affect.].
-Having no trust in elections and no expectation that electoral fraud will occur is functionally equivalent to having equal degree of both.
-Quite literally, an uncertain feeling of "it could go one way or the other".
-Operationally, this would reflect a middling 0 on a scale of *confidence*.
-Seeing as how expectation of electoral fraud is also a level of confidence, then it is reasonable to place all items onto a symmetric scale where positive values represent trust in elections and negative values represent expectation of electoral fraud.
+```{r}
+#| label: tbl-ttest
+#| tbl-cap: "Mean Difference Effect of Treatment Compared to Control Condition"
+#| tbl-pos: H
 
-The primary dependent variable is *confidence in elections*, which reflects one's trust in election administration minus their expectations of electoral fraud.
-Operationally, the dependent variable is a linear composite scale of item responses across items measuring trust in elections and expectations of electoral fraud re-scaled to range from -3 to 3.
-Items comprising trust in elections were positively coded to range from 0 "Not at all confident/committed" to 3 "Very confident/committed".
-Likewise, items capturing expectation of electoral fraud were coded negatively to range from 0 "Not likely at all" to -3 "Very likely".
+# conduct two t-tests using `rstatix::t_test`, bind results by row, and pipe
+# into table
+dplyr::bind_rows(
+  df |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
+  rstatix::t_test(formula = conf.az.rescaled ~ group,var.equal = F,detailed = T),
+  df |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
+  rstatix::t_test(formula = conf.lcl.rescaled ~ group,var.equal = F, detailed = T)
+  ) |> 
+  # specify columns and column names
+  select(
+    Diff = estimate,
+    treat_mean = estimate1,
+    control_mean = estimate2,
+    treat_n = n1,
+    control_n = n2,
+    t = statistic,
+    p, df, conf.low, conf.high) |> 
+  mutate(
+    Place = dplyr::case_when(
+      p <= 0.05 ~ "Maricopa County, AZ", 
+      p > 0.05 ~ "Local Area"), 
+    .before = Diff) |> 
+  insight::format_table(stars = T) |> 
+  # insight::export_table(format = "md") # alternate
+  # output table as `kable` for LaTeX pdf
+  kableExtra::kbl( 
+    booktabs = T,
+    col.names = c("Place", "$\\bar{x}_{diff}$", "$\\bar{x}_{treat}$", "$\\bar{x}_{control}$",
+                  "$treat_{n}$", "$control_{n}$", "t", "p", "df", "CI"), 
+    escape = F) |> 
+  kableExtra::footnote(general = "Welch Two Sample t-tests of difference between Confidence in Elections by Treatment Condition.") |> 
+  kableExtra::kable_styling(
+    font_size = 9, 
+    protect_latex = T)
 
-Computed mean or sum scores for multiple Likert items are commonly acceptable, as they are relatively robust in spite of violating assumptions of a normal distribution of data (or residuals).
-due to the somewhat non-normal distribution of the sum or mean scores and the ordinal nature of the variable items, an ordered regression analysis is preferred.
+```
 
-The primary independent variable is the prospect of military veterans as election workers (i.e., staff or volunteers).
+The results of @tbl-ttest show that, on a scale ranging from -3 to 3, the effect of the treatment is associated with a $0.20$ average difference in confidence in elections in Maricopa County, AZ, compared to the control group.
+When the dependent variable is centered to have a mean of $0$ and standard deviation of $1$, standardized parameters permit interpretation of the treatment effect in terms of standard deviations; the standardized difference in confidence between treatment and control is $0.16$ (CI $[0.06, 0.27]$).
+Nothing is more illustrative than graphs and lines, however.
 
-## Results
+```{r}
+#| label: fig-coef1
+#| layout-nrow: 2
+#| fig-height: 3.5
+#| fig-cap: "Confidence in Elections by Experiment Condition"
+#| fig-subcap: 
+#|   - "Confidence by Treatment Condition"
+#|   - "Trust and Distrust by Treatment Condition"
 
-The key question is whether trust in elections (or voter confidence) is response to the treatment vignette.
+# coef plot of treatment effect on confidence distinguished by location
+conf.coef1 <- jtools::plot_summs(
+  lm(conf.az.rescaled ~ group, data = df), 
+  lm(conf.lcl.rescaled ~ group, data = df), 
+  center = T, scale = T, transform.response = T,
+  model.names = c("Conf.AZ", "Conf.Local"),
+  coefs = c("Treatment" = "groupTreatment"), 
+  colors = c("red", "black"),
+  point.shape = c(8, 1))+
+  ggplot2::expand_limits(x = c(-0.25, 0.25))+
+  labs(y = "")+
+  theme_bw(base_family = "Palatino Linotype")
 
-Note that the question wording for the survey items derived from the 2022 SPAE are modified slightly but substantially.
-The question wording in this study is most similar to those in 2022 SPAE that assess confidence that votes will be counted as voters intend without specific reference to their own vote (e.g., in their county, state, or nationwide).
-In this study, two survey items ask about confidence in vote counts in one specific county in Arizona and another referencing their local community.
-Moreover, the 2022 SPAE includes "I don't know" as a response option, whereas the comparable item in this study did not include a "don't know" response option.
-Comparison between responses to the two similar items was conducted....
+# Coef plots of trust and distrust models for AZ and Local items
+conf.coef2 <- jtools::plot_summs(
+  lm(trust.scores.az ~ group, data = df),
+  lm(distrust.scores.az ~ group, data = df),
+  lm(trust.scores.lcl ~ group, data = df),
+  lm(distrust.scores.lcl ~ group, data = df),
+  center = T, scale = T, transform.response = T,
+  model.names = c("Trust.AZ", "Distrust.AZ", "Trust.Local", "Distrust.Local"),
+  coefs = c("Treatment" = "groupTreatment"),
+  colors = c("red", "red", "black", "black"),
+  point.shape = c(8, 8, 1, 1)
+)+
+  ggplot2::expand_limits(x = c(-0.25, 0.25))+
+  labs(y = "")+
+  theme_bw(base_family = "Palatino Linotype")
+
+conf.coef1
+conf.coef2
+
+```
+
+@fig-coef1 displays standard difference estimates of confidence in elections by treatment condition (control condition as reference).
+@fig-coef1-1 displays two models for confidence in elections in Maricopa County, AZ, and one's local area by treatment condition; @fig-coef1-2 displays four models for trust and distrust in elections in AZ or one's local area by treatment condition.
+These figures merely illustrate the effect of the treatment with respect to the relationship between trust and distrust; ultimately confidence improves.
+
+Confidence in elections was higher among those who read the treatment vignette but remained conditional on whether the survey questions inquired about elections in Maricopa County, AZ.
+This evidence suggests that announcing efforts to recruit veterans and their families to work as election staff and volunteers may increase confidence in elections administration in places outside of one's local area, but may not boost confidence in elections within one's local area.
+
+I now turn to results examining those who held onto the belief that the 2020 election results were illegitimate.
+I think check to see if recruiting veterans simply makes people feel safer at the polls.
 
@@
 
+Bear in mind that confidence in elections for one's local area is already higher than for those beyond.
+Thus, there's already more insecurity concerning elections elsewhere for whatever reason.
+In the anticipatory period prior to national elections, publicized efforts to recruit veterans to work as election staff and volunteers may be a small, but positive, step towards reducing insecurity in elections that occur elsewhere.
+Especially among those who maintained a steadfast degree of distrust in elections.
+Despite a lack of evidence that systematic electoral fraud had occurred in the 2020 election, a substantial proportion of the population were unwilling to affirm the legitimacy of the results.
+However, despite such legitimacy beliefs, most were not consistent as they expressed varying levels of trust in different aspects of elections administration.
+
 ### Limitations
 
-* limitations: interpretations of the treatment effect are limited.
-  + The sample may not be generalizable to the population.
-  + It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts.
-* Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
-* Moreover, results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons.
+As far as I'm aware, both the items, their wording, and their composition into measurement scales are unique to this study.
+This renders the composite scores for trust in elections sample dependent and limits comparability with other cross-sectional survey data.
+
+-   limitations: interpretations of the treatment effect are limited.
+    -   The sample may not be generalizable to the population.
+    -   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts.
+-   Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
+-   Moreover, results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons.
 - First, the vignettes and many survey questions ask about Maricopa County, AZ specifically.
@@
 The proportion of true Independents was 12.78%.
-
-::: {.content-visible when-format="html" unless-format="pdf"}
-```{r}
-#| label: tbl-desc
-#| tbl-cap: "Demographics and Balance"
-#| tbl-cap-location: top
-
-# quick, informative, easy table of sample demographics w/ some other questions.
-# best method for html document
-tbl.desc <- data |>  
-  labelled::set_variable_labels(
-    age_4cat = "Age group, in years",
-    gender_3cat = "Gender",
-    race2 = "Race/Ethnicity",
-    educ_4cat = "Education",
-    partyid_3cat = "Party ID"
-  ) |> 
-  gtsummary::tbl_summary(
-    by = group,
-    include = c(
-    age_4cat, 
-    gender_3cat, 
-    race2, 
-    educ_4cat, 
-    partyid_3cat),
-    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
-    missing = "ifany",
-    missing_text = "NA") |> 
-  gtsummary::add_n() |> 
-  gtsummary::add_overall() |> 
-  gtsummary::modify_header(label = "**Variable**") |> 
-  gtsummary::bold_labels()
-
-gtsummary::as_gt(tbl.desc) |>  
-  gt::tab_footnote(
-    footnote = "Independents do not identify nor 'lean' toward either political party",
-    placement = "left"
-    ) |>  
-  gt::cols_align(align = 'left', columns = everything()) |> 
-  gt::tab_options(
-    table.font.size = "small",
-    data_row.padding = gt::px(1)
-  )
-
-```
-:::
-
-There should be nothing below here
-
-::: {.content-hidden unless-format="pdf"}
-```{r}
-#| label: tbl-desc-pdf
-#| tbl-cap: "Demographics and Balance"
-#| tbl-cap-location: top
-
-gtsummary::as_gt(tbl.desc) |>  
-  gt::tab_footnote(
-    footnote = "Independents do not identify nor 'lean' toward either political party",
-    placement = "left"
-    ) |>  
-  gt::cols_align(align = 'left', columns = everything()) |> 
-  gt::tab_options(
-    table.font.size = "small",
-    data_row.padding = gt::px(1)
-  )
-
-```
-
-:::
 
@@
 
-[^3]: Note that *electoral anxiety* is used in place of electoral trust/confidence simply to emphasize the anticipatory nature of the attitudes in question.
-Election anxiety is not taken to be the inverse of trust and confidence.
-A lack of trust does not necessarily imply (a state of) anxiety.
+[^3]: Note that election insecurity is used in place of electoral confidence simply to emphasize the anticipatory nature of the attitudes in question.
+Election insecurity is taken to denote a lack of confidence.
 
@@
 
-[^6]: The methodological concerns between the use of (unit weighted) sum scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
-The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024].
+[^6]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
+
+[^7]: Survey item wording and responses are included in Appendix A.
+
+[^8]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
+The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024], yet there is no general consensus on the most appropriate method generally.
 The use of either appears to largely depend on the researcher's particular research objective, theoretical suppositions, and necessity.
@@
 
-[^7]: Note a lack of confidence that votes will be counted as voters intend does not imply an expectation of electoral fraud.
-The reason for one's lack of confidence is uncertain, which makes it suitable as a survey item to measure the presence of trust in election administration rather than an expectation of fraud.
+[^9]: This range is mostly arbitrary, as a range from -1 to 1 works much the same.
+When relying on simple sum total score, the scale ranges from -15 to 15.
+So a single point increase from 0 to 1 may reflect a combination of a single "Very confident" response on a trust item compensated by a single "Somewhat likely" response on a distrust item (i.e., 3-2 = 1), or some other equivalent combination.
+Although the use of mean scores would place scores back onto the response scale metric (e.g., from 0 to 3, reflective of "not at all" to "very"), this results in a unipolar scale (from 0 to 3).
+The bipolar scale resulting from the composition of positive trust and negative distrust engenders meaning to zero and negative values.
+As such, composite mean scores become inappropriate and interpretation of scores would no longer be feasible.
+In other words, negative values on the scale for confidence in elections hold substantive meaning (e.g., distrust, absent trust), which makes transforming scores to fit a unipolar scale inappropriate.

### 2025-02-28 docs/src/01-data.R

@@ -1,0 +1,909 @@
+# using data exported from Qualtrics on 2024-10-23
+# The most recent (i.e., last) response was recorded 2024-09-18 at 6:40pm (1840)
+# When exporting the data, Qualtrics allows me to recode 'seen but unanswered'
+# questions with code 99. I downloaded the data again just for that because I
+# want to see how many of the missing values in my 2024-09-11 dataset are
+# attributed to people who skipped survey questions.
+
+# load packages ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
+library(tidyverse)
+library(haven)
+library(surveytoolbox)
+library(labelled)
+library(sjlabelled)
+
+# load data ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
+
+# load raw SPSS export (includes display order vars)
+# downloaded on 2024-10-29 at 12:02 PM
+raw_spss <- haven::read_sav("data-raw/VMF_Election_Worker_Recruitment_Survey_with_display_order_20241029_T12.02.sav")
+
+# load raw SPSS export (doesn't include display order vars)
+# downloaded 2024-10-23 at 1:54 PM
+# raw_spss3 <- haven::read_sav(file = "data-raw/VMF_Election_Worker_Recruitment_Survey_2024-10-23_13.54.sav")
+
+# despite being a .sav file imported using `haven::read_sav()`, 
+# the data set is not "haven_labelled"
+# haven::is.labelled(raw_spss)
+
+# create data dictionary of raw SPSS data set ::::::::::::::::::::::::::::::####
+
+# A data dictionary contains metadata about the data. The
+# `labelled::generate_dictionary` function is used to create a data
+# dictionary. (alt. `surveytoolbox::data_dict`)
+# a data frame is loaded into the R environment with the number of
+# observations equal to number of variables in the original data set.
+# NOTE: surveytoolbox::data_dict function is used here because the resulting
+# dataframe can be saved as a .csv
+raw_spss_dict <- raw_spss |> surveytoolbox::data_dict()
+
+# save data dictionary of raw_spss dataset download
+write.csv(raw_spss_dict, file = "data/raw_spss_dict.csv")
+
+# create and save survey codebook ::::::::::::::::::::::::::::::::::::::::::####
+
+# this includes only the survey questions: question number (var), the question
[…]

### 2025-02-28 src/02-data-postprocessing.R

@@ -21,10 +21,11 @@ df <- data |>
     race_wnw,       # race dichotomous between White and Non-White
     educ_4cat,      # educational attainment in four categories
     educ_4cat.num,  # educational attainment in four categories, numeric
+    gender,         # male, female, Non-binary/Third gender, Pref. not to say
+    gender_3cat,    # male, female, other or preferred not to say
     age_4cat,       # age in years in 4 groups
     mil_anyrelation,# relation or no relationship with military service
     milrelation,    # particular relationship with military service
-    gender_3cat,    # gender: male, female, other or preferred not to say
     q5:q8,          # pre-treatment survey items
     q19:q24,        # trust in elections in Maricopa County, AZ
     q25:q26,        # concern for voter safety in Maricopa County, AZ
@@ -213,42 +214,3 @@ df <- df |>
 # variable order does not matter.
 df <- df |> 
   labelled::set_variable_labels(!!!df_labels)
-
-
-# Source R.script to generate scores :::::::::::::::::::::::::::::::::::::::####
-
-# source script that subsets dataframe (data -> df) and generates scores
-# generates sum and mean scores
-source(here::here('src', 'scores.R'))
-
-# Re-create df_dict (yes, again) :::::::::::::::::::::::::::::::::::::::::::####
-# Do this process again just to ensure that the variable labels for the sum and
-# composite scores are included in the dataframe.
-
-# create df dictionary
-df_dict <- labelled::generate_dictionary(df) |>
-  # this allows me to save dictionary as .csv file
-  labelled::convert_list_columns_to_character()
-
-
-# run these in case variable labels are removed
-df_labels <- df_dict |>
-  select(variable, label) |> 
-  deframe()
-
-# Now assign the labels using the splice operator. Using the splice operator,
-# labels are assigned via matching against the variable name, which means that
-# variable order does not matter.
-df <- df |> 
-  labelled::set_variable_labels(!!!df_labels)
-
-
-# save dataframe (df) to data folder :::::::::::::::::::::::::::::::::::::::####
-
-# save df processed data set.
-save(df, file = "data/research-paper-df-subset-20250203.Rdata")
-
-
-
-# save df dictionary
-write.csv(df_dict, file = "data/df_dictionary.csv")

### 2025-02-28 src/03-scores.R

@@ -27,7 +27,7 @@ conf.sum.scores <- psych::scoreItems(
 # The item by scale correlations for each item, corrected for item overlap by
 # replacing the item variance with the smc for that item.
 # Note that, when SMC < 0, SMC were set to .0
-item.cor.corrected <- conf.sum.scores$item.corrected
+# item.cor.corrected <- conf.sum.scores$item.corrected
 
 conf.mean.scores <- psych::scoreItems(
   keys = conf.keys,
@@ -120,4 +120,34 @@ df <- df |>
 
 # Delete unnecessary objects from global environment :::::::::::::::::::::::####
 
-rm(conf.mean.scores, conf.keys)
+rm(conf.sum.scores, conf.mean.scores, conf.keys)
+
+# Re-create df_dict (yes, again) :::::::::::::::::::::::::::::::::::::::::::####
+# Do this process again just to ensure that the variable labels for the sum and
+# composite scores are included in the dataframe.
+
+# create df dictionary
+df_dict <- labelled::generate_dictionary(df) |>
+  # this allows me to save dictionary as .csv file
+  labelled::convert_list_columns_to_character()
+
+
+# run these in case variable labels are removed
+df_labels <- df_dict |>
+  select(variable, label) |> 
+  deframe()
+
+# Now assign the labels using the splice operator. Using the splice operator,
+# labels are assigned via matching against the variable name, which means that
+# variable order does not matter.
+df <- df |> 
+  labelled::set_variable_labels(!!!df_labels)
+
+
+# save dataframe (df) to data folder :::::::::::::::::::::::::::::::::::::::####
+
+# save df processed data set.
+save(df, file = "data/research-paper-df-subset-20250203.Rdata")
+
+# save df dictionary
+write.csv(df_dict, file = "data/df_dictionary.csv")

### 2025-02-28 src/04-likert_plots.R

@@ -1,0 +1,727 @@
+# there's a lot of code here. It deserves its own script.
+
+set.seed(1234)
+library(tidyverse)
+library(patchwork)
+# library(pewmethods)
+
+
+# prep :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
+
+
+# shorten and 'unify' factor levels
+# Note: this removes variable labels
+df <- df |>
+  # use `pewmethods` to preserve order of factor levels
+  mutate(across(c(q19, q20, q21, q22, q23, q24,
+                  q30, q31, q32, q33, q34, q35),
+                ~pewmethods::fct_case_when(
+    .x %in% c("Not at all confident",
+              "Not at all committed",
+              "Not at all concerned") ~ "Not at all confident",
+    .x %in% c("Not too confident",
+              "Not too committed",
+              "Not too concerned",
+              "Somewhat unconcerned") ~ "Not too confident",
+    .x %in% c("Somewhat confident",
+              "Somewhat committed",
+              "Somewhat concerned") ~ "Somewhat confident",
+    .x %in% c("Very confident",
+              "Very committed",
+              "Very concerned") ~ "Very confident",
+    TRUE ~ NA
+  ))) |> 
+  # unify factor levels
+  mutate(across(c(q25, q36), ~ pewmethods::fct_case_when(
+    .x == "Very concerned" ~ "Very concerned",
+    .x == "Somewhat concerned" ~ "Somewhat concerned",
+    .x %in% c("Not too concerned", "Somewhat unconcerned") ~ "Not too concerned",
+    .x == "Not at all concerned" ~ "Not at all concerned",
+    TRUE ~ NA))) |>
+  # reverse factor levels
+  mutate(across(c(q25, q36), ~forcats::fct_rev(.)))
+
+# Return labels to df
+df <- df |> 
+  labelled::set_variable_labels(!!!df_labels)
+
+
+# set ggplot theme that will be used for every plot
+# theme_get()
+old <- theme_set(theme_bw()) # capture current theme
+
+# set/update new theme
+theme_set(
+  new = ggplot2::theme_bw(base_family = 'Palatino Linotype')+
+    theme(legend.position = 'bottom', axis.text.y.left = element_blank()))
+
+# assign items to particular vectors to avoid copy/pasting
+trust.az.items <- df |> select(q19, q20, q21, q22, q24) |> colnames() |> dput()
[…]

### 2025-02-28 src/funs.R

@@ -1,0 +1,328 @@
+# functions
+# https://adv-r.hadley.nz/functions.html
+# https://dereksonderegger.github.io/570L/12-user-defined-functions.html
+# 
+
+# fun: tabyl crosstabs :::::::::::::::::::::::::::::::::::::::::::::::::::####
+
+# function to create crosstabs using janitor::tabyl() with adorn functions as
+# arguments
+tabyl.crabs <- function(dat, var1, var2, var3, show_na=FALSE, totals = TRUE, margin_pcts = "row", digits = 2, affix_sign = F, ...){
+  
+  if (!missing(var1) && !missing(var2) && !missing(var3)){
+    crab_df <- dat |> janitor::tabyl({{ var1 }}, {{ var2 }}, {{ var3 }})
+  } else if (missing(var3) && !missing(var1) && !missing(var2)){
+    crab_df <- dat |> janitor::tabyl({{ var1 }}, {{ var2 }})
+  } else {
+    stop("please specify var1 & var2 or var1 & var2 & var3. Use janitor::tabyl for tabyl call on single vector")
+  }
+  
+  if (totals == TRUE) {
+    crab_df |> 
+      janitor::adorn_totals("both") |>
+      janitor::adorn_percentages(margin_pcts) |>
+      janitor::adorn_pct_formatting(digits = digits, affix_sign = affix_sign) |>
+      janitor::adorn_ns("rear") |>
+      janitor::adorn_title("combined")
+  } else {
+    crab_df |> 
+      janitor::adorn_percentages(margin_pcts) |>
+      janitor::adorn_pct_formatting(digits = digits, affix_sign = affix_sign) |>
+      janitor::adorn_ns("rear") |>
+      janitor::adorn_title("combined")
+  }
+  
+}
+
+# test it out. It works
+# tabyl.crabs(
+#   dat = df,
+#   var1 = group,
+#   var2 = q19,
+#   show_na = F,
+#   totals = T,
+#   margin_pcts = "row",
+#   digits = 2,
+#   affix_sign = F
+# )
+
+# works with 3 variables
+# tabyl.crabs(
+#   dat = df,
+#   var1 = group,
+#   var2 = q19,
+#   var3 = q7,
+#   show_na = F,
+#   totals = T,
+#   margin_pcts = "row",
+#   digits = 2,
+#   affix_sign = F
+# )
+
+# works with minimal input
+# tabyl.crabs(df, group, q19)
+
[…]

### 2025-03-01 docs/_tex/index.tex
push up second draft

@@
     % xetex/luatex font selection
-    \setmainfont[]{TeX Gyre Termes}
-  \setmathfont[]{TeX Gyre Termes Math}
+    \setmainfont[]{TeX Gyre Pagella}
+  \setmathfont[]{TeX Gyre Pagella Math}
 \fi
@@
 \usepackage{xcolor}
+\usepackage{caption}
+\usepackage{anyfontsize}
+\usepackage{dcolumn} 
 \makeatletter
@@
 (\citeproc{ref-steinhauer2020}{Steinhauer 2020}). Prior research has
-substantiated such a connection between veterans and militia groups. A.
+substantiated such a connection between veterans and militia groups.
 Cooter (\citeproc{ref-cooter2024}{2024}) notes from her 3-year
@@
 such groups, as opposed to being recruited by them''
-(\citeproc{ref-cooter2024}{2024}; see also \citeproc{ref-cooter2013}{A.
-B. Cooter 2013}). Thus, countering such associations by promoting a
-different image of veterans to the mass public and veterans alike seems
-like a reasonable motivation. Yet such speculation is just that.
+(\citeproc{ref-cooter2024}{2024}; see also
+\citeproc{ref-cooter2013}{Cooter 2013}). Thus, countering such
+associations by promoting a different image of veterans to the mass
+public and veterans alike seems like a reasonable motivation. Yet such
+speculation is just that.
 
@@
 Although military recruitment shows a downward trend as of late, public
-perception of veterans are overwhelmingly positive
+perceptions of veterans are overwhelmingly positive
 (\citeproc{ref-kleykamp2023}{Kleykamp, Schwam, and Wenig 2023}).
@@
 what I find. Polychoric correlations between the trust and distrust
-items negatively correlate as expected{[}\^{}See Appendix C{]}, as does
+items negatively correlate as expected\footnote{See Appendix C}, as does
 the correlation between the two sum score scales. Given the ordinal
@@
 
-\caption{\label{tbl-ttest}Mean Difference Effect of Treatment Compared
-to Control Condition}
+\caption{\label{tbl-ttest}Mean Difference of Treatment Compared to
+Control Condition}
 
@@
 in elections in Maricopa County, AZ, and one's local area by treatment
-condition; Figure~\ref{fig-coef1-2} displays four models for trust and
-distrust in elections in AZ or one's local area by treatment condition
-
-the treatment effect on both trust and distrust is clear. Although the
-effect is only there when questions pertained to Maricopa County, AZ.
-The treatment effect on trust and distrust is conditional on whether the
-survey questions inquired about elections in Maricopa County, AZ.
-Announcing efforts to recruit veterans and their families to work as
-election staff and volunteers increases confidence in elections
-administration in places outside of one's local area, but doesn't boost
-confidence in elections within one's local area. However, bear in mind
-that confidence in elections for one's local area is already higher than
-for those outside. Thus, there's already less insecurity concerning
-elections in one's local area, but publicized efforts to recruit
-veterans to work as election staff and volunteers is a small but
-positive step towards closing that gap in confidence for elections that
-occur elsewhere.
-
-I now turn to results examining those who held onto the belief that the
-2020 election results were illegitimate. I think check to see if
-recruiting veterans simply makes people feel safer at the polls.
-
-\pagebreak
+condition; Figure~\ref{fig-coef1-2} displays the same except
+\emph{confidence} is decomposed into its two components, \emph{trust}
+and \emph{distrust}. These figures merely illustrate the effect of the
+treatment with respect to the relationship between trust and distrust;
+ultimately confidence improves.
+
+Confidence in elections was higher among those who read the treatment
+vignette but remained conditional on whether the survey questions
+inquired about elections in Maricopa County, AZ. This evidence suggests
+that announcing efforts to recruit veterans and their families to work
+as election staff and volunteers may increase confidence in elections
+administration in places outside of one's local area, but may not boost
+confidence in elections within one's local area.
+
+\subsubsection{2020 Election Legitimacy
+Beliefs}\label{election-legitimacy-beliefs}
+
+I now turn to results examining the effect of the treatment on those who
+held onto the belief that the 2020 election results were illegitimate.
+First, reviewing responses to items that capture trust in elections, it
+is easy to recognize the difference between the way 2020 election
+deniers responded with respect to where elections were held.
+
+\phantomsection\label{cell-fig-legit}
+\begin{figure}[!t]
+
+\caption{\label{fig-legit}Trust in elections by treatment among those
+who refute the 2020 election results}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-legit-1.png}}
+
+}
+
+\end{figure}%
+
+Among those who belief the 2020 election results were illegitimate,
+trust in Maricopa County, AZ elections was lower for each item compared
+to items pertaining to elections within one's local area, regardless of
+treatment condition. However, notably, trust that election technology
+would be secure received the lowest confidence endorsement overall.
+There was also a notable lack of trust that the voting process would be
+fair relative to the other items.\footnote{What is interesting to note
+  here is that the first three items regard the more human element of
+  the election administration process, e.g., ensuring accuracy of
+  counts, competence, and commitment of election workers. Although a
+  neat line can't really be drawn between the first three and latter two
+  items presented here, it is interesting to see a divergence of the
+  usual high confidence placed in local area elections.} Now the
+comparative difference in responses between those in the treatment group
+compared to those in the control group appears substantial for items
+pertaining to elections in Maricopa County, AZ.
+
+\phantomsection\label{cell-fig-legit2}
+\begin{figure}[!t]
+
+\caption{\label{fig-legit2}Distrust in elections by treatment among
+those who refute the 2020 election results}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-legit2-1.png}}
+
+}
+
+\end{figure}%
+
+Concerning distrust among those who refuted the 2020 election results,
+responses items assessing one's expectation that election fraud would
+occur reveal the same pattern. Although there is not as stark a
+disparity between responses of those in the treatment and those in the
+control, among those in the treatment group, there does appear to be
+less expectation that election fraud would occur in Maricopa County, AZ.
+Overall, review of responses to trust (Figure~\ref{fig-legit}) and
+distrust survey items (Figure~\ref{fig-legit2}) does lend credence to
+the impact of the treatment.
+
+In order to substantiate the overall influence of the treatment on
+confidence in elections, I regressed the dependent variable confidence
+on legitimacy beliefs while controlling for partisanship.
+
+\begin{table}[H]
+
+\caption{\label{tbl-legit}Confidence in Elections by Treatment and
+Legitimacy Beliefs}
+
+\centering{
+
+\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-2} D{.}{.}{-2} } 
+\\[-1.8ex]\hline \\[-1.8ex] 
+ & \multicolumn{1}{c}{Confidence in AZ Elections} & \multicolumn{1}{c}{w/Interaction} \\ 
+\hline \\[-1.8ex] 
+ Treatment & 0.18^{***}$ $(0.05) & 0.09$ $(0.06) \\ 
+  Not Legitimate & -0.72^{***}$ $(0.07) & -0.86^{***}$ $(0.09) \\ 
+  Republican & 0.11$ $(0.08) & 0.12$ $(0.08) \\ 
+  Democrat & 0.17^{*}$ $(0.09) & 0.17^{**}$ $(0.09) \\ 
+  Not Legitimate * Treatment &  & 0.27^{**}$ $(0.11) \\ 
+  Constant & 0.03$ $(0.08) & 0.07$ $(0.08) \\ 
+ N & \multicolumn{1}{c}{1,263} & \multicolumn{1}{c}{1,263} \\ 
+R$^{2}$ & \multicolumn{1}{c}{0.14} & \multicolumn{1}{c}{0.14} \\ 
+Adjusted R$^{2}$ & \multicolumn{1}{c}{0.13} & \multicolumn{1}{c}{0.14} \\ 
+Residual Std. Error & \multicolumn{1}{c}{0.93 (df = 1258)} & \multicolumn{1}{c}{0.93 (df = 1257)} \\ 
+F Statistic & \multicolumn{1}{c}{49.92$^{***}$ (df = 4; 1258)} & \multicolumn{1}{c}{41.24$^{***}$ (df = 5; 1257)} \\ 
+\hline \\[-1.8ex] 
+\multicolumn{3}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\ 
+\end{tabular}
+
+}
+
+\end{table}%
+
+The first model in \ref{tbl-legit} shows that overall confidence in
+elections (trust - distrust) among those who read the treatment vignette
+was significantly (statistically) greater than those who read the
+control, on average and netting out the effects of partisanship and
+legitimacy beliefs. Democratic partisanship remains marginally
+significant at \(90\%\) confidence level (\(p = 0.055\)). Not believing
+the 2020 election of Joe Biden was legitimate is negatively associated
+with confidence in elections. In order to assess the magnitude of this
+interaction effect of the treatment on those who refuted the 2020
+election results, I ran a model where confidence in elections was
+regressed on the interaction between the treatment and legitimacy
+beliefs, controlling for partisanship.
+
+There's a positive interaction effect of the treatment vignette among
+those who believe that the 2020 election was not legitimate, on average
+and controlling for partisanship. This shows that the treatment effect
+was most influential upon those who believe the 2020 election results
+were illegitimate. The treatment alone does not reverse such beliefs,
+but this shows where its influence is perhaps most potent.
 
 \subsection{Conclusion}\label{conclusion}
+
+Publicized announcements that election officials are actively recruiting
+former military service members to work as election staff and volunteers
+is associated with slightly greater confidence in elections compared to
+election worker recruitment announcements that do not explicitly mention
+targeted recruitment of former military service members. Moreover,
+increased levels of confidence is limited to elections beyond one's
+local area and, of course, in anticipation of election night. Whether
+the increase in confidence is sustained post-election night cannot be
+inferred from these results.
+
+Bear in mind that confidence in elections for one's local area is
+already higher than for those beyond. Thus, there's already more
+insecurity concerning elections elsewhere for whatever reason. In the
+anticipatory period prior to national elections, publicized efforts to
+recruit veterans to work as election staff and volunteers may be a
+small, but positive, step towards reducing insecurity in elections that
+occur elsewhere. Especially among those who maintained a steadfast
+degree of distrust in elections. Despite a lack of evidence that
+systematic electoral fraud had occurred in the 2020 election, a
+substantial proportion of the population were unwilling to affirm the
+legitimacy of the results. However, despite such legitimacy beliefs,
+most were not consistent as they expressed varying levels of trust in
+different aspects of elections administration.
+
+These results speaks more to the influence that military veterans have
+among those who distrust the electoral process and refute the legitimacy
+of prior outcomes than it does to the public more generally. In general,
+public confidence appears strongest when the elections under
+consideration regard those within one's local community. Yet, such
+strong confidence is not generalized outward to the institution of
+elections administration as a whole. Insecurity in the integrity of the
+electoral process and its administration may be naturally higher for
+elections that occur further from home. Whether that is due to some
+local favorability bias or some outward negativity bias is hard to say.
+And seeing as how insecurity presents vulnerability, it is perhaps far
+easier to inspire a general sense of distrust in the process and its
+administration in places not near and around one's local area.
 
@@
 \item
-  Moreover, results are limited by the survey questions, questionnaire
-  design, and experimental stimulus (i.e., vignette) for two reasons. -
+  Results are limited by the survey questions, questionnaire design, and
+  experimental stimulus (i.e., vignette) for two reasons:
+
+  \begin{itemize}
+  \tightlist
+  \item
     First, the vignettes and many survey questions ask about Maricopa
-  County, AZ specifically. Adding a specific county in the vignette adds
-  in a factor that cannot be accounted for without additional treatments
-  that eliminate the setting as a potential influence. Moreover, the
-  specificity of the setting adds in even more unexplained error---some
-  people may have attitudes about the county in question, others won't,
-  while others may be muffed to consider a random county in the U.S.
-  they've know nothing about. Adding the county undermines the
-  confidence that treatment effects are solely attributable to veterans
-  to an unknown degree. - Second, questions ask about one's own local
-  community in addition to identical questions which asked about
-  Maricopa County, AZ. Consequently, many questions within the
-  questionnaire were duplicates with that one differences. This isn't
-  uncommon in surveys, however in this case, it lengthened the survey to
-  a degree that likely resulted in a higher drop off rate. More
-  importantly, the quality of responses were likely diminished to some
-  unknown extent. Although it is possible to compare questions asked
-  about Maricopa County, AZ to questions about one's local area, the
-  quality of that comparison is limited by the unknown extent of fatigue
+    County, AZ specifically. Adding a specific county in the vignette
+    adds in a factor that cannot be accounted for without additional
+    treatments that eliminate the setting as a potential influence.
+    Moreover, the specificity of the setting adds in even more
+    unexplained error---some people may have attitudes about the county
+    in question, others won't, while others may be muffed to consider
+    any random county in the U.S. they know nothing about. Adding the
+    county undermines the confidence that treatment effects are solely
+    attributable to veterans to an unknown degree.
+  \item
+    Second, questions ask about one's own local community in addition to
+    identical questions which asked about Maricopa County, AZ.
+    Consequently, many questions within the questionnaire were
+    duplicates with but one difference. This isn't uncommon in surveys,
+    however in this case, it lengthened the survey to a degree that
+    potentially resulted in a higher drop off rate. More importantly,
+    the quality of responses were likely diminished to some unknown
+    extent. Although it is possible to compare questions asked about
+    Maricopa County, AZ to questions about one's local area, the quality
+    of that comparison is limited by the unknown extent of fatigue
     induced by answering the same questions twice. It wasn't just that
-  some questions were asked multiple times, almost all of the questions
-  were duplicated; after completing a long series on Maricopa County,
-  participants then answered the same questions about the local
-  community. The rate to which participants dropped from the survey is
-  \_\_\_, which suggests fatigue as an important factor. Survey fatigue
-  is a known issue that should be taken into consideration. Comparison
-  of treatment effects between the MC series and the local area series
-  is undermined by the unknown influence that fatigue would have on
-  response choices. Any differences couldn't confidently be attributed
-  to ``my area'' vs Maricopa county. We also can't determine whether
-  treatment effects are sustained when comparing the Maricopa County
-  series to the local area series asked subsequently. We would have to
-  assume the setting as irrelevant, which we can't reasonably do.
+    some questions were asked multiple times, almost all of the
+    questions were duplicated. After completing a long series on
+    Maricopa County, participants then answered the same questions about
+    the local community. I haven't computed the rate to which
+    participants dropped from the survey, yet items contain more missing
+    values toward the end of the survey. Some participants dropped out,
+    but some simply skipped a few items. The extent to which this
+    occurred is minor, but it does suggest fatigue as a worthy of
+    consideration.
+  \end{itemize}
 \end{itemize}
@@
 
-\pagebreak
+\newpage
 
@@
 
-The median age was 46 (mean age was 47). There was 51.7\% (n = 658)
-women, 47\% (n = 598) men, and approximately 1.3\% who identified as
-either Non-binary/third gender (n = 7) or preferred not to say (n = 9).
-A large proportion of the sample identified as White or Caucasian (n =
-975, 76.65\%), while all other non-White respondents comprised 27.83\%
-of the sample. Those who held a graduate level degree (e.g., Master's,
-Doctorate, or Professional level) comprised 13\% of the sample; those
-with either degree at the Associate or Bachelor's level comprised
-36.24\%, while 22.25\% had some college but no degree; and 28.46\% had
-either a high school level or equivalent education or less than high
-school. The largest proportion of the sample identified as Democrat at
-44.64\%, followed by Republicans at 42.59\%. The proportion of true
-Independents was 12.78\%.
-
-\pagebreak
+The median age was 46 (mean age was \(47\)), \(51.7\%\) (\(n = 658\))
+women, \(47\%\) (\(n = 598\)) men, and approximately \(1.3\%\) who
+identified as either Non-binary/third gender (\(n = 7\)) or preferred
+not to say (\(n = 9\)). A large proportion of the sample identified as
+White or Caucasian (\(n = 975, 76.65\%\)), while all other non-White
+respondents comprised \(27.83\%\) (\(n = 297\)) of the sample. Those who
+held a graduate level degree (e.g., Master's, Doctorate, or Professional
+level) comprised \(13\%\) of the sample; those with either degree at the
+Associate or Bachelor's level comprised \(36.24\%\), while \(22.25\%\)
+had some college but no degree; and \(28.46\%\) had either a high school
+level or equivalent education or less than high school. The largest
+proportion of the sample identified as Democrat at \(44.64\%\), followed
+by Republicans at \(42.59\%\). The proportion of true
+Independents\footnote{Independent `leaners' were grouped into the
+  respective party affiliation in which they lean.} was \(12.78\%\).
+
+\begin{table}
+
+\caption{\label{tbl-demog}Sample Demographics}
+
+\centering{
+
+\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lllll}
+\toprule
+\textbf{Demographic} & \textbf{N} & \textbf{Overall}  N = 1,287\textsuperscript{\textit{1}} & \textbf{Control}  N = 637\textsuperscript{\textit{1}} & \textbf{Treatment}  N = 650\textsuperscript{\textit{1}} \\
+\midrule\addlinespace[2.5pt]
+{\bfseries Age group} & 1,287 &  &  &  \\ 
+    18-34 &  & 350 (27\%) & 170 (27\%) & 180 (28\%) \\ 
+    35-54 &  & 480 (37\%) & 245 (38\%) & 235 (36\%) \\ 
+    55-74 &  & 390 (30\%) & 198 (31\%) & 192 (30\%) \\ 
+    75-85+ &  & 67 (5.2\%) & 24 (3.8\%) & 43 (6.6\%) \\ 
+{\bfseries Gender} & 1,272 &  &  &  \\ 
+    Male &  & 598 (47\%) & 289 (46\%) & 309 (48\%) \\ 
+    Female &  & 658 (52\%) & 330 (52\%) & 328 (51\%) \\ 
+    Other/Refused &  & 16 (1.3\%) & 10 (1.6\%) & 6 (0.9\%) \\ 
+    NA &  & 15 & 8 & 7 \\ 
+{\bfseries Race/Ethnicity} & 1,272 &  &  &  \\ 
+    White &  & 975 (77\%) & 478 (76\%) & 497 (77\%) \\ 
+    Asian &  & 51 (4.0\%) & 25 (4.0\%) & 26 (4.0\%) \\ 
+    Black &  & 164 (13\%) & 85 (14\%) & 79 (12\%) \\ 
+    Other &  & 24 (1.9\%) & 12 (1.9\%) & 12 (1.9\%) \\ 
+    Hispanic &  & 44 (3.5\%) & 24 (3.8\%) & 20 (3.1\%) \\ 
+    American Indian &  & 14 (1.1\%) & 5 (0.8\%) & 9 (1.4\%) \\ 
+    NA &  & 15 & 8 & 7 \\ 
+{\bfseries White or Non-White} & 1,272 &  &  &  \\ 
+    Non-White &  & 297 (23\%) & 151 (24\%) & 146 (23\%) \\ 
+    White &  & 975 (77\%) & 478 (76\%) & 497 (77\%) \\ 
+    NA &  & 15 & 8 & 7 \\ 
+{\bfseries Education} & 1,272 &  &  &  \\ 
+    H.S. or less &  & 362 (28\%) & 174 (28\%) & 188 (29\%) \\ 
+    Some college no degree &  & 283 (22\%) & 142 (23\%) & 141 (22\%) \\ 
+    College degree &  & 461 (36\%) & 236 (38\%) & 225 (35\%) \\ 
+    Postgraduate degree &  & 166 (13\%) & 77 (12\%) & 89 (14\%) \\ 
+    NA &  & 15 & 8 & 7 \\ 
+{\bfseries Party ID} & 1,268 &  &  &  \\ 
+    Independent &  & 162 (13\%) & 83 (13\%) & 79 (12\%) \\ 
+    Republican &  & 540 (43\%) & 262 (42\%) & 278 (43\%) \\ 
+    Democrat &  & 566 (45\%) & 283 (45\%) & 283 (44\%) \\ 
+    NA &  & 19 & 9 & 10 \\ 
+{\bfseries Military Relation} & 1,272 &  &  &  \\ 
+    No relation &  & 789 (62\%) & 394 (63\%) & 395 (61\%) \\ 
+    Only family &  & 362 (28\%) & 182 (29\%) & 180 (28\%) \\ 
+    Served w/fam &  & 64 (5.0\%) & 31 (4.9\%) & 33 (5.1\%) \\ 
+    Served &  & 57 (4.5\%) & 22 (3.5\%) & 35 (5.4\%) \\ 
+    NA &  & 15 & 8 & 7 \\ 
+\bottomrule
+\end{tabular*}
+\begin{minipage}{\linewidth}
+Independents do not identify nor 'lean' toward either political party\\
+\textsuperscript{\textit{1}}n (\%)\\
+\end{minipage}
+
+}
+
+\end{table}%
+
+\newpage
+
+\subsection{Appendix C: Trust and Distrust}\label{sec-appendix-c}
+
+Polychoric correlation is a measure of association between two ordered
+categorical variables each assumed to represent (i.e., indicate, be
+influenced by) two normally distributed, continuous, latent variables.
+Due to the fact that each item is an ordered categorical variable
+assumed to represent one of two latent constructs (i.e., trust or
+distrust, respectively), I examined polychoric correlations between the
+items used to construct each scale. In addition, one set of the trust
+and distrust items pertained to Maricopa County, AZ, whereas the other
+set of items were identical except that these items pertained to one's
+local area.
+
+Since the two sets of items (AZ items and Local items) are, in theory,
+supposed to capture the same normally distributed continuous latent
+variables, then the polychoric inter-item correlations should be
+significantly associated, strong, and in the same direction for the
+items that measure trust regardless of whether the items pertain to AZ
+or one's local area (likewise for distrust). Simply, trust/distrust in
+elections in AZ should strongly and positively be associated with
+trust/distrust in elections in one's local area.
+
+Additionally, the items that indicate trust should negatively correlate
+with items that indicate distrust. Furthermore, the strength of the
+negative correlations between trust and distrust should closely
+approximate if not match.
+
+\phantomsection\label{cell-fig-polycor}
+\begin{figure}[h]
+
+\caption{\label{fig-polycor}Polychoric Item Correlation Matrix}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-polycor-1.png}}
+
+}
+
+\end{figure}%
+
+Indeed, this is what is revealed by the correlation matrix
+(Figure~\ref{fig-polycor}). Trust items correlate positively, strongly,
+and are significant regardless of location at which the items pertain.
+The same goes for distrust items. Also, items meant to measure trust
+negatively correlate with the items that measure distrust. However, the
+positive correlations are not nearly as high as would be expected
+supposing that the items are nearly identical theoretical indicators of
+the same hypothetical constructs, i.e., trust and distrust respectively.
+
+If the items accurately measure trust/distrust in elections regardless
+of where those elections are said to take place, then positive
+correlations between the AZ and Local area items should approach perfect
+correlation as though the same exact questions were asked twice. This
+result, however, suggests that the location of which the survey items
+pertain (and perhaps other factors) makes a substantial difference in
+the pattern of responses, but also raises valid questions as to whether
+the items accurately measure the latent variable constructs in the first
+place.
 
@@
 
+\bibitem[\citeproctext]{ref-cooter2013}
+Cooter, Amy. 2013. {``Americanness, {Masculinity}, and {Whiteness}: {How
+Michigan Militia Men Navigate Evolving Social Norms}.''} Thesis.
+\url{http://deepblue.lib.umich.edu/handle/2027.42/98077}.
+
 \bibitem[\citeproctext]{ref-cooter2024}
@@
 \url{https://www.middlebury.edu/institute/academics/centers-initiatives/ctec/ctec-publications/veterans-and-extremism-militias-january-6th}.
-
-\bibitem[\citeproctext]{ref-cooter2013}
-Cooter, Amy B. 2013. {``Americanness, {Masculinity}, and {Whiteness}:
-{How Michigan Militia Men Navigate Evolving Social Norms}.''} Thesis.
-\url{http://deepblue.lib.umich.edu/handle/2027.42/98077}.
 

### 2025-03-01 index.qmd
push up second draft

@@
 library(patchwork)
+library(jtools)
 
-# load data
-load("data/research-paper-df-20250203.Rdata") #df
+# load subset of processed dataframe that includes dv composite scores
+load("data/research-paper-df-subset-20250203.Rdata") #df
 
@@
 df_dict <- read.csv("data/df_dictionary.csv")
+
+# do next. a whole lotta Likert plots
+source(here::here('src', '03-likert_plots.R'))
 
@@
 Indeed, this is what I find.
-Polychoric correlations between the trust and distrust items negatively correlate as expected\[\^See Appendix C\], as does the correlation between the two sum score scales.
+Polychoric correlations between the trust and distrust items negatively correlate as expected^[See Appendix C], as does the correlation between the two sum score scales.
 Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
@@
 
-# Likert plot of trust and confidence in election admin comparing treatment and
-# control groups
-trust.likert.treat.az <- df |>
-  # relabel factor labels for plotting
-  mutate(across(
-    c(q19, q20, q21, q22, q23, q24, q30, q31, q32, q33, q34, q35),
-    ~ pewmethods::fct_case_when(
-      .x %in% c("Not at all confident", "Not at all committed") ~ "Not at all confident",
-      .x %in% c("Not too confident", "Not too committed") ~ "Not too confident",
-      .x %in% c("Somewhat confident", "Somewhat committed") ~ "Somewhat confident",
-      .x %in% c("Very confident", "Very committed") ~ "Very confident",
-      TRUE ~ NA
-    )
-  )) |>
-  ggstats::gglikert(
-    include = c(q19, q20, q21, q22, q24),
-    y = 'group',
-    facet_rows = vars(.question),
-    symmetric = F,
-    labels_size = 2.5,
-    add_totals = T
-  ) +
-  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
-  # ggplot2::scale_fill_brewer(palette = "Greys")+
-  labs(subtitle = str_wrap("Maricopa County, Arizona", width = 95)) +
-  theme_bw() +
-  theme(
-    text = element_text(family = "Palatino Linotype"),
-    legend.position = 'bottom',
-    axis.text.x = element_blank(), # remove percentage text along x-axis
-    strip.text.y.right = element_blank()
-  )
-
-# confidence in elections between experiment conditions for items concerning local area
-trust.likert.treat.lcl <- df |>
-  # relabel factor labels for plotting
-  mutate(across(
-    c(q19, q20, q21, q22, q23, q24, q30, q31, q32, q33, q34, q35),
-    ~ pewmethods::fct_case_when(
-      .x %in% c("Not at all confident", "Not at all committed") ~ "Not at all confident",
-      .x %in% c("Not too confident", "Not too committed") ~ "Not too confident",
-      .x %in% c("Somewhat confident", "Somewhat committed") ~ "Somewhat confident",
-      .x %in% c("Very confident", "Very committed") ~ "Very confident",
-      TRUE ~ NA
-    )
-  )) |>
-  ggstats::gglikert(
-    include = c(q30, q31, q32, q33, q35),
-    y = 'group',
-    facet_rows = vars(.question),
-    variable_labels = c(
-      q30 = "Votes counted as intended",
-      q31 = "Election officials will do good job",
-      q32 = "Election workers will be committed",
-      q33 = "Voting process will be fair",
-      q35 = "Election technology will be secure"
-    ),
-    facet_label_wrap = 10,
-    labels_size = 2.5,
-    symmetric = F,
-    add_totals = T
-  ) +
-  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
-  # ggplot2::scale_fill_brewer(palette = "Greys")+
-  labs(subtitle = str_wrap("Local Area", width = 95)) +
-  theme_bw() +
-  theme(
-    text = element_text(family = "Palatino Linotype"),
-    legend.position = 'bottom',
-    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
-    axis.text.x = element_blank(), # remove percentage text along x-axis
-    strip.text.y.right = element_text(angle = 0, size = 8)
-  )
-
-# trust.likert.treat.az
-# trust.likert.treat.lcl
-
-# Instead of two separate plots, arrange into one plot while remaining separated
-# use `ggpubr` package to print multiple plots side-by-side (or alt. row-by-row)
-ggpubr::ggarrange(
-  trust.likert.treat.az,
-  trust.likert.treat.lcl,
-  ncol = 2,
-  common.legend = T,
-  legend = "bottom", 
-  font.label = list(family = "Palatino Linotype")
-) +
-  # add figure footnote annotation
-  patchwork::plot_annotation(
-    caption = str_wrap("Missing values removed. Displays percent proportions of responses by experiment condition and combined percentage proportions for two categories.",
-               width = 85), theme = theme(text = element_text(family = "Palatino Linotype")))
+p10.trust.treat
 
@@
 
-# distrust in elections in AZ by experimental condition
-distrust.likert.az <- df |>
-  # reverse levels of factor vars to show positive difference in "not likely"
-  mutate(across(c(q28_1:q28_5), ~forcats::fct_rev(.))) |> 
-  ggstats::gglikert(
-    include = c(q28_1:q28_5),
-    y = 'group',
-    facet_rows = vars(.question),
-    variable_labels = c(
-      q28_1 = "Voter fraud will occur",
-      q28_2 = "Many votes won't be counted",
-      q28_3 = "Many voters will be turned away",
-      q28_4 = "Foreign Interference",
-      q28_5 = "Election officials will discourage voting"),
-    facet_label_wrap = 10,
-    labels_size = 2.5,
-    symmetric = F,
-    add_totals = T
-  ) +
-  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
-  # ggplot2::scale_fill_brewer(palette = "Greys")+
-  labs(subtitle = str_wrap("Maricopa County, Arizona", width = 95)) +
-  theme_bw() +
-  theme(
-    text = element_text(family = "Palatino Linotype"),
-    legend.position = 'bottom',
-    axis.text.x = element_blank(), # remove percentage text along x-axis
-    strip.text.y.right = element_blank()
-  )
-
-# distrust in elections in Local area by experimental condition
-distrust.likert.lcl <- df |>
-  # reverse levels of factor vars to show positive difference in "not likely"
-  mutate(across(c(q40_1:q40_5), ~forcats::fct_rev(.))) |> 
-  ggstats::gglikert(
-    include = c(q40_1:q40_5),
-    y = 'group',
-    facet_rows = vars(.question),
-    variable_labels = c(
-      q40_1 = "Voter Fraud will occur",
-      q40_2 = "Many Votes won't be counted",
-      q40_3 = "Many voters will be turned away",
-      q40_4 = "Foreign Interference",
-      q40_5 = "Election officials will discourage voting"),
-    facet_label_wrap = 10,
-    labels_size = 2.5,
-    symmetric = F,
-    add_totals = T
-  )+
-  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
-  # ggplot2::scale_fill_brewer(palette = "Greys")+
-  labs(subtitle = str_wrap("Local Area", width = 95)) +
-  theme_bw() +
-  theme(
-    text = element_text(family = "Palatino Linotype"),
-    legend.position = 'bottom',
-    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
-    axis.text.x = element_blank(), # remove percentage text along x-axis
-    strip.text.y.right = element_text(angle = 0, size = 8)
-  )
-
-# Instead of two separate plots, arrange into one plot while remaining separated
-# use `ggpubr` package to print multiple plots side-by-side (or alt. row-by-row)
-ggpubr::ggarrange(
-  distrust.likert.az,
-  distrust.likert.lcl,
-  ncol = 2,
-  common.legend = T,
-  legend = "bottom", 
-  font.label = list(family = "Palatino Linotype")
-) +
-  # add figure footnote annotation
-  patchwork::plot_annotation(
-    caption = str_wrap("Missing values removed. Displays percent proportions of responses by experiment condition and combined percentage proportions for two categories.",
-               width = 85), theme = theme(text = element_text(family = "Palatino Linotype")))
+p11.distrust.treat
 
@@
      width = 95)) +
-  theme_bw(base_family = "Palatino Linotype")
+  theme_bw(base_family = "TeX Gyre Pagella")
 
@@
 #| label: tbl-ttest
-#| tbl-cap: "Mean Difference Effect of Treatment Compared to Control Condition"
+#| tbl-cap: "Mean Difference of Treatment Compared to Control Condition"
 #| tbl-pos: H
@@
   labs(y = "")+
-  theme_bw(base_family = "Palatino Linotype")
+  theme_bw(base_family = "TeX Gyre Pagella")
 
@@
 @fig-coef1 displays standard difference estimates of confidence in elections by treatment condition (control condition as reference).
-@fig-coef1-1 displays two models for confidence in elections in Maricopa County, AZ, and one's local area by treatment condition; @fig-coef1-2 displays four models for trust and distrust in elections in AZ or one's local area by treatment condition.
+@fig-coef1-1 displays two models for confidence in elections in Maricopa County, AZ, and one's local area by treatment condition; @fig-coef1-2 displays the same except *confidence* is decomposed into its two components, *trust* and *distrust*.
 These figures merely illustrate the effect of the treatment with respect to the relationship between trust and distrust; ultimately confidence improves.
@@
 
-I now turn to results examining those who held onto the belief that the 2020 election results were illegitimate.
-I think check to see if recruiting veterans simply makes people feel safer at the polls.
+### 2020 Election Legitimacy Beliefs
 
-\pagebreak
+I now turn to results examining the effect of the treatment on those who held onto the belief that the 2020 election results were illegitimate.
+First, reviewing responses to items that capture trust in elections, it is easy to recognize the difference between the way 2020 election deniers responded with respect to where elections were held.
+
+```{r}
+#| label: fig-legit
+#| fig-cap: "Trust in elections by treatment among those who refute the 2020 election results"
+#| fig-height: 4.5
+
+p13.trust.treat.legit
+
+```
+
+Among those who belief the 2020 election results were illegitimate, trust in Maricopa County, AZ elections was lower for each item compared to items pertaining to elections within one's local area, regardless of treatment condition.
+However, notably, trust that election technology would be secure received the lowest confidence endorsement overall.
+There was also a notable lack of trust that the voting process would be fair relative to the other items.^[What is interesting to note here is that the first three items regard the more human element of the election administration process, e.g., ensuring accuracy of counts, competence, and commitment of election workers.
+Although a neat line can't really be drawn between the first three and latter two items presented here, it is interesting to see a divergence of the usual high confidence placed in local area elections.] Now the comparative difference in responses between those in the treatment group compared to those in the control group appears substantial for items pertaining to elections in Maricopa County, AZ.
+
+```{r}
+#| label: fig-legit2
+#| fig-cap: "Distrust in elections by treatment among those who refute the 2020 election results"
+#| fig-height: 4.5
+
+p14.distrust.treat.legit
+
+```
+
+Concerning distrust among those who refuted the 2020 election results, responses items assessing one's expectation that election fraud would occur reveal the same pattern.
+Although there is not as stark a disparity between responses of those in the treatment and those in the control, among those in the treatment group, there does appear to be less expectation that election fraud would occur in Maricopa County, AZ.
+Overall, review of responses to trust (@fig-legit) and distrust survey items (@fig-legit2) does lend credence to the impact of the treatment.
+
+In order to substantiate the overall influence of the treatment on confidence in elections, I regressed the dependent variable confidence on legitimacy beliefs while controlling for partisanship.
+
+```{r}
+#| label: tbl-legit
+#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
+#| tbl-pos: H
+#| results: asis
+
+# All continuous variables are mean-centered and scaled by 1 standard deviation.
+m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = df)
+m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = df)
+
+stargazer::stargazer(
+  m1,
+  m2,
+  type = "latex", 
+  style = 'apsr',
+  header = F,
+  float = F,
+  align = T, 
+  single.row = T, 
+  dep.var.labels.include = F, model.numbers = F,
+  digits = 2,
+  column.labels = c("Confidence in AZ Elections", "w/Interaction"),
+  covariate.labels = c(
+      "Treatment",
+      "Not Legitimate",
+      "Republican",
+      "Democrat",
+      "Not Legitimate * Treatment",
+      "Constant"
+    )
+)
+
+```
+
+The first model in \ref{tbl-legit} shows that overall confidence in elections (trust - distrust) among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
+Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
+Not believing the 2020 election of Joe Biden was legitimate is negatively associated with confidence in elections.
+In order to assess the magnitude of this interaction effect of the treatment on those who refuted the 2020 election results, I ran a model where confidence in elections was regressed on the interaction between the treatment and legitimacy beliefs, controlling for partisanship.
+
+There's a positive interaction effect of the treatment vignette among those who believe that the 2020 election was not legitimate, on average and controlling for partisanship.
+This shows that the treatment effect was most influential upon those who believe the 2020 election results were illegitimate.
+The treatment alone does not reverse such beliefs, but this shows where its influence is perhaps most potent.
 
@@
 Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
-
-Additionally, these results cannot give any indication whether confidence in the electoral process or its administration writ large is higher among those who, while voting in person, interacted with military veterans who were working as election staff or volunteers.
-In other words, this research can provide no indication that having veterans on staff at election sites or individual interaction with veterans while voting has any influence on voter confidence in the post-election period.
-
-All that can be said from the results presented is that public announcement of efforts to recruit veterans to work as election workers results in a small boost in confidence in elections held in places where confidence in elections administration is lower relative to the confidence in elections within one's local area.
 
@@
 -   limitations: interpretations of the treatment effect are limited.
-    -   The sample may not be generalizable to the population.
-    -   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts.
+    *   The sample may not be generalizable to the population.
+    *   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts.
 -   Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
--   Moreover, results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons.
-- First, the vignettes and many survey questions ask about Maricopa County, AZ specifically.
+-   Results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons: 
+    *  First, the vignettes and many survey questions ask about Maricopa County, AZ specifically.
 Adding a specific county in the vignette adds in a factor that cannot be accounted for without additional treatments that eliminate the setting as a potential influence.
-Moreover, the specificity of the setting adds in even more unexplained error---some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S.
-they've know nothing about.
+Moreover, the specificity of the setting adds in even more unexplained error---some people may have attitudes about the county in question, others won't, while others may be muffed to consider any random county in the U.S.
+they know nothing about.
 Adding the county undermines the confidence that treatment effects are solely attributable to veterans to an unknown degree.
-- Second, questions ask about one's own local community in addition to identical questions which asked about Maricopa County, AZ.
-Consequently, many questions within the questionnaire were duplicates with that one differences.
-This isn't uncommon in surveys, however in this case, it lengthened the survey to a degree that likely resulted in a higher drop off rate.
+    *   Second, questions ask about one's own local community in addition to identical questions which asked about Maricopa County, AZ.
+Consequently, many questions within the questionnaire were duplicates with but one difference.
+This isn't uncommon in surveys, however in this case, it lengthened the survey to a degree that potentially resulted in a higher drop off rate.
 More importantly, the quality of responses were likely diminished to some unknown extent.
 Although it is possible to compare questions asked about Maricopa County, AZ to questions about one's local area, the quality of that comparison is limited by the unknown extent of fatigue induced by answering the same questions twice.
-It wasn't just that some questions were asked multiple times, almost all of the questions were duplicated; after completing a long series on Maricopa County, participants then answered the same questions about the local community.
-The rate to which participants dropped from the survey is \_\_\_, which suggests fatigue as an important factor.
-Survey fatigue is a known issue that should be taken into consideration.
-Comparison of treatment effects between the MC series and the local area series is undermined by the unknown influence that fatigue would have on response choices.
-Any differences couldn't confidently be attributed to "my area" vs Maricopa county.
-We also can't determine whether treatment effects are sustained when comparing the Maricopa County series to the local area series asked subsequently.
-We would have to assume the setting as irrelevant, which we can't reasonably do.
+It wasn't just that some questions were asked multiple times, almost all of the questions were duplicated.
+After completing a long series on Maricopa County, participants then answered the same questions about the local community.
+I haven't computed the rate to which participants dropped from the survey, yet items contain more missing values toward the end of the survey.
+Some participants dropped out, but some simply skipped a few items.
+The extent to which this occurred is minor, but it does suggest fatigue as a worthy of consideration.
 
@@
 
-The median age was 46 (mean age was 47).
-There was 51.7% (n = 658) women, 47% (n = 598) men, and approximately 1.3% who identified as either Non-binary/third gender (n = 7) or preferred not to say (n = 9).
-A large proportion of the sample identified as White or Caucasian (n = 975, 76.65%), while all other non-White respondents comprised 27.83% of the sample.
-Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised 13% of the sample; those with either degree at the Associate or Bachelor's level comprised 36.24%, while 22.25% had some college but no degree; and 28.46% had either a high school level or equivalent education or less than high school.
-The largest proportion of the sample identified as Democrat at 44.64%, followed by Republicans at 42.59%.
-The proportion of true Independents was 12.78%.
+The median age was 46 (mean age was $47$), $51.7\%$ ($n = 658$) women, $47\%$ ($n = 598$) men, and approximately $1.3\%$ who identified as either Non-binary/third gender ($n = 7$) or preferred not to say ($n = 9$).
+A large proportion of the sample identified as White or Caucasian ($n = 975, 76.65\%$), while all other non-White respondents comprised $27.83\%$ ($n = 297$) of the sample.
+Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised $13\%$ of the sample; those with either degree at the Associate or Bachelor's level comprised $36.24\%$, while $22.25\%$ had some college but no degree; and $28.46\%$ had either a high school level or equivalent education or less than high school.
+The largest proportion of the sample identified as Democrat at $44.64\%$, followed by Republicans at $42.59\%$.
+The proportion of true Independents^[Independent 'leaners' were grouped into the respective party affiliation in which they lean.] was $12.78\%$.
 
-\pagebreak
+```{r}
+#| label: tbl-demog
+#| tbl-cap: "Sample Demographics"
+#|
+
+# descriptive stats of categorical variables
+# best method for html document
+tbl.desc <- df |>  
+  labelled::set_variable_labels(
+    age_4cat = "Age group",
+    gender_3cat = "Gender",
+    race2 = "Race/Ethnicity",
+    race_wnw = "White or Non-White",
+    educ_4cat = "Education",
+    partyid_3cat = "Party ID",
+    milrelation  = "Military Relation"
+  ) |> 
+  gtsummary::tbl_summary(
+    by = group,
+    include = c(
+    age_4cat, 
+    gender_3cat, 
+    race2,
+    race_wnw,
+    educ_4cat, 
+    partyid_3cat,
+    milrelation),
+    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
+    missing = "ifany",
+    missing_text = "NA") |> 
+  gtsummary::add_n() |> 
+  gtsummary::add_overall() |> 
+  gtsummary::modify_header(label = "**Demographic**") |> 
+  gtsummary::bold_labels()
+
+gtsummary::as_gt(tbl.desc) |>  
+  gt::tab_footnote(
+    footnote = "Independents do not identify nor 'lean' toward either political party",
+    placement = "left"
+    ) |>  
+  gt::cols_align(align = 'left', columns = everything()) |> 
+  gt::tab_options(
+    table.font.size = "small",
+    data_row.padding = gt::px(1)
+  )
+
+```
+
+\newpage
+
+## Appendix C: Trust and Distrust {#sec-appendix-c}
+
+Polychoric correlation is a measure of association between two ordered categorical variables each assumed to represent (i.e., indicate, be influenced by) two normally distributed, continuous, latent variables.
+Due to the fact that each item is an ordered categorical variable assumed to represent one of two latent constructs (i.e., trust or distrust, respectively), I examined polychoric correlations between the items used to construct each scale.
+In addition, one set of the trust and distrust items pertained to Maricopa County, AZ, whereas the other set of items were identical except that these items pertained to one's local area.
+
+Since the two sets of items (AZ items and Local items) are, in theory, supposed to capture the same normally distributed continuous latent variables, then the polychoric inter-item correlations should be significantly associated, strong, and in the same direction for the items that measure trust regardless of whether the items pertain to AZ or one's local area  (likewise for distrust).
+Simply, trust/distrust in elections in AZ should strongly and positively be associated with trust/distrust in elections in one's local area.
+
+Additionally, the items that indicate trust should negatively correlate with items that indicate distrust.
+Furthermore, the strength of the negative correlations between trust and distrust should closely approximate if not match.
+
+```{r}
+#| label: fig-polycor
+#| fig-cap: "Polychoric Item Correlation Matrix"
+#| fig-pos: 'h'
+
+# Get polychoric item correlation matrix.
+item.cor <- df |>
+  select(q19:q24, -q23, q28_1:q28_5, q30:q35, -q34, q40_1:q40_5) |> 
+  # ensure factors are ordered factors
+  mutate(across(where(is.factor), ~factor(., ordered = T))) |> 
+  # adjust variable column names of items
+  dplyr::rename(
+    trustvote_az     = q19,
+    trustadmin_az    = q20,
+    truststaff_az    = q21,
+    trustprcss_az    = q22,
+    trusttech_az     = q24,
+    votefraud_az     = q28_1,
+    miscount_az      = q28_2,
+    turnedaway_az    = q28_3,
+    foreigntamp_az   = q28_4,
+    discourage_az    = q28_5,
+    trustvote_lcl    = q30,
+    trustadmin_lcl   = q31,
+    truststaff_lcl   = q32,
+    trustprcss_lcl   = q33,
+    trusttech_lcl    = q35,
+    votefraud_lcl    = q40_1,
+    miscount_lcl     = q40_2,
+    turnedaway_lcl   = q40_3,
+    foreigntamp_lcl  = q40_4,
+    discourage_lcl   = q40_5
+  ) |> 
+  correlation::correlation(
+    select = 
+      c("trustvote_az", "trustadmin_az", "truststaff_az", "trustprcss_az", "trusttech_az",
+        "votefraud_az", "miscount_az", "turnedaway_az", "foreigntamp_az", "discourage_az"),
+    select2 =
+      c("trustvote_lcl", "trustadmin_lcl", "truststaff_lcl", "trustprcss_lcl","trusttech_lcl",
+        "votefraud_lcl", "miscount_lcl", "turnedaway_lcl", "foreigntamp_lcl","discourage_lcl"),
+    method = "polychoric") |>
+  summary()
+
+# plot item correlations
+plot(item.cor) + theme(axis.text.x = element_text(angle = 45, vjust = 0.6))
+
+```
+
+Indeed, this is what is revealed by the correlation matrix (@fig-polycor).
+Trust items correlate positively, strongly, and are significant regardless of location at which the items pertain.
+The same goes for distrust items.
+Also, items meant to measure trust negatively correlate with the items that measure distrust.
+However, the positive correlations are not nearly as high as would be expected supposing that the items are nearly identical theoretical indicators of the same hypothetical constructs, i.e., trust and distrust respectively.
+
+If the items accurately measure trust/distrust in elections regardless of where those elections are said to take place, then positive correlations between the AZ and Local area items should approach perfect correlation as though the same exact questions were asked twice.
+This result, however, suggests that the location of which the survey items pertain (and perhaps other factors) makes a substantial difference in the pattern of responses, but also raises valid questions as to whether the items accurately measure the latent variable constructs in the first place.
 

### 2025-03-01 docs/src/01-data.R

@@ -1,909 +1,0 @@
-# using data exported from Qualtrics on 2024-10-23
-# The most recent (i.e., last) response was recorded 2024-09-18 at 6:40pm (1840)
-# When exporting the data, Qualtrics allows me to recode 'seen but unanswered'
-# questions with code 99. I downloaded the data again just for that because I
-# want to see how many of the missing values in my 2024-09-11 dataset are
-# attributed to people who skipped survey questions.
-
-# load packages ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
-library(tidyverse)
-library(haven)
-library(surveytoolbox)
-library(labelled)
-library(sjlabelled)
-
-# load data ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
-
-# load raw SPSS export (includes display order vars)
-# downloaded on 2024-10-29 at 12:02 PM
-raw_spss <- haven::read_sav("data-raw/VMF_Election_Worker_Recruitment_Survey_with_display_order_20241029_T12.02.sav")
-
-# load raw SPSS export (doesn't include display order vars)
-# downloaded 2024-10-23 at 1:54 PM
-# raw_spss3 <- haven::read_sav(file = "data-raw/VMF_Election_Worker_Recruitment_Survey_2024-10-23_13.54.sav")
-
-# despite being a .sav file imported using `haven::read_sav()`, 
-# the data set is not "haven_labelled"
-# haven::is.labelled(raw_spss)
-
-# create data dictionary of raw SPSS data set ::::::::::::::::::::::::::::::####
-
-# A data dictionary contains metadata about the data. The
-# `labelled::generate_dictionary` function is used to create a data
-# dictionary. (alt. `surveytoolbox::data_dict`)
-# a data frame is loaded into the R environment with the number of
-# observations equal to number of variables in the original data set.
-# NOTE: surveytoolbox::data_dict function is used here because the resulting
-# dataframe can be saved as a .csv
-raw_spss_dict <- raw_spss |> surveytoolbox::data_dict()
-
-# save data dictionary of raw_spss dataset download
-write.csv(raw_spss_dict, file = "data/raw_spss_dict.csv")
-
-# create and save survey codebook ::::::::::::::::::::::::::::::::::::::::::####
-
-# this includes only the survey questions: question number (var), the question
[…]

### 2025-03-01 src/02-data-postprocessing.R

@@ -125,10 +125,10 @@ df <- df |>
 
 
 # check to confirm that all party ID modified variables match
-df |> 
-  select(partyid_3cat, partyid_5cat, party_strength, 6:12) |> 
-  group_by(party_strength, partyid_5cat) |> 
-  count(partyid_3cat)
+# df |> 
+#   select(partyid_3cat, partyid_5cat, party_strength, 6:12) |> 
+#   group_by(party_strength, partyid_5cat) |> 
+#   count(partyid_3cat)
 
 # reorder `party_strength`, `partyid_3cat`, and `partyid_5cat` factor levels
 # order so that "Independent" # becomes the reference level for each factor
@@ -141,9 +141,9 @@ df <- df |>
          partyid_5cat   = forcats::fct_relevel(partyid_5cat, "Independent", after = 0L))
 
 # note how it is now placed as the first level that appears
-df |> 
-  select(party_strength) |>  
-  count(party_strength)
+# df |> 
+#   select(party_strength) |>  
+#   count(party_strength)
 
 
 # collapse factor levels of safety items (except q38)
@@ -214,3 +214,155 @@ df <- df |>
 # variable order does not matter.
 df <- df |> 
   labelled::set_variable_labels(!!!df_labels)
+
+
+# Construct composite score variables using `psych::scoreItems` ::::::::::::####
+
+# create a list of scoring keys for scales for AZ and Local area
+conf.keys <- list(
+  conf.az = c("q19.r","q20.r","q21.r","q22.r","q24.r",
+              "q28_1.r","q28_2.r","q28_3.r","q28_4.r","q28_5.r"),
+  conf.local = c("q30.r","q31.r","q32.r","q33.r","q35.r",
+                 "q40_1.r","q40_2.r","q40_3.r","q40_4.r","q40_5.r"),
+  trust.az = c("q19.r","q20.r","q21.r","q22.r","q24.r"),
+  trust.local = c("q30.r","q31.r","q32.r","q33.r","q35.r"),
+  distrust.az = c("q28_1.n","q28_2.n","q28_3.n","q28_4.n","q28_5.n"),
+  distrust.local = c("q40_1.n","q40_2.n","q40_3.n","q40_4.n","q40_5.n")
+)
+
+
+conf.sum.scores <- psych::scoreItems(
+  keys = conf.keys,
+  items = df,
+  totals = T,
+  missing = T,
+  impute = "median"
+)
+
+# The item by scale correlations for each item, corrected for item overlap by
+# replacing the item variance with the smc for that item.
[…]

### 2025-03-01 src/03-scores.R

@@ -1,153 +1,0 @@
-set.seed(1234)
-
-
-# Construct composite score variables using `psych::scoreItems` ::::::::::::####
-
-# create a list of scoring keys for scales for AZ and Local area
-conf.keys <- list(
-  conf.az = c("q19.r","q20.r","q21.r","q22.r","q24.r",
-              "q28_1.r","q28_2.r","q28_3.r","q28_4.r","q28_5.r"),
-  conf.local = c("q30.r","q31.r","q32.r","q33.r","q35.r",
-                 "q40_1.r","q40_2.r","q40_3.r","q40_4.r","q40_5.r"),
-  trust.az = c("q19.r","q20.r","q21.r","q22.r","q24.r"),
-  trust.local = c("q30.r","q31.r","q32.r","q33.r","q35.r"),
-  distrust.az = c("q28_1.n","q28_2.n","q28_3.n","q28_4.n","q28_5.n"),
-  distrust.local = c("q40_1.n","q40_2.n","q40_3.n","q40_4.n","q40_5.n")
-)
-
-
-conf.sum.scores <- psych::scoreItems(
-  keys = conf.keys,
-  items = df,
-  totals = T,
-  missing = T,
-  impute = "median"
-)
-
-# The item by scale correlations for each item, corrected for item overlap by
-# replacing the item variance with the smc for that item.
-# Note that, when SMC < 0, SMC were set to .0
-# item.cor.corrected <- conf.sum.scores$item.corrected
-
-conf.mean.scores <- psych::scoreItems(
-  keys = conf.keys,
-  items = df,
-  totals = F,
-  missing = T,
-  impute = "mean"
-)
-
-
-
-# head(conf.sum.scores$scores)
-# conf.sum.scores$scores[,1] # conf.sum.az
-# conf.sum.scores$scores[,2] # conf.sum.lcl
-# conf.sum.scores$scores[,3] # trust.az
-# conf.sum.scores$scores[,4] # trust.lcl
-# conf.sum.scores$scores[,5] # distrust.az
-# conf.sum.scores$scores[,6] # distrust.lcl
-# 
-# head(conf.mean.scores$scores)
-# conf.mean.scores$scores[,1] # conf.sum.az
-# conf.mean.scores$scores[,2] # conf.sum.lcl
-# conf.mean.scores$scores[,3] # trust.az
-# conf.mean.scores$scores[,4] # trust.lcl
-# conf.mean.scores$scores[,5] # distrust.az
[…]

### 2025-03-01 src/04-likert_plots.R

@@ -1,727 +1,0 @@
-# there's a lot of code here. It deserves its own script.
-
-set.seed(1234)
-library(tidyverse)
-library(patchwork)
-# library(pewmethods)
-
-
-# prep :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
-
-
-# shorten and 'unify' factor levels
-# Note: this removes variable labels
-df <- df |>
-  # use `pewmethods` to preserve order of factor levels
-  mutate(across(c(q19, q20, q21, q22, q23, q24,
-                  q30, q31, q32, q33, q34, q35),
-                ~pewmethods::fct_case_when(
-    .x %in% c("Not at all confident",
-              "Not at all committed",
-              "Not at all concerned") ~ "Not at all confident",
-    .x %in% c("Not too confident",
-              "Not too committed",
-              "Not too concerned",
-              "Somewhat unconcerned") ~ "Not too confident",
-    .x %in% c("Somewhat confident",
-              "Somewhat committed",
-              "Somewhat concerned") ~ "Somewhat confident",
-    .x %in% c("Very confident",
-              "Very committed",
-              "Very concerned") ~ "Very confident",
-    TRUE ~ NA
-  ))) |> 
-  # unify factor levels
-  mutate(across(c(q25, q36), ~ pewmethods::fct_case_when(
-    .x == "Very concerned" ~ "Very concerned",
-    .x == "Somewhat concerned" ~ "Somewhat concerned",
-    .x %in% c("Not too concerned", "Somewhat unconcerned") ~ "Not too concerned",
-    .x == "Not at all concerned" ~ "Not at all concerned",
-    TRUE ~ NA))) |>
-  # reverse factor levels
-  mutate(across(c(q25, q36), ~forcats::fct_rev(.)))
-
-# Return labels to df
-df <- df |> 
-  labelled::set_variable_labels(!!!df_labels)
-
-
-# set ggplot theme that will be used for every plot
-# theme_get()
-old <- theme_set(theme_bw()) # capture current theme
-
-# set/update new theme
-theme_set(
-  new = ggplot2::theme_bw(base_family = 'Palatino Linotype')+
-    theme(legend.position = 'bottom', axis.text.y.left = element_blank()))
-
-# assign items to particular vectors to avoid copy/pasting
-trust.az.items <- df |> select(q19, q20, q21, q22, q24) |> colnames() |> dput()
[…]

### 2025-03-01 src/funs.R

@@ -110,6 +110,7 @@ run_crab <- function(data, row, col){
 likert_plot <- function(data, x, ...,  
                         symmetric = FALSE,
                         variable_labels = NULL,
+                        label_size = 3.0,
                         vline = FALSE,
                         title = waiver(), 
                         subtitle = waiver(),
@@ -124,7 +125,7 @@ likert_plot <- function(data, x, ...,
     # customize color
     ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
     # custom theme
-    theme_bw(base_family = "Palatino Linotype")+
+    theme_bw(base_family = "TeX Gyre Pagella")+
     theme(
       legend.position = 'bottom',    # place legend on bottom
       axis.text.x = element_blank(), # remove percentage text along x-axis

### 2025-03-01 notebooks/02-tables.qmd
checkpoint

@@
 # quick, informative, easy table of sample demographics w/ some other questions.
-tbl1 <- data |>  
+
+# best method for html document
+tbl.desc <- data |>  
   labelled::set_variable_labels(
-    age_cat = "Age group, in years"
+    age_4cat = "Age group, in years",
+    gender_3cat = "Gender",
+    race2 = "Race/Ethnicity",
+    educ_4cat = "Education",
+    partyid_3cat = "Party ID"
   ) |> 
   gtsummary::tbl_summary(
-    by = qset,
+    by = group,
     include = c(
-    qset,
-    age_cat, 
+    age_4cat, 
     gender_3cat, 
-    race, 
+    race2, 
     educ_4cat, 
-    partyid_3cat,
-    ideo,
-    ideolean,
-    voted2020,
-    choice2020, 
-    voteintent,
-    milserv1,
-    milserv2,
-    milservfam),
+    partyid_3cat),
     statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
-    type = list(milserv1 ~ "categorical",
-
-                milserv2 ~ "categorical",
-                milservfam ~"categorical"), 
-    missing = "no") |> 
+    missing = "ifany",
+    missing_text = "NA") |> 
   gtsummary::add_n() |> 
@@
 
-gtsummary::as_gt(tbl1) |>  
-  gt::tab_footnote(
-    footnote = "'true' Independents do not identify nor 'lean' toward either political party",
+gtsummary::as_gt(tbl.desc) |>  
+  gt::tab_footnote(
+    footnote = "Independents do not identify nor 'lean' toward either political party",
     placement = "left"
@@
   )
+
+gtsummary::as_kable_extra(
+  tbl.desc, 
+  booktabs = T,
+  digits = 2,
+  addtl_fmt = T,
+  linesep = ""
+) |> 
+  kableExtra::kable_styling(
+    latex_options = c("striped", "scale_down"),
+    font_size = 8)
 
@@
 # Likert table summary of Trust and confidence variables
-tbl_tc <- data |> 
-  select(q19:q24) |>
-  gtsummary::tbl_likert(
-    statistic = ~"{n} ({p}%)", 
-    label = list(q19 = "Votes will be counted as intended",
-                 q20 = "Election officials will do good job",
-                 q21 = "Election workers will be committed",
-                 q22 = "Voting process will be fair",
-                 q23 = "Voting outcome will be fair",
-                 q24 = "Election technology will be secure"))
-
-# add continuous summary of Likert scores. Merge tables into one
-tbl_tc_summary <- list(
-  tbl_tc,
-  gtsummary::tbl_wide_summary(
-    data |>
-      select(q19:q24) |> mutate(across(where(is.factor), as.numeric)),
-    statistic = c("{mean}", "{sd}"),
-    label = list(
-      q19 = "Votes will be counted as intended",
-      q20 = "Election officials will do good job",
-      q21 = "Election workers will be committed",
-      q22 = "Voting process will be fair",
-      q23 = "Voting outcome will be fair",
-      q24 = "Election technology will be secure"
-    ),
-    type = ~ "continuous"
-  )
-) |>
-  gtsummary::tbl_merge(tab_spanner = F) |> 
-  gtsummary::modify_header(label="")
-
-# print as huxtable and modify using `huxtable` R package
-gtsummary::as_hux_table(tbl_tc_summary) |>
-  huxtable::set_width(0.6) |> 
-  huxtable::set_col_width(rep(c(0.4))) |> 
-  huxtable::theme_article() |> 
-  huxtable::set_position("center")
+# best method for html document
+tbl.desc <- data |>  
+  labelled::set_variable_labels(
+    age_4cat = "Age group, in years",
+    gender_3cat = "Gender",
+    race2 = "Race/Ethnicity",
+    educ_4cat = "Education",
+    partyid_3cat = "Party ID"
+  ) |> 
+  gtsummary::tbl_summary(
+    by = group,
+    include = c(
+    age_4cat, 
+    gender_3cat, 
+    race2, 
+    educ_4cat, 
+    partyid_3cat),
+    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
+    missing = "ifany",
+    missing_text = "NA") |> 
+  gtsummary::add_n() |> 
+  gtsummary::add_overall() |> 
+  gtsummary::modify_header(label = "**Variable**") |> 
+  gtsummary::bold_labels()
+
+gtsummary::as_gt(tbl.desc) |>  
+  gt::tab_footnote(
+    footnote = "Independents do not identify nor 'lean' toward either political party",
+    placement = "left"
+    ) |>  
+  gt::cols_align(align = 'left', columns = everything()) |> 
+  gt::tab_options(
+    table.font.size = "small",
+    data_row.padding = gt::px(1)
+  )
+
+gtsummary::as_kable_extra(
+  tbl.desc, 
+  booktabs = T,
+  digits = 2,
+  addtl_fmt = T,
+  linesep = ""
+) |> 
+  kableExtra::kable_styling(
+    latex_options = c("striped", "scale_down"),
+    font_size = 8)
 

### 2025-03-01 notebooks/03-figures.qmd
checkpoint

--- 2024-10-16 notebooks/03-plots.qmd
@@
 ```
+
+```{r}
+#| label: fig-itemcor
+#| fig-cap: "Inter-item correlations between AZ and local area items"
+
+# Inter-item correlations between AZ and Local items
+# use the `easystats` correlation package
+item.cor <- df |>
+  dplyr::rename(
+    trustvote_az     = q19,
+    trustadmin_az    = q20,
+    truststaff_az    = q21,
+    trustprcss_az    = q22,
+    trusttech_az     = q24,
+    votefraud_az     = q28_1,
+    miscount_az      = q28_2,
+    turnedaway_az    = q28_3,
+    foreigntamp_az   = q28_4,
+    discourage_az    = q28_5,
+    trustvote_lcl    = q30,
+    trustadmin_lcl   = q31,
+    truststaff_lcl   = q32,
+    trustprcss_lcl   = q33,
+    trusttech_lcl    = q35,
+    votefraud_lcl    = q40_1,
+    miscount_lcl     = q40_2,
+    turnedaway_lcl   = q40_3,
+    foreigntamp_lcl  = q40_4,
+    discourage_lcl   = q40_5
+  ) |> 
+  correlation::correlation(
+    select = 
+      c("trustvote_az", "trustadmin_az", "truststaff_az", "trustprcss_az", "trusttech_az",
+        "votefraud_az", "miscount_az", "turnedaway_az", "foreigntamp_az", "discourage_az"),
+    select2 =
+      c("trustvote_lcl", "trustadmin_lcl", "truststaff_lcl", "trustprcss_lcl","trusttech_lcl",
+        "votefraud_lcl", "miscount_lcl", "turnedaway_lcl", "foreigntamp_lcl","discourage_lcl"),
+    method = "polychoric") |>
+  summary()
+
+layers <- correlation::visualisation_recipe(
+  item.cor, labs = list(title = "Polychoric Item Correlation Matrix"))
+layers
+
+plot(layers) + theme(axis.text.x = element_text(angle = 45, vjust = 0.6))
+
+```
+
+# Likert Plots
+
+```{r}
+#| label: fig-trustlikert
+#| fig-cap: "Trust in Election Administration by Experiment Condition"
+#| fig-height: 4.5
+#| fig-pos: "h"
+
+# Likert plot of trust and confidence in election admin comparing treatment and
+# control groups
+trust.likert.treat.az <- df |>
+  # relabel factor labels for plotting
+  mutate(across(
+    c(q19, q20, q21, q22, q23, q24, q30, q31, q32, q33, q34, q35),
+    ~ pewmethods::fct_case_when(
+      .x %in% c("Not at all confident", "Not at all committed") ~ "Not at all confident",
+      .x %in% c("Not too confident", "Not too committed") ~ "Not too confident",
+      .x %in% c("Somewhat confident", "Somewhat committed") ~ "Somewhat confident",
+      .x %in% c("Very confident", "Very committed") ~ "Very confident",
+      TRUE ~ NA
+    )
+  )) |>
+  ggstats::gglikert(
+    include = c(q19, q20, q21, q22, q24),
+    y = 'group',
+    facet_rows = vars(.question),
+    symmetric = F,
+    labels_size = 2.5,
+    add_totals = T
+  ) +
+  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+  # ggplot2::scale_fill_brewer(palette = "Greys")+
+  labs(subtitle = str_wrap("Maricopa County, Arizona", width = 95)) +
+  theme_bw() +
+  theme(
+    text = element_text(family = "Palatino Linotype"),
+    legend.position = 'bottom',
+    axis.text.x = element_blank(), # remove percentage text along x-axis
+    strip.text.y.right = element_blank()
+  )
+
+# confidence in elections between experiment conditions for items concerning local area
+trust.likert.treat.lcl <- df |>
+  # relabel factor labels for plotting
+  mutate(across(
+    c(q19, q20, q21, q22, q23, q24, q30, q31, q32, q33, q34, q35),
+    ~ pewmethods::fct_case_when(
+      .x %in% c("Not at all confident", "Not at all committed") ~ "Not at all confident",
+      .x %in% c("Not too confident", "Not too committed") ~ "Not too confident",
+      .x %in% c("Somewhat confident", "Somewhat committed") ~ "Somewhat confident",
+      .x %in% c("Very confident", "Very committed") ~ "Very confident",
+      TRUE ~ NA
+    )
+  )) |>
+  ggstats::gglikert(
+    include = c(q30, q31, q32, q33, q35),
+    y = 'group',
+    facet_rows = vars(.question),
+    variable_labels = c(
+      q30 = "Votes counted as intended",
+      q31 = "Election officials will do good job",
+      q32 = "Election workers will be committed",
+      q33 = "Voting process will be fair",
+      q35 = "Election technology will be secure"
+    ),
+    facet_label_wrap = 10,
+    labels_size = 2.5,
+    symmetric = F,
+    add_totals = T
+  ) +
+  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+  # ggplot2::scale_fill_brewer(palette = "Greys")+
+  labs(subtitle = str_wrap("Local Area", width = 95)) +
+  theme_bw() +
+  theme(
+    text = element_text(family = "Palatino Linotype"),
+    legend.position = 'bottom',
+    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
+    axis.text.x = element_blank(), # remove percentage text along x-axis
+    strip.text.y.right = element_text(angle = 0, size = 8)
+  )
+
+# trust.likert.treat.az
+# trust.likert.treat.lcl
+
+# Instead of two separate plots, arrange into one plot while remaining separated
+# use `ggpubr` package to print multiple plots side-by-side (or alt. row-by-row)
+ggpubr::ggarrange(
+  trust.likert.treat.az,
+  trust.likert.treat.lcl,
+  ncol = 2,
+  common.legend = T,
+  legend = "bottom", 
+  font.label = list(family = "Palatino Linotype")
+) +
+  # add figure footnote annotation
+  patchwork::plot_annotation(
+    caption = str_wrap("Missing values removed. Displays percent proportions of responses by experiment condition and combined percentage proportions for two categories.",
+               width = 85), theme = theme(text = element_text(family = "Palatino Linotype")))
+
+```
+
+```{r}
+#| label: fig-distrustlikert
+#| fig-cap: "Disrust in Election Administration by Experiment Condition"
+#| fig-height: 4.5
+#| fig-pos: "h"
+
+# distrust in elections in AZ by experimental condition
+distrust.likert.az <- df |>
+  # reverse levels of factor vars to show positive difference in "not likely"
+  mutate(across(c(q28_1:q28_5), ~forcats::fct_rev(.))) |> 
+  ggstats::gglikert(
+    include = c(q28_1:q28_5),
+    y = 'group',
+    facet_rows = vars(.question),
+    variable_labels = c(
+      q28_1 = "Voter fraud will occur",
+      q28_2 = "Many votes won't be counted",
+      q28_3 = "Many voters will be turned away",
+      q28_4 = "Foreign Interference",
+      q28_5 = "Election officials will discourage voting"),
+    facet_label_wrap = 10,
+    labels_size = 2.5,
+    symmetric = F,
+    add_totals = T
+  ) +
+  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+  # ggplot2::scale_fill_brewer(palette = "Greys")+
+  labs(subtitle = str_wrap("Maricopa County, Arizona", width = 95)) +
+  theme_bw() +
+  theme(
+    text = element_text(family = "Palatino Linotype"),
+    legend.position = 'bottom',
+    axis.text.x = element_blank(), # remove percentage text along x-axis
+    strip.text.y.right = element_blank()
+  )
+
+# distrust in elections in Local area by experimental condition
+distrust.likert.lcl <- df |>
+  # reverse levels of factor vars to show positive difference in "not likely"
+  mutate(across(c(q40_1:q40_5), ~forcats::fct_rev(.))) |> 
+  ggstats::gglikert(
+    include = c(q40_1:q40_5),
+    y = 'group',
+    facet_rows = vars(.question),
+    variable_labels = c(
+      q40_1 = "Voter Fraud will occur",
+      q40_2 = "Many Votes won't be counted",
+      q40_3 = "Many voters will be turned away",
+      q40_4 = "Foreign Interference",
+      q40_5 = "Election officials will discourage voting"),
+    facet_label_wrap = 10,
+    labels_size = 2.5,
+    symmetric = F,
+    add_totals = T
+  )+
+  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+  # ggplot2::scale_fill_brewer(palette = "Greys")+
+  labs(subtitle = str_wrap("Local Area", width = 95)) +
+  theme_bw() +
+  theme(
+    text = element_text(family = "Palatino Linotype"),
+    legend.position = 'bottom',
+    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
+    axis.text.x = element_blank(), # remove percentage text along x-axis
+    strip.text.y.right = element_text(angle = 0, size = 8)
+  )
+
+# Instead of two separate plots, arrange into one plot while remaining separated
+# use `ggpubr` package to print multiple plots side-by-side (or alt. row-by-row)
+ggpubr::ggarrange(
+  distrust.likert.az,
+  distrust.likert.lcl,
+  ncol = 2,
+  common.legend = T,
+  legend = "bottom", 
+  font.label = list(family = "Palatino Linotype")
+) +
+  # add figure footnote annotation
+  patchwork::plot_annotation(
+    caption = str_wrap("Missing values removed. Displays percent proportions of responses by experiment condition and combined percentage proportions for two categories.",
+               width = 85), theme = theme(text = element_text(family = "Palatino Linotype")))
+
+```

### 2025-03-01 hours.R

@@ -1,0 +1,153 @@
+# logging hours worked
+
+# create data.frame (or `tbl_df`)
+hours <- tibble::tribble(
+  ~ date,
+  ~ proj,
+  ~ weekday,
+  ~ start,
+  ~ end,
+  ~ duration.hours,
+  ~ duration.period,
+  ~ cumhours_per_proj
+)
+
+
+# d = Date
+d <- timestamp(
+  stamp = format(Sys.time(), "%Y-%m-%d"),
+  prefix = NULL,
+  suffix = NULL
+) |>
+  as.Date()
+
+# t1 = START TIME
+# NOTE: Run this once you START doing stuff to stamp "clock in" time
+t1 <- timestamp(
+  stamp = format(Sys.time(), "%H:%M:%S"),
+  prefix = NULL,
+  suffix = NULL
+) |> hms::as_hms()
+
+# alternative: input time manually  
+t1 <- hms::as_hms("09:20:55")
+
+# t2 = END TIME
+# NOTE: Run this once you STOP doing stuff to stamp "clock out" time
+t2 <- timestamp(
+  stamp = format(Sys.time(), "%H:%M:%S"),
+  prefix = NULL,
+  suffix = NULL
+) |> hms::as_hms()
+
+
+# tdiff = duration.hours
+tdiff <- round(difftime(t2, t1, units = "hours"), 2)
+
+# project/task worked on
+
+proj <- "vets survey"
+proj <- "text analysis"
+proj <- "prospectus"
+
+# add today's time stamps to data frame and add in additional variables
+hours <- hours |>
+  # add row to time sheet
+  dplyr::add_row(
+    date = d,
+    proj = proj,
+    start = t1,
+    end = t2,
+    duration.hours = tdiff
+  ) |>
+  
+  # add in column denoting day of the week
+  dplyr::mutate(weekday = lubridate::wday(date, label = T, abbr = F),
+                .before = start) |>
+  
+  # convert `duration.hours` to class `dbl` instead of class `difftime`
+  # dplyr::mutate(duration.hours = as.numeric(duration.hours), .keep = "unused") |>
+  
+  # see `duration.hours` as period with hours, minutes, and seconds
+  dplyr::mutate(duration.period = lubridate::as.period(duration.hours),
+                .after = duration.hours) |>
+  
+  # group by project/task in order to calculate cumulative hours worked on task
+  dplyr::group_by(proj) |>
+  
[…]

### 2025-03-11 notebooks/01-data-import-clean-process.qmd
Removed and added a slew of files

@@
 title: Data Import, Clean, and Process
-author: Isaiah
 format: 
-  html: 
+  bookup-html:
     code-fold: false
@@
 
+## Set up
+
 This document describes and executes the cleaning and processing of the survey data set downloaded from Qualtrics on 2024-10-23.
@@
 
+```{r}
+#| label: setup
+#| include: true
+#| eval: true
+#| echo: true
+
+set.seed(1234)
+
+# load packages
+library(tidyverse)
+
+```
+
 ## Load data
@@
 # downloaded on 2024-10-29 at 12:02 PM
-raw_spss <- haven::read_sav("data-raw/VMF_Election_Worker_Recruitment_Survey_with_display_order_20241029_T12.02.sav")
+raw_spss <- haven::read_sav("data-raw/vmf_election_worker_recruitment_survey_raw_spss_sanitized_20241029_T12.02.sav")
 
@@
 A data dictionary contains metadata about the data.
-The `labelled::generate_dictionary` function is used to create a data dictionary.
-A dataframe is loaded into the R environment with the number of observations equal to number of variables in the original data set.
-One problem that I encountered was that I was unable to quickly save the data dictionary generated using the `labelled` R package.
-As an alternative, I utilized the `data_dict()` function from the R package `surveytoolbox` in order to save the dictionary as a `.csv` file.
+The `labelled::generate_dictionary` function is used to create a data dictionary (alternatively, use the `data_dict()` function from R package [surveytoolbox](https://martinctc.github.io/surveytoolbox/)).
+This function produces a dataframe into the R environment with the number of observations (rows) equal to number of variables (columns) in the original data set.
+For ease, I prefer to save the codebook/data dictionary as a `.csv` file.
+In order to do so, ensure that the function `labelled::convert_list_columns_to_character()` is run on the data dictionary which allows you to save the data dictionary as a `.csv` file.
+Alternatively, the
+function `surveytoolbox::data_dict()` permits saving as a .csv file without the
+additional step.
+
+Also note that I use the native R pipe format ` |> ` (tip: try hotkey `CTRL + .`), which is essentially equivalent to the `magrittr` forward-pipe operator ` %>% `.
 
@@
 #| label: raw-data-dict
-
-# data dictionary from labelled package. Won't save as .csv file
-raw_spss_dict <- raw_spss |> labelled::generate_dictionary()
-
-# data dictionary from labelled package. Will save as .csv file
-raw_spss_dict <- raw_spss |> surveytoolbox::data_dict()
+#| echo: true
+
+# data dictionary from labelled package.
+raw_spss_dict <- raw_spss |> 
+  labelled::generate_dictionary() |> 
+  # this allows me to save dictionary as .csv file
+  labelled::convert_list_columns_to_character()
+
+# alternative
+# raw_spss_dict <- raw_spss |> surveytoolbox::data_dict()
 
@@
 
-The data dictionary is the same as a codebook, but I also wanted to have a codebook that contained only the survey questions, variable labels (i.e., question text), responses (value labels), and associated values.
+The data dictionary is the same as a codebook, but I also wanted to have a codebook that contained **only** the survey questions, variable labels (i.e., question text), responses (value labels), and associated values.
 So the saved `codebook` contains only the survey questions and the two grouping variables (`qset` and `group`).

### 2025-03-11 notebooks/appendix_A.qmd
Removed and added a slew of files

--- 2025-02-26 index.qmd
@@
 ---
-title: title
-subtitle: subtitle
-shorttitle: A Short title # aog-article-pdf
-shortauthors: Isaiah      # aog-article-pdf
-authors:
-  - name: Isaiah Espinoza
-    email: gespinoz@umd.edu
-    roles: author
-    affiliation:
-      - name: University of Maryland
-        department: Department of Government and Politics
-        city: College Park
-        state: MD
-        country: US
-reference-section-title: References
-date: "2024-10-16"
-date-modified: today
-knitr: 
-  opts_chunk: 
-    dev: "ragg_png" # same as knitr::opts_chunk$set(dev = "ragg_png")
-editor_options: 
-  chunk_output_type: console
+title: "Appendix A: Survey Experiment Vignettes and Survey Items"
+format:
+  bookup-html: 
+    toc: true
+    toc-depth: 3
+    embed-resources: false
+    embed-fonts: true
+    link-citations: true
+    smooth-scroll: true
+    link-external-newwindow: true
+    citations-hover: true
+    footnotes-hover: false
+    code-fold: show
+    code-overflow: wrap
+    code-tools: true
+    theme: 
+      light: [bookup.scss]
+      dark: [bookup.scss, bookup_dark.scss]
 ---
 
-```{r}
-#| label: setup
-#| include: false
-
-set.seed(1234)
-
-# load packages
-library(tidyverse)
-library(easystats)
-library(patchwork)
-
-# load data
-load("data/research-paper-df-20250203.Rdata") #df
-
-# load data dictionary/codebook
-codebook <- read.csv("data/survey_codebook.csv")
-df_dict <- read.csv("data/df_dictionary.csv")
-
-```
-
-\pagebreak
-
-## Introduction
-
-Election administration officials make efforts to sustain public trust and confidence in the fairness and accuracy of elections, and attempt to boost such confidence where it may be deprived.
-Concerns for safety have developed among election staff and voters in more recent elections.
-Regular measures are taken to enhance the *trustworthiness*[^1] of the electoral process through practices meant to improve the conduct, transparency, or overall administration of elections in the United States.
-
-Although election officials undertake great efforts to enhance the trustworthiness of election administration, public *trust* in elections is a psychological construct influenced by many things outside of election official control such as partisanship or elite rhetoric [@hooghe2018; @sances2015].
-Moreover, a person's evaluation of the election in hindsight is often influenced by the election outcome itself [@daniller2019; @stewart2022].
-Thus, measures taken by election officials can be undermined, trivialized, or made irrelevant depending on how one feels after the election results have come out.
-
-Such volatile attitudes and evaluations post-election can leave a lasting impression that election officials must contend with upon the next election cycle [@levendusky2024; @bowler2024].
-For instance, we have witnessed many people's outright refusal to accept the 2020 U.S.
-election results as legitimate despite consistent review of the evidence confirming the results as fair and accurate.
-Such a case demonstrates that public trust in elections is, at best, only partial to trustworthiness of election administration in the United States[^2].
-
-Even though election officials can do a lot to secure election integrity, there's not much they can do to cement public confidence after election night passes.
-At best, election officials can ease public insecurities prior to election night.
-
-One point of contention that election officials have faced in the past regard evaluation of election workers.
-Previous literature has focused on how voter interaction with election workers [@claassen2008], or the voter experience generally [@atkeson2007], influences evaluations of election administration.
-As such, election worker competency has been examined as a factor significant to evaluations of performance of elections [@hall2007; @hall2009].
-However, considering that individual perceptions and preconceived notions play a huge role in cognition [@cikara2014; @vanbavel2021], it is reasonable to expect that the group an election worker hails from would be an important influence upon the voter's evaluation of the electoral process.
-
-Supposing such is the case, we can expect that information about *who* (i.e., which groups) election officials are targeting in publicized recruitment efforts would lessen particular election insecurity, and concurrently, boost confidence.
-That is to say, it is reasonable to expect that telling people *who* will be working and volunteering as election staff would ease election insecurity, and therefore improve confidence that the election will be conducted fairly, accurately, and safe for all involved.
-
-In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
-Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity to a limited extent.
-Expectations of electoral fraud and concerns for voter safety were lower among those who read a fabricated announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned.
-Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
-
-This paper is structured as follows.
-First, I provide a brief background on public trust in election administration.
-I synthesize a review of relevant literature with a focus on how political and social science has conceptualized and ascertained public trust in elections.
-Next, I supply reasoning for why military veterans are singled out as the relevant subset of the population in this study.
-I then explicitly provide the simple theory and testable hypotheses of the study before moving on to describe the design of the survey, the measurement instruments therein, and the conceptual and operational definitions of the variables of interest.
-I explain my reasoning and method for constructing the primary dependent variable, which I broadly refer to as *confidence in elections*.
-I preview the different methods of analysis alongside presentation of the results.
-Before concluding, I dedicate time to discuss the limitations of the study and lessons learned.
-I close by offering my interpretation of the results and suggest potential avenues for future inquiry.
-
-## Background: Election Administration and Public Confidence
-
-Election officials have tried hard to inspire confidence in the administration and conduct of elections by improving the degree to which elections are trustworthy.
-Development and implementation of procedures such as post-election auditing of ballots and logic-and-accuracy testing of ballot tabulation equipment are prominent examples adding to the long history of efforts to enhance the trustworthiness of election administration in the United States.
-
-Prior to the year 2000, one of the main issues facing election administration was recruiting enough election workers to volunteer at the polls (i.e., poll workers) [@maidenberg1996].
-Election worker recruitment is still much of an issue in the current era as it was then, perhaps worse [@ferrer2024].
-In addition to ensuring election admin offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections.
-In particular, voting technology [@herrnson2009] and election worker competence was a of interest in election studies [@claassen2008; @hall2009; @hall2007].
-Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007].
-
-In 2024, election officials made valiant efforts to boost public confidence elections within an intensified political climate that appeared quite hostile to election officials [@edlin2024; @brennancenterforjustice2024].
-Although polling around the time indicated that most people thought that U.S.
-elections would be run at least somewhat well [@nadeem2024], many election officials nationwide took efforts to assuage the worry of those most skeptical.
-
-Election anxiety was high in the lead up to the 2024 elections in the United States.
-Concerns for voter safety and the prospect of political violence remained prescient and compelled many local officials to prepare for the worst [@edlin2024; @doubek2024].
-Election officials in Washoe County, Nevada, installed panic buttons for election staff that would alert a monitoring center to summon law enforcement [@lincoln2024].
-Nevada also passed a law making it a felony to harass, threaten, or intimidate election workers [@nevadasecretaryofstate2023].
-Leading up to election day, news outlets reported that election work had become a seemingly dangerous job [@wire2024].
-A Brennan Center survey report stated that, "...large numbers of election officials report having experienced threats, abuse, or harassment for doing their jobs" [@edlin2024].
-Concerns over the fairness of elections and accuracy of vote counts intensified, heightening concerns over the prospect of political violence and, in turn, increased worry for the safety of voters and election workers alike.
-
-Suffice to say, pre-election anxiety consists of more than confidence in fairness and accuracy of vote counts in light of added safety concerns.
-It is not hard to recognize that increased tension in the pre-election period makes for a volatile political environment.
-Sustaining trustworthiness in election administration is only more difficult in an environment where turnover of election workers increases and the struggle to recruit volunteers worsens in light of safety concerns.
-Since election worker performance is significant to public evaluation of elections, added safety concerns that drive out election staff and repel volunteers can only detract from trustworthiness of the institution.
-
-## Literature Reivew
-
-Trust and confidence in the conduct of elections concerns aspects of elections that fall squarely within the institution of election administration.
-At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended).
-Or in other words, by the extent the public is confident in the accurate administration of elections.
-
-Assessing the public's *trust* in elections has not been straightforward, however.
-Inquiry into public trust in elections has been approached by scholars of political science in many different ways [@cook2005; @hardin2004], often distinguishable by the scope of the research question and more or less constrained by the particular conception of public trust.
-Quite often, trust in election administration is conflated with trust in government *writ* large, government legitimacy, government or system responsiveness, or even satisfaction with democracy [@daniller2019].
-At this level, not only is the level of public trust in elections sometimes vague, but there's little consideration over the difference between such attitudes pre-election and post-election.
-In contrast, a considerable amount of research tends to conceive of public trust in accordance with the institution in question [@atkeson2007; @hooghe2018].
-
-Elections administration is just one institution a part of the larger set of institutions which form the electoral system.
-As such, the performance of the institution along with the rest "...lends credibility to the outcome of an election: whether it is considered by citizens and the international community to be fair and legitimate." [@stewart2022, 236].
-Intuitively, enhancing public trust in elections would best be accomplished by enhancing the *trustworthiness* of the institution, i.e., consistently doing the things that election officials already regularly do come election time.
-However, trust and confidence in elections has become ever more precarious over the last few election cycles.
-Especially considering public polling data since 2000 shows that confidence that votes were, or would be, counted as intended was in a consistent decline despite efforts towards bolstering election integrity and trustworthiness [@sances2015].
-This is even more pronounced considering the role that partisanship has had on such confidence over accuracy of vote count [@sances2015; @stewart2022].
-
-There's also stark difference in public trust before the election has occurred compared to after, a phenomenon referred to as the "winner-loser gap"; the "winners" are those who supported the winning candidate and the "losers" are those who supported the losing candidate.
-Much research has been dedicated to analyzing the sentiment of electoral winners vs losers, and vice versa [@nadeau1993; @daniller2019].
-Opinions of electoral trust gathered after the election has occurred are limited considering the well-recognized impact that the electoral outcome itself has on feelings of public trust in elections [@daniller2019].
-
-As such, it is questionable whether we can characterize public trust in the pre-election period as the same trust after the election results have come out.
-The former is *anticipatory*---i.e., the kind that is more or less anxious given the uncertainties surrounding the election.
-The latter is *empirical*---a judgement discerned in hindsight after the experience of the election event has occurred.
-Evaluations of one's own trust and confidence in election administration based on the experience of voting is influenced by that very experience.
-As discussed by @stewart2022, not only was confidence in vote count accuracy influenced by the voter experience, but so too were evaluations of election officials [-@stewart2022, 242-243].
-Not to mention the influence that the election results would also have on such evaluations.
-In other words, evaluations of trust and confidence post-election are influenced by one's interpretation of their experience.
-The subtle difference is simply the degree of uncertainty one feels in anticipation of the next election event.
-This study focuses primarily on that *anticipatory* kind of confidence, which speaks more to those insecurities[^3] based on perceptions of the institution's trustworthiness than upon the particular voter experience.
-
-Regardless of the measures taken by election officials to boost public confidence in the *trustworthiness* of election administration (e.g., conducting audits, testing election machines), public *trust* and confidence in elections more generally is apt to shift dramatically post-election based on factors such as partisanship, elite rhetoric, particular state policies, and more [@nadeau1993; @carter2024; @coll2024a].
-Moreover, prior research has found that evaluation of election workers themselves are an important factor when it comes to levels of public confidence in the electoral process [@hall2007; @hall2009; @claassen2008].
-Such studies focused on the quality of the voter experience with reference to the interaction between voter and election worker.
-
-Beyond the general competence of election workers, however, the quality of the voter experience may be influenced merely by *a priori* impressions about *who* comprises election staff and volunteers.
-Political and other social science researchers have recognized for some time the power that group identity can have over attitudes and perception [@xiao2016; @xiao2012; @vanbavel2021].
-As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve trust and confidence in election administration, and lessen expectations of electoral fraud.
-The next section elaborates on why military veterans are of particular interest in this regard.
-
-## Why Veterans
-
-Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work.
-Staffing issues have been an issue since at least the 1990s [@maidenberg1996; @ferrer2024].
-In 2020, such efforts were made far more difficult by the COVID-19 pandemic [@mena2020; @abbate2020a].
-Sure, it makes sense to recruit veterans, but no more than any other group.
-After all, ensuring election offices are adequately staffed is everyone's problem.
-So there's no special reason to target veterans for recruitment above other groups.
-Indeed, there's no reason to discriminate recruitment efforts at all if the point is purely to fill staffing vacancies.
-However the interest in veterans as a special group to consider arose in light of increased and sudden efforts to recruit veterans into election work.
-
-The reason why veterans arose as a special subset of the population to consider for this inquiry is because there was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021.
-After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterans2022; @nflfootballoperations2022].
-Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts [@powerthepolls2020; @herndon2020].
-Generally, however, recruitment efforts cast a wide net, indiscriminate of who applies [@ross2020; @conde2020].
-
-One can speculate that the motivation to associate military veterans with civic engagement and democracy may be intended to counter negative perceptions and impressions given by the proportion of veteran service members arrested for taking part in the events on January 6th [@milton2021; @loewenson2023; @jensen2022a].
-Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024].
-This is in addition to a strengthened association portrayed in media outlets between military veterans and militias [@steinhauer2020].
-Prior research has substantiated such a connection between veterans and militia groups.
-@cooter2024 notes from her 3-year ethnographic fieldwork among Michigan militia members that, "...approximately 40% of militia leaders and 30% of members had previous military experience.
-Most of these veterans actively sought out such groups, as opposed to being recruited by them" [-@cooter2024; see also @cooter2013].
-Thus, countering such associations by promoting a different image of veterans to the mass public and veterans alike seems like a reasonable motivation.
-Yet such speculation is just that.
-
-That being said, the general public perception, attitudes, or even stereotypes about military veterans are significant to consider.
-Although military recruitment shows a downward trend as of late, public perception of veterans are overwhelmingly positive [@kleykamp2023].
-Veterans are a particularly potent group where mention of veteran status seems to have a positive, calming, or nullifying effect on attitudes.
-For instance, recent research shows that, during his campaign in the 2020 Democratic Primaries, Pete Buttigieg's military background mitigated discrimination against him when he was presented as a veteran married to man [@magni2024].
-Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@hardy2019].
-Moreover, veteran status seems to mitigate or nullify usual stigmas associated with mental illness.
-That is to say, there is negative stigma associated with mental illness [@corrigan2002] and such stigma incurs labor market discrimination [@hipes2016], but evidence suggests that veteran status overrides such stigma and discrimination [@maclean2014].
-Or, in another light, mental illness is seemingly more *understandable* (i.e., permissible) for veterans given the presumptive reasons for their mental strife.
-And media framing as such plays an important role on public perception [@kleykamp2015].
-
-## Theory and Hypotheses
-
-Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veterans and their family members to work as election staff and volunteers would boost public confidence in election administration.
-Indeed, that is the primary hypothesis of this study.
-Although citizens may vote in various ways across the country (e.g., by mail, ballot drop box, in-person), the simple announcement that election officials are engaging in efforts to recruit veterans to work as election staff may boost confidence in elections administration regardless of how, or whether, an individual plans to vote.
-Formally,
-
-> H~1~: Announcements that election officials are recruiting miilitary service veterans to work as election staff and volunteers will be associated with greater confidence in elections administration compared to announcements that do not mention military veterans.
-
-I considered that veterans would elicit high degrees of approval and support for whatever cause or issue presented.
-For example, I'd expect high approval and support for recruiting veterans to baseball teams just as much as for recruiting them to work as election staff.
-Likewise, asking participants whether they supported programs intent on recruiting anyone to work as election staff would garner support regardless of the target group.
-Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require a survey experiment designed to determine whether publicized recruitment efforts targeting veterans as a group would have any special effect on confidence in elections administration.
-
-Since the results and events following the 2020 election loomed large in anticipation of the U.S.
-2024 general elections, it is reasonable to take into account beliefs about legitimacy of the 2020 election.
-This group who denies the legitimacy of the 2020 election results were possibly the most distrusting of the 2024 election.
-However, given that veteran service members are held in high regard, generally speaking, announcing that veterans are being actively recruited to work as election staff and volunteers is expected to positively influence confidence in elections among those who remained firm in the belief that the 2020 election results were illegitimate.
-I take into account that legitimacy beliefs about the 2020 election and expectations of electoral fraud are related to partisanship and include partisanship as a control in the analysis.
-
-In addition, I expect that both expectations of electoral fraud and concerns for voter safety would lessen (shrink) when presented with information that veterans are being actively recruited to work and volunteer in election offices.
-
-Finally, prior research has shown that confidence that one's own vote would be counted as intended has been much stronger than confidence that votes nationwide would be treated likewise [@sances2015; @stewart2022].
-In other words, the public is more trusting of elections closer to home.
-Taking into account that confidence is lower for elections conducted outside of one's local area, then information that veterans are being recruited to help conduct elections in locations beyond one's locale may close this gap between confidence in elections within one's local area and confidence in elections elsewhere.
-Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone.
-Therefore, any observed disparity of confidence in elections (i.e., the "confidence gap") between elections within one's local area and elections beyond will be smaller when people are presented with information about election official recruitment efforts of veteran service members.
-
-## Experiment Design and Survey Measures
-
-To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would improve confidence in elections and ease insecurity, a recent experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland.
-The survey was fielded from August 29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287 U.S.
-citizens 18 years of age or older.
-Respondents were randomly split into either the treatment ($n =$ 650) control ($n =$ 637) conditions[^4].
-
-Survey participants read either a treatment or control vignette, which was a fabricated news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election.
-The treatment vignette referred to a program designed to recruit veterans and their family members and describes an interviewee "Jordan Braxton" as an Army veteran.
-The control vignette simply omitted any mention of veterans and their family members, and didn't describe "Jordan Braxton" as an Army veteran.
-Beyond those small differences and the headlines, the article vignettes are identical.
-Therefore, effects can be attributed to the information about veterans in the treatment vignette[^5].
-
-It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignette due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
-Because of this, treatment effects are potentially limited or constrained to attitudes concerning the location specified in the vignette.
-A block of survey items asked specifically about Maricopa County, AZ, followed by an identical block of items that asked the same questions about one's local area.
-Later, I compare and discuss results between the items pertaining to different settings.
-
-Over the past two decades it became commonplace for national polls to gauge public confidence in election administration (i.e., voter confidence) by asking some variety of the question, "How confident are you that your vote \[will be/was\] counted as you intended in the most recent election?" [@hall2009; @sances2015; @stewart2022].
-In addition, since 2008, the Survey of the Performance of American Elections (SPAE) has included a good number of relevant questions to more thoroughly assess trust and confidence in election administration.
-Such questions inquire into the voter experience with the institution more directly.
-This study borrows, modifies, or takes inspiration from certain question items found within the 2022 SPAE and other survey items from the Pew Research Center's 2018 American Trends Panel wave 38 [@dunn2018].
-
-Note that, except for the item assessing voter confidence (i.e., votes counted as voters intend), most other question items from the 2022 SPAE inquire into the voter experience after the election has occurred.
-The items in this study, however, all inquire into confidence over one's expectations in anticipation of upcoming elections.
-In addition, other survey questionnaires ask similar questions that specifically contrast between a respondent's own local community, their state, and nationwide; this is in addition, or complementary to, items that distinguish between local area officials, state election officials, state government, and the U.S.
-federal government.
-The survey of this study, instead, focused on attitudes regarding election workers such as election officials, staff, and volunteers specific to the location mentioned in the vignette---Maricopa County, AZ---as well as specific to one's local area[^6].
-
-The survey included items that assessed both trust in elections administration and expectations of electoral fraud, referred to simply as *trust* and *distrust*, respectively.
-Responses from these two sets of items were utilized to construct the primary dependent variable, *confidence in elections*.
-
-Prior to the reading the treatment or control vignette, participants responded to distinct survey items assessing one's favorability to local election officials ("In general, how favorable or unfavorable is your impression of local election officials?") and legitimacy of the 2020 election results ("Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected?").
-The former presented five response options from "Strongly favorable" to "Strongly unfavorable"; the latter item presented a binary of either "Legitimate" or "Not Legitimate".
-
-The conventional multiple item assessment of partisanship was included and used to construct a variable of partisanship consisting of three categories: Democrat, Republican, and Independent.
-In this case, Independents are "true" Independents in that they do not identify with either political party and do not "lean" toward either Republican or Democratic parties.
-Self-described "Independent leaners" are re-coded as falling into the partisan category in which they lean e.g., Independents who expressly report that they lean Republican are denoted as Republican.
-
-Finally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
-The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^7].
-
-### Trust and Distrust in Elections
-
-A set of five survey items measured public trust in elections by inquiring into the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, and confidence that the voting process will be fair.
-Each item in this series presented four response options from "Not at all \[confident/committed\]", "Not too \[confident/committed\]", "Somewhat \[confident/committed\]", and "Very \[confident/committed\]".
-In total, five survey items measure different aspects of trust in elections administration.
-The items measuring confidence in elections include:
-
-Another series of five survey items captured an individual's level of *distrust* in elections administration based on the extent to which they *expect electoral fraud* to occur.
-These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in \[Maricopa County, AZ/ your local area\]?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
-
-```{r}
-#| label: tbl-items
-#| tbl-cap: "Survey Items for Trust and Distrust in Elections"
-
-trust_txt <- df |> select(q19, q20, q21, q22, q24) |>
-  labelled::set_variable_labels(
-    q21 = "How commited do you think election staff and volunteers in Maricopa County, AZ will be to making sure the elections are fair and accurate?"
-  ) |> 
-  labelled::generate_dictionary() |> 
-  dplyr::as_tibble() |> 
-  select(Trust=label)
-
-distrust_txt <- df |> select(q28_1:q28_5) |>
-  labelled::generate_dictionary() |> 
-  dplyr::as_tibble() |> 
-  select(Distrust=label)
-
-conf_items_text <- trust_txt |> 
-  mutate(Distrust = pull(distrust_txt))
-
-kableExtra::kbl(conf_items_text, booktabs = T,
-                col.names = c("Trust", "Distrust"),
-                linesep = "\\addlinespace") |> 
-  kableExtra::kable_styling(full_width = T,
-                            font_size = 8,
-                            latex_options = c("HOLD_position")) |> 
-  kableExtra::column_spec(column = 1:2, width = "8cm")
-
-```
-
-Similar to the items capturing trust in elections (@tbl-items), I computed a summated score for each respondent reflecting the extent of their distrust in elections.
-
-Upon construction of the two summated scales of *trust* and *distrust*, internal consistency reliability coefficient $\alpha$ were estimated for both and found to be adequate ($\alpha$ \> 0.8); the trust in elections scale $\alpha$ = 0.93 and the distrust scale $\alpha$ = 0.86.
-In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each.
-
-I expected item responses from these two scales to be inversely correlated among the sample, but not mutually exclusive.
-Indeed, this is what I find.
-Polychoric correlations between the trust and distrust items negatively correlate as expected\[\^See Appendix C\], as does the correlation between the two sum score scales.
-Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
-The negative correlation between the trust and distrust items and scores makes intuitive sense.
-
-## Data Specification
-
-The primary outcome of interest concerns public confidence in elections administration compensated by one's distrust in elections, i.e., their expectations of electoral fraud.
-Because trust and distrust are assessed by multiple Likert items, conventional methods call for combining the items of each set into separate Likert scales (also known as summated rating scales).
-Since the item response options are not symmetric---i.e., not bipolar with contrasting positive and negative response options to include a neutral middle option---then the *trust in elections* scale could only be understood as a measure of trust in the positive use of the term (i.e., unipolar).
-Likewise, the expectation of fraud items fit to a scale that corresponds to a unipolar measure of confident *distrust*, so to speak.
-However, many of the items comprising the trust scale directly oppose items capturing distrust.
-For instance, one item from the trust scale has the respondent report their confidence that votes will be counted as voter's intend, whereas a separate item from the distrust scale has the the respondent report their expectation that many votes will not be counted.
-Positive responses to these two items directly contradict each other, and would thus cancel out.
-
-The relationship is that trust and distrust represent opposing degrees of confidence along the same spectrum.
-However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling similarly confident in both respects.
-Accordingly, equivalent degrees of trust and distrust cancel out, rendering one relatively more *insecure* about their expectations of the future despite the fact that they may feel confident in either direction.
-When trust and distrust are considered as reflective of one's confidence about future expectations, then both can be placed along the same spectrum.
-Therefore, a lack of confidence denotes insecurity.
-
-Something may cause a person to have greater expectations that election fraud will occur, which in turn will always lower their trust in elections administration.
-In contrast, a person may feel a bit more confident in the integrity of elections, but this confidence is constrained by the extent to which they expect election fraud to occur.
-This means that a person's baseline level of confidence in elections admin must take into account their present degree of distrust---i.e., their expectations of electoral fraud.
-
-Those who are, or are close to being, equally confident in both directions would be the most *insecure* about their expectations.
-Having no trust in elections and no expectation that electoral fraud will occur is functionally equivalent to having equal degree of both.
-Quite literally, this reflects an uncertain feeling of "it could go one way or the other" with respect to the integrity of elections administration.
-Operationally, this would reflect a middling point on a scale of *confidence*.
-
-In light of this, I reverse coded positive expectations of electoral fraud and added responses from the distrust scale to the trust in elections scale.
-That is, item responses on the trust scale ranged from 0 ("Not confident at all") to 3 ("Very confident), whereas responses on the distrust scale ranged from 0 ("Not likely at all") to -3 ("Very likely").
-Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^8].
-On this scale, positive values reflect higher confidence in elections, negative values reflect greater distrust, and values closer to zero correspond to an individual's degree of insecurity.
-
-The advantage is that this permits a better test of the treatment effect as theorized.
-Of course, it is easy enough to examine the effect of the treatment on both trust and distrust separately.
-However, the theory presents a hypothesis that the treatment will impose influence upon both variables *concurrently and in a positive direction* with respect to the relationship between trust and distrust.
-That is to say, confidence increases insofar as trust in elections increases and distrust decreases; since distrust detracts from trust, then an accurate measure of confidence must take that constraint into account.
-
-## Results
-
-I first review responses to the survey items capturing trust and distrust separately by treatment condition.
-When distinguished by experiment condition, trust in elections admin is noticeably higher for those who read the treatment vignette.
-The difference is more pronounced for some items over others.
-That being said, there is a definite distinction between items pertaining to Maricopa County, AZ compared to items that pertain to a respondent's local area.
-In fact, the treatment appears to have hardly made a difference when the items concerned one's local area.
-
-```{r}
-#| label: fig-trustlikert
-#| fig-cap: "Trust in Election Administration by Experiment Condition"
-#| fig-height: 4.5
-#| fig-pos: "h"
-
-# Likert plot of trust and confidence in election admin comparing treatment and
-# control groups
-trust.likert.treat.az <- df |>
-  # relabel factor labels for plotting
-  mutate(across(
-    c(q19, q20, q21, q22, q23, q24, q30, q31, q32, q33, q34, q35),
-    ~ pewmethods::fct_case_when(
-      .x %in% c("Not at all confident", "Not at all committed") ~ "Not at all confident",
-      .x %in% c("Not too confident", "Not too committed") ~ "Not too confident",
-      .x %in% c("Somewhat confident", "Somewhat committed") ~ "Somewhat confident",
-      .x %in% c("Very confident", "Very committed") ~ "Very confident",
-      TRUE ~ NA
-    )
-  )) |>
-  ggstats::gglikert(
-    include = c(q19, q20, q21, q22, q24),
-    y = 'group',
-    facet_rows = vars(.question),
-    symmetric = F,
-    labels_size = 2.5,
-    add_totals = T
-  ) +
-  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
-  # ggplot2::scale_fill_brewer(palette = "Greys")+
-  labs(subtitle = str_wrap("Maricopa County, Arizona", width = 95)) +
-  theme_bw() +
-  theme(
-    text = element_text(family = "Palatino Linotype"),
-    legend.position = 'bottom',
-    axis.text.x = element_blank(), # remove percentage text along x-axis
-    strip.text.y.right = element_blank()
-  )
-
-# confidence in elections between experiment conditions for items concerning local area
-trust.likert.treat.lcl <- df |>
-  # relabel factor labels for plotting
-  mutate(across(
-    c(q19, q20, q21, q22, q23, q24, q30, q31, q32, q33, q34, q35),
-    ~ pewmethods::fct_case_when(
-      .x %in% c("Not at all confident", "Not at all committed") ~ "Not at all confident",
-      .x %in% c("Not too confident", "Not too committed") ~ "Not too confident",
-      .x %in% c("Somewhat confident", "Somewhat committed") ~ "Somewhat confident",
-      .x %in% c("Very confident", "Very committed") ~ "Very confident",
-      TRUE ~ NA
-    )
-  )) |>
-  ggstats::gglikert(
-    include = c(q30, q31, q32, q33, q35),
-    y = 'group',
-    facet_rows = vars(.question),
-    variable_labels = c(
-      q30 = "Votes counted as intended",
-      q31 = "Election officials will do good job",
-      q32 = "Election workers will be committed",
-      q33 = "Voting process will be fair",
-      q35 = "Election technology will be secure"
-    ),
-    facet_label_wrap = 10,
-    labels_size = 2.5,
-    symmetric = F,
-    add_totals = T
-  ) +
-  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
-  # ggplot2::scale_fill_brewer(palette = "Greys")+
-  labs(subtitle = str_wrap("Local Area", width = 95)) +
-  theme_bw() +
-  theme(
-    text = element_text(family = "Palatino Linotype"),
-    legend.position = 'bottom',
-    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
-    axis.text.x = element_blank(), # remove percentage text along x-axis
-    strip.text.y.right = element_text(angle = 0, size = 8)
-  )
-
-# trust.likert.treat.az
-# trust.likert.treat.lcl
-
-# Instead of two separate plots, arrange into one plot while remaining separated
-# use `ggpubr` package to print multiple plots side-by-side (or alt. row-by-row)
-ggpubr::ggarrange(
-  trust.likert.treat.az,
-  trust.likert.treat.lcl,
-  ncol = 2,
-  common.legend = T,
-  legend = "bottom", 
-  font.label = list(family = "Palatino Linotype")
-) +
-  # add figure footnote annotation
-  patchwork::plot_annotation(
-    caption = str_wrap("Missing values removed. Displays percent proportions of responses by experiment condition and combined percentage proportions for two categories.",
-               width = 85), theme = theme(text = element_text(family = "Palatino Linotype")))
-
-```
-
-Reviewing item responses distinguished by treatment condition reveals particulars of the treatment effect (@fig-trustlikert).
-Among the items that asked about Maricopa County, AZ, it is a bit easier to see upon which items the treatment vignette had the greatest effect.
-It appears that the main effect of the treatment is upon responses to the item that measures confidence in the security of election technology.
-
-Regarding confidence in the commitment of election staff and volunteers, a higher proportion of respondents in the treatment group selected "Very confident" over "Somewhat confident" compared to the control group, but only for items concerning Maricopa County, AZ.
-Although confidence in election workers was generally high across the board, the shift from "Somewhat" to "Very" confident for items pertaining to election worker *commitment* to fairness and accuracy seems to clearly speak to the group being recruited, i.e., veterans and family members.
-However, the same visible shift in proportion from "Somewhat" to "Very" confident isn't observed when items asked about one's local area, which undermines the suggestion that the treatment effect can be cleanly attributed to respondent's feelings about veteran service members and their families.
-It may be the case that respondents harbor particular attitudes or sentiment about Maricopa County, AZ itself, or there may be nothing uniquely special about Maricopa County, AZ supposing that elections anywhere beyond one's local area generally garner slightly less confidence.
-
-What this does suggest, however, is that trust in the fairness and accuracy of the electoral process is notably higher upon the notion that military veterans will be directly engaged as election staff and volunteers in places where such trust falters.
-The question turns to whether this also lowers distrust, or the extent to which one expects electoral fraud to occur.
-
-```{r}
-#| label: fig-distrustlikert
-#| fig-cap: "Disrust in Election Administration by Experiment Condition"
-#| fig-height: 4.5
-#| fig-pos: "h"
-
-# distrust in elections in AZ by experimental condition
-distrust.likert.az <- df |>
-  # reverse levels of factor vars to show positive difference in "not likely"
-  mutate(across(c(q28_1:q28_5), ~forcats::fct_rev(.))) |> 
-  ggstats::gglikert(
-    include = c(q28_1:q28_5),
-    y = 'group',
-    facet_rows = vars(.question),
-    variable_labels = c(
-      q28_1 = "Voter fraud will occur",
-      q28_2 = "Many votes won't be counted",
-      q28_3 = "Many voters will be turned away",
-      q28_4 = "Foreign Interference",
-      q28_5 = "Election officials will discourage voting"),
-    facet_label_wrap = 10,
-    labels_size = 2.5,
-    symmetric = F,
-    add_totals = T
-  ) +
-  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
-  # ggplot2::scale_fill_brewer(palette = "Greys")+
-  labs(subtitle = str_wrap("Maricopa County, Arizona", width = 95)) +
-  theme_bw() +
-  theme(
-    text = element_text(family = "Palatino Linotype"),
-    legend.position = 'bottom',
-    axis.text.x = element_blank(), # remove percentage text along x-axis
-    strip.text.y.right = element_blank()
-  )
-
-# distrust in elections in Local area by experimental condition
-distrust.likert.lcl <- df |>
-  # reverse levels of factor vars to show positive difference in "not likely"
-  mutate(across(c(q40_1:q40_5), ~forcats::fct_rev(.))) |> 
-  ggstats::gglikert(
-    include = c(q40_1:q40_5),
-    y = 'group',
-    facet_rows = vars(.question),
-    variable_labels = c(
-      q40_1 = "Voter Fraud will occur",
-      q40_2 = "Many Votes won't be counted",
-      q40_3 = "Many voters will be turned away",
-      q40_4 = "Foreign Interference",
-      q40_5 = "Election officials will discourage voting"),
-    facet_label_wrap = 10,
-    labels_size = 2.5,
-    symmetric = F,
-    add_totals = T
-  )+
-  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
-  # ggplot2::scale_fill_brewer(palette = "Greys")+
-  labs(subtitle = str_wrap("Local Area", width = 95)) +
-  theme_bw() +
-  theme(
-    text = element_text(family = "Palatino Linotype"),
-    legend.position = 'bottom',
-    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
-    axis.text.x = element_blank(), # remove percentage text along x-axis
-    strip.text.y.right = element_text(angle = 0, size = 8)
-  )
-
-# Instead of two separate plots, arrange into one plot while remaining separated
-# use `ggpubr` package to print multiple plots side-by-side (or alt. row-by-row)
-ggpubr::ggarrange(
-  distrust.likert.az,
-  distrust.likert.lcl,
-  ncol = 2,
-  common.legend = T,
-  legend = "bottom", 
-  font.label = list(family = "Palatino Linotype")
-) +
-  # add figure footnote annotation
-  patchwork::plot_annotation(
-    caption = str_wrap("Missing values removed. Displays percent proportions of responses by experiment condition and combined percentage proportions for two categories.",
-               width = 85), theme = theme(text = element_text(family = "Palatino Linotype")))
-
-```
-
-Similar to the trust scale items, the items on the distrust scale were associated with lower distrust in the treatment condition compared to the control.
-A quick glance at @fig-distrustlikert shows what appears to be a significant reduction in distrust, especially regarding the expectations that many votes wouldn't be counted, many voters would be turned away, and that election officials would discourage voters from casting a ballot.
-Interestingly, the expectation that there would be foreign interference in elections in Maricopa County, AZ were pretty resilient against the treatment.
-And again, responses for items pertaining to elections in one's local area are practically indistinguishable between treatment and control.
-
-### Confidence in elections
-
-Once trust and distrust were composed into unified variable of confidence in elections, I then examined distribution of the dependent variable followed by analysis of the effect of the treatment by comparison of mean differences between experiment conditions.
-Recall that on this scale, zero reflects insecurity (e.g., similar or equal values of trust and distrust), whereas values diverging from zero reflect confidence in either direction, trust or distrust respectively.
-Positive values reflect trust in elections administration (e.g., elections will be fair and accurate), whereas negative values reflect distrust in elections (i.e., expectation that election fraud will occur).
-To retain a meaningful zero, I rescaled the sum scores to range from -3 to 3[^9] and then superimposed two histograms of confidence scores: one derived from AZ items and another for scores derived from local area items.
-Doing this is illustrative of the relative distribution of confidence that differed depending on the location of elections referred to in the survey items (e.g., Maricopa County, AZ).
-
-As revealed by review of the item responses, the distribution of confidence differed depending on whether survey items pertained to elections in Maricopa County, AZ, or elections within one's local area.
-
-```{r}
-#| label: fig-dist
-#| fig-cap: "Overlapping Distribution of Confidence in Elections for AZ and Local Area"
-#| fig-pos: "H"
-
-ggplot(df) +
-  geom_histogram(
-    aes(x = conf.az.rescaled , y = after_stat(density)),
-    bins = 15,
-    alpha = 0.2,
-    color = 1,
-    fill = "red"
-  ) +
-  geom_histogram(
-    aes(x = conf.lcl.rescaled , y = after_stat(density)),
-    bins = 15,
-    alpha = 0.2,
-    color = 1,
-    fill = "blue"
-  ) +
-  geom_segment(
-    x = round(mean(df$conf.az.rescaled), 2),
-    y = 0,
-    yend = 0.35,
-    color = "firebrick",
-    lwd = 1.4,
-    linetype = 2
-  ) +
-  geom_segment(
-    x = round(mean(df$conf.lcl.rescaled), 2),
-    y = 0,
-    yend = 0.35,
-    color = "darkblue",
-    lwd = 1.4,
-    linetype = 2
-  ) +
-  annotate(
-    "text",
-    x = round(mean(df$conf.az.rescaled), 2),
-    y = 0.40,
-    label = paste("AZ =", round(mean(
-      df$conf.az.rescaled
-    ), 2), "(", round(sd(
-      df$conf.az.rescaled
-    ), 2), ")"),
-    color = "firebrick"
-  ) +
-  annotate(
-    "text",
-    x = round(mean(df$conf.lcl.rescaled), 2),
-    y = 0.43,
-    label = paste("Local area =", round(mean(
-      df$conf.lcl.rescaled
-    ), 2), "(", round(sd(
-      df$conf.lcl.rescaled
-    ), 2), ")"),
-    color = "darkblue"
-  ) +
-  labs(
-    x = str_wrap("Confidence", width = 85),
-    y = "Density",
-    caption = str_wrap(
-     "Mean (std.deviation). Mean difference = 0.33, CI [0.27, 0.38], t = 11.613, df = 1286, p < 0.01",
-     width = 95)) +
-  theme_bw(base_family = "Palatino Linotype")
-
-```
-
-Overall, the sample expressed more trust in elections relative to distrust seeing as how the distribution of confidence is largely positive (@fig-dist).
-However, there's a clear difference between confidence in Maricopa county, AZ elections and elections within one's local area.
-A paired t-test confirms that this difference was statistically significant, though somewhat small (mean difference $= 0.325$, $95\%$ CI $[0.27, 0.38]$, $t(1286) = 11.61$, $p < .001$).
-Nonetheless, respondents appeared less confident regarding elections in Maricopa County, AZ, but held more confidence in elections administration in their local area.
-This complements previous research that demonstrates a similar bias favorable to one's local area [@stewart2022].
-
-Accordingly, when confidence levels are distinguished by experiment condition, the treatment vignette only had an effect upon survey items pertaining to elections in Maricopa County, AZ.
-Conducting an independent samples t-test (i.e., Welch Two Sample t-test) suggests that the effect of the treatment compared to the control condition is positive, statistically significant, yet substantially pretty small.
-
-```{r}
-#| label: tbl-ttest
-#| tbl-cap: "Mean Difference Effect of Treatment Compared to Control Condition"
-#| tbl-pos: H
-
-# conduct two t-tests using `rstatix::t_test`, bind results by row, and pipe
-# into table
-dplyr::bind_rows(
-  df |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
-  rstatix::t_test(formula = conf.az.rescaled ~ group,var.equal = F,detailed = T),
-  df |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
-  rstatix::t_test(formula = conf.lcl.rescaled ~ group,var.equal = F, detailed = T)
-  ) |> 
-  # specify columns and column names
-  select(
-    Diff = estimate,
-    treat_mean = estimate1,
-    control_mean = estimate2,
-    treat_n = n1,
-    control_n = n2,
-    t = statistic,
-    p, df, conf.low, conf.high) |> 
-  mutate(
-    Place = dplyr::case_when(
-      p <= 0.05 ~ "Maricopa County, AZ", 
-      p > 0.05 ~ "Local Area"), 
-    .before = Diff) |> 
-  insight::format_table(stars = T) |> 
-  # insight::export_table(format = "md") # alternate
-  # output table as `kable` for LaTeX pdf
-  kableExtra::kbl(
-    format = "latex", 
-    booktabs = T,
-    col.names = c("Place", "$\\bar{x}_{diff}$", "$\\bar{x}_{treat}$", "$\\bar{x}_{control}$",
-                  "$treat_{n}$", "$control_{n}$", "t", "p", "df", "CI"), 
-    escape = F) |> 
-  kableExtra::footnote(general = "Welch Two Sample t-tests of difference between Confidence in Elections by Treatment Condition.") |> 
-  kableExtra::kable_styling(
-    font_size = 9, 
-    protect_latex = T)
-
-```
-
-The results of @tbl-ttest show that, on a scale ranging from -3 to 3, the effect of the treatment is associated with a $0.20$ average difference in confidence in elections in Maricopa County, AZ, compared to the control group.
-When the dependent variable is centered to have a mean of $0$ and standard deviation of $1$, standardized parameters permit interpretation of the treatment effect in terms of standard deviations; the standardized difference in confidence between treatment and control is $0.16$ (CI $[0.06, 0.27]$).
-Nothing is more illustrative than graphs and lines, however.
-
-```{r}
-#| label: fig-coef1
-#| layout-nrow: 2
-#| fig-height: 3.5
-#| fig-cap: "Confidence in Elections by Experiment Condition"
-#| fig-subcap: 
-#|   - "Confidence by Treatment Condition"
-#|   - "Trust and Distrust by Treatment Condition"
-
-# coef plot of treatment effect on confidence distinguished by location
-conf.coef1 <- jtools::plot_summs(
-  lm(conf.az.rescaled ~ group, data = df), 
-  lm(conf.lcl.rescaled ~ group, data = df), 
-  center = T, scale = T, transform.response = T,
-  model.names = c("Conf.AZ", "Conf.Local"),
-  coefs = c("Treatment" = "groupTreatment"), 
-  colors = c("red", "black"),
-  point.shape = c(8, 1))+
-  ggplot2::expand_limits(x = c(-0.25, 0.25))+
-  labs(y = "")+
-  theme_bw(base_family = "Palatino Linotype")
-
-# Coef plots of trust and distrust models for AZ and Local items
-conf.coef2 <- jtools::plot_summs(
-  lm(trust.scores.az ~ group, data = df),
-  lm(distrust.scores.az ~ group, data = df),
-  lm(trust.scores.lcl ~ group, data = df),
-  lm(distrust.scores.lcl ~ group, data = df),
-  center = T, scale = T, transform.response = T,
-  model.names = c("Trust.AZ", "Distrust.AZ", "Trust.Local", "Distrust.Local"),
-  coefs = c("Treatment" = "groupTreatment"),
-  colors = c("red", "red", "black", "black"),
-  point.shape = c(8, 8, 1, 1)
-)+
-  ggplot2::expand_limits(x = c(-0.25, 0.25))+
-  labs(y = "")+
-  theme_bw(base_family = "Palatino Linotype")
-
-conf.coef1
-conf.coef2
-
-```
-
-@fig-coef1 displays standard difference estimates of confidence in elections by treatment condition (control condition as reference).
-@fig-coef1-1 displays two models for confidence in elections in Maricopa County, AZ, and one's local area by treatment condition; @fig-coef1-2 displays four models for trust and distrust in elections in AZ or one's local area by treatment condition.
-These figures merely illustrate the effect of the treatment with respect to the relationship between trust and distrust; ultimately confidence improves.
-
-Confidence in elections was higher among those who read the treatment vignette but remained conditional on whether the survey questions inquired about elections in Maricopa County, AZ.
-This evidence suggests that announcing efforts to recruit veterans and their families to work as election staff and volunteers may increase confidence in elections administration in places outside of one's local area, but may not boost confidence in elections within one's local area.
-
-I now turn to results examining those who held onto the belief that the 2020 election results were illegitimate.
-I think check to see if recruiting veterans simply makes people feel safer at the polls.
-
-\pagebreak
-
-## Conclusion
-
-Bear in mind that confidence in elections for one's local area is already higher than for those beyond.
-Thus, there's already more insecurity concerning elections elsewhere for whatever reason.
-In the anticipatory period prior to national elections, publicized efforts to recruit veterans to work as election staff and volunteers may be a small, but positive, step towards reducing insecurity in elections that occur elsewhere.
-Especially among those who maintained a steadfast degree of distrust in elections.
-Despite a lack of evidence that systematic electoral fraud had occurred in the 2020 election, a substantial proportion of the population were unwilling to affirm the legitimacy of the results.
-However, despite such legitimacy beliefs, most were not consistent as they expressed varying levels of trust in different aspects of elections administration.
-
-### Limitations
-
-As far as I'm aware, both the items, their wording, and their composition into measurement scales are unique to this study.
-This renders the composite scores for trust in elections sample dependent and limits comparability with other cross-sectional survey data.
-
--   limitations: interpretations of the treatment effect are limited.
-    -   The sample may not be generalizable to the population.
-    -   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts.
--   Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
--   Moreover, results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons.
-- First, the vignettes and many survey questions ask about Maricopa County, AZ specifically.
-Adding a specific county in the vignette adds in a factor that cannot be accounted for without additional treatments that eliminate the setting as a potential influence.
-Moreover, the specificity of the setting adds in even more unexplained error---some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S.
-they've know nothing about.
-Adding the county undermines the confidence that treatment effects are solely attributable to veterans to an unknown degree.
-- Second, questions ask about one's own local community in addition to identical questions which asked about Maricopa County, AZ.
-Consequently, many questions within the questionnaire were duplicates with that one differences.
-This isn't uncommon in surveys, however in this case, it lengthened the survey to a degree that likely resulted in a higher drop off rate.
-More importantly, the quality of responses were likely diminished to some unknown extent.
-Although it is possible to compare questions asked about Maricopa County, AZ to questions about one's local area, the quality of that comparison is limited by the unknown extent of fatigue induced by answering the same questions twice.
-It wasn't just that some questions were asked multiple times, almost all of the questions were duplicated; after completing a long series on Maricopa County, participants then answered the same questions about the local community.
-The rate to which participants dropped from the survey is \_\_\_, which suggests fatigue as an important factor.
-Survey fatigue is a known issue that should be taken into consideration.
-Comparison of treatment effects between the MC series and the local area series is undermined by the unknown influence that fatigue would have on response choices.
-Any differences couldn't confidently be attributed to "my area" vs Maricopa county.
-We also can't determine whether treatment effects are sustained when comparing the Maricopa County series to the local area series asked subsequently.
-We would have to assume the setting as irrelevant, which we can't reasonably do.
-
-\pagebreak
-
-## Appendix A: Survey Experiment Vignettes and Survey Items {#sec-appendix-a}
+## Survey Experiment Vignettes
 
@@
 
-\pagebreak
+\newpage
 
-## Appendix B: Sample Demographics {#sec-appendix-b}
+## Survey Items
 
-The median age was 46 (mean age was 47).
-There was 51.7% (n = 658) women, 47% (n = 598) men, and approximately 1.3% who identified as either Non-binary/third gender (n = 7) or preferred not to say (n = 9).
-A large proportion of the sample identified as White or Caucasian (n = 975, 76.65%), while all other non-White respondents comprised 27.83% of the sample.
-Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised 13% of the sample; those with either degree at the Associate or Bachelor's level comprised 36.24%, while 22.25% had some college but no degree; and 28.46% had either a high school level or equivalent education or less than high school.
-The largest proportion of the sample identified as Democrat at 44.64%, followed by Republicans at 42.59%.
-The proportion of true Independents was 12.78%.
+```{r}
+#| label: tbl-4
+#| tbl-cap: "Survey Items and Response Options"
 
-\pagebreak
+df |> 
+  select(q6, q7, q25, q26) |> 
+  labelled::generate_dictionary() |> 
+  dplyr::as_tibble() |> 
+  mutate(value_labels = dplyr::case_when(
+    variable == 'q6' ~ "[Strongly unfavorable, Somewhat unfavorable, Neither, Somewhat favorable, Strongly favorable]",
+    variable == 'q7' ~ "Legitimate, Not legitimate",
+    variable == 'q25' ~ "Very concerned, Somewhat concerned, Not too concerned, Not at all concerned",
+    variable == 'q26' ~ "Not at all confident, Not too confident, Somewhat confident, Very confident"
+  )) |> 
+  select(Question = label, response = value_labels) |> 
+  kableExtra::kbl(booktabs = T, linesep = "\\addlinespace") |> 
+  kableExtra::kable_styling(full_width = T,
+                            font_size = 8,
+                            latex_options = c("HOLD_position")) |> 
+  kableExtra::column_spec(column = 1, width = "7cm") |> 
+  kableExtra::column_spec(column = 2, width = "4cm")
 
-\pagebreak
-
-[^1]: I adopt a distinction made between *trustworthiness* and *trust* in elections [@stewart2022].
-The "*worthiness*" of one's trust in the conduct and administration of elections is based on the extent that outcomes of an election reasonably follow the rules prescribed and can be adjudicated as such.
-To put it briefly, trustworthiness is built by the structure, procedures, and practices of the institution, in this case election administration.
-The public's trust in elections, however, is amendable to an indefinite number of factors that may be unrelated to the formal structure or procedures of election administration.
-To illustrate, I can recognize that my car is trustworthy prior to ever driving it because it is structurally sound; it passes whatever criteria upon inspection, it is sufficiently fueled, and appears to be in generally good working order.
-I have every reason to deem it *worthy of my trust*.
-However, I don't trust my car because I am sure it is haunted.
-
-[^2]: There's little that could justify a conceptual distinction between public trust pre-election and public trust post-election.
-The temporal element renders the difference between pre- and post-election more operative than conceptual at a foundational level.
-
-[^3]: Note that election insecurity is used in place of electoral confidence simply to emphasize the anticipatory nature of the attitudes in question.
-Election insecurity is taken to denote a lack of confidence.
-
-[^4]: Demographic breakdown of the sample are included in Appendix B.
-
-[^5]: Complete text of treatment and control vignettes are included in the Appendix
-
-[^6]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
-
-[^7]: Survey item wording and responses are included in Appendix A.
-
-[^8]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
-The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024], yet there is no general consensus on the most appropriate method generally.
-The use of either appears to largely depend on the researcher's particular research objective, theoretical suppositions, and necessity.
-Another common concern is the inappropriate treatment of ordinal variables as interval which levy strong assumptions, e.g., each item contributes equally to the variable being measured and that ordinal response categories are equidistant as though on an interval scale [@wang2013; for contrast, see @robitzsch2020].
-
-[^9]: This range is mostly arbitrary, as a range from -1 to 1 works much the same.
-When relying on simple sum total score, the scale ranges from -15 to 15.
-So a single point increase from 0 to 1 may reflect a combination of a single "Very confident" response on a trust item compensated by a single "Somewhat likely" response on a distrust item (i.e., 3-2 = 1), or some other equivalent combination.
-Although the use of mean scores would place scores back onto the response scale metric (e.g., from 0 to 3, reflective of "not at all" to "very"), this results in a unipolar scale (from 0 to 3).
-The bipolar scale resulting from the composition of positive trust and negative distrust engenders meaning to zero and negative values.
-As such, composite mean scores become inappropriate and interpretation of scores would no longer be feasible.
-In other words, negative values on the scale for confidence in elections hold substantive meaning (e.g., distrust, absent trust), which makes transforming scores to fit a unipolar scale inappropriate.
+```

### 2025-03-11 notebooks/appendix_B.qmd
Removed and added a slew of files

---
title: "Appendix B: Sample Demographics and Balance"
format:
  bookup-html: 
    toc: true
    toc-depth: 3
    embed-resources: false
    embed-fonts: true
    link-citations: true
    smooth-scroll: true
    link-external-newwindow: true
    citations-hover: true
    footnotes-hover: false
    code-fold: show
    code-overflow: wrap
    code-tools: true
    theme: 
      light: [bookup.scss]
      dark: [bookup.scss, bookup_dark.scss]
---

## Sample Demographics

The median age was 46 (mean age was $47$), $51.7\%$ ($n = 658$) women, $47\%$ ($n = 598$) men, and approximately $1.3\%$ who identified as either Non-binary/third gender ($n = 7$) or preferred not to say ($n = 9$). A large proportion of the sample identified as White or Caucasian ($n = 975, 76.65\%$), while all other non-White respondents comprised $27.83\%$ ($n = 297$) of the sample. Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised $13\%$ of the sample; those with either degree at the Associate or Bachelor's level comprised $36.24\%$, while $22.25\%$ had some college but no degree; and $28.46\%$ had either a high school level or equivalent education or less than high school. The largest proportion of the sample identified as Democrat at $44.64\%$, followed by Republicans at $42.59\%$. The proportion of true Independents^[Independent 'leaners' were grouped into the respective party affiliation in which they lean.] was $12.78\%$.

```{r}
#| label: tbl-demog
#| tbl-cap: "Sample Demographics"
#|

# descriptive stats of categorical variables
# best method for html document
tbl.desc <- df |>  
  labelled::set_variable_labels(
    age_4cat = "Age group",
    gender_3cat = "Gender",
    race2 = "Race/Ethnicity",
    race_wnw = "White or Non-White",
    educ_4cat = "Education",
    partyid_3cat = "Party ID",
    milrelation  = "Military Relation"
  ) |> 
  gtsummary::tbl_summary(
    by = group,
    include = c(
    age_4cat, 
    gender_3cat, 
    race2,
    race_wnw,
    educ_4cat, 
    partyid_3cat,
    milrelation),
    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
    missing = "ifany",
    missing_text = "NA") |> 
  gtsummary::add_n() |> 
  gtsummary::add_overall() |> 
  gtsummary::modify_header(label = "**Demographic**") |> 
  gtsummary::bold_labels()

gtsummary::as_kable_extra(tbl.desc, booktabs = T) |>
  kableExtra::add_footnote(
    label = "Independents do not identify nor 'lean' toward either political party") |> 
  kableExtra::kable_styling(
    font_size = 9, 
    protect_latex = T)

# gtsummary::as_gt(tbl.desc) |>  
#   gt::tab_footnote(
#     footnote = "Independents do not identify nor 'lean' toward either political party",
#     placement = "left"
#     ) |>  
#   gt::cols_align(align = 'left', columns = everything()) |> 
#   gt::tab_options(
#     table.font.size = "small",
#     data_row.padding = gt::px(1)
#   )

```

## Test of Random Assignment to Experiment Condition

@tbl-logit shows results of a logistic regression test of random assignment to the treatment group. Demographics such as age, gender, race, educational attainment, and party ID are included as predictor variables. Note that 19 missing observations were deleted. A $\chi^2(15) = 11.010$, with 15 degrees of freedom and associated p-value > 0.05 ($p = 0.75$) confirms that none of the demographic predictor variables significantly increased the log-odds---in turn, the probability---of being assigned to the treatment group.

```{r}
#| label: tbl-logit
#| tbl-cap: "Logistic Regression of Random Assignment to Treatment"

# simple logit of test of random assignment to treatment
# treatment is DV (treatment = 1, control = 0)
# demographic variables are IVs

df <- df |> 
  mutate(group.dum = dplyr::case_when(
    group == "Treatment" ~ 1,
    group == "Control" ~ 0,
    TRUE ~ NA), .after = group)

m1 <- glm(group.dum ~ age_4cat + gender_3cat + race2 + educ_4cat + partyid_3cat, 
          family = binomial(link = "logit"), data = df)

# A Chi-square of 11.01 with 15 degrees of freedom and associated p-value > 0.05 (p-value = 0.752) confirms that none of the demographic predictor variables significantly increased the probability of being assigned to the treatment group.

logit_tab <- gtsummary::tbl_regression(
    m1, 
    intercept = T,
    label = list(
      age_4cat ~"Age", 
      gender_3cat ~ "Gender", 
      race2 ~ "Race (includes Hispanic as race)",
      educ_4cat ~ "Educational Attainment", 
      partyid_3cat ~ "Party ID")) |> 
  gtsummary::add_global_p(keep = T) |> 
  gtsummary::add_nevent(location = c("label", "level")) |>
  gtsummary::bold_p() |> 
  gtsummary::bold_labels() |>
  # gtsummary::show_header_names()
  gtsummary::modify_header(
    label = " ",
    stat_nevent = "**Treatment N**") 
# 
#   gtsummary::modify_footnote_header(
#     footnote = "Chi-Squared ($\\chi^2$) = 11.01, d.f. = 15, p = 0.75", columns = "p.value")

gtsummary::as_kable_extra(logit_tab, 
                          booktabs = T, 
                          escape = F, 
                          addtl_fmt = T) |> 
  kableExtra::footnote("Chi-Squared = 11.01, d.f. = 15, p = 0.75", escape = F) |> 
  kableExtra::kable_styling(font_size = 9)

```

### 2025-03-11 notebooks/appendix_C.qmd
Removed and added a slew of files

--- 2025-03-01 index.qmd
@@
 ---
-title: title
-subtitle: subtitle
-shorttitle: A Short title # aog-article-pdf
-shortauthors: Isaiah      # aog-article-pdf
-authors:
-  - name: Isaiah Espinoza
-    email: gespinoz@umd.edu
-    roles: author
-    affiliation:
-      - name: University of Maryland
-        department: Department of Government and Politics
-        city: College Park
-        state: MD
-        country: US
-reference-section-title: References
-date: "2024-10-16"
-date-modified: today
-knitr: 
-  opts_chunk: 
-    dev: "ragg_png" # same as knitr::opts_chunk$set(dev = "ragg_png")
-editor_options: 
-  chunk_output_type: console
+title: "Appendix C: Trust and Distrust"
+subtitle: "Polychoric Item Correlations and Score Correlations"
+format:
+  bookup-html: 
+    toc: true
+    toc-depth: 3
+    embed-resources: false
+    embed-fonts: true
+    link-citations: true
+    smooth-scroll: true
+    link-external-newwindow: true
+    citations-hover: true
+    footnotes-hover: false
+    code-fold: show
+    code-overflow: wrap
+    code-tools: true
+    theme: 
+      light: [bookup.scss]
+      dark: [bookup.scss, bookup_dark.scss]
 ---
 
-```{r}
-#| label: setup
-#| include: false
-
-set.seed(1234)
-
-# load packages
-library(tidyverse)
-library(easystats)
-library(patchwork)
-library(jtools)
-
-# load subset of processed dataframe that includes dv composite scores
-load("data/research-paper-df-subset-20250203.Rdata") #df
-
-# load data dictionary/codebook
-codebook <- read.csv("data/survey_codebook.csv")
-df_dict <- read.csv("data/df_dictionary.csv")
-
-# do next. a whole lotta Likert plots
-source(here::here('src', '03-likert_plots.R'))
-
-```
-
-\pagebreak
-
-## Introduction
-
-Election administration officials make efforts to sustain public trust and confidence in the fairness and accuracy of elections, and attempt to boost such confidence where it may be deprived.
-Concerns for safety have developed among election staff and voters in more recent elections.
-Regular measures are taken to enhance the *trustworthiness*[^1] of the electoral process through practices meant to improve the conduct, transparency, or overall administration of elections in the United States.
-
-Although election officials undertake great efforts to enhance the trustworthiness of election administration, public *trust* in elections is a psychological construct influenced by many things outside of election official control such as partisanship or elite rhetoric [@hooghe2018; @sances2015].
-Moreover, a person's evaluation of the election in hindsight is often influenced by the election outcome itself [@daniller2019; @stewart2022].
-Thus, measures taken by election officials can be undermined, trivialized, or made irrelevant depending on how one feels after the election results have come out.
-
-Such volatile attitudes and evaluations post-election can leave a lasting impression that election officials must contend with upon the next election cycle [@levendusky2024; @bowler2024].
-For instance, we have witnessed many people's outright refusal to accept the 2020 U.S.
-election results as legitimate despite consistent review of the evidence confirming the results as fair and accurate.
-Such a case demonstrates that public trust in elections is, at best, only partial to trustworthiness of election administration in the United States[^2].
-
-Even though election officials can do a lot to secure election integrity, there's not much they can do to cement public confidence after election night passes.
-At best, election officials can ease public insecurities prior to election night.
-
-One point of contention that election officials have faced in the past regard evaluation of election workers.
-Previous literature has focused on how voter interaction with election workers [@claassen2008], or the voter experience generally [@atkeson2007], influences evaluations of election administration.
-As such, election worker competency has been examined as a factor significant to evaluations of performance of elections [@hall2007; @hall2009].
-However, considering that individual perceptions and preconceived notions play a huge role in cognition [@cikara2014; @vanbavel2021], it is reasonable to expect that the group an election worker hails from would be an important influence upon the voter's evaluation of the electoral process.
-
-Supposing such is the case, we can expect that information about *who* (i.e., which groups) election officials are targeting in publicized recruitment efforts would lessen particular election insecurity, and concurrently, boost confidence.
-That is to say, it is reasonable to expect that telling people *who* will be working and volunteering as election staff would ease election insecurity, and therefore improve confidence that the election will be conducted fairly, accurately, and safe for all involved.
-
-In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
-Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity to a limited extent.
-Expectations of electoral fraud and concerns for voter safety were lower among those who read a fabricated announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned.
-Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
-
-This paper is structured as follows.
-First, I provide a brief background on public trust in election administration.
-I synthesize a review of relevant literature with a focus on how political and social science has conceptualized and ascertained public trust in elections.
-Next, I supply reasoning for why military veterans are singled out as the relevant subset of the population in this study.
-I then explicitly provide the simple theory and testable hypotheses of the study before moving on to describe the design of the survey, the measurement instruments therein, and the conceptual and operational definitions of the variables of interest.
-I explain my reasoning and method for constructing the primary dependent variable, which I broadly refer to as *confidence in elections*.
-I preview the different methods of analysis alongside presentation of the results.
-Before concluding, I dedicate time to discuss the limitations of the study and lessons learned.
-I close by offering my interpretation of the results and suggest potential avenues for future inquiry.
-
-## Background: Election Administration and Public Confidence
-
-Election officials have tried hard to inspire confidence in the administration and conduct of elections by improving the degree to which elections are trustworthy.
-Development and implementation of procedures such as post-election auditing of ballots and logic-and-accuracy testing of ballot tabulation equipment are prominent examples adding to the long history of efforts to enhance the trustworthiness of election administration in the United States.
-
-Prior to the year 2000, one of the main issues facing election administration was recruiting enough election workers to volunteer at the polls (i.e., poll workers) [@maidenberg1996].
-Election worker recruitment is still much of an issue in the current era as it was then, perhaps worse [@ferrer2024].
-In addition to ensuring election admin offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections.
-In particular, voting technology [@herrnson2009] and election worker competence was a of interest in election studies [@claassen2008; @hall2009; @hall2007].
-Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007].
-
-In 2024, election officials made valiant efforts to boost public confidence elections within an intensified political climate that appeared quite hostile to election officials [@edlin2024; @brennancenterforjustice2024].
-Although polling around the time indicated that most people thought that U.S.
-elections would be run at least somewhat well [@nadeem2024], many election officials nationwide took efforts to assuage the worry of those most skeptical.
-
-Election anxiety was high in the lead up to the 2024 elections in the United States.
-Concerns for voter safety and the prospect of political violence remained prescient and compelled many local officials to prepare for the worst [@edlin2024; @doubek2024].
-Election officials in Washoe County, Nevada, installed panic buttons for election staff that would alert a monitoring center to summon law enforcement [@lincoln2024].
-Nevada also passed a law making it a felony to harass, threaten, or intimidate election workers [@nevadasecretaryofstate2023].
-Leading up to election day, news outlets reported that election work had become a seemingly dangerous job [@wire2024].
-A Brennan Center survey report stated that, "...large numbers of election officials report having experienced threats, abuse, or harassment for doing their jobs" [@edlin2024].
-Concerns over the fairness of elections and accuracy of vote counts intensified, heightening concerns over the prospect of political violence and, in turn, increased worry for the safety of voters and election workers alike.
-
-Suffice to say, pre-election anxiety consists of more than confidence in fairness and accuracy of vote counts in light of added safety concerns.
-It is not hard to recognize that increased tension in the pre-election period makes for a volatile political environment.
-Sustaining trustworthiness in election administration is only more difficult in an environment where turnover of election workers increases and the struggle to recruit volunteers worsens in light of safety concerns.
-Since election worker performance is significant to public evaluation of elections, added safety concerns that drive out election staff and repel volunteers can only detract from trustworthiness of the institution.
-
-## Literature Reivew
-
-Trust and confidence in the conduct of elections concerns aspects of elections that fall squarely within the institution of election administration.
-At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended).
-Or in other words, by the extent the public is confident in the accurate administration of elections.
-
-Assessing the public's *trust* in elections has not been straightforward, however.
-Inquiry into public trust in elections has been approached by scholars of political science in many different ways [@cook2005; @hardin2004], often distinguishable by the scope of the research question and more or less constrained by the particular conception of public trust.
-Quite often, trust in election administration is conflated with trust in government *writ* large, government legitimacy, government or system responsiveness, or even satisfaction with democracy [@daniller2019].
-At this level, not only is the level of public trust in elections sometimes vague, but there's little consideration over the difference between such attitudes pre-election and post-election.
-In contrast, a considerable amount of research tends to conceive of public trust in accordance with the institution in question [@atkeson2007; @hooghe2018].
-
-Elections administration is just one institution a part of the larger set of institutions which form the electoral system.
-As such, the performance of the institution along with the rest "...lends credibility to the outcome of an election: whether it is considered by citizens and the international community to be fair and legitimate." [@stewart2022, 236].
-Intuitively, enhancing public trust in elections would best be accomplished by enhancing the *trustworthiness* of the institution, i.e., consistently doing the things that election officials already regularly do come election time.
-However, trust and confidence in elections has become ever more precarious over the last few election cycles.
-Especially considering public polling data since 2000 shows that confidence that votes were, or would be, counted as intended was in a consistent decline despite efforts towards bolstering election integrity and trustworthiness [@sances2015].
-This is even more pronounced considering the role that partisanship has had on such confidence over accuracy of vote count [@sances2015; @stewart2022].
-
-There's also stark difference in public trust before the election has occurred compared to after, a phenomenon referred to as the "winner-loser gap"; the "winners" are those who supported the winning candidate and the "losers" are those who supported the losing candidate.
-Much research has been dedicated to analyzing the sentiment of electoral winners vs losers, and vice versa [@nadeau1993; @daniller2019].
-Opinions of electoral trust gathered after the election has occurred are limited considering the well-recognized impact that the electoral outcome itself has on feelings of public trust in elections [@daniller2019].
-
-As such, it is questionable whether we can characterize public trust in the pre-election period as the same trust after the election results have come out.
-The former is *anticipatory*---i.e., the kind that is more or less anxious given the uncertainties surrounding the election.
-The latter is *empirical*---a judgement discerned in hindsight after the experience of the election event has occurred.
-Evaluations of one's own trust and confidence in election administration based on the experience of voting is influenced by that very experience.
-As discussed by @stewart2022, not only was confidence in vote count accuracy influenced by the voter experience, but so too were evaluations of election officials [-@stewart2022, 242-243].
-Not to mention the influence that the election results would also have on such evaluations.
-In other words, evaluations of trust and confidence post-election are influenced by one's interpretation of their experience.
-The subtle difference is simply the degree of uncertainty one feels in anticipation of the next election event.
-This study focuses primarily on that *anticipatory* kind of confidence, which speaks more to those insecurities[^3] based on perceptions of the institution's trustworthiness than upon the particular voter experience.
-
-Regardless of the measures taken by election officials to boost public confidence in the *trustworthiness* of election administration (e.g., conducting audits, testing election machines), public *trust* and confidence in elections more generally is apt to shift dramatically post-election based on factors such as partisanship, elite rhetoric, particular state policies, and more [@nadeau1993; @carter2024; @coll2024a].
-Moreover, prior research has found that evaluation of election workers themselves are an important factor when it comes to levels of public confidence in the electoral process [@hall2007; @hall2009; @claassen2008].
-Such studies focused on the quality of the voter experience with reference to the interaction between voter and election worker.
-
-Beyond the general competence of election workers, however, the quality of the voter experience may be influenced merely by *a priori* impressions about *who* comprises election staff and volunteers.
-Political and other social science researchers have recognized for some time the power that group identity can have over attitudes and perception [@xiao2016; @xiao2012; @vanbavel2021].
-As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve trust and confidence in election administration, and lessen expectations of electoral fraud.
-The next section elaborates on why military veterans are of particular interest in this regard.
-
-## Why Veterans
-
-Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work.
-Staffing issues have been an issue since at least the 1990s [@maidenberg1996; @ferrer2024].
-In 2020, such efforts were made far more difficult by the COVID-19 pandemic [@mena2020; @abbate2020a].
-Sure, it makes sense to recruit veterans, but no more than any other group.
-After all, ensuring election offices are adequately staffed is everyone's problem.
-So there's no special reason to target veterans for recruitment above other groups.
-Indeed, there's no reason to discriminate recruitment efforts at all if the point is purely to fill staffing vacancies.
-However the interest in veterans as a special group to consider arose in light of increased and sudden efforts to recruit veterans into election work.
-
-The reason why veterans arose as a special subset of the population to consider for this inquiry is because there was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021.
-After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterans2022; @nflfootballoperations2022].
-Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts [@powerthepolls2020; @herndon2020].
-Generally, however, recruitment efforts cast a wide net, indiscriminate of who applies [@ross2020; @conde2020].
-
-One can speculate that the motivation to associate military veterans with civic engagement and democracy may be intended to counter negative perceptions and impressions given by the proportion of veteran service members arrested for taking part in the events on January 6th [@milton2021; @loewenson2023; @jensen2022a].
-Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024].
-This is in addition to a strengthened association portrayed in media outlets between military veterans and militias [@steinhauer2020].
-Prior research has substantiated such a connection between veterans and militia groups.
-@cooter2024 notes from her 3-year ethnographic fieldwork among Michigan militia members that, "...approximately 40% of militia leaders and 30% of members had previous military experience.
-Most of these veterans actively sought out such groups, as opposed to being recruited by them" [-@cooter2024; see also @cooter2013].
-Thus, countering such associations by promoting a different image of veterans to the mass public and veterans alike seems like a reasonable motivation.
-Yet such speculation is just that.
-
-That being said, the general public perception, attitudes, or even stereotypes about military veterans are significant to consider.
-Although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023].
-Veterans are a particularly potent group where mention of veteran status seems to have a positive, calming, or nullifying effect on attitudes.
-For instance, recent research shows that, during his campaign in the 2020 Democratic Primaries, Pete Buttigieg's military background mitigated discrimination against him when he was presented as a veteran married to man [@magni2024].
-Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@hardy2019].
-Moreover, veteran status seems to mitigate or nullify usual stigmas associated with mental illness.
-That is to say, there is negative stigma associated with mental illness [@corrigan2002] and such stigma incurs labor market discrimination [@hipes2016], but evidence suggests that veteran status overrides such stigma and discrimination [@maclean2014].
-Or, in another light, mental illness is seemingly more *understandable* (i.e., permissible) for veterans given the presumptive reasons for their mental strife.
-And media framing as such plays an important role on public perception [@kleykamp2015].
-
-## Theory and Hypotheses
-
-Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veterans and their family members to work as election staff and volunteers would boost public confidence in election administration.
-Indeed, that is the primary hypothesis of this study.
-Although citizens may vote in various ways across the country (e.g., by mail, ballot drop box, in-person), the simple announcement that election officials are engaging in efforts to recruit veterans to work as election staff may boost confidence in elections administration regardless of how, or whether, an individual plans to vote.
-Formally,
-
-> H~1~: Announcements that election officials are recruiting miilitary service veterans to work as election staff and volunteers will be associated with greater confidence in elections administration compared to announcements that do not mention military veterans.
-
-I considered that veterans would elicit high degrees of approval and support for whatever cause or issue presented.
-For example, I'd expect high approval and support for recruiting veterans to baseball teams just as much as for recruiting them to work as election staff.
-Likewise, asking participants whether they supported programs intent on recruiting anyone to work as election staff would garner support regardless of the target group.
-Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require a survey experiment designed to determine whether publicized recruitment efforts targeting veterans as a group would have any special effect on confidence in elections administration.
-
-Since the results and events following the 2020 election loomed large in anticipation of the U.S.
-2024 general elections, it is reasonable to take into account beliefs about legitimacy of the 2020 election.
-This group who denies the legitimacy of the 2020 election results were possibly the most distrusting of the 2024 election.
-However, given that veteran service members are held in high regard, generally speaking, announcing that veterans are being actively recruited to work as election staff and volunteers is expected to positively influence confidence in elections among those who remained firm in the belief that the 2020 election results were illegitimate.
-I take into account that legitimacy beliefs about the 2020 election and expectations of electoral fraud are related to partisanship and include partisanship as a control in the analysis.
-
-In addition, I expect that both expectations of electoral fraud and concerns for voter safety would lessen (shrink) when presented with information that veterans are being actively recruited to work and volunteer in election offices.
-
-Finally, prior research has shown that confidence that one's own vote would be counted as intended has been much stronger than confidence that votes nationwide would be treated likewise [@sances2015; @stewart2022].
-In other words, the public is more trusting of elections closer to home.
-Taking into account that confidence is lower for elections conducted outside of one's local area, then information that veterans are being recruited to help conduct elections in locations beyond one's locale may close this gap between confidence in elections within one's local area and confidence in elections elsewhere.
-Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone.
-Therefore, any observed disparity of confidence in elections (i.e., the "confidence gap") between elections within one's local area and elections beyond will be smaller when people are presented with information about election official recruitment efforts of veteran service members.
-
-## Experiment Design and Survey Measures
-
-To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would improve confidence in elections and ease insecurity, a recent experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland.
-The survey was fielded from August 29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287 U.S.
-citizens 18 years of age or older.
-Respondents were randomly split into either the treatment ($n =$ 650) control ($n =$ 637) conditions[^4].
-
-Survey participants read either a treatment or control vignette, which was a fabricated news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election.
-The treatment vignette referred to a program designed to recruit veterans and their family members and describes an interviewee "Jordan Braxton" as an Army veteran.
-The control vignette simply omitted any mention of veterans and their family members, and didn't describe "Jordan Braxton" as an Army veteran.
-Beyond those small differences and the headlines, the article vignettes are identical.
-Therefore, effects can be attributed to the information about veterans in the treatment vignette[^5].
-
-It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignette due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
-Because of this, treatment effects are potentially limited or constrained to attitudes concerning the location specified in the vignette.
-A block of survey items asked specifically about Maricopa County, AZ, followed by an identical block of items that asked the same questions about one's local area.
-Later, I compare and discuss results between the items pertaining to different settings.
-
-Over the past two decades it became commonplace for national polls to gauge public confidence in election administration (i.e., voter confidence) by asking some variety of the question, "How confident are you that your vote \[will be/was\] counted as you intended in the most recent election?" [@hall2009; @sances2015; @stewart2022].
-In addition, since 2008, the Survey of the Performance of American Elections (SPAE) has included a good number of relevant questions to more thoroughly assess trust and confidence in election administration.
-Such questions inquire into the voter experience with the institution more directly.
-This study borrows, modifies, or takes inspiration from certain question items found within the 2022 SPAE and other survey items from the Pew Research Center's 2018 American Trends Panel wave 38 [@dunn2018].
-
-Note that, except for the item assessing voter confidence (i.e., votes counted as voters intend), most other question items from the 2022 SPAE inquire into the voter experience after the election has occurred.
-The items in this study, however, all inquire into confidence over one's expectations in anticipation of upcoming elections.
-In addition, other survey questionnaires ask similar questions that specifically contrast between a respondent's own local community, their state, and nationwide; this is in addition, or complementary to, items that distinguish between local area officials, state election officials, state government, and the U.S.
-federal government.
-The survey of this study, instead, focused on attitudes regarding election workers such as election officials, staff, and volunteers specific to the location mentioned in the vignette---Maricopa County, AZ---as well as specific to one's local area[^6].
-
-The survey included items that assessed both trust in elections administration and expectations of electoral fraud, referred to simply as *trust* and *distrust*, respectively.
-Responses from these two sets of items were utilized to construct the primary dependent variable, *confidence in elections*.
-
-Prior to the reading the treatment or control vignette, participants responded to distinct survey items assessing one's favorability to local election officials ("In general, how favorable or unfavorable is your impression of local election officials?") and legitimacy of the 2020 election results ("Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected?").
-The former presented five response options from "Strongly favorable" to "Strongly unfavorable"; the latter item presented a binary of either "Legitimate" or "Not Legitimate".
-
-The conventional multiple item assessment of partisanship was included and used to construct a variable of partisanship consisting of three categories: Democrat, Republican, and Independent.
-In this case, Independents are "true" Independents in that they do not identify with either political party and do not "lean" toward either Republican or Democratic parties.
-Self-described "Independent leaners" are re-coded as falling into the partisan category in which they lean e.g., Independents who expressly report that they lean Republican are denoted as Republican.
-
-Finally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
-The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^7].
-
-### Trust and Distrust in Elections
-
-A set of five survey items measured public trust in elections by inquiring into the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, and confidence that the voting process will be fair.
-Each item in this series presented four response options from "Not at all \[confident/committed\]", "Not too \[confident/committed\]", "Somewhat \[confident/committed\]", and "Very \[confident/committed\]".
-In total, five survey items measure different aspects of trust in elections administration.
-The items measuring confidence in elections include:
-
-Another series of five survey items captured an individual's level of *distrust* in elections administration based on the extent to which they *expect electoral fraud* to occur.
-These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in \[Maricopa County, AZ/ your local area\]?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
-
-```{r}
-#| label: tbl-items
-#| tbl-cap: "Survey Items for Trust and Distrust in Elections"
-
-trust_txt <- df |> select(q19, q20, q21, q22, q24) |>
-  labelled::set_variable_labels(
-    q21 = "How commited do you think election staff and volunteers in Maricopa County, AZ will be to making sure the elections are fair and accurate?"
-  ) |> 
-  labelled::generate_dictionary() |> 
-  dplyr::as_tibble() |> 
-  select(Trust=label)
-
-distrust_txt <- df |> select(q28_1:q28_5) |>
-  labelled::generate_dictionary() |> 
-  dplyr::as_tibble() |> 
-  select(Distrust=label)
-
-conf_items_text <- trust_txt |> 
-  mutate(Distrust = pull(distrust_txt))
-
-kableExtra::kbl(conf_items_text, booktabs = T,
-                col.names = c("Trust", "Distrust"),
-                linesep = "\\addlinespace") |> 
-  kableExtra::kable_styling(full_width = T,
-                            font_size = 8,
-                            latex_options = c("HOLD_position")) |> 
-  kableExtra::column_spec(column = 1:2, width = "8cm")
-
-```
-
-Similar to the items capturing trust in elections (@tbl-items), I computed a summated score for each respondent reflecting the extent of their distrust in elections.
-
-Upon construction of the two summated scales of *trust* and *distrust*, internal consistency reliability coefficient $\alpha$ were estimated for both and found to be adequate ($\alpha$ \> 0.8); the trust in elections scale $\alpha$ = 0.93 and the distrust scale $\alpha$ = 0.86.
-In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each.
-
-I expected item responses from these two scales to be inversely correlated among the sample, but not mutually exclusive.
-Indeed, this is what I find.
-Polychoric correlations between the trust and distrust items negatively correlate as expected^[See Appendix C], as does the correlation between the two sum score scales.
-Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
-The negative correlation between the trust and distrust items and scores makes intuitive sense.
-
-## Data Specification
-
-The primary outcome of interest concerns public confidence in elections administration compensated by one's distrust in elections, i.e., their expectations of electoral fraud.
-Because trust and distrust are assessed by multiple Likert items, conventional methods call for combining the items of each set into separate Likert scales (also known as summated rating scales).
-Since the item response options are not symmetric---i.e., not bipolar with contrasting positive and negative response options to include a neutral middle option---then the *trust in elections* scale could only be understood as a measure of trust in the positive use of the term (i.e., unipolar).
-Likewise, the expectation of fraud items fit to a scale that corresponds to a unipolar measure of confident *distrust*, so to speak.
-However, many of the items comprising the trust scale directly oppose items capturing distrust.
-For instance, one item from the trust scale has the respondent report their confidence that votes will be counted as voter's intend, whereas a separate item from the distrust scale has the the respondent report their expectation that many votes will not be counted.
-Positive responses to these two items directly contradict each other, and would thus cancel out.
-
-The relationship is that trust and distrust represent opposing degrees of confidence along the same spectrum.
-However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling similarly confident in both respects.
-Accordingly, equivalent degrees of trust and distrust cancel out, rendering one relatively more *insecure* about their expectations of the future despite the fact that they may feel confident in either direction.
-When trust and distrust are considered as reflective of one's confidence about future expectations, then both can be placed along the same spectrum.
-Therefore, a lack of confidence denotes insecurity.
-
-Something may cause a person to have greater expectations that election fraud will occur, which in turn will always lower their trust in elections administration.
-In contrast, a person may feel a bit more confident in the integrity of elections, but this confidence is constrained by the extent to which they expect election fraud to occur.
-This means that a person's baseline level of confidence in elections admin must take into account their present degree of distrust---i.e., their expectations of electoral fraud.
-
-Those who are, or are close to being, equally confident in both directions would be the most *insecure* about their expectations.
-Having no trust in elections and no expectation that electoral fraud will occur is functionally equivalent to having equal degree of both.
-Quite literally, this reflects an uncertain feeling of "it could go one way or the other" with respect to the integrity of elections administration.
-Operationally, this would reflect a middling point on a scale of *confidence*.
-
-In light of this, I reverse coded positive expectations of electoral fraud and added responses from the distrust scale to the trust in elections scale.
-That is, item responses on the trust scale ranged from 0 ("Not confident at all") to 3 ("Very confident), whereas responses on the distrust scale ranged from 0 ("Not likely at all") to -3 ("Very likely").
-Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^8].
-On this scale, positive values reflect higher confidence in elections, negative values reflect greater distrust, and values closer to zero correspond to an individual's degree of insecurity.
-
-The advantage is that this permits a better test of the treatment effect as theorized.
-Of course, it is easy enough to examine the effect of the treatment on both trust and distrust separately.
-However, the theory presents a hypothesis that the treatment will impose influence upon both variables *concurrently and in a positive direction* with respect to the relationship between trust and distrust.
-That is to say, confidence increases insofar as trust in elections increases and distrust decreases; since distrust detracts from trust, then an accurate measure of confidence must take that constraint into account.
-
-## Results
-
-I first review responses to the survey items capturing trust and distrust separately by treatment condition.
-When distinguished by experiment condition, trust in elections admin is noticeably higher for those who read the treatment vignette.
-The difference is more pronounced for some items over others.
-That being said, there is a definite distinction between items pertaining to Maricopa County, AZ compared to items that pertain to a respondent's local area.
-In fact, the treatment appears to have hardly made a difference when the items concerned one's local area.
-
-```{r}
-#| label: fig-trustlikert
-#| fig-cap: "Trust in Election Administration by Experiment Condition"
-#| fig-height: 4.5
-#| fig-pos: "h"
-
-p10.trust.treat
-
-```
-
-Reviewing item responses distinguished by treatment condition reveals particulars of the treatment effect (@fig-trustlikert).
-Among the items that asked about Maricopa County, AZ, it is a bit easier to see upon which items the treatment vignette had the greatest effect.
-It appears that the main effect of the treatment is upon responses to the item that measures confidence in the security of election technology.
-
-Regarding confidence in the commitment of election staff and volunteers, a higher proportion of respondents in the treatment group selected "Very confident" over "Somewhat confident" compared to the control group, but only for items concerning Maricopa County, AZ.
-Although confidence in election workers was generally high across the board, the shift from "Somewhat" to "Very" confident for items pertaining to election worker *commitment* to fairness and accuracy seems to clearly speak to the group being recruited, i.e., veterans and family members.
-However, the same visible shift in proportion from "Somewhat" to "Very" confident isn't observed when items asked about one's local area, which undermines the suggestion that the treatment effect can be cleanly attributed to respondent's feelings about veteran service members and their families.
-It may be the case that respondents harbor particular attitudes or sentiment about Maricopa County, AZ itself, or there may be nothing uniquely special about Maricopa County, AZ supposing that elections anywhere beyond one's local area generally garner slightly less confidence.
-
-What this does suggest, however, is that trust in the fairness and accuracy of the electoral process is notably higher upon the notion that military veterans will be directly engaged as election staff and volunteers in places where such trust falters.
-The question turns to whether this also lowers distrust, or the extent to which one expects electoral fraud to occur.
-
-```{r}
-#| label: fig-distrustlikert
-#| fig-cap: "Disrust in Election Administration by Experiment Condition"
-#| fig-height: 4.5
-#| fig-pos: "h"
-
-p11.distrust.treat
-
-```
-
-Similar to the trust scale items, the items on the distrust scale were associated with lower distrust in the treatment condition compared to the control.
-A quick glance at @fig-distrustlikert shows what appears to be a significant reduction in distrust, especially regarding the expectations that many votes wouldn't be counted, many voters would be turned away, and that election officials would discourage voters from casting a ballot.
-Interestingly, the expectation that there would be foreign interference in elections in Maricopa County, AZ were pretty resilient against the treatment.
-And again, responses for items pertaining to elections in one's local area are practically indistinguishable between treatment and control.
-
-### Confidence in elections
-
-Once trust and distrust were composed into unified variable of confidence in elections, I then examined distribution of the dependent variable followed by analysis of the effect of the treatment by comparison of mean differences between experiment conditions.
-Recall that on this scale, zero reflects insecurity (e.g., similar or equal values of trust and distrust), whereas values diverging from zero reflect confidence in either direction, trust or distrust respectively.
-Positive values reflect trust in elections administration (e.g., elections will be fair and accurate), whereas negative values reflect distrust in elections (i.e., expectation that election fraud will occur).
-To retain a meaningful zero, I rescaled the sum scores to range from -3 to 3[^9] and then superimposed two histograms of confidence scores: one derived from AZ items and another for scores derived from local area items.
-Doing this is illustrative of the relative distribution of confidence that differed depending on the location of elections referred to in the survey items (e.g., Maricopa County, AZ).
-
-As revealed by review of the item responses, the distribution of confidence differed depending on whether survey items pertained to elections in Maricopa County, AZ, or elections within one's local area.
-
-```{r}
-#| label: fig-dist
-#| fig-cap: "Overlapping Distribution of Confidence in Elections for AZ and Local Area"
-#| fig-pos: "H"
-
-ggplot(df) +
-  geom_histogram(
-    aes(x = conf.az.rescaled , y = after_stat(density)),
-    bins = 15,
-    alpha = 0.2,
-    color = 1,
-    fill = "red"
-  ) +
-  geom_histogram(
-    aes(x = conf.lcl.rescaled , y = after_stat(density)),
-    bins = 15,
-    alpha = 0.2,
-    color = 1,
-    fill = "blue"
-  ) +
-  geom_segment(
-    x = round(mean(df$conf.az.rescaled), 2),
-    y = 0,
-    yend = 0.35,
-    color = "firebrick",
-    lwd = 1.4,
-    linetype = 2
-  ) +
-  geom_segment(
-    x = round(mean(df$conf.lcl.rescaled), 2),
-    y = 0,
-    yend = 0.35,
-    color = "darkblue",
-    lwd = 1.4,
-    linetype = 2
-  ) +
-  annotate(
-    "text",
-    x = round(mean(df$conf.az.rescaled), 2),
-    y = 0.40,
-    label = paste("AZ =", round(mean(
-      df$conf.az.rescaled
-    ), 2), "(", round(sd(
-      df$conf.az.rescaled
-    ), 2), ")"),
-    color = "firebrick"
-  ) +
-  annotate(
-    "text",
-    x = round(mean(df$conf.lcl.rescaled), 2),
-    y = 0.43,
-    label = paste("Local area =", round(mean(
-      df$conf.lcl.rescaled
-    ), 2), "(", round(sd(
-      df$conf.lcl.rescaled
-    ), 2), ")"),
-    color = "darkblue"
-  ) +
-  labs(
-    x = str_wrap("Confidence", width = 85),
-    y = "Density",
-    caption = str_wrap(
-     "Mean (std.deviation). Mean difference = 0.33, CI [0.27, 0.38], t = 11.613, df = 1286, p < 0.01",
-     width = 95)) +
-  theme_bw(base_family = "TeX Gyre Pagella")
-
-```
-
-Overall, the sample expressed more trust in elections relative to distrust seeing as how the distribution of confidence is largely positive (@fig-dist).
-However, there's a clear difference between confidence in Maricopa county, AZ elections and elections within one's local area.
-A paired t-test confirms that this difference was statistically significant, though somewhat small (mean difference $= 0.325$, $95\%$ CI $[0.27, 0.38]$, $t(1286) = 11.61$, $p < .001$).
-Nonetheless, respondents appeared less confident regarding elections in Maricopa County, AZ, but held more confidence in elections administration in their local area.
-This complements previous research that demonstrates a similar bias favorable to one's local area [@stewart2022].
-
-Accordingly, when confidence levels are distinguished by experiment condition, the treatment vignette only had an effect upon survey items pertaining to elections in Maricopa County, AZ.
-Conducting an independent samples t-test (i.e., Welch Two Sample t-test) suggests that the effect of the treatment compared to the control condition is positive, statistically significant, yet substantially pretty small.
-
-```{r}
-#| label: tbl-ttest
-#| tbl-cap: "Mean Difference of Treatment Compared to Control Condition"
-#| tbl-pos: H
-
-# conduct two t-tests using `rstatix::t_test`, bind results by row, and pipe
-# into table
-dplyr::bind_rows(
-  df |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
-  rstatix::t_test(formula = conf.az.rescaled ~ group,var.equal = F,detailed = T),
-  df |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
-  rstatix::t_test(formula = conf.lcl.rescaled ~ group,var.equal = F, detailed = T)
-  ) |> 
-  # specify columns and column names
-  select(
-    Diff = estimate,
-    treat_mean = estimate1,
-    control_mean = estimate2,
-    treat_n = n1,
-    control_n = n2,
-    t = statistic,
-    p, df, conf.low, conf.high) |> 
-  mutate(
-    Place = dplyr::case_when(
-      p <= 0.05 ~ "Maricopa County, AZ", 
-      p > 0.05 ~ "Local Area"), 
-    .before = Diff) |> 
-  insight::format_table(stars = T) |> 
-  # insight::export_table(format = "md") # alternate
-  # output table as `kable` for LaTeX pdf
-  kableExtra::kbl( 
-    booktabs = T,
-    col.names = c("Place", "$\\bar{x}_{diff}$", "$\\bar{x}_{treat}$", "$\\bar{x}_{control}$",
-                  "$treat_{n}$", "$control_{n}$", "t", "p", "df", "CI"), 
-    escape = F) |> 
-  kableExtra::footnote(general = "Welch Two Sample t-tests of difference between Confidence in Elections by Treatment Condition.") |> 
-  kableExtra::kable_styling(
-    font_size = 9, 
-    protect_latex = T)
-
-```
-
-The results of @tbl-ttest show that, on a scale ranging from -3 to 3, the effect of the treatment is associated with a $0.20$ average difference in confidence in elections in Maricopa County, AZ, compared to the control group.
-When the dependent variable is centered to have a mean of $0$ and standard deviation of $1$, standardized parameters permit interpretation of the treatment effect in terms of standard deviations; the standardized difference in confidence between treatment and control is $0.16$ (CI $[0.06, 0.27]$).
-Nothing is more illustrative than graphs and lines, however.
-
-```{r}
-#| label: fig-coef1
-#| layout-nrow: 2
-#| fig-height: 3.5
-#| fig-cap: "Confidence in Elections by Experiment Condition"
-#| fig-subcap: 
-#|   - "Confidence by Treatment Condition"
-#|   - "Trust and Distrust by Treatment Condition"
-
-# coef plot of treatment effect on confidence distinguished by location
-conf.coef1 <- jtools::plot_summs(
-  lm(conf.az.rescaled ~ group, data = df), 
-  lm(conf.lcl.rescaled ~ group, data = df), 
-  center = T, scale = T, transform.response = T,
-  model.names = c("Conf.AZ", "Conf.Local"),
-  coefs = c("Treatment" = "groupTreatment"), 
-  colors = c("red", "black"),
-  point.shape = c(8, 1))+
-  ggplot2::expand_limits(x = c(-0.25, 0.25))+
-  labs(y = "")+
-  theme_bw(base_family = "TeX Gyre Pagella")
-
-# Coef plots of trust and distrust models for AZ and Local items
-conf.coef2 <- jtools::plot_summs(
-  lm(trust.scores.az ~ group, data = df),
-  lm(distrust.scores.az ~ group, data = df),
-  lm(trust.scores.lcl ~ group, data = df),
-  lm(distrust.scores.lcl ~ group, data = df),
-  center = T, scale = T, transform.response = T,
-  model.names = c("Trust.AZ", "Distrust.AZ", "Trust.Local", "Distrust.Local"),
-  coefs = c("Treatment" = "groupTreatment"),
-  colors = c("red", "red", "black", "black"),
-  point.shape = c(8, 8, 1, 1)
-)+
-  ggplot2::expand_limits(x = c(-0.25, 0.25))+
-  labs(y = "")+
-  theme_bw(base_family = "TeX Gyre Pagella")
-
-conf.coef1
-conf.coef2
-
-```
-
-@fig-coef1 displays standard difference estimates of confidence in elections by treatment condition (control condition as reference).
-@fig-coef1-1 displays two models for confidence in elections in Maricopa County, AZ, and one's local area by treatment condition; @fig-coef1-2 displays the same except *confidence* is decomposed into its two components, *trust* and *distrust*.
-These figures merely illustrate the effect of the treatment with respect to the relationship between trust and distrust; ultimately confidence improves.
-
-Confidence in elections was higher among those who read the treatment vignette but remained conditional on whether the survey questions inquired about elections in Maricopa County, AZ.
-This evidence suggests that announcing efforts to recruit veterans and their families to work as election staff and volunteers may increase confidence in elections administration in places outside of one's local area, but may not boost confidence in elections within one's local area.
-
-### 2020 Election Legitimacy Beliefs
-
-I now turn to results examining the effect of the treatment on those who held onto the belief that the 2020 election results were illegitimate.
-First, reviewing responses to items that capture trust in elections, it is easy to recognize the difference between the way 2020 election deniers responded with respect to where elections were held.
-
-```{r}
-#| label: fig-legit
-#| fig-cap: "Trust in elections by treatment among those who refute the 2020 election results"
-#| fig-height: 4.5
-
-p13.trust.treat.legit
-
-```
-
-Among those who belief the 2020 election results were illegitimate, trust in Maricopa County, AZ elections was lower for each item compared to items pertaining to elections within one's local area, regardless of treatment condition.
-However, notably, trust that election technology would be secure received the lowest confidence endorsement overall.
-There was also a notable lack of trust that the voting process would be fair relative to the other items.^[What is interesting to note here is that the first three items regard the more human element of the election administration process, e.g., ensuring accuracy of counts, competence, and commitment of election workers.
-Although a neat line can't really be drawn between the first three and latter two items presented here, it is interesting to see a divergence of the usual high confidence placed in local area elections.] Now the comparative difference in responses between those in the treatment group compared to those in the control group appears substantial for items pertaining to elections in Maricopa County, AZ.
-
-```{r}
-#| label: fig-legit2
-#| fig-cap: "Distrust in elections by treatment among those who refute the 2020 election results"
-#| fig-height: 4.5
-
-p14.distrust.treat.legit
-
-```
-
-Concerning distrust among those who refuted the 2020 election results, responses items assessing one's expectation that election fraud would occur reveal the same pattern.
-Although there is not as stark a disparity between responses of those in the treatment and those in the control, among those in the treatment group, there does appear to be less expectation that election fraud would occur in Maricopa County, AZ.
-Overall, review of responses to trust (@fig-legit) and distrust survey items (@fig-legit2) does lend credence to the impact of the treatment.
-
-In order to substantiate the overall influence of the treatment on confidence in elections, I regressed the dependent variable confidence on legitimacy beliefs while controlling for partisanship.
-
-```{r}
-#| label: tbl-legit
-#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
-#| tbl-pos: H
-#| results: asis
-
-# All continuous variables are mean-centered and scaled by 1 standard deviation.
-m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = df)
-m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = df)
-
-stargazer::stargazer(
-  m1,
-  m2,
-  type = "latex", 
-  style = 'apsr',
-  header = F,
-  float = F,
-  align = T, 
-  single.row = T, 
-  dep.var.labels.include = F, model.numbers = F,
-  digits = 2,
-  column.labels = c("Confidence in AZ Elections", "w/Interaction"),
-  covariate.labels = c(
-      "Treatment",
-      "Not Legitimate",
-      "Republican",
-      "Democrat",
-      "Not Legitimate * Treatment",
-      "Constant"
-    )
-)
-
-```
-
-The first model in \ref{tbl-legit} shows that overall confidence in elections (trust - distrust) among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
-Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
-Not believing the 2020 election of Joe Biden was legitimate is negatively associated with confidence in elections.
-In order to assess the magnitude of this interaction effect of the treatment on those who refuted the 2020 election results, I ran a model where confidence in elections was regressed on the interaction between the treatment and legitimacy beliefs, controlling for partisanship.
-
-There's a positive interaction effect of the treatment vignette among those who believe that the 2020 election was not legitimate, on average and controlling for partisanship.
-This shows that the treatment effect was most influential upon those who believe the 2020 election results were illegitimate.
-The treatment alone does not reverse such beliefs, but this shows where its influence is perhaps most potent.
-
-## Conclusion
-
-Publicized announcements that election officials are actively recruiting former military service members to work as election staff and volunteers is associated with slightly greater confidence in elections compared to election worker recruitment announcements that do not explicitly mention targeted recruitment of former military service members.
-Moreover, increased levels of confidence is limited to elections beyond one's local area and, of course, in anticipation of election night.
-Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
-
-Bear in mind that confidence in elections for one's local area is already higher than for those beyond.
-Thus, there's already more insecurity concerning elections elsewhere for whatever reason.
-In the anticipatory period prior to national elections, publicized efforts to recruit veterans to work as election staff and volunteers may be a small, but positive, step towards reducing insecurity in elections that occur elsewhere.
-Especially among those who maintained a steadfast degree of distrust in elections.
-Despite a lack of evidence that systematic electoral fraud had occurred in the 2020 election, a substantial proportion of the population were unwilling to affirm the legitimacy of the results.
-However, despite such legitimacy beliefs, most were not consistent as they expressed varying levels of trust in different aspects of elections administration.
-
-These results speaks more to the influence that military veterans have among those who distrust the electoral process and refute the legitimacy of prior outcomes than it does to the public more generally.
-In general, public confidence appears strongest when the elections under consideration regard those within one's local community.
-Yet, such strong confidence is not generalized outward to the institution of elections administration as a whole.
-Insecurity in the integrity of the electoral process and its administration may be naturally higher for elections that occur further from home.
-Whether that is due to some local favorability bias or some outward negativity bias is hard to say.
-And seeing as how insecurity presents vulnerability, it is perhaps far easier to inspire a general sense of distrust in the process and its administration in places not near and around one's local area.
-
-### Limitations
-
-As far as I'm aware, both the items, their wording, and their composition into measurement scales are unique to this study.
-This renders the composite scores for trust in elections sample dependent and limits comparability with other cross-sectional survey data.
-
--   limitations: interpretations of the treatment effect are limited.
-    *   The sample may not be generalizable to the population.
-    *   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts.
--   Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
--   Results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons: 
-    *  First, the vignettes and many survey questions ask about Maricopa County, AZ specifically.
-Adding a specific county in the vignette adds in a factor that cannot be accounted for without additional treatments that eliminate the setting as a potential influence.
-Moreover, the specificity of the setting adds in even more unexplained error---some people may have attitudes about the county in question, others won't, while others may be muffed to consider any random county in the U.S.
-they know nothing about.
-Adding the county undermines the confidence that treatment effects are solely attributable to veterans to an unknown degree.
-    *   Second, questions ask about one's own local community in addition to identical questions which asked about Maricopa County, AZ.
-Consequently, many questions within the questionnaire were duplicates with but one difference.
-This isn't uncommon in surveys, however in this case, it lengthened the survey to a degree that potentially resulted in a higher drop off rate.
-More importantly, the quality of responses were likely diminished to some unknown extent.
-Although it is possible to compare questions asked about Maricopa County, AZ to questions about one's local area, the quality of that comparison is limited by the unknown extent of fatigue induced by answering the same questions twice.
-It wasn't just that some questions were asked multiple times, almost all of the questions were duplicated.
-After completing a long series on Maricopa County, participants then answered the same questions about the local community.
-I haven't computed the rate to which participants dropped from the survey, yet items contain more missing values toward the end of the survey.
-Some participants dropped out, but some simply skipped a few items.
-The extent to which this occurred is minor, but it does suggest fatigue as a worthy of consideration.
-
-\pagebreak
-
-## Appendix A: Survey Experiment Vignettes and Survey Items {#sec-appendix-a}
-
-::::: {#fig-vignettes .content-visible layout-ncol="2" when-format="html" unless-format="pdf"}
-::: {#fig-treatment}
-### Treatment Vignette
-
-| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Army veteran Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-::: {#fig-control}
-### Control Vignette
-
-| **Local Residents Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-Fabricated Article Vignettes utilized as Experimental Stimulus
-:::::
-
-::::: {.content-hidden unless-format="pdf" layout="[0.45, -0.1, 0.45]"}
-::: {#first-column}
-### Treatment Vignette
-
-| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Army veteran Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-::: {#second-column}
-### Control Vignette
-
-| **Local Residents Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-:::::
-
-\newpage
-
-## Appendix B: Sample Demographics {#sec-appendix-b}
-
-The median age was 46 (mean age was $47$), $51.7\%$ ($n = 658$) women, $47\%$ ($n = 598$) men, and approximately $1.3\%$ who identified as either Non-binary/third gender ($n = 7$) or preferred not to say ($n = 9$).
-A large proportion of the sample identified as White or Caucasian ($n = 975, 76.65\%$), while all other non-White respondents comprised $27.83\%$ ($n = 297$) of the sample.
-Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised $13\%$ of the sample; those with either degree at the Associate or Bachelor's level comprised $36.24\%$, while $22.25\%$ had some college but no degree; and $28.46\%$ had either a high school level or equivalent education or less than high school.
-The largest proportion of the sample identified as Democrat at $44.64\%$, followed by Republicans at $42.59\%$.
-The proportion of true Independents^[Independent 'leaners' were grouped into the respective party affiliation in which they lean.] was $12.78\%$.
-
-```{r}
-#| label: tbl-demog
-#| tbl-cap: "Sample Demographics"
-#|
-
-# descriptive stats of categorical variables
-# best method for html document
-tbl.desc <- df |>  
-  labelled::set_variable_labels(
-    age_4cat = "Age group",
-    gender_3cat = "Gender",
-    race2 = "Race/Ethnicity",
-    race_wnw = "White or Non-White",
-    educ_4cat = "Education",
-    partyid_3cat = "Party ID",
-    milrelation  = "Military Relation"
-  ) |> 
-  gtsummary::tbl_summary(
-    by = group,
-    include = c(
-    age_4cat, 
-    gender_3cat, 
-    race2,
-    race_wnw,
-    educ_4cat, 
-    partyid_3cat,
-    milrelation),
-    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
-    missing = "ifany",
-    missing_text = "NA") |> 
-  gtsummary::add_n() |> 
-  gtsummary::add_overall() |> 
-  gtsummary::modify_header(label = "**Demographic**") |> 
-  gtsummary::bold_labels()
-
-gtsummary::as_gt(tbl.desc) |>  
-  gt::tab_footnote(
-    footnote = "Independents do not identify nor 'lean' toward either political party",
-    placement = "left"
-    ) |>  
-  gt::cols_align(align = 'left', columns = everything()) |> 
-  gt::tab_options(
-    table.font.size = "small",
-    data_row.padding = gt::px(1)
-  )
-
-```
-
-\newpage
-
-## Appendix C: Trust and Distrust {#sec-appendix-c}
+## Trust and Distrust
 
@@
 This result, however, suggests that the location of which the survey items pertain (and perhaps other factors) makes a substantial difference in the pattern of responses, but also raises valid questions as to whether the items accurately measure the latent variable constructs in the first place.
-
-\pagebreak
-
-[^1]: I adopt a distinction made between *trustworthiness* and *trust* in elections [@stewart2022].
-The "*worthiness*" of one's trust in the conduct and administration of elections is based on the extent that outcomes of an election reasonably follow the rules prescribed and can be adjudicated as such.
-To put it briefly, trustworthiness is built by the structure, procedures, and practices of the institution, in this case election administration.
-The public's trust in elections, however, is amendable to an indefinite number of factors that may be unrelated to the formal structure or procedures of election administration.
-To illustrate, I can recognize that my car is trustworthy prior to ever driving it because it is structurally sound; it passes whatever criteria upon inspection, it is sufficiently fueled, and appears to be in generally good working order.
-I have every reason to deem it *worthy of my trust*.
-However, I don't trust my car because I am sure it is haunted.
-
-[^2]: There's little that could justify a conceptual distinction between public trust pre-election and public trust post-election.
-The temporal element renders the difference between pre- and post-election more operative than conceptual at a foundational level.
-
-[^3]: Note that election insecurity is used in place of electoral confidence simply to emphasize the anticipatory nature of the attitudes in question.
-Election insecurity is taken to denote a lack of confidence.
-
-[^4]: Demographic breakdown of the sample are included in Appendix B.
-
-[^5]: Complete text of treatment and control vignettes are included in the Appendix
-
-[^6]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
-
-[^7]: Survey item wording and responses are included in Appendix A.
-
-[^8]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
-The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024], yet there is no general consensus on the most appropriate method generally.
-The use of either appears to largely depend on the researcher's particular research objective, theoretical suppositions, and necessity.
-Another common concern is the inappropriate treatment of ordinal variables as interval which levy strong assumptions, e.g., each item contributes equally to the variable being measured and that ordinal response categories are equidistant as though on an interval scale [@wang2013; for contrast, see @robitzsch2020].
-
-[^9]: This range is mostly arbitrary, as a range from -1 to 1 works much the same.
-When relying on simple sum total score, the scale ranges from -15 to 15.
-So a single point increase from 0 to 1 may reflect a combination of a single "Very confident" response on a trust item compensated by a single "Somewhat likely" response on a distrust item (i.e., 3-2 = 1), or some other equivalent combination.
-Although the use of mean scores would place scores back onto the response scale metric (e.g., from 0 to 3, reflective of "not at all" to "very"), this results in a unipolar scale (from 0 to 3).
-The bipolar scale resulting from the composition of positive trust and negative distrust engenders meaning to zero and negative values.
-As such, composite mean scores become inappropriate and interpretation of scores would no longer be feasible.
-In other words, negative values on the scale for confidence in elections hold substantive meaning (e.g., distrust, absent trust), which makes transforming scores to fit a unipolar scale inappropriate.

### 2025-03-11 hours.R

@@ -1,153 +1,0 @@
-# logging hours worked
-
-# create data.frame (or `tbl_df`)
-hours <- tibble::tribble(
-  ~ date,
-  ~ proj,
-  ~ weekday,
-  ~ start,
-  ~ end,
-  ~ duration.hours,
-  ~ duration.period,
-  ~ cumhours_per_proj
-)
-
-
-# d = Date
-d <- timestamp(
-  stamp = format(Sys.time(), "%Y-%m-%d"),
-  prefix = NULL,
-  suffix = NULL
-) |>
-  as.Date()
-
-# t1 = START TIME
-# NOTE: Run this once you START doing stuff to stamp "clock in" time
-t1 <- timestamp(
-  stamp = format(Sys.time(), "%H:%M:%S"),
-  prefix = NULL,
-  suffix = NULL
-) |> hms::as_hms()
-
-# alternative: input time manually  
-t1 <- hms::as_hms("09:20:55")
-
-# t2 = END TIME
-# NOTE: Run this once you STOP doing stuff to stamp "clock out" time
-t2 <- timestamp(
-  stamp = format(Sys.time(), "%H:%M:%S"),
-  prefix = NULL,
-  suffix = NULL
-) |> hms::as_hms()
-
-
-# tdiff = duration.hours
-tdiff <- round(difftime(t2, t1, units = "hours"), 2)
-
-# project/task worked on
-
-proj <- "vets survey"
-proj <- "text analysis"
-proj <- "prospectus"
-
-# add today's time stamps to data frame and add in additional variables
-hours <- hours |>
-  # add row to time sheet
-  dplyr::add_row(
-    date = d,
-    proj = proj,
-    start = t1,
-    end = t2,
-    duration.hours = tdiff
-  ) |>
-  
-  # add in column denoting day of the week
-  dplyr::mutate(weekday = lubridate::wday(date, label = T, abbr = F),
-                .before = start) |>
-  
-  # convert `duration.hours` to class `dbl` instead of class `difftime`
-  # dplyr::mutate(duration.hours = as.numeric(duration.hours), .keep = "unused") |>
-  
-  # see `duration.hours` as period with hours, minutes, and seconds
-  dplyr::mutate(duration.period = lubridate::as.period(duration.hours),
-                .after = duration.hours) |>
-  
-  # group by project/task in order to calculate cumulative hours worked on task
-  dplyr::group_by(proj) |>
-  
[…]

### 2025-03-11 src/02-data-postprocessing.R

@@ -1,368 +1,0 @@
-set.seed(1234)
-
-# load packages
-library(tidyverse)
-
-# load data
-load("data/research-paper-data-20241029.Rdata")
-
-# subset data and do some other stuff ::::::::::::::::::::::::::::::::::::::####
-
-df <- data |> 
-  select(
-    rowID,
-    response_id,
-    group,          # Experimental condition: treatment or control
-    partyid_3cat,   # partyID in 3 categories, true independents (not leaners)
-    dem.dum,        # dummy variable of democrats
-    rep.dum,        # dummy variable of republican
-    ind.dum,        # dummy variable of independents
-    race2,          # race including Hispanic/Latino/Spanish origin
-    race_wnw,       # race dichotomous between White and Non-White
-    educ_4cat,      # educational attainment in four categories
-    educ_4cat.num,  # educational attainment in four categories, numeric
-    gender,         # male, female, Non-binary/Third gender, Pref. not to say
-    gender_3cat,    # male, female, other or preferred not to say
-    age_4cat,       # age in years in 4 groups
-    mil_anyrelation,# relation or no relationship with military service
-    milrelation,    # particular relationship with military service
-    q5:q8,          # pre-treatment survey items
-    q19:q24,        # trust in elections in Maricopa County, AZ
-    q25:q26,        # concern for voter safety in Maricopa County, AZ
-    q28_1:q28_5,    # eef in Maricopa County, AZ
-    q30:q35,        # trust in elections in local area
-    q36:q38,        # concern for voter safety in local area
-    q40_1:q40_5,    # eef in Maricopa County, AZ
-    contains(".r"), # recoded numeric versions of the variables above
-    contains(".n")  # recoded numeric versions of the variables above
-)
-
-df <- df |> labelled::set_variable_labels(
-  q28_1 ="There will be voter fraud, that is, people who are not eligible to vote will vote, or vote more than once",
-  q28_2 ="Many votes will not actually be counted",
-  q28_3 ="Many people will show up to vote and be told they are not eligible",
[…]

### 2025-03-11 docs/_tex/index.tex
removed a lot of clutter

@@
 \usepackage{xcolor}
-\usepackage{caption}
-\usepackage{anyfontsize}
 \usepackage{dcolumn} 
@@
   on the extent that outcomes of an election reasonably follow the rules
-  prescribed and can be adjudicated as such. To put it briefly,
-  trustworthiness is built by the structure, procedures, and practices
-  of the institution, in this case election administration. The public's
-  trust in elections, however, is amendable to an indefinite number of
-  factors that may be unrelated to the formal structure or procedures of
-  election administration. To illustrate, I can recognize that my car is
-  trustworthy prior to ever driving it because it is structurally sound;
-  it passes whatever criteria upon inspection, it is sufficiently
-  fueled, and appears to be in generally good working order. I have
+  prescribed and can be adjudicated as such. The public's \emph{trust}
+  in elections, however, is amendable to an indefinite number of factors
+  that may be unrelated to the formal structure or procedures of
+  election administration. I can recognize that my car is trustworthy
+  prior to ever driving it because it is structurally sound; I have
   every reason to deem it \emph{worthy of my trust}. However, I don't
@@
 
-Even though election officials can do a lot to secure election
-integrity, there's not much they can do to cement public confidence
-after election night passes. At best, election officials can ease public
-insecurities prior to election night.
-
 One point of contention that election officials have faced in the past
@@
 on how voter interaction with election workers
-(\citeproc{ref-claassen2008}{Claassen et al. 2008}), or the voter
-experience generally (\citeproc{ref-atkeson2007}{Atkeson and Saunders
-2007}), influences evaluations of election administration. As such,
-election worker competency has been examined as a factor significant to
-evaluations of performance of elections (\citeproc{ref-hall2007}{T.
-Hall, Monson, and Patterson 2007}; \citeproc{ref-hall2009}{T. E. Hall,
-Quin Monson, and Patterson 2009}). However, considering that individual
-perceptions and preconceived notions play a huge role in cognition
-(\citeproc{ref-cikara2014}{Cikara and Bavel 2014};
-\citeproc{ref-vanbavel2021}{Van Bavel and Packer 2021}), it is
-reasonable to expect that the group an election worker hails from would
-be an important influence upon the voter's evaluation of the electoral
-process.
+(\citeproc{ref-claassen2008}{Claassen et al. 2008}), voting technology
+(\citeproc{ref-herrnson2009}{Herrnson, Niemi, and Hanmer 2009}), and the
+voter experience generally (\citeproc{ref-atkeson2007}{Atkeson and
+Saunders 2007}), influences evaluations of election administration. As
+such, election worker competency has been examined as a factor
+significant to evaluations of performance of elections
+(\citeproc{ref-hall2007}{T. Hall, Monson, and Patterson 2007};
+\citeproc{ref-hall2009}{T. E. Hall, Quin Monson, and Patterson 2009}).
+However, considering that individual perceptions and preconceived
+notions play a huge role in cognition (\citeproc{ref-cikara2014}{Cikara
+and Bavel 2014}; \citeproc{ref-vanbavel2021}{Van Bavel and Packer
+2021}), it is reasonable to expect that the group an election worker
+hails from would be an important influence upon the voter's evaluation
+of the electoral process.
 
@@
 support the notion that emphasizing veterans as the target of election
-worker recruitment efforts eases pre-election insecurity to a limited
-extent. Expectations of electoral fraud and concerns for voter safety
-were lower among those who read a fabricated announcement that veterans
-are being recruited to work as election staff and volunteers compared to
-those who read a control vignette where veterans were not mentioned.
-Notable is that there was a significant difference in confidence among
-those in the treatment condition who believe that results of the 2020
-election were illegitimate.
+worker recruitment efforts eases pre-election insecurity. Expectations
+of electoral fraud and concerns for voter safety were lower among those
+who read an announcement that veterans are being recruited to work as
+election staff and volunteers compared to those who read a control
+vignette where veterans were not mentioned\footnote{The vignettes
+  written were based on real news stories}. Notable is that there was a
+significant difference in confidence among those in the treatment
+condition who believe that results of the 2020 election were
+illegitimate.
 
@@
 dependent variable, which I broadly refer to as \emph{confidence in
-elections}. I preview the different methods of analysis alongside
-presentation of the results. Before concluding, I dedicate time to
-discuss the limitations of the study and lessons learned. I close by
-offering my interpretation of the results and suggest potential avenues
-for future inquiry.
+elections}. I close by offering my interpretation of the results and
+suggest potential avenues for future inquiry.
 
@@
 (\citeproc{ref-ferrer2024}{Ferrer, Thompson, and Orey 2024}). In
-addition to ensuring election admin offices were adequately staffed, the
+addition to ensuring election offices were adequately staffed, the
 controversy of the 2000 general election made the public more attentive
@@
 particular, voting technology (\citeproc{ref-herrnson2009}{Herrnson,
-Niemi, and Hanmer 2009}) and election worker competence was a of
-interest in election studies (\citeproc{ref-claassen2008}{Claassen et
-al. 2008}; \citeproc{ref-hall2007}{T. Hall, Monson, and Patterson 2007};
+Niemi, and Hanmer 2009}) and election worker competence was of interest
+in election studies (\citeproc{ref-claassen2008}{Claassen et al. 2008};
+\citeproc{ref-hall2007}{T. Hall, Monson, and Patterson 2007};
 \citeproc{ref-hall2009}{T. E. Hall, Quin Monson, and Patterson 2009}).
@@
 turn, increased worry for the safety of voters and election workers
-alike.
-
-Suffice to say, pre-election anxiety consists of more than confidence in
-fairness and accuracy of vote counts in light of added safety concerns.
-It is not hard to recognize that increased tension in the pre-election
-period makes for a volatile political environment. Sustaining
-trustworthiness in election administration is only more difficult in an
-environment where turnover of election workers increases and the
-struggle to recruit volunteers worsens in light of safety concerns.
-Since election worker performance is significant to public evaluation of
-elections, added safety concerns that drive out election staff and repel
-volunteers can only detract from trustworthiness of the institution.
+alike. Since election worker performance is significant to public
+evaluation of elections, added safety concerns that drive out election
+staff and repel volunteers can only detract from trustworthiness of the
+institution.
 
@@
 by capturing assessments about the perceived accuracy of vote counts
-(e.g., whether votes are/were counted as intended). Or in other words,
-by the extent the public is confident in the accurate administration of
-elections.
-
-Assessing the public's \emph{trust} in elections has not been
-straightforward, however. Inquiry into public trust in elections has
-been approached by scholars of political science in many different ways
-(\citeproc{ref-cook2005}{Cook and Gronke 2005};
-\citeproc{ref-hardin2004}{Hardin 2004}), often distinguishable by the
-scope of the research question and more or less constrained by the
-particular conception of public trust. Quite often, trust in election
-administration is conflated with trust in government \emph{writ} large,
-government legitimacy, government or system responsiveness, or even
-satisfaction with democracy (\citeproc{ref-daniller2019}{Daniller and
-Mutz 2019}). At this level, not only is the level of public trust in
-elections sometimes vague, but there's little consideration over the
-difference between such attitudes pre-election and post-election. In
-contrast, a considerable amount of research tends to conceive of public
-trust in accordance with the institution in question
-(\citeproc{ref-atkeson2007}{Atkeson and Saunders 2007};
-\citeproc{ref-hooghe2018}{Hooghe 2018}).
-
-Elections administration is just one institution a part of the larger
-set of institutions which form the electoral system. As such, the
-performance of the institution along with the rest ``\ldots lends
-credibility to the outcome of an election: whether it is considered by
-citizens and the international community to be fair and legitimate.''
-(\citeproc{ref-stewart2022}{Stewart 2022, 236}). Intuitively, enhancing
-public trust in elections would best be accomplished by enhancing the
-\emph{trustworthiness} of the institution, i.e., consistently doing the
-things that election officials already regularly do come election time.
-However, trust and confidence in elections has become ever more
-precarious over the last few election cycles. Especially considering
-public polling data since 2000 shows that confidence that votes were, or
-would be, counted as intended was in a consistent decline despite
-efforts towards bolstering election integrity and trustworthiness
-(\citeproc{ref-sances2015}{Sances and Stewart 2015}). This is even more
-pronounced considering the role that partisanship has had on such
-confidence over accuracy of vote count (\citeproc{ref-sances2015}{Sances
-and Stewart 2015}; \citeproc{ref-stewart2022}{Stewart 2022}).
+(e.g., whether votes are/were counted as intended).
+
+Intuitively, enhancing public trust in elections would best be
+accomplished by enhancing the \emph{trustworthiness} of the institution,
+i.e., consistently doing the things that election officials already
+regularly do come election time. However, trust and confidence in
+elections has become ever more precarious over the last few election
+cycles. Especially considering public polling data since 2000 shows that
+confidence that votes were, or would be, counted as intended was in a
+consistent decline despite efforts towards bolstering election integrity
+and trustworthiness (\citeproc{ref-sances2015}{Sances and Stewart
+2015}). This is even more pronounced considering the role that
+partisanship has had on such confidence over accuracy of vote count
+(\citeproc{ref-sances2015}{Sances and Stewart 2015};
+\citeproc{ref-stewart2022}{Stewart 2022}).
 
@@
 election. The latter is \emph{empirical}---a judgement discerned in
-hindsight after the experience of the election event has occurred.
-Evaluations of one's own trust and confidence in election administration
-based on the experience of voting is influenced by that very experience.
-As discussed by Stewart (\citeproc{ref-stewart2022}{2022}), not only was
+hindsight after the experience of the election event has occurred. As
+discussed by Stewart (\citeproc{ref-stewart2022}{2022}), not only was
 confidence in vote count accuracy influenced by the voter experience,
@@
 influence that the election results would also have on such evaluations.
-In other words, evaluations of trust and confidence post-election are
-influenced by one's interpretation of their experience. The subtle
-difference is simply the degree of uncertainty one feels in anticipation
-of the next election event. This study focuses primarily on that
-\emph{anticipatory} kind of confidence, which speaks more to those
-insecurities\footnote{Note that election insecurity is used in place of
-  electoral confidence simply to emphasize the anticipatory nature of
-  the attitudes in question. Election insecurity is taken to denote a
-  lack of confidence.} based on perceptions of the institution's
-trustworthiness than upon the particular voter experience.
+In other words, trust evaluations post-election are influenced by one's
+interpretation of their experience and election results. This study, in
+contrast, focuses primarily on that \emph{anticipatory} kind of
+confidence, which speaks more to those insecurities based on perceptions
+of the institution's trustworthiness than upon the particular voter
+experience.
 
@@
 COVID-19 pandemic (\citeproc{ref-abbate2020a}{Abbate 2020};
-\citeproc{ref-mena2020}{Mena 2020}). Sure, it makes sense to recruit
-veterans, but no more than any other group. After all, ensuring election
-offices are adequately staffed is everyone's problem. So there's no
-special reason to target veterans for recruitment above other groups.
-Indeed, there's no reason to discriminate recruitment efforts at all if
-the point is purely to fill staffing vacancies. However the interest in
-veterans as a special group to consider arose in light of increased and
-sudden efforts to recruit veterans into election work.
+\citeproc{ref-mena2020}{Mena 2020}). There's no special reason to target
+veterans for recruitment above other groups. Indeed, there's no reason
+to discriminate recruitment efforts at all if the point is purely to
+fill staffing vacancies.
 
@@
 mitigated discrimination against him when he was presented as a veteran
-married to man (\citeproc{ref-magni2024}{Magni and Reynolds 2024}).
+married to a man (\citeproc{ref-magni2024}{Magni and Reynolds 2024}).
 Similar research has also found that a candidate's veteran status
@@
 recruitment of veterans and their family members to work as election
-staff and volunteers would boost public confidence in election
-administration. Indeed, that is the primary hypothesis of this study.
+staff and volunteers would boost public \emph{confidence in elections
+administration}. Indeed, that is the primary hypothesis of this study.
 Although citizens may vote in various ways across the country (e.g., by
@@
 
-I considered that veterans would elicit high degrees of approval and
-support for whatever cause or issue presented. For example, I'd expect
-high approval and support for recruiting veterans to baseball teams just
-as much as for recruiting them to work as election staff. Likewise,
-asking participants whether they supported programs intent on recruiting
+Asking participants whether they supported programs intent on recruiting
 anyone to work as election staff would garner support regardless of the
@@
 fraud are related to partisanship and include partisanship as a control
-in the analysis.
+in the analysis\footnote{To be clear, I conducted an auxiliary
+  regression analysis to examine the relationship between legitimacy
+  beliefs and partisanship. Results revealed a statistically significant
+  relationship between the two variables and thus omitting either would
+  result in biased estimates.}.
 
@@
 elections (i.e., the ``confidence gap'') between elections within one's
-local area and elections beyond will be smaller when people are
+local area and elections beyond will be smaller among those who are
 presented with information about election official recruitment efforts
@@
 Survey participants read either a treatment or control vignette, which
-was a fabricated news article about efforts in Maricopa County, AZ to
-recruit election staff and volunteers for the 2024 general election. The
-treatment vignette referred to a program designed to recruit veterans
-and their family members and describes an interviewee ``Jordan Braxton''
-as an Army veteran. The control vignette simply omitted any mention of
-veterans and their family members, and didn't describe ``Jordan
-Braxton'' as an Army veteran. Beyond those small differences and the
-headlines, the article vignettes are identical. Therefore, effects can
-be attributed to the information about veterans in the treatment
-vignette\footnote{Complete text of treatment and control vignettes are
-  included in the Appendix}.
+resembled a news article about efforts in Maricopa County, AZ to recruit
+election staff and volunteers for the 2024 general election\footnote{The
+  article vignettes were written and designed by Michael Hanmer Ph.D and
+  myself with input from We the Veterans, a non-profit organization}.
+The treatment vignette referred to a program designed to recruit
+veterans and their family members and describes an interviewee ``Jordan
+Braxton'' as an Army veteran. The control vignette simply omitted any
+mention of veterans and their family members, and didn't describe
+``Jordan Braxton'' as an Army veteran. Beyond those small differences
+and the headlines, the article vignettes are identical. Therefore,
+effects can be attributed to the information about veterans in the
+treatment vignette\footnote{Complete text of treatment and control
+  vignettes are included in the Appendix}.
 
@@
 
-Note that, except for the item assessing voter confidence (i.e., votes
-counted as voters intend), most other question items from the 2022 SPAE
-inquire into the voter experience after the election has occurred. The
-items in this study, however, all inquire into confidence over one's
-expectations in anticipation of upcoming elections. In addition, other
-survey questionnaires ask similar questions that specifically contrast
-between a respondent's own local community, their state, and nationwide;
-this is in addition, or complementary to, items that distinguish between
-local area officials, state election officials, state government, and
-the U.S. federal government. The survey of this study, instead, focused
-on attitudes regarding election workers such as election officials,
-staff, and volunteers specific to the location mentioned in the
-vignette---Maricopa County, AZ---as well as specific to one's local
-area\footnote{Note that I refer to the items as either `AZ items' or
-  `local items' in order to distinguish the location in which they
-  pertain.}.
+The items in this study all inquire into confidence over one's
+expectations in anticipation of upcoming elections. In addition, the
+survey of this study focused on attitudes regarding election workers
+such as election officials, staff, and volunteers specific to the
+location mentioned in the vignette---Maricopa County, AZ---as well as
+specific to one's local area\footnote{Note that I refer to the items as
+  either `AZ items' or `local items' in order to distinguish the
+  location in which they pertain.}.
 
@@
 and used to construct a variable of partisanship consisting of three
-categories: Democrat, Republican, and Independent. In this case,
-Independents are ``true'' Independents in that they do not identify with
-either political party and do not ``lean'' toward either Republican or
-Democratic parties. Self-described ``Independent leaners'' are re-coded
-as falling into the partisan category in which they lean e.g.,
-Independents who expressly report that they lean Republican are denoted
-as Republican.
+categories: Democrat, Republican, and independent.
 
@@
 ``Very {[}confident/committed{]}''. In total, five survey items measure
-different aspects of trust in elections administration. The items
-measuring confidence in elections include:
-
-Another series of five survey items captured an individual's level of
-\emph{distrust} in elections administration based on the extent to which
-they \emph{expect electoral fraud} to occur. These items were prefaced
-with the question, ``How likely do you think any or all of the following
-will happen during this year´s elections in {[}Maricopa County, AZ/ your
-local area{]}?'' Each item presented four response options: ``Not likely
-at all'', ``Not too likely'', ``Somewhat likely'', and ``Very likely''.
+different aspects of trust in elections administration.
 
@@
 
-\caption{\label{tbl-items}Survey Items for Trust and Distrust in
-Elections}
+\caption{\label{tbl-1}Survey Items for Trust and Distrust in Elections}
 
@@
 
-Similar to the items capturing trust in elections
-(Table~\ref{tbl-items}), I computed a summated score for each respondent
-reflecting the extent of their distrust in elections.
+Another series of five survey items captured an individual's level of
+\emph{distrust} in elections administration based on the extent to which
+they expect electoral fraud to occur. These items were prefaced with the
+question, ``How likely do you think any or all of the following will
+happen during this year´s elections in {[}Maricopa County, AZ/ your
+local area{]}?'' Each item presented four response options: ``Not likely
+at all'', ``Not too likely'', ``Somewhat likely'', and ``Very likely''.
+
+Similar to the items capturing trust in elections (Table~\ref{tbl-1}), I
+computed a summated score for each respondent reflecting the extent of
+their distrust in elections.
 
@@
 of the scales were intercorrelated well enough for each to compose a
-single scale presuming a unidimensional construct for each.
-
-I expected item responses from these two scales to be inversely
-correlated among the sample, but not mutually exclusive. Indeed, this is
-what I find. Polychoric correlations between the trust and distrust
-items negatively correlate as expected\footnote{See Appendix C}, as does
-the correlation between the two sum score scales. Given the ordinal
-nature of the variable items, I conducted a Spearman's rank correlation
-test (\citeproc{ref-spearman1907}{Spearman 1907}) and found a negative
+single scale presuming a unidimensional construct for each\footnote{I
+  expected item responses from the trust and distrust scales to be
+  inversely correlated among the sample, but not mutually exclusive.
+  Indeed, this is what I find. Polychoric correlations between the trust
+  and distrust items negatively correlate as expected, as does the
+  correlation between the two sum score scales. Given the ordinal nature
+  of the variable items, I conducted a Spearman's rank correlation test
+  (\citeproc{ref-spearman1907}{Spearman 1907}) and found a negative
   correlation of \(\rho = -0.49\) (\(95\%\) CI {[}-0.53, -0.44{]};
-Kendall's \(\tau = -0.39\)) between scores on the two scales for the AZ
-items (For the local item scale score correlation: \(\rho = -0.52\),
-\(95\%\) CI {[}-0.56, -0.48{]}; Kendall's \(\tau = -0.39\)). The
-negative correlation between the trust and distrust items and scores
-makes intuitive sense.
+  Kendall's \(\tau = -0.39\)) between scores on the two scales for the
+  AZ items (For the local item scale score correlation:
+  \(\rho = -0.52\), \(95\%\) CI {[}-0.56, -0.48{]}; Kendall's
+  \(\tau = -0.39\)). The negative correlation between the trust and
+  distrust items and scores makes intuitive sense. See Appendix C for
+  inter-item correlation}.
 
@@
 items of each set into separate Likert scales (also known as summated
-rating scales). Since the item response options are not
-symmetric---i.e., not bipolar with contrasting positive and negative
-response options to include a neutral middle option---then the
-\emph{trust in elections} scale could only be understood as a measure of
-trust in the positive use of the term (i.e., unipolar). Likewise, the
-expectation of fraud items fit to a scale that corresponds to a unipolar
-measure of confident \emph{distrust}, so to speak. However, many of the
-items comprising the trust scale directly oppose items capturing
-distrust. For instance, one item from the trust scale has the respondent
-report their confidence that votes will be counted as voter's intend,
-whereas a separate item from the distrust scale has the the respondent
-report their expectation that many votes will not be counted. Positive
-responses to these two items directly contradict each other, and would
-thus cancel out.
+rating scales). However, many of the items comprising the trust scale
+directly oppose items capturing distrust. For instance, one item from
+the trust scale has the respondent report their confidence that votes
+will be counted as voter's intend, whereas a separate item from the
+distrust scale has the the respondent report their expectation that many
+votes will not be counted. Positive responses to these two items
+directly contradict each other, and would thus cancel out.
 
@@
 distrust are considered as reflective of one's confidence about future
-expectations, then both can be placed along the same spectrum.
-Therefore, a lack of confidence denotes insecurity.
-
-Something may cause a person to have greater expectations that election
-fraud will occur, which in turn will always lower their trust in
-elections administration. In contrast, a person may feel a bit more
-confident in the integrity of elections, but this confidence is
-constrained by the extent to which they expect election fraud to occur.
-This means that a person's baseline level of confidence in elections
-admin must take into account their present degree of distrust---i.e.,
-their expectations of electoral fraud.
-
-Those who are, or are close to being, equally confident in both
-directions would be the most \emph{insecure} about their expectations.
-Having no trust in elections and no expectation that electoral fraud
-will occur is functionally equivalent to having equal degree of both.
-Quite literally, this reflects an uncertain feeling of ``it could go one
-way or the other'' with respect to the integrity of elections
+expectations, then both can be placed along the same spectrum. Quite
+literally, this reflects an uncertain feeling of ``it could go one way
+or the other'' with respect to the integrity of elections
 administration. Operationally, this would reflect a middling point on a
@@
 
-In light of this, I reverse coded positive expectations of electoral
-fraud and added responses from the distrust scale to the trust in
-elections scale. That is, item responses on the trust scale ranged from
-0 (``Not confident at all'') to 3 (``Very confident), whereas responses
-on the distrust scale ranged from 0 (''Not likely at all'') to -3
-(``Very likely''). Combining responses in this way resulted in an
-overall measure of \emph{confidence in elections} to serve as the
-dependent variable\footnote{The methodological concerns between the use
-  of (unit weighted) sum or mean scores compared to the use of estimated
-  factor scores for Likert scales composed of multiple Likert items are
-  legion. The use of either computed sum scores or estimated factor
-  scores as a general practice is continuously debated
-  (\citeproc{ref-mcneish2023}{McNeish 2023};
+In light of this, I reverse coded items on the distrust scale and
+combined responses to the trust in elections scale. That is, item
+responses on the trust scale ranged from 0 (``Not confident at all'') to
+3 (``Very confident), whereas responses on the distrust scale ranged
+from 0 (''Not likely at all'') to -3 (``Very likely''). Combining
+responses in this way resulted in an overall measure of \emph{confidence
+in elections} to serve as the dependent variable\footnote{The
+  methodological concerns between the use of (unit weighted) sum or mean
+  scores compared to the use of estimated factor scores for Likert
+  scales composed of multiple Likert items are legion. The use of either
+  computed sum scores or estimated factor scores as a general practice
+  is continuously debated (\citeproc{ref-mcneish2023}{McNeish 2023};
   \citeproc{ref-mcneish2020}{McNeish and Wolf 2020};
@@
 distinction between items pertaining to Maricopa County, AZ compared to
-items that pertain to a respondent's local area. In fact, the treatment
-appears to have hardly made a difference when the items concerned one's
-local area.
+items that pertain to a respondent's local area. In fact, as expected,
+the treatment appears to have hardly made a difference when the items
+concerned one's local area.
 
@@
 to ``Very'' confident isn't observed when items asked about one's local
-area, which undermines the suggestion that the treatment effect can be
-cleanly attributed to respondent's feelings about veteran service
-members and their families. It may be the case that respondents harbor
-particular attitudes or sentiment about Maricopa County, AZ itself, or
-there may be nothing uniquely special about Maricopa County, AZ
-supposing that elections anywhere beyond one's local area generally
-garner slightly less confidence.
+area. It may be the case that respondents harbor particular attitudes or
+sentiment about Maricopa County, AZ itself, or there may be nothing
+uniquely special about Maricopa County, AZ supposing that elections
+anywhere beyond one's local area generally garner slightly less
+confidence.
 
@@
 \phantomsection\label{cell-fig-distrustlikert}
-\begin{figure}[h]
+\begin{figure}[H]
 
@@
 the effect of the treatment compared to the control condition is
-positive, statistically significant, yet substantially pretty small.
+positive and statistically significant.
 
@@
 standard deviations; the standardized difference in confidence between
-treatment and control is \(0.16\) (CI \([0.06, 0.27]\)). Nothing is more
-illustrative than graphs and lines, however.
-
-\begin{figure}[!t]
+treatment and control is \(0.16\) (CI \([0.06, 0.27]\)).
+
+\begin{figure}[H]
 
@@
 
-Among those who belief the 2020 election results were illegitimate,
-trust in Maricopa County, AZ elections was lower for each item compared
-to items pertaining to elections within one's local area, regardless of
-treatment condition. However, notably, trust that election technology
-would be secure received the lowest confidence endorsement overall.
-There was also a notable lack of trust that the voting process would be
-fair relative to the other items.\footnote{What is interesting to note
-  here is that the first three items regard the more human element of
-  the election administration process, e.g., ensuring accuracy of
-  counts, competence, and commitment of election workers. Although a
-  neat line can't really be drawn between the first three and latter two
-  items presented here, it is interesting to see a divergence of the
-  usual high confidence placed in local area elections.} Now the
-comparative difference in responses between those in the treatment group
-compared to those in the control group appears substantial for items
-pertaining to elections in Maricopa County, AZ.
+Among those who refuted the 2020 election results, trust in Maricopa
+County, AZ elections was lower for each item compared to items
+pertaining to elections within one's local area, regardless of treatment
+condition. However, notably, trust that election technology would be
+secure received the lowest confidence endorsement overall. There was
+also a notable lack of trust that the voting process would be fair
+relative to the other items.\footnote{What is interesting to note here
+  is that the first three items regard the more human element of the
+  election administration process, e.g., ensuring accuracy of counts,
+  competence, and commitment of election workers. Although a neat line
+  can't really be drawn between the first three and latter two items
+  presented here, it is interesting to see a divergence of the usual
+  high confidence placed in local area elections.} Now the comparative
+difference in responses between those in the treatment group compared to
+those in the control group appears substantial for items pertaining to
+elections in Maricopa County, AZ.
 
@@
 
-The first model in \ref{tbl-legit} shows that overall confidence in
-elections (trust - distrust) among those who read the treatment vignette
-was significantly (statistically) greater than those who read the
-control, on average and netting out the effects of partisanship and
+The first model in Table \ref{tbl-legit} shows that overall confidence
+in elections (trust - distrust) among those who read the treatment
+vignette was significantly (statistically) greater than those who read
+the control, on average and netting out the effects of partisanship and
 legitimacy beliefs. Democratic partisanship remains marginally
@@
 were illegitimate. The treatment alone does not reverse such beliefs,
-but this shows where its influence is perhaps most potent.
+but this shows where its influence was most potent.
 
@@
 
-\subsubsection{Limitations}\label{limitations}
-
-As far as I'm aware, both the items, their wording, and their
-composition into measurement scales are unique to this study. This
-renders the composite scores for trust in elections sample dependent and
-limits comparability with other cross-sectional survey data.
-
-\begin{itemize}
-\tightlist
-\item
-  limitations: interpretations of the treatment effect are limited.
-
-  \begin{itemize}
-  \tightlist
-  \item
-    The sample may not be generalizable to the population.
-  \item
-    It's hard to say whether merely mentioning veterans is enough, as
-    compared to explicitly naming veterans as the target of particular
-    recruitment efforts.
-  \end{itemize}
-\item
-  Interpretation is also limited considering that no other particular
-  group, or groups are compared directly against the veteran treatment
-  vignette, i.e., additional vignettes for other comparable groups.
-\item
-  Results are limited by the survey questions, questionnaire design, and
-  experimental stimulus (i.e., vignette) for two reasons:
-
-  \begin{itemize}
-  \tightlist
-  \item
-    First, the vignettes and many survey questions ask about Maricopa
-    County, AZ specifically. Adding a specific county in the vignette
-    adds in a factor that cannot be accounted for without additional
-    treatments that eliminate the setting as a potential influence.
-    Moreover, the specificity of the setting adds in even more
-    unexplained error---some people may have attitudes about the county
-    in question, others won't, while others may be muffed to consider
-    any random county in the U.S. they know nothing about. Adding the
-    county undermines the confidence that treatment effects are solely
-    attributable to veterans to an unknown degree.
-  \item
-    Second, questions ask about one's own local community in addition to
-    identical questions which asked about Maricopa County, AZ.
-    Consequently, many questions within the questionnaire were
-    duplicates with but one difference. This isn't uncommon in surveys,
-    however in this case, it lengthened the survey to a degree that
-    potentially resulted in a higher drop off rate. More importantly,
-    the quality of responses were likely diminished to some unknown
-    extent. Although it is possible to compare questions asked about
-    Maricopa County, AZ to questions about one's local area, the quality
-    of that comparison is limited by the unknown extent of fatigue
-    induced by answering the same questions twice. It wasn't just that
-    some questions were asked multiple times, almost all of the
-    questions were duplicated. After completing a long series on
-    Maricopa County, participants then answered the same questions about
-    the local community. I haven't computed the rate to which
-    participants dropped from the survey, yet items contain more missing
-    values toward the end of the survey. Some participants dropped out,
-    but some simply skipped a few items. The extent to which this
-    occurred is minor, but it does suggest fatigue as a worthy of
-    consideration.
-  \end{itemize}
-\end{itemize}
-
-\pagebreak
-
-\subsection{Appendix A: Survey Experiment Vignettes and Survey
-Items}\label{sec-appendix-a}
-
-\begin{figure}
-
-\begin{minipage}{0.45\linewidth}
-
-\subsubsection{Treatment Vignette}\label{treatment-vignette-1}
-
-\textbf{Local Military Veterans Recruited for Election Jobs in Maricopa
-County}\\
-\strut \\
-\strut ~~PHOENIX (AP) --- Election officials in Maricopa County,
-Arizona, announced a program designed to recruit military veterans and
-their family members from the community to serve as election
-administrators, including election polling place workers, temporary
-workers, and full-time staff. As the U.S. general elections in November
-near, election officials must fill several thousand temporary positions
-and hundreds of other open positions to ensure sufficient staffing for
-the 2024 elections and beyond.\\
-\strut \\
-\strut ~~Army veteran Jordan Braxton just joined the elections
-workforce. Jordan believes their role is important to ensuring a secure,
-accurate, and transparent election, ``Many places are short on staff
-this election cycle. I served my country in the Army, and I want to do
-my part as a veteran and a citizen to ensure that everyone trusts the
-process and the outcome of the election.''
-
-\end{minipage}%
-%
-\begin{minipage}{0.10\linewidth}
-~\end{minipage}%
-%
-\begin{minipage}{0.45\linewidth}
-
-\subsubsection{Control Vignette}\label{control-vignette-1}
-
-\textbf{Local Residents Recruited for Election Jobs in Maricopa
-County}\\
-\strut \\
-\strut ~~PHOENIX (AP) ---Election officials in Maricopa County, Arizona,
-announced a program to recruit members of the community to serve as
-election administrators, including election polling place workers,
-temporary workers, and full-time staff. As the U.S. general elections in
-November near, election officials must fill several thousand temporary
-positions and hundreds of other open positions to ensure sufficient
-staffing for the 2024 elections and beyond.\\
-\strut \\
-\strut ~~Jordan Braxton just joined the elections workforce. Jordan
-believes their role is important to ensuring a secure, accurate, and
-transparent election, ``Many places are short on staff this election
-cycle. I want to do my part as a citizen to ensure that everyone trusts
-the process and the outcome of the election.''
-
-\end{minipage}%
-
-\end{figure}%
-
-\newpage
-
-\subsection{Appendix B: Sample Demographics}\label{sec-appendix-b}
-
-The median age was 46 (mean age was \(47\)), \(51.7\%\) (\(n = 658\))
-women, \(47\%\) (\(n = 598\)) men, and approximately \(1.3\%\) who
-identified as either Non-binary/third gender (\(n = 7\)) or preferred
-not to say (\(n = 9\)). A large proportion of the sample identified as
-White or Caucasian (\(n = 975, 76.65\%\)), while all other non-White
-respondents comprised \(27.83\%\) (\(n = 297\)) of the sample. Those who
-held a graduate level degree (e.g., Master's, Doctorate, or Professional
-level) comprised \(13\%\) of the sample; those with either degree at the
-Associate or Bachelor's level comprised \(36.24\%\), while \(22.25\%\)
-had some college but no degree; and \(28.46\%\) had either a high school
-level or equivalent education or less than high school. The largest
-proportion of the sample identified as Democrat at \(44.64\%\), followed
-by Republicans at \(42.59\%\). The proportion of true
-Independents\footnote{Independent `leaners' were grouped into the
-  respective party affiliation in which they lean.} was \(12.78\%\).
-
-\begin{table}
-
-\caption{\label{tbl-demog}Sample Demographics}
-
-\centering{
-
-\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lllll}
-\toprule
-\textbf{Demographic} & \textbf{N} & \textbf{Overall}  N = 1,287\textsuperscript{\textit{1}} & \textbf{Control}  N = 637\textsuperscript{\textit{1}} & \textbf{Treatment}  N = 650\textsuperscript{\textit{1}} \\
-\midrule\addlinespace[2.5pt]
-{\bfseries Age group} & 1,287 &  &  &  \\ 
-    18-34 &  & 350 (27\%) & 170 (27\%) & 180 (28\%) \\ 
-    35-54 &  & 480 (37\%) & 245 (38\%) & 235 (36\%) \\ 
-    55-74 &  & 390 (30\%) & 198 (31\%) & 192 (30\%) \\ 
-    75-85+ &  & 67 (5.2\%) & 24 (3.8\%) & 43 (6.6\%) \\ 
-{\bfseries Gender} & 1,272 &  &  &  \\ 
-    Male &  & 598 (47\%) & 289 (46\%) & 309 (48\%) \\ 
-    Female &  & 658 (52\%) & 330 (52\%) & 328 (51\%) \\ 
-    Other/Refused &  & 16 (1.3\%) & 10 (1.6\%) & 6 (0.9\%) \\ 
-    NA &  & 15 & 8 & 7 \\ 
-{\bfseries Race/Ethnicity} & 1,272 &  &  &  \\ 
-    White &  & 975 (77\%) & 478 (76\%) & 497 (77\%) \\ 
-    Asian &  & 51 (4.0\%) & 25 (4.0\%) & 26 (4.0\%) \\ 
-    Black &  & 164 (13\%) & 85 (14\%) & 79 (12\%) \\ 
-    Other &  & 24 (1.9\%) & 12 (1.9\%) & 12 (1.9\%) \\ 
-    Hispanic &  & 44 (3.5\%) & 24 (3.8\%) & 20 (3.1\%) \\ 
-    American Indian &  & 14 (1.1\%) & 5 (0.8\%) & 9 (1.4\%) \\ 
-    NA &  & 15 & 8 & 7 \\ 
-{\bfseries White or Non-White} & 1,272 &  &  &  \\ 
-    Non-White &  & 297 (23\%) & 151 (24\%) & 146 (23\%) \\ 
-    White &  & 975 (77\%) & 478 (76\%) & 497 (77\%) \\ 
-    NA &  & 15 & 8 & 7 \\ 
-{\bfseries Education} & 1,272 &  &  &  \\ 
-    H.S. or less &  & 362 (28\%) & 174 (28\%) & 188 (29\%) \\ 
-    Some college no degree &  & 283 (22\%) & 142 (23\%) & 141 (22\%) \\ 
-    College degree &  & 461 (36\%) & 236 (38\%) & 225 (35\%) \\ 
-    Postgraduate degree &  & 166 (13\%) & 77 (12\%) & 89 (14\%) \\ 
-    NA &  & 15 & 8 & 7 \\ 
-{\bfseries Party ID} & 1,268 &  &  &  \\ 
-    Independent &  & 162 (13\%) & 83 (13\%) & 79 (12\%) \\ 
-    Republican &  & 540 (43\%) & 262 (42\%) & 278 (43\%) \\ 
-    Democrat &  & 566 (45\%) & 283 (45\%) & 283 (44\%) \\ 
-    NA &  & 19 & 9 & 10 \\ 
-{\bfseries Military Relation} & 1,272 &  &  &  \\ 
-    No relation &  & 789 (62\%) & 394 (63\%) & 395 (61\%) \\ 
-    Only family &  & 362 (28\%) & 182 (29\%) & 180 (28\%) \\ 
-    Served w/fam &  & 64 (5.0\%) & 31 (4.9\%) & 33 (5.1\%) \\ 
-    Served &  & 57 (4.5\%) & 22 (3.5\%) & 35 (5.4\%) \\ 
-    NA &  & 15 & 8 & 7 \\ 
-\bottomrule
-\end{tabular*}
-\begin{minipage}{\linewidth}
-Independents do not identify nor 'lean' toward either political party\\
-\textsuperscript{\textit{1}}n (\%)\\
-\end{minipage}
-
-}
-
-\end{table}%
-
-\newpage
-
-\subsection{Appendix C: Trust and Distrust}\label{sec-appendix-c}
-
-Polychoric correlation is a measure of association between two ordered
-categorical variables each assumed to represent (i.e., indicate, be
-influenced by) two normally distributed, continuous, latent variables.
-Due to the fact that each item is an ordered categorical variable
-assumed to represent one of two latent constructs (i.e., trust or
-distrust, respectively), I examined polychoric correlations between the
-items used to construct each scale. In addition, one set of the trust
-and distrust items pertained to Maricopa County, AZ, whereas the other
-set of items were identical except that these items pertained to one's
-local area.
-
-Since the two sets of items (AZ items and Local items) are, in theory,
-supposed to capture the same normally distributed continuous latent
-variables, then the polychoric inter-item correlations should be
-significantly associated, strong, and in the same direction for the
-items that measure trust regardless of whether the items pertain to AZ
-or one's local area (likewise for distrust). Simply, trust/distrust in
-elections in AZ should strongly and positively be associated with
-trust/distrust in elections in one's local area.
-
-Additionally, the items that indicate trust should negatively correlate
-with items that indicate distrust. Furthermore, the strength of the
-negative correlations between trust and distrust should closely
-approximate if not match.
-
-\phantomsection\label{cell-fig-polycor}
-\begin{figure}[h]
-
-\caption{\label{fig-polycor}Polychoric Item Correlation Matrix}
-
-\centering{
-
-\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-polycor-1.png}}
-
-}
-
-\end{figure}%
-
-Indeed, this is what is revealed by the correlation matrix
-(Figure~\ref{fig-polycor}). Trust items correlate positively, strongly,
-and are significant regardless of location at which the items pertain.
-The same goes for distrust items. Also, items meant to measure trust
-negatively correlate with the items that measure distrust. However, the
-positive correlations are not nearly as high as would be expected
-supposing that the items are nearly identical theoretical indicators of
-the same hypothetical constructs, i.e., trust and distrust respectively.
-
-If the items accurately measure trust/distrust in elections regardless
-of where those elections are said to take place, then positive
-correlations between the AZ and Local area items should approach perfect
-correlation as though the same exact questions were asked twice. This
-result, however, suggests that the location of which the survey items
-pertain (and perhaps other factors) makes a substantial difference in
-the pattern of responses, but also raises valid questions as to whether
-the items accurately measure the latent variable constructs in the first
-place.
-
 \pagebreak
@@
 
-\bibitem[\citeproctext]{ref-cook2005}
-Cook, Timothy E., and Paul Gronke. 2005. {``The {Skeptical American}:
-{Revisiting} the {Meanings} of {Trust} in {Government} and {Confidence}
-in {Institutions}.''} \emph{The Journal of Politics} 67(3): 784--803.
-doi:\href{https://doi.org/10.1111/j.1468-2508.2005.00339.x}{10.1111/j.1468-2508.2005.00339.x}.
-
 \bibitem[\citeproctext]{ref-cooter2013}
@@
 doi:\href{https://doi.org/10.1017/S104909650707103X}{10.1017/S104909650707103X}.
-
-\bibitem[\citeproctext]{ref-hardin2004}
-Hardin, Russell. 2004. \emph{Distrust}. New York: Russell Sage
-Foundation.
 

### 2025-03-11 docs/index.qmd
removed a lot of clutter

@@
 library(easystats)
+library(odds.n.ends) # model sig from glm
 library(patchwork)
 
-# load data
-load("data/research-paper-df-20250203.Rdata") #df
+# load subset of processed dataframe that includes dv composite scores
+load("data/research-paper-df-subset-20250203.Rdata") #df
 
@@
 
-Even though election officials can do a lot to secure election integrity, there's not much they can do to cement public confidence after election night passes.
-At best, election officials can ease public insecurities prior to election night.
-
 One point of contention that election officials have faced in the past regard evaluation of election workers.
-Previous literature has focused on how voter interaction with election workers [@claassen2008], or the voter experience generally [@atkeson2007], influences evaluations of election administration.
+Previous literature has focused on how voter interaction with election workers [@claassen2008], voting technology [@herrnson2009], and the voter experience generally [@atkeson2007], influences evaluations of election administration.
 As such, election worker competency has been examined as a factor significant to evaluations of performance of elections [@hall2007; @hall2009].
@@
 In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
-Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity to a limited extent.
-Expectations of electoral fraud and concerns for voter safety were lower among those who read a fabricated announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned.
+Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
+Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned[^3].
 Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
@@
 I explain my reasoning and method for constructing the primary dependent variable, which I broadly refer to as *confidence in elections*.
-I preview the different methods of analysis alongside presentation of the results.
-Before concluding, I dedicate time to discuss the limitations of the study and lessons learned.
 I close by offering my interpretation of the results and suggest potential avenues for future inquiry.
@@
 Election worker recruitment is still much of an issue in the current era as it was then, perhaps worse [@ferrer2024].
-In addition to ensuring election admin offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections.
-In particular, voting technology [@herrnson2009] and election worker competence was a of interest in election studies [@claassen2008; @hall2009; @hall2007].
+In addition to ensuring election offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections.
+In particular, voting technology [@herrnson2009] and election worker competence was of interest in election studies [@claassen2008; @hall2009; @hall2007].
 Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007].
@@
 Concerns over the fairness of elections and accuracy of vote counts intensified, heightening concerns over the prospect of political violence and, in turn, increased worry for the safety of voters and election workers alike.
-
-Suffice to say, pre-election anxiety consists of more than confidence in fairness and accuracy of vote counts in light of added safety concerns.
-It is not hard to recognize that increased tension in the pre-election period makes for a volatile political environment.
-Sustaining trustworthiness in election administration is only more difficult in an environment where turnover of election workers increases and the struggle to recruit volunteers worsens in light of safety concerns.
 Since election worker performance is significant to public evaluation of elections, added safety concerns that drive out election staff and repel volunteers can only detract from trustworthiness of the institution.
@@
 At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended).
-Or in other words, by the extent the public is confident in the accurate administration of elections.
 
-Assessing the public's *trust* in elections has not been straightforward, however.
-Inquiry into public trust in elections has been approached by scholars of political science in many different ways [@cook2005; @hardin2004], often distinguishable by the scope of the research question and more or less constrained by the particular conception of public trust.
-Quite often, trust in election administration is conflated with trust in government *writ* large, government legitimacy, government or system responsiveness, or even satisfaction with democracy [@daniller2019].
-At this level, not only is the level of public trust in elections sometimes vague, but there's little consideration over the difference between such attitudes pre-election and post-election.
-In contrast, a considerable amount of research tends to conceive of public trust in accordance with the institution in question [@atkeson2007; @hooghe2018].
-
-Elections administration is just one institution a part of the larger set of institutions which form the electoral system.
-As such, the performance of the institution along with the rest "...lends credibility to the outcome of an election: whether it is considered by citizens and the international community to be fair and legitimate." [@stewart2022, 236].
 Intuitively, enhancing public trust in elections would best be accomplished by enhancing the *trustworthiness* of the institution, i.e., consistently doing the things that election officials already regularly do come election time.
@@
 The latter is *empirical*---a judgement discerned in hindsight after the experience of the election event has occurred.
-Evaluations of one's own trust and confidence in election administration based on the experience of voting is influenced by that very experience.
 As discussed by @stewart2022, not only was confidence in vote count accuracy influenced by the voter experience, but so too were evaluations of election officials [-@stewart2022, 242-243].
 Not to mention the influence that the election results would also have on such evaluations.
-In other words, evaluations of trust and confidence post-election are influenced by one's interpretation of their experience.
-The subtle difference is simply the degree of uncertainty one feels in anticipation of the next election event.
-This study focuses primarily on that *anticipatory* kind of confidence, which speaks more to those insecurities[^3] based on perceptions of the institution's trustworthiness than upon the particular voter experience.
+In other words, trust evaluations post-election are influenced by one's interpretation of their experience and election results.
+This study, in contrast, focuses primarily on that *anticipatory* kind of confidence, which speaks more to those insecurities based on perceptions of the institution's trustworthiness than upon the particular voter experience.
 
@@
 In 2020, such efforts were made far more difficult by the COVID-19 pandemic [@mena2020; @abbate2020a].
-Sure, it makes sense to recruit veterans, but no more than any other group.
-After all, ensuring election offices are adequately staffed is everyone's problem.
-So there's no special reason to target veterans for recruitment above other groups.
+There's no special reason to target veterans for recruitment above other groups.
 Indeed, there's no reason to discriminate recruitment efforts at all if the point is purely to fill staffing vacancies.
-However the interest in veterans as a special group to consider arose in light of increased and sudden efforts to recruit veterans into election work.
 
@@
 Veterans are a particularly potent group where mention of veteran status seems to have a positive, calming, or nullifying effect on attitudes.
-For instance, recent research shows that, during his campaign in the 2020 Democratic Primaries, Pete Buttigieg's military background mitigated discrimination against him when he was presented as a veteran married to man [@magni2024].
+For instance, recent research shows that, during his campaign in the 2020 Democratic Primaries, Pete Buttigieg's military background mitigated discrimination against him when he was presented as a veteran married to a man [@magni2024].
 Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@hardy2019].
@@
 
-Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veterans and their family members to work as election staff and volunteers would boost public confidence in election administration.
+Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veterans and their family members to work as election staff and volunteers would boost public *confidence in elections administration*.
 Indeed, that is the primary hypothesis of this study.
@@
 
-I considered that veterans would elicit high degrees of approval and support for whatever cause or issue presented.
-For example, I'd expect high approval and support for recruiting veterans to baseball teams just as much as for recruiting them to work as election staff.
-Likewise, asking participants whether they supported programs intent on recruiting anyone to work as election staff would garner support regardless of the target group.
+Asking participants whether they supported programs intent on recruiting anyone to work as election staff would garner support regardless of the target group.
 Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require a survey experiment designed to determine whether publicized recruitment efforts targeting veterans as a group would have any special effect on confidence in elections administration.
@@
 However, given that veteran service members are held in high regard, generally speaking, announcing that veterans are being actively recruited to work as election staff and volunteers is expected to positively influence confidence in elections among those who remained firm in the belief that the 2020 election results were illegitimate.
-I take into account that legitimacy beliefs about the 2020 election and expectations of electoral fraud are related to partisanship and include partisanship as a control in the analysis.
+I take into account that legitimacy beliefs about the 2020 election and expectations of electoral fraud are related to partisanship and include partisanship as a control in the analysis[^4].
 
@@
 Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone.
-Therefore, any observed disparity of confidence in elections (i.e., the "confidence gap") between elections within one's local area and elections beyond will be smaller when people are presented with information about election official recruitment efforts of veteran service members.
+Therefore, any observed disparity of confidence in elections (i.e., the "confidence gap") between elections within one's local area and elections beyond will be smaller among those who are presented with information about election official recruitment efforts of veteran service members.
 
@@
 citizens 18 years of age or older.
-Respondents were randomly split into either the treatment ($n =$ 650) control ($n =$ 637) conditions[^4].
+Respondents were randomly split into either the treatment ($n =$ 650) control ($n =$ 637) conditions[^5].
 
-Survey participants read either a treatment or control vignette, which was a fabricated news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election.
+Survey participants read either a treatment or control vignette, which resembled a news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election[^6].
 The treatment vignette referred to a program designed to recruit veterans and their family members and describes an interviewee "Jordan Braxton" as an Army veteran.
@@
 Beyond those small differences and the headlines, the article vignettes are identical.
-Therefore, effects can be attributed to the information about veterans in the treatment vignette[^5].
+Therefore, effects can be attributed to the information about veterans in the treatment vignette[^7].
 
@@
 
-Note that, except for the item assessing voter confidence (i.e., votes counted as voters intend), most other question items from the 2022 SPAE inquire into the voter experience after the election has occurred.
-The items in this study, however, all inquire into confidence over one's expectations in anticipation of upcoming elections.
-In addition, other survey questionnaires ask similar questions that specifically contrast between a respondent's own local community, their state, and nationwide; this is in addition, or complementary to, items that distinguish between local area officials, state election officials, state government, and the U.S.
-federal government.
-The survey of this study, instead, focused on attitudes regarding election workers such as election officials, staff, and volunteers specific to the location mentioned in the vignette---Maricopa County, AZ---as well as specific to one's local area[^6].
+The items in this study all inquire into confidence over one's expectations in anticipation of upcoming elections.
+In addition, the survey of this study focused on attitudes regarding election workers such as election officials, staff, and volunteers specific to the location mentioned in the vignette---Maricopa County, AZ---as well as specific to one's local area[^8].
 
@@
 
-The conventional multiple item assessment of partisanship was included and used to construct a variable of partisanship consisting of three categories: Democrat, Republican, and Independent.
-In this case, Independents are "true" Independents in that they do not identify with either political party and do not "lean" toward either Republican or Democratic parties.
-Self-described "Independent leaners" are re-coded as falling into the partisan category in which they lean e.g., Independents who expressly report that they lean Republican are denoted as Republican.
+The conventional multiple item assessment of partisanship was included and used to construct a variable of partisanship consisting of three categories: Democrat, Republican, and independent.
 
 Finally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
-The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^7].
+The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^9].
 
@@
 In total, five survey items measure different aspects of trust in elections administration.
-The items measuring confidence in elections include:
-
-Another series of five survey items captured an individual's level of *distrust* in elections administration based on the extent to which they *expect electoral fraud* to occur.
-These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in \[Maricopa County, AZ/ your local area\]?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
 
 ```{r}
-#| label: tbl-items
+#| label: tbl-1
 #| tbl-cap: "Survey Items for Trust and Distrust in Elections"
@@
 
-Similar to the items capturing trust in elections (@tbl-items), I computed a summated score for each respondent reflecting the extent of their distrust in elections.
+Another series of five survey items captured an individual's level of *distrust* in elections administration based on the extent to which they expect electoral fraud to occur.
+These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in \[Maricopa County, AZ/ your local area\]?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
+
+Similar to the items capturing trust in elections (@tbl-1), I computed a summated score for each respondent reflecting the extent of their distrust in elections.
 
 Upon construction of the two summated scales of *trust* and *distrust*, internal consistency reliability coefficient $\alpha$ were estimated for both and found to be adequate ($\alpha$ \> 0.8); the trust in elections scale $\alpha$ = 0.93 and the distrust scale $\alpha$ = 0.86.
-In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each.
-
-I expected item responses from these two scales to be inversely correlated among the sample, but not mutually exclusive.
-Indeed, this is what I find.
-Polychoric correlations between the trust and distrust items negatively correlate as expected\[\^See Appendix C\], as does the correlation between the two sum score scales.
-Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
-The negative correlation between the trust and distrust items and scores makes intuitive sense.
+In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each[^10].
 
@@
 Because trust and distrust are assessed by multiple Likert items, conventional methods call for combining the items of each set into separate Likert scales (also known as summated rating scales).
-Since the item response options are not symmetric---i.e., not bipolar with contrasting positive and negative response options to include a neutral middle option---then the *trust in elections* scale could only be understood as a measure of trust in the positive use of the term (i.e., unipolar).
-Likewise, the expectation of fraud items fit to a scale that corresponds to a unipolar measure of confident *distrust*, so to speak.
 However, many of the items comprising the trust scale directly oppose items capturing distrust.
@@
 When trust and distrust are considered as reflective of one's confidence about future expectations, then both can be placed along the same spectrum.
-Therefore, a lack of confidence denotes insecurity.
-
-Something may cause a person to have greater expectations that election fraud will occur, which in turn will always lower their trust in elections administration.
-In contrast, a person may feel a bit more confident in the integrity of elections, but this confidence is constrained by the extent to which they expect election fraud to occur.
-This means that a person's baseline level of confidence in elections admin must take into account their present degree of distrust---i.e., their expectations of electoral fraud.
-
-Those who are, or are close to being, equally confident in both directions would be the most *insecure* about their expectations.
-Having no trust in elections and no expectation that electoral fraud will occur is functionally equivalent to having equal degree of both.
 Quite literally, this reflects an uncertain feeling of "it could go one way or the other" with respect to the integrity of elections administration.
@@
 
-In light of this, I reverse coded positive expectations of electoral fraud and added responses from the distrust scale to the trust in elections scale.
+In light of this, I reverse coded items on the distrust scale and combined responses to the trust in elections scale.
 That is, item responses on the trust scale ranged from 0 ("Not confident at all") to 3 ("Very confident), whereas responses on the distrust scale ranged from 0 ("Not likely at all") to -3 ("Very likely").
-Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^8].
+Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^11].
 On this scale, positive values reflect higher confidence in elections, negative values reflect greater distrust, and values closer to zero correspond to an individual's degree of insecurity.
@@
 That being said, there is a definite distinction between items pertaining to Maricopa County, AZ compared to items that pertain to a respondent's local area.
-In fact, the treatment appears to have hardly made a difference when the items concerned one's local area.
+In fact, as expected, the treatment appears to have hardly made a difference when the items concerned one's local area.
 
@@
 Although confidence in election workers was generally high across the board, the shift from "Somewhat" to "Very" confident for items pertaining to election worker *commitment* to fairness and accuracy seems to clearly speak to the group being recruited, i.e., veterans and family members.
-However, the same visible shift in proportion from "Somewhat" to "Very" confident isn't observed when items asked about one's local area, which undermines the suggestion that the treatment effect can be cleanly attributed to respondent's feelings about veteran service members and their families.
+However, the same visible shift in proportion from "Somewhat" to "Very" confident isn't observed when items asked about one's local area.
 It may be the case that respondents harbor particular attitudes or sentiment about Maricopa County, AZ itself, or there may be nothing uniquely special about Maricopa County, AZ supposing that elections anywhere beyond one's local area generally garner slightly less confidence.
@@
 #| fig-height: 4.5
-#| fig-pos: "h"
+#| fig-pos: "H"
 
-# distrust in elections in AZ by experimental condition
-distrust.likert.az <- df |>
-  # reverse levels of factor vars to show positive difference in "not likely"
-  mutate(across(c(q28_1:q28_5), ~forcats::fct_rev(.))) |> 
-  ggstats::gglikert(
-    include = c(q28_1:q28_5),
-    y = 'group',
-    facet_rows = vars(.question),
-    variable_labels = c(
-      q28_1 = "Voter fraud will occur",
-      q28_2 = "Many votes won't be counted",
-      q28_3 = "Many voters will be turned away",
-      q28_4 = "Foreign Interference",
-      q28_5 = "Election officials will discourage voting"),
-    facet_label_wrap = 10,
-    labels_size = 2.5,
-    symmetric = F,
-    add_totals = T
-  ) +
-  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
-  # ggplot2::scale_fill_brewer(palette = "Greys")+
-  labs(subtitle = str_wrap("Maricopa County, Arizona", width = 95)) +
-  theme_bw() +
-  theme(
-    text = element_text(family = "Palatino Linotype"),
-    legend.position = 'bottom',
-    axis.text.x = element_blank(), # remove percentage text along x-axis
-    strip.text.y.right = element_blank()
-  )
-
-# distrust in elections in Local area by experimental condition
-distrust.likert.lcl <- df |>
-  # reverse levels of factor vars to show positive difference in "not likely"
-  mutate(across(c(q40_1:q40_5), ~forcats::fct_rev(.))) |> 
-  ggstats::gglikert(
-    include = c(q40_1:q40_5),
-    y = 'group',
-    facet_rows = vars(.question),
-    variable_labels = c(
-      q40_1 = "Voter Fraud will occur",
-      q40_2 = "Many Votes won't be counted",
-      q40_3 = "Many voters will be turned away",
-      q40_4 = "Foreign Interference",
-      q40_5 = "Election officials will discourage voting"),
-    facet_label_wrap = 10,
-    labels_size = 2.5,
-    symmetric = F,
-    add_totals = T
-  )+
-  ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
-  # ggplot2::scale_fill_brewer(palette = "Greys")+
-  labs(subtitle = str_wrap("Local Area", width = 95)) +
-  theme_bw() +
-  theme(
-    text = element_text(family = "Palatino Linotype"),
-    legend.position = 'bottom',
-    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
-    axis.text.x = element_blank(), # remove percentage text along x-axis
-    strip.text.y.right = element_text(angle = 0, size = 8)
-  )
-
-# Instead of two separate plots, arrange into one plot while remaining separated
-# use `ggpubr` package to print multiple plots side-by-side (or alt. row-by-row)
-ggpubr::ggarrange(
-  distrust.likert.az,
-  distrust.likert.lcl,
-  ncol = 2,
-  common.legend = T,
-  legend = "bottom", 
-  font.label = list(family = "Palatino Linotype")
-) +
-  # add figure footnote annotation
-  patchwork::plot_annotation(
-    caption = str_wrap("Missing values removed. Displays percent proportions of responses by experiment condition and combined percentage proportions for two categories.",
-               width = 85), theme = theme(text = element_text(family = "Palatino Linotype")))
+p11.distrust.treat
 
@@
 Positive values reflect trust in elections administration (e.g., elections will be fair and accurate), whereas negative values reflect distrust in elections (i.e., expectation that election fraud will occur).
-To retain a meaningful zero, I rescaled the sum scores to range from -3 to 3[^9] and then superimposed two histograms of confidence scores: one derived from AZ items and another for scores derived from local area items.
+To retain a meaningful zero, I rescaled the sum scores to range from -3 to 3[^12] and then superimposed two histograms of confidence scores: one derived from AZ items and another for scores derived from local area items.
 Doing this is illustrative of the relative distribution of confidence that differed depending on the location of elections referred to in the survey items (e.g., Maricopa County, AZ).
@@
 Accordingly, when confidence levels are distinguished by experiment condition, the treatment vignette only had an effect upon survey items pertaining to elections in Maricopa County, AZ.
-Conducting an independent samples t-test (i.e., Welch Two Sample t-test) suggests that the effect of the treatment compared to the control condition is positive, statistically significant, yet substantially pretty small.
+Conducting an independent samples t-test (i.e., Welch Two Sample t-test) suggests that the effect of the treatment compared to the control condition is positive and statistically significant.
 
@@
 When the dependent variable is centered to have a mean of $0$ and standard deviation of $1$, standardized parameters permit interpretation of the treatment effect in terms of standard deviations; the standardized difference in confidence between treatment and control is $0.16$ (CI $[0.06, 0.27]$).
-Nothing is more illustrative than graphs and lines, however.
 
@@
 #| fig-height: 3.5
+#| fig-pos: 'H'
 #| fig-cap: "Confidence in Elections by Experiment Condition"
@@
 
-I now turn to results examining those who held onto the belief that the 2020 election results were illegitimate.
-I think check to see if recruiting veterans simply makes people feel safer at the polls.
+### 2020 Election Legitimacy Beliefs
 
-\pagebreak
+I now turn to results examining the effect of the treatment on those who held onto the belief that the 2020 election results were illegitimate.
+First, reviewing responses to items that capture trust in elections, it is easy to recognize the difference between the way 2020 election deniers responded with respect to where elections were held.
+
+```{r}
+#| label: fig-legit
+#| fig-cap: "Trust in elections by treatment among those who refute the 2020 election results"
+#| fig-height: 4.5
+
+p13.trust.treat.legit
+
+```
+
+Among those who refuted the 2020 election results, trust in Maricopa County, AZ elections was lower for each item compared to items pertaining to elections within one's local area, regardless of treatment condition.
+However, notably, trust that election technology would be secure received the lowest confidence endorsement overall.
+There was also a notable lack of trust that the voting process would be fair relative to the other items.[^13] Now the comparative difference in responses between those in the treatment group compared to those in the control group appears substantial for items pertaining to elections in Maricopa County, AZ.
+
+```{r}
+#| label: fig-legit2
+#| fig-cap: "Distrust in elections by treatment among those who refute the 2020 election results"
+#| fig-height: 4.5
+
+p14.distrust.treat.legit
+
+```
+
+Concerning distrust among those who refuted the 2020 election results, responses items assessing one's expectation that election fraud would occur reveal the same pattern.
+Although there is not as stark a disparity between responses of those in the treatment and those in the control, among those in the treatment group, there does appear to be less expectation that election fraud would occur in Maricopa County, AZ.
+Overall, review of responses to trust (@fig-legit) and distrust survey items (@fig-legit2) does lend credence to the impact of the treatment.
+
+In order to substantiate the overall influence of the treatment on confidence in elections, I regressed the dependent variable confidence on legitimacy beliefs while controlling for partisanship.
+
+::: {.content-visible when-format="bookup-html"}
+
+```{r}
+#| label: tbl-legit-html
+#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
+#| tbl-pos: H
+
+# All continuous variables are mean-centered and scaled by 1 standard deviation.
+m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = df)
+m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = df)
+
+stargazer::stargazer(
+  m1,
+  m2,
+  type = "html",
+  style = 'apsr',
+  header = F,
+  float = F,
+  align = T, 
+  single.row = T, 
+  dep.var.labels.include = F, model.numbers = F,
+  digits = 2,
+  column.labels = c("Confidence in AZ Elections", "w/Interaction"),
+  covariate.labels = c(
+      "Treatment",
+      "Not Legitimate",
+      "Republican",
+      "Democrat",
+      "Not Legitimate * Treatment",
+      "Constant"
+    )
+)
+
+```
+
+The first model in Table @tbl-legit-html shows that overall confidence in elections (trust - distrust) among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
+Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
+Not believing the 2020 election of Joe Biden was legitimate is negatively associated with confidence in elections.
+In order to assess the magnitude of this interaction effect of the treatment on those who refuted the 2020 election results, I ran a model where confidence in elections was regressed on the interaction between the treatment and legitimacy beliefs, controlling for partisanship.
+
+There's a positive interaction effect of the treatment vignette among those who believe that the 2020 election was not legitimate, on average and controlling for partisanship.
+This shows that the treatment effect was most influential upon those who believe the 2020 election results were illegitimate.
+The treatment alone does not reverse such beliefs, but this shows where its influence was most potent.
+
+:::
+
+::: {.content-visible when-format="pdf"}
+
+```{r}
+#| label: tbl-legit-pdf
+#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
+#| tbl-pos: H
+#| results: asis
+
+# All continuous variables are mean-centered and scaled by 1 standard deviation.
+m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = df)
+m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = df)
+
+stargazer::stargazer(
+  m1,
+  m2,
+  type = "latex", 
+  style = 'apsr',
+  header = F,
+  float = F,
+  align = T, 
+  single.row = T, 
+  dep.var.labels.include = F, model.numbers = F,
+  digits = 2,
+  column.labels = c("Confidence in AZ Elections", "w/Interaction"),
+  covariate.labels = c(
+      "Treatment",
+      "Not Legitimate",
+      "Republican",
+      "Democrat",
+      "Not Legitimate * Treatment",
+      "Constant"
+    )
+)
+
+```
+
+The first model in Table \ref{tbl-legit-pdf} shows that overall confidence in elections (trust - distrust) among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
+Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
+Not believing the 2020 election of Joe Biden was legitimate is negatively associated with confidence in elections.
+In order to assess the magnitude of this interaction effect of the treatment on those who refuted the 2020 election results, I ran a model where confidence in elections was regressed on the interaction between the treatment and legitimacy beliefs, controlling for partisanship.
+
+There's a positive interaction effect of the treatment vignette among those who believe that the 2020 election was not legitimate, on average and controlling for partisanship.
+This shows that the treatment effect was most influential upon those who believe the 2020 election results were illegitimate.
+The treatment alone does not reverse such beliefs, but this shows where its influence was most potent.
+
+:::
 
 ## Conclusion
+
+Publicized announcements that election officials are actively recruiting former military service members to work as election staff and volunteers is associated with slightly greater confidence in elections compared to election worker recruitment announcements that do not explicitly mention targeted recruitment of former military service members.
+Moreover, increased levels of confidence is limited to elections beyond one's local area and, of course, in anticipation of election night.
+Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
 
@@
 
-### Limitations
-
-As far as I'm aware, both the items, their wording, and their composition into measurement scales are unique to this study.
-This renders the composite scores for trust in elections sample dependent and limits comparability with other cross-sectional survey data.
-
--   limitations: interpretations of the treatment effect are limited.
-    -   The sample may not be generalizable to the population.
-    -   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts.
--   Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
--   Moreover, results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons.
-- First, the vignettes and many survey questions ask about Maricopa County, AZ specifically.
-Adding a specific county in the vignette adds in a factor that cannot be accounted for without additional treatments that eliminate the setting as a potential influence.
-Moreover, the specificity of the setting adds in even more unexplained error---some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S.
-they've know nothing about.
-Adding the county undermines the confidence that treatment effects are solely attributable to veterans to an unknown degree.
-- Second, questions ask about one's own local community in addition to identical questions which asked about Maricopa County, AZ.
-Consequently, many questions within the questionnaire were duplicates with that one differences.
-This isn't uncommon in surveys, however in this case, it lengthened the survey to a degree that likely resulted in a higher drop off rate.
-More importantly, the quality of responses were likely diminished to some unknown extent.
-Although it is possible to compare questions asked about Maricopa County, AZ to questions about one's local area, the quality of that comparison is limited by the unknown extent of fatigue induced by answering the same questions twice.
-It wasn't just that some questions were asked multiple times, almost all of the questions were duplicated; after completing a long series on Maricopa County, participants then answered the same questions about the local community.
-The rate to which participants dropped from the survey is \_\_\_, which suggests fatigue as an important factor.
-Survey fatigue is a known issue that should be taken into consideration.
-Comparison of treatment effects between the MC series and the local area series is undermined by the unknown influence that fatigue would have on response choices.
-Any differences couldn't confidently be attributed to "my area" vs Maricopa county.
-We also can't determine whether treatment effects are sustained when comparing the Maricopa County series to the local area series asked subsequently.
-We would have to assume the setting as irrelevant, which we can't reasonably do.
-
-\pagebreak
-
-## Appendix A: Survey Experiment Vignettes and Survey Items {#sec-appendix-a}
-
-::::: {#fig-vignettes .content-visible layout-ncol="2" when-format="html" unless-format="pdf"}
-::: {#fig-treatment}
-### Treatment Vignette
-
-| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Army veteran Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-::: {#fig-control}
-### Control Vignette
-
-| **Local Residents Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-Fabricated Article Vignettes utilized as Experimental Stimulus
-:::::
-
-::::: {.content-hidden unless-format="pdf" layout="[0.45, -0.1, 0.45]"}
-::: {#first-column}
-### Treatment Vignette
-
-| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Army veteran Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-::: {#second-column}
-### Control Vignette
-
-| **Local Residents Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-:::::
-
-\pagebreak
-
-## Appendix B: Sample Demographics {#sec-appendix-b}
-
-The median age was 46 (mean age was 47).
-There was 51.7% (n = 658) women, 47% (n = 598) men, and approximately 1.3% who identified as either Non-binary/third gender (n = 7) or preferred not to say (n = 9).
-A large proportion of the sample identified as White or Caucasian (n = 975, 76.65%), while all other non-White respondents comprised 27.83% of the sample.
-Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised 13% of the sample; those with either degree at the Associate or Bachelor's level comprised 36.24%, while 22.25% had some college but no degree; and 28.46% had either a high school level or equivalent education or less than high school.
-The largest proportion of the sample identified as Democrat at 44.64%, followed by Republicans at 42.59%.
-The proportion of true Independents was 12.78%.
-
-\pagebreak
+These results speaks more to the influence that military veterans have among those who distrust the electoral process and refute the legitimacy of prior outcomes than it does to the public more generally.
+In general, public confidence appears strongest when the elections under consideration regard those within one's local community.
+Yet, such strong confidence is not generalized outward to the institution of elections administration as a whole.
+Insecurity in the integrity of the electoral process and its administration may be naturally higher for elections that occur further from home.
+Whether that is due to some local favorability bias or some outward negativity bias is hard to say.
+And seeing as how insecurity presents vulnerability, it is perhaps far easier to inspire a general sense of distrust in the process and its administration in places not near and around one's local area.
 
@@
 The "*worthiness*" of one's trust in the conduct and administration of elections is based on the extent that outcomes of an election reasonably follow the rules prescribed and can be adjudicated as such.
-To put it briefly, trustworthiness is built by the structure, procedures, and practices of the institution, in this case election administration.
-The public's trust in elections, however, is amendable to an indefinite number of factors that may be unrelated to the formal structure or procedures of election administration.
-To illustrate, I can recognize that my car is trustworthy prior to ever driving it because it is structurally sound; it passes whatever criteria upon inspection, it is sufficiently fueled, and appears to be in generally good working order.
-I have every reason to deem it *worthy of my trust*.
+The public's *trust* in elections, however, is amendable to an indefinite number of factors that may be unrelated to the formal structure or procedures of election administration.
+I can recognize that my car is trustworthy prior to ever driving it because it is structurally sound; I have every reason to deem it *worthy of my trust*.
 However, I don't trust my car because I am sure it is haunted.
@@
 
-[^3]: Note that election insecurity is used in place of electoral confidence simply to emphasize the anticipatory nature of the attitudes in question.
-Election insecurity is taken to denote a lack of confidence.
+[^3]: The vignettes written were based on real news stories
 
-[^4]: Demographic breakdown of the sample are included in Appendix B.
+[^4]: To be clear, I conducted an auxiliary regression analysis to examine the relationship between legitimacy beliefs and partisanship.
+Results revealed a statistically significant relationship between the two variables and thus omitting either would result in biased estimates.
 
-[^5]: Complete text of treatment and control vignettes are included in the Appendix
+[^5]: Demographic breakdown of the sample are included in Appendix B.
 
-[^6]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
+[^6]: The article vignettes were written and designed by Michael Hanmer Ph.D and myself with input from We the Veterans, a non-profit organization
 
-[^7]: Survey item wording and responses are included in Appendix A.
+[^7]: Complete text of treatment and control vignettes are included in the Appendix
 
-[^8]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
+[^8]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
+
+[^9]: Survey item wording and responses are included in Appendix A.
+
+[^10]: I expected item responses from the trust and distrust scales to be inversely correlated among the sample, but not mutually exclusive.
+Indeed, this is what I find.
+Polychoric correlations between the trust and distrust items negatively correlate as expected, as does the correlation between the two sum score scales.
+Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
+The negative correlation between the trust and distrust items and scores makes intuitive sense.
+See Appendix C for inter-item correlation
+
+[^11]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
 The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024], yet there is no general consensus on the most appropriate method generally.
@@
 
-[^9]: This range is mostly arbitrary, as a range from -1 to 1 works much the same.
+[^12]: This range is mostly arbitrary, as a range from -1 to 1 works much the same.
 When relying on simple sum total score, the scale ranges from -15 to 15.
@@
 In other words, negative values on the scale for confidence in elections hold substantive meaning (e.g., distrust, absent trust), which makes transforming scores to fit a unipolar scale inappropriate.
+
+[^13]: What is interesting to note here is that the first three items regard the more human element of the election administration process, e.g., ensuring accuracy of counts, competence, and commitment of election workers.
+Although a neat line can't really be drawn between the first three and latter two items presented here, it is interesting to see a slight divergence from the usual high confidence placed in local area elections.

### 2025-03-11 src/funs.R

@@ -327,3 +327,5 @@ clockin <- function(date = TRUE, time = FALSE, seconds = FALSE){
 
 
 
+
+

### 2025-03-13 docs/_tex/index.tex
reduced length. Moved content to appendices. Modified text. adjusted format. etc

@@
 \usepackage{amsmath,amssymb}
+\usepackage{setspace}
 \usepackage{iftex}
@@
 
+\setstretch{1.25}
 \pagebreak
@@
 \citeproc{ref-nadeau1993}{Nadeau and Blais 1993}). Opinions of electoral
-trust gathered after the election has occurred are limited considering
-the well-recognized impact that the electoral outcome itself has on
-feelings of public trust in elections
+trust gathered after the election has occurred, however, are limited
+considering the well-recognized impact that the electoral outcome itself
+has on feelings of public trust in elections
 (\citeproc{ref-daniller2019}{Daniller and Mutz 2019}).
@@
 Beyond the general competence of election workers, however, the quality
-of the voter experience may be influenced merely by \emph{a priori}
-impressions about \emph{who} comprises election staff and volunteers.
-Political and other social science researchers have recognized for some
-time the power that group identity can have over attitudes and
-perception (\citeproc{ref-vanbavel2021}{Van Bavel and Packer 2021};
+of the voter experience may be influenced merely by prior impressions
+about \emph{who} comprises election staff and volunteers. Political and
+other social science researchers have recognized for some time the power
+that group identity can have over attitudes and perception
+(\citeproc{ref-vanbavel2021}{Van Bavel and Packer 2021};
 \citeproc{ref-xiao2016}{Xiao, Coppin, and Van Bavel 2016};
@@
 group who denies the legitimacy of the 2020 election results were
-possibly the most distrusting of the 2024 election. However, given that
-veteran service members are held in high regard, generally speaking,
-announcing that veterans are being actively recruited to work as
-election staff and volunteers is expected to positively influence
-confidence in elections among those who remained firm in the belief that
-the 2020 election results were illegitimate. I take into account that
-legitimacy beliefs about the 2020 election and expectations of electoral
-fraud are related to partisanship and include partisanship as a control
-in the analysis\footnote{To be clear, I conducted an auxiliary
-  regression analysis to examine the relationship between legitimacy
-  beliefs and partisanship. Results revealed a statistically significant
-  relationship between the two variables and thus omitting either would
-  result in biased estimates.}.
+possibly the most apprehensive (distrusting) of the 2024 election.
+However, given that veteran service members are held in high regard,
+generally speaking, announcing that veterans are being actively
+recruited to work as election staff and volunteers is expected to
+positively influence confidence in elections among those who remained
+firm in the belief that the 2020 election results were illegitimate. I
+take into account that legitimacy beliefs about the 2020 election and
+expectations of electoral fraud are related to partisanship and include
+partisanship as a control in the analysis\footnote{To be clear, I
+  conducted an auxiliary regression analysis to examine the relationship
+  between legitimacy beliefs and partisanship. Results revealed a
+  statistically significant relationship between the two variables and
+  thus omitting either would result in biased estimates.}.
 
@@
 confidence is already expectedly lower---can help discern the impact of
-the group alone. Therefore, any observed disparity of confidence in
-elections (i.e., the ``confidence gap'') between elections within one's
-local area and elections beyond will be smaller among those who are
-presented with information about election official recruitment efforts
-of veteran service members.
+the group alone on public opinion. Therefore, any observed disparity of
+confidence in elections (i.e., the ``confidence gap'') between elections
+within one's local area and elections beyond will be smaller among those
+who are presented with information about election official recruitment
+efforts of veteran service members.
 
@@
 of the scales were intercorrelated well enough for each to compose a
-single scale presuming a unidimensional construct for each\footnote{I
-  expected item responses from the trust and distrust scales to be
-  inversely correlated among the sample, but not mutually exclusive.
-  Indeed, this is what I find. Polychoric correlations between the trust
-  and distrust items negatively correlate as expected, as does the
-  correlation between the two sum score scales. Given the ordinal nature
-  of the variable items, I conducted a Spearman's rank correlation test
-  (\citeproc{ref-spearman1907}{Spearman 1907}) and found a negative
-  correlation of \(\rho = -0.49\) (\(95\%\) CI {[}-0.53, -0.44{]};
-  Kendall's \(\tau = -0.39\)) between scores on the two scales for the
-  AZ items (For the local item scale score correlation:
-  \(\rho = -0.52\), \(95\%\) CI {[}-0.56, -0.48{]}; Kendall's
-  \(\tau = -0.39\)). The negative correlation between the trust and
-  distrust items and scores makes intuitive sense. See Appendix C for
-  inter-item correlation}.
+single scale presuming a unidimensional construct for each\footnote{See
+  Appendix C for analysis.}.
 
@@
 directly contradict each other, and would thus cancel out.
-
-The relationship is that trust and distrust represent opposing degrees
-of confidence along the same spectrum. However, despite the inherent
-contrast, one can hold both positive degrees of trust and distrust,
-feeling similarly confident in both respects. Accordingly, equivalent
-degrees of trust and distrust cancel out, rendering one relatively more
-\emph{insecure} about their expectations of the future despite the fact
-that they may feel confident in either direction. When trust and
-distrust are considered as reflective of one's confidence about future
-expectations, then both can be placed along the same spectrum. Quite
-literally, this reflects an uncertain feeling of ``it could go one way
-or the other'' with respect to the integrity of elections
-administration. Operationally, this would reflect a middling point on a
-scale of \emph{confidence}.
 
@@
 reflect greater distrust, and values closer to zero correspond to an
-individual's degree of insecurity.
-
-The advantage is that this permits a better test of the treatment effect
-as theorized. Of course, it is easy enough to examine the effect of the
-treatment on both trust and distrust separately. However, the theory
-presents a hypothesis that the treatment will impose influence upon both
-variables \emph{concurrently and in a positive direction} with respect
-to the relationship between trust and distrust. That is to say,
-confidence increases insofar as trust in elections increases and
-distrust decreases; since distrust detracts from trust, then an accurate
-measure of confidence must take that constraint into account.
+individual's degree of \emph{insecurity}.
 
@@
 
-\phantomsection\label{cell-fig-trustlikert}
 \begin{figure}[h]
 
-\caption{\label{fig-trustlikert}Trust in Election Administration by
+\caption{\label{fig-patch10}Trust in Election Administration by
 Experiment Condition}
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-trustlikert-1.png}}
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-figures-fig-patch10-output-1.png}}
 
@@
 Reviewing item responses distinguished by treatment condition reveals
-particulars of the treatment effect (Figure~\ref{fig-trustlikert}).
-Among the items that asked about Maricopa County, AZ, it is a bit easier
-to see upon which items the treatment vignette had the greatest effect.
-It appears that the main effect of the treatment is upon responses to
-the item that measures confidence in the security of election
-technology.
+particulars of the treatment effect (Figure~\ref{fig-patch10}). Among
+the items that asked about Maricopa County, AZ, it is a bit easier to
+see upon which items the treatment vignette had the greatest effect. It
+appears that the main effect of the treatment is upon responses to the
+item that measures confidence in the security of election technology.
 
@@
 
-\phantomsection\label{cell-fig-distrustlikert}
 \begin{figure}[H]
 
-\caption{\label{fig-distrustlikert}Disrust in Election Administration by
+\caption{\label{fig-patch11}Disrust in Election Administration by
 Experiment Condition}
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-distrustlikert-1.png}}
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-figures-fig-patch11-output-1.png}}
 
@@
 associated with lower distrust in the treatment condition compared to
-the control. A quick glance at Figure~\ref{fig-distrustlikert} shows
-what appears to be a significant reduction in distrust, especially
-regarding the expectations that many votes wouldn't be counted, many
-voters would be turned away, and that election officials would
-discourage voters from casting a ballot. Interestingly, the expectation
-that there would be foreign interference in elections in Maricopa
-County, AZ were pretty resilient against the treatment. And again,
-responses for items pertaining to elections in one's local area are
-practically indistinguishable between treatment and control.
+the control. A quick glance at Figure~\ref{fig-patch11} shows what
+appears to be a significant reduction in distrust, especially regarding
+the expectations that many votes wouldn't be counted, many voters would
+be turned away, and that election officials would discourage voters from
+casting a ballot. Interestingly, the expectation that there would be
+foreign interference in elections in Maricopa County, AZ were pretty
+resilient against the treatment. And again, responses for items
+pertaining to elections in one's local area are practically
+indistinguishable between treatment and control.
 
@@
 
-\phantomsection\label{cell-fig-dist}
 \begin{figure}[H]
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-dist-1.png}}
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-figures-fig-dist-output-1.png}}
 
@@
 \toprule
-Place & $\bar{x}_{diff}$ & $\bar{x}_{treat}$ & $\bar{x}_{control}$ & $treat_{n}$ & $control_{n}$ & t & p & df & CI\\
+Place & $\bar{x}_{diff}$ & $\bar{x}_{treat}$ & $\bar{x}_{control}$ & $treat_{n}$ & $control_{n}$ & t & p & data & CI\\
 \midrule
@@
 
-\phantomsection\label{cell-fig-legit}
 \begin{figure}[!t]
 
-\caption{\label{fig-legit}Trust in elections by treatment among those
+\caption{\label{fig-patch13}Trust in elections by treatment among those
 who refute the 2020 election results}
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-legit-1.png}}
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-figures-fig-patch13-output-1.png}}
 
@@
   can't really be drawn between the first three and latter two items
-  presented here, it is interesting to see a divergence of the usual
-  high confidence placed in local area elections.} Now the comparative
-difference in responses between those in the treatment group compared to
-those in the control group appears substantial for items pertaining to
-elections in Maricopa County, AZ.
-
-\phantomsection\label{cell-fig-legit2}
+  presented here, it is interesting to see a slight divergence from the
+  usual high confidence placed in local area elections.} Now the
+comparative difference in responses between those in the treatment group
+compared to those in the control group appears substantial for items
+pertaining to elections in Maricopa County, AZ.
+
 \begin{figure}[!t]
 
-\caption{\label{fig-legit2}Distrust in elections by treatment among
+\caption{\label{fig-patch14}Distrust in elections by treatment among
 those who refute the 2020 election results}
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-legit2-1.png}}
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-figures-fig-patch14-output-1.png}}
 
@@
 less expectation that election fraud would occur in Maricopa County, AZ.
-Overall, review of responses to trust (Figure~\ref{fig-legit}) and
-distrust survey items (Figure~\ref{fig-legit2}) does lend credence to
+Overall, review of responses to trust (Figure~\ref{fig-patch13}) and
+distrust survey items (Figure~\ref{fig-patch14}) does lend credence to
 the impact of the treatment.
@@
 
-\begin{table}[H]
-
-\caption{\label{tbl-legit}Confidence in Elections by Treatment and
-Legitimacy Beliefs}
-
-\centering{
-
-\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-2} D{.}{.}{-2} } 
-\\[-1.8ex]\hline \\[-1.8ex] 
- & \multicolumn{1}{c}{Confidence in AZ Elections} & \multicolumn{1}{c}{w/Interaction} \\ 
-\hline \\[-1.8ex] 
- Treatment & 0.18^{***}$ $(0.05) & 0.09$ $(0.06) \\ 
-  Not Legitimate & -0.72^{***}$ $(0.07) & -0.86^{***}$ $(0.09) \\ 
-  Republican & 0.11$ $(0.08) & 0.12$ $(0.08) \\ 
-  Democrat & 0.17^{*}$ $(0.09) & 0.17^{**}$ $(0.09) \\ 
-  Not Legitimate * Treatment &  & 0.27^{**}$ $(0.11) \\ 
-  Constant & 0.03$ $(0.08) & 0.07$ $(0.08) \\ 
- N & \multicolumn{1}{c}{1,263} & \multicolumn{1}{c}{1,263} \\ 
-R$^{2}$ & \multicolumn{1}{c}{0.14} & \multicolumn{1}{c}{0.14} \\ 
-Adjusted R$^{2}$ & \multicolumn{1}{c}{0.13} & \multicolumn{1}{c}{0.14} \\ 
-Residual Std. Error & \multicolumn{1}{c}{0.93 (df = 1258)} & \multicolumn{1}{c}{0.93 (df = 1257)} \\ 
-F Statistic & \multicolumn{1}{c}{49.92$^{***}$ (df = 4; 1258)} & \multicolumn{1}{c}{41.24$^{***}$ (df = 5; 1257)} \\ 
-\hline \\[-1.8ex] 
-\multicolumn{3}{l}{$^{*}$p $<$ .1; $^{**}$p $<$ .05; $^{***}$p $<$ .01} \\ 
-\end{tabular}
-
-}
-
-\end{table}%
-
 The first model in Table \ref{tbl-legit} shows that overall confidence
-in elections (trust - distrust) among those who read the treatment
-vignette was significantly (statistically) greater than those who read
-the control, on average and netting out the effects of partisanship and
-legitimacy beliefs. Democratic partisanship remains marginally
-significant at \(90\%\) confidence level (\(p = 0.055\)). Not believing
-the 2020 election of Joe Biden was legitimate is negatively associated
-with confidence in elections. In order to assess the magnitude of this
+in elections among those who read the treatment vignette was
+significantly (statistically) greater than those who read the control,
+on average and netting out the effects of partisanship and legitimacy
+beliefs. Democratic partisanship remains marginally significant at
+\(90\%\) confidence level (\(p = 0.055\)). Not believing the 2020
+election of Joe Biden was legitimate is negatively associated with
+confidence in elections. In order to assess the magnitude of this
 interaction effect of the treatment on those who refuted the 2020
@@
 small, but positive, step towards reducing insecurity in elections that
-occur elsewhere. Especially among those who maintained a steadfast
+occur elsewhere. Especially among those who maintained a steadataast
 degree of distrust in elections. Despite a lack of evidence that
@@
 
-\pagebreak
+\newpage
+
+\section{Appendix A: Survey Experiment Vignettes and Survey
+Items}\label{appendix-a-survey-experiment-vignettes-and-survey-items}
+
+\subsection{Survey Experiment
+Vignettes}\label{survey-experiment-vignettes}
+
+\begin{figure}
+
+\begin{minipage}{0.45\linewidth}
+
+\subsubsection{Treatment Vignette}\label{treatment-vignette-1}
+
+\textbf{Local Military Veterans Recruited for Election Jobs in Maricopa
+County}\\
+\strut \\
+\strut ~~PHOENIX (AP) --- Election officials in Maricopa County,
+Arizona, announced a program designed to recruit military veterans and
+their family members from the community to serve as election
+administrators, including election polling place workers, temporary
+workers, and full-time staff. As the U.S. general elections in November
+near, election officials must fill several thousand temporary positions
+and hundreds of other open positions to ensure sufficient staffing for
+the 2024 elections and beyond.\\
+\strut \\
+\strut ~~Army veteran Jordan Braxton just joined the elections
+workforce. Jordan believes their role is important to ensuring a secure,
+accurate, and transparent election, ``Many places are short on staff
+this election cycle. I served my country in the Army, and I want to do
+my part as a veteran and a citizen to ensure that everyone trusts the
+process and the outcome of the election.''
+
+\end{minipage}%
+%
+\begin{minipage}{0.10\linewidth}
+~\end{minipage}%
+%
+\begin{minipage}{0.45\linewidth}
+
+\subsubsection{Control Vignette}\label{control-vignette-1}
+
+\textbf{Local Residents Recruited for Election Jobs in Maricopa
+County}\\
+\strut \\
+\strut ~~PHOENIX (AP) ---Election officials in Maricopa County, Arizona,
+announced a program to recruit members of the community to serve as
+election administrators, including election polling place workers,
+temporary workers, and full-time staff. As the U.S. general elections in
+November near, election officials must fill several thousand temporary
+positions and hundreds of other open positions to ensure sufficient
+staffing for the 2024 elections and beyond.\\
+\strut \\
+\strut ~~Jordan Braxton just joined the elections workforce. Jordan
+believes their role is important to ensuring a secure, accurate, and
+transparent election, ``Many places are short on staff this election
+cycle. I want to do my part as a citizen to ensure that everyone trusts
+the process and the outcome of the election.''
+
+\end{minipage}%
+
+\end{figure}%
+
+\newpage
+
+\subsection{Survey Items}\label{survey-items}
+
+\begin{table}
+
+\caption{\label{tbl-4}Survey Items and Response Options}
+
+\centering{
+
+\begingroup\fontsize{8}{10}\selectfont
+
+\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{7cm}>{\raggedright\arraybackslash}p{4cm}}
+\toprule
+Question & response\\
+\midrule
+In general, how favorable or unfavorable is your impression of local election officials? & {}[Strongly unfavorable, Somewhat unfavorable, Neither, Somewhat favorable, Strongly favorable]\\
+\addlinespace
+Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected? & Legitimate, Not legitimate\\
+\addlinespace
+Thinking about Maricopa County, AZ, how concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place?
+& Very concerned, Somewhat concerned, Not too concerned, Not at all concerned\\
+\addlinespace
+How confident, if at all, are you that in person polling places in Maricopa County, AZ will be safe places for voters to cast their ballots during the upcoming elections in November?
+& Not at all confident, Not too confident, Somewhat confident, Very confident\\
+\bottomrule
+\end{tabu}
+\endgroup{}
+
+}
+
+\end{table}%
+
+\newpage
+
+\section{Appendix B: Sample Demographics and
+Balance}\label{appendix-b-sample-demographics-and-balance}
+
+\subsection{Sample Demographics}\label{sample-demographics}
+
+The median age was 46 (mean age was \(47\)), \(51.7\%\) (\(n = 658\))
+women, \(47\%\) (\(n = 598\)) men, and approximately \(1.3\%\) who
+identified as either Non-binary/third gender (\(n = 7\)) or preferred
+not to say (\(n = 9\)). A large proportion of the sample identified as
+White or Caucasian (\(n = 975, 76.65\%\)), while all other non-White
+respondents comprised \(27.83\%\) (\(n = 297\)) of the sample. Those who
+held a graduate level degree (e.g., Master's, Doctorate, or Professional
+level) comprised \(13\%\) of the sample; those with either degree at the
+Associate or Bachelor's level comprised \(36.24\%\), while \(22.25\%\)
+had some college but no degree; and \(28.46\%\) had either a high school
+level or equivalent education or less than high school. The largest
+proportion of the sample identified as Democrat at \(44.64\%\), followed
+by Republicans at \(42.59\%\). The proportion of true
+Independents\footnote{Independent `leaners' were grouped into the
+  respective party affiliation in which they lean.} was \(12.78\%\).
+
+\begin{table}
+
+\caption{\label{tbl-demog}Sample Demographics}
+
+\centering{
+
+\centering\begingroup\fontsize{9}{11}\selectfont
+
+\begin{tabular}{lcccc}
+\toprule
+\textbf{Demographic} & \textbf{N} & \makecell[c]{\textbf{Overall}\ \ \\N = 1,287} & \makecell[c]{\textbf{Control}\ \ \\N = 637} & \makecell[c]{\textbf{Treatment}\ \ \\N = 650}\\
+\midrule
+\textbf{Age group} & 1,287 &  &  & \\
+\hspace{1em}18-34 &  & 350 (27\%) & 170 (27\%) & 180 (28\%)\\
+\hspace{1em}35-54 &  & 480 (37\%) & 245 (38\%) & 235 (36\%)\\
+\hspace{1em}55-74 &  & 390 (30\%) & 198 (31\%) & 192 (30\%)\\
+\hspace{1em}75-85+ &  & 67 (5.2\%) & 24 (3.8\%) & 43 (6.6\%)\\
+\addlinespace
+\textbf{Gender} & 1,272 &  &  & \\
+\hspace{1em}Male &  & 598 (47\%) & 289 (46\%) & 309 (48\%)\\
+\hspace{1em}Female &  & 658 (52\%) & 330 (52\%) & 328 (51\%)\\
+\hspace{1em}Other/Refused &  & 16 (1.3\%) & 10 (1.6\%) & 6 (0.9\%)\\
+\hspace{1em}NA &  & 15 & 8 & \vphantom{4} 7\\
+\addlinespace
+\textbf{Race/Ethnicity} & 1,272 &  &  & \\
+\hspace{1em}White &  & 975 (77\%) & 478 (76\%) & 497 \vphantom{1} (77\%)\\
+\hspace{1em}Asian &  & 51 (4.0\%) & 25 (4.0\%) & 26 (4.0\%)\\
+\hspace{1em}Black &  & 164 (13\%) & 85 (14\%) & 79 (12\%)\\
+\hspace{1em}Other &  & 24 (1.9\%) & 12 (1.9\%) & 12 (1.9\%)\\
+\addlinespace
+\hspace{1em}Hispanic &  & 44 (3.5\%) & 24 (3.8\%) & 20 (3.1\%)\\
+\hspace{1em}American Indian &  & 14 (1.1\%) & 5 (0.8\%) & 9 (1.4\%)\\
+\hspace{1em}NA &  & 15 & 8 & \vphantom{3} 7\\
+\textbf{White or Non-White} & 1,272 &  &  & \\
+\hspace{1em}Non-White &  & 297 (23\%) & 151 (24\%) & 146 (23\%)\\
+\addlinespace
+\hspace{1em}White &  & 975 (77\%) & 478 (76\%) & 497 (77\%)\\
+\hspace{1em}NA &  & 15 & 8 & \vphantom{2} 7\\
+\textbf{Education} & 1,272 &  &  & \\
+\hspace{1em}H.S. or less &  & 362 (28\%) & 174 (28\%) & 188 (29\%)\\
+\hspace{1em}Some college no degree &  & 283 (22\%) & 142 (23\%) & 141 (22\%)\\
+\addlinespace
+\hspace{1em}College degree &  & 461 (36\%) & 236 (38\%) & 225 (35\%)\\
+\hspace{1em}Postgraduate degree &  & 166 (13\%) & 77 (12\%) & 89 (14\%)\\
+\hspace{1em}NA &  & 15 & 8 & \vphantom{1} 7\\
+\textbf{Party ID} & 1,268 &  &  & \\
+\hspace{1em}Independent &  & 162 (13\%) & 83 (13\%) & 79 (12\%)\\
+\addlinespace
+\hspace{1em}Republican &  & 540 (43\%) & 262 (42\%) & 278 (43\%)\\
+\hspace{1em}Democrat &  & 566 (45\%) & 283 (45\%) & 283 (44\%)\\
+\hspace{1em}NA &  & 19 & 9 & 10\\
+\textbf{Military Relation} & 1,272 &  &  & \\
+\hspace{1em}No relation &  & 789 (62\%) & 394 (63\%) & 395 (61\%)\\
+\addlinespace
+\hspace{1em}Only family &  & 362 (28\%) & 182 (29\%) & 180 (28\%)\\
+\hspace{1em}Served w/fam &  & 64 (5.0\%) & 31 (4.9\%) & 33 (5.1\%)\\
+\hspace{1em}Served &  & 57 (4.5\%) & 22 (3.5\%) & 35 (5.4\%)\\
+\hspace{1em}NA &  & 15 & 8 & 7\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
+\multicolumn{5}{l}{\textsuperscript{a} Independents do not identify nor 'lean' toward either political party}\\
+\end{tabular}
+\endgroup{}
+
+}
+
+\end{table}%
+
+\subsection{Test of Random Assignment to Experiment
+Condition}\label{test-of-random-assignment-to-experiment-condition}
+
+Table~\ref{tbl-logit} shows results of a logistic regression test of
+random assignment to the treatment group. Demographics such as age,
+gender, race, educational attainment, and party ID are included as
+predictor variables. Note that 19 missing observations were deleted. A
+\(\chi^2(15) = 11.010\), with 15 degrees of freedom and associated
+p-value \textgreater{} 0.05 (\(p = 0.75\)) confirms that none of the
+demographic predictor variables significantly increased the
+log-odds---in turn, the probability---of being assigned to the treatment
+group.
+
+\begin{table}
+
+\caption{\label{tbl-logit}Logistic Regression of Random Assignment to
+Treatment}
+
+\centering{
+
+\centering\begingroup\fontsize{9}{11}\selectfont
+
+\begin{tabular}{lcccc}
+\toprule
+  & \textbf{Treatment N} & \textbf{log(OR)} & \textbf{95\% CI} & \textbf{p-value}\\
+\midrule
+\textbf{(Intercept)} & 640 & 0.17 & -0.25, 0.59 & 0.4\\
+\textbf{Age} & 640 &  &  & 0.14\\
+\hspace{1em}18-34 & 179 & — & — & \\
+\hspace{1em}35-54 & 230 & -0.17 & -0.45, 0.12 & 0.2\\
+\hspace{1em}55-74 & 190 & -0.15 & -0.46, 0.15 & 0.3\\
+\addlinespace
+\hspace{1em}75-85+ & 41 & 0.40 & -0.15, 0.97 & 0.2\\
+\textbf{Gender} & 640 &  &  & 0.5\\
+\hspace{1em}Male & 308 & — & — & \\
+\hspace{1em}Female & 326 & -0.07 & -0.29, 0.15 & 0.5\\
+\hspace{1em}Other/Refused & 6 & -0.62 & -1.8, 0.42 & 0.2\\
+\addlinespace
+\textbf{Race (includes Hispanic as race)} & 640 &  &  & 0.9\\
+\hspace{1em}White & 495 & — & — & \\
+\hspace{1em}Asian & 26 & 0.03 & -0.55, 0.60 & >0.9\\
+\hspace{1em}Black & 79 & -0.08 & -0.43, 0.27 & 0.6\\
+\hspace{1em}Other & 11 & 0.05 & -0.82, 0.93 & >0.9\\
+\addlinespace
+\hspace{1em}Hispanic & 20 & -0.24 & -0.86, 0.38 & 0.5\\
+\hspace{1em}American Indian & 9 & 0.50 & -0.58, 1.7 & 0.4\\
+\textbf{Educational Attainment} & 640 &  &  & 0.6\\
+\hspace{1em}H.S. or less & 188 & — & — & \\
+\hspace{1em}Some college no degree & 140 & -0.10 & -0.42, 0.21 & 0.5\\
+\addlinespace
+\hspace{1em}College degree & 223 & -0.16 & -0.45, 0.12 & 0.3\\
+\hspace{1em}Postgraduate degree & 89 & 0.02 & -0.35, 0.40 & >0.9\\
+\textbf{Party ID} & 640 &  &  & 0.8\\
+\hspace{1em}Independent & 79 & — & — & \\
+\hspace{1em}Republican & 278 & 0.12 & -0.24, 0.48 & 0.5\\
+\addlinespace
+\hspace{1em}Democrat & 283 & 0.05 & -0.31, 0.40 & 0.8\\
+\bottomrule
+\multicolumn{5}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}Chi-Squared = 11.01, d.f. = 15, p = 0.75}\\
+\multicolumn{5}{l}{\rule{0pt}{1em}Abbreviations: CI = Confidence Interval, OR = Odds Ratio}\\
+\end{tabular}
+\endgroup{}
+
+}
+
+\end{table}%
+
+\newpage
+
+\section{Appendix C: Polychoric Item and Score Correlations of Trust and
+Distrust}\label{appendix-c-polychoric-item-and-score-correlations-of-trust-and-distrust}
+
+\subsection{Trust and Distrust}\label{trust-and-distrust}
+
+Polychoric correlation is a measure of association between two ordered
+categorical variables each assumed to represent (i.e., indicate, be
+influenced by) two normally distributed, continuous, latent variables.
+Due to the fact that each item is an ordered categorical variable
+assumed to represent one of two latent constructs (i.e., trust or
+distrust, respectively), I examined polychoric correlations between the
+items used to construct each scale. In addition, one set of the trust
+and distrust items pertained to Maricopa County, AZ, whereas the other
+set of items were identical except that these items pertained to one's
+local area.
+
+Since the two sets of items (AZ items and Local items) are, in theory,
+supposed to capture the same normally distributed continuous latent
+variables, then the polychoric inter-item correlations should be
+significantly associated, strong, and in the same direction for the
+items that measure trust regardless of whether the items pertain to AZ
+or one's local area (likewise for distrust). Simply, trust/distrust in
+elections in AZ should strongly and positively be associated with
+trust/distrust in elections in one's local area.
+
+Additionally, the items that indicate trust should negatively correlate
+with items that indicate distrust. Furthermore, the strength of the
+negative correlations between trust and distrust should closely
+approximate if not match.
+
+\phantomsection\label{cell-fig-polycor}
+\begin{figure}[h]
+
+\caption{\label{fig-polycor}Polychoric Item Correlation Matrix}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-polycor-1.png}}
+
+}
+
+\end{figure}%
+
+Indeed, this is what is revealed by the correlation matrix
+(Figure~\ref{fig-polycor}). Trust items correlate positively, strongly,
+and are significant regardless of location at which the items pertain.
+The same goes for distrust items. Also, items meant to measure trust
+negatively correlate with the items that measure distrust. However, the
+positive correlations are not nearly as high as would be expected
+supposing that the items are nearly identical theoretical indicators of
+the same hypothetical constructs, i.e., trust and distrust respectively.
+
+If the items accurately measure trust/distrust in elections regardless
+of where those elections are said to take place, then positive
+correlations between the AZ and Local area items should approach perfect
+correlation as though the same exact questions were asked twice. This
+result, however, suggests that the location of which the survey items
+pertain (and perhaps other factors) makes a substantial difference in
+the pattern of responses, but also raises valid questions as to whether
+the items accurately measure the latent variable constructs in the first
+place.
+
+Although I do not explicitly assume that the survey instruments
+perfectly measure the hypothetical constructs of interest (i.e., trust
+and distrust), perfect measurement is implicitly assumed by the method
+of combining multiple item responses into a sum or mean composite score.
+
+In short, I expected item responses from the trust and distrust scales
+to be inversely correlated among the sample, but not mutually exclusive.
+Indeed, this is what I find. Polychoric correlations between the trust
+and distrust items negatively correlate as expected, as does the
+correlation between the two sum score scales. Given the ordinal nature
+of the variable items, I conducted a Spearman's rank correlation test
+(\citeproc{ref-spearman1907}{Spearman 1907}) and found a negative
+correlation of \(\rho = -0.49\) (\(95\%\) CI {[}-0.53, -0.44{]};
+Kendall's \(\tau = -0.39\)) between scores on the two scales for the AZ
+items (For the local item scale score correlation: \(\rho = -0.52\),
+\(95\%\) CI {[}-0.56, -0.48{]}; Kendall's \(\tau = -0.39\)). The
+negative correlation between the trust and distrust items and scores
+makes intuitive sense.
+
+\newpage
 

### 2025-03-13 docs/index.qmd
reduced length. Moved content to appendices. Modified text. adjusted format. etc

@@
 subtitle: subtitle
-shorttitle: A Short title # aog-article-pdf
-shortauthors: Isaiah      # aog-article-pdf
+shorttitle: A Short title # aog-article-pdata
+shortauthors: Isaiah      # aog-article-pdata
 authors:
@@
 #| include: false
+#| echo: false
 
@@
 library(patchwork)
+library(texreg) # Conversion of R regression output into latex or HTML tables
 
-# load subset of processed dataframe that includes dv composite scores
-load("data/research-paper-df-subset-20250203.Rdata") #df
+# load data
+load("data/research-paper-data-20241029.Rdata")
 
@@
 codebook <- read.csv("data/survey_codebook.csv")
-df_dict <- read.csv("data/df_dictionary.csv")
+data_dict <- read.csv("data/data_dictionary.csv")
+```
 
-# do next. a whole lotta Likert plots
-source(here::here('src', '03-likert_plots.R'))
+```{r}
+#| label: setup-theme
+
+# set ggplot theme that will be used for every plot
+# theme_get()
+old <- ggplot2::theme_set(ggplot2::theme_bw())  # capture current theme
+
+# set/update new theme
+ggplot2::theme_set(
+  new = ggplot2::theme_bw(
+    base_family = 'TeX Gyre Pagella')+ # set font of ggplots
+    theme(legend.position = 'bottom')  # set legend position for all plots
+)
 
@@
 Much research has been dedicated to analyzing the sentiment of electoral winners vs losers, and vice versa [@nadeau1993; @daniller2019].
-Opinions of electoral trust gathered after the election has occurred are limited considering the well-recognized impact that the electoral outcome itself has on feelings of public trust in elections [@daniller2019].
+Opinions of electoral trust gathered after the election has occurred, however, are limited considering the well-recognized impact that the electoral outcome itself has on feelings of public trust in elections [@daniller2019].
 
@@
 
-Beyond the general competence of election workers, however, the quality of the voter experience may be influenced merely by *a priori* impressions about *who* comprises election staff and volunteers.
+Beyond the general competence of election workers, however, the quality of the voter experience may be influenced merely by prior impressions about *who* comprises election staff and volunteers.
 Political and other social science researchers have recognized for some time the power that group identity can have over attitudes and perception [@xiao2016; @xiao2012; @vanbavel2021].
@@
 2024 general elections, it is reasonable to take into account beliefs about legitimacy of the 2020 election.
-This group who denies the legitimacy of the 2020 election results were possibly the most distrusting of the 2024 election.
+This group who denies the legitimacy of the 2020 election results were possibly the most apprehensive (distrusting) of the 2024 election.
 However, given that veteran service members are held in high regard, generally speaking, announcing that veterans are being actively recruited to work as election staff and volunteers is expected to positively influence confidence in elections among those who remained firm in the belief that the 2020 election results were illegitimate.
@@
 Taking into account that confidence is lower for elections conducted outside of one's local area, then information that veterans are being recruited to help conduct elections in locations beyond one's locale may close this gap between confidence in elections within one's local area and confidence in elections elsewhere.
-Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone.
+Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone on public opinion.
 Therefore, any observed disparity of confidence in elections (i.e., the "confidence gap") between elections within one's local area and elections beyond will be smaller among those who are presented with information about election official recruitment efforts of veteran service members.
@@
 
-trust_txt <- df |> select(q19, q20, q21, q22, q24) |>
+trust_txt <- data |> select(q19, q20, q21, q22, q24) |>
   labelled::set_variable_labels(
@@
 
-distrust_txt <- df |> select(q28_1:q28_5) |>
+distrust_txt <- data |> select(q28_1:q28_5) |>
   labelled::generate_dictionary() |> 
@@
 
-The relationship is that trust and distrust represent opposing degrees of confidence along the same spectrum.
-However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling similarly confident in both respects.
-Accordingly, equivalent degrees of trust and distrust cancel out, rendering one relatively more *insecure* about their expectations of the future despite the fact that they may feel confident in either direction.
-When trust and distrust are considered as reflective of one's confidence about future expectations, then both can be placed along the same spectrum.
-Quite literally, this reflects an uncertain feeling of "it could go one way or the other" with respect to the integrity of elections administration.
-Operationally, this would reflect a middling point on a scale of *confidence*.
-
 In light of this, I reverse coded items on the distrust scale and combined responses to the trust in elections scale.
@@
 Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^11].
-On this scale, positive values reflect higher confidence in elections, negative values reflect greater distrust, and values closer to zero correspond to an individual's degree of insecurity.
-
-The advantage is that this permits a better test of the treatment effect as theorized.
-Of course, it is easy enough to examine the effect of the treatment on both trust and distrust separately.
-However, the theory presents a hypothesis that the treatment will impose influence upon both variables *concurrently and in a positive direction* with respect to the relationship between trust and distrust.
-That is to say, confidence increases insofar as trust in elections increases and distrust decreases; since distrust detracts from trust, then an accurate measure of confidence must take that constraint into account.
+On this scale, positive values reflect higher confidence in elections, negative values reflect greater distrust, and values closer to zero correspond to an individual's degree of *insecurity*.
 
@@
 
-```{r}
-#| label: fig-trustlikert
-#| fig-cap: "Trust in Election Administration by Experiment Condition"
-#| fig-height: 4.5
-#| fig-pos: "h"
+{{< embed notebooks/figures.qmd#fig-patch10 >}}
 
-p10.trust.treat
-
-```
-
-Reviewing item responses distinguished by treatment condition reveals particulars of the treatment effect (@fig-trustlikert).
+Reviewing item responses distinguished by treatment condition reveals particulars of the treatment effect (@fig-patch10).
 Among the items that asked about Maricopa County, AZ, it is a bit easier to see upon which items the treatment vignette had the greatest effect.
@@
 
-```{r}
-#| label: fig-distrustlikert
-#| fig-cap: "Disrust in Election Administration by Experiment Condition"
-#| fig-height: 4.5
-#| fig-pos: "H"
-
-p11.distrust.treat
-
-```
+{{< embed notebooks/figures.qmd#fig-patch11 >}}
 
 Similar to the trust scale items, the items on the distrust scale were associated with lower distrust in the treatment condition compared to the control.
-A quick glance at @fig-distrustlikert shows what appears to be a significant reduction in distrust, especially regarding the expectations that many votes wouldn't be counted, many voters would be turned away, and that election officials would discourage voters from casting a ballot.
+A quick glance at @fig-patch11 shows what appears to be a significant reduction in distrust, especially regarding the expectations that many votes wouldn't be counted, many voters would be turned away, and that election officials would discourage voters from casting a ballot.
 Interestingly, the expectation that there would be foreign interference in elections in Maricopa County, AZ were pretty resilient against the treatment.
@@
 
-```{r}
-#| label: fig-dist
-#| fig-cap: "Overlapping Distribution of Confidence in Elections for AZ and Local Area"
-#| fig-pos: "H"
-
-ggplot(df) +
-  geom_histogram(
-    aes(x = conf.az.rescaled , y = after_stat(density)),
-    bins = 15,
-    alpha = 0.2,
-    color = 1,
-    fill = "red"
-  ) +
-  geom_histogram(
-    aes(x = conf.lcl.rescaled , y = after_stat(density)),
-    bins = 15,
-    alpha = 0.2,
-    color = 1,
-    fill = "blue"
-  ) +
-  geom_segment(
-    x = round(mean(df$conf.az.rescaled), 2),
-    y = 0,
-    yend = 0.35,
-    color = "firebrick",
-    lwd = 1.4,
-    linetype = 2
-  ) +
-  geom_segment(
-    x = round(mean(df$conf.lcl.rescaled), 2),
-    y = 0,
-    yend = 0.35,
-    color = "darkblue",
-    lwd = 1.4,
-    linetype = 2
-  ) +
-  annotate(
-    "text",
-    x = round(mean(df$conf.az.rescaled), 2),
-    y = 0.40,
-    label = paste("AZ =", round(mean(
-      df$conf.az.rescaled
-    ), 2), "(", round(sd(
-      df$conf.az.rescaled
-    ), 2), ")"),
-    color = "firebrick"
-  ) +
-  annotate(
-    "text",
-    x = round(mean(df$conf.lcl.rescaled), 2),
-    y = 0.43,
-    label = paste("Local area =", round(mean(
-      df$conf.lcl.rescaled
-    ), 2), "(", round(sd(
-      df$conf.lcl.rescaled
-    ), 2), ")"),
-    color = "darkblue"
-  ) +
-  labs(
-    x = str_wrap("Confidence", width = 85),
-    y = "Density",
-    caption = str_wrap(
-     "Mean (std.deviation). Mean difference = 0.33, CI [0.27, 0.38], t = 11.613, df = 1286, p < 0.01",
-     width = 95)) +
-  theme_bw(base_family = "TeX Gyre Pagella")
-
-```
+{{< embed notebooks/figures.qmd#fig-dist >}}
 
@@
 dplyr::bind_rows(
-  df |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
+  data |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
   rstatix::t_test(formula = conf.az.rescaled ~ group,var.equal = F,detailed = T),
-  df |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
+  data |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
   rstatix::t_test(formula = conf.lcl.rescaled ~ group,var.equal = F, detailed = T)
@@
   # insight::export_table(format = "md") # alternate
-  # output table as `kable` for LaTeX pdf
+  # output table as `kable` for LaTeX pdata
   kableExtra::kbl( 
@@
     col.names = c("Place", "$\\bar{x}_{diff}$", "$\\bar{x}_{treat}$", "$\\bar{x}_{control}$",
-                  "$treat_{n}$", "$control_{n}$", "t", "p", "df", "CI"), 
+                  "$treat_{n}$", "$control_{n}$", "t", "p", "data", "CI"), 
     escape = F) |> 
@@
 conf.coef1 <- jtools::plot_summs(
-  lm(conf.az.rescaled ~ group, data = df), 
-  lm(conf.lcl.rescaled ~ group, data = df), 
+  lm(conf.az.rescaled ~ group, data = data), 
+  lm(conf.lcl.rescaled ~ group, data = data), 
   center = T, scale = T, transform.response = T,
@@
 conf.coef2 <- jtools::plot_summs(
-  lm(trust.scores.az ~ group, data = df),
-  lm(distrust.scores.az ~ group, data = df),
-  lm(trust.scores.lcl ~ group, data = df),
-  lm(distrust.scores.lcl ~ group, data = df),
+  lm(trust.scores.az ~ group, data = data),
+  lm(distrust.scores.az ~ group, data = data),
+  lm(trust.scores.lcl ~ group, data = data),
+  lm(distrust.scores.lcl ~ group, data = data),
   center = T, scale = T, transform.response = T,
@@
 
-```{r}
-#| label: fig-legit
-#| fig-cap: "Trust in elections by treatment among those who refute the 2020 election results"
-#| fig-height: 4.5
-
-p13.trust.treat.legit
-
-```
+{{< embed notebooks/figures.qmd#fig-patch13 >}}
 
@@
 
-```{r}
-#| label: fig-legit2
-#| fig-cap: "Distrust in elections by treatment among those who refute the 2020 election results"
-#| fig-height: 4.5
-
-p14.distrust.treat.legit
-
-```
+{{< embed notebooks/figures.qmd#fig-patch14 >}}
 
@@
 Although there is not as stark a disparity between responses of those in the treatment and those in the control, among those in the treatment group, there does appear to be less expectation that election fraud would occur in Maricopa County, AZ.
-Overall, review of responses to trust (@fig-legit) and distrust survey items (@fig-legit2) does lend credence to the impact of the treatment.
+Overall, review of responses to trust (@fig-patch13) and distrust survey items (@fig-patch14) does lend credence to the impact of the treatment.
 
@@
 
-::: {.content-visible when-format="bookup-html"}
+::: {.content-visible when-format="bookup-html" unless-format="submittable-pdf"}
 
 ```{r}
-#| label: tbl-legit-html
 #| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
@@
 # All continuous variables are mean-centered and scaled by 1 standard deviation.
-m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = df)
-m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = df)
+m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = data)
+m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = data)
 
-stargazer::stargazer(
-  m1,
-  m2,
-  type = "html",
-  style = 'apsr',
-  header = F,
-  float = F,
-  align = T, 
+texreg::htmlreg(
+  list(m1, m2), 
   single.row = T,
-  dep.var.labels.include = F, model.numbers = F,
-  digits = 2,
-  column.labels = c("Confidence in AZ Elections", "w/Interaction"),
-  covariate.labels = c(
+  caption.above = T,
+  custom.model.names = c("Confidence in AZ Elections", "w/Interaction"),
+  custom.coef.names = c(
+    "(Intercept)",
     "Treatment",
@@
     "Democrat",
-      "Not Legitimate * Treatment",
-      "Constant"
+    "Not Legitimate * Treatment"
     )
@@
 
-The first model in Table @tbl-legit-html shows that overall confidence in elections (trust - distrust) among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
+:::
+
+::: {.content-visible when-format="submittable-pdf" unless-format="bookup-html"}
+
+```{r}
+#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
+#| tbl-pos: H
+#| label: tbl-legit
+#| results: asis
+
+# All continuous variables are mean-centered and scaled by 1 standard deviation.
+m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = data)
+m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = data)
+
+texreg::texreg(
+  list(m1, m2),
+  single.row = T,
+  caption.above = T,
+  use.packages = F,
+  table = F, # Ensure this is set to FALSE so Quarto handles table cross-ref env
+  custom.model.names = c("Confidence in AZ Elections", "w/Interaction"),
+  custom.coef.names = c(
+    "(Intercept)",
+    "Treatment",
+    "Not Legitimate",
+    "Republican",
+    "Democrat",
+    "Not Legitimate * Treatment"
+    )
+)
+
+```
+
+:::
+
+The first model in Table \ref{tbl-legit} shows that overall confidence in elections among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
 Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
@@
 The treatment alone does not reverse such beliefs, but this shows where its influence was most potent.
-
-:::
-
-::: {.content-visible when-format="pdf"}
-
-```{r}
-#| label: tbl-legit-pdf
-#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
-#| tbl-pos: H
-#| results: asis
-
-# All continuous variables are mean-centered and scaled by 1 standard deviation.
-m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = df)
-m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = df)
-
-stargazer::stargazer(
-  m1,
-  m2,
-  type = "latex", 
-  style = 'apsr',
-  header = F,
-  float = F,
-  align = T, 
-  single.row = T, 
-  dep.var.labels.include = F, model.numbers = F,
-  digits = 2,
-  column.labels = c("Confidence in AZ Elections", "w/Interaction"),
-  covariate.labels = c(
-      "Treatment",
-      "Not Legitimate",
-      "Republican",
-      "Democrat",
-      "Not Legitimate * Treatment",
-      "Constant"
-    )
-)
-
-```
-
-The first model in Table \ref{tbl-legit-pdf} shows that overall confidence in elections (trust - distrust) among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
-Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
-Not believing the 2020 election of Joe Biden was legitimate is negatively associated with confidence in elections.
-In order to assess the magnitude of this interaction effect of the treatment on those who refuted the 2020 election results, I ran a model where confidence in elections was regressed on the interaction between the treatment and legitimacy beliefs, controlling for partisanship.
-
-There's a positive interaction effect of the treatment vignette among those who believe that the 2020 election was not legitimate, on average and controlling for partisanship.
-This shows that the treatment effect was most influential upon those who believe the 2020 election results were illegitimate.
-The treatment alone does not reverse such beliefs, but this shows where its influence was most potent.
-
-:::
 
@@
 In the anticipatory period prior to national elections, publicized efforts to recruit veterans to work as election staff and volunteers may be a small, but positive, step towards reducing insecurity in elections that occur elsewhere.
-Especially among those who maintained a steadfast degree of distrust in elections.
+Especially among those who maintained a steadataast degree of distrust in elections.
 Despite a lack of evidence that systematic electoral fraud had occurred in the 2020 election, a substantial proportion of the population were unwilling to affirm the legitimacy of the results.
@@
 
-\pagebreak
+\newpage
+
+# Appendix A: Survey Experiment Vignettes and Survey Items {.appendix}
+
+## Survey Experiment Vignettes
+
+::::: {#fig-vignettes .content-visible layout-ncol="2" when-format="html" unless-format="pdf"}
+::: {#fig-treatment}
+### Treatment Vignette
+
+| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
+| 
+|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
+As the U.S.
+general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
+| 
+|   Army veteran Jordan Braxton just joined the elections workforce.
+Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
+I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
+:::
+
+::: {#fig-control}
+### Control Vignette
+
+| **Local Residents Recruited for Election Jobs in Maricopa County**
+| 
+|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
+As the U.S.
+general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
+| 
+|   Jordan Braxton just joined the elections workforce.
+Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
+I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
+:::
+
+Fabricated Article Vignettes utilized as Experimental Stimulus
+:::::
+
+::::: {.content-hidden unless-format="pdf" layout="[0.45, -0.1, 0.45]"}
+::: {#first-column}
+### Treatment Vignette
+
+| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
+| 
+|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
+As the U.S.
+general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
+| 
+|   Army veteran Jordan Braxton just joined the elections workforce.
+Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
+I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
+:::
+
+::: {#second-column}
+### Control Vignette
+
+| **Local Residents Recruited for Election Jobs in Maricopa County**
+| 
+|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
+As the U.S.
+general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
+| 
+|   Jordan Braxton just joined the elections workforce.
+Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
+I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
+:::
+:::::
+
+\newpage
+
+## Survey Items
+
+```{r}
+#| label: tbl-4
+#| tbl-cap: "Survey Items and Response Options"
+
+data |> 
+  select(q6, q7, q25, q26) |> 
+  labelled::generate_dictionary() |> 
+  dplyr::as_tibble() |> 
+  mutate(value_labels = dplyr::case_when(
+    variable == 'q6' ~ "[Strongly unfavorable, Somewhat unfavorable, Neither, Somewhat favorable, Strongly favorable]",
+    variable == 'q7' ~ "Legitimate, Not legitimate",
+    variable == 'q25' ~ "Very concerned, Somewhat concerned, Not too concerned, Not at all concerned",
+    variable == 'q26' ~ "Not at all confident, Not too confident, Somewhat confident, Very confident"
+  )) |> 
+  select(Question = label, response = value_labels) |> 
+  kableExtra::kbl(booktabs = T, linesep = "\\addlinespace") |> 
+  kableExtra::kable_styling(full_width = T,
+                            font_size = 8,
+                            latex_options = c("HOLD_position")) |> 
+  kableExtra::column_spec(column = 1, width = "7cm") |> 
+  kableExtra::column_spec(column = 2, width = "4cm")
+
+```
+
+\newpage
+
+# Appendix B: Sample Demographics and Balance {.appendix}
+
+## Sample Demographics
+
+The median age was 46 (mean age was $47$), $51.7\%$ ($n = 658$) women, $47\%$ ($n = 598$) men, and approximately $1.3\%$ who identified as either Non-binary/third gender ($n = 7$) or preferred not to say ($n = 9$).
+A large proportion of the sample identified as White or Caucasian ($n = 975, 76.65\%$), while all other non-White respondents comprised $27.83\%$ ($n = 297$) of the sample.
+Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised $13\%$ of the sample; those with either degree at the Associate or Bachelor's level comprised $36.24\%$, while $22.25\%$ had some college but no degree; and $28.46\%$ had either a high school level or equivalent education or less than high school.
+The largest proportion of the sample identified as Democrat at $44.64\%$, followed by Republicans at $42.59\%$.
+The proportion of true Independents^[Independent 'leaners' were grouped into the respective party affiliation in which they lean.] was $12.78\%$.
+
+```{r}
+#| label: tbl-demog
+#| tbl-cap: "Sample Demographics"
+#|
+
+# descriptive stats of categorical variables
+# best method for html document
+tbl.desc <- data |>  
+  labelled::set_variable_labels(
+    age_4cat = "Age group",
+    gender_3cat = "Gender",
+    race2 = "Race/Ethnicity",
+    race_wnw = "White or Non-White",
+    educ_4cat = "Education",
+    partyid_3cat = "Party ID",
+    milrelation  = "Military Relation"
+  ) |> 
+  gtsummary::tbl_summary(
+    by = group,
+    include = c(
+    age_4cat, 
+    gender_3cat, 
+    race2,
+    race_wnw,
+    educ_4cat, 
+    partyid_3cat,
+    milrelation),
+    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
+    missing = "ifany",
+    missing_text = "NA") |> 
+  gtsummary::add_n() |> 
+  gtsummary::add_overall() |> 
+  gtsummary::modify_header(label = "**Demographic**") |> 
+  gtsummary::bold_labels()
+
+gtsummary::as_kable_extra(tbl.desc, booktabs = T) |>
+  kableExtra::add_footnote(
+    label = "Independents do not identify nor 'lean' toward either political party") |> 
+  kableExtra::kable_styling(
+    font_size = 9, 
+    protect_latex = T)
+
+# gtsummary::as_gt(tbl.desc) |>  
+#   gt::tab_footnote(
+#     footnote = "Independents do not identify nor 'lean' toward either political party",
+#     placement = "left"
+#     ) |>  
+#   gt::cols_align(align = 'left', columns = everything()) |> 
+#   gt::tab_options(
+#     table.font.size = "small",
+#     data_row.padding = gt::px(1)
+#   )
+
+```
+
+## Test of Random Assignment to Experiment Condition
+
+@tbl-logit shows results of a logistic regression test of random assignment to the treatment group.
+Demographics such as age, gender, race, educational attainment, and party ID are included as predictor variables.
+Note that 19 missing observations were deleted.
+A $\chi^2(15) = 11.010$, with 15 degrees of freedom and associated p-value > 0.05 ($p = 0.75$) confirms that none of the demographic predictor variables significantly increased the log-odds---in turn, the probability---of being assigned to the treatment group.
+
+```{r}
+#| label: tbl-logit
+#| tbl-cap: "Logistic Regression of Random Assignment to Treatment"
+
+# simple logit of test of random assignment to treatment
+# treatment is DV (treatment = 1, control = 0)
+# demographic variables are IVs
+
+data <- data |> 
+  mutate(group.dum = dplyr::case_when(
+    group == "Treatment" ~ 1,
+    group == "Control" ~ 0,
+    TRUE ~ NA), .after = group)
+
+m1 <- glm(group.dum ~ age_4cat + gender_3cat + race2 + educ_4cat + partyid_3cat, 
+          family = binomial(link = "logit"), data = data)
+
+# A Chi-square of 11.01 with 15 degrees of freedom and associated p-value > 0.05 (p-value = 0.752) confirms that none of the demographic predictor variables significantly increased the probability of being assigned to the treatment group.
+
+logit_tab <- gtsummary::tbl_regression(
+    m1, 
+    intercept = T,
+    label = list(
+      age_4cat ~"Age", 
+      gender_3cat ~ "Gender", 
+      race2 ~ "Race (includes Hispanic as race)",
+      educ_4cat ~ "Educational Attainment", 
+      partyid_3cat ~ "Party ID")) |> 
+  gtsummary::add_global_p(keep = T) |> 
+  gtsummary::add_nevent(location = c("label", "level")) |>
+  gtsummary::bold_p() |> 
+  gtsummary::bold_labels() |>
+  # gtsummary::show_header_names()
+  gtsummary::modify_header(
+    label = " ",
+    stat_nevent = "**Treatment N**") 
+# 
+#   gtsummary::modify_footnote_header(
+#     footnote = "Chi-Squared ($\\chi^2$) = 11.01, d.f. = 15, p = 0.75", columns = "p.value")
+
+gtsummary::as_kable_extra(logit_tab, 
+                          booktabs = T, 
+                          escape = F, 
+                          addtl_fmt = T) |> 
+  kableExtra::footnote("Chi-Squared = 11.01, d.f. = 15, p = 0.75", escape = F) |> 
+  kableExtra::kable_styling(font_size = 9)
+
+```
+
+\newpage
+
+# Appendix C: Polychoric Item and Score Correlations of Trust and Distrust {.appendix}
+
+## Trust and Distrust
+
+Polychoric correlation is a measure of association between two ordered categorical variables each assumed to represent (i.e., indicate, be influenced by) two normally distributed, continuous, latent variables.
+Due to the fact that each item is an ordered categorical variable assumed to represent one of two latent constructs (i.e., trust or distrust, respectively), I examined polychoric correlations between the items used to construct each scale.
+In addition, one set of the trust and distrust items pertained to Maricopa County, AZ, whereas the other set of items were identical except that these items pertained to one's local area.
+
+Since the two sets of items (AZ items and Local items) are, in theory, supposed to capture the same normally distributed continuous latent variables, then the polychoric inter-item correlations should be significantly associated, strong, and in the same direction for the items that measure trust regardless of whether the items pertain to AZ or one's local area  (likewise for distrust).
+Simply, trust/distrust in elections in AZ should strongly and positively be associated with trust/distrust in elections in one's local area.
+
+Additionally, the items that indicate trust should negatively correlate with items that indicate distrust.
+Furthermore, the strength of the negative correlations between trust and distrust should closely approximate if not match.
+
+```{r}
+#| label: fig-polycor
+#| fig-cap: "Polychoric Item Correlation Matrix"
+#| fig-pos: 'h'
+
+# Get polychoric item correlation matrix.
+item.cor <- data |>
+  select(q19:q24, -q23, q28_1:q28_5, q30:q35, -q34, q40_1:q40_5) |> 
+  # ensure factors are ordered factors
+  mutate(across(where(is.factor), ~factor(., ordered = T))) |> 
+  # adjust variable column names of items
+  dplyr::rename(
+    trustvote_az     = q19,
+    trustadmin_az    = q20,
+    truststaff_az    = q21,
+    trustprcss_az    = q22,
+    trusttech_az     = q24,
+    votefraud_az     = q28_1,
+    miscount_az      = q28_2,
+    turnedaway_az    = q28_3,
+    foreigntamp_az   = q28_4,
+    discourage_az    = q28_5,
+    trustvote_lcl    = q30,
+    trustadmin_lcl   = q31,
+    truststaff_lcl   = q32,
+    trustprcss_lcl   = q33,
+    trusttech_lcl    = q35,
+    votefraud_lcl    = q40_1,
+    miscount_lcl     = q40_2,
+    turnedaway_lcl   = q40_3,
+    foreigntamp_lcl  = q40_4,
+    discourage_lcl   = q40_5
+  ) |> 
+  correlation::correlation(
+    select = 
+      c("trustvote_az", "trustadmin_az", "truststaff_az", "trustprcss_az", "trusttech_az",
+        "votefraud_az", "miscount_az", "turnedaway_az", "foreigntamp_az", "discourage_az"),
+    select2 =
+      c("trustvote_lcl", "trustadmin_lcl", "truststaff_lcl", "trustprcss_lcl","trusttech_lcl",
+        "votefraud_lcl", "miscount_lcl", "turnedaway_lcl", "foreigntamp_lcl","discourage_lcl"),
+    method = "polychoric") |>
+  summary()
+
+# plot item correlations
+plot(item.cor) + theme(axis.text.x = element_text(angle = 45, vjust = 0.6))
+
+```
+
+Indeed, this is what is revealed by the correlation matrix (@fig-polycor).
+Trust items correlate positively, strongly, and are significant regardless of location at which the items pertain.
+The same goes for distrust items.
+Also, items meant to measure trust negatively correlate with the items that measure distrust.
+However, the positive correlations are not nearly as high as would be expected supposing that the items are nearly identical theoretical indicators of the same hypothetical constructs, i.e., trust and distrust respectively.
+
+If the items accurately measure trust/distrust in elections regardless of where those elections are said to take place, then positive correlations between the AZ and Local area items should approach perfect correlation as though the same exact questions were asked twice.
+This result, however, suggests that the location of which the survey items pertain (and perhaps other factors) makes a substantial difference in the pattern of responses, but also raises valid questions as to whether the items accurately measure the latent variable constructs in the first place.
+
+Although I do not explicitly assume that the survey instruments perfectly measure the hypothetical constructs of interest (i.e., trust and distrust), perfect measurement is implicitly assumed by the method of combining multiple item responses into a sum or mean composite score.
+
+In short, I expected item responses from the trust and distrust scales to be inversely correlated among the sample, but not mutually exclusive.
+Indeed, this is what I find.
+Polychoric correlations between the trust and distrust items negatively correlate as expected, as does the correlation between the two sum score scales.
+Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
+The negative correlation between the trust and distrust items and scores makes intuitive sense.
+
+\newpage
 
@@
 
-[^10]: I expected item responses from the trust and distrust scales to be inversely correlated among the sample, but not mutually exclusive.
-Indeed, this is what I find.
-Polychoric correlations between the trust and distrust items negatively correlate as expected, as does the correlation between the two sum score scales.
-Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
-The negative correlation between the trust and distrust items and scores makes intuitive sense.
-See Appendix C for inter-item correlation
+[^10]: See Appendix C for analysis.
 

### 2025-03-13 index.qmd
reduced length. Moved content to appendices. Modified text. adjusted format. etc

@@
 library(easystats)
+library(odds.n.ends) # model sig from glm
 library(patchwork)
-library(jtools)
+library(texreg) # Conversion of R regression output into latex or HTML tables
 
-# load subset of processed dataframe that includes dv composite scores
-load("data/research-paper-df-subset-20250203.Rdata") #df
+# load data
+load("data/research-paper-data-20241029.Rdata")
 
@@
 2024 general elections, it is reasonable to take into account beliefs about legitimacy of the 2020 election.
-This group who denies the legitimacy of the 2020 election results were possibly the most distrusting of the 2024 election.
+This group who denies the legitimacy of the 2020 election results were possibly the most apprehensive (distrusting) of the 2024 election.
 However, given that veteran service members are held in high regard, generally speaking, announcing that veterans are being actively recruited to work as election staff and volunteers is expected to positively influence confidence in elections among those who remained firm in the belief that the 2020 election results were illegitimate.
-I take into account that legitimacy beliefs about the 2020 election and expectations of electoral fraud are related to partisanship and include partisanship as a control in the analysis.
+I take into account that legitimacy beliefs about the 2020 election and expectations of electoral fraud are related to partisanship and include partisanship as a control in the analysis[^4].
 
@@
 Taking into account that confidence is lower for elections conducted outside of one's local area, then information that veterans are being recruited to help conduct elections in locations beyond one's locale may close this gap between confidence in elections within one's local area and confidence in elections elsewhere.
-Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone.
-Therefore, any observed disparity of confidence in elections (i.e., the "confidence gap") between elections within one's local area and elections beyond will be smaller when people are presented with information about election official recruitment efforts of veteran service members.
+Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone on public opinion.
+Therefore, any observed disparity of confidence in elections (i.e., the "confidence gap") between elections within one's local area and elections beyond will be smaller among those who are presented with information about election official recruitment efforts of veteran service members.
 
@@
 In total, five survey items measure different aspects of trust in elections administration.
-The items measuring confidence in elections include:
-
-Another series of five survey items captured an individual's level of *distrust* in elections administration based on the extent to which they *expect electoral fraud* to occur.
-These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in \[Maricopa County, AZ/ your local area\]?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
 
 ```{r}
-#| label: tbl-items
+#| label: tbl-1
 #| tbl-cap: "Survey Items for Trust and Distrust in Elections"
 
-trust_txt <- df |> select(q19, q20, q21, q22, q24) |>
+trust_txt <- data |> select(q19, q20, q21, q22, q24) |>
   labelled::set_variable_labels(
@@
 
-Similar to the items capturing trust in elections (@tbl-items), I computed a summated score for each respondent reflecting the extent of their distrust in elections.
+Another series of five survey items captured an individual's level of *distrust* in elections administration based on the extent to which they expect electoral fraud to occur.
+These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in \[Maricopa County, AZ/ your local area\]?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
+
+Similar to the items capturing trust in elections (@tbl-1), I computed a summated score for each respondent reflecting the extent of their distrust in elections.
 
 Upon construction of the two summated scales of *trust* and *distrust*, internal consistency reliability coefficient $\alpha$ were estimated for both and found to be adequate ($\alpha$ \> 0.8); the trust in elections scale $\alpha$ = 0.93 and the distrust scale $\alpha$ = 0.86.
-In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each.
-
-I expected item responses from these two scales to be inversely correlated among the sample, but not mutually exclusive.
-Indeed, this is what I find.
-Polychoric correlations between the trust and distrust items negatively correlate as expected^[See Appendix C], as does the correlation between the two sum score scales.
-Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
-The negative correlation between the trust and distrust items and scores makes intuitive sense.
+In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each[^10].
 
@@
 
-The relationship is that trust and distrust represent opposing degrees of confidence along the same spectrum.
-However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling similarly confident in both respects.
-Accordingly, equivalent degrees of trust and distrust cancel out, rendering one relatively more *insecure* about their expectations of the future despite the fact that they may feel confident in either direction.
-When trust and distrust are considered as reflective of one's confidence about future expectations, then both can be placed along the same spectrum.
-Therefore, a lack of confidence denotes insecurity.
-
-Something may cause a person to have greater expectations that election fraud will occur, which in turn will always lower their trust in elections administration.
-In contrast, a person may feel a bit more confident in the integrity of elections, but this confidence is constrained by the extent to which they expect election fraud to occur.
-This means that a person's baseline level of confidence in elections admin must take into account their present degree of distrust---i.e., their expectations of electoral fraud.
-
-Those who are, or are close to being, equally confident in both directions would be the most *insecure* about their expectations.
-Having no trust in elections and no expectation that electoral fraud will occur is functionally equivalent to having equal degree of both.
-Quite literally, this reflects an uncertain feeling of "it could go one way or the other" with respect to the integrity of elections administration.
-Operationally, this would reflect a middling point on a scale of *confidence*.
-
-In light of this, I reverse coded positive expectations of electoral fraud and added responses from the distrust scale to the trust in elections scale.
+In light of this, I reverse coded items on the distrust scale and combined responses to the trust in elections scale.
 That is, item responses on the trust scale ranged from 0 ("Not confident at all") to 3 ("Very confident), whereas responses on the distrust scale ranged from 0 ("Not likely at all") to -3 ("Very likely").
-Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^8].
-On this scale, positive values reflect higher confidence in elections, negative values reflect greater distrust, and values closer to zero correspond to an individual's degree of insecurity.
-
-The advantage is that this permits a better test of the treatment effect as theorized.
-Of course, it is easy enough to examine the effect of the treatment on both trust and distrust separately.
-However, the theory presents a hypothesis that the treatment will impose influence upon both variables *concurrently and in a positive direction* with respect to the relationship between trust and distrust.
-That is to say, confidence increases insofar as trust in elections increases and distrust decreases; since distrust detracts from trust, then an accurate measure of confidence must take that constraint into account.
+Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^11].
+On this scale, positive values reflect higher confidence in elections, negative values reflect greater distrust, and values closer to zero correspond to an individual's degree of *insecurity*.
 
@@
 That being said, there is a definite distinction between items pertaining to Maricopa County, AZ compared to items that pertain to a respondent's local area.
-In fact, the treatment appears to have hardly made a difference when the items concerned one's local area.
+In fact, as expected, the treatment appears to have hardly made a difference when the items concerned one's local area.
 
-```{r}
-#| label: fig-trustlikert
-#| fig-cap: "Trust in Election Administration by Experiment Condition"
-#| fig-height: 4.5
-#| fig-pos: "h"
+{{< embed notebooks/figures.qmd#fig-patch10 >}}
 
-p10.trust.treat
-
-```
-
-Reviewing item responses distinguished by treatment condition reveals particulars of the treatment effect (@fig-trustlikert).
+Reviewing item responses distinguished by treatment condition reveals particulars of the treatment effect (@fig-patch10).
 Among the items that asked about Maricopa County, AZ, it is a bit easier to see upon which items the treatment vignette had the greatest effect.
@@
 
-```{r}
-#| label: fig-distrustlikert
-#| fig-cap: "Disrust in Election Administration by Experiment Condition"
-#| fig-height: 4.5
-#| fig-pos: "h"
-
-p11.distrust.treat
-
-```
+{{< embed notebooks/figures.qmd#fig-patch11 >}}
 
 Similar to the trust scale items, the items on the distrust scale were associated with lower distrust in the treatment condition compared to the control.
-A quick glance at @fig-distrustlikert shows what appears to be a significant reduction in distrust, especially regarding the expectations that many votes wouldn't be counted, many voters would be turned away, and that election officials would discourage voters from casting a ballot.
+A quick glance at @fig-patch11 shows what appears to be a significant reduction in distrust, especially regarding the expectations that many votes wouldn't be counted, many voters would be turned away, and that election officials would discourage voters from casting a ballot.
 Interestingly, the expectation that there would be foreign interference in elections in Maricopa County, AZ were pretty resilient against the treatment.
@@
 
-```{r}
-#| label: fig-legit
-#| fig-cap: "Trust in elections by treatment among those who refute the 2020 election results"
-#| fig-height: 4.5
+{{< embed notebooks/figures.qmd#fig-patch13 >}}
 
-p13.trust.treat.legit
+Among those who refuted the 2020 election results, trust in Maricopa County, AZ elections was lower for each item compared to items pertaining to elections within one's local area, regardless of treatment condition.
+However, notably, trust that election technology would be secure received the lowest confidence endorsement overall.
+There was also a notable lack of trust that the voting process would be fair relative to the other items.[^13] Now the comparative difference in responses between those in the treatment group compared to those in the control group appears substantial for items pertaining to elections in Maricopa County, AZ.
 
-```
-
-Among those who belief the 2020 election results were illegitimate, trust in Maricopa County, AZ elections was lower for each item compared to items pertaining to elections within one's local area, regardless of treatment condition.
-However, notably, trust that election technology would be secure received the lowest confidence endorsement overall.
-There was also a notable lack of trust that the voting process would be fair relative to the other items.^[What is interesting to note here is that the first three items regard the more human element of the election administration process, e.g., ensuring accuracy of counts, competence, and commitment of election workers.
-Although a neat line can't really be drawn between the first three and latter two items presented here, it is interesting to see a divergence of the usual high confidence placed in local area elections.] Now the comparative difference in responses between those in the treatment group compared to those in the control group appears substantial for items pertaining to elections in Maricopa County, AZ.
-
-```{r}
-#| label: fig-legit2
-#| fig-cap: "Distrust in elections by treatment among those who refute the 2020 election results"
-#| fig-height: 4.5
-
-p14.distrust.treat.legit
-
-```
+{{< embed notebooks/figures.qmd#fig-patch14 >}}
 
@@
 
+::: {.content-visible when-format="bookup-html" unless-format="aog-article-pdf"}
+
 ```{r}
-#| label: tbl-legit
 #| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
 #| tbl-pos: H
-#| results: asis
 
 # All continuous variables are mean-centered and scaled by 1 standard deviation.
-m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = df)
-m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = df)
+m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = data)
+m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = data)
 
-stargazer::stargazer(
-  m1,
-  m2,
-  type = "latex", 
-  style = 'apsr',
-  header = F,
-  float = F,
-  align = T, 
+texreg::htmlreg(
+  list(m1, m2), 
   single.row = T,
-  dep.var.labels.include = F, model.numbers = F,
-  digits = 2,
-  column.labels = c("Confidence in AZ Elections", "w/Interaction"),
-  covariate.labels = c(
+  caption.above = T,
+  custom.model.names = c("Confidence in AZ Elections", "w/Interaction"),
+  custom.coef.names = c(
+    "(Intercept)",
     "Treatment",
@@
 
-The first model in \ref{tbl-legit} shows that overall confidence in elections (trust - distrust) among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
+:::
+
+::: {.content-visible when-format="aog-article-pdf" unless-format="bookup-html"}
+
+```{r}
+#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
+#| tbl-pos: H
+#| label: tbl-legit
+#| results: asis
+
+# All continuous variables are mean-centered and scaled by 1 standard deviation.
+m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = data)
+m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = data)
+
+texreg::texreg(
+  list(m1, m2),
+  single.row = T,
+  caption.above = T,
+  use.packages = F,
+  table = F, # Ensure this is set to FALSE so Quarto handles table cross-ref env
+  custom.model.names = c("Confidence in AZ Elections", "w/Interaction"),
+  custom.coef.names = c(
+    "(Intercept)",
+    "Treatment",
+    "Not Legitimate",
+    "Republican",
+    "Democrat",
+    "Not Legitimate * Treatment"
+    )
+)
+
+```
+
+:::
+
+The first model in Table \ref{tbl-legit} shows that overall confidence in elections among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
 Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
@@
 This shows that the treatment effect was most influential upon those who believe the 2020 election results were illegitimate.
-The treatment alone does not reverse such beliefs, but this shows where its influence is perhaps most potent.
+The treatment alone does not reverse such beliefs, but this shows where its influence was most potent.
 
@@
 
-### Limitations
+\newpage
 
-As far as I'm aware, both the items, their wording, and their composition into measurement scales are unique to this study.
-This renders the composite scores for trust in elections sample dependent and limits comparability with other cross-sectional survey data.
+# Appendix A: Survey Experiment Vignettes and Survey Items {.appendix}
 
--   limitations: interpretations of the treatment effect are limited.
-    *   The sample may not be generalizable to the population.
-    *   It's hard to say whether merely mentioning veterans is enough, as compared to explicitly naming veterans as the target of particular recruitment efforts.
--   Interpretation is also limited considering that no other particular group, or groups are compared directly against the veteran treatment vignette, i.e., additional vignettes for other comparable groups.
--   Results are limited by the survey questions, questionnaire design, and experimental stimulus (i.e., vignette) for two reasons: 
-    *  First, the vignettes and many survey questions ask about Maricopa County, AZ specifically.
-Adding a specific county in the vignette adds in a factor that cannot be accounted for without additional treatments that eliminate the setting as a potential influence.
-Moreover, the specificity of the setting adds in even more unexplained error---some people may have attitudes about the county in question, others won't, while others may be muffed to consider any random county in the U.S.
-they know nothing about.
-Adding the county undermines the confidence that treatment effects are solely attributable to veterans to an unknown degree.
-    *   Second, questions ask about one's own local community in addition to identical questions which asked about Maricopa County, AZ.
-Consequently, many questions within the questionnaire were duplicates with but one difference.
-This isn't uncommon in surveys, however in this case, it lengthened the survey to a degree that potentially resulted in a higher drop off rate.
-More importantly, the quality of responses were likely diminished to some unknown extent.
-Although it is possible to compare questions asked about Maricopa County, AZ to questions about one's local area, the quality of that comparison is limited by the unknown extent of fatigue induced by answering the same questions twice.
-It wasn't just that some questions were asked multiple times, almost all of the questions were duplicated.
-After completing a long series on Maricopa County, participants then answered the same questions about the local community.
-I haven't computed the rate to which participants dropped from the survey, yet items contain more missing values toward the end of the survey.
-Some participants dropped out, but some simply skipped a few items.
-The extent to which this occurred is minor, but it does suggest fatigue as a worthy of consideration.
-
-\pagebreak
-
-## Appendix A: Survey Experiment Vignettes and Survey Items {#sec-appendix-a}
+## Survey Experiment Vignettes
 
@@
 
-## Appendix B: Sample Demographics {#sec-appendix-b}
+## Survey Items
+
+```{r}
+#| label: tbl-4
+#| tbl-cap: "Survey Items and Response Options"
+
+data |> 
+  select(q6, q7, q25, q26) |> 
+  labelled::generate_dictionary() |> 
+  dplyr::as_tibble() |> 
+  mutate(value_labels = dplyr::case_when(
+    variable == 'q6' ~ "[Strongly unfavorable, Somewhat unfavorable, Neither, Somewhat favorable, Strongly favorable]",
+    variable == 'q7' ~ "Legitimate, Not legitimate",
+    variable == 'q25' ~ "Very concerned, Somewhat concerned, Not too concerned, Not at all concerned",
+    variable == 'q26' ~ "Not at all confident, Not too confident, Somewhat confident, Very confident"
+  )) |> 
+  select(Question = label, response = value_labels) |> 
+  kableExtra::kbl(booktabs = T, linesep = "\\addlinespace") |> 
+  kableExtra::kable_styling(full_width = T,
+                            font_size = 8,
+                            latex_options = c("HOLD_position")) |> 
+  kableExtra::column_spec(column = 1, width = "7cm") |> 
+  kableExtra::column_spec(column = 2, width = "4cm")
+
+```
+
+\newpage
+
+# Appendix B: Sample Demographics and Balance {.appendix}
+
+## Sample Demographics
 
@@
 # best method for html document
-tbl.desc <- df |>  
+tbl.desc <- data |>  
   labelled::set_variable_labels(
@@
 
-gtsummary::as_gt(tbl.desc) |>  
-  gt::tab_footnote(
-    footnote = "Independents do not identify nor 'lean' toward either political party",
-    placement = "left"
-    ) |>  
-  gt::cols_align(align = 'left', columns = everything()) |> 
-  gt::tab_options(
-    table.font.size = "small",
-    data_row.padding = gt::px(1)
-  )
+gtsummary::as_kable_extra(tbl.desc, booktabs = T) |>
+  kableExtra::add_footnote(
+    label = "Independents do not identify nor 'lean' toward either political party") |> 
+  kableExtra::kable_styling(
+    font_size = 9, 
+    protect_latex = T)
+
+# gtsummary::as_gt(tbl.desc) |>  
+#   gt::tab_footnote(
+#     footnote = "Independents do not identify nor 'lean' toward either political party",
+#     placement = "left"
+#     ) |>  
+#   gt::cols_align(align = 'left', columns = everything()) |> 
+#   gt::tab_options(
+#     table.font.size = "small",
+#     data_row.padding = gt::px(1)
+#   )
+
+```
+
+## Test of Random Assignment to Experiment Condition
+
+@tbl-logit shows results of a logistic regression test of random assignment to the treatment group.
+Demographics such as age, gender, race, educational attainment, and party ID are included as predictor variables.
+Note that 19 missing observations were deleted.
+A $\chi^2(15) = 11.010$, with 15 degrees of freedom and associated p-value > 0.05 ($p = 0.75$) confirms that none of the demographic predictor variables significantly increased the log-odds---in turn, the probability---of being assigned to the treatment group.
+
+```{r}
+#| label: tbl-logit
+#| tbl-cap: "Logistic Regression of Random Assignment to Treatment"
+
+# simple logit of test of random assignment to treatment
+# treatment is DV (treatment = 1, control = 0)
+# demographic variables are IVs
+
+data <- data |> 
+  mutate(group.dum = dplyr::case_when(
+    group == "Treatment" ~ 1,
+    group == "Control" ~ 0,
+    TRUE ~ NA), .after = group)
+
+m1 <- glm(group.dum ~ age_4cat + gender_3cat + race2 + educ_4cat + partyid_3cat, 
+          family = binomial(link = "logit"), data = data)
+
+# A Chi-square of 11.01 with 15 degrees of freedom and associated p-value > 0.05 (p-value = 0.752) confirms that none of the demographic predictor variables significantly increased the probability of being assigned to the treatment group.
+
+logit_tab <- gtsummary::tbl_regression(
+    m1, 
+    intercept = T,
+    label = list(
+      age_4cat ~"Age", 
+      gender_3cat ~ "Gender", 
+      race2 ~ "Race (includes Hispanic as race)",
+      educ_4cat ~ "Educational Attainment", 
+      partyid_3cat ~ "Party ID")) |> 
+  gtsummary::add_global_p(keep = T) |> 
+  gtsummary::add_nevent(location = c("label", "level")) |>
+  gtsummary::bold_p() |> 
+  gtsummary::bold_labels() |>
+  # gtsummary::show_header_names()
+  gtsummary::modify_header(
+    label = " ",
+    stat_nevent = "**Treatment N**") 
+# 
+#   gtsummary::modify_footnote_header(
+#     footnote = "Chi-Squared ($\\chi^2$) = 11.01, d.f. = 15, p = 0.75", columns = "p.value")
+
+gtsummary::as_kable_extra(logit_tab, 
+                          booktabs = T, 
+                          escape = F, 
+                          addtl_fmt = T) |> 
+  kableExtra::footnote("Chi-Squared = 11.01, d.f. = 15, p = 0.75", escape = F) |> 
+  kableExtra::kable_styling(font_size = 9)
 
@@
 
-## Appendix C: Trust and Distrust {#sec-appendix-c}
+# Appendix C: Polychoric Item and Score Correlations of Trust and Distrust {.appendix}
+
+## Trust and Distrust
 
@@
 # Get polychoric item correlation matrix.
-item.cor <- df |>
+item.cor <- data |>
   select(q19:q24, -q23, q28_1:q28_5, q30:q35, -q34, q40_1:q40_5) |> 
@@
 
-\pagebreak
+Although I do not explicitly assume that the survey instruments perfectly measure the hypothetical constructs of interest (i.e., trust and distrust), perfect measurement is implicitly assumed by the method of combining multiple item responses into a sum or mean composite score.
+
+In short, I expected item responses from the trust and distrust scales to be inversely correlated among the sample, but not mutually exclusive.
+Indeed, this is what I find.
+Polychoric correlations between the trust and distrust items negatively correlate as expected, as does the correlation between the two sum score scales.
+Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
+The negative correlation between the trust and distrust items and scores makes intuitive sense.
+
+\newpage
 
@@
 
-[^3]: Note that election insecurity is used in place of electoral confidence simply to emphasize the anticipatory nature of the attitudes in question.
-Election insecurity is taken to denote a lack of confidence.
+[^3]: The vignettes written were based on real news stories
 
-[^4]: Demographic breakdown of the sample are included in Appendix B.
+[^4]: To be clear, I conducted an auxiliary regression analysis to examine the relationship between legitimacy beliefs and partisanship.
+Results revealed a statistically significant relationship between the two variables and thus omitting either would result in biased estimates.
 
-[^5]: Complete text of treatment and control vignettes are included in the Appendix
+[^5]: Demographic breakdown of the sample are included in Appendix B.
 
-[^6]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
+[^6]: The article vignettes were written and designed by Michael Hanmer Ph.D and myself with input from We the Veterans, a non-profit organization
 
-[^7]: Survey item wording and responses are included in Appendix A.
+[^7]: Complete text of treatment and control vignettes are included in the Appendix
 
-[^8]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
+[^8]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
+
+[^9]: Survey item wording and responses are included in Appendix A.
+
+[^10]: See Appendix C for analysis.
+
+[^11]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
 The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024], yet there is no general consensus on the most appropriate method generally.

### 2025-03-13 notebooks/01-data-import-clean-process.qmd
reduced length. Moved content to appendices. Modified text. adjusted format. etc

@@
 
+# set seed for reproducibility
 set.seed(1234)
@@
 library(tidyverse)
+library(surveytoolbox)
+library(labelled)
+library(sjlabelled)
+library(pewmethods)
+library(fastDummies)
 
@@
 
+Note that the 'raw' data set here has been sanitized of respondent's potentially sensitive information.
+
 ```{r}
 #| label: load-data
-
-# load raw SPSS export (includes display order vars)
+#| echo: true
+
+# load SPSS export from Qualtrics (includes display order vars)
 # downloaded on 2024-10-29 at 12:02 PM
-raw_spss <- haven::read_sav("data-raw/vmf_election_worker_recruitment_survey_raw_spss_sanitized_20241029_T12.02.sav")
+raw_spss_sanitized <- haven::read_sav("vmf_election_worker_recruitment_survey_raw_spss_sanitized_20241029_T12.02.sav")
 
@@
 A data dictionary contains metadata about the data.
-The `labelled::generate_dictionary` function is used to create a data dictionary (alternatively, use the `data_dict()` function from R package [surveytoolbox](https://martinctc.github.io/surveytoolbox/)).
+The the `data_dict()` function from R package [surveytoolbox](https://martinctc.github.io/surveytoolbox/) is used to create a *data dictionary* (i.e., codebook).
+(alternatively, one can use the `generate_dictionary` from the [labelled](https://larmarange.github.io/labelled/) R package  to create a data dictionary with slightly different output.).
 This function produces a dataframe into the R environment with the number of observations (rows) equal to number of variables (columns) in the original data set.
 For ease, I prefer to save the codebook/data dictionary as a `.csv` file.
-In order to do so, ensure that the function `labelled::convert_list_columns_to_character()` is run on the data dictionary which allows you to save the data dictionary as a `.csv` file.
-Alternatively, the
-function `surveytoolbox::data_dict()` permits saving as a .csv file without the
-additional step.
 
@@
 # data dictionary from labelled package.
-raw_spss_dict <- raw_spss |> 
-  labelled::generate_dictionary() |> 
-  # this allows me to save dictionary as .csv file
-  labelled::convert_list_columns_to_character()
-
-# alternative
-# raw_spss_dict <- raw_spss |> surveytoolbox::data_dict()
-
-# save data dictionary of raw_spss dataset download
-write.csv(raw_spss_dict, file = "data/raw_spss_dict.csv")
-
-```
-
-The data dictionary is the same as a codebook, but I also wanted to have a codebook that contained **only** the survey questions, variable labels (i.e., question text), responses (value labels), and associated values.
-So the saved `codebook` contains only the survey questions and the two grouping variables (`qset` and `group`).
+raw_spss_sanitized_data_dict <- raw_spss_sanitized |> 
+  surveytoolbox::data_dict()
+
+```
+
+The data dictionary is the same as a codebook, but I also wanted to have a codebook that contained **only** the survey questions, variable labels (`var`, i.e., question text), responses (`label_var`, i.e., value labels), and associated values (simply, `value`).
+So the saved `codebook` contains only the survey questions and the two grouping variables `qset` and `group`.
+The latter refers to the Experiment condition where `1 = Treatment` and `0 = Control`.
+The other grouping variable `qset` refers to two distinct question sets (A or B) which aren't as important to cover at the moment.
+
+I run the code below to generate a codebook that contains only the survey question items (`var`), the question test (`label_var`), value labels (`label_val`) and corresponding numeric codes (`value`).
 
@@
 # text (label_var), the value labels (label_val), and the numeric codes (value)
-codebook <- raw_spss |> 
+codebook <- raw_spss_sanitized |> 
   janitor::clean_names() |> 
@@
   # Keep Qualtrics `response_id`
-  select(!1:8 & !10:17 & !265) |>
+  select(!1:7, !9:11, -q_data_policy_violations) |>
   # subset spss data set to omit the display order variables
@@
 
-# save codebook as .csv file in data/ directory
-write.csv(codebook, file = "data/survey_codebook.csv")
-
 ```
@@
 
-From the raw data set, there are `r dim(raw_spss)[1]` observations in the data set (each observation is a row). The survey was programmed in such a way to automatically drop participants who,
+From the raw data set, there are `r dim(raw_spss_sanitized)[1]` observations in the data set (each observation is a row).
+The survey was programmed in such a way to automatically drop participants who,
 
@@
 Although the survey was programmed in this way, however, any responses of these participants were still recorded and included in the data.
-Survey participants may not have been dropped from participating in the survey until after they had already entered in a few responses.
-For instance, a respondent failing both attention checks would not have been dropped from the survey until the tenth question (Q10) within the survey, but their responses prior to being dropped would still be included in a row within the data set.
+Survey participants may not have been dropped from participating in the survey until after they had already entered in a few responses, or at least responded to the first question requesting consent (Q1).
+Additionally, a respondent failing both attention checks would not have been dropped from the survey until the tenth question (Q10) within the survey, but their responses prior to being dropped would still be included in a row within the data set.
 This results in a lot of missing data (i.e., NA values) filling up observations (rows) in the data.

### 2025-03-13 notebooks/figures.qmd
reduced length. Moved content to appendices. Modified text. adjusted format. etc

---
title: "Figures"
execute:
  enabled: true
---

```{r}
#| label: packages
#| message: false

set.seed(1234)
library(tidyverse)
library(here)
library(patchwork)
library(pewmethods)
library(ggstats)

```

```{r}
#| label: data-import

# Load data
load(here::here('data', "research-paper-data-20241029.Rdata"))

# shorten and 'unify' factor levels
# Note: this removes variable labels
data <- data |>
  # use `pewmethods` to preserve order of factor levels
  mutate(across(c(q19, q20, q21, q22, q23, q24,
                  q30, q31, q32, q33, q34, q35),
                ~pewmethods::fct_case_when(
    .x %in% c("Not at all confident",
              "Not at all committed",
              "Not at all concerned") ~ "Not at all confident",
    .x %in% c("Not too confident",
              "Not too committed",
              "Not too concerned",
              "Somewhat unconcerned") ~ "Not too confident",
    .x %in% c("Somewhat confident",
              "Somewhat committed",
              "Somewhat concerned") ~ "Somewhat confident",
    .x %in% c("Very confident",
              "Very committed",
              "Very concerned") ~ "Very confident",
    TRUE ~ NA
  ))) |> 
  # unify factor levels
  mutate(across(c(q25, q36), ~ pewmethods::fct_case_when(
    .x == "Very concerned" ~ "Very concerned",
    .x == "Somewhat concerned" ~ "Somewhat concerned",
    .x %in% c("Not too concerned", "Somewhat unconcerned") ~ "Not too concerned",
    .x == "Not at all concerned" ~ "Not at all concerned",
    TRUE ~ NA))) |>
  # reverse factor levels
  mutate(across(c(q25, q36), ~forcats::fct_rev(.)))

```

```{r}
#| label: setup-theme

# set ggplot theme that will be used for every plot
# theme_get()
old <- ggplot2::theme_set(ggplot2::theme_bw())  # capture current theme

# set/update new theme
ggplot2::theme_set(
  new = ggplot2::theme_bw(
    base_family = 'TeX Gyre Pagella')+ # set font of ggplots
    theme(legend.position = 'bottom')  # set legend position for all plots
)

```

```{r}
#| label: custom-function

# custom function used to create Likert Plots

# To avoid excessive copy/paste, I made a function to create Likert plots
# it is mostly a wrapper around `ggstats::gglikert`, but with a specific set up
# particular colors, theme, etc. 
likert_plot <- function(data, x, ...,  
                        symmetric = FALSE,
                        variable_labels = NULL,
                        label_size = 2.5,
                        vline = FALSE,
                        title = waiver(), 
                        subtitle = waiver(),
                        caption = waiver(),
                        xlab = waiver()){

  p <- ggstats::gglikert(
    data = data, include = {{ x }}, ...,
    variable_labels = variable_labels,
    symmetric = symmetric)+

    # customize color
    ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
    # custom theme
    theme_bw(base_family = "TeX Gyre Pagella")+
    theme(
      legend.position = 'bottom',  # place legend on bottom
      axis.title.y.left = element_blank(), # blank out y-axis label
      axis.text.x = element_blank(), # remove percentage text along x-axis
      strip.text.y.right = element_text(angle = 0) # make facet label horizontal
        )

    if (vline==TRUE) {
    p <- p + geom_vline(xintercept = 0, color = 'black', linewidth = 1.2)
  } else {
      p
  }

  p <- p + ggplot2::labs(..., title = title, subtitle=subtitle, caption=caption, x = xlab)
  p

}

```

```{r}
#| eval: true
#| results: hide

# assign items to particular vectors to avoid copy/pasting
trust.az.items <- data |> select(q19, q20, q21, q22, q24) |> colnames() |> dput()
trust.lcl.items <- data |> select(q30, q31, q32, q33, q35)|> colnames() |> dput()
distrust.az.items <- data |> select(q28_1:q28_5)|> colnames() |> dput()
distrust.lcl.items <- data |> select(q40_1:q40_5)|> colnames() |> dput()

# variable labels for az and local area items, respectively
trust.az.varlabels <- c(
  q19 = "Votes counted as intended",
  q20 = "Election officials will do good job",
  q21 = "Election workers will be committed",
  q22 = "Voting process will be fair",
  q24 = "Election technology will be secure"
)

distrust.az.varlabels <- c(
  q28_1 = "Voter fraud will occur",
  q28_2 = "Many votes won't be counted",
  q28_3 = "Many voters will be turned away",
  q28_4 = "Foreign Interference",
  q28_5 = "Election officials will discourage voting"
)

trust.lcl.varlabels <- c(
  q30 = "Votes counted as intended",
  q31 = "Election officials will do good job",
  q32 = "Election workers will be committed",
  q33 = "Voting process will be fair",
  q35 = "Election technology will be secure"
)

distrust.lcl.varlabels <- c(
  q40_1 = "Voter fraud will occur",
  q40_2 = "Many Votes won't be counted",
  q40_3 = "Many voters will be turned away",
  q40_4 = "Foreign Interference",
  q40_5 = "Election officials will discourage voting"
)

```

## Trust in Elections across sample

```{r}
#| label: fig-p1
#| fig-cap: "Trust in Maricopa County, AZ, Elections"

# plot of trust in elections

# plot of trust in AZ elections 
trust.likertplot.az <- data |> likert_plot(
  x = all_of(trust.az.items),
  variable_labels = trust.az.varlabels,
  title = "Trust in Maricopa County, AZ, Elections"
)

trust.likertplot.az

```

```{r}
#| label: fig-p2
#| fig-cap: "Trust in Local Area Elections"

# plot of trust in Local Area elections 
trust.likertplot.lcl <- likert_plot(
  data = data, 
  x = all_of(trust.lcl.items),
  variable_labels = trust.lcl.varlabels,
  title = "Trust in Local Area Elections")

trust.likertplot.lcl

```

```{r}
#| label: fig-patch1
#| fig-cap: "Trust in Elections"

# Instead of two separate plots, arrange into one plot while remaining separated
p1.trust <- trust.likertplot.az / trust.likertplot.lcl+
  patchwork::plot_annotation(caption = "Missing values omitted")+
  patchwork::plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

p1.trust

```

## Distrust in elections across sample

```{r}
#| label: fig-p3
#| fig-cap: "Distrust in Maricopa County, AZ Elections"

# responses to distrust in AZ election items, overall sample
distrust.likert.az <- likert_plot(
  data, 
  x = all_of(distrust.az.items), 
  variable_labels = distrust.az.varlabels,
  title = "Distrust in Maricopa County, AZ Elections", 
  subtitle = str_wrap(
    "How likely do you think any or all of the following will happen during this year´s elections in Maricopa County, AZ?",width = 95))

distrust.likert.az

```

```{r}
#| label: fig-p4
#| fig-cap: "Distrust in Local Area Elections"

# responses to distrust in local election items, overall sample
distrust.likert.lcl <- likert_plot(
  data,
  x = all_of(distrust.lcl.items),
  variable_labels = distrust.lcl.varlabels,
  title = "Distrust in Local Area Elections",
  subtitle = str_wrap(
    "How likely do you think any or all of the following will happen during this year´s elections in your local area?",
    width = 95
  )
)

distrust.likert.lcl

```

```{r}
#| label: fig-patch2
#| fig-cap: "Distrust in Elections"

p2.distrust <- distrust.likert.az/distrust.likert.lcl+
  patchwork::plot_annotation(caption = "Missing values omitted")+
  patchwork::plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

p2.distrust

```

## Concerns for Violence and Confidence in Voter Safety Across Sample

```{r}
#| label: fig-p5

# plot of safety concerns and confidence ::::::::::::::::::::::::::::

safety.concerns.likert <- likert_plot(
  data, x = c(q25, q36), 
  y_label_wrap = 15, 
  variable_labels = c(
    q25 = 'Thinking about Maricopa County, AZ',
    q36 = "Thinking about Local Area"), 
  title = "Concern for Voter Intimidation, Threats, or Violence",
  subtitle = str_wrap(
    "How concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place?", width = 99))

safety.concerns.likert

```

```{r}
#| label: fig-p6

# q26 In-person voter safety at polling sites
safety.conf.likert <- likert_plot(
  data,
  x = c(q26, q37),
  y_label_wrap = 15,
  variable_labels = c(q26 = "In Maricopa County, AZ", q37 = "In your local area"),
  title = str_wrap("Confidence for In-person voter safety at Polling Sites", width = 95),
  subtitle = str_wrap(
    "How confident, if at all, are you that in person polling places will be safe places for voters to cast their ballots during the upcoming elections in November?",
    width = 95
  )
)

safety.conf.likert

```

```{r}
#| label: fig-patch3

p3.safety <- safety.concerns.likert/safety.conf.likert+
  patchwork::plot_annotation(caption = "Missing values omitted")+
  patchwork::plot_layout(guides = "keep") &
  theme(legend.position = "bottom")

```

## Trust and Distrust by Education, Gender, and Partisanship

```{r}
#| label: fig-p7

# plots of trust in AZ elections by educational attainment :::::::::: 
trust.az.educ.likert <- data |>   
  filter(!is.na(educ_4cat)) |> 
  mutate(
    educ_3cat = pewmethods::fct_case_when(
      educ_4cat %in% c("H.S. or less") ~ "H.S. or less",
      educ_4cat %in% c("Some college no degree") ~ "Some college no Degree",
      educ_4cat %in% c("Postgraduate degree", "College degree") ~ "College Graduate")
    ) |>  
  likert_plot(x = all_of(trust.az.items), y = 'educ_3cat', facet_rows = vars(.question),
              facet_label_wrap = 15,
              variable_labels = trust.az.varlabels,
              subtitle = "Maricopa County, AZ")
```

```{r}
#| label: fig-p8

# plots of trust in Local area elections by educational attainment :: 
trust.lcl.educ.likert <- data |>  
  filter(!is.na(educ_4cat)) |>  
  mutate(
    educ_3cat = pewmethods::fct_case_when(
      educ_4cat %in% c("H.S. or less") ~ "H.S. or less",
      educ_4cat %in% c("Some college no degree") ~ "Some college no Degree",
      educ_4cat %in% c("Postgraduate degree", "College degree") ~ "College Graduate")
    ) |>  
  likert_plot(
    x = all_of(trust.lcl.items), y = 'educ_3cat', facet_rows = vars(.question),
    facet_label_wrap = 15, variable_labels = trust.lcl.varlabels,
    subtitle = "Local Area"
  )
```

```{r}
#| label: fig-patch4

p4.trust.az.educ <- trust.az.educ.likert + trust.lcl.educ.likert + 
    patchwork::plot_layout(guides = "collect") &
    theme(legend.position = "bottom")

```

```{r}
#| label: fig-p9

# plot of distrust in AZ elections by educational attainment :::::::: 
distrust.az.educ.likert <- data |> 
  filter(!is.na(educ_4cat)) |> 
  mutate(
    educ_3cat = pewmethods::fct_case_when(
      educ_4cat %in% c("H.S. or less") ~ "H.S. or less",
      educ_4cat %in% c("Some college no degree") ~ "Some college no Degree",
      educ_4cat %in% c("Postgraduate degree", "College degree") ~ "College Graduate")
    ) |>  
  likert_plot(x = all_of(distrust.az.items), y = 'educ_3cat', facet_rows=vars(.question),
              facet_label_wrap = 15, variable_labels = distrust.az.varlabels,
              subtitle = "Maricopa County, AZ")
```

```{r}
#| label: fig-p10

# plot of distrust items by educational attainment
distrust.lcl.educ.likert <- data |> 
  filter(!is.na(educ_4cat)) |> 
  mutate(
    educ_3cat = pewmethods::fct_case_when(
      educ_4cat %in% c("H.S. or less") ~ "H.S. or less",
      educ_4cat %in% c("Some college no degree") ~ "Some college no Degree",
      educ_4cat %in% c("Postgraduate degree", "College degree") ~ "College Graduate")
    ) |>   
  likert_plot(
    x = all_of(distrust.lcl.items), y = 'educ_3cat', facet_rows = vars(.question),
    facet_label_wrap = 15, variable_labels = distrust.lcl.varlabels,
    subtitle = "Local Area"
  )

```

```{r}
#| label: fig-patch5

p5.distrust.az.educ <- distrust.az.educ.likert + distrust.lcl.educ.likert +
    patchwork::plot_layout(guides = "collect") & 
    theme(legend.position = "bottom")

p5.distrust.az.educ

```

```{r}
#| label: fig-p11

# plots of trust and distrust in AZ elections by gender ::::::::::::: 
trust.az.gender.likert <- data |>  
  filter(!is.na(gender_3cat), gender_3cat != 'Other/Refused') |> 
  likert_plot(
    x = all_of(trust.az.items), y = 'gender_3cat', facet_rows = vars(.question),
    facet_label_wrap = 15, variable_labels = trust.az.varlabels,
    subtitle = "Maricopa County, AZ Elections"
  )
```

```{r}
#| label: fig-p12

# plots of distrust in AZ elections by gender ::::::::::::: 
distrust.az.gender.likert <- data |> 
  filter(!is.na(gender_3cat), gender_3cat != 'Other/Refused') |>
  likert_plot(
    x = all_of(distrust.az.items), y = 'gender_3cat', facet_rows = vars(.question),
    facet_label_wrap = 15, variable_labels = distrust.az.varlabels,
    subtitle = "Maricopa County, AZ Elections"
  )
```

```{r}
#| label: fig-patch6

p6.trust.az.gender <- trust.az.gender.likert / distrust.az.gender.likert +
  patchwork::plot_annotation(
    caption = str_wrap(
      "Gender Non-binary (n=7) and those who preferred not to say (n=9) response categories omitted for lack of observations. Missing values omitted (n=15)",
      width = 150
    ),
    theme = theme(text = element_text(family = "Palatino Linotype"))
  ) +
  patchwork::plot_layout(guides = 'keep') &
  theme(legend.position = "bottom")

p6.trust.az.gender

```

```{r}
#| label: fig-p13

# plot of trust in local area elections by gender
trust.lcl.gender.likert <- data |>  
  filter(!is.na(gender_3cat), gender_3cat != 'Other/Refused') |> 
  likert_plot(
    x = all_of(trust.lcl.items), y = 'gender_3cat',
    facet_rows = vars(.question),
    facet_label_wrap = 15, variable_labels = trust.lcl.varlabels,
    subtitle = "Local Area Elections"
  )
```

```{r}
#| label: fig-p14

# plot of distrust in local area elections by gender
distrust.lcl.gender.likert <- data |> 
  filter(!is.na(gender_3cat), gender_3cat != 'Other/Refused') |> 
  likert_plot(
    x = all_of(distrust.lcl.items), y = 'gender_3cat',
    facet_rows = vars(.question),
    facet_label_wrap = 15, variable_labels = distrust.lcl.varlabels,
    subtitle = "Local Area Elections"
  )
```

```{r}
#| label: fig-patch7

p7.trust.lcl.gender <- trust.lcl.gender.likert/distrust.lcl.gender.likert+
  patchwork::plot_annotation(
    caption = str_wrap("Gender Non-binary (n=7) and those who preferred not to say (n=9) response categories omitted for lack of observations. Missing values omitted (n=15)",
                       width = 150), 
    theme = theme(text = element_text(family = "Palatino Linotype")))+
    patchwork::plot_layout(guides = 'keep') & 
    theme(legend.position = "bottom")
```

```{r}
#| label: fig-p15

# plot of trust in AZ elections by partisanship ::::::: 
trust.az.party.likert <- data |>  
  filter(!is.na(partyid_3cat)) |> 
  likert_plot(
    x = all_of(trust.az.items), y = 'partyid_3cat',
    facet_rows = vars(.question), 
    facet_label_wrap = 15,
    variable_labels = trust.az.varlabels,
    subtitle = "Maricopa County, AZ Elections"
  )
```

```{r}
#| label: fig-p16

# plot of distrust in AZ elections by partisanship ::::::: 
distrust.az.party.likert <- data |> 
  filter(!is.na(partyid_3cat)) |> 
  likert_plot(
    x = all_of(distrust.az.items), y = 'partyid_3cat',
    facet_rows = vars(.question), 
    facet_label_wrap = 15,
    variable_labels = distrust.az.varlabels,
    subtitle = "Maricopa County, AZ Elections"
  )
```

```{r}
#| label: fig-patch8

p8.trust.az.party <- trust.az.party.likert/distrust.az.party.likert+
    patchwork::plot_layout(guides = 'keep') & 
    theme(legend.position = "bottom")

p8.trust.az.party

```

```{r}
#| label: fig-p17

# plot of trust and distrust in local area elections by partisanship  
trust.lcl.party.likert <- data |>  
  filter(!is.na(partyid_3cat)) |> 
  likert_plot(
    x = all_of(trust.lcl.items), y = 'partyid_3cat',
    facet_rows = vars(.question), 
    facet_label_wrap = 15,
    variable_labels = trust.lcl.varlabels,
    subtitle = "Local Area Elections"
  )
```

```{r}
#| label: fig-p18

# plot of distrust in local area elections by partisanship  
distrust.lcl.party.likert <- data |> 
  filter(!is.na(partyid_3cat)) |>  
  likert_plot(
    x = all_of(distrust.lcl.items), y = 'partyid_3cat',
    facet_rows = vars(.question), 
    facet_label_wrap = 15,
    variable_labels = distrust.lcl.varlabels,
    subtitle = "Local Area Elections"
  )
```

```{r}
#| label: fig-patch9

p9.trust.lcl.party <- trust.lcl.party.likert/distrust.lcl.party.likert+
    patchwork::plot_layout(guides = 'keep') & 
    theme(legend.position = "bottom")

p9.trust.lcl.party

```

## Trust and Distrust by Treatment Condition

```{r}
#| label: fig-p19

# plot of trust in AZ elections by treatment condition
trust.likert.treat.az <- data |>
  likert_plot(x = all_of(trust.az.items), y = 'group', 
    facet_rows = vars(.question),
    subtitle = "Maricopa County, Arizona")+
  theme(strip.text.y.right = element_blank())

trust.likert.treat.az

```

```{r}
#| label: fig-p20

# plot of trust in local elections by treatment condition
trust.likert.treat.lcl <- data |>
  likert_plot(x = all_of(trust.lcl.items), y = 'group', 
    facet_rows = vars(.question),
    facet_label_wrap = 10,
    variable_labels = trust.lcl.varlabels, 
    subtitle = "Local Area")+
  theme(strip.text.y.right = element_blank()) +
  theme(
    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
    strip.text.y.right = element_text(angle = 0, size = 8)
  )

trust.likert.treat.lcl

```

```{r}
#| label: fig-patch10
#| fig-cap: "Trust in Election Administration by Experiment Condition"
#| fig-height: 4.5
#| fig-pos: "h"

p10.trust.treat <- trust.likert.treat.az + trust.likert.treat.lcl+
  patchwork::plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

p10.trust.treat

```

```{r}
#| label: fig-p21

# distrust in AZ elections by experimental condition
distrust.az.treat.likert <- data |>
  likert_plot(x = all_of(distrust.az.items), y = 'group', 
    facet_rows = vars(.question),
    subtitle = "Maricopa County, AZ")+
  theme(strip.text.y.right = element_blank())
```

```{r}
#| label: fig-p22

# distrust in local area elections by treatment condition
distrust.lcl.treat.likert <- data |>
  likert_plot(x = all_of(distrust.lcl.items), y = 'group', 
    facet_rows = vars(.question),
    facet_label_wrap = 10,
    variable_labels = distrust.lcl.varlabels,
    subtitle = "Local Area")+
  theme(strip.text.y.right = element_blank()) +
  theme(
    axis.text.y.left = element_blank(), # remove y-axis text on 2nd plot
    strip.text.y.right = element_text(angle = 0, size = 8)
  )
```

```{r}
#| label: fig-patch11
#| fig-cap: "Disrust in Election Administration by Experiment Condition"
#| fig-height: 4.5
#| fig-width: 8
#| fig-pos: "H"

p11.distrust.treat <- distrust.az.treat.likert + distrust.lcl.treat.likert+
  patchwork::plot_layout(guides = 'collect')

p11.distrust.treat

```

## trust and distrust by partisanship and treatment

```{r}
#| label: fig-p23

# plots of trust and distrust by partisanship and treatment :::::::::

# plot of trust in AZ elections by experiment condition and party id
trust.az.treat.partyid <- data |> 
  filter(!is.na(partyid_3cat)) |>
  likert_plot(
    x = all_of(trust.az.items),
    y = 'partyid_3cat',
    facet_rows = vars(.question),
    facet_cols = vars(group),
    facet_label_wrap = 15,
    variable_labels = trust.az.varlabels,
    title = "Trust in Maricopa County, AZ Elections by Treatment and Partisanship")
```

```{r}
#| label: fig-p24

# plot of trust in local elections by experiment condition and party id
trust.lcl.treat.partyid <- data |> 
  filter(!is.na(partyid_3cat)) |>
  likert_plot(
    x = all_of(trust.lcl.items),
    y = 'partyid_3cat',
    facet_rows = vars(.question),
    facet_cols = vars(group),
    facet_label_wrap = 15,
    variable_labels = trust.lcl.varlabels,
    title = "Trust in Local Area Elections by Treatment and Partisanship")
```

```{r}
#| label: fig-patch12

p12.trust.treat.partyid <- trust.az.treat.partyid / trust.lcl.treat.partyid+
  patchwork::plot_layout(guides = 'collect')

p12.trust.treat.partyid

```

## Trust and Distrust by Legitimacy beliefs and Treatment Condition

```{r}
#| label: fig-p25

# plots of trust and distrust by legitimacy and treatment :::::::::::

# trust in AZ elections by experiment conditions among those who believe the 2020
# election results were illegitimate
trust.az.treat.legit <- data |> 
  filter(!is.na(partyid_3cat), !is.na(q7)) |>
  filter(q7 == "Not legitimate") |> 
  likert_plot(
    x = all_of(trust.az.items), 
    y = 'group',
    facet_rows = vars(.question),
    facet_cols = vars(q7),
    facet_label_wrap = 15,
    variable_labels = trust.az.varlabels,
    subtitle = str_wrap("Maricopa County, AZ",
      width = 95) 
  )+
  theme(text = element_text(family = 'TeX Gyre Pagella'),
        strip.text.y.right = element_blank())
```

```{r}
#| label: fig-p26

# trust in local elections by experiment conditions among those who believe the
# 2020 election results were illegitimate
trust.lcl.treat.legit <- data |> 
  filter(!is.na(partyid_3cat), !is.na(q7)) |>
  filter(q7 == "Not legitimate") |> 
  likert_plot(
    x = all_of(trust.lcl.items), 
    y = 'group',
    facet_rows = vars(.question),
    facet_cols = vars(q7),
    facet_label_wrap = 15,
    variable_labels = trust.lcl.varlabels,
    subtitle = str_wrap("Local Area",
      width = 95) 
  )+
  theme(
    text = element_text(family = 'TeX Gyre Pagella'),
    axis.text.y.left = element_blank())
```

```{r}
#| label: fig-patch13
#| fig-cap: "Trust in elections by treatment among those who refute the 2020 election results"
#| fig-height: 4.5
#| fig-width: 8

p13.trust.treat.legit <- trust.az.treat.legit + trust.lcl.treat.legit+
  patchwork::plot_layout(guides = 'collect')

p13.trust.treat.legit

```

```{r}
#| label: fig-p27

# distrust in AZ elections by experiment conditions among those who believe the
# 2020 election results were illegitimate
distrust.az.treat.legit <- data |> 
  filter(!is.na(partyid_3cat), !is.na(q7)) |>
  filter(q7 == "Not legitimate") |> 
  likert_plot(
    x = all_of(distrust.az.items), 
    y = 'group',
    facet_rows = vars(.question),
    facet_cols = vars(q7),
    facet_label_wrap = 15,
    variable_labels = distrust.az.varlabels,
    subtitle = str_wrap("Maricopa County, AZ",
      width = 95) 
  )+
  theme(
    text = element_text(family = 'TeX Gyre Pagella'),
    strip.text.y.right = element_blank())

```

```{r}
#| label: fig-p28

# distrust in local elections by experiment conditions among those who believe
# the 2020 election results were illegitimate
distrust.lcl.treat.legit <- data |> 
  filter(!is.na(partyid_3cat), !is.na(q7)) |>
  filter(q7 == "Not legitimate") |> 
  likert_plot(
    x = all_of(distrust.lcl.items), 
    y = 'group',
    facet_rows = vars(.question),
    facet_cols = vars(q7),
    facet_label_wrap = 15,
    variable_labels = distrust.lcl.varlabels,
    subtitle = str_wrap("Local Area",
      width = 95) 
  )+
  theme(
    text = element_text(family = 'TeX Gyre Pagella'),
    axis.text.y.left = element_blank())

```

```{r}
#| label: fig-patch14
#| fig-cap: "Distrust in elections by treatment among those who refute the 2020 election results"
#| fig-height: 4.5
#| fig-width: 8

p14.distrust.treat.legit <- distrust.az.treat.legit + distrust.lcl.treat.legit+
  patchwork::plot_layout(guides = 'collect')

p14.distrust.treat.legit

```

## Concerns for Violence and Confidence in Voter Safety by Treatment

```{r}
#| label: fig-p29

# plot for safety concerns by treatment :::::::::::::::::::::::::::::

# Because q25 measures levels of concern/worry, it cannot be included in the
# same Likert plot as q26 as that measures reported confidence that voters will
# be safe to vote in-person

# safety concerns by treatment
safety.concern.treat.likert <- data |>
  # Need to slightly modify text of factor levels
  mutate(across(
    c(q25, q36),
    ~ pewmethods::fct_case_when(
      .x == "Very concerned" ~ "Very concerned",
      .x == "Somewhat concerned" ~ "Somewhat concerned",
      .x %in% c("Not too concerned", "Somewhat unconcerned") ~ "Not too concerned",
      .x == "Not at all concerned" ~ "Not at all concerned",
      TRUE ~ NA
    )
  )) |>
  likert_plot(
    x = c(q25, q36),
    y = 'group',
    facet_rows = vars(.question),
    facet_label_wrap = 15,
    variable_labels = c(q25 = 'Thinking about Maricopa County, AZ', q36 = "Thinking about Local Area"),
    title = "Concern for Voter Intimidation, Threats, or Violence by Treatment Condition",
    subtitle = str_wrap(
      "How concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place?",
      width = 99
    )
  )
```

```{r}
#| label: fig-p30

# q26 In-person voter safety at election sites by treatment
safety.conf.treat.likert <- data |>
  likert_plot(
    x = c(q26, q37), 
    y = 'group',
    facet_label_wrap = 15,
    facet_rows = vars(.question),
    variable_labels = c(
      q26 = "In Maricopa County, AZ",
      q37 = "In your local area"
    ),
    title = str_wrap("Confidence for In-person voter safety at Polling Sites by Treatment", width = 95),
    subtitle = str_wrap("How confident, if at all, are you that in person polling places will be safe places for voters to cast their ballots during the upcoming elections in November?", width = 95)
  )

```

```{r}
#| label: fig-patch15

p15.safety.treat <- safety.concern.treat.likert/safety.conf.treat.likert+
  patchwork::plot_layout(guides = "keep")

```

## Distribution of Confidence in Elections

```{r}
#| label: fig-dist
#| fig-cap: "Overlapping Distribution of Confidence in Elections for AZ and Local Area"
#| fig-pos: "H"

ggplot(data) +
  geom_histogram(
    aes(x = conf.az.rescaled , y = after_stat(density)),
    bins = 15,
    alpha = 0.2,
    color = 1,
    fill = "red"
  ) +
  geom_histogram(
    aes(x = conf.lcl.rescaled , y = after_stat(density)),
    bins = 15,
    alpha = 0.2,
    color = 1,
    fill = "blue"
  ) +
  geom_segment(
    x = round(mean(data$conf.az.rescaled), 2),
    y = 0,
    yend = 0.35,
    color = "firebrick",
    lwd = 1.4,
    linetype = 2
  ) +
  geom_segment(
    x = round(mean(data$conf.lcl.rescaled), 2),
    y = 0,
    yend = 0.35,
    color = "darkblue",
    lwd = 1.4,
    linetype = 2
  ) +
  annotate(
    "text",
    x = round(mean(data$conf.az.rescaled), 2),
    y = 0.40,
    label = paste("AZ =", round(mean(
      data$conf.az.rescaled
    ), 2), "(", round(sd(
      data$conf.az.rescaled
    ), 2), ")"),
    color = "firebrick"
  ) +
  annotate(
    "text",
    x = round(mean(data$conf.lcl.rescaled), 2),
    y = 0.43,
    label = paste("Local area =", round(mean(
      data$conf.lcl.rescaled
    ), 2), "(", round(sd(
      data$conf.lcl.rescaled
    ), 2), ")"),
    color = "darkblue"
  ) +
  labs(
    x = str_wrap("Confidence", width = 85),
    y = "Density",
    caption = str_wrap(
     "Mean (std.dev). Mean difference = 0.33, CI [0.27, 0.38], t = 11.613, data = 1286, p < 0.01",
     width = 95)) +
  theme_bw(base_family = "TeX Gyre Pagella")

```

## Coefficient Plot of Treatment on Confidence by Location

```{r}
#| label: fig-coef1
#| layout-nrow: 2
#| fig-height: 3.5
#| fig-pos: 'H'
#| fig-cap: "Confidence in Elections by Experiment Condition"
#| fig-subcap: 
#|   - "Confidence by Treatment Condition"
#|   - "Trust and Distrust by Treatment Condition"

# coef plot of treatment effect on confidence distinguished by location
conf.coef1 <- jtools::plot_summs(
  lm(conf.az.rescaled ~ group, data = data), 
  lm(conf.lcl.rescaled ~ group, data = data), 
  center = T, scale = T, transform.response = T,
  model.names = c("Conf.AZ", "Conf.Local"),
  coefs = c("Treatment" = "groupTreatment"), 
  colors = c("red", "black"),
  point.shape = c(8, 1))+
  ggplot2::expand_limits(x = c(-0.25, 0.25))+
  labs(y = "")+
  theme_bw(base_family = "TeX Gyre Pagella")

# Coef plots of trust and distrust models for AZ and Local items
conf.coef2 <- jtools::plot_summs(
  lm(trust.scores.az ~ group, data = data),
  lm(distrust.scores.az ~ group, data = data),
  lm(trust.scores.lcl ~ group, data = data),
  lm(distrust.scores.lcl ~ group, data = data),
  center = T, scale = T, transform.response = T,
  model.names = c("Trust.AZ", "Distrust.AZ", "Trust.Local", "Distrust.Local"),
  coefs = c("Treatment" = "groupTreatment"),
  colors = c("red", "red", "black", "black"),
  point.shape = c(8, 8, 1, 1)
)+
  ggplot2::expand_limits(x = c(-0.25, 0.25))+
  labs(y = "")+
  theme_bw(base_family = "TeX Gyre Pagella")

conf.coef1
conf.coef2

```

## Polychoric Item Correlation Plot

```{r}
#| label: fig-polycor
#| fig-cap: "Polychoric Item Correlation Matrix"
#| fig-pos: 'h'

# Get polychoric item correlation matrix.
item.cor <- data |>
  select(q19:q24, -q23, q28_1:q28_5, q30:q35, -q34, q40_1:q40_5) |> 
  # ensure factors are ordered factors
  mutate(across(where(is.factor), ~factor(., ordered = T))) |> 
  # adjust variable column names of items
  dplyr::rename(
    trustvote_az     = q19,
    trustadmin_az    = q20,
    truststaff_az    = q21,
    trustprcss_az    = q22,
    trusttech_az     = q24,
    votefraud_az     = q28_1,
    miscount_az      = q28_2,
    turnedaway_az    = q28_3,
    foreigntamp_az   = q28_4,
    discourage_az    = q28_5,
    trustvote_lcl    = q30,
    trustadmin_lcl   = q31,
    truststaff_lcl   = q32,
    trustprcss_lcl   = q33,
    trusttech_lcl    = q35,
    votefraud_lcl    = q40_1,
    miscount_lcl     = q40_2,
    turnedaway_lcl   = q40_3,
    foreigntamp_lcl  = q40_4,
    discourage_lcl   = q40_5
  ) |> 
  correlation::correlation(
    select = 
      c("trustvote_az", "trustadmin_az", "truststaff_az", "trustprcss_az", "trusttech_az",
        "votefraud_az", "miscount_az", "turnedaway_az", "foreigntamp_az", "discourage_az"),
    select2 =
      c("trustvote_lcl", "trustadmin_lcl", "truststaff_lcl", "trustprcss_lcl","trusttech_lcl",
        "votefraud_lcl", "miscount_lcl", "turnedaway_lcl", "foreigntamp_lcl","discourage_lcl"),
    method = "polychoric") |>
  summary()

# plot item correlations
plot(item.cor) + theme(axis.text.x = element_text(angle = 45, vjust = 0.6))

```

### 2025-03-13 docs/src/01-data-clean-process.R

@@ -1,0 +1,1106 @@
+# load, clean, and process data imported from Qualtrics
+# using data exported from Qualtrics on 2024-10-29 at 12:02 PM
+
+
+# load packages ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
+library(tidyverse)
+library(haven)
+library(surveytoolbox)
+library(labelled)
+library(sjlabelled)
+
+
+# load data ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
+
+# load raw SPSS export (includes display order vars)
+# downloaded on 2024-10-29 at 12:02 PM
+raw_spss <- haven::read_sav("data-raw/VMF_Election_Worker_Recruitment_Survey_with_display_order_20241029_T12.02.sav")
+
+# sanitize data downloaded from Qualtrics (i.e., remove PII) :::::::::::::::####
+
+# rename select variables. Identify Lucid embedded variable columns
+raw_spss_sanitized <- raw_spss |> 
+  # select and remove sensitive PII variables (e.g., IPAddress, Location)
+  dplyr::select(
+    -IPAddress,
+    -LocationLatitude,
+    -LocationLongitude,
+    -RecipientFirstName,
+    -RecipientLastName,
+    -RecipientEmail
+    )
+
+# create and save survey codebook ::::::::::::::::::::::::::::::::::::::::::####
+
+# this includes only the survey questions: question number (var), the question
+# text (label_var), the value labels (label_val), and the numeric codes (value)
+codebook <- raw_spss_sanitized |> 
+  janitor::clean_names() |> 
+  # get rid of superfluous Qualtrics columns
+  # Keep Qualtrics `response_id`
+  select(!1:7, !9:11, -q_data_policy_violations) |>
+  # subset spss data set to omit the display order variables
+  select(!contains("_do_")
+         & !contains("_ado_")
+         & !contains("_click")
+         & !contains("_count")) |>
+  select(contains("q"), group) |>
+  surveytoolbox::data_dict()
+
+# create data dictionary of sanitized raw SPSS data set ::::::::::::::::::::####
+
+# create data dictionary (I prefer output from surveytoolbox)
+raw_spss_sanitized_data_dict <- raw_spss_sanitized |> 
+  surveytoolbox::data_dict()
+
+
+
+# clean up data set ::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
+
[…]

### 2025-03-13 src/funs.R

@@ -110,7 +110,7 @@ run_crab <- function(data, row, col){
 likert_plot <- function(data, x, ...,  
                         symmetric = FALSE,
                         variable_labels = NULL,
-                        label_size = 3.0,
+                        label_size = 2.7,
                         vline = FALSE,
                         title = waiver(), 
                         subtitle = waiver(),

### 2025-03-19 docs/_tex/index.tex
draft 3 complete. Also full project render

@@
 % ---------------------------
+\usepackage{float}
+\usepackage{tabularray}
+\usepackage[normalem]{ulem}
+\usepackage{graphicx}
+\usepackage{rotating}
+\UseTblrLibrary{booktabs}
+\UseTblrLibrary{siunitx}
+\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
+\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
+\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
 \usepackage{booktabs}
@@
 \usepackage{wrapfig}
-\usepackage{float}
 \usepackage{colortbl}
@@
 \hypersetup{
-  pdftitle={title},
+  pdftitle={Inspiring Confidence and Easing Insecurity in the Pre-election period: The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections},
   colorlinks=true,
@@
 
-\title{title}
+\title{Inspiring Confidence and Easing Insecurity in the Pre-election
+period: The Effect of Recruiting Military Veterans on Confidence in 2024
+US Elections}
 % subtitles do not seem to work with article class?
-%%\usepackage{etoolbox}
-%\makeatletter
-%\providecommand{\subtitle}[1]{% add subtitle to \maketitle
-%  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
-%}
-%\makeatother
-%%\subtitle{subtitle}
+%%\subtitle{}
 
@@
 % add the short title to the fancy header
-\fancyhead[R]{A Short title}
+\fancyhead[R]{Effect of Recruiting Military Veterans on Confidence in
+2024 US Elections}
 \fancyhead[L]{Isaiah}
@@
 \setstretch{1.25}
-\pagebreak
+\newpage{}
 
@@
 developed among election staff and voters in more recent elections.
-Regular measures are taken to enhance the
-\emph{trustworthiness}\footnote{I adopt a distinction made between
+Regular measures are taken to enhance the \emph{trustworthiness} of the
+electoral process through practices meant to improve the conduct,
+transparency, or overall administration of elections in the United
+States.
+
+Although election officials undertake great efforts to enhance the
+\emph{trustworthiness} of election administration, public
+\emph{trust}\footnote{I adopt a distinction made between
   \emph{trustworthiness} and \emph{trust} in elections
@@
   every reason to deem it \emph{worthy of my trust}. However, I don't
-  trust my car because I am sure it is haunted.} of the electoral
-process through practices meant to improve the conduct, transparency, or
-overall administration of elections in the United States.
-
-Although election officials undertake great efforts to enhance the
-trustworthiness of election administration, public \emph{trust} in
-elections is a psychological construct influenced by many things outside
-of election official control such as partisanship or elite rhetoric
+  trust my car because I am sure it is haunted.} in elections is a
+psychological construct influenced by many things outside of election
+official control such as partisanship or elite rhetoric
 (\citeproc{ref-hooghe2018}{Hooghe 2018};
@@
 that public trust in elections is, at best, only partial to
-trustworthiness of election administration in the United
-States\footnote{There's little that could justify a conceptual
-  distinction between public trust pre-election and public trust
-  post-election. The temporal element renders the difference between
-  pre- and post-election more operative than conceptual at a
-  foundational level.}.
+trustworthiness of election administration in the United States.
 
@@
 
-Since the results and events following the 2020 election loomed large in
-anticipation of the U.S. 2024 general elections, it is reasonable to
-take into account beliefs about legitimacy of the 2020 election. This
-group who denies the legitimacy of the 2020 election results were
-possibly the most apprehensive (distrusting) of the 2024 election.
-However, given that veteran service members are held in high regard,
-generally speaking, announcing that veterans are being actively
-recruited to work as election staff and volunteers is expected to
-positively influence confidence in elections among those who remained
-firm in the belief that the 2020 election results were illegitimate. I
-take into account that legitimacy beliefs about the 2020 election and
-expectations of electoral fraud are related to partisanship and include
-partisanship as a control in the analysis\footnote{To be clear, I
-  conducted an auxiliary regression analysis to examine the relationship
-  between legitimacy beliefs and partisanship. Results revealed a
-  statistically significant relationship between the two variables and
-  thus omitting either would result in biased estimates.}.
-
-In addition, I expect that both expectations of electoral fraud and
-concerns for voter safety would lessen (shrink) when presented with
-information that veterans are being actively recruited to work and
-volunteer in election offices.
-
-Finally, prior research has shown that confidence that one's own vote
-would be counted as intended has been much stronger than confidence that
-votes nationwide would be treated likewise
+In addition, prior research has shown that confidence that one's own
+vote would be counted as intended has been much stronger than confidence
+that votes nationwide would be treated likewise
 (\citeproc{ref-sances2015}{Sances and Stewart 2015};
@@
 the group alone on public opinion. Therefore, any observed disparity of
-confidence in elections (i.e., the ``confidence gap'') between elections
-within one's local area and elections beyond will be smaller among those
-who are presented with information about election official recruitment
-efforts of veteran service members.
+confidence in elections between those within one's local area and those
+beyond will be smaller among those who are presented with information
+about election official recruitment efforts of veteran service members.
+
+Since the results and events following the 2020 election loomed large in
+anticipation of the U.S. 2024 general elections, it is reasonable to
+take into account beliefs about legitimacy of the 2020 election. This
+group who denies the legitimacy of the 2020 election results were
+possibly the most apprehensive (distrusting) of the 2024 election.
+However, given that veteran service members are held in high regard,
+generally speaking, announcing that veterans are being actively
+recruited to work as election staff and volunteers is expected to
+positively influence confidence in elections among those who remained
+firm in the belief that the 2020 election results were illegitimate.
+That is to say, despite their belief about the illegitimacy of the 2020
+election results, I expect that informing them about veteran recruitment
+efforts to improve their confidence in elections. I take into account
+the relationship between partisanship and 2020 election legitimacy
+beliefs and include partisanship as a control in the
+analysis\footnote{To be clear, I conducted an auxiliary regression
+  analysis to examine the relationship between legitimacy beliefs and
+  party ID. Results revealed a statistically significant relationship
+  between the two variables and thus omitting either would result in
+  biased estimates.}.
+
+Finally, I expect that concerns about potential for violence will
+lessen, and confidence in voter safety improve, when presented with
+information that veterans are being actively recruited to work and
+volunteer in election offices.
 
@@
 treatment vignette\footnote{Complete text of treatment and control
-  vignettes are included in the Appendix}.
+  vignettes are included in Appendix A}.
 
@@
 
-\begingroup\fontsize{8}{10}\selectfont
-
-\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{8cm}>{\raggedright\arraybackslash}p{8cm}}
+\centering
+\begin{tblr}[         %% tabularray outer open
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+width={1\linewidth},
+colspec={X[0.5]X[0.5]},
+column{1,2}={}{font=\fontsize{0.8em}{1.1em}\selectfont,},
+}                     %% tabularray inner close
 \toprule
-Trust & Distrust\\
-\midrule
+Trust & Distrust \\ \midrule %% TinyTableHeader
 How confident are you that votes in Maricopa County, AZ will be counted as voters intend in the elections this November?
-& There will be voter fraud, that is, people who are not eligible to vote will vote, or vote more than once\\
-\addlinespace
-How confident are you that election officials, their staff, and volunteers in Maricopa County, AZ will do a good job conducting the elections this November? & Many votes will not actually be counted\\
-\addlinespace
+& There will be voter fraud, that is, people who are not eligible to vote will vote, or vote more than once \\
+How confident are you that election officials, their staff, and volunteers in Maricopa County, AZ will do a good job conducting the elections this November?
+& Many votes will not actually be counted \\
 How commited do you think election staff and volunteers in Maricopa County, AZ will be to making sure the elections are fair and accurate?
-& Many people will show up to vote and be told they are not eligible\\
-\addlinespace
-How confident are you that the voting process will be fair in Maricopa County, AZ? & A foreign country will tamper with the votes cast in this area to change the results\\
-\addlinespace
+& Many people will show up to vote and be told they are not eligible \\
+How confident are you that the voting process will be fair in Maricopa County, AZ? & A foreign country will tamper with the votes cast in this area to change the results \\
 How confident are you that election systems in Maricopa County, AZ will be secure from hacking and other technological threats?
-& Election officials in Maricopa County, Arizona will try to discourage some people from voting\\
+& Election officials in Maricopa County, Arizona will try to discourage some people from voting \\
 \bottomrule
-\end{tabu}
-\endgroup{}
+\end{tblr}
 
@@
 single scale presuming a unidimensional construct for each\footnote{See
-  Appendix C for analysis.}.
+  Appendix C for Inter-item correlation analysis.}.
 
@@
   \citeproc{ref-robitzsch2020}{Robitzsch 2020}).}. On this scale,
-positive values reflect higher confidence in elections, negative values
-reflect greater distrust, and values closer to zero correspond to an
-individual's degree of \emph{insecurity}.
+positive values reflect higher confidence in elections (e.g., elections
+will be fair and accurate), negative values reflect greater distrust
+(i.e., expectation that election fraud will occur), and values closer to
+zero correspond to an individual's degree of \emph{insecurity}.
 
@@
 
-I first review responses to the survey items capturing trust and
-distrust separately by treatment condition. When distinguished by
-experiment condition, trust in elections admin is noticeably higher for
-those who read the treatment vignette. The difference is more pronounced
-for some items over others. That being said, there is a definite
-distinction between items pertaining to Maricopa County, AZ compared to
-items that pertain to a respondent's local area. In fact, as expected,
-the treatment appears to have hardly made a difference when the items
-concerned one's local area.
-
-\begin{figure}[h]
-
-\caption{\label{fig-patch10}Trust in Election Administration by
-Experiment Condition}
-
-\centering{
-
-\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-figures-fig-patch10-output-1.png}}
-
-}
-
-\end{figure}%
-
-Reviewing item responses distinguished by treatment condition reveals
-particulars of the treatment effect (Figure~\ref{fig-patch10}). Among
-the items that asked about Maricopa County, AZ, it is a bit easier to
-see upon which items the treatment vignette had the greatest effect. It
-appears that the main effect of the treatment is upon responses to the
-item that measures confidence in the security of election technology.
-
-Regarding confidence in the commitment of election staff and volunteers,
-a higher proportion of respondents in the treatment group selected
-``Very confident'' over ``Somewhat confident'' compared to the control
-group, but only for items concerning Maricopa County, AZ. Although
-confidence in election workers was generally high across the board, the
-shift from ``Somewhat'' to ``Very'' confident for items pertaining to
-election worker \emph{commitment} to fairness and accuracy seems to
-clearly speak to the group being recruited, i.e., veterans and family
-members. However, the same visible shift in proportion from ``Somewhat''
-to ``Very'' confident isn't observed when items asked about one's local
-area. It may be the case that respondents harbor particular attitudes or
-sentiment about Maricopa County, AZ itself, or there may be nothing
-uniquely special about Maricopa County, AZ supposing that elections
-anywhere beyond one's local area generally garner slightly less
-confidence.
-
-What this does suggest, however, is that trust in the fairness and
-accuracy of the electoral process is notably higher upon the notion that
-military veterans will be directly engaged as election staff and
-volunteers in places where such trust falters. The question turns to
-whether this also lowers distrust, or the extent to which one expects
-electoral fraud to occur.
-
-\begin{figure}[H]
-
-\caption{\label{fig-patch11}Disrust in Election Administration by
-Experiment Condition}
-
-\centering{
-
-\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-latex/notebooks-figures-fig-patch11-output-1.png}}
-
-}
-
-\end{figure}%
-
-Similar to the trust scale items, the items on the distrust scale were
-associated with lower distrust in the treatment condition compared to
-the control. A quick glance at Figure~\ref{fig-patch11} shows what
-appears to be a significant reduction in distrust, especially regarding
-the expectations that many votes wouldn't be counted, many voters would
-be turned away, and that election officials would discourage voters from
-casting a ballot. Interestingly, the expectation that there would be
-foreign interference in elections in Maricopa County, AZ were pretty
-resilient against the treatment. And again, responses for items
-pertaining to elections in one's local area are practically
-indistinguishable between treatment and control.
-
-\subsubsection{Confidence in elections}\label{confidence-in-elections}
-
 Once trust and distrust were composed into unified variable of
-confidence in elections, I then examined distribution of the dependent
+confidence in elections, I examined distribution of the dependent
 variable followed by analysis of the effect of the treatment by
-comparison of mean differences between experiment conditions. Recall
-that on this scale, zero reflects insecurity (e.g., similar or equal
-values of trust and distrust), whereas values diverging from zero
-reflect confidence in either direction, trust or distrust respectively.
-Positive values reflect trust in elections administration (e.g.,
-elections will be fair and accurate), whereas negative values reflect
-distrust in elections (i.e., expectation that election fraud will
-occur). To retain a meaningful zero, I rescaled the sum scores to range
-from -3 to 3\footnote{This range is mostly arbitrary, as a range from -1
-  to 1 works much the same. When relying on simple sum total score, the
-  scale ranges from -15 to 15. So a single point increase from 0 to 1
-  may reflect a combination of a single ``Very confident'' response on a
+comparison of mean differences between experiment conditions. To retain
+a meaningful zero, I rescaled the sum scores to range from -3 to
+3\footnote{This range is mostly arbitrary, as a range from -1 to 1 works
+  much the same. When relying on simple sum total score, the scale
+  ranges from -15 to 15. So a single point increase from 0 to 1 may
+  reflect a combination of a single ``Very confident'' response on a
   trust item compensated by a single ``Somewhat likely'' response on a
@@
   bipolar scale resulting from the composition of positive trust and
-  negative distrust engenders meaning to zero and negative values. As
-  such, composite mean scores become inappropriate and interpretation of
-  scores would no longer be feasible. In other words, negative values on
-  the scale for confidence in elections hold substantive meaning (e.g.,
-  distrust, absent trust), which makes transforming scores to fit a
-  unipolar scale inappropriate.} and then superimposed two histograms of
-confidence scores: one derived from AZ items and another for scores
-derived from local area items. Doing this is illustrative of the
-relative distribution of confidence that differed depending on the
-location of elections referred to in the survey items (e.g., Maricopa
-County, AZ).
-
-As revealed by review of the item responses, the distribution of
-confidence differed depending on whether survey items pertained to
-elections in Maricopa County, AZ, or elections within one's local area.
+  negative distrust engenders meaning to zero and negative values. In
+  other words, negative values on the scale for confidence in elections
+  hold substantive meaning (e.g., distrust, absent trust), which makes
+  transforming scores to fit a unipolar scale inappropriate.} and then
+superimposed two histograms of confidence scores: one derived from AZ
+items and another for scores derived from local area items
+(Figure~\ref{fig-dist}). Doing this is illustrative of the relative
+distribution of confidence that differed depending on the location of
+elections referred to in the survey items (e.g., Maricopa County, AZ).
+As expected, the distribution of confidence differed depending on
+whether survey items pertained to elections in Maricopa County, AZ, or
+elections within one's local area.
 
@@
 distrust seeing as how the distribution of confidence is largely
-positive (Figure~\ref{fig-dist}). However, there's a clear difference
-between confidence in Maricopa county, AZ elections and elections within
-one's local area. A paired t-test confirms that this difference was
-statistically significant, though somewhat small (mean difference
-\(= 0.325\), \(95\%\) CI \([0.27, 0.38]\), \(t(1286) = 11.61\),
-\(p < .001\)). Nonetheless, respondents appeared less confident
-regarding elections in Maricopa County, AZ, but held more confidence in
-elections administration in their local area. This complements previous
-research that demonstrates a similar bias favorable to one's local area
+positive. However, there's a clear difference between confidence in
+Maricopa county, AZ elections and elections within one's local area. A
+paired t-test confirms that this difference was statistically
+significant, though somewhat small (mean difference \(= 0.325\),
+\(95\%\) CI \([0.27, 0.38]\), \(t(1286) = 11.61\), \(p < .001\)).
+Nonetheless, respondents appeared less confident regarding elections in
+Maricopa County, AZ, but held more confidence in elections
+administration in their local area. This complements previous research
+that demonstrates a similar bias favorable to one's local area
 (\citeproc{ref-stewart2022}{Stewart 2022}).
@@
 
-\centering\begingroup\fontsize{9}{11}\selectfont
-
-\begin{tabular}[t]{llllllllll}
+\centering
+\begin{tblr}[         %% tabularray outer open
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
+column{1,2,3,4,5,6,7,8,9,10}={}{font=\fontsize{0.75em}{1.05em}\selectfont,},
+}                     %% tabularray inner close
 \toprule
-Place & $\bar{x}_{diff}$ & $\bar{x}_{treat}$ & $\bar{x}_{control}$ & $treat_{n}$ & $control_{n}$ & t & p & data & CI\\
-\midrule
-Maricopa County, AZ & 0.20 & 0.93 & 0.72 & 650.00 & 637.00 & 2.96 & 0.003** & 1283.73 & {}[ 0.07, 0.33]\\
-Local Area & 0.06 & 1.18 & 1.12 & 650.00 & 637.00 & 0.87 & 0.383 & 1282.95 & {}[-0.08, 0.20]\\
+Place & $\bar{x}_{diff}$ & $\bar{x}_{treat}$ & $\bar{x}_{control}$ & $n_{treat}$ & $n_{control}$ & t & p & df & CI \\ \midrule %% TinyTableHeader
+Maricopa County, AZ & $0.20$ & $0.93$ & $0.72$ & $650.00$ & $637.00$ & 2.96 & 0.003** & 1283.73 & [ 0.07, 0.33] \\
+Local Area & $0.06$ & $1.18$ & $1.12$ & $650.00$ & $637.00$ & 0.87 & 0.383 & 1282.95 & [-0.08, 0.20] \\
 \bottomrule
-\multicolumn{10}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{10}{l}{\rule{0pt}{1em}Welch Two Sample t-tests of difference between Confidence in Elections by Treatment Condition.}\\
-\end{tabular}
-\endgroup{}
+\end{tblr}
 
@@
 also a notable lack of trust that the voting process would be fair
-relative to the other items.\footnote{What is interesting to note here
-  is that the first three items regard the more human element of the
+relative to the other items\footnote{What is interesting to note here is
+  that the first three items regard the more human element of the
   election administration process, e.g., ensuring accuracy of counts,
@@
   presented here, it is interesting to see a slight divergence from the
-  usual high confidence placed in local area elections.} Now the
+  usual high confidence placed in local area elections.}. Now the
 comparative difference in responses between those in the treatment group
@@
 Concerning distrust among those who refuted the 2020 election results,
-responses items assessing one's expectation that election fraud would
+responses to items assessing one's expectation that election fraud would
 occur reveal the same pattern. Although there is not as stark a
@@
 on legitimacy beliefs while controlling for partisanship.
+
+\begin{table}[H]
+
+\caption{\label{tbl-legit}Confidence in Elections by Treatment and
+Legitimacy Beliefs}
+
+\centering{
+
+\begin{tabular}{l c c}
+\hline
+ & Confidence in AZ Elections & w/Interaction \\
+\hline
+(Intercept)                & $0.03 \; (0.08)$        & $0.07 \; (0.08)$        \\
+Treatment                  & $0.18 \; (0.05)^{***}$  & $0.09 \; (0.06)$        \\
+Not Legitimate             & $-0.72 \; (0.07)^{***}$ & $-0.86 \; (0.09)^{***}$ \\
+Republican                 & $0.11 \; (0.08)$        & $0.12 \; (0.08)$        \\
+Democrat                   & $0.17 \; (0.09)$        & $0.17 \; (0.09)^{*}$    \\
+Not Legitimate * Treatment &                         & $0.27 \; (0.11)^{*}$    \\
+\hline
+R$^2$                      & $0.14$                  & $0.14$                  \\
+Adj. R$^2$                 & $0.13$                  & $0.14$                  \\
+Num. obs.                  & $1263$                  & $1263$                  \\
+\hline
+\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
+\end{tabular}
+
+}
+
+\end{table}%
 
@@
 
+\subsubsection{Concerns for Violence and Voter
+Safety}\label{concerns-for-violence-and-voter-safety}
+
+Thus far, publicized announcements that election officials will be
+targeting veterans in their recruitment efforts does quite a bit to
+improve confidence in elections outside of one's local area (or, at
+least for elections held in Maricopa County, AZ), especially among those
+who believed the 2020 election results were illegitimate. While distrust
+is one concern during the pre-election period, it is not the only
+concern that arises in anticipation of US elections; the public must
+feel confident that voters are safe to cast a ballot in person. The
+survey included questions\footnote{See Table~\ref{tbl-4} in Appendix A}
+that allows me to assess whether those in the treatment condition
+expressed less concern for violence and more confidence in voter safety
+compared to those in the control condition.
+
+\begin{figure}[!t]
+
+\caption{\label{fig-safety-bars}Safety Concerns and Confidence by
+Treatment Condition}
+
+\begin{minipage}{\linewidth}
+
+\subcaption{\label{fig-safety-bars-1}Concern for Violence while voting
+in Maricopa County, AZ Elections}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-safety-bars-1.png}}
+
+}
+
+\end{minipage}%
+\newline
+\begin{minipage}{\linewidth}
+
+\subcaption{\label{fig-safety-bars-2}Confidence in Voter Saftey at
+Election Sites in Maricopa County, AZ}
+
+\centering{
+
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-safety-bars-2.png}}
+
+}
+
+\end{minipage}%
+
+\end{figure}%
+
+Briefly reviewing Figure~\ref{fig-safety-bars}, those in the treatment
+condition felt less concern over the potential for violence compared to
+those in the control. As for confidence in voter safety at election
+sites, it appears that more respondents in the treatment condition
+expressed that they were ``Very confident'' compared to those in the
+control, by approximately \(8\) percentage points.
+
+It would appear that the treatment vignette increased the likelihood
+that a respondent would select a higher response option compared to
+those in the control group. In order to assess whether that was the
+case, I conducted an ordered logistic regression on the relevant items
+using the experimental condition as a dichotomous predictor.
+
+Those in the treatment condition had lower probability to express that
+they were `Very' or `Somewhat' concerned for violence in Maricopa
+County, AZ Elections, yet higher probability of expressing `Not too' or
+`Not at all' concerned. As for confidence in voter safety, moving from
+treatment to control, the difference in predicted probability of a
+respondent selecting ``Very Confident'' was \(0.08\).
+Table~\ref{tbl-preds-diff1} and Table~\ref{tbl-preds-diff2} show the
+significant differences in predicted probabilities at 95\(\%\)
+confidence\footnote{The same models were run for items pertaining to
+  safety concerns in one's local area but results of the treatment were
+  not significantly different from the control. See Appendix D for full
+  results table of ordinal logistic regression}.
+
+\begin{table}
+
+\caption{\label{tbl-preds-diff1}Difference in Predicted Probabilities in
+Concern for violence, Threats of Violence, or Intimidation between
+Treatment and Control}
+
+\centering{
+
+\centering
+\begin{talltblr}[         %% tabularray outer open
+entry=none,label=none,
+note{}={{\fontsize{0.75em}{0.75em}\selectfont Results derived from proportional odds logistic regression model.
+Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher}},
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
+column{1,2,3,4,5,6,7}={}{font=\fontsize{0.8em}{1.1em}\selectfont,},
+}                     %% tabularray inner close
+\toprule
+Violence & hypothesis & estimate & std.error & z & Pr(>|z|) & conf.int \\ \midrule %% TinyTableHeader
+Very concerned & (Treatment) - (Control) & -0.027 & 0.011 & -2.463 & 0.014 & [-0.048, -0.005] \\
+Somewhat concerned & (Treatment) - (Control) & -0.037 & 0.015 & -2.468 & 0.014 & [-0.066, -0.008] \\
+Not too concerned & (Treatment) - (Control) & 0.032 & 0.013 & 2.460 & 0.014 & [ 0.007,  0.058] \\
+Not at all concerned & (Treatment) - (Control) & 0.031 & 0.013 & 2.472 & 0.013 & [ 0.006,  0.056] \\
+\bottomrule
+\end{talltblr}
+
+}
+
+\end{table}%
+
+\begin{table}
+
+\caption{\label{tbl-preds-diff2}Difference in Predicted Probabilities in
+Confidence that voters will be safe to vote in-person between Treatment
+and Control}
+
+\centering{
+
+\centering
+\begin{talltblr}[         %% tabularray outer open
+entry=none,label=none,
+note{}={{\fontsize{0.75em}{0.75em}\selectfont Results derived from proportional odds logistic regression model.
+Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher}},
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
+column{1,2,3,4,5,6,7}={}{font=\fontsize{0.8em}{1.1em}\selectfont,},
+}                     %% tabularray inner close
+\toprule
+Voter Safety & hypothesis & estimate & std.error & z & Pr(>|z|) & conf.int \\ \midrule %% TinyTableHeader
+Not at all confident & (Treatment) - (Control) & -0.0166 & 0.0048 & -3.4331 & 0.0006 & [-0.0260, -0.0071] \\
+Not too confident & (Treatment) - (Control) & -0.0444 & 0.0120 & -3.6929 & 0.0002 & [-0.0680, -0.0208] \\
+Somewhat confident & (Treatment) - (Control) & -0.0198 & 0.0066 & -3.0095 & 0.0026 & [-0.0327, -0.0069] \\
+Very confident & (Treatment) - (Control) & 0.0808 & 0.0215 & 3.7637 & 0.0002 & [ 0.0387,  0.1228] \\
+\bottomrule
+\end{talltblr}
+
+}
+
+\end{table}%
+
+\newpage
+
 \subsection{Conclusion}\label{conclusion}
@@
 former military service members to work as election staff and volunteers
-is associated with slightly greater confidence in elections compared to
-election worker recruitment announcements that do not explicitly mention
-targeted recruitment of former military service members. Moreover,
-increased levels of confidence is limited to elections beyond one's
-local area and, of course, in anticipation of election night. Whether
-the increase in confidence is sustained post-election night cannot be
-inferred from these results.
-
-Bear in mind that confidence in elections for one's local area is
-already higher than for those beyond. Thus, there's already more
-insecurity concerning elections elsewhere for whatever reason. In the
-anticipatory period prior to national elections, publicized efforts to
-recruit veterans to work as election staff and volunteers may be a
-small, but positive, step towards reducing insecurity in elections that
-occur elsewhere. Especially among those who maintained a steadataast
-degree of distrust in elections. Despite a lack of evidence that
-systematic electoral fraud had occurred in the 2020 election, a
-substantial proportion of the population were unwilling to affirm the
-legitimacy of the results. However, despite such legitimacy beliefs,
-most were not consistent as they expressed varying levels of trust in
-different aspects of elections administration.
-
-These results speaks more to the influence that military veterans have
-among those who distrust the electoral process and refute the legitimacy
-of prior outcomes than it does to the public more generally. In general,
-public confidence appears strongest when the elections under
+is associated with greater confidence in elections compared to election
+worker recruitment announcements that do not explicitly mention targeted
+efforts to recruit former military service members. In addition, such
+public announcements eased concerns about violence and increased
+confidence that voters would be safe to vote in person at election
+sites. Of course, the higher levels of confidence in elections and voter
+safety observed among the treatment group were limited to considerations
+about elections held in Maricopa County, AZ---presumably beyond one's
+local area. This is to be expected bearing in mind that confidence in
+elections for one's local area is usually higher than for those beyond.
+Thus, there's already more insecurity concerning elections elsewhere for
+whatever reason.
+
+One obvious contribution of these results shows that the perceived
+trustworthiness of elections administration is amendable to generalized
+impressions about the kind and character of the people who work and
+volunteer as election staff. Whatever election officials do to boost
+public confidence may be overshadowed by impressions about who is
+staffing election sites.
+
+It should be noted that these results are limited to one's expectations
+in anticipation of election night. Whether the increase in confidence is
+sustained post-election night cannot be inferred from these results.
+Moreover, It is yet unclear whether actually encountering and
+interacting with veterans working as staff or volunteers at election
+sites does much to improve voter confidence after election night
+compared to anyone else. It may be the case that assumptions that
+veterans are filling spots as election workers and volunteers simply
+primes positive expectations as one heads into an election site,
+potentially improving voters perceptions of their own experience on the
+way out. Further research would be needed to test such an idea.
+
+In general, public confidence appears strongest when the elections under
 consideration regard those within one's local community. Yet, such
@@
 easier to inspire a general sense of distrust in the process and its
-administration in places not near and around one's local area.
-
-\newpage
+administration in places more abstract.
+
+In the anticipatory period prior to national elections, publicized
+efforts to recruit veterans to work as election staff and volunteers may
+be a small, but positive, step towards reducing insecurity in elections
+that occur elsewhere. Especially among those who maintained a steadfast
+degree of distrust in elections. Despite a lack of evidence that
+systematic electoral fraud had occurred in the 2020 election, a
+substantial proportion of the population were unwilling to affirm the
+legitimacy of the results. However, despite such legitimacy beliefs,
+most were not consistent as they expressed varying levels of trust in
+different aspects of elections administration. These results say more
+about the influence that military veterans have among those who are most
+insecure than it does about the public more generally.
+
+\newpage{}
 
@@
 
-\newpage
-
-\subsection{Survey Items}\label{survey-items}
+\newpage{}
 
@@
 
-\begingroup\fontsize{8}{10}\selectfont
-
-\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{7cm}>{\raggedright\arraybackslash}p{4cm}}
+\centering
+\begin{tblr}[         %% tabularray outer open
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+width={1\linewidth},
+colspec={X[0.7]X[0.3]},
+column{1,2}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+}                     %% tabularray inner close
 \toprule
-Question & response\\
-\midrule
-In general, how favorable or unfavorable is your impression of local election officials? & {}[Strongly unfavorable, Somewhat unfavorable, Neither, Somewhat favorable, Strongly favorable]\\
-\addlinespace
-Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected? & Legitimate, Not legitimate\\
-\addlinespace
+Questions & Response \\ \midrule %% TinyTableHeader
+Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected? & \minipage{\textwidth}\begin{itemize}
+\item Legitimate
+
+\item Not legitimate
+
+\end{itemize}\endminipage \\
 Thinking about Maricopa County, AZ, how concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place?
-& Very concerned, Somewhat concerned, Not too concerned, Not at all concerned\\
-\addlinespace
+& \minipage{\textwidth}\begin{itemize}
+\item Very concerned
+
+\item Somewhat concerned
+
+\item Not too concerned
+
+\item Not at all concerned
+
+\end{itemize}\endminipage \\
 How confident, if at all, are you that in person polling places in Maricopa County, AZ will be safe places for voters to cast their ballots during the upcoming elections in November?
-& Not at all confident, Not too confident, Somewhat confident, Very confident\\
+& \minipage{\textwidth}\begin{itemize}
+\item Not at all confident
+
+\item Not too confident
+
+\item Somewhat confident
+
+\item Very confident
+
+\end{itemize}\endminipage \\
+Thinking about your local area, how concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place?
+& \minipage{\textwidth}\begin{itemize}
+\item Very concerned
+
+\item Somewhat concerned
+
+\item Somewhat unconcerned
+
+\item Not at all concerned
+
+\end{itemize}\endminipage \\
+How confident, if at all, are you that in person polling places in your local area will be safe places for voters to cast their ballots during the upcoming elections in November?
+& \minipage{\textwidth}\begin{itemize}
+\item Not at all confident
+
+\item Not too confident
+
+\item Somewhat confident
+
+\item Very confident
+
+\end{itemize}\endminipage \\
 \bottomrule
-\end{tabu}
-\endgroup{}
+\end{tblr}
 
@@
 
-\begin{table}
+\begin{table}[H]
 
@@
 predictor variables. Note that 19 missing observations were deleted. A
-\(\chi^2(15) = 11.010\), with 15 degrees of freedom and associated
-p-value \textgreater{} 0.05 (\(p = 0.75\)) confirms that none of the
-demographic predictor variables significantly increased the
-log-odds---in turn, the probability---of being assigned to the treatment
-group.
+\(\chi^2 = 11.010\), with 15 degrees of freedom and associated p-value
+\textgreater{} 0.05 (\(p = 0.75\)) confirms that none of the demographic
+predictor variables significantly increased the log-odds---in turn, the
+probability---of being assigned to the treatment group.
 
@@
 
-\centering\begingroup\fontsize{9}{11}\selectfont
-
-\begin{tabular}{lcccc}
+\centering
+\begin{tblr}[         %% tabularray outer open
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+width={0.8\linewidth},
+colspec={X[]X[]X[]},
+column{1,2,3}={}{font=\fontsize{0.8em}{1.1em}\selectfont,},
+hline{27}={1,2,3}{solid, black, 0.1em},
+}                     %% tabularray inner close
 \toprule
-  & \textbf{Treatment N} & \textbf{log(OR)} & \textbf{95\% CI} & \textbf{p-value}\\
-\midrule
-\textbf{(Intercept)} & 640 & 0.17 & -0.25, 0.59 & 0.4\\
-\textbf{Age} & 640 &  &  & 0.14\\
-\hspace{1em}18-34 & 179 & — & — & \\
-\hspace{1em}35-54 & 230 & -0.17 & -0.45, 0.12 & 0.2\\
-\hspace{1em}55-74 & 190 & -0.15 & -0.46, 0.15 & 0.3\\
-\addlinespace
-\hspace{1em}75-85+ & 41 & 0.40 & -0.15, 0.97 & 0.2\\
-\textbf{Gender} & 640 &  &  & 0.5\\
-\hspace{1em}Male & 308 & — & — & \\
-\hspace{1em}Female & 326 & -0.07 & -0.29, 0.15 & 0.5\\
-\hspace{1em}Other/Refused & 6 & -0.62 & -1.8, 0.42 & 0.2\\
-\addlinespace
-\textbf{Race (includes Hispanic as race)} & 640 &  &  & 0.9\\
-\hspace{1em}White & 495 & — & — & \\
-\hspace{1em}Asian & 26 & 0.03 & -0.55, 0.60 & >0.9\\
-\hspace{1em}Black & 79 & -0.08 & -0.43, 0.27 & 0.6\\
-\hspace{1em}Other & 11 & 0.05 & -0.82, 0.93 & >0.9\\
-\addlinespace
-\hspace{1em}Hispanic & 20 & -0.24 & -0.86, 0.38 & 0.5\\
-\hspace{1em}American Indian & 9 & 0.50 & -0.58, 1.7 & 0.4\\
-\textbf{Educational Attainment} & 640 &  &  & 0.6\\
-\hspace{1em}H.S. or less & 188 & — & — & \\
-\hspace{1em}Some college no degree & 140 & -0.10 & -0.42, 0.21 & 0.5\\
-\addlinespace
-\hspace{1em}College degree & 223 & -0.16 & -0.45, 0.12 & 0.3\\
-\hspace{1em}Postgraduate degree & 89 & 0.02 & -0.35, 0.40 & >0.9\\
-\textbf{Party ID} & 640 &  &  & 0.8\\
-\hspace{1em}Independent & 79 & — & — & \\
-\hspace{1em}Republican & 278 & 0.12 & -0.24, 0.48 & 0.5\\
-\addlinespace
-\hspace{1em}Democrat & 283 & 0.05 & -0.31, 0.40 & 0.8\\
+& \textbf{log(OR)} & \textbf{95\% CI} \\ \midrule %% TinyTableHeader
+\textbf{Age} &  &  \\
+18-34 &  &  \\
+35-54 & -0.17 & -0.45, 0.12 \\
+55-74 & -0.15 & -0.46, 0.15 \\
+75-85+ & 0.40 & -0.15, 0.97 \\
+\textbf{Gender} &  &  \\
+Male &  &  \\
+Female & -0.07 & -0.29, 0.15 \\
+Other/Refused & -0.62 & -1.8, 0.42 \\
+\textbf{Race/Ethnicity} &  &  \\
+White &  &  \\
+Asian & 0.03 & -0.55, 0.60 \\
+Black & -0.08 & -0.43, 0.27 \\
+Other & 0.05 & -0.82, 0.93 \\
+Hispanic & -0.24 & -0.86, 0.38 \\
+American Indian & 0.50 & -0.58, 1.7 \\
+\textbf{Education} &  &  \\
+H.S. or less &  &  \\
+Some college no degree & -0.10 & -0.42, 0.21 \\
+College degree & -0.16 & -0.45, 0.12 \\
+Postgraduate degree & 0.02 & -0.35, 0.40 \\
+\textbf{Party ID} &  &  \\
+Independent &  &  \\
+Republican & 0.12 & -0.24, 0.48 \\
+Democrat & 0.05 & -0.31, 0.40 \\
+Num.Obs & 1268 &  \\
+Log.Lik & -873.349 &  \\
+DF & 15 &  \\
+\(\chi^2\) & 11.01 &  \\
+\(P(>\chi^2)\) & 0.752 &  \\
+Deviance & 1746.698 &  \\
+Null Deviance & 1757.708 &  \\
 \bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{5}{l}{\rule{0pt}{1em}Chi-Squared = 11.01, d.f. = 15, p = 0.75}\\
-\multicolumn{5}{l}{\rule{0pt}{1em}Abbreviations: CI = Confidence Interval, OR = Odds Ratio}\\
-\end{tabular}
-\endgroup{}
+\end{tblr}
 
@@
 
-\newpage
+\newpage{}
 
@@
 
-\newpage
+\newpage{}
+
+\section{Appendix D: Predicted Probabilities of Safety Concerns by
+Treatment
+Condition}\label{appendix-d-predicted-probabilities-of-safety-concerns-by-treatment-condition}
+
+\begin{table}[H]
+
+\caption{\label{tbl-safety-logit}Ordinal Logistic Regression of Concerns
+for Violence and Confidence in Voter Safety Regressed on Experiment
+Condition}
+
+\centering{
+
+\centering
+\begin{talltblr}[         %% tabularray outer open
+entry=none,label=none,
+note{}={{\fontsize{0.75em}{0.75em}\selectfont + p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001}},
+note{ }={{\fontsize{0.75em}{0.75em}\selectfont Parameter estimate (and confidence intervals) exponentiated to show odds ratios.}},
+note{  }={{\fontsize{0.75em}{0.75em}\selectfont Uncertainty intervals (profile-likelihood) and p-values (two-tailed) computed using a Wald t-distribution approximation}},
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]},
+column{2,3}={}{halign=c, font=\fontsize{0.8em}{1.1em}\selectfont,},
+column{1}={}{halign=l, font=\fontsize{0.8em}{1.1em}\selectfont,},
+hline{16}={1,2,3}{solid, black, 0.05em},
+}                     %% tabularray inner close
+\toprule
+& Concerns for Violence (OR) & Confidence in Voter Safety (OR) \\ \midrule %% TinyTableHeader
+Treatment & 1.289* & 1.494*** \\
+& [1.055, 1.576] & [1.211, 1.844] \\
+Very concerned | Somewhat concerned & 0.153*** &  \\
+& [0.127, 0.186] &  \\
+Somewhat concerned | Not too concerned & 1.125 &  \\
+& [0.969, 1.305] &  \\
+Not too concerned | Not at all concerned & 6.762*** &  \\
+& [5.595, 8.171] &  \\
+Not at all confident | Not too confident &  & 0.055*** \\
+&  & [0.041, 0.073] \\
+Not too confident | Somewhat confident &  & 0.280*** \\
+&  & [0.237, 0.332] \\
+Somewhat confident | Very confident &  & 3.150*** \\
+&  & [2.667, 3.721] \\
+Num.Obs. & 1286 & 1285 \\
+RMSE & 2.44 & 2.91 \\
+\bottomrule
+\end{talltblr}
+
+}
+
+\end{table}%
+
+\begin{table}[H]
+
+\caption{\label{tbl-safety-preds1}Unit-level predicted probabilities of
+selecting response or higher comparing experiment condition}
+
+\centering{
+
+\centering
+\begin{talltblr}[         %% tabularray outer open
+entry=none,label=none,
+note{}={{\fontsize{0.75em}{0.75em}\selectfont Thinking about Maricopa County, AZ, how concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place?}},
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
+column{1,2,3,4,5,6,7}={}{font=\fontsize{0.8em}{1.1em}\selectfont,},
+}                     %% tabularray inner close
+\toprule
+Violence & Condition & estimate & std.error & z & Pr(>|z|) & conf.int \\ \midrule %% TinyTableHeader
+Very concerned & Control & 0.133 & 0.011 & 11.746 & 7.442e-32 & [0.111, 0.155] \\
+Very concerned & Treatment & 0.106 & 0.010 & 10.977 & 4.955e-28 & [0.087, 0.125] \\
+Somewhat concerned & Control & 0.396 & 0.016 & 25.430 & 1.175e-142 & [0.366, 0.427] \\
+Somewhat concerned & Treatment & 0.360 & 0.015 & 23.556 & 1.081e-122 & [0.330, 0.389] \\
+Not too concerned & Control & 0.342 & 0.015 & 23.296 & 4.890e-120 & [0.313, 0.371] \\
+Not too concerned & Treatment & 0.374 & 0.015 & 24.825 & 4.779e-136 & [0.344, 0.403] \\
+Not at all concerned & Control & 0.129 & 0.011 & 11.895 & 1.263e-32 & [0.108, 0.150] \\
+Not at all concerned & Treatment & 0.160 & 0.012 & 12.882 & 5.678e-38 & [0.136, 0.185] \\
+\bottomrule
+\end{talltblr}
+
+}
+
+\end{table}%
+
+\begin{table}[H]
+
+\caption{\label{tbl-safety-preds2}Unit-level predicted probabilities of
+selecting response or higher conditional to the Treatment experiment
+condition}
+
+\centering{
+
+\centering
+\begin{talltblr}[         %% tabularray outer open
+entry=none,label=none,
+note{}={{\fontsize{0.75em}{0.75em}\selectfont How confident, if at all, are you that in person polling places in Maricopa County, AZ will be safe places for voters to cast their ballots during the upcoming elections in November?}},
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
+column{1,2,3,4,5,6,7}={}{font=\fontsize{0.8em}{1.1em}\selectfont,},
+}                     %% tabularray inner close
+\toprule
+Voter Safety & Condition & estimate & std.error & z & Pr(>|z|) & conf.int \\ \midrule %% TinyTableHeader
+Not at all confident & Control & 0.052 & 0.007 & 7.302 & 2.845e-13 & [0.038, 0.066] \\
+Not at all confident & Treatment & 0.035 & 0.005 & 6.932 & 4.141e-12 & [0.025, 0.045] \\
+Not too confident & Control & 0.167 & 0.013 & 13.268 & 3.563e-40 & [0.142, 0.192] \\
+Not too confident & Treatment & 0.123 & 0.010 & 11.924 & 8.875e-33 & [0.102, 0.143] \\
+Somewhat confident & Control & 0.540 & 0.014 & 38.037 & 0.000 & [0.512, 0.568] \\
+Somewhat confident & Treatment & 0.520 & 0.014 & 36.134 & 6.715e-286 & [0.492, 0.549] \\
+Very confident & Control & 0.241 & 0.016 & 15.519 & 2.583e-54 & [0.211, 0.271] \\
+Very confident & Treatment & 0.322 & 0.017 & 18.550 & 8.104e-77 & [0.288, 0.356] \\
+\bottomrule
+\end{talltblr}
+
+}
+
+\end{table}%
+
+\newpage{}
 

### 2025-03-19 index.qmd
draft 3 complete. Also full project render

@@
 ---
-title: title
-subtitle: subtitle
-shorttitle: A Short title # aog-article-pdata
-shortauthors: Isaiah      # aog-article-pdata
+title: 'Inspiring Confidence and Easing Insecurity in the Pre-election period: The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections'
+# subtitle: 'The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections'
+shorttitle: 'Effect of Recruiting Military Veterans on Confidence in 2024 US Elections' # aog-article-pdf
+shortauthors: Isaiah      # aog-article-pdf
 authors:
@@
 library(tidyverse)
-library(easystats)
-library(odds.n.ends) # model sig from glm
-library(patchwork)
-library(texreg) # Conversion of R regression output into latex or HTML tables
+library(modelsummary)
+library(tinytable) # simple tables in html, LaTeX, markdown, word, pdf, typst
+library(litedown)
+# library(MASS)
+# library(ordinal)
+# library(marginaleffects)
+# library(easystats)
+# library(patchwork)
+
+# set some session options for `tinytable`
+options(tinytable_tt_digits = 3)
+# options(tinytable_theme_placement_latex_float = "H")
+options(tinytable_html_mathjax = TRUE) # set option to render math in html
+
+# apply Quarto data processing to all tables
+# theme_quarto <- function(x) format_tt(x, quarto = TRUE)
+# options(tinytable_tt_theme = theme_quarto)
 
@@
 data_dict <- read.csv("data/data_dictionary.csv")
-```
-
-```{r}
-#| label: setup-theme
-
-# set ggplot theme that will be used for every plot
-# theme_get()
-old <- ggplot2::theme_set(ggplot2::theme_bw())  # capture current theme
-
-# set/update new theme
-ggplot2::theme_set(
-  new = ggplot2::theme_bw(
-    base_family = 'TeX Gyre Pagella')+ # set font of ggplots
-    theme(legend.position = 'bottom')  # set legend position for all plots
+
+```
+
+```{r}
+#| label: fun-likert-plot
+
+# custom function used to create Likert Plots
+
+# To avoid excessive copy/paste, I made a function to create Likert plots
+# it is mostly a wrapper around `ggstats::gglikert`, but with a specific set up
+# particular colors, theme, etc. 
+likert_plot <- function(data, x, ...,  
+                        symmetric = FALSE,
+                        variable_labels = NULL,
+                        label_size = 2.5,
+                        vline = FALSE,
+                        title = waiver(), 
+                        subtitle = waiver(),
+                        caption = waiver(),
+                        xlab = waiver()){
+
+  p <- ggstats::gglikert(
+    data = data, include = {{ x }}, ...,
+    variable_labels = variable_labels,
+    symmetric = symmetric)+
+
+    # customize color
+    ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+    # custom theme
+    theme_bw(base_family = "TeX Gyre Pagella")+
+    theme(
+      legend.position = 'bottom',  # place legend on bottom
+      axis.title.y.left = element_blank(), # blank out y-axis label
+      axis.text.x = element_blank(), # remove percentage text along x-axis
+      strip.text.y.right = element_text(angle = 0) # make facet label horizontal
         )
 
-```
-
-\pagebreak
+    if (vline==TRUE) {
+    p <- p + geom_vline(xintercept = 0, color = 'black', linewidth = 1.2)
+  } else {
+      p
+  }
+
+  p <- p + ggplot2::labs(..., title = title, subtitle=subtitle, caption=caption, x = xlab)
+  p
+
+}
+
+```
+
+```{r}
+#| label: fun-barplot
+
+# function for creating barplots
+custom_barplot <- function(data, x, group, title = NULL, subtitle = NULL,
+                           caption = NULL, legend_fill = NULL,
+                           xlab = NULL){
+  b <- data |> 
+    group_by({{ group }}, {{ x }}) |> 
+    count() |> 
+    drop_na() |> 
+    group_by({{ group }}) |> 
+  mutate(prop = round(n/sum(n), digits = 3),
+         pct = prop*100,
+         res = str_c(pct,'% (', n, ')', sep = "")) |> 
+  ggplot(aes(x = {{ x }}, y = pct, fill = {{ group }}))+
+  geom_bar(position = 'dodge', stat = 'identity')+
+  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5, vjust = -0.7)+
+  scale_fill_grey(start = 0.5, end = 0.1)
+
+  b <- b + ggplot2::labs(
+    title = title,
+    subtitle = subtitle,
+    caption = stringr::str_wrap(caption, width = 99),
+    fill = legend_fill,
+    y = "Percentage",
+    x = stringr::str_wrap(xlab, width = 85))
+  b
+}
+
+```
+
+```{r}
+#| label: fun-logit-gof
+
+# custom function to return a certain selection of logistic regression model
+# goodness-of-fit statistics
+lrm.gof.stats <- function(x, ...){
+
+  out <- data.frame(
+    null.deviance = x$null.deviance,
+    df.null = x$df.null,
+    logLik = as.numeric(stats::logLik(x)),
+    AIC = stats::AIC(x),
+    BIC = stats::BIC(x),
+    deviance = stats::deviance(x),
+    df.residual = stats::df.residual(x),
+    nobs = stats::nobs(x),
+    chisq = as.numeric(x$null.deviance - stats::deviance(x)),
+    df = as.numeric(x$df.null - stats::df.residual(x)),
+    'P(>chi)' = pchisq(q=x$null.deviance - stats::deviance(x),
+                       df = x$df.null - stats::df.residual(x), 
+                       lower.tail = F)
+  )
+  out <- dplyr::as_tibble(out)
+  return(out)
+}
+
+```
+
+{{< pagebreak >}}
 
@@
 Concerns for safety have developed among election staff and voters in more recent elections.
-Regular measures are taken to enhance the *trustworthiness*[^1] of the electoral process through practices meant to improve the conduct, transparency, or overall administration of elections in the United States.
-
-Although election officials undertake great efforts to enhance the trustworthiness of election administration, public *trust* in elections is a psychological construct influenced by many things outside of election official control such as partisanship or elite rhetoric [@hooghe2018; @sances2015].
+Regular measures are taken to enhance the *trustworthiness* of the electoral process through practices meant to improve the conduct, transparency, or overall administration of elections in the United States.
+
+Although election officials undertake great efforts to enhance the *trustworthiness* of election administration, public *trust*[^1] in elections is a psychological construct influenced by many things outside of election official control such as partisanship or elite rhetoric [@hooghe2018; @sances2015].
 Moreover, a person's evaluation of the election in hindsight is often influenced by the election outcome itself [@daniller2019; @stewart2022].
@@
 election results as legitimate despite consistent review of the evidence confirming the results as fair and accurate.
-Such a case demonstrates that public trust in elections is, at best, only partial to trustworthiness of election administration in the United States[^2].
+Such a case demonstrates that public trust in elections is, at best, only partial to trustworthiness of election administration in the United States.
 
@@
 Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
-Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned[^3].
+Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned[^2].
 Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
@@
 
+In addition, prior research has shown that confidence that one's own vote would be counted as intended has been much stronger than confidence that votes nationwide would be treated likewise [@sances2015; @stewart2022].
+In other words, the public is more trusting of elections closer to home.
+Taking into account that confidence is lower for elections conducted outside of one's local area, then information that veterans are being recruited to help conduct elections in locations beyond one's locale may close this gap between confidence in elections within one's local area and confidence in elections elsewhere.
+Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone on public opinion.
+Therefore, any observed disparity of confidence in elections between those within one's local area and those beyond will be smaller among those who are presented with information about election official recruitment efforts of veteran service members.
+
 Since the results and events following the 2020 election loomed large in anticipation of the U.S.
@@
 However, given that veteran service members are held in high regard, generally speaking, announcing that veterans are being actively recruited to work as election staff and volunteers is expected to positively influence confidence in elections among those who remained firm in the belief that the 2020 election results were illegitimate.
-I take into account that legitimacy beliefs about the 2020 election and expectations of electoral fraud are related to partisanship and include partisanship as a control in the analysis[^4].
-
-In addition, I expect that both expectations of electoral fraud and concerns for voter safety would lessen (shrink) when presented with information that veterans are being actively recruited to work and volunteer in election offices.
-
-Finally, prior research has shown that confidence that one's own vote would be counted as intended has been much stronger than confidence that votes nationwide would be treated likewise [@sances2015; @stewart2022].
-In other words, the public is more trusting of elections closer to home.
-Taking into account that confidence is lower for elections conducted outside of one's local area, then information that veterans are being recruited to help conduct elections in locations beyond one's locale may close this gap between confidence in elections within one's local area and confidence in elections elsewhere.
-Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone on public opinion.
-Therefore, any observed disparity of confidence in elections (i.e., the "confidence gap") between elections within one's local area and elections beyond will be smaller among those who are presented with information about election official recruitment efforts of veteran service members.
+That is to say, despite their belief about the illegitimacy of the 2020 election results, I expect that informing them about veteran recruitment efforts to improve their confidence in elections.
+I take into account the relationship between partisanship and 2020 election legitimacy beliefs and include partisanship as a control in the analysis[^3].
+
+Finally, I expect that concerns about potential for violence will lessen, and confidence in voter safety improve, when presented with information that veterans are being actively recruited to work and volunteer in election offices.
 
@@
 citizens 18 years of age or older.
-Respondents were randomly split into either the treatment ($n =$ 650) control ($n =$ 637) conditions[^5].
-
-Survey participants read either a treatment or control vignette, which resembled a news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election[^6].
+Respondents were randomly split into either the treatment ($n =$ 650) control ($n =$ 637) conditions[^4].
+
+Survey participants read either a treatment or control vignette, which resembled a news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election[^5].
 The treatment vignette referred to a program designed to recruit veterans and their family members and describes an interviewee "Jordan Braxton" as an Army veteran.
@@
 Beyond those small differences and the headlines, the article vignettes are identical.
-Therefore, effects can be attributed to the information about veterans in the treatment vignette[^7].
+Therefore, effects can be attributed to the information about veterans in the treatment vignette[^6].
 
@@
 The items in this study all inquire into confidence over one's expectations in anticipation of upcoming elections.
-In addition, the survey of this study focused on attitudes regarding election workers such as election officials, staff, and volunteers specific to the location mentioned in the vignette---Maricopa County, AZ---as well as specific to one's local area[^8].
+In addition, the survey of this study focused on attitudes regarding election workers such as election officials, staff, and volunteers specific to the location mentioned in the vignette---Maricopa County, AZ---as well as specific to one's local area[^7].
 
@@
 Finally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
-The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^9].
+The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^8].
 
@@
   dplyr::as_tibble() |> 
-  select(Trust=label)
+  dplyr::select(Trust=label)
 
@@
   dplyr::as_tibble() |> 
-  select(Distrust=label)
+  dplyr::select(Distrust=label)
 
@@
 
-kableExtra::kbl(conf_items_text, booktabs = T,
-                col.names = c("Trust", "Distrust"),
-                linesep = "\\addlinespace") |> 
-  kableExtra::kable_styling(full_width = T,
-                            font_size = 8,
-                            latex_options = c("HOLD_position")) |> 
-  kableExtra::column_spec(column = 1:2, width = "8cm")
+tinytable::tt(conf_items_text, width = c(.5, .5)) |> 
+  tinytable::style_tt(fontsize = 0.80)
+
+# kableExtra::kbl(conf_items_text, booktabs = T,
+#                 col.names = c("Trust", "Distrust"),
+#                 linesep = "\\addlinespace") |> 
+#   kableExtra::kable_styling(full_width = T,
+#                             font_size = 8,
+#                             latex_options = c("HOLD_position")) |> 
+#   kableExtra::column_spec(column = 1:2, width = "8cm")
 
@@
 Upon construction of the two summated scales of *trust* and *distrust*, internal consistency reliability coefficient $\alpha$ were estimated for both and found to be adequate ($\alpha$ \> 0.8); the trust in elections scale $\alpha$ = 0.93 and the distrust scale $\alpha$ = 0.86.
-In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each[^10].
+In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each[^9].
 
@@
 That is, item responses on the trust scale ranged from 0 ("Not confident at all") to 3 ("Very confident), whereas responses on the distrust scale ranged from 0 ("Not likely at all") to -3 ("Very likely").
-Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^11].
-On this scale, positive values reflect higher confidence in elections, negative values reflect greater distrust, and values closer to zero correspond to an individual's degree of *insecurity*.
+Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^10].
+On this scale, positive values reflect higher confidence in elections (e.g., elections will be fair and accurate), negative values reflect greater distrust (i.e., expectation that election fraud will occur), and values closer to zero correspond to an individual's degree of *insecurity*.
 
@@
 
-I first review responses to the survey items capturing trust and distrust separately by treatment condition.
-When distinguished by experiment condition, trust in elections admin is noticeably higher for those who read the treatment vignette.
-The difference is more pronounced for some items over others.
-That being said, there is a definite distinction between items pertaining to Maricopa County, AZ compared to items that pertain to a respondent's local area.
-In fact, as expected, the treatment appears to have hardly made a difference when the items concerned one's local area.
-
-{{< embed notebooks/figures.qmd#fig-patch10 >}}
-
-Reviewing item responses distinguished by treatment condition reveals particulars of the treatment effect (@fig-patch10).
-Among the items that asked about Maricopa County, AZ, it is a bit easier to see upon which items the treatment vignette had the greatest effect.
-It appears that the main effect of the treatment is upon responses to the item that measures confidence in the security of election technology.
-
-Regarding confidence in the commitment of election staff and volunteers, a higher proportion of respondents in the treatment group selected "Very confident" over "Somewhat confident" compared to the control group, but only for items concerning Maricopa County, AZ.
-Although confidence in election workers was generally high across the board, the shift from "Somewhat" to "Very" confident for items pertaining to election worker *commitment* to fairness and accuracy seems to clearly speak to the group being recruited, i.e., veterans and family members.
-However, the same visible shift in proportion from "Somewhat" to "Very" confident isn't observed when items asked about one's local area.
-It may be the case that respondents harbor particular attitudes or sentiment about Maricopa County, AZ itself, or there may be nothing uniquely special about Maricopa County, AZ supposing that elections anywhere beyond one's local area generally garner slightly less confidence.
-
-What this does suggest, however, is that trust in the fairness and accuracy of the electoral process is notably higher upon the notion that military veterans will be directly engaged as election staff and volunteers in places where such trust falters.
-The question turns to whether this also lowers distrust, or the extent to which one expects electoral fraud to occur.
-
-{{< embed notebooks/figures.qmd#fig-patch11 >}}
-
-Similar to the trust scale items, the items on the distrust scale were associated with lower distrust in the treatment condition compared to the control.
-A quick glance at @fig-patch11 shows what appears to be a significant reduction in distrust, especially regarding the expectations that many votes wouldn't be counted, many voters would be turned away, and that election officials would discourage voters from casting a ballot.
-Interestingly, the expectation that there would be foreign interference in elections in Maricopa County, AZ were pretty resilient against the treatment.
-And again, responses for items pertaining to elections in one's local area are practically indistinguishable between treatment and control.
-
-### Confidence in elections
-
-Once trust and distrust were composed into unified variable of confidence in elections, I then examined distribution of the dependent variable followed by analysis of the effect of the treatment by comparison of mean differences between experiment conditions.
-Recall that on this scale, zero reflects insecurity (e.g., similar or equal values of trust and distrust), whereas values diverging from zero reflect confidence in either direction, trust or distrust respectively.
-Positive values reflect trust in elections administration (e.g., elections will be fair and accurate), whereas negative values reflect distrust in elections (i.e., expectation that election fraud will occur).
-To retain a meaningful zero, I rescaled the sum scores to range from -3 to 3[^12] and then superimposed two histograms of confidence scores: one derived from AZ items and another for scores derived from local area items.
+Once trust and distrust were composed into unified variable of confidence in elections, I examined distribution of the dependent variable followed by analysis of the effect of the treatment by comparison of mean differences between experiment conditions.
+To retain a meaningful zero, I rescaled the sum scores to range from -3 to 3[^11] and then superimposed two histograms of confidence scores: one derived from AZ items and another for scores derived from local area items (@fig-dist).
 Doing this is illustrative of the relative distribution of confidence that differed depending on the location of elections referred to in the survey items (e.g., Maricopa County, AZ).
-
-As revealed by review of the item responses, the distribution of confidence differed depending on whether survey items pertained to elections in Maricopa County, AZ, or elections within one's local area.
+As expected, the distribution of confidence differed depending on whether survey items pertained to elections in Maricopa County, AZ, or elections within one's local area.
 
@@
 
-Overall, the sample expressed more trust in elections relative to distrust seeing as how the distribution of confidence is largely positive (@fig-dist).
+Overall, the sample expressed more trust in elections relative to distrust seeing as how the distribution of confidence is largely positive.
 However, there's a clear difference between confidence in Maricopa county, AZ elections and elections within one's local area.
@@
 #| tbl-cap: "Mean Difference of Treatment Compared to Control Condition"
+#| tbl-colwidths: 80
 #| tbl-pos: H
@@
 # into table
-dplyr::bind_rows(
+tab_ttest <- dplyr::bind_rows(
   data |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
@@
     .before = Diff) |> 
-  insight::format_table(stars = T) |> 
-  # insight::export_table(format = "md") # alternate
-  # output table as `kable` for LaTeX pdata
-  kableExtra::kbl( 
-    booktabs = T,
-    col.names = c("Place", "$\\bar{x}_{diff}$", "$\\bar{x}_{treat}$", "$\\bar{x}_{control}$",
-                  "$treat_{n}$", "$control_{n}$", "t", "p", "data", "CI"), 
-    escape = F) |> 
-  kableExtra::footnote(general = "Welch Two Sample t-tests of difference between Confidence in Elections by Treatment Condition.") |> 
-  kableExtra::kable_styling(
-    font_size = 9, 
-    protect_latex = T)
+  insight::format_table(stars = T)
+
+# Output using `tinytable` R Package
+colnames(tab_ttest) <- c(
+  "Place",
+  "$\\bar{x}_{diff}$",
+  "$\\bar{x}_{treat}$",
+  "$\\bar{x}_{control}$",
+  "$n_{treat}$",
+  "$n_{control}$",
+  "t",
+  "p",
+  "df",
+  "CI")
+
+tinytable::tt(tab_ttest) |>
+  tinytable::format_tt(
+    j = 2:6, # specify columns  
+    math = T # apply mathmode to specified columns
+  ) |> 
+  tinytable::style_tt(fontsize = 0.75) # fontsize in em units (0.75*default fontsize)
+
+# output table as `kable` for LaTeX pdf
+# kableExtra::kbl(
+#   tab_ttest,
+#   booktabs = T,
+#   col.names = c(
+#     "Place",
+#     "$\\bar{x}_{diff}$",
+#     "$\\bar{x}_{treat}$",
+#     "$\\bar{x}_{control}$",
+#     "$treat_{n}$",
+#     "$control_{n}$",
+#     "t",
+#     "p",
+#     "data",
+#     "CI"
+#   ),
+#   escape = F
+# ) |>
+#   kableExtra::footnote(general = "Two Sample t-tests of difference between Confidence in Elections by Treatment Condition.") |>
+#   kableExtra::kable_styling(font_size = 9, protect_latex = T)
 
@@
 However, notably, trust that election technology would be secure received the lowest confidence endorsement overall.
-There was also a notable lack of trust that the voting process would be fair relative to the other items.[^13] Now the comparative difference in responses between those in the treatment group compared to those in the control group appears substantial for items pertaining to elections in Maricopa County, AZ.
+There was also a notable lack of trust that the voting process would be fair relative to the other items[^12].
+Now the comparative difference in responses between those in the treatment group compared to those in the control group appears substantial for items pertaining to elections in Maricopa County, AZ.
 
@@
 
-Concerning distrust among those who refuted the 2020 election results, responses items assessing one's expectation that election fraud would occur reveal the same pattern.
+Concerning distrust among those who refuted the 2020 election results, responses to items assessing one's expectation that election fraud would occur reveal the same pattern.
 Although there is not as stark a disparity between responses of those in the treatment and those in the control, among those in the treatment group, there does appear to be less expectation that election fraud would occur in Maricopa County, AZ.
@@
 
-::: {.content-visible when-format="bookup-html" unless-format="aog-article-pdf"}
+::: {.content-visible when-format="bookup-html" unless-format="pdf"}
 
@@
 
-::: {.content-visible when-format="aog-article-pdf" unless-format="bookup-html"}
+::: {.content-visible when-format="pdf" unless-format="bookup-html"}
 
@@
   single.row = T,
+  caption = NULL,
   caption.above = T,
   use.packages = F,
-  table = F, # Ensure this is set to FALSE so Quarto handles table cross-ref env
+  table = F, # set `table = FALSE`. Quarto handles table cross-ref env
   custom.model.names = c("Confidence in AZ Elections", "w/Interaction"),
@@
 
+### Concerns for Violence and Voter Safety
+
+Thus far, publicized announcements that election officials will be targeting veterans in their recruitment efforts does quite a bit to improve confidence in elections outside of one's local area (or, at least for elections held in Maricopa County, AZ), especially among those who believed the 2020 election results were illegitimate.
+While distrust is one concern during the pre-election period, it is not the only concern that arises in anticipation of US elections; the public must feel confident that voters are safe to cast a ballot in person.
+The survey included questions^[See @tbl-4 in Appendix A] that allows me to assess whether those in the treatment condition expressed less concern for violence and more confidence in voter safety compared to those in the control condition.
+```{r}
+#| label: fig-safety-bars
+#| layout-ncol: 1
+#| layout-nrow: 2
+#| fig-cap: "Safety Concerns and Confidence by Treatment Condition"
+#| fig-subcap: 
+#|   - "Concern for Violence while voting in Maricopa County, AZ Elections"
+#|   - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"
+
+# concern for violence by treatment
+bar_q25 <- custom_barplot(
+  data = data, 
+  x = q25, 
+  group = group,
+  subtitle = str_wrap(attr(data$q25, "label"), width = 85)
+  )+
+  theme(text = element_text(family = 'TeX Gyre Pagella'),
+        legend.position = "right")
+
+# confidence in voter safety by treatment
+bar_q26 <- custom_barplot(
+  data = data, 
+  x = q26, 
+  group = group,
+  subtitle = str_wrap(attr(data$q26, "label"), width = 85)
+  )+
+  theme(text = element_text(family = 'TeX Gyre Pagella'),
+        legend.position = "right")
+
+bar_q25
+bar_q26
+
+```
+
+Briefly reviewing @fig-safety-bars, those in the treatment condition felt less concern over the potential for violence compared to those in the control.
+As for confidence in voter safety at election sites, it appears that more respondents in the treatment condition expressed that they were "Very confident" compared to those in the control, by approximately $8$ percentage points.
+
+It would appear that the treatment vignette increased the likelihood that a respondent would select a higher response option compared to those in the control group.
+In order to assess whether that was the case, I conducted an ordered logistic regression on the relevant items using the experimental condition as a dichotomous predictor.
+
+Those in the treatment condition had lower probability to express that they were 'Very' or 'Somewhat' concerned for violence in Maricopa County, AZ Elections, yet higher probability of expressing 'Not too' or 'Not at all' concerned.
+As for confidence in voter safety, moving from treatment to control, the difference in predicted probability of a respondent selecting "Very Confident" was $0.08$.
+@tbl-preds-diff1 and @tbl-preds-diff2 show the significant differences in predicted probabilities at 95$\%$ confidence^[The same models were run for items pertaining to safety concerns in one's local area but results of the treatment were not significantly different from the control.
+See Appendix D for full results table of ordinal logistic regression].
+
+```{r}
+#| label: ordinal-logit
+#| include: false
+
+# needed to duplicate `group` variable with different column name due to
+# conflict with marginaleffects R package
+data <- data |>
+  mutate(condition = group)
+
+# running ordinal logisitc regression models (proportional odds logistic regression)
+m.q25 <- MASS::polr(q25 ~ condition, data = data, method = "logistic", Hess = T)
+m.q26 <- MASS::polr(q26 ~ condition, data = data, method = "logistic", Hess = T)
+m.q36 <- MASS::polr(q36 ~ condition, data = data, method = "logistic", Hess = T)
+m.q37 <- MASS::polr(q37 ~ condition, data = data, method = "logistic", Hess = T)
+
+# "Outcome predicted by a fitted model on a specified scale for a given
+# combination of values of the predictor variables, such as their observed
+# values, their means, or factor levels (a.k.a. "reference grid")".
+
+# predictions(): unit-level (conditional) estimates.
+
+# predicted probability estimates by treatment or control
+q25_preds <- marginaleffects::predictions(m.q25, by = "condition", type = "probs")
+q26_preds <- marginaleffects::predictions(m.q26, by = "condition", type = "probs")
+q36_preds <- marginaleffects::predictions(m.q36, by = "condition", type = "probs")
+q37_preds <- marginaleffects::predictions(m.q37, by = "condition", type = "probs")
+
+# this provides the difference in predicted probabilities between treatment and
+# control
+pdiff_q25 <- marginaleffects::predictions(
+  m.q25,
+  by = "condition",
+  type = "probs",
+  hypothesis = ~ reference | group
+)
+
+pdiff_q26 <- marginaleffects::predictions(
+  m.q26,
+  by = "condition",
+  type = "probs",
+  hypothesis = ~ reference | group
+)
+
+```
+
+```{r}
+#| label: tbl-preds-diff1
+#| tbl-colwidths: 80
+#| tbl-cap: "Difference in Predicted Probabilities in Concern for violence, Threats of Violence, or Intimidation between Treatment and Control"
+
+tab_q25_pdiff <- pdiff_q25 |>
+  dplyr::as_tibble() |>
+  dplyr::rename(
+    Violence = group,
+    z = statistic,
+    'Pr(>|z|)' = p.value) |>
+  select(Violence,
+         hypothesis,
+         estimate,
+         std.error,
+         z,
+         'Pr(>|z|)',
+         conf.low,
+         conf.high) |>
+  insight::format_table(stars = T, digits = 3)
+
+tinytable::tt(
+  tab_q25_pdiff, 
+  notes = "Results derived from proportional odds logistic regression model.
+Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |>
+  tinytable::style_tt(
+    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    ) |>  
+  tinytable::style_tt(i = "notes", fontsize = 0.75)
+
+  # kableExtra::kbl(tab_q25_pdiff, 
+  #                 booktabs = T) |> 
+  # kableExtra::footnote(general = "Results derived from proportional odds logistic regression model.
+Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher")
+```
+
+```{r}
+#| label: tbl-preds-diff2
+#| tbl-colwidths: 80
+#| tbl-cap: "Difference in Predicted Probabilities in Confidence that voters will be safe to vote in-person between Treatment and Control"
+
+tab_q26_pdiff <- pdiff_q26 |>
+  dplyr::as_tibble() |>
+  dplyr::rename('Voter Safety' = group,
+                z = statistic,
+                'Pr(>|z|)' = p.value) |>
+  select('Voter Safety',
+         hypothesis,
+         estimate,
+         std.error,
+         z,
+         'Pr(>|z|)',
+         conf.low,
+         conf.high) |>
+  insight::format_table(stars = T, digits = 4)
+
+tinytable::tt(
+  tab_q26_pdiff, 
+  notes = "Results derived from proportional odds logistic regression model.
+Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |>
+  tinytable::style_tt(
+    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    ) |>  
+  tinytable::style_tt(i = "notes", fontsize = 0.75) # style font of table notes
+
+  # kableExtra::kbl(tab_q26_pdiff, 
+  #                 booktabs = T) |> 
+  # kableExtra::footnote(general = "Results derived from proportional odds logistic regression model.
+Estimates are differences in predicted probabitilites transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher")
+
+```
+
+\newpage
+
 ## Conclusion
 
-Publicized announcements that election officials are actively recruiting former military service members to work as election staff and volunteers is associated with slightly greater confidence in elections compared to election worker recruitment announcements that do not explicitly mention targeted recruitment of former military service members.
-Moreover, increased levels of confidence is limited to elections beyond one's local area and, of course, in anticipation of election night.
+Publicized announcements that election officials are actively recruiting former military service members to work as election staff and volunteers is associated with greater confidence in elections compared to election worker recruitment announcements that do not explicitly mention targeted efforts to recruit former military service members.
+In addition, such public announcements eased concerns about violence and increased confidence that voters would be safe to vote in person at election sites.
+Of course, the higher levels of confidence in elections and voter safety observed among the treatment group were limited to considerations about elections held in Maricopa County, AZ---presumably beyond one's local area.
+This is to be expected bearing in mind that confidence in elections for one's local area is usually higher than for those beyond.
+Thus, there's already more insecurity concerning elections elsewhere for whatever reason.
+
+One obvious contribution of these results shows that the perceived trustworthiness of elections administration is amendable to generalized impressions about the kind and character of the people who work and volunteer as election staff.
+Whatever election officials do to boost public confidence may be overshadowed by impressions about who is staffing election sites.
+
+It should be noted that these results are limited to one's expectations in anticipation of election night.
 Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
-
-Bear in mind that confidence in elections for one's local area is already higher than for those beyond.
-Thus, there's already more insecurity concerning elections elsewhere for whatever reason.
-In the anticipatory period prior to national elections, publicized efforts to recruit veterans to work as election staff and volunteers may be a small, but positive, step towards reducing insecurity in elections that occur elsewhere.
-Especially among those who maintained a steadataast degree of distrust in elections.
-Despite a lack of evidence that systematic electoral fraud had occurred in the 2020 election, a substantial proportion of the population were unwilling to affirm the legitimacy of the results.
-However, despite such legitimacy beliefs, most were not consistent as they expressed varying levels of trust in different aspects of elections administration.
-
-These results speaks more to the influence that military veterans have among those who distrust the electoral process and refute the legitimacy of prior outcomes than it does to the public more generally.
+Moreover, It is yet unclear whether actually encountering and interacting with veterans working as staff or volunteers at election sites does much to improve voter confidence after election night compared to anyone else.
+It may be the case that assumptions that veterans are filling spots as election workers and volunteers simply primes positive expectations as one heads into an election site, potentially improving voters perceptions of their own experience on the way out.
+Further research would be needed to test such an idea.
+
 In general, public confidence appears strongest when the elections under consideration regard those within one's local community.
@@
 Whether that is due to some local favorability bias or some outward negativity bias is hard to say.
-And seeing as how insecurity presents vulnerability, it is perhaps far easier to inspire a general sense of distrust in the process and its administration in places not near and around one's local area.
-
-\newpage
+And seeing as how insecurity presents vulnerability, it is perhaps far easier to inspire a general sense of distrust in the process and its administration in places more abstract.
+
+In the anticipatory period prior to national elections, publicized efforts to recruit veterans to work as election staff and volunteers may be a small, but positive, step towards reducing insecurity in elections that occur elsewhere.
+Especially among those who maintained a steadfast degree of distrust in elections.
+Despite a lack of evidence that systematic electoral fraud had occurred in the 2020 election, a substantial proportion of the population were unwilling to affirm the legitimacy of the results.
+However, despite such legitimacy beliefs, most were not consistent as they expressed varying levels of trust in different aspects of elections administration.
+These results say more about the influence that military veterans have among those who are most insecure than it does about the public more generally.
+
+{{< pagebreak >}}
 
@@
 
-\newpage
-
-## Survey Items
+{{< pagebreak >}}
 
@@
 #| tbl-cap: "Survey Items and Response Options"
-
-data |> 
-  select(q6, q7, q25, q26) |> 
-  labelled::generate_dictionary() |> 
-  dplyr::as_tibble() |> 
-  mutate(value_labels = dplyr::case_when(
-    variable == 'q6' ~ "[Strongly unfavorable, Somewhat unfavorable, Neither, Somewhat favorable, Strongly favorable]",
-    variable == 'q7' ~ "Legitimate, Not legitimate",
-    variable == 'q25' ~ "Very concerned, Somewhat concerned, Not too concerned, Not at all concerned",
-    variable == 'q26' ~ "Not at all confident, Not too confident, Somewhat confident, Very confident"
-  )) |> 
-  select(Question = label, response = value_labels) |> 
-  kableExtra::kbl(booktabs = T, linesep = "\\addlinespace") |> 
-  kableExtra::kable_styling(full_width = T,
-                            font_size = 8,
-                            latex_options = c("HOLD_position")) |> 
-  kableExtra::column_spec(column = 1, width = "7cm") |> 
-  kableExtra::column_spec(column = 2, width = "4cm")
+#| tbl-colwidths: [70, 30]
+
+var_label_tab <- function(x){
+    purrr::map(x, ~attr(., "label")) |>
+    purrr::map(~ifelse(purrr::is_null(.), "No label", .)) |>
+    tibble::enframe(name = "var", value = "var_label") |>
+    tidyr::unnest(cols = c(var_label))
+}
+
+Questions <- data |> 
+  dplyr::select(q7, q25, q26, q36, q37) |>
+  dplyr::rename_with(.cols = everything(), .fn = ~snakecase::to_any_case(.,case = "upper_camel")) |> 
+  var_label_tab() |>
+  dplyr::select(Question = var_label) |> 
+  dplyr::pull(Question)
+
+items_responses <- data.frame(
+  Questions = Questions,
+  Response =c(
+    "- Legitimate\n- Not legitimate",
+    "- Very concerned\n- Somewhat concerned\n- Not too concerned\n- Not at all concerned",
+    "- Not at all confident\n- Not too confident\n- Somewhat confident\n- Very confident",
+    "- Very concerned\n- Somewhat concerned\n- Somewhat unconcerned\n- Not at all concerned",
+    "- Not at all confident\n- Not too confident\n- Somewhat confident\n- Very confident")
+)
+
+# wrap in a minipage environment
+minipagify <- function(x) {
+  sprintf(
+    "\\minipage{\\textwidth}%s\\endminipage",
+    sapply(x, mark, "latex")
+  )
+}
+
+# only in LaTeX
+is_latex <- identical(knitr::pandoc_to(), "latex")
+
+tab <- tinytable::tt(items_responses, width = c(0.7, 0.3)) |>
+  tinytable::style_tt(j = c(1,2), fontsize = 0.8, align = "l") |>
+  tinytable::format_tt(markdown = TRUE) |>
+  tinytable::format_tt(j = 2, fn = if (is_latex) minipagify else NULL)
+
+tab
+
+# 
+# Response <- data |> 
+#   dplyr::select(q7, q25, q26, q36, q37) |>
+#   surveytoolbox::data_dict() |> 
+#   dplyr::as_tibble() |> 
+#   dplyr::select(value)
+# 
+# 
+# item_table <- data |> 
+#   select(q7, q25, q26, q36, q37) |>
+#   dplyr::rename_with(.cols = everything(), .fn = ~snakecase::to_any_case(.,case = "upper_camel")) |> 
+#   var_label_tab() |>
+#   select(Question = var_label) |> 
+#   mutate(Response = Response$value)
+# 
+# item_table
+# 
+# tinytable::tt(item_table, width = c(.7, .3)) |> 
+#   tinytable::style_tt(fontsize = 0.80)
+
+# alternate
+# kableExtra::kbl(item_table, booktabs = T, linesep = "\\addlinespace[2mm]") |> 
+#   kableExtra::kable_styling(
+#     full_width = T,
+#     font_size = 9,
+#     latex_options = c("HOLD_position")
+#     ) |> 
+#   kableExtra::pack_rows(index = c("Legitimacy" = 1,
+#                                   "Safety Concerns" = 4))
 
@@
 \newpage
+
+<!-- {{< pagebreak >}} -->
 
@@
 #| tbl-cap: "Sample Demographics"
-#|
+#| tbl-pos: 'H'
 
@@
 Note that 19 missing observations were deleted.
-A $\chi^2(15) = 11.010$, with 15 degrees of freedom and associated p-value > 0.05 ($p = 0.75$) confirms that none of the demographic predictor variables significantly increased the log-odds---in turn, the probability---of being assigned to the treatment group.
+A $\chi^2 = 11.010$, with 15 degrees of freedom and associated p-value > 0.05 ($p = 0.75$) confirms that none of the demographic predictor variables significantly increased the log-odds---in turn, the probability---of being assigned to the treatment group.
 
@@
 # demographic variables are IVs
-
-data <- data |> 
-  mutate(group.dum = dplyr::case_when(
-    group == "Treatment" ~ 1,
-    group == "Control" ~ 0,
-    TRUE ~ NA), .after = group)
-
-m1 <- glm(group.dum ~ age_4cat + gender_3cat + race2 + educ_4cat + partyid_3cat, 
+m1 <- glm(group ~ age_4cat + gender_3cat + race2 + educ_4cat + partyid_3cat, 
           family = binomial(link = "logit"), data = data)
 
-# A Chi-square of 11.01 with 15 degrees of freedom and associated p-value > 0.05 (p-value = 0.752) confirms that none of the demographic predictor variables significantly increased the probability of being assigned to the treatment group.
-
+# use `gtsummary` package to build regression table, then output as tibble
 logit_tab <- gtsummary::tbl_regression(
     m1,
-    intercept = T,
+    intercept = F,
     label = list(
@@
       gender_3cat ~ "Gender",
-      race2 ~ "Race (includes Hispanic as race)",
-      educ_4cat ~ "Educational Attainment", 
+      race2 ~ "Race/Ethnicity",
+      educ_4cat ~ "Education",
       partyid_3cat ~ "Party ID")) |>
-  gtsummary::add_global_p(keep = T) |> 
-  gtsummary::add_nevent(location = c("label", "level")) |>
-  gtsummary::bold_p() |> 
   gtsummary::bold_labels() |>
@@
     label = " ",
-    stat_nevent = "**Treatment N**") 
-# 
-#   gtsummary::modify_footnote_header(
-#     footnote = "Chi-Squared ($\\chi^2$) = 11.01, d.f. = 15, p = 0.75", columns = "p.value")
-
-gtsummary::as_kable_extra(logit_tab, 
-                          booktabs = T, 
-                          escape = F, 
-                          addtl_fmt = T) |> 
-  kableExtra::footnote("Chi-Squared = 11.01, d.f. = 15, p = 0.75", escape = F) |> 
-  kableExtra::kable_styling(font_size = 9)
-
-```
-
-\newpage
+    stat_nevent = "**Treatment N**") |>
+  # output as_tibble
+  gtsummary::as_tibble() |>
+  # omit p.values
+  dplyr::select(-4)
+
+# transform tibble dataframe into `tinytable` and format as markdown
+# replace NA with blank " " (or "-" if desired)
+logit_tab <- tinytable::tt(logit_tab, width = 0.8) |> 
+  tinytable::format_tt(markdown = T) |> 
+  tinytable::format_tt(replace = " ")
+
+# create 2nd table containing only logit model fit statistics
+# using custom function, get logit regression model fit stats... 
+gof_stats <- lrm.gof.stats(m1) |> 
+  # omit certain stats (saves space)
+  dplyr::select(
+    nobs, logLik, df, chisq, P..chi., deviance, null.deviance,
+    -AIC, -BIC, -df.null, -df.residual) |> 
+  # rename column variables
+  dplyr::rename(
+    "Num.Obs"       = "nobs",
+    "Null Deviance" = "null.deviance",
+    "Deviance"      = "deviance",
+    "DF"            = "df",
+    "Log.Lik"       = "logLik",
+    "\\chi^2"       = "chisq",
+    "P(>\\chi^2)"   = "P..chi."
+  ) |> 
+  # pivot into two column long-form dataframe
+  tidyr::pivot_longer(cols = everything(),names_to = " ", values_to = '**log(OR)**') |>
+  # pipe into tinytable
+  tinytable::tt(width = 0.8) |> 
+  # ensure rows with math text are identified and formatted as math (i.e., $..$)
+  tinytable::format_tt(i = c(4,5), j = 1, math = T)
+
+# using `rbind2` function, bind 2nd table at bottom of first table 
+tinytable::rbind2(logit_tab, gof_stats, use_names = F, headers = F) |> 
+  # add horizontal line just above fit stats
+  tinytable::style_tt(i = 26, line = "t", line_color = "black", line_width = 0.1) |>
+  # adjust fontsize of text within table
+  tinytable::style_tt(fontsize = 0.8) |>
+  # finally, format markdown and blank out any NA fillers
+  tinytable::format_tt(markdown = T, replace = " ")
+
+```
+
+{{< pagebreak >}}
 
@@
 
-\newpage
+{{< pagebreak >}}
+
+# Appendix D: Predicted Probabilities of Safety Concerns by Treatment Condition {.appendix}
+
+```{r}
+#| label: tbl-safety-logit
+#| tbl-cap: "Ordinal Logistic Regression of Concerns for Violence and Confidence in Voter Safety Regressed on Experiment Condition"
+#| tbl-cap-location: top
+#| tbl-colwidths: 80
+#| tbl-pos: 'H'
+
+# save models to a list
+safety_models <- list(
+  "Concerns for Violence (OR)" = m.q25,
+  "Confidence in Voter Safety (OR)" = m.q26)
+
+cm <- c("conditionTreatment" = "Treatment",
+        "Very concerned|Somewhat concerned" = "Very concerned | Somewhat concerned",
+        "Somewhat concerned|Not too concerned" = "Somewhat concerned | Not too concerned",
+        "Not too concerned|Not at all concerned" = "Not too concerned | Not at all concerned",
+        "Not at all confident|Not too confident" = "Not at all confident | Not too confident",
+        "Not too confident|Somewhat confident" = "Not too confident | Somewhat confident",
+        "Somewhat confident|Very confident" = "Somewhat confident | Very confident"
+        )
+
+tbl_safety_logit <- modelsummary::modelsummary(
+  safety_models,  
+  fmt = 3,
+  output = "tinytable",
+  exponentiate = T, # show odds ratio 
+  # coef_omit = c(-4), # only the beta coef, not the intercepts
+  # coef_rename = c("conditionTreatment" = "Treatment"),
+  coef_map = cm,
+  stars = T,
+  # estimate = c("{estimate}{stars}"),
+  statistic = "conf.int",
+  gof_map = c("nobs", "rmse"), 
+  note = list(
+    "Parameter estimate (and confidence intervals) exponentiated to show odds ratios.",
+    "Uncertainty intervals (profile-likelihood) and p-values (two-tailed) computed using a Wald t-distribution approximation")
+  )
+
+tbl_safety_logit |>  
+  tinytable::style_tt(
+    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    ) |> 
+  tinytable::style_tt(i = "notes", fontsize = 0.75)
+
+```
+
+```{r}
+#| label: tbl-safety-preds1
+#| tbl-cap: "Unit-level predicted probabilities of selecting response or higher comparing experiment condition"
+#| tbl-colwidths: 80
+#| tbl-pos: 'H'
+
+# table that shows the predicted probability of selecting a response or lower
+# conditional to the Treatment experiment condition.
+tab_safety_preds1 <- q25_preds |>  
+  dplyr::as_tibble() |> 
+  select(group, condition, 
+         estimate, std.error, statistic,  p.value,
+         conf.low, conf.high) |> 
+  dplyr::rename(
+    Condition = condition,
+    Violence = group,
+    z = statistic,
+    'Pr(>|z|)' = p.value) |>
+  insight::format_table(digits = 3)
+
+tinytable::tt(
+  tab_safety_preds1, digits = 3,
+  notes = attr(data$q25, "label")) |> 
+  tinytable::style_tt(
+    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    ) |> 
+  tinytable::style_tt(i = "notes", fontsize = 0.75)
+
+```
+
+```{r}
+#| label: tbl-safety-preds2
+#| tbl-cap: "Unit-level predicted probabilities of selecting response or higher conditional to the Treatment experiment condition"
+#| tbl-colwidths: 80
+#| tbl-pos: 'H'
+
+# table that shows the predicted probability of selecting a response or lower
+# conditional to the Treatment experiment condition.
+tab_safety_preds2 <- q26_preds |> 
+  dplyr::as_tibble() |> 
+  select(group, condition, 
+         estimate, std.error, statistic,  p.value,
+         conf.low, conf.high) |> 
+  dplyr::rename(
+    Condition = condition,
+    'Voter Safety' = group,
+    z = statistic,
+    'Pr(>|z|)' = p.value) |>
+  insight::format_table(digits = 3)
+
+tinytable::tt(
+  tab_safety_preds2, digits = 3,
+  notes = attr(data$q26, "label")) |>  
+  tinytable::style_tt(
+    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    ) |> 
+  tinytable::style_tt(i = "notes", fontsize = 0.75)
+
+```
+
+{{< pagebreak >}}
 
@@
 
-[^2]: There's little that could justify a conceptual distinction between public trust pre-election and public trust post-election.
-The temporal element renders the difference between pre- and post-election more operative than conceptual at a foundational level.
-
-[^3]: The vignettes written were based on real news stories
-
-[^4]: To be clear, I conducted an auxiliary regression analysis to examine the relationship between legitimacy beliefs and partisanship.
+[^2]: The vignettes written were based on real news stories
+
+[^3]: To be clear, I conducted an auxiliary regression analysis to examine the relationship between legitimacy beliefs and party ID.
 Results revealed a statistically significant relationship between the two variables and thus omitting either would result in biased estimates.
 
-[^5]: Demographic breakdown of the sample are included in Appendix B.
-
-[^6]: The article vignettes were written and designed by Michael Hanmer Ph.D and myself with input from We the Veterans, a non-profit organization
-
-[^7]: Complete text of treatment and control vignettes are included in the Appendix
-
-[^8]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
-
-[^9]: Survey item wording and responses are included in Appendix A.
-
-[^10]: See Appendix C for analysis.
-
-[^11]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
+[^4]: Demographic breakdown of the sample are included in Appendix B.
+
+[^5]: The article vignettes were written and designed by Michael Hanmer Ph.D and myself with input from We the Veterans, a non-profit organization
+
+[^6]: Complete text of treatment and control vignettes are included in Appendix A
+
+[^7]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
+
+[^8]: Survey item wording and responses are included in Appendix A.
+
+[^9]: See Appendix C for Inter-item correlation analysis.
+
+[^10]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
 The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024], yet there is no general consensus on the most appropriate method generally.
@@
 
-[^12]: This range is mostly arbitrary, as a range from -1 to 1 works much the same.
+[^11]: This range is mostly arbitrary, as a range from -1 to 1 works much the same.
 When relying on simple sum total score, the scale ranges from -15 to 15.
@@
 The bipolar scale resulting from the composition of positive trust and negative distrust engenders meaning to zero and negative values.
-As such, composite mean scores become inappropriate and interpretation of scores would no longer be feasible.
 In other words, negative values on the scale for confidence in elections hold substantive meaning (e.g., distrust, absent trust), which makes transforming scores to fit a unipolar scale inappropriate.
 
-[^13]: What is interesting to note here is that the first three items regard the more human element of the election administration process, e.g., ensuring accuracy of counts, competence, and commitment of election workers.
+[^12]: What is interesting to note here is that the first three items regard the more human element of the election administration process, e.g., ensuring accuracy of counts, competence, and commitment of election workers.
 Although a neat line can't really be drawn between the first three and latter two items presented here, it is interesting to see a slight divergence from the usual high confidence placed in local area elections.

### 2025-03-19 notebooks/figures.qmd
draft 3 complete. Also full project render

@@
 }
+```
+
+```{r}
+#| label: custom-barplot
+
+# function for creating barplots
+custom_barplot <- function(data, x, group, title = NULL, subtitle = NULL,
+                           caption = NULL, legend_fill = NULL,
+                           xlab = NULL){
+  b <- data |> 
+    group_by({{ group }}, {{ x }}) |> 
+    count() |> 
+    drop_na() |> 
+    group_by({{ group }}) |> 
+  mutate(prop = round(n/sum(n), digits = 3),
+         pct = prop*100,
+         res = str_c(pct,'% (', n, ')', sep = "")) |> 
+  ggplot(aes(x = {{ x }}, y = pct, fill = {{ group }}))+
+  geom_bar(position = 'dodge', stat = 'identity')+
+  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5, vjust = -0.5)+
+  scale_fill_grey(start = 0.5, end = 0.1)
+
+  b <- b + ggplot2::labs(
+    title = title,
+    subtitle = subtitle,
+    caption = stringr::str_wrap(caption, width = 99),
+    fill = legend_fill,
+    y = "Percentage",
+    x = stringr::str_wrap(xlab, width = 85))
+  b
+}
 
@@
     variable_labels = c(q25 = 'Thinking about Maricopa County, AZ', q36 = "Thinking about Local Area"),
-    title = "Concern for Voter Intimidation, Threats, or Violence by Treatment Condition",
     subtitle = str_wrap(
@@
     )
-  )
+  )+
+  theme(
+    text = element_text(family = 'TeX Gyre Pagella'), 
+    axis.title.y.left = element_blank())
+
 ```
@@
     ),
-    title = str_wrap("Confidence for In-person voter safety at Polling Sites by Treatment", width = 95),
     subtitle = str_wrap("How confident, if at all, are you that in person polling places will be safe places for voters to cast their ballots during the upcoming elections in November?", width = 95)
-  )
+  )+
+  theme(
+    text = element_text(family = 'TeX Gyre Pagella'), 
+    axis.title.y.left = element_blank())
 
@@
 #| label: fig-patch15
+#| fig-height: 4.5
+#| fig-width: 8
 
 p15.safety.treat <- safety.concern.treat.likert/safety.conf.treat.likert+
-  patchwork::plot_layout(guides = "keep")
+  patchwork::plot_layout(guides = "keep")+
+  patchwork::plot_annotation(
+    title = str_wrap("Safety Concerns by Experiment Condition", width = 80), 
+    tag_levels = "a")
+
+p15.safety.treat
+
+```
+
+An alternative
+
+```{r}
+#| label: fig-safety
+#| layout-nrow: 2
+#| fig-height: 3.5
+#| fig-cap: "Safety Concerns by Experiment Condition"
+#| fig-subcap: 
+#|   - "Confidence for In-person voter safety at Election Sites"
+#|   - "Concern for Voter Intimidation, Threats, or Violence"
+
+# safety concerns by treatment
+safety.concern.treat.likert <- data |>
+  # Need to slightly modify text of factor levels
+  mutate(across(
+    c(q25, q36),
+    ~ pewmethods::fct_case_when(
+      .x == "Very concerned" ~ "Very concerned",
+      .x == "Somewhat concerned" ~ "Somewhat concerned",
+      .x %in% c("Not too concerned", "Somewhat unconcerned") ~ "Not too concerned",
+      .x == "Not at all concerned" ~ "Not at all concerned",
+      TRUE ~ NA
+    )
+  )) |>
+  likert_plot(
+    x = c(q25, q36),
+    y = 'group',
+    facet_rows = vars(.question),
+    facet_label_wrap = 15,
+    variable_labels = c(q25 = 'Thinking about Maricopa County, AZ', q36 = "Thinking about Local Area"),
+    subtitle = str_wrap(
+      "How concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place?",
+      width = 99
+    )
+  )+
+  theme(
+    text = element_text(family = 'TeX Gyre Pagella'), 
+    axis.title.y.left = element_blank())
+
+# In-person voter safety at election sites by treatment
+safety.conf.treat.likert <- data |>
+  likert_plot(
+    x = c(q26, q37), 
+    y = 'group',
+    facet_label_wrap = 15,
+    facet_rows = vars(.question),
+    variable_labels = c(
+      q26 = "In Maricopa County, AZ",
+      q37 = "In your local area"
+    ),
+    subtitle = str_wrap("How confident, if at all, are you that in person polling places will be safe places for voters to cast their ballots during the upcoming elections in November?", width = 95)
+  )+
+  theme(
+    text = element_text(family = 'TeX Gyre Pagella'), 
+    axis.title.y.left = element_blank())
+
+# fig a
+safety.concern.treat.likert
+
+# fig b
+safety.conf.treat.likert
 
@@
 ```
+
+## Barplots
+
+```{r}
+#| label: fig-bars-create
+#| eval: true
+#| include: false
+
+bar_q25 <- custom_barplot(
+    data = data,
+    x = q25,
+    group = group
+  ) +
+  coord_cartesian(ylim = c(0,60), expand = T)
+
+bar_q26 <- custom_barplot(
+  data = data,
+  x = q26,
+  group = group
+)  +
+  coord_cartesian(ylim = c(0,60), expand = T)
+
+bar_q36 <- custom_barplot(
+  data = data,
+  x = q36,
+  group = group
+)  +
+  coord_cartesian(ylim = c(0,60), expand = T)
+
+bar_q37 <- custom_barplot(
+  data = data,
+  x = q37,
+  group = group 
+) +
+  coord_cartesian(ylim = c(0,60), expand = T)
+
+```
+
+```{r}
+#| label: fig-bars1
+#| layout-ncol: 1
+#| layout-nrow: 2
+#| fig-cap: "Safety Concerns by Experiment Condition"
+#| fig-subcap: 
+#|   - "Concern for Violence in Maricopa County, AZ Elections"
+#|   - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"
+
+bar_q25
+bar_q26
+
+```
+
+```{r}
+#| label: fig-bars2
+#| layout-ncol: 1
+#| layout-nrow: 2
+#| fig-cap: "Safety Concerns by Experiment Condition"
+#| fig-subcap: 
+#|   - "Concern for Violence in Local Area Elections"
+#|   - "Confidence in Voter Saftey at Election Sites in Local Area"
+
+bar_q36
+bar_q37
+
+```
+
+```{r}
+#| label: fig-bars-alt
+#| layout-nrow: 2
+#| fig-cap: "Safety Concerns by Experiment Condition"
+#| fig-subcap: 
+#|   - "Concern for Violence in Maricopa County, AZ Elections"
+#|   - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"
+
+bar_q25 <- custom_barplot(
+    data = data,
+    x = q25,
+    group = group
+  ) +
+  coord_cartesian(ylim = c(0,60), expand = T)
+
+bar_q26 <- custom_barplot(
+  data = data,
+  x = q26,
+  group = group
+)  +
+  coord_cartesian(ylim = c(0,60), expand = T)
+
+bar_q36 <- custom_barplot(
+  data = data,
+  x = q36,
+  group = group
+)  +
+  coord_cartesian(ylim = c(0,60), expand = T)
+
+bar_q37 <- custom_barplot(
+  data = data,
+  x = q37,
+  group = group 
+) +
+  coord_cartesian(ylim = c(0,60), expand = T)
+
+bars1 <- (bar_q25 + bar_q26)+
+  patchwork::plot_layout(guides = "collect") &
+  theme(
+    text = element_text(family = "TeX Gyre Pagella"),
+    legend.position = "bottom", 
+    axis.title.y.left = element_blank(), 
+    axis.text.y.left = element_blank(), 
+    axis.ticks.y = element_blank())
+
+bars2 <- (bar_q36 + bar_q37)+
+  patchwork::plot_layout(guides = "collect") &
+  theme(
+    text = element_text(family = "TeX Gyre Pagella"),
+    legend.position = "bottom", 
+    axis.title.y.left = element_blank(), 
+    axis.text.y.left = element_blank(), 
+    axis.ticks.y = element_blank())
+
+bars1
+bars2
+
+```
+
+```{r}
+#| label: fig-bars-alt2
+#| layout-ncol: 2
+#| layout-nrow: 2
+#| fig-cap: "Concerns for Safety"
+#| fig-subcap:
+#|    - "Concern for Violence in Maricopa County, AZ Elections"
+#|    - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"
+#|    - "Concern for Violence in Local Area Elections"
+#|    - "Confidence in Voter Saftey at Election Sites in Local Area"
+
+bar_q25 <- custom_barplot(data = data, x = q25, group = group)
+
+bar_q26 <- custom_barplot(data = data, x = q26, group = group)
+
+bar_q36 <- custom_barplot(data = data, x = q36, group = group)
+
+bar_q37 <- custom_barplot(data = data, x = q37, group = group)
+
+bar_q25
+bar_q26
+bar_q36
+bar_q37
+
+```

### 2025-03-19 src/funs.R

@@ -180,9 +180,9 @@ custom_barplot <- function(data, x, group, title = NULL, subtitle = NULL,
   scale_fill_grey(start = 0.5, end = 0.1)
   
   b <- b + ggplot2::labs(
-    title = stringr::str_wrap(title, width = 85),
-    subtitle = stringr::str_wrap(subtitle, width = 85),
-    caption = stringr::str_wrap(caption, width = 85),
+    title = title,
+    subtitle = subtitle,
+    caption = stringr::str_wrap(caption, width = 99),
     fill = legend_fill,
     y = "Percentage",
     x = stringr::str_wrap(xlab, width = 85))
@@ -329,3 +329,38 @@ clockin <- function(date = TRUE, time = FALSE, seconds = FALSE){
 
 
 
+# fun: var_label_tab :::::::::::::::::::::::::::::::::::::::::::::::::::::::####
+
+var_label_tab <- function(x){
+    purrr::map(x, ~attr(., "label")) |>
+    purrr::map(~ifelse(purrr::is_null(.), "No label", .)) |> 
+    tibble::enframe(name = "var", value = "var_label") |>
+    tidyr::unnest(cols = c(var_label))
+}
+
+# fun: logistic regression model goodness-of-fit statistics ::::::::::::::::####
+
+# creating my own for now
+# logistic regression model goodness-of-fit statistics
+lrm.gof.stats <- function(x, ...){
+  
+  out <- data.frame(
+    null.deviance = x$null.deviance,
+    df.null = x$df.null,
+    logLik = as.numeric(stats::logLik(x)),
+    AIC = stats::AIC(x),
+    BIC = stats::BIC(x),
+    deviance = stats::deviance(x),
+    df.residual = stats::df.residual(x),
+    nobs = stats::nobs(x),
+    chisq = as.numeric(x$null.deviance - stats::deviance(x)),
+    df = as.numeric(x$df.null - stats::df.residual(x)),
+    'P(>chi)' = pchisq(q=x$null.deviance - stats::deviance(x),
+                       df = x$df.null - stats::df.residual(x), 
+                       lower.tail = F)
+  )
+  out <- dplyr::as_tibble(out)
+  return(out)
+}
+
+lrm.gof.stats(m1)

### 2025-03-19 docs/_tex/index.tex
clean repo and push to publish

@@
     \setmainfont[]{TeX Gyre Pagella}
+    \setsansfont[]{TeX Gyre Pagella}
   \setmathfont[]{TeX Gyre Pagella Math}
@@
 %\noindent \rule{\linewidth}{.5pt}
+\begin{abstract}
+In this paper, I report results from a recent survey experiment
+administered to test whether publicized efforts to recruit veterans to
+work as election staff and volunteers would improve public trust in
+elections and ease election insecurity. Results of the survey experiment
+support the notion that emphasizing veterans as the target of election
+worker recruitment efforts eases pre-election insecurity. Expectations
+of electoral fraud and concerns for voter safety were lower among those
+who read an announcement that veterans are being recruited to work as
+election staff and volunteers compared to those who read a control
+vignette where veterans were not mentioned. Notable is that there was a
+significant difference in confidence among those in the treatment
+condition who believe that results of the 2020 election were
+illegitimate. In addition, concerns over voter safety and potential for
+violence were lower among those who received the treatment.
+\end{abstract}
 %\noindent \rule{\linewidth}{.5pt}
@@
 condition who believe that results of the 2020 election were
-illegitimate.
+illegitimate. In addition, concerns over voter safety and potential for
+violence were lower among those who received the treatment.
 
@@
 accomplished by enhancing the \emph{trustworthiness} of the institution,
-i.e., consistently doing the things that election officials already
-regularly do come election time. However, trust and confidence in
-elections has become ever more precarious over the last few election
-cycles. Especially considering public polling data since 2000 shows that
-confidence that votes were, or would be, counted as intended was in a
-consistent decline despite efforts towards bolstering election integrity
-and trustworthiness (\citeproc{ref-sances2015}{Sances and Stewart
-2015}). This is even more pronounced considering the role that
-partisanship has had on such confidence over accuracy of vote count
+e.g., enhancing vote tabulation equipment and technology, conducting
+audits. However, trust and confidence in elections has become ever more
+precarious over the last few election cycles. Especially considering
+public polling data since 2000 shows that confidence that votes were, or
+would be, counted as intended was in a consistent decline despite
+efforts towards bolstering election integrity and trustworthiness
+(\citeproc{ref-sances2015}{Sances and Stewart 2015}). This is even more
+pronounced considering the role that partisanship has had on such
+confidence over accuracy of vote counts
 (\citeproc{ref-sances2015}{Sances and Stewart 2015};
@@
 influence that the election results would also have on such evaluations.
-In other words, trust evaluations post-election are influenced by one's
-interpretation of their experience and election results. This study, in
-contrast, focuses primarily on that \emph{anticipatory} kind of
-confidence, which speaks more to those insecurities based on perceptions
-of the institution's trustworthiness than upon the particular voter
-experience.
+In other words, evaluations of trust considered in hindsight are
+influenced by the voter experience and the outcome of the election
+results. This study, in contrast, focuses primarily on that
+\emph{anticipatory} kind of confidence, which speaks more to those
+insecurities based on perceptions of the institution's trustworthiness
+than upon the particular voter experience.
 
@@
 Election officials are likely to be agnostic as to who dedicates their
-time to civil service such as election work. Staffing issues have been
-an issue since at least the 1990s (\citeproc{ref-ferrer2024}{Ferrer,
-Thompson, and Orey 2024}; \citeproc{ref-maidenberg1996}{Maidenberg
-1996}). In 2020, such efforts were made far more difficult by the
-COVID-19 pandemic (\citeproc{ref-abbate2020a}{Abbate 2020};
-\citeproc{ref-mena2020}{Mena 2020}). There's no special reason to target
-veterans for recruitment above other groups. Indeed, there's no reason
-to discriminate recruitment efforts at all if the point is purely to
-fill staffing vacancies.
+time to civil service such as election work. Especially since staffing
+issues have been an issue since at least the 1990s
+(\citeproc{ref-ferrer2024}{Ferrer, Thompson, and Orey 2024};
+\citeproc{ref-maidenberg1996}{Maidenberg 1996}). In 2020, such efforts
+were made far more difficult by the COVID-19 pandemic
+(\citeproc{ref-abbate2020a}{Abbate 2020}; \citeproc{ref-mena2020}{Mena
+2020}). There's no special reason to target veterans for recruitment
+above other groups. Indeed, there's no reason to discriminate
+recruitment efforts at all if the point is purely to fill staffing
+vacancies.
 
@@
 about Maricopa County, AZ, followed by an identical block of items that
-asked the same questions about one's local area. Later, I compare and
-discuss results between the items pertaining to different settings.
+asked the same questions about one's local area. I compare and discuss
+results between the items pertaining to different settings.
 
@@
 two sets of items were utilized to construct the primary dependent
-variable, \emph{confidence in elections}.
+variable, \emph{confidence in elections}. Additionally, a pair of survey
+items assessed concerns for potential violence and confidence in voter
+safety. The pair was asked once in regard to Maricopa County, AZ and
+again with respect to one's local area\footnote{Question wording and
+  responses to a selection of survey items are included in Appendix A.}.
+Although two survey items are insufficient to serve as a composite
+scale, safety concerns will be evaluated by examination of response to
+these two questions in particular.
 
 Prior to the reading the treatment or control vignette, participants
-responded to distinct survey items assessing one's favorability to local
-election officials (``In general, how favorable or unfavorable is your
-impression of local election officials?'') and legitimacy of the 2020
-election results (``Regardless of whom you supported in the 2020
-election, do you think Joe Biden's election as president was legitimate,
-or was he not legitimately elected?''). The former presented five
-response options from ``Strongly favorable'' to ``Strongly
-unfavorable''; the latter item presented a binary of either
-``Legitimate'' or ``Not Legitimate''.
+responded to distinct survey items assessing one's beliefs about the
+legitimacy of the 2020 election results (``Regardless of whom you
+supported in the 2020 election, do you think Joe Biden's election as
+president was legitimate, or was he not legitimately elected?'').
+Respondents selected either ``Legitimate'' or ``Not Legitimate''.
 
@@
 categories: Democrat, Republican, and independent.
-
-Finally, a pair of survey items assessed concerns for potential violence
-and confidence in voter safety. The pair was asked once in regard to
-Maricopa County, AZ and again with respect to one's local
-area\footnote{Survey item wording and responses are included in Appendix
-  A.}.
 

### 2025-03-19 docs/index.qmd
clean repo and push to publish

@@
 ---
-title: title
-subtitle: subtitle
-shorttitle: A Short title # aog-article-pdata
-shortauthors: Isaiah      # aog-article-pdata
+title: 'Inspiring Confidence and Easing Insecurity in the Pre-election period: The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections'
+# subtitle: 'The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections'
+shorttitle: 'Effect of Recruiting Military Veterans on Confidence in 2024 US Elections' # aog-article-pdf
+shortauthors: Isaiah      # aog-article-pdf
+abstract: |
+  In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
+Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
+Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned.
+Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
+In addition, concerns over voter safety and potential for violence were lower among those who received the treatment.
 authors:
@@
 reference-section-title: References
-date: "2024-10-16"
-date-modified: today
 knitr: 
@@
 library(tidyverse)
+library(modelsummary)
+library(tinytable) # simple tables in html, LaTeX, markdown, word, pdf, typst
+library(litedown)
+library(ordinal)
+library(marginaleffects)
 library(easystats)
-library(odds.n.ends) # model sig from glm
 library(patchwork)
-library(texreg) # Conversion of R regression output into latex or HTML tables
+
+# set some session options for `tinytable`
+options(tinytable_tt_digits = 3)
+# options(tinytable_theme_placement_latex_float = "H")
+options(tinytable_html_mathjax = TRUE) # set option to render math in html
 
@@
 
-# load data dictionary/codebook
-codebook <- read.csv("data/survey_codebook.csv")
-data_dict <- read.csv("data/data_dictionary.csv")
-```
-
-```{r}
-#| label: setup-theme
-
-# set ggplot theme that will be used for every plot
-# theme_get()
-old <- ggplot2::theme_set(ggplot2::theme_bw())  # capture current theme
-
-# set/update new theme
-ggplot2::theme_set(
-  new = ggplot2::theme_bw(
-    base_family = 'TeX Gyre Pagella')+ # set font of ggplots
-    theme(legend.position = 'bottom')  # set legend position for all plots
+```
+
+```{r}
+#| label: fun-likert-plot
+
+# custom function used to create Likert Plots
+
+# To avoid excessive copy/paste, I made a function to create Likert plots
+# it is mostly a wrapper around `ggstats::gglikert`, but with a specific set up
+# particular colors, theme, etc. 
+likert_plot <- function(data, x, ...,  
+                        symmetric = FALSE,
+                        variable_labels = NULL,
+                        label_size = 2.5,
+                        vline = FALSE,
+                        title = waiver(), 
+                        subtitle = waiver(),
+                        caption = waiver(),
+                        xlab = waiver()){
+
+  p <- ggstats::gglikert(
+    data = data, include = {{ x }}, ...,
+    variable_labels = variable_labels,
+    symmetric = symmetric)+
+
+    # customize color
+    ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
+    # custom theme
+    theme_bw(base_family = "TeX Gyre Pagella")+
+    theme(
+      legend.position = 'bottom',  # place legend on bottom
+      axis.title.y.left = element_blank(), # blank out y-axis label
+      axis.text.x = element_blank(), # remove percentage text along x-axis
+      strip.text.y.right = element_text(angle = 0) # make facet label horizontal
         )
 
-```
-
-\pagebreak
+    if (vline==TRUE) {
+    p <- p + geom_vline(xintercept = 0, color = 'black', linewidth = 1.2)
+  } else {
+      p
+  }
+
+  p <- p + ggplot2::labs(..., title = title, subtitle=subtitle, caption=caption, x = xlab)
+  p
+
+}
+
+```
+
+```{r}
+#| label: fun-barplot
+
+# function for creating barplots
+custom_barplot <- function(data, x, group, title = NULL, subtitle = NULL,
+                           caption = NULL, legend_fill = NULL,
+                           xlab = NULL){
+  b <- data |> 
+    group_by({{ group }}, {{ x }}) |> 
+    count() |> 
+    drop_na() |> 
+    group_by({{ group }}) |> 
+  mutate(prop = round(n/sum(n), digits = 3),
+         pct = prop*100,
+         res = str_c(pct,'% (', n, ')', sep = "")) |> 
+  ggplot(aes(x = {{ x }}, y = pct, fill = {{ group }}))+
+  geom_bar(position = 'dodge', stat = 'identity')+
+  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5, vjust = -0.7)+
+  scale_fill_grey(start = 0.5, end = 0.1)
+
+  b <- b + ggplot2::labs(
+    title = title,
+    subtitle = subtitle,
+    caption = stringr::str_wrap(caption, width = 99),
+    fill = legend_fill,
+    y = "Percentage",
+    x = stringr::str_wrap(xlab, width = 85))
+  b
+}
+
+```
+
+```{r}
+#| label: fun-logit-gof
+
+# custom function to return a certain selection of logistic regression model
+# goodness-of-fit statistics
+lrm.gof.stats <- function(x, ...){
+
+  out <- data.frame(
+    null.deviance = x$null.deviance,
+    df.null = x$df.null,
+    logLik = as.numeric(stats::logLik(x)),
+    AIC = stats::AIC(x),
+    BIC = stats::BIC(x),
+    deviance = stats::deviance(x),
+    df.residual = stats::df.residual(x),
+    nobs = stats::nobs(x),
+    chisq = as.numeric(x$null.deviance - stats::deviance(x)),
+    df = as.numeric(x$df.null - stats::df.residual(x)),
+    'P(>chi)' = pchisq(q=x$null.deviance - stats::deviance(x),
+                       df = x$df.null - stats::df.residual(x), 
+                       lower.tail = F)
+  )
+  out <- dplyr::as_tibble(out)
+  return(out)
+}
+
+```
+
+{{< pagebreak >}}
 
@@
 Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
-Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned[^3].
+Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned[^2].
 Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
+In addition, concerns over voter safety and potential for violence were lower among those who received the treatment.
 
@@
 
-Intuitively, enhancing public trust in elections would best be accomplished by enhancing the *trustworthiness* of the institution, i.e., consistently doing the things that election officials already regularly do come election time.
+Intuitively, enhancing public trust in elections would best be accomplished by enhancing the *trustworthiness* of the institution, e.g., enhancing vote tabulation equipment and technology, conducting audits.
 However, trust and confidence in elections has become ever more precarious over the last few election cycles.
 Especially considering public polling data since 2000 shows that confidence that votes were, or would be, counted as intended was in a consistent decline despite efforts towards bolstering election integrity and trustworthiness [@sances2015].
-This is even more pronounced considering the role that partisanship has had on such confidence over accuracy of vote count [@sances2015; @stewart2022].
+This is even more pronounced considering the role that partisanship has had on such confidence over accuracy of vote counts [@sances2015; @stewart2022].
 
@@
 Not to mention the influence that the election results would also have on such evaluations.
-In other words, trust evaluations post-election are influenced by one's interpretation of their experience and election results.
+In other words, evaluations of trust considered in hindsight are influenced by the voter experience and the outcome of the election results.
 This study, in contrast, focuses primarily on that *anticipatory* kind of confidence, which speaks more to those insecurities based on perceptions of the institution's trustworthiness than upon the particular voter experience.
@@
 Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work.
-Staffing issues have been an issue since at least the 1990s [@maidenberg1996; @ferrer2024].
+Especially since staffing issues have been an issue since at least the 1990s [@maidenberg1996; @ferrer2024].
 In 2020, such efforts were made far more difficult by the COVID-19 pandemic [@mena2020; @abbate2020a].
@@
 A block of survey items asked specifically about Maricopa County, AZ, followed by an identical block of items that asked the same questions about one's local area.
-Later, I compare and discuss results between the items pertaining to different settings.
+I compare and discuss results between the items pertaining to different settings.
 
@@
 Responses from these two sets of items were utilized to construct the primary dependent variable, *confidence in elections*.
-
-Prior to the reading the treatment or control vignette, participants responded to distinct survey items assessing one's favorability to local election officials ("In general, how favorable or unfavorable is your impression of local election officials?") and legitimacy of the 2020 election results ("Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected?").
-The former presented five response options from "Strongly favorable" to "Strongly unfavorable"; the latter item presented a binary of either "Legitimate" or "Not Legitimate".
+Additionally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
+The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^8].
+Although two survey items are insufficient to serve as a composite scale, safety concerns will be evaluated by examination of response to these two questions in particular.
+
+Prior to the reading the treatment or control vignette, participants responded to distinct survey items assessing one's beliefs about the legitimacy of the 2020 election results ("Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected?").
+Respondents selected either "Legitimate" or "Not Legitimate".
 
 The conventional multiple item assessment of partisanship was included and used to construct a variable of partisanship consisting of three categories: Democrat, Republican, and independent.
-
-Finally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
-The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^9].
 
@@
 
-kableExtra::kbl(conf_items_text, booktabs = T,
-                col.names = c("Trust", "Distrust"),
-                linesep = "\\addlinespace") |> 
-  kableExtra::kable_styling(full_width = T,
-                            font_size = 8,
-                            latex_options = c("HOLD_position")) |> 
-  kableExtra::column_spec(column = 1:2, width = "8cm")
+tinytable::tt(conf_items_text, width = c(.5, .5)) |> 
+  tinytable::style_tt(fontsize = 0.80)
 
@@
     .before = Diff) |> 
-  insight::format_table(stars = T) |> 
-  # insight::export_table(format = "md") # alternate
-  # output table as `kable` for LaTeX pdata
-  kableExtra::kbl( 
-    booktabs = T,
-    col.names = c("Place", "$\\bar{x}_{diff}$", "$\\bar{x}_{treat}$", "$\\bar{x}_{control}$",
-                  "$treat_{n}$", "$control_{n}$", "t", "p", "data", "CI"), 
-    escape = F) |> 
-  kableExtra::footnote(general = "Welch Two Sample t-tests of difference between Confidence in Elections by Treatment Condition.") |> 
-  kableExtra::kable_styling(
-    font_size = 9, 
-    protect_latex = T)
+  insight::format_table(stars = T)
+
+# Output using `tinytable` R Package
+colnames(tab_ttest) <- c(
+  "Place",
+  "$\\bar{x}_{diff}$",
+  "$\\bar{x}_{treat}$",
+  "$\\bar{x}_{control}$",
+  "$n_{treat}$",
+  "$n_{control}$",
+  "t",
+  "p",
+  "df",
+  "CI")
+
+tinytable::tt(tab_ttest) |>
+  tinytable::format_tt(
+    j = 2:6, # specify columns  
+    math = T # apply mathmode to specified columns
+  ) |> 
+  tinytable::style_tt(fontsize = 0.75) # fontsize in em units (0.75*default fontsize)
 
@@
 
-::: {.content-visible when-format="bookup-html" unless-format="submittable-pdf"}
+::: {.content-visible when-format="bookup-html" unless-format="pdf"}
 
@@
 
-::: {.content-visible when-format="submittable-pdf" unless-format="bookup-html"}
+::: {.content-visible when-format="pdf" unless-format="bookup-html"}
 
@@
 
+### Concerns for Violence and Voter Safety
+
+Thus far, publicized announcements that election officials will be targeting veterans in their recruitment efforts does quite a bit to improve confidence in elections outside of one's local area (or, at least for elections held in Maricopa County, AZ), especially among those who believed the 2020 election results were illegitimate.
+While distrust is one concern during the pre-election period, it is not the only concern that arises in anticipation of US elections; the public must feel confident that voters are safe to cast a ballot in person.
+The survey included questions^[See @tbl-4 in Appendix A] that allows me to assess whether those in the treatment condition expressed less concern for violence and more confidence in voter safety compared to those in the control condition.
+```{r}
+#| label: fig-safety-bars
+#| layout-ncol: 1
+#| layout-nrow: 2
+#| fig-cap: "Safety Concerns and Confidence by Treatment Condition"
+#| fig-subcap: 
+#|   - "Concern for Violence while voting in Maricopa County, AZ Elections"
+#|   - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"
+
+# concern for violence by treatment
+bar_q25 <- custom_barplot(
+  data = data, 
+  x = q25, 
+  group = group,
+  subtitle = str_wrap(attr(data$q25, "label"), width = 85)
+  )+
+  theme(text = element_text(family = 'TeX Gyre Pagella'),
+        legend.position = "right")
+
+# confidence in voter safety by treatment
+bar_q26 <- custom_barplot(
+  data = data, 
+  x = q26, 
+  group = group,
+  subtitle = str_wrap(attr(data$q26, "label"), width = 85)
+  )+
+  theme(text = element_text(family = 'TeX Gyre Pagella'),
+        legend.position = "right")
+
+bar_q25
+bar_q26
+
+```
+
+Briefly reviewing @fig-safety-bars, those in the treatment condition felt less concern over the potential for violence compared to those in the control.
+As for confidence in voter safety at election sites, it appears that more respondents in the treatment condition expressed that they were "Very confident" compared to those in the control, by approximately $8$ percentage points.
+
+It would appear that the treatment vignette increased the likelihood that a respondent would select a higher response option compared to those in the control group.
+In order to assess whether that was the case, I conducted an ordered logistic regression on the relevant items using the experimental condition as a dichotomous predictor.
+
+Those in the treatment condition had lower probability to express that they were 'Very' or 'Somewhat' concerned for violence in Maricopa County, AZ Elections, yet higher probability of expressing 'Not too' or 'Not at all' concerned.
+As for confidence in voter safety, moving from treatment to control, the difference in predicted probability of a respondent selecting "Very Confident" was $0.08$.
+@tbl-preds-diff1 and @tbl-preds-diff2 show the significant differences in predicted probabilities at 95$\%$ confidence^[The same models were run for items pertaining to safety concerns in one's local area but results of the treatment were not significantly different from the control.
+See Appendix D for full results table of ordinal logistic regression].
+
+```{r}
+#| label: ordinal-logit
+#| include: false
+
+# needed to duplicate `group` variable with different column name due to
+# conflict with marginaleffects R package
+data <- data |>
+  mutate(condition = group)
+
+# running ordinal logisitc regression models (proportional odds logistic regression)
+m.q25 <- MASS::polr(q25 ~ condition, data = data, method = "logistic", Hess = T)
+m.q26 <- MASS::polr(q26 ~ condition, data = data, method = "logistic", Hess = T)
+m.q36 <- MASS::polr(q36 ~ condition, data = data, method = "logistic", Hess = T)
+m.q37 <- MASS::polr(q37 ~ condition, data = data, method = "logistic", Hess = T)
+
+# "Outcome predicted by a fitted model on a specified scale for a given
+# combination of values of the predictor variables, such as their observed
+# values, their means, or factor levels (a.k.a. "reference grid")".
+
+# predictions(): unit-level (conditional) estimates.
+
+# predicted probability estimates by treatment or control
+q25_preds <- marginaleffects::predictions(m.q25, by = "condition", type = "probs")
+q26_preds <- marginaleffects::predictions(m.q26, by = "condition", type = "probs")
+q36_preds <- marginaleffects::predictions(m.q36, by = "condition", type = "probs")
+q37_preds <- marginaleffects::predictions(m.q37, by = "condition", type = "probs")
+
+# this provides the difference in predicted probabilities between treatment and
+# control
+pdiff_q25 <- marginaleffects::predictions(
+  m.q25,
+  by = "condition",
+  type = "probs",
+  hypothesis = ~ reference | group
+)
+
+pdiff_q26 <- marginaleffects::predictions(
+  m.q26,
+  by = "condition",
+  type = "probs",
+  hypothesis = ~ reference | group
+)
+
+```
+
+```{r}
+#| label: tbl-preds-diff1
+#| tbl-colwidths: 80
+#| tbl-cap: "Difference in Predicted Probabilities in Concern for violence, Threats of Violence, or Intimidation between Treatment and Control"
+
+tab_q25_pdiff <- pdiff_q25 |>
+  dplyr::as_tibble() |>
+  dplyr::rename(
+    Violence = group,
+    z = statistic,
+    'Pr(>|z|)' = p.value) |>
+  select(Violence,
+         hypothesis,
+         estimate,
+         std.error,
+         z,
+         'Pr(>|z|)',
+         conf.low,
+         conf.high) |>
+  insight::format_table(stars = T, digits = 3)
+
+tinytable::tt(
+  tab_q25_pdiff, 
+  notes = "Results derived from proportional odds logistic regression model.
+Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |>
+  tinytable::style_tt(
+    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    ) |>  
+  tinytable::style_tt(i = "notes", fontsize = 0.75)
+
+```
+
+```{r}
+#| label: tbl-preds-diff2
+#| tbl-colwidths: 80
+#| tbl-cap: "Difference in Predicted Probabilities in Confidence that voters will be safe to vote in-person between Treatment and Control"
+
+tab_q26_pdiff <- pdiff_q26 |>
+  dplyr::as_tibble() |>
+  dplyr::rename('Voter Safety' = group,
+                z = statistic,
+                'Pr(>|z|)' = p.value) |>
+  select('Voter Safety',
+         hypothesis,
+         estimate,
+         std.error,
+         z,
+         'Pr(>|z|)',
+         conf.low,
+         conf.high) |>
+  insight::format_table(stars = T, digits = 4)
+
+tinytable::tt(
+  tab_q26_pdiff, 
+  notes = "Results derived from proportional odds logistic regression model.
+Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |>
+  tinytable::style_tt(
+    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    ) |>  
+  tinytable::style_tt(i = "notes", fontsize = 0.75) # style font of table notes
+
+```
+
+\newpage
+
 ## Conclusion
 
-Publicized announcements that election officials are actively recruiting former military service members to work as election staff and volunteers is associated with slightly greater confidence in elections compared to election worker recruitment announcements that do not explicitly mention targeted recruitment of former military service members.
-Moreover, increased levels of confidence is limited to elections beyond one's local area and, of course, in anticipation of election night.
+Publicized announcements that election officials are actively recruiting former military service members to work as election staff and volunteers is associated with greater confidence in elections compared to election worker recruitment announcements that do not explicitly mention targeted efforts to recruit former military service members.
+In addition, such public announcements eased concerns about violence and increased confidence that voters would be safe to vote in person at election sites.
+Of course, the higher levels of confidence in elections and voter safety observed among the treatment group were limited to considerations about elections held in Maricopa County, AZ---presumably beyond one's local area.
+This is to be expected bearing in mind that confidence in elections for one's local area is usually higher than for those beyond.
+Thus, there's already more insecurity concerning elections elsewhere for whatever reason.
+
+One obvious contribution of these results shows that the perceived trustworthiness of elections administration is amendable to generalized impressions about the kind and character of the people who work and volunteer as election staff.
+Whatever election officials do to boost public confidence may be overshadowed by impressions about who is staffing election sites.
+
+It should be noted that these results are limited to one's expectations in anticipation of election night.
 Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
-
-Bear in mind that confidence in elections for one's local area is already higher than for those beyond.
-Thus, there's already more insecurity concerning elections elsewhere for whatever reason.
-In the anticipatory period prior to national elections, publicized efforts to recruit veterans to work as election staff and volunteers may be a small, but positive, step towards reducing insecurity in elections that occur elsewhere.
-Especially among those who maintained a steadataast degree of distrust in elections.
-Despite a lack of evidence that systematic electoral fraud had occurred in the 2020 election, a substantial proportion of the population were unwilling to affirm the legitimacy of the results.
-However, despite such legitimacy beliefs, most were not consistent as they expressed varying levels of trust in different aspects of elections administration.
-
-These results speaks more to the influence that military veterans have among those who distrust the electoral process and refute the legitimacy of prior outcomes than it does to the public more generally.
+Moreover, It is yet unclear whether actually encountering and interacting with veterans working as staff or volunteers at election sites does much to improve voter confidence after election night compared to anyone else.
+It may be the case that assumptions that veterans are filling spots as election workers and volunteers simply primes positive expectations as one heads into an election site, potentially improving voters perceptions of their own experience on the way out.
+Further research would be needed to test such an idea.
+
 In general, public confidence appears strongest when the elections under consideration regard those within one's local community.
@@
 #| tbl-cap: "Survey Items and Response Options"
-
-data |> 
-  select(q6, q7, q25, q26) |> 
-  labelled::generate_dictionary() |> 
-  dplyr::as_tibble() |> 
-  mutate(value_labels = dplyr::case_when(
-    variable == 'q6' ~ "[Strongly unfavorable, Somewhat unfavorable, Neither, Somewhat favorable, Strongly favorable]",
-    variable == 'q7' ~ "Legitimate, Not legitimate",
-    variable == 'q25' ~ "Very concerned, Somewhat concerned, Not too concerned, Not at all concerned",
-    variable == 'q26' ~ "Not at all confident, Not too confident, Somewhat confident, Very confident"
-  )) |> 
-  select(Question = label, response = value_labels) |> 
-  kableExtra::kbl(booktabs = T, linesep = "\\addlinespace") |> 
-  kableExtra::kable_styling(full_width = T,
-                            font_size = 8,
-                            latex_options = c("HOLD_position")) |> 
-  kableExtra::column_spec(column = 1, width = "7cm") |> 
-  kableExtra::column_spec(column = 2, width = "4cm")
+#| tbl-colwidths: [70, 30]
+
+var_label_tab <- function(x){
+    purrr::map(x, ~attr(., "label")) |>
+    purrr::map(~ifelse(purrr::is_null(.), "No label", .)) |>
+    tibble::enframe(name = "var", value = "var_label") |>
+    tidyr::unnest(cols = c(var_label))
+}
+
+Questions <- data |> 
+  dplyr::select(q7, q25, q26, q36, q37) |>
+  dplyr::rename_with(.cols = everything(), .fn = ~snakecase::to_any_case(.,case = "upper_camel")) |> 
+  var_label_tab() |>
+  dplyr::select(Question = var_label) |> 
+  dplyr::pull(Question)
+
+items_responses <- data.frame(
+  Questions = Questions,
+  Response =c(
+    "- Legitimate\n- Not legitimate",
+    "- Very concerned\n- Somewhat concerned\n- Not too concerned\n- Not at all concerned",
+    "- Not at all confident\n- Not too confident\n- Somewhat confident\n- Very confident",
+    "- Very concerned\n- Somewhat concerned\n- Somewhat unconcerned\n- Not at all concerned",
+    "- Not at all confident\n- Not too confident\n- Somewhat confident\n- Very confident")
+)
+
+# wrap in a minipage environment
+minipagify <- function(x) {
+  sprintf(
+    "\\minipage{\\textwidth}%s\\endminipage",
+    sapply(x, mark, "latex")
+  )
+}
+
+# only in LaTeX
+is_latex <- identical(knitr::pandoc_to(), "latex")
+
+tab <- tinytable::tt(items_responses, width = c(0.7, 0.3)) |>
+  tinytable::style_tt(j = c(1,2), fontsize = 0.8, align = "l") |>
+  tinytable::format_tt(markdown = TRUE) |>
+  tinytable::format_tt(j = 2, fn = if (is_latex) minipagify else NULL)
+
+tab
 
@@
 
-[^2]: There's little that could justify a conceptual distinction between public trust pre-election and public trust post-election.
-The temporal element renders the difference between pre- and post-election more operative than conceptual at a foundational level.
-
-[^3]: The vignettes written were based on real news stories
-
-[^4]: To be clear, I conducted an auxiliary regression analysis to examine the relationship between legitimacy beliefs and partisanship.
+[^2]: The vignettes written were based on real news stories
+
+[^3]: To be clear, I conducted an auxiliary regression analysis to examine the relationship between legitimacy beliefs and party ID.
 Results revealed a statistically significant relationship between the two variables and thus omitting either would result in biased estimates.
 
-[^5]: Demographic breakdown of the sample are included in Appendix B.
-
-[^6]: The article vignettes were written and designed by Michael Hanmer Ph.D and myself with input from We the Veterans, a non-profit organization
-
-[^7]: Complete text of treatment and control vignettes are included in the Appendix
-
-[^8]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
-
-[^9]: Survey item wording and responses are included in Appendix A.
-
-[^10]: See Appendix C for analysis.
-
-[^11]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
+[^4]: Demographic breakdown of the sample are included in Appendix B.
+
+[^5]: The article vignettes were written and designed by Michael Hanmer Ph.D and myself with input from We the Veterans, a non-profit organization
+
+[^6]: Complete text of treatment and control vignettes are included in Appendix A
+
+[^7]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
+
+[^8]: Question wording and responses to a selection of survey items are included in Appendix A.
+
+[^9]: See Appendix C for Inter-item correlation analysis.
+
+[^10]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
 The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024], yet there is no general consensus on the most appropriate method generally.

### 2025-03-19 docs/src/01-data-clean-process.R

@@ -1,1106 +1,0 @@
-# load, clean, and process data imported from Qualtrics
-# using data exported from Qualtrics on 2024-10-29 at 12:02 PM
-
-
-# load packages ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
-library(tidyverse)
-library(haven)
-library(surveytoolbox)
-library(labelled)
-library(sjlabelled)
-
-
-# load data ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
-
-# load raw SPSS export (includes display order vars)
-# downloaded on 2024-10-29 at 12:02 PM
-raw_spss <- haven::read_sav("data-raw/VMF_Election_Worker_Recruitment_Survey_with_display_order_20241029_T12.02.sav")
-
-# sanitize data downloaded from Qualtrics (i.e., remove PII) :::::::::::::::####
-
-# rename select variables. Identify Lucid embedded variable columns
-raw_spss_sanitized <- raw_spss |> 
-  # select and remove sensitive PII variables (e.g., IPAddress, Location)
-  dplyr::select(
-    -IPAddress,
-    -LocationLatitude,
-    -LocationLongitude,
-    -RecipientFirstName,
-    -RecipientLastName,
-    -RecipientEmail
-    )
-
-# create and save survey codebook ::::::::::::::::::::::::::::::::::::::::::####
-
-# this includes only the survey questions: question number (var), the question
-# text (label_var), the value labels (label_val), and the numeric codes (value)
-codebook <- raw_spss_sanitized |> 
-  janitor::clean_names() |> 
-  # get rid of superfluous Qualtrics columns
-  # Keep Qualtrics `response_id`
-  select(!1:7, !9:11, -q_data_policy_violations) |>
-  # subset spss data set to omit the display order variables
-  select(!contains("_do_")
-         & !contains("_ado_")
-         & !contains("_click")
-         & !contains("_count")) |>
-  select(contains("q"), group) |>
-  surveytoolbox::data_dict()
-
-# create data dictionary of sanitized raw SPSS data set ::::::::::::::::::::####
-
-# create data dictionary (I prefer output from surveytoolbox)
-raw_spss_sanitized_data_dict <- raw_spss_sanitized |> 
-  surveytoolbox::data_dict()
-
-
-
-# clean up data set ::::::::::::::::::::::::::::::::::::::::::::::::::::::::####
-
[…]

### 2025-03-19 src/01-data-clean-process.R

@@ -1075,6 +1075,11 @@ data <- data |>
 save(data, file = "data/research-paper-data-20241029.Rdata")
 write.csv(data, file = "data/research-paper-data-20241029.csv")
 
+# Save sanitized raw data set for use as resource in manuscript
+haven::write_sav(
+  data = raw_spss_sanitized, 
+  path = "data/vmf_election_worker_recruitment_survey_raw_spss_sanitized_20241029_T12.02.sav")
+
 
 # save a data dict that can be saved as .csv
 # generate data dictionary
@@ -1083,19 +1088,13 @@ write.csv(data, file = "data/research-paper-data-20241029.csv")
 # labelled::generate_dictionary() because the codebook produced by the former is
 # preferred.
 data_dict <- surveytoolbox::data_dict(data)
-write.csv(data_dict, file = "data/data_dictionary.csv")
+write.csv(data_dict, file = "codebooks/data_dictionary.csv")
 
 # save data dictionary of raw_spss_sanitized dataset download
-write.csv(raw_spss_sanitized_data_dict, file = "data/raw_spss_sanitized_data_dict.csv")
+write.csv(raw_spss_sanitized_data_dict, file = "codebooks/raw_spss_sanitized_data_dict.csv")
 
 # save codebook as .csv file in data/ directory
-write.csv(codebook, file = "data/survey_codebook.csv")
-
-
-# Save sanitized raw data set for use as resource in manuscript
-haven::write_sav(
-  data = raw_spss_sanitized, 
-  path = "data/vmf_election_worker_recruitment_survey_raw_spss_sanitized_20241029_T12.02.sav")
+write.csv(codebook, file = "codebooks/survey_codebook.csv")
 
 
 # Delete unnecessary objects from global environment :::::::::::::::::::::::####

### 2025-03-19 index.qmd
minor fix to index.qmd

@@
 shortauthors: Isaiah      # aog-article-pdf
+abstract: |
+  In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
+Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
+Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned.
+Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
+In addition, concerns over voter safety and potential for violence were lower among those who received the treatment.
 authors:
@@
 library(tinytable) # simple tables in html, LaTeX, markdown, word, pdf, typst
-library(litedown)
-# library(MASS)
-# library(ordinal)
-# library(marginaleffects)
-# library(easystats)
-# library(patchwork)
+library(ordinal)
+library(marginaleffects)
+library(easystats)
+library(patchwork)
 
@@
 
-# apply Quarto data processing to all tables
-# theme_quarto <- function(x) format_tt(x, quarto = TRUE)
-# options(tinytable_tt_theme = theme_quarto)
-
 # load data
 load("data/research-paper-data-20241029.Rdata")
-
-# load data dictionary/codebook
-codebook <- read.csv("data/survey_codebook.csv")
-data_dict <- read.csv("data/data_dictionary.csv")
 
@@
 Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
+In addition, concerns over voter safety and potential for violence were lower among those who received the treatment.
 
@@
 Responses from these two sets of items were utilized to construct the primary dependent variable, *confidence in elections*.
-
-Prior to the reading the treatment or control vignette, participants responded to distinct survey items assessing one's favorability to local election officials ("In general, how favorable or unfavorable is your impression of local election officials?") and legitimacy of the 2020 election results ("Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected?").
-The former presented five response options from "Strongly favorable" to "Strongly unfavorable"; the latter item presented a binary of either "Legitimate" or "Not Legitimate".
+Additionally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
+The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^8].
+Although two survey items are insufficient to serve as a composite scale, safety concerns will be evaluated by examination of response to these two questions in particular.
+
+Prior to the reading the treatment or control vignette, participants responded to distinct survey items assessing one's beliefs about the legitimacy of the 2020 election results ("Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected?").
+Respondents selected either "Legitimate" or "Not Legitimate".
 
 The conventional multiple item assessment of partisanship was included and used to construct a variable of partisanship consisting of three categories: Democrat, Republican, and independent.
-
-Finally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
-The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^8].
 
@@
   tinytable::style_tt(fontsize = 0.80)
-
-# kableExtra::kbl(conf_items_text, booktabs = T,
-#                 col.names = c("Trust", "Distrust"),
-#                 linesep = "\\addlinespace") |> 
-#   kableExtra::kable_styling(full_width = T,
-#                             font_size = 8,
-#                             latex_options = c("HOLD_position")) |> 
-#   kableExtra::column_spec(column = 1:2, width = "8cm")
 
@@
 
-# output table as `kable` for LaTeX pdf
-# kableExtra::kbl(
-#   tab_ttest,
-#   booktabs = T,
-#   col.names = c(
-#     "Place",
-#     "$\\bar{x}_{diff}$",
-#     "$\\bar{x}_{treat}$",
-#     "$\\bar{x}_{control}$",
-#     "$treat_{n}$",
-#     "$control_{n}$",
-#     "t",
-#     "p",
-#     "data",
-#     "CI"
-#   ),
-#   escape = F
-# ) |>
-#   kableExtra::footnote(general = "Two Sample t-tests of difference between Confidence in Elections by Treatment Condition.") |>
-#   kableExtra::kable_styling(font_size = 9, protect_latex = T)
-
 ```
@@
 
-  # kableExtra::kbl(tab_q25_pdiff, 
-  #                 booktabs = T) |> 
-  # kableExtra::footnote(general = "Results derived from proportional odds logistic regression model.
-Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher")
 ```
@@
 
-  # kableExtra::kbl(tab_q26_pdiff, 
-  #                 booktabs = T) |> 
-  # kableExtra::footnote(general = "Results derived from proportional odds logistic regression model.
-Estimates are differences in predicted probabitilites transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher")
-
 ```
@@
 tab
-
-# 
-# Response <- data |> 
-#   dplyr::select(q7, q25, q26, q36, q37) |>
-#   surveytoolbox::data_dict() |> 
-#   dplyr::as_tibble() |> 
-#   dplyr::select(value)
-# 
-# 
-# item_table <- data |> 
-#   select(q7, q25, q26, q36, q37) |>
-#   dplyr::rename_with(.cols = everything(), .fn = ~snakecase::to_any_case(.,case = "upper_camel")) |> 
-#   var_label_tab() |>
-#   select(Question = var_label) |> 
-#   mutate(Response = Response$value)
-# 
-# item_table
-# 
-# tinytable::tt(item_table, width = c(.7, .3)) |> 
-#   tinytable::style_tt(fontsize = 0.80)
-
-# alternate
-# kableExtra::kbl(item_table, booktabs = T, linesep = "\\addlinespace[2mm]") |> 
-#   kableExtra::kable_styling(
-#     full_width = T,
-#     font_size = 9,
-#     latex_options = c("HOLD_position")
-#     ) |> 
-#   kableExtra::pack_rows(index = c("Legitimacy" = 1,
-#                                   "Safety Concerns" = 4))
 
@@
 
-[^8]: Survey item wording and responses are included in Appendix A.
+[^8]: Question wording and responses to a selection of survey items are included in Appendix A.
 

### 2025-03-19 docs/_tex/index.tex
reformated tables in appendix

@@
 \newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{wrapfig}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{xcolor}
 \usepackage{dcolumn}
+\usepackage{etoolbox}
+\AtBeginEnvironment{longtblr}{\begin{singlespacing}}
+\AtEndEnvironment{longtblr}{\end{singlespacing}}
 \makeatletter
@@
 
-\centering\begingroup\fontsize{9}{11}\selectfont
-
-\begin{tabular}{lcccc}
+\centering
+\begin{tblr}[         %% tabularray outer open
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]Q[]},
+column{1,2,3,4}={}{font=\fontsize{0.7em}{1em}\selectfont,},
+rowsep={0.1em}, colsep = {0.5em},
+}                     %% tabularray inner close
 \toprule
-\textbf{Demographic} & \textbf{N} & \makecell[c]{\textbf{Overall}\ \ \\N = 1,287} & \makecell[c]{\textbf{Control}\ \ \\N = 637} & \makecell[c]{\textbf{Treatment}\ \ \\N = 650}\\
-\midrule
-\textbf{Age group} & 1,287 &  &  & \\
-\hspace{1em}18-34 &  & 350 (27\%) & 170 (27\%) & 180 (28\%)\\
-\hspace{1em}35-54 &  & 480 (37\%) & 245 (38\%) & 235 (36\%)\\
-\hspace{1em}55-74 &  & 390 (30\%) & 198 (31\%) & 192 (30\%)\\
-\hspace{1em}75-85+ &  & 67 (5.2\%) & 24 (3.8\%) & 43 (6.6\%)\\
-\addlinespace
-\textbf{Gender} & 1,272 &  &  & \\
-\hspace{1em}Male &  & 598 (47\%) & 289 (46\%) & 309 (48\%)\\
-\hspace{1em}Female &  & 658 (52\%) & 330 (52\%) & 328 (51\%)\\
-\hspace{1em}Other/Refused &  & 16 (1.3\%) & 10 (1.6\%) & 6 (0.9\%)\\
-\hspace{1em}NA &  & 15 & 8 & \vphantom{4} 7\\
-\addlinespace
-\textbf{Race/Ethnicity} & 1,272 &  &  & \\
-\hspace{1em}White &  & 975 (77\%) & 478 (76\%) & 497 \vphantom{1} (77\%)\\
-\hspace{1em}Asian &  & 51 (4.0\%) & 25 (4.0\%) & 26 (4.0\%)\\
-\hspace{1em}Black &  & 164 (13\%) & 85 (14\%) & 79 (12\%)\\
-\hspace{1em}Other &  & 24 (1.9\%) & 12 (1.9\%) & 12 (1.9\%)\\
-\addlinespace
-\hspace{1em}Hispanic &  & 44 (3.5\%) & 24 (3.8\%) & 20 (3.1\%)\\
-\hspace{1em}American Indian &  & 14 (1.1\%) & 5 (0.8\%) & 9 (1.4\%)\\
-\hspace{1em}NA &  & 15 & 8 & \vphantom{3} 7\\
-\textbf{White or Non-White} & 1,272 &  &  & \\
-\hspace{1em}Non-White &  & 297 (23\%) & 151 (24\%) & 146 (23\%)\\
-\addlinespace
-\hspace{1em}White &  & 975 (77\%) & 478 (76\%) & 497 (77\%)\\
-\hspace{1em}NA &  & 15 & 8 & \vphantom{2} 7\\
-\textbf{Education} & 1,272 &  &  & \\
-\hspace{1em}H.S. or less &  & 362 (28\%) & 174 (28\%) & 188 (29\%)\\
-\hspace{1em}Some college no degree &  & 283 (22\%) & 142 (23\%) & 141 (22\%)\\
-\addlinespace
-\hspace{1em}College degree &  & 461 (36\%) & 236 (38\%) & 225 (35\%)\\
-\hspace{1em}Postgraduate degree &  & 166 (13\%) & 77 (12\%) & 89 (14\%)\\
-\hspace{1em}NA &  & 15 & 8 & \vphantom{1} 7\\
-\textbf{Party ID} & 1,268 &  &  & \\
-\hspace{1em}Independent &  & 162 (13\%) & 83 (13\%) & 79 (12\%)\\
-\addlinespace
-\hspace{1em}Republican &  & 540 (43\%) & 262 (42\%) & 278 (43\%)\\
-\hspace{1em}Democrat &  & 566 (45\%) & 283 (45\%) & 283 (44\%)\\
-\hspace{1em}NA &  & 19 & 9 & 10\\
-\textbf{Military Relation} & 1,272 &  &  & \\
-\hspace{1em}No relation &  & 789 (62\%) & 394 (63\%) & 395 (61\%)\\
-\addlinespace
-\hspace{1em}Only family &  & 362 (28\%) & 182 (29\%) & 180 (28\%)\\
-\hspace{1em}Served w/fam &  & 64 (5.0\%) & 31 (4.9\%) & 33 (5.1\%)\\
-\hspace{1em}Served &  & 57 (4.5\%) & 22 (3.5\%) & 35 (5.4\%)\\
-\hspace{1em}NA &  & 15 & 8 & 7\\
+\textbf{Demographic} & \textbf{Overall (N = 1287)} & \textbf{Control (N = 637)} & \textbf{Treatment (N = 650)} \\
+\textbf{Age group} &  &  &  \\
+18-34 & 350 (27\%) & 170 (27\%) & 180 (28\%) \\
+35-54 & 480 (37\%) & 245 (38\%) & 235 (36\%) \\
+55-74 & 390 (30\%) & 198 (31\%) & 192 (30\%) \\
+75-85+ & 67 (5.2\%) & 24 (3.8\%) & 43 (6.6\%) \\
+\textbf{Gender} &  &  &  \\
+Male & 598 (47\%) & 289 (46\%) & 309 (48\%) \\
+Female & 658 (52\%) & 330 (52\%) & 328 (51\%) \\
+Other/Refused & 16 (1.3\%) & 10 (1.6\%) & 6 (0.9\%) \\
+NA & 15 & 8 & 7 \\
+\textbf{Race/Ethnicity} &  &  &  \\
+White & 975 (77\%) & 478 (76\%) & 497 (77\%) \\
+Asian & 51 (4.0\%) & 25 (4.0\%) & 26 (4.0\%) \\
+Black & 164 (13\%) & 85 (14\%) & 79 (12\%) \\
+Other & 24 (1.9\%) & 12 (1.9\%) & 12 (1.9\%) \\
+Hispanic & 44 (3.5\%) & 24 (3.8\%) & 20 (3.1\%) \\
+American Indian & 14 (1.1\%) & 5 (0.8\%) & 9 (1.4\%) \\
+NA & 15 & 8 & 7 \\
+\textbf{Education} &  &  &  \\
+H.S. or less & 362 (28\%) & 174 (28\%) & 188 (29\%) \\
+Some college no degree & 283 (22\%) & 142 (23\%) & 141 (22\%) \\
+College degree & 461 (36\%) & 236 (38\%) & 225 (35\%) \\
+Postgraduate degree & 166 (13\%) & 77 (12\%) & 89 (14\%) \\
+NA & 15 & 8 & 7 \\
+\textbf{Party ID} &  &  &  \\
+Independent & 162 (13\%) & 83 (13\%) & 79 (12\%) \\
+Republican & 540 (43\%) & 262 (42\%) & 278 (43\%) \\
+Democrat & 566 (45\%) & 283 (45\%) & 283 (44\%) \\
+NA & 19 & 9 & 10 \\
 \bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
-\multicolumn{5}{l}{\textsuperscript{a} Independents do not identify nor 'lean' toward either political party}\\
-\end{tabular}
-\endgroup{}
+\end{tblr}
 

### 2025-03-19 index.qmd
reformated tables in appendix

@@
 library(tinytable) # simple tables in html, LaTeX, markdown, word, pdf, typst
+library(litedown)
 library(ordinal)
@@
 
-::: {.content-visible when-format="bookup-html" unless-format="pdf"}
+::: {.content-visible when-format="html" unless-format="pdf"}
 
@@
 
-::: {.content-visible when-format="pdf" unless-format="bookup-html"}
+::: {.content-visible when-format="pdf" unless-format="html"}
 
@@
 ```{r}
-#| label: tbl-demog
+#| label: sample-desc-setup
 #| tbl-cap: "Sample Demographics"
 #| tbl-pos: 'H'
+
+gtsummary::theme_gtsummary_compact()
 
@@
     race2 = "Race/Ethnicity",
-    race_wnw = "White or Non-White",
     educ_4cat = "Education",
-    partyid_3cat = "Party ID",
-    milrelation  = "Military Relation"
+    partyid_3cat = "Party ID"
   ) |> 
@@
     race2,
-    race_wnw,
     educ_4cat, 
-    partyid_3cat,
-    milrelation),
+    partyid_3cat),
     statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
@@
 
-gtsummary::as_kable_extra(tbl.desc, booktabs = T) |>
-  kableExtra::add_footnote(
-    label = "Independents do not identify nor 'lean' toward either political party") |> 
-  kableExtra::kable_styling(
-    font_size = 9, 
-    protect_latex = T)
-
-# gtsummary::as_gt(tbl.desc) |>  
-#   gt::tab_footnote(
-#     footnote = "Independents do not identify nor 'lean' toward either political party",
-#     placement = "left"
-#     ) |>  
-#   gt::cols_align(align = 'left', columns = everything()) |> 
-#   gt::tab_options(
-#     table.font.size = "small",
-#     data_row.padding = gt::px(1)
-#   )
+```
+
+```{r}
+#| label: tbl-demog
+#| tbl-cap: "Sample Demographics"
+#| tbl-colwidths: 80
+#| tbl-pos: 'H'
+
+tbl.desc |> 
+  gtsummary::as_tibble() |> 
+  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
+                "**Control (N = 637)**" = "**Control**  \nN = 637",
+                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
+  dplyr::select(-"**N**") |> 
+  tinytable::tt(theme = "spacing") |> 
+  tinytable::format_tt(markdown = T) |> 
+  tinytable::format_tt(replace = " ") |> 
+  tinytable::style_tt(fontsize = 0.70)
 

### 2025-03-20 docs/_tex/index.tex
fix html table in index.

@@
 
-\begin{tabular}{l c c}
-\hline
- & Confidence in AZ Elections & w/Interaction \\
-\hline
-(Intercept)                & $0.03 \; (0.08)$        & $0.07 \; (0.08)$        \\
-Treatment                  & $0.18 \; (0.05)^{***}$  & $0.09 \; (0.06)$        \\
-Not Legitimate             & $-0.72 \; (0.07)^{***}$ & $-0.86 \; (0.09)^{***}$ \\
-Republican                 & $0.11 \; (0.08)$        & $0.12 \; (0.08)$        \\
-Democrat                   & $0.17 \; (0.09)$        & $0.17 \; (0.09)^{*}$    \\
-Not Legitimate * Treatment &                         & $0.27 \; (0.11)^{*}$    \\
-\hline
-R$^2$                      & $0.14$                  & $0.14$                  \\
-Adj. R$^2$                 & $0.13$                  & $0.14$                  \\
-Num. obs.                  & $1263$                  & $1263$                  \\
-\hline
-\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-\end{tabular}
+\centering
+\begin{talltblr}[         %% tabularray outer open
+entry=none,label=none,
+note{}={{\fontsize{0.75em}{0.75em}\selectfont Outcome variable mean-centered and scaled by 1 standard deviation}},
+note{ }={{\fontsize{0.75em}{0.75em}\selectfont + p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001}},
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+width={0.8\linewidth},
+colspec={X[]X[]X[]},
+column{2,3}={}{halign=c, font=\fontsize{0.8em}{1.1em}\selectfont, halign=c,},
+column{1}={}{halign=l, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+hline{7}={1,2,3}{solid, black, 0.1em},
+}                     %% tabularray inner close
+\toprule
+& Confidence in AZ Elections & w/Interaction \\ \midrule %% TinyTableHeader
+(Intercept) & \num{0.03} (\num{0.08}) & \num{0.07} (\num{0.08}) \\
+Treatment & \num{0.18} (\num{0.05})*** & \num{0.09} (\num{0.06}) \\
+Not Legitimate & \num{-0.72} (\num{0.07})*** & \num{-0.86} (\num{0.09})*** \\
+Republican & \num{0.11} (\num{0.08}) & \num{0.12} (\num{0.08}) \\
+Democrat & \num{0.17} (\num{0.09})+ & \num{0.17} (\num{0.09})* \\
+Treatment:Not Legitimate &  & \num{0.27} (\num{0.11})* \\
+Num.Obs. & \num{1263} & \num{1263} \\
+R2 Adj. & \num{0.134} & \num{0.138} \\
+\bottomrule
+\end{talltblr}
 
@@
 
-The first model in Table \ref{tbl-legit} shows that overall confidence
+The first model in Table~\ref{tbl-legit} shows that overall confidence
 in elections among those who read the treatment vignette was
@@
 DF & 15 &  \\
-\(\chi^2\) & 11.01 &  \\
-\(P(>\chi^2)\) & 0.752 &  \\
+\(chisq\) & 11.01 &  \\
+\(P(>chisq)\) & 0.752 &  \\
 Deviance & 1746.698 &  \\

### 2025-03-20 index.qmd
fix html table in index.

@@
 
-::: {.content-visible when-format="html" unless-format="pdf"}
-
-```{r}
+```{r}
+#| label: tbl-legit
 #| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
@@
 
-texreg::htmlreg(
-  list(m1, m2), 
-  single.row = T,
-  caption.above = T,
-  custom.model.names = c("Confidence in AZ Elections", "w/Interaction"),
-  custom.coef.names = c(
-    "(Intercept)",
-    "Treatment",
-    "Not Legitimate",
-    "Republican",
-    "Democrat",
-    "Not Legitimate * Treatment"
+tab_legit <- modelsummary::modelsummary(
+  models = list(m1, m2), fmt = 2,
+  estimate = "{estimate} ({std.error}){stars}",
+  statistic = NULL,
+  stars = T,
+  coef_rename = c(
+    "(Intercept)"                        = "(Intercept)",
+    "groupTreatment"                     = "Treatment",
+    "q7Not legitimate"                   = "Not Legitimate",
+    "partyid_3catRepublican"             = "Republican",
+    "partyid_3catDemocrat"               = "Democrat",
+    "groupTreatment x q7Not legitimate"  = "Not Legitimate * Treatment"),
+  gof_map = c("nobs", "r2", "adj.r.squared"),
+  notes = list(
+    "Outcome variable mean-centered and scaled by 1 standard deviation",
+    "+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001"),
+  width = 0.8
 )
-)
-
-```
-
-:::
-
-::: {.content-visible when-format="pdf" unless-format="html"}
-
-```{r}
-#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
-#| tbl-pos: H
-#| label: tbl-legit
-#| results: asis
-
-# All continuous variables are mean-centered and scaled by 1 standard deviation.
-m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = data)
-m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = data)
-
-texreg::texreg(
-  list(m1, m2),
-  single.row = T,
-  caption = NULL,
-  caption.above = T,
-  use.packages = F,
-  table = F, # set `table = FALSE`. Quarto handles table cross-ref env
-  custom.model.names = c("Confidence in AZ Elections", "w/Interaction"),
-  custom.coef.names = c(
-    "(Intercept)",
-    "Treatment",
-    "Not Legitimate",
-    "Republican",
-    "Democrat",
-    "Not Legitimate * Treatment"
-    )
-)
-
-```
-
-:::
-
-The first model in Table \ref{tbl-legit} shows that overall confidence in elections among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
+
+colnames(tab_legit) <- c(" ", "Confidence in AZ Elections", "w/Interaction")
+
+tab_legit |> 
+  tinytable::style_tt(
+    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
+    align = "lcc"
+    ) |>  
+  tinytable::style_tt(i = 6, line = "t") |> 
+  tinytable::style_tt(i = "notes", fontsize = 0.75)
+
+```
+
+The first model in @tbl-legit shows that overall confidence in elections among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
 Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
@@
     "Log.Lik"       = "logLik",
-    "\\chi^2"       = "chisq",
-    "P(>\\chi^2)"   = "P..chi."
+    "chisq"       = "chisq",
+    "P(>chisq)"   = "P..chi."
   ) |> 

### 2025-03-20 notebooks/figures.qmd
clean repo and push to publish
fix html table in index.

@@
   enabled: true
+  warning: false
 ---
@@
               subtitle = "Maricopa County, AZ")
+
 ```
@@
 #| label: fig-patch5
+#| fig-cap: "Distrust by Educational Attainment"
+#| fig-width: 8
+#| column: body-outset
 
 p5.distrust.az.educ <- distrust.az.educ.likert + distrust.lcl.educ.likert +
-    patchwork::plot_layout(guides = "collect") & 
+    patchwork::plot_layout(guides = "collect", axes = "collect") & 
     theme(legend.position = "bottom")
@@
 #| label: fig-patch6
-
-p6.trust.az.gender <- trust.az.gender.likert / distrust.az.gender.likert +
+#| fig-cap: "Trust in Maricopa County, AZ Elections by Gender"
+#| fig-height: 8
+
+p6.trust.az.gender <- (trust.az.gender.likert + distrust.az.gender.likert) +
   patchwork::plot_annotation(
@@
       "Gender Non-binary (n=7) and those who preferred not to say (n=9) response categories omitted for lack of observations. Missing values omitted (n=15)",
-      width = 150
+      width = 80
     ),
-    theme = theme(text = element_text(family = "Palatino Linotype"))
-  ) +
-  patchwork::plot_layout(guides = 'keep') &
+    theme = theme(text = element_text(family = "TeX Gyre Pagella"))
+  ) +
+  patchwork::plot_layout(
+    ncol = 1, 
+    nrow = 2,
+    guides = 'keep', axes = "collect") &
   theme(legend.position = "bottom")
@@
 #| label: fig-p13
+#| warning: false
+#| message: false
 
@@
 #| label: fig-patch7
+#| fig-cap: "Trust in Local Area Elections by Gender"
+#| fig-height: 8
 
@@
     caption = str_wrap("Gender Non-binary (n=7) and those who preferred not to say (n=9) response categories omitted for lack of observations. Missing values omitted (n=15)",
-                       width = 150), 
-    theme = theme(text = element_text(family = "Palatino Linotype")))+
-    patchwork::plot_layout(guides = 'keep') & 
+                       width = 80), 
+    theme = theme(text = element_text(family = "TeX Gyre Pagella"))) +
+  patchwork::plot_layout(guides = 'keep', axes = "collect") &
   theme(legend.position = "bottom")
+
+p7.trust.lcl.gender
+
 ```
@@
 #| label: fig-patch8
-
-p8.trust.az.party <- trust.az.party.likert/distrust.az.party.likert+
-    patchwork::plot_layout(guides = 'keep') & 
+#| fig-height: 8
+
+p8.trust.az.party <- trust.az.party.likert/distrust.az.party.likert +
+  patchwork::plot_layout(guides = 'keep', axes = "collect") &
   theme(legend.position = "bottom")
@@
 #| label: fig-patch9
+#| fig-height: 8
 
 p9.trust.lcl.party <- trust.lcl.party.likert/distrust.lcl.party.likert+
-    patchwork::plot_layout(guides = 'keep') & 
+  patchwork::plot_layout(guides = 'keep', axes = "collect") &
   theme(legend.position = "bottom")
@@
   theme(strip.text.y.right = element_blank())
-
-trust.likert.treat.az
 
@@
 
-trust.likert.treat.lcl
-
 ```
@@
 #| fig-height: 4.5
+#| fig-width: 8
 #| fig-pos: "h"
@@
     variable_labels = trust.az.varlabels,
-    title = "Trust in Maricopa County, AZ Elections by Treatment and Partisanship")
+    subtitle = "Maricopa County, AZ")
 ```
@@
     variable_labels = trust.lcl.varlabels,
-    title = "Trust in Local Area Elections by Treatment and Partisanship")
+    subtitle = "Local Area")
 ```
@@
 #| label: fig-patch12
+#| fig-cap: "Trust in Elections by Treatment and Partisanship"
+#| fig-height: 8
 
@@
 #| label: fig-patch15
-#| fig-height: 4.5
+#| fig-height: 5.5
 #| fig-width: 8

### 2025-06-03 index.qmd
Updated formatting of html

@@
 options(tinytable_tt_digits = 3)
+# set option to render tinytable math in html
+options(tinytable_html_mathjax = TRUE)
+
+# options(tinytable_quarto_disable_processing = FALSE)
 # options(tinytable_theme_placement_latex_float = "H")
-options(tinytable_html_mathjax = TRUE) # set option to render math in html
 
@@
 
-trust_txt <- data |> select(q19, q20, q21, q22, q24) |>
+trust_txt <- data |> 
+  dplyr::select(q19, q20, q21, q22, q24) |>
   labelled::set_variable_labels(
@@
 
-distrust_txt <- data |> select(q28_1:q28_5) |>
+distrust_txt <- data |> 
+  dplyr::select(q28_1:q28_5) |>
   labelled::generate_dictionary() |> 
@@
 conf_items_text <- trust_txt |> 
-  mutate(Distrust = pull(distrust_txt))
+  dplyr::mutate(Distrust = dplyr::pull(distrust_txt))
 
 tinytable::tt(conf_items_text, width = c(.5, .5)) |> 
-  tinytable::style_tt(fontsize = 0.80)
+  tinytable::style_tt(fontsize = 0.80, align = "ll")
 
@@
 
-# Output using `tinytable` R Package
+# convert from `data.frame` to `tinytable` class object
+tab_ttest <- tinytable::tt(tab_ttest)
+
+# modify column names of table
 colnames(tab_ttest) <- c(
@@
 
-tinytable::tt(tab_ttest) |>
+# Output using `tinytable` R Package
+tab_ttest |> 
   tinytable::format_tt(
@@
   ) |> 
-  tinytable::style_tt(fontsize = 0.75) # fontsize in em units (0.75*default fontsize)
+  tinytable::style_tt(
+    fontsize = 0.75, # fontsize in em units (0.75*default fontsize)
+    align = "lccccccccc"
+    )
 
@@
   tinytable::style_tt(
-    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
+    align = "lcccccc"
     ) |>  
@@
 #| label: tbl-4
-#| tbl-cap: "Survey Items and Response Options"
+#| tbl-cap: "Pre-Treatment Survey Items and Response Options"
 #| tbl-colwidths: [70, 30]
@@
   tinytable::format_tt(replace = " ") |> 
-  tinytable::style_tt(fontsize = 0.70)
+  tinytable::style_tt(fontsize = 0.70, align = "lccc")
 
@@
   # adjust fontsize of text within table
-  tinytable::style_tt(fontsize = 0.8) |>
+  tinytable::style_tt(fontsize = 0.8, align = "lcc") |>
   # finally, format markdown and blank out any NA fillers
@@
     ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
+  tinytable::style_tt(i = "notes", fontsize = 0.75, align = "l")
 
@@
   tinytable::style_tt(
-    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
-    ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
+    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
+    align = "llccccc") |> 
+  tinytable::style_tt(i = "notes", fontsize = 0.75, align = "l")
 
@@
   tinytable::style_tt(
-    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
+    align = "llccccc"
     ) |> 

### 2025-06-03 src/funs.R

@@ -363,4 +363,4 @@ lrm.gof.stats <- function(x, ...){
   return(out)
 }
 
-lrm.gof.stats(m1)
+# lrm.gof.stats(m1)

### 2025-07-02 response_memo.qmd
response memo draft and revision draft

---
title: "Response to Reviewers"
format: 
  hikmah-response-typst:
    toc: false
    mainfont: TeX Gyre Pagella
    bibliography: references.bib
    bibliographystyle: american-political-science-association.csl

---

I thank the Reviewers for taking time to provide their thoughtful and constructive comments. The Reviewers' comments are cited or summarized in [red italicized text]{.memo-reviewer-inline}, and my responses are in black Roman text. I also include excerpts from my revised manuscript in [blue]{.memo-excerpt-inline}.

# General Reviewer concerns on theory and competing explanations

Both reviewers' concerns touched on the same general issue, and the offered critiques and recommendations complemented each other. *Reviewer 1*{.memo-reviewer-inline} notes a general lack of discussion on potential explanations or explicit conjecture on a potential mechanism. **Reviewer 2**{.memo-reviewer-inline} recognized the same as ambiguity within of the theory; synthesis of the context (i.e., background section) and the literature didn't lead to a clear and concise reason for "why veterans" would be expected to influence confidence in elections. I dedicated a separate section titled as such hoping to clarify the source of my stated expectations, however I agree that the issue needs to be expounded at both ends.

These added revisions are extensive, yet I believe adding a refined theory section and discussion section addresses the most immediate concerns raised by both reviewers. The theory section is revised to make clear "why veterans", noting the gaps in available literature while making the intent of the current study explicit; whereas the added discussion section complements the theory section by discussing potential explanations.

::: {.memo-reviewer}
***Reviewer 1***---***what is the mechanism here?***: We understand that veterans are generally viewed positively, and that’s part of why this approach might work. However, in the data, we don’t see any direct measures of how respondents feel about veterans—there’s no pre-treatment baseline for that. I understand that the data might not allow for it, or that asking upfront could interfere with the treatment, but still---it leaves us wondering: what exactly is driving the results? Is it the idea of integrity, a feeling of safety or strength, or a sense of national service? We don’t really know. For this paper, it might be acceptable to say we’re building on prior work and that the cue is sufficient, but it would be helpful to acknowledge that gap more directly and discuss potential explanations.
:::

In response to *Reviewer 1*'s{.memo-reviewer-inline} concerns, I extend a discussion prior to the conclusion in order address potential explanations as avenues for future research.

::: {.memo-excerpt}
The bluntness of the experimental stimulus and survey items don't allow us to establish exactly what it is about military veterans in particular that cues stronger confidence in elections. No survey items assessed public attitudes about military veterans specifically, pre- nor post-treatment. This unfortunately leaves no room for me to postulate and examine any potential mechanisms underlying results. As such, a question lingers about whether some antecedent mechanism transmits (i.e., mediates) the effects of the veteran treatment vignette to the outcome. To put simply, this study reiterates that there *is* something special about veterans in particular that elicits greater confidence in elections, but cannot go further in determining exactly *what* that special something might be.

Factors that *moderate* the relationship of the treatment on the outcome of interest are likely plenty, but one can only offer conjecture of a *mediator* driving results. One potential explanation is that veterans, and all those who serve in the military, potentially function as a national symbol. The group is abstract just as the nation is abstract, and the potency of the veteran group emulates the potency of a national symbol. Recall Benedict Anderson's [-@anderson2006] meditation on the Tomb of the Unknown Soldier, "...saturated with ghostly *national* imaginings" [-@anderson2006, 9, emphasis original]. In various studies, national symbols such as the flag, the national anthem, or even mere appeal to national identity have potent, yet variable, effects on different outcomes [@schatz2007; @butz2007; @kemmelmeier2008; @butz2009; @gangl2016; @kalmoe2016; @levendusky2018]. It is plausible that military service members and veterans function in much the same way---as a symbol of national loyalty, pride, and nationalism for people to praise and revere out of a sense of duty prescribed by social norm and reinforced by national sentiment. As such, it may be the case that the treatment effect on confidence in elections is mediated through an affective response to a national symbol---in this case, veterans. The veteran cue may indeed stimulate national sentiment and subsequently boost confidence in elections.

In results presented here, confidence in elections is associated with greater confidence among those in the treatment group, but neither vignette conveys information about the procedures or practices meant to safeguard election integrity; nothing in the treatment suggests to respondents that election integrity would be improved by recruiting veterans. Arguably, the results presented here speak to the "emotional pathway" mentioned in @gaudette2025 so long as we assume that there's an inherent appeal to national sentiment (e.g., nationalism, patriotism) by use of veterans[^13]. Importantly, if the veterans treatment is mediated by stimulation of affect for nation or national identity, then comparable stimulation of national sentiment unrelated to veterans should produce similar results via this "emotional-pathway". However, appeals to national sentiment by use of sterile national symbols (e.g., banal presentation of the U.S. flag, playing of the national anthem) may not have the same affective influence on confidence in elections.

[^13]: The study by @gaudette2025 included an experiment that examined the contrast between "emotional" versus "informational" appeals on trust in elections and beliefs that election fraud is prevalent. Authors presented one of two video messages created by election administration officials in either Virginia or Maricopa County, AZ; the former was "emotions-based" in that it provided little to no information about the voting process or election administration, whereas the latter provided, "...specific information about the processes used to ensure the integrity of the vote with no appeal to emotion or patriotism" [-@gaudette2025, 13].

In a similar vein, it is plausible that certain political apprehensions are nullified insofar as veterans as a group are generally perceived as 'apolitical'---which itself may be enough to engender favor among the mass public [@krupnikov2022]. Current and former military service members may be viewed by the public generally as 'apolitical', especially in comparison to practically any other social group. Indeed, an 'apolitical' reputation has been long desired by military leaders and top brass [@lagrone2019; @garamone2016; @garamone2016a; @baldor2020] despite evidence to the contrary [@betros2001; @mcnerney2006]. Nevertheless, the putative 'apolitical' nature of military service may generalize to veteran service members, and increase confidence in elections based on the assumption that veterans uphold a commitment to ensure election integrity above their own personal loyalties, partisanship, or politics. Prior research has relied on the assumption that such a "*group-based*" norm persists among military members, which prescribes that the military is, or ought to be, apolitical [@mullinix2022]. Although, the extent to which this perception generalizes widely among the mass public about the military in general, or about current and former service members in particular, has yet to be examined. Given recent events of far more overt politicization of the U.S. military [@baldor2025; @baldor2025a; @baldor2025b; @baldor2025c; @thomas2025], it would be useful for future research to consider whether perceptions about the military generally, and military leaders in particular, generalize to perceptions about current and former military service members. Especially insofar as such attitudes relate to confidence in the electoral process and administration.
:::

::: {.memo-reviewer}
***Reviewer 1***---***Hypothesis structure could be clearer***: You present H1 very clearly, which is great. However, later in the paper, there are additional expectations that seem like they could have been articulated as formal hypotheses too—perhaps H2, H3, or even sub-parts like H1a, H1b. While it’s not a major issue, clearer hypothesis structure would enhance readability and help clarify the paper’s logic as it progresses. Currently, it feels like a mix of formal and informal framing.
:::

Agreed. The revised text follows below.

::: {.memo-excerpt}

> H~2~: Differences in confidence in elections in one's local area and confidence in elections in Maricopa County, AZ, will be smaller among those who are presented with an announcement that election officials are recruiting miilitary service veterans to work as election staff and volunteers compared to those presented with an announcement of recruitment efforts that do not mention military veterans.

\dots

> H~3~: Among those who refute the legitimacy of the 2020 election results, those presented with an announcement that election officials are recruiting veteran service members for election jobs will be associated with greater levels of confidence in elections compared to those presented with an announcement of recruitment efforts that do not mention military veterans.

Prior research has found that political candidates benefit from having a military background [@mcdermott2015], especially evaluations of candidate's prospective performance on particular war issues (e.g., foreign policy, terrorism) [@hardy2019]. The idea is that prior military service provides meaningful information to use as a heuristic in regard to such "war issues". Although veterans are no longer actively serving, there's potentially some lingering general assumptions about the capacities and motives of military veterans to provide safety and security arising from the nature of their prior occupation as members of the U.S. armed forces. Insofar as the physical safety of people at election sites is a "military matter", then the potential that election sites may be staffed with military veterans may ease related concerns about the safety and security of those places. As such, I expect that concerns about potential for violence will be lower, and confidence in voter safety higher, when presented with information that veterans are being actively recruited to work and volunteer in election offices.

> H~4a~: Concerns about the potential for violence, threats of violence, or intimidation while voting in person will be lower among those presented with an announcement that election officials are recruiting veteran service members for election jobs compared to those presented with an announcement of recruitment efforts that do not mention military veterans.

> H~4b~: Confidence that voters will be safe to vote in-person at election sites will be higher among those presented with an announcement that election officials are recruiting veteran service members for election jobs compared to those presented with an announcement of recruitment efforts that do not mention military veterans. 
:::

::: {.memo-reviewer}
***Reviewer 1***---***Racial dynamics and trust***: This aspect also emerged for me. The sample is mostly white, making it challenging to draw conclusions about how this might work for communities of color. As we know, these communities often have long histories of institutional distrust—including towards the military. Thus, it’s possible the cue might not resonate in the same way, or perhaps it does, as many veterans are people of color too. We don’t know, and the current data cannot address that limitation—but acknowledging it and speculating could be beneficial.
:::

::: {.memo-reviewer}
***Reviewer 2***---***Data and Methods***: Manipulation check: Was one included? If not, I’d recommend at least discussing this. How do we know that respondents interpreted the “veteran” cue as the author expects? Could it conflate with race, gender, or general views of the military?"
:::

::: {.memo-reviewer}
***Reviewer 2***---***Data and Methods***: Relatedly, might respondents be reacting not to “veteran” status *per se*, but to broader schemas about military discipline, patriotism, or law and order? If so, could this effect be amplified (or diluted) depending on the respondent’s background? These questions may not require new data but should be acknowledged and theorized.
:::

The above concerns raised by each reviewer are similar as they concern the potential for differential effects of the veterans cue.

As for manipulation check, there were no *a priori* expectations regarding how respondents would cognitively interpret the veteran treatment vignette beyond what was stated in the hypotheses. Upon presentation of either the treatment or control vignette, survey respondents were unable to progress further in the survey until at least 15 seconds had elapsed. The survey included two "screener" items as an attention check prior to presenting either the treatment or control vignette. Respondents who failed to select a certain response twice in a row were removed from the survey.

In response, I included the following text in the revised discussion section.

::: {.memo-excerpt}
The data of the current study is limited in helping to discern whether the treatment garners greater confidence in elections uniformly across different racial or ethnic groups given that the largest proportion of the sample identified their race as White (77%). It is reasonable to suspect that the treatment vignette might differ by race and ethnicity, but the sample is insufficient to make such generalizations. Nevertheless, attitudes about veterans that differ by group may play an important role in determining whether publicized efforts to recruit military veterans boosts confidence in elections uniformly or whether the effect is merely partial to certain segments of the population. In their research examining whether groups differed in attitudes about veterans, @kleykamp2018 could only speculate as to why levels of support were lowest among Hispanic and Black respondents. Other research has found that attitudes about the U.S. military generally---though not about active or veteran military service members in particular---differs by race and ethnicity to varying extents, but could not supply reason for one groups' sentiment over another [@nichols2015].

Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly. One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S. military as an institution in general. For instance, some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally. In one such study, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes on homelessness and PTSD among the veteran population, but not among the general adult population [@tsai2021].

Perhaps unsurprisingly, military veterans appear to be uniquely deserving in the eyes of Republican partisans [@tsai2021; @mcdermott2015; @richardson2022]. As such, military veteran status may qualify favorable attitudes among Republican partisans whereas their regard for other non-veteran groups might otherwise express contempt or indifference. This further indicates a need for research to determine an underlying mechanism explaining why veterans incur special favor.
:::

::: {.memo-reviewer}
***Reviewer 1***---***How generalizable are these results***: I appreciate your honesty about how the strongest effects appear in Maricopa County, and that we don’t observe the same impact when people consider their own local elections. That’s interesting in itself, but it raises questions—can this approach be effective in other areas? Would appointing veterans as officials in lower-salience places have any impact? Or is this cue only meaningful in scrutinized locations? You touch on this briefly, but expanding this section would add depth, particularly for readers contemplating its implications for future elections.
:::

To address these concerns, I include the following text in the discussion

::: {.memo-excerpt}
As stated previously, the survey was fielded on a non-probability sample of 1,287 U.S. citizens 18 years of age or older. The results presented here are not assumed to be generalizable to the national population. It may be feasible to weigh the sample to demographics of the population at the time the survey was fielded, but this is unnecessary for the experimental purpose of the study. If similar findings complement or replicate these results, then the expense of drawing samples more representative of the national population may be justified. At this stage, however, the results are limited to demonstrating treatment effects that are sample dependent.

Note also that the measurement items of the components trust and distrust, and the method of computing scores for the dependent variable, confidence in elections, are unique to this study but falls under the methodological framework of Classical Test Theory (CTT). Although survey measurement items were either directly drawn from or inspired by similar survey items found in various other surveys (e.g., SPAE, Pew), the question wording, response choices, coding, and computation of sum scores of the dependent variable are specific, thus rendering measurement of the hypothetical constructs of interest (i.e., trust, distrust) less comparable across similar studies that profess measurement of similar constructs [@widaman2024]. Namely, trust, distrust, or confidence in elections as defined and measured here.

The setting of the vignette and specified in survey items might raise additional concerns on whether results are generalizable. Naming a specific county in the vignette adds in a potentially influential factor unaccounted for in the survey; some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S. they know nothing about. Naming a real and somewhat salient county potentially undermines confidence that the treatment effects are solely attributable to veterans to an unknown degree. Simply put, there may be something special about Maricopa County, AZ in particular that generalizes across attitudes of trust or distrust in elections.

Arguably, however, Maricopa County is indicated as the setting in both the treatment and control vignettes, thus the only actual difference between conditions is constrained to the target group being recruited. Future research may employ vignettes naming a fictional U.S. county to hopefully eliminate the setting as a concern. Alternatively additional survey items that ask directly about one's knowledge or sentiment about the county in question could inform researchers on whether the named county imposes any undue influence at all, or whether the setting is associated with other factors such as partisanship.
:::

## Reviewer 2

::: {.memo-reviewer}
***Reviewer 2***---***Theory***: "The author could be clearer about the puzzle: Why would identifying poll workers as veterans plausibly increase confidence in elections? Why might it not? The paper gestures at answers---trust, apolitical reputation, shared identity---but doesn’t quite fully develop the competing
expectations."
:::

In response to *Reviewer 2*'s comments concerning the theory, I restructure the theory section to incorporate the "Why veterans" section, expand on the premises, and add literature that better leads to the expectations. The text below reflects the revised theory section that better incorporates "Why Veterans".

::: {.memo-excerpt}
Election officials don't focus on recruiting people of a particular demographic, status, class, or prestige in order to shore up public trust in elections, and they don't discriminate recruitment efforts based on who the public thinks is best suited to secure elections from fraud.

Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work. Especially since staffing has been an issue since at least the 1990s [@maidenberg1996; @ferrer2024]. In 2020, such efforts were made far more difficult by the COVID-19 pandemic [@mena2020; @abbate2020a]. There's no special reason to target veterans for recruitment above other groups. Indeed, there's no reason to discriminate recruitment efforts at all if the point is purely to fill staffing vacancies.

Veteran military service members are, after all, civilians; Civilians with shared (but varied) experience and status of prior military service, but who are no more or less qualified for this civil service^[Research is limited and mixed on whether veterans in general are more inclined, however [@nesbit2011].] than non-veteran civilians. To be frank, announcements about concerted efforts to recruit veterans as election workers should not reasonably influence one's trust that votes will be counted more accurately, or that election fraud will not occur; there is no known evidence demonstrating that actually employing veterans as election staff or volunteers further improves the safety, security, and overall integrity of elections in the United States. Moreover, there's no known evidence of positive influence on public perceptions of said outcomes when voters encounter military veterans working as staff or volunteers at elections sites.

Rather, the claim that recruiting veterans to work as election staff and volunteers would improve public confidence in elections emerges as non-profit organizations---mainly comprised of veteran and military family members themselves---operate under, and promote, that assumption [@looker2024; @lawrence2024; @wentling2024]. Non-profit groups of late have made incredible strides in targeted recruitment efforts under the notion that veterans are uniquely capable, committed, and best fit to serve the needs of the United States as civil servants and volunteers at election sites. Indeed, this study can be seen as a test of a particular assumption that veterans have about themselves---the assumption that their mere presence and civic engagement will inspire confidence in elections among the public.

There was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021. After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterans2022; @nflfootballoperations2022]. Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts [@powerthepolls2020; @herndon2020]. Generally, however, recruitment efforts cast a wide net, indiscriminate of who applies [@ross2020; @conde2020].

One can speculate that the motivation to associate military veterans with civic engagement and democracy may be intended to counter negative perceptions and impressions given by the proportion of veteran service members arrested for taking part in the events on January 6th [@milton2021; @loewenson2023; @jensen2022a]. Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024]. This is in addition to a strengthened association portrayed in media outlets between military veterans and militias [@steinhauer2020]. Prior research has substantiated such a connection between veterans and militia groups. @cooter2024 notes from her 3-year ethnographic fieldwork among Michigan militia members that, "...approximately 40% of militia leaders and 30% of members had previous military experience. Most of these veterans actively sought out such groups, as opposed to being recruited by them" [see also @cooter2013]. Thus, countering such associations by promoting a different image of veterans to the mass public and veterans alike seems like a reasonable motivation. Yet such speculation is just that.

The key findings of literature on confidence in elections hardly point to public regard for veterans as a mechanism for the theoretical expectations of improving overall confidence in elections and improving feelings of voter safety at election sites. Comparable research finds that confidence in elections is increased through elite rhetoric from fellow partisans affirming legitimacy of elections [@clayton2023], or through the provision of information about the electoral process or other official messaging of election officials themselves [@gaudette2025]. Neither of the studies just cited, however, consider attitudes or sentiment about veterans as a source for dispelling distrust and improving trust in elections. To be clear, there is no immediate "puzzle" in the literature that immediately draws out public sentiment for military veterans as a source for bolstering confidence in elections. That being said, the general public perception, attitudes, or even stereotypes about military veterans are significant to consider.

It is important to make clear two considerations that underpin the notion that information about veterans will improve trust and quell distrust in elections. First, positive public regard for veterans *in general* is sufficient to elicit greater trust and lower distrust in elections despite the fact that information about veterans as election workers, or even merely information on efforts to recruit veterans, has no bearing on the actual integrity of the electoral process. An underlying assumption here is that there *is* something special about veterans, but this doesn't include a proposition on exactly *what* that special something might be in theory. This is partly due to the limited research available on public regard for veterans, specifically in terms of elucidating an underlying mechanism for such positive favor. Moreover, there is limited research on public opinion about former and active military service members distinguished separately from public opinion about the military as an institution in general. Endorsement or support of government policies intended to benefit veterans specifically (e.g., federal funding on veteran healthcare) are easy to conflate as interchangeable with public attitudes about veterans as a group in particular. This, in turn, permits general expectations of positive influence due to the public's overarching positive regard for veterans, but disallows for expectations regarding how respondents would actually process and interpret a treatment that only mentions efforts to recruit them for election work. In short, we are sure that people sustain positive views for veterans generally, but beyond that I make no special effort to propose and examine why that is the case in greater detail.

The evidence that can be gathered concerning public regard for military veterans shows that, generally, veterans are perceived favorably among the general public; although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023]. In my review of the literature, I found only one study which assessed public opinion about veterans specifically and examined whether attitudes differed by group [@kleykamp2018]. @kleykamp2018 investigated the extent to which positive regard for military veterans in terms of both social distance and deservingness varies across different groups, and the extent to which such support is exaggerated. Their research found that levels of support for veterans tended to be predictably lowest, but also most exaggerated, among those who were younger and non-White. Determining what groups hold special favor for veterans still leaves it unclear as to what it is about veterans that engenders greater confidence in elections. Yet, generally, all groups expressed exaggerated support for veterans in more than one way [@kleykamp2018], suggesting that public regard for veterans is prescribed by widespread social norm.

This is taken together with literature suggesting that public trust in elections is malleable to factors, experiences, events, or phenomena that range in logical relevance to the actual structure or administration of elections. On the one hand, public trust is, indeed, influenced by information specifically about the processes of conducting elections [@gaudette2025]. On the other hand, the public's trust in elections is not beholden to the demonstrated *trustworthiness* of the institution of election administration. Thus the first consideration is simply that the positive public regard for veterans in general may function sufficiently as a cue to elicit greater trust in elections despite relevance.

Second, veterans are a particularly potent group where mention of one's veteran status seems to have a positive, calming, or nullifying effect on attitudes. More so than just the general positive favor afforded to veterans, the group appears to have a somewhat pacifying effect on negative or otherwise contemptible discrimination, prejudice, and social stigma. For instance, recent research shows that, during his campaign in the 2020 Democratic Primaries, Pete Buttigieg's military background mitigated discrimination against him when he was presented as a veteran married to a man [@magni2024]. Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@teigen2013; @hardy2019]. Moreover, veteran status seems to mitigate or nullify usual stigmas associated with mental illness. That is to say, there is negative stigma associated with mental illness [@corrigan2002] and such stigma incurs labor market discrimination [@hipes2016], but evidence suggests that veteran status overrides such stigma and discrimination [@maclean2014]. Or, in another light, mental illness is seemingly more *understandable* (i.e., permissible) for veterans given the presumptive reasons for their mental strife. And media framing as such plays an important role on public perception [@kleykamp2015]. Relatedly, attitudes about homelessness and PTSD---ranging from perceived causes of homelessness, whether the federal government should dedicate more resources, perceived effectiveness of policies, to compassion for homeless individuals---are generally more favorable for the homeless population among veterans than for the homeless population of general adults [@tsai2021]. Such effects primarily pertain to attitudes about individual people or groups (e.g., a political candidate, prospective employees, the homeless population). The capacity of one's veteran status to pacify prejudice, discrimination, and stigma likely extends out to quell negative and disfavorable attitudes regarding institutions to a similar extent, e.g., distrust.

The question emerged in light of the recent surge of efforts nationwide to recruit veterans to serve as election workers [@lawrence2022; @wentling2024] midst an environment where election insecurities were heightened and intensified. Bearing that in mind, the heightened insecurities in anticipation of upcoming elections do not merely pertain to the election outcome (e.g., who wins), but to one's general sense of confidence in the integrity of elections administration and to the safety of casting a ballot in-person.

Given the heightened tensions and electoral anxieties, the expectations surrounding the unique pacifying effect that veterans have on attitudes about individuals or other groups is extended to determine whether a similar effect is found when the target of one's consideration is not just a person or group but the institution of election administration itself. Thus the second consideration for "why veterans" are expected to dispel distrust in elections pertains to pacifying effect of negative or disfavorable attitudes observed in relevant literature.

The stimulating influence of veterans as a group in the abstract is expected to counteract distrust and insecurity pertaining to the institution of elections administration, as well as inspire greater confidence in the same. There's scant research or evidence available to postulate a well-formed theory on the mechanism underlying the expected effects of veterans as a group on attitudes about institutions and processes, rather than on attitudes about persons or groups. What may be posited at best, however, is that distrust and insecurity in elections among the public is expectedly reduced to some extent through generally positive public regard for military veterans and their unique capacity to quell disfavorable attitudes.
:::

::: {.memo-reviewer}
***Reviewer 2***---***Theory***: Relatedly, I’d encourage the author to more clearly distinguish the scope conditions of this theory. For instance: Is this paper about elite signaling, political trust, or identity-based persuasion? Each of these frameworks could work, but right now they’re blended in a way that dilutes their force.
:::

In order to be more explicit, I added the following text.

::: {.memo-excerpt}
# Theory

This theory is constrained to public confidence in the administration of elections in the United States. To be clear, the scope conditions in which this theory applies concern public trust and distrust in election administration in the anticipatory period prior to the election event. Moreover, this study is, to a limited extent, indirectly related to public regard about veteran members of the U.S. Armed Forces.
:::

::: {.memo-reviewer}
***Reviewer 2***---***Theory***: Terms of art should be defined with precision. What do we mean by “voter confidence”? Is it about procedural trust? Belief in outcome integrity? Perceived impartiality? Greater clarity here will help structure the analysis and give readers clearer expectations.
:::

I agree with **Reviewer 2** and apologize for any confusion. In order to address the above concern, I inserted the following text which was initially cut from an earlier draft for length. This section follows the added text above within the theory section and also further addresses clarification of scope conditions.

::: {.memo-excerpt}
## Trust and Distrust in Elections

The theoretical relationship between trust and distrust is important to understand, especially when it comes to the dependent outcome of interest. Before going further, it is necessary to explicate the conception *confidence in elections* with respect to trust and distrust.

Trust is, after all, merely *belief* held in the face of uncertainty. Trust is reliance on the veracity of belief in the face of uncertainty. Said another way, trust is assured belief dependent on its supposed veracity; a state of certainty with respect to some belief or judgement. It is "assured" because it is one's belief that relies on something rather than nothing. Hence quantitative methods of the sciences are replete with things such as *confidence* intervals around our estimates. Therefore, I understand trust to refer to the state or quality of certainty around one's beliefs or expectations; the extent to which one is assured of their expectations regarding what is or what will be the case.

The kind of *trust in elections* I refer to concerns the expectations drawn up from one's judgement about the functioning of the electoral process---the extent to which one is assured in the belief that the electoral process will be fairly and accurately administered. I follow the notion of public trust in elections explicated by @stewart2022,

> "Public trust in U.S. election institutions comes down to whether voting machines accurately record votes, voter registration systems accurately record those eligible to vote, geographic information systems accurately assign voters to voting districts, election-night reporting systems accurately aggregate and communicate election results to officials and the public, and postelection audit and canvassing procedures proceed impartially and in accordance with the law." [-@stewart2022, 236]

That being said, I also account for expectations of electoral fraud, which I refer to as *distrust* in elections distinguished from trust. Distrust in this sense is also a belief, an expectation, about the anticipated functioning of the process. Note, however, that the prefix *dis-* in distrust implies "apart", "lack of, not" or "opposite". Conventionally, distrust is defined simply as the absence of trust, thus denoting a simple inverse and mutually exclusive relationship. However, as it concerns the psychology of an individual, *a lack of trust doesn't necessarily imply opposite expectations or opposing beliefs*. In particular, a lack of trust that votes will be accurately recorded, etc., doesn't necessarily imply inversely proportional expectations that electoral fraud will occur. In other words, although the relationship between trust and distrust is inverse, this relationship is not mutually exclusive.

A person who is certain that electoral fraud will occur clearly lacks trust in elections; an expectation that electoral fraud will occur necessarily implies a lack of trust in elections regardless of positive expressions of trust. However, the reverse isn't also true; expressing a lack of trust in elections *doesn't necessarily imply* an expectation that electoral fraud will occur. Rather, a lack of trust implies an absence of assurance in the belief that the process will be conducted fairly and accurately---a lacking quality of certainty around said belief. An absence of such assurance denotes a state of *insecurity*. Other sources of uncertainty may challenge a person's confidence regarding the integrity of elections independent from anything that would lead them to believe electoral fraud will occur or has occurred. However my use of distrust refers to the assured belief that the outcome will be invalid---that outcomes will be independent of the process as prescribed, thus rendering outcomes as arbitrary. Specifically, distrust implies assurance in the belief that electoral fraud will occur.

As such, trust and distrust represent opposing degrees of confidence along the same spectrum. However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling relatively confident in both respects. Accordingly, *equivalent degrees of trust and distrust cancel out*, rendering one relatively more insecure about their expectations of the future despite the fact that they may report feeling confident in either direction respectively. When trust and distrust are considered reflective of one's confidence about future expectations, then both can be placed along the same spectrum. Therefore, a lack of confidence denotes insecurity.

This means that a person's baseline level of confidence in elections must take into account their present degree of distrust---i.e., their expectations of electoral fraud. Something may cause a person to have greater expectations that election fraud will occur, which in turn will always lower their trust in elections. In contrast, a person's trust in the integrity of the electoral process is reduced by the extent to which they expect that electoral fraud will occur.

Thus, it follows that a person distrusts the integrity of the electoral process to the extent that they are to some extent certain that electoral fraud will occur or has occurred. They are, perhaps, poised to discount election results as invalid or illegitimate in advance. Either way, both trust and distrust refer to some positive degree of confidence (i.e., assurance) regarding one's expectations. They are distinguished by reference to either the normative idea about what *should* come about, or what is *supposed* to come about given the logical structure and integrity of the process. If the structure and integrity of some process is coherent and secure, respectively, then the outcome that follows will be valid. Should the integrity of that process be damaged or opaque, then the process becomes vulnerable and validity of the results are open to challenge. With respect to the administration of U.S. elections, the confident voter expects that votes will be counted as voters intend, election staff will competently administer elections, election technology will be secure from nefarious tampering, and that the process will be fair for all involved.
:::

::: {.memo-reviewer}
***Reviewer 2***---***Data and Methods***: It would be helpful to know more about sample composition. How diverse is the sample in terms of veteran status, ideology, partisanship, and race? This will help the reader interpret the subgroup analyses.
:::

The following brief description of the sample was added prior to description of the survey design under the "Experiment Design and Survey Measures" section.

::: {.memo-excerpt}
The median age was $46$ (mean age was $47$), $51.13\%$ ($n = 658$) women, $46.46\%$ ($n = 598$) men, and approximately $1.24\%$ who identified as either Non-binary/third gender ($n = 7$) or preferred not to say ($n = 9$). The sample primarily identified as White or Caucasian $75.76\%$ ($n = 975$), while all other non-White respondents comprised $23.08\%$ ($n = 297$) of the sample. Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised $12.9\%$ ($n = 166$) of the sample; those with either degree at the Associate or Bachelor's level comprised $35.82\%$ ($n = 461$), while $21.99\%$ ($n = 283$) had some college but no degree; and $28.13\%$ ($n = 362$) had either a high school level or equivalent education or less than high school. The largest proportion of the sample were Democrat at $43.98\%$ ($n = 566$), followed by Republicans at $41.96\%$ ($n = 540$). The proportion of true Independents^[Independent 'leaners' were grouped into the respective party affiliation in which they lean.] was $12.59\%$ ($n = 162$).

Among the sample, $34.11\%$ ($n = 439$) said they had an immediately family member who was currently serving or had previously served in the U.S. military; $64.72\%$ ($n = 833$) didn't have a family member who served. Approximately $8.24\%$ ($n = 106$) of the sample were veterans, while $1.17\%$ ($n = 15$) reported to be actively serving. 
:::

::: {.memo-reviewer}
***Reviewer 2***---***Findings***: The author identifies heterogeneous effects by election level (local vs. national), which is a fascinating and potentially important finding. But what does this mean substantively? Do voters view the stakes of “local” and “national” elections differently with respect to legitimacy? Do they associate veterans with one level more than another?
:::

Despite the limitations noted previously, I added the text below in response to **Reviewer 2**'s concerns on the potential substantive significance of the findings. This text can be found just prior to the subsection "2020 Election Legitimacy Beliefs".

::: {.memo-excerpt}
The veteran cue is potentially compensatory, which supports the second hypothesis (H~2~). That is, the gap in confidence in local elections and elections in Maricopa County is reduced by the veterans cue, therefore compensating for the otherwise lower confidence and greater insecurity in Maricopa County elections. This is analogous to studies showing that Republicans support for a Democratic candidate is compensated by a Democratic candidate's veteran status. Hypothetical Democratic veteran candidates were more palatable to Republican partisans than non-veteran Democrats [@mcdermott2015]. Similarly, Democratic veterans received higher support in Senate races, especially Democratic veteran Senate candidates whose military experience included deployment to conflict zones [@richardson2022]. The point of note is that it is *Democratic* candidates who receive *more* of a benefit that comes with veteran status[^]; the analogy being that it is elections located elsewhere that receive the benefits of the veteran cue whereas local elections do not. Note that the results can't necessarily be read as differing between elections at the local level versus national level, but rather heterogeneous effects differ by elections at the local level and elections in Maricopa County, AZ. The compensatory effect of the veteran cue may generalize to other jurisdictions other than one's local area, or the effect may be confined to Maricopa County, AZ given that this specific county had been made especially salient in the past.

[^]: Note that the war veteran classification provided benefits to Republican Senate candidates vote share distinct from "common" veterans---i.e., Republican Senate candidates who did not deploy to areas of conflict [@richardson2022].
:::

::: {.memo-reviewer}
***Reviewer 2***---***Findings***: The author should consider the magnitude and directionality of effects in relation to expectations. For instance: Are the observed changes in confidence substantively meaningful? Are they comparable to known effects in this literature (e.g., from partisan cues or fraud frames)?
:::

While this is understandable, I was unable to compare magnitude of effects between comparable studies due to the differences in measurements across multiple studies examining trust or confidence in elections. I include the following text within the discussion to address this point.

::: {.memo-excerpt}
It is difficult to compare magnitude of effect with other studies given that the item number, item wording, measurement, and computation of confidence in elections is unique across most individual studies to include this one. For instance, @gaudette2025 doesn't compose multiple items into a single composite measure, but subtracts pre-treatment values from post-treatment values for single-item measures with Likert-style response options. Whereas @clayton2023 develops a scale referred to as "Trust in American electoral process" by taking the mean from three items. The item wording of that scale is markedly similar to the items used to compose the trust scale of this study, but the range of response options differs considerably. Thus, while most studies examining public confidence in elections often include the core question "How confidence are you that your vote \[will be/was\] counted as you intended in the most recent election?", the different ways that researchers measure and compute variable scores on the outcome are most often, and unfortunately, sample dependent. The study of public confidence in elections is in desperate need of a standard method of measurement, or even a screened and validated item bank, and this study may be seen as a baby step to that end.

That being said, this study generally emulates treatment effects of comparable studies in the literature. @gaudette2025 found positive effects of official messaging from election officials on various items measuring trust in elections and expectations of electoral fraud. Similarly, @clayton2023, confined to a sample of Republican participants, found positive influence on perceptions of 2020 election legitimacy and trust in the American electoral process from official messaging by Republican politicians reaffirming the 2020 election results.
:::

::: {.memo-reviewer}
***Reviewer 2***---***Findings***: I also encourage more discussion of null results. Even where effects are weak or absent, that tells us something important—especially if veteran cues only resonate among certain audiences or in certain electoral contexts.
:::

Although I am sympathetic to this view, results permitted rejection of the null hypotheses posited in the research paper. It was expected that the veteran cue would not influence confidence in local elections, which was described in the findings. Further discussion addressing this concern was added to the description of the findings and also addressed in the revised discussion section.

### 2025-07-02 docs/_tex/index.tex
response memo draft and revision draft

@@
+% Options for packages loaded elsewhere
 % Options for packages loaded elsewhere
@@
 ]{article}
-
+\usepackage{xcolor}
+\usepackage[margin=1in]{geometry}
 \usepackage{amsmath,amssymb}
-\usepackage{setspace}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
@@
 }{}
+\usepackage{setspace}
 \makeatletter
@@
 \makeatother
-\usepackage{xcolor}
-\usepackage[margin=1in]{geometry}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+
+\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makeatother
+
 % definitions for citeproc citations
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
@@
 \makeatother
-
 \usepackage{bookmark}
-
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 \begin{abstract}
-In this paper, I report results from a recent survey experiment
-administered to test whether publicized efforts to recruit veterans to
-work as election staff and volunteers would improve public trust in
-elections and ease election insecurity. Results of the survey experiment
-support the notion that emphasizing veterans as the target of election
-worker recruitment efforts eases pre-election insecurity. Expectations
-of electoral fraud and concerns for voter safety were lower among those
-who read an announcement that veterans are being recruited to work as
-election staff and volunteers compared to those who read a control
-vignette where veterans were not mentioned. Notable is that there was a
-significant difference in confidence among those in the treatment
-condition who believe that results of the 2020 election were
-illegitimate. In addition, concerns over voter safety and potential for
-violence were lower among those who received the treatment.
+I report results from a recent survey experiment administered to test
+whether publicized efforts to recruit veterans to work as election staff
+and volunteers would improve public trust in elections and ease election
+insecurity. Results of the survey experiment support the notion that
+emphasizing veterans as the target of election worker recruitment
+efforts eases pre-election insecurity. Expectations of electoral fraud
+and concerns for voter safety were lower among those who read an
+announcement that veterans are being recruited to work as election staff
+and volunteers compared to those who read a control vignette where
+veterans were not mentioned. Notable is that there was a significant
+difference in confidence among those in the treatment condition who
+believe that results of the 2020 election were illegitimate. In
+addition, concerns over voter safety and potential for violence were
+lower among those who received the treatment.
 \end{abstract}
@@
 next election cycle (\citeproc{ref-bowler2024}{Bowler and Donovan 2024};
-\citeproc{ref-levendusky2024}{Levendusky et al. 2024}). For instance, we
-have witnessed many people's outright refusal to accept the 2020 U.S.
+\citeproc{ref-levendusky2024}{M. Levendusky et al. 2024}). For instance,
+we have witnessed many people's outright refusal to accept the 2020 U.S.
 election results as legitimate despite consistent review of the evidence
@@
 
-In this paper, I report results from a recent survey experiment
-administered to test whether publicized efforts to recruit veterans to
-work as election staff and volunteers would improve public trust in
-elections and ease election insecurity. Results of the survey experiment
-support the notion that emphasizing veterans as the target of election
-worker recruitment efforts eases pre-election insecurity. Expectations
-of electoral fraud and concerns for voter safety were lower among those
-who read an announcement that veterans are being recruited to work as
-election staff and volunteers compared to those who read a control
-vignette where veterans were not mentioned\footnote{The vignettes
-  written were based on real news stories}. Notable is that there was a
-significant difference in confidence among those in the treatment
-condition who believe that results of the 2020 election were
-illegitimate. In addition, concerns over voter safety and potential for
-violence were lower among those who received the treatment.
+I report results from a recent survey experiment administered to test
+whether publicized efforts to recruit veterans to work as election staff
+and volunteers would improve public trust in elections and ease election
+insecurity. Results of the survey experiment show that emphasizing
+veterans as the target of election worker recruitment efforts is
+associated with greater confidence in elections and lower pre-election
+insecurity. Expectations of electoral fraud and concerns for voter
+safety were lower among those who read an announcement that veterans are
+being recruited to work as election staff and volunteers compared to
+those who read a control vignette where veterans were not
+mentioned\footnote{The vignettes written were based on real news stories}.
+Notable is that there was a significant difference in confidence among
+those in the treatment condition who believe that results of the 2020
+election were illegitimate. In addition, concerns over voter safety and
+potential for violence were lower among those who received the
+treatment.
 
@@
 reasoning for why military veterans are singled out as the relevant
-subset of the population in this study. I then explicitly provide the
-simple theory and testable hypotheses of the study before moving on to
-describe the design of the survey, the measurement instruments therein,
-and the conceptual and operational definitions of the variables of
-interest. I explain my reasoning and method for constructing the primary
-dependent variable, which I broadly refer to as \emph{confidence in
-elections}. I close by offering my interpretation of the results and
-suggest potential avenues for future inquiry.
+subset of the population expected to influence confidence in elections.
+I provide testable hypotheses of the study before moving on to describe
+the design of the survey, the measurement instruments therein, and the
+conceptual and operational definitions of the variables of interest. I
+explain my reasoning and method for constructing the primary dependent
+variable, which I broadly refer to as \emph{confidence in elections}. I
+close by offering my interpretation of the results and suggest potential
+avenues for future inquiry.
 
@@
 
-Trust and confidence in the conduct of elections concerns aspects of
-elections that fall squarely within the institution of election
-administration. At this level, for instance, public trust is ascertained
-by capturing assessments about the perceived accuracy of vote counts
-(e.g., whether votes are/were counted as intended).
+Assessing the public's \emph{trust} in elections has not been
+straightforward. Inquiry into public trust in elections has been
+approached by scholars of political science in many different ways
+(\citeproc{ref-cook2005}{Cook and Gronke 2005}), often distinguishable
+by the scope of the research question and more or less constrained by
+the particular conception of public trust. Quite often, trust in
+election administration is conflated with trust in government writ
+large, government legitimacy, government or system responsiveness, or
+even satisfaction with democracy (\citeproc{ref-daniller2019}{Daniller
+and Mutz 2019}). At this level, not only is the level of public trust in
+elections sometimes vague, but there's little consideration over the
+difference between such attitudes pre-election and post-election. In
+contrast, a considerable amount of research tends to conceive of public
+trust in accordance with the institution in question
+(\citeproc{ref-atkeson2007}{Atkeson and Saunders 2007};
+\citeproc{ref-hooghe2018}{Hooghe 2018}).
+
+Election administration\footnote{It is important to point out here that
+  election administration is just one institution that interacts with
+  many other institutions and processes which form the electoral system
+  \emph{writ large} (\citeproc{ref-stewart2022}{Stewart 2022}). The way
+  in which I discuss the institution of election administration, as well
+  as the way in which I discuss and distinguish public trust in
+  elections from broader conceptions of public trust, is borrowed
+  substantively from Stewart (\citeproc{ref-stewart2022}{2022})'s
+  conceptual framework of the same. Distinctions between \emph{trust}
+  and \emph{trustworthiness} and the notion of election administration
+  as an institution are already apparent inspirations convenient for
+  situating the theory of this research inquiry.} is just one part of
+the larger set of institutions which form the electoral system. As such,
+the performance of the institution along with the rest ``\ldots lends
+credibility to the outcome of an election: whether it is considered by
+citizens and the international community to be fair and legitimate.''
+(\citeproc{ref-stewart2022}{Stewart 2022, 236}).
+
+Trust in the conduct of elections concerns aspects of elections that
+fall squarely within the institution of election administration. At this
+level, for instance, public trust in elections is ascertained by
+capturing assessments about the perceived accuracy of vote counts (e.g.,
+whether votes are/were counted as intended).
 
@@
 expect that information identifying the particular groups being
-recruited to serve as election staff will be enough to improve trust and
-confidence in election administration, and lessen expectations of
-electoral fraud. The next section elaborates on why military veterans
-are of particular interest in this regard.
+recruited to serve as election staff will be enough to improve
+confidence in elections, and lessen expectations of electoral fraud. The
+next section elaborates on the proposed theory, terms utilized, and why
+military veterans are of particular interest in this regard.
+
+\section{Theory}\label{theory}
+
+This theory is constrained to public confidence in the administration of
+elections in the United States. To be clear, the scope conditions in
+which this theory applies concern public trust and distrust in election
+administration in the anticipatory period prior to the election event.
+Moreover, this study is, to a limited extent, indirectly related to
+public regard about veteran members of the U.S. Armed Forces.
+
+\subsection{Trust and Distrust in
+Elections}\label{trust-and-distrust-in-elections}
+
+The theoretical relationship between trust and distrust is important to
+understand, especially when it comes to the dependent outcome of
+interest. Before going further, it is necessary to explicate the
+conception \emph{confidence in elections} with respect to trust and
+distrust.
+
+Trust is, after all, merely \emph{belief} held in the face of
+uncertainty. Trust is reliance on the veracity of belief in the face of
+uncertainty. Said another way, trust is assured belief dependent on its
+supposed veracity; a state of certainty with respect to some belief or
+judgement. It is ``assured'' because it is one's belief that relies on
+something rather than nothing. Hence quantitative methods of the
+sciences are replete with things such as \emph{confidence} intervals
+around our estimates. Therefore, I understand trust to refer to the
+state or quality of certainty around one's beliefs or expectations; the
+extent to which one is assured of their expectations regarding what is
+or what will be the case.
+
+The kind of \emph{trust in elections} I refer to concerns the
+expectations drawn up from one's judgement about the functioning of the
+electoral process---the extent to which one is assured in the belief
+that the electoral process will be fairly and accurately administered. I
+follow the notion of public trust in elections explicated by Stewart
+(\citeproc{ref-stewart2022}{2022}),
+
+\begin{quote}
+``Public trust in U.S. election institutions comes down to whether
+voting machines accurately record votes, voter registration systems
+accurately record those eligible to vote, geographic information systems
+accurately assign voters to voting districts, election-night reporting
+systems accurately aggregate and communicate election results to
+officials and the public, and postelection audit and canvassing
+procedures proceed impartially and in accordance with the law.''
+(\citeproc{ref-stewart2022}{2022, 236})
+\end{quote}
+
+That being said, I also account for expectations of electoral fraud,
+which I refer to as \emph{distrust} in elections distinguished from
+trust. Distrust in this sense is also a belief, an expectation, about
+the anticipated functioning of the process. Note, however, that the
+prefix \emph{dis-} in distrust implies ``apart'', ``lack of, not'' or
+``opposite''. Conventionally, distrust is defined simply as the absence
+of trust, thus denoting a simple inverse and mutually exclusive
+relationship. However, as it concerns the psychology of an individual,
+\emph{a lack of trust doesn't necessarily imply opposite expectations or
+opposing beliefs}. In particular, a lack of trust that votes will be
+accurately recorded, etc., doesn't necessarily imply inversely
+proportional expectations that electoral fraud will occur. In other
+words, although the relationship between trust and distrust is inverse,
+this relationship is not mutually exclusive.
+
+A person who is certain that electoral fraud will occur clearly lacks
+trust in elections; an expectation that electoral fraud will occur
+necessarily implies a lack of trust in elections regardless of positive
+expressions of trust. However, the reverse isn't also true; expressing a
+lack of trust in elections \emph{doesn't necessarily imply} an
+expectation that electoral fraud will occur. Rather, a lack of trust
+implies an absence of assurance in the belief that the process will be
+conducted fairly and accurately---a lacking quality of certainty around
+said belief. An absence of such assurance denotes a state of
+\emph{insecurity}. Other sources of uncertainty may challenge a person's
+confidence regarding the integrity of elections independent from
+anything that would lead them to believe electoral fraud will occur or
+has occurred. However my use of distrust refers to the assured belief
+that the outcome will be invalid---that outcomes will be independent of
+the process as prescribed, thus rendering outcomes as arbitrary.
+Specifically, distrust implies assurance in the belief that electoral
+fraud will occur.
+
+As such, trust and distrust represent opposing degrees of confidence
+along the same spectrum. However, despite the inherent contrast, one can
+hold both positive degrees of trust and distrust, feeling relatively
+confident in both respects. Accordingly, \emph{equivalent degrees of
+trust and distrust cancel out}, rendering one relatively more insecure
+about their expectations of the future despite the fact that they may
+report feeling confident in either direction respectively. When trust
+and distrust are considered reflective of one's confidence about future
+expectations, then both can be placed along the same spectrum.
+Therefore, a lack of confidence denotes insecurity.
+
+This means that a person's baseline level of confidence in elections
+must take into account their present degree of distrust---i.e., their
+expectations of electoral fraud. Something may cause a person to have
+greater expectations that election fraud will occur, which in turn will
+always lower their trust in elections. In contrast, a person's trust in
+the integrity of the electoral process is reduced by the extent to which
+they expect that electoral fraud will occur.
+
+Thus, it follows that a person distrusts the integrity of the electoral
+process to the extent that they are to some extent certain that
+electoral fraud will occur or has occurred. They are, perhaps, poised to
+discount election results as invalid or illegitimate in advance. Either
+way, both trust and distrust refer to some positive degree of confidence
+(i.e., assurance) regarding one's expectations. They are distinguished
+by reference to either the normative idea about what \emph{should} come
+about, or what is \emph{supposed} to come about given the logical
+structure and integrity of the process. If the structure and integrity
+of some process is coherent and secure, respectively, then the outcome
+that follows will be valid. Should the integrity of that process be
+damaged or opaque, then the process becomes vulnerable and validity of
+the results are open to challenge. With respect to the administration of
+U.S. elections, the confident voter expects that votes will be counted
+as voters intend, election staff will competently administer elections,
+election technology will be secure from nefarious tampering, and that
+the process will be fair for all involved.
 
 \subsection{Why Veterans}\label{why-veterans}
+
+Election officials don't focus on recruiting people of a particular
+demographic, status, class, or prestige in order to shore up public
+trust in elections, and they don't discriminate recruitment efforts
+based on who the public thinks is best suited to secure elections from
+fraud.
 
@@
 time to civil service such as election work. Especially since staffing
-issues have been an issue since at least the 1990s
+has been an issue since at least the 1990s
 (\citeproc{ref-ferrer2024}{Ferrer, Thompson, and Orey 2024};
@@
 
-The reason why veterans arose as a special subset of the population to
-consider for this inquiry is because there was a sudden push to target
-veterans for recruitment efforts that arose shortly after the events on
-Capitol Hill on January 6th, 2021. After the 2020 election, large
-efforts were made to recruit military veterans and their families to
-work or volunteer as election staff
+Veteran military service members are, after all, civilians; Civilians
+with shared (but varied) experience and status of prior military
+service, but who are no more or less qualified for this civil
+service\footnote{Research is limited and mixed on whether veterans in
+  general are more inclined, however (\citeproc{ref-nesbit2011}{Nesbit
+  and Reingold 2011}).} than non-veteran civilians. To be frank,
+announcements about concerted efforts to recruit veterans as election
+workers should not reasonably influence one's trust that votes will be
+counted more accurately, or that election fraud will not occur; there is
+no known evidence demonstrating that actually employing veterans as
+election staff or volunteers further improves the safety, security, and
+overall integrity of elections in the United States. Moreover, there's
+no known evidence of positive influence on public perceptions of said
+outcomes when voters encounter military veterans working as staff or
+volunteers at elections sites.
+
+Rather, the claim that recruiting veterans to work as election staff and
+volunteers would improve public confidence in elections emerges as
+non-profit organizations---mainly comprised of veteran and military
+family members themselves---operate under, and promote, that assumption
+(\citeproc{ref-lawrence2024}{Lawrence 2024};
+\citeproc{ref-looker2024}{Looker 2024};
+\citeproc{ref-wentling2024}{Wentling 2024}). Non-profit groups of late
+have made incredible strides in targeted recruitment efforts under the
+notion that veterans are uniquely capable, committed, and best fit to
+serve the needs of the United States as civil servants and volunteers at
+election sites. Indeed, this study can be seen as a test of a particular
+assumption that veterans have about themselves---the assumption that
+their mere presence and civic engagement will inspire confidence in
+elections among the public.
+
+There was a sudden push to target veterans for recruitment efforts that
+arose shortly after the events on Capitol Hill on January 6th, 2021.
+After the 2020 election, large efforts were made to recruit military
+veterans and their families to work or volunteer as election staff
 (\citeproc{ref-nflfootballoperations2022}{NFL Football Operations 2022};
@@
 previous military experience. Most of these veterans actively sought out
-such groups, as opposed to being recruited by them''
-(\citeproc{ref-cooter2024}{2024}; see also
+such groups, as opposed to being recruited by them'' (see also
 \citeproc{ref-cooter2013}{Cooter 2013}). Thus, countering such
@@
 
-That being said, the general public perception, attitudes, or even
-stereotypes about military veterans are significant to consider.
-Although military recruitment shows a downward trend as of late, public
-perceptions of veterans are overwhelmingly positive
-(\citeproc{ref-kleykamp2023}{Kleykamp, Schwam, and Wenig 2023}).
-Veterans are a particularly potent group where mention of veteran status
-seems to have a positive, calming, or nullifying effect on attitudes.
-For instance, recent research shows that, during his campaign in the
-2020 Democratic Primaries, Pete Buttigieg's military background
+The key findings of literature on confidence in elections hardly point
+to public regard for veterans as a mechanism for the theoretical
+expectations of improving overall confidence in elections and improving
+feelings of voter safety at election sites. Comparable research finds
+that confidence in elections is increased through elite rhetoric from
+fellow partisans affirming legitimacy of elections
+(\citeproc{ref-clayton2023}{Clayton and Willer 2023}), or through the
+provision of information about the electoral process or other official
+messaging of election officials themselves
+(\citeproc{ref-gaudette2025}{Gaudette et al. 2025}). Neither of the
+studies just cited, however, consider attitudes or sentiment about
+veterans as a source for dispelling distrust and improving trust in
+elections. To be clear, there is no immediate ``puzzle'' in the
+literature that immediately draws out public sentiment for military
+veterans as a source for bolstering confidence in elections. That being
+said, the general public perception, attitudes, or even stereotypes
+about military veterans are significant to consider.
+
+It is important to make clear two considerations that underpin the
+notion that information about veterans will improve trust and quell
+distrust in elections. First, positive public regard for veterans
+\emph{in general} is sufficient to elicit greater trust and lower
+distrust in elections despite the fact that information about veterans
+as election workers, or even merely information on efforts to recruit
+veterans, has no bearing on the actual integrity of the electoral
+process. An underlying assumption here is that there \emph{is} something
+special about veterans, but this doesn't include a proposition on
+exactly \emph{what} that special something might be in theory. This is
+partly due to the limited research available on public regard for
+veterans, specifically in terms of elucidating an underlying mechanism
+for such positive favor. Moreover, there is limited research on public
+opinion about former and active military service members distinguished
+separately from public opinion about the military as an institution in
+general. Endorsement or support of government policies intended to
+benefit veterans specifically (e.g., federal funding on veteran
+healthcare) are easy to conflate as interchangeable with public
+attitudes about veterans as a group in particular. This, in turn,
+permits general expectations of positive influence due to the public's
+overarching positive regard for veterans, but disallows for expectations
+regarding how respondents would actually process and interpret a
+treatment that only mentions efforts to recruit them for election work.
+In short, we are sure that people sustain positive views for veterans
+generally, but beyond that I make no special effort to propose and
+examine why that is the case in greater detail.
+
+The evidence that can be gathered concerning public regard for military
+veterans shows that, generally, veterans are perceived favorably among
+the general public; although military recruitment shows a downward trend
+as of late, public perceptions of veterans are overwhelmingly positive
+(\citeproc{ref-kleykamp2023}{Kleykamp, Schwam, and Wenig 2023}). In my
+review of the literature, I found only one study which assessed public
+opinion about veterans specifically and examined whether attitudes
+differed by group (\citeproc{ref-kleykamp2018}{Kleykamp, Hipes, and
+MacLean 2018}). Kleykamp, Hipes, and MacLean
+(\citeproc{ref-kleykamp2018}{2018}) investigated the extent to which
+positive regard for military veterans in terms of both social distance
+and deservingness varies across different groups, and the extent to
+which such support is exaggerated. Their research found that levels of
+support for veterans tended to be predictably lowest, but also most
+exaggerated, among those who were younger and non-White. Determining
+what groups hold special favor for veterans still leaves it unclear as
+to what it is about veterans that engenders greater confidence in
+elections. Yet, generally, all groups expressed exaggerated support for
+veterans in more than one way (\citeproc{ref-kleykamp2018}{Kleykamp,
+Hipes, and MacLean 2018}), suggesting that public regard for veterans is
+prescribed by widespread social norm.
+
+This is taken together with literature suggesting that public trust in
+elections is malleable to factors, experiences, events, or phenomena
+that range in logical relevance to the actual structure or
+administration of elections. On the one hand, public trust is, indeed,
+influenced by information specifically about the processes of conducting
+elections (\citeproc{ref-gaudette2025}{Gaudette et al. 2025}). On the
+other hand, the public's trust in elections is not beholden to the
+demonstrated \emph{trustworthiness} of the institution of election
+administration. Thus the first consideration is simply that the positive
+public regard for veterans in general may function sufficiently as a cue
+to elicit greater trust in elections despite relevance.
+
+Second, veterans are a particularly potent group where mention of one's
+veteran status seems to have a positive, calming, or nullifying effect
+on attitudes. More so than just the general positive favor afforded to
+veterans, the group appears to have a somewhat pacifying effect on
+negative or otherwise contemptible discrimination, prejudice, and social
+stigma. For instance, recent research shows that, during his campaign in
+the 2020 Democratic Primaries, Pete Buttigieg's military background
 mitigated discrimination against him when he was presented as a veteran
@@
 areas (e.g., war competence) (\citeproc{ref-hardy2019}{Hardy et al.
-2019}). Moreover, veteran status seems to mitigate or nullify usual
-stigmas associated with mental illness. That is to say, there is
-negative stigma associated with mental illness
-(\citeproc{ref-corrigan2002}{Corrigan et al. 2002}) and such stigma
-incurs labor market discrimination (\citeproc{ref-hipes2016}{Hipes et
-al. 2016}), but evidence suggests that veteran status overrides such
-stigma and discrimination (\citeproc{ref-maclean2014}{MacLean and
-Kleykamp 2014}). Or, in another light, mental illness is seemingly more
-\emph{understandable} (i.e., permissible) for veterans given the
-presumptive reasons for their mental strife. And media framing as such
-plays an important role on public perception
-(\citeproc{ref-kleykamp2015}{Kleykamp and Hipes 2015}).
-
-\subsection{Theory and Hypotheses}\label{theory-and-hypotheses}
-
+2019}; \citeproc{ref-teigen2013}{Teigen 2013}). Moreover, veteran status
+seems to mitigate or nullify usual stigmas associated with mental
+illness. That is to say, there is negative stigma associated with mental
+illness (\citeproc{ref-corrigan2002}{Corrigan et al. 2002}) and such
+stigma incurs labor market discrimination
+(\citeproc{ref-hipes2016}{Hipes et al. 2016}), but evidence suggests
+that veteran status overrides such stigma and discrimination
+(\citeproc{ref-maclean2014}{MacLean and Kleykamp 2014}). Or, in another
+light, mental illness is seemingly more \emph{understandable} (i.e.,
+permissible) for veterans given the presumptive reasons for their mental
+strife. And media framing as such plays an important role on public
+perception (\citeproc{ref-kleykamp2015}{Kleykamp and Hipes 2015}).
+Relatedly, attitudes about homelessness and PTSD---ranging from
+perceived causes of homelessness, whether the federal government should
+dedicate more resources, perceived effectiveness of policies, to
+compassion for homeless individuals---are generally more favorable for
+the homeless population among veterans than for the homeless population
+of general adults (\citeproc{ref-tsai2021}{Tsai et al. 2021}). Such
+effects primarily pertain to attitudes about individual people or groups
+(e.g., a political candidate, prospective employees, the homeless
+population). The capacity of one's veteran status to pacify prejudice,
+discrimination, and stigma likely extends out to quell negative and
+disfavorable attitudes regarding institutions to a similar extent, e.g.,
+distrust.
+
+The question emerged in light of the recent surge of efforts nationwide
+to recruit veterans to serve as election workers
+(\citeproc{ref-lawrence2022}{Lawrence 2022};
+\citeproc{ref-wentling2024}{Wentling 2024}) midst an environment where
+election insecurities were heightened and intensified. Bearing that in
+mind, the heightened insecurities in anticipation of upcoming elections
+do not merely pertain to the election outcome (e.g., who wins), but to
+one's general sense of confidence in the integrity of elections
+administration and to the safety of casting a ballot in-person.
+
+Given the heightened tensions and electoral anxieties, the expectations
+surrounding the unique pacifying effect that veterans have on attitudes
+about individuals or other groups is extended to determine whether a
+similar effect is found when the target of one's consideration is not
+just a person or group but the institution of election administration
+itself. Thus the second consideration for ``why veterans'' are expected
+to dispel distrust in elections pertains to pacifying effect of negative
+or disfavorable attitudes observed in relevant literature.
+
+The stimulating influence of veterans as a group in the abstract is
+expected to counteract distrust and insecurity pertaining to the
+institution of elections administration, as well as inspire greater
+confidence in the same. There's scant research or evidence available to
+postulate a well-formed theory on the mechanism underlying the expected
+effects of veterans as a group on attitudes about institutions and
+processes, rather than on attitudes about persons or groups. What may be
+posited at best, however, is that distrust and insecurity in elections
+among the public is expectedly reduced to some extent through generally
+positive public regard for military veterans and their unique capacity
+to quell disfavorable attitudes.
+
+\subsection{Hypotheses}\label{hypotheses}
+
+The outcome of interest is \emph{confidence in elections}, which refers
+to trust in elections---i.e., expectations that elections will be
+administered fairly and accurately---compensated by distrust in
+elections---i.e., expectations that electoral fraud will occur.
 Considering the generally positive perception afforded to veterans by
 the public, it is reasonable to suspect that efforts that promote
-recruitment of veterans and their family members to work as election
+recruitment of veteran military service members to work as election
 staff and volunteers would boost public \emph{confidence in elections
@@
 about election official recruitment efforts of veteran service members.
+Formally,
+
+\begin{quote}
+H\textsubscript{2}: Differences in confidence in elections in one's
+local area and confidence in elections in Maricopa County, AZ, will be
+smaller among those who are presented with an announcement that election
+officials are recruiting miilitary service veterans to work as election
+staff and volunteers compared to those presented with an announcement of
+recruitment efforts that do not mention military veterans.
+\end{quote}
 
@@
 
-Finally, I expect that concerns about potential for violence will
-lessen, and confidence in voter safety improve, when presented with
-information that veterans are being actively recruited to work and
-volunteer in election offices.
+\begin{quote}
+H\textsubscript{3}: Among those who refute the legitimacy of the 2020
+election results, those presented with an announcement that election
+officials are recruiting veteran service members for election jobs will
+be associated with greater levels of confidence in elections compared to
+those presented with an announcement of recruitment efforts that do not
+mention military veterans.
+\end{quote}
+
+Prior research has found that political candidates benefit from having a
+military background (\citeproc{ref-mcdermott2015}{McDermott and
+Panagopoulos 2015}), especially evaluations of candidate's prospective
+performance on particular war issues (e.g., foreign policy, terrorism)
+(\citeproc{ref-hardy2019}{Hardy et al. 2019}). The idea is that prior
+military service provides meaningful information to use as a heuristic
+in regard to such ``war issues''. Although veterans are no longer
+actively serving, there's potentially some lingering general assumptions
+about the capacities and motives of military veterans to provide safety
+and security arising from the nature of their prior occupation as
+members of the U.S. armed forces. Insofar as the physical safety of
+people at election sites is a ``military matter'', then the potential
+that election sites may be staffed with military veterans may ease
+related concerns about the safety and security of those places. As such,
+I expect that concerns about potential for violence will be lower, and
+confidence in voter safety higher, when presented with information that
+veterans are being actively recruited to work and volunteer in election
+offices.
+
+\begin{quote}
+H\textsubscript{4a}: Concerns about the potential for violence, threats
+of violence, or intimidation while voting in person will be lower among
+those presented with an announcement that election officials are
+recruiting veteran service members for election jobs compared to those
+presented with an announcement of recruitment efforts that do not
+mention military veterans.
+\end{quote}
+
+\begin{quote}
+H\textsubscript{4b}: Confidence that voters will be safe to vote
+in-person at election sites will be higher among those presented with an
+announcement that election officials are recruiting veteran service
+members for election jobs compared to those presented with an
+announcement of recruitment efforts that do not mention military
+veterans.
+\end{quote}
 
@@
 U.S. citizens 18 years of age or older. Respondents were randomly split
-into either the treatment (\(n =\) 650) control (\(n =\) 637)
+into either the treatment (\(n = 650\)) control (\(n = 637\))
 conditions\footnote{Demographic breakdown of the sample are included in
   Appendix B.}.
+
+The median age was \(46\) (mean age was \(47\)), \(51.13\%\)
+(\(n = 658\)) women, \(46.46\%\) (\(n = 598\)) men, and approximately
+\(1.24\%\) who identified as either Non-binary/third gender (\(n = 7\))
+or preferred not to say (\(n = 9\)). The sample primarily identified as
+White or Caucasian \(75.76\%\) (\(n = 975\)), while all other non-White
+respondents comprised \(23.08\%\) (\(n = 297\)) of the sample. Those who
+held a graduate level degree (e.g., Master's, Doctorate, or Professional
+level) comprised \(12.9\%\) (\(n = 166\)) of the sample; those with
+either degree at the Associate or Bachelor's level comprised \(35.82\%\)
+(\(n = 461\)), while \(21.99\%\) (\(n = 283\)) had some college but no
+degree; and \(28.13\%\) (\(n = 362\)) had either a high school level or
+equivalent education or less than high school. The largest proportion of
+the sample were Democrat at \(43.98\%\) (\(n = 566\)), followed by
+Republicans at \(41.96\%\) (\(n = 540\)). The proportion of true
+Independents\footnote{Independent `leaners' were grouped into the
+  respective party affiliation in which they lean.} was \(12.59\%\)
+(\(n = 162\)). Among the sample, \(34.11\%\) (\(n = 439\)) said they had
+an immediately family member who was currently serving or had previously
+served in the U.S. military; \(64.72\%\) (\(n = 833\)) didn't have a
+family member who served. Approximately \(8.24\%\) (\(n = 106\)) of the
+sample were veterans, while \(1.17\%\) (\(n = 15\)) reported to be
+actively serving.
 
@@
 
+The survey included two items as an attention check prior to presenting
+either the treatment or control vignette. Respondents who failed to
+select a certain response twice in a row were removed from the survey.
+Upon presentation of either the treatment or control vignette, survey
+respondents were unable to progress further in the survey until at least
+15 seconds had elapsed.
+
 It should be noted that Maricopa County, AZ was chosen as the setting of
@@
 
-\subsubsection{Trust and Distrust in
-Elections}\label{trust-and-distrust-in-elections}
-
 A set of five survey items measured public trust in elections by
@@
 colspec={X[0.5]X[0.5]},
-column{1,2}={}{font=\fontsize{0.8em}{1.1em}\selectfont,},
+column{1,2}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
 }                     %% tabularray inner close
@@
 single scale presuming a unidimensional construct for each\footnote{See
-  Appendix C for Inter-item correlation analysis.}.
+  Appendix D for Inter-item correlation analysis.}.
 
@@
 
-The primary outcome of interest concerns public confidence in elections
-administration compensated by one's distrust in elections, i.e., their
-expectations of electoral fraud. Because trust and distrust are assessed
-by multiple Likert items, conventional methods call for combining the
-items of each set into separate Likert scales (also known as summated
-rating scales). However, many of the items comprising the trust scale
-directly oppose items capturing distrust. For instance, one item from
-the trust scale has the respondent report their confidence that votes
-will be counted as voter's intend, whereas a separate item from the
-distrust scale has the the respondent report their expectation that many
-votes will not be counted. Positive responses to these two items
-directly contradict each other, and would thus cancel out.
+The outcome of interest is \emph{confidence in elections}, which is
+comprised of trust in elections---i.e., expectations that elections will
+be administered fairly and accurately---compensated by distrust in
+elections---i.e., expectations that electoral fraud will occur. Because
+trust and distrust are assessed by multiple Likert items, conventional
+methods call for combining the items of each set into separate Likert
+scales (also known as summated rating scales). However, many of the
+items comprising the trust scale directly oppose items capturing
+distrust. For instance, one item from the trust scale has the respondent
+report their confidence that votes will be counted as voter's intend,
+whereas a separate item from the distrust scale has the the respondent
+report their expectation that many votes will not be counted. Positive
+responses to these two items directly contradict each other, and would
+thus cancel out.
 
@@
 colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
-column{1,2,3,4,5,6,7,8,9,10}={}{font=\fontsize{0.75em}{1.05em}\selectfont,},
+column{2,3,4,5,6,7,8,9,10}={}{font=\fontsize{0.75em}{1.05em}\selectfont, halign=c,},
+column{1}={}{font=\fontsize{0.75em}{1.05em}\selectfont, halign=l,},
 }                     %% tabularray inner close
@@
 
+The veteran cue is potentially compensatory, which supports the second
+hypothesis (H\textsubscript{2}). That is, the gap in confidence in local
+elections and elections in Maricopa County is reduced by the veterans
+cue, therefore compensating for the otherwise lower confidence and
+greater insecurity in Maricopa County elections. This is analogous to
+studies showing that Republicans support for a Democratic candidate is
+compensated by a Democratic candidate's veteran status. Hypothetical
+Democratic veteran candidates were more palatable to Republican
+partisans than non-veteran Democrats
+(\citeproc{ref-mcdermott2015}{McDermott and Panagopoulos 2015}).
+Similarly, Democratic veterans received higher support in Senate races,
+especially Democratic veteran Senate candidates whose military
+experience included deployment to conflict zones
+(\citeproc{ref-richardson2022}{Richardson 2022}).
+
+The point of note is that it is \emph{Democratic} candidates who receive
+\emph{more} of a benefit that comes with veteran status\footnote{Note
+  that the war veteran classification provided benefits to Republican
+  Senate candidates vote share distinct from ``common'' veterans---i.e.,
+  Republican Senate candidates who did not deploy to areas of conflict
+  (\citeproc{ref-richardson2022}{Richardson 2022}).}; the analogy being
+that it is elections located elsewhere that receive the benefits of the
+veteran cue whereas local elections do not. Note that the results can't
+necessarily be read as differing between elections at the local level
+versus national level, but rather heterogeneous effects differ by
+elections at the local level and elections in Maricopa County, AZ. The
+compensatory effect of the veteran cue may generalize to other
+jurisdictions other than one's local area, or the effect may be confined
+to Maricopa County, AZ given that this specific county had been made
+especially salient in the past.
+
 \subsubsection{2020 Election Legitimacy
@@
 held onto the belief that the 2020 election results were illegitimate.
-First, reviewing responses to items that capture trust in elections, it
-is easy to recognize the difference between the way 2020 election
-deniers responded with respect to where elections were held.
+In short, findings support the third hypothesis (H\textsubscript{3})
+allowing me to reject the null. First, reviewing responses to items that
+capture trust in elections, it is easy to recognize the difference
+between the way 2020 election deniers responded with respect to where
+elections were held.
 
@@
 
+\newpage{}
+
 In order to substantiate the overall influence of the treatment on
@@
 
-\begin{table}[H]
+\begin{table}[t]
 
@@
 beliefs. Democratic partisanship remains marginally significant at
-\(90\%\) confidence level (\(p = 0.055\)). Not believing the 2020
-election of Joe Biden was legitimate is negatively associated with
-confidence in elections. In order to assess the magnitude of this
-interaction effect of the treatment on those who refuted the 2020
-election results, I ran a model where confidence in elections was
-regressed on the interaction between the treatment and legitimacy
-beliefs, controlling for partisanship.
+\(90\%\) confidence level (\(p = 0.055\)) compared to the reference
+group (Independents). Not believing the 2020 election of Joe Biden was
+legitimate is negatively associated with confidence in elections. In
+order to assess the magnitude of this interaction effect of the
+treatment on those who refuted the 2020 election results, I ran a model
+where confidence in elections was regressed on the interaction between
+the treatment and legitimacy beliefs, controlling for partisanship.
 
@@
 
-Thus far, publicized announcements that election officials will be
-targeting veterans in their recruitment efforts does quite a bit to
-improve confidence in elections outside of one's local area (or, at
-least for elections held in Maricopa County, AZ), especially among those
-who believed the 2020 election results were illegitimate. While distrust
-is one concern during the pre-election period, it is not the only
-concern that arises in anticipation of US elections; the public must
-feel confident that voters are safe to cast a ballot in person. The
-survey included questions\footnote{See Table~\ref{tbl-4} in Appendix A}
-that allows me to assess whether those in the treatment condition
-expressed less concern for violence and more confidence in voter safety
-compared to those in the control condition.
+While confidence in elections is one concern, it is not the only concern
+that arises in anticipation of US elections; the public must feel
+confident that voters are safe to cast a ballot in person. The survey
+included questions\footnote{See Table~\ref{tbl-6} in Appendix A} that
+allowed me to assess whether those in the treatment condition expressed
+less concern for violence and more confidence in voter safety compared
+to those in the control condition.
 
@@
 control, by approximately \(8\) percentage points.
+
+\newpage{}
 
@@
   safety concerns in one's local area but results of the treatment were
-  not significantly different from the control. See Appendix D for full
-  results table of ordinal logistic regression}.
-
-\begin{table}
+  not significantly different from the control. See Appendix E for full
+  results table of ordinal logistic regression}. These findings support
+both H\textsubscript{4a} and H\textsubscript{4b} respectively,
+permitting rejection of the null for each hypothesis.
+
+\begin{table}[t]
 
@@
 colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
-column{1,2,3,4,5,6,7}={}{font=\fontsize{0.8em}{1.1em}\selectfont,},
+column{2,3,4,5,6,7}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=c,},
+column{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
 }                     %% tabularray inner close
@@
 
-\begin{table}
+\begin{table}[t]
 
@@
 
-\newpage
+\newpage{}
+
+\subsection{Discussion}\label{discussion}
+
+It should be noted that these results are limited to one's expectations
+in anticipation of election night. Whether the increase in confidence is
+sustained post-election night cannot be inferred from these results.
+Moreover, It is yet unclear whether actually encountering and
+interacting with veterans working as staff or volunteers at election
+sites does much to improve voter confidence after election night
+compared to anyone else. It may be the case that assumptions that
+veterans are filling spots as election workers and volunteers simply
+primes positive expectations as one heads into an election site,
+potentially improving voters perceptions of their own experience on the
+way out. Further research would be needed to test such an idea.
+
+As stated previously, the survey was fielded on a non-probability sample
+of 1,287 U.S. citizens 18 years of age or older. The results presented
+here are not assumed to be generalizable to the national population. It
+may be feasible to weigh the sample to demographics of the population at
+the time the survey was fielded, but this is unnecessary for the
+experimental purpose of the study. If similar findings complement or
+replicate these results, then the expense of drawing samples more
+representative of the national population may be justified. At this
+stage, however, the results are limited to demonstrating treatment
+effects that are sample dependent.
+
+Note also that the measurement items of the components trust and
+distrust, and the method of computing scores for the dependent variable,
+confidence in elections, are unique to this study but falls under the
+methodological framework of Classical Test Theory (CTT). Although survey
+measurement items were either directly drawn from or inspired by similar
+survey items found in various other surveys (e.g., SPAE, Pew), the
+question wording, response choices, coding, and computation of sum
+scores of the dependent variable are specific, thus rendering
+measurement of the hypothetical constructs of interest (i.e., trust,
+distrust) less comparable across similar studies that profess
+measurement of similar constructs (\citeproc{ref-widaman2024}{Widaman
+and Revelle 2024}). Namely, trust, distrust, or confidence in elections
+as defined and measured here.
+
+It is difficult to compare magnitude of effect with other studies given
+that the item number, item wording, measurement, and computation of
+confidence in elections is unique across most individual studies to
+include this one. For instance, Gaudette et al.
+(\citeproc{ref-gaudette2025}{2025}) doesn't compose multiple items into
+a single composite measure, but subtracts pre-treatment values from
+post-treatment values for single-item measures with Likert-style
+response options. Whereas Clayton and Willer
+(\citeproc{ref-clayton2023}{2023}) develops a scale referred to as
+``Trust in American electoral process'' by taking the mean from three
+items. The item wording of that scale is markedly similar to the items
+used to compose the trust scale of this study, but the range of response
+options differs considerably. Thus, while most studies examining public
+confidence in elections often include the core question ``How confidence
+are you that your vote {[}will be/was{]} counted as you intended in the
+most recent election?'', the different ways that researchers measure and
+compute variable scores on the outcome are most often, and
+unfortunately, sample dependent. The study of public confidence in
+elections is in desperate need of a standard method of measurement, or
+even a screened and validated item bank, and this study may be seen as a
+baby step to that end.
+
+That being said, this study generally emulates treatment effects of
+comparable studies in the literature. Gaudette et al.
+(\citeproc{ref-gaudette2025}{2025}) found positive effects of official
+messaging from election officials on various items measuring trust in
+elections and expectations of electoral fraud. Similarly, Clayton and
+Willer (\citeproc{ref-clayton2023}{2023}), confined to a sample of
+Republican participants, found positive influence on perceptions of 2020
+election legitimacy and trust in the American electoral process from
+official messaging by Republican politicians reaffirming the 2020
+election results.
+
+The setting of the vignette and specified in survey items might raise
+additional concerns on whether results are generalizable. Naming a
+specific county in the vignette adds in a potentially influential factor
+unaccounted for in the survey; some people may have attitudes about the
+county in question, others won't, while others may be muffed to consider
+a random county in the U.S. they know nothing about. Naming a real and
+somewhat salient county potentially undermines confidence that the
+treatment effects are solely attributable to veterans to an unknown
+degree. Simply put, there may be something special about Maricopa
+County, AZ in particular that generalizes across attitudes of trust or
+distrust in elections.
+
+Arguably, however, Maricopa County is indicated as the setting in both
+the treatment and control vignettes, thus the only actual difference
+between conditions is constrained to the target group being recruited.
+Future research may employ vignettes naming a fictional U.S. county to
+hopefully eliminate the setting as a concern. Alternatively additional
+survey items that ask directly about one's knowledge or sentiment about
+the county in question could inform researchers on whether the named
+county imposes any undue influence at all, or whether the setting is
+associated with other factors such as partisanship.
+
+The data of the current study is limited in helping to discern whether
+the treatment garners greater confidence in elections uniformly across
+different racial or ethnic groups given that the largest proportion of
+the sample identified their race as White (77\%). It is reasonable to
+suspect that the treatment vignette might differ by race and ethnicity,
+but the sample is insufficient to make such generalizations.
+Nevertheless, attitudes about veterans that differ by group may play an
+important role in determining whether publicized efforts to recruit
+military veterans boosts confidence in elections uniformly or whether
+the effect is merely partial to certain segments of the population. In
+their research examining whether groups differed in attitudes about
+veterans, Kleykamp, Hipes, and MacLean
+(\citeproc{ref-kleykamp2018}{2018}) could only speculate as to why
+levels of support were lowest among Hispanic and Black respondents.
+Other research has found that attitudes about the U.S. military
+generally---though not about active or veteran military service members
+in particular---differs by race and ethnicity to varying extents, but
+could not supply reason for one groups' sentiment over another
+(\citeproc{ref-nichols2015}{Nichols 2015}).
+
+Other studies have drawn out disparities in public attitudes about
+veterans but in ways that are mostly indirect, i.e., without assessing
+public regard for veterans directly. One overarching issue is that
+there's limited research that differentiates public regard for veteran
+and active military service members from the U.S. military as an
+institution in general. For instance, some studies assess public regard
+for veterans indirectly by examining whether, and to what extent,
+endorsement of certain policies differentiate by whether such policies
+benefit veterans or the public generally. In one such study, Republican
+partisanship was shown to be the most consistent factor associated with
+more favorable attitudes on homelessness and PTSD among the veteran
+population, but not among the general adult population
+(\citeproc{ref-tsai2021}{Tsai et al. 2021}).
+
+Perhaps unsurprisingly, military veterans appear to be uniquely
+deserving in the eyes of Republican partisans
+(\citeproc{ref-mcdermott2015}{McDermott and Panagopoulos 2015};
+\citeproc{ref-richardson2022}{Richardson 2022};
+\citeproc{ref-tsai2021}{Tsai et al. 2021}). As such, military veteran
+status may qualify favorable attitudes among Republican partisans
+whereas their regard for other non-veteran groups might otherwise
+express contempt or indifference. This further indicates a need for
+research to determine an underlying mechanism explaining why veterans
+incur special favor.
+
+The bluntness of the experimental stimulus and survey items don't allow
+us to establish exactly what it is about military veterans in particular
+that cues stronger confidence in elections. No survey items assessed
+public attitudes about military veterans specifically, pre- nor
+post-treatment. This unfortunately leaves no room for me to postulate
+and examine any potential mechanisms underlying results. As such, a
+question lingers about whether some antecedent mechanism transmits
+(i.e., mediates) the effects of the veteran treatment vignette to the
+outcome. To put simply, this study reiterates that there \emph{is}
+something special about veterans in particular that elicits greater
+confidence in elections, but cannot go further in determining exactly
+\emph{what} that special something might be.
+
+Factors that \emph{moderate} the relationship of the treatment on the
+outcome of interest are likely plenty, but one can only offer conjecture
+of a \emph{mediator} driving results. One potential explanation is that
+veterans, and all those who serve in the military, potentially function
+as a national symbol. The group is abstract just as the nation is
+abstract, and the potency of the veteran group emulates the potency of a
+national symbol. Recall Benedict Anderson's
+(\citeproc{ref-anderson2006}{2006}) meditation on the Tomb of the
+Unknown Soldier, ``\ldots saturated with ghostly \emph{national}
+imaginings'' (\citeproc{ref-anderson2006}{2006, 9}, emphasis original).
+In various studies, national symbols such as the flag, the national
+anthem, or even mere appeal to national identity have potent, yet
+variable, effects on different outcomes (\citeproc{ref-butz2009}{Butz
+2009}; \citeproc{ref-butz2007}{Butz, Plant, and Doerr 2007};
+\citeproc{ref-gangl2016}{Gangl, Torgler, and Kirchler 2016};
+\citeproc{ref-kalmoe2016}{Kalmoe and Gross 2016};
+\citeproc{ref-kemmelmeier2008}{Kemmelmeier and Winter 2008};
+\citeproc{ref-levendusky2018}{M. S. Levendusky 2018};
+\citeproc{ref-schatz2007}{Schatz and Lavine 2007}). It is plausible that
+military service members and veterans function in much the same way---as
+a symbol of national loyalty, pride, and nationalism for people to
+praise and revere out of a sense of duty prescribed by social norm and
+reinforced by national sentiment. As such, it may be the case that the
+treatment effect on confidence in elections is mediated through an
+affective response to a national symbol---in this case, veterans. The
+veteran cue may indeed stimulate national sentiment and subsequently
+boost confidence in elections.
+
+In results presented here, confidence in elections is associated with
+greater confidence among those in the treatment group, but neither
+vignette conveys information about the procedures or practices meant to
+safeguard election integrity; nothing in the treatment suggests to
+respondents that election integrity would be improved by recruiting
+veterans. Arguably, the results presented here speak to the ``emotional
+pathway'' mentioned in Gaudette et al.
+(\citeproc{ref-gaudette2025}{2025}) so long as we assume that there's an
+inherent appeal to national sentiment (e.g., nationalism, patriotism) by
+use of veterans\footnote{The study by Gaudette et al.
+  (\citeproc{ref-gaudette2025}{2025}) included an experiment that
+  examined the contrast between ``emotional'' versus ``informational''
+  appeals on trust in elections and beliefs that election fraud is
+  prevalent. Authors presented one of two video messages created by
+  election administration officials in either Virginia or Maricopa
+  County, AZ; the former was ``emotions-based'' in that it provided
+  little to no information about the voting process or election
+  administration, whereas the latter provided, ``\ldots specific
+  information about the processes used to ensure the integrity of the
+  vote with no appeal to emotion or patriotism''
+  (\citeproc{ref-gaudette2025}{2025, 13}).}. Importantly, if the
+veterans treatment is mediated by stimulation of affect for nation or
+national identity, then comparable stimulation of national sentiment
+unrelated to veterans should produce similar results via this
+``emotional-pathway''. However, appeals to national sentiment by use of
+sterile national symbols (e.g., banal presentation of the U.S. flag,
+playing of the national anthem) may not have the same affective
+influence on confidence in elections.
+
+In a similar vein, it is plausible that certain political apprehensions
+are nullified insofar as veterans as a group are generally perceived as
+`apolitical'---which itself may be enough to engender favor among the
+mass public (\citeproc{ref-krupnikov2022}{Krupnikov and Ryan 2022}).
+Current and former military service members may be viewed by the public
+generally as `apolitical', especially in comparison to practically any
+other social group. Indeed, an `apolitical' reputation has been long
+desired by military leaders and top brass (\citeproc{ref-baldor2020}{L.
+C. Baldor 2020}; \citeproc{ref-garamone2016}{Garamone 2016b},
+\citeproc{ref-garamone2016a}{2016a}; \citeproc{ref-lagrone2019}{LaGrone
+2019}) despite evidence to the contrary
+(\citeproc{ref-betros2001}{Betros 2001};
+\citeproc{ref-mcnerney2006}{Mcnerney 2006}). Nevertheless, the putative
+`apolitical' nature of military service may generalize to veteran
+service members, and increase confidence in elections based on the
+assumption that veterans uphold a commitment to ensure election
+integrity above their own personal loyalties, partisanship, or politics.
+Prior research has relied on the assumption that such a
+``\emph{group-based}'' norm persists among military members, which
+prescribes that the military is, or ought to be, apolitical
+(\citeproc{ref-mullinix2022}{Mullinix and Lythgoe 2022}). Although, the
+extent to which this perception generalizes widely among the mass public
+about the military in general, or about current and former service
+members in particular, has yet to be examined. Given recent events of
+far more overt politicization of the U.S. military
+(\citeproc{ref-baldor2025}{L. C. Baldor 2025};
+\citeproc{ref-baldor2025a}{L. Baldor 2025b},
+\citeproc{ref-baldor2025b}{2025c}, \citeproc{ref-baldor2025c}{2025a};
+\citeproc{ref-thomas2025}{Thomas 2025}), it would be useful for future
+research to consider whether perceptions about the military generally,
+and military leaders in particular, generalize to perceptions about
+current and former military service members. Especially insofar as such
+attitudes relate to confidence in the electoral process and
+administration.
 
@@
 staffing election sites.
-
-It should be noted that these results are limited to one's expectations
-in anticipation of election night. Whether the increase in confidence is
-sustained post-election night cannot be inferred from these results.
-Moreover, It is yet unclear whether actually encountering and
-interacting with veterans working as staff or volunteers at election
-sites does much to improve voter confidence after election night
-compared to anyone else. It may be the case that assumptions that
-veterans are filling spots as election workers and volunteers simply
-primes positive expectations as one heads into an election site,
-potentially improving voters perceptions of their own experience on the
-way out. Further research would be needed to test such an idea.
 
@@
 
-\begin{table}
-
-\caption{\label{tbl-4}Survey Items and Response Options}
+\begin{table}[H]
+
+\caption{\label{tbl-6}Pre-Treatment Survey Items and Response Options}
 
@@
 
-The median age was 46 (mean age was \(47\)), \(51.7\%\) (\(n = 658\))
-women, \(47\%\) (\(n = 598\)) men, and approximately \(1.3\%\) who
-identified as either Non-binary/third gender (\(n = 7\)) or preferred
-not to say (\(n = 9\)). A large proportion of the sample identified as
-White or Caucasian (\(n = 975, 76.65\%\)), while all other non-White
-respondents comprised \(27.83\%\) (\(n = 297\)) of the sample. Those who
-held a graduate level degree (e.g., Master's, Doctorate, or Professional
-level) comprised \(13\%\) of the sample; those with either degree at the
-Associate or Bachelor's level comprised \(36.24\%\), while \(22.25\%\)
-had some college but no degree; and \(28.46\%\) had either a high school
-level or equivalent education or less than high school. The largest
-proportion of the sample identified as Democrat at \(44.64\%\), followed
-by Republicans at \(42.59\%\). The proportion of true
-Independents\footnote{Independent `leaners' were grouped into the
-  respective party affiliation in which they lean.} was \(12.78\%\).
-
-\begin{table}[H]
+\begin{table}
 
@@
 colspec={Q[]Q[]Q[]Q[]},
-column{1,2,3,4}={}{font=\fontsize{0.7em}{1em}\selectfont,},
-rowsep={0.1em}, colsep = {0.5em},
+cell{2}{1}={c=4}{},cell{5}{1}={c=4}{},cell{10}{1}={c=4}{},cell{15}{1}={c=4}{},cell{22}{1}={c=4}{},cell{27}{1}={c=4}{},cell{33}{1}={c=4}{},cell{39}{1}={c=4}{},cell{44}{1}={c=4}{},
+column{2,3,4}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=c,},
+cell{1}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{2}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{5}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{10}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{15}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{22}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{27}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{33}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{39}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{44}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{3}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{4}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{6}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{7}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{8}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{9}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{11}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{12}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{13}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{14}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{16}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{17}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{18}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{19}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{20}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{21}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{23}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{24}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{25}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{26}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{28}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{29}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{30}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{31}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{32}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{34}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{35}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{36}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{37}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{38}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{40}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{41}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{42}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{43}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{45}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{46}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{47}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{48}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+cell{49}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
 }                     %% tabularray inner close
 \toprule
-\textbf{Demographic} & \textbf{Overall (N = 1287)} & \textbf{Control (N = 637)} & \textbf{Treatment (N = 650)} \\
-\textbf{Age group} &  &  &  \\
-18-34 & 350 (27\%) & 170 (27\%) & 180 (28\%) \\
-35-54 & 480 (37\%) & 245 (38\%) & 235 (36\%) \\
-55-74 & 390 (30\%) & 198 (31\%) & 192 (30\%) \\
-75-85+ & 67 (5.2\%) & 24 (3.8\%) & 43 (6.6\%) \\
-\textbf{Gender} &  &  &  \\
-Male & 598 (47\%) & 289 (46\%) & 309 (48\%) \\
-Female & 658 (52\%) & 330 (52\%) & 328 (51\%) \\
-Other/Refused & 16 (1.3\%) & 10 (1.6\%) & 6 (0.9\%) \\
-NA & 15 & 8 & 7 \\
-\textbf{Race/Ethnicity} &  &  &  \\
-White & 975 (77\%) & 478 (76\%) & 497 (77\%) \\
-Asian & 51 (4.0\%) & 25 (4.0\%) & 26 (4.0\%) \\
-Black & 164 (13\%) & 85 (14\%) & 79 (12\%) \\
-Other & 24 (1.9\%) & 12 (1.9\%) & 12 (1.9\%) \\
-Hispanic & 44 (3.5\%) & 24 (3.8\%) & 20 (3.1\%) \\
-American Indian & 14 (1.1\%) & 5 (0.8\%) & 9 (1.4\%) \\
-NA & 15 & 8 & 7 \\
-\textbf{Education} &  &  &  \\
-H.S. or less & 362 (28\%) & 174 (28\%) & 188 (29\%) \\
-Some college no degree & 283 (22\%) & 142 (23\%) & 141 (22\%) \\
-College degree & 461 (36\%) & 236 (38\%) & 225 (35\%) \\
-Postgraduate degree & 166 (13\%) & 77 (12\%) & 89 (14\%) \\
-NA & 15 & 8 & 7 \\
-\textbf{Party ID} &  &  &  \\
-Independent & 162 (13\%) & 83 (13\%) & 79 (12\%) \\
-Republican & 540 (43\%) & 262 (42\%) & 278 (43\%) \\
-Democrat & 566 (45\%) & 283 (45\%) & 283 (44\%) \\
-NA & 19 & 9 & 10 \\
+& n & percent & valid percent \\ \midrule %% TinyTableHeader
+Experiment Condition &&& \\
+Control & 637 & 49.5 & - \\
+Treatment & 650 & 50.5 & - \\
+Age &&& \\
+18-34 & 350 & 27.2 & - \\
+35-54 & 480 & 37.3 & - \\
+55-74 & 390 & 30.3 & - \\
+75-85+ & 67 & 5.2 & - \\
+Gender &&& \\
+Male & 598 & 46.5 & 47.0 \\
+Female & 658 & 51.1 & 51.7 \\
+Other/Refused & 16 & 1.2 & 1.3 \\
+NA & 15 & 1.2 & - \\
+Race &&& \\
+White or Caucasian & 975 & 75.8 & 76.7 \\
+Black or African American & 164 & 12.7 & 12.9 \\
+American Indian & 22 & 1.7 & 1.7 \\
+Asian & 56 & 4.4 & 4.4 \\
+Other & 55 & 4.3 & 4.3 \\
+NA & 15 & 1.2 & - \\
+Hispanic, Latino, or Spanish Origin &&& \\
+Yes & 113 & 8.8 & 8.9 \\
+No & 1148 & 89.2 & 90.3 \\
+Prefer not to say & 11 & 0.9 & 0.9 \\
+NA & 15 & 1.2 & - \\
+Education &&& \\
+H.S. or less & 362 & 28.1 & 28.5 \\
+Some college no degree & 283 & 22.0 & 22.2 \\
+College degree & 461 & 35.8 & 36.2 \\
+Postgraduate degree & 166 & 12.9 & 13.1 \\
+NA & 15 & 1.2 & - \\
+Military Relation &&& \\
+Active Duty & 15 & 1.2 & 1.2 \\
+Has Family in Military & 362 & 28.1 & 28.5 \\
+No Family in Military & 789 & 61.3 & 62.0 \\
+Prior Service (Veteran) & 106 & 8.2 & 8.3 \\
+NA & 15 & 1.2 & - \\
+Party ID &&& \\
+Independent & 162 & 12.6 & 12.8 \\
+Republican & 540 & 42.0 & 42.6 \\
+Democrat & 566 & 44.0 & 44.6 \\
+NA & 19 & 1.5 & - \\
+Political Ideology &&& \\
+Conservative & 412 & 32.0 & 32.5 \\
+Liberal & 392 & 30.5 & 30.9 \\
+Moderate & 365 & 28.4 & 28.8 \\
+Unsure & 98 & 7.6 & 7.7 \\
+NA & 20 & 1.6 & - \\
 \bottomrule
@@
 
-\subsection{Test of Random Assignment to Experiment
-Condition}\label{test-of-random-assignment-to-experiment-condition}
+\newpage{}
+
+\section{Appendix C: Test of Random Assignment to Experiment
+Condition}\label{appendix-c-test-of-random-assignment-to-experiment-condition}
 
@@
 {                     %% tabularray inner open
-width={0.8\linewidth},
-colspec={X[]X[]X[]},
-column{1,2,3}={}{font=\fontsize{0.8em}{1.1em}\selectfont,},
-hline{27}={1,2,3}{solid, black, 0.1em},
+colspec={Q[]Q[]},
+cell{2}{1}={c=2}{},cell{6}{1}={c=2}{},cell{9}{1}={c=2}{},cell{15}{1}={c=2}{},cell{19}{1}={c=2}{},
+column{2}={}{halign=c, font=\fontsize{0.7em}{1em}\selectfont, halign=c,},
+cell{1}{1}={}{halign=l, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{2}{1}={}{halign=l, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{6}{1}={}{halign=l, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{9}{1}={}{halign=l, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{15}{1}={}{halign=l, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{19}{1}={}{halign=l, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{3}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{4}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{5}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{7}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{8}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{10}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{11}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{12}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{13}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{14}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{16}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{17}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{18}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{20}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{21}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{22}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{23}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{24}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{25}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{26}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+cell{27}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+hline{22}={1,2}{solid, black, 0.05em},
 }                     %% tabularray inner close
 \toprule
-& \textbf{log(OR)} & \textbf{95\% CI} \\ \midrule %% TinyTableHeader
-\textbf{Age} &  &  \\
-18-34 &  &  \\
-35-54 & -0.17 & -0.45, 0.12 \\
-55-74 & -0.15 & -0.46, 0.15 \\
-75-85+ & 0.40 & -0.15, 0.97 \\
-\textbf{Gender} &  &  \\
-Male &  &  \\
-Female & -0.07 & -0.29, 0.15 \\
-Other/Refused & -0.62 & -1.8, 0.42 \\
-\textbf{Race/Ethnicity} &  &  \\
-White &  &  \\
-Asian & 0.03 & -0.55, 0.60 \\
-Black & -0.08 & -0.43, 0.27 \\
-Other & 0.05 & -0.82, 0.93 \\
-Hispanic & -0.24 & -0.86, 0.38 \\
-American Indian & 0.50 & -0.58, 1.7 \\
-\textbf{Education} &  &  \\
-H.S. or less &  &  \\
-Some college no degree & -0.10 & -0.42, 0.21 \\
-College degree & -0.16 & -0.45, 0.12 \\
-Postgraduate degree & 0.02 & -0.35, 0.40 \\
-\textbf{Party ID} &  &  \\
-Independent &  &  \\
-Republican & 0.12 & -0.24, 0.48 \\
-Democrat & 0.05 & -0.31, 0.40 \\
-Num.Obs & 1268 &  \\
-Log.Lik & -873.349 &  \\
-DF & 15 &  \\
-\(chisq\) & 11.01 &  \\
-\(P(>chisq)\) & 0.752 &  \\
-Deviance & 1746.698 &  \\
-Null Deviance & 1757.708 &  \\
+& log(OR) \\ \midrule %% TinyTableHeader
+\textbf{Age} & \\
+35-54 & -0.166, {[}-0.449, 0.116{]} \\
+55-74 & -0.154, {[}-0.455, 0.146{]} \\
+75-85+ & 0.402, {[}-0.149, 0.972{]} \\
+\textbf{Gender} & \\
+Female & -0.069, {[}-0.293, 0.154{]} \\
+Other/Refused & -0.625, {[}-1.751, 0.419{]} \\
+\textbf{Race} & \\
+Asian & 0.028, {[}-0.547, 0.605{]} \\
+Black & -0.081, {[}-0.429, 0.267{]} \\
+Other & 0.054, {[}-0.821, 0.929{]} \\
+Hispanic & -0.236, {[}-0.864, 0.382{]} \\
+American Indian & 0.501, {[}-0.577, 1.693{]} \\
+\textbf{Education} & \\
+Some college no degree & -0.103, {[}-0.418, 0.211{]} \\
+College degree & -0.164, {[}-0.446, 0.118{]} \\
+Postgraduate degree & 0.023, {[}-0.353, 0.400{]} \\
+\textbf{Party ID} & \\
+Republican & 0.117, {[}-0.242, 0.477{]} \\
+Democrat & 0.048, {[}-0.308, 0.404{]} \\
+N & 1268 \\
+Log.Lik. & -873.349 \\
+Deviance & 1746.69809019881 \\
+Deviance Null & 1757.70768353601 \\
+Chi2 & 11.010 \\
+P(\textgreater{}chisq) & 0.752 \\
 \bottomrule
@@
 
-\section{Appendix C: Polychoric Item and Score Correlations of Trust and
-Distrust}\label{appendix-c-polychoric-item-and-score-correlations-of-trust-and-distrust}
+\section{Appendix D: Polychoric Item and Score Correlations of Trust and
+Distrust}\label{appendix-d-polychoric-item-and-score-correlations-of-trust-and-distrust}
 
@@
 
-\section{Appendix D: Predicted Probabilities of Safety Concerns by
+\section{Appendix E: Predicted Probabilities of Safety Concerns by
 Treatment
-Condition}\label{appendix-d-predicted-probabilities-of-safety-concerns-by-treatment-condition}
+Condition}\label{appendix-e-predicted-probabilities-of-safety-concerns-by-treatment-condition}
 
@@
 colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
-column{1,2,3,4,5,6,7}={}{font=\fontsize{0.8em}{1.1em}\selectfont,},
+column{3,4,5,6,7}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=c,},
+column{1,2}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
 }                     %% tabularray inner close
@@
 
+\bibitem[\citeproctext]{ref-anderson2006}
+Anderson, Benedict. 2006. \emph{Imagined Communities : Reflections on
+the Origin and Spread of Nationalism}. Revised edition. London ; Verso.
+
 \bibitem[\citeproctext]{ref-atkeson2007}
@@
 doi:\href{https://doi.org/10.1017/S1049096507071041}{10.1017/S1049096507071041}.
+
+\bibitem[\citeproctext]{ref-baldor2025c}
+Baldor, Lolita. 2025a. {``Military Commanders Will Be Told to Send
+Transgender Troops to Medical Checks to Oust Them.''}
+\url{https://apnews.com/article/transgender-ban-military-discharge-troops-0218f0b6fec595c420bd0ac072d87335}.
+
+\bibitem[\citeproctext]{ref-baldor2025a}
+Baldor, Lolita. 2025b. {``Military Parade to Celebrate the {Army}'s
+250th Anniversary Will Be Held on {Trump}'s Birthday.''}
+\url{https://apnews.com/article/trump-army-military-parade-birthday-2f5cd12c8ccd4efddc29bfa3cf8f2705}.
+
+\bibitem[\citeproctext]{ref-baldor2025b}
+Baldor, Lolita. 2025c. {``Pentagon Directs Military to Pull Library
+Books That Address Diversity, Anti-Racism, Gender Issues.''}
+\url{https://apnews.com/article/pentagon-hegseth-dei-library-books-770364ab99591402ddffe8758432ff26}.
+
+\bibitem[\citeproctext]{ref-baldor2020}
+Baldor, Lolita C. 2020. {``Military Wary That Shakeup Could Upend Its
+Apolitical Nature.''}
+\url{https://apnews.com/article/military-wary-shakeup-upend-apolitical-89eccf0aef7cf7b99208b3bfd0453a43}.
+
+\bibitem[\citeproctext]{ref-baldor2025}
+Baldor, Lolita C. 2025. {``Hegseth Orders the Name of Gay Rights
+Activist {Harvey Milk} Scrubbed from {Navy} Ship.''}
+\url{https://apnews.com/article/harvey-milk-navy-ship-renamed-pride-month-d6cda5df15ee5bc066092d54c591c6f2}.
+
+\bibitem[\citeproctext]{ref-betros2001}
+Betros, Lance. 2001. {``Political {Partisanship} and the {Military
+Ethic} in {America}.''} \emph{Armed Forces \& Society} 27(4): 501--23.
+doi:\href{https://doi.org/10.1177/0095327X0102700401}{10.1177/0095327X0102700401}.
 
@@
 
+\bibitem[\citeproctext]{ref-butz2009}
+Butz, David A. 2009. {``National {Symbols} as {Agents} of
+{Psychological} and {Social Change}.''} \emph{Political Psychology}
+30(5): 779--804.
+doi:\href{https://doi.org/10.1111/j.1467-9221.2009.00725.x}{10.1111/j.1467-9221.2009.00725.x}.
+
+\bibitem[\citeproctext]{ref-butz2007}
+Butz, David A., E. Ashby Plant, and Celeste E. Doerr. 2007. {``Liberty
+and {Justice} for {All}? {Implications} of {Exposure} to the {U}.{S}.
+{Flag} for {Intergroup Relations}.''} \emph{Personality and Social
+Psychology Bulletin} 33(3): 396--408.
+doi:\href{https://doi.org/10.1177/0146167206296299}{10.1177/0146167206296299}.
+
 \bibitem[\citeproctext]{ref-carter2024}
@@
 
+\bibitem[\citeproctext]{ref-clayton2023}
+Clayton, Katherine, and Robb Willer. 2023. {``Endorsements from
+{Republican} Politicians Can Increase Confidence in {U}.{S}.
+Elections.''} \emph{Research \& Politics} 10(1): 20531680221148967.
+doi:\href{https://doi.org/10.1177/20531680221148967}{10.1177/20531680221148967}.
+
 \bibitem[\citeproctext]{ref-coll2024a}
@@
 
+\bibitem[\citeproctext]{ref-cook2005}
+Cook, Timothy E., and Paul Gronke. 2005. {``The {Skeptical American}:
+{Revisiting} the {Meanings} of {Trust} in {Government} and {Confidence}
+in {Institutions}.''} \emph{The Journal of Politics} 67(3): 784--803.
+doi:\href{https://doi.org/10.1111/j.1468-2508.2005.00339.x}{10.1111/j.1468-2508.2005.00339.x}.
+
 \bibitem[\citeproctext]{ref-cooter2013}
@@
 \url{https://bipartisanpolicy.org/download/?file=/wp-content/uploads/2024/04/WEB_BPC_Elections_Admin_Turnover_R01.pdf}.
+
+\bibitem[\citeproctext]{ref-gangl2016}
+Gangl, Katharina, Benno Torgler, and Erich Kirchler. 2016.
+{``Patriotism's {Impact} on {Cooperation} with the {State}: {An
+Experimental Study} on {Tax Compliance}.''} \emph{Political Psychology}
+37(6): 867--81.
+doi:\href{https://doi.org/10.1111/pops.12294}{10.1111/pops.12294}.
+
+\bibitem[\citeproctext]{ref-garamone2016a}
+Garamone, Jim. 2016a. {``Active-{Duty Personnel Must Remain Apolitical},
+{Nonpartisan}, {Dunford Says}.''}
+\url{https://www.defense.gov/News/News-Stories/Article/Article/881624/active-duty-personnel-must-remain-apolitical-nonpartisan-dunford-says}.
+
+\bibitem[\citeproctext]{ref-garamone2016}
+Garamone, Jim. 2016b. {``{DOD} Civilians, Service Members Must Remain
+Non-Partisan, Apolitical.''}
+\url{https://www.defense.gov/News/Releases/Release/Article/975910/dod-civilians-service-members-must-remain-non-partisan-apolitical}.
+
+\bibitem[\citeproctext]{ref-gaudette2025}
+Gaudette, Jennifer, Seth J. Hill, Thad Kousser, Mackenzie Lockhart, and
+Mindy Romero. 2025. {``Can {Official Messaging} on {Trust} in {Elections
+Break Through Partisan Polarization}?''} \emph{British Journal of
+Political Science} 55: e16.
+doi:\href{https://doi.org/10.1017/S0007123424000681}{10.1017/S0007123424000681}.
 
@@
 
+\bibitem[\citeproctext]{ref-kalmoe2016}
+Kalmoe, Nathan P., and Kimberly Gross. 2016. {``Cueing {Patriotism},
+{Prejudice}, and {Partisanship} in the {Age} of {Obama}: {Experimental
+Tests} of {U}.{S}. {Flag Imagery Effects} in {Presidential Elections}:
+{Flag Imagery Effects} in {Presidential Elections}.''} \emph{Political
+Psychology} 37(6): 883--99.
+doi:\href{https://doi.org/10.1111/pops.12305}{10.1111/pops.12305}.
+
+\bibitem[\citeproctext]{ref-kemmelmeier2008}
+Kemmelmeier, Markus, and David G. Winter. 2008. {``Sowing {Patriotism},
+{But Reaping Nationalism}? {Consequences} of {Exposure} to the {American
+Flag}: {Exposure} to the {American Flag}.''} \emph{Political Psychology}
+29(6): 859--79.
+doi:\href{https://doi.org/10.1111/j.1467-9221.2008.00670.x}{10.1111/j.1467-9221.2008.00670.x}.
+
 \bibitem[\citeproctext]{ref-kleykamp2015}
@@
 
+\bibitem[\citeproctext]{ref-kleykamp2018}
+Kleykamp, Meredith, Crosby Hipes, and Alair MacLean. 2018. {``Who
+{Supports U}.{S}. {Veterans} and {Who Exaggerates Their Support}?''}
+\emph{Armed Forces \& Society} 44(1): 92--115.
+doi:\href{https://doi.org/10.1177/0095327X16682786}{10.1177/0095327X16682786}.
+
 \bibitem[\citeproctext]{ref-kleykamp2023}
@@
 \url{https://www.rand.org/pubs/research_reports/RRA1363-7.html}.
+
+\bibitem[\citeproctext]{ref-krupnikov2022}
+Krupnikov, Yanna, and John Barry Ryan. 2022. \emph{The Other Divide:
+Polarization and Disengagement in {American} Politics}. Cambridge,
+United Kingdom ; Cambridge University Press.
+
+\bibitem[\citeproctext]{ref-lagrone2019}
+LaGrone, Sam. 2019. {``Shanahan {Reminds Pentagon} to {Stay
+Apolitical}.''}
+\url{https://news.usni.org/2019/06/11/acting-secdef-shanahan-reminds-pentagon-to-stay-apolitical-following-mccain-situation}.
+
+\bibitem[\citeproctext]{ref-lawrence2022}
+Lawrence, Quil. 2022. {``Vetting the {Vote}: {Military} Veterans
+Volunteer as Impartial Poll Workers.''} \emph{NPR: National}.
+\url{https://www.npr.org/2022/11/04/1133920940/vetting-the-vote-military-veterans-volunteer-as-impartial-poll-workers}.
+
+\bibitem[\citeproctext]{ref-lawrence2024}
+Lawrence, Quil. 2024. {``As Fears about Election Security Grow, Military
+Veterans Are Filling as Poll Workers.''}
+\url{https://www.npr.org/2024/10/14/nx-s1-5144186/as-fears-about-election-security-grow-military-veterans-are-filling-as-poll-workers}.
+
+\bibitem[\citeproctext]{ref-levendusky2018}
+Levendusky, Matthew S. 2018. {``Americans, {Not Partisans}: {Can Priming
+American National Identity Reduce Affective Polarization}?''} \emph{The
+Journal of Politics} 80(1): 59--70.
+\url{https://www.jstor.org/stable/26551118} (June 4, 2025).
 
@@
 
+\bibitem[\citeproctext]{ref-looker2024}
+Looker, Rachel. 2024. {``How Some Veterans Find a Way to 'Serve the
+Country Again' on {Super Tuesday}.''}
+\url{https://www.usatoday.com/story/news/politics/elections/2024/03/05/veterans-poll-workers-election/72839163007/}.
+
 \bibitem[\citeproctext]{ref-maclean2014}
@@
 
+\bibitem[\citeproctext]{ref-mcdermott2015}
+McDermott, Monika L., and Costas Panagopoulos. 2015. {``Be {All} That
+{You Can Be}: {The Electoral Impact} of {Military Service} as an
+{Information Cue}.''} \emph{Political Research Quarterly} 68(2):
+293--305.
+doi:\href{https://doi.org/10.1177/1065912915572151}{10.1177/1065912915572151}.
+
 \bibitem[\citeproctext]{ref-mcneish2023}
@@
 
+\bibitem[\citeproctext]{ref-mcnerney2006}
+Mcnerney, Michael. 2006. {``Military {Partisanship}.''} \emph{Journal of
+Political \& Military Sociology} 34(2): 281--88.
+\url{https://www.jstor.org/stable/45294228} (June 4, 2025).
+
 \bibitem[\citeproctext]{ref-mena2020}
@@
 
+\bibitem[\citeproctext]{ref-mullinix2022}
+Mullinix, Kevin J., and Trent Lythgoe. 2022. {``Priming {Norms} to
+{Combat Affective Polarization}.''} \emph{Political Research Quarterly}:
+106591292110733.
+doi:\href{https://doi.org/10.1177/10659129211073319}{10.1177/10659129211073319}.
+
 \bibitem[\citeproctext]{ref-nadeau1993}
@@
 (November 5, 2024).
+
+\bibitem[\citeproctext]{ref-nesbit2011}
+Nesbit, Rebecca, and David A. Reingold. 2011. {``Soldiers to {Citizens}:
+{The Link} Between {Military Service} and {Volunteering}.''}
+\emph{Public Administration Review} 71(1): 67--76.
+doi:\href{https://doi.org/10.1111/j.1540-6210.2010.02307.x}{10.1111/j.1540-6210.2010.02307.x}.
 
@@
 
+\bibitem[\citeproctext]{ref-nichols2015}
+Nichols, Curt. 2015. {``Public {Opinion} and the {Military}: {A
+Multivariate Exploration} of {Attitudes} in {Texas}.''} \emph{Journal of
+Political \& Military Sociology} 43: 75--106.
+\url{https://www.jstor.org/stable/48599025} (June 12, 2025).
+
 \bibitem[\citeproctext]{ref-pape2024}
@@
 
+\bibitem[\citeproctext]{ref-richardson2022}
+Richardson, David K. 2022. {``The {Electoral Impact} of {Military
+Experience}: {Evidence From U}.{S}. {Senate Elections} (1982--2016).''}
+\emph{Armed Forces \& Society} 48(4): 961--81.
+doi:\href{https://doi.org/10.1177/0095327X211038032}{10.1177/0095327X211038032}.
+
 \bibitem[\citeproctext]{ref-robitzsch2020}
@@
 
+\bibitem[\citeproctext]{ref-schatz2007}
+Schatz, Robert T., and Howard Lavine. 2007. {``Waving the {Flag}:
+{National Symbolism}, {Social Identity}, and {Political Engagement}.''}
+\emph{Political Psychology} 28(3): 329--55.
+doi:\href{https://doi.org/10.1111/j.1467-9221.2007.00571.x}{10.1111/j.1467-9221.2007.00571.x}.
+
 \bibitem[\citeproctext]{ref-spearman1907}
@@
 doi:\href{https://doi.org/10.1162/daed_a_01953}{10.1162/daed\_a\_01953}.
+
+\bibitem[\citeproctext]{ref-teigen2013}
+Teigen, Jeremy M. 2013. {``Military {Experience} in {Elections} and
+{Perceptions} of {Issue Competence}: {An Experimental Study} with
+{Television Ads}.''} \emph{Armed Forces \& Society} 39(3): 415--33.
+doi:\href{https://doi.org/10.1177/0095327X12451561}{10.1177/0095327X12451561}.
+
+\bibitem[\citeproctext]{ref-thomas2025}
+Thomas, Ashley. 2025. {``Trump {White House} Marks {Black History Month}
+While {Defense Department} Declares 'Identity Months Dead'.''}
+\url{https://apnews.com/article/trump-black-history-month-ec046b1a8122b5af9d8b26516b6837c2}.
+
+\bibitem[\citeproctext]{ref-tsai2021}
+Tsai, Jack, Jianxun Shen, Steven M. Southwick, and Robert H. Pietrzak.
+2021. {``Is There More Public Support for {US Veterans} Who Experience
+Homelessness and Posttraumatic Stress Disorder Than Other {US}
+Adults?''} \emph{Military Psychology} 33(1): 15--22.
+doi:\href{https://doi.org/10.1080/08995605.2020.1842036}{10.1080/08995605.2020.1842036}.
 
@@
 
+\bibitem[\citeproctext]{ref-wentling2024}
+Wentling, Nikki. 2024. {``Veterans Group Hits Goal of Recruiting 100,000
+Election Workers.''} \emph{Military Times: name}.
+\url{https://www.militarytimes.com/news/your-military/2024/07/10/veterans-group-hits-goal-of-recruiting-100000-election-workers/}.
+
 \bibitem[\citeproctext]{ref-widaman2022}

### 2025-07-02 index.qmd
response memo draft and revision draft

@@
 abstract: |
-  In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
+  I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
 Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
@@
 
-In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
-Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
+I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
+Results of the survey experiment show that emphasizing veterans as the target of election worker recruitment efforts is associated with greater confidence in elections and lower pre-election insecurity.
 Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned[^2].
@@
 I synthesize a review of relevant literature with a focus on how political and social science has conceptualized and ascertained public trust in elections.
-Next, I supply reasoning for why military veterans are singled out as the relevant subset of the population in this study.
-I then explicitly provide the simple theory and testable hypotheses of the study before moving on to describe the design of the survey, the measurement instruments therein, and the conceptual and operational definitions of the variables of interest.
+Next, I supply reasoning for why military veterans are singled out as the relevant subset of the population expected to influence confidence in elections.
+I provide testable hypotheses of the study before moving on to describe the design of the survey, the measurement instruments therein, and the conceptual and operational definitions of the variables of interest.
 I explain my reasoning and method for constructing the primary dependent variable, which I broadly refer to as *confidence in elections*.
@@
 
-Trust and confidence in the conduct of elections concerns aspects of elections that fall squarely within the institution of election administration.
-At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended).
+Assessing the public's *trust* in elections has not been straightforward.
+Inquiry into public trust in elections has been approached by scholars of political science in many different ways [@cook2005], often distinguishable by the scope of the research question and more or less constrained by the particular conception of public trust.
+Quite often, trust in election administration is conflated with trust in government writ large, government legitimacy, government or system responsiveness, or even satisfaction with democracy [@daniller2019].
+At this level, not only is the level of public trust in elections sometimes vague, but there's little consideration over the difference between such attitudes pre-election and post-election.
+In contrast, a considerable amount of research tends to conceive of public trust in accordance with the institution in question [@atkeson2007; @hooghe2018].
+
+Election administration^[It is important to point out here that election administration is just one institution that interacts with many other institutions and processes which form the electoral system *writ large* [@stewart2022].
+The way in which I discuss the institution of election administration, as well as the way in which I discuss and distinguish public trust in elections from broader conceptions of public trust, is borrowed substantively from @stewart2022's conceptual framework of the same.
+Distinctions between *trust* and *trustworthiness* and the notion of election administration as an institution are already apparent inspirations convenient for situating the theory of this research inquiry.] is just one part of the larger set of institutions which form the electoral system.
+As such, the performance of the institution along with the rest "...lends credibility to the outcome of an election: whether it is considered by citizens and the international community to be fair and legitimate." [@stewart2022, 236].
+
+Trust in the conduct of elections concerns aspects of elections that fall squarely within the institution of election administration.
+At this level, for instance, public trust in elections is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended).
 
@@
 Political and other social science researchers have recognized for some time the power that group identity can have over attitudes and perception [@xiao2016; @xiao2012; @vanbavel2021].
-As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve trust and confidence in election administration, and lessen expectations of electoral fraud.
-The next section elaborates on why military veterans are of particular interest in this regard.
+As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve confidence in elections, and lessen expectations of electoral fraud.
+The next section elaborates on the proposed theory, terms utilized, and why military veterans are of particular interest in this regard.
+
+# Theory
+
+This theory is constrained to public confidence in the administration of elections in the United States.
+To be clear, the scope conditions in which this theory applies concern public trust and distrust in election administration in the anticipatory period prior to the election event.
+Moreover, this study is, to a limited extent, indirectly related to public regard about veteran members of the U.S.
+Armed Forces.
+
+## Trust and Distrust in Elections
+
+The theoretical relationship between trust and distrust is important to understand, especially when it comes to the dependent outcome of interest.
+Before going further, it is necessary to explicate the conception *confidence in elections* with respect to trust and distrust.
+
+Trust is, after all, merely *belief* held in the face of uncertainty.
+Trust is reliance on the veracity of belief in the face of uncertainty.
+Said another way, trust is assured belief dependent on its supposed veracity; a state of certainty with respect to some belief or judgement.
+It is "assured" because it is one's belief that relies on something rather than nothing.
+Hence quantitative methods of the sciences are replete with things such as *confidence* intervals around our estimates.
+Therefore, I understand trust to refer to the state or quality of certainty around one's beliefs or expectations; the extent to which one is assured of their expectations regarding what is or what will be the case.
+
+The kind of *trust in elections* I refer to concerns the expectations drawn up from one's judgement about the functioning of the electoral process---the extent to which one is assured in the belief that the electoral process will be fairly and accurately administered.
+I follow the notion of public trust in elections explicated by @stewart2022,
+
+> "Public trust in U.S.
+election institutions comes down to whether voting machines accurately record votes, voter registration systems accurately record those eligible to vote, geographic information systems accurately assign voters to voting districts, election-night reporting systems accurately aggregate and communicate election results to officials and the public, and postelection audit and canvassing procedures proceed impartially and in accordance with the law." [-@stewart2022, 236]
+
+That being said, I also account for expectations of electoral fraud, which I refer to as *distrust* in elections distinguished from trust.
+Distrust in this sense is also a belief, an expectation, about the anticipated functioning of the process.
+Note, however, that the prefix *dis-* in distrust implies "apart", "lack of, not" or "opposite".
+Conventionally, distrust is defined simply as the absence of trust, thus denoting a simple inverse and mutually exclusive relationship.
+However, as it concerns the psychology of an individual, *a lack of trust doesn't necessarily imply opposite expectations or opposing beliefs*.
+In particular, a lack of trust that votes will be accurately recorded, etc., doesn't necessarily imply inversely proportional expectations that electoral fraud will occur.
+In other words, although the relationship between trust and distrust is inverse, this relationship is not mutually exclusive.
+
+A person who is certain that electoral fraud will occur clearly lacks trust in elections; an expectation that electoral fraud will occur necessarily implies a lack of trust in elections regardless of positive expressions of trust.
+However, the reverse isn't also true; expressing a lack of trust in elections *doesn't necessarily imply* an expectation that electoral fraud will occur.
+Rather, a lack of trust implies an absence of assurance in the belief that the process will be conducted fairly and accurately---a lacking quality of certainty around said belief.
+An absence of such assurance denotes a state of *insecurity*.
+Other sources of uncertainty may challenge a person's confidence regarding the integrity of elections independent from anything that would lead them to believe electoral fraud will occur or has occurred.
+However my use of distrust refers to the assured belief that the outcome will be invalid---that outcomes will be independent of the process as prescribed, thus rendering outcomes as arbitrary.
+Specifically, distrust implies assurance in the belief that electoral fraud will occur.
+
+As such, trust and distrust represent opposing degrees of confidence along the same spectrum.
+However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling relatively confident in both respects.
+Accordingly, *equivalent degrees of trust and distrust cancel out*, rendering one relatively more insecure about their expectations of the future despite the fact that they may report feeling confident in either direction respectively.
+When trust and distrust are considered reflective of one's confidence about future expectations, then both can be placed along the same spectrum.
+Therefore, a lack of confidence denotes insecurity.
+
+This means that a person's baseline level of confidence in elections must take into account their present degree of distrust---i.e., their expectations of electoral fraud.
+Something may cause a person to have greater expectations that election fraud will occur, which in turn will always lower their trust in elections.
+In contrast, a person's trust in the integrity of the electoral process is reduced by the extent to which they expect that electoral fraud will occur.
+
+Thus, it follows that a person distrusts the integrity of the electoral process to the extent that they are to some extent certain that electoral fraud will occur or has occurred.
+They are, perhaps, poised to discount election results as invalid or illegitimate in advance.
+Either way, both trust and distrust refer to some positive degree of confidence (i.e., assurance) regarding one's expectations.
+They are distinguished by reference to either the normative idea about what *should* come about, or what is *supposed* to come about given the logical structure and integrity of the process.
+If the structure and integrity of some process is coherent and secure, respectively, then the outcome that follows will be valid.
+Should the integrity of that process be damaged or opaque, then the process becomes vulnerable and validity of the results are open to challenge.
+With respect to the administration of U.S.
+elections, the confident voter expects that votes will be counted as voters intend, election staff will competently administer elections, election technology will be secure from nefarious tampering, and that the process will be fair for all involved.
 
@@
 
+Election officials don't focus on recruiting people of a particular demographic, status, class, or prestige in order to shore up public trust in elections, and they don't discriminate recruitment efforts based on who the public thinks is best suited to secure elections from fraud.
+
 Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work.
-Especially since staffing issues have been an issue since at least the 1990s [@maidenberg1996; @ferrer2024].
+Especially since staffing has been an issue since at least the 1990s [@maidenberg1996; @ferrer2024].
 In 2020, such efforts were made far more difficult by the COVID-19 pandemic [@mena2020; @abbate2020a].
@@
 
-The reason why veterans arose as a special subset of the population to consider for this inquiry is because there was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021.
+Veteran military service members are, after all, civilians; Civilians with shared (but varied) experience and status of prior military service, but who are no more or less qualified for this civil service^[Research is limited and mixed on whether veterans in general are more inclined, however [@nesbit2011].] than non-veteran civilians.
+To be frank, announcements about concerted efforts to recruit veterans as election workers should not reasonably influence one's trust that votes will be counted more accurately, or that election fraud will not occur; there is no known evidence demonstrating that actually employing veterans as election staff or volunteers further improves the safety, security, and overall integrity of elections in the United States.
+Moreover, there's no known evidence of positive influence on public perceptions of said outcomes when voters encounter military veterans working as staff or volunteers at elections sites.
+
+Rather, the claim that recruiting veterans to work as election staff and volunteers would improve public confidence in elections emerges as non-profit organizations---mainly comprised of veteran and military family members themselves---operate under, and promote, that assumption [@looker2024; @lawrence2024; @wentling2024].
+Non-profit groups of late have made incredible strides in targeted recruitment efforts under the notion that veterans are uniquely capable, committed, and best fit to serve the needs of the United States as civil servants and volunteers at election sites.
+Indeed, this study can be seen as a test of a particular assumption that veterans have about themselves---the assumption that their mere presence and civic engagement will inspire confidence in elections among the public.
+
+There was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021.
 After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterans2022; @nflfootballoperations2022].
@@
 @cooter2024 notes from her 3-year ethnographic fieldwork among Michigan militia members that, "...approximately 40% of militia leaders and 30% of members had previous military experience.
-Most of these veterans actively sought out such groups, as opposed to being recruited by them" [-@cooter2024; see also @cooter2013].
+Most of these veterans actively sought out such groups, as opposed to being recruited by them" [see also @cooter2013].
 Thus, countering such associations by promoting a different image of veterans to the mass public and veterans alike seems like a reasonable motivation.
@@
 
+The key findings of literature on confidence in elections hardly point to public regard for veterans as a mechanism for the theoretical expectations of improving overall confidence in elections and improving feelings of voter safety at election sites.
+Comparable research finds that confidence in elections is increased through elite rhetoric from fellow partisans affirming legitimacy of elections [@clayton2023], or through the provision of information about the electoral process or other official messaging of election officials themselves [@gaudette2025].
+Neither of the studies just cited, however, consider attitudes or sentiment about veterans as a source for dispelling distrust and improving trust in elections.
+To be clear, there is no immediate "puzzle" in the literature that immediately draws out public sentiment for military veterans as a source for bolstering confidence in elections.
 That being said, the general public perception, attitudes, or even stereotypes about military veterans are significant to consider.
-Although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023].
-Veterans are a particularly potent group where mention of veteran status seems to have a positive, calming, or nullifying effect on attitudes.
+
+It is important to make clear two considerations that underpin the notion that information about veterans will improve trust and quell distrust in elections.
+First, positive public regard for veterans *in general* is sufficient to elicit greater trust and lower distrust in elections despite the fact that information about veterans as election workers, or even merely information on efforts to recruit veterans, has no bearing on the actual integrity of the electoral process.
+An underlying assumption here is that there *is* something special about veterans, but this doesn't include a proposition on exactly *what* that special something might be in theory.
+This is partly due to the limited research available on public regard for veterans, specifically in terms of elucidating an underlying mechanism for such positive favor.
+Moreover, there is limited research on public opinion about former and active military service members distinguished separately from public opinion about the military as an institution in general.
+Endorsement or support of government policies intended to benefit veterans specifically (e.g., federal funding on veteran healthcare) are easy to conflate as interchangeable with public attitudes about veterans as a group in particular.
+This, in turn, permits general expectations of positive influence due to the public's overarching positive regard for veterans, but disallows for expectations regarding how respondents would actually process and interpret a treatment that only mentions efforts to recruit them for election work.
+In short, we are sure that people sustain positive views for veterans generally, but beyond that I make no special effort to propose and examine why that is the case in greater detail.
+
+The evidence that can be gathered concerning public regard for military veterans shows that, generally, veterans are perceived favorably among the general public; although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023].
+In my review of the literature, I found only one study which assessed public opinion about veterans specifically and examined whether attitudes differed by group [@kleykamp2018].
+@kleykamp2018 investigated the extent to which positive regard for military veterans in terms of both social distance and deservingness varies across different groups, and the extent to which such support is exaggerated.
+Their research found that levels of support for veterans tended to be predictably lowest, but also most exaggerated, among those who were younger and non-White.
+Determining what groups hold special favor for veterans still leaves it unclear as to what it is about veterans that engenders greater confidence in elections.
+Yet, generally, all groups expressed exaggerated support for veterans in more than one way [@kleykamp2018], suggesting that public regard for veterans is prescribed by widespread social norm.
+
+This is taken together with literature suggesting that public trust in elections is malleable to factors, experiences, events, or phenomena that range in logical relevance to the actual structure or administration of elections.
+On the one hand, public trust is, indeed, influenced by information specifically about the processes of conducting elections [@gaudette2025].
+On the other hand, the public's trust in elections is not beholden to the demonstrated *trustworthiness* of the institution of election administration.
+Thus the first consideration is simply that the positive public regard for veterans in general may function sufficiently as a cue to elicit greater trust in elections despite relevance.
+
+Second, veterans are a particularly potent group where mention of one's veteran status seems to have a positive, calming, or nullifying effect on attitudes.
+More so than just the general positive favor afforded to veterans, the group appears to have a somewhat pacifying effect on negative or otherwise contemptible discrimination, prejudice, and social stigma.
 For instance, recent research shows that, during his campaign in the 2020 Democratic Primaries, Pete Buttigieg's military background mitigated discrimination against him when he was presented as a veteran married to a man [@magni2024].
-Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@hardy2019].
+Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@teigen2013; @hardy2019].
 Moreover, veteran status seems to mitigate or nullify usual stigmas associated with mental illness.
@@
 And media framing as such plays an important role on public perception [@kleykamp2015].
-
-## Theory and Hypotheses
-
-Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veterans and their family members to work as election staff and volunteers would boost public *confidence in elections administration*.
+Relatedly, attitudes about homelessness and PTSD---ranging from perceived causes of homelessness, whether the federal government should dedicate more resources, perceived effectiveness of policies, to compassion for homeless individuals---are generally more favorable for the homeless population among veterans than for the homeless population of general adults [@tsai2021].
+Such effects primarily pertain to attitudes about individual people or groups (e.g., a political candidate, prospective employees, the homeless population).
+The capacity of one's veteran status to pacify prejudice, discrimination, and stigma likely extends out to quell negative and disfavorable attitudes regarding institutions to a similar extent, e.g., distrust.
+
+The question emerged in light of the recent surge of efforts nationwide to recruit veterans to serve as election workers [@lawrence2022; @wentling2024] midst an environment where election insecurities were heightened and intensified.
+Bearing that in mind, the heightened insecurities in anticipation of upcoming elections do not merely pertain to the election outcome (e.g., who wins), but to one's general sense of confidence in the integrity of elections administration and to the safety of casting a ballot in-person.
+
+Given the heightened tensions and electoral anxieties, the expectations surrounding the unique pacifying effect that veterans have on attitudes about individuals or other groups is extended to determine whether a similar effect is found when the target of one's consideration is not just a person or group but the institution of election administration itself.
+Thus the second consideration for "why veterans" are expected to dispel distrust in elections pertains to pacifying effect of negative or disfavorable attitudes observed in relevant literature.
+
+The stimulating influence of veterans as a group in the abstract is expected to counteract distrust and insecurity pertaining to the institution of elections administration, as well as inspire greater confidence in the same.
+There's scant research or evidence available to postulate a well-formed theory on the mechanism underlying the expected effects of veterans as a group on attitudes about institutions and processes, rather than on attitudes about persons or groups.
+What may be posited at best, however, is that distrust and insecurity in elections among the public is expectedly reduced to some extent through generally positive public regard for military veterans and their unique capacity to quell disfavorable attitudes.
+
+## Hypotheses
+
+The outcome of interest is *confidence in elections*, which refers to trust in elections---i.e., expectations that elections will be administered fairly and accurately---compensated by distrust in elections---i.e., expectations that electoral fraud will occur.
+Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veteran military service members to work as election staff and volunteers would boost public *confidence in elections administration*.
 Indeed, that is the primary hypothesis of this study.
@@
 Therefore, any observed disparity of confidence in elections between those within one's local area and those beyond will be smaller among those who are presented with information about election official recruitment efforts of veteran service members.
+Formally,
+
+> H~2~: Differences in confidence in elections in one's local area and confidence in elections in Maricopa County, AZ, will be smaller among those who are presented with an announcement that election officials are recruiting miilitary service veterans to work as election staff and volunteers compared to those presented with an announcement of recruitment efforts that do not mention military veterans.
 
@@
 
-Finally, I expect that concerns about potential for violence will lessen, and confidence in voter safety improve, when presented with information that veterans are being actively recruited to work and volunteer in election offices.
+> H~3~: Among those who refute the legitimacy of the 2020 election results, those presented with an announcement that election officials are recruiting veteran service members for election jobs will be associated with greater levels of confidence in elections compared to those presented with an announcement of recruitment efforts that do not mention military veterans.
+
+Prior research has found that political candidates benefit from having a military background [@mcdermott2015], especially evaluations of candidate's prospective performance on particular war issues (e.g., foreign policy, terrorism) [@hardy2019].
+The idea is that prior military service provides meaningful information to use as a heuristic in regard to such "war issues".
+Although veterans are no longer actively serving, there's potentially some lingering general assumptions about the capacities and motives of military veterans to provide safety and security arising from the nature of their prior occupation as members of the U.S.
+armed forces.
+Insofar as the physical safety of people at election sites is a "military matter", then the potential that election sites may be staffed with military veterans may ease related concerns about the safety and security of those places.
+As such, I expect that concerns about potential for violence will be lower, and confidence in voter safety higher, when presented with information that veterans are being actively recruited to work and volunteer in election offices.
+
+> H~4a~: Concerns about the potential for violence, threats of violence, or intimidation while voting in person will be lower among those presented with an announcement that election officials are recruiting veteran service members for election jobs compared to those presented with an announcement of recruitment efforts that do not mention military veterans.
+
+> H~4b~: Confidence that voters will be safe to vote in-person at election sites will be higher among those presented with an announcement that election officials are recruiting veteran service members for election jobs compared to those presented with an announcement of recruitment efforts that do not mention military veterans.
 
@@
 citizens 18 years of age or older.
-Respondents were randomly split into either the treatment ($n =$ 650) control ($n =$ 637) conditions[^4].
+Respondents were randomly split into either the treatment ($n = 650$) control ($n = 637$) conditions[^4].
+
+The median age was $46$ (mean age was $47$), $51.13\%$ ($n = 658$) women, $46.46\%$ ($n = 598$) men, and approximately $1.24\%$ who identified as either Non-binary/third gender ($n = 7$) or preferred not to say ($n = 9$).
+The sample primarily identified as White or Caucasian $75.76\%$ ($n = 975$), while all other non-White respondents comprised $23.08\%$ ($n = 297$) of the sample.
+Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised $12.9\%$ ($n = 166$) of the sample; those with either degree at the Associate or Bachelor's level comprised $35.82\%$ ($n = 461$), while $21.99\%$ ($n = 283$) had some college but no degree; and $28.13\%$ ($n = 362$) had either a high school level or equivalent education or less than high school.
+The largest proportion of the sample were Democrat at $43.98\%$ ($n = 566$), followed by Republicans at $41.96\%$ ($n = 540$).
+The proportion of true Independents^[Independent 'leaners' were grouped into the respective party affiliation in which they lean.] was $12.59\%$ ($n = 162$).
+Among the sample, $34.11\%$ ($n = 439$) said they had an immediately family member who was currently serving or had previously served in the U.S.
+military; $64.72\%$ ($n = 833$) didn't have a family member who served.
+Approximately $8.24\%$ ($n = 106$) of the sample were veterans, while $1.17\%$ ($n = 15$) reported to be actively serving.
 
@@
 
+The survey included two items as an attention check prior to presenting either the treatment or control vignette.
+Respondents who failed to select a certain response twice in a row were removed from the survey.
+Upon presentation of either the treatment or control vignette, survey respondents were unable to progress further in the survey until at least 15 seconds had elapsed.
+
 It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignette due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
@@
 The conventional multiple item assessment of partisanship was included and used to construct a variable of partisanship consisting of three categories: Democrat, Republican, and independent.
-
-### Trust and Distrust in Elections
 
@@
 
-The primary outcome of interest concerns public confidence in elections administration compensated by one's distrust in elections, i.e., their expectations of electoral fraud.
+The outcome of interest is *confidence in elections*, which is comprised of trust in elections---i.e., expectations that elections will be administered fairly and accurately---compensated by distrust in elections---i.e., expectations that electoral fraud will occur.
 Because trust and distrust are assessed by multiple Likert items, conventional methods call for combining the items of each set into separate Likert scales (also known as summated rating scales).
@@
 #| tbl-cap: "Mean Difference of Treatment Compared to Control Condition"
-#| tbl-colwidths: 80
+#| tbl-colwidths: [80]
 #| tbl-pos: H
@@
 
+The veteran cue is potentially compensatory, which supports the second hypothesis (H~2~).
+That is, the gap in confidence in local elections and elections in Maricopa County is reduced by the veterans cue, therefore compensating for the otherwise lower confidence and greater insecurity in Maricopa County elections.
+This is analogous to studies showing that Republicans support for a Democratic candidate is compensated by a Democratic candidate's veteran status.
+Hypothetical Democratic veteran candidates were more palatable to Republican partisans than non-veteran Democrats [@mcdermott2015].
+Similarly, Democratic veterans received higher support in Senate races, especially Democratic veteran Senate candidates whose military experience included deployment to conflict zones [@richardson2022].
+
+The point of note is that it is *Democratic* candidates who receive *more* of a benefit that comes with veteran status^[Note that the war veteran classification provided benefits to Republican Senate candidates vote share distinct from "common" veterans---i.e., Republican Senate candidates who did not deploy to areas of conflict [@richardson2022].]; the analogy being that it is elections located elsewhere that receive the benefits of the veteran cue whereas local elections do not.
+Note that the results can't necessarily be read as differing between elections at the local level versus national level, but rather heterogeneous effects differ by elections at the local level and elections in Maricopa County, AZ.
+The compensatory effect of the veteran cue may generalize to other jurisdictions other than one's local area, or the effect may be confined to Maricopa County, AZ given that this specific county had been made especially salient in the past.
+
 ### 2020 Election Legitimacy Beliefs
@@
 I now turn to results examining the effect of the treatment on those who held onto the belief that the 2020 election results were illegitimate.
+In short, findings support the third hypothesis (H~3~) allowing me to reject the null.
 First, reviewing responses to items that capture trust in elections, it is easy to recognize the difference between the way 2020 election deniers responded with respect to where elections were held.
@@
 
+{{< pagebreak >}}
+
 In order to substantiate the overall influence of the treatment on confidence in elections, I regressed the dependent variable confidence on legitimacy beliefs while controlling for partisanship.
@@
 #| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
-#| tbl-pos: H
+#| tbl-pos: t
 
@@
 The first model in @tbl-legit shows that overall confidence in elections among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
-Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
+Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$) compared to the reference group (Independents).
 Not believing the 2020 election of Joe Biden was legitimate is negatively associated with confidence in elections.
@@
 
-Thus far, publicized announcements that election officials will be targeting veterans in their recruitment efforts does quite a bit to improve confidence in elections outside of one's local area (or, at least for elections held in Maricopa County, AZ), especially among those who believed the 2020 election results were illegitimate.
-While distrust is one concern during the pre-election period, it is not the only concern that arises in anticipation of US elections; the public must feel confident that voters are safe to cast a ballot in person.
-The survey included questions^[See @tbl-4 in Appendix A] that allows me to assess whether those in the treatment condition expressed less concern for violence and more confidence in voter safety compared to those in the control condition.
+While confidence in elections is one concern, it is not the only concern that arises in anticipation of US elections; the public must feel confident that voters are safe to cast a ballot in person.
+The survey included questions^[See @tbl-6 in Appendix A] that allowed me to assess whether those in the treatment condition expressed less concern for violence and more confidence in voter safety compared to those in the control condition.
+
 ```{r}
@@
 
+{{< pagebreak >}}
+
 It would appear that the treatment vignette increased the likelihood that a respondent would select a higher response option compared to those in the control group.
@@
 See Appendix D for full results table of ordinal logistic regression].
+These findings support both H~4a~ and H~4b~ respectively, permitting rejection of the null for each hypothesis.
 
@@
 #| label: tbl-preds-diff1
-#| tbl-colwidths: 80
+#| tbl-colwidths: [80]
+#| tbl-pos: t
 #| tbl-cap: "Difference in Predicted Probabilities in Concern for violence, Threats of Violence, or Intimidation between Treatment and Control"
@@
 #| label: tbl-preds-diff2
-#| tbl-colwidths: 80
+#| tbl-colwidths: [80]
+#| tbl-pos: t
 #| tbl-cap: "Difference in Predicted Probabilities in Confidence that voters will be safe to vote in-person between Treatment and Control"
@@
 
-\newpage
+{{< pagebreak >}}
+
+## Discussion
+
+It should be noted that these results are limited to one's expectations in anticipation of election night.
+Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
+Moreover, It is yet unclear whether actually encountering and interacting with veterans working as staff or volunteers at election sites does much to improve voter confidence after election night compared to anyone else.
+It may be the case that assumptions that veterans are filling spots as election workers and volunteers simply primes positive expectations as one heads into an election site, potentially improving voters perceptions of their own experience on the way out.
+Further research would be needed to test such an idea.
+
+As stated previously, the survey was fielded on a non-probability sample of 1,287 U.S.
+citizens 18 years of age or older.
+The results presented here are not assumed to be generalizable to the national population.
+It may be feasible to weigh the sample to demographics of the population at the time the survey was fielded, but this is unnecessary for the experimental purpose of the study.
+If similar findings complement or replicate these results, then the expense of drawing samples more representative of the national population may be justified.
+At this stage, however, the results are limited to demonstrating treatment effects that are sample dependent.
+
+Note also that the measurement items of the components trust and distrust, and the method of computing scores for the dependent variable, confidence in elections, are unique to this study but falls under the methodological framework of Classical Test Theory (CTT).
+Although survey measurement items were either directly drawn from or inspired by similar survey items found in various other surveys (e.g., SPAE, Pew), the question wording, response choices, coding, and computation of sum scores of the dependent variable are specific, thus rendering measurement of the hypothetical constructs of interest (i.e., trust, distrust) less comparable across similar studies that profess measurement of similar constructs [@widaman2024].
+Namely, trust, distrust, or confidence in elections as defined and measured here.
+
+It is difficult to compare magnitude of effect with other studies given that the item number, item wording, measurement, and computation of confidence in elections is unique across most individual studies to include this one.
+For instance, @gaudette2025 doesn't compose multiple items into a single composite measure, but subtracts pre-treatment values from post-treatment values for single-item measures with Likert-style response options.
+Whereas @clayton2023 develops a scale referred to as "Trust in American electoral process" by taking the mean from three items.
+The item wording of that scale is markedly similar to the items used to compose the trust scale of this study, but the range of response options differs considerably.
+Thus, while most studies examining public confidence in elections often include the core question "How confidence are you that your vote \[will be/was\] counted as you intended in the most recent election?", the different ways that researchers measure and compute variable scores on the outcome are most often, and unfortunately, sample dependent.
+The study of public confidence in elections is in desperate need of a standard method of measurement, or even a screened and validated item bank, and this study may be seen as a baby step to that end.
+
+That being said, this study generally emulates treatment effects of comparable studies in the literature.
+@gaudette2025 found positive effects of official messaging from election officials on various items measuring trust in elections and expectations of electoral fraud.
+Similarly, @clayton2023, confined to a sample of Republican participants, found positive influence on perceptions of 2020 election legitimacy and trust in the American electoral process from official messaging by Republican politicians reaffirming the 2020 election results.
+
+The setting of the vignette and specified in survey items might raise additional concerns on whether results are generalizable.
+Naming a specific county in the vignette adds in a potentially influential factor unaccounted for in the survey; some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S.
+they know nothing about.
+Naming a real and somewhat salient county potentially undermines confidence that the treatment effects are solely attributable to veterans to an unknown degree.
+Simply put, there may be something special about Maricopa County, AZ in particular that generalizes across attitudes of trust or distrust in elections.
+
+Arguably, however, Maricopa County is indicated as the setting in both the treatment and control vignettes, thus the only actual difference between conditions is constrained to the target group being recruited.
+Future research may employ vignettes naming a fictional U.S.
+county to hopefully eliminate the setting as a concern.
+Alternatively additional survey items that ask directly about one's knowledge or sentiment about the county in question could inform researchers on whether the named county imposes any undue influence at all, or whether the setting is associated with other factors such as partisanship.
+
+The data of the current study is limited in helping to discern whether the treatment garners greater confidence in elections uniformly across different racial or ethnic groups given that the largest proportion of the sample identified their race as White (77%).
+It is reasonable to suspect that the treatment vignette might differ by race and ethnicity, but the sample is insufficient to make such generalizations.
+Nevertheless, attitudes about veterans that differ by group may play an important role in determining whether publicized efforts to recruit military veterans boosts confidence in elections uniformly or whether the effect is merely partial to certain segments of the population.
+In their research examining whether groups differed in attitudes about veterans, @kleykamp2018 could only speculate as to why levels of support were lowest among Hispanic and Black respondents.
+Other research has found that attitudes about the U.S.
+military generally---though not about active or veteran military service members in particular---differs by race and ethnicity to varying extents, but could not supply reason for one groups' sentiment over another [@nichols2015].
+
+Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly.
+One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S.
+military as an institution in general.
+For instance, some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally.
+In one such study, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes on homelessness and PTSD among the veteran population, but not among the general adult population [@tsai2021].
+
+Perhaps unsurprisingly, military veterans appear to be uniquely deserving in the eyes of Republican partisans [@tsai2021; @mcdermott2015; @richardson2022].
+As such, military veteran status may qualify favorable attitudes among Republican partisans whereas their regard for other non-veteran groups might otherwise express contempt or indifference.
+This further indicates a need for research to determine an underlying mechanism explaining why veterans incur special favor.
+
+The bluntness of the experimental stimulus and survey items don't allow us to establish exactly what it is about military veterans in particular that cues stronger confidence in elections.
+No survey items assessed public attitudes about military veterans specifically, pre- nor post-treatment.
+This unfortunately leaves no room for me to postulate and examine any potential mechanisms underlying results.
+As such, a question lingers about whether some antecedent mechanism transmits (i.e., mediates) the effects of the veteran treatment vignette to the outcome.
+To put simply, this study reiterates that there *is* something special about veterans in particular that elicits greater confidence in elections, but cannot go further in determining exactly *what* that special something might be.
+
+Factors that *moderate* the relationship of the treatment on the outcome of interest are likely plenty, but one can only offer conjecture of a *mediator* driving results.
+One potential explanation is that veterans, and all those who serve in the military, potentially function as a national symbol.
+The group is abstract just as the nation is abstract, and the potency of the veteran group emulates the potency of a national symbol.
+Recall Benedict Anderson's [-@anderson2006] meditation on the Tomb of the Unknown Soldier, "...saturated with ghostly *national* imaginings" [-@anderson2006, 9, emphasis original].
+In various studies, national symbols such as the flag, the national anthem, or even mere appeal to national identity have potent, yet variable, effects on different outcomes [@schatz2007; @butz2007; @kemmelmeier2008; @butz2009; @gangl2016; @kalmoe2016; @levendusky2018].
+It is plausible that military service members and veterans function in much the same way---as a symbol of national loyalty, pride, and nationalism for people to praise and revere out of a sense of duty prescribed by social norm and reinforced by national sentiment.
+As such, it may be the case that the treatment effect on confidence in elections is mediated through an affective response to a national symbol---in this case, veterans.
+The veteran cue may indeed stimulate national sentiment and subsequently boost confidence in elections.
+
+In results presented here, confidence in elections is associated with greater confidence among those in the treatment group, but neither vignette conveys information about the procedures or practices meant to safeguard election integrity; nothing in the treatment suggests to respondents that election integrity would be improved by recruiting veterans.
+Arguably, the results presented here speak to the "emotional pathway" mentioned in @gaudette2025 so long as we assume that there's an inherent appeal to national sentiment (e.g., nationalism, patriotism) by use of veterans[^13].
+Importantly, if the veterans treatment is mediated by stimulation of affect for nation or national identity, then comparable stimulation of national sentiment unrelated to veterans should produce similar results via this "emotional-pathway".
+However, appeals to national sentiment by use of sterile national symbols (e.g., banal presentation of the U.S.
+flag, playing of the national anthem) may not have the same affective influence on confidence in elections.
+
+[^13]: The study by @gaudette2025 included an experiment that examined the contrast between "emotional" versus "informational" appeals on trust in elections and beliefs that election fraud is prevalent.
+Authors presented one of two video messages created by election administration officials in either Virginia or Maricopa County, AZ; the former was "emotions-based" in that it provided little to no information about the voting process or election administration, whereas the latter provided, "...specific information about the processes used to ensure the integrity of the vote with no appeal to emotion or patriotism" [-@gaudette2025, 13].
+
+In a similar vein, it is plausible that certain political apprehensions are nullified insofar as veterans as a group are generally perceived as 'apolitical'---which itself may be enough to engender favor among the mass public [@krupnikov2022].
+Current and former military service members may be viewed by the public generally as 'apolitical', especially in comparison to practically any other social group.
+Indeed, an 'apolitical' reputation has been long desired by military leaders and top brass [@lagrone2019; @garamone2016; @garamone2016a; @baldor2020] despite evidence to the contrary [@betros2001; @mcnerney2006].
+Nevertheless, the putative 'apolitical' nature of military service may generalize to veteran service members, and increase confidence in elections based on the assumption that veterans uphold a commitment to ensure election integrity above their own personal loyalties, partisanship, or politics.
+Prior research has relied on the assumption that such a "*group-based*" norm persists among military members, which prescribes that the military is, or ought to be, apolitical [@mullinix2022].
+Although, the extent to which this perception generalizes widely among the mass public about the military in general, or about current and former service members in particular, has yet to be examined.
+Given recent events of far more overt politicization of the U.S.
+military [@baldor2025; @baldor2025a; @baldor2025b; @baldor2025c; @thomas2025], it would be useful for future research to consider whether perceptions about the military generally, and military leaders in particular, generalize to perceptions about current and former military service members.
+Especially insofar as such attitudes relate to confidence in the electoral process and administration.
 
@@
 Whatever election officials do to boost public confidence may be overshadowed by impressions about who is staffing election sites.
-
-It should be noted that these results are limited to one's expectations in anticipation of election night.
-Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
-Moreover, It is yet unclear whether actually encountering and interacting with veterans working as staff or volunteers at election sites does much to improve voter confidence after election night compared to anyone else.
-It may be the case that assumptions that veterans are filling spots as election workers and volunteers simply primes positive expectations as one heads into an election site, potentially improving voters perceptions of their own experience on the way out.
-Further research would be needed to test such an idea.
 
@@
 ```{r}
-#| label: tbl-4
+#| label: tbl-6
 #| tbl-cap: "Pre-Treatment Survey Items and Response Options"
 #| tbl-colwidths: [70, 30]
+#| tbl-pos: H
 
@@
 
-\newpage
-
-<!-- {{< pagebreak >}} -->
+{{< pagebreak >}}
 
@@
 
-The median age was 46 (mean age was $47$), $51.7\%$ ($n = 658$) women, $47\%$ ($n = 598$) men, and approximately $1.3\%$ who identified as either Non-binary/third gender ($n = 7$) or preferred not to say ($n = 9$).
-A large proportion of the sample identified as White or Caucasian ($n = 975, 76.65\%$), while all other non-White respondents comprised $27.83\%$ ($n = 297$) of the sample.
-Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised $13\%$ of the sample; those with either degree at the Associate or Bachelor's level comprised $36.24\%$, while $22.25\%$ had some college but no degree; and $28.46\%$ had either a high school level or equivalent education or less than high school.
-The largest proportion of the sample identified as Democrat at $44.64\%$, followed by Republicans at $42.59\%$.
-The proportion of true Independents^[Independent 'leaners' were grouped into the respective party affiliation in which they lean.] was $12.78\%$.
-
-```{r}
-#| label: sample-desc-setup
+```{r}
+#| label: tbl-demog
 #| tbl-cap: "Sample Demographics"
-#| tbl-pos: 'H'
-
+#| tbl-colwidths: [70]
+#| tbl-pos: H
+
+# descriptive stats of categorical variables
+# gtsummary method
 gtsummary::theme_gtsummary_compact()
 
-# descriptive stats of categorical variables
-# best method for html document
 tbl.desc <- data |>  
-  labelled::set_variable_labels(
-    age_4cat = "Age group",
-    gender_3cat = "Gender",
-    race2 = "Race/Ethnicity",
-    educ_4cat = "Education",
-    partyid_3cat = "Party ID"
-  ) |> 
   gtsummary::tbl_summary( 
     by = group,
+    label = list(
+      age_cat = "Age group, in years",
+      gender = "Gender",
+      race = "Race",
+      hisp = "Hispanic, Latino, or Spanish origin?",
+      educ_4cat = "Education"
+      ),
     include = c(
-    age_4cat, 
-    gender_3cat, 
-    race2,
-    educ_4cat, 
-    partyid_3cat),
+      age_cat,
+      gender,
+      race,
+      hisp,
+      educ_4cat
+      ),
     statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
@@
     missing_text = "NA") |> 
-  gtsummary::add_n() |> 
   gtsummary::add_overall() |> 
-  gtsummary::modify_header(label = "**Demographic**") |> 
+  gtsummary::modify_header(label = "**Variable**") |> 
   gtsummary::bold_labels()
-
-```
-
-```{r}
-#| label: tbl-demog
-#| tbl-cap: "Sample Demographics"
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
 
@@
                 "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
-  dplyr::select(-"**N**") |> 
   tinytable::tt(theme = "spacing") |>
@@
 
+{{< pagebreak >}}
+
+```{r}
+#| label: tbl-demog2
+#| tbl-cap: "Sample Demographics"
+#| tbl-colwidths: [70]
+#| tbl-pos: H
+
+tbl.desc2 <- data |>  
+  gtsummary::tbl_summary( 
+    by = group,
+    label = list(
+      partyid_3cat = "Party ID",
+      ideo_3cat = "Political Ideology",
+      ideolean = "If R had to choose Political Ideology",
+      voted2020 = 'Did R Vote in 2020 Election',
+      choice2020 = 'Vote Choice in 2020 Election',
+      voteintent = 'Intent to Vote in 2024 Election'),
+    include = c(
+      partyid_3cat,
+      ideo_3cat, 
+      ideolean, 
+      voted2020, 
+      choice2020),
+    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
+    missing = "ifany",
+    missing_text = "NA") |> 
+  gtsummary::add_overall() |> 
+  gtsummary::modify_header(label = "**Variable**") |> 
+  gtsummary::bold_labels()
+
+tbl.desc2 |>
+  gtsummary::as_tibble() |>
+  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
+                "**Control (N = 637)**" = "**Control**  \nN = 637",
+                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
+  tinytable::tt(theme = "spacing") |>
+  tinytable::format_tt(markdown = T) |>
+  tinytable::format_tt(replace = " ") |>
+  tinytable::style_tt(fontsize = 0.70, align = "lccc")
+
+```
+
+{{< pagebreak >}}
+
+```{r}
+#| label: tbl-demog3
+#| tbl-cap: "Sample Demographics"
+#| tbl-colwidths: [70]
+#| tbl-pos: H
+
+tbl.desc3 <- data |>  
+  gtsummary::tbl_summary( 
+    by = group,
+    label = list(
+      milserv1 = "Military Service",
+      milserv2 = "Current Active Duty",
+      milservfam = "Military Service within Family?"
+      ),
+    include = c(
+      milserv1,
+      milserv2, 
+      milservfam), 
+    type = list(
+      milserv1 ~ "categorical",
+      milserv2 ~ "categorical",
+      milservfam ~ "categorical"
+      ),
+    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
+    missing = "ifany",
+    missing_text = "NA") |> 
+  gtsummary::add_overall() |> 
+  gtsummary::modify_header(label = "**Variable**") |> 
+  gtsummary::bold_labels()
+
+tbl.desc3 |>
+  gtsummary::as_tibble() |>
+  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
+                "**Control (N = 637)**" = "**Control**  \nN = 637",
+                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
+  tinytable::tt(theme = "spacing") |>
+  tinytable::format_tt(markdown = T) |>
+  tinytable::format_tt(replace = " ") |>
+  tinytable::style_tt(fontsize = 0.70, align = "lccc")
+
+```
+
+{{< pagebreak >}}
+
 ## Test of Random Assignment to Experiment Condition
@@
 #| tbl-cap: "Logistic Regression of Random Assignment to Treatment"
+#| tbl-colwidths: [70]
+#| tbl-pos: H
 
@@
 
-# use `gtsummary` package to build regression table, then output as tibble
-logit_tab <- gtsummary::tbl_regression(
-    m1,
-    intercept = F,
-    label = list(
-      age_4cat ~"Age",
-      gender_3cat ~ "Gender",
-      race2 ~ "Race/Ethnicity",
-      educ_4cat ~ "Education",
-      partyid_3cat ~ "Party ID")) |>
-  gtsummary::bold_labels() |>
-  # gtsummary::show_header_names()
-  gtsummary::modify_header(
-    label = " ",
-    stat_nevent = "**Treatment N**") |>
-  # output as_tibble
-  gtsummary::as_tibble() |>
-  # omit p.values
-  dplyr::select(-4)
-
-# transform tibble dataframe into `tinytable` and format as markdown
-# replace NA with blank " " (or "-" if desired)
-logit_tab <- tinytable::tt(logit_tab, width = 0.8) |> 
-  tinytable::format_tt(markdown = T) |> 
-  tinytable::format_tt(replace = " ")
+cmp <- c(
+  "age_4cat35-54"  = "35-54",
+  "age_4cat55-74"  = "55-74",
+  "age_4cat75-85+"  = "75-85+",
+  "gender_3catFemale"  = "Female",
+  "gender_3catOther/Refused"  = "Other/Refused",
+  "race2Asian"  = "Asian",
+  "race2Black"  = "Black",
+  "race2Other"  = "Other",
+  "race2Hispanic"  = "Hispanic",
+  "race2American Indian"  = "American Indian",
+  "educ_4catSome college no degree"  = "Some college no degree",
+  "educ_4catCollege degree"  = "College degree",
+  "educ_4catPostgraduate degree"  = "Postgraduate degree",
+  "partyid_3catRepublican"  = "Republican",
+  "partyid_3catDemocrat"  = "Democrat"
+)
+
+tab.logit <- modelsummary::modelsummary(m1, 
+                           output = "tinytable", 
+                           estimate = "{estimate},  [{conf.low}, {conf.high}]",
+                           statistic = NULL,
+                           coef_map = cmp, 
+                           gof_map = NA)
 
@@
 # using `rbind2` function, bind 2nd table at bottom of first table 
-tinytable::rbind2(logit_tab, gof_stats, use_names = F, headers = F) |> 
+tinytable::rbind2(tab.logit, gof_stats, use_names = F, headers = F) |> 
   # add horizontal line just above fit stats
-  tinytable::style_tt(i = 26, line = "t", line_color = "black", line_width = 0.1) |>
+  tinytable::style_tt(i = 16, line = "t", line_color = "black", line_width = 0.1) |>
   # adjust fontsize of text within table
-  tinytable::style_tt(fontsize = 0.8, align = "lcc") |>
+  tinytable::style_tt(fontsize = 0.7, align = "lc") |>
   # finally, format markdown and blank out any NA fillers
@@
 #| tbl-cap-location: top
-#| tbl-colwidths: 80
+#| tbl-colwidths: [80]
 #| tbl-pos: 'H'
@@
 #| tbl-cap: "Unit-level predicted probabilities of selecting response or higher comparing experiment condition"
-#| tbl-colwidths: 80
+#| tbl-colwidths: [80]
 #| tbl-pos: 'H'
@@
 #| tbl-cap: "Unit-level predicted probabilities of selecting response or higher conditional to the Treatment experiment condition"
-#| tbl-colwidths: 80
+#| tbl-colwidths: [80]
 #| tbl-pos: 'H'

### 2025-07-04 response_memo.qmd
manuscript update with revisions after review

@@
 ---
-title: "Response to Reviewers"
+title: "Response Memo"
 format: 
@@
     mainfont: TeX Gyre Pagella
+    fontsize: 11pt
     bibliography: references.bib
@@
 I thank the Reviewers for taking time to provide their thoughtful and constructive comments.
-The Reviewers' comments are cited or summarized in [red italicized text]{.memo-reviewer-inline}, and my responses are in black Roman text.
-I also include excerpts from my revised manuscript in [blue]{.memo-excerpt-inline}.
+I revised much of the initial manuscript by restructuring certain sections and added clarification where needed.
+The Reviewers' comments are cited or summarized in [red italicized text]{.memo-reviewer-inline}, and my responses are in black text.
+I include excerpts from my revised manuscript in [blue]{.memo-excerpt-inline}.
 
@@
 Both reviewers' concerns touched on the same general issue, and the offered critiques and recommendations complemented each other.
-*Reviewer 1*{.memo-reviewer-inline} notes a general lack of discussion on potential explanations or explicit conjecture on a potential mechanism.
-**Reviewer 2**{.memo-reviewer-inline} recognized the same as ambiguity within of the theory; synthesis of the context (i.e., background section) and the literature didn't lead to a clear and concise reason for "why veterans" would be expected to influence confidence in elections.
+[*Reviewer 1*]{.memo-reviewer-inline} notes a general lack of discussion on potential explanations or explicit conjecture on a potential mechanism.
+[*Reviewer 2*]{.memo-reviewer-inline} recognized the same as ambiguity within of the theory; synthesis of the context (i.e., background section) and the literature didn't lead to a clear and concise reason for "why veterans" would be expected to influence confidence in elections.
 I dedicated a separate section titled as such hoping to clarify the source of my stated expectations, however I agree that the issue needs to be expounded at both ends.
 
-These added revisions are extensive, yet I believe adding a refined theory section and discussion section addresses the most immediate concerns raised by both reviewers.
-The theory section is revised to make clear "why veterans", noting the gaps in available literature while making the intent of the current study explicit; whereas the added discussion section complements the theory section by discussing potential explanations.
+These additions and revisions are extensive, yet I believe adding a refined theory section and discussion section addresses the most immediate concerns raised by both reviewers.
+The theory section is revised to make clear "why veterans", noting the gaps in available literature while making the intent of the current study explicit.
+The added discussion section complements the theory section by discussing potential explanations.
+
+# Reviewer 1
 
@@
 
-In response to *Reviewer 1*'s{.memo-reviewer-inline} concerns, I extend a discussion prior to the conclusion in order address potential explanations as avenues for future research.
+In response to [*Reviewer 1*]{.memo-reviewer-inline}'s comment above, I included the following text in the '**Limitations**' section,
 
 ::: {.memo-excerpt}
+## Limitations
+
 The bluntness of the experimental stimulus and survey items don't allow us to establish exactly what it is about military veterans in particular that cues stronger confidence in elections.
@@
 This unfortunately leaves no room for me to postulate and examine any potential mechanisms underlying results.
-As such, a question lingers about whether some antecedent mechanism transmits (i.e., mediates) the effects of the veteran treatment vignette to the outcome.
+:::
+
+To fully address the above comments of both reviewers, I extended a discussion prior to the conclusion on potential explanations and avenues for future research.
+
+::: {.memo-excerpt}
+## Discussion
+
+```{=typst}
+#sym.dots.h.c
+
+```
+
+A question lingers about whether some antecedent mechanism transmits (i.e., mediates) the effects of the veteran treatment vignette to the outcome.
 To put simply, this study reiterates that there *is* something special about veterans in particular that elicits greater confidence in elections, but cannot go further in determining exactly *what* that special something might be.
+Factors that *moderate* the relationship of the treatment on the outcome of interest are likely plenty, but one can only offer conjecture of a *mediator* driving results.
 
-Factors that *moderate* the relationship of the treatment on the outcome of interest are likely plenty, but one can only offer conjecture of a *mediator* driving results.
 One potential explanation is that veterans, and all those who serve in the military, potentially function as a national symbol.
@@
 
-Agreed. The revised text follows below.
+Agreed.
+I revised and inserted the following hypotheses more formally, and also inserted text to make more explicit the reasoning behind the latter hypotheses.
+The text of the '**Hypotheses**' section is unchanged save for inclusion of the following text.
 
 ::: {.memo-excerpt}
+## Hypotheses
+
+```{=typst}
+#sym.dots.h.c
+```
 
@@
 
-\dots
+```{=typst}
+#sym.dots.h.c
+```
 
@@
 
-::: {.memo-reviewer}
-***Reviewer 2***---***Data and Methods***: Manipulation check: Was one included?
-If not, I’d recommend at least discussing this.
-How do we know that respondents interpreted the “veteran” cue as the author expects?
-Could it conflate with race, gender, or general views of the military?"
-:::
-
-::: {.memo-reviewer}
-***Reviewer 2***---***Data and Methods***: Relatedly, might respondents be reacting not to “veteran” status *per se*, but to broader schemas about military discipline, patriotism, or law and order?
-If so, could this effect be amplified (or diluted) depending on the respondent’s background?
-These questions may not require new data but should be acknowledged and theorized.
-:::
-
-The above concerns raised by each reviewer are similar as they concern the potential for differential effects of the veterans cue.
-
-As for manipulation check, there were no *a priori* expectations regarding how respondents would cognitively interpret the veteran treatment vignette beyond what was stated in the hypotheses.
-Upon presentation of either the treatment or control vignette, survey respondents were unable to progress further in the survey until at least 15 seconds had elapsed.
-The survey included two "screener" items as an attention check prior to presenting either the treatment or control vignette.
-Respondents who failed to select a certain response twice in a row were removed from the survey.
-
-In response, I included the following text in the revised discussion section.
+I included the following text in the discussion to address [**Reviewer 1**]{.memo-reviewer-inline}'s comment above.
 
@@
 Nevertheless, attitudes about veterans that differ by group may play an important role in determining whether publicized efforts to recruit military veterans boosts confidence in elections uniformly or whether the effect is merely partial to certain segments of the population.
+
 In their research examining whether groups differed in attitudes about veterans, @kleykamp2018 could only speculate as to why levels of support were lowest among Hispanic and Black respondents.
+Their study was distinctive in that it stands as a rare case in which public attitudes about veteran military members was the specific focus of inquiry as opposed to studies that examine public opinion about the military in general.
 Other research has found that attitudes about the U.S.
-military generally---though not about active or veteran military service members in particular---differs by race and ethnicity to varying extents, but could not supply reason for one groups' sentiment over another [@nichols2015].
-
-Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly.
-One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S.
-military as an institution in general.
-For instance, some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally.
-In one such study, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes on homelessness and PTSD among the veteran population, but not among the general adult population [@tsai2021].
-
-Perhaps unsurprisingly, military veterans appear to be uniquely deserving in the eyes of Republican partisans [@tsai2021; @mcdermott2015; @richardson2022].
-As such, military veteran status may qualify favorable attitudes among Republican partisans whereas their regard for other non-veteran groups might otherwise express contempt or indifference.
-This further indicates a need for research to determine an underlying mechanism explaining why veterans incur special favor.
+military generally---though not about active or veteran military service members in particular---differs by race and ethnicity to varying extents, but also could not supply reason for one groups' sentiment over another^[Note, however, that the sample examined by @nichols2015 was constrained to Texas residents, and the military-related issues concerned, among other things, favor for reinstatement of a military draft, support for allowing undocumented immigrants who live in the U.S.
+to serve in the U.S.
+Armed Forces, and whether undocumented immigrants should be granted U.S.
+citizenship as a result of military service.
+Although the authors found high overall support for the military as an institution, the other military-related attitudes of interest diverge far from public opinion about veterans.
+As such, differential effects found among different racial or ethnic groups likely have little to do with attitudes about former or active military service members.] [@nichols2015].
 :::
@@
 
-To address these concerns, I include the following text in the discussion
+To address these concerns, I include the following text in the '**Limitations**' section
 
 ::: {.memo-excerpt}
-As stated previously, the survey was fielded on a non-probability sample of 1,287 U.S.
-citizens 18 years of age or older.
-The results presented here are not assumed to be generalizable to the national population.
-It may be feasible to weigh the sample to demographics of the population at the time the survey was fielded, but this is unnecessary for the experimental purpose of the study.
-If similar findings complement or replicate these results, then the expense of drawing samples more representative of the national population may be justified.
-At this stage, however, the results are limited to demonstrating treatment effects that are sample dependent.
-
-Note also that the measurement items of the components trust and distrust, and the method of computing scores for the dependent variable, confidence in elections, are unique to this study but falls under the methodological framework of Classical Test Theory (CTT).
-Although survey measurement items were either directly drawn from or inspired by similar survey items found in various other surveys (e.g., SPAE, Pew), the question wording, response choices, coding, and computation of sum scores of the dependent variable are specific, thus rendering measurement of the hypothetical constructs of interest (i.e., trust, distrust) less comparable across similar studies that profess measurement of similar constructs [@widaman2024].
-Namely, trust, distrust, or confidence in elections as defined and measured here.
-
 The setting of the vignette and specified in survey items might raise additional concerns on whether results are generalizable.
@@
 Alternatively additional survey items that ask directly about one's knowledge or sentiment about the county in question could inform researchers on whether the named county imposes any undue influence at all, or whether the setting is associated with other factors such as partisanship.
+
+As stated previously, the survey was fielded on a non-probability sample of 1,287 U.S.
+citizens 18 years of age or older.
+The results presented here are not assumed to be generalizable to the national population.
+It may be feasible to weigh the sample to demographics of the population at the time the survey was fielded, but this is unnecessary for the experimental purpose of the study.
+If similar findings complement or replicate these results, then the expense of drawing samples more representative of the national population may be justified.
+At this stage, however, the results are limited to demonstrating treatment effects.
+
+Note also that the measurement items of the components trust and distrust, and the method of computing scores for the dependent variable, confidence in elections, are unique to this study but falls under the methodological framework of Classical Test Theory (CTT).
+Although survey measurement items were either directly drawn from or inspired by similar survey items found in various other surveys (e.g., SPAE, Pew), the question wording, response choices, coding, and computation of sum scores of the dependent variable are specific, thus rendering measurement of the hypothetical constructs of interest (i.e., trust, distrust) less comparable across similar studies that profess measurement of similar constructs [@widaman2024].
+Namely, trust, distrust, or confidence in elections as defined and measured here.
 :::
 
-## Reviewer 2
+# Reviewer 2
 
@@
 
-In response to *Reviewer 2*'s comments concerning the theory, I restructure the theory section to incorporate the "Why veterans" section, expand on the premises, and add literature that better leads to the expectations.
+In response to [*Reviewer 2*]{.memo-reviewer-inline}'s comments concerning the theory, I restructure the theory section to incorporate the "Why veterans" section, expand on the premises, and add literature that better leads to the expectations.
 The text below reflects the revised theory section that better incorporates "Why Veterans".
@@
 ::: {.memo-excerpt}
+## Why Veterans
+
 Election officials don't focus on recruiting people of a particular demographic, status, class, or prestige in order to shore up public trust in elections, and they don't discriminate recruitment efforts based on who the public thinks is best suited to secure elections from fraud.
@@
 
-The key findings of literature on confidence in elections hardly point to public regard for veterans as a mechanism for the theoretical expectations of improving overall confidence in elections and improving feelings of voter safety at election sites.
+The key findings of literature on confidence in elections hardly point to public regard for veterans as a means for improving overall confidence in elections and improving feelings of voter safety at election sites.
 Comparable research finds that confidence in elections is increased through elite rhetoric from fellow partisans affirming legitimacy of elections [@clayton2023], or through the provision of information about the electoral process or other official messaging of election officials themselves [@gaudette2025].
@@
 
-The question emerged in light of the recent surge of efforts nationwide to recruit veterans to serve as election workers [@lawrence2022; @wentling2024] midst an environment where election insecurities were heightened and intensified.
-Bearing that in mind, the heightened insecurities in anticipation of upcoming elections do not merely pertain to the election outcome (e.g., who wins), but to one's general sense of confidence in the integrity of elections administration and to the safety of casting a ballot in-person.
-
 Given the heightened tensions and electoral anxieties, the expectations surrounding the unique pacifying effect that veterans have on attitudes about individuals or other groups is extended to determine whether a similar effect is found when the target of one's consideration is not just a person or group but the institution of election administration itself.
@@
 
-I agree with **Reviewer 2** and apologize for any confusion.
+I agree with [**Reviewer 2**]{.memo-reviewer-inline} and apologize for any confusion.
 In order to address the above concern, I inserted the following text which was initially cut from an earlier draft for length.
-This section follows the added text above within the theory section and also further addresses clarification of scope conditions.
+This section follows the added text above within the theory section and also further clarifies scope conditions.
 
@@
 ::: {.memo-reviewer}
+***Reviewer 2***---***Data and Methods***: Manipulation check: Was one included?
+If not, I’d recommend at least discussing this.
+How do we know that respondents interpreted the “veteran” cue as the author expects?
+Could it conflate with race, gender, or general views of the military?"
+:::
+
+Each reviewer raised similar concerns about the potential for differential effects of the veterans cue.
+
+As for [*Reviewer 2's*]{.memo-reviewer-inline} concern about inclusion of a manipulation check, there were no *a priori* expectations regarding how respondents would cognitively interpret the veteran treatment vignette beyond what was stated in the hypotheses.
+That is, there's no reason to suspect that respondents would misinterpret or confuse "military veterans" within the treatment vignette as a reference to some particular racial group or gender, or anything other than veteran military service members.
+
+I can't be sure as to whether respondent's views of the military generalize to attitudes about active service members and veterans, however that is a separate question that deserves further inquiry since it isn't adequately acknowledged or addressed in the literature.
+I included note of this with respect to discussion of the current study.
+
+:::{.memo-excerpt}
+Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly.
+One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S.
+military as an institution in general.
+Some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally.
+In one such study by @tsai2021, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes (e.g., compassion) toward homelessness and PTSD among the veteran population, but not among the general adult population.
+Additionally, Republican partisans tended to show greater support for federal funding for homelessness and PTSD research when the reference population was military veterans.
+That study, however, suggests that the effect of the veteran status cue is sensitive to the topic in question.
+
+Perhaps unsurprisingly, military veterans appear to be uniquely deserving in the eyes of Republican partisans [@tsai2021; @mcdermott2015; @richardson2022].
+As such, military veteran status may qualify favorable attitudes among Republican partisans whereas their regard for other non-veteran groups might otherwise express contempt or indifference.
+This further indicates a need for research to determine an underlying mechanism explaining why veterans incur special favor.
+:::
+
+::: {.memo-reviewer}
+***Reviewer 2***---***Data and Methods***: Relatedly, might respondents be reacting not to “veteran” status *per se*, but to broader schemas about military discipline, patriotism, or law and order?
+If so, could this effect be amplified (or diluted) depending on the respondent’s background?
+These questions may not require new data but should be acknowledged and theorized.
+:::
+
+This comment touches on similar concerns raised by [**Reviewer 1**]{.memo-reviwer-inline} with respect to differential effects of the treatment by group.
+The added text in the '**Discussion**' section addresses this comment.
+
+::: {.memo-reviewer}
 ***Reviewer 2***---***Data and Methods***: It would be helpful to know more about sample composition.
@@
 
-Despite the limitations noted previously, I added the text below in response to **Reviewer 2**'s concerns on the potential substantive significance of the findings.
-This text can be found just prior to the subsection "2020 Election Legitimacy Beliefs".
+Despite the limitations noted previously, I added the text below in response to [**Reviewer 2**]{.memo-reviewer-inline}'s concerns on the potential substantive significance of the findings.
+This text can be found just prior to the subsection '**2020 Election Legitimacy Beliefs**'.
 
@@
 Similarly, Democratic veterans received higher support in Senate races, especially Democratic veteran Senate candidates whose military experience included deployment to conflict zones [@richardson2022].
-The point of note is that it is *Democratic* candidates who receive *more* of a benefit that comes with veteran status[^]; the analogy being that it is elections located elsewhere that receive the benefits of the veteran cue whereas local elections do not.
+
+The point of note is that it is *Democratic* candidates who receive *more* of a benefit that comes with veteran status^[Note that the war veteran classification provided benefits to Republican Senate candidates vote share distinct from "common" veterans---i.e., Republican Senate candidates who did not deploy to areas of conflict [@richardson2022].]; the analogy being that it is elections located elsewhere that receive the benefits of the veteran cue whereas local elections do not.
 Note that the results can't necessarily be read as differing between elections at the local level versus national level, but rather heterogeneous effects differ by elections at the local level and elections in Maricopa County, AZ.
 The compensatory effect of the veteran cue may generalize to other jurisdictions other than one's local area, or the effect may be confined to Maricopa County, AZ given that this specific county had been made especially salient in the past.
-
-[^]: Note that the war veteran classification provided benefits to Republican Senate candidates vote share distinct from "common" veterans---i.e., Republican Senate candidates who did not deploy to areas of conflict [@richardson2022].
 :::
@@
 
-While this is understandable, I was unable to compare magnitude of effects between comparable studies due to the differences in measurements across multiple studies examining trust or confidence in elections.
-I include the following text within the discussion to address this point.
+While this is understandable, I was unable to compare magnitude of effects between comparable studies due to the differences in measurements used in multiple studies examining confidence in elections.
+To put bluntly, the percentage point differences reported in related experimental studies are mostly incomparable due to substantial differences in measurement.
+I include the following text within the conclusion stating this point.
 
@@
 
-Although I am sympathetic to this view, results permitted rejection of the null hypotheses posited in the research paper.
-It was expected that the veteran cue would not influence confidence in local elections, which was described in the findings.
-Further discussion addressing this concern was added to the description of the findings and also addressed in the revised discussion section.
+Although I am more than sympathetic to this view, I didn't have null results to report.
+However, the additions included in added the **Limitations** and **Discussion** sections speak to the concerns raised here.
+
+{{< pagebreak >}}

### 2025-07-04 docs/_tex/index.tex
manuscript update with revisions after review

@@
 
-The question emerged in light of the recent surge of efforts nationwide
-to recruit veterans to serve as election workers
-(\citeproc{ref-lawrence2022}{Lawrence 2022};
-\citeproc{ref-wentling2024}{Wentling 2024}) midst an environment where
-election insecurities were heightened and intensified. Bearing that in
-mind, the heightened insecurities in anticipation of upcoming elections
-do not merely pertain to the election outcome (e.g., who wins), but to
-one's general sense of confidence in the integrity of elections
-administration and to the safety of casting a ballot in-person.
-
 Given the heightened tensions and electoral anxieties, the expectations
@@
 
-\subsection{Discussion}\label{discussion}
+\subsection{Limitations}\label{limitations}
+
+The bluntness of the experimental stimulus and survey items don't allow
+us to establish exactly what it is about military veterans in particular
+that cues stronger confidence in elections. No survey items assessed
+public attitudes about military veterans specifically, pre- nor
+post-treatment. This unfortunately leaves no room for me to postulate
+and examine any potential mechanisms underlying results.
 
@@
 
+The setting of the vignette and specified in survey items might raise
+additional concerns on whether results are generalizable. Naming a
+specific county in the vignette adds in a potentially influential factor
+unaccounted for in the survey; some people may have attitudes about the
+county in question, others won't, while others may be muffed to consider
+a random county in the U.S. they know nothing about. Naming a real and
+somewhat salient county potentially undermines confidence that the
+treatment effects are solely attributable to veterans to an unknown
+degree. Simply put, there may be something special about Maricopa
+County, AZ in particular that generalizes across attitudes of trust or
+distrust in elections.
+
+Arguably, however, Maricopa County is indicated as the setting in both
+the treatment and control vignettes, thus the only actual difference
+between conditions is constrained to the target group being recruited.
+Future research may employ vignettes naming a fictional U.S. county to
+hopefully eliminate the setting as a concern. Alternatively additional
+survey items that ask directly about one's knowledge or sentiment about
+the county in question could inform researchers on whether the named
+county imposes any undue influence at all, or whether the setting is
+associated with other factors such as partisanship.
+
 As stated previously, the survey was fielded on a non-probability sample
@@
 stage, however, the results are limited to demonstrating treatment
-effects that are sample dependent.
+effects.
 
@@
 
-It is difficult to compare magnitude of effect with other studies given
-that the item number, item wording, measurement, and computation of
-confidence in elections is unique across most individual studies to
-include this one. For instance, Gaudette et al.
-(\citeproc{ref-gaudette2025}{2025}) doesn't compose multiple items into
-a single composite measure, but subtracts pre-treatment values from
-post-treatment values for single-item measures with Likert-style
-response options. Whereas Clayton and Willer
-(\citeproc{ref-clayton2023}{2023}) develops a scale referred to as
-``Trust in American electoral process'' by taking the mean from three
-items. The item wording of that scale is markedly similar to the items
-used to compose the trust scale of this study, but the range of response
-options differs considerably. Thus, while most studies examining public
-confidence in elections often include the core question ``How confidence
-are you that your vote {[}will be/was{]} counted as you intended in the
-most recent election?'', the different ways that researchers measure and
-compute variable scores on the outcome are most often, and
-unfortunately, sample dependent. The study of public confidence in
-elections is in desperate need of a standard method of measurement, or
-even a screened and validated item bank, and this study may be seen as a
-baby step to that end.
-
-That being said, this study generally emulates treatment effects of
-comparable studies in the literature. Gaudette et al.
-(\citeproc{ref-gaudette2025}{2025}) found positive effects of official
-messaging from election officials on various items measuring trust in
-elections and expectations of electoral fraud. Similarly, Clayton and
-Willer (\citeproc{ref-clayton2023}{2023}), confined to a sample of
-Republican participants, found positive influence on perceptions of 2020
-election legitimacy and trust in the American electoral process from
-official messaging by Republican politicians reaffirming the 2020
-election results.
-
-The setting of the vignette and specified in survey items might raise
-additional concerns on whether results are generalizable. Naming a
-specific county in the vignette adds in a potentially influential factor
-unaccounted for in the survey; some people may have attitudes about the
-county in question, others won't, while others may be muffed to consider
-a random county in the U.S. they know nothing about. Naming a real and
-somewhat salient county potentially undermines confidence that the
-treatment effects are solely attributable to veterans to an unknown
-degree. Simply put, there may be something special about Maricopa
-County, AZ in particular that generalizes across attitudes of trust or
-distrust in elections.
-
-Arguably, however, Maricopa County is indicated as the setting in both
-the treatment and control vignettes, thus the only actual difference
-between conditions is constrained to the target group being recruited.
-Future research may employ vignettes naming a fictional U.S. county to
-hopefully eliminate the setting as a concern. Alternatively additional
-survey items that ask directly about one's knowledge or sentiment about
-the county in question could inform researchers on whether the named
-county imposes any undue influence at all, or whether the setting is
-associated with other factors such as partisanship.
-
-The data of the current study is limited in helping to discern whether
-the treatment garners greater confidence in elections uniformly across
-different racial or ethnic groups given that the largest proportion of
-the sample identified their race as White (77\%). It is reasonable to
-suspect that the treatment vignette might differ by race and ethnicity,
-but the sample is insufficient to make such generalizations.
-Nevertheless, attitudes about veterans that differ by group may play an
-important role in determining whether publicized efforts to recruit
-military veterans boosts confidence in elections uniformly or whether
-the effect is merely partial to certain segments of the population. In
-their research examining whether groups differed in attitudes about
-veterans, Kleykamp, Hipes, and MacLean
-(\citeproc{ref-kleykamp2018}{2018}) could only speculate as to why
-levels of support were lowest among Hispanic and Black respondents.
-Other research has found that attitudes about the U.S. military
-generally---though not about active or veteran military service members
-in particular---differs by race and ethnicity to varying extents, but
-could not supply reason for one groups' sentiment over another
-(\citeproc{ref-nichols2015}{Nichols 2015}).
-
-Other studies have drawn out disparities in public attitudes about
-veterans but in ways that are mostly indirect, i.e., without assessing
-public regard for veterans directly. One overarching issue is that
-there's limited research that differentiates public regard for veteran
-and active military service members from the U.S. military as an
-institution in general. For instance, some studies assess public regard
-for veterans indirectly by examining whether, and to what extent,
-endorsement of certain policies differentiate by whether such policies
-benefit veterans or the public generally. In one such study, Republican
-partisanship was shown to be the most consistent factor associated with
-more favorable attitudes on homelessness and PTSD among the veteran
-population, but not among the general adult population
-(\citeproc{ref-tsai2021}{Tsai et al. 2021}).
-
-Perhaps unsurprisingly, military veterans appear to be uniquely
-deserving in the eyes of Republican partisans
-(\citeproc{ref-mcdermott2015}{McDermott and Panagopoulos 2015};
-\citeproc{ref-richardson2022}{Richardson 2022};
-\citeproc{ref-tsai2021}{Tsai et al. 2021}). As such, military veteran
-status may qualify favorable attitudes among Republican partisans
-whereas their regard for other non-veteran groups might otherwise
-express contempt or indifference. This further indicates a need for
-research to determine an underlying mechanism explaining why veterans
-incur special favor.
-
-The bluntness of the experimental stimulus and survey items don't allow
-us to establish exactly what it is about military veterans in particular
-that cues stronger confidence in elections. No survey items assessed
-public attitudes about military veterans specifically, pre- nor
-post-treatment. This unfortunately leaves no room for me to postulate
-and examine any potential mechanisms underlying results. As such, a
-question lingers about whether some antecedent mechanism transmits
+\subsection{Discussion}\label{discussion}
+
+The research question emerged in light of the recent surge of efforts
+nationwide to recruit veterans to serve as election workers
+(\citeproc{ref-lawrence2022}{Lawrence 2022};
+\citeproc{ref-wentling2024}{Wentling 2024}) midst an environment where
+election insecurities were heightened and intensified. Heightened
+insecurities in anticipation of upcoming elections do not merely pertain
+to the election outcome (e.g., who wins), but to one's general sense of
+confidence in the administration of elections, the integrity of the
+electoral process, and to the safety of casting a ballot in-person. This
+study demonstrated that information neutral to the trustworthiness of
+election administration can not only improve trust in elections, but
+simultaneously reduce distrust in elections. Those who were presented
+information about veteran recruitment efforts reported greater trust
+that votes will be counted accurately, that election staff will
+competently administer elections, that election technology will be
+secure from nefarious tampering, and that the process will be fair for
+all involved. Moreover, those presented with information about veteran
+recruitment efforts reported lower expectations that electoral fraud
+will occur. They also felt that election sites would be safe for voters
+to cast a ballot in person and were less concerned about potential
+violence compared to those who were not presented information about
+veteran recruitment efforts.
+
+Confidence in elections was greater among those who read the treatment
+vignette announcing efforts to recruit veterans to work as election
+staff and volunteers, but this effect was conditional on whether survey
+questions asked about elections Maricopa County, AZ. When survey
+questions asked about elections in one's local area, confidence in
+elections among the treatment group was not significantly different from
+the control group. However, the sample's confidence in their local area
+elections was high in general relative to elections in Maricopa County,
+AZ (Figure~\ref{fig-dist}). The results presented here suggest that the
+effect of the veteran cue in the treatment vignette is compensatory.
+That is, the gap in confidence in local elections and elections in
+Maricopa County is reduced by the veterans cue, therefore compensating
+for the otherwise lower confidence and greater insecurity in Maricopa
+County elections.
+
+A question lingers about whether some antecedent mechanism transmits
 (i.e., mediates) the effects of the veteran treatment vignette to the
@@
 confidence in elections, but cannot go further in determining exactly
-\emph{what} that special something might be.
-
-Factors that \emph{moderate} the relationship of the treatment on the
-outcome of interest are likely plenty, but one can only offer conjecture
-of a \emph{mediator} driving results. One potential explanation is that
-veterans, and all those who serve in the military, potentially function
-as a national symbol. The group is abstract just as the nation is
-abstract, and the potency of the veteran group emulates the potency of a
-national symbol. Recall Benedict Anderson's
-(\citeproc{ref-anderson2006}{2006}) meditation on the Tomb of the
-Unknown Soldier, ``\ldots saturated with ghostly \emph{national}
+\emph{what} that special something might be. Factors that
+\emph{moderate} the relationship of the treatment on the outcome of
+interest are likely plenty, but one can only offer conjecture of a
+\emph{mediator} driving results.
+
+One potential explanation is that veterans, and all those who serve in
+the military, potentially function as a national symbol. The group is
+abstract just as the nation is abstract, and the potency of the veteran
+group emulates the potency of a national symbol. Recall Benedict
+Anderson's (\citeproc{ref-anderson2006}{2006}) meditation on the Tomb of
+the Unknown Soldier, ``\ldots saturated with ghostly \emph{national}
 imaginings'' (\citeproc{ref-anderson2006}{2006, 9}, emphasis original).
@@
 administration.
+
+It is difficult to compare magnitude of effect with other studies given
+that the item number, item wording, measurement, and computation of
+confidence in elections is unique across most individual studies to
+include this one. For instance, Gaudette et al.
+(\citeproc{ref-gaudette2025}{2025}) doesn't compose multiple items into
+a single composite measure, but subtracts pre-treatment values from
+post-treatment values for single-item measures with Likert-style
+response options. Whereas Clayton and Willer
+(\citeproc{ref-clayton2023}{2023}) develops a scale referred to as
+``Trust in American electoral process'' by taking the mean from three
+items. The item wording of that scale is markedly similar to the items
+used to compose the trust scale of this study, but the range of response
+options differs considerably. Thus, while most studies examining public
+confidence in elections often include the core question ``How confidence
+are you that your vote {[}will be/was{]} counted as you intended in the
+most recent election?'', the different ways that researchers measure and
+compute variable scores on the outcome most often produces results that
+are, unfortunately, sample dependent. The study of public confidence in
+elections is in desperate need of a standard method of measurement, or
+even a screened and validated item bank, and this study may be seen as a
+baby step to that end.
+
+That being said, this study generally emulates treatment effects of
+comparable studies in the literature. Gaudette et al.
+(\citeproc{ref-gaudette2025}{2025}) found positive effects of official
+messaging from election officials on various items measuring trust in
+elections and expectations of electoral fraud. Similarly, Clayton and
+Willer (\citeproc{ref-clayton2023}{2023}), confined to a sample of
+Republican participants, found positive influence on perceptions of 2020
+election legitimacy and trust in the American electoral process from
+official messaging by Republican politicians reaffirming the 2020
+election results.
+
+The data of the current study is limited in helping to discern whether
+the treatment garners greater confidence in elections uniformly across
+different racial or ethnic groups given that the largest proportion of
+the sample identified their race as White (77\%). It is reasonable to
+suspect that the treatment vignette might differ by race and ethnicity,
+but the sample is insufficient to make such generalizations.
+Nevertheless, attitudes about veterans that differ by group may play an
+important role in determining whether publicized efforts to recruit
+military veterans boosts confidence in elections uniformly or whether
+the effect is merely partial to certain segments of the population.
+
+In their research examining whether groups differed in attitudes about
+veterans, Kleykamp, Hipes, and MacLean
+(\citeproc{ref-kleykamp2018}{2018}) could only speculate as to why
+levels of support were lowest among Hispanic and Black respondents.
+Their study was distinctive in that it stands as a rare case in which
+public attitudes about veteran military members was the specific focus
+of inquiry as opposed to studies that examine public opinion about the
+military in general. Other research has found that attitudes about the
+U.S. military generally---though not about active or veteran military
+service members in particular---differs by race and ethnicity to varying
+extents, but also could not supply reason for one groups' sentiment over
+another\footnote{Note, however, that the sample examined by Nichols
+  (\citeproc{ref-nichols2015}{2015}) was constrained to Texas residents,
+  and the military-related issues concerned, among other things, favor
+  for reinstatement of a military draft, support for allowing
+  undocumented immigrants who live in the U.S. to serve in the U.S.
+  Armed Forces, and whether undocumented immigrants should be granted
+  U.S. citizenship as a result of military service. Although the authors
+  found high overall support for the military as an institution, the
+  other military-related attitudes of interest diverge far from public
+  opinion about veterans. As such, differential effects found among
+  different racial or ethnic groups likely have little to do with
+  attitudes about former or active military service members.}
+(\citeproc{ref-nichols2015}{Nichols 2015}).
+
+Other studies have drawn out disparities in public attitudes about
+veterans but in ways that are mostly indirect, i.e., without assessing
+public regard for veterans directly. One overarching issue is that
+there's limited research that differentiates public regard for veteran
+and active military service members from the U.S. military as an
+institution in general. Some studies assess public regard for veterans
+indirectly by examining whether, and to what extent, endorsement of
+certain policies differentiate by whether such policies benefit veterans
+or the public generally. In one such study by Tsai et al.
+(\citeproc{ref-tsai2021}{2021}), Republican partisanship was shown to be
+the most consistent factor associated with more favorable attitudes
+(e.g., compassion) toward homelessness and PTSD among the veteran
+population, but not among the general adult population. Additionally,
+Republican partisans tended to show greater support for federal funding
+for homelessness and PTSD research when the reference population was
+military veterans. That study, however, suggests that the effect of the
+veteran status cue is sensitive to the topic in question.
+
+Perhaps unsurprisingly, military veterans appear to be uniquely
+deserving in the eyes of Republican partisans
+(\citeproc{ref-mcdermott2015}{McDermott and Panagopoulos 2015};
+\citeproc{ref-richardson2022}{Richardson 2022};
+\citeproc{ref-tsai2021}{Tsai et al. 2021}). As such, military veteran
+status may qualify favorable attitudes among Republican partisans
+whereas their regard for other non-veteran groups might otherwise
+express contempt or indifference. This further indicates a need for
+research to determine an underlying mechanism explaining why veterans
+incur special favor.
 

### 2025-07-04 index.qmd
manuscript update with revisions after review

@@
 # goodness-of-fit statistics
-lrm.gof.stats <- function(x, ...){
+lrm.gof.stats <- function(model, ...){
 
   out <- data.frame(
-    null.deviance = x$null.deviance,
-    df.null = x$df.null,
-    logLik = as.numeric(stats::logLik(x)),
-    AIC = stats::AIC(x),
-    BIC = stats::BIC(x),
-    deviance = stats::deviance(x),
-    df.residual = stats::df.residual(x),
-    nobs = stats::nobs(x),
-    chisq = as.numeric(x$null.deviance - stats::deviance(x)),
-    df = as.numeric(x$df.null - stats::df.residual(x)),
-    'P(>chi)' = pchisq(q=x$null.deviance - stats::deviance(x),
-                       df = x$df.null - stats::df.residual(x), 
+    nobs = stats::nobs(model),
+    null.deviance = model$null.deviance,
+    df.null = model$df.null,
+    logLik = as.numeric(stats::logLik(model)),
+    deviance = stats::deviance(model),
+    df.residual = stats::df.residual(model),
+    chisq = as.numeric(model$null.deviance - stats::deviance(model)),
+    df = as.numeric(model$df.null - stats::df.residual(model)),
+    'P(>chi)' = pchisq(q=model$null.deviance - stats::deviance(model),
+                       df = model$df.null - stats::df.residual(model), 
                        lower.tail = F)
   )
-  out <- dplyr::as_tibble(out)
+  out <- dplyr::as_tibble(out) |>  
+  # rename column variables
+  dplyr::rename(
+    "Num.Obs."      = "nobs",
+    "Log.Lik"       = "logLik",
+    "Deviance"      = "deviance",
+    "Deviance Null" = "null.deviance",
+    "DF"            = "df",
+    "chisq"          = "chisq",
+    "P(>chisq)"     = "P..chi."
+  )
   return(out)
@@
 The capacity of one's veteran status to pacify prejudice, discrimination, and stigma likely extends out to quell negative and disfavorable attitudes regarding institutions to a similar extent, e.g., distrust.
-
-The question emerged in light of the recent surge of efforts nationwide to recruit veterans to serve as election workers [@lawrence2022; @wentling2024] midst an environment where election insecurities were heightened and intensified.
-Bearing that in mind, the heightened insecurities in anticipation of upcoming elections do not merely pertain to the election outcome (e.g., who wins), but to one's general sense of confidence in the integrity of elections administration and to the safety of casting a ballot in-person.
 
@@
 @tbl-preds-diff1 and @tbl-preds-diff2 show the significant differences in predicted probabilities at 95$\%$ confidence^[The same models were run for items pertaining to safety concerns in one's local area but results of the treatment were not significantly different from the control.
-See Appendix D for full results table of ordinal logistic regression].
+See Appendix E for full results table of ordinal logistic regression].
 These findings support both H~4a~ and H~4b~ respectively, permitting rejection of the null for each hypothesis.
@@
 
-## Discussion
+## Limitations
+
+The bluntness of the experimental stimulus and survey items don't allow us to establish exactly what it is about military veterans in particular that cues stronger confidence in elections.
+No survey items assessed public attitudes about military veterans specifically, pre- nor post-treatment.
+This unfortunately leaves no room for me to postulate and examine any potential mechanisms underlying results.
 
@@
 
+The setting of the vignette and specified in survey items might raise additional concerns on whether results are generalizable.
+Naming a specific county in the vignette adds in a potentially influential factor unaccounted for in the survey; some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S.
+they know nothing about.
+Naming a real and somewhat salient county potentially undermines confidence that the treatment effects are solely attributable to veterans to an unknown degree.
+Simply put, there may be something special about Maricopa County, AZ in particular that generalizes across attitudes of trust or distrust in elections.
+
+Arguably, however, Maricopa County is indicated as the setting in both the treatment and control vignettes, thus the only actual difference between conditions is constrained to the target group being recruited.
+Future research may employ vignettes naming a fictional U.S.
+county to hopefully eliminate the setting as a concern.
+Alternatively additional survey items that ask directly about one's knowledge or sentiment about the county in question could inform researchers on whether the named county imposes any undue influence at all, or whether the setting is associated with other factors such as partisanship.
+
 As stated previously, the survey was fielded on a non-probability sample of 1,287 U.S.
@@
 If similar findings complement or replicate these results, then the expense of drawing samples more representative of the national population may be justified.
-At this stage, however, the results are limited to demonstrating treatment effects that are sample dependent.
+At this stage, however, the results are limited to demonstrating treatment effects.
 
@@
 
-It is difficult to compare magnitude of effect with other studies given that the item number, item wording, measurement, and computation of confidence in elections is unique across most individual studies to include this one.
-For instance, @gaudette2025 doesn't compose multiple items into a single composite measure, but subtracts pre-treatment values from post-treatment values for single-item measures with Likert-style response options.
-Whereas @clayton2023 develops a scale referred to as "Trust in American electoral process" by taking the mean from three items.
-The item wording of that scale is markedly similar to the items used to compose the trust scale of this study, but the range of response options differs considerably.
-Thus, while most studies examining public confidence in elections often include the core question "How confidence are you that your vote \[will be/was\] counted as you intended in the most recent election?", the different ways that researchers measure and compute variable scores on the outcome are most often, and unfortunately, sample dependent.
-The study of public confidence in elections is in desperate need of a standard method of measurement, or even a screened and validated item bank, and this study may be seen as a baby step to that end.
-
-That being said, this study generally emulates treatment effects of comparable studies in the literature.
-@gaudette2025 found positive effects of official messaging from election officials on various items measuring trust in elections and expectations of electoral fraud.
-Similarly, @clayton2023, confined to a sample of Republican participants, found positive influence on perceptions of 2020 election legitimacy and trust in the American electoral process from official messaging by Republican politicians reaffirming the 2020 election results.
-
-The setting of the vignette and specified in survey items might raise additional concerns on whether results are generalizable.
-Naming a specific county in the vignette adds in a potentially influential factor unaccounted for in the survey; some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S.
-they know nothing about.
-Naming a real and somewhat salient county potentially undermines confidence that the treatment effects are solely attributable to veterans to an unknown degree.
-Simply put, there may be something special about Maricopa County, AZ in particular that generalizes across attitudes of trust or distrust in elections.
-
-Arguably, however, Maricopa County is indicated as the setting in both the treatment and control vignettes, thus the only actual difference between conditions is constrained to the target group being recruited.
-Future research may employ vignettes naming a fictional U.S.
-county to hopefully eliminate the setting as a concern.
-Alternatively additional survey items that ask directly about one's knowledge or sentiment about the county in question could inform researchers on whether the named county imposes any undue influence at all, or whether the setting is associated with other factors such as partisanship.
-
-The data of the current study is limited in helping to discern whether the treatment garners greater confidence in elections uniformly across different racial or ethnic groups given that the largest proportion of the sample identified their race as White (77%).
-It is reasonable to suspect that the treatment vignette might differ by race and ethnicity, but the sample is insufficient to make such generalizations.
-Nevertheless, attitudes about veterans that differ by group may play an important role in determining whether publicized efforts to recruit military veterans boosts confidence in elections uniformly or whether the effect is merely partial to certain segments of the population.
-In their research examining whether groups differed in attitudes about veterans, @kleykamp2018 could only speculate as to why levels of support were lowest among Hispanic and Black respondents.
-Other research has found that attitudes about the U.S.
-military generally---though not about active or veteran military service members in particular---differs by race and ethnicity to varying extents, but could not supply reason for one groups' sentiment over another [@nichols2015].
-
-Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly.
-One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S.
-military as an institution in general.
-For instance, some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally.
-In one such study, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes on homelessness and PTSD among the veteran population, but not among the general adult population [@tsai2021].
-
-Perhaps unsurprisingly, military veterans appear to be uniquely deserving in the eyes of Republican partisans [@tsai2021; @mcdermott2015; @richardson2022].
-As such, military veteran status may qualify favorable attitudes among Republican partisans whereas their regard for other non-veteran groups might otherwise express contempt or indifference.
-This further indicates a need for research to determine an underlying mechanism explaining why veterans incur special favor.
-
-The bluntness of the experimental stimulus and survey items don't allow us to establish exactly what it is about military veterans in particular that cues stronger confidence in elections.
-No survey items assessed public attitudes about military veterans specifically, pre- nor post-treatment.
-This unfortunately leaves no room for me to postulate and examine any potential mechanisms underlying results.
-As such, a question lingers about whether some antecedent mechanism transmits (i.e., mediates) the effects of the veteran treatment vignette to the outcome.
+## Discussion
+
+The research question emerged in light of the recent surge of efforts nationwide to recruit veterans to serve as election workers [@lawrence2022; @wentling2024] midst an environment where election insecurities were heightened and intensified.
+Heightened insecurities in anticipation of upcoming elections do not merely pertain to the election outcome (e.g., who wins), but to one's general sense of confidence in the administration of elections, the integrity of the electoral process, and to the safety of casting a ballot in-person.
+This study demonstrated that information neutral to the trustworthiness of election administration can not only improve trust in elections, but simultaneously reduce distrust in elections.
+Those who were presented information about veteran recruitment efforts reported greater trust that votes will be counted accurately, that election staff will competently administer elections, that election technology will be secure from nefarious tampering, and that the process will be fair for all involved.
+Moreover, those presented with information about veteran recruitment efforts reported lower expectations that electoral fraud will occur.
+They also felt that election sites would be safe for voters to cast a ballot in person and were less concerned about potential violence compared to those who were not presented information about veteran recruitment efforts.
+
+Confidence in elections was greater among those who read the treatment vignette announcing efforts to recruit veterans to work as election staff and volunteers, but this effect was conditional on whether survey questions asked about elections Maricopa County, AZ.
+When survey questions asked about elections in one's local area, confidence in elections among the treatment group was not significantly different from the control group.
+However, the sample's confidence in their local area elections was high in general relative to elections in Maricopa County, AZ (@fig-dist).
+The results presented here suggest that the effect of the veteran cue in the treatment vignette is compensatory.
+That is, the gap in confidence in local elections and elections in Maricopa County is reduced by the veterans cue, therefore compensating for the otherwise lower confidence and greater insecurity in Maricopa County elections.
+
+A question lingers about whether some antecedent mechanism transmits (i.e., mediates) the effects of the veteran treatment vignette to the outcome.
 To put simply, this study reiterates that there *is* something special about veterans in particular that elicits greater confidence in elections, but cannot go further in determining exactly *what* that special something might be.
-
 Factors that *moderate* the relationship of the treatment on the outcome of interest are likely plenty, but one can only offer conjecture of a *mediator* driving results.
+
 One potential explanation is that veterans, and all those who serve in the military, potentially function as a national symbol.
@@
 Especially insofar as such attitudes relate to confidence in the electoral process and administration.
+
+It is difficult to compare magnitude of effect with other studies given that the item number, item wording, measurement, and computation of confidence in elections is unique across most individual studies to include this one.
+For instance, @gaudette2025 doesn't compose multiple items into a single composite measure, but subtracts pre-treatment values from post-treatment values for single-item measures with Likert-style response options.
+Whereas @clayton2023 develops a scale referred to as "Trust in American electoral process" by taking the mean from three items.
+The item wording of that scale is markedly similar to the items used to compose the trust scale of this study, but the range of response options differs considerably.
+Thus, while most studies examining public confidence in elections often include the core question "How confidence are you that your vote \[will be/was\] counted as you intended in the most recent election?", the different ways that researchers measure and compute variable scores on the outcome most often produces results that are, unfortunately, sample dependent.
+The study of public confidence in elections is in desperate need of a standard method of measurement, or even a screened and validated item bank, and this study may be seen as a baby step to that end.
+
+That being said, this study generally emulates treatment effects of comparable studies in the literature.
+@gaudette2025 found positive effects of official messaging from election officials on various items measuring trust in elections and expectations of electoral fraud.
+Similarly, @clayton2023, confined to a sample of Republican participants, found positive influence on perceptions of 2020 election legitimacy and trust in the American electoral process from official messaging by Republican politicians reaffirming the 2020 election results.
+
+The data of the current study is limited in helping to discern whether the treatment garners greater confidence in elections uniformly across different racial or ethnic groups given that the largest proportion of the sample identified their race as White (77%).
+It is reasonable to suspect that the treatment vignette might differ by race and ethnicity, but the sample is insufficient to make such generalizations.
+Nevertheless, attitudes about veterans that differ by group may play an important role in determining whether publicized efforts to recruit military veterans boosts confidence in elections uniformly or whether the effect is merely partial to certain segments of the population.
+
+In their research examining whether groups differed in attitudes about veterans, @kleykamp2018 could only speculate as to why levels of support were lowest among Hispanic and Black respondents.
+Their study was distinctive in that it stands as a rare case in which public attitudes about veteran military members was the specific focus of inquiry as opposed to studies that examine public opinion about the military in general.
+Other research has found that attitudes about the U.S.
+military generally---though not about active or veteran military service members in particular---differs by race and ethnicity to varying extents, but also could not supply reason for one groups' sentiment over another^[Note, however, that the sample examined by @nichols2015 was constrained to Texas residents, and the military-related issues concerned, among other things, favor for reinstatement of a military draft, support for allowing undocumented immigrants who live in the U.S.
+to serve in the U.S.
+Armed Forces, and whether undocumented immigrants should be granted U.S.
+citizenship as a result of military service.
+Although the authors found high overall support for the military as an institution, the other military-related attitudes of interest diverge far from public opinion about veterans.
+As such, differential effects found among different racial or ethnic groups likely have little to do with attitudes about former or active military service members.] [@nichols2015].
+
+Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly.
+One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S.
+military as an institution in general.
+Some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally.
+In one such study by @tsai2021, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes (e.g., compassion) toward homelessness and PTSD among the veteran population, but not among the general adult population.
+Additionally, Republican partisans tended to show greater support for federal funding for homelessness and PTSD research when the reference population was military veterans.
+That study, however, suggests that the effect of the veteran status cue is sensitive to the topic in question.
+
+Perhaps unsurprisingly, military veterans appear to be uniquely deserving in the eyes of Republican partisans [@tsai2021; @mcdermott2015; @richardson2022].
+As such, military veteran status may qualify favorable attitudes among Republican partisans whereas their regard for other non-veteran groups might otherwise express contempt or indifference.
+This further indicates a need for research to determine an underlying mechanism explaining why veterans incur special favor.
 
@@
 #| tbl-colwidths: [70]
-#| tbl-pos: H
-
-# descriptive stats of categorical variables
-# gtsummary method
-gtsummary::theme_gtsummary_compact()
-
-tbl.desc <- data |>  
-  gtsummary::tbl_summary( 
-    by = group,
-    label = list(
-      age_cat = "Age group, in years",
-      gender = "Gender",
-      race = "Race",
-      hisp = "Hispanic, Latino, or Spanish origin?",
-      educ_4cat = "Education"
-      ),
-    include = c(
-      age_cat,
-      gender,
+
+df <- data |>
+  dplyr::mutate(
+    mil = dplyr::case_when(
+      milserv1 =="Yes" & milserv2 == "Yes" ~ "Active Duty",
+      milserv1 =="Yes" & milserv2 == "No" ~ "Prior Service (Veteran)",
+      milservfam == "Yes" ~ "Has Family in Military",
+      milservfam == "No" ~ "No Family in Military",
+      TRUE ~ NA),
+    ideo_3cat = dplyr::case_when(
+      ideo %in% c("Extremely Liberal",
+                  "Slightly liberal",
+                  "Liberal") ~ "Liberal",
+      ideo %in% c("Extremely conservative",
+                  "Slightly conservative",
+                  "Conservative") ~ "Conservative",
+      ideo %in% c("Moderate: middle of the road") ~ "Moderate",
+      ideo %in% c("Haven't thought much about this") ~ "Unsure",
+      TRUE ~ NA)
+    ) |> 
+  dplyr::select(
+    group,
+    age_4cat,
+    gender_3cat,
     race,
     hisp,
-      educ_4cat
-      ),
-    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
-    missing = "ifany",
-    missing_text = "NA") |> 
-  gtsummary::add_overall() |> 
-  gtsummary::modify_header(label = "**Variable**") |> 
-  gtsummary::bold_labels()
-
-tbl.desc |>
-  gtsummary::as_tibble() |>
-  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
-                "**Control (N = 637)**" = "**Control**  \nN = 637",
-                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
-  tinytable::tt(theme = "spacing") |>
-  tinytable::format_tt(markdown = T) |>
-  tinytable::format_tt(replace = " ") |>
-  tinytable::style_tt(fontsize = 0.70, align = "lccc")
+    educ_4cat,
+    mil, 
+    partyid_3cat,
+    ideo_3cat
+    ) |> 
+  labelled::set_variable_labels(
+    age_4cat = "Age groups, in years",
+    gender_3cat = "Gender",
+    race = "Race",
+    hisp = "Is R of Hispanic, Latino, or Spanish origin",
+    educ_4cat = "Education",
+    mil = "Military Relation",
+    partyid_3cat = "Party ID", 
+    ideo_3cat = "Political Ideology")
+
+freqs <- df |> 
+  dplyr::mutate(dplyr::across(where(is.character), ~as.factor(.))) |>
+  purrr::map(janitor::tabyl, show_na = T) |> 
+  purrr::map(janitor::adorn_pct_formatting, affix_sign = F)
+
+freqs <- purrr::list_rbind(freqs) |> 
+  dplyr::rename(" " = '.x[[i]]',
+                "valid percent" = "valid_percent") |>
+  dplyr::as_tibble() |> 
+  dplyr::mutate(across(where(is.factor), ~as.character(.)))
+
+tinytable::tt(freqs) |>
+  tinytable::format_tt(j = "valid percent", replace = "-") |> 
+  tinytable::group_tt(i = list(
+    "Experiment Condition" = 1,
+    "Age" = 3,
+    "Gender" = 7,
+    "Race" = 11,
+    "Hispanic, Latino, or Spanish Origin" = 17,
+    "Education" = 21,
+    "Military Relation" = 26,
+    "Party ID" = 31,
+    "Political Ideology" = 35),
+    indent = 2
+    ) |>
+  tinytable::style_tt(fontsize = 0.80, align = "lccc")
 
@@
 
-```{r}
-#| label: tbl-demog2
-#| tbl-cap: "Sample Demographics"
-#| tbl-colwidths: [70]
-#| tbl-pos: H
-
-tbl.desc2 <- data |>  
-  gtsummary::tbl_summary( 
-    by = group,
-    label = list(
-      partyid_3cat = "Party ID",
-      ideo_3cat = "Political Ideology",
-      ideolean = "If R had to choose Political Ideology",
-      voted2020 = 'Did R Vote in 2020 Election',
-      choice2020 = 'Vote Choice in 2020 Election',
-      voteintent = 'Intent to Vote in 2024 Election'),
-    include = c(
-      partyid_3cat,
-      ideo_3cat, 
-      ideolean, 
-      voted2020, 
-      choice2020),
-    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
-    missing = "ifany",
-    missing_text = "NA") |> 
-  gtsummary::add_overall() |> 
-  gtsummary::modify_header(label = "**Variable**") |> 
-  gtsummary::bold_labels()
-
-tbl.desc2 |>
-  gtsummary::as_tibble() |>
-  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
-                "**Control (N = 637)**" = "**Control**  \nN = 637",
-                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
-  tinytable::tt(theme = "spacing") |>
-  tinytable::format_tt(markdown = T) |>
-  tinytable::format_tt(replace = " ") |>
-  tinytable::style_tt(fontsize = 0.70, align = "lccc")
-
-```
-
-{{< pagebreak >}}
-
-```{r}
-#| label: tbl-demog3
-#| tbl-cap: "Sample Demographics"
-#| tbl-colwidths: [70]
-#| tbl-pos: H
-
-tbl.desc3 <- data |>  
-  gtsummary::tbl_summary( 
-    by = group,
-    label = list(
-      milserv1 = "Military Service",
-      milserv2 = "Current Active Duty",
-      milservfam = "Military Service within Family?"
-      ),
-    include = c(
-      milserv1,
-      milserv2, 
-      milservfam), 
-    type = list(
-      milserv1 ~ "categorical",
-      milserv2 ~ "categorical",
-      milservfam ~ "categorical"
-      ),
-    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
-    missing = "ifany",
-    missing_text = "NA") |> 
-  gtsummary::add_overall() |> 
-  gtsummary::modify_header(label = "**Variable**") |> 
-  gtsummary::bold_labels()
-
-tbl.desc3 |>
-  gtsummary::as_tibble() |>
-  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
-                "**Control (N = 637)**" = "**Control**  \nN = 637",
-                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
-  tinytable::tt(theme = "spacing") |>
-  tinytable::format_tt(markdown = T) |>
-  tinytable::format_tt(replace = " ") |>
-  tinytable::style_tt(fontsize = 0.70, align = "lccc")
-
-```
-
-{{< pagebreak >}}
-
-## Test of Random Assignment to Experiment Condition
+# Appendix C: Test of Random Assignment to Experiment Condition {.appendix}
 
@@
 
-tab.logit <- modelsummary::modelsummary(m1, 
+gm <- list(
+  list("raw" = "nobs", "clean" = "N", "fmt" = 0),
+  list("raw" = "logLik", "clean" = "Log.Lik.", "fmt" = 3),
+  list("raw" = "deviance", "clean" = "Deviance", "fmt" = 2),
+  list("raw" = "null.deviance", "clean" = "Deviance Null", "fmt" = 2),
+  list("raw" = "df", "clean" = "DF", "fmt" = 0),
+  list("raw" = "chisq", "clean" = "Chi2", "fmt" = 3),
+  list("raw" = "P(>chisq)", "clean" = "P(>chisq)", "fmt" = 3))
+
+tab.logit <- modelsummary::modelsummary(
+  list("log(OR)" = m1),
   output = "tinytable",
@@
   coef_map = cmp,
-                           gof_map = NA)
-
-# create 2nd table containing only logit model fit statistics
-# using custom function, get logit regression model fit stats... 
-gof_stats <- lrm.gof.stats(m1) |> 
-  # omit certain stats (saves space)
-  dplyr::select(
-    nobs, logLik, df, chisq, P..chi., deviance, null.deviance,
-    -AIC, -BIC, -df.null, -df.residual) |> 
-  # rename column variables
-  dplyr::rename(
-    "Num.Obs"       = "nobs",
-    "Null Deviance" = "null.deviance",
-    "Deviance"      = "deviance",
-    "DF"            = "df",
-    "Log.Lik"       = "logLik",
-    "chisq"       = "chisq",
-    "P(>chisq)"   = "P..chi."
+  gof_function = lrm.gof.stats,
+  gof_map = gm,
+  gof_omit = "AIC|BIC|F|RMSE"
   ) |> 
-  # pivot into two column long-form dataframe
-  tidyr::pivot_longer(cols = everything(),names_to = " ", values_to = '**log(OR)**') |>
-  # pipe into tinytable
-  tinytable::tt(width = 0.8) |> 
-  # ensure rows with math text are identified and formatted as math (i.e., $..$)
-  tinytable::format_tt(i = c(4,5), j = 1, math = T)
-
-# using `rbind2` function, bind 2nd table at bottom of first table 
-tinytable::rbind2(tab.logit, gof_stats, use_names = F, headers = F) |> 
-  # add horizontal line just above fit stats
-  tinytable::style_tt(i = 16, line = "t", line_color = "black", line_width = 0.1) |>
+  tinytable::strip_tt(line = TRUE)
+
+tab.logit |> 
+  tinytable::group_tt(i = list(
+    "**Age**" = 1,
+    "**Gender**" = 4,
+    "**Race**" = 6,
+    "**Education**" = 11,
+    "**Party ID**" = 14), 
+    indent = 2
+    ) |> 
+  tinytable::style_tt(i = 20, line = "b", line_color = "black", line_width = .05) |> 
   # adjust fontsize of text within table
@@
 
-# Appendix C: Polychoric Item and Score Correlations of Trust and Distrust {.appendix}
+# Appendix D: Polychoric Item and Score Correlations of Trust and Distrust {.appendix}
 
@@
 
-# Appendix D: Predicted Probabilities of Safety Concerns by Treatment Condition {.appendix}
+# Appendix E: Predicted Probabilities of Safety Concerns by Treatment Condition {.appendix}
 
@@
 
-[^9]: See Appendix C for Inter-item correlation analysis.
+[^9]: See Appendix D for Inter-item correlation analysis.
 

### 2025-07-04 supplemental/appendix_A.qmd
manuscript update with revisions after review

---
title: "Appendix A"
subtitle: "Survey Experiment Vignettes and Survey Items"
format:
  typst: 
    toc: false
    keep-typ: true
    papersize: us-letter
    mainfont: TeX Gyre Pagella
    fontsize: 11pt
    include-in-header: 
      - text: |
        #show footnote.entry: set text(size: 10pt)
execute: 
  echo: false
---

```{r}
#| label: setup
#| include: false
#| echo: false

set.seed(1234)

# load packages
library(tidyverse)
library(modelsummary)
library(tinytable) # simple tables in html, LaTeX, markdown, word, pdf, typst
library(litedown)

# set some session options for `tinytable`
options(tinytable_tt_digits = 3)
# set option to render tinytable math in html
options(tinytable_html_mathjax = TRUE)

# options(tinytable_quarto_disable_processing = FALSE)
# options(tinytable_theme_placement_latex_float = "H")

# load data
load(here::here("data", "research-paper-data-20241029.Rdata"))
# load("data/research-paper-data-20241029.Rdata")

```

```{r}
#| label: functions
#| include: false

var_label_tab <- function(x){
    purrr::map(x, ~attr(., "label")) |>
    purrr::map(~ifelse(purrr::is_null(.), "No label", .)) |>
    tibble::enframe(name = "var", value = "var_label") |>
    tidyr::unnest(cols = c(var_label))
}

# only in LaTeX
is_latex <- identical(knitr::pandoc_to(), "latex")

# wrap in a minipage environment
minipagify <- function(x) {
  sprintf(
    "\\minipage{\\textwidth}%s\\endminipage",
    sapply(x, mark, "latex")
  )
}

```

::::: {#fig-vignettes layout-ncol="2"}
::: {#fig-treatment}
### Treatment Vignette

| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
| 
|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff. As the U.S. general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
| 
|   Army veteran Jordan Braxton just joined the elections workforce. Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle. I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
:::

::: {#fig-control}
### Control Vignette

| **Local Residents Recruited for Election Jobs in Maricopa County**
| 
|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff. As the U.S. general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
| 
|   Jordan Braxton just joined the elections workforce. Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle. I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
:::

**Fabricated Article Vignettes utilized as Experimental Stimulus**
:::::

::::: {.content-hidden unless-format="pdf" layout="[0.45, -0.1, 0.45]"}
::: {#first-column}
### Treatment Vignette

| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
| 
|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff. As the U.S. general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
| 
|   Army veteran Jordan Braxton just joined the elections workforce. Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle. I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
:::

::: {#second-column}
### Control Vignette

| **Local Residents Recruited for Election Jobs in Maricopa County**
| 
|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff. As the U.S. general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
| 
|   Jordan Braxton just joined the elections workforce. Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle. I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
:::
:::::

{{< pagebreak >}}

## Survey Items

```{r}
#| label: tbl-1
#| tbl-cap: "Pre-Treatment Survey Items and Response Options"

pre_treat <- data |> 
  dplyr::select(q5:q8, -legitimate, -not_legitimate) |> 
  dplyr::rename_with(
    .cols = everything(), 
    .fn = ~snakecase::to_any_case(.,case = "upper_camel")
    ) |> 
  var_label_tab() |>
  dplyr::select(Question = var_label) |> 
  dplyr::pull(Question)

# NOTE: when using format: typst, and creating a table using `tinytable`,
# multi-line cells can be written by using `\\` to break lines.
# see https://tex.stackexchange.com/a/599076

res1 <- data.frame(
  Items = pre_treat,
  Response =c(
    "Never \\
    Sometimes\\
    About half the time\\
    Most of the Time\\
    Always",
    "Strongly unfavorable\\
    Somewhat unfavorable\\
    Neither favorable nor unfavorable\\
    Somewhat favorable\\
    Strongly favorable",
    "Legitimate\\
    Not legitimate",
    "Never \\
    Sometimes\\
    About half the time\\
    Most of the Time\\
    Always")
)

tinytable::tt(res1, width = c(0.7, 0.3)) |>
  tinytable::style_tt(i = 1:4, j = 1, fontsize = 0.8, align = "l") |>
  tinytable::style_tt(i = 1:4, j = 2, fontsize = 0.65, align = "l") |>
  tinytable::format_tt(markdown = TRUE) |>
  tinytable::format_tt(j = 2, fn = if (is_latex) minipagify else NULL)

```

{{< pagebreak >}}

```{r}
#| label: tbl-2
#| tbl-cap: "Trust Items and Response Options"

trust.qs <- data |> 
  dplyr::select(q19:q24, -q23, q30:q35, -q34) |> 
  dplyr::rename_with(
    .cols = everything(), 
    .fn = ~snakecase::to_any_case(.,case = "upper_camel")
    ) |> 
  var_label_tab() |>
  dplyr::select(Question = var_label) |> 
  dplyr::pull(Question)

# data |> 
#   dplyr::select(q19:q24, -q23, q30:q35, -q34) |>
#   purrr::map(~attr(., "levels"))

res2 <- data.frame(
  Trust = trust.qs,
  Response = c(
    "Not at all confident\\
    Not too confident\\
    Somewhat confident\\
    Very confident",
    "Not at all confident\\
    Not too confident\\
    Somewhat confident\\
    Very committed",
    "Not at all committed\\
    Not too committed\\
    Somewhat committed\\
    Very committed",
    "Not at all confident\\
    Not too confident\\
    Somewhat confident\\
    Very confident",
    "Not at all confident\\
    Not too confident\\
    Somewhat confident\\
    Very confident",
    "Not at all confident\\
    Not too confident\\
    Somewhat confident\\
    Very confident",
    "Not at all confident\\
    Not too confident\\
    Somewhat confident\\
    Very confident",
    "Not at all committed\\
    Not too committed\\
    Somewhat committed\\
    Very committed",
    "Not at all confident\\
    Not too confident\\
    Somewhat confident\\
    Very confident",
    "Not at all confident\\
    Not too confident\\
    Somewhat confident\\
    Very confident")
  )

tinytable::tt(res2, width = c(0.7, 0.3)) |>
  tinytable::style_tt(i = 1:12, j = 1, align = "l", fontsize = 0.8) |>
  tinytable::style_tt(i = 1:12, j = 2, align = "l", fontsize = 0.65) |>
  tinytable::group_tt(i = list("AZ" = 1, "Local Area" = 6), indent = 2) |> 
  tinytable::style_tt(i = c(1,7), bold = T, line = "b", line_width = 0.05) |> 
  tinytable::format_tt(markdown = TRUE) |> 
  tinytable::theme_tt(theme = "resize", width = 0.9)

```

{{< pagebreak >}}

```{r}
#| label: tbl-3
#| tbl-cap: "Distrust Items and Response Options"

distrust.qs <- data |> 
  dplyr::select(q28_1:q28_5) |>  
  dplyr::rename_with(
    .cols = everything(), 
    .fn = ~snakecase::to_any_case(.,case = "upper_camel")
    ) |> 
  var_label_tab() |>
  dplyr::select(Question = var_label) |> 
  dplyr::pull(Question)

res3 <- data.frame(
  Distrust = distrust.qs,
  Response = c(
    "Not likely at all\\
    Not too likely\\
    Somewhat likely\\
    Very likely",
    "Not likely at all\\
    Not too likely\\
    Somewhat likely\\
    Very likely",
    "Not likely at all\\
    Not too likely\\
    Somewhat likely\\
    Very likely",
    "Not likely at all\\
    Not too likely\\
    Somewhat likely\\
    Very likely",
    "Not likely at all\\
    Not too likely\\
    Somewhat likely\\
    Very likely"
  )
)

tinytable::tt(res3, width = c(0.7, 0.3)) |>
  tinytable::style_tt(i = 1:10, j = 1, align = "l", fontsize = 0.8) |>
  tinytable::style_tt(i = 1:10, j = 2, align = "l", fontsize = 0.65) |>
  tinytable::group_tt(i = list(
    "How likely do you think any or all of the following will happen during this year´s elections in Maricopa County, AZ/your local area?" = 1)) |> 
  tinytable::style_tt(i = 1, bold = T, line = "b") |> 
  tinytable::format_tt(markdown = TRUE) |> 
  tinytable::theme_tt(theme = "resize", width = 0.9)

```

{{< pagebreak >}}

```{r}
#| label: tbl-4
#| tbl-cap: "Safety Items and Response Options"

safety.qs <- data |>
  dplyr::select(q25:q26, q36:q37) |>
  dplyr::rename_with(
    .cols = everything(),
    .fn = ~ snakecase::to_any_case(., case = "upper_camel")) |>
  var_label_tab() |>
  dplyr::select(Question = var_label) |>
  dplyr::pull(Question)

res4 <- data.frame(
  Safety = safety.qs,
  Response =c(
    "Very concerned\\
    Somewhat concerned\\
    Not too concerned\\
    Not at all concerned",
    "Not at all confident\\
    Not too confident\\
    Somewhat confident\\
    Very confident",
    "Very concerned\\
    Somewhat concerned\\
    Somewhat unconcerned\\
    Not at all concerned",
    "Not at all confident\\
    Not too confident\\
    Somewhat confident\\
    Very confident")
)

tinytable::tt(res4, width = c(0.7, 0.3)) |>
  tinytable::style_tt(i = 1:6, j = 1, fontsize = 0.8, align = "l") |>
  tinytable::style_tt(i = 1:6, j = 2, fontsize = 0.65, align = "l") |>
  tinytable::group_tt(i = list("AZ" = 1, "Local Area" = 3), indent = 2) |> 
  tinytable::style_tt(i = c(1,4), bold = T, line = "b", line_width = 0.05) |> 
  tinytable::format_tt(markdown = TRUE) |>
  tinytable::theme_tt(theme = "resize", width = 0.9)

```

### 2025-07-04 supplemental/appendix_B.qmd
manuscript update with revisions after review

--- 2025-06-03 index.qmd
@@
 ---
-title: 'Inspiring Confidence and Easing Insecurity in the Pre-election period: The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections'
-# subtitle: 'The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections'
-shorttitle: 'Effect of Recruiting Military Veterans on Confidence in 2024 US Elections' # aog-article-pdf
-shortauthors: Isaiah      # aog-article-pdf
-abstract: |
-  In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
-Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
-Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned.
-Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
-In addition, concerns over voter safety and potential for violence were lower among those who received the treatment.
-authors:
-  - name: Isaiah Espinoza
-    email: gespinoz@umd.edu
-    roles: author
-    affiliation:
-      - name: University of Maryland
-        department: Department of Government and Politics
-        city: College Park
-        state: MD
-        country: US
-reference-section-title: References
-knitr: 
-  opts_chunk: 
-    dev: "ragg_png" # same as knitr::opts_chunk$set(dev = "ragg_png")
-editor_options: 
-  chunk_output_type: console
+title: "Appendix B"
+subtitle: "Sample Demographics and Balance"
+format:
+  typst: 
+    toc: false
+    keep-typ: true
+    papersize: us-letter
+    mainfont: TeX Gyre Pagella
+    fontsize: 11pt
+execute: 
+  echo: false
 ---
@@
 library(litedown)
-library(ordinal)
-library(marginaleffects)
-library(easystats)
-library(patchwork)
 
@@
 # load data
-load("data/research-paper-data-20241029.Rdata")
-
-```
-
-```{r}
-#| label: fun-likert-plot
-
-# custom function used to create Likert Plots
-
-# To avoid excessive copy/paste, I made a function to create Likert plots
-# it is mostly a wrapper around `ggstats::gglikert`, but with a specific set up
-# particular colors, theme, etc. 
-likert_plot <- function(data, x, ...,  
-                        symmetric = FALSE,
-                        variable_labels = NULL,
-                        label_size = 2.5,
-                        vline = FALSE,
-                        title = waiver(), 
-                        subtitle = waiver(),
-                        caption = waiver(),
-                        xlab = waiver()){
-
-  p <- ggstats::gglikert(
-    data = data, include = {{ x }}, ...,
-    variable_labels = variable_labels,
-    symmetric = symmetric)+
-
-    # customize color
-    ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
-    # custom theme
-    theme_bw(base_family = "TeX Gyre Pagella")+
-    theme(
-      legend.position = 'bottom',  # place legend on bottom
-      axis.title.y.left = element_blank(), # blank out y-axis label
-      axis.text.x = element_blank(), # remove percentage text along x-axis
-      strip.text.y.right = element_text(angle = 0) # make facet label horizontal
-        )
-
-    if (vline==TRUE) {
-    p <- p + geom_vline(xintercept = 0, color = 'black', linewidth = 1.2)
-  } else {
-      p
-  }
-
-  p <- p + ggplot2::labs(..., title = title, subtitle=subtitle, caption=caption, x = xlab)
-  p
-
-}
-
-```
-
-```{r}
-#| label: fun-barplot
-
-# function for creating barplots
-custom_barplot <- function(data, x, group, title = NULL, subtitle = NULL,
-                           caption = NULL, legend_fill = NULL,
-                           xlab = NULL){
-  b <- data |> 
-    group_by({{ group }}, {{ x }}) |> 
-    count() |> 
-    drop_na() |> 
-    group_by({{ group }}) |> 
-  mutate(prop = round(n/sum(n), digits = 3),
-         pct = prop*100,
-         res = str_c(pct,'% (', n, ')', sep = "")) |> 
-  ggplot(aes(x = {{ x }}, y = pct, fill = {{ group }}))+
-  geom_bar(position = 'dodge', stat = 'identity')+
-  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5, vjust = -0.7)+
-  scale_fill_grey(start = 0.5, end = 0.1)
-
-  b <- b + ggplot2::labs(
-    title = title,
-    subtitle = subtitle,
-    caption = stringr::str_wrap(caption, width = 99),
-    fill = legend_fill,
-    y = "Percentage",
-    x = stringr::str_wrap(xlab, width = 85))
-  b
-}
+load(here::here("data", "research-paper-data-20241029.Rdata"))
+# load("data/research-paper-data-20241029.Rdata")
 
@@
 
-{{< pagebreak >}}
-
-## Introduction
-
-Election administration officials make efforts to sustain public trust and confidence in the fairness and accuracy of elections, and attempt to boost such confidence where it may be deprived.
-Concerns for safety have developed among election staff and voters in more recent elections.
-Regular measures are taken to enhance the *trustworthiness* of the electoral process through practices meant to improve the conduct, transparency, or overall administration of elections in the United States.
-
-Although election officials undertake great efforts to enhance the *trustworthiness* of election administration, public *trust*[^1] in elections is a psychological construct influenced by many things outside of election official control such as partisanship or elite rhetoric [@hooghe2018; @sances2015].
-Moreover, a person's evaluation of the election in hindsight is often influenced by the election outcome itself [@daniller2019; @stewart2022].
-Thus, measures taken by election officials can be undermined, trivialized, or made irrelevant depending on how one feels after the election results have come out.
-
-Such volatile attitudes and evaluations post-election can leave a lasting impression that election officials must contend with upon the next election cycle [@levendusky2024; @bowler2024].
-For instance, we have witnessed many people's outright refusal to accept the 2020 U.S.
-election results as legitimate despite consistent review of the evidence confirming the results as fair and accurate.
-Such a case demonstrates that public trust in elections is, at best, only partial to trustworthiness of election administration in the United States.
-
-One point of contention that election officials have faced in the past regard evaluation of election workers.
-Previous literature has focused on how voter interaction with election workers [@claassen2008], voting technology [@herrnson2009], and the voter experience generally [@atkeson2007], influences evaluations of election administration.
-As such, election worker competency has been examined as a factor significant to evaluations of performance of elections [@hall2007; @hall2009].
-However, considering that individual perceptions and preconceived notions play a huge role in cognition [@cikara2014; @vanbavel2021], it is reasonable to expect that the group an election worker hails from would be an important influence upon the voter's evaluation of the electoral process.
-
-Supposing such is the case, we can expect that information about *who* (i.e., which groups) election officials are targeting in publicized recruitment efforts would lessen particular election insecurity, and concurrently, boost confidence.
-That is to say, it is reasonable to expect that telling people *who* will be working and volunteering as election staff would ease election insecurity, and therefore improve confidence that the election will be conducted fairly, accurately, and safe for all involved.
-
-In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
-Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
-Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned[^2].
-Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
-In addition, concerns over voter safety and potential for violence were lower among those who received the treatment.
-
-This paper is structured as follows.
-First, I provide a brief background on public trust in election administration.
-I synthesize a review of relevant literature with a focus on how political and social science has conceptualized and ascertained public trust in elections.
-Next, I supply reasoning for why military veterans are singled out as the relevant subset of the population in this study.
-I then explicitly provide the simple theory and testable hypotheses of the study before moving on to describe the design of the survey, the measurement instruments therein, and the conceptual and operational definitions of the variables of interest.
-I explain my reasoning and method for constructing the primary dependent variable, which I broadly refer to as *confidence in elections*.
-I close by offering my interpretation of the results and suggest potential avenues for future inquiry.
-
-## Background: Election Administration and Public Confidence
-
-Election officials have tried hard to inspire confidence in the administration and conduct of elections by improving the degree to which elections are trustworthy.
-Development and implementation of procedures such as post-election auditing of ballots and logic-and-accuracy testing of ballot tabulation equipment are prominent examples adding to the long history of efforts to enhance the trustworthiness of election administration in the United States.
-
-Prior to the year 2000, one of the main issues facing election administration was recruiting enough election workers to volunteer at the polls (i.e., poll workers) [@maidenberg1996].
-Election worker recruitment is still much of an issue in the current era as it was then, perhaps worse [@ferrer2024].
-In addition to ensuring election offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections.
-In particular, voting technology [@herrnson2009] and election worker competence was of interest in election studies [@claassen2008; @hall2009; @hall2007].
-Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007].
-
-In 2024, election officials made valiant efforts to boost public confidence elections within an intensified political climate that appeared quite hostile to election officials [@edlin2024; @brennancenterforjustice2024].
-Although polling around the time indicated that most people thought that U.S.
-elections would be run at least somewhat well [@nadeem2024], many election officials nationwide took efforts to assuage the worry of those most skeptical.
-
-Election anxiety was high in the lead up to the 2024 elections in the United States.
-Concerns for voter safety and the prospect of political violence remained prescient and compelled many local officials to prepare for the worst [@edlin2024; @doubek2024].
-Election officials in Washoe County, Nevada, installed panic buttons for election staff that would alert a monitoring center to summon law enforcement [@lincoln2024].
-Nevada also passed a law making it a felony to harass, threaten, or intimidate election workers [@nevadasecretaryofstate2023].
-Leading up to election day, news outlets reported that election work had become a seemingly dangerous job [@wire2024].
-A Brennan Center survey report stated that, "...large numbers of election officials report having experienced threats, abuse, or harassment for doing their jobs" [@edlin2024].
-Concerns over the fairness of elections and accuracy of vote counts intensified, heightening concerns over the prospect of political violence and, in turn, increased worry for the safety of voters and election workers alike.
-Since election worker performance is significant to public evaluation of elections, added safety concerns that drive out election staff and repel volunteers can only detract from trustworthiness of the institution.
-
-## Literature Reivew
-
-Trust and confidence in the conduct of elections concerns aspects of elections that fall squarely within the institution of election administration.
-At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended).
-
-Intuitively, enhancing public trust in elections would best be accomplished by enhancing the *trustworthiness* of the institution, e.g., enhancing vote tabulation equipment and technology, conducting audits.
-However, trust and confidence in elections has become ever more precarious over the last few election cycles.
-Especially considering public polling data since 2000 shows that confidence that votes were, or would be, counted as intended was in a consistent decline despite efforts towards bolstering election integrity and trustworthiness [@sances2015].
-This is even more pronounced considering the role that partisanship has had on such confidence over accuracy of vote counts [@sances2015; @stewart2022].
-
-There's also stark difference in public trust before the election has occurred compared to after, a phenomenon referred to as the "winner-loser gap"; the "winners" are those who supported the winning candidate and the "losers" are those who supported the losing candidate.
-Much research has been dedicated to analyzing the sentiment of electoral winners vs losers, and vice versa [@nadeau1993; @daniller2019].
-Opinions of electoral trust gathered after the election has occurred, however, are limited considering the well-recognized impact that the electoral outcome itself has on feelings of public trust in elections [@daniller2019].
-
-As such, it is questionable whether we can characterize public trust in the pre-election period as the same trust after the election results have come out.
-The former is *anticipatory*---i.e., the kind that is more or less anxious given the uncertainties surrounding the election.
-The latter is *empirical*---a judgement discerned in hindsight after the experience of the election event has occurred.
-As discussed by @stewart2022, not only was confidence in vote count accuracy influenced by the voter experience, but so too were evaluations of election officials [-@stewart2022, 242-243].
-Not to mention the influence that the election results would also have on such evaluations.
-In other words, evaluations of trust considered in hindsight are influenced by the voter experience and the outcome of the election results.
-This study, in contrast, focuses primarily on that *anticipatory* kind of confidence, which speaks more to those insecurities based on perceptions of the institution's trustworthiness than upon the particular voter experience.
-
-Regardless of the measures taken by election officials to boost public confidence in the *trustworthiness* of election administration (e.g., conducting audits, testing election machines), public *trust* and confidence in elections more generally is apt to shift dramatically post-election based on factors such as partisanship, elite rhetoric, particular state policies, and more [@nadeau1993; @carter2024; @coll2024a].
-Moreover, prior research has found that evaluation of election workers themselves are an important factor when it comes to levels of public confidence in the electoral process [@hall2007; @hall2009; @claassen2008].
-Such studies focused on the quality of the voter experience with reference to the interaction between voter and election worker.
-
-Beyond the general competence of election workers, however, the quality of the voter experience may be influenced merely by prior impressions about *who* comprises election staff and volunteers.
-Political and other social science researchers have recognized for some time the power that group identity can have over attitudes and perception [@xiao2016; @xiao2012; @vanbavel2021].
-As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve trust and confidence in election administration, and lessen expectations of electoral fraud.
-The next section elaborates on why military veterans are of particular interest in this regard.
-
-## Why Veterans
-
-Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work.
-Especially since staffing issues have been an issue since at least the 1990s [@maidenberg1996; @ferrer2024].
-In 2020, such efforts were made far more difficult by the COVID-19 pandemic [@mena2020; @abbate2020a].
-There's no special reason to target veterans for recruitment above other groups.
-Indeed, there's no reason to discriminate recruitment efforts at all if the point is purely to fill staffing vacancies.
-
-The reason why veterans arose as a special subset of the population to consider for this inquiry is because there was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021.
-After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterans2022; @nflfootballoperations2022].
-Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts [@powerthepolls2020; @herndon2020].
-Generally, however, recruitment efforts cast a wide net, indiscriminate of who applies [@ross2020; @conde2020].
-
-One can speculate that the motivation to associate military veterans with civic engagement and democracy may be intended to counter negative perceptions and impressions given by the proportion of veteran service members arrested for taking part in the events on January 6th [@milton2021; @loewenson2023; @jensen2022a].
-Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024].
-This is in addition to a strengthened association portrayed in media outlets between military veterans and militias [@steinhauer2020].
-Prior research has substantiated such a connection between veterans and militia groups.
-@cooter2024 notes from her 3-year ethnographic fieldwork among Michigan militia members that, "...approximately 40% of militia leaders and 30% of members had previous military experience.
-Most of these veterans actively sought out such groups, as opposed to being recruited by them" [-@cooter2024; see also @cooter2013].
-Thus, countering such associations by promoting a different image of veterans to the mass public and veterans alike seems like a reasonable motivation.
-Yet such speculation is just that.
-
-That being said, the general public perception, attitudes, or even stereotypes about military veterans are significant to consider.
-Although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023].
-Veterans are a particularly potent group where mention of veteran status seems to have a positive, calming, or nullifying effect on attitudes.
-For instance, recent research shows that, during his campaign in the 2020 Democratic Primaries, Pete Buttigieg's military background mitigated discrimination against him when he was presented as a veteran married to a man [@magni2024].
-Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@hardy2019].
-Moreover, veteran status seems to mitigate or nullify usual stigmas associated with mental illness.
-That is to say, there is negative stigma associated with mental illness [@corrigan2002] and such stigma incurs labor market discrimination [@hipes2016], but evidence suggests that veteran status overrides such stigma and discrimination [@maclean2014].
-Or, in another light, mental illness is seemingly more *understandable* (i.e., permissible) for veterans given the presumptive reasons for their mental strife.
-And media framing as such plays an important role on public perception [@kleykamp2015].
-
-## Theory and Hypotheses
-
-Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veterans and their family members to work as election staff and volunteers would boost public *confidence in elections administration*.
-Indeed, that is the primary hypothesis of this study.
-Although citizens may vote in various ways across the country (e.g., by mail, ballot drop box, in-person), the simple announcement that election officials are engaging in efforts to recruit veterans to work as election staff may boost confidence in elections administration regardless of how, or whether, an individual plans to vote.
-Formally,
-
-> H~1~: Announcements that election officials are recruiting miilitary service veterans to work as election staff and volunteers will be associated with greater confidence in elections administration compared to announcements that do not mention military veterans.
-
-Asking participants whether they supported programs intent on recruiting anyone to work as election staff would garner support regardless of the target group.
-Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require a survey experiment designed to determine whether publicized recruitment efforts targeting veterans as a group would have any special effect on confidence in elections administration.
-
-In addition, prior research has shown that confidence that one's own vote would be counted as intended has been much stronger than confidence that votes nationwide would be treated likewise [@sances2015; @stewart2022].
-In other words, the public is more trusting of elections closer to home.
-Taking into account that confidence is lower for elections conducted outside of one's local area, then information that veterans are being recruited to help conduct elections in locations beyond one's locale may close this gap between confidence in elections within one's local area and confidence in elections elsewhere.
-Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone on public opinion.
-Therefore, any observed disparity of confidence in elections between those within one's local area and those beyond will be smaller among those who are presented with information about election official recruitment efforts of veteran service members.
-
-Since the results and events following the 2020 election loomed large in anticipation of the U.S.
-2024 general elections, it is reasonable to take into account beliefs about legitimacy of the 2020 election.
-This group who denies the legitimacy of the 2020 election results were possibly the most apprehensive (distrusting) of the 2024 election.
-However, given that veteran service members are held in high regard, generally speaking, announcing that veterans are being actively recruited to work as election staff and volunteers is expected to positively influence confidence in elections among those who remained firm in the belief that the 2020 election results were illegitimate.
-That is to say, despite their belief about the illegitimacy of the 2020 election results, I expect that informing them about veteran recruitment efforts to improve their confidence in elections.
-I take into account the relationship between partisanship and 2020 election legitimacy beliefs and include partisanship as a control in the analysis[^3].
-
-Finally, I expect that concerns about potential for violence will lessen, and confidence in voter safety improve, when presented with information that veterans are being actively recruited to work and volunteer in election offices.
-
-## Experiment Design and Survey Measures
-
-To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would improve confidence in elections and ease insecurity, a recent experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland.
-The survey was fielded from August 29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287 U.S.
-citizens 18 years of age or older.
-Respondents were randomly split into either the treatment ($n =$ 650) control ($n =$ 637) conditions[^4].
-
-Survey participants read either a treatment or control vignette, which resembled a news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election[^5].
-The treatment vignette referred to a program designed to recruit veterans and their family members and describes an interviewee "Jordan Braxton" as an Army veteran.
-The control vignette simply omitted any mention of veterans and their family members, and didn't describe "Jordan Braxton" as an Army veteran.
-Beyond those small differences and the headlines, the article vignettes are identical.
-Therefore, effects can be attributed to the information about veterans in the treatment vignette[^6].
-
-It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignette due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
-Because of this, treatment effects are potentially limited or constrained to attitudes concerning the location specified in the vignette.
-A block of survey items asked specifically about Maricopa County, AZ, followed by an identical block of items that asked the same questions about one's local area.
-I compare and discuss results between the items pertaining to different settings.
-
-Over the past two decades it became commonplace for national polls to gauge public confidence in election administration (i.e., voter confidence) by asking some variety of the question, "How confident are you that your vote \[will be/was\] counted as you intended in the most recent election?" [@hall2009; @sances2015; @stewart2022].
-In addition, since 2008, the Survey of the Performance of American Elections (SPAE) has included a good number of relevant questions to more thoroughly assess trust and confidence in election administration.
-Such questions inquire into the voter experience with the institution more directly.
-This study borrows, modifies, or takes inspiration from certain question items found within the 2022 SPAE and other survey items from the Pew Research Center's 2018 American Trends Panel wave 38 [@dunn2018].
-
-The items in this study all inquire into confidence over one's expectations in anticipation of upcoming elections.
-In addition, the survey of this study focused on attitudes regarding election workers such as election officials, staff, and volunteers specific to the location mentioned in the vignette---Maricopa County, AZ---as well as specific to one's local area[^7].
-
-The survey included items that assessed both trust in elections administration and expectations of electoral fraud, referred to simply as *trust* and *distrust*, respectively.
-Responses from these two sets of items were utilized to construct the primary dependent variable, *confidence in elections*.
-Additionally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
-The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^8].
-Although two survey items are insufficient to serve as a composite scale, safety concerns will be evaluated by examination of response to these two questions in particular.
-
-Prior to the reading the treatment or control vignette, participants responded to distinct survey items assessing one's beliefs about the legitimacy of the 2020 election results ("Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected?").
-Respondents selected either "Legitimate" or "Not Legitimate".
-
-The conventional multiple item assessment of partisanship was included and used to construct a variable of partisanship consisting of three categories: Democrat, Republican, and independent.
-
-### Trust and Distrust in Elections
-
-A set of five survey items measured public trust in elections by inquiring into the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, and confidence that the voting process will be fair.
-Each item in this series presented four response options from "Not at all \[confident/committed\]", "Not too \[confident/committed\]", "Somewhat \[confident/committed\]", and "Very \[confident/committed\]".
-In total, five survey items measure different aspects of trust in elections administration.
-
-```{r}
-#| label: tbl-1
-#| tbl-cap: "Survey Items for Trust and Distrust in Elections"
-
-trust_txt <- data |> 
-  dplyr::select(q19, q20, q21, q22, q24) |>
-  labelled::set_variable_labels(
-    q21 = "How commited do you think election staff and volunteers in Maricopa County, AZ will be to making sure the elections are fair and accurate?"
-  ) |> 
-  labelled::generate_dictionary() |> 
-  dplyr::as_tibble() |> 
-  dplyr::select(Trust=label)
-
-distrust_txt <- data |> 
-  dplyr::select(q28_1:q28_5) |>
-  labelled::generate_dictionary() |> 
-  dplyr::as_tibble() |> 
-  dplyr::select(Distrust=label)
-
-conf_items_text <- trust_txt |> 
-  dplyr::mutate(Distrust = dplyr::pull(distrust_txt))
-
-tinytable::tt(conf_items_text, width = c(.5, .5)) |> 
-  tinytable::style_tt(fontsize = 0.80, align = "ll")
-
+```{=typst}
+#show figure: set block(breakable: true)
 ```
 
-Another series of five survey items captured an individual's level of *distrust* in elections administration based on the extent to which they expect electoral fraud to occur.
-These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in \[Maricopa County, AZ/ your local area\]?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
-
-Similar to the items capturing trust in elections (@tbl-1), I computed a summated score for each respondent reflecting the extent of their distrust in elections.
-
-Upon construction of the two summated scales of *trust* and *distrust*, internal consistency reliability coefficient $\alpha$ were estimated for both and found to be adequate ($\alpha$ \> 0.8); the trust in elections scale $\alpha$ = 0.93 and the distrust scale $\alpha$ = 0.86.
-In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each[^9].
-
-## Data Specification
-
-The primary outcome of interest concerns public confidence in elections administration compensated by one's distrust in elections, i.e., their expectations of electoral fraud.
-Because trust and distrust are assessed by multiple Likert items, conventional methods call for combining the items of each set into separate Likert scales (also known as summated rating scales).
-However, many of the items comprising the trust scale directly oppose items capturing distrust.
-For instance, one item from the trust scale has the respondent report their confidence that votes will be counted as voter's intend, whereas a separate item from the distrust scale has the the respondent report their expectation that many votes will not be counted.
-Positive responses to these two items directly contradict each other, and would thus cancel out.
-
-In light of this, I reverse coded items on the distrust scale and combined responses to the trust in elections scale.
-That is, item responses on the trust scale ranged from 0 ("Not confident at all") to 3 ("Very confident), whereas responses on the distrust scale ranged from 0 ("Not likely at all") to -3 ("Very likely").
-Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^10].
-On this scale, positive values reflect higher confidence in elections (e.g., elections will be fair and accurate), negative values reflect greater distrust (i.e., expectation that election fraud will occur), and values closer to zero correspond to an individual's degree of *insecurity*.
-
-## Results
-
-Once trust and distrust were composed into unified variable of confidence in elections, I examined distribution of the dependent variable followed by analysis of the effect of the treatment by comparison of mean differences between experiment conditions.
-To retain a meaningful zero, I rescaled the sum scores to range from -3 to 3[^11] and then superimposed two histograms of confidence scores: one derived from AZ items and another for scores derived from local area items (@fig-dist).
-Doing this is illustrative of the relative distribution of confidence that differed depending on the location of elections referred to in the survey items (e.g., Maricopa County, AZ).
-As expected, the distribution of confidence differed depending on whether survey items pertained to elections in Maricopa County, AZ, or elections within one's local area.
-
-{{< embed notebooks/figures.qmd#fig-dist >}}
-
-Overall, the sample expressed more trust in elections relative to distrust seeing as how the distribution of confidence is largely positive.
-However, there's a clear difference between confidence in Maricopa county, AZ elections and elections within one's local area.
-A paired t-test confirms that this difference was statistically significant, though somewhat small (mean difference $= 0.325$, $95\%$ CI $[0.27, 0.38]$, $t(1286) = 11.61$, $p < .001$).
-Nonetheless, respondents appeared less confident regarding elections in Maricopa County, AZ, but held more confidence in elections administration in their local area.
-This complements previous research that demonstrates a similar bias favorable to one's local area [@stewart2022].
-
-Accordingly, when confidence levels are distinguished by experiment condition, the treatment vignette only had an effect upon survey items pertaining to elections in Maricopa County, AZ.
-Conducting an independent samples t-test (i.e., Welch Two Sample t-test) suggests that the effect of the treatment compared to the control condition is positive and statistically significant.
-
-```{r}
-#| label: tbl-ttest
-#| tbl-cap: "Mean Difference of Treatment Compared to Control Condition"
-#| tbl-colwidths: 80
-#| tbl-pos: H
-
-# conduct two t-tests using `rstatix::t_test`, bind results by row, and pipe
-# into table
-tab_ttest <- dplyr::bind_rows(
-  data |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
-  rstatix::t_test(formula = conf.az.rescaled ~ group,var.equal = F,detailed = T),
-  data |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
-  rstatix::t_test(formula = conf.lcl.rescaled ~ group,var.equal = F, detailed = T)
-  ) |> 
-  # specify columns and column names
-  select(
-    Diff = estimate,
-    treat_mean = estimate1,
-    control_mean = estimate2,
-    treat_n = n1,
-    control_n = n2,
-    t = statistic,
-    p, df, conf.low, conf.high) |> 
-  mutate(
-    Place = dplyr::case_when(
-      p <= 0.05 ~ "Maricopa County, AZ", 
-      p > 0.05 ~ "Local Area"), 
-    .before = Diff) |> 
-  insight::format_table(stars = T)
-
-# convert from `data.frame` to `tinytable` class object
-tab_ttest <- tinytable::tt(tab_ttest)
-
-# modify column names of table
-colnames(tab_ttest) <- c(
-  "Place",
-  "$\\bar{x}_{diff}$",
-  "$\\bar{x}_{treat}$",
-  "$\\bar{x}_{control}$",
-  "$n_{treat}$",
-  "$n_{control}$",
-  "t",
-  "p",
-  "df",
-  "CI")
-
-# Output using `tinytable` R Package
-tab_ttest |> 
-  tinytable::format_tt(
-    j = 2:6, # specify columns
-    math = T # apply mathmode to specified columns
-  ) |> 
-  tinytable::style_tt(
-    fontsize = 0.75, # fontsize in em units (0.75*default fontsize)
-    align = "lccccccccc"
+```{=typst}
+#set block(spacing: 2em)
+#set par(first-line-indent: (
+  amount: 1.5em,
+  all: true),
+  leading: 0.85em,
+  spacing: 1.5em
   )
-
 ```
 
-The results of @tbl-ttest show that, on a scale ranging from -3 to 3, the effect of the treatment is associated with a $0.20$ average difference in confidence in elections in Maricopa County, AZ, compared to the control group.
-When the dependent variable is centered to have a mean of $0$ and standard deviation of $1$, standardized parameters permit interpretation of the treatment effect in terms of standard deviations; the standardized difference in confidence between treatment and control is $0.16$ (CI $[0.06, 0.27]$).
+## Sample
 
-```{r}
-#| label: fig-coef1
-#| layout-nrow: 2
-#| fig-height: 3.5
-#| fig-pos: 'H'
-#| fig-cap: "Confidence in Elections by Experiment Condition"
-#| fig-subcap: 
-#|   - "Confidence by Treatment Condition"
-#|   - "Trust and Distrust by Treatment Condition"
-
-# coef plot of treatment effect on confidence distinguished by location
-conf.coef1 <- jtools::plot_summs(
-  lm(conf.az.rescaled ~ group, data = data), 
-  lm(conf.lcl.rescaled ~ group, data = data), 
-  center = T, scale = T, transform.response = T,
-  model.names = c("Conf.AZ", "Conf.Local"),
-  coefs = c("Treatment" = "groupTreatment"), 
-  colors = c("red", "black"),
-  point.shape = c(8, 1))+
-  ggplot2::expand_limits(x = c(-0.25, 0.25))+
-  labs(y = "")+
-  theme_bw(base_family = "TeX Gyre Pagella")
-
-# Coef plots of trust and distrust models for AZ and Local items
-conf.coef2 <- jtools::plot_summs(
-  lm(trust.scores.az ~ group, data = data),
-  lm(distrust.scores.az ~ group, data = data),
-  lm(trust.scores.lcl ~ group, data = data),
-  lm(distrust.scores.lcl ~ group, data = data),
-  center = T, scale = T, transform.response = T,
-  model.names = c("Trust.AZ", "Distrust.AZ", "Trust.Local", "Distrust.Local"),
-  coefs = c("Treatment" = "groupTreatment"),
-  colors = c("red", "red", "black", "black"),
-  point.shape = c(8, 8, 1, 1)
-)+
-  ggplot2::expand_limits(x = c(-0.25, 0.25))+
-  labs(y = "")+
-  theme_bw(base_family = "TeX Gyre Pagella")
-
-conf.coef1
-conf.coef2
-
-```
-
-@fig-coef1 displays standard difference estimates of confidence in elections by treatment condition (control condition as reference).
-@fig-coef1-1 displays two models for confidence in elections in Maricopa County, AZ, and one's local area by treatment condition; @fig-coef1-2 displays the same except *confidence* is decomposed into its two components, *trust* and *distrust*.
-These figures merely illustrate the effect of the treatment with respect to the relationship between trust and distrust; ultimately confidence improves.
-
-Confidence in elections was higher among those who read the treatment vignette but remained conditional on whether the survey questions inquired about elections in Maricopa County, AZ.
-This evidence suggests that announcing efforts to recruit veterans and their families to work as election staff and volunteers may increase confidence in elections administration in places outside of one's local area, but may not boost confidence in elections within one's local area.
-
-### 2020 Election Legitimacy Beliefs
-
-I now turn to results examining the effect of the treatment on those who held onto the belief that the 2020 election results were illegitimate.
-First, reviewing responses to items that capture trust in elections, it is easy to recognize the difference between the way 2020 election deniers responded with respect to where elections were held.
-
-{{< embed notebooks/figures.qmd#fig-patch13 >}}
-
-Among those who refuted the 2020 election results, trust in Maricopa County, AZ elections was lower for each item compared to items pertaining to elections within one's local area, regardless of treatment condition.
-However, notably, trust that election technology would be secure received the lowest confidence endorsement overall.
-There was also a notable lack of trust that the voting process would be fair relative to the other items[^12].
-Now the comparative difference in responses between those in the treatment group compared to those in the control group appears substantial for items pertaining to elections in Maricopa County, AZ.
-
-{{< embed notebooks/figures.qmd#fig-patch14 >}}
-
-Concerning distrust among those who refuted the 2020 election results, responses to items assessing one's expectation that election fraud would occur reveal the same pattern.
-Although there is not as stark a disparity between responses of those in the treatment and those in the control, among those in the treatment group, there does appear to be less expectation that election fraud would occur in Maricopa County, AZ.
-Overall, review of responses to trust (@fig-patch13) and distrust survey items (@fig-patch14) does lend credence to the impact of the treatment.
-
-In order to substantiate the overall influence of the treatment on confidence in elections, I regressed the dependent variable confidence on legitimacy beliefs while controlling for partisanship.
-
-```{r}
-#| label: tbl-legit
-#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
-#| tbl-pos: H
-
-# All continuous variables are mean-centered and scaled by 1 standard deviation.
-m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = data)
-m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = data)
-
-tab_legit <- modelsummary::modelsummary(
-  models = list(m1, m2), fmt = 2,
-  estimate = "{estimate} ({std.error}){stars}",
-  statistic = NULL,
-  stars = T,
-  coef_rename = c(
-    "(Intercept)"                        = "(Intercept)",
-    "groupTreatment"                     = "Treatment",
-    "q7Not legitimate"                   = "Not Legitimate",
-    "partyid_3catRepublican"             = "Republican",
-    "partyid_3catDemocrat"               = "Democrat",
-    "groupTreatment x q7Not legitimate"  = "Not Legitimate * Treatment"),
-  gof_map = c("nobs", "r2", "adj.r.squared"),
-  notes = list(
-    "Outcome variable mean-centered and scaled by 1 standard deviation",
-    "+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001"),
-  width = 0.8
-)
-
-colnames(tab_legit) <- c(" ", "Confidence in AZ Elections", "w/Interaction")
-
-tab_legit |> 
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "lcc"
-    ) |>  
-  tinytable::style_tt(i = 6, line = "t") |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
-
-```
-
-The first model in @tbl-legit shows that overall confidence in elections among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
-Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
-Not believing the 2020 election of Joe Biden was legitimate is negatively associated with confidence in elections.
-In order to assess the magnitude of this interaction effect of the treatment on those who refuted the 2020 election results, I ran a model where confidence in elections was regressed on the interaction between the treatment and legitimacy beliefs, controlling for partisanship.
-
-There's a positive interaction effect of the treatment vignette among those who believe that the 2020 election was not legitimate, on average and controlling for partisanship.
-This shows that the treatment effect was most influential upon those who believe the 2020 election results were illegitimate.
-The treatment alone does not reverse such beliefs, but this shows where its influence was most potent.
-
-### Concerns for Violence and Voter Safety
-
-Thus far, publicized announcements that election officials will be targeting veterans in their recruitment efforts does quite a bit to improve confidence in elections outside of one's local area (or, at least for elections held in Maricopa County, AZ), especially among those who believed the 2020 election results were illegitimate.
-While distrust is one concern during the pre-election period, it is not the only concern that arises in anticipation of US elections; the public must feel confident that voters are safe to cast a ballot in person.
-The survey included questions^[See @tbl-4 in Appendix A] that allows me to assess whether those in the treatment condition expressed less concern for violence and more confidence in voter safety compared to those in the control condition.
-```{r}
-#| label: fig-safety-bars
-#| layout-ncol: 1
-#| layout-nrow: 2
-#| fig-cap: "Safety Concerns and Confidence by Treatment Condition"
-#| fig-subcap: 
-#|   - "Concern for Violence while voting in Maricopa County, AZ Elections"
-#|   - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"
-
-# concern for violence by treatment
-bar_q25 <- custom_barplot(
-  data = data, 
-  x = q25, 
-  group = group,
-  subtitle = str_wrap(attr(data$q25, "label"), width = 85)
-  )+
-  theme(text = element_text(family = 'TeX Gyre Pagella'),
-        legend.position = "right")
-
-# confidence in voter safety by treatment
-bar_q26 <- custom_barplot(
-  data = data, 
-  x = q26, 
-  group = group,
-  subtitle = str_wrap(attr(data$q26, "label"), width = 85)
-  )+
-  theme(text = element_text(family = 'TeX Gyre Pagella'),
-        legend.position = "right")
-
-bar_q25
-bar_q26
-
-```
-
-Briefly reviewing @fig-safety-bars, those in the treatment condition felt less concern over the potential for violence compared to those in the control.
-As for confidence in voter safety at election sites, it appears that more respondents in the treatment condition expressed that they were "Very confident" compared to those in the control, by approximately $8$ percentage points.
-
-It would appear that the treatment vignette increased the likelihood that a respondent would select a higher response option compared to those in the control group.
-In order to assess whether that was the case, I conducted an ordered logistic regression on the relevant items using the experimental condition as a dichotomous predictor.
-
-Those in the treatment condition had lower probability to express that they were 'Very' or 'Somewhat' concerned for violence in Maricopa County, AZ Elections, yet higher probability of expressing 'Not too' or 'Not at all' concerned.
-As for confidence in voter safety, moving from treatment to control, the difference in predicted probability of a respondent selecting "Very Confident" was $0.08$.
-@tbl-preds-diff1 and @tbl-preds-diff2 show the significant differences in predicted probabilities at 95$\%$ confidence^[The same models were run for items pertaining to safety concerns in one's local area but results of the treatment were not significantly different from the control.
-See Appendix D for full results table of ordinal logistic regression].
-
-```{r}
-#| label: ordinal-logit
-#| include: false
-
-# needed to duplicate `group` variable with different column name due to
-# conflict with marginaleffects R package
-data <- data |>
-  mutate(condition = group)
-
-# running ordinal logisitc regression models (proportional odds logistic regression)
-m.q25 <- MASS::polr(q25 ~ condition, data = data, method = "logistic", Hess = T)
-m.q26 <- MASS::polr(q26 ~ condition, data = data, method = "logistic", Hess = T)
-m.q36 <- MASS::polr(q36 ~ condition, data = data, method = "logistic", Hess = T)
-m.q37 <- MASS::polr(q37 ~ condition, data = data, method = "logistic", Hess = T)
-
-# "Outcome predicted by a fitted model on a specified scale for a given
-# combination of values of the predictor variables, such as their observed
-# values, their means, or factor levels (a.k.a. "reference grid")".
-
-# predictions(): unit-level (conditional) estimates.
-
-# predicted probability estimates by treatment or control
-q25_preds <- marginaleffects::predictions(m.q25, by = "condition", type = "probs")
-q26_preds <- marginaleffects::predictions(m.q26, by = "condition", type = "probs")
-q36_preds <- marginaleffects::predictions(m.q36, by = "condition", type = "probs")
-q37_preds <- marginaleffects::predictions(m.q37, by = "condition", type = "probs")
-
-# this provides the difference in predicted probabilities between treatment and
-# control
-pdiff_q25 <- marginaleffects::predictions(
-  m.q25,
-  by = "condition",
-  type = "probs",
-  hypothesis = ~ reference | group
-)
-
-pdiff_q26 <- marginaleffects::predictions(
-  m.q26,
-  by = "condition",
-  type = "probs",
-  hypothesis = ~ reference | group
-)
-
-```
-
-```{r}
-#| label: tbl-preds-diff1
-#| tbl-colwidths: 80
-#| tbl-cap: "Difference in Predicted Probabilities in Concern for violence, Threats of Violence, or Intimidation between Treatment and Control"
-
-tab_q25_pdiff <- pdiff_q25 |>
-  dplyr::as_tibble() |>
-  dplyr::rename(
-    Violence = group,
-    z = statistic,
-    'Pr(>|z|)' = p.value) |>
-  select(Violence,
-         hypothesis,
-         estimate,
-         std.error,
-         z,
-         'Pr(>|z|)',
-         conf.low,
-         conf.high) |>
-  insight::format_table(stars = T, digits = 3)
-
-tinytable::tt(
-  tab_q25_pdiff,
-  notes = "Results derived from proportional odds logistic regression model.
-Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |>
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "lcccccc"
-    ) |>  
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
-
-```
-
-```{r}
-#| label: tbl-preds-diff2
-#| tbl-colwidths: 80
-#| tbl-cap: "Difference in Predicted Probabilities in Confidence that voters will be safe to vote in-person between Treatment and Control"
-
-tab_q26_pdiff <- pdiff_q26 |>
-  dplyr::as_tibble() |>
-  dplyr::rename('Voter Safety' = group,
-                z = statistic,
-                'Pr(>|z|)' = p.value) |>
-  select('Voter Safety',
-         hypothesis,
-         estimate,
-         std.error,
-         z,
-         'Pr(>|z|)',
-         conf.low,
-         conf.high) |>
-  insight::format_table(stars = T, digits = 4)
-
-tinytable::tt(
-  tab_q26_pdiff,
-  notes = "Results derived from proportional odds logistic regression model.
-Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |>
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "lcccccc"
-    ) |>  
-  tinytable::style_tt(i = "notes", fontsize = 0.75) # style font of table notes
-
-```
-
-\newpage
-
-## Conclusion
-
-Publicized announcements that election officials are actively recruiting former military service members to work as election staff and volunteers is associated with greater confidence in elections compared to election worker recruitment announcements that do not explicitly mention targeted efforts to recruit former military service members.
-In addition, such public announcements eased concerns about violence and increased confidence that voters would be safe to vote in person at election sites.
-Of course, the higher levels of confidence in elections and voter safety observed among the treatment group were limited to considerations about elections held in Maricopa County, AZ---presumably beyond one's local area.
-This is to be expected bearing in mind that confidence in elections for one's local area is usually higher than for those beyond.
-Thus, there's already more insecurity concerning elections elsewhere for whatever reason.
-
-One obvious contribution of these results shows that the perceived trustworthiness of elections administration is amendable to generalized impressions about the kind and character of the people who work and volunteer as election staff.
-Whatever election officials do to boost public confidence may be overshadowed by impressions about who is staffing election sites.
-
-It should be noted that these results are limited to one's expectations in anticipation of election night.
-Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
-Moreover, It is yet unclear whether actually encountering and interacting with veterans working as staff or volunteers at election sites does much to improve voter confidence after election night compared to anyone else.
-It may be the case that assumptions that veterans are filling spots as election workers and volunteers simply primes positive expectations as one heads into an election site, potentially improving voters perceptions of their own experience on the way out.
-Further research would be needed to test such an idea.
-
-In general, public confidence appears strongest when the elections under consideration regard those within one's local community.
-Yet, such strong confidence is not generalized outward to the institution of elections administration as a whole.
-Insecurity in the integrity of the electoral process and its administration may be naturally higher for elections that occur further from home.
-Whether that is due to some local favorability bias or some outward negativity bias is hard to say.
-And seeing as how insecurity presents vulnerability, it is perhaps far easier to inspire a general sense of distrust in the process and its administration in places more abstract.
-
-In the anticipatory period prior to national elections, publicized efforts to recruit veterans to work as election staff and volunteers may be a small, but positive, step towards reducing insecurity in elections that occur elsewhere.
-Especially among those who maintained a steadfast degree of distrust in elections.
-Despite a lack of evidence that systematic electoral fraud had occurred in the 2020 election, a substantial proportion of the population were unwilling to affirm the legitimacy of the results.
-However, despite such legitimacy beliefs, most were not consistent as they expressed varying levels of trust in different aspects of elections administration.
-These results say more about the influence that military veterans have among those who are most insecure than it does about the public more generally.
-
-{{< pagebreak >}}
-
-# Appendix A: Survey Experiment Vignettes and Survey Items {.appendix}
-
-## Survey Experiment Vignettes
-
-::::: {#fig-vignettes .content-visible layout-ncol="2" when-format="html" unless-format="pdf"}
-::: {#fig-treatment}
-### Treatment Vignette
-
-| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Army veteran Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-::: {#fig-control}
-### Control Vignette
-
-| **Local Residents Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-Fabricated Article Vignettes utilized as Experimental Stimulus
-:::::
-
-::::: {.content-hidden unless-format="pdf" layout="[0.45, -0.1, 0.45]"}
-::: {#first-column}
-### Treatment Vignette
-
-| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Army veteran Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-::: {#second-column}
-### Control Vignette
-
-| **Local Residents Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-:::::
-
-{{< pagebreak >}}
-
-```{r}
-#| label: tbl-4
-#| tbl-cap: "Pre-Treatment Survey Items and Response Options"
-#| tbl-colwidths: [70, 30]
-
-var_label_tab <- function(x){
-    purrr::map(x, ~attr(., "label")) |>
-    purrr::map(~ifelse(purrr::is_null(.), "No label", .)) |>
-    tibble::enframe(name = "var", value = "var_label") |>
-    tidyr::unnest(cols = c(var_label))
-}
-
-Questions <- data |> 
-  dplyr::select(q7, q25, q26, q36, q37) |>
-  dplyr::rename_with(.cols = everything(), .fn = ~snakecase::to_any_case(.,case = "upper_camel")) |> 
-  var_label_tab() |>
-  dplyr::select(Question = var_label) |> 
-  dplyr::pull(Question)
-
-items_responses <- data.frame(
-  Questions = Questions,
-  Response =c(
-    "- Legitimate\n- Not legitimate",
-    "- Very concerned\n- Somewhat concerned\n- Not too concerned\n- Not at all concerned",
-    "- Not at all confident\n- Not too confident\n- Somewhat confident\n- Very confident",
-    "- Very concerned\n- Somewhat concerned\n- Somewhat unconcerned\n- Not at all concerned",
-    "- Not at all confident\n- Not too confident\n- Somewhat confident\n- Very confident")
-)
-
-# wrap in a minipage environment
-minipagify <- function(x) {
-  sprintf(
-    "\\minipage{\\textwidth}%s\\endminipage",
-    sapply(x, mark, "latex")
-  )
-}
-
-# only in LaTeX
-is_latex <- identical(knitr::pandoc_to(), "latex")
-
-tab <- tinytable::tt(items_responses, width = c(0.7, 0.3)) |>
-  tinytable::style_tt(j = c(1,2), fontsize = 0.8, align = "l") |>
-  tinytable::format_tt(markdown = TRUE) |>
-  tinytable::format_tt(j = 2, fn = if (is_latex) minipagify else NULL)
-
-tab
-
-```
-
-\newpage
-
-<!-- {{< pagebreak >}} -->
-
-# Appendix B: Sample Demographics and Balance {.appendix}
-
-## Sample Demographics
-
-The median age was 46 (mean age was $47$), $51.7\%$ ($n = 658$) women, $47\%$ ($n = 598$) men, and approximately $1.3\%$ who identified as either Non-binary/third gender ($n = 7$) or preferred not to say ($n = 9$).
-A large proportion of the sample identified as White or Caucasian ($n = 975, 76.65\%$), while all other non-White respondents comprised $27.83\%$ ($n = 297$) of the sample.
-Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised $13\%$ of the sample; those with either degree at the Associate or Bachelor's level comprised $36.24\%$, while $22.25\%$ had some college but no degree; and $28.46\%$ had either a high school level or equivalent education or less than high school.
-The largest proportion of the sample identified as Democrat at $44.64\%$, followed by Republicans at $42.59\%$.
-The proportion of true Independents^[Independent 'leaners' were grouped into the respective party affiliation in which they lean.] was $12.78\%$.
-
-```{r}
-#| label: sample-desc-setup
-#| tbl-cap: "Sample Demographics"
-#| tbl-pos: 'H'
-
-gtsummary::theme_gtsummary_compact()
-
-# descriptive stats of categorical variables
-# best method for html document
-tbl.desc <- data |>  
-  labelled::set_variable_labels(
-    age_4cat = "Age group",
-    gender_3cat = "Gender",
-    race2 = "Race/Ethnicity",
-    educ_4cat = "Education",
-    partyid_3cat = "Party ID"
-  ) |> 
-  gtsummary::tbl_summary(
-    by = group,
-    include = c(
-    age_4cat, 
-    gender_3cat, 
-    race2,
-    educ_4cat, 
-    partyid_3cat),
-    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
-    missing = "ifany",
-    missing_text = "NA") |> 
-  gtsummary::add_n() |> 
-  gtsummary::add_overall() |> 
-  gtsummary::modify_header(label = "**Demographic**") |> 
-  gtsummary::bold_labels()
-
-```
+The survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland was fielded from August 29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287 U.S.
+citizens 18 years of age or older.
+Respondents were randomly split into either the treatment ($n = 650$) control ($n = 637$) conditions
 
@@
 #| tbl-cap: "Sample Demographics"
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
 
-tbl.desc |> 
-  gtsummary::as_tibble() |> 
-  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
-                "**Control (N = 637)**" = "**Control**  \nN = 637",
-                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
-  dplyr::select(-"**N**") |> 
-  tinytable::tt(theme = "spacing") |> 
-  tinytable::format_tt(markdown = T) |> 
-  tinytable::format_tt(replace = " ") |> 
-  tinytable::style_tt(fontsize = 0.70, align = "lccc")
+df <- data |>
+  dplyr::mutate(
+    mil = dplyr::case_when(
+      milserv1 =="Yes" & milserv2 == "Yes" ~ "Active Duty",
+      milserv1 =="Yes" & milserv2 == "No" ~ "Prior Service (Veteran)",
+      milservfam == "Yes" ~ "Has Family in Military",
+      milservfam == "No" ~ "No Family in Military",
+      TRUE ~ NA),
+    ideo_3cat = dplyr::case_when(
+      ideo %in% c("Extremely Liberal",
+                  "Slightly liberal",
+                  "Liberal") ~ "Liberal",
+      ideo %in% c("Extremely conservative",
+                  "Slightly conservative",
+                  "Conservative") ~ "Conservative",
+      ideo %in% c("Moderate: middle of the road") ~ "Moderate",
+      ideo %in% c("Haven't thought much about this") ~ "Unsure",
+      TRUE ~ NA)
+    ) |> 
+  dplyr::mutate(dplyr::across(where(is.character), ~as.factor(.))) |>
+  dplyr::select(
+    group,
+    age_4cat,
+    gender_3cat,
+    race,
+    hisp,
+    educ_4cat,
+    mil, 
+    partyid_3cat,
+    ideo_3cat
+    ) |> 
+  labelled::set_variable_labels(
+    age_4cat = "Age groups, in years",
+    gender_3cat = "Gender",
+    race = "Race",
+    hisp = "Is R of Hispanic, Latino, or Spanish origin",
+    educ_4cat = "Education",
+    mil = "Military Relation",
+    partyid_3cat = "Party ID", 
+    ideo_3cat = "Political Ideology"
+    )
+
+freqs <- df |> 
+  dplyr::mutate(dplyr::across(where(is.character), ~as.factor(.))) |>
+  purrr::map(janitor::tabyl, show_na = T) |> 
+  purrr::map(janitor::adorn_pct_formatting, affix_sign = F)
+
+freqs <- purrr::list_rbind(freqs) |> 
+  dplyr::rename(" " = '.x[[i]]',
+                "valid percent" = "valid_percent") |>
+  dplyr::as_tibble() |> 
+  dplyr::mutate(across(where(is.factor), ~as.character(.)))
+
+# inner <- "rows={abovesep=0pt, belowsep=0pt}"
+inner <- "rowsep=0pt"
+
+tinytable::tt(freqs, width = c(3, 1, 1, 1)) |>
+  tinytable::format_tt(j = "valid percent", replace = "-") |> 
+  tinytable::group_tt(i = list(
+    "Experiment Condition" = 1,
+    "Age" = 3,
+    "Gender" = 7,
+    "Race" = 11,
+    "Hispanic, Latino, or Spanish Origin" = 17,
+    "Education" = 21,
+    "Military Relation" = 26,
+    "Party ID" = 31,
+    "Political Ideology" = 35),
+    indent = 2
+    ) |>
+  tinytable::style_tt(fontsize = 0.65, align = "lrrr", tabularray_inner = inner)
 
 ```
+
+{{< pagebreak >}}
 
@@
 
-# use `gtsummary` package to build regression table, then output as tibble
-logit_tab <- gtsummary::tbl_regression(
-    m1,
-    intercept = F,
-    label = list(
-      age_4cat ~"Age",
-      gender_3cat ~ "Gender",
-      race2 ~ "Race/Ethnicity",
-      educ_4cat ~ "Education",
-      partyid_3cat ~ "Party ID")) |>
-  gtsummary::bold_labels() |>
-  # gtsummary::show_header_names()
-  gtsummary::modify_header(
-    label = " ",
-    stat_nevent = "**Treatment N**") |>
-  # output as_tibble
-  gtsummary::as_tibble() |>
-  # omit p.values
-  dplyr::select(-4)
+cmp <- c(
+  "age_4cat35-54"  = "35-54",
+  "age_4cat55-74"  = "55-74",
+  "age_4cat75-85+"  = "75-85+",
+  "gender_3catFemale"  = "Female",
+  "gender_3catOther/Refused"  = "Other/Refused",
+  "race2Asian"  = "Asian",
+  "race2Black"  = "Black",
+  "race2Other"  = "Other",
+  "race2Hispanic"  = "Hispanic",
+  "race2American Indian"  = "American Indian",
+  "educ_4catSome college no degree"  = "Some college no degree",
+  "educ_4catCollege degree"  = "College degree",
+  "educ_4catPostgraduate degree"  = "Postgraduate degree",
+  "partyid_3catRepublican"  = "Republican",
+  "partyid_3catDemocrat"  = "Democrat"
+)
 
-# transform tibble dataframe into `tinytable` and format as markdown
-# replace NA with blank " " (or "-" if desired)
-logit_tab <- tinytable::tt(logit_tab, width = 0.8) |> 
-  tinytable::format_tt(markdown = T) |> 
-  tinytable::format_tt(replace = " ")
+gm <- list(
+  list("raw" = "nobs", "clean" = "N", "fmt" = 0),
+  list("raw" = "logLik", "clean" = "Log.Lik.", "fmt" = 3),
+  list("raw" = "deviance", "clean" = "Deviance", "fmt" = 2),
+  list("raw" = "null.deviance", "clean" = "Deviance Null", "fmt" = 2),
+  list("raw" = "df", "clean" = "DF", "fmt" = 0),
+  list("raw" = "chisq", "clean" = "Chi2", "fmt" = 3),
+  list("raw" = "P(>chisq)", "clean" = "P(>chisq)", "fmt" = 3))
 
-# create 2nd table containing only logit model fit statistics
-# using custom function, get logit regression model fit stats... 
-gof_stats <- lrm.gof.stats(m1) |> 
-  # omit certain stats (saves space)
-  dplyr::select(
-    nobs, logLik, df, chisq, P..chi., deviance, null.deviance,
-    -AIC, -BIC, -df.null, -df.residual) |> 
-  # rename column variables
-  dplyr::rename(
-    "Num.Obs"       = "nobs",
-    "Null Deviance" = "null.deviance",
-    "Deviance"      = "deviance",
-    "DF"            = "df",
-    "Log.Lik"       = "logLik",
-    "chisq"       = "chisq",
-    "P(>chisq)"   = "P..chi."
+tab.logit <- modelsummary::modelsummary(
+  list("log(OR)" = m1),
+  output = "tinytable",
+  estimate = "{estimate}, [{conf.low}, {conf.high}]",
+  statistic = NULL,
+  coef_map = cmp,
+  gof_function = lrm.gof.stats,
+  gof_map = gm,
+  gof_omit = "AIC|BIC|F|RMSE",
+  width = c(2,1)
   ) |> 
-  # pivot into two column long-form dataframe
-  tidyr::pivot_longer(cols = everything(),names_to = " ", values_to = '**log(OR)**') |>
-  # pipe into tinytable
-  tinytable::tt(width = 0.8) |> 
-  # ensure rows with math text are identified and formatted as math (i.e., $..$)
-  tinytable::format_tt(i = c(4,5), j = 1, math = T)
+  tinytable::strip_tt(line = TRUE)
 
-# using `rbind2` function, bind 2nd table at bottom of first table 
-tinytable::rbind2(logit_tab, gof_stats, use_names = F, headers = F) |> 
-  # add horizontal line just above fit stats
-  tinytable::style_tt(i = 26, line = "t", line_color = "black", line_width = 0.1) |>
+tab.logit |> 
+  tinytable::group_tt(i = list(
+    "Age" = 1,
+    "Gender" = 4,
+    "Race" = 6,
+    "Education" = 11,
+    "Party ID" = 14), 
+    indent = 2
+    ) |> 
+  tinytable::style_tt(i = 20, line = "b", line_color = "black") |> 
   # adjust fontsize of text within table
-  tinytable::style_tt(fontsize = 0.8, align = "lcc") |>
+  tinytable::style_tt(fontsize = 0.65, align = "lc", tabularray_inner = inner) |>
   # finally, format markdown and blank out any NA fillers
@@
 ```
-
-{{< pagebreak >}}
-
-# Appendix C: Polychoric Item and Score Correlations of Trust and Distrust {.appendix}
-
-## Trust and Distrust
-
-Polychoric correlation is a measure of association between two ordered categorical variables each assumed to represent (i.e., indicate, be influenced by) two normally distributed, continuous, latent variables.
-Due to the fact that each item is an ordered categorical variable assumed to represent one of two latent constructs (i.e., trust or distrust, respectively), I examined polychoric correlations between the items used to construct each scale.
-In addition, one set of the trust and distrust items pertained to Maricopa County, AZ, whereas the other set of items were identical except that these items pertained to one's local area.
-
-Since the two sets of items (AZ items and Local items) are, in theory, supposed to capture the same normally distributed continuous latent variables, then the polychoric inter-item correlations should be significantly associated, strong, and in the same direction for the items that measure trust regardless of whether the items pertain to AZ or one's local area  (likewise for distrust).
-Simply, trust/distrust in elections in AZ should strongly and positively be associated with trust/distrust in elections in one's local area.
-
-Additionally, the items that indicate trust should negatively correlate with items that indicate distrust.
-Furthermore, the strength of the negative correlations between trust and distrust should closely approximate if not match.
-
-```{r}
-#| label: fig-polycor
-#| fig-cap: "Polychoric Item Correlation Matrix"
-#| fig-pos: 'h'
-
-# Get polychoric item correlation matrix.
-item.cor <- data |>
-  select(q19:q24, -q23, q28_1:q28_5, q30:q35, -q34, q40_1:q40_5) |> 
-  # ensure factors are ordered factors
-  mutate(across(where(is.factor), ~factor(., ordered = T))) |> 
-  # adjust variable column names of items
-  dplyr::rename(
-    trustvote_az     = q19,
-    trustadmin_az    = q20,
-    truststaff_az    = q21,
-    trustprcss_az    = q22,
-    trusttech_az     = q24,
-    votefraud_az     = q28_1,
-    miscount_az      = q28_2,
-    turnedaway_az    = q28_3,
-    foreigntamp_az   = q28_4,
-    discourage_az    = q28_5,
-    trustvote_lcl    = q30,
-    trustadmin_lcl   = q31,
-    truststaff_lcl   = q32,
-    trustprcss_lcl   = q33,
-    trusttech_lcl    = q35,
-    votefraud_lcl    = q40_1,
-    miscount_lcl     = q40_2,
-    turnedaway_lcl   = q40_3,
-    foreigntamp_lcl  = q40_4,
-    discourage_lcl   = q40_5
-  ) |> 
-  correlation::correlation(
-    select = 
-      c("trustvote_az", "trustadmin_az", "truststaff_az", "trustprcss_az", "trusttech_az",
-        "votefraud_az", "miscount_az", "turnedaway_az", "foreigntamp_az", "discourage_az"),
-    select2 =
-      c("trustvote_lcl", "trustadmin_lcl", "truststaff_lcl", "trustprcss_lcl","trusttech_lcl",
-        "votefraud_lcl", "miscount_lcl", "turnedaway_lcl", "foreigntamp_lcl","discourage_lcl"),
-    method = "polychoric") |>
-  summary()
-
-# plot item correlations
-plot(item.cor) + theme(axis.text.x = element_text(angle = 45, vjust = 0.6))
-
-```
-
-Indeed, this is what is revealed by the correlation matrix (@fig-polycor).
-Trust items correlate positively, strongly, and are significant regardless of location at which the items pertain.
-The same goes for distrust items.
-Also, items meant to measure trust negatively correlate with the items that measure distrust.
-However, the positive correlations are not nearly as high as would be expected supposing that the items are nearly identical theoretical indicators of the same hypothetical constructs, i.e., trust and distrust respectively.
-
-If the items accurately measure trust/distrust in elections regardless of where those elections are said to take place, then positive correlations between the AZ and Local area items should approach perfect correlation as though the same exact questions were asked twice.
-This result, however, suggests that the location of which the survey items pertain (and perhaps other factors) makes a substantial difference in the pattern of responses, but also raises valid questions as to whether the items accurately measure the latent variable constructs in the first place.
-
-Although I do not explicitly assume that the survey instruments perfectly measure the hypothetical constructs of interest (i.e., trust and distrust), perfect measurement is implicitly assumed by the method of combining multiple item responses into a sum or mean composite score.
-
-In short, I expected item responses from the trust and distrust scales to be inversely correlated among the sample, but not mutually exclusive.
-Indeed, this is what I find.
-Polychoric correlations between the trust and distrust items negatively correlate as expected, as does the correlation between the two sum score scales.
-Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
-The negative correlation between the trust and distrust items and scores makes intuitive sense.
-
-{{< pagebreak >}}
-
-# Appendix D: Predicted Probabilities of Safety Concerns by Treatment Condition {.appendix}
-
-```{r}
-#| label: tbl-safety-logit
-#| tbl-cap: "Ordinal Logistic Regression of Concerns for Violence and Confidence in Voter Safety Regressed on Experiment Condition"
-#| tbl-cap-location: top
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
-
-# save models to a list
-safety_models <- list(
-  "Concerns for Violence (OR)" = m.q25,
-  "Confidence in Voter Safety (OR)" = m.q26)
-
-cm <- c("conditionTreatment" = "Treatment",
-        "Very concerned|Somewhat concerned" = "Very concerned | Somewhat concerned",
-        "Somewhat concerned|Not too concerned" = "Somewhat concerned | Not too concerned",
-        "Not too concerned|Not at all concerned" = "Not too concerned | Not at all concerned",
-        "Not at all confident|Not too confident" = "Not at all confident | Not too confident",
-        "Not too confident|Somewhat confident" = "Not too confident | Somewhat confident",
-        "Somewhat confident|Very confident" = "Somewhat confident | Very confident"
-        )
-
-tbl_safety_logit <- modelsummary::modelsummary(
-  safety_models,  
-  fmt = 3,
-  output = "tinytable",
-  exponentiate = T, # show odds ratio 
-  # coef_omit = c(-4), # only the beta coef, not the intercepts
-  # coef_rename = c("conditionTreatment" = "Treatment"),
-  coef_map = cm,
-  stars = T,
-  # estimate = c("{estimate}{stars}"),
-  statistic = "conf.int",
-  gof_map = c("nobs", "rmse"), 
-  note = list(
-    "Parameter estimate (and confidence intervals) exponentiated to show odds ratios.",
-    "Uncertainty intervals (profile-likelihood) and p-values (two-tailed) computed using a Wald t-distribution approximation")
-  )
-
-tbl_safety_logit |>  
-  tinytable::style_tt(
-    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
-    ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75, align = "l")
-
-```
-
-```{r}
-#| label: tbl-safety-preds1
-#| tbl-cap: "Unit-level predicted probabilities of selecting response or higher comparing experiment condition"
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
-
-# table that shows the predicted probability of selecting a response or lower
-# conditional to the Treatment experiment condition.
-tab_safety_preds1 <- q25_preds |>  
-  dplyr::as_tibble() |> 
-  select(group, condition, 
-         estimate, std.error, statistic,  p.value,
-         conf.low, conf.high) |> 
-  dplyr::rename(
-    Condition = condition,
-    Violence = group,
-    z = statistic,
-    'Pr(>|z|)' = p.value) |>
-  insight::format_table(digits = 3)
-
-tinytable::tt(
-  tab_safety_preds1, digits = 3,
-  notes = attr(data$q25, "label")) |> 
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "llccccc") |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75, align = "l")
-
-```
-
-```{r}
-#| label: tbl-safety-preds2
-#| tbl-cap: "Unit-level predicted probabilities of selecting response or higher conditional to the Treatment experiment condition"
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
-
-# table that shows the predicted probability of selecting a response or lower
-# conditional to the Treatment experiment condition.
-tab_safety_preds2 <- q26_preds |> 
-  dplyr::as_tibble() |> 
-  select(group, condition, 
-         estimate, std.error, statistic,  p.value,
-         conf.low, conf.high) |> 
-  dplyr::rename(
-    Condition = condition,
-    'Voter Safety' = group,
-    z = statistic,
-    'Pr(>|z|)' = p.value) |>
-  insight::format_table(digits = 3)
-
-tinytable::tt(
-  tab_safety_preds2, digits = 3,
-  notes = attr(data$q26, "label")) |>  
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "llccccc"
-    ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
-
-```
-
-{{< pagebreak >}}
-
-[^1]: I adopt a distinction made between *trustworthiness* and *trust* in elections [@stewart2022].
-The "*worthiness*" of one's trust in the conduct and administration of elections is based on the extent that outcomes of an election reasonably follow the rules prescribed and can be adjudicated as such.
-The public's *trust* in elections, however, is amendable to an indefinite number of factors that may be unrelated to the formal structure or procedures of election administration.
-I can recognize that my car is trustworthy prior to ever driving it because it is structurally sound; I have every reason to deem it *worthy of my trust*.
-However, I don't trust my car because I am sure it is haunted.
-
-[^2]: The vignettes written were based on real news stories
-
-[^3]: To be clear, I conducted an auxiliary regression analysis to examine the relationship between legitimacy beliefs and party ID.
-Results revealed a statistically significant relationship between the two variables and thus omitting either would result in biased estimates.
-
-[^4]: Demographic breakdown of the sample are included in Appendix B.
-
-[^5]: The article vignettes were written and designed by Michael Hanmer Ph.D and myself with input from We the Veterans, a non-profit organization
-
-[^6]: Complete text of treatment and control vignettes are included in Appendix A
-
-[^7]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
-
-[^8]: Question wording and responses to a selection of survey items are included in Appendix A.
-
-[^9]: See Appendix C for Inter-item correlation analysis.
-
-[^10]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
-The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024], yet there is no general consensus on the most appropriate method generally.
-The use of either appears to largely depend on the researcher's particular research objective, theoretical suppositions, and necessity.
-Another common concern is the inappropriate treatment of ordinal variables as interval which levy strong assumptions, e.g., each item contributes equally to the variable being measured and that ordinal response categories are equidistant as though on an interval scale [@wang2013; for contrast, see @robitzsch2020].
-
-[^11]: This range is mostly arbitrary, as a range from -1 to 1 works much the same.
-When relying on simple sum total score, the scale ranges from -15 to 15.
-So a single point increase from 0 to 1 may reflect a combination of a single "Very confident" response on a trust item compensated by a single "Somewhat likely" response on a distrust item (i.e., 3-2 = 1), or some other equivalent combination.
-Although the use of mean scores would place scores back onto the response scale metric (e.g., from 0 to 3, reflective of "not at all" to "very"), this results in a unipolar scale (from 0 to 3).
-The bipolar scale resulting from the composition of positive trust and negative distrust engenders meaning to zero and negative values.
-In other words, negative values on the scale for confidence in elections hold substantive meaning (e.g., distrust, absent trust), which makes transforming scores to fit a unipolar scale inappropriate.
-
-[^12]: What is interesting to note here is that the first three items regard the more human element of the election administration process, e.g., ensuring accuracy of counts, competence, and commitment of election workers.
-Although a neat line can't really be drawn between the first three and latter two items presented here, it is interesting to see a slight divergence from the usual high confidence placed in local area elections.

### 2025-07-04 supplemental/appendix_C.qmd
manuscript update with revisions after review

--- 2025-06-03 index.qmd
@@
 ---
-title: 'Inspiring Confidence and Easing Insecurity in the Pre-election period: The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections'
-# subtitle: 'The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections'
-shorttitle: 'Effect of Recruiting Military Veterans on Confidence in 2024 US Elections' # aog-article-pdf
-shortauthors: Isaiah      # aog-article-pdf
-abstract: |
-  In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
-Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
-Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned.
-Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
-In addition, concerns over voter safety and potential for violence were lower among those who received the treatment.
-authors:
-  - name: Isaiah Espinoza
-    email: gespinoz@umd.edu
-    roles: author
-    affiliation:
-      - name: University of Maryland
-        department: Department of Government and Politics
-        city: College Park
-        state: MD
-        country: US
-reference-section-title: References
+title: "Appendix C"
+subtitle: "Polychoric Item and Score Correlations of Trust and Distrust"
+format:
+  typst: 
+    toc: false
+    keep-typ: true
+    papersize: us-letter
+    mainfont: TeX Gyre Pagella
+    fontsize: 11pt
+execute: 
+  echo: false
 knitr: 
@@
     dev: "ragg_png" # same as knitr::opts_chunk$set(dev = "ragg_png")
-editor_options: 
-  chunk_output_type: console
 ---
@@
 # load data
-load("data/research-paper-data-20241029.Rdata")
+load(here::here("data", "research-paper-data-20241029.Rdata"))
+
+# set ggplot theme that will be used for every plot
+# theme_get()
+old <- theme_set(theme_bw()) # capture current theme
+
+# set/update new theme
+ggplot2::theme_set(
+  new = ggplot2::theme_bw(base_family = 'TeX Gyre Pagella')+
+    ggplot2::theme(legend.position = 'bottom'))
 
 ```
-
-```{r}
-#| label: fun-likert-plot
-
-# custom function used to create Likert Plots
-
-# To avoid excessive copy/paste, I made a function to create Likert plots
-# it is mostly a wrapper around `ggstats::gglikert`, but with a specific set up
-# particular colors, theme, etc. 
-likert_plot <- function(data, x, ...,  
-                        symmetric = FALSE,
-                        variable_labels = NULL,
-                        label_size = 2.5,
-                        vline = FALSE,
-                        title = waiver(), 
-                        subtitle = waiver(),
-                        caption = waiver(),
-                        xlab = waiver()){
-
-  p <- ggstats::gglikert(
-    data = data, include = {{ x }}, ...,
-    variable_labels = variable_labels,
-    symmetric = symmetric)+
-
-    # customize color
-    ggplot2::scale_fill_grey(start = 0.5, end = 0.1)+
-    # custom theme
-    theme_bw(base_family = "TeX Gyre Pagella")+
-    theme(
-      legend.position = 'bottom',  # place legend on bottom
-      axis.title.y.left = element_blank(), # blank out y-axis label
-      axis.text.x = element_blank(), # remove percentage text along x-axis
-      strip.text.y.right = element_text(angle = 0) # make facet label horizontal
-        )
-
-    if (vline==TRUE) {
-    p <- p + geom_vline(xintercept = 0, color = 'black', linewidth = 1.2)
-  } else {
-      p
-  }
-
-  p <- p + ggplot2::labs(..., title = title, subtitle=subtitle, caption=caption, x = xlab)
-  p
-
-}
-
-```
-
-```{r}
-#| label: fun-barplot
-
-# function for creating barplots
-custom_barplot <- function(data, x, group, title = NULL, subtitle = NULL,
-                           caption = NULL, legend_fill = NULL,
-                           xlab = NULL){
-  b <- data |> 
-    group_by({{ group }}, {{ x }}) |> 
-    count() |> 
-    drop_na() |> 
-    group_by({{ group }}) |> 
-  mutate(prop = round(n/sum(n), digits = 3),
-         pct = prop*100,
-         res = str_c(pct,'% (', n, ')', sep = "")) |> 
-  ggplot(aes(x = {{ x }}, y = pct, fill = {{ group }}))+
-  geom_bar(position = 'dodge', stat = 'identity')+
-  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5, vjust = -0.7)+
-  scale_fill_grey(start = 0.5, end = 0.1)
-
-  b <- b + ggplot2::labs(
-    title = title,
-    subtitle = subtitle,
-    caption = stringr::str_wrap(caption, width = 99),
-    fill = legend_fill,
-    y = "Percentage",
-    x = stringr::str_wrap(xlab, width = 85))
-  b
-}
-
-```
-
-```{r}
-#| label: fun-logit-gof
-
-# custom function to return a certain selection of logistic regression model
-# goodness-of-fit statistics
-lrm.gof.stats <- function(x, ...){
-
-  out <- data.frame(
-    null.deviance = x$null.deviance,
-    df.null = x$df.null,
-    logLik = as.numeric(stats::logLik(x)),
-    AIC = stats::AIC(x),
-    BIC = stats::BIC(x),
-    deviance = stats::deviance(x),
-    df.residual = stats::df.residual(x),
-    nobs = stats::nobs(x),
-    chisq = as.numeric(x$null.deviance - stats::deviance(x)),
-    df = as.numeric(x$df.null - stats::df.residual(x)),
-    'P(>chi)' = pchisq(q=x$null.deviance - stats::deviance(x),
-                       df = x$df.null - stats::df.residual(x), 
-                       lower.tail = F)
-  )
-  out <- dplyr::as_tibble(out)
-  return(out)
-}
-
-```
-
-{{< pagebreak >}}
-
-## Introduction
-
-Election administration officials make efforts to sustain public trust and confidence in the fairness and accuracy of elections, and attempt to boost such confidence where it may be deprived.
-Concerns for safety have developed among election staff and voters in more recent elections.
-Regular measures are taken to enhance the *trustworthiness* of the electoral process through practices meant to improve the conduct, transparency, or overall administration of elections in the United States.
-
-Although election officials undertake great efforts to enhance the *trustworthiness* of election administration, public *trust*[^1] in elections is a psychological construct influenced by many things outside of election official control such as partisanship or elite rhetoric [@hooghe2018; @sances2015].
-Moreover, a person's evaluation of the election in hindsight is often influenced by the election outcome itself [@daniller2019; @stewart2022].
-Thus, measures taken by election officials can be undermined, trivialized, or made irrelevant depending on how one feels after the election results have come out.
-
-Such volatile attitudes and evaluations post-election can leave a lasting impression that election officials must contend with upon the next election cycle [@levendusky2024; @bowler2024].
-For instance, we have witnessed many people's outright refusal to accept the 2020 U.S.
-election results as legitimate despite consistent review of the evidence confirming the results as fair and accurate.
-Such a case demonstrates that public trust in elections is, at best, only partial to trustworthiness of election administration in the United States.
-
-One point of contention that election officials have faced in the past regard evaluation of election workers.
-Previous literature has focused on how voter interaction with election workers [@claassen2008], voting technology [@herrnson2009], and the voter experience generally [@atkeson2007], influences evaluations of election administration.
-As such, election worker competency has been examined as a factor significant to evaluations of performance of elections [@hall2007; @hall2009].
-However, considering that individual perceptions and preconceived notions play a huge role in cognition [@cikara2014; @vanbavel2021], it is reasonable to expect that the group an election worker hails from would be an important influence upon the voter's evaluation of the electoral process.
-
-Supposing such is the case, we can expect that information about *who* (i.e., which groups) election officials are targeting in publicized recruitment efforts would lessen particular election insecurity, and concurrently, boost confidence.
-That is to say, it is reasonable to expect that telling people *who* will be working and volunteering as election staff would ease election insecurity, and therefore improve confidence that the election will be conducted fairly, accurately, and safe for all involved.
-
-In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
-Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
-Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned[^2].
-Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
-In addition, concerns over voter safety and potential for violence were lower among those who received the treatment.
-
-This paper is structured as follows.
-First, I provide a brief background on public trust in election administration.
-I synthesize a review of relevant literature with a focus on how political and social science has conceptualized and ascertained public trust in elections.
-Next, I supply reasoning for why military veterans are singled out as the relevant subset of the population in this study.
-I then explicitly provide the simple theory and testable hypotheses of the study before moving on to describe the design of the survey, the measurement instruments therein, and the conceptual and operational definitions of the variables of interest.
-I explain my reasoning and method for constructing the primary dependent variable, which I broadly refer to as *confidence in elections*.
-I close by offering my interpretation of the results and suggest potential avenues for future inquiry.
-
-## Background: Election Administration and Public Confidence
-
-Election officials have tried hard to inspire confidence in the administration and conduct of elections by improving the degree to which elections are trustworthy.
-Development and implementation of procedures such as post-election auditing of ballots and logic-and-accuracy testing of ballot tabulation equipment are prominent examples adding to the long history of efforts to enhance the trustworthiness of election administration in the United States.
-
-Prior to the year 2000, one of the main issues facing election administration was recruiting enough election workers to volunteer at the polls (i.e., poll workers) [@maidenberg1996].
-Election worker recruitment is still much of an issue in the current era as it was then, perhaps worse [@ferrer2024].
-In addition to ensuring election offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections.
-In particular, voting technology [@herrnson2009] and election worker competence was of interest in election studies [@claassen2008; @hall2009; @hall2007].
-Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007].
-
-In 2024, election officials made valiant efforts to boost public confidence elections within an intensified political climate that appeared quite hostile to election officials [@edlin2024; @brennancenterforjustice2024].
-Although polling around the time indicated that most people thought that U.S.
-elections would be run at least somewhat well [@nadeem2024], many election officials nationwide took efforts to assuage the worry of those most skeptical.
-
-Election anxiety was high in the lead up to the 2024 elections in the United States.
-Concerns for voter safety and the prospect of political violence remained prescient and compelled many local officials to prepare for the worst [@edlin2024; @doubek2024].
-Election officials in Washoe County, Nevada, installed panic buttons for election staff that would alert a monitoring center to summon law enforcement [@lincoln2024].
-Nevada also passed a law making it a felony to harass, threaten, or intimidate election workers [@nevadasecretaryofstate2023].
-Leading up to election day, news outlets reported that election work had become a seemingly dangerous job [@wire2024].
-A Brennan Center survey report stated that, "...large numbers of election officials report having experienced threats, abuse, or harassment for doing their jobs" [@edlin2024].
-Concerns over the fairness of elections and accuracy of vote counts intensified, heightening concerns over the prospect of political violence and, in turn, increased worry for the safety of voters and election workers alike.
-Since election worker performance is significant to public evaluation of elections, added safety concerns that drive out election staff and repel volunteers can only detract from trustworthiness of the institution.
-
-## Literature Reivew
-
-Trust and confidence in the conduct of elections concerns aspects of elections that fall squarely within the institution of election administration.
-At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended).
-
-Intuitively, enhancing public trust in elections would best be accomplished by enhancing the *trustworthiness* of the institution, e.g., enhancing vote tabulation equipment and technology, conducting audits.
-However, trust and confidence in elections has become ever more precarious over the last few election cycles.
-Especially considering public polling data since 2000 shows that confidence that votes were, or would be, counted as intended was in a consistent decline despite efforts towards bolstering election integrity and trustworthiness [@sances2015].
-This is even more pronounced considering the role that partisanship has had on such confidence over accuracy of vote counts [@sances2015; @stewart2022].
-
-There's also stark difference in public trust before the election has occurred compared to after, a phenomenon referred to as the "winner-loser gap"; the "winners" are those who supported the winning candidate and the "losers" are those who supported the losing candidate.
-Much research has been dedicated to analyzing the sentiment of electoral winners vs losers, and vice versa [@nadeau1993; @daniller2019].
-Opinions of electoral trust gathered after the election has occurred, however, are limited considering the well-recognized impact that the electoral outcome itself has on feelings of public trust in elections [@daniller2019].
-
-As such, it is questionable whether we can characterize public trust in the pre-election period as the same trust after the election results have come out.
-The former is *anticipatory*---i.e., the kind that is more or less anxious given the uncertainties surrounding the election.
-The latter is *empirical*---a judgement discerned in hindsight after the experience of the election event has occurred.
-As discussed by @stewart2022, not only was confidence in vote count accuracy influenced by the voter experience, but so too were evaluations of election officials [-@stewart2022, 242-243].
-Not to mention the influence that the election results would also have on such evaluations.
-In other words, evaluations of trust considered in hindsight are influenced by the voter experience and the outcome of the election results.
-This study, in contrast, focuses primarily on that *anticipatory* kind of confidence, which speaks more to those insecurities based on perceptions of the institution's trustworthiness than upon the particular voter experience.
-
-Regardless of the measures taken by election officials to boost public confidence in the *trustworthiness* of election administration (e.g., conducting audits, testing election machines), public *trust* and confidence in elections more generally is apt to shift dramatically post-election based on factors such as partisanship, elite rhetoric, particular state policies, and more [@nadeau1993; @carter2024; @coll2024a].
-Moreover, prior research has found that evaluation of election workers themselves are an important factor when it comes to levels of public confidence in the electoral process [@hall2007; @hall2009; @claassen2008].
-Such studies focused on the quality of the voter experience with reference to the interaction between voter and election worker.
-
-Beyond the general competence of election workers, however, the quality of the voter experience may be influenced merely by prior impressions about *who* comprises election staff and volunteers.
-Political and other social science researchers have recognized for some time the power that group identity can have over attitudes and perception [@xiao2016; @xiao2012; @vanbavel2021].
-As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve trust and confidence in election administration, and lessen expectations of electoral fraud.
-The next section elaborates on why military veterans are of particular interest in this regard.
-
-## Why Veterans
-
-Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work.
-Especially since staffing issues have been an issue since at least the 1990s [@maidenberg1996; @ferrer2024].
-In 2020, such efforts were made far more difficult by the COVID-19 pandemic [@mena2020; @abbate2020a].
-There's no special reason to target veterans for recruitment above other groups.
-Indeed, there's no reason to discriminate recruitment efforts at all if the point is purely to fill staffing vacancies.
-
-The reason why veterans arose as a special subset of the population to consider for this inquiry is because there was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021.
-After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterans2022; @nflfootballoperations2022].
-Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts [@powerthepolls2020; @herndon2020].
-Generally, however, recruitment efforts cast a wide net, indiscriminate of who applies [@ross2020; @conde2020].
-
-One can speculate that the motivation to associate military veterans with civic engagement and democracy may be intended to counter negative perceptions and impressions given by the proportion of veteran service members arrested for taking part in the events on January 6th [@milton2021; @loewenson2023; @jensen2022a].
-Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024].
-This is in addition to a strengthened association portrayed in media outlets between military veterans and militias [@steinhauer2020].
-Prior research has substantiated such a connection between veterans and militia groups.
-@cooter2024 notes from her 3-year ethnographic fieldwork among Michigan militia members that, "...approximately 40% of militia leaders and 30% of members had previous military experience.
-Most of these veterans actively sought out such groups, as opposed to being recruited by them" [-@cooter2024; see also @cooter2013].
-Thus, countering such associations by promoting a different image of veterans to the mass public and veterans alike seems like a reasonable motivation.
-Yet such speculation is just that.
-
-That being said, the general public perception, attitudes, or even stereotypes about military veterans are significant to consider.
-Although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023].
-Veterans are a particularly potent group where mention of veteran status seems to have a positive, calming, or nullifying effect on attitudes.
-For instance, recent research shows that, during his campaign in the 2020 Democratic Primaries, Pete Buttigieg's military background mitigated discrimination against him when he was presented as a veteran married to a man [@magni2024].
-Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@hardy2019].
-Moreover, veteran status seems to mitigate or nullify usual stigmas associated with mental illness.
-That is to say, there is negative stigma associated with mental illness [@corrigan2002] and such stigma incurs labor market discrimination [@hipes2016], but evidence suggests that veteran status overrides such stigma and discrimination [@maclean2014].
-Or, in another light, mental illness is seemingly more *understandable* (i.e., permissible) for veterans given the presumptive reasons for their mental strife.
-And media framing as such plays an important role on public perception [@kleykamp2015].
-
-## Theory and Hypotheses
-
-Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veterans and their family members to work as election staff and volunteers would boost public *confidence in elections administration*.
-Indeed, that is the primary hypothesis of this study.
-Although citizens may vote in various ways across the country (e.g., by mail, ballot drop box, in-person), the simple announcement that election officials are engaging in efforts to recruit veterans to work as election staff may boost confidence in elections administration regardless of how, or whether, an individual plans to vote.
-Formally,
-
-> H~1~: Announcements that election officials are recruiting miilitary service veterans to work as election staff and volunteers will be associated with greater confidence in elections administration compared to announcements that do not mention military veterans.
-
-Asking participants whether they supported programs intent on recruiting anyone to work as election staff would garner support regardless of the target group.
-Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require a survey experiment designed to determine whether publicized recruitment efforts targeting veterans as a group would have any special effect on confidence in elections administration.
-
-In addition, prior research has shown that confidence that one's own vote would be counted as intended has been much stronger than confidence that votes nationwide would be treated likewise [@sances2015; @stewart2022].
-In other words, the public is more trusting of elections closer to home.
-Taking into account that confidence is lower for elections conducted outside of one's local area, then information that veterans are being recruited to help conduct elections in locations beyond one's locale may close this gap between confidence in elections within one's local area and confidence in elections elsewhere.
-Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone on public opinion.
-Therefore, any observed disparity of confidence in elections between those within one's local area and those beyond will be smaller among those who are presented with information about election official recruitment efforts of veteran service members.
-
-Since the results and events following the 2020 election loomed large in anticipation of the U.S.
-2024 general elections, it is reasonable to take into account beliefs about legitimacy of the 2020 election.
-This group who denies the legitimacy of the 2020 election results were possibly the most apprehensive (distrusting) of the 2024 election.
-However, given that veteran service members are held in high regard, generally speaking, announcing that veterans are being actively recruited to work as election staff and volunteers is expected to positively influence confidence in elections among those who remained firm in the belief that the 2020 election results were illegitimate.
-That is to say, despite their belief about the illegitimacy of the 2020 election results, I expect that informing them about veteran recruitment efforts to improve their confidence in elections.
-I take into account the relationship between partisanship and 2020 election legitimacy beliefs and include partisanship as a control in the analysis[^3].
-
-Finally, I expect that concerns about potential for violence will lessen, and confidence in voter safety improve, when presented with information that veterans are being actively recruited to work and volunteer in election offices.
-
-## Experiment Design and Survey Measures
-
-To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would improve confidence in elections and ease insecurity, a recent experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland.
-The survey was fielded from August 29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287 U.S.
-citizens 18 years of age or older.
-Respondents were randomly split into either the treatment ($n =$ 650) control ($n =$ 637) conditions[^4].
-
-Survey participants read either a treatment or control vignette, which resembled a news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election[^5].
-The treatment vignette referred to a program designed to recruit veterans and their family members and describes an interviewee "Jordan Braxton" as an Army veteran.
-The control vignette simply omitted any mention of veterans and their family members, and didn't describe "Jordan Braxton" as an Army veteran.
-Beyond those small differences and the headlines, the article vignettes are identical.
-Therefore, effects can be attributed to the information about veterans in the treatment vignette[^6].
-
-It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignette due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
-Because of this, treatment effects are potentially limited or constrained to attitudes concerning the location specified in the vignette.
-A block of survey items asked specifically about Maricopa County, AZ, followed by an identical block of items that asked the same questions about one's local area.
-I compare and discuss results between the items pertaining to different settings.
-
-Over the past two decades it became commonplace for national polls to gauge public confidence in election administration (i.e., voter confidence) by asking some variety of the question, "How confident are you that your vote \[will be/was\] counted as you intended in the most recent election?" [@hall2009; @sances2015; @stewart2022].
-In addition, since 2008, the Survey of the Performance of American Elections (SPAE) has included a good number of relevant questions to more thoroughly assess trust and confidence in election administration.
-Such questions inquire into the voter experience with the institution more directly.
-This study borrows, modifies, or takes inspiration from certain question items found within the 2022 SPAE and other survey items from the Pew Research Center's 2018 American Trends Panel wave 38 [@dunn2018].
-
-The items in this study all inquire into confidence over one's expectations in anticipation of upcoming elections.
-In addition, the survey of this study focused on attitudes regarding election workers such as election officials, staff, and volunteers specific to the location mentioned in the vignette---Maricopa County, AZ---as well as specific to one's local area[^7].
-
-The survey included items that assessed both trust in elections administration and expectations of electoral fraud, referred to simply as *trust* and *distrust*, respectively.
-Responses from these two sets of items were utilized to construct the primary dependent variable, *confidence in elections*.
-Additionally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
-The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^8].
-Although two survey items are insufficient to serve as a composite scale, safety concerns will be evaluated by examination of response to these two questions in particular.
-
-Prior to the reading the treatment or control vignette, participants responded to distinct survey items assessing one's beliefs about the legitimacy of the 2020 election results ("Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected?").
-Respondents selected either "Legitimate" or "Not Legitimate".
-
-The conventional multiple item assessment of partisanship was included and used to construct a variable of partisanship consisting of three categories: Democrat, Republican, and independent.
-
-### Trust and Distrust in Elections
-
-A set of five survey items measured public trust in elections by inquiring into the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, and confidence that the voting process will be fair.
-Each item in this series presented four response options from "Not at all \[confident/committed\]", "Not too \[confident/committed\]", "Somewhat \[confident/committed\]", and "Very \[confident/committed\]".
-In total, five survey items measure different aspects of trust in elections administration.
-
-```{r}
-#| label: tbl-1
-#| tbl-cap: "Survey Items for Trust and Distrust in Elections"
-
-trust_txt <- data |> 
-  dplyr::select(q19, q20, q21, q22, q24) |>
-  labelled::set_variable_labels(
-    q21 = "How commited do you think election staff and volunteers in Maricopa County, AZ will be to making sure the elections are fair and accurate?"
-  ) |> 
-  labelled::generate_dictionary() |> 
-  dplyr::as_tibble() |> 
-  dplyr::select(Trust=label)
-
-distrust_txt <- data |> 
-  dplyr::select(q28_1:q28_5) |>
-  labelled::generate_dictionary() |> 
-  dplyr::as_tibble() |> 
-  dplyr::select(Distrust=label)
-
-conf_items_text <- trust_txt |> 
-  dplyr::mutate(Distrust = dplyr::pull(distrust_txt))
-
-tinytable::tt(conf_items_text, width = c(.5, .5)) |> 
-  tinytable::style_tt(fontsize = 0.80, align = "ll")
-
-```
-
-Another series of five survey items captured an individual's level of *distrust* in elections administration based on the extent to which they expect electoral fraud to occur.
-These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in \[Maricopa County, AZ/ your local area\]?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
-
-Similar to the items capturing trust in elections (@tbl-1), I computed a summated score for each respondent reflecting the extent of their distrust in elections.
-
-Upon construction of the two summated scales of *trust* and *distrust*, internal consistency reliability coefficient $\alpha$ were estimated for both and found to be adequate ($\alpha$ \> 0.8); the trust in elections scale $\alpha$ = 0.93 and the distrust scale $\alpha$ = 0.86.
-In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each[^9].
-
-## Data Specification
-
-The primary outcome of interest concerns public confidence in elections administration compensated by one's distrust in elections, i.e., their expectations of electoral fraud.
-Because trust and distrust are assessed by multiple Likert items, conventional methods call for combining the items of each set into separate Likert scales (also known as summated rating scales).
-However, many of the items comprising the trust scale directly oppose items capturing distrust.
-For instance, one item from the trust scale has the respondent report their confidence that votes will be counted as voter's intend, whereas a separate item from the distrust scale has the the respondent report their expectation that many votes will not be counted.
-Positive responses to these two items directly contradict each other, and would thus cancel out.
-
-In light of this, I reverse coded items on the distrust scale and combined responses to the trust in elections scale.
-That is, item responses on the trust scale ranged from 0 ("Not confident at all") to 3 ("Very confident), whereas responses on the distrust scale ranged from 0 ("Not likely at all") to -3 ("Very likely").
-Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^10].
-On this scale, positive values reflect higher confidence in elections (e.g., elections will be fair and accurate), negative values reflect greater distrust (i.e., expectation that election fraud will occur), and values closer to zero correspond to an individual's degree of *insecurity*.
-
-## Results
-
-Once trust and distrust were composed into unified variable of confidence in elections, I examined distribution of the dependent variable followed by analysis of the effect of the treatment by comparison of mean differences between experiment conditions.
-To retain a meaningful zero, I rescaled the sum scores to range from -3 to 3[^11] and then superimposed two histograms of confidence scores: one derived from AZ items and another for scores derived from local area items (@fig-dist).
-Doing this is illustrative of the relative distribution of confidence that differed depending on the location of elections referred to in the survey items (e.g., Maricopa County, AZ).
-As expected, the distribution of confidence differed depending on whether survey items pertained to elections in Maricopa County, AZ, or elections within one's local area.
-
-{{< embed notebooks/figures.qmd#fig-dist >}}
-
-Overall, the sample expressed more trust in elections relative to distrust seeing as how the distribution of confidence is largely positive.
-However, there's a clear difference between confidence in Maricopa county, AZ elections and elections within one's local area.
-A paired t-test confirms that this difference was statistically significant, though somewhat small (mean difference $= 0.325$, $95\%$ CI $[0.27, 0.38]$, $t(1286) = 11.61$, $p < .001$).
-Nonetheless, respondents appeared less confident regarding elections in Maricopa County, AZ, but held more confidence in elections administration in their local area.
-This complements previous research that demonstrates a similar bias favorable to one's local area [@stewart2022].
-
-Accordingly, when confidence levels are distinguished by experiment condition, the treatment vignette only had an effect upon survey items pertaining to elections in Maricopa County, AZ.
-Conducting an independent samples t-test (i.e., Welch Two Sample t-test) suggests that the effect of the treatment compared to the control condition is positive and statistically significant.
-
-```{r}
-#| label: tbl-ttest
-#| tbl-cap: "Mean Difference of Treatment Compared to Control Condition"
-#| tbl-colwidths: 80
-#| tbl-pos: H
-
-# conduct two t-tests using `rstatix::t_test`, bind results by row, and pipe
-# into table
-tab_ttest <- dplyr::bind_rows(
-  data |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
-  rstatix::t_test(formula = conf.az.rescaled ~ group,var.equal = F,detailed = T),
-  data |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
-  rstatix::t_test(formula = conf.lcl.rescaled ~ group,var.equal = F, detailed = T)
-  ) |> 
-  # specify columns and column names
-  select(
-    Diff = estimate,
-    treat_mean = estimate1,
-    control_mean = estimate2,
-    treat_n = n1,
-    control_n = n2,
-    t = statistic,
-    p, df, conf.low, conf.high) |> 
-  mutate(
-    Place = dplyr::case_when(
-      p <= 0.05 ~ "Maricopa County, AZ", 
-      p > 0.05 ~ "Local Area"), 
-    .before = Diff) |> 
-  insight::format_table(stars = T)
-
-# convert from `data.frame` to `tinytable` class object
-tab_ttest <- tinytable::tt(tab_ttest)
-
-# modify column names of table
-colnames(tab_ttest) <- c(
-  "Place",
-  "$\\bar{x}_{diff}$",
-  "$\\bar{x}_{treat}$",
-  "$\\bar{x}_{control}$",
-  "$n_{treat}$",
-  "$n_{control}$",
-  "t",
-  "p",
-  "df",
-  "CI")
-
-# Output using `tinytable` R Package
-tab_ttest |> 
-  tinytable::format_tt(
-    j = 2:6, # specify columns
-    math = T # apply mathmode to specified columns
-  ) |> 
-  tinytable::style_tt(
-    fontsize = 0.75, # fontsize in em units (0.75*default fontsize)
-    align = "lccccccccc"
-    )
-
-```
-
-The results of @tbl-ttest show that, on a scale ranging from -3 to 3, the effect of the treatment is associated with a $0.20$ average difference in confidence in elections in Maricopa County, AZ, compared to the control group.
-When the dependent variable is centered to have a mean of $0$ and standard deviation of $1$, standardized parameters permit interpretation of the treatment effect in terms of standard deviations; the standardized difference in confidence between treatment and control is $0.16$ (CI $[0.06, 0.27]$).
-
-```{r}
-#| label: fig-coef1
-#| layout-nrow: 2
-#| fig-height: 3.5
-#| fig-pos: 'H'
-#| fig-cap: "Confidence in Elections by Experiment Condition"
-#| fig-subcap: 
-#|   - "Confidence by Treatment Condition"
-#|   - "Trust and Distrust by Treatment Condition"
-
-# coef plot of treatment effect on confidence distinguished by location
-conf.coef1 <- jtools::plot_summs(
-  lm(conf.az.rescaled ~ group, data = data), 
-  lm(conf.lcl.rescaled ~ group, data = data), 
-  center = T, scale = T, transform.response = T,
-  model.names = c("Conf.AZ", "Conf.Local"),
-  coefs = c("Treatment" = "groupTreatment"), 
-  colors = c("red", "black"),
-  point.shape = c(8, 1))+
-  ggplot2::expand_limits(x = c(-0.25, 0.25))+
-  labs(y = "")+
-  theme_bw(base_family = "TeX Gyre Pagella")
-
-# Coef plots of trust and distrust models for AZ and Local items
-conf.coef2 <- jtools::plot_summs(
-  lm(trust.scores.az ~ group, data = data),
-  lm(distrust.scores.az ~ group, data = data),
-  lm(trust.scores.lcl ~ group, data = data),
-  lm(distrust.scores.lcl ~ group, data = data),
-  center = T, scale = T, transform.response = T,
-  model.names = c("Trust.AZ", "Distrust.AZ", "Trust.Local", "Distrust.Local"),
-  coefs = c("Treatment" = "groupTreatment"),
-  colors = c("red", "red", "black", "black"),
-  point.shape = c(8, 8, 1, 1)
-)+
-  ggplot2::expand_limits(x = c(-0.25, 0.25))+
-  labs(y = "")+
-  theme_bw(base_family = "TeX Gyre Pagella")
-
-conf.coef1
-conf.coef2
-
-```
-
-@fig-coef1 displays standard difference estimates of confidence in elections by treatment condition (control condition as reference).
-@fig-coef1-1 displays two models for confidence in elections in Maricopa County, AZ, and one's local area by treatment condition; @fig-coef1-2 displays the same except *confidence* is decomposed into its two components, *trust* and *distrust*.
-These figures merely illustrate the effect of the treatment with respect to the relationship between trust and distrust; ultimately confidence improves.
-
-Confidence in elections was higher among those who read the treatment vignette but remained conditional on whether the survey questions inquired about elections in Maricopa County, AZ.
-This evidence suggests that announcing efforts to recruit veterans and their families to work as election staff and volunteers may increase confidence in elections administration in places outside of one's local area, but may not boost confidence in elections within one's local area.
-
-### 2020 Election Legitimacy Beliefs
-
-I now turn to results examining the effect of the treatment on those who held onto the belief that the 2020 election results were illegitimate.
-First, reviewing responses to items that capture trust in elections, it is easy to recognize the difference between the way 2020 election deniers responded with respect to where elections were held.
-
-{{< embed notebooks/figures.qmd#fig-patch13 >}}
-
-Among those who refuted the 2020 election results, trust in Maricopa County, AZ elections was lower for each item compared to items pertaining to elections within one's local area, regardless of treatment condition.
-However, notably, trust that election technology would be secure received the lowest confidence endorsement overall.
-There was also a notable lack of trust that the voting process would be fair relative to the other items[^12].
-Now the comparative difference in responses between those in the treatment group compared to those in the control group appears substantial for items pertaining to elections in Maricopa County, AZ.
-
-{{< embed notebooks/figures.qmd#fig-patch14 >}}
-
-Concerning distrust among those who refuted the 2020 election results, responses to items assessing one's expectation that election fraud would occur reveal the same pattern.
-Although there is not as stark a disparity between responses of those in the treatment and those in the control, among those in the treatment group, there does appear to be less expectation that election fraud would occur in Maricopa County, AZ.
-Overall, review of responses to trust (@fig-patch13) and distrust survey items (@fig-patch14) does lend credence to the impact of the treatment.
-
-In order to substantiate the overall influence of the treatment on confidence in elections, I regressed the dependent variable confidence on legitimacy beliefs while controlling for partisanship.
-
-```{r}
-#| label: tbl-legit
-#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
-#| tbl-pos: H
-
-# All continuous variables are mean-centered and scaled by 1 standard deviation.
-m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = data)
-m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = data)
-
-tab_legit <- modelsummary::modelsummary(
-  models = list(m1, m2), fmt = 2,
-  estimate = "{estimate} ({std.error}){stars}",
-  statistic = NULL,
-  stars = T,
-  coef_rename = c(
-    "(Intercept)"                        = "(Intercept)",
-    "groupTreatment"                     = "Treatment",
-    "q7Not legitimate"                   = "Not Legitimate",
-    "partyid_3catRepublican"             = "Republican",
-    "partyid_3catDemocrat"               = "Democrat",
-    "groupTreatment x q7Not legitimate"  = "Not Legitimate * Treatment"),
-  gof_map = c("nobs", "r2", "adj.r.squared"),
-  notes = list(
-    "Outcome variable mean-centered and scaled by 1 standard deviation",
-    "+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001"),
-  width = 0.8
-)
-
-colnames(tab_legit) <- c(" ", "Confidence in AZ Elections", "w/Interaction")
-
-tab_legit |> 
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "lcc"
-    ) |>  
-  tinytable::style_tt(i = 6, line = "t") |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
-
-```
-
-The first model in @tbl-legit shows that overall confidence in elections among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
-Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
-Not believing the 2020 election of Joe Biden was legitimate is negatively associated with confidence in elections.
-In order to assess the magnitude of this interaction effect of the treatment on those who refuted the 2020 election results, I ran a model where confidence in elections was regressed on the interaction between the treatment and legitimacy beliefs, controlling for partisanship.
-
-There's a positive interaction effect of the treatment vignette among those who believe that the 2020 election was not legitimate, on average and controlling for partisanship.
-This shows that the treatment effect was most influential upon those who believe the 2020 election results were illegitimate.
-The treatment alone does not reverse such beliefs, but this shows where its influence was most potent.
-
-### Concerns for Violence and Voter Safety
-
-Thus far, publicized announcements that election officials will be targeting veterans in their recruitment efforts does quite a bit to improve confidence in elections outside of one's local area (or, at least for elections held in Maricopa County, AZ), especially among those who believed the 2020 election results were illegitimate.
-While distrust is one concern during the pre-election period, it is not the only concern that arises in anticipation of US elections; the public must feel confident that voters are safe to cast a ballot in person.
-The survey included questions^[See @tbl-4 in Appendix A] that allows me to assess whether those in the treatment condition expressed less concern for violence and more confidence in voter safety compared to those in the control condition.
-```{r}
-#| label: fig-safety-bars
-#| layout-ncol: 1
-#| layout-nrow: 2
-#| fig-cap: "Safety Concerns and Confidence by Treatment Condition"
-#| fig-subcap: 
-#|   - "Concern for Violence while voting in Maricopa County, AZ Elections"
-#|   - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"
-
-# concern for violence by treatment
-bar_q25 <- custom_barplot(
-  data = data, 
-  x = q25, 
-  group = group,
-  subtitle = str_wrap(attr(data$q25, "label"), width = 85)
-  )+
-  theme(text = element_text(family = 'TeX Gyre Pagella'),
-        legend.position = "right")
-
-# confidence in voter safety by treatment
-bar_q26 <- custom_barplot(
-  data = data, 
-  x = q26, 
-  group = group,
-  subtitle = str_wrap(attr(data$q26, "label"), width = 85)
-  )+
-  theme(text = element_text(family = 'TeX Gyre Pagella'),
-        legend.position = "right")
-
-bar_q25
-bar_q26
-
-```
-
-Briefly reviewing @fig-safety-bars, those in the treatment condition felt less concern over the potential for violence compared to those in the control.
-As for confidence in voter safety at election sites, it appears that more respondents in the treatment condition expressed that they were "Very confident" compared to those in the control, by approximately $8$ percentage points.
-
-It would appear that the treatment vignette increased the likelihood that a respondent would select a higher response option compared to those in the control group.
-In order to assess whether that was the case, I conducted an ordered logistic regression on the relevant items using the experimental condition as a dichotomous predictor.
-
-Those in the treatment condition had lower probability to express that they were 'Very' or 'Somewhat' concerned for violence in Maricopa County, AZ Elections, yet higher probability of expressing 'Not too' or 'Not at all' concerned.
-As for confidence in voter safety, moving from treatment to control, the difference in predicted probability of a respondent selecting "Very Confident" was $0.08$.
-@tbl-preds-diff1 and @tbl-preds-diff2 show the significant differences in predicted probabilities at 95$\%$ confidence^[The same models were run for items pertaining to safety concerns in one's local area but results of the treatment were not significantly different from the control.
-See Appendix D for full results table of ordinal logistic regression].
-
-```{r}
-#| label: ordinal-logit
-#| include: false
-
-# needed to duplicate `group` variable with different column name due to
-# conflict with marginaleffects R package
-data <- data |>
-  mutate(condition = group)
-
-# running ordinal logisitc regression models (proportional odds logistic regression)
-m.q25 <- MASS::polr(q25 ~ condition, data = data, method = "logistic", Hess = T)
-m.q26 <- MASS::polr(q26 ~ condition, data = data, method = "logistic", Hess = T)
-m.q36 <- MASS::polr(q36 ~ condition, data = data, method = "logistic", Hess = T)
-m.q37 <- MASS::polr(q37 ~ condition, data = data, method = "logistic", Hess = T)
-
-# "Outcome predicted by a fitted model on a specified scale for a given
-# combination of values of the predictor variables, such as their observed
-# values, their means, or factor levels (a.k.a. "reference grid")".
-
-# predictions(): unit-level (conditional) estimates.
-
-# predicted probability estimates by treatment or control
-q25_preds <- marginaleffects::predictions(m.q25, by = "condition", type = "probs")
-q26_preds <- marginaleffects::predictions(m.q26, by = "condition", type = "probs")
-q36_preds <- marginaleffects::predictions(m.q36, by = "condition", type = "probs")
-q37_preds <- marginaleffects::predictions(m.q37, by = "condition", type = "probs")
-
-# this provides the difference in predicted probabilities between treatment and
-# control
-pdiff_q25 <- marginaleffects::predictions(
-  m.q25,
-  by = "condition",
-  type = "probs",
-  hypothesis = ~ reference | group
-)
-
-pdiff_q26 <- marginaleffects::predictions(
-  m.q26,
-  by = "condition",
-  type = "probs",
-  hypothesis = ~ reference | group
-)
-
-```
-
-```{r}
-#| label: tbl-preds-diff1
-#| tbl-colwidths: 80
-#| tbl-cap: "Difference in Predicted Probabilities in Concern for violence, Threats of Violence, or Intimidation between Treatment and Control"
-
-tab_q25_pdiff <- pdiff_q25 |>
-  dplyr::as_tibble() |>
-  dplyr::rename(
-    Violence = group,
-    z = statistic,
-    'Pr(>|z|)' = p.value) |>
-  select(Violence,
-         hypothesis,
-         estimate,
-         std.error,
-         z,
-         'Pr(>|z|)',
-         conf.low,
-         conf.high) |>
-  insight::format_table(stars = T, digits = 3)
-
-tinytable::tt(
-  tab_q25_pdiff,
-  notes = "Results derived from proportional odds logistic regression model.
-Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |>
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "lcccccc"
-    ) |>  
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
-
-```
-
-```{r}
-#| label: tbl-preds-diff2
-#| tbl-colwidths: 80
-#| tbl-cap: "Difference in Predicted Probabilities in Confidence that voters will be safe to vote in-person between Treatment and Control"
-
-tab_q26_pdiff <- pdiff_q26 |>
-  dplyr::as_tibble() |>
-  dplyr::rename('Voter Safety' = group,
-                z = statistic,
-                'Pr(>|z|)' = p.value) |>
-  select('Voter Safety',
-         hypothesis,
-         estimate,
-         std.error,
-         z,
-         'Pr(>|z|)',
-         conf.low,
-         conf.high) |>
-  insight::format_table(stars = T, digits = 4)
-
-tinytable::tt(
-  tab_q26_pdiff,
-  notes = "Results derived from proportional odds logistic regression model.
-Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |>
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "lcccccc"
-    ) |>  
-  tinytable::style_tt(i = "notes", fontsize = 0.75) # style font of table notes
-
-```
-
-\newpage
-
-## Conclusion
-
-Publicized announcements that election officials are actively recruiting former military service members to work as election staff and volunteers is associated with greater confidence in elections compared to election worker recruitment announcements that do not explicitly mention targeted efforts to recruit former military service members.
-In addition, such public announcements eased concerns about violence and increased confidence that voters would be safe to vote in person at election sites.
-Of course, the higher levels of confidence in elections and voter safety observed among the treatment group were limited to considerations about elections held in Maricopa County, AZ---presumably beyond one's local area.
-This is to be expected bearing in mind that confidence in elections for one's local area is usually higher than for those beyond.
-Thus, there's already more insecurity concerning elections elsewhere for whatever reason.
-
-One obvious contribution of these results shows that the perceived trustworthiness of elections administration is amendable to generalized impressions about the kind and character of the people who work and volunteer as election staff.
-Whatever election officials do to boost public confidence may be overshadowed by impressions about who is staffing election sites.
-
-It should be noted that these results are limited to one's expectations in anticipation of election night.
-Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
-Moreover, It is yet unclear whether actually encountering and interacting with veterans working as staff or volunteers at election sites does much to improve voter confidence after election night compared to anyone else.
-It may be the case that assumptions that veterans are filling spots as election workers and volunteers simply primes positive expectations as one heads into an election site, potentially improving voters perceptions of their own experience on the way out.
-Further research would be needed to test such an idea.
-
-In general, public confidence appears strongest when the elections under consideration regard those within one's local community.
-Yet, such strong confidence is not generalized outward to the institution of elections administration as a whole.
-Insecurity in the integrity of the electoral process and its administration may be naturally higher for elections that occur further from home.
-Whether that is due to some local favorability bias or some outward negativity bias is hard to say.
-And seeing as how insecurity presents vulnerability, it is perhaps far easier to inspire a general sense of distrust in the process and its administration in places more abstract.
-
-In the anticipatory period prior to national elections, publicized efforts to recruit veterans to work as election staff and volunteers may be a small, but positive, step towards reducing insecurity in elections that occur elsewhere.
-Especially among those who maintained a steadfast degree of distrust in elections.
-Despite a lack of evidence that systematic electoral fraud had occurred in the 2020 election, a substantial proportion of the population were unwilling to affirm the legitimacy of the results.
-However, despite such legitimacy beliefs, most were not consistent as they expressed varying levels of trust in different aspects of elections administration.
-These results say more about the influence that military veterans have among those who are most insecure than it does about the public more generally.
-
-{{< pagebreak >}}
-
-# Appendix A: Survey Experiment Vignettes and Survey Items {.appendix}
-
-## Survey Experiment Vignettes
-
-::::: {#fig-vignettes .content-visible layout-ncol="2" when-format="html" unless-format="pdf"}
-::: {#fig-treatment}
-### Treatment Vignette
-
-| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Army veteran Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-::: {#fig-control}
-### Control Vignette
-
-| **Local Residents Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-Fabricated Article Vignettes utilized as Experimental Stimulus
-:::::
-
-::::: {.content-hidden unless-format="pdf" layout="[0.45, -0.1, 0.45]"}
-::: {#first-column}
-### Treatment Vignette
-
-| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Army veteran Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-::: {#second-column}
-### Control Vignette
-
-| **Local Residents Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-:::::
-
-{{< pagebreak >}}
-
-```{r}
-#| label: tbl-4
-#| tbl-cap: "Pre-Treatment Survey Items and Response Options"
-#| tbl-colwidths: [70, 30]
-
-var_label_tab <- function(x){
-    purrr::map(x, ~attr(., "label")) |>
-    purrr::map(~ifelse(purrr::is_null(.), "No label", .)) |>
-    tibble::enframe(name = "var", value = "var_label") |>
-    tidyr::unnest(cols = c(var_label))
-}
-
-Questions <- data |> 
-  dplyr::select(q7, q25, q26, q36, q37) |>
-  dplyr::rename_with(.cols = everything(), .fn = ~snakecase::to_any_case(.,case = "upper_camel")) |> 
-  var_label_tab() |>
-  dplyr::select(Question = var_label) |> 
-  dplyr::pull(Question)
-
-items_responses <- data.frame(
-  Questions = Questions,
-  Response =c(
-    "- Legitimate\n- Not legitimate",
-    "- Very concerned\n- Somewhat concerned\n- Not too concerned\n- Not at all concerned",
-    "- Not at all confident\n- Not too confident\n- Somewhat confident\n- Very confident",
-    "- Very concerned\n- Somewhat concerned\n- Somewhat unconcerned\n- Not at all concerned",
-    "- Not at all confident\n- Not too confident\n- Somewhat confident\n- Very confident")
-)
-
-# wrap in a minipage environment
-minipagify <- function(x) {
-  sprintf(
-    "\\minipage{\\textwidth}%s\\endminipage",
-    sapply(x, mark, "latex")
-  )
-}
-
-# only in LaTeX
-is_latex <- identical(knitr::pandoc_to(), "latex")
-
-tab <- tinytable::tt(items_responses, width = c(0.7, 0.3)) |>
-  tinytable::style_tt(j = c(1,2), fontsize = 0.8, align = "l") |>
-  tinytable::format_tt(markdown = TRUE) |>
-  tinytable::format_tt(j = 2, fn = if (is_latex) minipagify else NULL)
-
-tab
-
-```
-
-\newpage
-
-<!-- {{< pagebreak >}} -->
-
-# Appendix B: Sample Demographics and Balance {.appendix}
-
-## Sample Demographics
-
-The median age was 46 (mean age was $47$), $51.7\%$ ($n = 658$) women, $47\%$ ($n = 598$) men, and approximately $1.3\%$ who identified as either Non-binary/third gender ($n = 7$) or preferred not to say ($n = 9$).
-A large proportion of the sample identified as White or Caucasian ($n = 975, 76.65\%$), while all other non-White respondents comprised $27.83\%$ ($n = 297$) of the sample.
-Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised $13\%$ of the sample; those with either degree at the Associate or Bachelor's level comprised $36.24\%$, while $22.25\%$ had some college but no degree; and $28.46\%$ had either a high school level or equivalent education or less than high school.
-The largest proportion of the sample identified as Democrat at $44.64\%$, followed by Republicans at $42.59\%$.
-The proportion of true Independents^[Independent 'leaners' were grouped into the respective party affiliation in which they lean.] was $12.78\%$.
-
-```{r}
-#| label: sample-desc-setup
-#| tbl-cap: "Sample Demographics"
-#| tbl-pos: 'H'
-
-gtsummary::theme_gtsummary_compact()
-
-# descriptive stats of categorical variables
-# best method for html document
-tbl.desc <- data |>  
-  labelled::set_variable_labels(
-    age_4cat = "Age group",
-    gender_3cat = "Gender",
-    race2 = "Race/Ethnicity",
-    educ_4cat = "Education",
-    partyid_3cat = "Party ID"
-  ) |> 
-  gtsummary::tbl_summary(
-    by = group,
-    include = c(
-    age_4cat, 
-    gender_3cat, 
-    race2,
-    educ_4cat, 
-    partyid_3cat),
-    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
-    missing = "ifany",
-    missing_text = "NA") |> 
-  gtsummary::add_n() |> 
-  gtsummary::add_overall() |> 
-  gtsummary::modify_header(label = "**Demographic**") |> 
-  gtsummary::bold_labels()
-
-```
-
-```{r}
-#| label: tbl-demog
-#| tbl-cap: "Sample Demographics"
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
-
-tbl.desc |> 
-  gtsummary::as_tibble() |> 
-  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
-                "**Control (N = 637)**" = "**Control**  \nN = 637",
-                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
-  dplyr::select(-"**N**") |> 
-  tinytable::tt(theme = "spacing") |> 
-  tinytable::format_tt(markdown = T) |> 
-  tinytable::format_tt(replace = " ") |> 
-  tinytable::style_tt(fontsize = 0.70, align = "lccc")
-
-```
-
-## Test of Random Assignment to Experiment Condition
-
-@tbl-logit shows results of a logistic regression test of random assignment to the treatment group.
-Demographics such as age, gender, race, educational attainment, and party ID are included as predictor variables.
-Note that 19 missing observations were deleted.
-A $\chi^2 = 11.010$, with 15 degrees of freedom and associated p-value > 0.05 ($p = 0.75$) confirms that none of the demographic predictor variables significantly increased the log-odds---in turn, the probability---of being assigned to the treatment group.
-
-```{r}
-#| label: tbl-logit
-#| tbl-cap: "Logistic Regression of Random Assignment to Treatment"
-
-# simple logit of test of random assignment to treatment
-# treatment is DV (treatment = 1, control = 0)
-# demographic variables are IVs
-m1 <- glm(group ~ age_4cat + gender_3cat + race2 + educ_4cat + partyid_3cat, 
-          family = binomial(link = "logit"), data = data)
-
-# use `gtsummary` package to build regression table, then output as tibble
-logit_tab <- gtsummary::tbl_regression(
-    m1,
-    intercept = F,
-    label = list(
-      age_4cat ~"Age",
-      gender_3cat ~ "Gender",
-      race2 ~ "Race/Ethnicity",
-      educ_4cat ~ "Education",
-      partyid_3cat ~ "Party ID")) |>
-  gtsummary::bold_labels() |>
-  # gtsummary::show_header_names()
-  gtsummary::modify_header(
-    label = " ",
-    stat_nevent = "**Treatment N**") |>
-  # output as_tibble
-  gtsummary::as_tibble() |>
-  # omit p.values
-  dplyr::select(-4)
-
-# transform tibble dataframe into `tinytable` and format as markdown
-# replace NA with blank " " (or "-" if desired)
-logit_tab <- tinytable::tt(logit_tab, width = 0.8) |> 
-  tinytable::format_tt(markdown = T) |> 
-  tinytable::format_tt(replace = " ")
-
-# create 2nd table containing only logit model fit statistics
-# using custom function, get logit regression model fit stats... 
-gof_stats <- lrm.gof.stats(m1) |> 
-  # omit certain stats (saves space)
-  dplyr::select(
-    nobs, logLik, df, chisq, P..chi., deviance, null.deviance,
-    -AIC, -BIC, -df.null, -df.residual) |> 
-  # rename column variables
-  dplyr::rename(
-    "Num.Obs"       = "nobs",
-    "Null Deviance" = "null.deviance",
-    "Deviance"      = "deviance",
-    "DF"            = "df",
-    "Log.Lik"       = "logLik",
-    "chisq"       = "chisq",
-    "P(>chisq)"   = "P..chi."
-  ) |> 
-  # pivot into two column long-form dataframe
-  tidyr::pivot_longer(cols = everything(),names_to = " ", values_to = '**log(OR)**') |>
-  # pipe into tinytable
-  tinytable::tt(width = 0.8) |> 
-  # ensure rows with math text are identified and formatted as math (i.e., $..$)
-  tinytable::format_tt(i = c(4,5), j = 1, math = T)
-
-# using `rbind2` function, bind 2nd table at bottom of first table 
-tinytable::rbind2(logit_tab, gof_stats, use_names = F, headers = F) |> 
-  # add horizontal line just above fit stats
-  tinytable::style_tt(i = 26, line = "t", line_color = "black", line_width = 0.1) |>
-  # adjust fontsize of text within table
-  tinytable::style_tt(fontsize = 0.8, align = "lcc") |>
-  # finally, format markdown and blank out any NA fillers
-  tinytable::format_tt(markdown = T, replace = " ")
-
-```
-
-{{< pagebreak >}}
-
-# Appendix C: Polychoric Item and Score Correlations of Trust and Distrust {.appendix}
 
@@
 #| fig-cap: "Polychoric Item Correlation Matrix"
-#| fig-pos: 'h'
+#| fig-pos: '!t'
+#| fig-height: 5
+#| fig-width: 7.5
+#| fig-cap-location: top
 
@@
 item.cor <- data |>
-  select(q19:q24, -q23, q28_1:q28_5, q30:q35, -q34, q40_1:q40_5) |> 
+  dplyr::select(q19:q24, -q23, q28_1:q28_5, q30:q35, -q34, q40_1:q40_5) |> 
   # ensure factors are ordered factors
-  mutate(across(where(is.factor), ~factor(., ordered = T))) |> 
+  dplyr::mutate(dplyr::across(where(is.factor), ~factor(., ordered = T))) |> 
   # adjust variable column names of items
@@
 # plot item correlations
-plot(item.cor) + theme(axis.text.x = element_text(angle = 45, vjust = 0.6))
+plot(item.cor) + ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 45, vjust = 0.6))
 
@@
 This result, however, suggests that the location of which the survey items pertain (and perhaps other factors) makes a substantial difference in the pattern of responses, but also raises valid questions as to whether the items accurately measure the latent variable constructs in the first place.
-
-Although I do not explicitly assume that the survey instruments perfectly measure the hypothetical constructs of interest (i.e., trust and distrust), perfect measurement is implicitly assumed by the method of combining multiple item responses into a sum or mean composite score.
-
-In short, I expected item responses from the trust and distrust scales to be inversely correlated among the sample, but not mutually exclusive.
-Indeed, this is what I find.
-Polychoric correlations between the trust and distrust items negatively correlate as expected, as does the correlation between the two sum score scales.
-Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
-The negative correlation between the trust and distrust items and scores makes intuitive sense.
-
-{{< pagebreak >}}
-
-# Appendix D: Predicted Probabilities of Safety Concerns by Treatment Condition {.appendix}
-
-```{r}
-#| label: tbl-safety-logit
-#| tbl-cap: "Ordinal Logistic Regression of Concerns for Violence and Confidence in Voter Safety Regressed on Experiment Condition"
-#| tbl-cap-location: top
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
-
-# save models to a list
-safety_models <- list(
-  "Concerns for Violence (OR)" = m.q25,
-  "Confidence in Voter Safety (OR)" = m.q26)
-
-cm <- c("conditionTreatment" = "Treatment",
-        "Very concerned|Somewhat concerned" = "Very concerned | Somewhat concerned",
-        "Somewhat concerned|Not too concerned" = "Somewhat concerned | Not too concerned",
-        "Not too concerned|Not at all concerned" = "Not too concerned | Not at all concerned",
-        "Not at all confident|Not too confident" = "Not at all confident | Not too confident",
-        "Not too confident|Somewhat confident" = "Not too confident | Somewhat confident",
-        "Somewhat confident|Very confident" = "Somewhat confident | Very confident"
-        )
-
-tbl_safety_logit <- modelsummary::modelsummary(
-  safety_models,  
-  fmt = 3,
-  output = "tinytable",
-  exponentiate = T, # show odds ratio 
-  # coef_omit = c(-4), # only the beta coef, not the intercepts
-  # coef_rename = c("conditionTreatment" = "Treatment"),
-  coef_map = cm,
-  stars = T,
-  # estimate = c("{estimate}{stars}"),
-  statistic = "conf.int",
-  gof_map = c("nobs", "rmse"), 
-  note = list(
-    "Parameter estimate (and confidence intervals) exponentiated to show odds ratios.",
-    "Uncertainty intervals (profile-likelihood) and p-values (two-tailed) computed using a Wald t-distribution approximation")
-  )
-
-tbl_safety_logit |>  
-  tinytable::style_tt(
-    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
-    ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75, align = "l")
-
-```
-
-```{r}
-#| label: tbl-safety-preds1
-#| tbl-cap: "Unit-level predicted probabilities of selecting response or higher comparing experiment condition"
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
-
-# table that shows the predicted probability of selecting a response or lower
-# conditional to the Treatment experiment condition.
-tab_safety_preds1 <- q25_preds |>  
-  dplyr::as_tibble() |> 
-  select(group, condition, 
-         estimate, std.error, statistic,  p.value,
-         conf.low, conf.high) |> 
-  dplyr::rename(
-    Condition = condition,
-    Violence = group,
-    z = statistic,
-    'Pr(>|z|)' = p.value) |>
-  insight::format_table(digits = 3)
-
-tinytable::tt(
-  tab_safety_preds1, digits = 3,
-  notes = attr(data$q25, "label")) |> 
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "llccccc") |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75, align = "l")
-
-```
-
-```{r}
-#| label: tbl-safety-preds2
-#| tbl-cap: "Unit-level predicted probabilities of selecting response or higher conditional to the Treatment experiment condition"
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
-
-# table that shows the predicted probability of selecting a response or lower
-# conditional to the Treatment experiment condition.
-tab_safety_preds2 <- q26_preds |> 
-  dplyr::as_tibble() |> 
-  select(group, condition, 
-         estimate, std.error, statistic,  p.value,
-         conf.low, conf.high) |> 
-  dplyr::rename(
-    Condition = condition,
-    'Voter Safety' = group,
-    z = statistic,
-    'Pr(>|z|)' = p.value) |>
-  insight::format_table(digits = 3)
-
-tinytable::tt(
-  tab_safety_preds2, digits = 3,
-  notes = attr(data$q26, "label")) |>  
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "llccccc"
-    ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
-
-```
-
-{{< pagebreak >}}
-
-[^1]: I adopt a distinction made between *trustworthiness* and *trust* in elections [@stewart2022].
-The "*worthiness*" of one's trust in the conduct and administration of elections is based on the extent that outcomes of an election reasonably follow the rules prescribed and can be adjudicated as such.
-The public's *trust* in elections, however, is amendable to an indefinite number of factors that may be unrelated to the formal structure or procedures of election administration.
-I can recognize that my car is trustworthy prior to ever driving it because it is structurally sound; I have every reason to deem it *worthy of my trust*.
-However, I don't trust my car because I am sure it is haunted.
-
-[^2]: The vignettes written were based on real news stories
-
-[^3]: To be clear, I conducted an auxiliary regression analysis to examine the relationship between legitimacy beliefs and party ID.
-Results revealed a statistically significant relationship between the two variables and thus omitting either would result in biased estimates.
-
-[^4]: Demographic breakdown of the sample are included in Appendix B.
-
-[^5]: The article vignettes were written and designed by Michael Hanmer Ph.D and myself with input from We the Veterans, a non-profit organization
-
-[^6]: Complete text of treatment and control vignettes are included in Appendix A
-
-[^7]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
-
-[^8]: Question wording and responses to a selection of survey items are included in Appendix A.
-
-[^9]: See Appendix C for Inter-item correlation analysis.
-
-[^10]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
-The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024], yet there is no general consensus on the most appropriate method generally.
-The use of either appears to largely depend on the researcher's particular research objective, theoretical suppositions, and necessity.
-Another common concern is the inappropriate treatment of ordinal variables as interval which levy strong assumptions, e.g., each item contributes equally to the variable being measured and that ordinal response categories are equidistant as though on an interval scale [@wang2013; for contrast, see @robitzsch2020].
-
-[^11]: This range is mostly arbitrary, as a range from -1 to 1 works much the same.
-When relying on simple sum total score, the scale ranges from -15 to 15.
-So a single point increase from 0 to 1 may reflect a combination of a single "Very confident" response on a trust item compensated by a single "Somewhat likely" response on a distrust item (i.e., 3-2 = 1), or some other equivalent combination.
-Although the use of mean scores would place scores back onto the response scale metric (e.g., from 0 to 3, reflective of "not at all" to "very"), this results in a unipolar scale (from 0 to 3).
-The bipolar scale resulting from the composition of positive trust and negative distrust engenders meaning to zero and negative values.
-In other words, negative values on the scale for confidence in elections hold substantive meaning (e.g., distrust, absent trust), which makes transforming scores to fit a unipolar scale inappropriate.
-
-[^12]: What is interesting to note here is that the first three items regard the more human element of the election administration process, e.g., ensuring accuracy of counts, competence, and commitment of election workers.
-Although a neat line can't really be drawn between the first three and latter two items presented here, it is interesting to see a slight divergence from the usual high confidence placed in local area elections.

### 2025-07-04 supplemental/appendix_D.qmd
manuscript update with revisions after review

--- 2025-06-03 index.qmd
@@
 ---
-title: 'Inspiring Confidence and Easing Insecurity in the Pre-election period: The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections'
-# subtitle: 'The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections'
-shorttitle: 'Effect of Recruiting Military Veterans on Confidence in 2024 US Elections' # aog-article-pdf
-shortauthors: Isaiah      # aog-article-pdf
-abstract: |
-  In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
-Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
-Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned.
-Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
-In addition, concerns over voter safety and potential for violence were lower among those who received the treatment.
-authors:
-  - name: Isaiah Espinoza
-    email: gespinoz@umd.edu
-    roles: author
-    affiliation:
-      - name: University of Maryland
-        department: Department of Government and Politics
-        city: College Park
-        state: MD
-        country: US
-reference-section-title: References
-knitr: 
-  opts_chunk: 
-    dev: "ragg_png" # same as knitr::opts_chunk$set(dev = "ragg_png")
-editor_options: 
-  chunk_output_type: console
+title: "Appendix D"
+subtitle: "Predicted Probabilities of Safety Concerns by Treatment Condition"
+format:
+  typst: 
+    toc: false
+    keep-typ: true
+    papersize: us-letter
+    mainfont: TeX Gyre Pagella
+    fontsize: 11pt
+execute: 
+  echo: false
 ---
@@
 
-{{< pagebreak >}}
+```{r}
 
-## Introduction
+# see here: https://vincentarelbundock.github.io/tinytable/vignettes/theme.html#user-written-themes
 
-Election administration officials make efforts to sustain public trust and confidence in the fairness and accuracy of elections, and attempt to boost such confidence where it may be deprived.
-Concerns for safety have developed among election staff and voters in more recent elections.
-Regular measures are taken to enhance the *trustworthiness* of the electoral process through practices meant to improve the conduct, transparency, or overall administration of elections in the United States.
-
-Although election officials undertake great efforts to enhance the *trustworthiness* of election administration, public *trust*[^1] in elections is a psychological construct influenced by many things outside of election official control such as partisanship or elite rhetoric [@hooghe2018; @sances2015].
-Moreover, a person's evaluation of the election in hindsight is often influenced by the election outcome itself [@daniller2019; @stewart2022].
-Thus, measures taken by election officials can be undermined, trivialized, or made irrelevant depending on how one feels after the election results have come out.
-
-Such volatile attitudes and evaluations post-election can leave a lasting impression that election officials must contend with upon the next election cycle [@levendusky2024; @bowler2024].
-For instance, we have witnessed many people's outright refusal to accept the 2020 U.S.
-election results as legitimate despite consistent review of the evidence confirming the results as fair and accurate.
-Such a case demonstrates that public trust in elections is, at best, only partial to trustworthiness of election administration in the United States.
-
-One point of contention that election officials have faced in the past regard evaluation of election workers.
-Previous literature has focused on how voter interaction with election workers [@claassen2008], voting technology [@herrnson2009], and the voter experience generally [@atkeson2007], influences evaluations of election administration.
-As such, election worker competency has been examined as a factor significant to evaluations of performance of elections [@hall2007; @hall2009].
-However, considering that individual perceptions and preconceived notions play a huge role in cognition [@cikara2014; @vanbavel2021], it is reasonable to expect that the group an election worker hails from would be an important influence upon the voter's evaluation of the electoral process.
-
-Supposing such is the case, we can expect that information about *who* (i.e., which groups) election officials are targeting in publicized recruitment efforts would lessen particular election insecurity, and concurrently, boost confidence.
-That is to say, it is reasonable to expect that telling people *who* will be working and volunteering as election staff would ease election insecurity, and therefore improve confidence that the election will be conducted fairly, accurately, and safe for all involved.
-
-In this paper, I report results from a recent survey experiment administered to test whether publicized efforts to recruit veterans to work as election staff and volunteers would improve public trust in elections and ease election insecurity.
-Results of the survey experiment support the notion that emphasizing veterans as the target of election worker recruitment efforts eases pre-election insecurity.
-Expectations of electoral fraud and concerns for voter safety were lower among those who read an announcement that veterans are being recruited to work as election staff and volunteers compared to those who read a control vignette where veterans were not mentioned[^2].
-Notable is that there was a significant difference in confidence among those in the treatment condition who believe that results of the 2020 election were illegitimate.
-In addition, concerns over voter safety and potential for violence were lower among those who received the treatment.
-
-This paper is structured as follows.
-First, I provide a brief background on public trust in election administration.
-I synthesize a review of relevant literature with a focus on how political and social science has conceptualized and ascertained public trust in elections.
-Next, I supply reasoning for why military veterans are singled out as the relevant subset of the population in this study.
-I then explicitly provide the simple theory and testable hypotheses of the study before moving on to describe the design of the survey, the measurement instruments therein, and the conceptual and operational definitions of the variables of interest.
-I explain my reasoning and method for constructing the primary dependent variable, which I broadly refer to as *confidence in elections*.
-I close by offering my interpretation of the results and suggest potential avenues for future inquiry.
-
-## Background: Election Administration and Public Confidence
-
-Election officials have tried hard to inspire confidence in the administration and conduct of elections by improving the degree to which elections are trustworthy.
-Development and implementation of procedures such as post-election auditing of ballots and logic-and-accuracy testing of ballot tabulation equipment are prominent examples adding to the long history of efforts to enhance the trustworthiness of election administration in the United States.
-
-Prior to the year 2000, one of the main issues facing election administration was recruiting enough election workers to volunteer at the polls (i.e., poll workers) [@maidenberg1996].
-Election worker recruitment is still much of an issue in the current era as it was then, perhaps worse [@ferrer2024].
-In addition to ensuring election offices were adequately staffed, the controversy of the 2000 general election made the public more attentive to issues concerning the conduct and administration of elections.
-In particular, voting technology [@herrnson2009] and election worker competence was of interest in election studies [@claassen2008; @hall2009; @hall2007].
-Following the passage of the Help America Vote Act in 2002, election officials efforts to boost public confidence in the conduct and administration of elections revolved primarily around the accuracy of vote counts, ballot tabulation equipment or voting machines, the commitment of election staff, and more [@atkeson2007].
-
-In 2024, election officials made valiant efforts to boost public confidence elections within an intensified political climate that appeared quite hostile to election officials [@edlin2024; @brennancenterforjustice2024].
-Although polling around the time indicated that most people thought that U.S.
-elections would be run at least somewhat well [@nadeem2024], many election officials nationwide took efforts to assuage the worry of those most skeptical.
-
-Election anxiety was high in the lead up to the 2024 elections in the United States.
-Concerns for voter safety and the prospect of political violence remained prescient and compelled many local officials to prepare for the worst [@edlin2024; @doubek2024].
-Election officials in Washoe County, Nevada, installed panic buttons for election staff that would alert a monitoring center to summon law enforcement [@lincoln2024].
-Nevada also passed a law making it a felony to harass, threaten, or intimidate election workers [@nevadasecretaryofstate2023].
-Leading up to election day, news outlets reported that election work had become a seemingly dangerous job [@wire2024].
-A Brennan Center survey report stated that, "...large numbers of election officials report having experienced threats, abuse, or harassment for doing their jobs" [@edlin2024].
-Concerns over the fairness of elections and accuracy of vote counts intensified, heightening concerns over the prospect of political violence and, in turn, increased worry for the safety of voters and election workers alike.
-Since election worker performance is significant to public evaluation of elections, added safety concerns that drive out election staff and repel volunteers can only detract from trustworthiness of the institution.
-
-## Literature Reivew
-
-Trust and confidence in the conduct of elections concerns aspects of elections that fall squarely within the institution of election administration.
-At this level, for instance, public trust is ascertained by capturing assessments about the perceived accuracy of vote counts (e.g., whether votes are/were counted as intended).
-
-Intuitively, enhancing public trust in elections would best be accomplished by enhancing the *trustworthiness* of the institution, e.g., enhancing vote tabulation equipment and technology, conducting audits.
-However, trust and confidence in elections has become ever more precarious over the last few election cycles.
-Especially considering public polling data since 2000 shows that confidence that votes were, or would be, counted as intended was in a consistent decline despite efforts towards bolstering election integrity and trustworthiness [@sances2015].
-This is even more pronounced considering the role that partisanship has had on such confidence over accuracy of vote counts [@sances2015; @stewart2022].
-
-There's also stark difference in public trust before the election has occurred compared to after, a phenomenon referred to as the "winner-loser gap"; the "winners" are those who supported the winning candidate and the "losers" are those who supported the losing candidate.
-Much research has been dedicated to analyzing the sentiment of electoral winners vs losers, and vice versa [@nadeau1993; @daniller2019].
-Opinions of electoral trust gathered after the election has occurred, however, are limited considering the well-recognized impact that the electoral outcome itself has on feelings of public trust in elections [@daniller2019].
-
-As such, it is questionable whether we can characterize public trust in the pre-election period as the same trust after the election results have come out.
-The former is *anticipatory*---i.e., the kind that is more or less anxious given the uncertainties surrounding the election.
-The latter is *empirical*---a judgement discerned in hindsight after the experience of the election event has occurred.
-As discussed by @stewart2022, not only was confidence in vote count accuracy influenced by the voter experience, but so too were evaluations of election officials [-@stewart2022, 242-243].
-Not to mention the influence that the election results would also have on such evaluations.
-In other words, evaluations of trust considered in hindsight are influenced by the voter experience and the outcome of the election results.
-This study, in contrast, focuses primarily on that *anticipatory* kind of confidence, which speaks more to those insecurities based on perceptions of the institution's trustworthiness than upon the particular voter experience.
-
-Regardless of the measures taken by election officials to boost public confidence in the *trustworthiness* of election administration (e.g., conducting audits, testing election machines), public *trust* and confidence in elections more generally is apt to shift dramatically post-election based on factors such as partisanship, elite rhetoric, particular state policies, and more [@nadeau1993; @carter2024; @coll2024a].
-Moreover, prior research has found that evaluation of election workers themselves are an important factor when it comes to levels of public confidence in the electoral process [@hall2007; @hall2009; @claassen2008].
-Such studies focused on the quality of the voter experience with reference to the interaction between voter and election worker.
-
-Beyond the general competence of election workers, however, the quality of the voter experience may be influenced merely by prior impressions about *who* comprises election staff and volunteers.
-Political and other social science researchers have recognized for some time the power that group identity can have over attitudes and perception [@xiao2016; @xiao2012; @vanbavel2021].
-As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve trust and confidence in election administration, and lessen expectations of electoral fraud.
-The next section elaborates on why military veterans are of particular interest in this regard.
-
-## Why Veterans
-
-Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work.
-Especially since staffing issues have been an issue since at least the 1990s [@maidenberg1996; @ferrer2024].
-In 2020, such efforts were made far more difficult by the COVID-19 pandemic [@mena2020; @abbate2020a].
-There's no special reason to target veterans for recruitment above other groups.
-Indeed, there's no reason to discriminate recruitment efforts at all if the point is purely to fill staffing vacancies.
-
-The reason why veterans arose as a special subset of the population to consider for this inquiry is because there was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021.
-After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterans2022; @nflfootballoperations2022].
-Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts [@powerthepolls2020; @herndon2020].
-Generally, however, recruitment efforts cast a wide net, indiscriminate of who applies [@ross2020; @conde2020].
-
-One can speculate that the motivation to associate military veterans with civic engagement and democracy may be intended to counter negative perceptions and impressions given by the proportion of veteran service members arrested for taking part in the events on January 6th [@milton2021; @loewenson2023; @jensen2022a].
-Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024].
-This is in addition to a strengthened association portrayed in media outlets between military veterans and militias [@steinhauer2020].
-Prior research has substantiated such a connection between veterans and militia groups.
-@cooter2024 notes from her 3-year ethnographic fieldwork among Michigan militia members that, "...approximately 40% of militia leaders and 30% of members had previous military experience.
-Most of these veterans actively sought out such groups, as opposed to being recruited by them" [-@cooter2024; see also @cooter2013].
-Thus, countering such associations by promoting a different image of veterans to the mass public and veterans alike seems like a reasonable motivation.
-Yet such speculation is just that.
-
-That being said, the general public perception, attitudes, or even stereotypes about military veterans are significant to consider.
-Although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023].
-Veterans are a particularly potent group where mention of veteran status seems to have a positive, calming, or nullifying effect on attitudes.
-For instance, recent research shows that, during his campaign in the 2020 Democratic Primaries, Pete Buttigieg's military background mitigated discrimination against him when he was presented as a veteran married to a man [@magni2024].
-Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@hardy2019].
-Moreover, veteran status seems to mitigate or nullify usual stigmas associated with mental illness.
-That is to say, there is negative stigma associated with mental illness [@corrigan2002] and such stigma incurs labor market discrimination [@hipes2016], but evidence suggests that veteran status overrides such stigma and discrimination [@maclean2014].
-Or, in another light, mental illness is seemingly more *understandable* (i.e., permissible) for veterans given the presumptive reasons for their mental strife.
-And media framing as such plays an important role on public perception [@kleykamp2015].
-
-## Theory and Hypotheses
-
-Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veterans and their family members to work as election staff and volunteers would boost public *confidence in elections administration*.
-Indeed, that is the primary hypothesis of this study.
-Although citizens may vote in various ways across the country (e.g., by mail, ballot drop box, in-person), the simple announcement that election officials are engaging in efforts to recruit veterans to work as election staff may boost confidence in elections administration regardless of how, or whether, an individual plans to vote.
-Formally,
-
-> H~1~: Announcements that election officials are recruiting miilitary service veterans to work as election staff and volunteers will be associated with greater confidence in elections administration compared to announcements that do not mention military veterans.
-
-Asking participants whether they supported programs intent on recruiting anyone to work as election staff would garner support regardless of the target group.
-Considering that support and admiration for veterans is generally high among the population [@kleykamp2023], then discerning the impact on one's confidence would require a survey experiment designed to determine whether publicized recruitment efforts targeting veterans as a group would have any special effect on confidence in elections administration.
-
-In addition, prior research has shown that confidence that one's own vote would be counted as intended has been much stronger than confidence that votes nationwide would be treated likewise [@sances2015; @stewart2022].
-In other words, the public is more trusting of elections closer to home.
-Taking into account that confidence is lower for elections conducted outside of one's local area, then information that veterans are being recruited to help conduct elections in locations beyond one's locale may close this gap between confidence in elections within one's local area and confidence in elections elsewhere.
-Although it may be difficult to discern whether recruiting veteran service members would improve confidence in elections near one's local area in light of such hometown favoritism, a positive effect on confidence in elections held beyond one's local area---where confidence is already expectedly lower---can help discern the impact of the group alone on public opinion.
-Therefore, any observed disparity of confidence in elections between those within one's local area and those beyond will be smaller among those who are presented with information about election official recruitment efforts of veteran service members.
-
-Since the results and events following the 2020 election loomed large in anticipation of the U.S.
-2024 general elections, it is reasonable to take into account beliefs about legitimacy of the 2020 election.
-This group who denies the legitimacy of the 2020 election results were possibly the most apprehensive (distrusting) of the 2024 election.
-However, given that veteran service members are held in high regard, generally speaking, announcing that veterans are being actively recruited to work as election staff and volunteers is expected to positively influence confidence in elections among those who remained firm in the belief that the 2020 election results were illegitimate.
-That is to say, despite their belief about the illegitimacy of the 2020 election results, I expect that informing them about veteran recruitment efforts to improve their confidence in elections.
-I take into account the relationship between partisanship and 2020 election legitimacy beliefs and include partisanship as a control in the analysis[^3].
-
-Finally, I expect that concerns about potential for violence will lessen, and confidence in voter safety improve, when presented with information that veterans are being actively recruited to work and volunteer in election offices.
-
-## Experiment Design and Survey Measures
-
-To test the theory that publicized efforts to recruit veterans to work as election staff and volunteers would improve confidence in elections and ease insecurity, a recent experiment was embedded in a survey developed and conducted by the Center for Democracy and Civic Engagement (CDCE) at the University of Maryland.
-The survey was fielded from August 29th, 2024 to September 18th, 2024 on a non-probability sample of 1,287 U.S.
-citizens 18 years of age or older.
-Respondents were randomly split into either the treatment ($n =$ 650) control ($n =$ 637) conditions[^4].
-
-Survey participants read either a treatment or control vignette, which resembled a news article about efforts in Maricopa County, AZ to recruit election staff and volunteers for the 2024 general election[^5].
-The treatment vignette referred to a program designed to recruit veterans and their family members and describes an interviewee "Jordan Braxton" as an Army veteran.
-The control vignette simply omitted any mention of veterans and their family members, and didn't describe "Jordan Braxton" as an Army veteran.
-Beyond those small differences and the headlines, the article vignettes are identical.
-Therefore, effects can be attributed to the information about veterans in the treatment vignette[^6].
-
-It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignette due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
-Because of this, treatment effects are potentially limited or constrained to attitudes concerning the location specified in the vignette.
-A block of survey items asked specifically about Maricopa County, AZ, followed by an identical block of items that asked the same questions about one's local area.
-I compare and discuss results between the items pertaining to different settings.
-
-Over the past two decades it became commonplace for national polls to gauge public confidence in election administration (i.e., voter confidence) by asking some variety of the question, "How confident are you that your vote \[will be/was\] counted as you intended in the most recent election?" [@hall2009; @sances2015; @stewart2022].
-In addition, since 2008, the Survey of the Performance of American Elections (SPAE) has included a good number of relevant questions to more thoroughly assess trust and confidence in election administration.
-Such questions inquire into the voter experience with the institution more directly.
-This study borrows, modifies, or takes inspiration from certain question items found within the 2022 SPAE and other survey items from the Pew Research Center's 2018 American Trends Panel wave 38 [@dunn2018].
-
-The items in this study all inquire into confidence over one's expectations in anticipation of upcoming elections.
-In addition, the survey of this study focused on attitudes regarding election workers such as election officials, staff, and volunteers specific to the location mentioned in the vignette---Maricopa County, AZ---as well as specific to one's local area[^7].
-
-The survey included items that assessed both trust in elections administration and expectations of electoral fraud, referred to simply as *trust* and *distrust*, respectively.
-Responses from these two sets of items were utilized to construct the primary dependent variable, *confidence in elections*.
-Additionally, a pair of survey items assessed concerns for potential violence and confidence in voter safety.
-The pair was asked once in regard to Maricopa County, AZ and again with respect to one's local area[^8].
-Although two survey items are insufficient to serve as a composite scale, safety concerns will be evaluated by examination of response to these two questions in particular.
-
-Prior to the reading the treatment or control vignette, participants responded to distinct survey items assessing one's beliefs about the legitimacy of the 2020 election results ("Regardless of whom you supported in the 2020 election, do you think Joe Biden's election as president was legitimate, or was he not legitimately elected?").
-Respondents selected either "Legitimate" or "Not Legitimate".
-
-The conventional multiple item assessment of partisanship was included and used to construct a variable of partisanship consisting of three categories: Democrat, Republican, and independent.
-
-### Trust and Distrust in Elections
-
-A set of five survey items measured public trust in elections by inquiring into the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, and confidence that the voting process will be fair.
-Each item in this series presented four response options from "Not at all \[confident/committed\]", "Not too \[confident/committed\]", "Somewhat \[confident/committed\]", and "Very \[confident/committed\]".
-In total, five survey items measure different aspects of trust in elections administration.
-
-```{r}
-#| label: tbl-1
-#| tbl-cap: "Survey Items for Trust and Distrust in Elections"
-
-trust_txt <- data |> 
-  dplyr::select(q19, q20, q21, q22, q24) |>
-  labelled::set_variable_labels(
-    q21 = "How commited do you think election staff and volunteers in Maricopa County, AZ will be to making sure the elections are fair and accurate?"
-  ) |> 
-  labelled::generate_dictionary() |> 
-  dplyr::as_tibble() |> 
-  dplyr::select(Trust=label)
-
-distrust_txt <- data |> 
-  dplyr::select(q28_1:q28_5) |>
-  labelled::generate_dictionary() |> 
-  dplyr::as_tibble() |> 
-  dplyr::select(Distrust=label)
-
-conf_items_text <- trust_txt |> 
-  dplyr::mutate(Distrust = dplyr::pull(distrust_txt))
-
-tinytable::tt(conf_items_text, width = c(.5, .5)) |> 
-  tinytable::style_tt(fontsize = 0.80, align = "ll")
+theme_mitex <- function(x, ...) {
+    fn <- function(table) {
+        if (isTRUE(table@output == "typst")) {
+          table@table_string <- gsub(
+            "\\$(.*?)\\$",
+            "#mitex(`\\1`)",
+            table@table_string)
+        }
+        return(table)
+    }
+    x <- style_tt(x, finalize = fn)
+    return(x)
+}
 
@@
 
-Another series of five survey items captured an individual's level of *distrust* in elections administration based on the extent to which they expect electoral fraud to occur.
-These items were prefaced with the question, "How likely do you think any or all of the following will happen during this year´s elections in \[Maricopa County, AZ/ your local area\]?" Each item presented four response options: "Not likely at all", "Not too likely", "Somewhat likely", and "Very likely".
-
-Similar to the items capturing trust in elections (@tbl-1), I computed a summated score for each respondent reflecting the extent of their distrust in elections.
-
-Upon construction of the two summated scales of *trust* and *distrust*, internal consistency reliability coefficient $\alpha$ were estimated for both and found to be adequate ($\alpha$ \> 0.8); the trust in elections scale $\alpha$ = 0.93 and the distrust scale $\alpha$ = 0.86.
-In other words, the items in each of the scales were intercorrelated well enough for each to compose a single scale presuming a unidimensional construct for each[^9].
-
-## Data Specification
-
-The primary outcome of interest concerns public confidence in elections administration compensated by one's distrust in elections, i.e., their expectations of electoral fraud.
-Because trust and distrust are assessed by multiple Likert items, conventional methods call for combining the items of each set into separate Likert scales (also known as summated rating scales).
-However, many of the items comprising the trust scale directly oppose items capturing distrust.
-For instance, one item from the trust scale has the respondent report their confidence that votes will be counted as voter's intend, whereas a separate item from the distrust scale has the the respondent report their expectation that many votes will not be counted.
-Positive responses to these two items directly contradict each other, and would thus cancel out.
-
-In light of this, I reverse coded items on the distrust scale and combined responses to the trust in elections scale.
-That is, item responses on the trust scale ranged from 0 ("Not confident at all") to 3 ("Very confident), whereas responses on the distrust scale ranged from 0 ("Not likely at all") to -3 ("Very likely").
-Combining responses in this way resulted in an overall measure of *confidence in elections* to serve as the dependent variable[^10].
-On this scale, positive values reflect higher confidence in elections (e.g., elections will be fair and accurate), negative values reflect greater distrust (i.e., expectation that election fraud will occur), and values closer to zero correspond to an individual's degree of *insecurity*.
-
-## Results
-
-Once trust and distrust were composed into unified variable of confidence in elections, I examined distribution of the dependent variable followed by analysis of the effect of the treatment by comparison of mean differences between experiment conditions.
-To retain a meaningful zero, I rescaled the sum scores to range from -3 to 3[^11] and then superimposed two histograms of confidence scores: one derived from AZ items and another for scores derived from local area items (@fig-dist).
-Doing this is illustrative of the relative distribution of confidence that differed depending on the location of elections referred to in the survey items (e.g., Maricopa County, AZ).
-As expected, the distribution of confidence differed depending on whether survey items pertained to elections in Maricopa County, AZ, or elections within one's local area.
-
-{{< embed notebooks/figures.qmd#fig-dist >}}
-
-Overall, the sample expressed more trust in elections relative to distrust seeing as how the distribution of confidence is largely positive.
-However, there's a clear difference between confidence in Maricopa county, AZ elections and elections within one's local area.
-A paired t-test confirms that this difference was statistically significant, though somewhat small (mean difference $= 0.325$, $95\%$ CI $[0.27, 0.38]$, $t(1286) = 11.61$, $p < .001$).
-Nonetheless, respondents appeared less confident regarding elections in Maricopa County, AZ, but held more confidence in elections administration in their local area.
-This complements previous research that demonstrates a similar bias favorable to one's local area [@stewart2022].
-
-Accordingly, when confidence levels are distinguished by experiment condition, the treatment vignette only had an effect upon survey items pertaining to elections in Maricopa County, AZ.
-Conducting an independent samples t-test (i.e., Welch Two Sample t-test) suggests that the effect of the treatment compared to the control condition is positive and statistically significant.
-
-```{r}
-#| label: tbl-ttest
-#| tbl-cap: "Mean Difference of Treatment Compared to Control Condition"
-#| tbl-colwidths: 80
-#| tbl-pos: H
-
-# conduct two t-tests using `rstatix::t_test`, bind results by row, and pipe
-# into table
-tab_ttest <- dplyr::bind_rows(
-  data |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
-  rstatix::t_test(formula = conf.az.rescaled ~ group,var.equal = F,detailed = T),
-  data |> mutate(group = forcats::fct_relevel(group, "Treatment", after = 0L)) |>
-  rstatix::t_test(formula = conf.lcl.rescaled ~ group,var.equal = F, detailed = T)
-  ) |> 
-  # specify columns and column names
-  select(
-    Diff = estimate,
-    treat_mean = estimate1,
-    control_mean = estimate2,
-    treat_n = n1,
-    control_n = n2,
-    t = statistic,
-    p, df, conf.low, conf.high) |> 
-  mutate(
-    Place = dplyr::case_when(
-      p <= 0.05 ~ "Maricopa County, AZ", 
-      p > 0.05 ~ "Local Area"), 
-    .before = Diff) |> 
-  insight::format_table(stars = T)
-
-# convert from `data.frame` to `tinytable` class object
-tab_ttest <- tinytable::tt(tab_ttest)
-
-# modify column names of table
-colnames(tab_ttest) <- c(
-  "Place",
-  "$\\bar{x}_{diff}$",
-  "$\\bar{x}_{treat}$",
-  "$\\bar{x}_{control}$",
-  "$n_{treat}$",
-  "$n_{control}$",
-  "t",
-  "p",
-  "df",
-  "CI")
-
-# Output using `tinytable` R Package
-tab_ttest |> 
-  tinytable::format_tt(
-    j = 2:6, # specify columns
-    math = T # apply mathmode to specified columns
-  ) |> 
-  tinytable::style_tt(
-    fontsize = 0.75, # fontsize in em units (0.75*default fontsize)
-    align = "lccccccccc"
-    )
-
+```{=typst}
+#show figure: set block(breakable: true)
 ```
 
-The results of @tbl-ttest show that, on a scale ranging from -3 to 3, the effect of the treatment is associated with a $0.20$ average difference in confidence in elections in Maricopa County, AZ, compared to the control group.
-When the dependent variable is centered to have a mean of $0$ and standard deviation of $1$, standardized parameters permit interpretation of the treatment effect in terms of standard deviations; the standardized difference in confidence between treatment and control is $0.16$ (CI $[0.06, 0.27]$).
-
-```{r}
-#| label: fig-coef1
-#| layout-nrow: 2
-#| fig-height: 3.5
-#| fig-pos: 'H'
-#| fig-cap: "Confidence in Elections by Experiment Condition"
-#| fig-subcap: 
-#|   - "Confidence by Treatment Condition"
-#|   - "Trust and Distrust by Treatment Condition"
-
-# coef plot of treatment effect on confidence distinguished by location
-conf.coef1 <- jtools::plot_summs(
-  lm(conf.az.rescaled ~ group, data = data), 
-  lm(conf.lcl.rescaled ~ group, data = data), 
-  center = T, scale = T, transform.response = T,
-  model.names = c("Conf.AZ", "Conf.Local"),
-  coefs = c("Treatment" = "groupTreatment"), 
-  colors = c("red", "black"),
-  point.shape = c(8, 1))+
-  ggplot2::expand_limits(x = c(-0.25, 0.25))+
-  labs(y = "")+
-  theme_bw(base_family = "TeX Gyre Pagella")
-
-# Coef plots of trust and distrust models for AZ and Local items
-conf.coef2 <- jtools::plot_summs(
-  lm(trust.scores.az ~ group, data = data),
-  lm(distrust.scores.az ~ group, data = data),
-  lm(trust.scores.lcl ~ group, data = data),
-  lm(distrust.scores.lcl ~ group, data = data),
-  center = T, scale = T, transform.response = T,
-  model.names = c("Trust.AZ", "Distrust.AZ", "Trust.Local", "Distrust.Local"),
-  coefs = c("Treatment" = "groupTreatment"),
-  colors = c("red", "red", "black", "black"),
-  point.shape = c(8, 8, 1, 1)
-)+
-  ggplot2::expand_limits(x = c(-0.25, 0.25))+
-  labs(y = "")+
-  theme_bw(base_family = "TeX Gyre Pagella")
-
-conf.coef1
-conf.coef2
-
+```{=typst}
+#set block(spacing: 2em)
+#set par(first-line-indent: (
+  amount: 1.5em,
+  all: true),
+  leading: 0.85em,
+  spacing: 1.5em
+  )
 ```
-
-@fig-coef1 displays standard difference estimates of confidence in elections by treatment condition (control condition as reference).
-@fig-coef1-1 displays two models for confidence in elections in Maricopa County, AZ, and one's local area by treatment condition; @fig-coef1-2 displays the same except *confidence* is decomposed into its two components, *trust* and *distrust*.
-These figures merely illustrate the effect of the treatment with respect to the relationship between trust and distrust; ultimately confidence improves.
-
-Confidence in elections was higher among those who read the treatment vignette but remained conditional on whether the survey questions inquired about elections in Maricopa County, AZ.
-This evidence suggests that announcing efforts to recruit veterans and their families to work as election staff and volunteers may increase confidence in elections administration in places outside of one's local area, but may not boost confidence in elections within one's local area.
-
-### 2020 Election Legitimacy Beliefs
-
-I now turn to results examining the effect of the treatment on those who held onto the belief that the 2020 election results were illegitimate.
-First, reviewing responses to items that capture trust in elections, it is easy to recognize the difference between the way 2020 election deniers responded with respect to where elections were held.
-
-{{< embed notebooks/figures.qmd#fig-patch13 >}}
-
-Among those who refuted the 2020 election results, trust in Maricopa County, AZ elections was lower for each item compared to items pertaining to elections within one's local area, regardless of treatment condition.
-However, notably, trust that election technology would be secure received the lowest confidence endorsement overall.
-There was also a notable lack of trust that the voting process would be fair relative to the other items[^12].
-Now the comparative difference in responses between those in the treatment group compared to those in the control group appears substantial for items pertaining to elections in Maricopa County, AZ.
-
-{{< embed notebooks/figures.qmd#fig-patch14 >}}
-
-Concerning distrust among those who refuted the 2020 election results, responses to items assessing one's expectation that election fraud would occur reveal the same pattern.
-Although there is not as stark a disparity between responses of those in the treatment and those in the control, among those in the treatment group, there does appear to be less expectation that election fraud would occur in Maricopa County, AZ.
-Overall, review of responses to trust (@fig-patch13) and distrust survey items (@fig-patch14) does lend credence to the impact of the treatment.
-
-In order to substantiate the overall influence of the treatment on confidence in elections, I regressed the dependent variable confidence on legitimacy beliefs while controlling for partisanship.
-
-```{r}
-#| label: tbl-legit
-#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
-#| tbl-pos: H
-
-# All continuous variables are mean-centered and scaled by 1 standard deviation.
-m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = data)
-m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = data)
-
-tab_legit <- modelsummary::modelsummary(
-  models = list(m1, m2), fmt = 2,
-  estimate = "{estimate} ({std.error}){stars}",
-  statistic = NULL,
-  stars = T,
-  coef_rename = c(
-    "(Intercept)"                        = "(Intercept)",
-    "groupTreatment"                     = "Treatment",
-    "q7Not legitimate"                   = "Not Legitimate",
-    "partyid_3catRepublican"             = "Republican",
-    "partyid_3catDemocrat"               = "Democrat",
-    "groupTreatment x q7Not legitimate"  = "Not Legitimate * Treatment"),
-  gof_map = c("nobs", "r2", "adj.r.squared"),
-  notes = list(
-    "Outcome variable mean-centered and scaled by 1 standard deviation",
-    "+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001"),
-  width = 0.8
-)
-
-colnames(tab_legit) <- c(" ", "Confidence in AZ Elections", "w/Interaction")
-
-tab_legit |> 
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "lcc"
-    ) |>  
-  tinytable::style_tt(i = 6, line = "t") |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
-
-```
-
-The first model in @tbl-legit shows that overall confidence in elections among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
-Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
-Not believing the 2020 election of Joe Biden was legitimate is negatively associated with confidence in elections.
-In order to assess the magnitude of this interaction effect of the treatment on those who refuted the 2020 election results, I ran a model where confidence in elections was regressed on the interaction between the treatment and legitimacy beliefs, controlling for partisanship.
-
-There's a positive interaction effect of the treatment vignette among those who believe that the 2020 election was not legitimate, on average and controlling for partisanship.
-This shows that the treatment effect was most influential upon those who believe the 2020 election results were illegitimate.
-The treatment alone does not reverse such beliefs, but this shows where its influence was most potent.
-
-### Concerns for Violence and Voter Safety
-
-Thus far, publicized announcements that election officials will be targeting veterans in their recruitment efforts does quite a bit to improve confidence in elections outside of one's local area (or, at least for elections held in Maricopa County, AZ), especially among those who believed the 2020 election results were illegitimate.
-While distrust is one concern during the pre-election period, it is not the only concern that arises in anticipation of US elections; the public must feel confident that voters are safe to cast a ballot in person.
-The survey included questions^[See @tbl-4 in Appendix A] that allows me to assess whether those in the treatment condition expressed less concern for violence and more confidence in voter safety compared to those in the control condition.
-```{r}
-#| label: fig-safety-bars
-#| layout-ncol: 1
-#| layout-nrow: 2
-#| fig-cap: "Safety Concerns and Confidence by Treatment Condition"
-#| fig-subcap: 
-#|   - "Concern for Violence while voting in Maricopa County, AZ Elections"
-#|   - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"
-
-# concern for violence by treatment
-bar_q25 <- custom_barplot(
-  data = data, 
-  x = q25, 
-  group = group,
-  subtitle = str_wrap(attr(data$q25, "label"), width = 85)
-  )+
-  theme(text = element_text(family = 'TeX Gyre Pagella'),
-        legend.position = "right")
-
-# confidence in voter safety by treatment
-bar_q26 <- custom_barplot(
-  data = data, 
-  x = q26, 
-  group = group,
-  subtitle = str_wrap(attr(data$q26, "label"), width = 85)
-  )+
-  theme(text = element_text(family = 'TeX Gyre Pagella'),
-        legend.position = "right")
-
-bar_q25
-bar_q26
-
-```
-
-Briefly reviewing @fig-safety-bars, those in the treatment condition felt less concern over the potential for violence compared to those in the control.
-As for confidence in voter safety at election sites, it appears that more respondents in the treatment condition expressed that they were "Very confident" compared to those in the control, by approximately $8$ percentage points.
-
-It would appear that the treatment vignette increased the likelihood that a respondent would select a higher response option compared to those in the control group.
-In order to assess whether that was the case, I conducted an ordered logistic regression on the relevant items using the experimental condition as a dichotomous predictor.
-
-Those in the treatment condition had lower probability to express that they were 'Very' or 'Somewhat' concerned for violence in Maricopa County, AZ Elections, yet higher probability of expressing 'Not too' or 'Not at all' concerned.
-As for confidence in voter safety, moving from treatment to control, the difference in predicted probability of a respondent selecting "Very Confident" was $0.08$.
-@tbl-preds-diff1 and @tbl-preds-diff2 show the significant differences in predicted probabilities at 95$\%$ confidence^[The same models were run for items pertaining to safety concerns in one's local area but results of the treatment were not significantly different from the control.
-See Appendix D for full results table of ordinal logistic regression].
 
@@
 ```{r}
-#| label: tbl-preds-diff1
-#| tbl-colwidths: 80
-#| tbl-cap: "Difference in Predicted Probabilities in Concern for violence, Threats of Violence, or Intimidation between Treatment and Control"
-
-tab_q25_pdiff <- pdiff_q25 |>
-  dplyr::as_tibble() |>
-  dplyr::rename(
-    Violence = group,
-    z = statistic,
-    'Pr(>|z|)' = p.value) |>
-  select(Violence,
-         hypothesis,
-         estimate,
-         std.error,
-         z,
-         'Pr(>|z|)',
-         conf.low,
-         conf.high) |>
-  insight::format_table(stars = T, digits = 3)
-
-tinytable::tt(
-  tab_q25_pdiff,
-  notes = "Results derived from proportional odds logistic regression model.
-Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |>
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "lcccccc"
-    ) |>  
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
-
-```
-
-```{r}
-#| label: tbl-preds-diff2
-#| tbl-colwidths: 80
-#| tbl-cap: "Difference in Predicted Probabilities in Confidence that voters will be safe to vote in-person between Treatment and Control"
-
-tab_q26_pdiff <- pdiff_q26 |>
-  dplyr::as_tibble() |>
-  dplyr::rename('Voter Safety' = group,
-                z = statistic,
-                'Pr(>|z|)' = p.value) |>
-  select('Voter Safety',
-         hypothesis,
-         estimate,
-         std.error,
-         z,
-         'Pr(>|z|)',
-         conf.low,
-         conf.high) |>
-  insight::format_table(stars = T, digits = 4)
-
-tinytable::tt(
-  tab_q26_pdiff,
-  notes = "Results derived from proportional odds logistic regression model.
-Estimates are differences in predicted probabilities transformed from log odds ratios, and represent difference in estimated prediction of choosing a particular response or higher") |>
-  tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
-    align = "lcccccc"
-    ) |>  
-  tinytable::style_tt(i = "notes", fontsize = 0.75) # style font of table notes
-
-```
-
-\newpage
-
-## Conclusion
-
-Publicized announcements that election officials are actively recruiting former military service members to work as election staff and volunteers is associated with greater confidence in elections compared to election worker recruitment announcements that do not explicitly mention targeted efforts to recruit former military service members.
-In addition, such public announcements eased concerns about violence and increased confidence that voters would be safe to vote in person at election sites.
-Of course, the higher levels of confidence in elections and voter safety observed among the treatment group were limited to considerations about elections held in Maricopa County, AZ---presumably beyond one's local area.
-This is to be expected bearing in mind that confidence in elections for one's local area is usually higher than for those beyond.
-Thus, there's already more insecurity concerning elections elsewhere for whatever reason.
-
-One obvious contribution of these results shows that the perceived trustworthiness of elections administration is amendable to generalized impressions about the kind and character of the people who work and volunteer as election staff.
-Whatever election officials do to boost public confidence may be overshadowed by impressions about who is staffing election sites.
-
-It should be noted that these results are limited to one's expectations in anticipation of election night.
-Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
-Moreover, It is yet unclear whether actually encountering and interacting with veterans working as staff or volunteers at election sites does much to improve voter confidence after election night compared to anyone else.
-It may be the case that assumptions that veterans are filling spots as election workers and volunteers simply primes positive expectations as one heads into an election site, potentially improving voters perceptions of their own experience on the way out.
-Further research would be needed to test such an idea.
-
-In general, public confidence appears strongest when the elections under consideration regard those within one's local community.
-Yet, such strong confidence is not generalized outward to the institution of elections administration as a whole.
-Insecurity in the integrity of the electoral process and its administration may be naturally higher for elections that occur further from home.
-Whether that is due to some local favorability bias or some outward negativity bias is hard to say.
-And seeing as how insecurity presents vulnerability, it is perhaps far easier to inspire a general sense of distrust in the process and its administration in places more abstract.
-
-In the anticipatory period prior to national elections, publicized efforts to recruit veterans to work as election staff and volunteers may be a small, but positive, step towards reducing insecurity in elections that occur elsewhere.
-Especially among those who maintained a steadfast degree of distrust in elections.
-Despite a lack of evidence that systematic electoral fraud had occurred in the 2020 election, a substantial proportion of the population were unwilling to affirm the legitimacy of the results.
-However, despite such legitimacy beliefs, most were not consistent as they expressed varying levels of trust in different aspects of elections administration.
-These results say more about the influence that military veterans have among those who are most insecure than it does about the public more generally.
-
-{{< pagebreak >}}
-
-# Appendix A: Survey Experiment Vignettes and Survey Items {.appendix}
-
-## Survey Experiment Vignettes
-
-::::: {#fig-vignettes .content-visible layout-ncol="2" when-format="html" unless-format="pdf"}
-::: {#fig-treatment}
-### Treatment Vignette
-
-| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Army veteran Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-::: {#fig-control}
-### Control Vignette
-
-| **Local Residents Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-Fabricated Article Vignettes utilized as Experimental Stimulus
-:::::
-
-::::: {.content-hidden unless-format="pdf" layout="[0.45, -0.1, 0.45]"}
-::: {#first-column}
-### Treatment Vignette
-
-| **Local Military Veterans Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) — Election officials in Maricopa County, Arizona, announced a program designed to recruit military veterans and their family members from the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Army veteran Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I served my country in the Army, and I want to do my part as a veteran and a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-
-::: {#second-column}
-### Control Vignette
-
-| **Local Residents Recruited for Election Jobs in Maricopa County**
-| 
-|   PHOENIX (AP) —Election officials in Maricopa County, Arizona, announced a program to recruit members of the community to serve as election administrators, including election polling place workers, temporary workers, and full-time staff.
-As the U.S.
-general elections in November near, election officials must fill several thousand temporary positions and hundreds of other open positions to ensure sufficient staffing for the 2024 elections and beyond.
-| 
-|   Jordan Braxton just joined the elections workforce.
-Jordan believes their role is important to ensuring a secure, accurate, and transparent election, “Many places are short on staff this election cycle.
-I want to do my part as a citizen to ensure that everyone trusts the process and the outcome of the election.”
-:::
-:::::
-
-{{< pagebreak >}}
-
-```{r}
-#| label: tbl-4
-#| tbl-cap: "Pre-Treatment Survey Items and Response Options"
-#| tbl-colwidths: [70, 30]
-
-var_label_tab <- function(x){
-    purrr::map(x, ~attr(., "label")) |>
-    purrr::map(~ifelse(purrr::is_null(.), "No label", .)) |>
-    tibble::enframe(name = "var", value = "var_label") |>
-    tidyr::unnest(cols = c(var_label))
-}
-
-Questions <- data |> 
-  dplyr::select(q7, q25, q26, q36, q37) |>
-  dplyr::rename_with(.cols = everything(), .fn = ~snakecase::to_any_case(.,case = "upper_camel")) |> 
-  var_label_tab() |>
-  dplyr::select(Question = var_label) |> 
-  dplyr::pull(Question)
-
-items_responses <- data.frame(
-  Questions = Questions,
-  Response =c(
-    "- Legitimate\n- Not legitimate",
-    "- Very concerned\n- Somewhat concerned\n- Not too concerned\n- Not at all concerned",
-    "- Not at all confident\n- Not too confident\n- Somewhat confident\n- Very confident",
-    "- Very concerned\n- Somewhat concerned\n- Somewhat unconcerned\n- Not at all concerned",
-    "- Not at all confident\n- Not too confident\n- Somewhat confident\n- Very confident")
-)
-
-# wrap in a minipage environment
-minipagify <- function(x) {
-  sprintf(
-    "\\minipage{\\textwidth}%s\\endminipage",
-    sapply(x, mark, "latex")
-  )
-}
-
-# only in LaTeX
-is_latex <- identical(knitr::pandoc_to(), "latex")
-
-tab <- tinytable::tt(items_responses, width = c(0.7, 0.3)) |>
-  tinytable::style_tt(j = c(1,2), fontsize = 0.8, align = "l") |>
-  tinytable::format_tt(markdown = TRUE) |>
-  tinytable::format_tt(j = 2, fn = if (is_latex) minipagify else NULL)
-
-tab
-
-```
-
-\newpage
-
-<!-- {{< pagebreak >}} -->
-
-# Appendix B: Sample Demographics and Balance {.appendix}
-
-## Sample Demographics
-
-The median age was 46 (mean age was $47$), $51.7\%$ ($n = 658$) women, $47\%$ ($n = 598$) men, and approximately $1.3\%$ who identified as either Non-binary/third gender ($n = 7$) or preferred not to say ($n = 9$).
-A large proportion of the sample identified as White or Caucasian ($n = 975, 76.65\%$), while all other non-White respondents comprised $27.83\%$ ($n = 297$) of the sample.
-Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised $13\%$ of the sample; those with either degree at the Associate or Bachelor's level comprised $36.24\%$, while $22.25\%$ had some college but no degree; and $28.46\%$ had either a high school level or equivalent education or less than high school.
-The largest proportion of the sample identified as Democrat at $44.64\%$, followed by Republicans at $42.59\%$.
-The proportion of true Independents^[Independent 'leaners' were grouped into the respective party affiliation in which they lean.] was $12.78\%$.
-
-```{r}
-#| label: sample-desc-setup
-#| tbl-cap: "Sample Demographics"
-#| tbl-pos: 'H'
-
-gtsummary::theme_gtsummary_compact()
-
-# descriptive stats of categorical variables
-# best method for html document
-tbl.desc <- data |>  
-  labelled::set_variable_labels(
-    age_4cat = "Age group",
-    gender_3cat = "Gender",
-    race2 = "Race/Ethnicity",
-    educ_4cat = "Education",
-    partyid_3cat = "Party ID"
-  ) |> 
-  gtsummary::tbl_summary(
-    by = group,
-    include = c(
-    age_4cat, 
-    gender_3cat, 
-    race2,
-    educ_4cat, 
-    partyid_3cat),
-    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
-    missing = "ifany",
-    missing_text = "NA") |> 
-  gtsummary::add_n() |> 
-  gtsummary::add_overall() |> 
-  gtsummary::modify_header(label = "**Demographic**") |> 
-  gtsummary::bold_labels()
-
-```
-
-```{r}
-#| label: tbl-demog
-#| tbl-cap: "Sample Demographics"
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
-
-tbl.desc |> 
-  gtsummary::as_tibble() |> 
-  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
-                "**Control (N = 637)**" = "**Control**  \nN = 637",
-                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
-  dplyr::select(-"**N**") |> 
-  tinytable::tt(theme = "spacing") |> 
-  tinytable::format_tt(markdown = T) |> 
-  tinytable::format_tt(replace = " ") |> 
-  tinytable::style_tt(fontsize = 0.70, align = "lccc")
-
-```
-
-## Test of Random Assignment to Experiment Condition
-
-@tbl-logit shows results of a logistic regression test of random assignment to the treatment group.
-Demographics such as age, gender, race, educational attainment, and party ID are included as predictor variables.
-Note that 19 missing observations were deleted.
-A $\chi^2 = 11.010$, with 15 degrees of freedom and associated p-value > 0.05 ($p = 0.75$) confirms that none of the demographic predictor variables significantly increased the log-odds---in turn, the probability---of being assigned to the treatment group.
-
-```{r}
-#| label: tbl-logit
-#| tbl-cap: "Logistic Regression of Random Assignment to Treatment"
-
-# simple logit of test of random assignment to treatment
-# treatment is DV (treatment = 1, control = 0)
-# demographic variables are IVs
-m1 <- glm(group ~ age_4cat + gender_3cat + race2 + educ_4cat + partyid_3cat, 
-          family = binomial(link = "logit"), data = data)
-
-# use `gtsummary` package to build regression table, then output as tibble
-logit_tab <- gtsummary::tbl_regression(
-    m1,
-    intercept = F,
-    label = list(
-      age_4cat ~"Age",
-      gender_3cat ~ "Gender",
-      race2 ~ "Race/Ethnicity",
-      educ_4cat ~ "Education",
-      partyid_3cat ~ "Party ID")) |>
-  gtsummary::bold_labels() |>
-  # gtsummary::show_header_names()
-  gtsummary::modify_header(
-    label = " ",
-    stat_nevent = "**Treatment N**") |>
-  # output as_tibble
-  gtsummary::as_tibble() |>
-  # omit p.values
-  dplyr::select(-4)
-
-# transform tibble dataframe into `tinytable` and format as markdown
-# replace NA with blank " " (or "-" if desired)
-logit_tab <- tinytable::tt(logit_tab, width = 0.8) |> 
-  tinytable::format_tt(markdown = T) |> 
-  tinytable::format_tt(replace = " ")
-
-# create 2nd table containing only logit model fit statistics
-# using custom function, get logit regression model fit stats... 
-gof_stats <- lrm.gof.stats(m1) |> 
-  # omit certain stats (saves space)
-  dplyr::select(
-    nobs, logLik, df, chisq, P..chi., deviance, null.deviance,
-    -AIC, -BIC, -df.null, -df.residual) |> 
-  # rename column variables
-  dplyr::rename(
-    "Num.Obs"       = "nobs",
-    "Null Deviance" = "null.deviance",
-    "Deviance"      = "deviance",
-    "DF"            = "df",
-    "Log.Lik"       = "logLik",
-    "chisq"       = "chisq",
-    "P(>chisq)"   = "P..chi."
-  ) |> 
-  # pivot into two column long-form dataframe
-  tidyr::pivot_longer(cols = everything(),names_to = " ", values_to = '**log(OR)**') |>
-  # pipe into tinytable
-  tinytable::tt(width = 0.8) |> 
-  # ensure rows with math text are identified and formatted as math (i.e., $..$)
-  tinytable::format_tt(i = c(4,5), j = 1, math = T)
-
-# using `rbind2` function, bind 2nd table at bottom of first table 
-tinytable::rbind2(logit_tab, gof_stats, use_names = F, headers = F) |> 
-  # add horizontal line just above fit stats
-  tinytable::style_tt(i = 26, line = "t", line_color = "black", line_width = 0.1) |>
-  # adjust fontsize of text within table
-  tinytable::style_tt(fontsize = 0.8, align = "lcc") |>
-  # finally, format markdown and blank out any NA fillers
-  tinytable::format_tt(markdown = T, replace = " ")
-
-```
-
-{{< pagebreak >}}
-
-# Appendix C: Polychoric Item and Score Correlations of Trust and Distrust {.appendix}
-
-## Trust and Distrust
-
-Polychoric correlation is a measure of association between two ordered categorical variables each assumed to represent (i.e., indicate, be influenced by) two normally distributed, continuous, latent variables.
-Due to the fact that each item is an ordered categorical variable assumed to represent one of two latent constructs (i.e., trust or distrust, respectively), I examined polychoric correlations between the items used to construct each scale.
-In addition, one set of the trust and distrust items pertained to Maricopa County, AZ, whereas the other set of items were identical except that these items pertained to one's local area.
-
-Since the two sets of items (AZ items and Local items) are, in theory, supposed to capture the same normally distributed continuous latent variables, then the polychoric inter-item correlations should be significantly associated, strong, and in the same direction for the items that measure trust regardless of whether the items pertain to AZ or one's local area  (likewise for distrust).
-Simply, trust/distrust in elections in AZ should strongly and positively be associated with trust/distrust in elections in one's local area.
-
-Additionally, the items that indicate trust should negatively correlate with items that indicate distrust.
-Furthermore, the strength of the negative correlations between trust and distrust should closely approximate if not match.
-
-```{r}
-#| label: fig-polycor
-#| fig-cap: "Polychoric Item Correlation Matrix"
-#| fig-pos: 'h'
-
-# Get polychoric item correlation matrix.
-item.cor <- data |>
-  select(q19:q24, -q23, q28_1:q28_5, q30:q35, -q34, q40_1:q40_5) |> 
-  # ensure factors are ordered factors
-  mutate(across(where(is.factor), ~factor(., ordered = T))) |> 
-  # adjust variable column names of items
-  dplyr::rename(
-    trustvote_az     = q19,
-    trustadmin_az    = q20,
-    truststaff_az    = q21,
-    trustprcss_az    = q22,
-    trusttech_az     = q24,
-    votefraud_az     = q28_1,
-    miscount_az      = q28_2,
-    turnedaway_az    = q28_3,
-    foreigntamp_az   = q28_4,
-    discourage_az    = q28_5,
-    trustvote_lcl    = q30,
-    trustadmin_lcl   = q31,
-    truststaff_lcl   = q32,
-    trustprcss_lcl   = q33,
-    trusttech_lcl    = q35,
-    votefraud_lcl    = q40_1,
-    miscount_lcl     = q40_2,
-    turnedaway_lcl   = q40_3,
-    foreigntamp_lcl  = q40_4,
-    discourage_lcl   = q40_5
-  ) |> 
-  correlation::correlation(
-    select = 
-      c("trustvote_az", "trustadmin_az", "truststaff_az", "trustprcss_az", "trusttech_az",
-        "votefraud_az", "miscount_az", "turnedaway_az", "foreigntamp_az", "discourage_az"),
-    select2 =
-      c("trustvote_lcl", "trustadmin_lcl", "truststaff_lcl", "trustprcss_lcl","trusttech_lcl",
-        "votefraud_lcl", "miscount_lcl", "turnedaway_lcl", "foreigntamp_lcl","discourage_lcl"),
-    method = "polychoric") |>
-  summary()
-
-# plot item correlations
-plot(item.cor) + theme(axis.text.x = element_text(angle = 45, vjust = 0.6))
-
-```
-
-Indeed, this is what is revealed by the correlation matrix (@fig-polycor).
-Trust items correlate positively, strongly, and are significant regardless of location at which the items pertain.
-The same goes for distrust items.
-Also, items meant to measure trust negatively correlate with the items that measure distrust.
-However, the positive correlations are not nearly as high as would be expected supposing that the items are nearly identical theoretical indicators of the same hypothetical constructs, i.e., trust and distrust respectively.
-
-If the items accurately measure trust/distrust in elections regardless of where those elections are said to take place, then positive correlations between the AZ and Local area items should approach perfect correlation as though the same exact questions were asked twice.
-This result, however, suggests that the location of which the survey items pertain (and perhaps other factors) makes a substantial difference in the pattern of responses, but also raises valid questions as to whether the items accurately measure the latent variable constructs in the first place.
-
-Although I do not explicitly assume that the survey instruments perfectly measure the hypothetical constructs of interest (i.e., trust and distrust), perfect measurement is implicitly assumed by the method of combining multiple item responses into a sum or mean composite score.
-
-In short, I expected item responses from the trust and distrust scales to be inversely correlated among the sample, but not mutually exclusive.
-Indeed, this is what I find.
-Polychoric correlations between the trust and distrust items negatively correlate as expected, as does the correlation between the two sum score scales.
-Given the ordinal nature of the variable items, I conducted a Spearman's rank correlation test [@spearman1907] and found a negative correlation of $\rho = -0.49$ ($95\%$ CI \[-0.53, -0.44\]; Kendall's $\tau = -0.39$) between scores on the two scales for the AZ items (For the local item scale score correlation: $\rho = -0.52$, $95\%$ CI \[-0.56, -0.48\]; Kendall's $\tau = -0.39$).
-The negative correlation between the trust and distrust items and scores makes intuitive sense.
-
-{{< pagebreak >}}
-
-# Appendix D: Predicted Probabilities of Safety Concerns by Treatment Condition {.appendix}
-
-```{r}
 #| label: tbl-safety-logit
@@
 #| tbl-cap-location: top
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
 
@@
   coef_map = cm,
-  stars = T,
-  # estimate = c("{estimate}{stars}"),
-  statistic = "conf.int",
+  stars = F,
+  estimate = c("{estimate}, [{conf.low}, {conf.high}]"),
+  statistic = NULL, 
   gof_map = c("nobs", "rmse"),
-  note = list(
-    "Parameter estimate (and confidence intervals) exponentiated to show odds ratios.",
-    "Uncertainty intervals (profile-likelihood) and p-values (two-tailed) computed using a Wald t-distribution approximation")
+  note = "Parameter estimate (and confidence intervals) exponentiated to show odds ratios.",
+  width = c(2, 1, 1)
   )
@@
   tinytable::style_tt(
-    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    fontsize = 0.65 # fontsize of text in table in em units (0.75*default)
     ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75, align = "l")
+  tinytable::style_tt(i = "notes", fontsize = 0.65, align = "l") |> 
+  tinytable::theme_tt(theme = theme_mitex)
 
@@
 #| tbl-cap: "Unit-level predicted probabilities of selecting response or higher comparing experiment condition"
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
 
@@
   dplyr::as_tibble() |> 
+  dplyr::mutate('Pr(>|z|)' = dplyr::case_when(
+    p.value < 0.05 ~ '\\<0.05',
+    p.value < 0.01 ~ '\\<0.01',
+    .default = as.character(p.value)
+  )) |> 
   select(group, condition, 
-         estimate, std.error, statistic,  p.value,
+         estimate, std.error, statistic, 'Pr(>|z|)',
          conf.low, conf.high) |> 
@@
     Violence = group,
-    z = statistic,
-    'Pr(>|z|)' = p.value) |>
+    z = statistic) |>
   insight::format_table(digits = 3)
@@
   tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
+    fontsize = 0.65, # fontsize of text in table in em units (0.75*default)
     align = "llccccc") |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75, align = "l")
+  tinytable::style_tt(i = "notes", fontsize = 0.65, align = "l")
 
@@
 #| tbl-cap: "Unit-level predicted probabilities of selecting response or higher conditional to the Treatment experiment condition"
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
 
@@
     'Voter Safety' = group,
-    z = statistic,
-    'Pr(>|z|)' = p.value) |>
+    z = statistic) |>
   insight::format_table(digits = 3)
@@
   tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
+    fontsize = 0.65, # fontsize of text in table in em units (0.75*default)
     align = "llccccc"
     ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
+  tinytable::style_tt(i = "notes", fontsize = 0.65)
 
 ```
-
-{{< pagebreak >}}
-
-[^1]: I adopt a distinction made between *trustworthiness* and *trust* in elections [@stewart2022].
-The "*worthiness*" of one's trust in the conduct and administration of elections is based on the extent that outcomes of an election reasonably follow the rules prescribed and can be adjudicated as such.
-The public's *trust* in elections, however, is amendable to an indefinite number of factors that may be unrelated to the formal structure or procedures of election administration.
-I can recognize that my car is trustworthy prior to ever driving it because it is structurally sound; I have every reason to deem it *worthy of my trust*.
-However, I don't trust my car because I am sure it is haunted.
-
-[^2]: The vignettes written were based on real news stories
-
-[^3]: To be clear, I conducted an auxiliary regression analysis to examine the relationship between legitimacy beliefs and party ID.
-Results revealed a statistically significant relationship between the two variables and thus omitting either would result in biased estimates.
-
-[^4]: Demographic breakdown of the sample are included in Appendix B.
-
-[^5]: The article vignettes were written and designed by Michael Hanmer Ph.D and myself with input from We the Veterans, a non-profit organization
-
-[^6]: Complete text of treatment and control vignettes are included in Appendix A
-
-[^7]: Note that I refer to the items as either 'AZ items' or 'local items' in order to distinguish the location in which they pertain.
-
-[^8]: Question wording and responses to a selection of survey items are included in Appendix A.
-
-[^9]: See Appendix C for Inter-item correlation analysis.
-
-[^10]: The methodological concerns between the use of (unit weighted) sum or mean scores compared to the use of estimated factor scores for Likert scales composed of multiple Likert items are legion.
-The use of either computed sum scores or estimated factor scores as a general practice is continuously debated [@mcneish2020; @widaman2022; @mcneish2023; @widaman2024], yet there is no general consensus on the most appropriate method generally.
-The use of either appears to largely depend on the researcher's particular research objective, theoretical suppositions, and necessity.
-Another common concern is the inappropriate treatment of ordinal variables as interval which levy strong assumptions, e.g., each item contributes equally to the variable being measured and that ordinal response categories are equidistant as though on an interval scale [@wang2013; for contrast, see @robitzsch2020].
-
-[^11]: This range is mostly arbitrary, as a range from -1 to 1 works much the same.
-When relying on simple sum total score, the scale ranges from -15 to 15.
-So a single point increase from 0 to 1 may reflect a combination of a single "Very confident" response on a trust item compensated by a single "Somewhat likely" response on a distrust item (i.e., 3-2 = 1), or some other equivalent combination.
-Although the use of mean scores would place scores back onto the response scale metric (e.g., from 0 to 3, reflective of "not at all" to "very"), this results in a unipolar scale (from 0 to 3).
-The bipolar scale resulting from the composition of positive trust and negative distrust engenders meaning to zero and negative values.
-In other words, negative values on the scale for confidence in elections hold substantive meaning (e.g., distrust, absent trust), which makes transforming scores to fit a unipolar scale inappropriate.
-
-[^12]: What is interesting to note here is that the first three items regard the more human element of the election administration process, e.g., ensuring accuracy of counts, competence, and commitment of election workers.
-Although a neat line can't really be drawn between the first three and latter two items presented here, it is interesting to see a slight divergence from the usual high confidence placed in local area elections.

### 2025-07-04 src/funs.R

@@ -103,6 +103,26 @@ run_crab <- function(data, row, col){
   return(out)
 }
 
+
+# fun: frequency tibble ::::::::::::::::::::::::::::::::::::::::::::::::::::####
+
+freq_tibble <- function(data, var1, var2) {
+  var1 <- rlang::enquo(var1)
+  var2 <- rlang::enquo(var2)
+  
+  data %>%
+    dplyr::count(!!var1, !!var2) %>%
+    tidyr::spread(!!var2, n, fill = 0) %>%
+    dplyr::mutate(Total := rowSums(dplyr::select(., -!!var1))) %>%
+    dplyr::bind_rows(dplyr::bind_cols(
+      !!rlang::quo_name(var1) := "Total",
+      dplyr::summarize_if(., is.numeric, sum)
+    ))
+}
+
+# example
+# freq_tibble(df, var1 = Gender, var2 = Condition)
+
 # fun: Likert Plots:::::::::::::::::::::::::::::::::::::::::::::::::::::::####
 # To avoid excessive copy/paste, I made a function to create Likert plots
 # it is mostly a wrapper around `ggstats::gglikert`, but with a specific set up
@@ -218,8 +238,7 @@ count_prop <- function(dat, x, drop_na = FALSE, sort = FALSE, pcts = FALSE){
 # count_prop <- function(df, var, sort = FALSE) {
 #   df |>
 #     count({{ var }}, sort = sort) |>
-#     mutate(prop = n / sum(n),
-#            n_miss = sum(is.na({{ var }})))
+#     mutate(prop = n / sum(n))
 # }
 
 
@@ -364,3 +383,50 @@ lrm.gof.stats <- function(x, ...){
 }
 
 # lrm.gof.stats(m1)
+
+# logistic regression model goodness-of-fit statistics
+lrm.gof.stats <- function(model, ...){
+  
+  out <- data.frame(
+    nobs = stats::nobs(model),
+    null.deviance = model$null.deviance,
+    df.null = model$df.null,
+    logLik = as.numeric(stats::logLik(model)),
+    deviance = stats::deviance(model),
+    df.residual = stats::df.residual(model),
+    chisq = as.numeric(model$null.deviance - stats::deviance(model)),
+    df = as.numeric(model$df.null - stats::df.residual(model)),
+    'P(>chi)' = pchisq(q=model$null.deviance - stats::deviance(model),
+                       df = model$df.null - stats::df.residual(model), 
+                       lower.tail = F)
+  )
[…]

### 2025-07-07 response_memo.qmd
revisions

@@
     bibliographystyle: american-political-science-association.csl
-
 ---
@@
 I include excerpts from my revised manuscript in [blue]{.memo-excerpt-inline}.
+Note that an ellipses ($...$) within an excerpt of the manuscript stands in for the main text.
 
@@
 
-# Reviewer 1
+## ***Reviewer 1***---***what is the mechanism here?***
 
-::: {.memo-reviewer}
-***Reviewer 1***---***what is the mechanism here?***: We understand that veterans are generally viewed positively, and that’s part of why this approach might work.
+::: memo-reviewer
+We understand that veterans are generally viewed positively, and that’s part of why this approach might work.
 However, in the data, we don’t see any direct measures of how respondents feel about veterans—there’s no pre-treatment baseline for that.
@@
 
-::: {.memo-excerpt}
+::: memo-excerpt
 ## Limitations
@@
 
-To fully address the above comments of both reviewers, I extended a discussion prior to the conclusion on potential explanations and avenues for future research.
+Also, I extended a discussion prior to the conclusion on potential explanations and avenues for future research.
 
-::: {.memo-excerpt}
+::: memo-excerpt
 ## Discussion
@@
 #sym.dots.h.c
-
 ```
-
 A question lingers about whether some antecedent mechanism transmits (i.e., mediates) the effects of the veteran treatment vignette to the outcome.
@@
 In results presented here, confidence in elections is associated with greater confidence among those in the treatment group, but neither vignette conveys information about the procedures or practices meant to safeguard election integrity; nothing in the treatment suggests to respondents that election integrity would be improved by recruiting veterans.
-Arguably, the results presented here speak to the "emotional pathway" mentioned in @gaudette2025 so long as we assume that there's an inherent appeal to national sentiment (e.g., nationalism, patriotism) by use of veterans[^13].
+Arguably, the results presented here speak to the "emotional pathway" mentioned in @gaudette2025 so long as we assume that there's an inherent appeal to national sentiment (e.g., nationalism, patriotism) by use of veterans[^1].
 Importantly, if the veterans treatment is mediated by stimulation of affect for nation or national identity, then comparable stimulation of national sentiment unrelated to veterans should produce similar results via this "emotional-pathway".
@@
 flag, playing of the national anthem) may not have the same affective influence on confidence in elections.
-
-[^13]: The study by @gaudette2025 included an experiment that examined the contrast between "emotional" versus "informational" appeals on trust in elections and beliefs that election fraud is prevalent.
-Authors presented one of two video messages created by election administration officials in either Virginia or Maricopa County, AZ; the former was "emotions-based" in that it provided little to no information about the voting process or election administration, whereas the latter provided, "...specific information about the processes used to ensure the integrity of the vote with no appeal to emotion or patriotism" [-@gaudette2025, 13].
 
@@
 
-::: {.memo-reviewer}
-***Reviewer 1***---***Hypothesis structure could be clearer***: You present H1 very clearly, which is great.
+## ***Reviewer 1***---***Hypothesis structure could be clearer***
+
+::: memo-reviewer
+You present H1 very clearly, which is great.
 However, later in the paper, there are additional expectations that seem like they could have been articulated as formal hypotheses too—perhaps H2, H3, or even sub-parts like H1a, H1b.
@@
 
-::: {.memo-excerpt}
+::: memo-excerpt
 ## Hypotheses
@@
 ```
-
 > H~2~: Differences in confidence in elections in one's local area and confidence in elections in Maricopa County, AZ, will be smaller among those who are presented with an announcement that election officials are recruiting miilitary service veterans to work as election staff and volunteers compared to those presented with an announcement of recruitment efforts that do not mention military veterans.
@@
 ```
-
 > H~3~: Among those who refute the legitimacy of the 2020 election results, those presented with an announcement that election officials are recruiting veteran service members for election jobs will be associated with greater levels of confidence in elections compared to those presented with an announcement of recruitment efforts that do not mention military veterans.
@@
 
-::: {.memo-reviewer}
-***Reviewer 1***---***Racial dynamics and trust***: This aspect also emerged for me.
+## ***Reviewer 1***---***Racial dynamics and trust***
+
+::: memo-reviewer
+This aspect also emerged for me.
 The sample is mostly white, making it challenging to draw conclusions about how this might work for communities of color.
@@
 
-::: {.memo-excerpt}
+::: memo-excerpt
 The data of the current study is limited in helping to discern whether the treatment garners greater confidence in elections uniformly across different racial or ethnic groups given that the largest proportion of the sample identified their race as White (77%).
@@
 Nevertheless, attitudes about veterans that differ by group may play an important role in determining whether publicized efforts to recruit military veterans boosts confidence in elections uniformly or whether the effect is merely partial to certain segments of the population.
+
+It is definitely plausible that the public, to some unknown extent, associates a particular gender or race, or both, with former and active military members which may, in turn, mediate the effect of the veteran cue.
+Additionally, I can't be sure as to whether respondent's views of the military generalize to attitudes about active service members and veterans.
+However that is a separate question about the source of public opinion about military members themselves beyond the scope of this study.
+
+There's scant research or evidence available to postulate a well-formed theory on the mechanism underlying the expected effects of veterans as a group on attitudes about institutions and processes, rather than on attitudes about persons or groups.
+That is to say, there's not much research on how the public feels, or what they think, about former members of the U.S.
+Armed Forces.
 
@@
 As such, differential effects found among different racial or ethnic groups likely have little to do with attitudes about former or active military service members.] [@nichols2015].
+
+Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly.
+One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S.
+military as an institution in general.
+Some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally.
+In one such study by @tsai2021, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes (e.g., compassion) toward homelessness and PTSD among the veteran population, but not among the general adult population.
+Additionally, Republican partisans tended to show greater support for federal funding for homelessness and PTSD research when the reference population was military veterans.
+That study, however, suggests that the effect of the veteran status cue is sensitive to the topic in question.
+
+Perhaps unsurprisingly, military veterans appear to be uniquely deserving in the eyes of Republican partisans [@tsai2021; @mcdermott2015; @richardson2022].
+As such, military veteran status may qualify favorable attitudes among Republican partisans whereas their regard for other non-veteran groups might otherwise express contempt or indifference.
+This further indicates a need for research to determine an underlying mechanism explaining why, and for whom, veterans incur special favor.
 :::
 
-::: {.memo-reviewer}
-***Reviewer 1***---***How generalizable are these results***: I appreciate your honesty about how the strongest effects appear in Maricopa County, and that we don’t observe the same impact when people consider their own local elections.
+## ***Reviewer 1***---***How generalizable are these results***
+
+::: memo-reviewer
+I appreciate your honesty about how the strongest effects appear in Maricopa County, and that we don’t observe the same impact when people consider their own local elections.
 That’s interesting in itself, but it raises questions—can this approach be effective in other areas?
@@
 
-::: {.memo-excerpt}
+::: memo-excerpt
 The setting of the vignette and specified in survey items might raise additional concerns on whether results are generalizable.
@@
 
-# Reviewer 2
+## ***Reviewer 2***---***Theory***
 
-::: {.memo-reviewer}
-***Reviewer 2***---***Theory***: "The author could be clearer about the puzzle: Why would identifying poll workers as veterans plausibly increase confidence in elections?
+::: memo-reviewer
+The author could be clearer about the puzzle: Why would identifying poll workers as veterans plausibly increase confidence in elections?
 Why might it not?
-The paper gestures at answers---trust, apolitical reputation, shared identity---but doesn’t quite fully develop the competing
-expectations."
+The paper gestures at answers---trust, apolitical reputation, shared identity---but doesn’t quite fully develop the competing expectations.
 :::
 
-In response to [*Reviewer 2*]{.memo-reviewer-inline}'s comments concerning the theory, I restructure the theory section to incorporate the "Why veterans" section, expand on the premises, and add literature that better leads to the expectations.
+In response to [*Reviewer 2*]{.memo-reviewer-inline}'s comments concerning the theory, I restructured the theory section ("**Why veterans**"), expand on the premises, and add literature that better leads to the expectations.
 The text below reflects the revised theory section that better incorporates "Why Veterans".
 
-::: {.memo-excerpt}
-## Why Veterans
+::: memo-excerpt
+## Theory: Why Veterans
+
+The theory tested in this study is this: when the public is informed that election officials are actively recruiting veteran military service members to work at election sites as staff or volunteers, their overall confidence in the fairness, accuracy, and integrity of the electoral process will improve.
+Said another way, insecurities over the integrity of elections administration and safety of voters lessen as the public learns that military service veterans are being sought out by election officials to staff or volunteer at election sites.
+The stimulating influence of veterans as a group in the abstract is expected to counteract distrust and insecurity pertaining to the institution of elections administration, as well as inspire greater trust in the same.
+This prompts an obvious question: why would information about efforts to recruit veterans to work as election staff and volunteers have any influence on confidence in elections?
 
 Election officials don't focus on recruiting people of a particular demographic, status, class, or prestige in order to shore up public trust in elections, and they don't discriminate recruitment efforts based on who the public thinks is best suited to secure elections from fraud.
-
 Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work.
@@
 
-Veteran military service members are, after all, civilians; Civilians with shared (but varied) experience and status of prior military service, but who are no more or less qualified for this civil service^[Research is limited and mixed on whether veterans in general are more inclined, however [@nesbit2011].] than non-veteran civilians.
-To be frank, announcements about concerted efforts to recruit veterans as election workers should not reasonably influence one's trust that votes will be counted more accurately, or that election fraud will not occur; there is no known evidence demonstrating that actually employing veterans as election staff or volunteers further improves the safety, security, and overall integrity of elections in the United States.
-Moreover, there's no known evidence of positive influence on public perceptions of said outcomes when voters encounter military veterans working as staff or volunteers at elections sites.
+There was a sudden push to target veterans for recruitment efforts $...$
 
-Rather, the claim that recruiting veterans to work as election staff and volunteers would improve public confidence in elections emerges as non-profit organizations---mainly comprised of veteran and military family members themselves---operate under, and promote, that assumption [@looker2024; @lawrence2024; @wentling2024].
+One can speculate that $...$
+
+The claim that recruiting veterans to work as election staff and volunteers would improve public confidence in elections emerges as non-profit organizations---mainly comprised of veteran and military family members themselves---operate under, and promote, that assumption [@looker2024; @lawrence2024; @wentling2024].
 Non-profit groups of late have made incredible strides in targeted recruitment efforts under the notion that veterans are uniquely capable, committed, and best fit to serve the needs of the United States as civil servants and volunteers at election sites.
@@
 
-There was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021.
-After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterans2022; @nflfootballoperations2022].
-Prior to that point, young people were sometimes given special mention as targets of election worker recruitment efforts [@powerthepolls2020; @herndon2020].
-Generally, however, recruitment efforts cast a wide net, indiscriminate of who applies [@ross2020; @conde2020].
+Veterans are, after all, civilians.
+Civilians with shared (but varied) experience and status of prior military service, but who are no more or less qualified for this civil service[^3] over non-veteran civilians.
+To be frank, announcements about concerted efforts to recruit veterans as election workers should not reasonably influence one's trust that votes will be counted more accurately, or that election fraud will not occur; there is no known evidence demonstrating that actually employing veterans as election staff or volunteers further improves the safety, security, and overall integrity of elections in the United States.
+Moreover, there's no known evidence of positive influence on public perceptions of said outcomes when voters encounter military veterans working as staff or volunteers at elections sites.
+So, why veterans?
 
-One can speculate that the motivation to associate military veterans with civic engagement and democracy may be intended to counter negative perceptions and impressions given by the proportion of veteran service members arrested for taking part in the events on January 6th [@milton2021; @loewenson2023; @jensen2022a].
-Especially with regard to research demonstrating that willingness to support violent efforts to overturn election results (in support of Trump) is, on average, more common among veterans than among matched samples of non-veterans [@pape2024].
-This is in addition to a strengthened association portrayed in media outlets between military veterans and militias [@steinhauer2020].
-Prior research has substantiated such a connection between veterans and militia groups.
-@cooter2024 notes from her 3-year ethnographic fieldwork among Michigan militia members that, "...approximately 40% of militia leaders and 30% of members had previous military experience.
-Most of these veterans actively sought out such groups, as opposed to being recruited by them" [see also @cooter2013].
-Thus, countering such associations by promoting a different image of veterans to the mass public and veterans alike seems like a reasonable motivation.
-Yet such speculation is just that.
+Two considerations underpin the notion that information about veterans will improve trust and quell distrust in elections.
+First, positive public regard for veterans *in general* is sufficient to elicit greater trust and lower distrust in elections despite the fact that information about veterans as election workers, or even merely information on efforts to recruit veterans, has no bearing on the actual integrity of the electoral process.
 
-The key findings of literature on confidence in elections hardly point to public regard for veterans as a means for improving overall confidence in elections and improving feelings of voter safety at election sites.
-Comparable research finds that confidence in elections is increased through elite rhetoric from fellow partisans affirming legitimacy of elections [@clayton2023], or through the provision of information about the electoral process or other official messaging of election officials themselves [@gaudette2025].
-Neither of the studies just cited, however, consider attitudes or sentiment about veterans as a source for dispelling distrust and improving trust in elections.
-To be clear, there is no immediate "puzzle" in the literature that immediately draws out public sentiment for military veterans as a source for bolstering confidence in elections.
-That being said, the general public perception, attitudes, or even stereotypes about military veterans are significant to consider.
+An underlying assumption here is that there *is* something special about veterans in the eyes of the public generally, but this doesn't include a proposition on exactly *what* that special something might be in theory.
+This is partly due to there being limited research on public opinion about former and active military service members distinguished separately from public opinion about the military as an institution in general.
+Support for the military is generally pretty high, but attitudes about the military in general can't be construed as public opinion about veterans as a group.
+The evidence that can be gathered concerning public regard for military veterans shows that, generally, veterans are perceived favorably among the general public and all groups exaggerate support for veterans in more than one way [@kleykamp2018], suggesting that public regard for veterans is prescribed by widespread social norm.
+Although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023].
 
-It is important to make clear two considerations that underpin the notion that information about veterans will improve trust and quell distrust in elections.
-First, positive public regard for veterans *in general* is sufficient to elicit greater trust and lower distrust in elections despite the fact that information about veterans as election workers, or even merely information on efforts to recruit veterans, has no bearing on the actual integrity of the electoral process.
-An underlying assumption here is that there *is* something special about veterans, but this doesn't include a proposition on exactly *what* that special something might be in theory.
-This is partly due to the limited research available on public regard for veterans, specifically in terms of elucidating an underlying mechanism for such positive favor.
-Moreover, there is limited research on public opinion about former and active military service members distinguished separately from public opinion about the military as an institution in general.
-Endorsement or support of government policies intended to benefit veterans specifically (e.g., federal funding on veteran healthcare) are easy to conflate as interchangeable with public attitudes about veterans as a group in particular.
-This, in turn, permits general expectations of positive influence due to the public's overarching positive regard for veterans, but disallows for expectations regarding how respondents would actually process and interpret a treatment that only mentions efforts to recruit them for election work.
-In short, we are sure that people sustain positive views for veterans generally, but beyond that I make no special effort to propose and examine why that is the case in greater detail.
+Beyond such findings, it is overtly clear that former and active military service members are highly revered nationwide.
+Veteran's day is a national holiday, and custom prescribes thanking military members for their service.
+Calls to "support the troops" are distinct from calls to support the politics the troops are deployed to pursue.
+In 2016, former NFL player Colin Kaepernick went from sitting to kneeling in protest during the playing of the National Anthem upon criticism that sitting in protest implied disrespect for active and former military service members [@haerens2018].
 
-The evidence that can be gathered concerning public regard for military veterans shows that, generally, veterans are perceived favorably among the general public; although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023].
-In my review of the literature, I found only one study which assessed public opinion about veterans specifically and examined whether attitudes differed by group [@kleykamp2018].
-@kleykamp2018 investigated the extent to which positive regard for military veterans in terms of both social distance and deservingness varies across different groups, and the extent to which such support is exaggerated.
-Their research found that levels of support for veterans tended to be predictably lowest, but also most exaggerated, among those who were younger and non-White.
-Determining what groups hold special favor for veterans still leaves it unclear as to what it is about veterans that engenders greater confidence in elections.
-Yet, generally, all groups expressed exaggerated support for veterans in more than one way [@kleykamp2018], suggesting that public regard for veterans is prescribed by widespread social norm.
-
-This is taken together with literature suggesting that public trust in elections is malleable to factors, experiences, events, or phenomena that range in logical relevance to the actual structure or administration of elections.
+Generally high public regard for veterans is taken together with literature suggesting that public trust in elections is malleable to factors that range in logical relevance to the actual structure or administration of elections.
 On the one hand, public trust is, indeed, influenced by information specifically about the processes of conducting elections [@gaudette2025].
 On the other hand, the public's trust in elections is not beholden to the demonstrated *trustworthiness* of the institution of election administration.
-Thus the first consideration is simply that the positive public regard for veterans in general may function sufficiently as a cue to elicit greater trust in elections despite relevance.
+Whether generally high public reverence for veterans is due to injunctive social norms or not, what may be posited is simply that positive regard for veterans in general may function sufficiently as a cue to elicit greater trust in elections despite relevance.
 
-Second, veterans are a particularly potent group where mention of one's veteran status seems to have a positive, calming, or nullifying effect on attitudes.
+Second, veterans are a particularly potent group where mention of one's veteran status seems to have a calming effect on attitudes.
 More so than just the general positive favor afforded to veterans, the group appears to have a somewhat pacifying effect on negative or otherwise contemptible discrimination, prejudice, and social stigma.
-For instance, recent research shows that, during his campaign in the 2020 Democratic Primaries, Pete Buttigieg's military background mitigated discrimination against him when he was presented as a veteran married to a man [@magni2024].
-Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@teigen2013; @hardy2019].
-Moreover, veteran status seems to mitigate or nullify usual stigmas associated with mental illness.
-That is to say, there is negative stigma associated with mental illness [@corrigan2002] and such stigma incurs labor market discrimination [@hipes2016], but evidence suggests that veteran status overrides such stigma and discrimination [@maclean2014].
-Or, in another light, mental illness is seemingly more *understandable* (i.e., permissible) for veterans given the presumptive reasons for their mental strife.
-And media framing as such plays an important role on public perception [@kleykamp2015].
-Relatedly, attitudes about homelessness and PTSD---ranging from perceived causes of homelessness, whether the federal government should dedicate more resources, perceived effectiveness of policies, to compassion for homeless individuals---are generally more favorable for the homeless population among veterans than for the homeless population of general adults [@tsai2021].
+For instance, $...$ Relatedly, attitudes about homelessness and PTSD---ranging from perceived causes of homelessness, whether the federal government should dedicate more resources, perceived effectiveness of policies, to compassion for homeless individuals---are generally more favorable for the homeless population among veterans than for the homeless population of general adults [@tsai2021].
+
 Such effects primarily pertain to attitudes about individual people or groups (e.g., a political candidate, prospective employees, the homeless population).
-The capacity of one's veteran status to pacify prejudice, discrimination, and stigma likely extends out to quell negative and disfavorable attitudes regarding institutions to a similar extent, e.g., distrust.
-
-Given the heightened tensions and electoral anxieties, the expectations surrounding the unique pacifying effect that veterans have on attitudes about individuals or other groups is extended to determine whether a similar effect is found when the target of one's consideration is not just a person or group but the institution of election administration itself.
-Thus the second consideration for "why veterans" are expected to dispel distrust in elections pertains to pacifying effect of negative or disfavorable attitudes observed in relevant literature.
-
-The stimulating influence of veterans as a group in the abstract is expected to counteract distrust and insecurity pertaining to the institution of elections administration, as well as inspire greater confidence in the same.
-There's scant research or evidence available to postulate a well-formed theory on the mechanism underlying the expected effects of veterans as a group on attitudes about institutions and processes, rather than on attitudes about persons or groups.
-What may be posited at best, however, is that distrust and insecurity in elections among the public is expectedly reduced to some extent through generally positive public regard for military veterans and their unique capacity to quell disfavorable attitudes.
+The capacity of one's veteran status to pacify prejudice, discrimination, and stigma likely extends out to veterans as a group in a similar fashion.
+Information that election sites will be staffed by veterans may be enough to ease insecurities about the competence and commitment of the institution to conduct fair and accurate elections.
 :::
 
-::: {.memo-reviewer}
-***Reviewer 2***---***Theory***: Relatedly, I’d encourage the author to more clearly distinguish the scope conditions of this theory.
+## ***Reviewer 2***---***Theory***
+
+::: memo-reviewer
+Relatedly, I’d encourage the author to more clearly distinguish the scope conditions of this theory.
 For instance: Is this paper about elite signaling, political trust, or identity-based persuasion?
@@
 
-In order to be more explicit, I added the following text.
+[**Reviewer 2**]{.memo-reviewer-inline} expressed concern about ambiguity of scope conditions.
+In order to be more explicit, I added text addressing this explicitly under an additional section "**Trust and Distrust in Elections**" where component terms are clarified.
+The revised text also addresses [**Reviewer 2**]{.memo-reviewer-inline}'s related concern about defining the terms of the study.
 
-::: {.memo-excerpt}
-# Theory
-
-This theory is constrained to public confidence in the administration of elections in the United States.
-To be clear, the scope conditions in which this theory applies concern public trust and distrust in election administration in the anticipatory period prior to the election event.
-Moreover, this study is, to a limited extent, indirectly related to public regard about veteran members of the U.S.
-Armed Forces.
-:::
-
-::: {.memo-reviewer}
-***Reviewer 2***---***Theory***: Terms of art should be defined with precision.
+::: memo-reviewer
+Terms of art should be defined with precision.
 What do we mean by “voter confidence”?
@@
 I agree with [**Reviewer 2**]{.memo-reviewer-inline} and apologize for any confusion.
-In order to address the above concern, I inserted the following text which was initially cut from an earlier draft for length.
-This section follows the added text above within the theory section and also further clarifies scope conditions.
+The additional section "**Trust and Distrust in Elections**" is meant to address this concern.
+I inserted the following text which was initially cut from an earlier draft for length.
 
-::: {.memo-excerpt}
+::: memo-excerpt
 ## Trust and Distrust in Elections
 
+This theory is constrained to public confidence in the administration of elections in the United States.
+To be clear, the scope conditions in which this theory applies concern public trust and distrust in election administration in the anticipatory period prior to the election event.
 The theoretical relationship between trust and distrust is important to understand, especially when it comes to the dependent outcome of interest.
-Before going further, it is necessary to explicate the conception *confidence in elections* with respect to trust and distrust.
+Before going further, it is necessary to explicate the conception *confidence in elections* with respect to how I've defined trust and distrust in elections.
 
@@
 Trust is reliance on the veracity of belief in the face of uncertainty.
-Said another way, trust is assured belief dependent on its supposed veracity; a state of certainty with respect to some belief or judgement.
+Said another way, trust is *assured belief* dependent on its supposed veracity; a state of certainty with respect to some belief or judgement.
 It is "assured" because it is one's belief that relies on something rather than nothing.
@@
 
-::: {.memo-reviewer}
-***Reviewer 2***---***Data and Methods***: Manipulation check: Was one included?
+## ***Reviewer 2***---***Data and Methods***
+
+::: memo-reviewer
+Manipulation check: Was one included?
 If not, I’d recommend at least discussing this.
@@
 
-Each reviewer raised similar concerns about the potential for differential effects of the veterans cue.
+My thanks to [**Reviewer 2**]{.memo-reviewer-inline} for noting my failure to mention the manipulation checks included in the initial manuscript.
+I added the excerpt below to the description of the experiment design.
 
-As for [*Reviewer 2's*]{.memo-reviewer-inline} concern about inclusion of a manipulation check, there were no *a priori* expectations regarding how respondents would cognitively interpret the veteran treatment vignette beyond what was stated in the hypotheses.
-That is, there's no reason to suspect that respondents would misinterpret or confuse "military veterans" within the treatment vignette as a reference to some particular racial group or gender, or anything other than veteran military service members.
-
-I can't be sure as to whether respondent's views of the military generalize to attitudes about active service members and veterans, however that is a separate question that deserves further inquiry since it isn't adequately acknowledged or addressed in the literature.
-I included note of this with respect to discussion of the current study.
-
-:::{.memo-excerpt}
-Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly.
-One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S.
-military as an institution in general.
-Some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally.
-In one such study by @tsai2021, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes (e.g., compassion) toward homelessness and PTSD among the veteran population, but not among the general adult population.
-Additionally, Republican partisans tended to show greater support for federal funding for homelessness and PTSD research when the reference population was military veterans.
-That study, however, suggests that the effect of the veteran status cue is sensitive to the topic in question.
-
-Perhaps unsurprisingly, military veterans appear to be uniquely deserving in the eyes of Republican partisans [@tsai2021; @mcdermott2015; @richardson2022].
-As such, military veteran status may qualify favorable attitudes among Republican partisans whereas their regard for other non-veteran groups might otherwise express contempt or indifference.
-This further indicates a need for research to determine an underlying mechanism explaining why veterans incur special favor.
+::: memo-excerpt
+A manipulation check is intended to ensure that the experimental treatment (or manipulation) is received by respondents as the researcher intends.
+Since this experiment required respondents to read a faux news article, inattention or speeding through vignette presentation would undermine results.
+To mitigate this as much as possible, the survey included two items as an attention check prior to presenting either the treatment or control vignette.
+Respondents who failed to select a certain response twice in a row were removed from the survey.
+Upon presentation of either the treatment or control vignette, survey respondents were unable to progress further in the survey until at least 15 seconds had elapsed.
 :::
 
-::: {.memo-reviewer}
-***Reviewer 2***---***Data and Methods***: Relatedly, might respondents be reacting not to “veteran” status *per se*, but to broader schemas about military discipline, patriotism, or law and order?
+That being said, there were no *a priori* expectations regarding how respondents would cognitively interpret the veteran treatment vignette beyond what was stated in the hypotheses.
+That is, there's no reason to suspect that respondents misinterpreted or confused "military veterans" within the treatment vignette as a reference to some particular racial group or gender, or anything other than veteran military service members.
+Moreover, I wrote a name ambiguous to gender and race ("Jordan Braxton") in the vignettes to avoid cues to either as much as possible.
+
+See my response to [**Reviewer 1**]{.memo-reviewer-inline} who raised similar concerns about [**Racial dynamics and trust**]{.memo-reviewer-inline} above.
+
+## ***Reviewer 2***---***Data and Methods***
+
+::: memo-reviewer
+Relatedly, might respondents be reacting not to “veteran” status *per se*, but to broader schemas about military discipline, patriotism, or law and order?
 If so, could this effect be amplified (or diluted) depending on the respondent’s background?
@@
 
-::: {.memo-reviewer}
-***Reviewer 2***---***Data and Methods***: It would be helpful to know more about sample composition.
+## ***Reviewer 2***---***Data and Methods***
+
+::: memo-reviewer
+It would be helpful to know more about sample composition.
 How diverse is the sample in terms of veteran status, ideology, partisanship, and race?
@@
 
-The following brief description of the sample was added prior to description of the survey design under the "Experiment Design and Survey Measures" section.
+The following brief description of the sample was added prior to description of the survey design under the "**Experiment Design and Survey Measures**" section.
 
-::: {.memo-excerpt}
+::: memo-excerpt
 The median age was $46$ (mean age was $47$), $51.13\%$ ($n = 658$) women, $46.46\%$ ($n = 598$) men, and approximately $1.24\%$ who identified as either Non-binary/third gender ($n = 7$) or preferred not to say ($n = 9$).
@@
 The largest proportion of the sample were Democrat at $43.98\%$ ($n = 566$), followed by Republicans at $41.96\%$ ($n = 540$).
-The proportion of true Independents^[Independent 'leaners' were grouped into the respective party affiliation in which they lean.] was $12.59\%$ ($n = 162$).
+The proportion of true Independents[^4] was $12.59\%$ ($n = 162$).
 
@@
 
-::: {.memo-reviewer}
-***Reviewer 2***---***Findings***: The author identifies heterogeneous effects by election level (local vs.
+## ***Reviewer 2***---***Findings***
+
+::: memo-reviewer
+The author identifies heterogeneous effects by election level (local vs.
 national), which is a fascinating and potentially important finding.
@@
 Despite the limitations noted previously, I added the text below in response to [**Reviewer 2**]{.memo-reviewer-inline}'s concerns on the potential substantive significance of the findings.
-This text can be found just prior to the subsection '**2020 Election Legitimacy Beliefs**'.
+This text can be found just prior to the subsection "**2020 Election Legitimacy Beliefs**".
 
-::: {.memo-excerpt}
+::: memo-excerpt
 The veteran cue is potentially compensatory, which supports the second hypothesis (H~2~).
@@
 
-The point of note is that it is *Democratic* candidates who receive *more* of a benefit that comes with veteran status^[Note that the war veteran classification provided benefits to Republican Senate candidates vote share distinct from "common" veterans---i.e., Republican Senate candidates who did not deploy to areas of conflict [@richardson2022].]; the analogy being that it is elections located elsewhere that receive the benefits of the veteran cue whereas local elections do not.
+The point of note is that it is *Democratic* candidates who receive *more* of a benefit that comes with veteran status[^5]; the analogy being that it is elections located elsewhere that receive the benefits of the veteran cue whereas local elections do not.
 Note that the results can't necessarily be read as differing between elections at the local level versus national level, but rather heterogeneous effects differ by elections at the local level and elections in Maricopa County, AZ.
@@
 
-::: {.memo-reviewer}
-***Reviewer 2***---***Findings***: The author should consider the magnitude and directionality of effects in relation to expectations.
+## ***Reviewer 2***---***Findings***
+
+::: memo-reviewer
+The author should consider the magnitude and directionality of effects in relation to expectations.
 For instance: Are the observed changes in confidence substantively meaningful?
@@
 
-While this is understandable, I was unable to compare magnitude of effects between comparable studies due to the differences in measurements used in multiple studies examining confidence in elections.
+While [**Reviewer 2**]{.memo-reviewer-inline}'s concern is understandable, I was unable to compare magnitude of effects between comparable studies due to the differences in measurements used in multiple studies examining confidence in elections.
 To put bluntly, the percentage point differences reported in related experimental studies are mostly incomparable due to substantial differences in measurement.
-I include the following text within the conclusion stating this point.
+I include the following text within the **Discussion** stating this point.
 
-::: {.memo-excerpt}
+::: memo-excerpt
 It is difficult to compare magnitude of effect with other studies given that the item number, item wording, measurement, and computation of confidence in elections is unique across most individual studies to include this one.
@@
 
-::: {.memo-reviewer}
+::: memo-reviewer
 ***Reviewer 2***---***Findings***: I also encourage more discussion of null results.
@@
 {{< pagebreak >}}
+
+[^1]: The study by @gaudette2025 included an experiment that examined the contrast between "emotional" versus "informational" appeals on trust in elections and beliefs that election fraud is prevalent.
+Authors presented one of two video messages created by election administration officials in either Virginia or Maricopa County, AZ; the former was "emotions-based" in that it provided little to no information about the voting process or election administration, whereas the latter provided, "...specific information about the processes used to ensure the integrity of the vote with no appeal to emotion or patriotism" [-@gaudette2025, 13].
+
+[^2]: Note, however, that the sample examined by @nichols2015 was constrained to Texas residents, and the military-related issues concerned, among other things, favor for reinstatement of a military draft, support for allowing undocumented immigrants who live in the U.S.
+to serve in the U.S.
+Armed Forces, and whether undocumented immigrants should be granted U.S.
+citizenship as a result of military service.
+Although the authors found high overall support for the military as an institution, the other military-related attitudes of interest diverge far from public opinion about veterans.
+As such, differential effects found among different racial or ethnic groups likely have little to do with attitudes about former or active military service members.
+
+[^3]: Research is limited and mixed on whether veterans in general are more inclined, however [@nesbit2011].
+
+[^4]: Independent 'leaners' were grouped into the respective party affiliation in which they lean.
+
+[^5]: Note that the war veteran classification provided benefits to Republican Senate candidates vote share distinct from "common" veterans---i.e., Republican Senate candidates who did not deploy to areas of conflict [@richardson2022].

### 2025-07-07 docs/_tex/index.tex
revisions

@@
 \citeproc{ref-coll2024a}{Coll and Clark 2024};
-\citeproc{ref-nadeau1993}{Nadeau and Blais 1993}). Moreover, prior
+\citeproc{ref-nadeau1993}{Nadeau and Blais 1993}). Comparable research
+finds that confidence in elections is increased through elite rhetoric
+from fellow partisans affirming legitimacy of elections
+(\citeproc{ref-clayton2023}{Clayton and Willer 2023}), or through the
+provision of information about the electoral process or other official
+messaging of election officials themselves
+(\citeproc{ref-gaudette2025}{Gaudette et al. 2025}). Moreover, prior
 research has found that evaluation of election workers themselves are an
@@
 confidence in elections, and lessen expectations of electoral fraud. The
-next section elaborates on the proposed theory, terms utilized, and why
-military veterans are of particular interest in this regard.
-
-\section{Theory}\label{theory}
-
-This theory is constrained to public confidence in the administration of
-elections in the United States. To be clear, the scope conditions in
-which this theory applies concern public trust and distrust in election
-administration in the anticipatory period prior to the election event.
-Moreover, this study is, to a limited extent, indirectly related to
-public regard about veteran members of the U.S. Armed Forces.
-
-\subsection{Trust and Distrust in
-Elections}\label{trust-and-distrust-in-elections}
-
-The theoretical relationship between trust and distrust is important to
-understand, especially when it comes to the dependent outcome of
-interest. Before going further, it is necessary to explicate the
-conception \emph{confidence in elections} with respect to trust and
-distrust.
-
-Trust is, after all, merely \emph{belief} held in the face of
-uncertainty. Trust is reliance on the veracity of belief in the face of
-uncertainty. Said another way, trust is assured belief dependent on its
-supposed veracity; a state of certainty with respect to some belief or
-judgement. It is ``assured'' because it is one's belief that relies on
-something rather than nothing. Hence quantitative methods of the
-sciences are replete with things such as \emph{confidence} intervals
-around our estimates. Therefore, I understand trust to refer to the
-state or quality of certainty around one's beliefs or expectations; the
-extent to which one is assured of their expectations regarding what is
-or what will be the case.
-
-The kind of \emph{trust in elections} I refer to concerns the
-expectations drawn up from one's judgement about the functioning of the
-electoral process---the extent to which one is assured in the belief
-that the electoral process will be fairly and accurately administered. I
-follow the notion of public trust in elections explicated by Stewart
-(\citeproc{ref-stewart2022}{2022}),
-
-\begin{quote}
-``Public trust in U.S. election institutions comes down to whether
-voting machines accurately record votes, voter registration systems
-accurately record those eligible to vote, geographic information systems
-accurately assign voters to voting districts, election-night reporting
-systems accurately aggregate and communicate election results to
-officials and the public, and postelection audit and canvassing
-procedures proceed impartially and in accordance with the law.''
-(\citeproc{ref-stewart2022}{2022, 236})
-\end{quote}
-
-That being said, I also account for expectations of electoral fraud,
-which I refer to as \emph{distrust} in elections distinguished from
-trust. Distrust in this sense is also a belief, an expectation, about
-the anticipated functioning of the process. Note, however, that the
-prefix \emph{dis-} in distrust implies ``apart'', ``lack of, not'' or
-``opposite''. Conventionally, distrust is defined simply as the absence
-of trust, thus denoting a simple inverse and mutually exclusive
-relationship. However, as it concerns the psychology of an individual,
-\emph{a lack of trust doesn't necessarily imply opposite expectations or
-opposing beliefs}. In particular, a lack of trust that votes will be
-accurately recorded, etc., doesn't necessarily imply inversely
-proportional expectations that electoral fraud will occur. In other
-words, although the relationship between trust and distrust is inverse,
-this relationship is not mutually exclusive.
-
-A person who is certain that electoral fraud will occur clearly lacks
-trust in elections; an expectation that electoral fraud will occur
-necessarily implies a lack of trust in elections regardless of positive
-expressions of trust. However, the reverse isn't also true; expressing a
-lack of trust in elections \emph{doesn't necessarily imply} an
-expectation that electoral fraud will occur. Rather, a lack of trust
-implies an absence of assurance in the belief that the process will be
-conducted fairly and accurately---a lacking quality of certainty around
-said belief. An absence of such assurance denotes a state of
-\emph{insecurity}. Other sources of uncertainty may challenge a person's
-confidence regarding the integrity of elections independent from
-anything that would lead them to believe electoral fraud will occur or
-has occurred. However my use of distrust refers to the assured belief
-that the outcome will be invalid---that outcomes will be independent of
-the process as prescribed, thus rendering outcomes as arbitrary.
-Specifically, distrust implies assurance in the belief that electoral
-fraud will occur.
-
-As such, trust and distrust represent opposing degrees of confidence
-along the same spectrum. However, despite the inherent contrast, one can
-hold both positive degrees of trust and distrust, feeling relatively
-confident in both respects. Accordingly, \emph{equivalent degrees of
-trust and distrust cancel out}, rendering one relatively more insecure
-about their expectations of the future despite the fact that they may
-report feeling confident in either direction respectively. When trust
-and distrust are considered reflective of one's confidence about future
-expectations, then both can be placed along the same spectrum.
-Therefore, a lack of confidence denotes insecurity.
-
-This means that a person's baseline level of confidence in elections
-must take into account their present degree of distrust---i.e., their
-expectations of electoral fraud. Something may cause a person to have
-greater expectations that election fraud will occur, which in turn will
-always lower their trust in elections. In contrast, a person's trust in
-the integrity of the electoral process is reduced by the extent to which
-they expect that electoral fraud will occur.
-
-Thus, it follows that a person distrusts the integrity of the electoral
-process to the extent that they are to some extent certain that
-electoral fraud will occur or has occurred. They are, perhaps, poised to
-discount election results as invalid or illegitimate in advance. Either
-way, both trust and distrust refer to some positive degree of confidence
-(i.e., assurance) regarding one's expectations. They are distinguished
-by reference to either the normative idea about what \emph{should} come
-about, or what is \emph{supposed} to come about given the logical
-structure and integrity of the process. If the structure and integrity
-of some process is coherent and secure, respectively, then the outcome
-that follows will be valid. Should the integrity of that process be
-damaged or opaque, then the process becomes vulnerable and validity of
-the results are open to challenge. With respect to the administration of
-U.S. elections, the confident voter expects that votes will be counted
-as voters intend, election staff will competently administer elections,
-election technology will be secure from nefarious tampering, and that
-the process will be fair for all involved.
-
-\subsection{Why Veterans}\label{why-veterans}
+next section elaborates on the proposed theory and why military veterans
+are of particular interest in this regard.
+
+\subsection{Theory: Why Veterans}\label{theory-why-veterans}
+
+The theory tested in this study is this: when the public is informed
+that election officials are actively recruiting veteran military service
+members to work at election sites as staff or volunteers, their overall
+confidence in the fairness, accuracy, and integrity of the electoral
+process will improve. Said another way, insecurities over the integrity
+of elections administration and safety of voters lessen as the public
+learns that military service veterans are being sought out by election
+officials to staff or volunteer at election sites. The stimulating
+influence of veterans as a group in the abstract is expected to
+counteract distrust and insecurity pertaining to the institution of
+elections administration, as well as inspire greater trust in the same.
+This prompts an obvious question: why would information about efforts to
+recruit veterans to work as election staff and volunteers have any
+influence on confidence in elections?
 
@@
 based on who the public thinks is best suited to secure elections from
-fraud.
-
-Election officials are likely to be agnostic as to who dedicates their
-time to civil service such as election work. Especially since staffing
-has been an issue since at least the 1990s
+fraud. Election officials are likely to be agnostic as to who dedicates
+their time to civil service such as election work. Especially since
+staffing has been an issue since at least the 1990s
 (\citeproc{ref-ferrer2024}{Ferrer, Thompson, and Orey 2024};
@@
 vacancies.
-
-Veteran military service members are, after all, civilians; Civilians
-with shared (but varied) experience and status of prior military
-service, but who are no more or less qualified for this civil
-service\footnote{Research is limited and mixed on whether veterans in
-  general are more inclined, however (\citeproc{ref-nesbit2011}{Nesbit
-  and Reingold 2011}).} than non-veteran civilians. To be frank,
-announcements about concerted efforts to recruit veterans as election
-workers should not reasonably influence one's trust that votes will be
-counted more accurately, or that election fraud will not occur; there is
-no known evidence demonstrating that actually employing veterans as
-election staff or volunteers further improves the safety, security, and
-overall integrity of elections in the United States. Moreover, there's
-no known evidence of positive influence on public perceptions of said
-outcomes when voters encounter military veterans working as staff or
-volunteers at elections sites.
-
-Rather, the claim that recruiting veterans to work as election staff and
-volunteers would improve public confidence in elections emerges as
-non-profit organizations---mainly comprised of veteran and military
-family members themselves---operate under, and promote, that assumption
-(\citeproc{ref-lawrence2024}{Lawrence 2024};
-\citeproc{ref-looker2024}{Looker 2024};
-\citeproc{ref-wentling2024}{Wentling 2024}). Non-profit groups of late
-have made incredible strides in targeted recruitment efforts under the
-notion that veterans are uniquely capable, committed, and best fit to
-serve the needs of the United States as civil servants and volunteers at
-election sites. Indeed, this study can be seen as a test of a particular
-assumption that veterans have about themselves---the assumption that
-their mere presence and civic engagement will inspire confidence in
-elections among the public.
 
@@
 
-The key findings of literature on confidence in elections hardly point
-to public regard for veterans as a mechanism for the theoretical
-expectations of improving overall confidence in elections and improving
-feelings of voter safety at election sites. Comparable research finds
-that confidence in elections is increased through elite rhetoric from
-fellow partisans affirming legitimacy of elections
-(\citeproc{ref-clayton2023}{Clayton and Willer 2023}), or through the
-provision of information about the electoral process or other official
-messaging of election officials themselves
-(\citeproc{ref-gaudette2025}{Gaudette et al. 2025}). Neither of the
-studies just cited, however, consider attitudes or sentiment about
-veterans as a source for dispelling distrust and improving trust in
-elections. To be clear, there is no immediate ``puzzle'' in the
-literature that immediately draws out public sentiment for military
-veterans as a source for bolstering confidence in elections. That being
-said, the general public perception, attitudes, or even stereotypes
-about military veterans are significant to consider.
-
-It is important to make clear two considerations that underpin the
-notion that information about veterans will improve trust and quell
-distrust in elections. First, positive public regard for veterans
-\emph{in general} is sufficient to elicit greater trust and lower
-distrust in elections despite the fact that information about veterans
-as election workers, or even merely information on efforts to recruit
-veterans, has no bearing on the actual integrity of the electoral
-process. An underlying assumption here is that there \emph{is} something
-special about veterans, but this doesn't include a proposition on
-exactly \emph{what} that special something might be in theory. This is
-partly due to the limited research available on public regard for
-veterans, specifically in terms of elucidating an underlying mechanism
-for such positive favor. Moreover, there is limited research on public
-opinion about former and active military service members distinguished
-separately from public opinion about the military as an institution in
-general. Endorsement or support of government policies intended to
-benefit veterans specifically (e.g., federal funding on veteran
-healthcare) are easy to conflate as interchangeable with public
-attitudes about veterans as a group in particular. This, in turn,
-permits general expectations of positive influence due to the public's
-overarching positive regard for veterans, but disallows for expectations
-regarding how respondents would actually process and interpret a
-treatment that only mentions efforts to recruit them for election work.
-In short, we are sure that people sustain positive views for veterans
-generally, but beyond that I make no special effort to propose and
-examine why that is the case in greater detail.
-
-The evidence that can be gathered concerning public regard for military
-veterans shows that, generally, veterans are perceived favorably among
-the general public; although military recruitment shows a downward trend
-as of late, public perceptions of veterans are overwhelmingly positive
-(\citeproc{ref-kleykamp2023}{Kleykamp, Schwam, and Wenig 2023}). In my
-review of the literature, I found only one study which assessed public
-opinion about veterans specifically and examined whether attitudes
-differed by group (\citeproc{ref-kleykamp2018}{Kleykamp, Hipes, and
-MacLean 2018}). Kleykamp, Hipes, and MacLean
-(\citeproc{ref-kleykamp2018}{2018}) investigated the extent to which
-positive regard for military veterans in terms of both social distance
-and deservingness varies across different groups, and the extent to
-which such support is exaggerated. Their research found that levels of
-support for veterans tended to be predictably lowest, but also most
-exaggerated, among those who were younger and non-White. Determining
-what groups hold special favor for veterans still leaves it unclear as
-to what it is about veterans that engenders greater confidence in
-elections. Yet, generally, all groups expressed exaggerated support for
-veterans in more than one way (\citeproc{ref-kleykamp2018}{Kleykamp,
-Hipes, and MacLean 2018}), suggesting that public regard for veterans is
-prescribed by widespread social norm.
-
-This is taken together with literature suggesting that public trust in
-elections is malleable to factors, experiences, events, or phenomena
-that range in logical relevance to the actual structure or
+The claim that recruiting veterans to work as election staff and
+volunteers would improve public confidence in elections emerges as
+non-profit organizations---mainly comprised of veteran and military
+family members themselves---operate under, and promote, that assumption
+(\citeproc{ref-lawrence2024}{Lawrence 2024};
+\citeproc{ref-looker2024}{Looker 2024};
+\citeproc{ref-wentling2024}{Wentling 2024}). Non-profit groups of late
+have made incredible strides in targeted recruitment efforts under the
+notion that veterans are uniquely capable, committed, and best fit to
+serve the needs of the United States as civil servants and volunteers at
+election sites. Indeed, this study can be seen as a test of a particular
+assumption that veterans have about themselves---the assumption that
+their mere presence and civic engagement will inspire confidence in
+elections among the public.
+
+Veterans are, after all, civilians. Civilians with shared (but varied)
+experience and status of prior military service, but who are no more or
+less qualified for this civil service\footnote{Research is limited and
+  mixed on whether veterans in general are more inclined, however
+  (\citeproc{ref-nesbit2011}{Nesbit and Reingold 2011}).} over
+non-veteran civilians. To be frank, announcements about concerted
+efforts to recruit veterans as election workers should not reasonably
+influence one's trust that votes will be counted more accurately, or
+that election fraud will not occur; there is no known evidence
+demonstrating that actually employing veterans as election staff or
+volunteers further improves the safety, security, and overall integrity
+of elections in the United States. Moreover, there's no known evidence
+of positive influence on public perceptions of said outcomes when voters
+encounter military veterans working as staff or volunteers at elections
+sites. So, why veterans?
+
+Two considerations underpin the notion that information about veterans
+will improve trust and quell distrust in elections. First, positive
+public regard for veterans \emph{in general} is sufficient to elicit
+greater trust and lower distrust in elections despite the fact that
+information about veterans as election workers, or even merely
+information on efforts to recruit veterans, has no bearing on the actual
+integrity of the electoral process.
+
+An underlying assumption here is that there \emph{is} something special
+about veterans in the eyes of the public generally, but this doesn't
+include a proposition on exactly \emph{what} that special something
+might be in theory. This is partly due to there being limited research
+on public opinion about former and active military service members
+distinguished separately from public opinion about the military as an
+institution in general. Support for the military is generally pretty
+high, but attitudes about the military in general can't be construed as
+public opinion about veterans as a group. The evidence that can be
+gathered concerning public regard for military veterans shows that,
+generally, veterans are perceived favorably among the general public and
+all groups express exaggerated support for veterans in more than one way
+(\citeproc{ref-kleykamp2018}{Kleykamp, Hipes, and MacLean 2018}),
+suggesting that public regard for veterans is prescribed by widespread
+social norm. Although military recruitment shows a downward trend as of
+late, public perceptions of veterans are overwhelmingly positive
+(\citeproc{ref-kleykamp2023}{Kleykamp, Schwam, and Wenig 2023}).
+
+Beyond such findings, it is overtly clear that former and active
+military service members are highly revered nationwide. Veteran's day is
+a national holiday, and custom prescribes thanking military members for
+their service. Calls to ``support the troops'' are distinct from calls
+to support the politics the troops are deployed to pursue. In 2016,
+former NFL player Colin Kaepernick went from sitting to kneeling in
+protest during the playing of the National Anthem upon criticism that
+sitting in protest implied disrespect for active and former military
+service members (\citeproc{ref-haerens2018}{Haerens 2018}).
+
+Generally high public regard for veterans is taken together with
+literature suggesting that public trust in elections is malleable to
+factors that range in logical relevance to the actual structure or
 administration of elections. On the one hand, public trust is, indeed,
@@
 demonstrated \emph{trustworthiness} of the institution of election
-administration. Thus the first consideration is simply that the positive
-public regard for veterans in general may function sufficiently as a cue
-to elicit greater trust in elections despite relevance.
+administration. Whether generally high public reverence for veterans is
+due to injunctive social norms or not, what may be posited is simply
+that positive regard for veterans in general may function sufficiently
+as a cue to elicit greater trust in elections despite relevance.
 
 Second, veterans are a particularly potent group where mention of one's
-veteran status seems to have a positive, calming, or nullifying effect
-on attitudes. More so than just the general positive favor afforded to
-veterans, the group appears to have a somewhat pacifying effect on
-negative or otherwise contemptible discrimination, prejudice, and social
-stigma. For instance, recent research shows that, during his campaign in
-the 2020 Democratic Primaries, Pete Buttigieg's military background
-mitigated discrimination against him when he was presented as a veteran
-married to a man (\citeproc{ref-magni2024}{Magni and Reynolds 2024}).
-Similar research has also found that a candidate's veteran status
-affords them better evaluations regarding competency in particular issue
-areas (e.g., war competence) (\citeproc{ref-hardy2019}{Hardy et al.
-2019}; \citeproc{ref-teigen2013}{Teigen 2013}). Moreover, veteran status
-seems to mitigate or nullify usual stigmas associated with mental
-illness. That is to say, there is negative stigma associated with mental
-illness (\citeproc{ref-corrigan2002}{Corrigan et al. 2002}) and such
-stigma incurs labor market discrimination
-(\citeproc{ref-hipes2016}{Hipes et al. 2016}), but evidence suggests
-that veteran status overrides such stigma and discrimination
-(\citeproc{ref-maclean2014}{MacLean and Kleykamp 2014}). Or, in another
-light, mental illness is seemingly more \emph{understandable} (i.e.,
-permissible) for veterans given the presumptive reasons for their mental
-strife. And media framing as such plays an important role on public
-perception (\citeproc{ref-kleykamp2015}{Kleykamp and Hipes 2015}).
-Relatedly, attitudes about homelessness and PTSD---ranging from
-perceived causes of homelessness, whether the federal government should
-dedicate more resources, perceived effectiveness of policies, to
-compassion for homeless individuals---are generally more favorable for
-the homeless population among veterans than for the homeless population
-of general adults (\citeproc{ref-tsai2021}{Tsai et al. 2021}). Such
-effects primarily pertain to attitudes about individual people or groups
-(e.g., a political candidate, prospective employees, the homeless
+veteran status seems to have a calming effect on attitudes. More so than
+just the general positive favor afforded to veterans, the group appears
+to have a somewhat pacifying effect on negative or otherwise
+contemptible discrimination, prejudice, and social stigma. For instance,
+recent research shows that, during his campaign in the 2020 Democratic
+Primaries, Pete Buttigieg's military background mitigated discrimination
+against him when he was presented as a veteran married to a man
+(\citeproc{ref-magni2024}{Magni and Reynolds 2024}). Similar research
+has also found that a candidate's veteran status affords them better
+evaluations regarding competency in particular issue areas (e.g., war
+competence) (\citeproc{ref-hardy2019}{Hardy et al. 2019};
+\citeproc{ref-teigen2013}{Teigen 2013}). Moreover, veteran status seems
+to mitigate or nullify usual stigmas associated with mental illness.
+That is to say, there is negative stigma associated with mental illness
+(\citeproc{ref-corrigan2002}{Corrigan et al. 2002}) and such stigma
+incurs labor market discrimination (\citeproc{ref-hipes2016}{Hipes et
+al. 2016}), but evidence suggests that veteran status overrides such
+stigma and discrimination (\citeproc{ref-maclean2014}{MacLean and
+Kleykamp 2014}). Or, in another light, mental illness is seemingly more
+\emph{understandable} (i.e., permissible) for veterans given the
+presumptive reasons for their mental strife. And media framing as such
+plays an important role on public perception
+(\citeproc{ref-kleykamp2015}{Kleykamp and Hipes 2015}). Relatedly,
+attitudes about homelessness and PTSD---ranging from perceived causes of
+homelessness, whether the federal government should dedicate more
+resources, perceived effectiveness of policies, to compassion for
+homeless individuals---are generally more favorable for the homeless
+population among veterans than for the homeless population of general
+adults (\citeproc{ref-tsai2021}{Tsai et al. 2021}).
+
+Such effects primarily pertain to attitudes about individual people or
+groups (e.g., a political candidate, prospective employees, the homeless
 population). The capacity of one's veteran status to pacify prejudice,
-discrimination, and stigma likely extends out to quell negative and
-disfavorable attitudes regarding institutions to a similar extent, e.g.,
-distrust.
-
-Given the heightened tensions and electoral anxieties, the expectations
-surrounding the unique pacifying effect that veterans have on attitudes
-about individuals or other groups is extended to determine whether a
-similar effect is found when the target of one's consideration is not
-just a person or group but the institution of election administration
-itself. Thus the second consideration for ``why veterans'' are expected
-to dispel distrust in elections pertains to pacifying effect of negative
-or disfavorable attitudes observed in relevant literature.
-
-The stimulating influence of veterans as a group in the abstract is
-expected to counteract distrust and insecurity pertaining to the
-institution of elections administration, as well as inspire greater
-confidence in the same. There's scant research or evidence available to
-postulate a well-formed theory on the mechanism underlying the expected
-effects of veterans as a group on attitudes about institutions and
-processes, rather than on attitudes about persons or groups. What may be
-posited at best, however, is that distrust and insecurity in elections
-among the public is expectedly reduced to some extent through generally
-positive public regard for military veterans and their unique capacity
-to quell disfavorable attitudes.
+discrimination, and stigma likely extends out to veterans as a group in
+a similar fashion. Information that election sites will be staffed by
+veterans may be enough to ease insecurities about the competence and
+commitment of the institution to conduct fair and accurate elections.
+
+\subsection{Trust and Distrust in
+Elections}\label{trust-and-distrust-in-elections}
+
+This theory is constrained to public confidence in the administration of
+elections in the United States. To be clear, the scope conditions in
+which this theory applies concern public trust and distrust in election
+administration in the anticipatory period prior to the election event.
+The theoretical relationship between trust and distrust is important to
+understand, especially when it comes to the dependent outcome of
+interest. Before going further, it is necessary to explicate the
+conception \emph{confidence in elections} with respect to how I've
+defined trust and distrust in elections.
+
+Trust is, after all, merely \emph{belief} held in the face of
+uncertainty. Trust is reliance on the veracity of belief in the face of
+uncertainty. Said another way, trust is \emph{assured belief} dependent
+on its supposed veracity; a state of certainty with respect to some
+belief or judgement. It is ``\emph{assured}'' because it is one's belief
+that relies on something rather than nothing. Hence quantitative methods
+of the sciences are replete with things such as \emph{confidence}
+intervals around our estimates. Therefore, I understand trust to refer
+to the state or quality of certainty around one's beliefs or
+expectations; the extent to which one is assured of their expectations
+regarding what is or what will be the case.
+
+The kind of \emph{trust in elections} I refer to concerns the
+expectations drawn up from one's judgement about the functioning of the
+electoral process---the extent to which one is assured in the belief
+that the electoral process will be fairly and accurately administered. I
+follow the notion of public trust in elections explicated by Stewart
+(\citeproc{ref-stewart2022}{2022}),
+
+\begin{quote}
+``Public trust in U.S. election institutions comes down to whether
+voting machines accurately record votes, voter registration systems
+accurately record those eligible to vote, geographic information systems
+accurately assign voters to voting districts, election-night reporting
+systems accurately aggregate and communicate election results to
+officials and the public, and postelection audit and canvassing
+procedures proceed impartially and in accordance with the law.''
+(\citeproc{ref-stewart2022}{2022, 236})
+\end{quote}
+
+That being said, I also account for expectations of electoral fraud,
+which I refer to as \emph{distrust} in elections distinguished from
+trust. Distrust in this sense is also a belief, an expectation, about
+the anticipated functioning of the process. Note, however, that the
+prefix \emph{dis-} in distrust implies ``apart'', ``lack of, not'' or
+``opposite''. Conventionally, distrust is defined simply as the absence
+of trust, thus denoting a simple inverse and mutually exclusive
+relationship. However, as it concerns the psychology of an individual,
+\emph{a lack of trust doesn't necessarily imply opposite expectations or
+opposing beliefs}. In particular, a lack of trust that votes will be
+accurately recorded, etc., doesn't necessarily imply inversely
+proportional expectations that electoral fraud will occur. In other
+words, although the relationship between trust and distrust is inverse,
+this relationship is not mutually exclusive.
+
+A person who is certain that electoral fraud will occur clearly lacks
+trust in elections; an expectation that electoral fraud will occur
+necessarily implies a lack of trust in elections regardless of positive
+expressions of trust. However, the reverse isn't also true; expressing a
+lack of trust in elections \emph{doesn't necessarily imply} an
+expectation that electoral fraud will occur. Rather, a lack of trust
+implies an absence of assurance in the belief that the process will be
+conducted fairly and accurately---a lacking quality of certainty around
+said belief. An absence of such assurance denotes a state of
+\emph{insecurity}. Other sources of uncertainty may challenge a person's
+confidence regarding the integrity of elections independent from
+anything that would lead them to believe electoral fraud will occur or
+has occurred. However my use of distrust refers to the assured belief
+that the outcome will be invalid---that outcomes will be independent of
+the process as prescribed, thus rendering outcomes as arbitrary.
+Specifically, distrust implies assurance in the belief that electoral
+fraud will occur.
+
+As such, trust and distrust represent opposing degrees of confidence
+along the same spectrum. However, despite the inherent contrast, one can
+hold both positive degrees of trust and distrust, feeling relatively
+confident in both respects. Accordingly, \emph{equivalent degrees of
+trust and distrust cancel out}, rendering one relatively more insecure
+about their expectations of the future despite the fact that they may
+report feeling confident in either direction respectively. When trust
+and distrust are considered reflective of one's confidence about future
+expectations, then both can be placed along the same spectrum.
+Therefore, a lack of confidence denotes insecurity.
+
+This means that a person's baseline level of confidence in elections
+must take into account their present degree of distrust---i.e., their
+expectations of electoral fraud. Something may cause a person to have
+greater expectations that election fraud will occur, which in turn will
+always lower their trust in elections. In contrast, a person's trust in
+the integrity of the electoral process is reduced by the extent to which
+they expect that electoral fraud will occur.
+
+Thus, it follows that a person distrusts the integrity of the electoral
+process to the extent that they are to some extent certain that
+electoral fraud will occur or has occurred. They are, perhaps, poised to
+discount election results as invalid or illegitimate in advance. Either
+way, both trust and distrust refer to some positive degree of confidence
+(i.e., assurance) regarding one's expectations. They are distinguished
+by reference to either the normative idea about what \emph{should} come
+about, or what is \emph{supposed} to come about given the logical
+structure and integrity of the process. If the structure and integrity
+of some process is coherent and secure, respectively, then the outcome
+that follows will be valid. Should the integrity of that process be
+damaged or opaque, then the process becomes vulnerable and validity of
+the results are open to challenge. With respect to the administration of
+U.S. elections, the confident voter expects that votes will be counted
+as voters intend, election staff will competently administer elections,
+election technology will be secure from nefarious tampering, and that
+the process will be fair for all involved.
 
@@
 
-The survey included two items as an attention check prior to presenting
-either the treatment or control vignette. Respondents who failed to
-select a certain response twice in a row were removed from the survey.
-Upon presentation of either the treatment or control vignette, survey
+A manipulation check is intended to ensure that the experimental
+treatment (or manipulation) is received by respondents as the researcher
+intends. Since this experiment required respondents to read a faux news
+article, inattention or speeding through vignette presentation would
+undermine results. To mitigate this as much as possible, the survey
+included two items as an attention check prior to presenting either the
+treatment or control vignette. Respondents who failed to select a
+certain response twice in a row were removed from the survey. Upon
+presentation of either the treatment or control vignette, survey
 respondents were unable to progress further in the survey until at least
@@
 
+\phantomsection\label{cell-fig-coef1}
 \begin{figure}[H]
@@
 
-\begin{minipage}{\linewidth}
-
-\subcaption{\label{fig-coef1-1}Confidence by Treatment Condition}
-
 \centering{
@@
 
-\end{minipage}%
-\newline
-\begin{minipage}{\linewidth}
-
-\subcaption{\label{fig-coef1-2}Trust and Distrust by Treatment
-Condition}
+\end{figure}%
+
+Figure~\ref{fig-coef1} displays standard difference estimates of two
+models for confidence in elections in Maricopa County, AZ, and one's
+local area by treatment condition (control condition as reference).
+
+\phantomsection\label{cell-fig-coef2}
+\begin{figure}[H]
+
+\caption{\label{fig-coef2}Trust and Distrust by Treatment Condition}
 
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-coef1-2.png}}
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-coef2-1.png}}
 
@@
 
-\end{minipage}%
-
 \end{figure}%
 
-Figure~\ref{fig-coef1} displays standard difference estimates of
-confidence in elections by treatment condition (control condition as
-reference). Figure~\ref{fig-coef1-1} displays two models for confidence
-in elections in Maricopa County, AZ, and one's local area by treatment
-condition; Figure~\ref{fig-coef1-2} displays the same except
-\emph{confidence} is decomposed into its two components, \emph{trust}
-and \emph{distrust}. These figures merely illustrate the effect of the
-treatment with respect to the relationship between trust and distrust;
-ultimately confidence improves.
+Figure~\ref{fig-coef2} displays the same except \emph{confidence} is
+decomposed into its two components, \emph{trust} and \emph{distrust}.
+Figure~\ref{fig-coef2} merely illustrates the effect of the treatment
+with respect to the relationship between trust and distrust; ultimately
+confidence improves.
 
@@
 
-\caption{\label{fig-safety-bars}Safety Concerns and Confidence by
-Treatment Condition}
+\caption{\label{fig-safety1}Safety Concerns by Treatment Condition}
 
@@
 
-\subcaption{\label{fig-safety-bars-1}Concern for Violence while voting
-in Maricopa County, AZ Elections}
+\subcaption{\label{fig-safety1-1}Concerns for Violence}
 
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-safety-bars-1.png}}
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-safety1-1.png}}
 
@@
 
-\subcaption{\label{fig-safety-bars-2}Confidence in Voter Saftey at
-Election Sites in Maricopa County, AZ}
+\subcaption{\label{fig-safety1-2}Confidence in Voter Safety}
 
@@
 
-\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-safety-bars-2.png}}
+\pandocbounded{\includegraphics[keepaspectratio]{index_files/figure-pdf/fig-safety1-2.png}}
 
@@
 
-Briefly reviewing Figure~\ref{fig-safety-bars}, those in the treatment
+Briefly reviewing Figure~\ref{fig-safety1}, those in the treatment
 condition felt less concern over the potential for violence compared to
-those in the control. As for confidence in voter safety at election
-sites, it appears that more respondents in the treatment condition
-expressed that they were ``Very confident'' compared to those in the
-control, by approximately \(8\) percentage points.
-
-\newpage{}
+those in the control.
+
+As for confidence in voter safety at election sites, it appears that
+more respondents in the treatment condition expressed that they were
+``Very confident'' compared to those in the control, by approximately
+\(8\) percentage points.
 
@@
 
-Those in the treatment condition had lower probability to express that
-they were `Very' or `Somewhat' concerned for violence in Maricopa
-County, AZ Elections, yet higher probability of expressing `Not too' or
-`Not at all' concerned. As for confidence in voter safety, moving from
-treatment to control, the difference in predicted probability of a
-respondent selecting ``Very Confident'' was \(0.08\).
-Table~\ref{tbl-preds-diff1} and Table~\ref{tbl-preds-diff2} show the
-significant differences in predicted probabilities at 95\(\%\)
-confidence\footnote{The same models were run for items pertaining to
-  safety concerns in one's local area but results of the treatment were
-  not significantly different from the control. See Appendix E for full
-  results table of ordinal logistic regression}. These findings support
-both H\textsubscript{4a} and H\textsubscript{4b} respectively,
-permitting rejection of the null for each hypothesis.
-
-\begin{table}[t]
+\begin{table}[H]
 
@@
 
-\begin{table}[t]
+Shown in Table~\ref{tbl-preds-diff1}, those in the treatment condition
+had lower probability to express that they were `Very' or `Somewhat'
+concerned for violence in Maricopa County, AZ Elections, yet higher
+probability of expressing `Not too' or `Not at all' concerned.
+
+\begin{table}[H]
 
@@
 
-\newpage{}
-
-\subsection{Limitations}\label{limitations}
-
-The bluntness of the experimental stimulus and survey items don't allow
-us to establish exactly what it is about military veterans in particular
-that cues stronger confidence in elections. No survey items assessed
-public attitudes about military veterans specifically, pre- nor
-post-treatment. This unfortunately leaves no room for me to postulate
-and examine any potential mechanisms underlying results.
-
-It should be noted that these results are limited to one's expectations
-in anticipation of election night. Whether the increase in confidence is
-sustained post-election night cannot be inferred from these results.
-Moreover, It is yet unclear whether actually encountering and
-interacting with veterans working as staff or volunteers at election
-sites does much to improve voter confidence after election night
-compared to anyone else. It may be the case that assumptions that
-veterans are filling spots as election workers and volunteers simply
-primes positive expectations as one heads into an election site,
-potentially improving voters perceptions of their own experience on the
-way out. Further research would be needed to test such an idea.
-
-The setting of the vignette and specified in survey items might raise
-additional concerns on whether results are generalizable. Naming a
-specific county in the vignette adds in a potentially influential factor
-unaccounted for in the survey; some people may have attitudes about the
-county in question, others won't, while others may be muffed to consider
-a random county in the U.S. they know nothing about. Naming a real and
-somewhat salient county potentially undermines confidence that the
-treatment effects are solely attributable to veterans to an unknown
-degree. Simply put, there may be something special about Maricopa
-County, AZ in particular that generalizes across attitudes of trust or
-distrust in elections.
-
-Arguably, however, Maricopa County is indicated as the setting in both
-the treatment and control vignettes, thus the only actual difference
-between conditions is constrained to the target group being recruited.
-Future research may employ vignettes naming a fictional U.S. county to
-hopefully eliminate the setting as a concern. Alternatively additional
-survey items that ask directly about one's knowledge or sentiment about
-the county in question could inform researchers on whether the named
-county imposes any undue influence at all, or whether the setting is
-associated with other factors such as partisanship.
-
-As stated previously, the survey was fielded on a non-probability sample
-of 1,287 U.S. citizens 18 years of age or older. The results presented
-here are not assumed to be generalizable to the national population. It
-may be feasible to weigh the sample to demographics of the population at
-the time the survey was fielded, but this is unnecessary for the
-experimental purpose of the study. If similar findings complement or
-replicate these results, then the expense of drawing samples more
-representative of the national population may be justified. At this
-stage, however, the results are limited to demonstrating treatment
-effects.
-
-Note also that the measurement items of the components trust and
-distrust, and the method of computing scores for the dependent variable,
-confidence in elections, are unique to this study but falls under the
-methodological framework of Classical Test Theory (CTT). Although survey
-measurement items were either directly drawn from or inspired by similar
-survey items found in various other surveys (e.g., SPAE, Pew), the
-question wording, response choices, coding, and computation of sum
-scores of the dependent variable are specific, thus rendering
-measurement of the hypothetical constructs of interest (i.e., trust,
-distrust) less comparable across similar studies that profess
-measurement of similar constructs (\citeproc{ref-widaman2024}{Widaman
-and Revelle 2024}). Namely, trust, distrust, or confidence in elections
-as defined and measured here.
+As for confidence in voter safety in Table~\ref{tbl-preds-diff2}, moving
+from treatment to control, the difference in predicted probability of a
+respondent selecting ``Very Confident'' was \(0.08\). Both tables show
+the significant differences in predicted probabilities at 95\(\%\)
+confidence\footnote{The same models were run for items pertaining to
+  safety concerns in one's local area but results of the treatment were
+  not significantly different from the control. See Appendix E for full
+  results table of ordinal logistic regression}. These findings support
+both H\textsubscript{4a} and H\textsubscript{4b} respectively,
+permitting rejection of the null for each hypothesis.
 
@@
 
+It is definitely plausible that the public, to some unknown extent,
+associates a particular gender or race, or both, with former and active
+military members which may, in turn, mediate the effect of the veteran
+cue. Additionally, I can't be sure as to whether respondent's views of
+the military generalize to attitudes about active service members and
+veterans. However that is a separate question about the source of public
+opinion about military members themselves beyond the scope of this
+study.
+
+There's scant research or evidence available to postulate a well-formed
+theory on the mechanism underlying the expected effects of veterans as a
+group on attitudes about institutions and processes, rather than on
+attitudes about persons or groups. That is to say, there's not much
+research on how the public feels, or what they think, about former
+members of the U.S. Armed Forces.
+
 In their research examining whether groups differed in attitudes about
@@
 express contempt or indifference. This further indicates a need for
-research to determine an underlying mechanism explaining why veterans
-incur special favor.
+research to determine an underlying mechanism explaining why, and for
+whom, veterans incur special favor.
+
+\subsection{Limitations}\label{limitations}
+
+The bluntness of the experimental stimulus and survey items don't allow
+us to establish exactly what it is about military veterans in particular
+that cues stronger confidence in elections. No survey items assessed
+public attitudes about military veterans specifically, pre- nor
+post-treatment. This unfortunately leaves no room for me to postulate
+and examine any potential mechanisms underlying results.
+
+It should be noted that these results are limited to one's expectations
+in anticipation of election night. Whether the increase in confidence is
+sustained post-election night cannot be inferred from these results.
+Moreover, It is yet unclear whether actually encountering and
+interacting with veterans working as staff or volunteers at election
+sites does much to improve voter confidence after election night
+compared to anyone else. It may be the case that assumptions that
+veterans are filling spots as election workers and volunteers simply
+primes positive expectations as one heads into an election site,
+potentially improving voters perceptions of their own experience on the
+way out. Further research would be needed to test such an idea.
+
+The setting of the vignette and specified in survey items might raise
+additional concerns on whether results are generalizable. Naming a
+specific county in the vignette adds in a potentially influential factor
+unaccounted for in the survey; some people may have attitudes about the
+county in question, others won't, while others may be muffed to consider
+a random county in the U.S. they know nothing about. Naming a real and
+somewhat salient county potentially undermines confidence that the
+treatment effects are solely attributable to veterans to an unknown
+degree. Simply put, there may be something special about Maricopa
+County, AZ in particular that generalizes across attitudes of trust or
+distrust in elections.
+
+Arguably, however, Maricopa County is indicated as the setting in both
+the treatment and control vignettes, thus the only actual difference
+between conditions is constrained to the target group being recruited.
+Future research may employ vignettes naming a fictional U.S. county to
+hopefully eliminate the setting as a concern. Alternatively additional
+survey items that ask directly about one's knowledge or sentiment about
+the county in question could inform researchers on whether the named
+county imposes any undue influence at all, or whether the setting is
+associated with other factors such as partisanship.
+
+As stated previously, the survey was fielded on a non-probability sample
+of 1,287 U.S. citizens 18 years of age or older. The results presented
+here are not assumed to be generalizable to the national population. It
+may be feasible to weigh the sample to demographics of the population at
+the time the survey was fielded, but this is unnecessary for the
+experimental purpose of the study. If similar findings complement or
+replicate these results, then the expense of drawing samples more
+representative of the national population may be justified. At this
+stage, however, the results are limited to demonstrating treatment
+effects.
+
+Note also that the measurement items of the components trust and
+distrust, and the method of computing scores for the dependent variable,
+confidence in elections, are unique to this study but falls under the
+methodological framework of Classical Test Theory (CTT). Although survey
+measurement items were either directly drawn from or inspired by similar
+survey items found in various other surveys (e.g., SPAE, Pew), the
+question wording, response choices, coding, and computation of sum
+scores of the dependent variable are specific, thus rendering
+measurement of the hypothetical constructs of interest (i.e., trust,
+distrust) less comparable across similar studies that profess
+measurement of similar constructs (\citeproc{ref-widaman2024}{Widaman
+and Revelle 2024}). Namely, trust, distrust, or confidence in elections
+as defined and measured here.
 
@@
 colspec={Q[]Q[]Q[]Q[]},
-cell{2}{1}={c=4}{},cell{5}{1}={c=4}{},cell{10}{1}={c=4}{},cell{15}{1}={c=4}{},cell{22}{1}={c=4}{},cell{27}{1}={c=4}{},cell{33}{1}={c=4}{},cell{39}{1}={c=4}{},cell{44}{1}={c=4}{},
-column{2,3,4}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=c,},
-cell{1}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{2}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{5}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{10}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{15}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{22}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{27}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{33}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{39}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{44}{1}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{3}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{4}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{6}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{7}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{8}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{9}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{11}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{12}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{13}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{14}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{16}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{17}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{18}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{19}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{20}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{21}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{23}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{24}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{25}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{26}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{28}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{29}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{30}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{31}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{32}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{34}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{35}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{36}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{37}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{38}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{40}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{41}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{42}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{43}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{45}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{46}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{47}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{48}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
-cell{49}{1}={}{preto={\hspace{2em}}, font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+column{2,3,4}={}{font=\fontsize{0.7em}{1em}\selectfont, halign=c,},
+column{1}={}{font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+rowsep={0.1em}, colsep = {0.5em},
 }                     %% tabularray inner close
 \toprule
-& n & percent & valid percent \\ \midrule %% TinyTableHeader
-Experiment Condition &&& \\
-Control & 637 & 49.5 & - \\
-Treatment & 650 & 50.5 & - \\
-Age &&& \\
-18-34 & 350 & 27.2 & - \\
-35-54 & 480 & 37.3 & - \\
-55-74 & 390 & 30.3 & - \\
-75-85+ & 67 & 5.2 & - \\
-Gender &&& \\
-Male & 598 & 46.5 & 47.0 \\
-Female & 658 & 51.1 & 51.7 \\
-Other/Refused & 16 & 1.2 & 1.3 \\
-NA & 15 & 1.2 & - \\
-Race &&& \\
-White or Caucasian & 975 & 75.8 & 76.7 \\
-Black or African American & 164 & 12.7 & 12.9 \\
-American Indian & 22 & 1.7 & 1.7 \\
-Asian & 56 & 4.4 & 4.4 \\
-Other & 55 & 4.3 & 4.3 \\
-NA & 15 & 1.2 & - \\
-Hispanic, Latino, or Spanish Origin &&& \\
-Yes & 113 & 8.8 & 8.9 \\
-No & 1148 & 89.2 & 90.3 \\
-Prefer not to say & 11 & 0.9 & 0.9 \\
-NA & 15 & 1.2 & - \\
-Education &&& \\
-H.S. or less & 362 & 28.1 & 28.5 \\
-Some college no degree & 283 & 22.0 & 22.2 \\
-College degree & 461 & 35.8 & 36.2 \\
-Postgraduate degree & 166 & 12.9 & 13.1 \\
-NA & 15 & 1.2 & - \\
-Military Relation &&& \\
-Active Duty & 15 & 1.2 & 1.2 \\
-Has Family in Military & 362 & 28.1 & 28.5 \\
-No Family in Military & 789 & 61.3 & 62.0 \\
-Prior Service (Veteran) & 106 & 8.2 & 8.3 \\
-NA & 15 & 1.2 & - \\
-Party ID &&& \\
-Independent & 162 & 12.6 & 12.8 \\
-Republican & 540 & 42.0 & 42.6 \\
-Democrat & 566 & 44.0 & 44.6 \\
-NA & 19 & 1.5 & - \\
-Political Ideology &&& \\
-Conservative & 412 & 32.0 & 32.5 \\
-Liberal & 392 & 30.5 & 30.9 \\
-Moderate & 365 & 28.4 & 28.8 \\
-Unsure & 98 & 7.6 & 7.7 \\
-NA & 20 & 1.6 & - \\
+\textbf{Variable} & \textbf{Overall (N = 1287)} & \textbf{Control (N = 637)} & \textbf{Treatment (N = 650)} \\
+\textbf{Age group, in years} &  &  &  \\
+18-34 & 350 (27\%) & 170 (27\%) & 180 (28\%) \\
+35-54 & 480 (37\%) & 245 (38\%) & 235 (36\%) \\
+55-74 & 390 (30\%) & 198 (31\%) & 192 (30\%) \\
+75-85+ & 67 (5.2\%) & 24 (3.8\%) & 43 (6.6\%) \\
+\textbf{Gender} &  &  &  \\
+Male & 598 (47\%) & 289 (46\%) & 309 (48\%) \\
+Female & 658 (52\%) & 330 (52\%) & 328 (51\%) \\
+Other/Refused & 16 (1.3\%) & 10 (1.6\%) & 6 (0.9\%) \\
+NA & 15 & 8 & 7 \\
+\textbf{Race} &  &  &  \\
+White or Caucasian & 975 (77\%) & 478 (76\%) & 497 (77\%) \\
+Black or African American & 164 (13\%) & 85 (14\%) & 79 (12\%) \\
+American Indian & 22 (1.7\%) & 10 (1.6\%) & 12 (1.9\%) \\
+Asian & 56 (4.4\%) & 26 (4.1\%) & 30 (4.7\%) \\
+Other & 55 (4.3\%) & 30 (4.8\%) & 25 (3.9\%) \\
+NA & 15 & 8 & 7 \\
+\textbf{Hispanic, Latino, or Spanish origin?} &  &  &  \\
+Yes & 113 (8.9\%) & 53 (8.4\%) & 60 (9.3\%) \\
+No & 1,148 (90\%) & 567 (90\%) & 581 (90\%) \\
+Prefer not to say & 11 (0.9\%) & 9 (1.4\%) & 2 (0.3\%) \\
+NA & 15 & 8 & 7 \\
+\textbf{Education} &  &  &  \\
+H.S. or less & 362 (28\%) & 174 (28\%) & 188 (29\%) \\
+Some college no degree & 283 (22\%) & 142 (23\%) & 141 (22\%) \\
+College degree & 461 (36\%) & 236 (38\%) & 225 (35\%) \\
+Postgraduate degree & 166 (13\%) & 77 (12\%) & 89 (14\%) \\
+NA & 15 & 8 & 7 \\
 \bottomrule
@@
 
-\section{Appendix C: Test of Random Assignment to Experiment
-Condition}\label{appendix-c-test-of-random-assignment-to-experiment-condition}
+\begin{table}[H]
+
+\caption{\label{tbl-demog2}Sample Demographics}
+
+\centering{
+
+\centering
+\begin{tblr}[         %% tabularray outer open
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]Q[]Q[]},
+column{2,3,4}={}{font=\fontsize{0.7em}{1em}\selectfont, halign=c,},
+column{1}={}{font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+rowsep={0.1em}, colsep = {0.5em},
+}                     %% tabularray inner close
+\toprule
+\textbf{Variable} & \textbf{Overall (N = 1287)} & \textbf{Control (N = 637)} & \textbf{Treatment (N = 650)} \\
+\textbf{Party ID} &  &  &  \\
+Independent & 162 (13\%) & 83 (13\%) & 79 (12\%) \\
+Republican & 540 (43\%) & 262 (42\%) & 278 (43\%) \\
+Democrat & 566 (45\%) & 283 (45\%) & 283 (44\%) \\
+NA & 19 & 9 & 10 \\
+\textbf{Political Ideology} &  &  &  \\
+Liberal & 392 (31\%) & 201 (32\%) & 191 (30\%) \\
+Conservative & 412 (33\%) & 205 (33\%) & 207 (32\%) \\
+Extremely Liberal & 0 (0\%) & 0 (0\%) & 0 (0\%) \\
+Slightly liberal & 0 (0\%) & 0 (0\%) & 0 (0\%) \\
+Moderate: middle of the road & 365 (29\%) & 179 (29\%) & 186 (29\%) \\
+Slightly conservative & 0 (0\%) & 0 (0\%) & 0 (0\%) \\
+Extremely conservative & 0 (0\%) & 0 (0\%) & 0 (0\%) \\
+Haven't thought much about this & 98 (7.7\%) & 43 (6.8\%) & 55 (8.6\%) \\
+NA & 20 & 9 & 11 \\
+\textbf{If R had to choose Political Ideology} &  &  &  \\
+Liberal & 11 (11\%) & 3 (7.0\%) & 8 (15\%) \\
+Conservative & 19 (19\%) & 8 (19\%) & 11 (20\%) \\
+None of these & 68 (69\%) & 32 (74\%) & 36 (65\%) \\
+NA & 1,189 & 594 & 595 \\
+\textbf{Did R Vote in 2020 Election} &  &  &  \\
+I'm sure I didn't vote & 185 (15\%) & 97 (15\%) & 88 (14\%) \\
+I don't think I voted & 64 (5.0\%) & 33 (5.2\%) & 31 (4.8\%) \\
+I think I voted & 43 (3.4\%) & 19 (3.0\%) & 24 (3.7\%) \\
+Yes, I'm sure I voted & 920 (72\%) & 449 (71\%) & 471 (73\%) \\
+I was not eligible to vote & 60 (4.7\%) & 31 (4.9\%) & 29 (4.5\%) \\
+NA & 15 & 8 & 7 \\
+\textbf{Vote Choice in 2020 Election} &  &  &  \\
+Donald Trump & 439 (43\%) & 215 (43\%) & 224 (43\%) \\
+Joe Biden & 527 (51\%) & 255 (51\%) & 272 (52\%) \\
+Other & 59 (5.8\%) & 30 (6.0\%) & 29 (5.5\%) \\
+NA & 262 & 137 & 125 \\
+\bottomrule
+\end{tblr}
+
+}
+
+\end{table}%
+
+\newpage{}
+
+\begin{table}[H]
+
+\caption{\label{tbl-demog3}Sample Demographics}
+
+\centering{
+
+\centering
+\begin{tblr}[         %% tabularray outer open
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+width={1\linewidth},
+colspec={X[]X[]X[]X[]},
+column{2,3,4}={}{font=\fontsize{0.7em}{1em}\selectfont, halign=c,},
+column{1}={}{font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
+rowsep={0.1em}, colsep = {0.5em},
+}                     %% tabularray inner close
+\toprule
+\textbf{Variable} & \textbf{Overall (N = 1287)} & \textbf{Control (N = 637)} & \textbf{Treatment (N = 650)} \\
+\textbf{Military Service} &  &  &  \\
+Yes & 121 (9.5\%) & 53 (8.4\%) & 68 (11\%) \\
+No & 1,151 (90\%) & 576 (92\%) & 575 (89\%) \\
+NA & 15 & 8 & 7 \\
+\textbf{Current Active Duty} &  &  &  \\
+Yes & 15 (12\%) & 5 (9.4\%) & 10 (15\%) \\
+No & 106 (88\%) & 48 (91\%) & 58 (85\%) \\
+NA & 1,166 & 584 & 582 \\
+\textbf{Military Service within Family?} &  &  &  \\
+Yes & 439 (35\%) & 216 (34\%) & 223 (35\%) \\
+No & 833 (65\%) & 413 (66\%) & 420 (65\%) \\
+NA & 15 & 8 & 7 \\
+\bottomrule
+\end{tblr}
+
+}
+
+\end{table}%
+
+\newpage{}
+
+\section{Appendix B: Test of Random Assignment to Experiment
+Condition}\label{appendix-b-test-of-random-assignment-to-experiment-condition}
 
@@
 
-\begin{table}[H]
+\begin{table}
 
@@
 {                     %% tabularray inner open
-colspec={Q[]Q[]},
+width={1\linewidth},
+colspec={X[0.666666666666667]X[0.333333333333333]},
 cell{2}{1}={c=2}{},cell{6}{1}={c=2}{},cell{9}{1}={c=2}{},cell{15}{1}={c=2}{},cell{19}{1}={c=2}{},
-column{2}={}{halign=c, font=\fontsize{0.7em}{1em}\selectfont, halign=c,},
-cell{1}{1}={}{halign=l, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{2}{1}={}{halign=l, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{6}{1}={}{halign=l, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{9}{1}={}{halign=l, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{15}{1}={}{halign=l, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{19}{1}={}{halign=l, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{3}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{4}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{5}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{7}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{8}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{10}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{11}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{12}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{13}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{14}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{16}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{17}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{18}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{20}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{21}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{22}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{23}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{24}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{25}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{26}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-cell{27}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.7em}{1em}\selectfont, halign=l,},
-hline{22}={1,2}{solid, black, 0.05em},
+column{2}={}{halign=c, font=\fontsize{0.65em}{0.95em}\selectfont, halign=c,},
+cell{1}{1}={}{halign=l, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{2}{1}={}{halign=l, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{6}{1}={}{halign=l, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{9}{1}={}{halign=l, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{15}{1}={}{halign=l, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{19}{1}={}{halign=l, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{3}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{4}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{5}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{7}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{8}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{10}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{11}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{12}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{13}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{14}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{16}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{17}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{18}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{20}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{21}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{22}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{23}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{24}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{25}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{26}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+cell{27}{1}={}{halign=l, preto={\hspace{2em}}, font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
+hline{22}={1,2}{solid, black, 0.1em},
 }                     %% tabularray inner close
@@
 & log(OR) \\ \midrule %% TinyTableHeader
-\textbf{Age} & \\
+Age & \\
 35-54 & -0.166, {[}-0.449, 0.116{]} \\
@@
 75-85+ & 0.402, {[}-0.149, 0.972{]} \\
-\textbf{Gender} & \\
+Gender & \\
 Female & -0.069, {[}-0.293, 0.154{]} \\
 Other/Refused & -0.625, {[}-1.751, 0.419{]} \\
-\textbf{Race} & \\
+Race & \\
 Asian & 0.028, {[}-0.547, 0.605{]} \\
@@
 American Indian & 0.501, {[}-0.577, 1.693{]} \\
-\textbf{Education} & \\
+Education & \\
 Some college no degree & -0.103, {[}-0.418, 0.211{]} \\
@@
 Postgraduate degree & 0.023, {[}-0.353, 0.400{]} \\
-\textbf{Party ID} & \\
+Party ID & \\
 Republican & 0.117, {[}-0.242, 0.477{]} \\
@@
 entry=none,label=none,
-note{}={{\fontsize{0.75em}{0.75em}\selectfont + p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001}},
-note{ }={{\fontsize{0.75em}{0.75em}\selectfont Parameter estimate (and confidence intervals) exponentiated to show odds ratios.}},
-note{  }={{\fontsize{0.75em}{0.75em}\selectfont Uncertainty intervals (profile-likelihood) and p-values (two-tailed) computed using a Wald t-distribution approximation}},
+note{}={{\fontsize{0.65em}{0.65em}\selectfont Parameter estimate (and confidence intervals) exponentiated to show odds ratios.}},
 ]                     %% tabularray outer close
 {                     %% tabularray inner open
-colspec={Q[]Q[]Q[]},
-column{2,3}={}{halign=c, font=\fontsize{0.8em}{1.1em}\selectfont,},
-column{1}={}{halign=l, font=\fontsize{0.8em}{1.1em}\selectfont,},
-hline{16}={1,2,3}{solid, black, 0.05em},
+width={1\linewidth},
+colspec={X[0.5]X[0.25]X[0.25]},
+column{2,3}={}{halign=c, font=\fontsize{0.65em}{0.95em}\selectfont,},
+column{1}={}{halign=l, font=\fontsize{0.65em}{0.95em}\selectfont,},
+hline{9}={1,2,3}{solid, black, 0.05em},
 }                     %% tabularray inner close
@@
 & Concerns for Violence (OR) & Confidence in Voter Safety (OR) \\ \midrule %% TinyTableHeader
-Treatment & 1.289* & 1.494*** \\
-& [1.055, 1.576] & [1.211, 1.844] \\
-Very concerned | Somewhat concerned & 0.153*** &  \\
-& [0.127, 0.186] &  \\
-Somewhat concerned | Not too concerned & 1.125 &  \\
-& [0.969, 1.305] &  \\
-Not too concerned | Not at all concerned & 6.762*** &  \\
-& [5.595, 8.171] &  \\
-Not at all confident | Not too confident &  & 0.055*** \\
-&  & [0.041, 0.073] \\
-Not too confident | Somewhat confident &  & 0.280*** \\
-&  & [0.237, 0.332] \\
-Somewhat confident | Very confident &  & 3.150*** \\
-&  & [2.667, 3.721] \\
+Treatment & 1.289, [1.055, 1.576] & 1.494, [1.211, 1.844] \\
+Very concerned | Somewhat concerned & 0.153, [0.127, 0.186] &  \\
+Somewhat concerned | Not too concerned & 1.125, [0.969, 1.305] &  \\
+Not too concerned | Not at all concerned & 6.762, [5.595, 8.171] &  \\
+Not at all confident | Not too confident &  & 0.055, [0.041, 0.073] \\
+Not too confident | Somewhat confident &  & 0.280, [0.237, 0.332] \\
+Somewhat confident | Very confident &  & 3.150, [2.667, 3.721] \\
 Num.Obs. & 1286 & 1285 \\
@@
 entry=none,label=none,
-note{}={{\fontsize{0.75em}{0.75em}\selectfont Thinking about Maricopa County, AZ, how concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place?}},
+note{}={{\fontsize{0.65em}{0.65em}\selectfont Thinking about Maricopa County, AZ, how concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place?}},
 ]                     %% tabularray outer close
@@
 colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
-column{3,4,5,6,7}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=c,},
-column{1,2}={}{font=\fontsize{0.8em}{1.1em}\selectfont, halign=l,},
+column{3,4,5,6,7}={}{font=\fontsize{0.65em}{0.95em}\selectfont, halign=c,},
+column{1,2}={}{font=\fontsize{0.65em}{0.95em}\selectfont, halign=l,},
 }                     %% tabularray inner close
@@
 Violence & Condition & estimate & std.error & z & Pr(>|z|) & conf.int \\ \midrule %% TinyTableHeader
-Very concerned & Control & 0.133 & 0.011 & 11.746 & 7.442e-32 & [0.111, 0.155] \\
-Very concerned & Treatment & 0.106 & 0.010 & 10.977 & 4.955e-28 & [0.087, 0.125] \\
-Somewhat concerned & Control & 0.396 & 0.016 & 25.430 & 1.175e-142 & [0.366, 0.427] \\
-Somewhat concerned & Treatment & 0.360 & 0.015 & 23.556 & 1.081e-122 & [0.330, 0.389] \\
-Not too concerned & Control & 0.342 & 0.015 & 23.296 & 4.890e-120 & [0.313, 0.371] \\
-Not too concerned & Treatment & 0.374 & 0.015 & 24.825 & 4.779e-136 & [0.344, 0.403] \\
-Not at all concerned & Control & 0.129 & 0.011 & 11.895 & 1.263e-32 & [0.108, 0.150] \\
-Not at all concerned & Treatment & 0.160 & 0.012 & 12.882 & 5.678e-38 & [0.136, 0.185] \\
+Very concerned & Control & 0.133 & 0.011 & 11.746 & <0.05 & [0.111, 0.155] \\
+Very concerned & Treatment & 0.106 & 0.010 & 10.977 & <0.05 & [0.087, 0.125] \\
+Somewhat concerned & Control & 0.396 & 0.016 & 25.430 & <0.05 & [0.366, 0.427] \\
+Somewhat concerned & Treatment & 0.360 & 0.015 & 23.556 & <0.05 & [0.330, 0.389] \\
+Not too concerned & Control & 0.342 & 0.015 & 23.296 & <0.05 & [0.313, 0.371] \\
+Not too concerned & Treatment & 0.374 & 0.015 & 24.825 & <0.05 & [0.344, 0.403] \\
+Not at all concerned & Control & 0.129 & 0.011 & 11.895 & <0.05 & [0.108, 0.150] \\
+Not at all concerned & Treatment & 0.160 & 0.012 & 12.882 & <0.05 & [0.136, 0.185] \\
 \bottomrule
@@
 entry=none,label=none,
-note{}={{\fontsize{0.75em}{0.75em}\selectfont How confident, if at all, are you that in person polling places in Maricopa County, AZ will be safe places for voters to cast their ballots during the upcoming elections in November?}},
+note{}={{\fontsize{0.65em}{0.65em}\selectfont How confident, if at all, are you that in person polling places in Maricopa County, AZ will be safe places for voters to cast their ballots during the upcoming elections in November?}},
 ]                     %% tabularray outer close
@@
 Voter Safety & Condition & estimate & std.error & z & Pr(>|z|) & conf.int \\ \midrule %% TinyTableHeader
-Not at all confident & Control & 0.052 & 0.007 & 7.302 & 2.845e-13 & [0.038, 0.066] \\
-Not at all confident & Treatment & 0.035 & 0.005 & 6.932 & 4.141e-12 & [0.025, 0.045] \\
-Not too confident & Control & 0.167 & 0.013 & 13.268 & 3.563e-40 & [0.142, 0.192] \\
-Not too confident & Treatment & 0.123 & 0.010 & 11.924 & 8.875e-33 & [0.102, 0.143] \\
-Somewhat confident & Control & 0.540 & 0.014 & 38.037 & 0.000 & [0.512, 0.568] \\
-Somewhat confident & Treatment & 0.520 & 0.014 & 36.134 & 6.715e-286 & [0.492, 0.549] \\
-Very confident & Control & 0.241 & 0.016 & 15.519 & 2.583e-54 & [0.211, 0.271] \\
-Very confident & Treatment & 0.322 & 0.017 & 18.550 & 8.104e-77 & [0.288, 0.356] \\
+Not at all confident & Control & 0.052 & 0.007 & 7.302 & <0.05 & [0.038, 0.066] \\
+Not at all confident & Treatment & 0.035 & 0.005 & 6.932 & <0.05 & [0.025, 0.045] \\
+Not too confident & Control & 0.167 & 0.013 & 13.268 & <0.05 & [0.142, 0.192] \\
+Not too confident & Treatment & 0.123 & 0.010 & 11.924 & <0.05 & [0.102, 0.143] \\
+Somewhat confident & Control & 0.540 & 0.014 & 38.037 & <0.05 & [0.512, 0.568] \\
+Somewhat confident & Treatment & 0.520 & 0.014 & 36.134 & <0.05 & [0.492, 0.549] \\
+Very confident & Control & 0.241 & 0.016 & 15.519 & <0.05 & [0.211, 0.271] \\
+Very confident & Treatment & 0.322 & 0.017 & 18.550 & <0.05 & [0.288, 0.356] \\
 \bottomrule
@@
 Abbate, Andrea. 2020. {``39 {Ways Election Offices} Are {Responding} to
-{COVID-19}.''}
-\url{https://www.techandciviclife.org/covid-19-responses/}.
+{COVID-19}.''} \emph{Center for Tech and Civic Life}.
 
@@
 Baldor, Lolita. 2025a. {``Military Commanders Will Be Told to Send
-Transgender Troops to Medical Checks to Oust Them.''}
-\url{https://apnews.com/article/transgender-ban-military-discharge-troops-0218f0b6fec595c420bd0ac072d87335}.
+Transgender Troops to Medical Checks to Oust Them.''} \emph{AP News}.
 
@@
 Baldor, Lolita. 2025b. {``Military Parade to Celebrate the {Army}'s
-250th Anniversary Will Be Held on {Trump}'s Birthday.''}
-\url{https://apnews.com/article/trump-army-military-parade-birthday-2f5cd12c8ccd4efddc29bfa3cf8f2705}.
+250th Anniversary Will Be Held on {Trump}'s Birthday.''} \emph{AP News}.
 
@@
 Baldor, Lolita. 2025c. {``Pentagon Directs Military to Pull Library
-Books That Address Diversity, Anti-Racism, Gender Issues.''}
-\url{https://apnews.com/article/pentagon-hegseth-dei-library-books-770364ab99591402ddffe8758432ff26}.
+Books That Address Diversity, Anti-Racism, Gender Issues.''} \emph{AP
+News}.
 
@@
 Baldor, Lolita C. 2020. {``Military Wary That Shakeup Could Upend Its
-Apolitical Nature.''}
-\url{https://apnews.com/article/military-wary-shakeup-upend-apolitical-89eccf0aef7cf7b99208b3bfd0453a43}.
+Apolitical Nature.''} \emph{AP News}.
 
@@
 Baldor, Lolita C. 2025. {``Hegseth Orders the Name of Gay Rights
-Activist {Harvey Milk} Scrubbed from {Navy} Ship.''}
-\url{https://apnews.com/article/harvey-milk-navy-ship-renamed-pride-month-d6cda5df15ee5bc066092d54c591c6f2}.
+Activist {Harvey Milk} Scrubbed from {Navy} Ship.''} \emph{AP News}.
 
@@
 Brennan Center for Justice. 2024. \emph{Local {Election Officials
-Survey} --- {May} 2024 \textbar{} {Brennan Center} for {Justice}}.
+Survey} --- {May} 2024 {\textbar} {Brennan Center} for {Justice}}.
 Brennan Center Research Department.
-\url{https://www.brennancenter.org/our-work/research-reports/local-election-officials-survey-may-2024}
-(November 5, 2024).
 
@@
 Systems}, {Donald Trump}, and {Voter Confidence}.''} \emph{Public
-Opinion Quarterly} 88: 516--35.
+Opinion Quarterly} 88(SI): 516--35.
 doi:\href{https://doi.org/10.1093/poq/nfae034}{10.1093/poq/nfae034}.
@@
 Policies} and {Voter Confidence} for {Black} and {White Voters}.''}
-\emph{Public Opinion Quarterly} 88: 561--84.
+\emph{Public Opinion Quarterly} 88(SI): 561--84.
 doi:\href{https://doi.org/10.1093/poq/nfae032}{10.1093/poq/nfae032}.
@@
 Workers for {Election Day} Are Paying Off.''} \emph{WHYY NPR}.
-\url{https://whyy.org/articles/philly-area-counties-say-efforts-to-recruit-poll-workers-for-election-day-are-paying-off/}.
 
@@
 Michigan Militia Men Navigate Evolving Social Norms}.''} Thesis.
-\url{http://deepblue.lib.umich.edu/handle/2027.42/98077}.
 
@@
 Cooter, Amy. 2024. {``Veterans and {Extremism}: {From Militias} to
-{January} 6th and {Real Patriots} \textbar{} {Middlebury Institute} of
+{January} 6th and {Real Patriots} {\textbar} {Middlebury Institute} of
 {International Studies} at {Monterey}.''}
-\url{https://www.middlebury.edu/institute/academics/centers-initiatives/ctec/ctec-publications/veterans-and-extremism-militias-january-6th}.
 
@@
 Doubek, James. 2024. {``States and Cities Beef up Security to Prepare
-for Potential Election-Related Violence.''} \emph{NPR: 2024 Election}.
-\url{https://www.npr.org/2024/11/04/nx-s1-5178083/national-guard-police-election-security}
-(November 5, 2024).
+for Potential Election-Related Violence.''} \emph{NPR}.
 
@@
 Dunn, Amina. 2018. {``Elections in {America}: {Concerns Over Security},
-{Divisions Over Expanding Access} to {Voting}.''}
-\url{https://www.pewresearch.org/politics/2018/10/29/elections-in-america-concerns-over-security-divisions-over-expanding-access-to-voting/}.
+{Divisions Over Expanding Access} to {Voting}.''} \emph{Pew Research
+Center}.
 
@@
 Edlin, Ruby, and Lawrence Norden. 2024. {``Poll of {Election Officials
-Finds Concerns About Safety}, {Political Interference} \textbar{}
-{Brennan Center} for {Justice}.''}
-\url{https://www.brennancenter.org/our-work/analysis-opinion/poll-election-officials-finds-concerns-about-safety-political}.
+Finds Concerns About Safety}, {Political Interference} {\textbar}
+{Brennan Center} for {Justice}.''} \emph{Brennan Center For Justice}.
 
@@
 {Official Turnover Rates} from 2000--2024}. Bipartisan Policy Center.
-\url{https://bipartisanpolicy.org/download/?file=/wp-content/uploads/2024/04/WEB_BPC_Elections_Admin_Turnover_R01.pdf}.
 
@@
 Garamone, Jim. 2016a. {``Active-{Duty Personnel Must Remain Apolitical},
-{Nonpartisan}, {Dunford Says}.''}
-\url{https://www.defense.gov/News/News-Stories/Article/Article/881624/active-duty-personnel-must-remain-apolitical-nonpartisan-dunford-says}.
+{Nonpartisan}, {Dunford Says}.''} \emph{DOD News {\textbar} U.S.
+Department of Defense}.
 
@@
 Garamone, Jim. 2016b. {``{DOD} Civilians, Service Members Must Remain
-Non-Partisan, Apolitical.''}
-\url{https://www.defense.gov/News/Releases/Release/Article/975910/dod-civilians-service-members-must-remain-non-partisan-apolitical}.
+Non-Partisan, Apolitical.''} \emph{DOD News {\textbar} U.S. Department
+of Defense}.
 
@@
 Giles, Ben. 2021. {``Arizona {Recount Of} 2020 {Election Ballots Found
-No Proof Of Corruption}.''} \emph{NPR: 2024 Election}.
-\url{https://www.npr.org/2021/09/25/1040672550/az-audit}.
+No Proof Of Corruption}.''} \emph{NPR}.
+
+\bibitem[\citeproctext]{ref-haerens2018}
+Haerens, Margaret. 2018. \emph{The {NFL National Anthem Protests}}.
+Santa Barbara, California: Bloomsbury Publishing.
 
@@
 Herndon, Astead W. 2020. {``{LeBron James} and a {Multimillion-Dollar
-Push} for {More Poll Workers}.''} \emph{The New York Times: U.S.}
-\url{https://www.nytimes.com/2020/08/24/us/politics/lebron-james-poll-workers.html}
-(November 13, 2024).
+Push} for {More Poll Workers}.''} \emph{The New York Times}.
 
@@
 Terrorism (START): College Park}.
-\url{https://www.start.umd.edu/pubs/Radicalization\%20in\%20the\%20Ranks_April\%202022.pdf}.
 
@@
 a {Nationally Representative Survey}}. RAND Corporation.
-\url{https://www.rand.org/pubs/research_reports/RRA1363-7.html}.
 
@@
 LaGrone, Sam. 2019. {``Shanahan {Reminds Pentagon} to {Stay
-Apolitical}.''}
-\url{https://news.usni.org/2019/06/11/acting-secdef-shanahan-reminds-pentagon-to-stay-apolitical-following-mccain-situation}.
+Apolitical}.''} \emph{USNI News}.
 
@@
 Lawrence, Quil. 2022. {``Vetting the {Vote}: {Military} Veterans
-Volunteer as Impartial Poll Workers.''} \emph{NPR: National}.
-\url{https://www.npr.org/2022/11/04/1133920940/vetting-the-vote-military-veterans-volunteer-as-impartial-poll-workers}.
+Volunteer as Impartial Poll Workers.''} \emph{NPR}.
 
@@
 Lawrence, Quil. 2024. {``As Fears about Election Security Grow, Military
-Veterans Are Filling as Poll Workers.''}
-\url{https://www.npr.org/2024/10/14/nx-s1-5144186/as-fears-about-election-security-grow-military-veterans-are-filling-as-poll-workers}.
+Veterans Are Filling as Poll Workers.''} \emph{NPR}.
 
@@
 Journal of Politics} 80(1): 59--70.
-\url{https://www.jstor.org/stable/26551118} (June 4, 2025).
 
@@
 Lincoln, Sophie. 2024. {``Washoe {County} Staff Prepare for {Election
-Day}, Announce New Safety Feature at Polls.''}
-\url{https://mynews4.com/news/local/washoe-county-staff-prepare-for-election-day-announce-new-safety-feature-at-polls}
-(November 5, 2024).
+Day}, Announce New Safety Feature at Polls.''} \emph{News4 KRNV}.
 
@@
 Loewenson, Irene. 2023. {``Mattis Says Vets at {Jan}. 6 {Capitol} Riot
-{`Don't Define the Military'}.''} \emph{Marine Corps Times: name}.
-\url{https://www.marinecorpstimes.com/news/your-marine-corps/2023/11/06/mattis-says-vets-at-jan-6-capitol-riot-dont-define-the-military/}.
+{`Don't Define the Military'}.''} \emph{Marine Corps Times}.
 
@@
 Looker, Rachel. 2024. {``How Some Veterans Find a Way to 'Serve the
-Country Again' on {Super Tuesday}.''}
-\url{https://www.usatoday.com/story/news/politics/elections/2024/03/05/veterans-poll-workers-election/72839163007/}.
+Country Again' on {Super Tuesday}.''} \emph{USA TODAY}.
 
@@
 Election Administration, Federal Election Commission.
-\url{https://purl.fdlp.gov/GPO/gpo18585}.
 
@@
 Department and Office of the Recorder}.
-\url{https://elections.maricopa.gov/asset/jcr:a9e03750-0a8f-4162-859f-1d46ac54b485/Correcting\%20The\%20Record\%20-\%20January\%202022\%20Report.pdf}.
 
@@
 Political \& Military Sociology} 34(2): 281--88.
-\url{https://www.jstor.org/stable/45294228} (June 4, 2025).
 
@@
 Mena, Kelly. 2020. {``States Scramble to Recruit Thousands of Poll
-Workers Amid Pandemic Shortage \textbar{} {CNN Politics}.''}
-\url{https://www.cnn.com/2020/08/13/politics/poll-worker-shortage-2020-election/index.html}.
+Workers Amid Pandemic Shortage {\textbar} {CNN Politics}.''} \emph{CNN}.
 
@@
 Nadeem, Reem. 2024. {``Harris, {Trump Voters Differ Over Election
-Security}, {Vote Counts} and {Hacking Concerns}.''}
-\url{https://www.pewresearch.org/politics/2024/10/24/harris-trump-voters-differ-over-election-security-vote-counts-and-hacking-concerns/}
-(November 5, 2024).
+Security}, {Vote Counts} and {Hacking Concerns}.''} \emph{Pew Research
+Center}.
 
@@
 of {State Francisco V}. {Aguilar} Sign {Election Worker Protection Bill}
-into Law.''}
-\url{https://www.nvsos.gov/sos/Home/Components/News/News/3368/309?backlist=\%2Fsos}
-(November 5, 2024).
+into Law.''} \emph{Press Release {\textbar} Nevada Secretary of State}.
 
@@
 NFL Football Operations. 2022. {``Vet the {Vote}.''}
-\url{https://operations.nfl.com/inside-football-ops/social-justice/vet-the-vote/}.
 
@@
 Political \& Military Sociology} 43: 75--106.
-\url{https://www.jstor.org/stable/48599025} (June 12, 2025).
 
@@
 Effort} to {Recruit New Wave} of {Poll Workers} for {Election Day}.''}
-\url{https://www.powerthepolls.org/press-release-2020-06-30}.
+\emph{Power the Polls}.
 
@@
 to Work Polls.''} \emph{nwitimes.com}.
-\url{https://www.nwitimes.com/news/local/porter/porter-newsletter/porter-county-election-officials-recruit-students-to-work-polls/article_b2f1aaf8-1e5f-550e-bbbe-113dcb679f7e.html}.
 
@@
 \bibitem[\citeproctext]{ref-spearman1907}
-Spearman, Charles. 1907. {``Demonstration of {Formulæ} for {True
+Spearman, Charles. 1907. {``Demonstration of {Formul{æ}} for {True
 Measurement} of {Correlation}.''} \emph{The American Journal of
@@
 Steinhauer, Jennifer. 2020. {``Veterans {Fortify} the {Ranks} of
-{Militias Aligned With Trump}'s {Views}.''} \emph{The New York Times:
-U.S.}
-\url{https://www.nytimes.com/2020/09/11/us/politics/veterans-trump-protests-militias.html}.
+{Militias Aligned With Trump}'s {Views}.''} \emph{The New York Times}.
 
@@
 Thomas, Ashley. 2025. {``Trump {White House} Marks {Black History Month}
-While {Defense Department} Declares 'Identity Months Dead'.''}
-\url{https://apnews.com/article/trump-black-history-month-ec046b1a8122b5af9d8b26516b6837c2}.
+While {Defense Department} Declares 'Identity Months Dead'.''} \emph{AP
+News}.
 
@@
 \bibitem[\citeproctext]{ref-wetheveterans2022}
-We The Veterans. 2022. {``Launch of {Vet} the {Vote}.''}
-\url{https://vetthe.vote/blogs/news/launch-of-vet-the-vote}.
+We The Veterans. 2022. {``Launch of {Vet} the {Vote}.''} \emph{Vet The
+Vote}.
 
@@
 Wentling, Nikki. 2024. {``Veterans Group Hits Goal of Recruiting 100,000
-Election Workers.''} \emph{Military Times: name}.
-\url{https://www.militarytimes.com/news/your-military/2024/07/10/veterans-group-hits-goal-of-recruiting-100000-election-workers/}.
+Election Workers.''} \emph{Military Times}.
 
@@
 Is Now a Dangerous Job: How It Feels for Frontline, Swing-State
-Workers.''}
-\url{https://www.usatoday.com/story/news/politics/elections/2024/10/28/election-workers-2024-hostility/75586254007/}
-(November 5, 2024).
+Workers.''} \emph{USA TODAY}.
 
@@
 Model} of {Intergroup Relations}.''} \emph{Psychological Inquiry} 27(4):
-255--74. \url{https://www.jstor.org/stable/26159704} (October 26, 2024).
+255--74.
 

### 2025-07-07 docs/index.qmd
revisions

@@
 # goodness-of-fit statistics
-lrm.gof.stats <- function(x, ...){
+lrm.gof.stats <- function(model, ...){
 
   out <- data.frame(
-    null.deviance = x$null.deviance,
-    df.null = x$df.null,
-    logLik = as.numeric(stats::logLik(x)),
-    AIC = stats::AIC(x),
-    BIC = stats::BIC(x),
-    deviance = stats::deviance(x),
-    df.residual = stats::df.residual(x),
-    nobs = stats::nobs(x),
-    chisq = as.numeric(x$null.deviance - stats::deviance(x)),
-    df = as.numeric(x$df.null - stats::df.residual(x)),
-    'P(>chi)' = pchisq(q=x$null.deviance - stats::deviance(x),
-                       df = x$df.null - stats::df.residual(x), 
+    nobs = stats::nobs(model),
+    null.deviance = model$null.deviance,
+    df.null = model$df.null,
+    logLik = as.numeric(stats::logLik(model)),
+    deviance = stats::deviance(model),
+    df.residual = stats::df.residual(model),
+    chisq = as.numeric(model$null.deviance - stats::deviance(model)),
+    df = as.numeric(model$df.null - stats::df.residual(model)),
+    'P(>chi)' = pchisq(q=model$null.deviance - stats::deviance(model),
+                       df = model$df.null - stats::df.residual(model), 
                        lower.tail = F)
   )
-  out <- dplyr::as_tibble(out)
+  out <- dplyr::as_tibble(out) |>  
+  # rename column variables
+  dplyr::rename(
+    "Num.Obs."      = "nobs",
+    "Log.Lik"       = "logLik",
+    "Deviance"      = "deviance",
+    "Deviance Null" = "null.deviance",
+    "DF"            = "df",
+    "chisq"          = "chisq",
+    "P(>chisq)"     = "P..chi."
+  )
   return(out)
+}
+
+```
+
+```{r}
+#| label: tinytable-theme
+
+# see here: https://vincentarelbundock.github.io/tinytable/vignettes/theme.html#user-written-themes
+
+theme_mitex <- function(x, ...) {
+    fn <- function(table) {
+        if (isTRUE(table@output == "typst")) {
+          table@table_string <- gsub(
+            "\\$(.*?)\\$",
+            "#mitex(`\\1`)",
+            table@table_string)
+        }
+        return(table)
+    }
+    x <- style_tt(x, finalize = fn)
+    return(x)
 }
@@
 Regardless of the measures taken by election officials to boost public confidence in the *trustworthiness* of election administration (e.g., conducting audits, testing election machines), public *trust* and confidence in elections more generally is apt to shift dramatically post-election based on factors such as partisanship, elite rhetoric, particular state policies, and more [@nadeau1993; @carter2024; @coll2024a].
+Comparable research finds that confidence in elections is increased through elite rhetoric from fellow partisans affirming legitimacy of elections [@clayton2023], or through the provision of information about the electoral process or other official messaging of election officials themselves [@gaudette2025].
 Moreover, prior research has found that evaluation of election workers themselves are an important factor when it comes to levels of public confidence in the electoral process [@hall2007; @hall2009; @claassen2008].
@@
 Political and other social science researchers have recognized for some time the power that group identity can have over attitudes and perception [@xiao2016; @xiao2012; @vanbavel2021].
-As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve trust and confidence in election administration, and lessen expectations of electoral fraud.
-The next section elaborates on why military veterans are of particular interest in this regard.
-
-## Why Veterans
-
+As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve confidence in elections, and lessen expectations of electoral fraud.
+The next section elaborates on the proposed theory and why military veterans are of particular interest in this regard.
+
+## Theory: Why Veterans
+
+The theory tested in this study is this: when the public is informed that election officials are actively recruiting veteran military service members to work at election sites as staff or volunteers, their overall confidence in the fairness, accuracy, and integrity of the electoral process will improve.
+Said another way, insecurities over the integrity of elections administration and safety of voters lessen as the public learns that military service veterans are being sought out by election officials to staff or volunteer at election sites.
+The stimulating influence of veterans as a group in the abstract is expected to counteract distrust and insecurity pertaining to the institution of elections administration, as well as inspire greater trust in the same.
+This prompts an obvious question: why would information about efforts to recruit veterans to work as election staff and volunteers have any influence on confidence in elections?
+
+Election officials don't focus on recruiting people of a particular demographic, status, class, or prestige in order to shore up public trust in elections, and they don't discriminate recruitment efforts based on who the public thinks is best suited to secure elections from fraud.
 Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work.
-Especially since staffing issues have been an issue since at least the 1990s [@maidenberg1996; @ferrer2024].
+Especially since staffing has been an issue since at least the 1990s [@maidenberg1996; @ferrer2024].
 In 2020, such efforts were made far more difficult by the COVID-19 pandemic [@mena2020; @abbate2020a].
@@
 
-The reason why veterans arose as a special subset of the population to consider for this inquiry is because there was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021.
+There was a sudden push to target veterans for recruitment efforts that arose shortly after the events on Capitol Hill on January 6th, 2021.
 After the 2020 election, large efforts were made to recruit military veterans and their families to work or volunteer as election staff [@wetheveterans2022; @nflfootballoperations2022].
@@
 
-That being said, the general public perception, attitudes, or even stereotypes about military veterans are significant to consider.
+The claim that recruiting veterans to work as election staff and volunteers would improve public confidence in elections emerges as non-profit organizations---mainly comprised of veteran and military family members themselves---operate under, and promote, that assumption [@looker2024; @lawrence2024; @wentling2024].
+Non-profit groups of late have made incredible strides in targeted recruitment efforts under the notion that veterans are uniquely capable, committed, and best fit to serve the needs of the United States as civil servants and volunteers at election sites.
+Indeed, this study can be seen as a test of a particular assumption that veterans have about themselves---the assumption that their mere presence and civic engagement will inspire confidence in elections among the public.
+
+Veterans are, after all, civilians.
+Civilians with shared (but varied) experience and status of prior military service, but who are no more or less qualified for this civil service^[Research is limited and mixed on whether veterans in general are more inclined, however [@nesbit2011].] over non-veteran civilians.
+To be frank, announcements about concerted efforts to recruit veterans as election workers should not reasonably influence one's trust that votes will be counted more accurately, or that election fraud will not occur; there is no known evidence demonstrating that actually employing veterans as election staff or volunteers further improves the safety, security, and overall integrity of elections in the United States.
+Moreover, there's no known evidence of positive influence on public perceptions of said outcomes when voters encounter military veterans working as staff or volunteers at elections sites.
+So, why veterans?
+
+Two considerations underpin the notion that information about veterans will improve trust and quell distrust in elections.
+First, positive public regard for veterans *in general* is sufficient to elicit greater trust and lower distrust in elections despite the fact that information about veterans as election workers, or even merely information on efforts to recruit veterans, has no bearing on the actual integrity of the electoral process.
+
+An underlying assumption here is that there *is* something special about veterans in the eyes of the public generally, but this doesn't include a proposition on exactly *what* that special something might be in theory.
+This is partly due to there being limited research on public opinion about former and active military service members distinguished separately from public opinion about the military as an institution in general.
+Support for the military is generally pretty high, but attitudes about the military in general can't be construed as public opinion about veterans as a group.
+The evidence that can be gathered concerning public regard for military veterans shows that, generally, veterans are perceived favorably among the general public and all groups express exaggerated support for veterans in more than one way [@kleykamp2018], suggesting that public regard for veterans is prescribed by widespread social norm.
 Although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023].
-Veterans are a particularly potent group where mention of veteran status seems to have a positive, calming, or nullifying effect on attitudes.
+
+Beyond such findings, it is overtly clear that former and active military service members are highly revered nationwide.
+Veteran's day is a national holiday, and custom prescribes thanking military members for their service.
+Calls to "support the troops" are distinct from calls to support the politics the troops are deployed to pursue.
+In 2016, former NFL player Colin Kaepernick went from sitting to kneeling in protest during the playing of the National Anthem upon criticism that sitting in protest implied disrespect for active and former military service members [@haerens2018].
+
+Generally high public regard for veterans is taken together with literature suggesting that public trust in elections is malleable to factors that range in logical relevance to the actual structure or administration of elections.
+On the one hand, public trust is, indeed, influenced by information specifically about the processes of conducting elections [@gaudette2025].
+On the other hand, the public's trust in elections is not beholden to the demonstrated *trustworthiness* of the institution of election administration.
+Whether generally high public reverence for veterans is due to injunctive social norms or not, what may be posited is simply that positive regard for veterans in general may function sufficiently as a cue to elicit greater trust in elections despite relevance.
+
+Second, veterans are a particularly potent group where mention of one's veteran status seems to have a calming effect on attitudes.
+More so than just the general positive favor afforded to veterans, the group appears to have a somewhat pacifying effect on negative or otherwise contemptible discrimination, prejudice, and social stigma.
 For instance, recent research shows that, during his campaign in the 2020 Democratic Primaries, Pete Buttigieg's military background mitigated discrimination against him when he was presented as a veteran married to a man [@magni2024].
-Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@hardy2019].
+Similar research has also found that a candidate's veteran status affords them better evaluations regarding competency in particular issue areas (e.g., war competence) [@teigen2013; @hardy2019].
 Moreover, veteran status seems to mitigate or nullify usual stigmas associated with mental illness.
@@
 And media framing as such plays an important role on public perception [@kleykamp2015].
-
-## Theory and Hypotheses
-
-Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veterans and their family members to work as election staff and volunteers would boost public *confidence in elections administration*.
+Relatedly, attitudes about homelessness and PTSD---ranging from perceived causes of homelessness, whether the federal government should dedicate more resources, perceived effectiveness of policies, to compassion for homeless individuals---are generally more favorable for the homeless population among veterans than for the homeless population of general adults [@tsai2021].
+
+Such effects primarily pertain to attitudes about individual people or groups (e.g., a political candidate, prospective employees, the homeless population).
+The capacity of one's veteran status to pacify prejudice, discrimination, and stigma likely extends out to veterans as a group in a similar fashion.
+Information that election sites will be staffed by veterans may be enough to ease insecurities about the competence and commitment of the institution to conduct fair and accurate elections.
+
+## Trust and Distrust in Elections
+
+This theory is constrained to public confidence in the administration of elections in the United States.
+To be clear, the scope conditions in which this theory applies concern public trust and distrust in election administration in the anticipatory period prior to the election event.
+The theoretical relationship between trust and distrust is important to understand, especially when it comes to the dependent outcome of interest.
+Before going further, it is necessary to explicate the conception *confidence in elections* with respect to how I've defined trust and distrust in elections.
+
+Trust is, after all, merely *belief* held in the face of uncertainty.
+Trust is reliance on the veracity of belief in the face of uncertainty.
+Said another way, trust is *assured belief* dependent on its supposed veracity; a state of certainty with respect to some belief or judgement.
+It is "*assured*" because it is one's belief that relies on something rather than nothing.
+Hence quantitative methods of the sciences are replete with things such as *confidence* intervals around our estimates.
+Therefore, I understand trust to refer to the state or quality of certainty around one's beliefs or expectations; the extent to which one is assured of their expectations regarding what is or what will be the case.
+
+The kind of *trust in elections* I refer to concerns the expectations drawn up from one's judgement about the functioning of the electoral process---the extent to which one is assured in the belief that the electoral process will be fairly and accurately administered.
+I follow the notion of public trust in elections explicated by @stewart2022,
+
+> "Public trust in U.S.
+election institutions comes down to whether voting machines accurately record votes, voter registration systems accurately record those eligible to vote, geographic information systems accurately assign voters to voting districts, election-night reporting systems accurately aggregate and communicate election results to officials and the public, and postelection audit and canvassing procedures proceed impartially and in accordance with the law." [-@stewart2022, 236]
+
+That being said, I also account for expectations of electoral fraud, which I refer to as *distrust* in elections distinguished from trust.
+Distrust in this sense is also a belief, an expectation, about the anticipated functioning of the process.
+Note, however, that the prefix *dis-* in distrust implies "apart", "lack of, not" or "opposite".
+Conventionally, distrust is defined simply as the absence of trust, thus denoting a simple inverse and mutually exclusive relationship.
+However, as it concerns the psychology of an individual, *a lack of trust doesn't necessarily imply opposite expectations or opposing beliefs*.
+In particular, a lack of trust that votes will be accurately recorded, etc., doesn't necessarily imply inversely proportional expectations that electoral fraud will occur.
+In other words, although the relationship between trust and distrust is inverse, this relationship is not mutually exclusive.
+
+A person who is certain that electoral fraud will occur clearly lacks trust in elections; an expectation that electoral fraud will occur necessarily implies a lack of trust in elections regardless of positive expressions of trust.
+However, the reverse isn't also true; expressing a lack of trust in elections *doesn't necessarily imply* an expectation that electoral fraud will occur.
+Rather, a lack of trust implies an absence of assurance in the belief that the process will be conducted fairly and accurately---a lacking quality of certainty around said belief.
+An absence of such assurance denotes a state of *insecurity*.
+Other sources of uncertainty may challenge a person's confidence regarding the integrity of elections independent from anything that would lead them to believe electoral fraud will occur or has occurred.
+However my use of distrust refers to the assured belief that the outcome will be invalid---that outcomes will be independent of the process as prescribed, thus rendering outcomes as arbitrary.
+Specifically, distrust implies assurance in the belief that electoral fraud will occur.
+
+As such, trust and distrust represent opposing degrees of confidence along the same spectrum.
+However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling relatively confident in both respects.
+Accordingly, *equivalent degrees of trust and distrust cancel out*, rendering one relatively more insecure about their expectations of the future despite the fact that they may report feeling confident in either direction respectively.
+When trust and distrust are considered reflective of one's confidence about future expectations, then both can be placed along the same spectrum.
+Therefore, a lack of confidence denotes insecurity.
+
+This means that a person's baseline level of confidence in elections must take into account their present degree of distrust---i.e., their expectations of electoral fraud.
+Something may cause a person to have greater expectations that election fraud will occur, which in turn will always lower their trust in elections.
+In contrast, a person's trust in the integrity of the electoral process is reduced by the extent to which they expect that electoral fraud will occur.
+
+Thus, it follows that a person distrusts the integrity of the electoral process to the extent that they are to some extent certain that electoral fraud will occur or has occurred.
+They are, perhaps, poised to discount election results as invalid or illegitimate in advance.
+Either way, both trust and distrust refer to some positive degree of confidence (i.e., assurance) regarding one's expectations.
+They are distinguished by reference to either the normative idea about what *should* come about, or what is *supposed* to come about given the logical structure and integrity of the process.
+If the structure and integrity of some process is coherent and secure, respectively, then the outcome that follows will be valid.
+Should the integrity of that process be damaged or opaque, then the process becomes vulnerable and validity of the results are open to challenge.
+With respect to the administration of U.S.
+elections, the confident voter expects that votes will be counted as voters intend, election staff will competently administer elections, election technology will be secure from nefarious tampering, and that the process will be fair for all involved.
+
+## Hypotheses
+
+The outcome of interest is *confidence in elections*, which refers to trust in elections---i.e., expectations that elections will be administered fairly and accurately---compensated by distrust in elections---i.e., expectations that electoral fraud will occur.
+Considering the generally positive perception afforded to veterans by the public, it is reasonable to suspect that efforts that promote recruitment of veteran military service members to work as election staff and volunteers would boost public *confidence in elections administration*.
 Indeed, that is the primary hypothesis of this study.
@@
 
+A manipulation check is intended to ensure that the experimental treatment (or manipulation) is received by respondents as the researcher intends.
+Since this experiment required respondents to read a faux news article, inattention or speeding through vignette presentation would undermine results.
+To mitigate this as much as possible, the survey included two items as an attention check prior to presenting either the treatment or control vignette.
+Respondents who failed to select a certain response twice in a row were removed from the survey.
+Upon presentation of either the treatment or control vignette, survey respondents were unable to progress further in the survey until at least 15 seconds had elapsed.
+
 It should be noted that Maricopa County, AZ was chosen as the setting of the story in the vignette due to the increased scrutiny levied toward election administration there after the 2020 election [@giles2021; @maricopacountyelectionsdepartment2022].
@@
 
-### Trust and Distrust in Elections
-
 A set of five survey items measured public trust in elections by inquiring into the degree of confidence that votes will be counted as voters intend, confidence that electoral systems are secure from technological threats, perceived commitment of election staff, confidence that outcomes will be fair, and confidence that the voting process will be fair.
@@
 #| label: fig-coef1
-#| layout-nrow: 2
 #| fig-height: 3.5
@@
 #| fig-cap: "Confidence in Elections by Experiment Condition"
-#| fig-subcap: 
-#|   - "Confidence by Treatment Condition"
-#|   - "Trust and Distrust by Treatment Condition"
 
@@
   theme_bw(base_family = "TeX Gyre Pagella")
+
+conf.coef1
+
+```
+
+@fig-coef1 displays standard difference estimates of two models for confidence in elections in Maricopa County, AZ, and one's local area by treatment condition (control condition as reference).
+
+```{r}
+#| label: fig-coef2
+#| fig-height: 3.5
+#| fig-pos: 'H'
+#| fig-cap: "Trust and Distrust by Treatment Condition"
 
@@
 
-conf.coef1
 conf.coef2
@@
 
-@fig-coef1 displays standard difference estimates of confidence in elections by treatment condition (control condition as reference).
-@fig-coef1-1 displays two models for confidence in elections in Maricopa County, AZ, and one's local area by treatment condition; @fig-coef1-2 displays the same except *confidence* is decomposed into its two components, *trust* and *distrust*.
-These figures merely illustrate the effect of the treatment with respect to the relationship between trust and distrust; ultimately confidence improves.
+@fig-coef2 displays the same except *confidence* is decomposed into its two components, *trust* and *distrust*.
+@fig-coef2 merely illustrates the effect of the treatment with respect to the relationship between trust and distrust; ultimately confidence improves.
 
@@
 
+{{< pagebreak >}}
+
 In order to substantiate the overall influence of the treatment on confidence in elections, I regressed the dependent variable confidence on legitimacy beliefs while controlling for partisanship.
 
-::: {.content-visible when-format="bookup-html" unless-format="pdf"}
-
-```{r}
+```{r}
+#| label: tbl-legit
 #| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
-#| tbl-pos: H
+#| tbl-pos: t
 
@@
 
-texreg::htmlreg(
-  list(m1, m2), 
-  single.row = T,
-  caption.above = T,
-  custom.model.names = c("Confidence in AZ Elections", "w/Interaction"),
-  custom.coef.names = c(
-    "(Intercept)",
-    "Treatment",
-    "Not Legitimate",
-    "Republican",
-    "Democrat",
-    "Not Legitimate * Treatment"
+tab_legit <- modelsummary::modelsummary(
+  models = list(m1, m2), fmt = 2,
+  estimate = "{estimate} ({std.error}){stars}",
+  statistic = NULL,
+  stars = T,
+  coef_rename = c(
+    "(Intercept)"                        = "(Intercept)",
+    "groupTreatment"                     = "Treatment",
+    "q7Not legitimate"                   = "Not Legitimate",
+    "partyid_3catRepublican"             = "Republican",
+    "partyid_3catDemocrat"               = "Democrat",
+    "groupTreatment x q7Not legitimate"  = "Not Legitimate * Treatment"),
+  gof_map = c("nobs", "r2", "adj.r.squared"),
+  notes = list(
+    "Outcome variable mean-centered and scaled by 1 standard deviation",
+    "+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001"),
+  width = 0.8
 )
-)
-
-```
-
-:::
-
-::: {.content-visible when-format="pdf" unless-format="bookup-html"}
-
-```{r}
-#| tbl-cap: "Confidence in Elections by Treatment and Legitimacy Beliefs"
-#| tbl-pos: H
-#| label: tbl-legit
-#| results: asis
-
-# All continuous variables are mean-centered and scaled by 1 standard deviation.
-m1 <- lm(scale(conf.scores.az) ~ group + q7 + partyid_3cat, data = data)
-m2 <- lm(scale(conf.scores.az) ~ group * q7 + partyid_3cat, data = data)
-
-texreg::texreg(
-  list(m1, m2),
-  single.row = T,
-  caption = NULL,
-  caption.above = T,
-  use.packages = F,
-  table = F, # set `table = FALSE`. Quarto handles table cross-ref env
-  custom.model.names = c("Confidence in AZ Elections", "w/Interaction"),
-  custom.coef.names = c(
-    "(Intercept)",
-    "Treatment",
-    "Not Legitimate",
-    "Republican",
-    "Democrat",
-    "Not Legitimate * Treatment"
-    )
-)
-
-```
-
-:::
-
-The first model in Table \ref{tbl-legit} shows that overall confidence in elections among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
-Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$).
+
+colnames(tab_legit) <- c(" ", "Confidence in AZ Elections", "w/Interaction")
+
+tab_legit |> 
+  tinytable::style_tt(
+    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
+    align = "lcc"
+    ) |>  
+  tinytable::style_tt(i = 6, line = "t") |> 
+  tinytable::style_tt(i = "notes", fontsize = 0.75)
+
+```
+
+The first model in @tbl-legit shows that overall confidence in elections among those who read the treatment vignette was significantly (statistically) greater than those who read the control, on average and netting out the effects of partisanship and legitimacy beliefs.
+Democratic partisanship remains marginally significant at $90\%$ confidence level ($p = 0.055$) compared to the reference group (Independents).
 Not believing the 2020 election of Joe Biden was legitimate is negatively associated with confidence in elections.
@@
 
-Thus far, publicized announcements that election officials will be targeting veterans in their recruitment efforts does quite a bit to improve confidence in elections outside of one's local area (or, at least for elections held in Maricopa County, AZ), especially among those who believed the 2020 election results were illegitimate.
-While distrust is one concern during the pre-election period, it is not the only concern that arises in anticipation of US elections; the public must feel confident that voters are safe to cast a ballot in person.
-The survey included questions^[See @tbl-4 in Appendix A] that allows me to assess whether those in the treatment condition expressed less concern for violence and more confidence in voter safety compared to those in the control condition.
-```{r}
-#| label: fig-safety-bars
-#| layout-ncol: 1
-#| layout-nrow: 2
-#| fig-cap: "Safety Concerns and Confidence by Treatment Condition"
-#| fig-subcap: 
-#|   - "Concern for Violence while voting in Maricopa County, AZ Elections"
-#|   - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"
+While confidence in elections is one concern, it is not the only concern that arises in anticipation of US elections; the public must feel confident that voters are safe to cast a ballot in person.
+The survey included questions^[See @tbl-6 in Appendix A] that allowed me to assess whether those in the treatment condition expressed less concern for violence and more confidence in voter safety compared to those in the control condition.
+
+```{r}
+#| label: barplot-setup
+#| include: false
 
@@
 
+```
+
+```{r}
+#| label: fig-safety1
+#| layout-nrow: 2
+#| fig-cap: "Safety Concerns by Treatment Condition"
+#| fig-subcap:  
+#|   - "Concerns for Violence"
+#|   - "Confidence in Voter Safety"
+
 bar_q25
@@
 
-Briefly reviewing @fig-safety-bars, those in the treatment condition felt less concern over the potential for violence compared to those in the control.
+Briefly reviewing @fig-safety1, those in the treatment condition felt less concern over the potential for violence compared to those in the control.
+
 As for confidence in voter safety at election sites, it appears that more respondents in the treatment condition expressed that they were "Very confident" compared to those in the control, by approximately $8$ percentage points.
@@
 In order to assess whether that was the case, I conducted an ordered logistic regression on the relevant items using the experimental condition as a dichotomous predictor.
-
-Those in the treatment condition had lower probability to express that they were 'Very' or 'Somewhat' concerned for violence in Maricopa County, AZ Elections, yet higher probability of expressing 'Not too' or 'Not at all' concerned.
-As for confidence in voter safety, moving from treatment to control, the difference in predicted probability of a respondent selecting "Very Confident" was $0.08$.
-@tbl-preds-diff1 and @tbl-preds-diff2 show the significant differences in predicted probabilities at 95$\%$ confidence^[The same models were run for items pertaining to safety concerns in one's local area but results of the treatment were not significantly different from the control.
-See Appendix D for full results table of ordinal logistic regression].
 
@@
 #| label: tbl-preds-diff1
-#| tbl-colwidths: 80
+#| tbl-colwidths: [80]
+#| tbl-pos: 'H'
 #| tbl-cap: "Difference in Predicted Probabilities in Concern for violence, Threats of Violence, or Intimidation between Treatment and Control"
@@
 
+Shown in @tbl-preds-diff1, those in the treatment condition had lower probability to express that they were 'Very' or 'Somewhat' concerned for violence in Maricopa County, AZ Elections, yet higher probability of expressing 'Not too' or 'Not at all' concerned.
+
 ```{r}
 #| label: tbl-preds-diff2
-#| tbl-colwidths: 80
+#| tbl-colwidths: [80]
+#| tbl-pos: 'H'
 #| tbl-cap: "Difference in Predicted Probabilities in Confidence that voters will be safe to vote in-person between Treatment and Control"
@@
 
-\newpage
+As for confidence in voter safety in @tbl-preds-diff2, moving from treatment to control, the difference in predicted probability of a respondent selecting "Very Confident" was $0.08$.
+Both tables show the significant differences in predicted probabilities at 95$\%$ confidence^[The same models were run for items pertaining to safety concerns in one's local area but results of the treatment were not significantly different from the control.
+See Appendix E for full results table of ordinal logistic regression].
+These findings support both H~4a~ and H~4b~ respectively, permitting rejection of the null for each hypothesis.
+
+## Discussion
+
+The research question emerged in light of the recent surge of efforts nationwide to recruit veterans to serve as election workers [@lawrence2022; @wentling2024] midst an environment where election insecurities were heightened and intensified.
+Heightened insecurities in anticipation of upcoming elections do not merely pertain to the election outcome (e.g., who wins), but to one's general sense of confidence in the administration of elections, the integrity of the electoral process, and to the safety of casting a ballot in-person.
+This study demonstrated that information neutral to the trustworthiness of election administration can not only improve trust in elections, but simultaneously reduce distrust in elections.
+Those who were presented information about veteran recruitment efforts reported greater trust that votes will be counted accurately, that election staff will competently administer elections, that election technology will be secure from nefarious tampering, and that the process will be fair for all involved.
+Moreover, those presented with information about veteran recruitment efforts reported lower expectations that electoral fraud will occur.
+They also felt that election sites would be safe for voters to cast a ballot in person and were less concerned about potential violence compared to those who were not presented information about veteran recruitment efforts.
+
+Confidence in elections was greater among those who read the treatment vignette announcing efforts to recruit veterans to work as election staff and volunteers, but this effect was conditional on whether survey questions asked about elections Maricopa County, AZ.
+When survey questions asked about elections in one's local area, confidence in elections among the treatment group was not significantly different from the control group.
+However, the sample's confidence in their local area elections was high in general relative to elections in Maricopa County, AZ (@fig-dist).
+The results presented here suggest that the effect of the veteran cue in the treatment vignette is compensatory.
+That is, the gap in confidence in local elections and elections in Maricopa County is reduced by the veterans cue, therefore compensating for the otherwise lower confidence and greater insecurity in Maricopa County elections.
+
+A question lingers about whether some antecedent mechanism transmits (i.e., mediates) the effects of the veteran treatment vignette to the outcome.
+To put simply, this study reiterates that there *is* something special about veterans in particular that elicits greater confidence in elections, but cannot go further in determining exactly *what* that special something might be.
+Factors that *moderate* the relationship of the treatment on the outcome of interest are likely plenty, but one can only offer conjecture of a *mediator* driving results.
+
+One potential explanation is that veterans, and all those who serve in the military, potentially function as a national symbol.
+The group is abstract just as the nation is abstract, and the potency of the veteran group emulates the potency of a national symbol.
+Recall Benedict Anderson's [-@anderson2006] meditation on the Tomb of the Unknown Soldier, "...saturated with ghostly *national* imaginings" [-@anderson2006, 9, emphasis original].
+In various studies, national symbols such as the flag, the national anthem, or even mere appeal to national identity have potent, yet variable, effects on different outcomes [@schatz2007; @butz2007; @kemmelmeier2008; @butz2009; @gangl2016; @kalmoe2016; @levendusky2018].
+It is plausible that military service members and veterans function in much the same way---as a symbol of national loyalty, pride, and nationalism for people to praise and revere out of a sense of duty prescribed by social norm and reinforced by national sentiment.
+As such, it may be the case that the treatment effect on confidence in elections is mediated through an affective response to a national symbol---in this case, veterans.
+The veteran cue may indeed stimulate national sentiment and subsequently boost confidence in elections.
+
+In results presented here, confidence in elections is associated with greater confidence among those in the treatment group, but neither vignette conveys information about the procedures or practices meant to safeguard election integrity; nothing in the treatment suggests to respondents that election integrity would be improved by recruiting veterans.
+Arguably, the results presented here speak to the "emotional pathway" mentioned in @gaudette2025 so long as we assume that there's an inherent appeal to national sentiment (e.g., nationalism, patriotism) by use of veterans[^13].
+Importantly, if the veterans treatment is mediated by stimulation of affect for nation or national identity, then comparable stimulation of national sentiment unrelated to veterans should produce similar results via this "emotional-pathway".
+However, appeals to national sentiment by use of sterile national symbols (e.g., banal presentation of the U.S.
+flag, playing of the national anthem) may not have the same affective influence on confidence in elections.
+
+[^13]: The study by @gaudette2025 included an experiment that examined the contrast between "emotional" versus "informational" appeals on trust in elections and beliefs that election fraud is prevalent.
+Authors presented one of two video messages created by election administration officials in either Virginia or Maricopa County, AZ; the former was "emotions-based" in that it provided little to no information about the voting process or election administration, whereas the latter provided, "...specific information about the processes used to ensure the integrity of the vote with no appeal to emotion or patriotism" [-@gaudette2025, 13].
+
+In a similar vein, it is plausible that certain political apprehensions are nullified insofar as veterans as a group are generally perceived as 'apolitical'---which itself may be enough to engender favor among the mass public [@krupnikov2022].
+Current and former military service members may be viewed by the public generally as 'apolitical', especially in comparison to practically any other social group.
+Indeed, an 'apolitical' reputation has been long desired by military leaders and top brass [@lagrone2019; @garamone2016; @garamone2016a; @baldor2020] despite evidence to the contrary [@betros2001; @mcnerney2006].
+Nevertheless, the putative 'apolitical' nature of military service may generalize to veteran service members, and increase confidence in elections based on the assumption that veterans uphold a commitment to ensure election integrity above their own personal loyalties, partisanship, or politics.
+Prior research has relied on the assumption that such a "*group-based*" norm persists among military members, which prescribes that the military is, or ought to be, apolitical [@mullinix2022].
+Although, the extent to which this perception generalizes widely among the mass public about the military in general, or about current and former service members in particular, has yet to be examined.
+Given recent events of far more overt politicization of the U.S.
+military [@baldor2025; @baldor2025a; @baldor2025b; @baldor2025c; @thomas2025], it would be useful for future research to consider whether perceptions about the military generally, and military leaders in particular, generalize to perceptions about current and former military service members.
+Especially insofar as such attitudes relate to confidence in the electoral process and administration.
+
+It is difficult to compare magnitude of effect with other studies given that the item number, item wording, measurement, and computation of confidence in elections is unique across most individual studies to include this one.
+For instance, @gaudette2025 doesn't compose multiple items into a single composite measure, but subtracts pre-treatment values from post-treatment values for single-item measures with Likert-style response options.
+Whereas @clayton2023 develops a scale referred to as "Trust in American electoral process" by taking the mean from three items.
+The item wording of that scale is markedly similar to the items used to compose the trust scale of this study, but the range of response options differs considerably.
+Thus, while most studies examining public confidence in elections often include the core question "How confidence are you that your vote \[will be/was\] counted as you intended in the most recent election?", the different ways that researchers measure and compute variable scores on the outcome most often produces results that are, unfortunately, sample dependent.
+The study of public confidence in elections is in desperate need of a standard method of measurement, or even a screened and validated item bank, and this study may be seen as a baby step to that end.
+
+That being said, this study generally emulates treatment effects of comparable studies in the literature.
+@gaudette2025 found positive effects of official messaging from election officials on various items measuring trust in elections and expectations of electoral fraud.
+Similarly, @clayton2023, confined to a sample of Republican participants, found positive influence on perceptions of 2020 election legitimacy and trust in the American electoral process from official messaging by Republican politicians reaffirming the 2020 election results.
+
+The data of the current study is limited in helping to discern whether the treatment garners greater confidence in elections uniformly across different racial or ethnic groups given that the largest proportion of the sample identified their race as White (77%).
+It is reasonable to suspect that the treatment vignette might differ by race and ethnicity, but the sample is insufficient to make such generalizations.
+Nevertheless, attitudes about veterans that differ by group may play an important role in determining whether publicized efforts to recruit military veterans boosts confidence in elections uniformly or whether the effect is merely partial to certain segments of the population.
+
+It is definitely plausible that the public, to some unknown extent, associates a particular gender or race, or both, with former and active military members which may, in turn, mediate the effect of the veteran cue.
+Additionally, I can't be sure as to whether respondent's views of the military generalize to attitudes about active service members and veterans.
+However that is a separate question about the source of public opinion about military members themselves beyond the scope of this study.
+
+There's scant research or evidence available to postulate a well-formed theory on the mechanism underlying the expected effects of veterans as a group on attitudes about institutions and processes, rather than on attitudes about persons or groups.
+That is to say, there's not much research on how the public feels, or what they think, about former members of the U.S.
+Armed Forces.
+
+In their research examining whether groups differed in attitudes about veterans, @kleykamp2018 could only speculate as to why levels of support were lowest among Hispanic and Black respondents.
+Their study was distinctive in that it stands as a rare case in which public attitudes about veteran military members was the specific focus of inquiry as opposed to studies that examine public opinion about the military in general.
+Other research has found that attitudes about the U.S.
+military generally---though not about active or veteran military service members in particular---differs by race and ethnicity to varying extents, but also could not supply reason for one groups' sentiment over another^[Note, however, that the sample examined by @nichols2015 was constrained to Texas residents, and the military-related issues concerned, among other things, favor for reinstatement of a military draft, support for allowing undocumented immigrants who live in the U.S.
+to serve in the U.S.
+Armed Forces, and whether undocumented immigrants should be granted U.S.
+citizenship as a result of military service.
+Although the authors found high overall support for the military as an institution, the other military-related attitudes of interest diverge far from public opinion about veterans.
+As such, differential effects found among different racial or ethnic groups likely have little to do with attitudes about former or active military service members.] [@nichols2015].
+
+Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly.
+One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S.
+military as an institution in general.
+Some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally.
+In one such study by @tsai2021, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes (e.g., compassion) toward homelessness and PTSD among the veteran population, but not among the general adult population.
+Additionally, Republican partisans tended to show greater support for federal funding for homelessness and PTSD research when the reference population was military veterans.
+That study, however, suggests that the effect of the veteran status cue is sensitive to the topic in question.
+
+Perhaps unsurprisingly, military veterans appear to be uniquely deserving in the eyes of Republican partisans [@tsai2021; @mcdermott2015; @richardson2022].
+As such, military veteran status may qualify favorable attitudes among Republican partisans whereas their regard for other non-veteran groups might otherwise express contempt or indifference.
+This further indicates a need for research to determine an underlying mechanism explaining why, and for whom, veterans incur special favor.
+
+## Limitations
+
+The bluntness of the experimental stimulus and survey items don't allow us to establish exactly what it is about military veterans in particular that cues stronger confidence in elections.
+No survey items assessed public attitudes about military veterans specifically, pre- nor post-treatment.
+This unfortunately leaves no room for me to postulate and examine any potential mechanisms underlying results.
+
+It should be noted that these results are limited to one's expectations in anticipation of election night.
+Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
+Moreover, It is yet unclear whether actually encountering and interacting with veterans working as staff or volunteers at election sites does much to improve voter confidence after election night compared to anyone else.
+It may be the case that assumptions that veterans are filling spots as election workers and volunteers simply primes positive expectations as one heads into an election site, potentially improving voters perceptions of their own experience on the way out.
+Further research would be needed to test such an idea.
+
+The setting of the vignette and specified in survey items might raise additional concerns on whether results are generalizable.
+Naming a specific county in the vignette adds in a potentially influential factor unaccounted for in the survey; some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S.
+they know nothing about.
+Naming a real and somewhat salient county potentially undermines confidence that the treatment effects are solely attributable to veterans to an unknown degree.
+Simply put, there may be something special about Maricopa County, AZ in particular that generalizes across attitudes of trust or distrust in elections.
+
+Arguably, however, Maricopa County is indicated as the setting in both the treatment and control vignettes, thus the only actual difference between conditions is constrained to the target group being recruited.
+Future research may employ vignettes naming a fictional U.S.
+county to hopefully eliminate the setting as a concern.
+Alternatively additional survey items that ask directly about one's knowledge or sentiment about the county in question could inform researchers on whether the named county imposes any undue influence at all, or whether the setting is associated with other factors such as partisanship.
+
+As stated previously, the survey was fielded on a non-probability sample of 1,287 U.S.
+citizens 18 years of age or older.
+The results presented here are not assumed to be generalizable to the national population.
+It may be feasible to weigh the sample to demographics of the population at the time the survey was fielded, but this is unnecessary for the experimental purpose of the study.
+If similar findings complement or replicate these results, then the expense of drawing samples more representative of the national population may be justified.
+At this stage, however, the results are limited to demonstrating treatment effects.
+
+Note also that the measurement items of the components trust and distrust, and the method of computing scores for the dependent variable, confidence in elections, are unique to this study but falls under the methodological framework of Classical Test Theory (CTT).
+Although survey measurement items were either directly drawn from or inspired by similar survey items found in various other surveys (e.g., SPAE, Pew), the question wording, response choices, coding, and computation of sum scores of the dependent variable are specific, thus rendering measurement of the hypothetical constructs of interest (i.e., trust, distrust) less comparable across similar studies that profess measurement of similar constructs [@widaman2024].
+Namely, trust, distrust, or confidence in elections as defined and measured here.
 
@@
 ```{r}
-#| label: tbl-4
-#| tbl-cap: "Survey Items and Response Options"
+#| label: tbl-6
+#| tbl-cap: "Pre-Treatment Survey Items and Response Options"
 #| tbl-colwidths: [70, 30]
+#| tbl-pos: H
 
@@
 ## Sample Demographics
-
-The median age was 46 (mean age was $47$), $51.7\%$ ($n = 658$) women, $47\%$ ($n = 598$) men, and approximately $1.3\%$ who identified as either Non-binary/third gender ($n = 7$) or preferred not to say ($n = 9$).
-A large proportion of the sample identified as White or Caucasian ($n = 975, 76.65\%$), while all other non-White respondents comprised $27.83\%$ ($n = 297$) of the sample.
-Those who held a graduate level degree (e.g., Master's, Doctorate, or Professional level) comprised $13\%$ of the sample; those with either degree at the Associate or Bachelor's level comprised $36.24\%$, while $22.25\%$ had some college but no degree; and $28.46\%$ had either a high school level or equivalent education or less than high school.
-The largest proportion of the sample identified as Democrat at $44.64\%$, followed by Republicans at $42.59\%$.
-The proportion of true Independents^[Independent 'leaners' were grouped into the respective party affiliation in which they lean.] was $12.78\%$.
 
@@
 #| tbl-cap: "Sample Demographics"
-#| tbl-pos: 'H'
+#| tbl-colwidths: [70]
+#| tbl-pos: H
 
 # descriptive stats of categorical variables
-# best method for html document
+# gtsummary method
+gtsummary::theme_gtsummary_compact()
+
 tbl.desc <- data |>  
-  labelled::set_variable_labels(
-    age_4cat = "Age group",
-    gender_3cat = "Gender",
-    race2 = "Race/Ethnicity",
-    race_wnw = "White or Non-White",
-    educ_4cat = "Education",
-    partyid_3cat = "Party ID",
-    milrelation  = "Military Relation"
-  ) |> 
   gtsummary::tbl_summary( 
     by = group,
+    label = list(
+      age_4cat = "Age group, in years",
+      gender_3cat = "Gender",
+      race = "Race",
+      hisp = "Hispanic, Latino, or Spanish origin?",
+      educ_4cat = "Education"
+      ),
     include = c(
@@
       gender_3cat,
-    race2,
-    race_wnw,
-    educ_4cat, 
-    partyid_3cat,
-    milrelation),
+      race,
+      hisp,
+      educ_4cat
+      ),
     statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
@@
     missing_text = "NA") |> 
-  gtsummary::add_n() |> 
   gtsummary::add_overall() |> 
-  gtsummary::modify_header(label = "**Demographic**") |> 
+  gtsummary::modify_header(label = "**Variable**") |> 
   gtsummary::bold_labels()
 
-gtsummary::as_kable_extra(tbl.desc, booktabs = T) |>
-  kableExtra::add_footnote(
-    label = "Independents do not identify nor 'lean' toward either political party") |> 
-  kableExtra::kable_styling(
-    font_size = 9, 
-    protect_latex = T)
-
-# gtsummary::as_gt(tbl.desc) |>  
-#   gt::tab_footnote(
-#     footnote = "Independents do not identify nor 'lean' toward either political party",
-#     placement = "left"
-#     ) |>  
-#   gt::cols_align(align = 'left', columns = everything()) |> 
-#   gt::tab_options(
-#     table.font.size = "small",
-#     data_row.padding = gt::px(1)
-#   )
-
-```
-
-## Test of Random Assignment to Experiment Condition
+tbl.desc |>
+  gtsummary::as_tibble() |>
+  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
+                "**Control (N = 637)**" = "**Control**  \nN = 637",
+                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
+  tinytable::tt(theme = "spacing") |>
+  tinytable::format_tt(markdown = T) |>
+  tinytable::format_tt(replace = " ") |>
+  tinytable::style_tt(fontsize = 0.70, align = "lccc")
+
+```
+
+{{< pagebreak >}}
+
+```{r}
+#| label: tbl-demog2
+#| tbl-cap: "Sample Demographics"
+#| tbl-colwidths: [70]
+#| tbl-pos: H
+
+tbl.desc2 <- data |>  
+  gtsummary::tbl_summary( 
+    by = group,
+    label = list(
+      partyid_3cat = "Party ID",
+      ideo_3cat = "Political Ideology",
+      ideolean = "If R had to choose Political Ideology",
+      voted2020 = 'Did R Vote in 2020 Election',
+      choice2020 = 'Vote Choice in 2020 Election'),
+    include = c(
+      partyid_3cat,
+      ideo_3cat, 
+      ideolean, 
+      voted2020, 
+      choice2020),
+    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
+    missing = "ifany",
+    missing_text = "NA") |> 
+  gtsummary::add_overall() |> 
+  gtsummary::modify_header(label = "**Variable**") |> 
+  gtsummary::bold_labels()
+
+tbl.desc2 |>
+  gtsummary::as_tibble() |>
+  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
+                "**Control (N = 637)**" = "**Control**  \nN = 637",
+                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
+  tinytable::tt(theme = "spacing") |>
+  tinytable::format_tt(markdown = T) |>
+  tinytable::format_tt(replace = " ") |>
+  tinytable::style_tt(fontsize = 0.70, align = "lccc")
+
+```
+
+{{< pagebreak >}}
+
+```{r}
+#| label: tbl-demog3
+#| tbl-cap: "Sample Demographics"
+#| tbl-pos: H
+
+tbl.desc3 <- data |>  
+  gtsummary::tbl_summary( 
+    by = group,
+    label = list(
+      milserv1 = "Military Service",
+      milserv2 = "Current Active Duty",
+      milservfam = "Military Service within Family?"
+      ),
+    include = c(
+      milserv1,
+      milserv2, 
+      milservfam), 
+    type = list(
+      milserv1 ~ "categorical",
+      milserv2 ~ "categorical",
+      milservfam ~ "categorical"
+      ),
+    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
+    missing = "ifany",
+    missing_text = "NA") |> 
+  gtsummary::add_overall() |> 
+  gtsummary::modify_header(label = "**Variable**") |> 
+  gtsummary::bold_labels()
+
+tbl.desc3 |>
+  gtsummary::as_tibble() |>
+  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
+                "**Control (N = 637)**" = "**Control**  \nN = 637",
+                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
+  tinytable::tt(theme = "spacing", width = 1) |>
+  tinytable::format_tt(markdown = T) |>
+  tinytable::format_tt(replace = " ") |>
+  tinytable::style_tt(fontsize = 0.70, align = "lccc")
+
+```
+
+{{< pagebreak >}}
+
+# Appendix B: Test of Random Assignment to Experiment Condition {.appendix}
 
@@
 
-# use `gtsummary` package to build regression table, then output as tibble
-logit_tab <- gtsummary::tbl_regression(
-    m1,
-    intercept = F,
-    label = list(
-      age_4cat ~"Age",
-      gender_3cat ~ "Gender",
-      race2 ~ "Race/Ethnicity",
-      educ_4cat ~ "Education",
-      partyid_3cat ~ "Party ID")) |>
-  gtsummary::bold_labels() |>
-  # gtsummary::show_header_names()
-  gtsummary::modify_header(
-    label = " ",
-    stat_nevent = "**Treatment N**") |>
-  # output as_tibble
-  gtsummary::as_tibble() |>
-  # omit p.values
-  dplyr::select(-4)
-
-# transform tibble dataframe into `tinytable` and format as markdown
-# replace NA with blank " " (or "-" if desired)
-logit_tab <- tinytable::tt(logit_tab, width = 0.8) |> 
-  tinytable::format_tt(markdown = T) |> 
-  tinytable::format_tt(replace = " ")
-
-# create 2nd table containing only logit model fit statistics
-# using custom function, get logit regression model fit stats... 
-gof_stats <- lrm.gof.stats(m1) |> 
-  # omit certain stats (saves space)
-  dplyr::select(
-    nobs, logLik, df, chisq, P..chi., deviance, null.deviance,
-    -AIC, -BIC, -df.null, -df.residual) |> 
-  # rename column variables
-  dplyr::rename(
-    "Num.Obs"       = "nobs",
-    "Null Deviance" = "null.deviance",
-    "Deviance"      = "deviance",
-    "DF"            = "df",
-    "Log.Lik"       = "logLik",
-    "\\chi^2"       = "chisq",
-    "P(>\\chi^2)"   = "P..chi."
+cmp <- c(
+  "age_4cat35-54"  = "35-54",
+  "age_4cat55-74"  = "55-74",
+  "age_4cat75-85+"  = "75-85+",
+  "gender_3catFemale"  = "Female",
+  "gender_3catOther/Refused"  = "Other/Refused",
+  "race2Asian"  = "Asian",
+  "race2Black"  = "Black",
+  "race2Other"  = "Other",
+  "race2Hispanic"  = "Hispanic",
+  "race2American Indian"  = "American Indian",
+  "educ_4catSome college no degree"  = "Some college no degree",
+  "educ_4catCollege degree"  = "College degree",
+  "educ_4catPostgraduate degree"  = "Postgraduate degree",
+  "partyid_3catRepublican"  = "Republican",
+  "partyid_3catDemocrat"  = "Democrat"
+)
+
+gm <- list(
+  list("raw" = "nobs", "clean" = "N", "fmt" = 0),
+  list("raw" = "logLik", "clean" = "Log.Lik.", "fmt" = 3),
+  list("raw" = "deviance", "clean" = "Deviance", "fmt" = 2),
+  list("raw" = "null.deviance", "clean" = "Deviance Null", "fmt" = 2),
+  list("raw" = "df", "clean" = "DF", "fmt" = 0),
+  list("raw" = "chisq", "clean" = "Chi2", "fmt" = 3),
+  list("raw" = "P(>chisq)", "clean" = "P(>chisq)", "fmt" = 3))
+
+tab.logit <- modelsummary::modelsummary(
+  list("log(OR)" = m1),
+  output = "tinytable",
+  estimate = "{estimate}, [{conf.low}, {conf.high}]",
+  statistic = NULL,
+  coef_map = cmp,
+  gof_function = lrm.gof.stats,
+  gof_map = gm,
+  gof_omit = "AIC|BIC|F|RMSE",
+  width = c(2,1)
   ) |> 
-  # pivot into two column long-form dataframe
-  tidyr::pivot_longer(cols = everything(),names_to = " ", values_to = '**log(OR)**') |>
-  # pipe into tinytable
-  tinytable::tt(width = 0.8) |> 
-  # ensure rows with math text are identified and formatted as math (i.e., $..$)
-  tinytable::format_tt(i = c(4,5), j = 1, math = T)
-
-# using `rbind2` function, bind 2nd table at bottom of first table 
-tinytable::rbind2(logit_tab, gof_stats, use_names = F, headers = F) |> 
-  # add horizontal line just above fit stats
-  tinytable::style_tt(i = 26, line = "t", line_color = "black", line_width = 0.1) |>
+  tinytable::strip_tt(line = TRUE)
+
+tab.logit |> 
+  tinytable::group_tt(i = list(
+    "Age" = 1,
+    "Gender" = 4,
+    "Race" = 6,
+    "Education" = 11,
+    "Party ID" = 14), 
+    indent = 2
+    ) |> 
+  tinytable::style_tt(i = 20, line = "b", line_color = "black") |> 
   # adjust fontsize of text within table
-  tinytable::style_tt(fontsize = 0.8) |>
+  tinytable::style_tt(fontsize = 0.65, align = "lc") |>
   # finally, format markdown and blank out any NA fillers
@@
 #| tbl-cap-location: top
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
+#| tbl-pos: H
 
@@
   tinytable::style_tt(
-    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    fontsize = 0.65 # fontsize of text in table in em units (0.75*default)
     ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
+  tinytable::style_tt(i = "notes", fontsize = 0.65, align = "l")
 
@@
 #| tbl-cap: "Unit-level predicted probabilities of selecting response or higher comparing experiment condition"
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
+#| tbl-pos: H
 
@@
   dplyr::as_tibble() |> 
+  dplyr::mutate('Pr(>|z|)' = dplyr::case_when(
+    p.value < 0.05 ~ '<0.05',
+    p.value < 0.01 ~ '<0.01',
+    .default = as.character(p.value)
+  )) |> 
   select(group, condition, 
-         estimate, std.error, statistic,  p.value,
+         estimate, std.error, statistic, 'Pr(>|z|)',
          conf.low, conf.high) |> 
@@
   tinytable::style_tt(
-    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
-    ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
+    fontsize = 0.65, # fontsize of text in table in em units (0.75*default)
+    align = "llccccc") |> 
+  tinytable::style_tt(i = "notes", fontsize = 0.65, align = "l")
 
@@
 #| tbl-cap: "Unit-level predicted probabilities of selecting response or higher conditional to the Treatment experiment condition"
-#| tbl-colwidths: 80
-#| tbl-pos: 'H'
+#| tbl-pos: H
 
@@
   tinytable::style_tt(
-    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    fontsize = 0.65, # fontsize of text in table in em units (0.75*default)
+    align = "llccccc"
     ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
+  tinytable::style_tt(i = "notes", fontsize = 0.65)
 

### 2025-07-18 response_memo.qmd
modified revisions

@@
 title: "Response Memo"
+author: Isaiah Espinoza
 format: 
   hikmah-response-typst:
+    keep-typ: true
     toc: false
-    mainfont: TeX Gyre Pagella
+    mainfont: STIX Two Text
     fontsize: 11pt
@@
 
-I thank the Reviewers for taking time to provide their thoughtful and constructive comments.
+I thank the Reviewers for taking time to provide their thoughtful and constructive comments to my research paper "*Effect of Recruiting Military Veterans on Confidence in 2024 US Elections*".
 I revised much of the initial manuscript by restructuring certain sections and added clarification where needed.
@@
 No survey items assessed public attitudes about military veterans specifically, pre- nor post-treatment.
+Of course, inquiring into attitudes about veterans pre-treatment could prime respondents in a way that would contaminate the experiment.
+Moreover, responses to questions about veterans post-treatment might, indeed, be influenced by the treatment.
 This unfortunately leaves no room for me to postulate and examine any potential mechanisms underlying results.
+That being said, attempting to understand and explain why veterans are viewed favorably in general goes beyond the scope of this study.
+This study relied on the literature showing that overwhelmingly positive perceptions of veterans persists among the public *writ large*.
+It is surely important for future work to focus on understanding why veterans are generally favored in order to posit a potential mechanism that transmits the effect of the veterans cue on confidence in elections.
 :::
@@
 
-```{=typst}
-#sym.dots.h.c
-```
+($...$)
+
 > H~2~: Differences in confidence in elections in one's local area and confidence in elections in Maricopa County, AZ, will be smaller among those who are presented with an announcement that election officials are recruiting miilitary service veterans to work as election staff and volunteers compared to those presented with an announcement of recruitment efforts that do not mention military veterans.
 
-```{=typst}
-#sym.dots.h.c
-```
+($...$)
+
 > H~3~: Among those who refute the legitimacy of the 2020 election results, those presented with an announcement that election officials are recruiting veteran service members for election jobs will be associated with greater levels of confidence in elections compared to those presented with an announcement of recruitment efforts that do not mention military veterans.
@@
 Armed Forces.
-
-In their research examining whether groups differed in attitudes about veterans, @kleykamp2018 could only speculate as to why levels of support were lowest among Hispanic and Black respondents.
-Their study was distinctive in that it stands as a rare case in which public attitudes about veteran military members was the specific focus of inquiry as opposed to studies that examine public opinion about the military in general.
-Other research has found that attitudes about the U.S.
-military generally---though not about active or veteran military service members in particular---differs by race and ethnicity to varying extents, but also could not supply reason for one groups' sentiment over another^[Note, however, that the sample examined by @nichols2015 was constrained to Texas residents, and the military-related issues concerned, among other things, favor for reinstatement of a military draft, support for allowing undocumented immigrants who live in the U.S.
-to serve in the U.S.
-Armed Forces, and whether undocumented immigrants should be granted U.S.
-citizenship as a result of military service.
-Although the authors found high overall support for the military as an institution, the other military-related attitudes of interest diverge far from public opinion about veterans.
-As such, differential effects found among different racial or ethnic groups likely have little to do with attitudes about former or active military service members.] [@nichols2015].
-
-Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly.
-One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S.
-military as an institution in general.
-Some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally.
-In one such study by @tsai2021, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes (e.g., compassion) toward homelessness and PTSD among the veteran population, but not among the general adult population.
-Additionally, Republican partisans tended to show greater support for federal funding for homelessness and PTSD research when the reference population was military veterans.
-That study, however, suggests that the effect of the veteran status cue is sensitive to the topic in question.
-
-Perhaps unsurprisingly, military veterans appear to be uniquely deserving in the eyes of Republican partisans [@tsai2021; @mcdermott2015; @richardson2022].
-As such, military veteran status may qualify favorable attitudes among Republican partisans whereas their regard for other non-veteran groups might otherwise express contempt or indifference.
-This further indicates a need for research to determine an underlying mechanism explaining why, and for whom, veterans incur special favor.
 :::
@@
 
-To address these concerns, I include the following text in the '**Limitations**' section
+I share [**Reviewer 1**]{.memo-reviewer-inline}'s concerns regarding whether results are generalizable.
+I do interpret results as somewhat limited, and accordingly aim to limit what can be justifiably said in that regard.
+
+I acknowledge this limitation of the results with the excerpt below.
+Importantly, I also clarify that the source of this limitation does not arise from specifying the location in the vignette as Maricopa County, AZ, but rather results are limited because the survey items ask specifically about elections in Maricopa County, AZ.
 
 ::: memo-excerpt
-The setting of the vignette and specified in survey items might raise additional concerns on whether results are generalizable.
-Naming a specific county in the vignette adds in a potentially influential factor unaccounted for in the survey; some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S.
-they know nothing about.
-Naming a real and somewhat salient county potentially undermines confidence that the treatment effects are solely attributable to veterans to an unknown degree.
-Simply put, there may be something special about Maricopa County, AZ in particular that generalizes across attitudes of trust or distrust in elections.
+The election setting specified in survey items might raise concerns about whether results are generalizable to other places or counties nationwide.
+That is, whether promoting the recruitment of veterans in *any* county nationwide would similarly increase confidence in elections, or whether effects of the veteran cue is limited to elections in Maricopa County, AZ or similar places.
 
-Arguably, however, Maricopa County is indicated as the setting in both the treatment and control vignettes, thus the only actual difference between conditions is constrained to the target group being recruited.
-Future research may employ vignettes naming a fictional U.S.
-county to hopefully eliminate the setting as a concern.
-Alternatively additional survey items that ask directly about one's knowledge or sentiment about the county in question could inform researchers on whether the named county imposes any undue influence at all, or whether the setting is associated with other factors such as partisanship.
+Maricopa County was specified *in the vignettes* because of the increased scrutiny levied toward elections admin there after 2020.
+This doesn't mean, necessarily, that Maricopa County, AZ, would therefore be salient to respondents generally and for that reason, if at all.
+There's no problem in asking about confidence in elections nationwide and in local elections while still keeping Maricopa County as the setting in the vignettes; even though the setting is specified in the vignettes, the setting acts only as a stand-in for counties nationwide.
+Maricopa County is indicated as the setting in both the treatment and control vignettes, thus the only actual difference between conditions is constrained to the target group being recruited.
 
-As stated previously, the survey was fielded on a non-probability sample of 1,287 U.S.
-citizens 18 years of age or older.
-The results presented here are not assumed to be generalizable to the national population.
-It may be feasible to weigh the sample to demographics of the population at the time the survey was fielded, but this is unnecessary for the experimental purpose of the study.
-If similar findings complement or replicate these results, then the expense of drawing samples more representative of the national population may be justified.
-At this stage, however, the results are limited to demonstrating treatment effects.
-
-Note also that the measurement items of the components trust and distrust, and the method of computing scores for the dependent variable, confidence in elections, are unique to this study but falls under the methodological framework of Classical Test Theory (CTT).
-Although survey measurement items were either directly drawn from or inspired by similar survey items found in various other surveys (e.g., SPAE, Pew), the question wording, response choices, coding, and computation of sum scores of the dependent variable are specific, thus rendering measurement of the hypothetical constructs of interest (i.e., trust, distrust) less comparable across similar studies that profess measurement of similar constructs [@widaman2024].
-Namely, trust, distrust, or confidence in elections as defined and measured here.
+The problem arises because the subsequent survey questions ask specifically about elections in Maricopa County; I cannot attest to whether the effect of the veterans cue generalizes to confidence in elections in places other than Maricopa County.
+To be clear, this limitation arises because *subsequent survey questions ask respondents to consider elections in Maricopa County specifically*.
 :::
@@
 
-There was a sudden push to target veterans for recruitment efforts $...$
+There was a sudden push to target veterans for recruitment efforts ($...$)
 
-One can speculate that $...$
+One can speculate that ($...$)
 
@@
 
-A person who is certain that electoral fraud will occur clearly lacks trust in elections; an expectation that electoral fraud will occur necessarily implies a lack of trust in elections regardless of positive expressions of trust.
-However, the reverse isn't also true; expressing a lack of trust in elections *doesn't necessarily imply* an expectation that electoral fraud will occur.
-Rather, a lack of trust implies an absence of assurance in the belief that the process will be conducted fairly and accurately---a lacking quality of certainty around said belief.
-An absence of such assurance denotes a state of *insecurity*.
-Other sources of uncertainty may challenge a person's confidence regarding the integrity of elections independent from anything that would lead them to believe electoral fraud will occur or has occurred.
-However my use of distrust refers to the assured belief that the outcome will be invalid---that outcomes will be independent of the process as prescribed, thus rendering outcomes as arbitrary.
-Specifically, distrust implies assurance in the belief that electoral fraud will occur.
-
 As such, trust and distrust represent opposing degrees of confidence along the same spectrum.
 However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling relatively confident in both respects.
-Accordingly, *equivalent degrees of trust and distrust cancel out*, rendering one relatively more insecure about their expectations of the future despite the fact that they may report feeling confident in either direction respectively.
+Accordingly, *equivalent degrees of trust and distrust cancel out*, rendering one relatively more *insecure* about their expectations of the future despite the fact that they may report feeling confident in either direction respectively.
 When trust and distrust are considered reflective of one's confidence about future expectations, then both can be placed along the same spectrum.
@@
 
-This means that a person's baseline level of confidence in elections must take into account their present degree of distrust---i.e., their expectations of electoral fraud.
-Something may cause a person to have greater expectations that election fraud will occur, which in turn will always lower their trust in elections.
-In contrast, a person's trust in the integrity of the electoral process is reduced by the extent to which they expect that electoral fraud will occur.
-
-Thus, it follows that a person distrusts the integrity of the electoral process to the extent that they are to some extent certain that electoral fraud will occur or has occurred.
-They are, perhaps, poised to discount election results as invalid or illegitimate in advance.
-Either way, both trust and distrust refer to some positive degree of confidence (i.e., assurance) regarding one's expectations.
-They are distinguished by reference to either the normative idea about what *should* come about, or what is *supposed* to come about given the logical structure and integrity of the process.
-If the structure and integrity of some process is coherent and secure, respectively, then the outcome that follows will be valid.
-Should the integrity of that process be damaged or opaque, then the process becomes vulnerable and validity of the results are open to challenge.
 With respect to the administration of U.S.
@@
 
+It is important to emphasize that results are limited to comparison of heterogeneous effects at between confidence in Maricopa County, AZ elections versus and local area elections, and should not be mistaken as demonstrating heterogeneous effects on confidence in elections at the national versus local level.
+
 Despite the limitations noted previously, I added the text below in response to [**Reviewer 2**]{.memo-reviewer-inline}'s concerns on the potential substantive significance of the findings.
@@
 
+## ***Reviewer 2***---***Findings***
+
 ::: memo-reviewer
-***Reviewer 2***---***Findings***: I also encourage more discussion of null results.
+I also encourage more discussion of null results.
 Even where effects are weak or absent, that tells us something important—especially if veteran cues only resonate among certain audiences or in certain electoral contexts.

### 2025-07-18 docs/_tex/index.tex
modified revisions

@@
 on its supposed veracity; a state of certainty with respect to some
-belief or judgement. It is ``\emph{assured}'' because it is one's belief
-that relies on something rather than nothing. Hence quantitative methods
-of the sciences are replete with things such as \emph{confidence}
-intervals around our estimates. Therefore, I understand trust to refer
-to the state or quality of certainty around one's beliefs or
-expectations; the extent to which one is assured of their expectations
-regarding what is or what will be the case.
+belief or judgement. It is ``assured'' because it is one's belief that
+relies on something rather than nothing. Hence quantitative methods of
+the sciences are replete with things such as \emph{confidence} intervals
+around our estimates. Therefore, I understand trust to refer to the
+state or quality of certainty around one's beliefs or expectations; the
+extent to which one is assured of their expectations regarding what is
+or what will be the case.
 
@@
 
-A person who is certain that electoral fraud will occur clearly lacks
-trust in elections; an expectation that electoral fraud will occur
-necessarily implies a lack of trust in elections regardless of positive
-expressions of trust. However, the reverse isn't also true; expressing a
-lack of trust in elections \emph{doesn't necessarily imply} an
-expectation that electoral fraud will occur. Rather, a lack of trust
-implies an absence of assurance in the belief that the process will be
-conducted fairly and accurately---a lacking quality of certainty around
-said belief. An absence of such assurance denotes a state of
-\emph{insecurity}. Other sources of uncertainty may challenge a person's
-confidence regarding the integrity of elections independent from
-anything that would lead them to believe electoral fraud will occur or
-has occurred. However my use of distrust refers to the assured belief
-that the outcome will be invalid---that outcomes will be independent of
-the process as prescribed, thus rendering outcomes as arbitrary.
-Specifically, distrust implies assurance in the belief that electoral
-fraud will occur.
-
 As such, trust and distrust represent opposing degrees of confidence
@@
 confident in both respects. Accordingly, \emph{equivalent degrees of
-trust and distrust cancel out}, rendering one relatively more insecure
-about their expectations of the future despite the fact that they may
-report feeling confident in either direction respectively. When trust
-and distrust are considered reflective of one's confidence about future
-expectations, then both can be placed along the same spectrum.
-Therefore, a lack of confidence denotes insecurity.
-
-This means that a person's baseline level of confidence in elections
-must take into account their present degree of distrust---i.e., their
-expectations of electoral fraud. Something may cause a person to have
-greater expectations that election fraud will occur, which in turn will
-always lower their trust in elections. In contrast, a person's trust in
-the integrity of the electoral process is reduced by the extent to which
-they expect that electoral fraud will occur.
-
-Thus, it follows that a person distrusts the integrity of the electoral
-process to the extent that they are to some extent certain that
-electoral fraud will occur or has occurred. They are, perhaps, poised to
-discount election results as invalid or illegitimate in advance. Either
-way, both trust and distrust refer to some positive degree of confidence
-(i.e., assurance) regarding one's expectations. They are distinguished
-by reference to either the normative idea about what \emph{should} come
-about, or what is \emph{supposed} to come about given the logical
-structure and integrity of the process. If the structure and integrity
-of some process is coherent and secure, respectively, then the outcome
-that follows will be valid. Should the integrity of that process be
-damaged or opaque, then the process becomes vulnerable and validity of
-the results are open to challenge. With respect to the administration of
-U.S. elections, the confident voter expects that votes will be counted
-as voters intend, election staff will competently administer elections,
-election technology will be secure from nefarious tampering, and that
-the process will be fair for all involved.
+trust and distrust cancel out}, rendering one relatively more
+\emph{insecure} about their expectations of the future despite the fact
+that they may report feeling confident in either direction respectively.
+When trust and distrust are considered reflective of one's confidence
+about future expectations, then both can be placed along the same
+spectrum. Therefore, a lack of confidence denotes insecurity.
+
+With respect to the administration of U.S. elections, the confident
+voter expects that votes will be counted as voters intend, election
+staff will competently administer elections, election technology will be
+secure from nefarious tampering, and that the process will be fair for
+all involved.
 
@@
 
-In their research examining whether groups differed in attitudes about
-veterans, Kleykamp, Hipes, and MacLean
-(\citeproc{ref-kleykamp2018}{2018}) could only speculate as to why
-levels of support were lowest among Hispanic and Black respondents.
-Their study was distinctive in that it stands as a rare case in which
-public attitudes about veteran military members was the specific focus
-of inquiry as opposed to studies that examine public opinion about the
-military in general. Other research has found that attitudes about the
-U.S. military generally---though not about active or veteran military
-service members in particular---differs by race and ethnicity to varying
-extents, but also could not supply reason for one groups' sentiment over
-another\footnote{Note, however, that the sample examined by Nichols
-  (\citeproc{ref-nichols2015}{2015}) was constrained to Texas residents,
-  and the military-related issues concerned, among other things, favor
-  for reinstatement of a military draft, support for allowing
-  undocumented immigrants who live in the U.S. to serve in the U.S.
-  Armed Forces, and whether undocumented immigrants should be granted
-  U.S. citizenship as a result of military service. Although the authors
-  found high overall support for the military as an institution, the
-  other military-related attitudes of interest diverge far from public
-  opinion about veterans. As such, differential effects found among
-  different racial or ethnic groups likely have little to do with
-  attitudes about former or active military service members.}
-(\citeproc{ref-nichols2015}{Nichols 2015}).
-
-Other studies have drawn out disparities in public attitudes about
-veterans but in ways that are mostly indirect, i.e., without assessing
-public regard for veterans directly. One overarching issue is that
-there's limited research that differentiates public regard for veteran
-and active military service members from the U.S. military as an
-institution in general. Some studies assess public regard for veterans
-indirectly by examining whether, and to what extent, endorsement of
-certain policies differentiate by whether such policies benefit veterans
-or the public generally. In one such study by Tsai et al.
-(\citeproc{ref-tsai2021}{2021}), Republican partisanship was shown to be
-the most consistent factor associated with more favorable attitudes
-(e.g., compassion) toward homelessness and PTSD among the veteran
-population, but not among the general adult population. Additionally,
-Republican partisans tended to show greater support for federal funding
-for homelessness and PTSD research when the reference population was
-military veterans. That study, however, suggests that the effect of the
-veteran status cue is sensitive to the topic in question.
-
-Perhaps unsurprisingly, military veterans appear to be uniquely
-deserving in the eyes of Republican partisans
-(\citeproc{ref-mcdermott2015}{McDermott and Panagopoulos 2015};
-\citeproc{ref-richardson2022}{Richardson 2022};
-\citeproc{ref-tsai2021}{Tsai et al. 2021}). As such, military veteran
-status may qualify favorable attitudes among Republican partisans
-whereas their regard for other non-veteran groups might otherwise
-express contempt or indifference. This further indicates a need for
-research to determine an underlying mechanism explaining why, and for
-whom, veterans incur special favor.
-
 \subsection{Limitations}\label{limitations}
@@
 public attitudes about military veterans specifically, pre- nor
-post-treatment. This unfortunately leaves no room for me to postulate
-and examine any potential mechanisms underlying results.
-
-It should be noted that these results are limited to one's expectations
-in anticipation of election night. Whether the increase in confidence is
-sustained post-election night cannot be inferred from these results.
-Moreover, It is yet unclear whether actually encountering and
-interacting with veterans working as staff or volunteers at election
-sites does much to improve voter confidence after election night
-compared to anyone else. It may be the case that assumptions that
-veterans are filling spots as election workers and volunteers simply
-primes positive expectations as one heads into an election site,
-potentially improving voters perceptions of their own experience on the
-way out. Further research would be needed to test such an idea.
-
-The setting of the vignette and specified in survey items might raise
-additional concerns on whether results are generalizable. Naming a
-specific county in the vignette adds in a potentially influential factor
-unaccounted for in the survey; some people may have attitudes about the
-county in question, others won't, while others may be muffed to consider
-a random county in the U.S. they know nothing about. Naming a real and
-somewhat salient county potentially undermines confidence that the
-treatment effects are solely attributable to veterans to an unknown
-degree. Simply put, there may be something special about Maricopa
-County, AZ in particular that generalizes across attitudes of trust or
-distrust in elections.
-
-Arguably, however, Maricopa County is indicated as the setting in both
-the treatment and control vignettes, thus the only actual difference
-between conditions is constrained to the target group being recruited.
-Future research may employ vignettes naming a fictional U.S. county to
-hopefully eliminate the setting as a concern. Alternatively additional
-survey items that ask directly about one's knowledge or sentiment about
-the county in question could inform researchers on whether the named
-county imposes any undue influence at all, or whether the setting is
-associated with other factors such as partisanship.
+post-treatment. Of course, inquiring into attitudes about veterans
+pre-treatment could prime respondents in a way that would contaminate
+the experiment. Moreover, responses to questions about veterans
+post-treatment might, indeed, be influenced by the treatment. This
+unfortunately leaves no room for me to postulate and examine any
+potential mechanisms underlying results. That being said, attempting to
+understand and explain why veterans are viewed favorably in general goes
+beyond the scope of this study. This study relied on the literature
+showing that overwhelmingly positive perceptions of veterans persists
+among the public \emph{writ large}. It is surely important for future
+work to focus on understanding why veterans are generally favored in
+order to posit a potential mechanism that transmits the effect of the
+veterans cue on confidence in elections.
+
+The election setting specified in survey items might raise concerns
+about whether results are generalizable to other places or counties
+nationwide. That is, whether promoting the recruitment of veterans in
+\emph{any} county nationwide would similarly increase confidence in
+elections, or whether effects of the veteran cue is limited to elections
+in Maricopa County, AZ or similar places.
+
+Maricopa County was specified \emph{in the vignettes} because of the
+increased scrutiny levied toward elections admin there after 2020. This
+doesn't mean, necessarily, that Maricopa County, AZ, would therefore be
+salient to respondents generally and for that reason, if at all. There's
+no problem in asking about confidence in elections nationwide and in
+local elections while still keeping Maricopa County as the setting in
+the vignettes; even though the setting is specified in the vignettes,
+the setting acts only as a stand-in for counties nationwide. Maricopa
+County is indicated as the setting in both the treatment and control
+vignettes, thus the only actual difference between conditions is
+constrained to the target group being recruited.
+
+The problem arises because the subsequent survey questions ask
+specifically about elections in Maricopa County; I cannot attest to
+whether the effect of the veterans cue generalizes to confidence in
+elections in places other than Maricopa County. To be clear, this
+limitation arises because \emph{subsequent survey questions ask
+respondents to consider elections in Maricopa County specifically}.
 
@@
 effects.
-
-Note also that the measurement items of the components trust and
-distrust, and the method of computing scores for the dependent variable,
-confidence in elections, are unique to this study but falls under the
-methodological framework of Classical Test Theory (CTT). Although survey
-measurement items were either directly drawn from or inspired by similar
-survey items found in various other surveys (e.g., SPAE, Pew), the
-question wording, response choices, coding, and computation of sum
-scores of the dependent variable are specific, thus rendering
-measurement of the hypothetical constructs of interest (i.e., trust,
-distrust) less comparable across similar studies that profess
-measurement of similar constructs (\citeproc{ref-widaman2024}{Widaman
-and Revelle 2024}). Namely, trust, distrust, or confidence in elections
-as defined and measured here.
 
@@
 Abbate, Andrea. 2020. {``39 {Ways Election Offices} Are {Responding} to
-{COVID-19}.''} \emph{Center for Tech and Civic Life}.
+{COVID-19}.''}
+\url{https://www.techandciviclife.org/covid-19-responses/}.
 
@@
 Baldor, Lolita. 2025a. {``Military Commanders Will Be Told to Send
-Transgender Troops to Medical Checks to Oust Them.''} \emph{AP News}.
+Transgender Troops to Medical Checks to Oust Them.''}
+\url{https://apnews.com/article/transgender-ban-military-discharge-troops-0218f0b6fec595c420bd0ac072d87335}.
 
@@
 Baldor, Lolita. 2025b. {``Military Parade to Celebrate the {Army}'s
-250th Anniversary Will Be Held on {Trump}'s Birthday.''} \emph{AP News}.
+250th Anniversary Will Be Held on {Trump}'s Birthday.''}
+\url{https://apnews.com/article/trump-army-military-parade-birthday-2f5cd12c8ccd4efddc29bfa3cf8f2705}.
 
@@
 Baldor, Lolita. 2025c. {``Pentagon Directs Military to Pull Library
-Books That Address Diversity, Anti-Racism, Gender Issues.''} \emph{AP
-News}.
+Books That Address Diversity, Anti-Racism, Gender Issues.''}
+\url{https://apnews.com/article/pentagon-hegseth-dei-library-books-770364ab99591402ddffe8758432ff26}.
 
@@
 Baldor, Lolita C. 2020. {``Military Wary That Shakeup Could Upend Its
-Apolitical Nature.''} \emph{AP News}.
+Apolitical Nature.''}
+\url{https://apnews.com/article/military-wary-shakeup-upend-apolitical-89eccf0aef7cf7b99208b3bfd0453a43}.
 
@@
 Baldor, Lolita C. 2025. {``Hegseth Orders the Name of Gay Rights
-Activist {Harvey Milk} Scrubbed from {Navy} Ship.''} \emph{AP News}.
+Activist {Harvey Milk} Scrubbed from {Navy} Ship.''}
+\url{https://apnews.com/article/harvey-milk-navy-ship-renamed-pride-month-d6cda5df15ee5bc066092d54c591c6f2}.
 
@@
 Brennan Center for Justice. 2024. \emph{Local {Election Officials
-Survey} --- {May} 2024 {\textbar} {Brennan Center} for {Justice}}.
+Survey} --- {May} 2024 \textbar{} {Brennan Center} for {Justice}}.
 Brennan Center Research Department.
+\url{https://www.brennancenter.org/our-work/research-reports/local-election-officials-survey-may-2024}
+(November 5, 2024).
 
@@
 Systems}, {Donald Trump}, and {Voter Confidence}.''} \emph{Public
-Opinion Quarterly} 88(SI): 516--35.
+Opinion Quarterly} 88: 516--35.
 doi:\href{https://doi.org/10.1093/poq/nfae034}{10.1093/poq/nfae034}.
@@
 Policies} and {Voter Confidence} for {Black} and {White Voters}.''}
-\emph{Public Opinion Quarterly} 88(SI): 561--84.
+\emph{Public Opinion Quarterly} 88: 561--84.
 doi:\href{https://doi.org/10.1093/poq/nfae032}{10.1093/poq/nfae032}.
@@
 Workers for {Election Day} Are Paying Off.''} \emph{WHYY NPR}.
+\url{https://whyy.org/articles/philly-area-counties-say-efforts-to-recruit-poll-workers-for-election-day-are-paying-off/}.
 
@@
 Michigan Militia Men Navigate Evolving Social Norms}.''} Thesis.
+\url{http://deepblue.lib.umich.edu/handle/2027.42/98077}.
 
@@
 Cooter, Amy. 2024. {``Veterans and {Extremism}: {From Militias} to
-{January} 6th and {Real Patriots} {\textbar} {Middlebury Institute} of
+{January} 6th and {Real Patriots} \textbar{} {Middlebury Institute} of
 {International Studies} at {Monterey}.''}
+\url{https://www.middlebury.edu/institute/academics/centers-initiatives/ctec/ctec-publications/veterans-and-extremism-militias-january-6th}.
 
@@
 Doubek, James. 2024. {``States and Cities Beef up Security to Prepare
-for Potential Election-Related Violence.''} \emph{NPR}.
+for Potential Election-Related Violence.''} \emph{NPR: 2024 Election}.
+\url{https://www.npr.org/2024/11/04/nx-s1-5178083/national-guard-police-election-security}
+(November 5, 2024).
 
@@
 Dunn, Amina. 2018. {``Elections in {America}: {Concerns Over Security},
-{Divisions Over Expanding Access} to {Voting}.''} \emph{Pew Research
-Center}.
+{Divisions Over Expanding Access} to {Voting}.''}
+\url{https://www.pewresearch.org/politics/2018/10/29/elections-in-america-concerns-over-security-divisions-over-expanding-access-to-voting/}.
 
@@
 Edlin, Ruby, and Lawrence Norden. 2024. {``Poll of {Election Officials
-Finds Concerns About Safety}, {Political Interference} {\textbar}
-{Brennan Center} for {Justice}.''} \emph{Brennan Center For Justice}.
+Finds Concerns About Safety}, {Political Interference} \textbar{}
+{Brennan Center} for {Justice}.''}
+\url{https://www.brennancenter.org/our-work/analysis-opinion/poll-election-officials-finds-concerns-about-safety-political}.
 
@@
 {Official Turnover Rates} from 2000--2024}. Bipartisan Policy Center.
+\url{https://bipartisanpolicy.org/download/?file=/wp-content/uploads/2024/04/WEB_BPC_Elections_Admin_Turnover_R01.pdf}.
 
@@
 Garamone, Jim. 2016a. {``Active-{Duty Personnel Must Remain Apolitical},
-{Nonpartisan}, {Dunford Says}.''} \emph{DOD News {\textbar} U.S.
-Department of Defense}.
+{Nonpartisan}, {Dunford Says}.''}
+\url{https://www.defense.gov/News/News-Stories/Article/Article/881624/active-duty-personnel-must-remain-apolitical-nonpartisan-dunford-says}.
 
@@
 Garamone, Jim. 2016b. {``{DOD} Civilians, Service Members Must Remain
-Non-Partisan, Apolitical.''} \emph{DOD News {\textbar} U.S. Department
-of Defense}.
+Non-Partisan, Apolitical.''}
+\url{https://www.defense.gov/News/Releases/Release/Article/975910/dod-civilians-service-members-must-remain-non-partisan-apolitical}.
 
@@
 Giles, Ben. 2021. {``Arizona {Recount Of} 2020 {Election Ballots Found
-No Proof Of Corruption}.''} \emph{NPR}.
+No Proof Of Corruption}.''} \emph{NPR: 2024 Election}.
+\url{https://www.npr.org/2021/09/25/1040672550/az-audit}.
 
@@
 Herndon, Astead W. 2020. {``{LeBron James} and a {Multimillion-Dollar
-Push} for {More Poll Workers}.''} \emph{The New York Times}.
+Push} for {More Poll Workers}.''} \emph{The New York Times: U.S.}
+\url{https://www.nytimes.com/2020/08/24/us/politics/lebron-james-poll-workers.html}
+(November 13, 2024).
 
@@
 Terrorism (START): College Park}.
+\url{https://www.start.umd.edu/pubs/Radicalization\%20in\%20the\%20Ranks_April\%202022.pdf}.
 
@@
 a {Nationally Representative Survey}}. RAND Corporation.
+\url{https://www.rand.org/pubs/research_reports/RRA1363-7.html}.
 
@@
 LaGrone, Sam. 2019. {``Shanahan {Reminds Pentagon} to {Stay
-Apolitical}.''} \emph{USNI News}.
+Apolitical}.''}
+\url{https://news.usni.org/2019/06/11/acting-secdef-shanahan-reminds-pentagon-to-stay-apolitical-following-mccain-situation}.
 
@@
 Lawrence, Quil. 2022. {``Vetting the {Vote}: {Military} Veterans
-Volunteer as Impartial Poll Workers.''} \emph{NPR}.
+Volunteer as Impartial Poll Workers.''} \emph{NPR: National}.
+\url{https://www.npr.org/2022/11/04/1133920940/vetting-the-vote-military-veterans-volunteer-as-impartial-poll-workers}.
 
@@
 Lawrence, Quil. 2024. {``As Fears about Election Security Grow, Military
-Veterans Are Filling as Poll Workers.''} \emph{NPR}.
+Veterans Are Filling as Poll Workers.''}
+\url{https://www.npr.org/2024/10/14/nx-s1-5144186/as-fears-about-election-security-grow-military-veterans-are-filling-as-poll-workers}.
 
@@
 Journal of Politics} 80(1): 59--70.
+\url{https://www.jstor.org/stable/26551118} (June 4, 2025).
 
@@
 Lincoln, Sophie. 2024. {``Washoe {County} Staff Prepare for {Election
-Day}, Announce New Safety Feature at Polls.''} \emph{News4 KRNV}.
+Day}, Announce New Safety Feature at Polls.''}
+\url{https://mynews4.com/news/local/washoe-county-staff-prepare-for-election-day-announce-new-safety-feature-at-polls}
+(November 5, 2024).
 
@@
 Loewenson, Irene. 2023. {``Mattis Says Vets at {Jan}. 6 {Capitol} Riot
-{`Don't Define the Military'}.''} \emph{Marine Corps Times}.
+{`Don't Define the Military'}.''} \emph{Marine Corps Times: name}.
+\url{https://www.marinecorpstimes.com/news/your-marine-corps/2023/11/06/mattis-says-vets-at-jan-6-capitol-riot-dont-define-the-military/}.
 
@@
 Looker, Rachel. 2024. {``How Some Veterans Find a Way to 'Serve the
-Country Again' on {Super Tuesday}.''} \emph{USA TODAY}.
+Country Again' on {Super Tuesday}.''}
+\url{https://www.usatoday.com/story/news/politics/elections/2024/03/05/veterans-poll-workers-election/72839163007/}.
 
@@
 Election Administration, Federal Election Commission.
+\url{https://purl.fdlp.gov/GPO/gpo18585}.
 
@@
 Department and Office of the Recorder}.
+\url{https://elections.maricopa.gov/asset/jcr:a9e03750-0a8f-4162-859f-1d46ac54b485/Correcting\%20The\%20Record\%20-\%20January\%202022\%20Report.pdf}.
 
@@
 Political \& Military Sociology} 34(2): 281--88.
+\url{https://www.jstor.org/stable/45294228} (June 4, 2025).
 
@@
 Mena, Kelly. 2020. {``States Scramble to Recruit Thousands of Poll
-Workers Amid Pandemic Shortage {\textbar} {CNN Politics}.''} \emph{CNN}.
+Workers Amid Pandemic Shortage \textbar{} {CNN Politics}.''}
+\url{https://www.cnn.com/2020/08/13/politics/poll-worker-shortage-2020-election/index.html}.
 
@@
 Nadeem, Reem. 2024. {``Harris, {Trump Voters Differ Over Election
-Security}, {Vote Counts} and {Hacking Concerns}.''} \emph{Pew Research
-Center}.
+Security}, {Vote Counts} and {Hacking Concerns}.''}
+\url{https://www.pewresearch.org/politics/2024/10/24/harris-trump-voters-differ-over-election-security-vote-counts-and-hacking-concerns/}
+(November 5, 2024).
 
@@
 of {State Francisco V}. {Aguilar} Sign {Election Worker Protection Bill}
-into Law.''} \emph{Press Release {\textbar} Nevada Secretary of State}.
+into Law.''}
+\url{https://www.nvsos.gov/sos/Home/Components/News/News/3368/309?backlist=\%2Fsos}
+(November 5, 2024).
 
@@
 NFL Football Operations. 2022. {``Vet the {Vote}.''}
-
-\bibitem[\citeproctext]{ref-nichols2015}
-Nichols, Curt. 2015. {``Public {Opinion} and the {Military}: {A
-Multivariate Exploration} of {Attitudes} in {Texas}.''} \emph{Journal of
-Political \& Military Sociology} 43: 75--106.
+\url{https://operations.nfl.com/inside-football-ops/social-justice/vet-the-vote/}.
 
@@
 Effort} to {Recruit New Wave} of {Poll Workers} for {Election Day}.''}
-\emph{Power the Polls}.
+\url{https://www.powerthepolls.org/press-release-2020-06-30}.
 
@@
 to Work Polls.''} \emph{nwitimes.com}.
+\url{https://www.nwitimes.com/news/local/porter/porter-newsletter/porter-county-election-officials-recruit-students-to-work-polls/article_b2f1aaf8-1e5f-550e-bbbe-113dcb679f7e.html}.
 
@@
 \bibitem[\citeproctext]{ref-spearman1907}
-Spearman, Charles. 1907. {``Demonstration of {Formul{æ}} for {True
+Spearman, Charles. 1907. {``Demonstration of {Formulæ} for {True
 Measurement} of {Correlation}.''} \emph{The American Journal of
@@
 Steinhauer, Jennifer. 2020. {``Veterans {Fortify} the {Ranks} of
-{Militias Aligned With Trump}'s {Views}.''} \emph{The New York Times}.
+{Militias Aligned With Trump}'s {Views}.''} \emph{The New York Times:
+U.S.}
+\url{https://www.nytimes.com/2020/09/11/us/politics/veterans-trump-protests-militias.html}.
 
@@
 Thomas, Ashley. 2025. {``Trump {White House} Marks {Black History Month}
-While {Defense Department} Declares 'Identity Months Dead'.''} \emph{AP
-News}.
+While {Defense Department} Declares 'Identity Months Dead'.''}
+\url{https://apnews.com/article/trump-black-history-month-ec046b1a8122b5af9d8b26516b6837c2}.
 
@@
 \bibitem[\citeproctext]{ref-wetheveterans2022}
-We The Veterans. 2022. {``Launch of {Vet} the {Vote}.''} \emph{Vet The
-Vote}.
+We The Veterans. 2022. {``Launch of {Vet} the {Vote}.''}
+\url{https://vetthe.vote/blogs/news/launch-of-vet-the-vote}.
 
@@
 Wentling, Nikki. 2024. {``Veterans Group Hits Goal of Recruiting 100,000
-Election Workers.''} \emph{Military Times}.
+Election Workers.''} \emph{Military Times: name}.
+\url{https://www.militarytimes.com/news/your-military/2024/07/10/veterans-group-hits-goal-of-recruiting-100000-election-workers/}.
 
@@
 Is Now a Dangerous Job: How It Feels for Frontline, Swing-State
-Workers.''} \emph{USA TODAY}.
+Workers.''}
+\url{https://www.usatoday.com/story/news/politics/elections/2024/10/28/election-workers-2024-hostility/75586254007/}
+(November 5, 2024).
 
@@
 Model} of {Intergroup Relations}.''} \emph{Psychological Inquiry} 27(4):
-255--74.
+255--74. \url{https://www.jstor.org/stable/26159704} (October 26, 2024).
 

### 2025-07-18 index.qmd
modified revisions

@@
 
+```{r}
+#| label: tinytable-theme
+
+# see here: https://vincentarelbundock.github.io/tinytable/vignettes/theme.html#user-written-themes
+
+theme_mitex <- function(x, ...) {
+    fn <- function(table) {
+        if (isTRUE(table@output == "typst")) {
+          table@table_string <- gsub(
+            "\\$(.*?)\\$",
+            "#mitex(`\\1`)",
+            table@table_string)
+        }
+        return(table)
+    }
+    x <- style_tt(x, finalize = fn)
+    return(x)
+}
+
+```
+
 {{< pagebreak >}}
@@
 As such, we can expect that information identifying the particular groups being recruited to serve as election staff will be enough to improve confidence in elections, and lessen expectations of electoral fraud.
-The next section elaborates on the proposed theory, terms utilized, and why military veterans are of particular interest in this regard.
-
-# Theory
-
-This theory is constrained to public confidence in the administration of elections in the United States.
-To be clear, the scope conditions in which this theory applies concern public trust and distrust in election administration in the anticipatory period prior to the election event.
-Moreover, this study is, to a limited extent, indirectly related to public regard about veteran members of the U.S.
-Armed Forces.
-
-## Trust and Distrust in Elections
-
-The theoretical relationship between trust and distrust is important to understand, especially when it comes to the dependent outcome of interest.
-Before going further, it is necessary to explicate the conception *confidence in elections* with respect to trust and distrust.
-
-Trust is, after all, merely *belief* held in the face of uncertainty.
-Trust is reliance on the veracity of belief in the face of uncertainty.
-Said another way, trust is assured belief dependent on its supposed veracity; a state of certainty with respect to some belief or judgement.
-It is "assured" because it is one's belief that relies on something rather than nothing.
-Hence quantitative methods of the sciences are replete with things such as *confidence* intervals around our estimates.
-Therefore, I understand trust to refer to the state or quality of certainty around one's beliefs or expectations; the extent to which one is assured of their expectations regarding what is or what will be the case.
-
-The kind of *trust in elections* I refer to concerns the expectations drawn up from one's judgement about the functioning of the electoral process---the extent to which one is assured in the belief that the electoral process will be fairly and accurately administered.
-I follow the notion of public trust in elections explicated by @stewart2022,
-
-> "Public trust in U.S.
-election institutions comes down to whether voting machines accurately record votes, voter registration systems accurately record those eligible to vote, geographic information systems accurately assign voters to voting districts, election-night reporting systems accurately aggregate and communicate election results to officials and the public, and postelection audit and canvassing procedures proceed impartially and in accordance with the law." [-@stewart2022, 236]
-
-That being said, I also account for expectations of electoral fraud, which I refer to as *distrust* in elections distinguished from trust.
-Distrust in this sense is also a belief, an expectation, about the anticipated functioning of the process.
-Note, however, that the prefix *dis-* in distrust implies "apart", "lack of, not" or "opposite".
-Conventionally, distrust is defined simply as the absence of trust, thus denoting a simple inverse and mutually exclusive relationship.
-However, as it concerns the psychology of an individual, *a lack of trust doesn't necessarily imply opposite expectations or opposing beliefs*.
-In particular, a lack of trust that votes will be accurately recorded, etc., doesn't necessarily imply inversely proportional expectations that electoral fraud will occur.
-In other words, although the relationship between trust and distrust is inverse, this relationship is not mutually exclusive.
-
-A person who is certain that electoral fraud will occur clearly lacks trust in elections; an expectation that electoral fraud will occur necessarily implies a lack of trust in elections regardless of positive expressions of trust.
-However, the reverse isn't also true; expressing a lack of trust in elections *doesn't necessarily imply* an expectation that electoral fraud will occur.
-Rather, a lack of trust implies an absence of assurance in the belief that the process will be conducted fairly and accurately---a lacking quality of certainty around said belief.
-An absence of such assurance denotes a state of *insecurity*.
-Other sources of uncertainty may challenge a person's confidence regarding the integrity of elections independent from anything that would lead them to believe electoral fraud will occur or has occurred.
-However my use of distrust refers to the assured belief that the outcome will be invalid---that outcomes will be independent of the process as prescribed, thus rendering outcomes as arbitrary.
-Specifically, distrust implies assurance in the belief that electoral fraud will occur.
-
-As such, trust and distrust represent opposing degrees of confidence along the same spectrum.
-However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling relatively confident in both respects.
-Accordingly, *equivalent degrees of trust and distrust cancel out*, rendering one relatively more insecure about their expectations of the future despite the fact that they may report feeling confident in either direction respectively.
-When trust and distrust are considered reflective of one's confidence about future expectations, then both can be placed along the same spectrum.
-Therefore, a lack of confidence denotes insecurity.
-
-This means that a person's baseline level of confidence in elections must take into account their present degree of distrust---i.e., their expectations of electoral fraud.
-Something may cause a person to have greater expectations that election fraud will occur, which in turn will always lower their trust in elections.
-In contrast, a person's trust in the integrity of the electoral process is reduced by the extent to which they expect that electoral fraud will occur.
-
-Thus, it follows that a person distrusts the integrity of the electoral process to the extent that they are to some extent certain that electoral fraud will occur or has occurred.
-They are, perhaps, poised to discount election results as invalid or illegitimate in advance.
-Either way, both trust and distrust refer to some positive degree of confidence (i.e., assurance) regarding one's expectations.
-They are distinguished by reference to either the normative idea about what *should* come about, or what is *supposed* to come about given the logical structure and integrity of the process.
-If the structure and integrity of some process is coherent and secure, respectively, then the outcome that follows will be valid.
-Should the integrity of that process be damaged or opaque, then the process becomes vulnerable and validity of the results are open to challenge.
-With respect to the administration of U.S.
-elections, the confident voter expects that votes will be counted as voters intend, election staff will competently administer elections, election technology will be secure from nefarious tampering, and that the process will be fair for all involved.
-
-## Why Veterans
+The next section elaborates on the proposed theory and why military veterans are of particular interest in this regard.
+
+## Theory: Why Veterans
+
+The theory tested in this study is this: when the public is informed that election officials are actively recruiting veteran military service members to work at election sites as staff or volunteers, their overall confidence in the fairness, accuracy, and integrity of the electoral process will improve.
+Said another way, insecurities over the integrity of elections administration and safety of voters lessen as the public learns that military service veterans are being sought out by election officials to staff or volunteer at election sites.
+The stimulating influence of veterans as a group in the abstract is expected to counteract distrust and insecurity pertaining to the institution of elections administration, as well as inspire greater trust in the same.
+This prompts an obvious question: why would information about efforts to recruit veterans to work as election staff and volunteers have any influence on confidence in elections?
 
 Election officials don't focus on recruiting people of a particular demographic, status, class, or prestige in order to shore up public trust in elections, and they don't discriminate recruitment efforts based on who the public thinks is best suited to secure elections from fraud.
-
 Election officials are likely to be agnostic as to who dedicates their time to civil service such as election work.
@@
 Indeed, there's no reason to discriminate recruitment efforts at all if the point is purely to fill staffing vacancies.
-
-Veteran military service members are, after all, civilians; Civilians with shared (but varied) experience and status of prior military service, but who are no more or less qualified for this civil service^[Research is limited and mixed on whether veterans in general are more inclined, however [@nesbit2011].] than non-veteran civilians.
-To be frank, announcements about concerted efforts to recruit veterans as election workers should not reasonably influence one's trust that votes will be counted more accurately, or that election fraud will not occur; there is no known evidence demonstrating that actually employing veterans as election staff or volunteers further improves the safety, security, and overall integrity of elections in the United States.
-Moreover, there's no known evidence of positive influence on public perceptions of said outcomes when voters encounter military veterans working as staff or volunteers at elections sites.
-
-Rather, the claim that recruiting veterans to work as election staff and volunteers would improve public confidence in elections emerges as non-profit organizations---mainly comprised of veteran and military family members themselves---operate under, and promote, that assumption [@looker2024; @lawrence2024; @wentling2024].
-Non-profit groups of late have made incredible strides in targeted recruitment efforts under the notion that veterans are uniquely capable, committed, and best fit to serve the needs of the United States as civil servants and volunteers at election sites.
-Indeed, this study can be seen as a test of a particular assumption that veterans have about themselves---the assumption that their mere presence and civic engagement will inspire confidence in elections among the public.
 
@@
 
-The key findings of literature on confidence in elections hardly point to public regard for veterans as a mechanism for the theoretical expectations of improving overall confidence in elections and improving feelings of voter safety at election sites.
-Comparable research finds that confidence in elections is increased through elite rhetoric from fellow partisans affirming legitimacy of elections [@clayton2023], or through the provision of information about the electoral process or other official messaging of election officials themselves [@gaudette2025].
-Neither of the studies just cited, however, consider attitudes or sentiment about veterans as a source for dispelling distrust and improving trust in elections.
-To be clear, there is no immediate "puzzle" in the literature that immediately draws out public sentiment for military veterans as a source for bolstering confidence in elections.
-That being said, the general public perception, attitudes, or even stereotypes about military veterans are significant to consider.
-
-It is important to make clear two considerations that underpin the notion that information about veterans will improve trust and quell distrust in elections.
+The claim that recruiting veterans to work as election staff and volunteers would improve public confidence in elections emerges as non-profit organizations---mainly comprised of veteran and military family members themselves---operate under, and promote, that assumption [@looker2024; @lawrence2024; @wentling2024].
+Non-profit groups of late have made incredible strides in targeted recruitment efforts under the notion that veterans are uniquely capable, committed, and best fit to serve the needs of the United States as civil servants and volunteers at election sites.
+Indeed, this study can be seen as a test of a particular assumption that veterans have about themselves---the assumption that their mere presence and civic engagement will inspire confidence in elections among the public.
+
+Veterans are, after all, civilians.
+Civilians with shared (but varied) experience and status of prior military service, but who are no more or less qualified for this civil service^[Research is limited and mixed on whether veterans in general are more inclined, however [@nesbit2011].] over non-veteran civilians.
+To be frank, announcements about concerted efforts to recruit veterans as election workers should not reasonably influence one's trust that votes will be counted more accurately, or that election fraud will not occur; there is no known evidence demonstrating that actually employing veterans as election staff or volunteers further improves the safety, security, and overall integrity of elections in the United States.
+Moreover, there's no known evidence of positive influence on public perceptions of said outcomes when voters encounter military veterans working as staff or volunteers at elections sites.
+So, why veterans?
+
+Two considerations underpin the notion that information about veterans will improve trust and quell distrust in elections.
 First, positive public regard for veterans *in general* is sufficient to elicit greater trust and lower distrust in elections despite the fact that information about veterans as election workers, or even merely information on efforts to recruit veterans, has no bearing on the actual integrity of the electoral process.
-An underlying assumption here is that there *is* something special about veterans, but this doesn't include a proposition on exactly *what* that special something might be in theory.
-This is partly due to the limited research available on public regard for veterans, specifically in terms of elucidating an underlying mechanism for such positive favor.
-Moreover, there is limited research on public opinion about former and active military service members distinguished separately from public opinion about the military as an institution in general.
-Endorsement or support of government policies intended to benefit veterans specifically (e.g., federal funding on veteran healthcare) are easy to conflate as interchangeable with public attitudes about veterans as a group in particular.
-This, in turn, permits general expectations of positive influence due to the public's overarching positive regard for veterans, but disallows for expectations regarding how respondents would actually process and interpret a treatment that only mentions efforts to recruit them for election work.
-In short, we are sure that people sustain positive views for veterans generally, but beyond that I make no special effort to propose and examine why that is the case in greater detail.
-
-The evidence that can be gathered concerning public regard for military veterans shows that, generally, veterans are perceived favorably among the general public; although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023].
-In my review of the literature, I found only one study which assessed public opinion about veterans specifically and examined whether attitudes differed by group [@kleykamp2018].
-@kleykamp2018 investigated the extent to which positive regard for military veterans in terms of both social distance and deservingness varies across different groups, and the extent to which such support is exaggerated.
-Their research found that levels of support for veterans tended to be predictably lowest, but also most exaggerated, among those who were younger and non-White.
-Determining what groups hold special favor for veterans still leaves it unclear as to what it is about veterans that engenders greater confidence in elections.
-Yet, generally, all groups expressed exaggerated support for veterans in more than one way [@kleykamp2018], suggesting that public regard for veterans is prescribed by widespread social norm.
-
-This is taken together with literature suggesting that public trust in elections is malleable to factors, experiences, events, or phenomena that range in logical relevance to the actual structure or administration of elections.
+
+An underlying assumption here is that there *is* something special about veterans in the eyes of the public generally, but this doesn't include a proposition on exactly *what* that special something might be in theory.
+This is partly due to there being limited research on public opinion about former and active military service members distinguished separately from public opinion about the military as an institution in general.
+Support for the military is generally pretty high, but attitudes about the military in general can't be construed as public opinion about veterans as a group.
+The evidence that can be gathered concerning public regard for military veterans shows that, generally, veterans are perceived favorably among the general public and all groups express exaggerated support for veterans in more than one way [@kleykamp2018], suggesting that public regard for veterans is prescribed by widespread social norm.
+Although military recruitment shows a downward trend as of late, public perceptions of veterans are overwhelmingly positive [@kleykamp2023].
+
+Beyond such findings, it is overtly clear that former and active military service members are highly revered nationwide.
+Veteran's day is a national holiday, and custom prescribes thanking military members for their service.
+Calls to "support the troops" are distinct from calls to support the politics the troops are deployed to pursue.
+In 2016, former NFL player Colin Kaepernick went from sitting to kneeling in protest during the playing of the National Anthem upon criticism that sitting in protest implied disrespect for active and former military service members [@haerens2018].
+
+Generally high public regard for veterans is taken together with literature suggesting that public trust in elections is malleable to factors that range in logical relevance to the actual structure or administration of elections.
 On the one hand, public trust is, indeed, influenced by information specifically about the processes of conducting elections [@gaudette2025].
 On the other hand, the public's trust in elections is not beholden to the demonstrated *trustworthiness* of the institution of election administration.
-Thus the first consideration is simply that the positive public regard for veterans in general may function sufficiently as a cue to elicit greater trust in elections despite relevance.
-
-Second, veterans are a particularly potent group where mention of one's veteran status seems to have a positive, calming, or nullifying effect on attitudes.
+Whether generally high public reverence for veterans is due to injunctive social norms or not, what may be posited is simply that positive regard for veterans in general may function sufficiently as a cue to elicit greater trust in elections despite relevance.
+
+Second, veterans are a particularly potent group where mention of one's veteran status seems to have a calming effect on attitudes.
 More so than just the general positive favor afforded to veterans, the group appears to have a somewhat pacifying effect on negative or otherwise contemptible discrimination, prejudice, and social stigma.
@@
 Relatedly, attitudes about homelessness and PTSD---ranging from perceived causes of homelessness, whether the federal government should dedicate more resources, perceived effectiveness of policies, to compassion for homeless individuals---are generally more favorable for the homeless population among veterans than for the homeless population of general adults [@tsai2021].
+
 Such effects primarily pertain to attitudes about individual people or groups (e.g., a political candidate, prospective employees, the homeless population).
-The capacity of one's veteran status to pacify prejudice, discrimination, and stigma likely extends out to quell negative and disfavorable attitudes regarding institutions to a similar extent, e.g., distrust.
-
-Given the heightened tensions and electoral anxieties, the expectations surrounding the unique pacifying effect that veterans have on attitudes about individuals or other groups is extended to determine whether a similar effect is found when the target of one's consideration is not just a person or group but the institution of election administration itself.
-Thus the second consideration for "why veterans" are expected to dispel distrust in elections pertains to pacifying effect of negative or disfavorable attitudes observed in relevant literature.
-
-The stimulating influence of veterans as a group in the abstract is expected to counteract distrust and insecurity pertaining to the institution of elections administration, as well as inspire greater confidence in the same.
-There's scant research or evidence available to postulate a well-formed theory on the mechanism underlying the expected effects of veterans as a group on attitudes about institutions and processes, rather than on attitudes about persons or groups.
-What may be posited at best, however, is that distrust and insecurity in elections among the public is expectedly reduced to some extent through generally positive public regard for military veterans and their unique capacity to quell disfavorable attitudes.
+The capacity of one's veteran status to pacify prejudice, discrimination, and stigma likely extends out to veterans as a group in a similar fashion.
+Information that election sites will be staffed by veterans may be enough to ease insecurities about the competence and commitment of the institution to conduct fair and accurate elections.
+
+## Trust and Distrust in Elections
+
+This theory is constrained to public confidence in the administration of elections in the United States.
+To be clear, the scope conditions in which this theory applies concern public trust and distrust in election administration in the anticipatory period prior to the election event.
+The theoretical relationship between trust and distrust is important to understand, especially when it comes to the dependent outcome of interest.
+Before going further, it is necessary to explicate the conception *confidence in elections* with respect to how I've defined trust and distrust in elections.
+
+Trust is, after all, merely *belief* held in the face of uncertainty.
+Trust is reliance on the veracity of belief in the face of uncertainty.
+Said another way, trust is *assured belief* dependent on its supposed veracity; a state of certainty with respect to some belief or judgement.
+It is "assured" because it is one's belief that relies on something rather than nothing.
+Hence quantitative methods of the sciences are replete with things such as *confidence* intervals around our estimates.
+Therefore, I understand trust to refer to the state or quality of certainty around one's beliefs or expectations; the extent to which one is assured of their expectations regarding what is or what will be the case.
+
+The kind of *trust in elections* I refer to concerns the expectations drawn up from one's judgement about the functioning of the electoral process---the extent to which one is assured in the belief that the electoral process will be fairly and accurately administered.
+I follow the notion of public trust in elections explicated by @stewart2022,
+
+> "Public trust in U.S.
+election institutions comes down to whether voting machines accurately record votes, voter registration systems accurately record those eligible to vote, geographic information systems accurately assign voters to voting districts, election-night reporting systems accurately aggregate and communicate election results to officials and the public, and postelection audit and canvassing procedures proceed impartially and in accordance with the law." [-@stewart2022, 236]
+
+That being said, I also account for expectations of electoral fraud, which I refer to as *distrust* in elections distinguished from trust.
+Distrust in this sense is also a belief, an expectation, about the anticipated functioning of the process.
+Note, however, that the prefix *dis-* in distrust implies "apart", "lack of, not" or "opposite".
+Conventionally, distrust is defined simply as the absence of trust, thus denoting a simple inverse and mutually exclusive relationship.
+However, as it concerns the psychology of an individual, *a lack of trust doesn't necessarily imply opposite expectations or opposing beliefs*.
+In particular, a lack of trust that votes will be accurately recorded, etc., doesn't necessarily imply inversely proportional expectations that electoral fraud will occur.
+In other words, although the relationship between trust and distrust is inverse, this relationship is not mutually exclusive.
+
+As such, trust and distrust represent opposing degrees of confidence along the same spectrum.
+However, despite the inherent contrast, one can hold both positive degrees of trust and distrust, feeling relatively confident in both respects.
+Accordingly, *equivalent degrees of trust and distrust cancel out*, rendering one relatively more *insecure* about their expectations of the future despite the fact that they may report feeling confident in either direction respectively.
+When trust and distrust are considered reflective of one's confidence about future expectations, then both can be placed along the same spectrum.
+Therefore, a lack of confidence denotes insecurity.
+
+With respect to the administration of U.S.
+elections, the confident voter expects that votes will be counted as voters intend, election staff will competently administer elections, election technology will be secure from nefarious tampering, and that the process will be fair for all involved.
 
@@
 
-The survey included two items as an attention check prior to presenting either the treatment or control vignette.
+A manipulation check is intended to ensure that the experimental treatment (or manipulation) is received by respondents as the researcher intends.
+Since this experiment required respondents to read a faux news article, inattention or speeding through vignette presentation would undermine results.
+To mitigate this as much as possible, the survey included two items as an attention check prior to presenting either the treatment or control vignette.
 Respondents who failed to select a certain response twice in a row were removed from the survey.
@@
 ```{r}
-#| label: fig-safety-bars
-#| layout-ncol: 1
-#| layout-nrow: 2
-#| fig-cap: "Safety Concerns and Confidence by Treatment Condition"
-#| fig-subcap: 
-#|   - "Concern for Violence while voting in Maricopa County, AZ Elections"
-#|   - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"
+#| label: barplot-setup
+#| include: false
 
@@
 
-Briefly reviewing @fig-safety-bars, those in the treatment condition felt less concern over the potential for violence compared to those in the control.
+Briefly reviewing @fig-safety1, those in the treatment condition felt less concern over the potential for violence compared to those in the control.
+
 As for confidence in voter safety at election sites, it appears that more respondents in the treatment condition expressed that they were "Very confident" compared to those in the control, by approximately $8$ percentage points.
-
-{{< pagebreak >}}
 
@@
 In order to assess whether that was the case, I conducted an ordered logistic regression on the relevant items using the experimental condition as a dichotomous predictor.
-
-Those in the treatment condition had lower probability to express that they were 'Very' or 'Somewhat' concerned for violence in Maricopa County, AZ Elections, yet higher probability of expressing 'Not too' or 'Not at all' concerned.
-As for confidence in voter safety, moving from treatment to control, the difference in predicted probability of a respondent selecting "Very Confident" was $0.08$.
-@tbl-preds-diff1 and @tbl-preds-diff2 show the significant differences in predicted probabilities at 95$\%$ confidence^[The same models were run for items pertaining to safety concerns in one's local area but results of the treatment were not significantly different from the control.
-See Appendix E for full results table of ordinal logistic regression].
-These findings support both H~4a~ and H~4b~ respectively, permitting rejection of the null for each hypothesis.
 
@@
 #| tbl-colwidths: [80]
-#| tbl-pos: t
+#| tbl-pos: 'H'
 #| tbl-cap: "Difference in Predicted Probabilities in Concern for violence, Threats of Violence, or Intimidation between Treatment and Control"
@@
 
+Shown in @tbl-preds-diff1, those in the treatment condition had lower probability to express that they were 'Very' or 'Somewhat' concerned for violence in Maricopa County, AZ Elections, yet higher probability of expressing 'Not too' or 'Not at all' concerned.
+
 ```{r}
@@
 #| tbl-colwidths: [80]
-#| tbl-pos: t
+#| tbl-pos: 'H'
 #| tbl-cap: "Difference in Predicted Probabilities in Confidence that voters will be safe to vote in-person between Treatment and Control"
@@
 
-{{< pagebreak >}}
-
-## Limitations
-
-The bluntness of the experimental stimulus and survey items don't allow us to establish exactly what it is about military veterans in particular that cues stronger confidence in elections.
-No survey items assessed public attitudes about military veterans specifically, pre- nor post-treatment.
-This unfortunately leaves no room for me to postulate and examine any potential mechanisms underlying results.
-
-It should be noted that these results are limited to one's expectations in anticipation of election night.
-Whether the increase in confidence is sustained post-election night cannot be inferred from these results.
-Moreover, It is yet unclear whether actually encountering and interacting with veterans working as staff or volunteers at election sites does much to improve voter confidence after election night compared to anyone else.
-It may be the case that assumptions that veterans are filling spots as election workers and volunteers simply primes positive expectations as one heads into an election site, potentially improving voters perceptions of their own experience on the way out.
-Further research would be needed to test such an idea.
-
-The setting of the vignette and specified in survey items might raise additional concerns on whether results are generalizable.
-Naming a specific county in the vignette adds in a potentially influential factor unaccounted for in the survey; some people may have attitudes about the county in question, others won't, while others may be muffed to consider a random county in the U.S.
-they know nothing about.
-Naming a real and somewhat salient county potentially undermines confidence that the treatment effects are solely attributable to veterans to an unknown degree.
-Simply put, there may be something special about Maricopa County, AZ in particular that generalizes across attitudes of trust or distrust in elections.
-
-Arguably, however, Maricopa County is indicated as the setting in both the treatment and control vignettes, thus the only actual difference between conditions is constrained to the target group being recruited.
-Future research may employ vignettes naming a fictional U.S.
-county to hopefully eliminate the setting as a concern.
-Alternatively additional survey items that ask directly about one's knowledge or sentiment about the county in question could inform researchers on whether the named county imposes any undue influence at all, or whether the setting is associated with other factors such as partisanship.
-
-As stated previously, the survey was fielded on a non-probability sample of 1,287 U.S.
-citizens 18 years of age or older.
-The results presented here are not assumed to be generalizable to the national population.
-It may be feasible to weigh the sample to demographics of the population at the time the survey was fielded, but this is unnecessary for the experimental purpose of the study.
-If similar findings complement or replicate these results, then the expense of drawing samples more representative of the national population may be justified.
-At this stage, however, the results are limited to demonstrating treatment effects.
-
-Note also that the measurement items of the components trust and distrust, and the method of computing scores for the dependent variable, confidence in elections, are unique to this study but falls under the methodological framework of Classical Test Theory (CTT).
-Although survey measurement items were either directly drawn from or inspired by similar survey items found in various other surveys (e.g., SPAE, Pew), the question wording, response choices, coding, and computation of sum scores of the dependent variable are specific, thus rendering measurement of the hypothetical constructs of interest (i.e., trust, distrust) less comparable across similar studies that profess measurement of similar constructs [@widaman2024].
-Namely, trust, distrust, or confidence in elections as defined and measured here.
+As for confidence in voter safety in @tbl-preds-diff2, moving from treatment to control, the difference in predicted probability of a respondent selecting "Very Confident" was $0.08$.
+Both tables show the significant differences in predicted probabilities at 95$\%$ confidence^[The same models were run for items pertaining to safety concerns in one's local area but results of the treatment were not significantly different from the control.
+See Appendix E for full results table of ordinal logistic regression].
+These findings support both H~4a~ and H~4b~ respectively, permitting rejection of the null for each hypothesis.
 
@@
 
-In their research examining whether groups differed in attitudes about veterans, @kleykamp2018 could only speculate as to why levels of support were lowest among Hispanic and Black respondents.
-Their study was distinctive in that it stands as a rare case in which public attitudes about veteran military members was the specific focus of inquiry as opposed to studies that examine public opinion about the military in general.
-Other research has found that attitudes about the U.S.
-military generally---though not about active or veteran military service members in particular---differs by race and ethnicity to varying extents, but also could not supply reason for one groups' sentiment over another^[Note, however, that the sample examined by @nichols2015 was constrained to Texas residents, and the military-related issues concerned, among other things, favor for reinstatement of a military draft, support for allowing undocumented immigrants who live in the U.S.
-to serve in the U.S.
-Armed Forces, and whether undocumented immigrants should be granted U.S.
-citizenship as a result of military service.
-Although the authors found high overall support for the military as an institution, the other military-related attitudes of interest diverge far from public opinion about veterans.
-As such, differential effects found among different racial or ethnic groups likely have little to do with attitudes about former or active military service members.] [@nichols2015].
-
-Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly.
-One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S.
-military as an institution in general.
-Some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally.
-In one such study by @tsai2021, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes (e.g., compassion) toward homelessness and PTSD among the veteran population, but not among the general adult population.
-Additionally, Republican partisans tended to show greater support for federal funding for homelessness and PTSD research when the reference population was military veterans.
-That study, however, suggests that the effect of the veteran status cue is sensitive to the topic in question.
-
-Perhaps unsurprisingly, military veterans appear to be uniquely deserving in the eyes of Republican partisans [@tsai2021; @mcdermott2015; @richardson2022].
-As such, military veteran status may qualify favorable attitudes among Republican partisans whereas their regard for other non-veteran groups might otherwise express contempt or indifference.
-This further indicates a need for research to determine an underlying mechanism explaining why veterans incur special favor.
+It is definitely plausible that the public, to some unknown extent, associates a particular gender or race, or both, with former and active military members which may, in turn, mediate the effect of the veteran cue.
+Additionally, I can't be sure as to whether respondent's views of the military generalize to attitudes about active service members and veterans.
+However that is a separate question about the source of public opinion about military members themselves beyond the scope of this study.
+
+There's scant research or evidence available to postulate a well-formed theory on the mechanism underlying the expected effects of veterans as a group on attitudes about institutions and processes, rather than on attitudes about persons or groups.
+That is to say, there's not much research on how the public feels, or what they think, about former members of the U.S.
+Armed Forces.
+
+## Limitations
+
+The bluntness of the experimental stimulus and survey items don't allow us to establish exactly what it is about military veterans in particular that cues stronger confidence in elections.
+No survey items assessed public attitudes about military veterans specifically, pre- nor post-treatment.
+Of course, inquiring into attitudes about veterans pre-treatment could prime respondents in a way that would contaminate the experiment.
+Moreover, responses to questions about veterans post-treatment might, indeed, be influenced by the treatment.
+This unfortunately leaves no room for me to postulate and examine any potential mechanisms underlying results.
+That being said, attempting to understand and explain why veterans are viewed favorably in general goes beyond the scope of this study.
+This study relied on the literature showing that overwhelmingly positive perceptions of veterans persists among the public *writ large*.
+It is surely important for future work to focus on understanding why veterans are generally favored in order to posit a potential mechanism that transmits the effect of the veterans cue on confidence in elections.
+
+The election setting specified in survey items might raise concerns about whether results are generalizable to other places or counties nationwide.
+That is, whether promoting the recruitment of veterans in *any* county nationwide would similarly increase confidence in elections, or whether effects of the veteran cue is limited to elections in Maricopa County, AZ or similar places.
+
+Maricopa County was specified *in the vignettes* because of the increased scrutiny levied toward elections admin there after 2020.
+This doesn't mean, necessarily, that Maricopa County, AZ, would therefore be salient to respondents generally and for that reason, if at all.
+There's no problem in asking about confidence in elections nationwide and in local elections while still keeping Maricopa County as the setting in the vignettes; even though the setting is specified in the vignettes, the setting acts only as a stand-in for counties nationwide.
+Maricopa County is indicated as the setting in both the treatment and control vignettes, thus the only actual difference between conditions is constrained to the target group being recruited.
+
+The problem arises because the subsequent survey questions ask specifically about elections in Maricopa County; I cannot attest to whether the effect of the veterans cue generalizes to confidence in elections in places other than Maricopa County.
+To be clear, this limitation arises because *subsequent survey questions ask respondents to consider elections in Maricopa County specifically*.
+
+As stated previously, the survey was fielded on a non-probability sample of 1,287 U.S.
+citizens 18 years of age or older.
+The results presented here are not assumed to be generalizable to the national population.
+It may be feasible to weigh the sample to demographics of the population at the time the survey was fielded, but this is unnecessary for the experimental purpose of the study.
+If similar findings complement or replicate these results, then the expense of drawing samples more representative of the national population may be justified.
+At this stage, however, the results are limited to demonstrating treatment effects.
 
@@
 #| tbl-colwidths: [70]
-
-df <- data |>
-  dplyr::mutate(
-    mil = dplyr::case_when(
-      milserv1 =="Yes" & milserv2 == "Yes" ~ "Active Duty",
-      milserv1 =="Yes" & milserv2 == "No" ~ "Prior Service (Veteran)",
-      milservfam == "Yes" ~ "Has Family in Military",
-      milservfam == "No" ~ "No Family in Military",
-      TRUE ~ NA),
-    ideo_3cat = dplyr::case_when(
-      ideo %in% c("Extremely Liberal",
-                  "Slightly liberal",
-                  "Liberal") ~ "Liberal",
-      ideo %in% c("Extremely conservative",
-                  "Slightly conservative",
-                  "Conservative") ~ "Conservative",
-      ideo %in% c("Moderate: middle of the road") ~ "Moderate",
-      ideo %in% c("Haven't thought much about this") ~ "Unsure",
-      TRUE ~ NA)
-    ) |> 
-  dplyr::select(
-    group,
+#| tbl-pos: H
+
+# descriptive stats of categorical variables
+# gtsummary method
+gtsummary::theme_gtsummary_compact()
+
+tbl.desc <- data |>  
+  gtsummary::tbl_summary( 
+    by = group,
+    label = list(
+      age_4cat = "Age group, in years",
+      gender_3cat = "Gender",
+      race = "Race",
+      hisp = "Hispanic, Latino, or Spanish origin?",
+      educ_4cat = "Education"
+      ),
+    include = c(
       age_4cat,
@@
       hisp,
-    educ_4cat,
-    mil, 
+      educ_4cat
+      ),
+    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
+    missing = "ifany",
+    missing_text = "NA") |> 
+  gtsummary::add_overall() |> 
+  gtsummary::modify_header(label = "**Variable**") |> 
+  gtsummary::bold_labels()
+
+tbl.desc |>
+  gtsummary::as_tibble() |>
+  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
+                "**Control (N = 637)**" = "**Control**  \nN = 637",
+                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
+  tinytable::tt(theme = "spacing") |>
+  tinytable::format_tt(markdown = T) |>
+  tinytable::format_tt(replace = " ") |>
+  tinytable::style_tt(fontsize = 0.70, align = "lccc")
+
+```
+
+{{< pagebreak >}}
+
+```{r}
+#| label: tbl-demog2
+#| tbl-cap: "Sample Demographics"
+#| tbl-colwidths: [70]
+#| tbl-pos: H
+
+tbl.desc2 <- data |>  
+  gtsummary::tbl_summary( 
+    by = group,
+    label = list(
+      partyid_3cat = "Party ID",
+      ideo_3cat = "Political Ideology",
+      ideolean = "If R had to choose Political Ideology",
+      voted2020 = 'Did R Vote in 2020 Election',
+      choice2020 = 'Vote Choice in 2020 Election'),
+    include = c(
       partyid_3cat,
-    ideo_3cat
-    ) |> 
-  labelled::set_variable_labels(
-    age_4cat = "Age groups, in years",
-    gender_3cat = "Gender",
-    race = "Race",
-    hisp = "Is R of Hispanic, Latino, or Spanish origin",
-    educ_4cat = "Education",
-    mil = "Military Relation",
-    partyid_3cat = "Party ID", 
-    ideo_3cat = "Political Ideology")
-
-freqs <- df |> 
-  dplyr::mutate(dplyr::across(where(is.character), ~as.factor(.))) |>
-  purrr::map(janitor::tabyl, show_na = T) |> 
-  purrr::map(janitor::adorn_pct_formatting, affix_sign = F)
-
-freqs <- purrr::list_rbind(freqs) |> 
-  dplyr::rename(" " = '.x[[i]]',
-                "valid percent" = "valid_percent") |>
-  dplyr::as_tibble() |> 
-  dplyr::mutate(across(where(is.factor), ~as.character(.)))
-
-tinytable::tt(freqs) |>
-  tinytable::format_tt(j = "valid percent", replace = "-") |> 
-  tinytable::group_tt(i = list(
-    "Experiment Condition" = 1,
-    "Age" = 3,
-    "Gender" = 7,
-    "Race" = 11,
-    "Hispanic, Latino, or Spanish Origin" = 17,
-    "Education" = 21,
-    "Military Relation" = 26,
-    "Party ID" = 31,
-    "Political Ideology" = 35),
-    indent = 2
-    ) |>
-  tinytable::style_tt(fontsize = 0.80, align = "lccc")
+      ideo_3cat, 
+      ideolean, 
+      voted2020, 
+      choice2020),
+    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
+    missing = "ifany",
+    missing_text = "NA") |> 
+  gtsummary::add_overall() |> 
+  gtsummary::modify_header(label = "**Variable**") |> 
+  gtsummary::bold_labels()
+
+tbl.desc2 |>
+  gtsummary::as_tibble() |>
+  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
+                "**Control (N = 637)**" = "**Control**  \nN = 637",
+                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
+  tinytable::tt(theme = "spacing") |>
+  tinytable::format_tt(markdown = T) |>
+  tinytable::format_tt(replace = " ") |>
+  tinytable::style_tt(fontsize = 0.70, align = "lccc")
 
@@
 
-# Appendix C: Test of Random Assignment to Experiment Condition {.appendix}
+```{r}
+#| label: tbl-demog3
+#| tbl-cap: "Sample Demographics"
+#| tbl-pos: H
+
+tbl.desc3 <- data |>  
+  gtsummary::tbl_summary( 
+    by = group,
+    label = list(
+      milserv1 = "Military Service",
+      milserv2 = "Current Active Duty",
+      milservfam = "Military Service within Family?"
+      ),
+    include = c(
+      milserv1,
+      milserv2, 
+      milservfam), 
+    type = list(
+      milserv1 ~ "categorical",
+      milserv2 ~ "categorical",
+      milservfam ~ "categorical"
+      ),
+    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
+    missing = "ifany",
+    missing_text = "NA") |> 
+  gtsummary::add_overall() |> 
+  gtsummary::modify_header(label = "**Variable**") |> 
+  gtsummary::bold_labels()
+
+tbl.desc3 |>
+  gtsummary::as_tibble() |>
+  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
+                "**Control (N = 637)**" = "**Control**  \nN = 637",
+                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
+  tinytable::tt(theme = "spacing", width = 1) |>
+  tinytable::format_tt(markdown = T) |>
+  tinytable::format_tt(replace = " ") |>
+  tinytable::style_tt(fontsize = 0.70, align = "lccc")
+
+```
+
+{{< pagebreak >}}
+
+# Appendix B: Test of Random Assignment to Experiment Condition {.appendix}
 
@@
 #| tbl-cap: "Logistic Regression of Random Assignment to Treatment"
-#| tbl-colwidths: [70]
-#| tbl-pos: H
 
@@
   gof_map = gm,
-  gof_omit = "AIC|BIC|F|RMSE"
+  gof_omit = "AIC|BIC|F|RMSE",
+  width = c(2,1)
   ) |> 
@@
   tinytable::group_tt(i = list(
-    "**Age**" = 1,
-    "**Gender**" = 4,
-    "**Race**" = 6,
-    "**Education**" = 11,
-    "**Party ID**" = 14), 
+    "Age" = 1,
+    "Gender" = 4,
+    "Race" = 6,
+    "Education" = 11,
+    "Party ID" = 14), 
     indent = 2
     ) |> 
-  tinytable::style_tt(i = 20, line = "b", line_color = "black", line_width = .05) |> 
+  tinytable::style_tt(i = 20, line = "b", line_color = "black") |> 
   # adjust fontsize of text within table
-  tinytable::style_tt(fontsize = 0.7, align = "lc") |>
+  tinytable::style_tt(fontsize = 0.65, align = "lc") |>
   # finally, format markdown and blank out any NA fillers
@@
 #| tbl-cap-location: top
-#| tbl-colwidths: [80]
-#| tbl-pos: 'H'
+#| tbl-pos: H
 
@@
   tinytable::style_tt(
-    fontsize = 0.80 # fontsize of text in table in em units (0.75*default)
+    fontsize = 0.65 # fontsize of text in table in em units (0.75*default)
     ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75, align = "l")
+  tinytable::style_tt(i = "notes", fontsize = 0.65, align = "l")
 
@@
 #| tbl-cap: "Unit-level predicted probabilities of selecting response or higher comparing experiment condition"
-#| tbl-colwidths: [80]
-#| tbl-pos: 'H'
+#| tbl-pos: H
 
@@
 #| tbl-cap: "Unit-level predicted probabilities of selecting response or higher conditional to the Treatment experiment condition"
-#| tbl-colwidths: [80]
-#| tbl-pos: 'H'
+#| tbl-pos: H
 
@@
   tinytable::style_tt(
-    fontsize = 0.80, # fontsize of text in table in em units (0.75*default)
+    fontsize = 0.65, # fontsize of text in table in em units (0.75*default)
     align = "llccccc"
     ) |> 
-  tinytable::style_tt(i = "notes", fontsize = 0.75)
+  tinytable::style_tt(i = "notes", fontsize = 0.65)
 
